### 2015-07-22 latex/derivation.tex
Add latex stuff.

\documentclass[11pt, landscape]{article}

\newcommand{\shellcmd}[1]{\texttt{\footnotesize #1}}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}

\newtheorem{theorem}{Theorem}

\title{Brownian Dynein Model}

\newcommand{\mn}{\scalebox{0.7}[1.0]{-}}

\begin{document}

\maketitle

\section{Cartesian from Angular Coordinates}
$$X_{bl}$$
$$X_{ml} = X_{bl}+L_{t}*Cos(\Theta_{bl})$$
$$X_{t}  = X_{ml}+L_{s}*Cos(\Theta_{ml})$$
$$X_{mr} = X_{t} +L_{s}*Cos(\Theta_{mr}-\pi)$$
$$X_{br} = X_{mr}+L_{t}*Cos(\Theta_{br}-\pi)$$

$$Y_{bl}$$
$$Y_{ml} = Y_{bl}+L_{t}*Sin(\Theta_{bl})$$
$$Y_{t}  = Y_{ml}+L_{s}*Sin(\Theta_{ml})$$
$$Y_{mr} = Y_{t} +L_{s}*Sin(\Theta_{mr}-\pi)$$
$$Y_{br} = Y_{mr}+L_{t}*Sin(\Theta_{br}-\pi)$$

\section{Cartesian Velocities}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*Sin(\Theta_{bl})     * \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*Cos(\Theta_{bl})     * \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

\section{Cartesian Velocities (expanded)}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*Cos(\Theta_{ml}) * \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*Cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*Cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

\section{Brownian Equations}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml}$$
$$\dot{X}_{t } = \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt }$$
$$\dot{X}_{mr} = \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr}$$
$$\dot{X}_{br} = \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}$$

$$\dot{Y}_{bl} = 0$$
$$\dot{Y}_{ml} = \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml}$$
$$\dot{Y}_{t}  = \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt }$$
$$\dot{Y}_{mr} = \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr}$$
$$\dot{Y}_{br} = \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}$$

\section{System of Equations}

$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*Sin(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$

$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*Cos(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$

\section{System after Eliminating $\lambda$s via Addition}

$$
\dot{X}_{bl} + L_{t}*Sin(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - 
$$
$$
\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
$$

$$
\hspace*{-4cm} \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
$$

$$\dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$

$$\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$

$$
\hspace*{-7cm} \dot{Y}_{bl} + \mn L_{t}*Cos(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
$$

$$
\hspace*{-4cm} \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
$$

$$
\hspace*{-2cm} \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$\dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$

\section{Solution for $\Theta_{br}$}

$$
\hspace*{-4cm} \Big (\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
$$

$$
\hspace*{-4cm} \Big (L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
$$

$$
\hspace*{-4cm} \Big (L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$
\hspace*{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}*Sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*Cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}*Sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*Cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
\\

\section{Solution for $\Theta_{mr}$}

$$
\dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
$$

$$
\dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$
\Big ( \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
$$
$$
\Big ( \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
$$

$$
\hspace*{-4cm} L_{s}Sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}Cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
$$
$$
\hspace*{-7.5cm} \mn L_{t}Cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}Sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
$$

$$
\hspace*{-4cm} \dot{\Theta}_{mr} =
$$
$$
\hspace*{-7cm} \frac{ \Big (\mn L_{t}Cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}Sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
{L_{s}Sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}Cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
$$

\end{document}

### 2015-07-22 latex/derivation.tex
use \sin and \cos and fullpage

@@
 \usepackage{graphicx}
+
+\usepackage{fullpage}
 
@@
 $$X_{bl}$$
-$$X_{ml} = X_{bl}+L_{t}*Cos(\Theta_{bl})$$
-$$X_{t}  = X_{ml}+L_{s}*Cos(\Theta_{ml})$$
-$$X_{mr} = X_{t} +L_{s}*Cos(\Theta_{mr}-\pi)$$
-$$X_{br} = X_{mr}+L_{t}*Cos(\Theta_{br}-\pi)$$
+$$X_{ml} = X_{bl}+L_{t}*\cos(\Theta_{bl})$$
+$$X_{t}  = X_{ml}+L_{s}*\cos(\Theta_{ml})$$
+$$X_{mr} = X_{t} +L_{s}*\cos(\Theta_{mr}-\pi)$$
+$$X_{br} = X_{mr}+L_{t}*\cos(\Theta_{br}-\pi)$$
 
 $$Y_{bl}$$
-$$Y_{ml} = Y_{bl}+L_{t}*Sin(\Theta_{bl})$$
-$$Y_{t}  = Y_{ml}+L_{s}*Sin(\Theta_{ml})$$
-$$Y_{mr} = Y_{t} +L_{s}*Sin(\Theta_{mr}-\pi)$$
-$$Y_{br} = Y_{mr}+L_{t}*Sin(\Theta_{br}-\pi)$$
+$$Y_{ml} = Y_{bl}+L_{t}*\sin(\Theta_{bl})$$
+$$Y_{t}  = Y_{ml}+L_{s}*\sin(\Theta_{ml})$$
+$$Y_{mr} = Y_{t} +L_{s}*\sin(\Theta_{mr}-\pi)$$
+$$Y_{br} = Y_{mr}+L_{t}*\sin(\Theta_{br}-\pi)$$
 
@@
 $$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*Sin(\Theta_{bl})     * \dot{\Theta}_{bl}$$
-$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
-$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl}$$
+$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
+$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
+$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
 
 $$\dot{Y}_{bl} = 0$$                                                               
-$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*Cos(\Theta_{bl})     * \dot{\Theta}_{bl}$$
-$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml}$$
-$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl}$$
+$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml}$$
+$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
+$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
 
@@
 $$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl}$$
-$$\dot{X}_{t } = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
-$$\dot{X}_{mr} = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{X}_{br} = L_{t}*Sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{X}_{ml} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl}$$
+$$\dot{X}_{t } = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
+$$\dot{X}_{mr} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
+$$\dot{X}_{br} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
 
 $$\dot{Y}_{bl} = 0$$                                                               
-$$\dot{Y}_{ml} = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl}$$
-$$\dot{Y}_{t}  = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*Cos(\Theta_{ml}) * \dot{\Theta}_{ml}$$
-$$\dot{Y}_{mr} = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*Cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{Y}_{br} = \mn L_{t}*Cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*Cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{Y}_{ml} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl}$$
+$$\dot{Y}_{t}  = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml}$$
+$$\dot{Y}_{mr} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
+$$\dot{Y}_{br} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
 
@@
 
-$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*Sin(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
-$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
-$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
-$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$
+$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
+$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
+$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
+$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$
 
-$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*Cos(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
-$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
-$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
-$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$
+$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
+$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
+$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
+$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$
 
@@
 $$
-\dot{X}_{bl} + L_{t}*Sin(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} -
+\dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} -
 $$
 $$
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
+\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
 $$
@@
 $$
-\hspace*{-4cm} \dot{X}_{ml} + L_{s}*Sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
+\hspace*{-4cm} \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
 $$
 
-$$\dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$
+$$\dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$
 
-$$\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$
+$$\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$
 
 $$
-\hspace*{-7cm} \dot{Y}_{bl} + \mn L_{t}*Cos(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
+\hspace*{-7cm} \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
 $$
@@
 $$
-\hspace*{-4cm} \dot{Y}_{ml} + \mn L_{s}*Cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
+\hspace*{-4cm} \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
 $$
@@
 $$
-\hspace*{-2cm} \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
+\hspace*{-2cm} \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
 $$
 
-$$\dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$
+$$\dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$
 
@@
 $$
-\hspace*{-4cm} \Big (\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
+\hspace*{-4cm} \Big (\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
 $$
@@
 $$
-\hspace*{-4cm} \Big (L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
+\hspace*{-4cm} \Big (L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
 $$
@@
 $$
-\hspace*{-4cm} \Big (L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+\hspace*{-4cm} \Big (L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
 $$
@@
 $$
-\hspace*{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}*Sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*Cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+\hspace*{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}*\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
 $$
 
-$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}*Sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*Cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
+$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}*\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
 \\
@@
 $$
-\dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
+\dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
 $$
@@
 $$
-\dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
+\dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
 $$
@@
 $$
-\Big ( \dot{X}_{t } + L_{s}*Sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}*Sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
+\Big ( \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
 $$
 $$
-\Big ( \dot{Y}_{t } + \mn L_{s}*Cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*Cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
+\Big ( \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
 $$
@@
 $$
-\hspace*{-4cm} L_{s}Sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}Cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
+\hspace*{-4cm} L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
 $$
 $$
-\hspace*{-7.5cm} \mn L_{t}Cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}Sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
+\hspace*{-7.5cm} \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
 $$
@@
 $$
-\hspace*{-7cm} \frac{ \Big (\mn L_{t}Cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}Sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
-{L_{s}Sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}Cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
+\hspace*{-7cm} \frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
+{L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
 $$

### 2015-07-22 latex/derivation.tex
slightly clean up last equation.

@@
 
-$$
-\hspace*{-4cm} \dot{\Theta}_{mr} =
-$$
-$$
-\hspace*{-7cm} \frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
+\begin{align}
+\dot{\Theta}_{mr} &= \nonumber \\
+&\frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
 {L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
-$$
+\end{align}
 

### 2015-07-22 latex/derivation.tex
clean up last equation two ways

--- 2015-07-22 latex/derivation.tex
@@
 
-$$
-\hspace*{-4cm} \dot{\Theta}_{mr} =
-$$
-$$
-\hspace*{-7cm} \frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
-{L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
-$$
+\begin{multline}
+\dot{\Theta}_{mr} =
+\Bigg( \left(\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} +
+  \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -
+  R_{ybr} - \frac{1}{\gamma}F_{ybr} \right) (Y_{mr} - Y_{t })
+  \\
+  - \left(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t }
+          - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -
+          \frac{1}{\gamma}F_{xbr} \right) (X_{mr} - X_{t })
+          \Bigg) \\
+/ \left(L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })\right)
+\end{multline}
+or alternatively
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{ \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} +
+  \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -
+  R_{ybr} - \frac{1}{\gamma}F_{ybr}
+}{
+  L_{s}\sin(\Theta_{mr}-\pi)\frac{X_{mr} - X_{t}}{Y_{mr} - Y_{t }} +
+  L_{s}\cos(\Theta_{mr}-\pi)
+}
+  \\
+  - \frac{L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t }
+          - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -
+          \frac{1}{\gamma}F_{xbr}
+          }{
+ L_{s}\sin(\Theta_{mr}-\pi) +
+L_{s}\cos(\Theta_{mr}-\pi)\frac{Y_{mr} - Y_{t }}{X_{mr} - X_{t }}
+}
+\end{multline}
 

### 2015-07-22 latex/derivation.tex
get rid of * for multiplication

@@
 $$X_{bl}$$
-$$X_{ml} = X_{bl}+L_{t}*\cos(\Theta_{bl})$$
-$$X_{t}  = X_{ml}+L_{s}*\cos(\Theta_{ml})$$
-$$X_{mr} = X_{t} +L_{s}*\cos(\Theta_{mr}-\pi)$$
-$$X_{br} = X_{mr}+L_{t}*\cos(\Theta_{br}-\pi)$$
+$$X_{ml} = X_{bl}+L_{t}\cos(\Theta_{bl})$$
+$$X_{t}  = X_{ml}+L_{s}\cos(\Theta_{ml})$$
+$$X_{mr} = X_{t} +L_{s}\cos(\Theta_{mr}-\pi)$$
+$$X_{br} = X_{mr}+L_{t}\cos(\Theta_{br}-\pi)$$
 
 $$Y_{bl}$$
-$$Y_{ml} = Y_{bl}+L_{t}*\sin(\Theta_{bl})$$
-$$Y_{t}  = Y_{ml}+L_{s}*\sin(\Theta_{ml})$$
-$$Y_{mr} = Y_{t} +L_{s}*\sin(\Theta_{mr}-\pi)$$
-$$Y_{br} = Y_{mr}+L_{t}*\sin(\Theta_{br}-\pi)$$
+$$Y_{ml} = Y_{bl}+L_{t}\sin(\Theta_{bl})$$
+$$Y_{t}  = Y_{ml}+L_{s}\sin(\Theta_{ml})$$
+$$Y_{mr} = Y_{t} +L_{s}\sin(\Theta_{mr}-\pi)$$
+$$Y_{br} = Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)$$
 
@@
 $$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl}$$
-$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
-$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl}$$
+$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
+$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
+$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
 
 $$\dot{Y}_{bl} = 0$$                                                               
-$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl}$$
-$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml}$$
-$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl}$$
+$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml}$$
+$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
+$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
 
@@
 $$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl}$$
-$$\dot{X}_{t } = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
-$$\dot{X}_{mr} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{X}_{br} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{X}_{ml} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl}$$
+$$\dot{X}_{t } = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
+$$\dot{X}_{mr} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
+$$\dot{X}_{br} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
 
 $$\dot{Y}_{bl} = 0$$                                                               
-$$\dot{Y}_{ml} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl}$$
-$$\dot{Y}_{t}  = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml}$$
-$$\dot{Y}_{mr} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
-$$\dot{Y}_{br} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$
+$$\dot{Y}_{ml} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl}$$
+$$\dot{Y}_{t}  = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}$$
+$$\dot{Y}_{mr} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
+$$\dot{Y}_{br} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
 
@@
 
-$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
-$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
-$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
-$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$
+$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
+$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
+$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
+$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$
 
-$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
-$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
-$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
-$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$
+$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
+$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
+$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
+$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$
 
@@
 $$
-\dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} -
+\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} -
 $$
 $$
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
+\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
 $$
@@
 $$
-\hspace*{-4cm} \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
+\hspace*{-4cm} \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
 $$
 
-$$\dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$
+$$\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$
 
-$$\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$
+$$\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$
 
 $$
-\hspace*{-7cm} \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
+\hspace{-7cm} \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
 $$
@@
 $$
-\hspace*{-4cm} \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
+\hspace{-4cm} \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
 $$
@@
 $$
-\hspace*{-2cm} \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
+\hspace{-2cm} \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
 $$
 
-$$\dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$
+$$\dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$
 
@@
 $$
-\hspace*{-4cm} \Big (\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
+\hspace{-4cm} \Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
 $$
@@
 $$
-\hspace*{-4cm} \Big (L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
+\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
 $$
@@
 $$
-\hspace*{-4cm} \Big (L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
 $$
@@
 $$
-\hspace*{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}*\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+\hspace{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
 $$
 
-$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}*\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
+$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
 \\
@@
 $$
-\dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
+\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
 $$
@@
 $$
-\dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
+\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
 $$
@@
 $$
-\Big ( \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
+\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
 $$
 $$
-\Big ( \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
+\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
 $$
@@
 $$
-\hspace*{-4cm} L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
+\hspace{-4cm} L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
 $$
 $$
-\hspace*{-7.5cm} \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
+\hspace{-7.5cm} \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
 $$

### 2015-07-22 latex/derivation.tex
convert equations to align

@@
 \section{Cartesian from Angular Coordinates}
-$$X_{bl}$$
-$$X_{ml} = X_{bl}+L_{t}\cos(\Theta_{bl})$$
-$$X_{t}  = X_{ml}+L_{s}\cos(\Theta_{ml})$$
-$$X_{mr} = X_{t} +L_{s}\cos(\Theta_{mr}-\pi)$$
-$$X_{br} = X_{mr}+L_{t}\cos(\Theta_{br}-\pi)$$
+\begin{align}
+  X_{bl} &= 0 \\
+  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
+  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
+  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
+  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi) \label{eq:br-definition}
+\end{align}
+
+As we found in Eq.~\ref{eq:br-definition}... just kidding!
 

### 2015-07-23 latex/derivation.tex
Add rest of angle derivative solutions. Next step: simplify and make numerically computable.

@@
   X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
-  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi) \label{eq:br-definition}
+  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
 \end{align}
 
-As we found in Eq.~\ref{eq:br-definition}... just kidding!
-
-$$Y_{bl}$$
-$$Y_{ml} = Y_{bl}+L_{t}\sin(\Theta_{bl})$$
-$$Y_{t}  = Y_{ml}+L_{s}\sin(\Theta_{ml})$$
-$$Y_{mr} = Y_{t} +L_{s}\sin(\Theta_{mr}-\pi)$$
-$$Y_{br} = Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)$$
+\begin{align}
+  Y_{bl} &= 0 \\
+  Y_{ml} &= Y_{bl}+L_{t}\sin(\Theta_{bl}) \\
+  Y_{t}  &= Y_{ml}+L_{s}\sin(\Theta_{ml}) \\
+  Y_{mr} &= Y_{t} +L_{s}\sin(\Theta_{mr}-\pi) \\
+  Y_{br} &= Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)
+\end{align}
 
 \section{Cartesian Velocities}
-$$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl}$$
-$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
-$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
-$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
+\begin{align}
+  \dot{X}_{bl} &= 0 \\
+  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+\end{align}
 
-$$\dot{Y}_{bl} = 0$$                                                               
-$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl}$$
-$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml}$$
-$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
-$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
+\begin{align}                                                                          
+  \dot{Y}_{bl} &= 0 \\                                                        
+  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+\end{align}
 
 \section{Cartesian Velocities (expanded)}
-$$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl}$$
-$$\dot{X}_{t } = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
-$$\dot{X}_{mr} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
-$$\dot{X}_{br} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
+\begin{align}
+  \dot{X}_{bl} &= 0 \\
+  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+\end{align}
 
-$$\dot{Y}_{bl} = 0$$                                                               
-$$\dot{Y}_{ml} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl}$$
-$$\dot{Y}_{t}  = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}$$
-$$\dot{Y}_{mr} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
-$$\dot{Y}_{br} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$
+\begin{align}                                                                               
+  \dot{Y}_{bl} &= 0 \\                                                               
+  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+\end{align}
 
   \section{Brownian Equations}
-$$\dot{X}_{bl} = 0$$
-$$\dot{X}_{ml} = \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml}$$
-$$\dot{X}_{t } = \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt }$$
-$$\dot{X}_{mr} = \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr}$$
-$$\dot{X}_{br} = \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}$$
+\begin{align}  
+  \dot{X}_{bl} &= 0 \\
+  \dot{X}_{ml} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml} \\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt } \\
+  \dot{X}_{mr} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr} \\
+  \dot{X}_{br} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}
+\end{align}
 
-$$\dot{Y}_{bl} = 0$$
-$$\dot{Y}_{ml} = \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml}$$
-$$\dot{Y}_{t}  = \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt }$$
-$$\dot{Y}_{mr} = \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr}$$
-$$\dot{Y}_{br} = \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}$$
+\begin{align}  
+  \dot{Y}_{bl} &= 0 \\
+  \dot{Y}_{ml} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml} \\
+  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt } \\
+  \dot{Y}_{mr} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr} \\
+  \dot{Y}_{br} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}
+\end{align}
 
@@
 
-$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
-$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
-$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
-$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$
+\begin{align}  
+  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
+  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
+  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
+\end{align}
 
-$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
-$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
-$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
-$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$
+\begin{align}  
+  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
+  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
+\end{align}
 
-\section{System after Eliminating $\lambda$s via Addition}
+\section{System after Addition to simplify RHS}
 
-$$
-\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} -
-$$
-$$
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
-$$
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
+\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{multline}
 
-$$
-\hspace*{-4cm} \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
-$$
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
+\dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{multline}
 
-$$\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
+\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{equation}
 
-$$\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
+\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{equation}
 
-$$
-\hspace{-7cm} \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
-$$
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
+\dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{multline}
 
-$$
-\hspace{-4cm} \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
-$$
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) =
+\dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{multline}
 
-$$
-\hspace{-2cm} \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
-$$
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) =
+\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+- R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{equation}
 
-$$\dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{equation}
 
-\section{Solution for $\Theta_{br}$}
+\section{Solution for $\dot{\Theta_{br}}$}
 
-$$
-\hspace{-4cm} \Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
-$$
+\begin{multline}
+\Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs}
+= \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
+\end{multline}
 
-$$
-\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
-$$
+\begin{multline}
+\Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+= \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
+\end{multline}
 
-$$
-\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
-$$
+\begin{multline}
+\Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr})
+= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+\end{multline}
 
-$$
-\hspace{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
-$$
+\begin{multline}
+\dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg )
+= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+\end{multline}
 
-$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
-\\
+\begin{equation}
+\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} 
+- R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}
+\end{equation}
 
-\section{Solution for $\Theta_{mr}$}
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\frac{(Y_{br} - Y_{mr})}{(X_{br} - X_{mr})} + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\frac{(X_{br} - X_{mr})}{(Y_{br} - Y_{mr})}}
+\end{equation}
 
-$$
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\frac{L_{t}\sin(\Theta_{br}-\pi)}{L_{t}\cos(\Theta_{br}-\pi)} + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\frac{L_{t}\cos(\Theta_{br}-\pi)}{L_{t}\sin(\Theta_{br}-\pi)}}
+\end{equation}
+
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\tan(\Theta_{br}-\pi) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\tan^{-1}(\Theta_{br}-\pi)}
+\end{equation}
+
+\section{Solution for $\dot{\Theta_{mr}}$}
+
+\begin{equation}
 \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
 \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
-$$
+\end{equation}
 
-$$
-\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
-$$
+\begin{equation}
+\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} +
+\dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
+\end{equation}
 
-$$
-\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
-$$
-$$
-\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
-$$
+\begin{multline}
+\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
++ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) = \\
+\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
++ \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
+\end{multline}
 
-$$
-\hspace{-4cm} L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
-$$
-$$
-\hspace{-7.5cm} \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
-$$
+\begin{multline}
+L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
+\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) \\
++ \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) 
+- \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
+\end{multline}
 
@@
 \dot{\Theta}_{mr} =
-\Bigg( \left(\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} +
-  \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -
-  R_{ybr} - \frac{1}{\gamma}F_{ybr} \right) (Y_{mr} - Y_{t })
-  \\
-  - \left(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t }
-          - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -
-          \frac{1}{\gamma}F_{xbr} \right) (X_{mr} - X_{t })
-          \Bigg) \\
-/ \left(L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })\right)
+\frac{ \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}}
+{L_{s}\sin(\Theta_{mr}-\pi)\frac{X_{mr} - X_{t}}{Y_{mr} - Y_{t }} + L_{s}\cos(\Theta_{mr}-\pi)} \\
+  - \frac{L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr}}
+  {L_{s}\sin(\Theta_{mr}-\pi) + L_{s}\cos(\Theta_{mr}-\pi)\frac{Y_{mr} - Y_{t }}{X_{mr} - X_{t }}}
 \end{multline}
-or alternatively
+
+\section{Solution for $\dot{\Theta_{ml}}$}
+
 \begin{multline}
-\dot{\Theta}_{mr} =
-\frac{ \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} +
-  \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -
-  R_{ybr} - \frac{1}{\gamma}F_{ybr}
-}{
-  L_{s}\sin(\Theta_{mr}-\pi)\frac{X_{mr} - X_{t}}{Y_{mr} - Y_{t }} +
-  L_{s}\cos(\Theta_{mr}-\pi)
-}
-  \\
-  - \frac{L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t }
-          - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -
-          \frac{1}{\gamma}F_{xbr}
-          }{
- L_{s}\sin(\Theta_{mr}-\pi) +
-L_{s}\cos(\Theta_{mr}-\pi)\frac{Y_{mr} - Y_{t }}{X_{mr} - X_{t }}
-}
+\mn\frac{1}{\gamma}\lambda_{lt} =
+\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\end{multline}
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{lt} =
+\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+\end{multline}
+
+\begin{multline}
+\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+\end{multline}
+
+\begin{multline}
+(Y_{t } - Y_{ml}) \Big( \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+\end{multline}
+
+\begin{multline}
+(Y_{t } - Y_{ml})(L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) + (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+(X_{t } - X_{ml})(\mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) + (X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+\end{multline}
+
+\begin{multline}
+(Y_{t } - Y_{ml})(L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) - (X_{t } - X_{ml})(\mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) = \\
+(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
+- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{ml} \Big((Y_{t } - Y_{ml})L_{s}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{s}\cos(\Theta_{ml}) \Big) = \\
+(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
+- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{ml} = \\
+\frac{(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
+{\Big((Y_{t } - Y_{ml})L_{s}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{s}\cos(\Theta_{ml}) \Big)} \\
+- \frac{(Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{\Big((Y_{t } - Y_{ml})L_{s}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{s}\cos(\Theta_{ml}) \Big)}
+\end{multline}
+
+\section{Solution for $\dot{\Theta_{bl}}$}
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{ls} =
+\frac{1}{(X_{ml} - X_{bl})}\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{multline}
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{ls} =
+\frac{1}{(Y_{ml} - Y_{bl})}\dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{multline}
+
+\begin{multline}
+(Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
+\end{multline}
+
+\begin{multline}
+(Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+\mn (X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
+\end{multline}
+
+\begin{multline}
+(X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \dot{\Theta}_{bl} = \\
+(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big) \\
+- (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
++ \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{bl} = \\
+\hspace*{-1.5cm}\frac{\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)}
+{\frac{1}{(X_{ml} - X_{bl})}\Big( (X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \Big)} \\
+- \hspace*{-1.5cm}\frac{\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
++ \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{\frac{1}{(Y_{ml} - Y_{bl})}\Big( (X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \Big)}
 \end{multline}

### 2015-07-23 latex/derivation.tex
Add simplified angular velocity equations.

@@
 
-\section{Solution for $\dot{\Theta_{br}}$}
+\section{Solution for $\dot{\Theta}_{br}$}
 
@@
 \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\tan(\Theta_{br}-\pi) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
+{\Big (\frac{{L_{t}}^2\sin^2(\Theta_{br}-\pi)}{L_{t}\cos(\Theta_{br}-\pi)}\Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
 + \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\tan^{-1}(\Theta_{br}-\pi)}
+{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (\frac{{L_{t}}^2\cos^2(\Theta_{br}-\pi)}{L_{t}\sin(\Theta_{br}-\pi)} \Big) }
 \end{equation}
 
-\section{Solution for $\dot{\Theta_{mr}}$}
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
+{\Big( {L_{t}}^2\sin^2(\Theta_{br}-\pi)\Big) + \Big ({L_{t}}^2\cos^2(\Theta_{br}-\pi) \Big)}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
+{\Big ({L_{t}}^2\sin^2(\Theta_{br}-\pi) \Big) + \Big( {L_{t}}^2\cos^2(\Theta_{br}-\pi) \Big) }
+\end{equation}
+
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
+{{L_{t}}^2}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
+{{L_{t}}^2}
+\end{equation}
+
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
++ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
+\end{equation}
+
+\section{Solution for $\dot{\Theta}_{mr}$}
 
@@
 \Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
-+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) = \\
++ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t }) = \\
 \Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
++ \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t })
 \end{multline}
@@
 \begin{multline}
-L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
-\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) \\
-+ \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) 
-- \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
+L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) =
+\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) \\
++ \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t }) 
+- \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t })
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{ \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}}
-{L_{s}\sin(\Theta_{mr}-\pi)\frac{X_{mr} - X_{t}}{Y_{mr} - Y_{t }} + L_{s}\cos(\Theta_{mr}-\pi)} \\
-  - \frac{L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr}}
-  {L_{s}\sin(\Theta_{mr}-\pi) + L_{s}\cos(\Theta_{mr}-\pi)\frac{Y_{mr} - Y_{t }}{X_{mr} - X_{t }}}
+\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (X_{mr} - X_{t })}
+{L_{s}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t}) + L_{s}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })} \\
+  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(Y_{mr} - Y_{t })}
+  {L_{s}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{s}\cos(\Theta_{mr}-\pi))}
+{L_{s}\sin(\Theta_{mr}-\pi)(L_{s}\sin(\Theta_{mr}-\pi)) + L_{s}\cos(\Theta_{mr}-\pi)(L_{s}\cos(\Theta_{mr}-\pi))} \\
+  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))}
+  {L_{s}\sin(\Theta_{mr}-\pi)(L_{s}\sin(\Theta_{mr}-\pi)) + L_{s}\cos(\Theta_{mr}-\pi)(L_{s}\cos(\Theta_{mr}-\pi))}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{s}\cos(\Theta_{mr}-\pi))}
+{{L_{s}}^2\sin^2(\Theta_{mr}-\pi) + {L_{s}}^2\cos^2(\Theta_{mr}-\pi)} \\
+  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))}
+  {{L_{s}}^2\sin^2(\Theta_{mr}-\pi) + {L_{s}}^2\cos^2(\Theta_{mr}-\pi)}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big) (L_{s}\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))
 \end{multline}
@@
 
+\begin{multline}
+\dot{\Theta}_{ml} = \\
+\frac{L_{s}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
+{\Big((L_{s}\sin(\Theta_{ml}))L_{s}\sin(\Theta_{ml}) + (L_{s}\cos(\Theta_{ml}))L_{s}\cos(\Theta_{ml}) \Big)} \\
+- \frac{(L_{s}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{\Big((L_{s}\sin(\Theta_{ml}))L_{s}\sin(\Theta_{ml}) + (L_{s}\cos(\Theta_{ml}))L_{s}\cos(\Theta_{ml}) \Big)}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{ml} = \\
+\frac{L_{s}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
+{{L_s}^2} \\
+- \frac{(L_{s}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{{L_s}^2}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{ml} = \\
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big( \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+ + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
++ \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+
 \section{Solution for $\dot{\Theta_{bl}}$}
@@
 
+\begin{multline}
+\dot{\Theta}_{bl} = \\
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big( \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
++ \dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big( L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
++ \dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+
 \end{document}

### 2015-07-24 latex/derivation.tex
Simplify angular solutions more. Add all solutions at bottom of document. Next step: Find way to actually solve, if possible.

@@
 \dot{\Theta}_{mr} =
-\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big) (L_{s}\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))
+\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
 \end{multline}
 
-\section{Solution for $\dot{\Theta_{ml}}$}
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+\end{multline}
+
+\section{Solution for $\dot{\Theta}_{ml}$}
 
@@
 
-\section{Solution for $\dot{\Theta_{bl}}$}
+\begin{multline}
+\dot{\Theta}_{ml} =
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
+- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
+- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+
+\section{Solution for $\dot{\Theta}_{bl}$}
 
@@
 
+\begin{multline}
+\dot{\Theta}_{bl} = \\
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
+- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
+ - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+
+\clearpage
+
+\section{All Angular Velocity Solutions}
+
+\begin{equation}
+\dot{\Theta}_{br} =
+\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
++ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
+\end{equation}
+
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{ml} =
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
+- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
+- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{bl} = \\
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
+- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
+ - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+
 \end{document}

### 2015-07-24 latex/derivation.tex
Add another attempt at solving angular velocities to derivation.tex.

@@
 \section{Cartesian from Angular Coordinates}
+This section lays out the definitions of the coordinates of the Dynein model. \\
 \begin{align}
@@
 \section{Cartesian Velocities}
+This section shows the velocity definitions. \\
 \begin{align}
@@
 \section{Cartesian Velocities (expanded)}
+This section expands the above definitions. \\
 \begin{align}
@@
 \section{Brownian Equations}
+This section shows the velocity definitions using the Brownian dynamics equation. \\
 \begin{align}  
@@
 
+\section{Expanded Brownian Equations}
+
+\begin{align}
+  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
+  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
+  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
+  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
+\end{align}
+
+\begin{align}
+  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
+  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
+  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
+  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
+\end{align}
+
+\section{System after Subtracting out Angular Velocity Terms}
+This is the system after subtracting equations from each other to eliminate some angular velocity terms.\\
+
+\begin{align}
+  L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
+  L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
+  L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
+  L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr}
+\end{align}
+
+\begin{align}
+  \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
+  \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
+  \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
+  \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr}
+\end{align}
+
 \section{System of Equations}
+This section creates a system of equations by equating the Cartesian and Brownian velocity definitions from above. \\
 
@@
 
-\section{System after Addition to simplify RHS}
+\section{System after Addition}
+By adding coordinates for br to mr, mr to t, and t to ml, we simplify one side of our equations. \\
 
@@
 \section{Solution for $\dot{\Theta}_{br}$}
+The following sections come up with solutions for $\dot{\Theta}_{br}$, $\dot{\Theta}_{mr}$, $\dot{\Theta}_{ml}$ and $\dot{\Theta}_{bl}$ using the equations we found in the previous section. \\
 
@@
 \begin{multline}
-\dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
+\dot{\Theta}_{bl} =
+\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
 - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
+- \frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
  - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)

### 2015-07-25 latex/derivation.tex
Expand solutions on final page to include only angular velocity terms. The solutions now look really bad and don't seem to be solvable. New approach time?

@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 \end{align}
@@
   \dot{Y}_{bl} &= 0 \\                                                               
-  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 \end{align}
@@
 \section{System after Addition}
-By adding coordinates for br to mr, mr to t, and t to ml, we simplify one side of our equations. \\
+By adding equations from our system together we can isolate the $\lambda$ values. \\
 
@@
 \end{equation}
+\\
+Now expand the cartesian velocity definition: \\
 
-\begin{equation}
+\begin{multline}
 \dot{\Theta}_{br} =
-\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
-+ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
-\end{equation}
+\frac{1}{L_{t}}\Big(\mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
++ \frac{1}{L_{t}}\Big(L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
+\end{multline}
 
@@
 \frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+  - \frac{1}{L_{s}}\Big(\dot{X}_{br} + \dot{X}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+\end{multline}
+\\
+Now expand the cartesian velocity definition: \\
+
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{1}{L_{s}} \Big(\mn 2L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{s}}\Big(2L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+   - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
 \end{multline}
@@
 \dot{\Theta}_{ml} =
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{Y}_{br} + \dot{Y}_{ml}
 - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
 - \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
+- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
+\\
+Now expand the cartesian velocity definition: \\
+
+\begin{multline}
+\dot{\Theta}_{ml} =
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
@@
 \end{multline}
+\\
+Now expand the cartesian velocity definition: \\
+
+\begin{multline}
+\dot{\Theta}_{bl} = \\
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\end{multline}
 
@@
 
-\begin{equation}
+\begin{multline}
 \dot{\Theta}_{br} =
-\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
-+ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
-\end{equation}
+\frac{1}{L_{t}}\Big(\mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
++ \frac{1}{L_{t}}\Big(L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
+\end{multline}
 
@@
 \dot{\Theta}_{mr} =
-\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+\frac{1}{L_{s}} \Big(\mn 2L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{s}}\Big(2L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+   - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
 \end{multline}
@@
 \dot{\Theta}_{ml} =
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
@@
 \begin{multline}
-\dot{\Theta}_{bl} =
-\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
+\dot{\Theta}_{bl} = \\
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)

### 2015-07-28 latex/derivation.tex
Prepare equations for matrix form.

@@
 
+\section{Preparing Equations for Matrix Form}
+
+\begin{multline}
+\dot{\Theta}_{br} =
+\big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
+\frac{L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{t}}\dot{\Theta}_{ml}  + \\
+\frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}}\dot{\Theta}_{mr} - 
+\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} - 
+\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{mr} =
+\frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{bl} + 
+\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
+\big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi)\big)\dot{\Theta}_{mr} + 
+\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{br} + \\
+\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
+\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{ml} =
+\frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
+\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
+\big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
+\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} + \\
+\frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
+\frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
+\end{multline}
+
+\begin{multline}
+\dot{\Theta}_{bl} =
+\big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) \big)\dot{\Theta}_{bl} +
+\frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
+\frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
+\big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} + \\
+\frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}{\gamma L_t} + \\
+\frac{\sin(\Theta_{bl})R_{xml} + \mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t}
+\end{multline}
+
+\section{All velocity terms on LHS:}
+
+\begin{multline}
+\big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
+\frac{L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{t}}\dot{\Theta}_{ml}  + \\
+\frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}}\dot{\Theta}_{mr} +
+\mn\dot{\Theta}_{br} =
+\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} + \\
+\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}}
+\end{multline}
+
+\begin{multline}
+\frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{bl} + 
+\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
+\big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big)\dot{\Theta}_{mr} + 
+\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{br} = \\
+\mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
+\mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
+\end{multline}
+
+\begin{multline}
+\frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
+\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big)\dot{\Theta}_{ml} + \\
+\big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
+\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} = \\
+\mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
+\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
+\end{multline}
+
+\begin{multline}
+\big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big)\dot{\Theta}_{bl} +
+\frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
+\frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
+\big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} = \\
+\mn \frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}{\gamma L_t} + \\
+\mn \frac{\sin(\Theta_{bl})R_{xml} + \mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t}
+\end{multline}
+
 \end{document}

### 2015-07-28 latex/derivation.tex
sketch for how to finish solution
Add beginnings of matrix diagonalization.

@@
 
+\section{Make a matrix!}
+
+\begin{align}
+  A_1 &= \mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn +
+  3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1 \\
+  A_2 &= \frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
+  A_3 &= \frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}} \\
+  A_4 &= -1 \\
+  B_1 &= \frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}} \\
+  B_2 &= \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big) \\
+  B_3 &= \big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big) \\
+  B_4 &= \frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}} \\
+  C_1 &= \frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s} \\
+  C_2 &= \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big) \\
+  C_3 &= \big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big) \\
+  C_4 &= \frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s} \\
+  D_1 &= \big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big) \\
+  D_2 &= \frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
+  D_3 &= \frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} \\
+  D_4 &= \big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \\
+\end{align}
+
+\begin{multline}
+  X_1 = \frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} + \frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}} \\
+\end{multline}
+
+\begin{multline}
+  X_2 = \mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
+  \mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
+\end{multline}
+
+\begin{multline}
+  X_3 = \mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
+	\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
+\end{multline}
+
+\begin{multline}
+  X_4 = \mn \frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}
+  {\gamma L_t} \\+ \mn \frac{\sin(\Theta_{bl})R_{xml} +\mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t} \\
+\end{multline}
+
+\begin{align}
+  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
+  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
+  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\end{align}
+
+\begin{align}
+  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
+  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
+  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
+  \frac{A_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{A_4D_2}{D_4}\dot{\Theta}_{ml} + \frac{A_4D_3}{D_4}\dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= \frac{A_4}{D_4}X_4 \\
+\end{align}
+
+\begin{align}
+  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
+  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
+  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
+  \frac{B_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{D_4}\dot{\Theta}_{ml} + \frac{B_4D_3}{D_4}\dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= \frac{B_4}{D_4}X_4 \\
+\end{align}
+
+\begin{align}
+  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
+  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
+  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
+  \frac{C_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{C_4}\dot{\Theta}_{ml} + \frac{C_4D_3}{D_4}\dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= \frac{C_4}{D_4}X_4 \\
+\end{align}
+
+\begin{align}
+  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
+  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
+  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
+  \frac{C_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{C_4}\dot{\Theta}_{ml} + \frac{C_4D_3}{D_4}\dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= \frac{C_4}{D_4}X_4 \\
+\end{align}
+
+\begin{align}
+  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
+  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
+  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
+  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
+  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\end{align}
+
+\begin{align}
+  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
+  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
+  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
+  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
+  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\end{align}
+
 \end{document}

### 2015-07-29 latex/derivation.tex

@@
 
+This system is solved via Mathematica...\\
+
+\end{document}
+
 \begin{align}
@@
 \begin{align}
-  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
+  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
+		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
   \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
-  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
-  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
-  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
+  \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
+		\frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
+		\left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
   D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
@@
 
-\end{document}
+\begin{align}
+  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
+		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
+ \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
+		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
+  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\end{align}
+
+\begin{multline}
+  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 =
+		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
+\end{multline}
+\begin{multline}
+ \hspace*{-2cm}\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 = \\
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right) \\
+\end{multline}
+\begin{align}
+  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\end{align}
+
+\begin{multline}
+  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
+  \frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)\dot{\Theta}_{bl} + \\
+		0 + 0 + 0 =
+		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\\
+\end{multline}
+\begin{align}
+  \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
+		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
+  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4
+\end{align}
+
+\begin{multline}
+  \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} = \\
+		\frac{\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)}
+		{\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)} * \\
+		\left(X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\right)
+\end{multline}
+\begin{align}
+  \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
+		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
+		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
+  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4
+\end{align}
+
+\begin{multline}
+  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
+  \frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)\dot{\Theta}_{bl} = \\
+		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\\
+\end{multline}
+\begin{multline}
+		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} =
+		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -\\
+		\frac{\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)}
+		{\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)} * \\
+		\left(X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
+		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
+		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\right)
+\end{multline}
+\begin{align}
+  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4
+\end{align}

### 2015-07-29 latex/derivation.tex
Add Mathematica symbolic matrix equation solution.
Add Mathematica formatted (ish) equations.
Add symbols to numerically solve for angular velocities to derivation.tex.
Hit problem with ftest: cannot evaluate test expressions with manually-set angular velocities. Modifying dynein_struct.cpp to calculate angular velocities.

--- 2015-07-28 latex/derivation.tex
@@
 \usepackage{graphicx}
-
+\usepackage{mathtools}
 \usepackage{fullpage}
-
-\newtheorem{theorem}{Theorem}
 
@@
 
-\section{Preparing Equations for Matrix Form}
+\section{Making solvable system of equations}
 
@@
 
-\section{Make a matrix!}
+\section{Breaking terms down into symbols}
 
 \begin{align}
-  A_1 &= \mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn +
-  3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1 \\
+  A_1 &= \mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1 \\
   A_2 &= \frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
@@
 
-\begin{align}
-  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
-  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
-  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
-  \frac{A_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{A_4D_2}{D_4}\dot{\Theta}_{ml} + \frac{A_4D_3}{D_4}\dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= \frac{A_4}{D_4}X_4 \\
-\end{align}
+\section{System solution!}
+This system is solved via Mathematica...\\
+\begin{multline}
+N_{bl} =
+(-B_2 C_4 D_3 X_1 + B_2 C_3 D_4 X_1 + A_4 C_3 D_2 X_2 - A_3 C_4 D_2 X_2 - A_4 C_2 D_3 X_2 + A_2 C_4 D_3 X_2 +\\
+ A_3 C_2 D_4 X_2 - A_2 C_3 D_4 X_2 + A_4 B_2 D_3 X_3 - A_3 B_2 D_4 X_3 - A_4 B_2 C_3 X_4 + A_3 B_2 C_4 X_4 +\\
+B_4 (-C_3 D_2 X_1 + C_2 D_3 X_1 + A_3 D_2 X_3 - A_2 D_3 X_3 - A_3 C_2 X_4 + A_2 C_3 X_4) + B_3 (C_4 D_2 X_1 - \\
+C_2 D_4 X_1 - A_4 D_2 X_3 + A_2 D_4 X_3 + A_4 C_2 X_4 - A_2 C_4 X_4)) \\
+\end{multline}
+
+\begin{multline}
+N_{ml} =
+(B_1 C_4 D_3 X_1 - B_1 C_3 D_4 X_1 - A_4 C_3 D1 X_2 + A_3 C_4 D1 X_2 + A_4 C_1 D_3 X_2 - A_1 C_4 D_3 X_2 - \\
+A_3 C_1 D_4 X_2 + A_1 C_3 D_4 X_2 - A_4 B_1 D_3 X_3 + A_3 B_1 D_4 X_3 + A_4 B_1 C_3 X_4 - A_3 B_1 C_4 X_4 +\\
+B_4 (C_3 D1 X_1 - C_1 D_3 X_1 - A_3 D1 X_3 + A_1 D_3 X_3 + A_3 C_1 X_4 - A_1 C_3 X_4) + B_3 (-C_4 D1 X_1 + \\
+C_1 D_4 X_1 + A_4 D1 X_3 - A_1 D_4 X_3 - A_4 C_1 X_4 + A_1 C_4 X_4)) \\
+\end{multline}
+
+\begin{multline}
+N_{mr} =
+(-B_1 C_4 D_2 X_1 + B_1 C_2 D_4 X_1 + A_4 C_2 D1 X_2 - A_2 C_4 D1 X_2 - A_4 C_1 D_2 X_2 + A_1 C_4 D_2 X_2 + \\
+A_2 C_1 D_4 X_2 - A_1 C_2 D_4 X_2 + A_4 B_1 D_2 X_3 - A_2 B_1 D_4 X_3 - A_4 B_1 C_2 X_4 + A_2 B_1 C_4 X_4 +\\
+B_4 (-C_2 D1 X_1 + C_1 D_2 X_1 + A_2 D1 X_3 - A_1 D_2 X_3 - A_2 C_1 X_4 + A_1 C_2 X_4) + \\
+B_2 (C_4 D1 X_1 - C_1 D_4 X_1 - A_4 D1 X_3 + A_1 D_4 X_3 + A_4 C_1 X_4 - A_1 C_4 X_4)) \\
+\end{multline}
+
+\begin{multline}
+N_{br} =
+(B_1 C_3 D_2 X_1 - B_1 C_2 D_3 X_1 - A_3 C_2 D1 X_2 + A_2 C_3 D1 X_2 + A_3 C_1 D_2 X_2 - A_1 C_3 D_2 X_2 - \\
+A_2 C_1 D_3 X_2 + A_1 C_2 D_3 X_2 - A_3 B_1 D_2 X_3 + A_2 B_1 D_3 X_3 + A_3 B_1 C_2 X_4 - A_2 B_1 C_3 X_4 +\\
+B_3 (C_2 D1 X_1 - C_1 D_2 X_1 - A_2 D1 X_3 + A_1 D_2 X_3 + A_2 C_1 X_4 - A_1 C_2 X_4) + \\
+B_2 (-C_3 D1 X_1 + C_1 D_3 X_1 + A_3 D1 X_3 - A_1 D_3 X_3 - A_3 C_1 X_4 + A_1 C_3 X_4)) \\
+\end{multline}
+
+\begin{multline}
+D = (A_2 B_4 C_3 D1 - A_2 B_3 C_4 D1 - A_1 B_4 C_3 D_2 + A_1 B_3 C_4 D_2 - A_2 B_4 C_1 D_3 + A_1 B_4 C_2 D_3 + \\
+A_2 B_1 C_4 D_3 - A_1 B_2 C_4 D_3 + A_4 (B_3 C_2 D1 - B_2 C_3 D1 - B_3 C_1 D_2 + B_1 C_3 D_2 + B_2 C_1 D_3 - B_1 C_2 D_3) + \\
+A_2 B_3 C_1 D_4 - A_1 B_3 C_2 D_4 - A_2 B_1 C_3 D_4 + A_1 B_2 C_3 D_4 + A_3 (-B_4 C_2 D1 + B_2 C_4 D1 + B_4 C_1 D_2 - B_1 C_4 D_2 - B_2 C_1 D_4 + B_1 C_2 D_4))
+\end{multline}
 
 \begin{align}
-  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
-  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
-  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
-  \frac{B_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{D_4}\dot{\Theta}_{ml} + \frac{B_4D_3}{D_4}\dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= \frac{B_4}{D_4}X_4 \\
-\end{align}
-
-\begin{align}
-  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
-  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
-  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
-  \frac{C_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{C_4}\dot{\Theta}_{ml} + \frac{C_4D_3}{D_4}\dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= \frac{C_4}{D_4}X_4 \\
-\end{align}
-
-\begin{align}
-  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
-  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
-  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
-  \frac{C_4D_1}{D_4}\dot{\Theta}_{bl} + \frac{B_4D_2}{C_4}\dot{\Theta}_{ml} + \frac{C_4D_3}{D_4}\dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= \frac{C_4}{D_4}X_4 \\
-\end{align}
-
-\begin{align}
-  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
-  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
-  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
-  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
-  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
-  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
-\end{align}
-
-\begin{align}
-  \left(A_1 - \frac{A_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(A_2 - \frac{A_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{A_4}{D_4}X_4\\
-  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
-  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
-  \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
-  \left(A_3 - \frac{A_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
-  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\dot{\Theta}_{bl} &= \frac{N_{bl}}{D} \\
+\dot{\Theta}_{ml} &= \frac{N_{ml}}{D} \\
+\dot{\Theta}_{mr} &= \frac{N_{mr}}{D} \\
+\dot{\Theta}_{br} &= \frac{N_{br}}{D}
 \end{align}

### 2015-07-30 latex/derivation.tex
add a simplified expression for X_3 as an example

@@
 \end{multline}
+The following is David's simplification of $X_3$:
+\begin{align}
+  X_3 &= -\frac{1}{L_s}\left\{ \sin(\Theta_{ml})\left(\frac{F_{xt}+F_{xmr}+F_{xbr}}{\gamma} + R_{xt }+R_{xmr}+R_{xbr}\right) -
+    \cos(\Theta_{ml})\left(\frac{F_{yt }+F_{ymr}+F_{ybr}}{\gamma} +
+    R_{yt}+R_{ymr}+R_{ybr}\right) \right\}
+    \\
+    &?= \frac{\hat{a}_{ml}\cdot \vec{F}_{tot_{ml}}}{\gamma L_s}
+\end{align}
+where $\hat a$ is a unit vector in a the direction related to the $ml$
+segment, and $\vec{F}_{tot_{ml}}$ is a total force of some sort,
+including the random fluctuations.  I don't think we want to write the
+formula in this final way, but it may help in thinking about the
+equations.  I certainly think that the form with just one $\sin$ and
+one $\cos$ is an improvement, and reduces the likelihood of
+introducing sign errors (or sine errors, for that matter).
 

### 2015-08-06 latex/derivation.tex

@@
 \usepackage{fullpage}
+\usepackage{verbatim}
 
@@
   X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
-  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
-  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
+  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) = X_{t} + \mn L_{s}\cos(\Theta_{mr}) \\
+  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi) = X_{mr}+ \mn L_{t}\cos(\Theta_{br})
 \end{align}
@@
   Y_{t}  &= Y_{ml}+L_{s}\sin(\Theta_{ml}) \\
-  Y_{mr} &= Y_{t} +L_{s}\sin(\Theta_{mr}-\pi) \\
-  Y_{br} &= Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)
+  Y_{mr} &= Y_{t} +L_{s}\sin(\Theta_{mr}-\pi) = Y_{t} + \mn L_{s}\sin(\Theta_{mr}) \\
+  Y_{br} &= Y_{mr}+L_{t}\sin(\Theta_{br}-\pi) = Y_{mr}+ \mn L_{t}\sin(\Theta_{br})
 \end{align}
@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= \dot{X}_{ml} + \mn L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{Y}_{bl} &= 0 \\                                                        
-  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  \dot{X}_{ml} &= \mn L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= \mn L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= \mn L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= \mn L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{Y}_{bl} &= 0 \\                                                               
-  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  \dot{Y}_{ml} &= L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr})\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
 
+%Unnecessary section commented out
+\begin{comment}
 \section{Expanded Brownian Equations}
@@
 \end{align}
+\end{comment}
 

### 2015-08-06 latex/derivation.tex
Add changes to derivation.tex from Mathematica verification.

--- 2015-07-30 latex/derivation.tex
@@
   X_{bl} &= 0 \\
-  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
-  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
-  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
-  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
+  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
+  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
+  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} + \mn L_{t}\cos(\Theta_{mr}) \\
+  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr}+ \mn L_{s}\cos(\Theta_{br})
 \end{align}
@@
   Y_{bl} &= 0 \\
-  Y_{ml} &= Y_{bl}+L_{t}\sin(\Theta_{bl}) \\
-  Y_{t}  &= Y_{ml}+L_{s}\sin(\Theta_{ml}) \\
-  Y_{mr} &= Y_{t} +L_{s}\sin(\Theta_{mr}-\pi) \\
-  Y_{br} &= Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)
+  Y_{ml} &= Y_{bl}+L_{s}\sin(\Theta_{bl}) \\
+  Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
+  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} + \mn L_{t}\sin(\Theta_{mr}) \\
+  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr}+ \mn L_{s}\sin(\Theta_{br})
 \end{align}
@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{Y}_{bl} &= 0 \\                                                        
-  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  \dot{X}_{ml} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{Y}_{bl} &= 0 \\                                                               
-  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  \dot{Y}_{ml} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
 \begin{align}
-  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
-  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
-  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
-  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
+  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
+  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
+  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
+  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
 \end{align}
@@
 \begin{align}
-  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
-  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
-  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
-  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
+  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
+  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
+  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
+  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
 \end{align}
@@
 \begin{align}
-  L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
-  L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
-  L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
-  L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr}
+  L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
+  L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
+  L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
+  L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr}
 \end{align}
@@
 \begin{align}
-  \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
-  \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
-  \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
-  \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr}
+  \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
+  \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
+  \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
+  \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr}
 \end{align}
+\end{comment}
 
@@
 \begin{align}  
-  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
-  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
-  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
+  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
+  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
+  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{ml} &= \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
-  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
+  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
+  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
 \end{align}
@@
 \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
-\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\end{multline}
+\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{multline}%Fix'd
 
@@
 \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
-\dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\end{multline}
+\dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{multline}%Fix'd
 
@@
 \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
-\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\end{equation}
+\dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{equation}%Fix'd
 
@@
 \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
-\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\end{equation}
+\dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\end{equation}%Fix'd
 
@@
 \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
-\dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \end{multline}
@@
 \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) =
-\dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\end{multline}
+\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{multline}%Fix'd
 
@@
 \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) =
-\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
+\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
 - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\end{equation}
+\end{equation}%Fix'd
 
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\end{equation}
+\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\end{equation}%Fix'd
 
@@
 \begin{multline}
-\Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs}
-= \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
+\Big (\dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs}
+= \Big (\dot{Y}_{mr} - L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
 \end{multline}
@@
 \begin{multline}
-\Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
-= \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
+\Big (L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
+= \Big (\mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
 \end{multline}
@@
 \begin{multline}
-\Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr})
+\Big (L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr})
 = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
@@
 \begin{multline}
-\dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg )
+\dot{\Theta}_{br} \Bigg(\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg )
 = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
@@
 \dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} 
-- R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}
+- R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}
 \end{equation}
@@
 \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\frac{(Y_{br} - Y_{mr})}{(X_{br} - X_{mr})} + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
+{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)\frac{(Y_{br} - Y_{mr})}{(X_{br} - X_{mr})} + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
 + \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\frac{(X_{br} - X_{mr})}{(Y_{br} - Y_{mr})}}
+{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)\frac{(X_{br} - X_{mr})}{(Y_{br} - Y_{mr})}}
 \end{equation}
@@
 \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)\frac{L_{t}\sin(\Theta_{br}-\pi)}{L_{t}\cos(\Theta_{br}-\pi)} + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
+{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)\frac{L_{s}\sin(\Theta_{br}-\pi)}{L_{s}\cos(\Theta_{br}-\pi)} + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
 + \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)\frac{L_{t}\cos(\Theta_{br}-\pi)}{L_{t}\sin(\Theta_{br}-\pi)}}
+{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)\frac{L_{s}\cos(\Theta_{br}-\pi)}{L_{s}\sin(\Theta_{br}-\pi)}}
 \end{equation}
@@
 \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (\frac{{L_{t}}^2\sin^2(\Theta_{br}-\pi)}{L_{t}\cos(\Theta_{br}-\pi)}\Big) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)}
+{\Big (\frac{{L_{s}}^2\sin^2(\Theta_{br}-\pi)}{L_{s}\cos(\Theta_{br}-\pi)}\Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
 + \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big) + \Big (\frac{{L_{t}}^2\cos^2(\Theta_{br}-\pi)}{L_{t}\sin(\Theta_{br}-\pi)} \Big) }
+{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (\frac{{L_{s}}^2\cos^2(\Theta_{br}-\pi)}{L_{s}\sin(\Theta_{br}-\pi)} \Big) }
 \end{equation}
@@
 \dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
-{\Big( {L_{t}}^2\sin^2(\Theta_{br}-\pi)\Big) + \Big ({L_{t}}^2\cos^2(\Theta_{br}-\pi) \Big)}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
-{\Big ({L_{t}}^2\sin^2(\Theta_{br}-\pi) \Big) + \Big( {L_{t}}^2\cos^2(\Theta_{br}-\pi) \Big) }
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{s}\cos(\Theta_{br}-\pi))}
+{\Big( {L_{s}}^2\sin^2(\Theta_{br}-\pi)\Big) + \Big ({L_{s}}^2\cos^2(\Theta_{br}-\pi) \Big)}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{br}-\pi))}
+{\Big ({L_{s}}^2\sin^2(\Theta_{br}-\pi) \Big) + \Big( {L_{s}}^2\cos^2(\Theta_{br}-\pi) \Big) }
 \end{equation}
@@
 \dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
-{{L_{t}}^2}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
-{{L_{t}}^2}
+\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{s}\cos(\Theta_{br}-\pi))}
+{{L_{s}}^2}
++ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{br}-\pi))}
+{{L_{s}}^2}
 \end{equation}
@@
 \dot{\Theta}_{br} =
-\frac{1}{L_{t}}\Big(\mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
-+ \frac{1}{L_{t}}\Big(L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
+\frac{1}{L_{s}}\Big(\mn L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
++ \frac{1}{L_{s}}\Big(L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
 \end{multline}
@@
 \begin{equation}
-\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
+\dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
+\dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
 \end{equation}
@@
 \begin{equation}
-\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} +
-\dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
+\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} +
+\dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
 \end{equation}
@@
 \begin{multline}
-\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
-+ \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t }) = \\
-\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t })
+\Big ( \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
++ \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t }) = \\
+\Big ( \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
++ \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t })
 \end{multline}
@@
 \begin{multline}
-L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) =
-\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) \\
+L_{t}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) + L_{t}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) =
+\mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) - L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) \\
 + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t }) 
@@
 \dot{\Theta}_{mr} =
-\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (X_{mr} - X_{t })}
-{L_{s}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t}) + L_{s}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })} \\
-  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(Y_{mr} - Y_{t })}
-  {L_{s}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })}
+\frac{\Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (X_{mr} - X_{t })}
+{L_{t}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t}) + L_{t}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })} \\
+  - \frac{\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(Y_{mr} - Y_{t })}
+  {L_{t}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t }) + L_{t}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })}
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{s}\cos(\Theta_{mr}-\pi))}
-{L_{s}\sin(\Theta_{mr}-\pi)(L_{s}\sin(\Theta_{mr}-\pi)) + L_{s}\cos(\Theta_{mr}-\pi)(L_{s}\cos(\Theta_{mr}-\pi))} \\
-  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))}
-  {L_{s}\sin(\Theta_{mr}-\pi)(L_{s}\sin(\Theta_{mr}-\pi)) + L_{s}\cos(\Theta_{mr}-\pi)(L_{s}\cos(\Theta_{mr}-\pi))}
+\frac{\Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{t}\cos(\Theta_{mr}-\pi))}
+{L_{t}\sin(\Theta_{mr}-\pi)(L_{t}\sin(\Theta_{mr}-\pi)) + L_{t}\cos(\Theta_{mr}-\pi)(L_{t}\cos(\Theta_{mr}-\pi))} \\
+  - \frac{\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{t}\sin(\Theta_{mr}-\pi))}
+  {L_{t}\sin(\Theta_{mr}-\pi)(L_{t}\sin(\Theta_{mr}-\pi)) + L_{t}\cos(\Theta_{mr}-\pi)(L_{t}\cos(\Theta_{mr}-\pi))}
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{\Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{s}\cos(\Theta_{mr}-\pi))}
-{{L_{s}}^2\sin^2(\Theta_{mr}-\pi) + {L_{s}}^2\cos^2(\Theta_{mr}-\pi)} \\
-  - \frac{\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))}
-  {{L_{s}}^2\sin^2(\Theta_{mr}-\pi) + {L_{s}}^2\cos^2(\Theta_{mr}-\pi)}
+\frac{\Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{t}\cos(\Theta_{mr}-\pi))}
+{{L_{t}}^2\sin^2(\Theta_{mr}-\pi) + {L_{t}}^2\cos^2(\Theta_{mr}-\pi)} \\
+  - \frac{\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{t}\sin(\Theta_{mr}-\pi))}
+  {{L_{t}}^2\sin^2(\Theta_{mr}-\pi) + {L_{t}}^2\cos^2(\Theta_{mr}-\pi)}
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+\frac{1}{L_{t}} \Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{t}}\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{s}}\Big(\dot{X}_{br} + \dot{X}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+\frac{1}{L_{t}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
+  - \frac{1}{L_{t}}\Big(\dot{X}_{br} + \dot{X}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{1}{L_{s}} \Big(\mn 2L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+\frac{1}{L_{t}} \Big(\mn 2L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
   - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{s}}\Big(2L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+  - \frac{1}{L_{t}}\Big(2L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
    - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
@@
 \mn\frac{1}{\gamma}\lambda_{lt} =
-\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
 \end{multline}
@@
 \mn\frac{1}{\gamma}\lambda_{lt} =
-\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
 \end{multline}
@@
 \begin{multline}
-\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
 \end{multline}
@@
 \begin{multline}
-(Y_{t } - Y_{ml}) \Big( \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+(Y_{t } - Y_{ml}) \Big( \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
 \end{multline}
@@
 \begin{multline}
-(Y_{t } - Y_{ml})(L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) + (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-(X_{t } - X_{ml})(\mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) + (X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
+(Y_{t } - Y_{ml})(L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) + (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+(X_{t } - X_{ml})(\mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) + (X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
 \end{multline}
@@
 \begin{multline}
-(Y_{t } - Y_{ml})(L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) - (X_{t } - X_{ml})(\mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) = \\
-(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
-- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+(Y_{t } - Y_{ml})(L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) - (X_{t } - X_{ml})(\mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) = \\
+(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
+- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{ml} \Big((Y_{t } - Y_{ml})L_{s}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{s}\cos(\Theta_{ml}) \Big) = \\
-(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
-- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\dot{\Theta}_{ml} \Big((Y_{t } - Y_{ml})L_{t}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{t}\cos(\Theta_{ml}) \Big) = \\
+(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
+- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
 \end{multline}
@@
 \dot{\Theta}_{ml} = \\
-\frac{(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
-{\Big((Y_{t } - Y_{ml})L_{s}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{s}\cos(\Theta_{ml}) \Big)} \\
-- \frac{(Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{\Big((Y_{t } - Y_{ml})L_{s}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{s}\cos(\Theta_{ml}) \Big)}
+\frac{(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
+{\Big((Y_{t } - Y_{ml})L_{t}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{t}\cos(\Theta_{ml}) \Big)} \\
+- \frac{(Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{\Big((Y_{t } - Y_{ml})L_{t}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{t}\cos(\Theta_{ml}) \Big)}
 \end{multline}
@@
 \dot{\Theta}_{ml} = \\
-\frac{L_{s}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
-{\Big((L_{s}\sin(\Theta_{ml}))L_{s}\sin(\Theta_{ml}) + (L_{s}\cos(\Theta_{ml}))L_{s}\cos(\Theta_{ml}) \Big)} \\
-- \frac{(L_{s}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{\Big((L_{s}\sin(\Theta_{ml}))L_{s}\sin(\Theta_{ml}) + (L_{s}\cos(\Theta_{ml}))L_{s}\cos(\Theta_{ml}) \Big)}
+\frac{L_{t}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
+{\Big((L_{t}\sin(\Theta_{ml}))L_{t}\sin(\Theta_{ml}) + (L_{t}\cos(\Theta_{ml}))L_{t}\cos(\Theta_{ml}) \Big)} \\
+- \frac{(L_{t}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{\Big((L_{t}\sin(\Theta_{ml}))L_{t}\sin(\Theta_{ml}) + (L_{t}\cos(\Theta_{ml}))L_{t}\cos(\Theta_{ml}) \Big)}
 \end{multline}
@@
 \dot{\Theta}_{ml} = \\
-\frac{L_{s}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
+\frac{L_{t}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
 {{L_s}^2} \\
-- \frac{(L_{s}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+- \frac{(L_{t}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
 {{L_s}^2}
@@
 \dot{\Theta}_{ml} = \\
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big( \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big( \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
  + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
@@
 \dot{\Theta}_{ml} =
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
@@
 \mn\frac{1}{\gamma}\lambda_{ls} =
-\frac{1}{(X_{ml} - X_{bl})}\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\frac{1}{(X_{ml} - X_{bl})}\dot{X}_{bl} + L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \end{multline}
@@
 \mn\frac{1}{\gamma}\lambda_{ls} =
-\frac{1}{(Y_{ml} - Y_{bl})}\dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\frac{1}{(Y_{ml} - Y_{bl})}\dot{Y}_{bl} + \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \end{multline}
@@
 \begin{multline}
-(Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
+(Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} + L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} + \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
 \end{multline}
@@
 \begin{multline}
-(Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-\mn (X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
+(Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
+\mn (X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
 \end{multline}
@@
 \begin{multline}
-(X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \dot{\Theta}_{bl} = \\
-(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big) \\
-- (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
-+ \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+(X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \dot{\Theta}_{bl} = \\
+(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big) \\
+- (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
++ \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
 \end{multline}
@@
 \dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)}
-{\frac{1}{(X_{ml} - X_{bl})}\Big( (X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \Big)} \\
-- \hspace*{-1.5cm}\frac{\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
-+ \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{\frac{1}{(Y_{ml} - Y_{bl})}\Big( (X_{ml} - X_{bl}) L_{t}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{t}\sin(\Theta_{bl}) \Big)}
+\hspace*{-1.5cm}\frac{\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)}
+{\frac{1}{(X_{ml} - X_{bl})}\Big( (X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \Big)} \\
+- \hspace*{-1.5cm}\frac{\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
++ \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
+{\frac{1}{(Y_{ml} - Y_{bl})}\Big( (X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \Big)}
 \end{multline}
@@
 \dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big( \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big( \mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 + \dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big( L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big( L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 + \dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
@@
 \dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
+\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
+- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
@@
 \big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
-\frac{L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{t}}\dot{\Theta}_{ml}  + \\
-\frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}}\dot{\Theta}_{mr} - 
-\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} - 
-\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}}
+\frac{L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{s}}\dot{\Theta}_{ml}  + \\
+\frac{L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{s}}\dot{\Theta}_{mr} - 
+\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} - 
+\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}}
 \end{multline}
@@
 \dot{\Theta}_{mr} =
-\frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{bl} + 
+\frac{2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{bl} + 
 \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
 \big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi)\big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{br} + \\
-\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
-\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
+\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{br} + \\
+\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
+\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
 \end{multline}
@@
 \dot{\Theta}_{ml} =
-\frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
+\frac{\mn 3L_{s}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{s}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
 \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
 \big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} + \\
+\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} + \\
 \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
@@
 \big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) \big)\dot{\Theta}_{bl} +
-\frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
-\frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
+\frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
+\frac{\mn 2L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
 \big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} + \\
@@
 \big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
-\frac{L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{t}}\dot{\Theta}_{ml}  + \\
-\frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}}\dot{\Theta}_{mr} +
+\frac{L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{s}}\dot{\Theta}_{ml}  + \\
+\frac{L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{s}}\dot{\Theta}_{mr} +
 \mn\dot{\Theta}_{br} =
-\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} + \\
-\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}}
+\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} + \\
+\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}}
 \end{multline}
@@
 \begin{multline}
-\frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{bl} + 
+\frac{2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{bl} + 
 \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
 \big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{br} = \\
-\mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
-\mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
+\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{br} = \\
+\mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
+\mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
 \end{multline}
@@
 \begin{multline}
-\frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
+\frac{\mn 3L_{s}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{s}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
 \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big)\dot{\Theta}_{ml} + \\
 \big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} = \\
+\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} = \\
 \mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
@@
 \big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big)\dot{\Theta}_{bl} +
-\frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
-\frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
+\frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
+\frac{\mn 2L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
 \big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} = \\
@@
   A_1 &= \mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1 \\
-  A_2 &= \frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
-  A_3 &= \frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}} \\
+  A_2 &= \frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
+  A_3 &= \frac{L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{s}} \\
   A_4 &= -1 \\
-  B_1 &= \frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}} \\
+  B_1 &= \frac{2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{t}} \\
   B_2 &= \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big) \\
   B_3 &= \big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big) \\
-  B_4 &= \frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}} \\
-  C_1 &= \frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s} \\
+  B_4 &= \frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{t}} \\
+  C_1 &= \frac{\mn 3L_{s}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{s}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s} \\
   C_2 &= \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big) \\
   C_3 &= \big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big) \\
-  C_4 &= \frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s} \\
+  C_4 &= \frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s} \\
   D_1 &= \big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big) \\
-  D_2 &= \frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
-  D_3 &= \frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} \\
+  D_2 &= \frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
+  D_3 &= \frac{\mn 2L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} \\
   D_4 &= \big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \\
@@
 \begin{multline}
-  X_1 = \frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} + \frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}} \\
+  X_1 = \frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} + \frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}} \\
 \end{multline}
@@
 \begin{multline}
-  X_2 = \mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
-  \mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
+  X_2 = \mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
+  \mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
 \end{multline}

### 2015-08-12 dynein_test.cpp
Add rudimentary tests and notes for more tests to write.

@@ -11,6 +11,20 @@ int equal(float v1, float v2) {
 	else return fabs(v1 - v2)/fabs(v1) <= EPSILON;
 }
 
+int test(float one, float two) {
+
+  if (equal(one, two))
+  {
+    printf("yes, struct says %f and calculation says %f.\n", one, two);
+    return 0;
+  }
+  else 
+  {
+    printf("no! struct says %f and calculation says %f. Exiting.\n\n", one, two);
+    exit(EXIT_FAILURE);
+  }
+}
+
 int main() {
 	
 	float one, two;
@@ -28,131 +42,66 @@ int main() {
 	f.f_mrx = 0;     f.f_mry = 0;
 	f.f_brx = 0;     f.f_bry = 0;
 	
-	printf("\n\nRunning dynein_struct member value check...\n\n");
+	printf("\n\nRunning dynein_struct member value check...\n");
 	
-	//Dynein* dyn = new Dynein(( 90 / 180)*M_PI, ( 90 / 180)*M_PI, ( -90 / 180)*M_PI, ( -90 / 180)*M_PI, f);
+	// Dynein in normal pentagon conformation, do the velocities agree with the velocity definitions?
 	Dynein* dyn = new Dynein((108.0 / 180) * M_PI, (36.0 / 180) * M_PI, -(144.0 / 180) * M_PI, -(72.0 / 180) * M_PI, f);
 	
 	printf("\tIs d_blx defined properly..........");
 	one = dyn->get_d_blx();
 	two = 0;
-	if (equal(one, two))
-	{
-		printf("yes, struct says %f and calculation says %f.\n", one, two);
-	} else 
-	{
-		printf("no! struct says %f and calculation says %f. Exiting.\n\n", one, two);
-		exit(EXIT_FAILURE);
-	}
+	test(one, two);
 	
 	printf("\tIs d_bly defined properly..........");
 	one = dyn->get_d_bly();
 	two = 0;
-	if (equal(one, two))
-	{
-		printf("yes, struct says %f and calculation says %f.\n", one, two);
-	} else 
-	{
-		printf("no! struct says %f and calculation says %f. Exiting.\n\n", one, two);
-		exit(EXIT_FAILURE);
-	}
+        test(one, two);
 	
 	printf("\tIs d_mlx defined properly..........");
 	one = dyn->get_d_mlx();
 	two = -ls*sin(dyn->get_bla())*dyn->get_d_bla();
[…]

### 2015-08-12 latex/derivation.tex
Add rudimentary tests and notes for more tests to write.
a few tweaks while meeting

@@
   X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
-  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} + \mn L_{t}\cos(\Theta_{mr}) \\
-  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr}+ \mn L_{s}\cos(\Theta_{br})
+  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
+  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
 \end{align}
@@
 + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\end{multline}
+\end{multline}%Fix'd
 

### 2015-08-21 latex/derivation.tex
Add labels to derivation.tex system equations.
Add half-made changes to derivation.tex to correctly compute angular velocity matrix terms.

@@
   X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
-  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
-  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
+  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} - L_{t}\cos(\Theta_{mr}) \\
+  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr} - L_{s}\cos(\Theta_{br})
 \end{align}
@@
   Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
-  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} + \mn L_{t}\sin(\Theta_{mr}) \\
-  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr}+ \mn L_{s}\sin(\Theta_{br})
+  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} - L_{t}\sin(\Theta_{mr}) \\
+  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr} - L_{s}\sin(\Theta_{br})
 \end{align}
@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{ml} &= \dot{X}_{bl} - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= \dot{X}_{ml} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
   \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
@@
   \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+  \dot{Y}_{mr} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+  \dot{X}_{ml} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
+  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
+  \dot{X}_{mr} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{X}_{br} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
   \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
 \end{align}
@@
 \section{System after Addition}
-By adding equations from our system together we can isolate the $\lambda$ values. \\
+By adding equations from our system together we can isolate the $\lambda$ values. This system has been verified via CAS.\\
 
@@
 -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Ax}
 \end{multline}%Fix'd
@@
 - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Bx}
 \end{multline}%Fix'd
@@
 + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Cx}
 \end{equation}%Fix'd
@@
 \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Dx}
 \end{equation}%Fix'd
@@
 + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:Ay}
 \end{multline}%Fix'd
@@
 - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:By}
 \end{multline}%Fix'd
@@
 - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:Cy}
 \end{equation}%Fix'd
@@
 \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:Dy}
 \end{equation}%Fix'd
 
-\section{Solution for $\dot{\Theta}_{br}$}
-The following sections come up with solutions for $\dot{\Theta}_{br}$, $\dot{\Theta}_{mr}$, $\dot{\Theta}_{ml}$ and $\dot{\Theta}_{bl}$ using the equations we found in the previous section. \\
+\section{Creating Angular Velocity Matrix}
 
-\begin{multline}
-\Big (\dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs}
-= \Big (\dot{Y}_{mr} - L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
-\end{multline}
+Our goal is to take the above system of equations and put it in this form:
 
-\begin{multline}
-\Big (L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
-= \Big (\mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
-\end{multline}
+\begin{align}
+  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
+  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
+  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
+  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+\end{align}
 
-\begin{multline}
-\Big (L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr})
-= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
-\end{multline}
+where $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s.
+We accomplish this by taking the above system of equations, equating terms with equal lambda terms to eliminate lambdas, and rearranging.
 
-\begin{multline}
-\dot{\Theta}_{br} \Bigg(\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg )
-= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
-\end{multline}
-
-\begin{equation}
-\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} 
-- R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}
-\end{equation}
-
-\begin{equation}
-\dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)\frac{(Y_{br} - Y_{mr})}{(X_{br} - X_{mr})} + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)\frac{(X_{br} - X_{mr})}{(Y_{br} - Y_{mr})}}
-\end{equation}
-
-\begin{equation}
-\dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)\frac{L_{s}\sin(\Theta_{br}-\pi)}{L_{s}\cos(\Theta_{br}-\pi)} + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)\frac{L_{s}\cos(\Theta_{br}-\pi)}{L_{s}\sin(\Theta_{br}-\pi)}}
-\end{equation}
-
-\begin{equation}
-\dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
-{\Big (\frac{{L_{s}}^2\sin^2(\Theta_{br}-\pi)}{L_{s}\cos(\Theta_{br}-\pi)}\Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
-{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (\frac{{L_{s}}^2\cos^2(\Theta_{br}-\pi)}{L_{s}\sin(\Theta_{br}-\pi)} \Big) }
-\end{equation}
-
-\begin{equation}
-\dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{s}\cos(\Theta_{br}-\pi))}
-{\Big( {L_{s}}^2\sin^2(\Theta_{br}-\pi)\Big) + \Big ({L_{s}}^2\cos^2(\Theta_{br}-\pi) \Big)}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{br}-\pi))}
-{\Big ({L_{s}}^2\sin^2(\Theta_{br}-\pi) \Big) + \Big( {L_{s}}^2\cos^2(\Theta_{br}-\pi) \Big) }
-\end{equation}
-
-\begin{equation}
-\dot{\Theta}_{br} =
-\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{s}\cos(\Theta_{br}-\pi))}
-{{L_{s}}^2}
-+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{br}-\pi))}
-{{L_{s}}^2}
-\end{equation}
-\\
-Now expand the cartesian velocity definition: \\
-
-\begin{multline}
-\dot{\Theta}_{br} =
-\frac{1}{L_{s}}\Big(\mn L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
-+ \frac{1}{L_{s}}\Big(L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
-\end{multline}
-
-\section{Solution for $\dot{\Theta}_{mr}$}
-
-\begin{equation}
-\dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
-\dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
-\end{equation}
-
-\begin{equation}
-\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} +
-\dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
-\end{equation}
-
-\begin{multline}
-\Big ( \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} 
-+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t }) = \\
-\Big ( \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t })
-\end{multline}
-
-\begin{multline}
-L_{t}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) + L_{t}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) =
-\mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) - L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) \\
-+ \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (X_{mr} - X_{t }) 
-- \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (Y_{mr} - Y_{t })
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{mr} =
-\frac{\Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (X_{mr} - X_{t })}
-{L_{t}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t}) + L_{t}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })} \\
-  - \frac{\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(Y_{mr} - Y_{t })}
-  {L_{t}\sin(\Theta_{mr}-\pi)(Y_{mr} - Y_{t }) + L_{t}\cos(\Theta_{mr}-\pi)(X_{mr} - X_{t })}
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{mr} =
-\frac{\Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{t}\cos(\Theta_{mr}-\pi))}
-{L_{t}\sin(\Theta_{mr}-\pi)(L_{t}\sin(\Theta_{mr}-\pi)) + L_{t}\cos(\Theta_{mr}-\pi)(L_{t}\cos(\Theta_{mr}-\pi))} \\
-  - \frac{\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{t}\sin(\Theta_{mr}-\pi))}
-  {L_{t}\sin(\Theta_{mr}-\pi)(L_{t}\sin(\Theta_{mr}-\pi)) + L_{t}\cos(\Theta_{mr}-\pi)(L_{t}\cos(\Theta_{mr}-\pi))}
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{mr} =
-\frac{\Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) (L_{t}\cos(\Theta_{mr}-\pi))}
-{{L_{t}}^2\sin^2(\Theta_{mr}-\pi) + {L_{t}}^2\cos^2(\Theta_{mr}-\pi)} \\
-  - \frac{\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -\frac{1}{\gamma}F_{xbr} \Big)(L_{t}\sin(\Theta_{mr}-\pi))}
-  {{L_{t}}^2\sin^2(\Theta_{mr}-\pi) + {L_{t}}^2\cos^2(\Theta_{mr}-\pi)}
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{mr} =
-\frac{1}{L_{t}} \Big( \mn L_{s}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{t}}\Big(L_{s}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{mr} =
-\frac{1}{L_{t}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{t}}\Big(\dot{X}_{br} + \dot{X}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
-\end{multline}
-\\
-Now expand the cartesian velocity definition: \\
-
-\begin{multline}
-\dot{\Theta}_{mr} =
-\frac{1}{L_{t}} \Big(\mn 2L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-  - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{t}}\Big(2L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-   - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
-\end{multline}
-
-\section{Solution for $\dot{\Theta}_{ml}$}
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{lt} =
-\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
-\end{multline}
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{lt} =
-\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
-\end{multline}
-
-\begin{multline}
-\frac{1}{(X_{t } - X_{ml})} \Big( \dot{X}_{ml} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-\frac{1}{(Y_{t } - Y_{ml})} \Big( \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
-\end{multline}
-
-\begin{multline}
-(Y_{t } - Y_{ml}) \Big( \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
-\end{multline}
-
-\begin{multline}
-(Y_{t } - Y_{ml})(L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) + (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-(X_{t } - X_{ml})(\mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) + (X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)
-\end{multline}
-
-\begin{multline}
-(Y_{t } - Y_{ml})(L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml}) - (X_{t } - X_{ml})(\mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}) = \\
-(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
-- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{ml} \Big((Y_{t } - Y_{ml})L_{t}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{t}\cos(\Theta_{ml}) \Big) = \\
-(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \\
-- (Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{ml} = \\
-\frac{(X_{t } - X_{ml}) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
-{\Big((Y_{t } - Y_{ml})L_{t}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{t}\cos(\Theta_{ml}) \Big)} \\
-- \frac{(Y_{t } - Y_{ml})\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{\Big((Y_{t } - Y_{ml})L_{t}\sin(\Theta_{ml}) + (X_{t } - X_{ml})L_{t}\cos(\Theta_{ml}) \Big)}
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{ml} = \\
-\frac{L_{t}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
-{\Big((L_{t}\sin(\Theta_{ml}))L_{t}\sin(\Theta_{ml}) + (L_{t}\cos(\Theta_{ml}))L_{t}\cos(\Theta_{ml}) \Big)} \\
-- \frac{(L_{t}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{\Big((L_{t}\sin(\Theta_{ml}))L_{t}\sin(\Theta_{ml}) + (L_{t}\cos(\Theta_{ml}))L_{t}\cos(\Theta_{ml}) \Big)}
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{ml} = \\
-\frac{L_{t}\cos(\Theta_{ml})) \Big( \dot{Y}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)}
-{{L_s}^2} \\
-- \frac{(L_{t}\sin(\Theta_{ml}))\Big( \dot{X}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{{L_s}^2}
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{ml} = \\
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big( \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
- + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-+ \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
-\end{multline}
-
-\begin{multline}
-\dot{\Theta}_{ml} =
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{Y}_{br} + \dot{Y}_{ml}
-- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
-- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
-\end{multline}
-\\
-Now expand the cartesian velocity definition: \\
-
-\begin{multline}
-\dot{\Theta}_{ml} =
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
-\end{multline}
-
-\section{Solution for $\dot{\Theta}_{bl}$}
+\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
+Here we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$
 
@@
 \mn\frac{1}{\gamma}\lambda_{ls} =
-\frac{1}{(X_{ml} - X_{bl})}\dot{X}_{bl} + L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\Big(\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\frac{1}{(X_{ml} - X_{bl})}
 \end{multline}
@@
 \mn\frac{1}{\gamma}\lambda_{ls} =
-\frac{1}{(Y_{ml} - Y_{bl})}\dot{Y}_{bl} + \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\Big( \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
++ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\frac{1}{(Y_{ml} - Y_{bl})}
 \end{multline}
@@
 \begin{multline}
-(Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} + L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} + \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
+\Big(\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(Y_{ml} - Y_{bl}) = \\
+\Big( \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} \\
++ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(X_{ml} - X_{bl})
 \end{multline}
@@
 \begin{multline}
-(Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} 
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big) = \\
-\mn (X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)
+\Big(\dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} 
+- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \\
+- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
+- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
+\Big(\dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr}
++ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} \\
+- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
+- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
 \end{multline}
@@
 \begin{multline}
-(X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) \dot{\Theta}_{bl} + (Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \dot{\Theta}_{bl} = \\
-(X_{ml} - X_{bl})\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big) \\
-- (Y_{ml} - Y_{bl})\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
-+ \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)
+\Big(
+- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl}
+- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml}
+- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}\\
+- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
+- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
+\Big(
++ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl}
++ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
++ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}\\
++ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
+- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{\Big( \dot{Y}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{t}\cos(\Theta_{ml}) \dot{\Theta}_{ml}
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big)}
-{\frac{1}{(X_{ml} - X_{bl})}\Big( (X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \Big)} \\
-- \hspace*{-1.5cm}\frac{\Big( \dot{X}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{t}\sin(\Theta_{ml}) \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt }
-+ \dot{X}_{t } + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr}  -\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big)}
-{\frac{1}{(Y_{ml} - Y_{bl})}\Big( (X_{ml} - X_{bl}) L_{s}\cos(\Theta_{bl}) + (Y_{ml} - Y_{bl})L_{s}\sin(\Theta_{bl}) \Big)}
+\Big(- 4L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
+- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
+\Big(4L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
+- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big( \mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-+ \dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big( L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-+ \dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+\Big(- 4L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml}
++ 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_s\sin(\Theta_{bl}))\\
+\Big(-4L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
++ 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_s\cos(\Theta_{bl}))= \\
+\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
++ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(L_s\sin(\Theta_{bl}))
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
-- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
- - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
-\end{multline}
-\\
-Now expand the cartesian velocity definition: \\
-
-\begin{multline}
-\dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
-\end{multline}
-
-\clearpage
-
-\section{All Angular Velocity Solutions}
-
-\begin{multline}
-\dot{\Theta}_{br} =
-\frac{1}{L_{s}}\Big(\mn L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
-+ \frac{1}{L_{s}}\Big(L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
+\Big(- 4L_{s}\sin(\Theta_{bl})\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl})\dot{\Theta}_{ml}
++ 2L_{t}\sin(\Theta_{mr})\sin(\Theta_{bl})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\sin(\Theta_{bl})\dot{\Theta}_{br}\Big)\\
+\Big(-4L_{s}\cos(\Theta_{bl})\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})\dot{\Theta}_{ml}
++ 2L_{t}\cos(\Theta_{mr})\cos(\Theta_{bl})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\cos(\Theta_{bl})\dot{\Theta}_{br}\Big)= \\
+\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))
++ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{mr} =
-\frac{1}{L_{t}} \Big(\mn 2L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-  - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
-  - \frac{1}{L_{t}}\Big(2L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-   - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
+-4L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{bl}) + \cos(\Theta_{bl})\cos(\Theta_{bl})\Big)\dot{\Theta}_{bl}
+-3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\dot{\Theta}_{ml}\\
++2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{bl}) + \cos(\Theta_{mr})\cos(\Theta_{bl})\Big)\dot{\Theta}_{mr}
++ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{bl}) + \cos(\Theta_{br})\cos(\Theta_{bl})\Big)\dot{\Theta}_{br}= \\
+\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))
++ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
+\end{multline}
+
+\begin{align}
+  A_1 &= -4L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{bl}) + \cos(\Theta_{bl})\cos(\Theta_{bl})\Big)\\
+  A_2 &= -3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\\
+  A_3 &= 2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{bl}) + \cos(\Theta_{mr})\cos(\Theta_{bl})\Big)\\
+  A_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{bl}) + \cos(\Theta_{br})\cos(\Theta_{bl})\Big)\\
+  X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))+\\
+      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))\\
+\end{align}
+
+\subsection{Solving for $B_1$, $B_2$, $B_3$, $B_4$ and $X_2$}
+Here we take Equations (\ref{eq:Bx}) and (\ref{eq:By}), equate them and manipulate them to be in form $B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} = X_2$
+
+\begin{multline}
+-\frac{1}{\gamma}\lambda_{lt} =
+\Big(
+\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
+- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
+- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
+- R_{xt } - R_{xmr} - R_{xbr}\Big) \frac{1}{(X_{t } - X_{ml})}
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{ml} =
-\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
-- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
+-\frac{1}{\gamma}\lambda_{lt} =
+\Big(\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{t } - Y_{ml})}
+\end{multline}
+
+\subsection{Solving for $C_1$, $C_2$, $C_3$, $C_4$ and $X_3$}
+Here we take Equations (\ref{eq:Cx}) and (\ref{eq:Cy}), equate them and manipulate them to be in form $ C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} = X_3$
+
+\begin{equation}
+-\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big) \frac{1}{(X_{mr} - X_{t })}
+\end{equation}
+
+\begin{equation}
+-\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
++ \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{mr} - Y_{t })}
+\end{equation}
+
+\begin{multline}
+\Big( \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(-L_{t}\sin(\Theta_{mr})) = \\
+\Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
++ \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(-L_{t}\cos(\Theta_{mr}))
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{bl} = \\
-\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
-- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
-- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
-\end{multline}
-
-\section{Making solvable system of equations}
-
-\begin{multline}
-\dot{\Theta}_{br} =
-\big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
-\frac{L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{s}}\dot{\Theta}_{ml}  + \\
-\frac{L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{s}}\dot{\Theta}_{mr} - 
-\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} - 
-\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}}
+\Big( \dot{X}_{t } + \dot{X}_{mr} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr}) +
+\Big(- R_{xmr} - \frac{1}{\gamma}F_{xmr} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr}) = \\
+\Big(\dot{Y}_{t } + \dot{Y}_{mr} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) +
+\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{mr} =
-\frac{2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{bl} + 
-\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
-\big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi)\big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{br} + \\
-\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
-\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
+\Big( \dot{X}_{t } + \dot{X}_{mr} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr})
++ \Big(-\dot{Y}_{t } - \dot{Y}_{mr} + L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) = \\
+\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})
++ \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{ml} =
-\frac{\mn 3L_{s}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{s}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
-\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
-\big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} + \\
-\frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
-\frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
+\Big(- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + -L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} +
+L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} +L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr}) \\
++ \Big(-(L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}) -(L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} -
+L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}) + L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) =\\
+\Big(-R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
 \end{multline}
@@
 \begin{multline}
-\dot{\Theta}_{bl} =
-\big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) \big)\dot{\Theta}_{bl} +
-\frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
-\frac{\mn 2L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
-\big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} + \\
-\frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}{\gamma L_t} + \\
-\frac{\sin(\Theta_{bl})R_{xml} + \mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t}
-\end{multline}
-
-\section{All velocity terms on LHS:}
-
-\begin{multline}
-\big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
-\frac{L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{s}}\dot{\Theta}_{ml}  + \\
-\frac{L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{s}}\dot{\Theta}_{mr} +
-\mn\dot{\Theta}_{br} =
-\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} + \\
-\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}}
+\Big(-2L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
++ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr}) \\
++ \Big(-2L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 2L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
++ L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) =\\
+\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
 \end{multline}
@@
 \begin{multline}
-\frac{2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{bl} + 
-\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
-\big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{t}}\dot{\Theta}_{br} = \\
-\mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
-\mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
+\Big(-2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr})\dot{\Theta}_{bl} - 2L_{t}\sin(\Theta_{ml})\sin(\Theta_{mr})\dot{\Theta}_{ml}
++ 2L_{t}\sin(\Theta_{mr})\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\sin(\Theta_{mr})\dot{\Theta}_{br} \Big)\\
++ \Big(-2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr})\dot{\Theta}_{bl} - 2L_{t}\cos(\Theta_{ml})\cos(\Theta_{mr})\dot{\Theta}_{ml}
++ 2L_{t}\cos(\Theta_{mr})\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\cos(\Theta_{mr})\dot{\Theta}_{br}\Big) =\\
+\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
 \end{multline}
@@
 \begin{multline}
-\frac{\mn 3L_{s}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{s}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
-\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big)\dot{\Theta}_{ml} + \\
-\big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
-\frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} = \\
-\mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
-\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
+- 2L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{mr}) + \cos(\Theta_{bl})\cos(\Theta_{mr})\Big)\dot{\Theta}_{bl}
+- 2L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{mr}) + \cos(\Theta_{ml})\cos(\Theta_{mr})\Big)\dot{\Theta}_{ml}\\
++ 2L_{t}\Big(\sin^2(\Theta_{mr}) + \cos^2(\Theta_{mr})\Big)\dot{\Theta}_{mr}
++ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big)\dot{\Theta}_{br} =\\
+\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+\end{multline}
+
+\begin{align}
+  C_1 &= - 2L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{mr}) + \cos(\Theta_{bl})\cos(\Theta_{mr})\Big) \\
+  C_2 &= - 2L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{mr}) + \cos(\Theta_{ml})\cos(\Theta_{mr})\Big) \\
+  C_3 &= 2L_{t} \\
+  C_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big) \\
+  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr}) \\
+\end{align}
+
+\subsection{Solving for $D_1$, $D_2$, $D_3$, $D_4$ and $X_4$}
+Here we take Equations (\ref{eq:Dx}) and (\ref{eq:Dy}), equate them and manipulate them to be in form $D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} = X_4$.
+
+\begin{equation}
+-\frac{1}{\gamma}\lambda_{rs} = \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) \frac{1}{(Y_{br} - Y_{mr})}
+\end{equation}
+
+\begin{equation}
+-\frac{1}{\gamma}\lambda_{rs} = \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) \frac{1}{(X_{br} - X_{mr})}
+\end{equation}
+
+\begin{equation}
+  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (X_{br} - X_{mr}) =
+  \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (Y_{br} - Y_{mr})
+\end{equation}
+
+\begin{equation}
+  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (-L_s\cos{\Theta_{br}}) =
+  \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (-L_s\sin{\Theta_{br}})
+\end{equation}
+
+\begin{equation}
+  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{br}}) =
+  \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{br}})
+\end{equation}
+
+\begin{equation}
+  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\big)(\cos{\Theta_{br}}) + \big(-\dot{X}_{mr} - L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\big)(\sin{\Theta_{br}}) =
+  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{br}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{br}})
+\end{equation}
+
+\begin{multline}
+  \big(L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\big)(\cos{\Theta_{br}})\\
++ \big(L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\big)(\sin{\Theta_{br}}) = \\
+  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{br}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{br}})
 \end{multline}
@@
 \begin{multline}
-\big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big)\dot{\Theta}_{bl} +
-\frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
-\frac{\mn 2L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
-\big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} = \\
-\mn \frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}{\gamma L_t} + \\
-\mn \frac{\sin(\Theta_{bl})R_{xml} + \mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t}
+  L_{s}(\cos(\Theta_{br})\cos(\Theta_{bl}) + \sin(\Theta_{br})\sin(\Theta_{bl}))\dot{\Theta}_{bl}
+  + L_{t}(\cos(\Theta_{br})\cos(\Theta_{ml}) + \sin(\Theta_{br})\sin(\Theta_{ml}))\dot{\Theta}_{ml} \\
+  - L_{t}(\cos(\Theta_{br})\cos(\Theta_{mr}) + \sin(\Theta_{br})\sin(\Theta_{mr}))\dot{\Theta}_{mr}
+  - L_{s}(\cos^2(\Theta_{br}) + \sin^2(\Theta_{br}))\dot{\Theta}_{br} = \\
+  (R_{ybr} + \frac{1}{\gamma}F_{ybr}) (\cos{\Theta_{br}}) - (R_{xbr} + \frac{1}{\gamma}F_{xbr} ) (\sin{\Theta_{br}})
 \end{multline}
 
+\begin{align}
+  D_1 &= L_{s}\Big(\cos(\Theta_{br})\cos(\Theta_{bl}) + \sin(\Theta_{br})\sin(\Theta_{bl})\Big)\\
+  D_2 &= L_{t}\Big(\cos(\Theta_{br})\cos(\Theta_{ml}) + \sin(\Theta_{br})\sin(\Theta_{ml})\Big)\\
+  D_3 &= -L_{t}\Big(\cos(\Theta_{br})\cos(\Theta_{mr}) + \sin(\Theta_{br})\sin(\Theta_{mr})\Big)\\
+  D_4 &= -L_{s}\\
+  X_4 &= (R_{ybr} + \frac{1}{\gamma}F_{ybr})\cos{\Theta_{br}} - (R_{xbr} + \frac{1}{\gamma}F_{xbr})\sin(\Theta_{br})
+\end{align}
+
 \section{Breaking terms down into symbols}
-
-\begin{align}
-  A_1 &= \mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1 \\
-  A_2 &= \frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
-  A_3 &= \frac{L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{s}} \\
-  A_4 &= -1 \\
-  B_1 &= \frac{2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{t}} \\
-  B_2 &= \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big) \\
-  B_3 &= \big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big) \\
-  B_4 &= \frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{t}} \\
-  C_1 &= \frac{\mn 3L_{s}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{s}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s} \\
-  C_2 &= \big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big) \\
-  C_3 &= \big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big) \\
-  C_4 &= \frac{\mn L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s} \\
-  D_1 &= \big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big) \\
-  D_2 &= \frac{\mn 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t} \\
-  D_3 &= \frac{\mn 2L_{t}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{t}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} \\
-  D_4 &= \big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \\
-\end{align}
 
@@
 \end{multline}
-
-\begin{align}
-  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
-  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
-  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
-  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
-\end{align}
 

### 2015-08-22 latex/derivation.tex
Finish re-derivation of angular velocity matrix equation terms.

@@
 
-Our goal is to take the above system of equations and put it in this form:
+Our goal is to take the above system of equations and put it in matrix form:
 
@@
 
-where $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s.
-We accomplish this by taking the above system of equations, equating terms with equal lambda terms to eliminate lambdas, and rearranging.
+This will allow us to perform a matrix solution for the angular velocities.
+$X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s.
+The above system of equations has four lambda terms: $\lambda_{ls}, \lambda_{lt}, \lambda_{rt}$ and $\lambda_{ls}$.
+Each term is present in two equations.
+We will use this redundancy to eliminate the lambda terms and create the above matrix.
 
 \subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
-Here we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$
+In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$\\
+
+We start by dividing out the position terms in Equations (\ref{eq:Ax}) and (\ref{eq:Ay}) to make their LHSs identical.
 
@@
 
+We then equate them.
+
 \begin{multline}
@@
 \end{multline}
+
+Then we group like terms for clarity.
 
@@
 \end{multline}
+
+We then expand all the $\dot{X}$ terms using their definitions from the Cartesian Velocities section above.
 
@@
 
+Then we group together the like terms from the expansion.
+
 \begin{multline}
@@
 \end{multline}
+
+We then bring all the angular velocity terms to one side and all the force terms to the other side.
 
@@
 
+We then distribute the $L_s\sin(\Theta_{bl})$ and $L_s\cos(\Theta_{bl})$ terms into the expression.
+
 \begin{multline}
@@
 \end{multline}
+
+Finally, we group all terms by their angular velocity.
 
@@
 
+This is the form we want. We now know the value of $A_1, A_2, A_3, A_4$ and $X_1$.
+
 \begin{align}
-  A_1 &= -4L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{bl}) + \cos(\Theta_{bl})\cos(\Theta_{bl})\Big)\\
+  A_1 &= -4L_{s}\\
   A_2 &= -3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\\
@@
   X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))+\\
-      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))\\
+      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
 \end{align}
@@
 -\frac{1}{\gamma}\lambda_{lt} =
-\Big(\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{t } - Y_{ml})}
+\Big(
+\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
++ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
+- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
+- R_{yt} - R_{ymr} - R_{ybr}\Big) \frac{1}{(Y_{t } - Y_{ml})}
 \end{multline}
+
+\begin{multline}
+\Big(
+\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
+- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
+- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
+- R_{xt } - R_{xmr} - R_{xbr}\Big)(Y_{t } - Y_{ml}) =\\
+\Big(
+\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
++ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
+- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
+- R_{yt} - R_{ymr} - R_{ybr}\Big)(X_{t } - X_{ml})
+\end{multline}
+
+\begin{multline}
+\Big(
+\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
+- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
+- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
+- R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml})) =\\
+\Big(
+\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
++ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
+- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
+- R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
+\end{multline}
+
+\begin{multline}
+\Big(\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
+- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
+- \Big(\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
++ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
+- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\end{multline}
+
+\begin{multline}
+\Big( -3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
++ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
+- \Big( 3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} -2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
+- L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
+- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\end{multline}
+
+\begin{multline}
+\Big( -3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
++ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
++ \Big(-3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
++ L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
++ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\end{multline}
+
+\begin{multline}
+\Big( -3L_{s}\sin(\Theta_{bl})L_t\sin(\Theta_{ml})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})L_t\sin(\Theta_{ml})\dot{\Theta}_{ml}
++ 2L_{t}\sin(\Theta_{mr})L_t\sin(\Theta_{ml})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})L_t\sin(\Theta_{ml})\dot{\Theta}_{br}\Big)\\
++ \Big(-3L_{s}\cos(\Theta_{bl})L_t\cos(\Theta_{ml})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})L_t\cos(\Theta_{ml})\dot{\Theta}_{ml}
++ 2L_{t}\cos(\Theta_{mr})L_t\cos(\Theta_{ml})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})L_t\cos(\Theta_{ml})\dot{\Theta}_{br}\Big) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
++ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\end{multline}
+
+\begin{multline}
+-3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\dot{\Theta}_{bl}
+-3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{ml}) + \cos(\Theta_{ml})\cos(\Theta_{ml})\Big)\dot{\Theta}_{ml}\\
++2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\dot{\Theta}_{mr}
++ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\dot{\Theta}_{br} =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))
++ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
+\end{multline}
+
+\begin{align}
+  C_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
+  C_2 &= -3L_{t}\\
+  C_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
+  C_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
+  X_3 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
+      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
+\end{align}
 
@@
   C_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big) \\
-  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr}) \\
+  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})\\
+      &+ \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
 \end{align}
@@
 
-\section{Breaking terms down into symbols}
+\section{CAS solution to Matrix Equation}
 
-\begin{multline}
-  X_1 = \frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} + \frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}} \\
-\end{multline}
+We now have our equations in the following form:
 
-\begin{multline}
-  X_2 = \mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
-  \mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
-\end{multline}
+\begin{equation}
+  \begin{pmatrix}
+    A_1 & A_2 & A_3 & A_4 \\
+    B_1 & B_2 & B_3 & B_4 \\
+    C_1 & C_2 & C_3 & C_4 \\
+    D_1 & D_2 & D_3 & D_4 \\    
+  \end{pmatrix}
+\times
+  \begin{pmatrix}
+    \Theta_{bl} \\
+    \Theta_{ml} \\
+    \Theta_{mr} \\
+    \Theta_{br} \\
+  \end{pmatrix}
+=
+  \begin{pmatrix}
+    X_1 \\
+    X_2 \\
+    X_3 \\
+    X_4 \\
+  \end{pmatrix}
+\end{equation}
 
-\begin{multline}
-  X_3 = \mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
-	\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
-\end{multline}
-The following is David's simplification of $X_3$:
+We use a CAS (Mathematica) to solve this equation for the angular velocities. We arrive at the following expressions, which we have broken up into numerator and denominator for legibility:
+
 \begin{align}
-  X_3 &= -\frac{1}{L_s}\left\{ \sin(\Theta_{ml})\left(\frac{F_{xt}+F_{xmr}+F_{xbr}}{\gamma} + R_{xt }+R_{xmr}+R_{xbr}\right) -
-    \cos(\Theta_{ml})\left(\frac{F_{yt }+F_{ymr}+F_{ybr}}{\gamma} +
-    R_{yt}+R_{ymr}+R_{ybr}\right) \right\}
-    \\
-    &?= \frac{\hat{a}_{ml}\cdot \vec{F}_{tot_{ml}}}{\gamma L_s}
+\dot{\Theta}_{bl} &= \frac{N_{bl}}{D} \\
+\dot{\Theta}_{ml} &= \frac{N_{ml}}{D} \\
+\dot{\Theta}_{mr} &= \frac{N_{mr}}{D} \\
+\dot{\Theta}_{br} &= \frac{N_{br}}{D}
 \end{align}
-where $\hat a$ is a unit vector in a the direction related to the $ml$
-segment, and $\vec{F}_{tot_{ml}}$ is a total force of some sort,
-including the random fluctuations.  I don't think we want to write the
-formula in this final way, but it may help in thinking about the
-equations.  I certainly think that the form with just one $\sin$ and
-one $\cos$ is an improvement, and reduces the likelihood of
-introducing sign errors (or sine errors, for that matter).
 
-\begin{multline}
-  X_4 = \mn \frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}
-  {\gamma L_t} \\+ \mn \frac{\sin(\Theta_{bl})R_{xml} +\mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t} \\
-\end{multline}
-
-\section{System solution!}
-This system is solved via Mathematica...\\
 \begin{multline}
@@
 
-\begin{align}
-\dot{\Theta}_{bl} &= \frac{N_{bl}}{D} \\
-\dot{\Theta}_{ml} &= \frac{N_{ml}}{D} \\
-\dot{\Theta}_{mr} &= \frac{N_{mr}}{D} \\
-\dot{\Theta}_{br} &= \frac{N_{br}}{D}
-\end{align}
-
 \end{document}

### 2015-08-22 latex/derivation.tex

@@
   X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
-  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} - L_{t}\cos(\Theta_{mr}) \\
-  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr} - L_{s}\cos(\Theta_{br})
+  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
+  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
 \end{align}

### 2015-08-22 latex/derivation.tex
Update dynein_struct.cpp with new angular velocity matrix terms.

@@
 \begin{align}
-  C_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
-  C_2 &= -3L_{t}\\
-  C_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
-  C_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
-  X_3 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
+  B_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
+  B_2 &= -3L_{t}\\
+  B_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
+  B_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
+  X_2 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
       &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))

### 2015-08-22 dynein_struct.h

@@ -23,7 +23,7 @@ const double f_mrx_init = 0;   const double f_mry_init = 0;
 const double f_brx_init = 0;   const double f_bry_init = 0;
 
 const double inctime = 0.1;
-const double runtime = 1.0;
+const double runtime = 50.0;
 
 typedef enum {
 	LEFTBOUND,

### 2015-08-22 dynein_test.cpp

@@ -41,7 +41,7 @@ int main() {
 	forces zero_f;
 	zero_f.r_blx = 0;     zero_f.r_bly = 0;
 	zero_f.r_mlx = 0;     zero_f.r_mly = 0;
-	zero_f.r_tx  = 0;	 zero_f.r_ty  = 0;
+	zero_f.r_tx  = 0;     zero_f.r_ty  = 0;
 	zero_f.r_mrx = 0;     zero_f.r_mry = 0;
 	zero_f.r_brx = 0;     zero_f.r_bry = 0;
 
@@ -83,7 +83,7 @@ int main() {
                              (90.0 / 180) * M_PI,
                              -(90.0 / 180) * M_PI,
                              -(90.0 / 180) * M_PI,
-                             zero_f);
+                             f);
     printf("\n");
     num_failures += test("it is standing up (y)", dyn->get_bry(), 4*10);
     num_failures += test("it is standing up (x)", dyn->get_brx(), 0);
@@ -109,7 +109,7 @@ int main() {
                              (0.0 / 180) * M_PI,
                              -(180.0 / 180) * M_PI,
                              -(180.0 / 180) * M_PI,
-                             zero_f);
+                             f);
     printf("\n");
     num_failures += test("it is lying down (bry)", dyn->get_bry(), 0);
     num_failures += test("it is lying down (mry)", dyn->get_mry(), 0);

### 2015-09-01 latex/derivation.tex
add some text regarding physical parameters.

@@
 
+\begin{twocolumn}
+\section{Notes on physical parameters}
+
+Stoke's Law states that the relationship between viscosity, force, and
+velocity for a spherical particle is given by:
+\begin{align}
+  \mathbf{v} &= \frac{\mathbf{F}}{6\pi \mu R}
+\end{align}
+where $\mu$ is the viscosity of the fluid, and $R$ is the radius of
+the particle.  Thus in our terminology:
+\begin{align}
+  \gamma &= 6\pi \mu R.
+\end{align}
+Note that the viscosity of water is temperature-dependent and around
+0.7~mPa~s at body temperature.  However, the viscosity of cytoplasm
+may be rather different, and will of course depend on length scale.
+But for our purposes we can probably get away with this value.
+
+The random force $\mathbf{R}(t)$ should have a Gaussian distribution
+with variance~1, but then be divided by $\sqrt{\Delta t}$.  Thus, the
+smaller the time step, the larger the random force we will apply.  We
+can understand this in the backwards direction.  When we observe a
+larger time step, the ``random force'' results from many smaller
+random forces added together, and these smaller forces often cancel,
+leading to this reduction in the total force over that time period.
+
+Finally, we will need estimates for the radii of each domain (to go
+into the $\gamma$ parameter, the equilibrium angles for each hinge, and
+the spring constants for each hinge.  The first two we can estimate
+from the structure of dynein.  The third will require a rough guess.
+We can get a ball-park guess by deciding how much we want the angle to
+fluctuate (e.g. $\ll \pi$ for each angle!), and then take our spring
+constant to be $kT$ divided by that anglular fluctuation squared.
+
+\end{twocolumn}
+
 \end{document}

### 2015-09-12 latex/derivation.tex
Change naming scheme from left and right to bound and free. Add 'natural' mode to simulate.py.

@@
 \begin{align}
-  X_{bl} &= 0 \\
-  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
-  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
-  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
-  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
+  X_{bb} &= 0 \\
+  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
+  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
+  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
+  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
 \end{align}
@@
 \begin{align}
-  Y_{bl} &= 0 \\
-  Y_{ml} &= Y_{bl}+L_{s}\sin(\Theta_{bl}) \\
-  Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
-  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} - L_{t}\sin(\Theta_{mr}) \\
-  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr} - L_{s}\sin(\Theta_{br})
+  Y_{bb} &= 0 \\
+  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
+  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
+  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
+  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
 \end{align}
@@
 \begin{align}
-  \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= \dot{X}_{bl} - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= \dot{X}_{ml} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+  \dot{X}_{bb} &= 0 \\
+  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
+  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
+  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
+  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
 \end{align}
@@
 \begin{align}                                                                          
-  \dot{Y}_{bl} &= 0 \\                                                        
-  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+  \dot{Y}_{bb} &= 0 \\                                                        
+  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
+  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
+  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
+  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 \end{align}
@@
 \begin{align}
-  \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{X}_{mr} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{X}_{br} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+  \dot{X}_{bb} &= 0 \\
+  \dot{X}_{bm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
+  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
+  \dot{X}_{fm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
+  \dot{X}_{fb} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
 \end{align}
@@
 \begin{align}                                                                               
-  \dot{Y}_{bl} &= 0 \\                                                               
-  \dot{Y}_{ml} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
-  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
-  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+  \dot{Y}_{bb} &= 0 \\                                                               
+  \dot{Y}_{bm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
+  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
+  \dot{Y}_{fm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
+  \dot{Y}_{fb} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 \end{align}
@@
 \begin{align}  
-  \dot{X}_{bl} &= 0 \\
-  \dot{X}_{ml} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml} \\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt } \\
-  \dot{X}_{mr} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr} \\
-  \dot{X}_{br} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}
+  \dot{X}_{bb} &= 0 \\
+  \dot{X}_{bm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{bm} - X_{bb}) + \lambda_{lt}(X_{t } - X_{bm}) \Big) + R_{xml} \\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{bm}) + \lambda_{rt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
+  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{fm} - X_{t }) + \lambda_{rs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
+  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{bl} &= 0 \\
-  \dot{Y}_{ml} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml} \\
-  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt } \\
-  \dot{Y}_{mr} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr} \\
-  \dot{Y}_{br} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}
+  \dot{Y}_{bb} &= 0 \\
+  \dot{Y}_{bm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{bm} - Y_{bb}) + \lambda_{lt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
+  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{bm}) + \lambda_{rt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
+  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{fm} - Y_{t }) + \lambda_{rs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
+  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
 \end{align}
@@
 \begin{align}
-  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
-  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
-  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
-  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } \\
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} \\
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr}
 \end{align}
@@
 \begin{align}
-  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
-  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
-  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
-  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } \\
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr}
 \end{align}
@@
 \begin{align}
-  L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
-  L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
-  L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
-  L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr}
+  L_{s}\sin(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
+  L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) - R_{xml} \\
+  L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) - R_{xt } \\
+  L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) - R_{xmr}
 \end{align}
@@
 \begin{align}
-  \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
-  \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
-  \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
-  \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr}
+  \mn L_{s}\cos(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  \mn L_{t}\cos(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) - R_{yml}\\
+  \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) - R_{yt } \\
+  \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) - R_{ymr}
 \end{align}
@@
 \begin{align}  
-  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
-  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
-  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
+  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } \\
+  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} \\
+  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
-  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
+  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
+  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr}
 \end{align}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
-\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) =
+\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Ax}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
-\dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) =
+\dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Bx}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
-\dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) =
+\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Cx}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
-\dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) = 
+\dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Dx}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
-\dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) =
+\dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
++ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:Ay}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) =
-\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) =
+\dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:By}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) =
-\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+\mn\frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) =
+\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 - R_{ybr} - \frac{1}{\gamma}F_{ybr}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:Dy}
@@
 \begin{align}
-  A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} &= X_1 \\
-  B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} &= X_2 \\
-  C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} &= X_3 \\
-  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
+  A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} &= X_1 \\
+  B_1\dot{\Theta}_{bb} + B_2 \dot{\Theta}_{bm} + B_3 \dot{\Theta}_{fm} + B_4 \dot{\Theta}_{fb} &= X_2 \\
+  C_1\dot{\Theta}_{bb} + C_2 \dot{\Theta}_{bm} + C_3 \dot{\Theta}_{fm} + C_4 \dot{\Theta}_{fb} &= X_3 \\
+  D_1\dot{\Theta}_{bb} + D_2 \dot{\Theta}_{bm} + D_3 \dot{\Theta}_{fm} + D_4 \dot{\Theta}_{fb} &= X_4 \\
 \end{align}
@@
 \subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
-In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$\\
+In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} = X_1$\\
 
@@
 \mn\frac{1}{\gamma}\lambda_{ls} =
-\Big(\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\frac{1}{(X_{ml} - X_{bl})}
+\Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\frac{1}{(X_{bm} - X_{bb})}
 \end{multline}
@@
 \mn\frac{1}{\gamma}\lambda_{ls} =
-\Big( \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
-+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\frac{1}{(Y_{ml} - Y_{bl})}
+\Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
++ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\frac{1}{(Y_{bm} - Y_{bb})}
 \end{multline}
@@
 \begin{multline}
-\Big(\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(Y_{ml} - Y_{bl}) = \\
-\Big( \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} \\
-+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(X_{ml} - X_{bl})
+\Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(Y_{bm} - Y_{bb}) = \\
+\Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} \\
++ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(X_{bm} - X_{bb})
 \end{multline}
@@
 \begin{multline}
-\Big(\dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} 
-- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \\
+\Big(\dot{X}_{bb} + \dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm} 
+- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \\
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
-\Big(\dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr}
-+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} \\
+- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
+\Big(\dot{Y}_{bb} + \dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm}
++ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} \\
 - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
+- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
 \end{multline}
@@
 \Big(
-- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl}
-- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml}
-- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}\\
-- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb}
+- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
+- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}\\
+- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
+- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
 \Big(
-+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl}
-+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
-+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}\\
-+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
++ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb}
++ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
++ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}\\
++ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
+- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
 \end{multline}
@@
 \begin{multline}
-\Big(- 4L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
+\Big(- 4L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
-\Big(4L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
+- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
+\Big(4L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 - \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
+- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
 \end{multline}
@@
 \begin{multline}
-\Big(- 4L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml}
-+ 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_s\sin(\Theta_{bl}))\\
-\Big(-4L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
-+ 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_s\cos(\Theta_{bl}))= \\
-\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
-+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(L_s\sin(\Theta_{bl}))
+\Big(- 4L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
++ 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_s\sin(\Theta_{bb}))\\
+\Big(-4L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
++ 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_s\cos(\Theta_{bb}))= \\
+\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
++ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(L_s\sin(\Theta_{bb}))
 \end{multline}
 
-We then distribute the $L_s\sin(\Theta_{bl})$ and $L_s\cos(\Theta_{bl})$ terms into the expression.
+We then distribute the $L_s\sin(\Theta_{bb})$ and $L_s\cos(\Theta_{bb})$ terms into the expression.
 
 \begin{multline}
-\Big(- 4L_{s}\sin(\Theta_{bl})\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\sin(\Theta_{bl})\dot{\Theta}_{ml}
-+ 2L_{t}\sin(\Theta_{mr})\sin(\Theta_{bl})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\sin(\Theta_{bl})\dot{\Theta}_{br}\Big)\\
-\Big(-4L_{s}\cos(\Theta_{bl})\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\cos(\Theta_{bl})\dot{\Theta}_{ml}
-+ 2L_{t}\cos(\Theta_{mr})\cos(\Theta_{bl})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\cos(\Theta_{bl})\dot{\Theta}_{br}\Big)= \\
-\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))
-+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
+\Big(- 4L_{s}\sin(\Theta_{bb})\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\sin(\Theta_{bb})\dot{\Theta}_{bm}
++ 2L_{t}\sin(\Theta_{fm})\sin(\Theta_{bb})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\sin(\Theta_{bb})\dot{\Theta}_{fb}\Big)\\
+\Big(-4L_{s}\cos(\Theta_{bb})\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\cos(\Theta_{bb})\dot{\Theta}_{bm}
++ 2L_{t}\cos(\Theta_{fm})\cos(\Theta_{bb})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\cos(\Theta_{bb})\dot{\Theta}_{fb}\Big)= \\
+\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bb}))
++ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bb}))
 \end{multline}
@@
 \begin{multline}
--4L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{bl}) + \cos(\Theta_{bl})\cos(\Theta_{bl})\Big)\dot{\Theta}_{bl}
--3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\dot{\Theta}_{ml}\\
-+2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{bl}) + \cos(\Theta_{mr})\cos(\Theta_{bl})\Big)\dot{\Theta}_{mr}
-+ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{bl}) + \cos(\Theta_{br})\cos(\Theta_{bl})\Big)\dot{\Theta}_{br}= \\
-\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))
-+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
+-4L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{bb}) + \cos(\Theta_{bb})\cos(\Theta_{bb})\Big)\dot{\Theta}_{bb}
+-3L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{bb}) + \cos(\Theta_{bm})\cos(\Theta_{bb})\Big)\dot{\Theta}_{bm}\\
++2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bb}) + \cos(\Theta_{fm})\cos(\Theta_{bb})\Big)\dot{\Theta}_{fm}
++ L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bb}) + \cos(\Theta_{fb})\cos(\Theta_{bb})\Big)\dot{\Theta}_{fb}= \\
+\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bb}))
++ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bb}))
 \end{multline}
@@
   A_1 &= -4L_{s}\\
-  A_2 &= -3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\\
-  A_3 &= 2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{bl}) + \cos(\Theta_{mr})\cos(\Theta_{bl})\Big)\\
-  A_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{bl}) + \cos(\Theta_{br})\cos(\Theta_{bl})\Big)\\
-  X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))+\\
-      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
+  A_2 &= -3L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{bb}) + \cos(\Theta_{bm})\cos(\Theta_{bb})\Big)\\
+  A_3 &= 2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bb}) + \cos(\Theta_{fm})\cos(\Theta_{bb})\Big)\\
+  A_4 &= L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bb}) + \cos(\Theta_{fb})\cos(\Theta_{bb})\Big)\\
+  X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bb}))+\\
+      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bb}))
 \end{align}
@@
 \subsection{Solving for $B_1$, $B_2$, $B_3$, $B_4$ and $X_2$}
-Here we take Equations (\ref{eq:Bx}) and (\ref{eq:By}), equate them and manipulate them to be in form $B_1\dot{\Theta}_{bl} + B_2 \dot{\Theta}_{ml} + B_3 \dot{\Theta}_{mr} + B_4 \dot{\Theta}_{br} = X_2$
+Here we take Equations (\ref{eq:Bx}) and (\ref{eq:By}), equate them and manipulate them to be in form $B_1\dot{\Theta}_{bb} + B_2 \dot{\Theta}_{bm} + B_3 \dot{\Theta}_{fm} + B_4 \dot{\Theta}_{fb} = X_2$
 
@@
 \Big(
-\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
-- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
+\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
+- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} 
 - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xt } - R_{xmr} - R_{xbr}\Big) \frac{1}{(X_{t } - X_{ml})}
+- R_{xt } - R_{xmr} - R_{xbr}\Big) \frac{1}{(X_{t } - X_{bm})}
 \end{multline}
@@
 \Big(
-\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
-+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
+\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
++ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} 
 - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yt} - R_{ymr} - R_{ybr}\Big) \frac{1}{(Y_{t } - Y_{ml})}
+- R_{yt} - R_{ymr} - R_{ybr}\Big) \frac{1}{(Y_{t } - Y_{bm})}
 \end{multline}
@@
 \Big(
-\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
-- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
+\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
+- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} 
 - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xt } - R_{xmr} - R_{xbr}\Big)(Y_{t } - Y_{ml}) =\\
+- R_{xt } - R_{xmr} - R_{xbr}\Big)(Y_{t } - Y_{bm}) =\\
 \Big(
-\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
-+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
+\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
++ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} 
 - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yt} - R_{ymr} - R_{ybr}\Big)(X_{t } - X_{ml})
+- R_{yt} - R_{ymr} - R_{ybr}\Big)(X_{t } - X_{bm})
 \end{multline}
@@
 \Big(
-\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
-- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
+\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
+- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} 
 - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml})) =\\
+- R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{bm})) =\\
 \Big(
-\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
-+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
+\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
++ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} 
 - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
+- R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
 \end{multline}
@@
 \begin{multline}
-\Big(\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
-- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
-- \Big(\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
-+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
-- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\Big(\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
+- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\sin(\Theta_{bm}))\\
+- \Big(\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
++ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\cos(\Theta_{bm})) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
+- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
 \end{multline}
@@
 \begin{multline}
-\Big( -3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
-+ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
-- \Big( 3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} -2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
-- L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
-- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\Big( -3L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}
++ L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\sin(\Theta_{bm}))\\
+- \Big( 3L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} -2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}
+- L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\cos(\Theta_{bm})) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
+- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
 \end{multline}
@@
 \begin{multline}
-\Big( -3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
-+ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
-+ \Big(-3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
-+ L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
-+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\Big( -3L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}
++ L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\sin(\Theta_{bm}))\\
++ \Big(-3L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}
++ L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\cos(\Theta_{bm})) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
++ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
 \end{multline}
@@
 \begin{multline}
-\Big( -3L_{s}\sin(\Theta_{bl})L_t\sin(\Theta_{ml})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})L_t\sin(\Theta_{ml})\dot{\Theta}_{ml}
-+ 2L_{t}\sin(\Theta_{mr})L_t\sin(\Theta_{ml})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})L_t\sin(\Theta_{ml})\dot{\Theta}_{br}\Big)\\
-+ \Big(-3L_{s}\cos(\Theta_{bl})L_t\cos(\Theta_{ml})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})L_t\cos(\Theta_{ml})\dot{\Theta}_{ml}
-+ 2L_{t}\cos(\Theta_{mr})L_t\cos(\Theta_{ml})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})L_t\cos(\Theta_{ml})\dot{\Theta}_{br}\Big) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
-+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
+\Big( -3L_{s}\sin(\Theta_{bb})L_t\sin(\Theta_{bm})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})L_t\sin(\Theta_{bm})\dot{\Theta}_{bm}
++ 2L_{t}\sin(\Theta_{fm})L_t\sin(\Theta_{bm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})L_t\sin(\Theta_{bm})\dot{\Theta}_{fb}\Big)\\
++ \Big(-3L_{s}\cos(\Theta_{bb})L_t\cos(\Theta_{bm})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})L_t\cos(\Theta_{bm})\dot{\Theta}_{bm}
++ 2L_{t}\cos(\Theta_{fm})L_t\cos(\Theta_{bm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})L_t\cos(\Theta_{bm})\dot{\Theta}_{fb}\Big) =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
++ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
 \end{multline}
@@
 \begin{multline}
--3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\dot{\Theta}_{bl}
--3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{ml}) + \cos(\Theta_{ml})\cos(\Theta_{ml})\Big)\dot{\Theta}_{ml}\\
-+2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\dot{\Theta}_{mr}
-+ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\dot{\Theta}_{br} =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))
-+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
+-3L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{bm}) + \cos(\Theta_{bb})\cos(\Theta_{bm})\Big)\dot{\Theta}_{bb}
+-3L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{bm}) + \cos(\Theta_{bm})\cos(\Theta_{bm})\Big)\dot{\Theta}_{bm}\\
++2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bm}) + \cos(\Theta_{fm})\cos(\Theta_{bm})\Big)\dot{\Theta}_{fm}
++ L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bm}) + \cos(\Theta_{fb})\cos(\Theta_{bm})\Big)\dot{\Theta}_{fb} =\\
+\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bm}))
++ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{bm}))
 \end{multline}
@@
 \begin{align}
-  B_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
+  B_1 &= -3L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{bm}) + \cos(\Theta_{bb})\cos(\Theta_{bm})\Big)\\
   B_2 &= -3L_{t}\\
-  B_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
-  B_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
-  X_2 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
-      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
+  B_3 &= +2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bm}) + \cos(\Theta_{fm})\cos(\Theta_{bm})\Big)\\
+  B_4 &= + L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bm}) + \cos(\Theta_{fb})\cos(\Theta_{bm})\Big)\\
+  X_2 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bm}))\\
+      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{bm}))
 \end{align}
@@
 \subsection{Solving for $C_1$, $C_2$, $C_3$, $C_4$ and $X_3$}
-Here we take Equations (\ref{eq:Cx}) and (\ref{eq:Cy}), equate them and manipulate them to be in form $ C_1\dot{\Theta}_{bl} + C_2 \dot{\Theta}_{ml} + C_3 \dot{\Theta}_{mr} + C_4 \dot{\Theta}_{br} = X_3$
+Here we take Equations (\ref{eq:Cx}) and (\ref{eq:Cy}), equate them and manipulate them to be in form $ C_1\dot{\Theta}_{bb} + C_2 \dot{\Theta}_{bm} + C_3 \dot{\Theta}_{fm} + C_4 \dot{\Theta}_{fb} = X_3$
 
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big) \frac{1}{(X_{mr} - X_{t })}
+-\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big) \frac{1}{(X_{fm} - X_{t })}
 \end{equation}
@@
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{mr} - Y_{t })}
+-\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
++ \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{fm} - Y_{t })}
 \end{equation}
@@
 \begin{multline}
-\Big( \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(-L_{t}\sin(\Theta_{mr})) = \\
-\Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(-L_{t}\cos(\Theta_{mr}))
+\Big( \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(-L_{t}\sin(\Theta_{fm})) = \\
+\Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
++ \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(-L_{t}\cos(\Theta_{fm}))
 \end{multline}
@@
 \begin{multline}
-\Big( \dot{X}_{t } + \dot{X}_{mr} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr}) +
-\Big(- R_{xmr} - \frac{1}{\gamma}F_{xmr} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr}) = \\
-\Big(\dot{Y}_{t } + \dot{Y}_{mr} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) +
-\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})
+\Big( \dot{X}_{t } + \dot{X}_{fm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm}) +
+\Big(- R_{xmr} - \frac{1}{\gamma}F_{xmr} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm}) = \\
+\Big(\dot{Y}_{t } + \dot{Y}_{fm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) +
+\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm})
 \end{multline}
@@
 \begin{multline}
-\Big( \dot{X}_{t } + \dot{X}_{mr} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr})
-+ \Big(-\dot{Y}_{t } - \dot{Y}_{mr} + L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) = \\
-\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})
-+ \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+\Big( \dot{X}_{t } + \dot{X}_{fm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm})
++ \Big(-\dot{Y}_{t } - \dot{Y}_{fm} + L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) = \\
+\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm})
++ \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
 \end{multline}
@@
 \begin{multline}
-\Big(- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + -L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} +
-L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} +L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr}) \\
-+ \Big(-(L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}) -(L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} -
-L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}) + L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) =\\
-\Big(-R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+\Big(- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + -L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} +
+L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} +L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm}) \\
++ \Big(-(L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}) -(L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} -
+L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}) + L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) =\\
+\Big(-R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
 \end{multline}
@@
 \begin{multline}
-\Big(-2L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 2L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
-+ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \Big)\sin(\Theta_{mr}) \\
-+ \Big(-2L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 2L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
-+ L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)\cos(\Theta_{mr}) =\\
-\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+\Big(-2L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 2L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}
++ L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm}) \\
++ \Big(-2L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 2L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}
++ L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) =\\
+\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
 \end{multline}
@@
 \begin{multline}
-\Big(-2L_{s}\sin(\Theta_{bl})\sin(\Theta_{mr})\dot{\Theta}_{bl} - 2L_{t}\sin(\Theta_{ml})\sin(\Theta_{mr})\dot{\Theta}_{ml}
-+ 2L_{t}\sin(\Theta_{mr})\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\sin(\Theta_{mr})\dot{\Theta}_{br} \Big)\\
-+ \Big(-2L_{s}\cos(\Theta_{bl})\cos(\Theta_{mr})\dot{\Theta}_{bl} - 2L_{t}\cos(\Theta_{ml})\cos(\Theta_{mr})\dot{\Theta}_{ml}
-+ 2L_{t}\cos(\Theta_{mr})\cos(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})\cos(\Theta_{mr})\dot{\Theta}_{br}\Big) =\\
-\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+\Big(-2L_{s}\sin(\Theta_{bb})\sin(\Theta_{fm})\dot{\Theta}_{bb} - 2L_{t}\sin(\Theta_{bm})\sin(\Theta_{fm})\dot{\Theta}_{bm}
++ 2L_{t}\sin(\Theta_{fm})\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\sin(\Theta_{fm})\dot{\Theta}_{fb} \Big)\\
++ \Big(-2L_{s}\cos(\Theta_{bb})\cos(\Theta_{fm})\dot{\Theta}_{bb} - 2L_{t}\cos(\Theta_{bm})\cos(\Theta_{fm})\dot{\Theta}_{bm}
++ 2L_{t}\cos(\Theta_{fm})\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\cos(\Theta_{fm})\dot{\Theta}_{fb}\Big) =\\
+\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
 \end{multline}
@@
 \begin{multline}
-- 2L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{mr}) + \cos(\Theta_{bl})\cos(\Theta_{mr})\Big)\dot{\Theta}_{bl}
-- 2L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{mr}) + \cos(\Theta_{ml})\cos(\Theta_{mr})\Big)\dot{\Theta}_{ml}\\
-+ 2L_{t}\Big(\sin^2(\Theta_{mr}) + \cos^2(\Theta_{mr})\Big)\dot{\Theta}_{mr}
-+ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big)\dot{\Theta}_{br} =\\
-\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+- 2L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{fm}) + \cos(\Theta_{bb})\cos(\Theta_{fm})\Big)\dot{\Theta}_{bb}
+- 2L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{fm}) + \cos(\Theta_{bm})\cos(\Theta_{fm})\Big)\dot{\Theta}_{bm}\\
++ 2L_{t}\Big(\sin^2(\Theta_{fm}) + \cos^2(\Theta_{fm})\Big)\dot{\Theta}_{fm}
++ L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{fm}) + \cos(\Theta_{fb})\cos(\Theta_{fm})\Big)\dot{\Theta}_{fb} =\\
+\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
++ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
 \end{multline}
@@
 \begin{align}
-  C_1 &= - 2L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{mr}) + \cos(\Theta_{bl})\cos(\Theta_{mr})\Big) \\
-  C_2 &= - 2L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{mr}) + \cos(\Theta_{ml})\cos(\Theta_{mr})\Big) \\
+  C_1 &= - 2L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{fm}) + \cos(\Theta_{bb})\cos(\Theta_{fm})\Big) \\
+  C_2 &= - 2L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{fm}) + \cos(\Theta_{bm})\cos(\Theta_{fm})\Big) \\
   C_3 &= 2L_{t} \\
-  C_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big) \\
-  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})\\
-      &+ \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
+  C_4 &= L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{fm}) + \cos(\Theta_{fb})\cos(\Theta_{fm})\Big) \\
+  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm})\\
+      &+ \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
 \end{align}
@@
 \subsection{Solving for $D_1$, $D_2$, $D_3$, $D_4$ and $X_4$}
-Here we take Equations (\ref{eq:Dx}) and (\ref{eq:Dy}), equate them and manipulate them to be in form $D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} = X_4$.
+Here we take Equations (\ref{eq:Dx}) and (\ref{eq:Dy}), equate them and manipulate them to be in form $D_1\dot{\Theta}_{bb} + D_2 \dot{\Theta}_{bm} + D_3 \dot{\Theta}_{fm} + D_4 \dot{\Theta}_{fb} = X_4$.
 
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rs} = \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) \frac{1}{(Y_{br} - Y_{mr})}
+-\frac{1}{\gamma}\lambda_{rs} = \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) \frac{1}{(Y_{fb} - Y_{fm})}
 \end{equation}
@@
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rs} = \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) \frac{1}{(X_{br} - X_{mr})}
+-\frac{1}{\gamma}\lambda_{rs} = \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) \frac{1}{(X_{fb} - X_{fm})}
 \end{equation}
@@
 \begin{equation}
-  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (X_{br} - X_{mr}) =
-  \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (Y_{br} - Y_{mr})
+  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (X_{fb} - X_{fm}) =
+  \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (Y_{fb} - Y_{fm})
 \end{equation}
@@
 \begin{equation}
-  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (-L_s\cos{\Theta_{br}}) =
-  \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (-L_s\sin{\Theta_{br}})
+  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (-L_s\cos{\Theta_{fb}}) =
+  \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (-L_s\sin{\Theta_{fb}})
 \end{equation}
@@
 \begin{equation}
-  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{br}}) =
-  \big( \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{br}})
+  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{fb}}) =
+  \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{fb}})
 \end{equation}
@@
 \begin{equation}
-  \big( \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\big)(\cos{\Theta_{br}}) + \big(-\dot{X}_{mr} - L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\big)(\sin{\Theta_{br}}) =
-  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{br}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{br}})
+  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\big)(\cos{\Theta_{fb}}) + \big(-\dot{X}_{fm} - L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\big)(\sin{\Theta_{fb}}) =
+  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{fb}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{fb}})
 \end{equation}
@@
 \begin{multline}
-  \big(L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\big)(\cos{\Theta_{br}})\\
-+ \big(L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\big)(\sin{\Theta_{br}}) = \\
-  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{br}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{br}})
+  \big(L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\big)(\cos{\Theta_{fb}})\\
++ \big(L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\big)(\sin{\Theta_{fb}}) = \\
+  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{fb}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{fb}})
 \end{multline}
@@
 \begin{multline}
-  L_{s}(\cos(\Theta_{br})\cos(\Theta_{bl}) + \sin(\Theta_{br})\sin(\Theta_{bl}))\dot{\Theta}_{bl}
-  + L_{t}(\cos(\Theta_{br})\cos(\Theta_{ml}) + \sin(\Theta_{br})\sin(\Theta_{ml}))\dot{\Theta}_{ml} \\
-  - L_{t}(\cos(\Theta_{br})\cos(\Theta_{mr}) + \sin(\Theta_{br})\sin(\Theta_{mr}))\dot{\Theta}_{mr}
-  - L_{s}(\cos^2(\Theta_{br}) + \sin^2(\Theta_{br}))\dot{\Theta}_{br} = \\
-  (R_{ybr} + \frac{1}{\gamma}F_{ybr}) (\cos{\Theta_{br}}) - (R_{xbr} + \frac{1}{\gamma}F_{xbr} ) (\sin{\Theta_{br}})
+  L_{s}(\cos(\Theta_{fb})\cos(\Theta_{bb}) + \sin(\Theta_{fb})\sin(\Theta_{bb}))\dot{\Theta}_{bb}
+  + L_{t}(\cos(\Theta_{fb})\cos(\Theta_{bm}) + \sin(\Theta_{fb})\sin(\Theta_{bm}))\dot{\Theta}_{bm} \\
+  - L_{t}(\cos(\Theta_{fb})\cos(\Theta_{fm}) + \sin(\Theta_{fb})\sin(\Theta_{fm}))\dot{\Theta}_{fm}
+  - L_{s}(\cos^2(\Theta_{fb}) + \sin^2(\Theta_{fb}))\dot{\Theta}_{fb} = \\
+  (R_{ybr} + \frac{1}{\gamma}F_{ybr}) (\cos{\Theta_{fb}}) - (R_{xbr} + \frac{1}{\gamma}F_{xbr} ) (\sin{\Theta_{fb}})
 \end{multline}
@@
 \begin{align}
-  D_1 &= L_{s}\Big(\cos(\Theta_{br})\cos(\Theta_{bl}) + \sin(\Theta_{br})\sin(\Theta_{bl})\Big)\\
-  D_2 &= L_{t}\Big(\cos(\Theta_{br})\cos(\Theta_{ml}) + \sin(\Theta_{br})\sin(\Theta_{ml})\Big)\\
-  D_3 &= -L_{t}\Big(\cos(\Theta_{br})\cos(\Theta_{mr}) + \sin(\Theta_{br})\sin(\Theta_{mr})\Big)\\
+  D_1 &= L_{s}\Big(\cos(\Theta_{fb})\cos(\Theta_{bb}) + \sin(\Theta_{fb})\sin(\Theta_{bb})\Big)\\
+  D_2 &= L_{t}\Big(\cos(\Theta_{fb})\cos(\Theta_{bm}) + \sin(\Theta_{fb})\sin(\Theta_{bm})\Big)\\
+  D_3 &= -L_{t}\Big(\cos(\Theta_{fb})\cos(\Theta_{fm}) + \sin(\Theta_{fb})\sin(\Theta_{fm})\Big)\\
   D_4 &= -L_{s}\\
-  X_4 &= (R_{ybr} + \frac{1}{\gamma}F_{ybr})\cos{\Theta_{br}} - (R_{xbr} + \frac{1}{\gamma}F_{xbr})\sin(\Theta_{br})
+  X_4 &= (R_{ybr} + \frac{1}{\gamma}F_{ybr})\cos{\Theta_{fb}} - (R_{xbr} + \frac{1}{\gamma}F_{xbr})\sin(\Theta_{fb})
 \end{align}
@@
   \begin{pmatrix}
-    \Theta_{bl} \\
-    \Theta_{ml} \\
-    \Theta_{mr} \\
-    \Theta_{br} \\
+    \Theta_{bb} \\
+    \Theta_{bm} \\
+    \Theta_{fm} \\
+    \Theta_{fb} \\
   \end{pmatrix}
@@
 \begin{align}
-\dot{\Theta}_{bl} &= \frac{N_{bl}}{D} \\
-\dot{\Theta}_{ml} &= \frac{N_{ml}}{D} \\
-\dot{\Theta}_{mr} &= \frac{N_{mr}}{D} \\
-\dot{\Theta}_{br} &= \frac{N_{br}}{D}
+\dot{\Theta}_{bb} &= \frac{N_{bb}}{D} \\
+\dot{\Theta}_{bm} &= \frac{N_{bm}}{D} \\
+\dot{\Theta}_{fm} &= \frac{N_{fm}}{D} \\
+\dot{\Theta}_{fb} &= \frac{N_{fb}}{D}
 \end{align}
@@
 \begin{multline}
-N_{bl} =
+N_{bb} =
 (-B_2 C_4 D_3 X_1 + B_2 C_3 D_4 X_1 + A_4 C_3 D_2 X_2 - A_3 C_4 D_2 X_2 - A_4 C_2 D_3 X_2 + A_2 C_4 D_3 X_2 +\\
@@
 \begin{multline}
-N_{ml} =
+N_{bm} =
 (B_1 C_4 D_3 X_1 - B_1 C_3 D_4 X_1 - A_4 C_3 D1 X_2 + A_3 C_4 D1 X_2 + A_4 C_1 D_3 X_2 - A_1 C_4 D_3 X_2 - \\
@@
 \begin{multline}
-N_{mr} =
+N_{fm} =
 (-B_1 C_4 D_2 X_1 + B_1 C_2 D_4 X_1 + A_4 C_2 D1 X_2 - A_2 C_4 D1 X_2 - A_4 C_1 D_2 X_2 + A_1 C_4 D_2 X_2 + \\
@@
 \begin{multline}
-N_{br} =
+N_{fb} =
 (B_1 C_3 D_2 X_1 - B_1 C_2 D_3 X_1 - A_3 C_2 D1 X_2 + A_2 C_3 D1 X_2 + A_3 C_1 D_2 X_2 - A_1 C_3 D_2 X_2 - \\

### 2015-09-12 dynein_struct.cpp

@@ -8,16 +8,16 @@ extern double dt;
 
 /* *********************************** DYNEIN FUNCTIONS ****************************************** */
 
-Dynein::Dynein(double bla_init, double mla_init, double mra_init, double bra_init,
+Dynein::Dynein(double bba_init, double bma_init, double fma_init, double fba_init,
                State s, forces *internal_test, forces *brownian_test, equilibrium_angles* eq_angles) {
-  blx = 0;
-  bly = 0;
+  bbx = 0;
+  bby = 0;
   mode = PRE_POWERSTROKE;
   
-  bla = bla_init;
-  mla = mla_init;
-  mra = mra_init;
-  bra = bra_init;
+  bba = bba_init;
+  bma = bma_init;
+  fma = fma_init;
+  fba = fba_init;
   
   state = s;
   internal_testcase = internal_test;
@@ -40,14 +40,14 @@ void Dynein::update_brownian_forces() {
   if (brownian_testcase) {
     r = *brownian_testcase; // just copy over forces!
   } else {
-    rand.gauss2(sqrt(2*kb*T/(gb*dt)), &r.blx, &r.bly);
-    rand.gauss2(sqrt(2*kb*T/(gm*dt)), &r.mlx, &r.mly);
+    rand.gauss2(sqrt(2*kb*T/(gb*dt)), &r.bbx, &r.bby);
+    rand.gauss2(sqrt(2*kb*T/(gm*dt)), &r.bmx, &r.bmy);
     rand.gauss2(sqrt(2*kb*T/(gt*dt)), &r.tx, &r.ty);
-    rand.gauss2(sqrt(2*kb*T/(gm*dt)), &r.mrx, &r.mry);
-    rand.gauss2(sqrt(2*kb*T/(gb*dt)), &r.brx, &r.bry);
+    rand.gauss2(sqrt(2*kb*T/(gm*dt)), &r.fmx, &r.fmy);
+    rand.gauss2(sqrt(2*kb*T/(gb*dt)), &r.fbx, &r.fby);
 
-    r.blx = 0;
-    r.bly = 0;
+    r.bbx = 0;
+    r.bby = 0;
   }
 }
 
[…]

### 2015-09-12 dynein_test.cpp

@@ -41,41 +41,41 @@ int main() {
 
   //runtime = 1*runtime;
 
-  double bla_eq = pre_powerstroke_leftbound_internal_angles.bla;
-  double la_eq  = pre_powerstroke_leftbound_internal_angles.la;
+  double bba_eq = pre_powerstroke_leftbound_internal_angles.bba;
+  double ba_eq  = pre_powerstroke_leftbound_internal_angles.ba;
   double ta_eq  = pre_powerstroke_leftbound_internal_angles.ta;
-  double ra_eq  = pre_powerstroke_leftbound_internal_angles.ra;
+  double fa_eq  = pre_powerstroke_leftbound_internal_angles.fa;
   
-  forces no_forces =    {0,0,0,0,0,0,0,0,0,0}; // blx, bly, mlx, mly, ...
+  forces no_forces =    {0,0,0,0,0,0,0,0,0,0}; // bbx, bby, bmx, bmy, ...
   forces right_forces = {1,0,1,0,1,0,1,0,1,0};
   forces left_forces =  {-1,0,-1,0,-1,0,-1,0,-1,0};
   forces up_forces =    {0,1,0,1,0,1,0,1,0,1};
   
   int num_failures = 0;
   {
-    Dynein* dyn = new Dynein(bla_eq,                                           // starting bla
-                             bla_eq + la_eq - M_PI,                            // starting mla
-                             bla_eq + la_eq - M_PI + ta_eq,                    // starting mra
-                             bla_eq + la_eq - M_PI + ta_eq + M_PI - ra_eq,     // starting bra
+    Dynein* dyn = new Dynein(bba_eq,                                           // starting bba
+                             bba_eq + ba_eq - M_PI,                            // starting bma
+                             bba_eq + ba_eq - M_PI + ta_eq,                    // starting fma
+                             bba_eq + ba_eq - M_PI + ta_eq + M_PI - fa_eq,     // starting fba
 			     LEFTBOUND,                                        // starting state
 			     &no_forces,                         // optional specified internal forces
 			     &no_forces,                         // optional specified brownian forces
[…]

### 2015-09-12 dynein_walk.cpp

@@ -15,43 +15,43 @@ double dt;
 void simulateProtein(Dynein* dyn, double dt, double tf) {
   double t = 0;
   
-  double temp_bla;
-  double temp_mla;
-  double temp_mra;
-  double temp_bra;
+  double temp_bba;
+  double temp_bma;
+  double temp_fma;
+  double temp_fba;
 
   srand(time(NULL));
   
   while( t < tf ) {
 
-    if (std::abs(dyn->get_bry()) < 0.1 && rand() % 2 == 0) {
-      double temp_brx = dyn->get_brx();
-      double temp_bry = dyn->get_bry();
-      double temp_bla = dyn->get_bla();
-      double temp_mla = dyn->get_mla();
-      double temp_mra = dyn->get_mra();
-      double temp_bra = dyn->get_bra();
-      dyn->set_blx(temp_brx);
-      dyn->set_bly(temp_bry);
-      dyn->set_bla(temp_bra);
-      dyn->set_mla(temp_mra);
-      dyn->set_mra(temp_mla);
-      dyn->set_bra(temp_bla);
+    if (std::abs(dyn->get_fby()) < 0.1 && rand() % 2 == 0) {
+      double temp_fbx = dyn->get_fbx();
+      double temp_fby = dyn->get_fby();
+      double temp_bba = dyn->get_bba();
+      double temp_bma = dyn->get_bma();
+      double temp_fma = dyn->get_fma();
+      double temp_fba = dyn->get_fba();
+      dyn->set_bbx(temp_fbx);
+      dyn->set_bby(temp_fby);
+      dyn->set_bba(temp_fba);
+      dyn->set_bma(temp_fma);
+      dyn->set_fma(temp_bma);
+      dyn->set_fba(temp_bba);
       if (dyn->get_state() == LEFTBOUND) dyn->set_state(RIGHTBOUND);
       else dyn->set_state(LEFTBOUND);
     }
     
     dyn->update_velocities();
     
-    temp_bla = dyn->get_bla() + dyn->get_d_bla() * dt;
-    temp_mla = dyn->get_mla() + dyn->get_d_mla() * dt;
-    temp_mra = dyn->get_mra() + dyn->get_d_mra() * dt;
-    temp_bra = dyn->get_bra() + dyn->get_d_bra() * dt;
+    temp_bba = dyn->get_bba() + dyn->get_d_bba() * dt;
+    temp_bma = dyn->get_bma() + dyn->get_d_bma() * dt;
[…]

### 2015-09-13 latex/derivation.tex
Add beginnings of bothbound solution to derivation.tex.

@@
   \dot{X}_{bb} &= 0 \\
-  \dot{X}_{bm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{bm} - X_{bb}) + \lambda_{lt}(X_{t } - X_{bm}) \Big) + R_{xml} \\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{bm}) + \lambda_{rt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
-  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{fm} - X_{t }) + \lambda_{rs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
-  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
+  \dot{X}_{bm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
+  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
+  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
 \end{align}
@@
   \dot{Y}_{bb} &= 0 \\
-  \dot{Y}_{bm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{bm} - Y_{bb}) + \lambda_{lt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
-  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{bm}) + \lambda_{rt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
-  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{fm} - Y_{t }) + \lambda_{rs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
+  \dot{Y}_{bm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
+  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
+  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
+  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
 \end{align}
@@
 \begin{align}
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } \\
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} \\
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr}
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
+  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
 \end{align}
@@
 \begin{align}
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } \\
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr}
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
+  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
 \end{align}
@@
 \begin{align}
-  L_{s}\sin(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
-  L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) - R_{xml} \\
-  L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) - R_{xt } \\
-  L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) - R_{xmr}
+  L_{s}\sin(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
+  L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) - R_{xml} \\
+  L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) - R_{xt } \\
+  L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) - R_{xmr}
 \end{align}
@@
 \begin{align}
-  \mn L_{s}\cos(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  \mn L_{t}\cos(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) - R_{yml}\\
-  \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) - R_{yt } \\
-  \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) - R_{ymr}
+  \mn L_{s}\cos(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  \mn L_{t}\cos(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) - R_{yml}\\
+  \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) - R_{yt } \\
+  \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) - R_{ymr}
 \end{align}
@@
 \begin{align}  
-  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } \\
-  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} \\
-  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr}
+  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
+  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
+  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
-  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr}
+  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
+  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
 \end{align}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) =
+\mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) =
 \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) =
+\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) =
 \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) =
+\mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) =
 \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) = 
+\mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) = 
 \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) =
+\mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) =
 \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) =
+\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) =
 \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) =
+\mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) =
 \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:Dy}
@@
 $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s.
-The above system of equations has four lambda terms: $\lambda_{ls}, \lambda_{lt}, \lambda_{rt}$ and $\lambda_{ls}$.
+The above system of equations has four lambda terms: $\lambda_{bs}, \lambda_{bt}, \lambda_{ft}$ and $\lambda_{bs}$.
 Each term is present in two equations.
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{ls} =
+\mn\frac{1}{\gamma}\lambda_{bs} =
 \Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{ls} =
+\mn\frac{1}{\gamma}\lambda_{bs} =
 \Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
@@
 \begin{multline}
--\frac{1}{\gamma}\lambda_{lt} =
+-\frac{1}{\gamma}\lambda_{bt} =
 \Big(
@@
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+-\frac{1}{\gamma}\lambda_{ft} = \Big( \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
 + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big) \frac{1}{(X_{fm} - X_{t })}
@@
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rt} = \Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
+-\frac{1}{\gamma}\lambda_{ft} = \Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
 + \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{fm} - Y_{t })}
@@
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rs} = \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) \frac{1}{(Y_{fb} - Y_{fm})}
+-\frac{1}{\gamma}\lambda_{fs} = \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) \frac{1}{(Y_{fb} - Y_{fm})}
 \end{equation}
@@
 \begin{equation}
--\frac{1}{\gamma}\lambda_{rs} = \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) \frac{1}{(X_{fb} - X_{fm})}
+-\frac{1}{\gamma}\lambda_{fs} = \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) \frac{1}{(X_{fb} - X_{fm})}
 \end{equation}
@@
 
+\clearpage
+{\huge Bothbound Solution} \\
+We now do a similar solution for velocities in the case where both of the model's binding domains are stuck to the microtubule.
+
+\section{Cartesian from Angular Coordinates}
+This section lays out the definitions of the coordinates of the Dynein model. \\
+\begin{align}
+  X_{b1} &= ?? \\
+  X_{m1} &= ?? \\
+  X_{t}  &= ?? \\
+  X_{m2} &= ?? \\
+  X_{b2} &= ??
+\end{align}
+
+\begin{align}
+  Y_{b1} &= ?? \\
+  Y_{m1} &= ?? \\
+  Y_{t}  &= ?? \\
+  Y_{m2} &= ?? \\
+  Y_{b2} &= ??
+\end{align}
+
+\section{Cartesian Velocities}
+This section shows the velocity definitions. \\
+\begin{align}
+  \dot{X}_{b1} &= ?? \\
+  \dot{X}_{m1} &= ?? \\
+  \dot{X}_{t } &= ?? \\
+  \dot{X}_{m2} &= ?? \\
+  \dot{X}_{b2} &= ??
+\end{align}
+
+\begin{align}                                                                          
+  \dot{Y}_{b1} &= ?? \\                                                        
+  \dot{Y}_{m1} &= ?? \\
+  \dot{Y}_{t}  &= ?? \\
+  \dot{Y}_{m2} &= ?? \\
+  \dot{Y}_{b2} &= ?? \\
+\end{align}
+
+\section{Cartesian Velocities (expanded)}
+This section expands the above definitions. \\
+\begin{align}
+  \dot{X}_{b1} &= ?? \\
+  \dot{X}_{m1} &= ?? \\
+  \dot{X}_{t } &= ?? \\
+  \dot{X}_{m2} &= ?? \\
+  \dot{X}_{b2} &= ?? \\
+\end{align}
+
+\begin{align}                                                                               
+  \dot{Y}_{b1} &= ?? \\
+  \dot{Y}_{m1} &= ?? \\
+  \dot{Y}_{t}  &= ?? \\
+  \dot{Y}_{m2} &= ?? \\
+  \dot{Y}_{b2} &= ?? \\
+\end{align}
+
+\section{Brownian Equations}
+This section shows the velocity definitions using the Brownian dynamics equation. \\
+\begin{align}  
+  \dot{X}_{b1} &= 0 \\
+  \dot{X}_{m1} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{m1} - X_{b1}) + \lambda_{bt}(X_{t } - X_{m1}) \Big) + R_{xml} \\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{m1}) + \lambda_{bt}(X_{m2} - X_{t }) \Big) + R_{xt } \\
+  \dot{X}_{m2} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{m2} - X_{t }) + \lambda_{fs}(X_{b2} - X_{m2}) \Big) + R_{xmr} \\
+  \dot{X}_{b2} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{b2} - X_{m2})                                 \Big) + R_{xbr}
+\end{align}
+
+\begin{align}  
+  \dot{Y}_{b1} &= 0 \\
+  \dot{Y}_{m1} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{m1} - Y_{b1}) + \lambda_{bt}(Y_{t } - Y_{m1}) \Big) + R_{yml} \\
+  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{m1}) + \lambda_{bt}(Y_{m2} - Y_{t }) \Big) + R_{yt } \\
+  \dot{Y}_{m2} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{m2} - Y_{t }) + \lambda_{fs}(Y_{b2} - Y_{m2}) \Big) + R_{ymr} \\
+  \dot{Y}_{b2} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{b2} - Y_{m2})                                 \Big) + R_{ybr}
+\end{align}
+
+\section{System of Equations}
+This section creates a system of equations by equating the Cartesian and Brownian velocity definitions from above. \\
+
+\begin{align}  
+  \dot{X}_{m1} &= \dot{X}_{b1} + \mn L_{s}\sin(\Theta_{b1})\dot{\Theta}_{b1} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{m1} - X_{b1}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) + \frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) + R_{xt } \\
+  \dot{X}_{m2} &= \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) + R_{xmr} \\
+  \dot{X}_{b2} &= \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) + R_{xbr}
+\end{align}
+
+\begin{align}  
+  \dot{Y}_{m1} &= \dot{Y}_{b1} + L_{s}\cos(\Theta_{b1})\dot{\Theta}_{b1} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{m1} - Y_{b1}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) + \frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{m2} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) + R_{ymr} \\
+  \dot{Y}_{b2} &= \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) + R_{ybr}
+\end{align}
+
+\section{System after Addition}
+By adding equations from our system together we can isolate the $\lambda$ values. This system has been verified via CAS.\\
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{bs}(X_{m1} - X_{b1}) =
+\dot{X}_{b1} + \mn L_{s}\sin(\Theta_{b1})\dot{\Theta}_{b1} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Ax}
+\end{multline}%Fix'd
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) =
+\dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Bx}
+\end{multline}%Fix'd
+
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) =
+\dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Cx}
+\end{equation}%Fix'd
+
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) = 
+\dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\label{eq:Dx}
+\end{equation}%Fix'd
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{bs}(Y_{m1} - Y_{b1}) =
+\dot{Y}_{b1} + L_{s}\cos(\Theta_{b1})\dot{\Theta}_{b1} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2}
++ \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:Ay}
+\end{multline}%Fix'd
+
+\begin{multline}
+\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) =
+\dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:By}
+\end{multline}%Fix'd
+
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) =
+\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2}
+- R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:Cy}
+\end{equation}%Fix'd
+
+\begin{equation}
+\mn\frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) = \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\label{eq:Dy}
+\end{equation}%Fix'd
+
 \begin{twocolumn}

### 2015-09-16 latex/derivation.tex
Make preparations for bothbound solution.
Add beginnings of bothbound derivation

@@
 
+\begin{figure}[h!]
+  \caption{Key lengths and angles in bothbound dynein model.}
+  \centering
+    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
+\end{figure}
+
+\section{Cartesian Coordinate Derivation}
+
+By the law of cosines:
+\begin{align}
+  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
+  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
+\end{align}
+
+Also by the law of cosines, we see that:
+\begin{align}
+  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
+  \Theta_{2} &= \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
+\end{align}
+
+We use these equations to solve for our nm (near motor) coordinates:
+
+\begin{align}
+  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
+     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
+     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
+  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
+     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
+     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
+\end{align}
+
+We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = ab - \sqrt{1-a^2}\sqrt{1-b^2}$$ and $$\sin\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = \sqrt{1-a^2}b+a\sqrt{1-b^2}$$ to simplify our expressions:
+
+\begin{align}
+  X_{nm} &= L_{s}*((\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}) - \sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
+  Y_{nm} &= L_{s}*(\sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})+(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
+\end{align}
+
 \section{Cartesian from Angular Coordinates}
@@
 \begin{align}
-  X_{b1} &= ?? \\
-  X_{m1} &= ?? \\
+  X_{b1} &= 0 \\
+  X_{m1} &= L_{s}*\cos(\Theta_{b1}) \\
   X_{t}  &= ?? \\
-  X_{m2} &= ?? \\
-  X_{b2} &= ??
+  X_{m2} &= L_{s}*\cos(\Theta_{b2}) \\
+  X_{b2} &= L \\
 \end{align}
@@
 \begin{align}
-  Y_{b1} &= ?? \\
-  Y_{m1} &= ?? \\
+  Y_{b1} &= 0 \\
+  Y_{m1} &= L_{s}*\sin(\Theta_{b1}) \\
   Y_{t}  &= ?? \\
-  Y_{m2} &= ?? \\
-  Y_{b2} &= ??
+  Y_{m2} &= L_{s}*\sin(\Theta_{b2}) \\
+  Y_{b2} &= 0
 \end{align}
@@
 \begin{align}
-  \dot{X}_{b1} &= ?? \\
-  \dot{X}_{m1} &= ?? \\
+  \dot{X}_{b1} &= 0 \\
+  \dot{X}_{m1} &= -L_{s}*\sin(\Theta_{b1})*\dot{\Theta}_{b1} \\
   \dot{X}_{t } &= ?? \\
-  \dot{X}_{m2} &= ?? \\
-  \dot{X}_{b2} &= ??
+  \dot{X}_{m2} &= -L_{s}*\sin(\Theta_{b2})*\dot{\Theta}_{b2} \\
+  \dot{X}_{b2} &= 0
 \end{align}
@@
 \begin{align}                                                                          
-  \dot{Y}_{b1} &= ?? \\                                                        
-  \dot{Y}_{m1} &= ?? \\
+  \dot{Y}_{b1} &= 0 \\                                         
+  \dot{Y}_{m1} &= L_{s}*\cos(\Theta_{b1})*\dot{\Theta}_{b1} \\
   \dot{Y}_{t}  &= ?? \\
-  \dot{Y}_{m2} &= ?? \\
-  \dot{Y}_{b2} &= ?? \\
-\end{align}
-
-\section{Cartesian Velocities (expanded)}
-This section expands the above definitions. \\
-\begin{align}
-  \dot{X}_{b1} &= ?? \\
-  \dot{X}_{m1} &= ?? \\
-  \dot{X}_{t } &= ?? \\
-  \dot{X}_{m2} &= ?? \\
-  \dot{X}_{b2} &= ?? \\
-\end{align}
-
-\begin{align}                                                                               
-  \dot{Y}_{b1} &= ?? \\
-  \dot{Y}_{m1} &= ?? \\
-  \dot{Y}_{t}  &= ?? \\
-  \dot{Y}_{m2} &= ?? \\
-  \dot{Y}_{b2} &= ?? \\
+  \dot{Y}_{m2} &= L_{s}*\cos(\Theta_{b2})*\dot{\Theta}_{b2} \\
+  \dot{Y}_{b2} &= 0 \\
 \end{align}

### 2015-09-16 latex/derivation.tex
Add changes to bothbound solution.

@@
 \begin{align}
-  X_{nm} &= L_{s}*((\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}) - \sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
-  Y_{nm} &= L_{s}*(\sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})+(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
+  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) - \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}+\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
 \end{align}
@@
 \begin{align}
-  X_{b1} &= 0 \\
-  X_{m1} &= L_{s}*\cos(\Theta_{b1}) \\
+  X_{nb} &= 0 \\
+  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
   X_{t}  &= ?? \\
-  X_{m2} &= L_{s}*\cos(\Theta_{b2}) \\
-  X_{b2} &= L \\
+  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
+  X_{fb} &= L \\
 \end{align}
@@
 \begin{align}
-  Y_{b1} &= 0 \\
-  Y_{m1} &= L_{s}*\sin(\Theta_{b1}) \\
+  Y_{nb} &= 0 \\
+  Y_{nm} &= L_{s}*\sin(\Theta_{nb}) \\
   Y_{t}  &= ?? \\
-  Y_{m2} &= L_{s}*\sin(\Theta_{b2}) \\
-  Y_{b2} &= 0
+  Y_{fm} &= L_{s}*\sin(\Theta_{fb}) \\
+  Y_{fb} &= 0
 \end{align}
@@
 \begin{align}
-  \dot{X}_{b1} &= 0 \\
-  \dot{X}_{m1} &= -L_{s}*\sin(\Theta_{b1})*\dot{\Theta}_{b1} \\
+  \dot{X}_{nb} &= 0 \\
+  \dot{X}_{nm} &= -L_{s}*\sin(\Theta_{nb})*\dot{\Theta}_{nb} \\
   \dot{X}_{t } &= ?? \\
-  \dot{X}_{m2} &= -L_{s}*\sin(\Theta_{b2})*\dot{\Theta}_{b2} \\
-  \dot{X}_{b2} &= 0
+  \dot{X}_{fm} &= -L_{s}*\sin(\Theta_{fb})*\dot{\Theta}_{fb} \\
+  \dot{X}_{fb} &= 0
 \end{align}
@@
 \begin{align}                                                                          
-  \dot{Y}_{b1} &= 0 \\                                         
-  \dot{Y}_{m1} &= L_{s}*\cos(\Theta_{b1})*\dot{\Theta}_{b1} \\
+  \dot{Y}_{nb} &= 0 \\                                         
+  \dot{Y}_{nm} &= L_{s}*\cos(\Theta_{nb})*\dot{\Theta}_{nb} \\
   \dot{Y}_{t}  &= ?? \\
-  \dot{Y}_{m2} &= L_{s}*\cos(\Theta_{b2})*\dot{\Theta}_{b2} \\
-  \dot{Y}_{b2} &= 0 \\
+  \dot{Y}_{fm} &= L_{s}*\cos(\Theta_{fb})*\dot{\Theta}_{fb} \\
+  \dot{Y}_{fb} &= 0 \\
 \end{align}
@@
 \begin{align}  
-  \dot{X}_{b1} &= 0 \\
-  \dot{X}_{m1} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{m1} - X_{b1}) + \lambda_{bt}(X_{t } - X_{m1}) \Big) + R_{xml} \\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{m1}) + \lambda_{bt}(X_{m2} - X_{t }) \Big) + R_{xt } \\
-  \dot{X}_{m2} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{m2} - X_{t }) + \lambda_{fs}(X_{b2} - X_{m2}) \Big) + R_{xmr} \\
-  \dot{X}_{b2} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{b2} - X_{m2})                                 \Big) + R_{xbr}
+  \dot{X}_{nb} &= 0 \\
+  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{nm}) + \lambda_{bt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
+  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
+  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{b1} &= 0 \\
-  \dot{Y}_{m1} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{m1} - Y_{b1}) + \lambda_{bt}(Y_{t } - Y_{m1}) \Big) + R_{yml} \\
-  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{m1}) + \lambda_{bt}(Y_{m2} - Y_{t }) \Big) + R_{yt } \\
-  \dot{Y}_{m2} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{m2} - Y_{t }) + \lambda_{fs}(Y_{b2} - Y_{m2}) \Big) + R_{ymr} \\
-  \dot{Y}_{b2} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{b2} - Y_{m2})                                 \Big) + R_{ybr}
+  \dot{Y}_{nb} &= 0 \\
+  \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
+  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{nm}) + \lambda_{bt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
+  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
+  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
 \end{align}
@@
 \begin{align}  
-  \dot{X}_{m1} &= \dot{X}_{b1} + \mn L_{s}\sin(\Theta_{b1})\dot{\Theta}_{b1} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{m1} - X_{b1}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) + \frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) + R_{xt } \\
-  \dot{X}_{m2} &= \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) + R_{xmr} \\
-  \dot{X}_{b2} &= \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) + R_{xbr}
+  \dot{X}_{nm} &= \dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + \frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + R_{xt } \\
+  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
+  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{m1} &= \dot{Y}_{b1} + L_{s}\cos(\Theta_{b1})\dot{\Theta}_{b1} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{m1} - Y_{b1}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) + \frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{m2} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) + R_{ymr} \\
-  \dot{Y}_{b2} &= \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) + R_{ybr}
+  \dot{Y}_{nm} &= \dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + \frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
+  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
 \end{align}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs}(X_{m1} - X_{b1}) =
-\dot{X}_{b1} + \mn L_{s}\sin(\Theta_{b1})\dot{\Theta}_{b1} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) =
+\dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } \\
+- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
+-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Ax}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) =
-\dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) =
+\dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
+- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Bx}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) =
-\dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) =
+\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
++ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Cx}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) = 
-\dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
+\mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) = 
+\dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
 \label{eq:Dx}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs}(Y_{m1} - Y_{b1}) =
-\dot{Y}_{b1} + L_{s}\cos(\Theta_{b1})\dot{\Theta}_{b1} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2}
-+ \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) =
+\dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} \\
+- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
++ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:Ay}
@@
 \begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) =
-\dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) =
+\dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
+- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:By}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) =
-\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2}
+\mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) =
+\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 - R_{ybr} - \frac{1}{\gamma}F_{ybr}
@@
 \begin{equation}
-\mn\frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) = \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
+\mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
 \label{eq:Dy}

### 2015-09-18 latex/derivation.tex
Adding changes to the bothbound solution.

@@
 
+Also by the law of cosines, we can see that:
+
+\begin{equation}
+   \Theta_{1} = \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})
+\end{equation}
+
+We use this to find the value of $X_{t}$ and $Y_{t}$:
+
+\begin{align}
+  X_{t} &= L_n\cos(\Theta_{1}) \\
+       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
+       &= \frac{L^2 + L_s^2 + L_t^2 - 2L_tL_s\cos(\Theta_{nm}) - L_s^2 - L_t^2 + 2L_sL_t\cos(\Theta_{fm})}{2L} \\
+       &= \frac{L^2 + 2L_tL_s\big(\cos(\Theta_{fm})-\cos(\Theta_{nm})\big)}{2L}
+\end{align}
+
+and
+
+\begin{align}
+  Y_{t} &= L_n\sin(\Theta_{1}) \\
+        &=
+\end{align}
+
+This is getting ugly and complicated. I will not do it. I will do it when I need to. \\
 \section{Cartesian from Angular Coordinates}
@@
 \begin{align}  
-  \dot{X}_{nb} &= 0 \\
+  \dot{X}_{nb} &= \frac{1}{\gamma} \Big(F_{xnb} + \lambda_{fs}(X_{nm} - X_{nb})\Big) + R_{xnb} \\
   \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
@@
   \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
-  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
+  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})\Big) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{nb} &= 0 \\
+  \dot{Y}_{nb} &= \frac{1}{\gamma} \Big(F_{ynb} + \lambda_{fs}(Y_{nm} - Y_{nb})\Big) + R_{ynb} \\
   \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
@@
   \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
+  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})\Big) + R_{ybr}
 \end{align}

### 2015-09-18 dynein_walk.cpp

@@ -19,27 +19,8 @@ void simulateProtein(Dynein* dyn, double dt, double tf) {
   double temp_bma;
   double temp_fma;
   double temp_fba;
-
-  srand(time(NULL));
   
   while( t < tf ) {
-
-    if (std::abs(dyn->get_fby()) < 0.1 && rand() % 2 == 0) {
-      double temp_fbx = dyn->get_fbx();
-      double temp_fby = dyn->get_fby();
-      double temp_bba = dyn->get_bba();
-      double temp_bma = dyn->get_bma();
-      double temp_fma = dyn->get_fma();
-      double temp_fba = dyn->get_fba();
-      dyn->set_bbx(temp_fbx);
-      dyn->set_bby(temp_fby);
-      dyn->set_bba(temp_fba);
-      dyn->set_bma(temp_fma);
-      dyn->set_fma(temp_bma);
-      dyn->set_fba(temp_bba);
-      if (dyn->get_state() == LEFTBOUND) dyn->set_state(RIGHTBOUND);
-      else dyn->set_state(LEFTBOUND);
-    }
     
     dyn->update_velocities();
     

### 2015-09-23 dynein_struct.cpp
Slight change to derivation.tex.

@@ -28,7 +28,7 @@ Dynein::Dynein(double bba_init, double bma_init, double fma_init, double fba_ini
   } else if (state == NEARBOUND or state == FARBOUND) {
     eq = near_farbound_post_powerstroke_internal_angles;
   }
-
+  
   update_velocities();
 }
 

### 2015-09-29 latex/derivation.tex
Slight change to derivation.tex.
Add work to derivation.tex.

@@
 
-Also by the law of cosines, we can see that:
+We can also use the law of cosines to find an expression for $\Theta_{1}$:
 
-\begin{equation}
-   \Theta_{1} = \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})
-\end{equation}
+\begin{align}
+   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
+   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
+\end{align}
 
-We use this to find the value of $X_{t}$ and $Y_{t}$:
+We use this to find the value of $X_{t}$:
 
@@
 
-and
+To find $Y_{t}$ we do something similar:
 
 \begin{align}
+  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
   Y_{t} &= L_n\sin(\Theta_{1}) \\
-        &=
+       &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
+       &= L_n\sqrt{1 - (\frac{L^2+L_n^2-L_f^2}{2LL_n})^2} \\
 \end{align}
 
-This is getting ugly and complicated. I will not do it. I will do it when I need to. \\
 \section{Cartesian from Angular Coordinates}

### 2015-09-29 latex/derivation.tex
changes from our meeting

@@
   \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
-  \Theta_{2} &= \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
+  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
 \end{align}
@@
      L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
-     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
+     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
   Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
      L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
-     + \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
+     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
 \end{align}
 
-We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = ab - \sqrt{1-a^2}\sqrt{1-b^2}$$ and $$\sin\Big(cos^{-1}(a)+cos^{-1}(b)\Big) = \sqrt{1-a^2}b+a\sqrt{1-b^2}$$ to simplify our expressions:
+We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
+cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
+and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:
 

### 2015-09-29 dynein_struct.cpp

@@ -220,15 +220,16 @@ void Dynein::update_velocities_bothbound() {
   // To be implemented
 }
 
-double Dynein::get_binding_probability() {
+double Dynein::get_binding_rate() {
   if (get_fby() < MICROTUBULE_BINDING_DISTANCE) {
-    return 0.01;
+    double bound_energy = 0.5*cb*square(fba - eq.bba);
+    return 1e10*exp(-bound_energy/kb/T); // per second
   } else {
     return 0;
   }
 }
 
-double Dynein::get_unbinding_probability() {
+double Dynein::get_unbinding_rate() {
   if (f.bby + r.bby >= UNBINDING_FORCE) { // bad, doesn't take into account forces on other domains
     printf("unbinding...\n");
     return 1.0;

### 2015-09-29 dynein_walk.cpp

@@ -23,11 +23,11 @@ void simulateProtein(Dynein* dyn, double tf) {
   FILE* data_file = fopen("data.txt", "a+");
   
   while( t < tf ) {
-    if (dyn->rand->rand() < dyn->get_unbinding_probability()) {
+    if (dyn->rand->rand() < dyn->get_unbinding_rate()*dt) {
         dyn->unbind();
 	dyn->log(t, data_file);
 	exit(EXIT_SUCCESS);
-    } else if (dyn->rand->rand() < dyn->get_binding_probability()) {
+    } else if (dyn->rand->rand() < dyn->get_binding_rate()*dt) {
         dyn->switch_to_bothbound();
     }
     

### 2015-09-29 plot.py

@@ -41,6 +41,7 @@ ax.set_xlim(-40,40)
 ax.set_ylim(-40,40)
 
 microtubule = plt.plot([-400, 400], [-2, -2])
+plt.xlabel('$x$ (nm)')
 plt.setp(microtubule, color='c', alpha=0.8, linewidth=17.0)
 
 stalk1, = plt.plot([ X[0], X[1] ], [ Y[0], Y[1] ], color="black")

### 2015-09-29 latex/derivation.tex
Start of work on derivation.tex

@@
 \begin{align}
-  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) - \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
-  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}+\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+\end{align}
+
+We simplify...
+
+\begin{align}
+  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\Big) \mp \sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
+  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2L}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
+\end{align}
+
+We then expand $L_{n}$...
+
+\begin{align}
+  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\Big)\Big(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\Big) \mp \\
+  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
+  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2} \pm \\
+  & \frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
 \end{align}

### 2015-09-30 latex/derivation.tex
Simplify cartesian motor solutions. Next step: further simplification and verification.

@@
 
-We then expand $L_{n}$...
+We then expand $L_{n}^2$...
 
@@
   & \frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
+\end{align}
+
+and $L_{f}^2$...
+
+\begin{align}
+  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\Big)\Big(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\Big) \mp \\
+  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\bigg)^2}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
+  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\bigg)^2} \pm \\
+  & \frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
+\end{align}
+
+We then do some simplification...
+
+\begin{align}
+  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\Big)\Big(2L_{s}-L_{t}\cos(\Theta_{nm})\Big) \mp \\
+  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2}\sqrt{L_{t}^2-L_{t}^2\cos^2(\Theta_{nm})} \Bigg) \\
+  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(L_{s}-L_{t}\cos(\Theta_{nm})\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \pm \\
+  & \frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\sqrt{L_{t}^2-L_{t}^2\cos^2(\Theta_{nm})} \Bigg) \\
+\end{align}
+
+And even more simplification...
+
+\begin{align}
+  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\Big)\Big(2L_{s}-L_{t}\cos(\Theta_{nm})\Big) \mp \\
+  & L_{t}\sin(\Theta_{nm})\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \Bigg) \\
+  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg((L_{s}-L_{t}\cos(\Theta_{nm}))\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \pm \\
+  & \frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}L_{t}\sin(\Theta_{nm}) \Bigg) \\
 \end{align}

### 2015-10-06 latex/derivation.tex
Add little more to d4erivation.

@@
 
+We then combine terms and make the equations messier (TODO: Finish this part):
+
+\begin{multline}
+  X_{nm} = \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{2L^2L_s - L^2L_t\cos(\Theta_{nm}) + 4L_{t}L_{s}^2(\cos(\Theta_{fm})-\cos(\Theta_{nm})) - 2L_{t}^2L_{s}(\cos(\Theta_{fm})\cos(\Theta_{nm}) - \cos^2(\Theta_{nm}))}{2L}\Big) \mp \\
+\hspace*{-2 cm}  L_{t}\sin(\Theta_{nm})\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s} \cos(\Theta_{nm})-\bigg(
+    \frac{L^2+4L_{t}^2L_{s}^2\cos^2(\Theta_{fm})+ 4L_{t}^2L_{s}^2\cos^2(\Theta_{nm}) - 8L_{t}^2L_{s}^2\cos(\Theta_{fm})\cos(\Theta_{nm}) + 4L^2L_{t}L_{s}\cos(\Theta_{fm}) - 4L^2L_{t}L_{s}\cos(\Theta_{nm})}{2L}\bigg)} \Bigg) \\
+  Y_{nm} = \frac{L_{s}}{L_{n}}\Bigg((L_{s}-L_{t}\cos(\Theta_{nm}))\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \pm \\
+   \frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}L_{t}\sin(\Theta_{nm}) \Bigg) \\
+\end{multline}
+
 We can also use the law of cosines to find an expression for $\Theta_{1}$:
@@
   &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
-       &= L_n\sqrt{1 - (\frac{L^2+L_n^2-L_f^2}{2LL_n})^2} \\
+  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
+  &= L_n\sqrt{1 - (\frac{(L^2 + L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm}) - (L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})))^2}{4L^2L_n^2})} \\
+  &= L_n\sqrt{1 - (\frac{(L^2 - 2L_{t}L_{s}(\cos(\Theta_{fm}) - \cos(\Theta_{nm})))^2}{4L^2L_n^2})} \\
+  &= L_n\sqrt{1 - (\frac{(L^4 + 4L_{t}^2L_{s}^2(\cos^2(\Theta_{fm}) + \cos^2(\Theta_{nm}) - 2\cos(\Theta_{fm})\cos(\Theta_{nm})) - 4L^2L_{t}L_{s}(\cos(\Theta_{fm}) - \cos(\Theta_{nm})))}{4L^2(L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm}))})} \\
 \end{align}

### 2015-10-11 latex/derivation.tex
New cartesian solving strategy: simplify up to Ln/Lf in Latex, solve for actual angles in C.

--- 2015-09-29 latex/derivation.tex
@@
 
+We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\
+
 Also by the law of cosines, we see that:
@@
 
-We then expand $L_{n}$...
-
-\begin{align}
-  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\Big)\Big(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\Big) \mp \\
-  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
-  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2} \pm \\
-  & \frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
-\end{align}
-
 We can also use the law of cosines to find an expression for $\Theta_{1}$:
@@
        &= \frac{L^2+L_n^2-L_f^2}{2L} \\
-       &= \frac{L^2 + L_s^2 + L_t^2 - 2L_tL_s\cos(\Theta_{nm}) - L_s^2 - L_t^2 + 2L_sL_t\cos(\Theta_{fm})}{2L} \\
-       &= \frac{L^2 + 2L_tL_s\big(\cos(\Theta_{fm})-\cos(\Theta_{nm})\big)}{2L}
 \end{align}
@@
   &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
-       &= L_n\sqrt{1 - (\frac{L^2+L_n^2-L_f^2}{2LL_n})^2} \\
+  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
 \end{align}
@@
   X_{nb} &= 0 \\
-  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
-  X_{t}  &= ?? \\
-  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
+  X_{nm} &=  \\
+  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
+  X_{fm} &=  \\
   X_{fb} &= L \\
@@
   Y_{nb} &= 0 \\
-  Y_{nm} &= L_{s}*\sin(\Theta_{nb}) \\
-  Y_{t}  &= ?? \\
-  Y_{fm} &= L_{s}*\sin(\Theta_{fb}) \\
+  Y_{nm} &=  \\
+  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
+  Y_{fm} &=  \\
   Y_{fb} &= 0
@@
   \dot{X}_{nb} &= 0 \\
-  \dot{X}_{nm} &= -L_{s}*\sin(\Theta_{nb})*\dot{\Theta}_{nb} \\
-  \dot{X}_{t } &= ?? \\
-  \dot{X}_{fm} &= -L_{s}*\sin(\Theta_{fb})*\dot{\Theta}_{fb} \\
+  \dot{X}_{nm} &= \\
+  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
+  \dot{X}_{fm} &= \\
   \dot{X}_{fb} &= 0
@@
   \dot{Y}_{nb} &= 0 \\                                         
-  \dot{Y}_{nm} &= L_{s}*\cos(\Theta_{nb})*\dot{\Theta}_{nb} \\
-  \dot{Y}_{t}  &= ?? \\
-  \dot{Y}_{fm} &= L_{s}*\cos(\Theta_{fb})*\dot{\Theta}_{fb} \\
+  \dot{Y}_{nm} &= \\
+  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
+  \dot{Y}_{fm} &= \\
   \dot{Y}_{fb} &= 0 \\

### 2015-10-23 latex/derivation.tex
Add one derivative to latex derivation.

@@
 
-We simplify...
+We simplify further...
 
 \begin{align}
-  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\Big) \mp \sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
-  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2L}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
+  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
 \end{align}
+
+\begin{align}
+  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
+\end{align}
+
+Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
+
+\begin{align}
+  \dot{X}_{nm} =
+  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
+   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
+   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
+   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
+   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
+   \text{Ln}(t)^2}\right)}{2
+   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
+   \text{Ln}(t)^2}}} - \\
+  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
+   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
+   \text{Ln}(t)^3}\\
+  &-\frac{\text{Ls}
+   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
+   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
+   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
+   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
+   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
+       \text{Ln}(t)^2}}}\\
+  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
+   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
+   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
+   \text{Ln}(t)^2}
+\end{align}
+
+This is becoming really ugly!
+I think I want to try another thing.
+Tomorrow I'll try and implement a different angle scheme and see if it works out easier...this is not tenable.
+The advantage to this scheme is that it avoids ambiguity, but it is also really really complicated.
+And even this model has ambiguity in that certain angles could have positive/negative values, so the C code will have to have memory and guess which value is correct.
+So I think it would be good to choose a simpler ambiguous model and code in ambiguity-resolution to the C code.\\
 
@@
 
-\section{Brownian Equations}
-This section shows the velocity definitions using the Brownian dynamics equation. \\
-\begin{align}  
-  \dot{X}_{nb} &= \frac{1}{\gamma} \Big(F_{xnb} + \lambda_{fs}(X_{nm} - X_{nb})\Big) + R_{xnb} \\
-  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{nm}) + \lambda_{bt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
-  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
-  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})\Big) + R_{xbr}
-\end{align}
-
-\begin{align}  
-  \dot{Y}_{nb} &= \frac{1}{\gamma} \Big(F_{ynb} + \lambda_{fs}(Y_{nm} - Y_{nb})\Big) + R_{ynb} \\
-  \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
-  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{nm}) + \lambda_{bt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
-  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})\Big) + R_{ybr}
-\end{align}
-
-\section{System of Equations}
-This section creates a system of equations by equating the Cartesian and Brownian velocity definitions from above. \\
-
-\begin{align}
-  \dot{X}_{nm} &= \dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + \frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + R_{xt } \\
-  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
-  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
-\end{align}
-
-\begin{align}  
-  \dot{Y}_{nm} &= \dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + \frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
-  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
-\end{align}
-
-\section{System after Addition}
-By adding equations from our system together we can isolate the $\lambda$ values. This system has been verified via CAS.\\
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) =
-\dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Ax}
-\end{multline}%Fix'd
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) =
-\dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Bx}
-\end{multline}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) =
-\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Cx}
-\end{equation}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) = 
-\dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Dx}
-\end{equation}%Fix'd
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) =
-\dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
-+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:Ay}
-\end{multline}%Fix'd
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) =
-\dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:By}
-\end{multline}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) =
-\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-- R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:Cy}
-\end{equation}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:Dy}
-\end{equation}%Fix'd
-
 \begin{twocolumn}

### 2015-10-25 latex/derivation.tex
Change bothbound angle schemes and add lots of stuff to derivation.tex. Make sure to check if the Xt/Yt derivatives are right.

@@
 \usepackage{verbatim}
+
+\allowdisplaybreaks
 
@@
 
-\begin{figure}[h!]
-  \caption{Key lengths and angles in bothbound dynein model.}
-  \centering
-    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
-\end{figure}
+%% \begin{figure}[h!]
+%%   \caption{Key lengths and angles in bothbound dynein model.}
+%%   \centering
+%%     \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
+%% \end{figure}
 
-\section{Cartesian Coordinate Derivation}
+\section{Derivation of bothbound tail coordinates}
 
-By the law of cosines:
-\begin{align}
-  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
-  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
-\end{align}
+\begin{align*}
+  \theta_1 &= \cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right)\\
+  \theta_2 &= \cos^{-1}\left(\frac{L}{2L_t}\right)\\
+  L &= \sqrt{(X_{fm}-X_{nm})^2+(Y_{fm}-Y_{nm})^2}\\
+\end{align*}
 
-We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\
+\subsection{$X_t$}
+\begin{align*}
+  X_t &= X_{nm} + L_t\cos(\theta_1 \pm \theta_2)\\
+  &= X_{nm} + L_t\cos\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
+  \hspace*{1in} \cos\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}\\
+  &= X_{nm} + L_t\left(\frac{X_{fm}-X_{nm}}{2L_t} \mp \sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{1 - \frac{L^2}{4L_t^2}}\right)\\
+  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{4L_t - L^2}\\
+  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2L}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2}\sqrt{4L_t - L^2}\\
+  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
+  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
+  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
+  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
+  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))(L_s\cos(\theta_{nb})) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
+  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
+  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
+  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+\end{align*}
 
-Also by the law of cosines, we see that:
-\begin{align}
-  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
-  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
-\end{align}
-
-We use these equations to solve for our nm (near motor) coordinates:
-
-\begin{align}
-  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
-     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
-     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
-  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
-     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
-     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
-\end{align}
-
-We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
-cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
-and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:
-
-\begin{align}
-  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
-  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
-\end{align}
-
-We simplify further...
-
-\begin{align}
-  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-\end{align}
-
-\begin{align}
-  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-\end{align}
-
-Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
-
-\begin{align}
-  \dot{X}_{nm} =
-  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
-   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
-   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
-   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
-   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
-   \text{Ln}(t)^2}\right)}{2
-   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
-   \text{Ln}(t)^2}}} - \\
-  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
-   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
-   \text{Ln}(t)^3}\\
-  &-\frac{\text{Ls}
-   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
-   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
-   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
-   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
-   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
-       \text{Ln}(t)^2}}}\\
-  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
-   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
-   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
-   \text{Ln}(t)^2}
-\end{align}
-
-This is becoming really ugly!
-I think I want to try another thing.
-Tomorrow I'll try and implement a different angle scheme and see if it works out easier...this is not tenable.
-The advantage to this scheme is that it avoids ambiguity, but it is also really really complicated.
-And even this model has ambiguity in that certain angles could have positive/negative values, so the C code will have to have memory and guess which value is correct.
-So I think it would be good to choose a simpler ambiguous model and code in ambiguity-resolution to the C code.\\
-
-We can also use the law of cosines to find an expression for $\Theta_{1}$:
-
-\begin{align}
-   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
-   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
-\end{align}
-
-We use this to find the value of $X_{t}$:
-
-\begin{align}
-  X_{t} &= L_n\cos(\Theta_{1}) \\
-       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
-\end{align}
-
-To find $Y_{t}$ we do something similar:
-
-\begin{align}
-  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
-  Y_{t} &= L_n\sin(\Theta_{1}) \\
-  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
-  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
-\end{align}
+\subsection{$Y_t$}
+\begin{align*}
+  Y_t &= Y_{nm} + L_t\sin(\theta_1 \pm \theta_2)\\
+  &= Y_{nm} + L_t\sin\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
+  \hspace*{1in} \sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}\\
+  &= Y_{nm} + L_t\left(\frac{L}{2L_t}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{L}\sqrt{1 - \frac{L^2}{4L^2_t}}\right)\\
+  &= Y_{nm} + \frac{L}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{2L}\sqrt{4L_t^2 - L^2}\\
+  &= Y_{nm} + \frac{1}{2}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{L^2} - 1}\\
+  &= Y_{nm} + \frac{1}{2}\sqrt{\left(Y_{fm}-Y_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
+  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
+  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} - 1}\\
+  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
+  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
+  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
+  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
+  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+\end{align*}
 
 \section{Cartesian from Angular Coordinates}
-This section lays out the definitions of the coordinates of the Dynein model. \\
+This section lays out the definitions of the coordinates of the bothbound Dynein model.\\
 \begin{align}
-  X_{nb} &= 0 \\
-  X_{nm} &=  \\
-  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
-  X_{fm} &=  \\
-  X_{fb} &= L \\
+  X_{nb} &= 0\\
+  X_{nm} &= L_s\cos(\theta_{nb})\\
+  X_{t}  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+  X_{fm} &= B + L_s\cos(\theta_{fb})\\
+  X_{fb} &= B \\
 \end{align}
@@
   Y_{nb} &= 0 \\
-  Y_{nm} &=  \\
-  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
-  Y_{fm} &=  \\
-  Y_{fb} &= 0
+  Y_{nm} &= L_s\sin(\theta_{nb})\\
+  Y_{t}  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  Y_{fm} &= L_s\sin(\theta_{fb})\\
+  Y_{fb} &= 0\\
 \end{align}
@@
   \dot{X}_{nb} &= 0 \\
-  \dot{X}_{nm} &= \\
-  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
-  \dot{X}_{fm} &= \\
+  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
+  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + -L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+  &\pm \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2} \left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
+  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\
   \dot{X}_{fb} &= 0
@@
   \dot{Y}_{nb} &= 0 \\                                 
-  \dot{Y}_{nm} &= \\
-  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
-  \dot{Y}_{fm} &= \\
+  \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb}\\
+  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\pm \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1} \\
+ &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}-BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
+  \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb}\\
   \dot{Y}_{fb} &= 0 \\

### 2015-10-25 latex/derivation.tex
Add small redo of Xt derivative.

@@
   &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+  \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
+  &\mp \frac{d}{dt} \left(\frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+  &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{d}{dt} \left(\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\right)\\
+   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
+  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{1}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right) *\\
+   &\left(\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right) *\\
+   &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)\\
+   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
+  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{\left(\frac{-4L_t^2\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right)\\
 \end{align*}

### 2015-10-27 latex/derivation.tex
Add work on derivation.tex X/Y_t derivatives.

@@
   &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
-  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
+  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
   &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
@@
    &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)\\
-   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
-  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{\left(\frac{-4L_t^2\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right)\\
+   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+   &\pm \frac{L_{t}^2\left(L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
 \end{align*}
@@
   &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
-  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
+  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
   &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
-  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
-  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
+  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  \dot{Y}_t &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\\
+  &\pm \frac{d}{dt}\left(\frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} \frac{d}{dt}\left(\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\right)\\
+  \dot{Y}_t &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\\
+  &\pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} \left(\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\right)*\\
+  &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)\\\\
+  \dot{Y}_t &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2} \pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\mp \frac{L_t^2\left(B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
 \end{align*}
@@
   \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
-  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + -L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-  &\pm \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2} \left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
+  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+   &\pm \frac{L_{t}^2\left(L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
   \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\

### 2015-10-27 latex/derivation.tex
Add system of equations (with addition to eliminate lambda forces) to bothbound solution.

@@
   Y_{nm} &= L_s\sin(\theta_{nb})\\
-  Y_{t}  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  Y_{t}  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
   Y_{fm} &= L_s\sin(\theta_{fb})\\
@@
   \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb}\\
-  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\pm \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1} \\
- &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}-BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
+  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2} \pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\mp \frac{L_t^2\left(B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
   \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb}\\
   \dot{Y}_{fb} &= 0 \\
+\end{align}
+
+\section{System of Equations}
+
+\begin{align}
+  \dot{X}_{nb} &= 0 = \frac{1}{\gamma}F_{xnb} + \frac{1}{\gamma}\lambda_{ns}(X_{nm} - X_{nb}) + R_{xnb} \\
+  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb} = \frac{1}{\gamma}F_{xnm} + \mn\frac{1}{\gamma}\lambda_{ns}(X_{nm} - X_{nb}) + \frac{1}{\gamma}\lambda_{nt}(X_{t } - X_{nm}) + R_{xnm} \\
+  \dot{X}_{t}  &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+   &\pm \frac{L_{t}^2\left(L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\ &= \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{nt}(X_{t } - X_{nm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
+  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb} = \frac{1}{\gamma}F_{xfm} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xfm} \\
+  \dot{X}_{fb} &= 0 = \frac{1}{\gamma}F_{xfb} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xfb}
+\end{align}
+
+\begin{align}
+  \dot{Y}_{nb} &= 0 = \frac{1}{\gamma}F_{ynb} + \frac{1}{\gamma}\lambda_{ns}(Y_{nm} - Y_{nb}) + R_{ynb} \\
+  \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb} = \frac{1}{\gamma}F_{ynm} + \mn\frac{1}{\gamma}\lambda_{ns}(Y_{nm} - Y_{nb}) + \frac{1}{\gamma}\lambda_{nt}(Y_{t } - Y_{nm}) + R_{ynm} \\
+  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2} \pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\mp \frac{L_t^2\left(B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\ &= \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{nt}(Y_{t } - Y_{nm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb} = \frac{1}{\gamma}F_{yfm} + \mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{yfm} \\
+  \dot{Y}_{fb} &= 0 = \frac{1}{\gamma}F_{yfb} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{yfb}
+\end{align} \\ \\
+
+\section{System After Addition?}
+
+\begin{align}
+  \dot{X}_{nb} &= 0 = \frac{1}{\gamma}F_{xnb} + \frac{1}{\gamma}\lambda_{ns}(X_{nm} - X_{nb}) + R_{xnb} \\
+  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb} = \frac{1}{\gamma}F_{xnm} + \frac{1}{\gamma}F_{xnb} + \frac{1}{\gamma}\lambda_{nt}(X_{t } - X_{nm}) + R_{xnm} + R_{xnb}\\
+  \dot{X}_{t}  &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
+   &\pm \frac{L_{t}^2\left(L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\ &- L_s\sin(\theta_{nb})\dot{\theta}_{nb} - L_s\sin(\theta_{fb})\dot{\theta}_{fb} =\\ &\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xnm} + \frac{1}{\gamma}F_{xnb} + \frac{1}{\gamma}F_{xfm} + \frac{1}{\gamma}F_{xfb} + R_{xt } + R_{xnm} + R_{xnb} + R_{xfm} + R_{xfb}\\
+  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb} = \frac{1}{\gamma}F_{xfm} + \frac{1}{\gamma}F_{xfb} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xfm} + R_{xfb} \\
+  \dot{X}_{fb} &= 0 = \frac{1}{\gamma}F_{xfb} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xfb}
+\end{align}
+
+\begin{align}
+  \dot{Y}_{nb} &= 0 = \frac{1}{\gamma}F_{ynb} + \frac{1}{\gamma}\lambda_{ns}(Y_{nm} - Y_{nb}) + R_{ynb} \\
+  \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb} = \frac{1}{\gamma}F_{ynm} + \frac{1}{\gamma}F_{ynb} + \frac{1}{\gamma}\lambda_{nt}(Y_{t } - Y_{nm}) + R_{ynm} + R_{ynb}\\
+  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2} \pm \left(\frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
+  &\mp \frac{L_t^2\left(B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})\right)\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb} - \dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\ &+ L_s\cos(\theta_{nb})\dot{\theta}_{nb} + L_s\cos(\theta_{fb})\dot{\theta}_{fb} =\\ & \frac{1}{\gamma}F_{yt } + \frac{1}{\gamma}F_{ynm} + \frac{1}{\gamma}F_{ynb} + \frac{1}{\gamma}F_{yfm} + \frac{1}{\gamma}F_{yfb} + \mn\frac{1}{\gamma}\lambda_{nt}(Y_{t } - Y_{nm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } + R_{ynm} + R_{ynb} + R_{yfm} + R_{yfb}\\
+  \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb} = \frac{1}{\gamma}F_{yfm} + \frac{1}{\gamma}F_{yfb} + \mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yfm} + R_{yfb}\\
+  \dot{Y}_{fb} &= 0 = \frac{1}{\gamma}F_{yfb} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{yfb}
 \end{align}

### 2015-10-29 latex/derivation.tex
Revert to Ln/Lf unambiguous model.

--- 2015-10-25 latex/derivation.tex
@@
 \usepackage{verbatim}
-
-\allowdisplaybreaks
 
@@
 
-%% \begin{figure}[h!]
-%%   \caption{Key lengths and angles in bothbound dynein model.}
-%%   \centering
-%%     \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
-%% \end{figure}
+\begin{figure}[h!]
+  \caption{Key lengths and angles in bothbound dynein model.}
+  \centering
+    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
+\end{figure}
 
-\section{Derivation of bothbound tail coordinates}
+\section{Cartesian Coordinate Derivation}
 
-\begin{align*}
-  \theta_1 &= \cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right)\\
-  \theta_2 &= \cos^{-1}\left(\frac{L}{2L_t}\right)\\
-  L &= \sqrt{(X_{fm}-X_{nm})^2+(Y_{fm}-Y_{nm})^2}\\
-\end{align*}
+By the law of cosines:
+\begin{align}
+  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
+  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
+\end{align}
 
-\subsection{$X_t$}
-\begin{align*}
-  X_t &= X_{nm} + L_t\cos(\theta_1 \pm \theta_2)\\
-  &= X_{nm} + L_t\cos\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
-  \hspace*{1in} \cos\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}\\
-  &= X_{nm} + L_t\left(\frac{X_{fm}-X_{nm}}{2L_t} \mp \sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{1 - \frac{L^2}{4L_t^2}}\right)\\
-  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{4L_t - L^2}\\
-  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2L}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2}\sqrt{4L_t - L^2}\\
-  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
-  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
-  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
-  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
-  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))(L_s\cos(\theta_{nb})) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
-  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
-  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
-  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-  \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
-  &\mp \frac{d}{dt} \left(\frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-  &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{d}{dt} \left(\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\right)\\
-   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
-  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{1}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right) *\\
-   &\left(\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right) *\\
-   &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)\\
-   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
-  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{\left(\frac{-4L_t^2\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right)\\
-\end{align*}
+We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\
 
-\subsection{$Y_t$}
-\begin{align*}
-  Y_t &= Y_{nm} + L_t\sin(\theta_1 \pm \theta_2)\\
-  &= Y_{nm} + L_t\sin\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
-  \hspace*{1in} \sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}\\
-  &= Y_{nm} + L_t\left(\frac{L}{2L_t}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{L}\sqrt{1 - \frac{L^2}{4L^2_t}}\right)\\
-  &= Y_{nm} + \frac{L}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{2L}\sqrt{4L_t^2 - L^2}\\
-  &= Y_{nm} + \frac{1}{2}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{L^2} - 1}\\
-  &= Y_{nm} + \frac{1}{2}\sqrt{\left(Y_{fm}-Y_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
-  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
-  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} - 1}\\
-  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
-  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
-  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
-  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
-  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
-\end{align*}
+Also by the law of cosines, we see that:
+\begin{align}
+  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
+  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
+\end{align}
+
+We use these equations to solve for our nm (near motor) coordinates:
+
+\begin{align}
+  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
+     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
+     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
+  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
+     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
+     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
+\end{align}
+
+We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
+cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
+and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:
+
+\begin{align}
+  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+\end{align}
+
+We simplify further...
+
+\begin{align}
+  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
+\end{align}
+
+\begin{align}
+  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
+\end{align}
+
+Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
+
+\begin{align}
+  \dot{X}_{nm} =
+  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
+   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
+   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
+   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
+   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
+   \text{Ln}(t)^2}\right)}{2
+   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
+   \text{Ln}(t)^2}}} - \\
+  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
+   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
+   \text{Ln}(t)^3}\\
+  &-\frac{\text{Ls}
+   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
+   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
+   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
+   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
+   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
+       \text{Ln}(t)^2}}}\\
+  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
+   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
+   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
+   \text{Ln}(t)^2}
+\end{align}
+
+We can also use the law of cosines to find an expression for $\Theta_{1}$:
+
+\begin{align}
+   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
+   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
+\end{align}
+
+We use this to find the value of $X_{t}$:
+
+\begin{align}
+  X_{t} &= L_n\cos(\Theta_{1}) \\
+       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
+\end{align}
+
+To find $Y_{t}$ we do something similar:
+
+\begin{align}
+  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
+  Y_{t} &= L_n\sin(\Theta_{1}) \\
+  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
+  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
+\end{align}
 
 \section{Cartesian from Angular Coordinates}
-This section lays out the definitions of the coordinates of the bothbound Dynein model.\\
+This section lays out the definitions of the coordinates of the Dynein model. \\
 \begin{align}
-  X_{nb} &= 0\\
-  X_{nm} &= L_s\cos(\theta_{nb})\\
-  X_{t}  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-  X_{fm} &= B + L_s\cos(\theta_{fb})\\
-  X_{fb} &= B \\
+  X_{nb} &= 0 \\
+  X_{nm} &=  \\
+  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
+  X_{fm} &=  \\
+  X_{fb} &= L \\
 \end{align}
@@
   Y_{nb} &= 0 \\
-  Y_{nm} &= L_s\sin(\theta_{nb})\\
-  Y_{t}  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
-  Y_{fm} &= L_s\sin(\theta_{fb})\\
-  Y_{fb} &= 0\\
+  Y_{nm} &=  \\
+  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
+  Y_{fm} &=  \\
+  Y_{fb} &= 0
 \end{align}
@@
   \dot{X}_{nb} &= 0 \\
-  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
-  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + -L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
-  &\pm \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2} \left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
-  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\
+  \dot{X}_{nm} &= \\
+  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
+  \dot{X}_{fm} &= \\
   \dot{X}_{fb} &= 0
@@
   \dot{Y}_{nb} &= 0 \\                                         
-  \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb}\\
-  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\pm \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1} \\
- &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}-BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
-  \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb}\\
+  \dot{Y}_{nm} &= \\
+  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
+  \dot{Y}_{fm} &= \\
   \dot{Y}_{fb} &= 0 \\

### 2015-10-29 latex/derivation.tex
quick commitgit add latex/derivation.tex

@@
 
-\newcommand{\shellcmd}[1]{\texttt{\footnotesize #1}}
+\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins
 
@@
 
-We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\
-
-Also by the law of cosines, we see that:
+By the law of cosines, we see that:
 \begin{align}
@@
 
-We use these equations to solve for our nm (near motor) coordinates:
+\subsection{Solving for $X_{nm}$ and $Y_{nm}$}
 
@@
 \begin{align}
-  \dot{X}_{nm} =
-  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
-   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
-   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
-   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
-   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
-   \text{Ln}(t)^2}\right)}{2
-   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
-   \text{Ln}(t)^2}}} - \\
-  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
-   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
-   \text{Ln}(t)^3}\\
-  &-\frac{\text{Ls}
-   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
-   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
-   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
-   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
-   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
-       \text{Ln}(t)^2}}}\\
-  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
-   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
-   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
-   \text{Ln}(t)^2}
+  \dot{X}_{nm} &=\\
 \end{align}
 
-We can also use the law of cosines to find an expression for $\Theta_{1}$:
-
-\begin{align}
-   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
-   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
-\end{align}
-
-We use this to find the value of $X_{t}$:
+\subsection{$X_t$ and $Y_t$}
 
@@
 
-To find $Y_{t}$ we do something similar:
-
 \begin{align}
-  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
   Y_{t} &= L_n\sin(\Theta_{1}) \\

### 2015-10-30 latex/derivation.tex
mini commit for adding derivatives.

@@
 
+\begin{align}
+  X_{nm} &= \frac{L_s^2L^2 + L_n^2L^2 - L_t^2L^2 + L_s^2L_{n}^2 + L_n^2L_{n}^2 - L_t^2L_{n}^2 - L_s^2L_{f}^2 - L_n^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2LL_s}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2L^2_{n}}}\\ &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}L^2_{n}}}\\
+\end{align}
+
 Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
@@
 \begin{align}
-  \dot{X}_{nm} &=\\
+  \dot{X}_{nm} &= \frac{1}{{2L_n^{-3}LL_s}}\left(-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2\right)\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
+  &\mp L_s\frac{\frac{d}{dt}\left(1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\frac{\frac{d}{dt}\left(1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
+\end{align}
+
+\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
+The nearbound and farbound angles are symmetric. We switch all instances of $L_n$ and $L_f$.
+
+\begin{align}
+  X_{fm} &= \frac{1}{4LL_s}\Big(L^2+L_{f}^2-L_{n}^2\Big)\Big(L_{s}^2+L_{f}^2-L_{t}^2\Big)\big(L_f \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{s}L_{f}}\bigg)^2}\\
+  Y_{fm} &= \frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{f}}\sqrt{1-\bigg(\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\bigg)^2} \pm L_s\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{s}L_{f}}\bigg)^2} \Bigg)\\
 \end{align}

### 2015-11-02 latex/derivation.tex
Modifying derivation.tex

@@
 
+\begin{align}
+  \dot{X}_{nm} &= \frac{1}{{2L_n^{-3}LL_s}}\left(-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2\right)\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
+  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L^2L_{f}\dot{L}_f  + 4L_{f}^3\dot{L}_f}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\frac{\frac{d}{dt} \left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
+    - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
+\end{align}
+
 \subsection{Solving for $X_{fm}$ and $Y_{fm}$}
@@
 
-\subsection{$X_t$ and $Y_t$}
+\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
+The near motor and far motor cases are equivalent. If the farbound binding angles are set to take the same values and positions as $\theta_1$ and $\theta_2$, then we can see that
+
+\subsection{Solving for $X_t$ and $Y_t$}
 

### 2015-11-03 latex/derivation.tex
Add Xnm derivative, todo: Ynm, Xfm, Yfm

--- 2015-10-30 latex/derivation.tex
@@
 \begin{align}
-  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
-  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
+  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
+  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
 \end{align}
@@
 
+\begin{align}
+  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
+  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L^2L_{f}\dot{L}_f  + 4L_{f}^3\dot{L}_f}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}\dot{L}_n
+    - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
+\end{align}
+
+\begin{align}
+  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\
+  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n + \frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s}\dot{L}_f\\
+  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_n\\
+  &\mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_f\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
+    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\dot{L}_n\\
+\end{align}
+
+\begin{align}
+  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
+  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
+  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
+    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
+  &+ \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\dot{L}_f\\
+\end{align}
+
 \subsection{Solving for $X_{fm}$ and $Y_{fm}$}
@@
 
-\subsection{$X_t$ and $Y_t$}
+\subsection{Solving for $X_t$ and $Y_t$}
 
@@
   &= \frac{L^2+L_n^2-L_f^2}{2L} \\
+  \dot{X}_t &= \frac{L_n}{L}\dot{L}_n - \frac{L_f}{L}\dot{L}_f\\
 \end{align}
@@
   Y_{t} &= L_n\sin(\Theta_{1}) \\
-  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
-  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
+  &= L_n\sin\left(\cos^{-1}\left(\frac{L^2+L_n^2-L_f^2}{2LL_n}\right)\right) \\
+  &= L_n\sqrt{1 - \left(\frac{L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
+  &= \sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2} \\
+  \dot{Y}_t &= \frac{2L_n\dot{L}_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n\dot{L}_n - L_f\dot{L}_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
+  \dot{Y}_t &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\dot{L}_n +
+  \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\dot{L}_f\\
 \end{align}
@@
   Y_{nm} &=  \\
-  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
+  Y_{t}  &= L_n\sqrt{1 - \left(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
   Y_{fm} &=  \\
@@
 This section shows the velocity definitions. \\
+
+\textbf{REFORMAT!}
+
+\begin{align}
+  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
+  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
+  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
+  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
+    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
+  A_{xf} &= \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\\
+  B_{xn} &= \frac{L_n}{L}\\
+  B_{xf} &= -\frac{L_f}{L}\\
+  C_{xn} &= \\
+  C_{xf} &= \\
+  A_{yn} &= \\
+  A_{yf} &= \\
+  B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
+  B_{yf} &= \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
+  C_{yn} &= \\
+  C_{yf} &= \\
+\end{align}
+
 \begin{align}
   \dot{X}_{nb} &= 0 \\
-  \dot{X}_{nm} &= \\
-  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
-  \dot{X}_{fm} &= \\
+  \dot{X}_{nm} &= A_{xn}\dot{L}_n + A_{xf}\dot{L}_f\\
+  \dot{X}_{t } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
+  \dot{X}_{fm} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f\\
   \dot{X}_{fb} &= 0
@@
   \dot{Y}_{nb} &= 0 \\                           
-  \dot{Y}_{nm} &= \\
-  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
-  \dot{Y}_{fm} &= \\
+  \dot{Y}_{nm} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
+  \dot{Y}_{t}  &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
+  \dot{Y}_{fm} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f\\
   \dot{Y}_{fb} &= 0 \\

### 2015-11-03 latex/derivation.tex
Add work to derivation.tex.
Add work on Ynm derivative.

@@
 
+We now do the same for $\dot{Y}_{nm}$.
+
+\begin{align}
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}} \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}}\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
+\end{align}
+
+\begin{align}
+  \dot{Y}_{nm} &= \left(\frac{L_{s}^2+2L_{n}\dot{L}_n - L_{t}^2}{2L^2_{n}} - 2\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^3_{n}}\dot{L}_n\right) \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
+  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}} \left(\frac{d}{dt} \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\right)\\
+  &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{d}{dt} \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\right)\\
+\end{align}
+
+\begin{align}
+  \dot{Y}_{nm} &= \left(\frac{L_{s}^2+2L_{n}\dot{L}_n - L_{t}^2}{2L^2_{n}} - 2\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^3_{n}}\dot{L}_n\right) \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
+  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}}   \frac{2L_n\dot{L}_n - \frac{L^4 + 2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_fL_{n}^2\dot{L}_f - 2L_f^2L_{n}\dot{L}_n - 2L^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 4L_{f}^3\dot{L}_f}{4L^2}}{2\sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}}\\
+  &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{d}{dt} \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\right)\\
+\end{align}
+
 \subsection{Solving for $X_{fm}$ and $Y_{fm}$}

### 2015-11-04 latex/derivation.tex
Add redo of derivatives.

@@
   &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{d}{dt} \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\right)\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{2L_n\dot{L}_n - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{4L^2_{s}}}{2\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}} \right)\\
+\end{align}
+
+\begin{align}
+  \dot{Y}_{nm} &= \left(\frac{L_{s}^2+2L_{n}\dot{L}_n - L_{t}^2}{2L^2_{n}} - 2\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^3_{n}}\dot{L}_n\right) \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
+  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}}   \frac{2L_n\dot{L}_n - \frac{L^4 + 2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_fL_{n}^2\dot{L}_f - 2L_f^2L_{n}\dot{L}_n - 2L^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 4L_{f}^3\dot{L}_f}{4L^2}}{2\sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}}\\
+  &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{2L_n\dot{L}_n - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{4L^2_{s}}}{2\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}} \right)\\
 \end{align}

### 2015-11-16 latex/derivation.tex
Add brief work on derivation.tex.
Finish-ish velocities. They are probably mostly right. If wrong, we can come back later and fix them without wasting effort, since the actual values are now defined as coefficients A, B, C, etc...

@@
 \begin{align}
-  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
-  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
-  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
-  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
-    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
-  &+ \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\dot{L}_f\\
+  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
+  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
+  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
+  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
+  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
+    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
+  &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
+  &\Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
+  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
+  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
+  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
+  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\dot{L}_f\\
+    %% &+ \Bigg(\frac{-L_s^2L_{f} - L_n^2L_{f} + L_t^2L_{f}}{2L_n^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
+  %% &\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)\Bigg)\dot{L}_f\\
 \end{align}
@@
 
+\begin{align}
+    \dot{Y}_{nm} &=
+    \Bigg(\left(-\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2} + 1\right)\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}} +\\
+    &\frac{-2\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^3} + \frac{4L_n^3 + 4L^2L_n - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \pm\\
+    &\left(-L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}} \pm\\
+    &L_s\frac{-2\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^3} + \frac{4L_n^3 + 4L_sL_n - 4L_nL_t^2}{4L_s^2L_n^2}}{2\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}}\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Bigg)\dot{L}_n\\
+    + &\Bigg(\frac{\frac{4L_f^3 - 4L^2L_f - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\\
+    \pm &\left(\frac{-L_sL_{f}}{LL_{n}}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}\Bigg)\dot{L}_f\\
+\end{align}
+
 \subsection{Solving for $X_{fm}$ and $Y_{fm}$}
@@
   Y_{fm} &= \frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{f}}\sqrt{1-\bigg(\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\bigg)^2} \pm L_s\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{s}L_{f}}\bigg)^2} \Bigg)\\
+\end{align}
+
+\begin{align}
+  \dot{X}_{fm} &= \Bigg(\frac{-L_s^2L^2 - L_f^2L^2 + L_t^2L^2 - L_s^2L_f^2 - L_f^2L_f^2 + L_t^2L_f^2 + L_s^2L_n^2 + L_f^2L_n^2 - L_t^2L_n^2}{{2L_f^{3}L}}\\
+  &+ \frac{2L_fL^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_n^2}{4L_f^2L}\\
+  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_f^2}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L_f^2}}}*\\
+  &\left(L_s\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L^3_{n}} - L_s\frac{2L_fL^2 + 2L^2L_f + 4L_f^3}{4L^2L_f^2}\right)\\
+  &\mp \left(L_s\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
+    - L_s\frac{2L_fL_{s}^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_{t}^2}{4L_{s}^2L_f^2}\right)\\
+  &\frac{\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}{2\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}\Bigg)\dot{L}_f\\
+  &\Bigg(\frac{-2L_nL_s^2 - 2L_nL_f^2 + 2L_nL_t^2}{4LL_f^2}
+  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}
+  *\left(\frac{2L^2L_n - 2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L^2L_f^2}\right)\\
+  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}
+  *\left(\frac{-2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L_{s}^2L_f^2}\right)\Bigg)\dot{L}_n\\
+    %% &+ \Bigg(\frac{-L_s^2L_n - L_f^2L_n + L_t^2L_n}{2L_f^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}*\\
+  %% &\left(-\frac{-2L_nL^2 - 2L^2L_n + 4L_n^3}{2LL_f}\right)\Bigg)\dot{L}_f\\
+\end{align}
+
+\begin{align}
+    \dot{Y}_{fm} &=
+    \Bigg(\left(-\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2} + 1\right)\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}} +\\
+    &\frac{-2\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^3} + \frac{4L_f^3 + 4L^2L_f - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f} \pm\\
+    &\left(-L_s\frac{L^2+L_f^2-L_n^2}{2LL_f^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}} \pm\\
+    &L_s\frac{-2\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^3} + \frac{4L_f^3 + 4L_sL_f - 4L_fL_t^2}{4L_s^2L_f^2}}{2\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}}\frac{L^2+L_f^2-L_n^2}{2LL_f}\Bigg)\dot{L}_f\\
+    + &\Bigg(\frac{\frac{4L_n^3 - 4L^2L_n - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\\
+    \pm &\left(\frac{-L_sL_n}{LL_f}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}\Bigg)\dot{L}_n\\
 \end{align}
@@
 
-\textbf{REFORMAT!}
-
-\begin{align}
-  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
-  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
-  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
-  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
-    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
-  A_{xf} &= \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\\
-  B_{xn} &= \frac{L_n}{L}\\
-  B_{xf} &= -\frac{L_f}{L}\\
-  C_{xn} &= \\
-  C_{xf} &= \\
-  A_{yn} &= \\
-  A_{yf} &= \\
-  B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
-  B_{yf} &= \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
-  C_{yn} &= \\
-  C_{yf} &= \\
-\end{align}
+\subsection{Velocity Coefficients}
+This subsection defines the coeffients to be used in further derivation.\\
 
@@
   \dot{Y}_{fb} &= 0 \\
+\end{align}
+
+\begin{align}
+  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
+  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
+  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
+  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
+  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
+    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
+    &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
+  A_{xf} &= \Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
+  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
+  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
+  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
+  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\\
+  B_{xn} &= \frac{L_n}{L}\\
+  B_{xf} &= - \frac{L_f}{L}\\
+\end{align}
+\begin{align}
+  C_{xn} &= \Bigg(\frac{-2L_nL_s^2 - 2L_nL_f^2 + 2L_nL_t^2}{4LL_f^2}
+  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}
+  *\left(\frac{2L^2L_n - 2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L^2L_f^2}\right)\\
+  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}
+  *\left(\frac{-2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L_{s}^2L_f^2}\right)\Bigg)\\
+  C_{xf} &= \Bigg(\frac{-L_s^2L^2 - L_f^2L^2 + L_t^2L^2 - L_s^2L_f^2 - L_f^2L_f^2 + L_t^2L_f^2 + L_s^2L_n^2 + L_f^2L_n^2 - L_t^2L_n^2}{{2L_f^{3}L}}\\
+  &+ \frac{2L_fL^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_n^2}{4L_f^2L}\\
+  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_f^2}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L_f^2}}}*\\
+  &\left(L_s\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L^3_{n}} - L_s\frac{2L_fL^2 + 2L^2L_f + 4L_f^3}{4L^2L_f^2}\right)\\
+  &\mp \left(L_s\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
+    - L_s\frac{2L_fL_{s}^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_{t}^2}{4L_{s}^2L_f^2}\right)\\
+    &\frac{\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}{2\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}\Bigg)\\
+\end{align}
+\begin{align}
+  A_{yn} &= \Bigg(\left(-\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2} + 1\right)\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}} +\\
+    &\frac{-2\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^3} + \frac{4L_n^3 + 4L^2L_n - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \pm\\
+    &\left(-L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}} \pm\\
+    &L_s\frac{-2\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^3} + \frac{4L_n^3 + 4L_sL_n - 4L_nL_t^2}{4L_s^2L_n^2}}{2\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}}\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Bigg)\\
+  A_{yf} &= \Bigg(\frac{\frac{4L_f^3 - 4L^2L_f - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\\
+    \pm &\left(\frac{-L_sL_{f}}{LL_{n}}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}\Bigg)\\
+  B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
+  B_{yf} &= \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
+\end{align}
+\begin{align}
+  C_{yn} &= \Bigg(\frac{\frac{4L_n^3 - 4L^2L_n - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\\
+    \pm &\left(\frac{-L_sL_n}{LL_f}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}\Bigg)\\
+  C_{yf} &= \Bigg(\left(-\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2} + 1\right)\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}} +\\
+    &\frac{-2\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^3} + \frac{4L_f^3 + 4L^2L_f - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f} \pm\\
+    &\left(-L_s\frac{L^2+L_f^2-L_n^2}{2LL_f^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}} \pm\\
+    &L_s\frac{-2\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^3} + \frac{4L_f^3 + 4L_sL_f - 4L_fL_t^2}{4L_s^2L_f^2}}{2\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}}\frac{L^2+L_f^2-L_n^2}{2LL_f}\Bigg)\\
 \end{align}

### 2015-11-19 latex/derivation.tex
Add bothbound system to derivation.tex.

--- 2015-11-16 latex/derivation.tex
@@
 
+\section{System of Equations}
+This section creates a system of equations by equating the Brownian dynamics equations for velocity with the derivatives we just found.
+
+\begin{align}  
+  \dot{X}_{bm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}  &= A_{nx}\dot{L}_n + A_{fx}\dot{L}_f\\
+  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
+  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f
+\end{align}
+
+\begin{align}  
+  \dot{Y}_{bm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
+  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
+  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f
+\end{align}
+
+\section{Matrix Solution via Mathematica}
+Here we convert the above system into matrix form, solve it in Mathematica and list the results.
+
+\[
+\begin{pmatrix}
+  -A_{xn} & -A_{xf} & -\frac{X_{bm}-X_{bb}}{\gamma} & \frac{X_{t}-X_{bm}}{\gamma} & 0 & 0\\
+  -B_{xn} & -B_{xf} & 0 & -\frac{X_{t}-X_{bm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
+  -C_{xn} & -C_{xf} & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
+  -A_{yn} & -A_{yf} & -\frac{Y_{bm}-Y_{bb}}{\gamma} & \frac{Y_{t}-Y_{bm}}{\gamma} & 0 & 0\\
+  -B_{yn} & -B_{yf} & 0 & -\frac{Y_{t}-Y_{bm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
+  -C_{yn} & -C_{yf} & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
+\end{pmatrix}
+\begin{pmatrix}
+  \dot{L}_n\\
+  \dot{L}_f\\
+  \lambda_{bs}\\
+  \lambda_{bt}\\
+  \lambda_{ft}\\
+  \lambda_{fs}\\
+\end{pmatrix}
+=
+\begin{pmatrix}
+  -\frac{F_{xml}}{\gamma} - R_{xml}\\
+  -\frac{F_{xt}}{\gamma} - R_{xt}\\
+  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
+  -\frac{F_{yml}}{\gamma} - R_{yml}\\
+  -\frac{F_{yt}}{\gamma} - R_{yt}\\
+  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
+\end{pmatrix}
+\]
+
 \begin{twocolumn}

### 2015-11-19 latex/derivation.tex
Add system of equations for bothbound.

@@
 
-\section{Matrix Solution via Mathematica}
-Here we convert the above system into matrix form, solve it in Mathematica and list the results.
-
-\[
-\begin{pmatrix}
-  -A_{xn} & -A_{xf} & -\frac{X_{bm}-X_{bb}}{\gamma} & \frac{X_{t}-X_{bm}}{\gamma} & 0 & 0\\
-  -B_{xn} & -B_{xf} & 0 & -\frac{X_{t}-X_{bm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
-  -C_{xn} & -C_{xf} & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
-  -A_{yn} & -A_{yf} & -\frac{Y_{bm}-Y_{bb}}{\gamma} & \frac{Y_{t}-Y_{bm}}{\gamma} & 0 & 0\\
-  -B_{yn} & -B_{yf} & 0 & -\frac{Y_{t}-Y_{bm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
-  -C_{yn} & -C_{yf} & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
-\end{pmatrix}
-\begin{pmatrix}
-  \dot{L}_n\\
-  \dot{L}_f\\
-  \lambda_{bs}\\
-  \lambda_{bt}\\
-  \lambda_{ft}\\
-  \lambda_{fs}\\
-\end{pmatrix}
-=
-\begin{pmatrix}
-  -\frac{F_{xml}}{\gamma} - R_{xml}\\
-  -\frac{F_{xt}}{\gamma} - R_{xt}\\
-  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
-  -\frac{F_{yml}}{\gamma} - R_{yml}\\
-  -\frac{F_{yt}}{\gamma} - R_{yt}\\
-  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
-\end{pmatrix}
-\]
-
 \begin{twocolumn}

### 2015-12-17 latex/derivation.tex
Add changes to cartesian coordinate definitions.

--- 2015-11-19 latex/derivation.tex
@@
 
+We now note the time derivatives of $\Theta$. We don't use them explicitly here, as we will be solving for $\dot{L_n}$ and $\dot{L_f}$ for simplicity. We will need these $\Theta$ derivatives later.
+
+\begin{align}
+  \dot{\Theta_{1}} &= \frac{1}{\sqrt{1-\left(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\right)^2}}\left(\frac{2L_n\dot{L_n} - 2L_f\dot{L_f}}{2LL_n}\right)\left(\frac{L^2+L_n^2-L_f^2}{-2LL_n^2\dot{L_n}}\right)\\
+  \dot{\Theta_{2}} &= \pm \frac{1}{\sqrt{1-\left(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\right)^2}}\left(\frac{L_n\dot{L_n}}{L_s}\right)\left(\frac{L_s^2+L_{n}^2-L_t^2}{-2L_sL_n^2\dot{L_n}}\right)\\
+\end{align}
+
 \subsection{Solving for $X_{nm}$ and $Y_{nm}$}
@@
 \begin{align}
-  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
+  X_{nm} &= \frac{1}{4LL_n^2}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
   Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
@@
 \begin{align}
-  X_{nm} &= \frac{L_s^2L^2 + L_n^2L^2 - L_t^2L^2 + L_s^2L_{n}^2 + L_n^2L_{n}^2 - L_t^2L_{n}^2 - L_s^2L_{f}^2 - L_n^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2LL_s}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2L^2_{n}}}\\ &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}L^2_{n}}}\\
-\end{align}
-
+  X_{nm} &= \frac{L_s^2L^2 + L_n^2L^2 - L_t^2L^2 + L_s^2L_{n}^2 + L_n^2L_{n}^2 - L_t^2L_{n}^2 - L_s^2L_{f}^2 - L_n^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_{n}^2}}*\\
+  &\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_s^2L_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_{s}^2L_{n}^2}}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L^2_{n}}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_n^4 + L_t^4 + 2L_s^2L_n^2 - 2L_s^2L_t^2 - 2L_n^2L_f^2}{4L^2_{s}L^2_{n}}}\\
+\end{align}
+
+\begin{align}
+  X_{nm} &= \frac{L_s^2L^2 - L_t^2L^2 - L_s^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L} + \frac{L + L_s^2 + L_n^2 - L_t^2 - L_{f}^2}{4L}\\
+  &\mp L_s\sqrt{1-\frac{L^4 + L_f^4 - 2L^2L_f^2}{4L^2L_{n}^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}*\\
+  &\sqrt{1-\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}\\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\frac{L^4 + L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
+\end{align}
+
+Now i'm here. Just fixed the above, now go redo these derivations.\\
 Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
-
+\subsection{New derivation}
+\begin{align}
+  hi
+\end{align}
+
+\subsection{Old derivation}
 \begin{align}

### 2015-12-17 dynein_struct.cpp

@@ -224,13 +224,7 @@ void Dynein::update_velocities_bothbound() {
   int pm = 1;
   int mp = 0;
   
-  double Axn = ((-ls*ls*l*l - ln*ln*l*l + lt*lt*l*t - ls*ls*ln*ln - ln*ln*ln*ln + lt*lt*ln*ln + ls*ls*lf*lf + ln*ln*lf*lf - lt*lt*lf*lf) / (2*ln*ln*ln*l) +
-		(2*ln*l*l + 2*ls*ls*ln + 4*ln*ln*ln - 2*lt*lt*ln - 2*ln*lf*lf)/(4*ln*ln*l) +
-		mp*(sqrt(1 - (ls*ls*ls*ls + ln*ln*ls*ls - lt*lt*ls*ls + ls*ls*ln*ln + ln*ln*ln*ln - lt*lt*ln*ln - ls*ls*lt*lt - ln*ln*lt*lt + lt*lt*lt*lt)/(4*ls*ls*ln*ln) ))/(2*sqrt(1 - (l*l*l*l + ln*ln*l*l - lf*lf*l*l + l*l*ln*ln + ln*ln*ln*ln - lf*lf*ln*ln - l*l*lf*lf + ln*ln*lf*lf + lf*lf*lf*lf)/(4*l*l*ln*ln) )) *
-		ls*( (l*l*l*l + ln*ln*l*l - lf*lf*l*l + l*l*ln*ln + ln*ln*ln*ln - lf*lf*ln*ln - l*l*lf*lf + ln*ln*lf*lf + lf*lf*lf*lf)/(4*l*l*ln*ln*ln) - (2*ln*l*l + 2*l*l*ln + 4*ln*ln*ln)/(4*ls*ls*ln*ln) ) +
-		mp*ls*( ... )
-
-		)
+  double Axn =;
   double Axf =;
   double Bxn =;
   double Bxf =;
@@ -243,6 +237,9 @@ void Dynein::update_velocities_bothbound() {
   double Byf =;
   double Cyn =;
   double Cyf =;
+
+  double Lndot = ; // from Mathematica
+  double Lfdot = ; // from Mathematica
 }
 
 double Dynein::get_binding_rate() {

### 2015-12-26 latex/derivation.tex
Add nm cartesian derivatives which need checking.
Add solutions for farbound case, which are symmetric. Improve bothbound figure to properly represent farbound motor angle Theta_fm. Update coefficients definitions for cartesian velocities. TODO: Solve matrix, input matrix solution into dynein_struct, input coefficients into dynein_struct.

@@
 \begin{align}
-  X_{nm} &= \frac{L_s^2L^2 - L_t^2L^2 - L_s^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L} + \frac{L + L_s^2 + L_n^2 - L_t^2 - L_{f}^2}{4L}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_f^4 - 2L^2L_f^2}{4L^2L_{n}^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}*\\
-  &\sqrt{1-\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\frac{L^4 + L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
+  X_{nm} &= \frac{L_s^2L^2 - L_t^2L^2}{4L_n^2L} + \frac{-L_s^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L} + \frac{L + L_s^2 + L_n^2 - L_t^2 - L_{f}^2}{4L}\\
+  &\mp L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}*\\
+  &\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}\\  
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
   &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
@@
 
-Now i'm here. Just fixed the above, now go redo these derivations.\\
 Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
-\subsection{New derivation}
+
 \begin{align}
-  hi
-\end{align}
-
-\subsection{Old derivation}
-\begin{align}
-  \dot{X}_{nm} &= \frac{1}{{2L_n^{-3}LL_s}}\left(-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2\right)\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
-  &\mp L_s\frac{\frac{d}{dt}\left(1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
-  &\frac{\frac{d}{dt}\left(1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
+  \dot{X}_{nm} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L}\dot{L}_n + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L}\dot{L}_f + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\dot{L}_n\\
+  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3}\dot{L}_n - \frac{L_f^3 - L^2L_f}{L^2L_n^2}\dot{L}_f + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3}\dot{L}_n - \frac{L_n}{2L^2}\dot{L}_n + \frac{L_f}{L^2}\dot{L}_f\right)\\
+  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
+  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3}\dot{L}_n - \frac{L_n}{2L_s^2}\dot{L}_n\right)
 \end{align}
@@
 \begin{align}
-  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
-  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L^2L_{f}\dot{L}_f  + 4L_{f}^3\dot{L}_f}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
-  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}\dot{L}_n
-    - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
+  \dot{Y}_{nm} &= \left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\dot{L}_n\\
+  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3}\dot{L}_n - \frac{L_f^3 - L^2L_f}{L^2L^2_{n}}\dot{L}_f + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n}\dot{L}_n - \frac{L_n}{2L^2}\dot{L}_n + \frac{L_f}{L^2}\dot{L}_f\right)\\
+  &\pm L_s\left(\frac{1}{L}\dot{L}_n - \frac{L_f}{LL_{n}}\dot{L}_f - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\dot{L}_n\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
+  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3}\dot{L}_n - \frac{L_n}{2L_s^2}\dot{L}_n + \frac{L_f}{L_s^2}\dot{L}_f\right)
 \end{align}
@@
 \begin{align}
-  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\
-  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n + \frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s}\dot{L}_f\\
-  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_n\\
-  &\mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_f\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
-  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
-    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\dot{L}_n\\
+  \dot{X}_{nm} &= \Bigg[\frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L} + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L} + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\\
+  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3} - \frac{L_n}{2L^2}\right)\\
+  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
+  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3} - \frac{L_n}{2L_s^2}\right)\Bigg]\dot{L}_n\\
+  &\mp \Bigg[L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L_n^2} + \frac{L_f}{L^2}\right)\Bigg]\dot{L}_f\\
 \end{align}
@@
 \begin{align}
-  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
-  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
-  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
-  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
-  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
-    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
-  &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
-  &\Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
-  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
-  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
-  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
-  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\dot{L}_f\\
-    %% &+ \Bigg(\frac{-L_s^2L_{f} - L_n^2L_{f} + L_t^2L_{f}}{2L_n^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
-  %% &\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)\Bigg)\dot{L}_f\\
+  \dot{Y}_{nm} &= \bigg[\left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
+    &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n} - \frac{L_n}{2L^2}\right)\\
+    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3} - \frac{L_n}{2L_s^2}\right)
+  \bigg]\dot{L}_n\\
+  &+\bigg[\frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L^2_{n}} + \frac{L_f}{L^2}\right)\\
+    &\pm L_s\left(-\frac{L_f}{LL_{n}}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_f}{L_s^2}\right)
+  \bigg]\dot{L}_f
 \end{align}
 
-We now do the same for $\dot{Y}_{nm}$.
+\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
+The only way to differentiate the near- and far-bound sides of the molecule is by looking at the definition of $L_n$ and $L_f$.
+Because of this, to calculate the values of $X_{fm}$ and $Y_{fm}$, we can just switch all instances of $L_n$ and $L_f$.
 
 \begin{align}
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}} \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}}\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
+  \dot{X}_{fm} &= \Bigg[\frac{-L_s^2L^2 + L_t^2L^2}{2L_f^3L} + \frac{-L_s^2L_n + L_t^2L_n}{2L_f^2L} + \frac{L_s^2L_n^2 - L_t^2L_n^2}{2L_f^3L}\\
+  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
+  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
+  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_f^3} - \frac{L_f}{2L_s^2}\right)\Bigg]\dot{L}_f\\
+  &\mp \Bigg[L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L_f^2} + \frac{L_n}{L^2}\right)\Bigg]\dot{L}_n\\
 \end{align}
@@
 \begin{align}
-  \dot{Y}_{nm} &= \left(\frac{L_{s}^2+2L_{n}\dot{L}_n - L_{t}^2}{2L^2_{n}} - 2\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^3_{n}}\dot{L}_n\right) \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
-  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}} \left(\frac{d}{dt} \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\right)\\
-  &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{d}{dt} \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\right)\\
-\end{align}
-
-\begin{align}
-  \dot{Y}_{nm} &= \left(\frac{L_{s}^2+2L_{n}\dot{L}_n - L_{t}^2}{2L^2_{n}} - 2\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^3_{n}}\dot{L}_n\right) \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
-  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}}   \frac{2L_n\dot{L}_n - \frac{L^4 + 2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_fL_{n}^2\dot{L}_f - 2L_f^2L_{n}\dot{L}_n - 2L^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 4L_{f}^3\dot{L}_f}{4L^2}}{2\sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}}\\
-  &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{2L_n\dot{L}_n - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{4L^2_{s}}}{2\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}} \right)\\
-\end{align}
-
-\begin{align}
-  \dot{Y}_{nm} &= \left(\frac{L_{s}^2+2L_{n}\dot{L}_n - L_{t}^2}{2L^2_{n}} - 2\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^3_{n}}\dot{L}_n\right) \sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}\\
-  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L^2_{n}}   \frac{2L_n\dot{L}_n - \frac{L^4 + 2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_fL_{n}^2\dot{L}_f - 2L_f^2L_{n}\dot{L}_n - 2L^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 4L_{f}^3\dot{L}_f}{4L^2}}{2\sqrt{L_n^2-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 - L_n^2L_{f}^2 + L_{f}^4}{4L^2}}}\\
-  &\pm L_s\left(\frac{L^2+2L_{n}\dot{L}_n - 2L_{f}\dot{L}_f}{2LL^2_n} - 2\frac{L^2+L_{n}^2-L_{f}^2}{2LL^3_n}\dot{L}_n\right) \sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL^2_{n}} \left(\frac{2L_n\dot{L}_n - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{4L^2_{s}}}{2\sqrt{L^2_n - \frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L^2_{s}}}} \right)\\
-\end{align}
-
-\begin{align}
-    \dot{Y}_{nm} &=
-    \Bigg(\left(-\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2} + 1\right)\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}} +\\
-    &\frac{-2\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^3} + \frac{4L_n^3 + 4L^2L_n - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \pm\\
-    &\left(-L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}} \pm\\
-    &L_s\frac{-2\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^3} + \frac{4L_n^3 + 4L_sL_n - 4L_nL_t^2}{4L_s^2L_n^2}}{2\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}}\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Bigg)\dot{L}_n\\
-    + &\Bigg(\frac{\frac{4L_f^3 - 4L^2L_f - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\\
-    \pm &\left(\frac{-L_sL_{f}}{LL_{n}}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}\Bigg)\dot{L}_f\\
-\end{align}
-
-\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
-The nearbound and farbound angles are symmetric. We switch all instances of $L_n$ and $L_f$.
-
-\begin{align}
-  X_{fm} &= \frac{1}{4LL_s}\Big(L^2+L_{f}^2-L_{n}^2\Big)\Big(L_{s}^2+L_{f}^2-L_{t}^2\Big)\big(L_f \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{s}L_{f}}\bigg)^2}\\
-  Y_{fm} &= \frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{f}}\sqrt{1-\bigg(\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\bigg)^2} \pm L_s\frac{L^2+L_{f}^2-L_{n}^2}{2LL_{f}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{f}^2-L_{t}^2}{2L_{s}L_{f}}\bigg)^2} \Bigg)\\
-\end{align}
-
-\begin{align}
-  \dot{X}_{fm} &= \Bigg(\frac{-L_s^2L^2 - L_f^2L^2 + L_t^2L^2 - L_s^2L_f^2 - L_f^2L_f^2 + L_t^2L_f^2 + L_s^2L_n^2 + L_f^2L_n^2 - L_t^2L_n^2}{{2L_f^{3}L}}\\
-  &+ \frac{2L_fL^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_n^2}{4L_f^2L}\\
-  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_f^2}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L_f^2}}}*\\
-  &\left(L_s\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L^3_{n}} - L_s\frac{2L_fL^2 + 2L^2L_f + 4L_f^3}{4L^2L_f^2}\right)\\
-  &\mp \left(L_s\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
-    - L_s\frac{2L_fL_{s}^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_{t}^2}{4L_{s}^2L_f^2}\right)\\
-  &\frac{\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}{2\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}\Bigg)\dot{L}_f\\
-  &\Bigg(\frac{-2L_nL_s^2 - 2L_nL_f^2 + 2L_nL_t^2}{4LL_f^2}
-  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}
-  *\left(\frac{2L^2L_n - 2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L^2L_f^2}\right)\\
-  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}
-  *\left(\frac{-2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L_{s}^2L_f^2}\right)\Bigg)\dot{L}_n\\
-    %% &+ \Bigg(\frac{-L_s^2L_n - L_f^2L_n + L_t^2L_n}{2L_f^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}*\\
-  %% &\left(-\frac{-2L_nL^2 - 2L^2L_n + 4L_n^3}{2LL_f}\right)\Bigg)\dot{L}_f\\
-\end{align}
-
-\begin{align}
-    \dot{Y}_{fm} &=
-    \Bigg(\left(-\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2} + 1\right)\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}} +\\
-    &\frac{-2\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^3} + \frac{4L_f^3 + 4L^2L_f - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f} \pm\\
-    &\left(-L_s\frac{L^2+L_f^2-L_n^2}{2LL_f^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}} \pm\\
-    &L_s\frac{-2\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^3} + \frac{4L_f^3 + 4L_sL_f - 4L_fL_t^2}{4L_s^2L_f^2}}{2\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}}\frac{L^2+L_f^2-L_n^2}{2LL_f}\Bigg)\dot{L}_f\\
-    + &\Bigg(\frac{\frac{4L_n^3 - 4L^2L_n - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\\
-    \pm &\left(\frac{-L_sL_n}{LL_f}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}\Bigg)\dot{L}_n\\
+  \dot{Y}_{fm} &= \bigg[\left(1 - \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2}\right)\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}\\
+    &+ \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
+    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_f^2-L_n^2}{2LL_f^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_f^3} - \frac{L_f}{2L_s^2}\right)
+  \bigg]\dot{L}_f\\
+  &+\bigg[\frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L^2_{n}} + \frac{L_n}{L^2}\right)\\
+    &\pm L_s\left(-\frac{L_n}{LL_f}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_n}{L_s^2}\right)
+  \bigg]\dot{L}_n
 \end{align}
@@
   X_{nb} &= 0 \\
-  X_{nm} &=  \\
+  X_{nm} &= \frac{1}{4LL_n^2}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
   X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
-  X_{fm} &=  \\
+  X_{fm} &= \frac{1}{4LL_f^2}\Big(L^2+L_f^2-L_n^2\Big)\Big(L_{s}^2+L_f^2-L_{t}^2\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_f^2-L_n^2}{2LL_f}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_{s}L_f}\bigg)^2}\\
   X_{fb} &= L \\
@@
   Y_{nb} &= 0 \\
-  Y_{nm} &=  \\
+  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
   Y_{t}  &= L_n\sqrt{1 - \left(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
-  Y_{fm} &=  \\
+  Y_{fm} &= \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\sqrt{1-\bigg(\frac{L^2+L_f^2-L_n^2}{2LL_f}\bigg)^2} \pm L_s\frac{L^2+L_f^2-L_n^2}{2LL_f}\sqrt{1-\bigg(\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_{s}L_f}\bigg)^2} \Bigg)\\
   Y_{fb} &= 0
@@
 \begin{align}
-  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
-  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
-  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
-  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
-  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
-    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
-    &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
-  A_{xf} &= \Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
-  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
-  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
-  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
-  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\\
+  A_{xn} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L} + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L} + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\\
+  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3} - \frac{L_n}{2L^2}\right)\\
+  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
+  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3} - \frac{L_n}{2L_s^2}\right)\\
+  A_{xf} &= \mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L_n^2} + \frac{L_f}{L^2}\right)\\
   B_{xn} &= \frac{L_n}{L}\\
@@
 \begin{align}
-  C_{xn} &= \Bigg(\frac{-2L_nL_s^2 - 2L_nL_f^2 + 2L_nL_t^2}{4LL_f^2}
-  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}
-  *\left(\frac{2L^2L_n - 2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L^2L_f^2}\right)\\
-  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}
-  *\left(\frac{-2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L_{s}^2L_f^2}\right)\Bigg)\\
-  C_{xf} &= \Bigg(\frac{-L_s^2L^2 - L_f^2L^2 + L_t^2L^2 - L_s^2L_f^2 - L_f^2L_f^2 + L_t^2L_f^2 + L_s^2L_n^2 + L_f^2L_n^2 - L_t^2L_n^2}{{2L_f^{3}L}}\\
-  &+ \frac{2L_fL^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_n^2}{4L_f^2L}\\
-  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_f^2}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L_f^2}}}*\\
-  &\left(L_s\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L^3_{n}} - L_s\frac{2L_fL^2 + 2L^2L_f + 4L_f^3}{4L^2L_f^2}\right)\\
-  &\mp \left(L_s\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
-    - L_s\frac{2L_fL_{s}^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_{t}^2}{4L_{s}^2L_f^2}\right)\\
-    &\frac{\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}{2\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}\Bigg)\\
+  C_{xn} &= \mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L_f^2} + \frac{L_n}{L^2}\right)\\
+  C_{xf} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_f^3L} + \frac{-L_s^2L_n + L_t^2L_n}{2L_f^2L} + \frac{L_s^2L_n^2 - L_t^2L_n^2}{2L_f^3L}\\
+  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
+  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
+  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_f^3} - \frac{L_f}{2L_s^2}\right)\\
 \end{align}
 \begin{align}
-  A_{yn} &= \Bigg(\left(-\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2} + 1\right)\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}} +\\
-    &\frac{-2\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^3} + \frac{4L_n^3 + 4L^2L_n - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \pm\\
-    &\left(-L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}} \pm\\
-    &L_s\frac{-2\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^3} + \frac{4L_n^3 + 4L_sL_n - 4L_nL_t^2}{4L_s^2L_n^2}}{2\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}}\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Bigg)\\
-  A_{yf} &= \Bigg(\frac{\frac{4L_f^3 - 4L^2L_f - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\\
-    \pm &\left(\frac{-L_sL_{f}}{LL_{n}}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}\Bigg)\\
+  A_{yn} &= \left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
+    &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n} - \frac{L_n}{2L^2}\right)\\
+    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3} - \frac{L_n}{2L_s^2}\right)\\
+  A_{yf} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L^2_{n}} + \frac{L_f}{L^2}\right)\\
+    &\pm L_s\left(-\frac{L_f}{LL_{n}}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_f}{L_s^2}\right)\\
   B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
@@
 \begin{align}
-  C_{yn} &= \Bigg(\frac{\frac{4L_n^3 - 4L^2L_n - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\\
-    \pm &\left(\frac{-L_sL_n}{LL_f}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}\Bigg)\\
-  C_{yf} &= \Bigg(\left(-\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2} + 1\right)\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}} +\\
-    &\frac{-2\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^3} + \frac{4L_f^3 + 4L^2L_f - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f} \pm\\
-    &\left(-L_s\frac{L^2+L_f^2-L_n^2}{2LL_f^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}} \pm\\
-    &L_s\frac{-2\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^3} + \frac{4L_f^3 + 4L_sL_f - 4L_fL_t^2}{4L_s^2L_f^2}}{2\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}}\frac{L^2+L_f^2-L_n^2}{2LL_f}\Bigg)\\
+  C_{yn} &= \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L^2_{n}} + \frac{L_n}{L^2}\right)\\
+    &\pm L_s\left(-\frac{L_n}{LL_f}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_n}{L_s^2}\right)\\
+  C_{yf} &= \left(1 - \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2}\right)\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}\\
+    &+ \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
+    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_f^2-L_n^2}{2LL_f^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
+    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_f^3} - \frac{L_f}{2L_s^2}\right)\\
 \end{align}

### 2016-01-12 latex/paper.tex
add garbage paper for code-related diagrams

--- 2015-12-26 latex/derivation.tex
@@
-\documentclass[11pt, landscape]{article}
+\documentclass[11pt]{article}
 
@@
 
-\section{Cartesian from Angular Coordinates}
-This section lays out the definitions of the coordinates of the Dynein model. \\
-\begin{align}
-  X_{bb} &= 0 \\
-  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
-  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
-  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
-  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
-\end{align}
+Hello world
 
-\begin{align}
-  Y_{bb} &= 0 \\
-  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
-  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
-  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
-  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
-\end{align}
-
-\section{Cartesian Velocities}
-This section shows the velocity definitions. \\
-\begin{align}
-  \dot{X}_{bb} &= 0 \\
-  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
-  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
-\end{align}
-
-\begin{align}                                                                          
-  \dot{Y}_{bb} &= 0 \\                                                        
-  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
-  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-\end{align}
-
-\section{Cartesian Velocities (expanded)}
-This section expands the above definitions. \\
-\begin{align}
-  \dot{X}_{bb} &= 0 \\
-  \dot{X}_{bm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
-  \dot{X}_{fm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-  \dot{X}_{fb} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
-\end{align}
-
-\begin{align}                                                                               
-  \dot{Y}_{bb} &= 0 \\                                                               
-  \dot{Y}_{bm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
-  \dot{Y}_{fm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-  \dot{Y}_{fb} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-\end{align}
-
-\section{Brownian Equations}
-This section shows the velocity definitions using the Brownian dynamics equation. \\
-\begin{align}  
-  \dot{X}_{bb} &= 0 \\
-  \dot{X}_{bm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
-  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
-  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
-\end{align}
-
-\begin{align}  
-  \dot{Y}_{bb} &= 0 \\
-  \dot{Y}_{bm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
-  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
-  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
-\end{align}
-
-%Unnecessary section commented out
-\begin{comment}
-\section{Expanded Brownian Equations}
-
-\begin{align}
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
-  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
-\end{align}
-
-\begin{align}
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
-  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
-\end{align}
-
-\section{System after Subtracting out Angular Velocity Terms}
-This is the system after subtracting equations from each other to eliminate some angular velocity terms.\\
-
-\begin{align}
-  L_{s}\sin(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
-  L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) - R_{xml} \\
-  L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) - R_{xt } \\
-  L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) - R_{xmr}
-\end{align}
-
-\begin{align}
-  \mn L_{s}\cos(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  \mn L_{t}\cos(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) - R_{yml}\\
-  \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) - R_{yt } \\
-  \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) - R_{ymr}
-\end{align}
-\end{comment}
-
-\section{System of Equations}
-This section creates a system of equations by equating the Cartesian and Brownian velocity definitions from above. \\
-
-\begin{align}  
-  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
-  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
-  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
-\end{align}
-
-\begin{align}  
-  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
-  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
-\end{align}
-
-\section{System after Addition}
-By adding equations from our system together we can isolate the $\lambda$ values. This system has been verified via CAS.\\
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) =
-\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Ax}
-\end{multline}%Fix'd
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) =
-\dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Bx}
-\end{multline}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) =
-\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Cx}
-\end{equation}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) = 
-\dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
-\label{eq:Dx}
-\end{equation}%Fix'd
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) =
-\dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
-+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:Ay}
-\end{multline}%Fix'd
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) =
-\dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:By}
-\end{multline}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) =
-\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-- R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:Cy}
-\end{equation}%Fix'd
-
-\begin{equation}
-\mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
-\label{eq:Dy}
-\end{equation}%Fix'd
-
-\section{Creating Angular Velocity Matrix}
-
-Our goal is to take the above system of equations and put it in matrix form:
-
-\begin{align}
-  A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} &= X_1 \\
-  B_1\dot{\Theta}_{bb} + B_2 \dot{\Theta}_{bm} + B_3 \dot{\Theta}_{fm} + B_4 \dot{\Theta}_{fb} &= X_2 \\
-  C_1\dot{\Theta}_{bb} + C_2 \dot{\Theta}_{bm} + C_3 \dot{\Theta}_{fm} + C_4 \dot{\Theta}_{fb} &= X_3 \\
-  D_1\dot{\Theta}_{bb} + D_2 \dot{\Theta}_{bm} + D_3 \dot{\Theta}_{fm} + D_4 \dot{\Theta}_{fb} &= X_4 \\
-\end{align}
-
-This will allow us to perform a matrix solution for the angular velocities.
-$X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s.
-The above system of equations has four lambda terms: $\lambda_{bs}, \lambda_{bt}, \lambda_{ft}$ and $\lambda_{bs}$.
-Each term is present in two equations.
-We will use this redundancy to eliminate the lambda terms and create the above matrix.
-
-\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
-In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} = X_1$\\
-
-We start by dividing out the position terms in Equations (\ref{eq:Ax}) and (\ref{eq:Ay}) to make their LHSs identical.
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs} =
-\Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\frac{1}{(X_{bm} - X_{bb})}
-\end{multline}
-
-\begin{multline}
-\mn\frac{1}{\gamma}\lambda_{bs} =
-\Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
-+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\frac{1}{(Y_{bm} - Y_{bb})}
-\end{multline}
-
-We then equate them.
-
-\begin{multline}
-\Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
-- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
--\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(Y_{bm} - Y_{bb}) = \\
-\Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
-- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} \\
-+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(X_{bm} - X_{bb})
-\end{multline}
-
-Then we group like terms for clarity.
-
-\begin{multline}
-\Big(\dot{X}_{bb} + \dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm} 
-- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \\
-- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
-\Big(\dot{Y}_{bb} + \dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm}
-+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} \\
-- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
-\end{multline}
-
-We then expand all the $\dot{X}$ terms using their definitions from the Cartesian Velocities section above.
-
-\begin{multline}
-\Big(
-- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb}
-- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
-- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}\\
-- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
-- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
-\Big(
-+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb}
-+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
-+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}\\
-+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
-\end{multline}
-
-Then we group together the like terms from the expansion.
-
-\begin{multline}
-\Big(- 4L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
-- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
-\Big(4L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
-\end{multline}
-
-We then bring all the angular velocity terms to one side and all the force terms to the other side.
-
-\begin{multline}
-\Big(- 4L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
-+ 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_s\sin(\Theta_{bb}))\\
-\Big(-4L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
-+ 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_s\cos(\Theta_{bb}))= \\
-\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
-+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(L_s\sin(\Theta_{bb}))
-\end{multline}
-
-We then distribute the $L_s\sin(\Theta_{bb})$ and $L_s\cos(\Theta_{bb})$ terms into the expression.
-
-\begin{multline}
-\Big(- 4L_{s}\sin(\Theta_{bb})\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\sin(\Theta_{bb})\dot{\Theta}_{bm}
-+ 2L_{t}\sin(\Theta_{fm})\sin(\Theta_{bb})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\sin(\Theta_{bb})\dot{\Theta}_{fb}\Big)\\
-\Big(-4L_{s}\cos(\Theta_{bb})\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\cos(\Theta_{bb})\dot{\Theta}_{bm}
-+ 2L_{t}\cos(\Theta_{fm})\cos(\Theta_{bb})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\cos(\Theta_{bb})\dot{\Theta}_{fb}\Big)= \\
-\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bb}))
-+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bb}))
-\end{multline}
-
-Finally, we group all terms by their angular velocity.
-
-\begin{multline}
--4L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{bb}) + \cos(\Theta_{bb})\cos(\Theta_{bb})\Big)\dot{\Theta}_{bb}
--3L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{bb}) + \cos(\Theta_{bm})\cos(\Theta_{bb})\Big)\dot{\Theta}_{bm}\\
-+2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bb}) + \cos(\Theta_{fm})\cos(\Theta_{bb})\Big)\dot{\Theta}_{fm}
-+ L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bb}) + \cos(\Theta_{fb})\cos(\Theta_{bb})\Big)\dot{\Theta}_{fb}= \\
-\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bb}))
-+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bb}))
-\end{multline}
-
-This is the form we want. We now know the value of $A_1, A_2, A_3, A_4$ and $X_1$.
-
-\begin{align}
-  A_1 &= -4L_{s}\\
-  A_2 &= -3L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{bb}) + \cos(\Theta_{bm})\cos(\Theta_{bb})\Big)\\
-  A_3 &= 2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bb}) + \cos(\Theta_{fm})\cos(\Theta_{bb})\Big)\\
-  A_4 &= L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bb}) + \cos(\Theta_{fb})\cos(\Theta_{bb})\Big)\\
-  X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bb}))+\\
-      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bb}))
-\end{align}
-
-\subsection{Solving for $B_1$, $B_2$, $B_3$, $B_4$ and $X_2$}
-Here we take Equations (\ref{eq:Bx}) and (\ref{eq:By}), equate them and manipulate them to be in form $B_1\dot{\Theta}_{bb} + B_2 \dot{\Theta}_{bm} + B_3 \dot{\Theta}_{fm} + B_4 \dot{\Theta}_{fb} = X_2$
-
-\begin{multline}
--\frac{1}{\gamma}\lambda_{bt} =
-\Big(
-\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
-- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} 
-- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xt } - R_{xmr} - R_{xbr}\Big) \frac{1}{(X_{t } - X_{bm})}
-\end{multline}
-
-\begin{multline}
--\frac{1}{\gamma}\lambda_{bt} =
-\Big(
-\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
-+ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} 
-- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yt} - R_{ymr} - R_{ybr}\Big) \frac{1}{(Y_{t } - Y_{bm})}
-\end{multline}
-
-\begin{multline}
-\Big(
-\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
-- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} 
-- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xt } - R_{xmr} - R_{xbr}\Big)(Y_{t } - Y_{bm}) =\\
-\Big(
-\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
-+ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} 
-- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yt} - R_{ymr} - R_{ybr}\Big)(X_{t } - X_{bm})
-\end{multline}
-
-\begin{multline}
-\Big(
-\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
-- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} 
-- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
-- R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{bm})) =\\
-\Big(
-\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
-+ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} 
-- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
-- R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
-\end{multline}
-
-\begin{multline}
-\Big(\dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm}
-- L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\sin(\Theta_{bm}))\\
-- \Big(\dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm} 
-+ L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\cos(\Theta_{bm})) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
-- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
-\end{multline}
-
-\begin{multline}
-\Big( -3L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}
-+ L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\sin(\Theta_{bm}))\\
-- \Big( 3L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} -2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}
-- L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\cos(\Theta_{bm})) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
-- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
-\end{multline}
-
-\begin{multline}
-\Big( -3L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}
-+ L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\sin(\Theta_{bm}))\\
-+ \Big(-3L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}
-+ L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_t\cos(\Theta_{bm})) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
-+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
-\end{multline}
-
-\begin{multline}
-\Big( -3L_{s}\sin(\Theta_{bb})L_t\sin(\Theta_{bm})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})L_t\sin(\Theta_{bm})\dot{\Theta}_{bm}
-+ 2L_{t}\sin(\Theta_{fm})L_t\sin(\Theta_{bm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})L_t\sin(\Theta_{bm})\dot{\Theta}_{fb}\Big)\\
-+ \Big(-3L_{s}\cos(\Theta_{bb})L_t\cos(\Theta_{bm})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})L_t\cos(\Theta_{bm})\dot{\Theta}_{bm}
-+ 2L_{t}\cos(\Theta_{fm})L_t\cos(\Theta_{bm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})L_t\cos(\Theta_{bm})\dot{\Theta}_{fb}\Big) =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{bm}))
-+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{bm}))
-\end{multline}
-
-\begin{multline}
--3L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{bm}) + \cos(\Theta_{bb})\cos(\Theta_{bm})\Big)\dot{\Theta}_{bb}
--3L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{bm}) + \cos(\Theta_{bm})\cos(\Theta_{bm})\Big)\dot{\Theta}_{bm}\\
-+2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bm}) + \cos(\Theta_{fm})\cos(\Theta_{bm})\Big)\dot{\Theta}_{fm}
-+ L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bm}) + \cos(\Theta_{fb})\cos(\Theta_{bm})\Big)\dot{\Theta}_{fb} =\\
-\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bm}))
-+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{bm}))
-\end{multline}
-
-\begin{align}
-  B_1 &= -3L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{bm}) + \cos(\Theta_{bb})\cos(\Theta_{bm})\Big)\\
-  B_2 &= -3L_{t}\\
-  B_3 &= +2L_{t}\Big(\sin(\Theta_{fm})\sin(\Theta_{bm}) + \cos(\Theta_{fm})\cos(\Theta_{bm})\Big)\\
-  B_4 &= + L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{bm}) + \cos(\Theta_{fb})\cos(\Theta_{bm})\Big)\\
-  X_2 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bm}))\\
-      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{bm}))
-\end{align}
-
-\subsection{Solving for $C_1$, $C_2$, $C_3$, $C_4$ and $X_3$}
-Here we take Equations (\ref{eq:Cx}) and (\ref{eq:Cy}), equate them and manipulate them to be in form $ C_1\dot{\Theta}_{bb} + C_2 \dot{\Theta}_{bm} + C_3 \dot{\Theta}_{fm} + C_4 \dot{\Theta}_{fb} = X_3$
-
-\begin{equation}
--\frac{1}{\gamma}\lambda_{ft} = \Big( \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big) \frac{1}{(X_{fm} - X_{t })}
-\end{equation}
-
-\begin{equation}
--\frac{1}{\gamma}\lambda_{ft} = \Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{fm} - Y_{t })}
-\end{equation}
-
-\begin{multline}
-\Big( \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
-+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(-L_{t}\sin(\Theta_{fm})) = \\
-\Big( \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr}
-+ \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(-L_{t}\cos(\Theta_{fm}))
-\end{multline}
-
-\begin{multline}
-\Big( \dot{X}_{t } + \dot{X}_{fm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm}) +
-\Big(- R_{xmr} - \frac{1}{\gamma}F_{xmr} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm}) = \\
-\Big(\dot{Y}_{t } + \dot{Y}_{fm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) +
-\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm})
-\end{multline}
-
-\begin{multline}
-\Big( \dot{X}_{t } + \dot{X}_{fm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm})
-+ \Big(-\dot{Y}_{t } - \dot{Y}_{fm} + L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) = \\
-\Big(- R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm})
-+ \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
-\end{multline}
-
-\begin{multline}
-\Big(- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + -L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} +
-L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} +L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm}) \\
-+ \Big(-(L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}) -(L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} -
-L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}) + L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) =\\
-\Big(-R_{ymr} - \frac{1}{\gamma}F_{ymr} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + \frac{1}{\gamma}F_{xmr} + R_{xbr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
-\end{multline}
-
-\begin{multline}
-\Big(-2L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 2L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}
-+ L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \Big)\sin(\Theta_{fm}) \\
-+ \Big(-2L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 2L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}
-+ L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)\cos(\Theta_{fm}) =\\
-\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
-\end{multline}
-
-\begin{multline}
-\Big(-2L_{s}\sin(\Theta_{bb})\sin(\Theta_{fm})\dot{\Theta}_{bb} - 2L_{t}\sin(\Theta_{bm})\sin(\Theta_{fm})\dot{\Theta}_{bm}
-+ 2L_{t}\sin(\Theta_{fm})\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\sin(\Theta_{fm})\dot{\Theta}_{fb} \Big)\\
-+ \Big(-2L_{s}\cos(\Theta_{bb})\cos(\Theta_{fm})\dot{\Theta}_{bb} - 2L_{t}\cos(\Theta_{bm})\cos(\Theta_{fm})\dot{\Theta}_{bm}
-+ 2L_{t}\cos(\Theta_{fm})\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\cos(\Theta_{fm})\dot{\Theta}_{fb}\Big) =\\
-\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
-\end{multline}
-
-\begin{multline}
-- 2L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{fm}) + \cos(\Theta_{bb})\cos(\Theta_{fm})\Big)\dot{\Theta}_{bb}
-- 2L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{fm}) + \cos(\Theta_{bm})\cos(\Theta_{fm})\Big)\dot{\Theta}_{bm}\\
-+ 2L_{t}\Big(\sin^2(\Theta_{fm}) + \cos^2(\Theta_{fm})\Big)\dot{\Theta}_{fm}
-+ L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{fm}) + \cos(\Theta_{fb})\cos(\Theta_{fm})\Big)\dot{\Theta}_{fb} =\\
-\Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
-+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
-\end{multline}
-
-\begin{align}
-  C_1 &= - 2L_{s}\Big(\sin(\Theta_{bb})\sin(\Theta_{fm}) + \cos(\Theta_{bb})\cos(\Theta_{fm})\Big) \\
-  C_2 &= - 2L_{t}\Big(\sin(\Theta_{bm})\sin(\Theta_{fm}) + \cos(\Theta_{bm})\cos(\Theta_{fm})\Big) \\
-  C_3 &= 2L_{t} \\
-  C_4 &= L_{s}\Big(\sin(\Theta_{fb})\sin(\Theta_{fm}) + \cos(\Theta_{fb})\cos(\Theta_{fm})\Big) \\
-  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{fm})\\
-      &+ \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{fm})
-\end{align}
-
-\subsection{Solving for $D_1$, $D_2$, $D_3$, $D_4$ and $X_4$}
-Here we take Equations (\ref{eq:Dx}) and (\ref{eq:Dy}), equate them and manipulate them to be in form $D_1\dot{\Theta}_{bb} + D_2 \dot{\Theta}_{bm} + D_3 \dot{\Theta}_{fm} + D_4 \dot{\Theta}_{fb} = X_4$.
-
-\begin{equation}
--\frac{1}{\gamma}\lambda_{fs} = \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) \frac{1}{(Y_{fb} - Y_{fm})}
-\end{equation}
-
-\begin{equation}
--\frac{1}{\gamma}\lambda_{fs} = \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) \frac{1}{(X_{fb} - X_{fm})}
-\end{equation}
-
-\begin{equation}
-  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (X_{fb} - X_{fm}) =
-  \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (Y_{fb} - Y_{fm})
-\end{equation}
-
-\begin{equation}
-  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (-L_s\cos{\Theta_{fb}}) =
-  \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (-L_s\sin{\Theta_{fb}})
-\end{equation}
-
-\begin{equation}
-  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{fb}}) =
-  \big( \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{fb}})
-\end{equation}
-
-\begin{equation}
-  \big( \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\big)(\cos{\Theta_{fb}}) + \big(-\dot{X}_{fm} - L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\big)(\sin{\Theta_{fb}}) =
-  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{fb}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{fb}})
-\end{equation}
-
-\begin{multline}
-  \big(L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\big)(\cos{\Theta_{fb}})\\
-+ \big(L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\big)(\sin{\Theta_{fb}}) = \\
-  \big(- R_{xbr} - \frac{1}{\gamma}F_{xbr} \big) (\sin{\Theta_{fb}}) + \big(R_{ybr} + \frac{1}{\gamma}F_{ybr}\big) (\cos{\Theta_{fb}})
-\end{multline}
-
-\begin{multline}
-  L_{s}(\cos(\Theta_{fb})\cos(\Theta_{bb}) + \sin(\Theta_{fb})\sin(\Theta_{bb}))\dot{\Theta}_{bb}
-  + L_{t}(\cos(\Theta_{fb})\cos(\Theta_{bm}) + \sin(\Theta_{fb})\sin(\Theta_{bm}))\dot{\Theta}_{bm} \\
-  - L_{t}(\cos(\Theta_{fb})\cos(\Theta_{fm}) + \sin(\Theta_{fb})\sin(\Theta_{fm}))\dot{\Theta}_{fm}
-  - L_{s}(\cos^2(\Theta_{fb}) + \sin^2(\Theta_{fb}))\dot{\Theta}_{fb} = \\
-  (R_{ybr} + \frac{1}{\gamma}F_{ybr}) (\cos{\Theta_{fb}}) - (R_{xbr} + \frac{1}{\gamma}F_{xbr} ) (\sin{\Theta_{fb}})
-\end{multline}
-
-\begin{align}
-  D_1 &= L_{s}\Big(\cos(\Theta_{fb})\cos(\Theta_{bb}) + \sin(\Theta_{fb})\sin(\Theta_{bb})\Big)\\
-  D_2 &= L_{t}\Big(\cos(\Theta_{fb})\cos(\Theta_{bm}) + \sin(\Theta_{fb})\sin(\Theta_{bm})\Big)\\
-  D_3 &= -L_{t}\Big(\cos(\Theta_{fb})\cos(\Theta_{fm}) + \sin(\Theta_{fb})\sin(\Theta_{fm})\Big)\\
-  D_4 &= -L_{s}\\
-  X_4 &= (R_{ybr} + \frac{1}{\gamma}F_{ybr})\cos{\Theta_{fb}} - (R_{xbr} + \frac{1}{\gamma}F_{xbr})\sin(\Theta_{fb})
-\end{align}
-
-\section{CAS solution to Matrix Equation}
-
-We now have our equations in the following form:
-
-\begin{equation}
-  \begin{pmatrix}
-    A_1 & A_2 & A_3 & A_4 \\
-    B_1 & B_2 & B_3 & B_4 \\
-    C_1 & C_2 & C_3 & C_4 \\
-    D_1 & D_2 & D_3 & D_4 \\    
-  \end{pmatrix}
-\times
-  \begin{pmatrix}
-    \Theta_{bb} \\
-    \Theta_{bm} \\
-    \Theta_{fm} \\
-    \Theta_{fb} \\
-  \end{pmatrix}
-=
-  \begin{pmatrix}
-    X_1 \\
-    X_2 \\
-    X_3 \\
-    X_4 \\
-  \end{pmatrix}
-\end{equation}
-
-We use a CAS (Mathematica) to solve this equation for the angular velocities. We arrive at the following expressions, which we have broken up into numerator and denominator for legibility:
-
-\begin{align}
-\dot{\Theta}_{bb} &= \frac{N_{bb}}{D} \\
-\dot{\Theta}_{bm} &= \frac{N_{bm}}{D} \\
-\dot{\Theta}_{fm} &= \frac{N_{fm}}{D} \\
-\dot{\Theta}_{fb} &= \frac{N_{fb}}{D}
-\end{align}
-
-\begin{multline}
-N_{bb} =
-(-B_2 C_4 D_3 X_1 + B_2 C_3 D_4 X_1 + A_4 C_3 D_2 X_2 - A_3 C_4 D_2 X_2 - A_4 C_2 D_3 X_2 + A_2 C_4 D_3 X_2 +\\
- A_3 C_2 D_4 X_2 - A_2 C_3 D_4 X_2 + A_4 B_2 D_3 X_3 - A_3 B_2 D_4 X_3 - A_4 B_2 C_3 X_4 + A_3 B_2 C_4 X_4 +\\
-B_4 (-C_3 D_2 X_1 + C_2 D_3 X_1 + A_3 D_2 X_3 - A_2 D_3 X_3 - A_3 C_2 X_4 + A_2 C_3 X_4) + B_3 (C_4 D_2 X_1 - \\
-C_2 D_4 X_1 - A_4 D_2 X_3 + A_2 D_4 X_3 + A_4 C_2 X_4 - A_2 C_4 X_4)) \\
-\end{multline}
-
-\begin{multline}
-N_{bm} =
-(B_1 C_4 D_3 X_1 - B_1 C_3 D_4 X_1 - A_4 C_3 D1 X_2 + A_3 C_4 D1 X_2 + A_4 C_1 D_3 X_2 - A_1 C_4 D_3 X_2 - \\
-A_3 C_1 D_4 X_2 + A_1 C_3 D_4 X_2 - A_4 B_1 D_3 X_3 + A_3 B_1 D_4 X_3 + A_4 B_1 C_3 X_4 - A_3 B_1 C_4 X_4 +\\
-B_4 (C_3 D1 X_1 - C_1 D_3 X_1 - A_3 D1 X_3 + A_1 D_3 X_3 + A_3 C_1 X_4 - A_1 C_3 X_4) + B_3 (-C_4 D1 X_1 + \\
-C_1 D_4 X_1 + A_4 D1 X_3 - A_1 D_4 X_3 - A_4 C_1 X_4 + A_1 C_4 X_4)) \\
-\end{multline}
-
-\begin{multline}
-N_{fm} =
-(-B_1 C_4 D_2 X_1 + B_1 C_2 D_4 X_1 + A_4 C_2 D1 X_2 - A_2 C_4 D1 X_2 - A_4 C_1 D_2 X_2 + A_1 C_4 D_2 X_2 + \\
-A_2 C_1 D_4 X_2 - A_1 C_2 D_4 X_2 + A_4 B_1 D_2 X_3 - A_2 B_1 D_4 X_3 - A_4 B_1 C_2 X_4 + A_2 B_1 C_4 X_4 +\\
-B_4 (-C_2 D1 X_1 + C_1 D_2 X_1 + A_2 D1 X_3 - A_1 D_2 X_3 - A_2 C_1 X_4 + A_1 C_2 X_4) + \\
-B_2 (C_4 D1 X_1 - C_1 D_4 X_1 - A_4 D1 X_3 + A_1 D_4 X_3 + A_4 C_1 X_4 - A_1 C_4 X_4)) \\
-\end{multline}
-
-\begin{multline}
-N_{fb} =
-(B_1 C_3 D_2 X_1 - B_1 C_2 D_3 X_1 - A_3 C_2 D1 X_2 + A_2 C_3 D1 X_2 + A_3 C_1 D_2 X_2 - A_1 C_3 D_2 X_2 - \\
-A_2 C_1 D_3 X_2 + A_1 C_2 D_3 X_2 - A_3 B_1 D_2 X_3 + A_2 B_1 D_3 X_3 + A_3 B_1 C_2 X_4 - A_2 B_1 C_3 X_4 +\\
-B_3 (C_2 D1 X_1 - C_1 D_2 X_1 - A_2 D1 X_3 + A_1 D_2 X_3 + A_2 C_1 X_4 - A_1 C_2 X_4) + \\
-B_2 (-C_3 D1 X_1 + C_1 D_3 X_1 + A_3 D1 X_3 - A_1 D_3 X_3 - A_3 C_1 X_4 + A_1 C_3 X_4)) \\
-\end{multline}
-
-\begin{multline}
-D = (A_2 B_4 C_3 D1 - A_2 B_3 C_4 D1 - A_1 B_4 C_3 D_2 + A_1 B_3 C_4 D_2 - A_2 B_4 C_1 D_3 + A_1 B_4 C_2 D_3 + \\
-A_2 B_1 C_4 D_3 - A_1 B_2 C_4 D_3 + A_4 (B_3 C_2 D1 - B_2 C_3 D1 - B_3 C_1 D_2 + B_1 C_3 D_2 + B_2 C_1 D_3 - B_1 C_2 D_3) + \\
-A_2 B_3 C_1 D_4 - A_1 B_3 C_2 D_4 - A_2 B_1 C_3 D_4 + A_1 B_2 C_3 D_4 + A_3 (-B_4 C_2 D1 + B_2 C_4 D1 + B_4 C_1 D_2 - B_1 C_4 D_2 - B_2 C_1 D_4 + B_1 C_2 D_4))
-\end{multline}
-
-\clearpage
-{\huge Bothbound Solution} \\
-We now do a similar solution for velocities in the case where both of the model's binding domains are stuck to the microtubule.
-
-\begin{figure}[h!]
-  \caption{Key lengths and angles in bothbound dynein model.}
-  \centering
-    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
-\end{figure}
-
-\section{Cartesian Coordinate Derivation}
-
-By the law of cosines:
-\begin{align}
-  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
-  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
-\end{align}
-
-By the law of cosines, we see that:
-\begin{align}
-  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
-  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
-\end{align}
-
-We now note the time derivatives of $\Theta$. We don't use them explicitly here, as we will be solving for $\dot{L_n}$ and $\dot{L_f}$ for simplicity. We will need these $\Theta$ derivatives later.
-
-\begin{align}
-  \dot{\Theta_{1}} &= \frac{1}{\sqrt{1-\left(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\right)^2}}\left(\frac{2L_n\dot{L_n} - 2L_f\dot{L_f}}{2LL_n}\right)\left(\frac{L^2+L_n^2-L_f^2}{-2LL_n^2\dot{L_n}}\right)\\
-  \dot{\Theta_{2}} &= \pm \frac{1}{\sqrt{1-\left(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\right)^2}}\left(\frac{L_n\dot{L_n}}{L_s}\right)\left(\frac{L_s^2+L_{n}^2-L_t^2}{-2L_sL_n^2\dot{L_n}}\right)\\
-\end{align}
-
-\subsection{Solving for $X_{nm}$ and $Y_{nm}$}
-
-\begin{align}
-  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
-     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
-     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
-  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
-     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
-     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
-\end{align}
-
-We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
-cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
-and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:
-
-\begin{align}
-  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-\end{align}
-
-We simplify further...
-
-\begin{align}
-  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-\end{align}
-
-\begin{align}
-  X_{nm} &= \frac{1}{4LL_n^2}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-\end{align}
-
-\begin{align}
-  X_{nm} &= \frac{L_s^2L^2 + L_n^2L^2 - L_t^2L^2 + L_s^2L_{n}^2 + L_n^2L_{n}^2 - L_t^2L_{n}^2 - L_s^2L_{f}^2 - L_n^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L}\\
-  &\mp L_s\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_{n}^2}}*\\
-  &\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_s^2L_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_{s}^2L_{n}^2}}\\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L^2_{n}}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_n^4 + L_t^4 + 2L_s^2L_n^2 - 2L_s^2L_t^2 - 2L_n^2L_f^2}{4L^2_{s}L^2_{n}}}\\
-\end{align}
-
-\begin{align}
-  X_{nm} &= \frac{L_s^2L^2 - L_t^2L^2}{4L_n^2L} + \frac{-L_s^2L_{f}^2 + L_t^2L_{f}^2}{4L_n^2L} + \frac{L + L_s^2 + L_n^2 - L_t^2 - L_{f}^2}{4L}\\
-  &\mp L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}*\\
-  &\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}\\  
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
-\end{align}
-
-Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.
-
-\begin{align}
-  \dot{X}_{nm} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L}\dot{L}_n + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L}\dot{L}_f + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\dot{L}_n\\
-  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3}\dot{L}_n - \frac{L_f^3 - L^2L_f}{L^2L_n^2}\dot{L}_f + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3}\dot{L}_n - \frac{L_n}{2L^2}\dot{L}_n + \frac{L_f}{L^2}\dot{L}_f\right)\\
-  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
-  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3}\dot{L}_n - \frac{L_n}{2L_s^2}\dot{L}_n\right)
-\end{align}
-
-\begin{align}
-  \dot{Y}_{nm} &= \left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\dot{L}_n\\
-  &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3}\dot{L}_n - \frac{L_f^3 - L^2L_f}{L^2L^2_{n}}\dot{L}_f + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n}\dot{L}_n - \frac{L_n}{2L^2}\dot{L}_n + \frac{L_f}{L^2}\dot{L}_f\right)\\
-  &\pm L_s\left(\frac{1}{L}\dot{L}_n - \frac{L_f}{LL_{n}}\dot{L}_f - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\dot{L}_n\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
-  &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3}\dot{L}_n - \frac{L_n}{2L_s^2}\dot{L}_n + \frac{L_f}{L_s^2}\dot{L}_f\right)
-\end{align}
-
-\begin{align}
-  \dot{X}_{nm} &= \Bigg[\frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L} + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L} + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\\
-  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3} - \frac{L_n}{2L^2}\right)\\
-  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
-  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3} - \frac{L_n}{2L_s^2}\right)\Bigg]\dot{L}_n\\
-  &\mp \Bigg[L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L_n^2} + \frac{L_f}{L^2}\right)\Bigg]\dot{L}_f\\
-\end{align}
-
-\begin{align}
-  \dot{Y}_{nm} &= \bigg[\left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
-    &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n} - \frac{L_n}{2L^2}\right)\\
-    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3} - \frac{L_n}{2L_s^2}\right)
-  \bigg]\dot{L}_n\\
-  &+\bigg[\frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L^2_{n}} + \frac{L_f}{L^2}\right)\\
-    &\pm L_s\left(-\frac{L_f}{LL_{n}}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_f}{L_s^2}\right)
-  \bigg]\dot{L}_f
-\end{align}
-
-\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
-The only way to differentiate the near- and far-bound sides of the molecule is by looking at the definition of $L_n$ and $L_f$.
-Because of this, to calculate the values of $X_{fm}$ and $Y_{fm}$, we can just switch all instances of $L_n$ and $L_f$.
-
-\begin{align}
-  \dot{X}_{fm} &= \Bigg[\frac{-L_s^2L^2 + L_t^2L^2}{2L_f^3L} + \frac{-L_s^2L_n + L_t^2L_n}{2L_f^2L} + \frac{L_s^2L_n^2 - L_t^2L_n^2}{2L_f^3L}\\
-  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
-  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
-  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_f^3} - \frac{L_f}{2L_s^2}\right)\Bigg]\dot{L}_f\\
-  &\mp \Bigg[L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L_f^2} + \frac{L_n}{L^2}\right)\Bigg]\dot{L}_n\\
-\end{align}
-
-\begin{align}
-  \dot{Y}_{fm} &= \bigg[\left(1 - \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2}\right)\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}\\
-    &+ \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
-    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_f^2-L_n^2}{2LL_f^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_f^3} - \frac{L_f}{2L_s^2}\right)
-  \bigg]\dot{L}_f\\
-  &+\bigg[\frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L^2_{n}} + \frac{L_n}{L^2}\right)\\
-    &\pm L_s\left(-\frac{L_n}{LL_f}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_n}{L_s^2}\right)
-  \bigg]\dot{L}_n
-\end{align}
-
-\subsection{Solving for $X_t$ and $Y_t$}
-
-\begin{align}
-  X_{t} &= L_n\cos(\Theta_{1}) \\
-  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
-  \dot{X}_t &= \frac{L_n}{L}\dot{L}_n - \frac{L_f}{L}\dot{L}_f\\
-\end{align}
-
-\begin{align}
-  Y_{t} &= L_n\sin(\Theta_{1}) \\
-  &= L_n\sin\left(\cos^{-1}\left(\frac{L^2+L_n^2-L_f^2}{2LL_n}\right)\right) \\
-  &= L_n\sqrt{1 - \left(\frac{L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
-  &= \sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2} \\
-  \dot{Y}_t &= \frac{2L_n\dot{L}_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n\dot{L}_n - L_f\dot{L}_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
-  \dot{Y}_t &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\dot{L}_n +
-  \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\dot{L}_f\\
-\end{align}
-
-\section{Cartesian from Angular Coordinates}
-This section lays out the definitions of the coordinates of the Dynein model. \\
-\begin{align}
-  X_{nb} &= 0 \\
-  X_{nm} &= \frac{1}{4LL_n^2}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
-  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
-  X_{fm} &= \frac{1}{4LL_f^2}\Big(L^2+L_f^2-L_n^2\Big)\Big(L_{s}^2+L_f^2-L_{t}^2\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_f^2-L_n^2}{2LL_f}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_{s}L_f}\bigg)^2}\\
-  X_{fb} &= L \\
-\end{align}
-
-\begin{align}
-  Y_{nb} &= 0 \\
-  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
-  Y_{t}  &= L_n\sqrt{1 - \left(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
-  Y_{fm} &= \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\sqrt{1-\bigg(\frac{L^2+L_f^2-L_n^2}{2LL_f}\bigg)^2} \pm L_s\frac{L^2+L_f^2-L_n^2}{2LL_f}\sqrt{1-\bigg(\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_{s}L_f}\bigg)^2} \Bigg)\\
-  Y_{fb} &= 0
-\end{align}
-
-\section{Cartesian Velocities}
-This section shows the velocity definitions. \\
-
-\subsection{Velocity Coefficients}
-This subsection defines the coeffients to be used in further derivation.\\
-
-\begin{align}
-  \dot{X}_{nb} &= 0 \\
-  \dot{X}_{nm} &= A_{xn}\dot{L}_n + A_{xf}\dot{L}_f\\
-  \dot{X}_{t } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
-  \dot{X}_{fm} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f\\
-  \dot{X}_{fb} &= 0
-\end{align}
-
-\begin{align}                                                                          
-  \dot{Y}_{nb} &= 0 \\                           
-  \dot{Y}_{nm} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
-  \dot{Y}_{t}  &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
-  \dot{Y}_{fm} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f\\
-  \dot{Y}_{fb} &= 0 \\
-\end{align}
-
-\begin{align}
-  A_{xn} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_n^3L} + \frac{-L_s^2L_{f} + L_t^2L_{f}}{2L_n^2L} + \frac{L_s^2L_{f}^2 - L_t^2L_{f}^2}{2L_n^3L}\\
-  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L_n^3} - \frac{L_n}{2L^2}\right)\\
-  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
-  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_{n}^3} - \frac{L_n}{2L_s^2}\right)\\
-  A_{xf} &= \mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_{n}^2} - \frac{L_n^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_n^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L_n^2} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L_n^2} + \frac{L_f}{L^2}\right)\\
-  B_{xn} &= \frac{L_n}{L}\\
-  B_{xf} &= - \frac{L_f}{L}\\
-\end{align}
-\begin{align}
-  C_{xn} &= \mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L_f^2} + \frac{L_n}{L^2}\right)\\
-  C_{xf} &= \frac{-L_s^2L^2 + L_t^2L^2}{2L_f^3L} + \frac{-L_s^2L_n + L_t^2L_n}{2L_f^2L} + \frac{L_s^2L_n^2 - L_t^2L_n^2}{2L_f^3L}\\
-  &\mp L_s\frac{\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}{2\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
-  &\mp \frac{L_s\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L_f^2} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}{2\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_{s}^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_t^2}{4L_s^2}}}
-  \left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_{s}^2L_f^3} - \frac{L_f}{2L_s^2}\right)\\
-\end{align}
-\begin{align}
-  A_{yn} &= \left(1 - \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2}\right)\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}\\
-    &+ \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(\frac{L^2}{2L_n^3} + \frac{L_f^4 - 2L^2L_f^2}{2L^2L^3_n} - \frac{L_n}{2L^2}\right)\\
-    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_{n}^2-L_{f}^2}{2LL_n^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_n^3} - \frac{L_n}{2L_s^2}\right)\\
-  A_{yf} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{4L_{n}\sqrt{1 - \frac{L^2}{4L_{n}^2} - \frac{L_f^4 - 2L^2L_f^2}{4L^2L^2_{n}} - \frac{L_n^2 + 2L^2 - 2L_f^2}{4L^2}}}\left(-\frac{L_f^3 - L^2L_f}{L^2L^2_{n}} + \frac{L_f}{L^2}\right)\\
-    &\pm L_s\left(-\frac{L_f}{LL_{n}}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{4LL_{n}\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_n^2} - \frac{L_n^2 + 2L_s^2 - 2L_f^2}{4L_s^2}}}\left(\frac{L_f}{L_s^2}\right)\\
-  B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
-  B_{yf} &= \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
-\end{align}
-\begin{align}
-  C_{yn} &= \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(-\frac{L_n^3 - L^2L_n}{L^2L^2_{n}} + \frac{L_n}{L^2}\right)\\
-    &\pm L_s\left(-\frac{L_n}{LL_f}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_n}{L_s^2}\right)\\
-  C_{yf} &= \left(1 - \frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2}\right)\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}\\
-    &+ \frac{L_{s}^2+L_f^2-L_{t}^2}{4L_f\sqrt{1 - \frac{L^2}{4L_f^2} - \frac{L_n^4 - 2L^2L_n^2}{4L^2L^2_{n}} - \frac{L_f^2 + 2L^2 - 2L_n^2}{4L^2}}}\left(\frac{L^2}{2L_f^3} + \frac{L_n^4 - 2L^2L_n^2}{2L^2L_f^3} - \frac{L_f}{2L^2}\right)\\
-    &\pm L_s\left(\frac{1}{L} - \frac{L^2+L_f^2-L_n^2}{2LL_f^2}\right)\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}\\
-    &\pm L_s\frac{L^2+L_f^2-L_n^2}{4LL_f\sqrt{1 - \frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{4L_s^2L_f^2} - \frac{L_f^2 + 2L_s^2 - 2L_n^2}{4L_s^2}}}\left(\frac{L_s^4 + L_t^4 - 2L_s^2L_t^2}{2L_s^2L_f^3} - \frac{L_f}{2L_s^2}\right)\\
-\end{align}
-
-\section{System of Equations}
-This section creates a system of equations by equating the Brownian dynamics equations for velocity with the derivatives we just found.
-
-\begin{align}  
-  \dot{X}_{bm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}  &= A_{nx}\dot{L}_n + A_{fx}\dot{L}_f\\
-  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
-  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f
-\end{align}
-
-\begin{align}  
-  \dot{Y}_{bm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
-  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
-  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f
-\end{align}
-
-\section{Matrix Solution via Mathematica}
-Here we convert the above system into matrix form, solve it in Mathematica and list the results.
-
-\[
-\begin{pmatrix}
-  -A_{xn} & -A_{xf} & -\frac{X_{bm}-X_{bb}}{\gamma} & \frac{X_{t}-X_{bm}}{\gamma} & 0 & 0\\
-  -B_{xn} & -B_{xf} & 0 & -\frac{X_{t}-X_{bm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
-  -C_{xn} & -C_{xf} & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
-  -A_{yn} & -A_{yf} & -\frac{Y_{bm}-Y_{bb}}{\gamma} & \frac{Y_{t}-Y_{bm}}{\gamma} & 0 & 0\\
-  -B_{yn} & -B_{yf} & 0 & -\frac{Y_{t}-Y_{bm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
-  -C_{yn} & -C_{yf} & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
-\end{pmatrix}
-\begin{pmatrix}
-  \dot{L}_n\\
-  \dot{L}_f\\
-  \lambda_{bs}\\
-  \lambda_{bt}\\
-  \lambda_{ft}\\
-  \lambda_{fs}\\
-\end{pmatrix}
-=
-\begin{pmatrix}
-  -\frac{F_{xml}}{\gamma} - R_{xml}\\
-  -\frac{F_{xt}}{\gamma} - R_{xt}\\
-  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
-  -\frac{F_{yml}}{\gamma} - R_{yml}\\
-  -\frac{F_{yt}}{\gamma} - R_{yt}\\
-  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
-\end{pmatrix}
-\]
-
-\begin{twocolumn}
-\section{Notes on physical parameters}
-
-Stoke's Law states that the relationship between viscosity, force, and
-velocity for a spherical particle is given by:
-\begin{align}
-  \mathbf{v} &= \frac{\mathbf{F}}{6\pi \mu R}
-\end{align}
-where $\mu$ is the viscosity of the fluid, and $R$ is the radius of
-the particle.  Thus in our terminology:
-\begin{align}
-  \gamma &= 6\pi \mu R.
-\end{align}
-Note that the viscosity of water is temperature-dependent and around
-0.7~mPa~s at body temperature.  However, the viscosity of cytoplasm
-may be rather different, and will of course depend on length scale.
-But for our purposes we can probably get away with this value.
-
-The random force $\mathbf{R}(t)$ should have a Gaussian distribution
-with variance~1, but then be divided by $\sqrt{\Delta t}$.  Thus, the
-smaller the time step, the larger the random force we will apply.  We
-can understand this in the backwards direction.  When we observe a
-larger time step, the ``random force'' results from many smaller
-random forces added together, and these smaller forces often cancel,
-leading to this reduction in the total force over that time period.
-
-Finally, we will need estimates for the radii of each domain (to go
-into the $\gamma$ parameter, the equilibrium angles for each hinge, and
-the spring constants for each hinge.  The first two we can estimate
-from the structure of dynein.  The third will require a rough guess.
-We can get a ball-park guess by deciding how much we want the angle to
-fluctuate (e.g. $\ll \pi$ for each angle!), and then take our spring
-constant to be $kT$ divided by that anglular fluctuation squared.
-
-\end{twocolumn}
+\includegraphics[width=3cm]{../figures/code-bothbound}
 

### 2016-01-12 figures/fac.py

@@ -1,0 +1,8 @@
+#!/usr/bin/python2
+
+import glob
+
+for svg in glob.glob('*.svg'):
+    print "| inkscape -D --export-pdf %s %s" % (svg[:-3]+'pdf', svg)
+    print "C ~/.config"
+    print

### 2016-01-29 latex/paper.tex
a bit of inkscape to make the illustration for bothbound case.
a bit more diagramming
fix one word in text
edits from our meeting

@@
-\documentclass[11pt]{article}
+\documentclass[11pt,twocolumn]{article}
 
@@
 
-Hello world
+\section{Both bound}
 
-\includegraphics[width=3cm]{../figures/code-bothbound}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../figures/code-bothbound}
+  \caption{Angles used in both-bound case.}\label{fig:bothbound}
+\end{figure}
+
+In the both-bound case, we use two angles, as illustrated in
+Fig.~\ref{fig:bothbound}.
+
+These are the distances to the tail domain from the near and far
+binding domains:
+\begin{align}
+  L_n &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{nm}}} \\
+  L_f &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{fm}}}
+\end{align}
+We use two angles to determine the position of the motor domain:
+\begin{align}
+  \cos\theta_n &= \frac{L^2 + L_n^2 - L_f^2}{2L L_n} \\
+  \sin\theta_{n} &= \sqrt{1 - \cos^2\theta_{n}} \\
+  \cos\theta_{ns} &= \frac{L_s^2 + L_n^2 - L_t^2}{2L_s L_n} \\
+  \sin\theta_{ns} &=
+  \begin{cases}
+    +\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} < \pi \\
+    -\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} > \pi
+  \end{cases}
+\end{align}
+Given these definitions, the position of the motor domain is given
+simply by $\cos$ and $\sin$ of $\theta_n$ and $\theta_{ns}$:
+\begin{align}
+  X_{nm} &= L_s\left(
+  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
+  \right)
+  \\
+  Y_{nm} &= L_s\left(
+  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
+  \right)
+\end{align}
+Looking at their derivatives gives
+\begin{align}
+  \dot{X}_{nm} &= ??? L_s\left(
+  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
+  \right) \dot{\cos\theta_n}
+  \\
+  \dot{Y}_{nm} &= ??? L_s\left(
+  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
+  \right)
+\end{align}
+
+\section{One bound}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../figures/code-onebound}
+  \caption{Angles used in one-bound case.}\label{fig:onebound}
+\end{figure}
+
+In the one-bound case, we use four angles, as illustrated in
+Fig.~\ref{fig:onebound}.
 

### 2016-01-29 dynein_struct_bothbound.cpp

@@ -4,13 +4,17 @@
 
 #include "dynein_struct.h"
 
+inline double sqr(double x) {
+  return x*x;
+}
+
 /* ********************* BOTHBOUND DYNEIN FUNCTIONS ****************************** */
 
-Dynein::Dynein_bothbound(double nma_init, double fma_init, double nbx_init,
-			 double nby_init, double L_init,
-			 bothbound_forces* internal_test,
-			 bothbound_forces* brownian_test,
-			 bothbound_equilibrium_angles* eq_angles) {
+Dynein_bothbound::Dynein_bothbound(double nma_init, double fma_init, double nbx_init,
+                                   double nby_init, double L_init,
+                                   bothbound_forces* internal_test,
+                                   bothbound_forces* brownian_test,
+                                   bothbound_equilibrium_angles* eq_angles) {
   nbx = nbx_init;
   nby = nby_init;
 
@@ -34,9 +38,6 @@ Dynein::Dynein_bothbound(double nma_init, double fma_init, double nbx_init,
 Dynein_bothbound::Dynein_bothbound(Dynein_onebound* old_dynein, MTRand* mtrand) { // out of old dyn
   rand = mtrand;
 
-  distance_traveled = old_dynein->distance_traveled;
-  steps = old_dynein->steps;
-
   if (old_dynein->get_state() == State::NEARBOUND) {
     nbx = old_dynein->get_bbx();
     nby = 0;
[…]

### 2016-03-07 latex/paper.tex
try out some simplifications in the paper
Add minor Makefile changes.
Add PNG versions of SVGs (code-*bound), since I dont' know how to make LaTeX display SVGs.
more thoughts on simplifying math (and code!)

@@
 Looking at their derivatives gives
+\begin{multline}
+  \dot{X}_{nm} = L_s\Big(
+  \cos\theta_n\dot{\cos\theta_{ns}} + \cos\theta_{ns}\dot{\cos\theta_{n}} \\
+  - \sin\theta_n\dot{\sin\theta_{ns}} - \sin\theta_{ns}\dot{\sin\theta_{n}}
+  \Big)
+\end{multline}
+\begin{multline}
+  \dot{Y}_{nm} = L_s\Big(
+  \cos\theta_n\dot{\sin\theta_{ns}} + \sin\theta_{ns}\dot{\cos\theta_{n}} \\
+  + \sin\theta_n\dot{\cos\theta_{ns}} + \cos\theta_{ns}\dot{\sin\theta_{n}}
+  \Big)
+\end{multline}
+which we can apply the chain rule to using
 \begin{align}
-  \dot{X}_{nm} &= ??? L_s\left(
-  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
-  \right) \dot{\cos\theta_n}
-  \\
-  \dot{Y}_{nm} &= ??? L_s\left(
-  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
-  \right)
+  \dot{Y}_{nm} = \frac{\partial Y_{nm}}{\partial L_n} \dot{L_n}
+  +  \frac{\partial Y_{nm}}{\partial L_{f}} \dot{L_{f}}
 \end{align}
+and correspondingly for the $X$ formula.  So that now the interesting
+things to compute in order to relate the time derivatives of $L_n$ and
+$L_f$ to that of $Y_{nm}$ can easily be expressed in terms of these
+partial derivatives with respect to the lengths $L_n$ and $L_f$.  This
+gives us something like
+\begin{multline}
+  \frac{\partial X_{nm}}{\partial L_n} = L_s\Bigg(
+  \cos\theta_n\frac{\partial \cos\theta_{ns}}{\partial L_n}
+  + \cos\theta_{ns}\frac{\partial \cos\theta_{n}}{\partial L_n} \\
+  - \sin\theta_n\frac{\partial \sin\theta_{ns}}{\partial L_n}
+  - \sin\theta_{ns}\frac{\partial \sin\theta_{n}}{\partial L_n}
+  \Bigg)
+\end{multline}
+However, the $\sin$s of our angles are expressed in terms of the
+cosines, so we will (in practice) want to make use of the fact that
+\begin{align}
+  \frac{\partial \sin\theta_{n}}{\partial L_n} &=
+  \frac{d \sin\theta_{n}}{d \cos\theta_n}
+  \frac{\partial \cos\theta_{n}}{\partial L_n} \\
+  &=
+  -\frac{\cos\theta_{n}}{\sin\theta_n}
+  \frac{\partial \cos\theta_{n}}{\partial L_n}
+\end{align}
+Using this we could imagine simplifying our former equation using this
+expression for $\frac{\partial \sin\theta_{n}}{\partial L_n}$, but
+that would only make it harder to read and check.  Let's keep all
+chain rules and derivatives as explicit as possible!
+
+The
+corresponding C++ code could look like:
+\begin{verbatim}
+  dXnm_dLn = Ls*(cosAn*dcosAns_dLn
+                 + cosAns*dcosAn_dLn
+                 - sinAn*dsinAns_dLn
+                 - sinAns*dsinAn_dLn);
+\end{verbatim}
+Basically, we have lots of chain rules.
 

### 2016-04-02 latex/paper.tex
Add some d cos / d Ln/f derivatives to paper.tex
Add changes to paper.tex.

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../figures/code-bothbound}
+  \includegraphics[width=\columnwidth]{../figures/code-bothbound.png}
   \caption{Angles used in both-bound case.}\label{fig:bothbound}
@@
 \end{align}
+
+and the derivatives are given by:
+
+\begin{align}
+  \frac{\partial \cos\theta_n}{\partial L_n} &= \frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\\
+  \frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{LL_n}\\
+  \frac{\partial \sin\theta_n}{\partial L_n} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
+  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
+  \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
+  \left(\frac{-L_f}{LLn}\right)\\
+  \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
+  - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
+  \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
+  \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
+  \begin{cases}
+    \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
+    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
+    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
+    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
+  \end{cases}\\
+  \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0\\
+\end{align}
+
 Given these definitions, the position of the motor domain is given
@@
   \right)
+  \\
+  X_{t} &= L_n\cos\theta_n\\
+  Y_{t} &= L_n\sin\theta_n\\
 \end{align}
-Looking at their derivatives gives
+
+Looking at their derivatives gives:
+
+\begin{align}
+  \frac{dX_{nm}}{dL_n} &= L_s\Big(
+  \cos\theta_n\frac{d\cos\theta_{ns}}{dL_n}
+  + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
+  &- \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n}
+  - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
+  \Big)\\
+\end{align}
 \begin{multline}
-  \dot{X}_{nm} = L_s\Big(
-  \cos\theta_n\dot{\cos\theta_{ns}} + \cos\theta_{ns}\dot{\cos\theta_{n}} \\
-  - \sin\theta_n\dot{\sin\theta_{ns}} - \sin\theta_{ns}\dot{\sin\theta_{n}}
+  \frac{dY_{nm}}{dL_n} = L_s\Big(
+  \cos\theta_n\frac{d\sin\theta_{ns}}{dL_n}
+  + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
+  + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n}
+  + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
+  \Big)
+\end{multline}
+
+\begin{multline}
+  \frac{dX_{nm}}{dL_f} = L_s\Big(
+  \cos\theta_n\frac{d\cos\theta_{ns}}{dL_f}
+  + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} \\
+  - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f}
+  - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}
   \Big)
@@
 \begin{multline}
-  \dot{Y}_{nm} = L_s\Big(
-  \cos\theta_n\dot{\sin\theta_{ns}} + \sin\theta_{ns}\dot{\cos\theta_{n}} \\
-  + \sin\theta_n\dot{\cos\theta_{ns}} + \cos\theta_{ns}\dot{\sin\theta_{n}}
+  \frac{dY_{nm}}{dL_f} = L_s\Big(
+  \cos\theta_n\frac{d\sin\theta_{ns}}{dL_f}
+  + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} \\
+  + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f}
+  + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}
   \Big)
 \end{multline}
-which we can apply the chain rule to using
+
+\begin{align}
+  \frac{dX_{t}}{dL_n} &= \cos\theta_n\\
+  \frac{dY_{t}}{dL_n} &= \sin\theta_n\\
+  \frac{dX_{t}}{dL_f} &= 0\\
+  \frac{dY_{t}}{dL_f} &= 0\\
+\end{align}
+
+which we apply our coordinate derivatives to and get:
+
+\begin{align}
+  \frac{dX_{nm}}{dL_n} &= L_s\Big(
+  \cos\theta_n\left(\frac{1}{L_s} - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\right)\\
+  &+ \cos\theta_{ns}\left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
+  &- \sin\theta_n\frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
+  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
+  &\pm \sin\theta_{ns}
+    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
+    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right)
+  \Big)
+\end{align}
+
+which we can apply the chain rule to using:
+
 \begin{align}

### 2016-04-02 latex/derivation.tex
Add some new BOTHBOUND code. Code doesn't compile, but is getting there. Add new struct members, change how dynein_walk handles BOTHBOUND, change the way forces are stored to use BOTHBOUND names, some other changes as well.
Add incomplete bothbound velocity equations to dynein_struct_bothbound.cpp. Incomplete!

@@
 \begin{align}
-  \dot{\Theta_{1}} &= \frac{1}{\sqrt{1-\left(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\right)^2}}\left(\frac{2L_n\dot{L_n} - 2L_f\dot{L_f}}{2LL_n}\right)\left(\frac{L^2+L_n^2-L_f^2}{-2LL_n^2\dot{L_n}}\right)\\
-  \dot{\Theta_{2}} &= \pm \frac{1}{\sqrt{1-\left(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\right)^2}}\left(\frac{L_n\dot{L_n}}{L_s}\right)\left(\frac{L_s^2+L_{n}^2-L_t^2}{-2L_sL_n^2\dot{L_n}}\right)\\
+  \dot{\Theta_1} &= \frac{-1}{\sqrt{1-\left(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\right)^2}}\left(\frac{2L_n\dot{L_n} - 2L_f\dot{L_f}}{2LL_n} - \frac{L^2+L_n^2-L_f^2}{2LL_n^2}\dot{L_n}\right)\\
+  \dot{\Theta_2} &= \mp \frac{1}{\sqrt{1-\left(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\right)^2}}\left(\frac{\dot{L}_n}{L_s} - \frac{L_s^2+L_{n}^2-L_t^2}{2L_sL_n^2\dot{L_n}}\right)\\
 \end{align}
@@
 \begin{align}  
-  \dot{X}_{bm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}  &= A_{nx}\dot{L}_n + A_{fx}\dot{L}_f\\
+  \dot{X}_{nm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}  &= A_{nx}\dot{L}_n + A_{fx}\dot{L}_f\\
   \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
@@
 \begin{align}  
-  \dot{Y}_{bm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
+  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
   \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\

### 2016-04-02 latex/paper.tex
Add incomplete bothbound velocity equations to dynein_struct_bothbound.cpp. Incomplete!

@@
 
-\begin{align}
-  \frac{dX_{nm}}{dL_n} &= L_s\Big(
+\begin{multline}
+  \frac{dX_{nm}}{dL_n} = L_s\Big(
   \cos\theta_n\frac{d\cos\theta_{ns}}{dL_n}
   + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
-  &- \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n}
+  - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n}
   - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
   \Big)\\
-\end{align}
+\end{multline}
+
 \begin{multline}
@@
 \end{multline}
+
 \begin{multline}
@@
 
-which we apply our coordinate derivatives to and get:
-
-\begin{align}
-  \frac{dX_{nm}}{dL_n} &= L_s\Big(
-  \cos\theta_n\left(\frac{1}{L_s} - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\right)\\
-  &+ \cos\theta_{ns}\left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
-  &- \sin\theta_n\frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
-  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
-  &\pm \sin\theta_{ns}
-    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
-    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right)
-  \Big)
-\end{align}
-
-which we can apply the chain rule to using:
-
-\begin{align}
-  \dot{Y}_{nm} = \frac{\partial Y_{nm}}{\partial L_n} \dot{L_n}
-  +  \frac{\partial Y_{nm}}{\partial L_{f}} \dot{L_{f}}
-\end{align}
-and correspondingly for the $X$ formula.  So that now the interesting
-things to compute in order to relate the time derivatives of $L_n$ and
-$L_f$ to that of $Y_{nm}$ can easily be expressed in terms of these
-partial derivatives with respect to the lengths $L_n$ and $L_f$.  This
-gives us something like
-\begin{multline}
-  \frac{\partial X_{nm}}{\partial L_n} = L_s\Bigg(
-  \cos\theta_n\frac{\partial \cos\theta_{ns}}{\partial L_n}
-  + \cos\theta_{ns}\frac{\partial \cos\theta_{n}}{\partial L_n} \\
-  - \sin\theta_n\frac{\partial \sin\theta_{ns}}{\partial L_n}
-  - \sin\theta_{ns}\frac{\partial \sin\theta_{n}}{\partial L_n}
-  \Bigg)
-\end{multline}
-However, the $\sin$s of our angles are expressed in terms of the
-cosines, so we will (in practice) want to make use of the fact that
-\begin{align}
-  \frac{\partial \sin\theta_{n}}{\partial L_n} &=
-  \frac{d \sin\theta_{n}}{d \cos\theta_n}
-  \frac{\partial \cos\theta_{n}}{\partial L_n} \\
-  &=
-  -\frac{\cos\theta_{n}}{\sin\theta_n}
-  \frac{\partial \cos\theta_{n}}{\partial L_n}
-\end{align}
-Using this we could imagine simplifying our former equation using this
-expression for $\frac{\partial \sin\theta_{n}}{\partial L_n}$, but
-that would only make it harder to read and check.  Let's keep all
-chain rules and derivatives as explicit as possible!
-
-The
-corresponding C++ code could look like:
+The corresponding C++ code could look like:
 \begin{verbatim}
@@
 \end{verbatim}
-Basically, we have lots of chain rules.
+Basically, we have lots of chain rules.\\
+
+We then create a system of equations by equating velocities from Brownian dynamics to the velocities
+we derived above:
+
+\onecolumn
+
+\begin{align}
+  \dot{X}_{nm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb})
+  + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}
+  &= \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
+  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm})
+  + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
+  &= \frac{X_{t}}{Ln}\dot{L}_n + \frac{X_{t}}{Lf}\dot{L}_f\\
+  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t })
+  + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
+  &= \frac{X_{fm}}{Ln}\dot{L}_n + \frac{X_{fm}}{Lf}\dot{L}_f
+\end{align}
+
+\begin{align}
+  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb})
+  + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
+  &= \frac{Y_{nm}}{Ln}\dot{L}_n + \frac{Y_{nm}}{Lf}\dot{L}_f\\
+  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm})
+  + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
+  &= \frac{Y_{t}}{Ln}\dot{L}_n + \frac{Y_{t}}{Lf}\dot{L}_f\\
+  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t })
+  + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
+  &= \frac{Y_{fm}}{Ln}\dot{L}_n + \frac{Y_{fm}}{Lf}\dot{L}_f
+\end{align}
+
+\section{Matrix Solution via Mathematica}
+Here we convert the above system into matrix form, solve it in Mathematica and list the results.
+
+\[
+\begin{pmatrix}
+  -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
+  & -\frac{X_{bm}-X_{bb}}{\gamma} & \frac{X_{t}-X_{bm}}{\gamma} & 0 & 0\\
+  -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
+  & 0 & -\frac{X_{t}-X_{bm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
+  -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
+  & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
+  -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
+  & -\frac{Y_{bm}-Y_{bb}}{\gamma} & \frac{Y_{t}-Y_{bm}}{\gamma} & 0 & 0\\
+  -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
+  & 0 & -\frac{Y_{t}-Y_{bm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
+  -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}
+  & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
+\end{pmatrix}
+\begin{pmatrix}
+  \dot{L}_n\\
+  \dot{L}_f\\
+  \lambda_{bs}\\
+  \lambda_{bt}\\
+  \lambda_{ft}\\
+  \lambda_{fs}\\
+\end{pmatrix}
+=
+\begin{pmatrix}
+  -\frac{F_{xml}}{\gamma} - R_{xml}\\
+  -\frac{F_{xt}}{\gamma} - R_{xt}\\
+  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
+  -\frac{F_{yml}}{\gamma} - R_{yml}\\
+  -\frac{F_{yt}}{\gamma} - R_{yt}\\
+  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
+\end{pmatrix}
+\]
+
+\twocolumn
 

### 2016-04-02 dynein_struct_bothbound.cpp

@@ -166,168 +166,26 @@ void Dynein_bothbound::update_velocities() {
   update_internal_forces();
   update_brownian_forces();
 
-  double pm_n = 1; // plus or minus
-  double pm_f = 1;
   if (nma > M_PI) pm_n = -1;
   if (fma > M_PI) pm_f = -1;
 
-  double Axn = (pow(L, 2)*pow(lt, 2) - pow(L, 2)*pow(ls, 2)) / (2*(L*pow(Ln, 3)))
-  + (Lf*pow(lt, 2) - Lf*pow(ls, 2)) / (2*(L*pow(Ln, 2)))
-  + (pow(Lf, 2)*pow(ls, 2) - pow(Lf, 2)*pow(lt, 2)) / (2*(L*pow(Ln, 3)))
-  - ls*(pm_n*((pow(L, 2) / (2*pow(Ln, 3))
-  + (pow(Lf, 4) - 2*(pow(L, 2)*pow(Lf, 2))) / (2*(pow(L, 2)*pow(Ln, 3)))
-  - Ln / (2*pow(L, 2)))
- *sqrt((2*(pow(ls, 2)*pow(lt, 2)) - pow(ls, 4) - pow(lt, 4))
-         / (4*(pow(Ln, 2)*pow(ls, 2)))
-         + (2*pow(lt, 2) - pow(Ln, 2) - 2*pow(ls, 2)) / (4*pow(ls, 2)) + 1)))
-      / (2*sqrt(1 - pow(L, 2) / (4*pow(Ln, 2))
-  + (2*(pow(L, 2)*pow(Lf, 2)) - pow(Lf, 4)) / (4*(pow(L, 2)*pow(Ln, 2)))
-  + (2*pow(Lf, 2) - pow(Ln, 2) - 2*pow(L, 2)) / (4*pow(L, 2))))
-  - ls*(pm_n*(((pow(ls, 4) + pow(lt, 4) - 2*(pow(ls, 2)*pow(lt, 2)))
-  / (2*(pow(Ln, 3)*pow(ls, 2))) - Ln / (2*pow(ls, 2)))
- *sqrt(1 - pow(L, 2) / (4*pow(Ln, 2))
-         + (2*(pow(L, 2)*pow(Lf, 2)) - pow(Lf, 4)) / (4*(pow(L, 2)*pow(Ln, 2)))
[…]

### 2016-04-03 dynein_struct_bothbound.cpp
Add rest of new bothbound dLn, dLf calculations. TODO: Figure out why dynein immediately (?) unbinds.

@@ -166,130 +166,171 @@ void Dynein_bothbound::update_velocities() {
   update_internal_forces();
   update_brownian_forces();
 
-  if (nma > M_PI) pm_n = -1;
-  if (fma > M_PI) pm_f = -1;
-
   double cosAn = (L*L + Ln*Ln - Lf*Lf) / (2*L*Ln);
   double sinAn = sqrt(1 - cosAn*cosAn);
   double cosAns = (Ls*Ls + Ln*Ln - Lt*Lt) / (2*Ls*Ln);
   double sinAns = (nma < M_PI) ? sqrt(1-cosAns*cosAns) : -sqrt(1-cosAns*cosAns);
 
+  double cosAf = (L*L + Lf*Lf - Ln*Ln) / (2*L*Lf);
+  double sinAf = sqrt(1 - cosAf*cosAf);
+  double cosAfs = (Ls*Ls + Lf*Lf - Lt*Lt) / (2*Ls*Lf);
+  double sinAfs = (fma < M_PI) ? sqrt(1-cosAfs*cosAfs) : -sqrt(1-cosAfs*cosAfs);
+
   double dcosAn_dLn = (1/L) - (L*L + Ln*Ln - Lf*Lf) / (2*L*Ln*Ln);
   double dcosAn_dLf = -(Lf) / (L*Ln);
   double dsinAn_dLn = -cosAn / sqrt(1 - cosAn*cosAn) * (1/L - (L*L + Ln*Ln - Lf*Lf) / (2*L*Ln*Ln));
   double dsinAn_dLf = cosAn / sqrt(1 - cosAn*cosAn) * Lf / (L*Ln);
-  
+  double dcosAns_dLn = 1/Ls - (Ls*Ls + Ln*Ln - Lt*Lt) / (2*Ls*Ln*Ln);
+  double dcosAns_dLf = 0;
+  double dsinAns_dLn = (nma < M_PI) ?
+     -cosAns/sqrt(1-cosAns*cosAns) * (1/Ls - (Ls*Ls+Ln*Ln-Lt*Lt)/(2*L*Ln*Ln))
+    : cosAns/sqrt(1-cosAns*cosAns) * (1/Ls - (Ls*Ls+Ln*Ln-Lt*Lt)/(2*L*Ln*Ln));
[…]

### 2016-04-07 latex/paper.tex
Add rest of new bothbound dLn, dLf calculations. TODO: Figure out why dynein immediately (?) unbinds.
a few minor latex tweaks

@@
 \end{align}
+
+\subsection{Nearbound and Tail coordinates}
+
 We use two angles to determine the position of the motor domain:
@@
   \end{cases}\\
-  \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0\\
+  \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
 \end{align}
@@
 \begin{align}
-  \dot{X}_{nm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb})
+  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb})
   + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}
-  &= \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
-  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm})
+  &=& \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm})
   + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
-  &= \frac{X_{t}}{Ln}\dot{L}_n + \frac{X_{t}}{Lf}\dot{L}_f\\
-  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t })
+  &=& \frac{X_{t}}{Ln}\dot{L}_n + \frac{X_{t}}{Lf}\dot{L}_f\\
+  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t })
   + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
-  &= \frac{X_{fm}}{Ln}\dot{L}_n + \frac{X_{fm}}{Lf}\dot{L}_f
+  &=& \frac{X_{fm}}{Ln}\dot{L}_n + \frac{X_{fm}}{Lf}\dot{L}_f
 \end{align}
@@
 \end{align}
+
+\subsection{Farbound coordinates}
+The farbound coordinates are defined identically to the nearbound coordinates, except
+Ln and Lf coordinates switch places.
 

### 2016-04-14 latex/paper.tex
we discovered a mistake in "far" angle handling, now partially documented

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../figures/code-bothbound.png}
+  \includegraphics[width=\columnwidth]{../figures/code-bothbound}
   \caption{Angles used in both-bound case.}\label{fig:bothbound}
@@
 
+\twocolumn
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../figures/similar-bothbound}
+  \caption{Angles used in both-bound case.}\label{fig:similar}
+\end{figure}
+
 \subsection{Farbound coordinates}
-The farbound coordinates are defined identically to the nearbound coordinates, except
-Ln and Lf coordinates switch places.
+The farbound coordinates are defined similarly (but not quite) to the nearbound coordinates, with
+$L_n$ and $L_f$ coordinates switched places.
+\begin{align}
+  \cos\theta_f &= -\frac{L^2 + L_f^2 - L_n^2}{2L L_f} \\
+  \sin\theta_{f} &= \sqrt{1 - \cos^2\theta_{f}} \\
+  \cos\theta_{fs} &= \frac{L_s^2 + L_f^2 - L_t^2}{2L_s L_f} \\
+  \sin\theta_{fs} &=
+  \begin{cases}
+    +\sqrt{1 - \cos^2\theta_{fs}} & \theta_{fm} < \pi \\
+    -\sqrt{1 - \cos^2\theta_{fs}} & \theta_{fm} > \pi
+  \end{cases}
+\end{align}
+
+\onecolumn
 

### 2016-05-11 latex/paper.tex
Small change to make Theta_f make more sense to me in paper.
Small change to fix paper.tex system of equations symbols.

@@
 \begin{align}
-  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb})
-  + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}
+  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ns}(X_{bm} - X_{bb})
+  + \lambda_{nt}(X_{t } - X_{bm}) \Big) + R_{xml}
   &=& \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm})
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{nt}(X_{t } - X_{bm})
   + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
@@
 \begin{align}
-  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb})
-  + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
+  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ns}(Y_{bm} - Y_{bb})
+  + \lambda_{nt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
   &= \frac{Y_{nm}}{Ln}\dot{L}_n + \frac{Y_{nm}}{Lf}\dot{L}_f\\
-  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm})
+  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{nt}(Y_{t } - Y_{bm})
   + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
@@
 \begin{align}
-  \cos\theta_f &= -\frac{L^2 + L_f^2 - L_n^2}{2L L_f} \\
+  \cos\theta_f &= -\frac{L^2 + L_f^2 - L_n^2}{2L L_f}\\
+  &\Bigg( \mbox{Or equivalently...   }
+  \cos\left(\pi - \theta_f\right) &= \frac{L^2 + L_f^2 - L_n^2}{2L L_f}\Bigg)\\
   \sin\theta_{f} &= \sqrt{1 - \cos^2\theta_{f}} \\
@@
   \dot{L}_f\\
-  \lambda_{bs}\\
-  \lambda_{bt}\\
+  \lambda_{ns}\\
+  \lambda_{nt}\\
   \lambda_{ft}\\

### 2016-05-11 latex/paper.tex
Add beginnings of newly-solved system of equations.

@@
   -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
-  & -\frac{X_{bm}-X_{bb}}{\gamma} & \frac{X_{t}-X_{bm}}{\gamma} & 0 & 0\\
+  & -\frac{X_{nm}-X_{nb}}{\gamma} & \frac{X_{t}-X_{nm}}{\gamma} & 0 & 0\\
   -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
-  & 0 & -\frac{X_{t}-X_{bm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
+  & 0 & -\frac{X_{t}-X_{nm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
   -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
@@
   -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
-  & -\frac{Y_{bm}-Y_{bb}}{\gamma} & \frac{Y_{t}-Y_{bm}}{\gamma} & 0 & 0\\
+  & -\frac{Y_{nm}-Y_{nb}}{\gamma} & \frac{Y_{t}-Y_{nm}}{\gamma} & 0 & 0\\
   -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
-  & 0 & -\frac{Y_{t}-Y_{bm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
+  & 0 & -\frac{Y_{t}-Y_{nm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
   -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}

### 2016-05-11 latex/paper.tex
Add new test for +x forces, still needs work.

@@
 \begin{pmatrix}
-  -\frac{F_{xml}}{\gamma} - R_{xml}\\
-  -\frac{F_{xt}}{\gamma} - R_{xt}\\
-  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
-  -\frac{F_{yml}}{\gamma} - R_{yml}\\
-  -\frac{F_{yt}}{\gamma} - R_{yt}\\
-  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
+  -\frac{F_{nmx}}{\gamma} - R_{nmx}\\
+  -\frac{F_{tx}}{\gamma} - R_{tx}\\
+  -\frac{F_{fmx}}{\gamma} - R_{fmx}\\
+  -\frac{F_{nmy}}{\gamma} - R_{nmy}\\
+  -\frac{F_{ty}}{\gamma} - R_{ty}\\
+  -\frac{F_{fmy}}{\gamma} - R_{fmy}\\
 \end{pmatrix}

### 2016-05-11 dynein_struct.h

@@ -9,8 +9,7 @@ const double kb = 1.3806e-5; // nm^2 * kg / (s^2 * K)
 const double T = 293.0; // K
 
 const double lt = 10.0;   // nm, guess - not sure how DNA tail-bridge works
-const double ls = 10.0; // for debugging
-//const double ls = 21.22; // nm, derived from PyMol dynein crystal struct 3VKH, 212.2 angstroms
+const double ls = 21.22; // nm, derived from PyMol dynein crystal struct 3VKH, 212.2 angstroms
 const double Lt = lt;
 const double Ls = ls; // FIXME remove ls and lt in favor of Ls and Lt
 

### 2016-06-13 latex/paper.tex
fix a few bugs while meeting together

@@
 \title{Brownian Dynein Model}
-
-\newcommand{\mn}{\scalebox{0.7}[1.0]{-}}
 
@@
 \begin{align}
-  \frac{dX_{t}}{dL_n} &= \cos\theta_n\\
-  \frac{dY_{t}}{dL_n} &= \sin\theta_n\\
-  \frac{dX_{t}}{dL_f} &= 0\\
-  \frac{dY_{t}}{dL_f} &= 0\\
+  \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} &= \frac{L_n}{L}\\
+  \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
+  \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{L}\\
+  \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
 \end{align}
@@
 \begin{align}
-  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ns}(X_{bm} - X_{bb})
+  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} - \lambda_{ns}(X_{bm} - X_{bb})
   + \lambda_{nt}(X_{t } - X_{bm}) \Big) + R_{xml}
-  &=& \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{nt}(X_{t } - X_{bm})
+  &=& \frac{\partial X_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{nm}}{\partial L_f}\dot{L}_f\\
+  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } - \lambda_{nt}(X_{t } - X_{bm})
   + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
-  &=& \frac{X_{t}}{Ln}\dot{L}_n + \frac{X_{t}}{Lf}\dot{L}_f\\
-  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t })
+  &=& \frac{\partial X_{t}}{\partial L_n}\dot{L}_n + \frac{\partial X_{t}}{\partial L_f}\dot{L}_f\\
+  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} - \lambda_{ft}(X_{fm} - X_{t })
   + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
-  &=& \frac{X_{fm}}{Ln}\dot{L}_n + \frac{X_{fm}}{Lf}\dot{L}_f
+  &=& \frac{\partial X_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{fm}}{\partial L_f}\dot{L}_f
 \end{align}
@@
 \begin{align}
-  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ns}(Y_{bm} - Y_{bb})
+  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} - \lambda_{ns}(Y_{bm} - Y_{bb})
   + \lambda_{nt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
-  &= \frac{Y_{nm}}{Ln}\dot{L}_n + \frac{Y_{nm}}{Lf}\dot{L}_f\\
-  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{nt}(Y_{t } - Y_{bm})
+  &= \frac{\partial Y_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{nm}}{\partial L_f}\dot{L}_f\\
+  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } - \lambda_{nt}(Y_{t } - Y_{bm})
   + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
-  &= \frac{Y_{t}}{Ln}\dot{L}_n + \frac{Y_{t}}{Lf}\dot{L}_f\\
-  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t })
+  &= \frac{\partial Y_{t}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{t}}{\partial L_f}\dot{L}_f\\
+  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} - \lambda_{ft}(Y_{fm} - Y_{t })
   + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
-  &= \frac{Y_{fm}}{Ln}\dot{L}_n + \frac{Y_{fm}}{Lf}\dot{L}_f
+  &= \frac{\partial Y_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{fm}}{\partial L_f}\dot{L}_f
 \end{align}

### 2016-06-13 dynein_struct.h

@@ -302,6 +302,11 @@ private:
   double nmx, fmx, tx;
   double nmy, fmy, ty;
 
+  // Various interesting derivatives that are used in finding the
+  // velocities (and are set by update_velocities).
+  double dXnm_dLn, dYnm_dLn, dXnm_dLf, dYnm_dLf, dXfm_dLf, dYfm_dLf,
+    dXfm_dLn, dYfm_dLn, dXt_dLn, dYt_dLn, dXt_dLf, dYt_dLf;
+
   // Angles needed for torque computations
   double nba, fba;
 };

### 2016-06-13 dynein_struct_bothbound.cpp

@@ -179,7 +179,6 @@ void Dynein_bothbound::update_coordinates() {
   nba = atan2(nmy, nmx - nbx);
   fba = atan2(fmy, fmx - (nbx + L));
 
-  printf("Ln: %g, Lf: %g, fabs(L): %g\n", Ln, Lf, fabs(L));
   assert(Ln + Lf > fabs(L)); // this geometrically must be true!
   assert(nma != M_PI);
   assert(fma != M_PI);
@@ -228,28 +227,28 @@ void Dynein_bothbound::update_velocities() {
     : cosAfs/sqrt(1-cosAfs*cosAfs) * (1/Ls - (Ls*Ls+Lf*Lf-Lt*Lt)/(2*L*Lf*Lf));
   double dsinAfs_dLn = 0;
 
-  double dXnm_dLn = Ls*(cosAn * dcosAn_dLn + cosAns * dcosAn_dLn
-			- sinAn * dsinAns_dLn - sinAns * dsinAn_dLn);
-  double dYnm_dLn = Ls*(cosAn * dsinAns_dLn + sinAns * dcosAn_dLn
-			+ sinAn * dcosAns_dLn + cosAns * dsinAn_dLn);
-  double dXnm_dLf = Ls*(cosAn * dcosAns_dLf + cosAns * dcosAn_dLf
-			- sinAn * dsinAns_dLf - sinAns * dsinAn_dLf);
-  double dYnm_dLf = Ls*(cosAn * dsinAns_dLf + sinAns * dcosAn_dLf
-			+ sinAn * dcosAns_dLf + cosAns * dsinAn_dLf);
-
-  double dXfm_dLf = Ls*(cosAf * dcosAf_dLf + cosAfs * dcosAf_dLf
-			- sinAf * dsinAfs_dLf - sinAfs * dsinAf_dLf);
-  double dYfm_dLf = Ls*(cosAf * dsinAfs_dLf + sinAfs * dcosAf_dLf
-			+ sinAf * dcosAfs_dLf + cosAfs * dsinAf_dLf);
-  double dXfm_dLn = Ls*(cosAf * dcosAfs_dLn + cosAfs * dcosAf_dLn
-			- sinAf * dsinAfs_dLn - sinAfs * dsinAf_dLn);
-  double dYfm_dLn = Ls*(cosAf * dsinAfs_dLn + sinAfs * dcosAf_dLn
[…]

### 2016-06-14 latex/paper.tex
Add bit to paper.tex on why we do not need to treat negative L values any different from positive ones.

@@
 
+The only change between the near and far coordinates (other than switching $L_n$ and $L_f$) is the
+sign of $\cos\theta_{n/f}$. This is because, for positive L, $\theta_n$ is an internal angle and
+$\theta_f$ is an external angle to the $L-L_n-L_f$ triangle. To properly deal with the $\theta_f$
+angle, we must use its complement: $\pi - \theta_f$. The sign switch is because
+$\cos\left(\pi - \theta_f\right) = -\cos\theta_f$.\\
+
+For negative L values, the only change to the model is that $\theta_n$ becomes an external angle and
+$\theta_f$ becomes internal. As we know, we must introduce a sign shift to account for this.
+However we do not need to do any extra work, since the L in the denominator of $\cos\theta_f$
+provides the necessary sign shift for $\theta_n$ going from internal to external.
+
 \onecolumn

### 2016-06-15 latex/paper.tex
Put internal force coefficient in update_internal_forces, so the values of r and f are comparable.

@@
 
-\section{Matrix Solution via Mathematica}
+\section{Matrix Form}
 Here we convert the above system into matrix form, solve it in Mathematica and list the results.
@@
 \begin{pmatrix}
-  -\frac{F_{nmx}}{\gamma} - R_{nmx}\\
-  -\frac{F_{tx}}{\gamma} - R_{tx}\\
-  -\frac{F_{fmx}}{\gamma} - R_{fmx}\\
-  -\frac{F_{nmy}}{\gamma} - R_{nmy}\\
-  -\frac{F_{ty}}{\gamma} - R_{ty}\\
-  -\frac{F_{fmy}}{\gamma} - R_{fmy}\\
+  -\frac{1}{\gamma}F_{nmx} - R_{nmx}\\
+  -\frac{1}{\gamma}F_{tx}  - R_{tx}\\
+  -\frac{1}{\gamma}F_{fmx} - R_{fmx}\\
+  -\frac{1}{\gamma}F_{nmy} - R_{nmy}\\
+  -\frac{1}{\gamma}F_{ty}  - R_{ty}\\
+  -\frac{1}{\gamma}F_{fmy} - R_{fmy}\\
 \end{pmatrix}

### 2016-06-15 dynein_struct_bothbound.cpp

@@ -92,10 +92,10 @@ void Dynein_bothbound::update_internal_forces() {
     f2 = T/ls;
     f2x = f2 * sin(nba);
     f2y = f2 * -cos(nba);
-    f.nmx += f2x;
-    f.nmy += f2y;
-    f.nbx += -f2x; // Equal and opposite forces!  :)
-    f.nby += -f2y; // Equal and opposite forces!  :)
+    f.nmx += f2x / gm;
+    f.nmy += f2y / gm;
+    f.nbx += -f2x / gb; // Equal and opposite forces!  :)
+    f.nby += -f2y / gb; // Equal and opposite forces!  :)
 
     T = cm*(nma - eq.nma);
     f1 = T/ls;
@@ -104,12 +104,12 @@ void Dynein_bothbound::update_internal_forces() {
     f1y = f1 * -cos(nba);
     f2x = f2 * sin(nma - (M_PI - nba));
     f2y = f2 * -cos(nma - (M_PI - nba));
-    f.nbx += f1x;
-    f.nby += f1y;
-    f.tx  += f2x;
-    f.ty  += f2y;
-    f.nmx += -(f1x + f2x);
-    f.nmy += -(f1y + f2y);
+    f.nbx += f1x / gb;
+    f.nby += f1y / gb;
+    f.tx  += f2x / gt;
+    f.ty  += f2y / gt;
+    f.nmx += -(f1x + f2x) / gm;
+    f.nmy += -(f1y + f2y) / gm;
 
     T = ct*(fma + fba - nma - nba - eq.ta);
     f1 = T / lt;
@@ -118,12 +118,12 @@ void Dynein_bothbound::update_internal_forces() {
     f1y = f1 * -cos(nma + nba - M_PI);
     f2x = f2 * -sin(fma + fba - M_PI);
     f2y = f2 * cos(fma + fba - M_PI);
-    f.nmx += f1x;
-    f.nmy += f1y;
-    f.fmx += f2x; // should be: positive
-    f.fmy += f2y; // should be: positive
-    f.tx  += -(f1x + f2x);
-    f.ty  += -(f1y + f2y);
+    f.nmx += f1x / gm;
+    f.nmy += f1y / gm;
+    f.fmx += f2x / gm; // should be: positive
+    f.fmy += f2y / gm; // should be: positive
[…]

### 2016-06-30 thesis_stuff/random_derivations.tex
Add minor change to thesis/stuff directory.

\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

\usepackage{marvosym} % Required for symbols in the colored box

\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

% Fonts and tweaks for XeLaTeX
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
%\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Colors for links, text and headings
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
\definecolor{shade}{HTML}{F5DD9D} % Peach color for the contact information box
\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
\definecolor{headings}{HTML}{701112} % Dark red color for headings
% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080

\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors

\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

\usepackage{titlesec} % Allows creating custom \section's

% Format of the section titles
\titleformat{\section}{\color{headings}
\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]

\title{Cool thesis-related derivations, papers}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

\begin{document}

\maketitle{}

\section{Brownian motion via Langevin Equation and Equipartition Theorem}

\begin{align*}
  \frac{d\vec{v}}{dt} &= \frac{1}{m}\left(\frac{-mv}{\tau} + R\right)\\
  \frac{d\vec{v}}{dt} &= \frac{-v}{\tau} + \frac{R}{m}\\
  <\vec{r} \cdot \frac{d\vec{v}}{dt} > + \frac{1}{\tau}<\vec{R} \cdot \vec{v}> &= 0\\
  \frac{1}{2}\frac{d^2}{dt^2}(r^2) + \frac{1}{2\tau}\frac{d}{dt}(r^2) - v^2 &= 0 \hspace{2cm} \Bigg(
  \frac{d}{dt}\left(\vec{r} \cdot \vec{v}\right) = v^2 + \left(\vec{r} \cdot \frac{d\vec{v}}{dt}\right)
  \mbox{ and }
  \frac{d^2}{dt^2}\left(\vec{r} \cdot \vec{r}\right) = 2\left(\vec{r} \cdot \vec{v}\right) \Bigg)\\
  \frac{d^2}{dt^2}(r^2) + \frac{1}{\tau}\frac{d}{dt}(r^2) &= 2<v^2> = \frac{6k_BT}{m}\\
  <r^2> &= \frac{6k_BT\tau^2}{m}\left(e^{-t/\tau}-1+\frac{t}{\tau}\right)\\
\end{align*}

so...

\begin{align*}
  \left(t << \tau \right) \rightarrow <r^2> = \frac{3k_BT}{m}t^2 \hspace{2cm}\mbox{free particle motion}\\
  \left(t >> \tau \right) \rightarrow <r^2> = \frac{6k_BT\tau}{m}t \hspace{2cm}\mbox{motion proportional to }\sqrt{t}\\
\end{align*}

\section{Equipartition Theorem for quadratic energies}

\begin{align*}
  Z &= \int_{-\infty}^{\infty} e^{-\beta Ax^2}dx = \sqrt{\frac{\pi}{\beta A}}\\
  <E> &= - \frac{d\ln Z}{d\beta} = -\left(\sqrt{\frac{\beta A}{\pi}}\right)\left(\frac{\sqrt{\beta A}}{2\sqrt{\pi}}\right)\frac{-\pi}{A\beta^2}\\
  &= \frac{k_BT}{2}\\
\end{align*}

\end{document}

### 2016-06-30 dynein_struct.h

@@ -1,6 +1,7 @@
+#include <csignal>
+#include <fenv.h>
 #include <math.h>
 #include <stdbool.h>
-#include <fenv.h>
 
 #include "MersenneTwister.h"
 
@@ -289,7 +290,8 @@ double fifth(double num);
 void simulate(double runtime, double rand_seed, State init_state, double* init_position,
 	      void (*job)(void* dyn, State s, void* job_msg, void* job_data, int iteration),
 	      void* job_msg, void* job_data);
-double get_average(double* data, int len);
+double get_average(double* data,  int len);
+double get_variance(double* data, int len);
 void FPE_signal_handler(int signum);
 
 #endif

### 2016-06-30 dynein_struct_bothbound.cpp

@@ -167,7 +167,6 @@ void Dynein_bothbound::update_internal_forces() {
     if (get_nmy() < 0) f.nmy += MICROTUBULE_REPULSION_FORCE * fabs(get_nmy());
     if (get_ty()  < 0) f.ty  += MICROTUBULE_REPULSION_FORCE * fabs(get_ty());
     if (get_fmy() < 0) f.fmy += MICROTUBULE_REPULSION_FORCE * fabs(get_fmy());
-
   }
 }
 

### 2016-06-30 utilities.cpp

@@ -42,6 +42,15 @@ double get_average(double* data, int len) {
   return sum / len;
 }
 
+double get_variance(double* data, int len) {
+  double sum = 0;
+  double ave = get_average(data, len);
+  for (int i = 0; i < len; i++) {
+    sum += (data[i] - ave)*(data[i] - ave);
+  }
+  return sum / len;
+}
+
 void FPE_signal_handler(int signum) {
   fexcept_t flag;
   fegetexceptflag(&flag, FE_ALL_EXCEPT);

### 2016-07-08 thesis_stuff/thesis_stuff.tex
Add stuff to thesis_stuff.tex about equipartition theorem.

\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

\usepackage{marvosym} % Required for symbols in the colored box

\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

% Fonts and tweaks for XeLaTeX
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
%\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Colors for links, text and headings
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
\definecolor{shade}{HTML}{F5DD9D} % Peach color for the contact information box
\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
\definecolor{headings}{HTML}{701112} % Dark red color for headings
% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080

\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors

\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

\usepackage{titlesec} % Allows creating custom \section's

% Format of the section titles
\titleformat{\section}{\color{headings}
\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]

\title{Dynein project log}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

\begin{document}

\maketitle{}

\section{Equipartition Theorem}
The Equipartition Theorem (ET) predicts the average energy per degree of freedom of a system with energy which depends on the square of each degree of freedom. Mathematically is is expressed as:

\begin{align*}
  Z &= \int_{-\infty}^{\infty} e^{-\beta Ax^2}dx = \sqrt{\frac{\pi}{\beta A}}\\
  <E> &= - \frac{d\ln Z}{d\beta} = -\left(\sqrt{\frac{\beta A}{\pi}}\right)\left(\frac{\sqrt{\beta A}}{2\sqrt{\pi}}\right)\frac{-\pi}{A\beta^2}\\
  &= \frac{1}{2}k_BT\\
\end{align*}

where Z is the partition function and x a degree of freedom.\\

For our model, each domain feels three separate forces:

\textbf{Brownian forces}: Random forces due to water particle collisions. Gaussian-sampled with a
variance $\sqrt{\frac{\gamma k_BT}{dt}}$. Brownian forces are somehow necessary for the ET energy
to be realized.\\

\textbf{Conformational forces}: Spring forces from the molecule deviating from its lowest-energy
conformation. The energy from these forces is quadratic with respect to angle, and so each free
angle should contribute to the average energy by ET.\\

\textbf{Internal forces}. Tension forces (constraint forces) felt between domains which keep
the protein rigid. These are not quadratic, so it is unclear how they contribute to energy!\\

\subsection{Onebound case}
The conformational forces are:\\
\begin{align*}
  |\vec{F_{ub}}| &\approx \frac{c_m\theta_{um}}{L_s}\\
  |\vec{F_{um}}| &\approx \frac{c_m\theta_{um}}{L_s} + \frac{c_m\theta_{um}}{L_t} + \frac{c_t\theta_{t}}{L_t}\\
  |\vec{F_{t}}| &\approx \frac{c_m\theta_{um}}{L_t} + 2\frac{c_t\theta_t}{L_t} + \frac{c_m\theta_{bm}}{L_t}\\
  |\vec{F_{bm}}| &\approx \frac{c_t\theta_t}{L_t} + \frac{c_m\theta_{bm}}{L_t} + \frac{c_m\theta_{bm}}{L_s} + \frac{c_b\theta_{bb}}{L_s}\\
  |\vec{F_{bb}}| &\approx \frac{c_m\theta_{bm}}{L_s} + \frac{c_b\theta_{bb}}{L_s}\\
\end{align*}

From this we can come up with rough order-of-magnitude estimates of the energy of each domain is:

\begin{align*}
  PE_{ub} &\approx \frac{c_m}{L_s}\theta_{um}^2 + \frac{c_m}{L_t}\theta_{um}^2\\
  PE_{t} &\approx \frac{c_t}{L_t}\theta_{t}^2\\
  PE_{bm} &\approx \frac{c_m}{L_s}\theta_{bm}^2 + \frac{c_m}{L_t}\theta_{bm}^2\\
  PE_{bb} &\approx \frac{c_m}{L_s}\theta_{um}^2\\
\end{align*}

From this we can see that the conformational PE of each domain depends on different combinations of
stalk/tail length and spring constants.

\textbf{When is equipartition behaved?}
It seems like ET should be behaved when we have an even balance of Brownian and conformational forces:

\begin{align*}
  F_{conf} &\approx F_{Brownian}\\
  \frac{c}{L}\theta &\approx \sqrt{\frac{k_BT\gamma}{dt}}\\
\end{align*}

Is this reflected in our simulation? Well take a look at %% Fig ($\ref{fig:latent-heat}$)
...

%% \begin{figure}[h!]
%%   \centering
%%   \includegraphics[width=0.5\textwidth]{../figures/ob_equipartition_vs_force_ratio.pdf}
%%   \caption{Onebound conformational energy follows equipartition best when the ratio of conformational
%%   forces to Brownian forces is one.}
%%   \label{fig:equipartition_vs_force_ratio}
%% \end{figure}

\end{document}

### 2016-07-14 thesis_stuff/random_derivations.tex
Add stuff on Brownian dynamics, motion to thesis_stuff.pdf

@@
 
-\section{Brownian motion via Langevin Equation and Equipartition Theorem}
+\section{Brownian motion}
+\subsection{Derivation} \label{sec:bmotion-derivation}
+We can derive the equation for the position of a particle using the simple Newtonian mechanics. We
+start with the general $2^{nd}$ law equation for a particle with random forces and drag (the
+Langevin equation). We then take the time-averages of all variables (using expectation value signs)
+to eliminate the effect of random Brownian forces. After some algebra we arrive at a differential
+equation for squared position. We solve it and simplify its expression for limits when $t >> \tau$
+and $t << \tau$.\\
 
@@
   \frac{d\vec{v}}{dt} &= \frac{-v}{\tau} + \frac{R}{m}\\
-  <\vec{r} \cdot \frac{d\vec{v}}{dt} > + \frac{1}{\tau}<\vec{R} \cdot \vec{v}> &= 0\\
-  \frac{1}{2}\frac{d^2}{dt^2}(r^2) + \frac{1}{2\tau}\frac{d}{dt}(r^2) - v^2 &= 0 \hspace{2cm} \Bigg(
-  \frac{d}{dt}\left(\vec{r} \cdot \vec{v}\right) = v^2 + \left(\vec{r} \cdot \frac{d\vec{v}}{dt}\right)
+  <\vec{r} \cdot \frac{d\vec{v}}{dt} > &+ \frac{1}{\tau}<\vec{r} \cdot \vec{v}> = 0\\
+  \frac{1}{2}\frac{d^2}{dt^2}(r^2) &+ \frac{1}{2\tau}\frac{d}{dt}(r^2) - v^2 = 0 \hspace{1cm} \Bigg(\mbox{b/c }\frac{d}{dt}\left(\vec{r} \cdot \vec{v}\right) = v^2 + \left(\vec{r} \cdot \frac{d\vec{v}}{dt}\right)
   \mbox{ and }
-  \frac{d^2}{dt^2}\left(\vec{r} \cdot \vec{r}\right) = 2\left(\vec{r} \cdot \vec{v}\right) \Bigg)\\
-  \frac{d^2}{dt^2}(r^2) + \frac{1}{\tau}\frac{d}{dt}(r^2) &= 2<v^2> = \frac{6k_BT}{m}\\
+  \frac{d}{dt}\left(\vec{r} \cdot \vec{r}\right) = 2\left(\vec{r} \cdot \vec{v}\right) \Bigg)\\
+  \frac{d^2}{dt^2}(<r^2>) + &\frac{1}{\tau}\frac{d}{dt}(<r^2>) = 2<v^2> = \frac{6k_BT}{m} \hspace{1cm}\left(\mbox{Equipartition Theorem}\right)\\
   <r^2> &= \frac{6k_BT\tau^2}{m}\left(e^{-t/\tau}-1+\frac{t}{\tau}\right)\\
@@
 
+\textbf{Averaging over time?}
+In the above derivation we use time averaging to eliminate the effect of Brownian forces. This is
+essentially just discussing the motion of a particle on a timescale where Brownian forces go to
+zero. The variance of the Brownian force R is:
+
+\begin{align*}
+  \sigma_R^2 &= \sqrt{\frac{2k_BTm}{\tau dt}}\\
+\end{align*}
+
+(TODO: further justify the dt in the variance)\\
+Thus over larger timescales (bigger dt's) the Brownian force is smaller. When time averaging, all
+we are saying is that our dt is large enough that Brownian forces are negligible.\\
+
+An interesting observation is that the motion equation for a particle feeling Brownian forces is
+identical to the equation for a macroscopic object feeling drag forces, which makes sense, since
+to solve the Brownian motion equation we just eliminate R.\\
+
+\section{Brownian dynamics}
+We use Brownian dynamics as our equation of motion. BD is just the special case of Langevin dynamics
+
+\begin{align*}
+  m\frac{d\vec{v}}{dt} &= -\frac{m}{\tau}\vec{v} + \vec{F} + \vec{R}\\
+\end{align*}
+
+where $m\rightarrow0$:
+
+\begin{align*}
+  \vec{v} &= \frac{\tau}{m}\vec{F} + \frac{\tau}{m}\vec{R}\\
+\end{align*}
+
+where m is the mass, $\tau$ the time constant, $\vec{F}$ a generic force and $\vec{R}$ the Brownian
+force. Mass ``going to zero'' means we are discussing particles where $m << $ any other variable.
+Because m is tiny the particle effectively has no net force on it, so the drag force must cancel
+out the other forces. From this we can find velocity.\\
+
+\subsection{What is $\tau$?}
+Tau is a time constant that describes the behavior of a system with respect to time. By looking at
+the motion equations for Brownian systems in Section (\ref{sec:bmotion-derivation}), we see that the
+size of t with respect to $\tau$ decides what type of motion the particle will feel. On the ``small''
+timescale the system displays free particle motion, but on the ``large'' timescale, the system
+displays Brownian motion. $\tau$ can be thought of as the time the system switches from free to
+Brownian motion.\\
+
 \section{Equipartition Theorem for quadratic energies}
-
 \begin{align*}

### 2016-07-15 thesis_stuff/thesis_stuff.tex
Add contents of random_derivations.pdf to thesis_stuff.pdf.

@@
 
+\section{Brownian motion}
+\subsection{Derivation} \label{sec:bmotion-derivation}
+We can derive the equation for the position of a particle using the simple Newtonian mechanics. We
+start with the general $2^{nd}$ law equation for a particle with random forces and drag (the
+Langevin equation). We then take the time-averages of all variables (using expectation value signs)
+to eliminate the effect of random Brownian forces. After some algebra we arrive at a differential
+equation for squared position. We solve it and simplify its expression for limits when $t >> \tau$
+and $t << \tau$.\\
+
+\begin{align*}
+  \frac{d\vec{v}}{dt} &= \frac{1}{m}\left(\frac{-mv}{\tau} + R\right)\\
+  \frac{d\vec{v}}{dt} &= \frac{-v}{\tau} + \frac{R}{m}\\
+  <\vec{r} \cdot \frac{d\vec{v}}{dt} > &+ \frac{1}{\tau}<\vec{r} \cdot \vec{v}> = 0\\
+  \frac{1}{2}\frac{d^2}{dt^2}(r^2) &+ \frac{1}{2\tau}\frac{d}{dt}(r^2) - v^2 = 0 \hspace{1cm} \Bigg(\mbox{b/c }\frac{d}{dt}\left(\vec{r} \cdot \vec{v}\right) = v^2 + \left(\vec{r} \cdot \frac{d\vec{v}}{dt}\right)
+  \mbox{ and }
+  \frac{d}{dt}\left(\vec{r} \cdot \vec{r}\right) = 2\left(\vec{r} \cdot \vec{v}\right) \Bigg)\\
+  \frac{d^2}{dt^2}(<r^2>) + &\frac{1}{\tau}\frac{d}{dt}(<r^2>) = 2<v^2> = \frac{6k_BT}{m} \hspace{1cm}\left(\mbox{Equipartition Theorem}\right)\\
+  <r^2> &= \frac{6k_BT\tau^2}{m}\left(e^{-t/\tau}-1+\frac{t}{\tau}\right)\\
+\end{align*}
+
+so...
+
+\begin{align*}
+  \left(t << \tau \right) \rightarrow <r^2> = \frac{3k_BT}{m}t^2 \hspace{2cm}\mbox{free particle motion}\\
+  \left(t >> \tau \right) \rightarrow <r^2> = \frac{6k_BT\tau}{m}t \hspace{2cm}\mbox{motion proportional to }\sqrt{t}\\
+\end{align*}
+
+\textbf{Averaging over time?}
+In the above derivation we use time averaging to eliminate the effect of Brownian forces. This is
+essentially just discussing the motion of a particle on a timescale where Brownian forces go to
+zero. The variance of the Brownian force R is:
+
+\begin{align*}
+  \sigma_R^2 &= \sqrt{\frac{2k_BTm}{\tau dt}}\\
+\end{align*}
+
+(TODO: further justify the dt in the variance)\\
+Thus over larger timescales (bigger dt's) the Brownian force is smaller. When time averaging, all
+we are saying is that our dt is large enough that Brownian forces are negligible.\\
+
+An interesting observation is that the motion equation for a particle feeling Brownian forces is
+identical to the equation for a macroscopic object feeling drag forces, which makes sense, since
+to solve the Brownian motion equation we just eliminate R.\\
+
+\section{Brownian dynamics}
+We use Brownian dynamics as our equation of motion. BD is just the special case of Langevin dynamics
+
+\begin{align*}
+  m\frac{d\vec{v}}{dt} &= -\frac{m}{\tau}\vec{v} + \vec{F} + \vec{R}\\
+\end{align*}
+
+where $m\rightarrow0$:
+
+\begin{align*}
+  \vec{v} &= \frac{\tau}{m}\vec{F} + \frac{\tau}{m}\vec{R}\\
+\end{align*}
+
+where m is the mass, $\tau$ the time constant, $\vec{F}$ a generic force and $\vec{R}$ the Brownian
+force. Mass ``going to zero'' means we are discussing particles where $m << $ any other variable.
+Because m is tiny the particle effectively has no net force on it, so the drag force must cancel
+out the other forces. From this we can find velocity.\\
+
+\subsection{What is $\tau$?}
+Tau is a time constant that describes the behavior of a system with respect to time. By looking at
+the motion equations for Brownian systems in Section (\ref{sec:bmotion-derivation}), we see that the
+size of t with respect to $\tau$ decides what type of motion the particle will feel. On the ``small''
+timescale the system displays free particle motion, but on the ``large'' timescale, the system
+displays Brownian motion. $\tau$ can be thought of as the time the system switches from free to
+Brownian motion.\\
+
+\section{Finding a reasonable dt}
+The timescale of our simulation
+
+\section{Equipartition Theorem for quadratic energies}
+\begin{align*}
+  Z &= \int_{-\infty}^{\infty} e^{-\beta Ax^2}dx = \sqrt{\frac{\pi}{\beta A}}\\
+  <E> &= - \frac{d\ln Z}{d\beta} = -\left(\sqrt{\frac{\beta A}{\pi}}\right)\left(\frac{\sqrt{\beta A}}{2\sqrt{\pi}}\right)\frac{-\pi}{A\beta^2}\\
+  &= \frac{k_BT}{2}\\
+\end{align*}
+
 \end{document}

### 2016-07-15 thesis_stuff/thesis_stuff.tex
Add derivation of D to thesis_stuff.pdf.

@@
 \section{Finding a reasonable dt}
-The timescale of our simulation
+TODO: describe the relationship between diffusion constant D, time constant $\tau$ and dt.\\
+
+\subsection{Relating D to $\tau$}
+
+I don't really understand this derivation:
+
+\begin{align*}
+  \sin\left(\delta\theta\right) &\approx \delta\theta = \frac{x}{L}\\
+  \delta\theta^2 &= \frac{x^2}{L^2} = \frac{Dt}{L^2}\\
+\end{align*}
+
+We set our $\tau$ to be the time when $<\delta\theta^2> \approx 1$, so:
+
+\begin{align*}
+  \tau = \frac{L^2}{D}\\
+\end{align*}
+
+\subsection{Finding D}
+For a particle feeling Brownian motion:
+
+\begin{align*}
+  \frac{\delta x}{\delta t} &= \frac{\tau}{m} R\\
+\end{align*}
+
+We say the magnitude of R is the standard deviation of a Gaussian process:
+
+\begin{align*}
+  \frac{\delta x}{\delta t} &= \frac{\tau}{m}\sqrt{\frac{2k_BTm}{\tau \delta t}}\\
+  \delta x &= \sqrt{\frac{2k_BT\tau}{m\delta t}}\\
+  <\delta x^2> &= \frac{2k_BT\tau}{m}\delta t\\
+\end{align*}
+
+We then use the Brownian motion equation for $t >> \tau$ to find D:\\
+
+\begin{align*}
+  <\delta x^2> &= D\delta t = \frac{2k_BT\tau}{m}\delta t\\
+  D = \frac{2k_BT\tau}{m}\\
+\end{align*}
+
+\subsection{Alternative derivation of D (Einstein relation)}
+We can also arrive at an expression for D through an equilibrium argument. There are two forces which cause currents in solutions: drift and diffusion.
+Drift is motion due to a force acting on particles. Diffusion is current due to random, natural motions of particles. Our equilibrium condition is when
+the flux of particles due to both effects is equal, so there is no net particle flow. We first need to describe these fluxes:
+
+\textbf{Drift flux}\\
+Our particles obey Brownian dynamics, so $\gamma\dot{x} = F$, where $\gamma$ is the drag force constant. Flux J, or particles per second-area, can be
+found by multiplying the velocity of particles by the concentration $\rho$:
+
+\begin{align*}
+  J_{drift} &= \frac{1}{\gamma}F(x)\rho(x)\\
+  &= -\frac{1}{\gamma}\rho(x)\nabla U\\
+\end{align*}
+
+\textbf{Diffusion flux}\\
+Flux due to diffusion is proportional to the negative gradient in concentration and D:
+
+\begin{align*}
+  J_{diff} &= -D\nabla \rho(x)\\
+\end{align*}
+
+\textbf{Solving for D}
+The concentration gradient in a solution is proportional to the energy gradient. By the chain rule:
+
+\begin{align*}
+  \nabla \rho &= \frac{\partial\rho}{\partial U} \nabla U\\
+\end{align*}
+
+We then set the sum of our two fluxes to zero and solve for the equilibrium condition:
+
+\begin{align*}
+  J_{diff} + J_{drift} &= 0\\
+  -\frac{1}{\gamma}\rho(x)\nabla U - D\nabla \rho(x) &= 0\\
+  \frac{1}{\gamma}\rho(x)\nabla U + D \frac{\partial\rho}{\partial U} \nabla U&= 0\\
+  \left(\frac{1}{\gamma}\rho(x) + D\frac{\partial\rho}{\partial U}\right)\nabla U &= 0\\
+\end{align*}
+
+because $\nabla U$ is not guarenteed to be zero everywhere, it must be the case that:
+
+\begin{align*}
+  \frac{1}{\gamma}\rho(x) &= -D\frac{\partial\rho}{\partial U}\\
+  \frac{-\rho(x)}{\gamma\frac{\partial\rho}{\partial U}} &= D\\
+\end{align*}
+
+\textbf{Finding d$\rho$/dU}
+To simplify this value, we note that, because the particles do not interact, energy is purely a function of position. Thus, by
+Maxwell-Boltzman statistics, the probability of being at a location x (i.e $\rho(x)$) is proportional to $e^{-\beta U(x)}$.
+From this we can find an expression for concentration and d$\rho(x)/dU(x)$:
+
+\begin{align*}
+  \rho(x) &= Ae^{-\beta U(x)}\\
+  \frac{\partial \rho(x)}{\partial U} &= \frac{-1}{k_BT}Ae^{-\beta U(x)}\\
+\end{align*}
+
+Plugging these expressions into our D equation, in addition to our definition for $\gamma$, we can see that:
+
+\begin{align*}
+  \frac{-1}{\gamma\frac{-1}{k_BT}} &= D\\
+  D &= \frac{k_BT}{\gamma} = \frac{k_BT\tau}{m}\\
+\end{align*}
 

### 2016-07-17 thesis_stuff/thesis_stuff.tex
Fix up derivation in thesis_stuff.pdf a bit.

@@
 \begin{align*}
-  \sin\left(\delta\theta\right) &\approx \delta\theta = \frac{x}{L}\\
-  \delta\theta^2 &= \frac{x^2}{L^2} = \frac{Dt}{L^2}\\
+  \sin\left(\Delta\theta\right) &\approx \Delta\theta = \frac{x}{L}\\
+  \Delta\theta^2 &= \frac{x^2}{L^2} = \frac{Dt}{L^2}\\
 \end{align*}
 
-We set our $\tau$ to be the time when $<\delta\theta^2> \approx 1$, so:
+We set our $\tau$ to be the time when $<\Delta\theta^2> \approx 1$, so:
 
@@
 \subsection{Finding D}
-For a particle feeling Brownian motion:
+For a particle feeling Brownian forces:
 
 \begin{align*}
-  \frac{\delta x}{\delta t} &= \frac{\tau}{m} R\\
+  \frac{\Delta x}{\Delta t} &= \frac{\tau}{m} R\\
 \end{align*}
@@
 \begin{align*}
-  \frac{\delta x}{\delta t} &= \frac{\tau}{m}\sqrt{\frac{2k_BTm}{\tau \delta t}}\\
-  \delta x &= \sqrt{\frac{2k_BT\tau}{m\delta t}}\\
-  <\delta x^2> &= \frac{2k_BT\tau}{m}\delta t\\
+  \frac{\Delta x}{\Delta t} &= \frac{\tau}{m}\sqrt{\frac{2k_BTm}{\tau \Delta t}}\\
+  \Delta x &= \sqrt{\frac{2k_BT\tau}{m\Delta t}}\Delta t\\
+  <\Delta x^2> &= \frac{2k_BT\tau}{m}\Delta t\\
 \end{align*}
@@
 \begin{align*}
-  <\delta x^2> &= D\delta t = \frac{2k_BT\tau}{m}\delta t\\
-  D = \frac{2k_BT\tau}{m}\\
+  <\Delta x^2> &= D\Delta t = \frac{2k_BT\tau}{m}\Delta t\\
+  D = \frac{2k_BT\tau}{m} = \frac{2k_BT}{\gamma}\\
 \end{align*}
@@
 Drift is motion due to a force acting on particles. Diffusion is current due to random, natural motions of particles. Our equilibrium condition is when
-the flux of particles due to both effects is equal, so there is no net particle flow. We first need to describe these fluxes:
+the flux of particles due to both effects is equal, so there is no net particle flow. We first need to describe these fluxes:\\
 
@@
 
-\textbf{Solving for D}
+\textbf{Solving for D}\\
 The concentration gradient in a solution is proportional to the energy gradient. By the chain rule:
@@
 
-\textbf{Finding d$\rho$/dU}
+\textbf{Finding d$\rho$/dU}\\
 To simplify this value, we note that, because the particles do not interact, energy is purely a function of position. Thus, by

### 2016-07-28 latex/derivation.tex

@@
 
-\begin{twocolumn}
-\section{Notes on physical parameters}
-
-Stoke's Law states that the relationship between viscosity, force, and
-velocity for a spherical particle is given by:
-\begin{align}
-  \mathbf{v} &= \frac{\mathbf{F}}{6\pi \mu R}
-\end{align}
-where $\mu$ is the viscosity of the fluid, and $R$ is the radius of
-the particle.  Thus in our terminology:
-\begin{align}
-  \gamma &= 6\pi \mu R.
-\end{align}
-Note that the viscosity of water is temperature-dependent and around
-0.7~mPa~s at body temperature.  However, the viscosity of cytoplasm
-may be rather different, and will of course depend on length scale.
-But for our purposes we can probably get away with this value.
-
-The random force $\mathbf{R}(t)$ should have a Gaussian distribution
-with variance~1, but then be divided by $\sqrt{\Delta t}$.  Thus, the
-smaller the time step, the larger the random force we will apply.  We
-can understand this in the backwards direction.  When we observe a
-larger time step, the ``random force'' results from many smaller
-random forces added together, and these smaller forces often cancel,
-leading to this reduction in the total force over that time period.
-
-Finally, we will need estimates for the radii of each domain (to go
-into the $\gamma$ parameter, the equilibrium angles for each hinge, and
-the spring constants for each hinge.  The first two we can estimate
-from the structure of dynein.  The third will require a rough guess.
-We can get a ball-park guess by deciding how much we want the angle to
-fluctuate (e.g. $\ll \pi$ for each angle!), and then take our spring
-constant to be $kT$ divided by that anglular fluctuation squared.
-
-\end{twocolumn}
-
 \end{document}

### 2016-07-28 thesis_stuff/thesis_stuff.tex

@@
 
+\section{Gamma derivation}
+
+Stoke's Law states that the relationship between viscosity, force, and
+velocity for a spherical particle is given by:
+\begin{align}
+  \mathbf{v} &= \frac{\mathbf{F}}{6\pi \mu R}
+\end{align}
+where $\mu$ is the viscosity of the fluid, and $R$ is the radius of
+the particle.  Thus in our terminology:
+\begin{align}
+  \gamma &= 6\pi \mu R.
+\end{align}
+Note that the viscosity of water is temperature-dependent and around
+0.7~mPa~s at body temperature.  However, the viscosity of cytoplasm
+may be rather different, and will of course depend on length scale.
+But for our purposes we can probably get away with this value.
+
+The random force $\mathbf{R}(t)$ should have a Gaussian distribution
+with variance~1, but then be divided by $\sqrt{\Delta t}$.  Thus, the
+smaller the time step, the larger the random force we will apply.  We
+can understand this in the backwards direction.  When we observe a
+larger time step, the ``random force'' results from many smaller
+random forces added together, and these smaller forces often cancel,
+leading to this reduction in the total force over that time period.
+
+Finally, we will need estimates for the radii of each domain (to go
+into the $\gamma$ parameter, the equilibrium angles for each hinge, and
+the spring constants for each hinge.  The first two we can estimate
+from the structure of dynein.  The third will require a rough guess.
+We can get a ball-park guess by deciding how much we want the angle to
+fluctuate (e.g. $\ll \pi$ for each angle!), and then take our spring
+constant to be $kT$ divided by that anglular fluctuation squared.
+
 \end{document}

### 2016-08-02 thesis_stuff/thesis_stuff.tex
Add beginning of CLT derivation.

@@
 
+\section{Background of Correlation function}
+This is based on the Autocorrelation procedure (see Convolution on Wikipedia).
+In our correlation function code, we take the autocorrelation function of our
+potential and time-translate it to get the time at which there is zero correlation
+between the functions. Flesh this out sometime!\\
+
+\section{CLT (and/or Brownian distribution is Gaussian?) Derivation}
+Here we show that, given an initial PDF as a delta function $P(t_0,x) = \delta(x)$
+and any transition likelihood $W(s)$ for some step size s and 1 timestep, P
+eventually evolves into a Gaussian function.\\
+
+We use a discrete time, continuous position model:\\
+
+\begin{align}
+  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\\
+\end{align}
+
+This matches the form of a convolution integral:
+
+\begin{align*}
+  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx\\
+\end{align*}
+
+By the Convolution Theorem (prove?) we can simplify the above expression:
+
+\begin{align}
+  F{P(t_0+1,x')} &= F{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx}\\
+  \tilde{P(t_0+1,k)} &= N\tilde{W(k)}\tilde{P(t_0,k)}\\
+\end{align}
+
+We now let our initial time $t_0$ be zero and note that, because
+$W_n(\delta x) = W(\delta x)^n$, we can simplify our expression to:
+
+\begin{align}
+  \tilde{P(n,k)} &= N\tilde{W(k)}^n\tilde{P(t_0,k)}\\
+\end{align}
+
+We then take the Inverse Fourier Transform of this expression, yielding:
+
+\begin{align}
+  P(n,x) &= \int_{-\infty}^{\infty}\tilde{P(n,k)}e^{2\pi ikx}dk
+  = N\int_{-\infty}^{\infty}\tilde{W(k)}^n\tilde{P(t_0,k)}e^{2\pi ikx}dk\\
+\end{align}
+
+Since $P(0,x)$ is a delta function, we know that $\tilde{P}(0,x) = 1$, so:
+
+\begin{align}
+  P(n,x) &=  N\int_{-\infty}^{\infty}\tilde{W(k)}^ne^{2\pi ikx}dk\\
+\end{align}
+
 \end{document}

### 2016-08-03 thesis_stuff/thesis_stuff.tex
Add a bit to the CLT derivation.

@@
 \begin{align}
-  F{P(t_0+1,x')} &= F{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx}\\
-  \tilde{P(t_0+1,k)} &= N\tilde{W(k)}\tilde{P(t_0,k)}\\
+  F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
+  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)\\
 \end{align}
@@
 We now let our initial time $t_0$ be zero and note that, because
-$W_n(\delta x) = W(\delta x)^n$, we can simplify our expression to:
+$W_n(\Delta x) = W(\Delta x)^n$, we can simplify our expression to:
 
 \begin{align}
-  \tilde{P(n,k)} &= N\tilde{W(k)}^n\tilde{P(t_0,k)}\\
+  \widetilde{P}(n,k) &= \widetilde{W}(k)^n\widetilde{P}(t_0,k)\\
 \end{align}
@@
 \begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\tilde{P(n,k)}e^{2\pi ikx}dk
-  = N\int_{-\infty}^{\infty}\tilde{W(k)}^n\tilde{P(t_0,k)}e^{2\pi ikx}dk\\
+  P(n,x) &= \int_{-\infty}^{\infty}\widetilde{P}(n,k)e^{2\pi ikx}dk
+  = \int_{-\infty}^{\infty}\widetilde{W}(k)^n\widetilde{P}(t_0,k)e^{2\pi ikx}dk\\
 \end{align}
 
-Since $P(0,x)$ is a delta function, we know that $\tilde{P}(0,x) = 1$, so:
+Since $P(0,x)$ is a delta function, we know that $\widetilde{P}(0,x) = 1$, so:
 
 \begin{align}
-  P(n,x) &=  N\int_{-\infty}^{\infty}\tilde{W(k)}^ne^{2\pi ikx}dk\\
+  P(n,x) &=  \int_{-\infty}^{\infty}\widetilde{W}(k)^ne^{2\pi ikx}dk\\
+\end{align}
+
+%% The Taylor Series for $\widetilde{W}(k)$ is:
+
+%% \begin{align*}
+%%   \widetilde{W}(k) &= \widetilde{W}(0) + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_2}(0)\\
+%%   &= 1 + \frac{k^2}{2}\widetilde{W_2}(0)\\
+%% \end{align*}
+
+%% \textbf{Because W(k) is an even Gaussian function, $W'(0)$ = 0 and $W(0) = 1$} - is this right?\\
+
+We then make the substitution $\widetilde{W}(k) = \widetilde{C}-1$, so we can use the Binomial Expansion:
+
+\begin{align}
+  P(n,x) &=  \int_{-\infty}^{\infty}\left(1 + \widetilde{c}\right)^ne^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n {}_nC_\alpha \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+\end{align}
+
+The Taylor Series of our goal, the Gaussian function, is:\\
+
+\begin{align*}
+  e^{\frac{-x^2}{2\sigma^2}} &= \sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\left(\frac{x}{\sqrt{2}\sigma}\right)^{2\alpha}\\
+\end{align*}
+
+We want to make our expression for $P(n,x)$ resemble this. We begin by saying that, for sufficiently large $n$, the higher-order
+$\alpha$ terms in the sum go to zero due to the $1/\alpha!$. Thus, we can extend our sum to infinity:\\
+
+\begin{align}
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+\end{align}
+
+We then apply Sterling's Approximation in the form $Z! = e^{Z\ln(Z)-Z}$:
+
+\begin{align}
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{e^{n\ln(n)-n}}{e^{(n-\alpha)\ln(n-\alpha)-(n-\alpha)}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+\end{align}
+
+Because n is large, we can get rid of its decaying exponentials and simplify:\\
+
+\begin{align}
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}e^{\alpha}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk\\
 \end{align}

### 2016-08-03 thesis_stuff/thesis_stuff.tex
Even more to CLT derivation.

@@
 \begin{align}
-  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\\
+  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx
 \end{align}
@@
 \begin{align*}
-  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx\\
+  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx
 \end{align*}
@@
   F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
-  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)\\
+  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)
 \end{align}
@@
 \begin{align}
-  \widetilde{P}(n,k) &= \widetilde{W}(k)^n\widetilde{P}(t_0,k)\\
+  \widetilde{P}(n,k) &= \widetilde{W}(k)^n\widetilde{P}(t_0,k)
 \end{align}
@@
   P(n,x) &= \int_{-\infty}^{\infty}\widetilde{P}(n,k)e^{2\pi ikx}dk
-  = \int_{-\infty}^{\infty}\widetilde{W}(k)^n\widetilde{P}(t_0,k)e^{2\pi ikx}dk\\
+  = \int_{-\infty}^{\infty}\widetilde{W}(k)^n\widetilde{P}(t_0,k)e^{2\pi ikx}dk
 \end{align}
@@
 \begin{align}
-  P(n,x) &=  \int_{-\infty}^{\infty}\widetilde{W}(k)^ne^{2\pi ikx}dk\\
+  P(n,x) &=  \int_{-\infty}^{\infty}\widetilde{W}(k)^ne^{2\pi ikx}dk
 \end{align}
@@
   &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n {}_nC_\alpha \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
 \end{align}
@@
 \begin{align*}
-  e^{\frac{-x^2}{2\sigma^2}} &= \sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\left(\frac{x}{\sqrt{2}\sigma}\right)^{2\alpha}\\
+  e^{\frac{-x^2}{2\sigma^2}} &= \sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\left(\frac{x}{\sqrt{2}\sigma}\right)^{2\alpha}
 \end{align*}
@@
 \begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
 \end{align}
@@
   P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{e^{n\ln(n)-n}}{e^{(n-\alpha)\ln(n-\alpha)-(n-\alpha)}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
 \end{align}
@@
   P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}e^{\alpha}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^\alpha}{(1-\frac{\alpha}{n})^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
 \end{align}
 
+We now use the following simplification, assuming that $\alpha/n < 1$:
+
+\begin{align*}
+  \left(1-\frac{\alpha}{n}\right)^{n-\alpha} &= \sigma_{x=0}^{n-\alpha} \frac{(n-\alpha)!}{(n-\alpha-x)!x!} \left(\frac{\alpha}{n}\right)^x\\
+  &= 1 - (n-\alpha)\left(\frac{\alpha}{n}\right) + (n-\alpha)(n-\alpha-1)\left(\frac{\alpha}{n}\right)^2
+\end{align*}
+
+  take further $\alpha/n$ terms out?\\
+
 \end{document}

### 2016-08-03 thesis_stuff/thesis_stuff.tex
Finish transcribing CLT derivation (nonworking) into Latex.

@@
 
-%% The Taylor Series for $\widetilde{W}(k)$ is:
+The Taylor Series for $\widetilde{W}(k)$ is:
 
-%% \begin{align*}
-%%   \widetilde{W}(k) &= \widetilde{W}(0) + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_2}(0)\\
-%%   &= 1 + \frac{k^2}{2}\widetilde{W_2}(0)\\
-%% \end{align*}
+\begin{align*}
+  \widetilde{W}(k) &= \widetilde{W}(0) + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_3}(0) + ...\\
+  &= 1 + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_3}(0) ...\\
+\end{align*}
 
-%% \textbf{Because W(k) is an even Gaussian function, $W'(0)$ = 0 and $W(0) = 1$} - is this right?\\
+We define a variable $\widetilde{W}$ such that:
 
-We then make the substitution $\widetilde{W}(k) = \widetilde{C}-1$, so we can use the Binomial Expansion:
+\begin{align*}
+  \widetilde{W}(k) &= 1 - \widetilde{C}\\
+  \widetilde{C} &= -(k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_3}(0) ...)\\
+\end{align*}
+
+This allows us to substitute in $\widetilde{C}$ and use the Binomial Expansion:
 
 \begin{align}
-  P(n,x) &=  \int_{-\infty}^{\infty}\left(1 + \widetilde{c}\right)^ne^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n {}_nC_\alpha \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
+  P(n,x) &=  \int_{-\infty}^{\infty}\left(1 - \widetilde{C}\right)^ne^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n {}_nC_\alpha\left(-\widetilde{C}\right)^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!(-1)^\alpha}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
 \end{align}
@@
 \begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
 \end{align}
@@
 \begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{e^{n\ln(n)-n}}{e^{(n-\alpha)\ln(n-\alpha)-(n-\alpha)}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{e^{n\ln(n)-n}}{e^{(n-\alpha)\ln(n-\alpha)-(n-\alpha)}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
 \end{align}
@@
 \begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}e^{\alpha}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^\alpha}{(1-\frac{\alpha}{n})^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}e^{\alpha}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^\alpha}{(1-\frac{\alpha}{n})^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
 \end{align}
 
-We now use the following simplification, assuming that $\alpha/n < 1$:
+%% We now use the following simplification, assuming that $\alpha/n < 1$:
 
-\begin{align*}
-  \left(1-\frac{\alpha}{n}\right)^{n-\alpha} &= \sigma_{x=0}^{n-\alpha} \frac{(n-\alpha)!}{(n-\alpha-x)!x!} \left(\frac{\alpha}{n}\right)^x\\
-  &= 1 - (n-\alpha)\left(\frac{\alpha}{n}\right) + (n-\alpha)(n-\alpha-1)\left(\frac{\alpha}{n}\right)^2
-\end{align*}
+%% \begin{align*}
+%%   \left(1-\frac{\alpha}{n}\right)^{n-\alpha} &= \sum_{x=0}^{n-\alpha} \frac{(n-\alpha)!}{(n-\alpha-x)!x!} \left(\frac{\alpha}{n}\right)^x\\
+%%   &= 1 - (n-\alpha)\left(\frac{\alpha}{n}\right) + (n-\alpha)(n-\alpha-1)\left(\frac{\alpha}{n}\right)^2\\
+%%   &= 1 - \alpha + \frac{\alpha^2}{n} + \alpha^2 + \frac{-\alpha^3}{n} + \frac{-\alpha^2}{n} + \frac{-\alpha^3}{n} + \frac{\alpha^4}{n^2} + \frac{\alpha^3}{n^2}\\
+%%   &= 1 - \alpha + \alpha^2 + \frac{-2\alpha^3}{n} + \frac{\alpha^4}{n^2} + \frac{\alpha^3}{n^2}\\
+%% \end{align*}
 
-  take further $\alpha/n$ terms out?\\
+We then supply the middle factorial fraction with a name, $m = \frac{1}{(1-\frac{\alpha}{n})^{n-\alpha}}$:
+
+\begin{align}
+  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{m(-1)^\alpha}{\alpha!}\sqrt{\frac{n\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
+\end{align}
+
+\textbf{TODO: figure out why m is there}
+
+We then are \textit{almost} in a form where we can invert the Gaussian Taylor Expansion. We try it anyway, ignoring m. We also make the assumptions
+that our second $\widetilde{W}_1(0)$ Taylor Expansion term in $\widetilde{C}$ is zero and the third term is negative.\\
+
+\begin{align}
+  P(n,x) &= \int_{-\infty}^{\infty}e^{\frac{-k^2}{\sqrt{2}\frac{e}{|nW_2(0)|}}}e^{2\pi ikx}dk\\
+  &= \int_{-\infty}^{\infty}e^{\frac{-k^2}{\sqrt{2}\sigma^2}}e^{2\pi ikx}dk
+\end{align}
+
+We finally use the fact that Gaussians take the same form in real and Fourier space to undo the transform:
+
+\begin{align}
+  P(n,x) &= e^{\frac{-k^2}{\sqrt{2}\sigma^2}}\\
+\end{align}
+
+where
+
+\begin{align}
+  \sigma^2 = \frac{e}{n|W_2(0)|}\\
+\end{align}
+
+%% We then solve for $\widetilde{W}_2(0)$ to find our variance:
+
+%% \begin{align}
+%%   \widetilde{W}_2(0) &= \frac{d^2}{dk^2}\widetilde{W}(0)\\
+%%   &= \left(\frac{d^2}{dk^2}\int_{-\infty}^{\infty}W(x)e^{2\pi ikx}dx\right)_{k=0}\\
+%% \end{align}
 

### 2016-08-05 thesis_stuff/thesis_stuff.tex
Add new CLT derivation using new math.

@@
 
+\section{Alternative CLT Derivation}
+Here we show that, given an initial PDF as a delta function $P(t_0,x) = \delta(x)$
+and any transition likelihood $W(s)$ for some step size s and 1 timestep, P
+eventually evolves into a Gaussian function.\\
+
+We use a discrete time, continuous position model:\\
+
+\begin{align}
+  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx
+\end{align}
+
+This matches the form of a convolution integral:
+
+\begin{align*}
+  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx
+\end{align*}
+
+By the Convolution Theorem (prove?) we can simplify the above expression:
+
+\begin{align}
+  F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
+  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)
+\end{align}
+
+We see that in general, the transformed probability distribution after n
+timsteps is given by:\\
+
+\begin{align}
+  \widetilde{P}(t_0+n,k) &= \widetilde{W}(k)\widetilde{P}(t_0+n-1,k)
+\end{align}
+
+Thus our distribution after n timesteps can be expressed as:
+
+\begin{align}
+  \widetilde{P}(t_0+n,k) &= \widetilde{W}^n(k)\widetilde{P}(t_0,k)\\
+\end{align}
+
+We wish to solve for the non-transformed probability distribution, so we
+apply the inverse Fourier Transform:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}\widetilde{W}^n(k)\widetilde{P}(t_0,k)e^{ikx}dk\\
+\end{align}
+
+We specified our initial probability as a delta function, which Fourier Transforms to unity:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}\widetilde{W}^n(k)e^{ikx}dk\\
+\end{align}
+
+We now introduce a new definition $\widetilde{W} = e^{\widetilde{L}}$:\\
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{n\widetilde{L}}e^{ikx}dk\\
+\end{align}
+
+We now need to expand $\widetilde{L}$. We use a Taylor Series:
+
+\begin{align*}
+  \widetilde{L}(k) &= \ln(\widetilde{W}) = \sum\frac{k^n\frac{d^n}{dk^n}\ln(\widetilde{W})}{n!}\\
+  &= \ln\left(\widetilde{W}(0)\right) + k\frac{\widetilde{W}_1(0)}{\widetilde{W}(0)}
+  + \frac{k^2}{2}\left(\frac{\widetilde{W}_2(0)}{\widetilde{W}(0)} - \frac{\widetilde{W}_1(0)^2}{\widetilde{W}_0(0)^2}\right)
+  + \frac{k^3}{6}\left(\frac{2\widetilde{W}_1(0)^3}{\widetilde{W}_(0)^3} + \frac{\widetilde{W}_3(0)}{\widetilde{W}(0)}
+     - \frac{3\widetilde{W}_1(0)\widetilde{W}_2(0)}{\widetilde{W}(0)^2}\right)
+  + \frac{k^4}{24}\left(\frac{6\widetilde{W}_1(0)^2\widetilde{W}_2(0)}{\widetilde{W}(0)^3} - \frac{6\widetilde{W}_1(0)^4}{\widetilde{W}(0)^4}
+  - \frac{3\widetilde{W}_2(0)^2}{\widetilde{W}(0)^2} - \frac{3\widetilde{W}_1(0)\widetilde{W}_3(0)}{\widetilde{W}(0)^2}
+  + \frac{6\widetilde{W}_1(0)^2\widetilde{W}_2(0)}{\widetilde{W}(0)^3} + \frac{\widetilde{W}_4(0)}{\widetilde{W}(0)}
+  - \frac{\widetilde{W}_1(0)\widetilde{W}_3(0)}{\widetilde{W}(0)^2}\right) + O(5)\\   
+\end{align*}
+
+We then make the following assumption: \textbf{Assume all odd terms in $\widetilde{W}$'s expansion are zero}. We justify this by imposing that
+$\widetilde{W}$ must be symmetric about the y-axis. We also say that $\widetilde{W}_1(0)=1$, which I don't know how to justify -- (just because
+W is normalized to one doesn't mean its maximum point equals one?). These assumptions allow us to simplify $\widetilde{L}$:\\
+
+\begin{align*}
+  \widetilde{L}(k) &= \frac{k^2}{2}\widetilde{W}_2(0) + \frac{k^4}{24}\left(\widetilde{W}_4(0) - 3\widetilde{W}_2(0)\right)\\
+  &\approx \frac{k^2}{2}\widetilde{W}_2(0)
+\end{align*}
+
+We then plug this into our definition for $P(t_0+n,k)$:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{n\frac{k^2}{2}\widetilde{W}_2(0)}e^{ikx}dk\\
+\end{align}
+
+In order to be normalizable, all derivatives of $\widetilde{W}$ must be negative. Thus we rewrite
+$\widetilde{W}_2$:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{-n\frac{k^2}{2}|\widetilde{W}_2(0)|}e^{ikx}dk\\
+\end{align}
+
+This takes the form of a Gaussian. We know that Gaussians are invariant under Fourier Transsform,
+so:\\
+
+\begin{align}
+  P(t_0+n,k) &= e^{\frac{k^2}{2\sigma^2}}\\
+\end{align}
+
+where $\sigma = \sqrt{\frac{1}{n\widetilde{W}_2(0)}}$. As expected by the CLT, the standard deviation of our
+new probability depends on $\frac{1}{\sqrt{n}}$!\\
+
 \end{document}

### 2016-08-05 thesis_stuff/thesis_stuff.tex
Add more to CLT new derivation. Still lots of confusion, the result is close but not quite there, and involves lots of unjustified assumptions.

--- 2016-08-03 thesis_stuff/thesis_stuff.tex
@@
 
+\section{Alternative CLT Derivation}
+Here we show that, given an initial PDF as a delta function $P(t_0,x) = \delta(x)$
+and any transition likelihood $W(s)$ for some step size s and 1 timestep, P
+eventually evolves into a Gaussian function.\\
+
+We use a discrete time, continuous position model:\\
+
+\begin{align}
+  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx
+\end{align}
+
+This matches the form of a convolution integral:
+
+\begin{align*}
+  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx
+\end{align*}
+
+By the Convolution Theorem (prove?) we can simplify the above expression:
+
+\begin{align}
+  F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
+  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)
+\end{align}
+
+We see that in general, the transformed probability distribution after n
+timsteps is given by:\\
+
+\begin{align}
+  \widetilde{P}(t_0+n,k) &= \widetilde{W}(k)\widetilde{P}(t_0+n-1,k)
+\end{align}
+
+Thus our distribution after n timesteps can be expressed as:
+
+\begin{align}
+  \widetilde{P}(t_0+n,k) &= \widetilde{W}^n(k)\widetilde{P}(t_0,k)
+\end{align}
+
+We wish to solve for the non-transformed probability distribution, so we
+apply the inverse Fourier Transform:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}\widetilde{W}^n(k)\widetilde{P}(t_0,k)e^{ikx}dk
+\end{align}
+
+We specified our initial probability as a delta function, which Fourier Transforms to unity:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}\widetilde{W}^n(k)e^{ikx}dk
+\end{align}
+
+We now introduce a new definition $\widetilde{W} = e^{\widetilde{L}}$:\\
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{n\widetilde{L}}e^{ikx}dk
+\end{align}
+
+We now need to expand $\widetilde{L}$. We use a Taylor Series:
+
+\begin{align*}
+  \widetilde{L}(k) &= \ln(\widetilde{W}) = \sum\frac{k^n\frac{d^n}{dk^n}\ln(\widetilde{W})}{n!}\\
+  &= \ln\left(\widetilde{W}(0)\right) + k\frac{\widetilde{W}_1(0)}{\widetilde{W}(0)}
+  + \frac{k^2}{2}\left(\frac{\widetilde{W}_2(0)}{\widetilde{W}(0)} - \frac{\widetilde{W}_1(0)^2}{\widetilde{W}_0(0)^2}\right)
+  + \frac{k^3}{6}\left(\frac{2\widetilde{W}_1(0)^3}{\widetilde{W}_(0)^3} + \frac{\widetilde{W}_3(0)}{\widetilde{W}(0)}
+     - \frac{3\widetilde{W}_1(0)\widetilde{W}_2(0)}{\widetilde{W}(0)^2}\right)\\
+  &+ \frac{k^4}{24}\left(\frac{6\widetilde{W}_1(0)^2\widetilde{W}_2(0)}{\widetilde{W}(0)^3} - \frac{6\widetilde{W}_1(0)^4}{\widetilde{W}(0)^4}
+  - \frac{3\widetilde{W}_2(0)^2}{\widetilde{W}(0)^2} - \frac{3\widetilde{W}_1(0)\widetilde{W}_3(0)}{\widetilde{W}(0)^2}
+  + \frac{6\widetilde{W}_1(0)^2\widetilde{W}_2(0)}{\widetilde{W}(0)^3} + \frac{\widetilde{W}_4(0)}{\widetilde{W}(0)}
+  - \frac{\widetilde{W}_1(0)\widetilde{W}_3(0)}{\widetilde{W}(0)^2}\right) + O(5)
+\end{align*}
+
+We then make the following assumption: \textbf{Assume all odd terms in $\widetilde{W}$'s expansion are zero}. We justify this by imposing that
+$\widetilde{W}$ must be symmetric about the y-axis. We also say that $\widetilde{W}_1(0)=1$, which I don't know how to justify -- (just because
+W is normalized to one doesn't mean its maximum point equals one?). These assumptions allow us to simplify $\widetilde{L}$:\\
+
+\begin{align*}
+  \widetilde{L}(k) &= \frac{k^2}{2}\widetilde{W}_2(0) + \frac{k^4}{24}\left(\widetilde{W}_4(0) - 3\widetilde{W}_2(0)\right)
+\end{align*}
+
+I'm not really sure how to justify this part either:
+
+\begin{align}
+  \widetilde{L}(k) &\approx \frac{k^2}{2}\widetilde{W}_2(0)
+\end{align}
+
+We then plug this into our definition for $P(t_0+n,k)$:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{n\frac{k^2}{2}\widetilde{W}_2(0)}e^{ikx}dk
+\end{align}
+
+In order to be normalizable, all derivatives of $\widetilde{W}$ must be negative. Thus we rewrite
+$\widetilde{W}_2$:
+
+\begin{align}
+  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{-n\frac{k^2}{2}|\widetilde{W}_2(0)|}e^{ikx}dk
+\end{align}
+
+This takes the form of a Gaussian. We know that Gaussians are invariant under Fourier Transform,
+so:\\
+
+\begin{align}
+  P(t_0+n,k) &= e^{\frac{k^2}{2\sigma^2}}
+\end{align}
+
+where $\sigma = \sqrt{\frac{1}{n\widetilde{W}_2(0)}}$. As expected by the CLT, the standard deviation of our
+new probability depends on $\frac{1}{\sqrt{n}}$!\\
+
+We now try and find more out about $|\widetilde{W}_2(k)|$:
+
+\begin{align*}
+  \widetilde{W}_2(k) &= \frac{d^2}{dk^2}\widetilde{W}(k)\\
+  &= \frac{d^2}{dk^2}\int_{-\infty}^\infty W(x)e^{-ikx}dx\\
+  &= \frac{d}{dk}\int_{-\infty}^\infty -ixW(x)e^{-ikx}dx\\
+  &= -\int_{-\infty}^\infty x^2W(x)e^{-ikx}dx\\
+\end{align*}
+
+We are specifically interested in the case where $k=0$:
+
+\begin{align*}
+  \widetilde{W}_2(0) &= -\int_{-\infty}^\infty x^2W(x)dx
+\end{align*}
+
+We explicitly denote $\widetilde{W}_2$'s negativity:
+
+\begin{align*}
+  |\widetilde{W}_2(0)| &= \int_{-\infty}^\infty x^2W(x)dx
+\end{align*}
+
+and finally note that, since W is the transition probability per timestep, this looks like the expected squared deviation
+in a single timestep:
+
+\begin{align*}
+  |\widetilde{W}_2(0)| &= \int_{-\infty}^\infty x^2W(x)dx = <\Delta x>
+\end{align*}
+
+We plug this back into our Gaussian to get our final answer:
+
+\begin{align}
+  P(t_0+n,k) &= e^{\frac{k^2}{2\frac{1}{n<\Delta x>}}}
+\end{align}
+
+A $\sigma = \sqrt{\frac{1}{n<W>}}$ does not make sense. For one, $\sqrt{<\Delta x>}$ should be in the numerator, since it is the
+single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
+$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...
+
 \end{document}

### 2016-08-15 thesis_stuff/thesis_stuff.tex

@@
 
+\section{Biochemistry Papers}
+
+\subsection{Winch Model (dx.doi.org/10.1016/j.bpj.2014.06.022)}
+-Communication between motors and BDs possible through $\alpha$-helix sliding. Bidirectional communication. [24,25]\\
+-Pre, post-powerstroke states\\
+-Pre-powerstroke: unbound state after ATP hydrolysis (our onebound)\\
+-Post-powerstroke: bound state (our bothbound)\\
+-Elastic stalk, unlike our rigid one\\
+-Only tail angle changes between pre and post-powerstroke\\
+-MTBD decides directionality?\\
+-Tail-tail interaction, also motor-motor stacking interaction\\
+-rate constant simulation, does not do dynamics to take into account time spent in a state\\
+
+\subsection{Physical Parameters from Winch Model paper}
+Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
+domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when
+prestroke.
+
 \end{document}

### 2016-08-21 latex/derivation.tex
Minor adds.

@@
 \begin{align}  
-  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
-  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
-  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
-  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
+  \dot{X}_{bm} &= \dot{X}_{bb} + - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + -\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
+  \dot{X}_{t}  &= \dot{X}_{bm} + - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + -\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
+  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + -\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
+  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + -\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
 \end{align}
@@
 \begin{align}  
-  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
-  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
-  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
+  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + -\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
+  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + -\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
+  \dot{Y}_{fm} &= \dot{Y}_{t } + - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + -\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
+  \dot{Y}_{fb} &= \dot{Y}_{fm} + - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + -\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
 \end{align}

### 2016-08-21 dynein_struct_onebound.cpp

@@ -154,65 +154,6 @@ void Dynein_onebound::update_internal_forces() {
   }
 }
 
-// void Dynein_onebound::switch_to_bothbound() {
-//   double temp_nma;
-//   double temp_fma;
-
-//   if (state == NEARBOUND) {
-//     temp_nma = M_PI + bma - bba;
-//     temp_fma = M_PI + uma - uba;
-//     nbx = get_bbx();
-//     L = fbx - nbx;
-//   } else {
-//     temp_nma = M_PI + uma - uba;
-//     temp_fma = M_PI + bma - bba;
-//     nbx = get_fbx();
-//     L = bbx - fbx;
-//   }
-
-//   distance_traveled += fabs(get_ubx() - get_bbx());
-//   steps++;
-
-//   state = BOTHBOUND;
-//   nma = temp_nma;
-//   fma = temp_fma;
-// }
-
-// void Dynein_onebound::switch_to_nearbound() {
-//   //nearbound -> bma is nma
-//   double temp_bba = get_nba();
-//   double temp_bma = nma;
-//   double temp_uma = fma;
-//   double temp_uba = get_fba();
-
-//   bbx = get_nbx();
-//   bby = 0;
-
-//   bba = temp_bba;
-//   bma = temp_bma;
-//   uma = temp_uma;
-//   uba = temp_uba;
-
-//   state = NEARBOUND;
-// }
-
-// void Dynein_onebound::switch_to_farbound() {
-//   //nearbound -> bma is fma
-//   double temp_bba = get_fba();
-//   double temp_bma = fma;
-//   double temp_uma = nma;
-//   double temp_uba = get_nba();
-
-//   bbx = get_fbx();
-//   bby = 0;
-
-//   bba = temp_bba;
-//   bma = temp_bma;
-//   uma = temp_uma;
-//   uba = temp_uba;
-
-//   state = FARBOUND;
-// }
 
 void Dynein_onebound::update_velocities() {
   update_internal_forces();

### 2016-08-21 thesis_stuff/simulate_diffusion.py

@@ -1,0 +1,51 @@
+#!/usr/bin/python2.7
+
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+
+def get_cell_potential_gradient(pos):
+    return np.array([0, 0, 0])
+
+def simulate_particle(init_position):
+    t = 0
+    pos = np.array(init_position)
+    trajectory = [pos]
+    while t < runtime:
+        F = -get_cell_potential_gradient(pos)
+        R = np.random.normal(0, 2*kb*T*gamma/dt, 3)
+        v = F/gamma + R
+        pos += v*dt
+        if int(t/dt) % 100 == 0:
+            print "Position: " + str(pos) +  "completion: " + str(t / runtime)
+        trajectory.append(pos.copy())
+        t += dt
+    return trajectory
+
+def make_gif(trajectories):
+    fig = plt.figure()
+    ax = fig.add_subplot(111, projection='3d')
+    for trajectory in trajectories:
+        xs = [point[0] for point in trajectory]
+        ys = [point[1] for point in trajectory]
+        zs = [point[2] for point in trajectory]
+        ax.plot(xs, ys, zs)
+
+    # ax.set_xlim([-radius, radius])
+    # ax.set_ylim([-radius, radius])
+    # ax.set_zlim([-radius, radius])
+    plt.title("Diffusion trajectories")
+    plt.show()
+
+def main():
+    trajectories = []
+    for n in range(N):
+        init_position = np.array([0.0, 0.0, 0.0])
+        trajectory = simulate_particle(init_position)
+        trajectories.append(trajectory)
+    make_gif(trajectories)
+
+if __name__ == "__main__":
+    main()

### 2016-08-27 latex/paper.tex
Add first half of new onebound derivation.

@@
 
-\section{One bound}
+\section{Onebound}
 
@@
 
-In the one-bound case, we use four angles, as illustrated in
-Fig.~\ref{fig:onebound}.
+First, some definitions...
+\begin{align*}
+F_{bmx} &= \frac{f_{bmx} + R_{bmx}}{\gamma}\\
+F_{xt } &= \frac{f_{xt} + R_{xt}}{\gamma}\\
+...\\
+X_{bs} &= \frac{X_{bm} - X_{bb}}{\gamma}\\
+X_{bt} &= \frac{X_t - X_{bm}}{\gamma}\\
+...\\
+\end{align*}
+
+\subsection{Brownian Dynamics equations}
+\begin{align*}
+  \dot{X}_{bm} &= F_{bmx} - \gm\lambda_{bs}X_{bs} + \gm\lambda_{bt}X_{bt}\\
+  \dot{X}_{t}  &= F_{tx}  - \gt\lambda_{bt}X_{bt} + \gt\lambda_{ut}X_{ut}\\
+  \dot{X}_{um} &= F_{umx} - \gm\lambda_{ut}X_{ut} + \gm\lambda_{us}X_{us}\\
+  \dot{X}_{ub} &= F_{ubx} - \gb\lambda_{us}X_{us}
+\end{align*}
+
+\begin{align*}
+  \dot{Y}_{bm} &= F_{bmx} - \gm\lambda_{bs}Y_{bs} + \gm\lambda_{bt}Y_{bt}\\
+  \dot{Y}_{t}  &= F_{tx}  - \gt\lambda_{bt}Y_{bt} + \gt\lambda_{ut}Y_{ut}\\
+  \dot{Y}_{um} &= F_{umx} - \gm\lambda_{ut}Y_{ut} + \gm\lambda_{us}Y_{us}\\
+  \dot{Y}_{ub} &= F_{ubx} - \gb\lambda_{us}Y_{us}
+\end{align*}
+
+\subsection{Expanded velocities}
+
+\begin{align*}
+\dot{X}_{bm} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
+\dot{X}_{t } &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
+\dot{X}_{um} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
+\dot{X}_{ub} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
+\end{align*}
+
+\begin{align*}
+\dot{Y}_{bm} &= L_s\cos(\theta_{bb})\dot{\theta}_{bm}\\
+\dot{Y}_{t } &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm}\\
+\dot{Y}_{um} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um}\\
+\dot{Y}_{ub} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub}\\
+\end{align*}
+
+\subsection{System of Equations}
+Now to create our system of equations, we combine the Brownian equations with our expanded velocities.
+This system of equations takes into account both the dynamics of Brownian Mechanics (from the BD equations) as well as the constraints of our coordinate system (from the velocity expansions).
+
+\begin{align*}
+F_{bmx} - \gm\lambda_{bs}X_{bs} + \gm\lambda_{bt}X_{bt} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
+F_{tx}  - \gt\lambda_{bt}X_{bt} + \gt\lambda_{ut}X_{ut} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
+F_{umx} - \gm\lambda_{ut}X_{ut} + \gm\lambda_{us}X_{us} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
+F_{ubx} - \gb\lambda_{us}X_{us} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
+\\
+F_{bmy} - \gm\lambda_{bs}Y_{bs} + \gm\lambda_{bt}Y_{bt} &= L_s\cos(\theta_{bb})\dot{\theta}_{bm}\\
+F_{ty}  - \gt\lambda_{bt}Y_{bt} + \gt\lambda_{ut}Y_{ut} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm}\\
+F_{umy} - \gm\lambda_{ut}Y_{ut} + \gm\lambda_{us}Y_{us} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um}\\
+F_{uby} - \gb\lambda_{us}Y_{us} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub}\\
+\end{align*}
+
+\subsection{Matrix form}
+
+\[
+\hspace{-2.5cm}
+\begin{pmatrix}
+  L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gm X_{bs} & \gm\lambda_{bt}X_{bt} & 0 & 0\\
+  L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gt X_{bt} & \gt X_{ut} & 0\\
+  L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gm X_{ut} & \gm X_{us}\\
+  L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gb X_{us}\\
+  -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gm Y_{bs} & \gm Y_{bt} & 0 & 0\\
+  -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gt Y_{bt} & \gt Y_{ut} & 0\\
+  -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gm Y_{ut} & \gm Y_{us}\\
+  -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gb Y_{us}\\
+\end{pmatrix}
+\begin{pmatrix}
+  \dot{\theta}_{bb}\\
+  \dot{\theta}_{bm}\\
+  \dot{\theta}_{um}\\
+  \dot{\theta}_{ub}\\
+  \lambda_{bs}\\
+  \lambda_{bt}\\
+  \lambda_{ut}\\
+  \lambda_{us}\\
+\end{pmatrix}
+=
+\begin{pmatrix}
+  -F_{bmx}\\
+  -F_{tx}\\
+  -F_{umx}\\
+  -F_{ubx}\\
+  -F_{bmy}\\
+  -F_{ty}\\
+  -F_{umy}\\
+  -F_{uby}\\
+\end{pmatrix}
+\]
+
+\subsection{Mathematica input}
+The above matrix equation can be represented as follows and solved via Mathematica:
+
+\begin{align*}
+AA &= L_s\sin\theta_{bb}      &  LL &= -L_s\cos(\theta_{bb})\\
+BB &= L_t\sin(\theta_{bm})    &	 MM &= -L_t\cos(\theta_{bm})\\
+CC &= -L_t\sin(\theta_{um})   &	 NN &= L_t\cos(\theta_{um})\\
+DD &= -L_s\sin(\theta_{ub})   &	 OO &= L_s\cos(\theta_{ub})\\
+\\
+EE &= -\gm X_{bs}       &    PP &= -\gm Y_{bs}\\
+FF &= \gm X_{bt}	    &	 QQ &= \gm Y_{bt}\\ 
+GG &= -\gt X_{bt}	    &	 RR &= -\gt Y_{bt}\\
+HH &= \gt X_{ut}	    &	 SS &= \gt Y_{ut}\\ 
+II &= -\gm X_{ut}	    &	 TT &= -\gm Y_{ut}\\
+JJ &= \gm X_{us}	    &	 UU &= \gm Y_{us}\\ 
+KK &= -\gb X_{us}       &	 VV &= -\gb Y_{us}\\
+\end{align*}
+
+\[
+\begin{pmatrix}
+  AA & 0 & 0 & 0 & EE & FF & 0 & 0\\
+  AA & BB & 0 & 0 & 0 & GG & HH & 0\\
+  AA & BB & CC & 0 & 0 & 0 & II & JJ\\
+  AA & BB & CC & DD & 0 & 0 & 0 & KK\\
+  LL & 0 & 0 & 0 & PP & QQ & 0 & 0\\
+  LL & MM & 0 & 0 & 0 & RR & SS & 0\\
+  LL & MM & NN & 0 & 0 & 0 & TT & UU\\
+  LL & MM & NN & OO & 0 & 0 & 0 & VV\\
+\end{pmatrix}
+V
+=
+\begin{pmatrix}
+  X1\\
+  X2\\
+  X3\\
+  X4\\
+  X5\\
+  X6\\
+  X7\\
+  X8\\
+\end{pmatrix}
+\]
 

### 2016-09-01 latex/paper.tex
Fix paper.tex changes.
Add minor changes to paper.tex.

@@
 \usepackage{verbatim}
+
+\newcommand{\gb}{\frac{1}{\gamma_b}}
+\newcommand{\gm}{\frac{1}{\gamma_m}}
+\newcommand{\gt}{\frac{1}{\gamma_t}}
 
@@
 
-\twocolumn
-
-\section{Onebound}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../figures/code-onebound}
-  \caption{Angles used in one-bound case.}\label{fig:onebound}
-\end{figure}
+\section{Onebound derivation}
 
@@
 F_{xt } &= \frac{f_{xt} + R_{xt}}{\gamma}\\
-...\\
+..\\
+\end{align*}
+
+\begin{align*}
 X_{bs} &= \frac{X_{bm} - X_{bb}}{\gamma}\\
-X_{bt} &= \frac{X_t - X_{bm}}{\gamma}\\
-...\\
+X_{bt} &= \frac{X_{t} - X_{bm}}{\gamma}\\
+X_{ut} &= \frac{X_{um} - X_{t}}{\gamma}\\
+X_{us} &= \frac{X_{ub} - X_{um}}{\gamma}\\
+\end{align*}
+
+\begin{align*}
+Y_{bs} &= \frac{Y_{bm} - Y_{bb}}{\gamma}\\
+Y_{bt} &= \frac{Y_{t} - Y_{bm}}{\gamma}\\
+Y_{ut} &= \frac{Y_{um} - Y_{t}}{\gamma}\\
+Y_{us} &= \frac{Y_{ub} - Y_{um}}{\gamma}\\
+\end{align*}
+
+\subsection{Domain positions}
+\begin{align*}
+X_{bm} &= L_s\cos(\theta_{bb})\\
+X_{t } &= L_s\cos(\theta_{bb}) + L_t\cos(\theta_{bm})\\
+X_{um} &= L_s\cos(\theta_{bb}) + L_t\cos(\theta_{bm}) - L_t\cos(\theta_{um})\\
+X_{ub} &= L_s\cos(\theta_{bb}) + L_t\cos(\theta_{bm}) - L_t\cos(\theta_{um}) - L_s\cos(\theta_{ub})\\
+\end{align*}
+
+\begin{align*}
+Y_{bm} &= L_s\sin(\theta_{bb})\\
+Y_{t } &= L_s\sin(\theta_{bb}) + L_t\sin(\theta_{bm})\\
+Y_{um} &= L_s\sin(\theta_{bb}) + L_t\sin(\theta_{bm}) - L_t\sin(\theta_{um})\\
+Y_{ub} &= L_s\sin(\theta_{bb}) + L_t\sin(\theta_{bm}) - L_t\sin(\theta_{um}) - L_s\sin(\theta_{ub})\\
+\end{align*}
+
+\subsection{Domain velocities}
+\begin{align*}
+\dot{X}_{bm} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
+\dot{X}_{t } &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
+\dot{X}_{um} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
+\dot{X}_{ub} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
+\end{align*}
+
+\begin{align*}
+\dot{Y}_{bm} &= L_s\cos(\theta_{bb})\dot{\theta}_{bm}\\
+\dot{Y}_{t } &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm}\\
+\dot{Y}_{um} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um}\\
+\dot{Y}_{ub} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub}\\
 \end{align*}
@@
   \dot{Y}_{ub} &= F_{ubx} - \gb\lambda_{us}Y_{us}
-\end{align*}
-
-\subsection{Expanded velocities}
-
-\begin{align*}
-\dot{X}_{bm} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
-\dot{X}_{t } &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
-\dot{X}_{um} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
-\dot{X}_{ub} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
-\end{align*}
-
-\begin{align*}
-\dot{Y}_{bm} &= L_s\cos(\theta_{bb})\dot{\theta}_{bm}\\
-\dot{Y}_{t } &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm}\\
-\dot{Y}_{um} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um}\\
-\dot{Y}_{ub} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub}\\
 \end{align*}

### 2016-09-05 thesis_stuff/thesis_stuff.tex
Add citations to thesis_stuff.tex

@@
 Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
-domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when
-prestroke.
+domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when prestroke.
+
+\section{Citations}
+Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\
+
+Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S.
+``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural & Molecular Biology}.
+2012, 19:193-200.\\
 

### 2016-09-05 thesis_stuff/thesis_stuff.tex
Add notes on Dynein pre-powerstroke crystal structure paper.

@@
 \section{Citations}
+\subsection{Annual Review, 8-state Mechanochemical diagram}
 Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\
 
+Goes over in detail the various steps of the Dynein chemical cycle. Links to a lot of good papers.\\
+
+\subsection{Weihong's Dynein stepping data}
 Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S.
@@
 
+Has the stepping histograms we are trying to reproduce computationally.
+
+\subsection{Pre-powerstroke structure, linker remodel details}
+Schmidt, H*., Zalyte, R*., Urnavicius, L., Carter, AP. ``Structure of human cytoplasmic dynein-2 primed for its power stroke.'' \textit{Nature} 2014. 518:435-438.
+
+Describes how ATP hydrolysis ``closes the ring,'' sterically interacting with the linker to cause the pre-powerstroke conformation.
+Does so by presenting the crystal structure of Dynein AAA1-ADP.Vanadate.
+Goes over AAs responsible for nucleotide binding.
+Supplemental video of AAA1L-AAA2L gap closing in response to nucleotide-Vi binding.
+Supplemental video of linker swinging in response to ring closure.
+AAA2-4 system acts rigidly during the cycle.
+Discusses how steric clash is what makes the linker take on a 90-degree bent shape when the ring closes.
+Figure on Dynein-ADP buttress having no kink, whereas Dynein-ADP.Vi having a kink.
+The kink presumably changes MTDB binding affinity.
+
 \end{document}

### 2016-09-06 thesis_stuff/thesis_stuff.tex
Add notes on annual review paper.

@@
 \usepackage{amsmath}
-\usepackage{physics}
 \usepackage{amssymb}
@@
 single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
-$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...
-
-\section{Biochemistry Papers}
+$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...\\
+\\
+\section{Papers}
 
@@
 
-\subsection{Physical Parameters from Winch Model paper}
+\textbf{Physical Parameters from Winch Model paper}:\\
 Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
@@
 
-\section{Citations}
 \subsection{Annual Review, 8-state Mechanochemical diagram}
@@
 
-Goes over in detail the various steps of the Dynein chemical cycle. Links to a lot of good papers.\\
+Goes over in detail the various steps of the Dynein chemical cycle. Eight-state model as follows:\\
+
+\begin{enumerate}
+\item Dynein begins cycle with AAA1 binding site open.
+\item ATP then binds to the AAA1 binding site.
+\item ATP binding causes ``ring closure,'' where the AAA1 and AAA2 subdomains shift closer together.
+\item Ring closure (ie ATP binding) causes the buttress to shift, causing the MTBD to lose MT affinity.
+\item Ring closure (ATP binding) also causes the linker to bend 90 degrees, causing the monomer to enter the pre-powerstroke state.
+The order of states 4.
+and 5.
+is unknown, but entering pre-powerstroke \textit{after} unbinding from the MT causes more directional motion.
+The role of ATP hydrolysis also is not understood as of this paper (2015).
+\item Random walk of the low-MT-affinity MTBD eventually leads to weak rebinding at a new place on the MT.
+\item Rebinding causes a change in the MTBD back to its high affinity state.
+AAA4 moves to prevent steric clash when the linker straightens.
+AAA5/6 move away from AAA1 and the linker straightens to its post-powerstroke conformation.
+NOTE: this is distinct from the conformation in steps 1-4 in that AAA1/2 is still closed.
+\item The linker shifts some more and AAA1/2 opens up, releasing ADP.
+\end{enumerate}
 
@@
 Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S.
-``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural & Molecular Biology}.
+``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural \& Molecular Biology}.
 2012, 19:193-200.\\

### 2016-09-06 thesis_stuff/thesis_stuff.tex
Add binding constants to thesis_stuff.pdf.
Add Equipartition Theorem agreement figures to thesis_stuff.pdf.

@@
 
-and finally note that, since W is the transition probability per timestep, this looks like the expected squared deviation
-in a single timestep:
+and finally note that, since W is the transition probability per timestep, this looks like the expected squared deviation in a single timestep:
 
@@
 \\
+
+\section{Un/binding constants}
+We let our un/binding rates $k_b$ and $k_u$ be, according to the Arrhenius equation:
+
+\begin{align}
+  k_b &= A_be^{\Delta G_{u\rightarrow b}\beta}\\
+  k_u &= A_ue^{\Delta G_{b\rightarrow u}\beta}
+\end{align}
+
+Our Gibb's free energy changes are given as functions of angular state $\theta$:
+
+\begin{align}
+  \Delta G_{u\rightarrow b}(\theta) &= \sum_i \frac{1}{2}c_{bi}\Delta\theta_{bi}^2 - \sum_i \frac{1}{2}c_{ui}\Delta\theta_{ui}^2 + G_{bind}\\
+  \Delta G_{u\rightarrow b}(\theta) &= \sum_i \frac{1}{2}c_{ui}\Delta\theta_{ui}^2 - \sum_i \frac{1}{2}c_{bi}\Delta\theta_{bi}^2 + G_{unbind}\\
+\end{align}
+
+\section{Equipartition Theorem}
+Both bothbound and onebound states show good agreement with the equipartition theorem. Horizontal dashed line represents Equipartition Thorem energy $\frac{1}{2}k_BT$.
+
+\begin{figure}[h!]
+  \centering
+
+  \begin{minipage}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
+    \caption{Onebound PE vs time.}
+  \end{minipage}
+  \begin{minipage}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
+    \caption{Bothbound PE vs time.}
+  \end{minipage}
+  \label{fig:equipartition_agreement}
+\end{figure}
+
 \section{Papers}
-
 \subsection{Winch Model (dx.doi.org/10.1016/j.bpj.2014.06.022)}

### 2016-09-17 thesis_stuff/thesis_stuff.tex
Minor modification to thesis_stuff.tex.

@@
 
+\section{Physical Parameters}
+\subsection{Stalk and tail length}
+Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and XXXX (pre and post-powerstroke) to find
+these values.
+
 \section{Papers}
@@
 
+\subsection{3D Pre/Post-PS structures, there are two Pre-PS states!}
+Jianfeng Lin, Kyoko Okada, Milen Raytchev, Maria C. Smith \& Daniela Nicastro. ``Structural mechanism of the dynein power stroke.'' \textit{Nature Cell Biology} 2014. 16:479-485.
+
+This paper finds the 3D structures of both pre (3J68) and post (3J67)-powerstroke dynein.
+This paper is about \textbf{axonmenal} dynein, which seems to be wildly different from cytoplasmic dynein, but this paper doesn't really mention any differences.
+The paper claims there are three conformational states: prestroke-1 immediately after MT unbinding, prestroke-2 after MT-binding, then poststroke after the powerstroke.
+This paper claims that transitioning between the post and pre-powerstroke ``resembled an opening jackknife with an angular amplitude of ~65$^{\circ}$ or ~50$^{\circ}$, depending on which axonemal dynein.
+It is unclear what this jackknife metaphor is referring to - the linker?.
+They make the claim that \textit{rotation of the head is the principle mechanism of Dynein powerstroke, not linker remodelling}.
+They seem to be claiming that the major thing differentiating the three states is the motor domain/head angle.
+It starts out facing the MT in post-stroke, then rotates away from the MT by 50-70 degrees into pre-1, then rotates towards the MT by 20 degrees to enter pre-2.\\
+
+These figures show different measurements for equilibrium angles from the data in this paper:\\
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
+    \caption{Post-powerstroke equilibrium angles from EM tomography.}
+  \end{minipage}
+  \hspace{5mm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
+    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
+  \end{minipage}
+  \label{fig:em_tomography_eq_angles}
+\end{figure}
+
 \end{document}

### 2016-09-17 thesis_stuff/thesis_stuff.tex
Add new paper to thesis_stuff.tex, eq angle figures inbound.

@@
 \subsection{3D Pre/Post-PS structures, there are two Pre-PS states!}
-Jianfeng Lin, Kyoko Okada, Milen Raytchev, Maria C. Smith \& Daniela Nicastro. ``Structural mechanism of the dynein power stroke.'' \textit{Nature Cell Biology} 2014. 16:479-485.
+Jianfeng Lin, Kyoko Okada, Milen Raytchev, Maria C. Smith & Daniela Nicastro. ``Structural mechanism of the dynein power stroke.'' \textit{Nature Cell Biology} 2014. 16:479-485.
 
@@
 The paper claims there are three conformational states: prestroke-1 immediately after MT unbinding, prestroke-2 after MT-binding, then poststroke after the powerstroke.
-This paper claims that transitioning between the post and pre-powerstroke ``resembled an opening jackknife with an angular amplitude of ~65$^{\circ}$ or ~50$^{\circ}$, depending on which axonemal dynein.
+This paper claims that transitioning between the post and pre-powerstroke ``resembled an opening jackknife with an angular amplitude of ~65$\cdot$ or ~50$\cdot$, depending on which axonemal dynein.
 It is unclear what this jackknife metaphor is referring to - the linker?.
@@
 They seem to be claiming that the major thing differentiating the three states is the motor domain/head angle.
-It starts out facing the MT in post-stroke, then rotates away from the MT by 50-70 degrees into pre-1, then rotates towards the MT by 20 degrees to enter pre-2.\\
-
-These figures show different measurements for equilibrium angles from the data in this paper:\\
-
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
-    \caption{Post-powerstroke equilibrium angles from EM tomography.}
-  \end{minipage}
-  \hspace{5mm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
-    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
-  \end{minipage}
-  \label{fig:em_tomography_eq_angles}
-\end{figure}
-
+It starts out facing the MT in post-stroke, then rotates away from the MT by 50-70 degrees into pre-1, then rotates towards the MT by 20 degrees to enter pre-2
 \end{document}

### 2016-09-18 thesis_stuff/thesis_stuff.tex
Make latex compile.

--- 2016-09-17 thesis_stuff/thesis_stuff.tex
@@
 
+\section{Interesting Crystal Structures}
+\textbf{3VKH} - 2.8A x-ray resolution full dynein motor, from Kon 2012 (2.8A crystal structure of the dynein motor domain).
+Probably what we'll use to get some equilibrium angles and lengths, though not sure if crystal structures are identical to in vivo structures.
+Discusses amino acid chemistry of the powerstroke and long-distance MTBD/ATPase communication.\\
+\textbf{3J67/3J68} 34A EM structure of pre/post motor (from Structural Mechanism of dynein power stroke 2014).
+Shows in-depth changes to motor, but appears to only be the six ATPases and possibly buttress.
+\textbf{3J1T/3J1U} 9.7A EM structure of tightly/loosly bound tubulin-MTBD binding from (Structural basis for microtubule binding and release by dynein).\\
+\textbf{4RH7} 2.3A x-ray crystal structure of dynein motor/stalk with ADP.Vi (pre-stroke) from (Structure of human cytoplasmic dynein-2 primed for its power stroke).
+Could be another good place to get angles for pre-stroke, since 3VKH is post-stroke.\\
+
 \section{Papers}
@@
 They seem to be claiming that the major thing differentiating the three states is the motor domain/head angle.
-It starts out facing the MT in post-stroke, then rotates away from the MT by 50-70 degrees into pre-1, then rotates towards the MT by 20 degrees to enter pre-2.\\
+It starts out facing the MT in post-stroke, then rotates away from the MT by 50-70 degrees into pre-1, then rotates towards the MT by 20 degrees to enter pre-2.
+Not entirely sure if it's all axonemal, since the PDB page for the structures says it's a cytoplasmic gene.\\
 
@@
   \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
+    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
     \caption{Post-powerstroke equilibrium angles from EM tomography.}
@@
   \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
+    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
     \caption{Pre-powerstroke equilibrium angles from EM tomography.}

### 2016-09-18 thesis_stuff/thesis_stuff.tex
Add table summarizing papers' estimations of some figures, or at least the beginning of such a table. Note: summary of Winch paper is likely wrong for rate constants.

@@
 \section{Physical Parameters}
+
+\begin{center}
+  \begin{tabular}{| l | l | l | l | l | l |}
+    \hline
+    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
+    Ls & 12nm & & & &\\ \hline
+    Lt &  & & & &\\ \hline
+    $\theta_{m}^{Pre}$ & & & & &\\ \hline
+    $\theta_{m}^{Post}$ & & & & &\\ \hline
+    $\theta_{b}$ & 56 & & & &\\ \hline
+    $\theta_{t}$ & 0 & & & &\\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
+    $k_b$ & $1000 s^{-1,b}$ & & & &\\ \hline
+  \end{tabular}
+\end{center}
+
+a: The transition from post-stroke to prestroke in the Winch paper is given by three transitions: the binding of ATP ($k_{+ATP} = 2.2*10^{6} M^{-1}s^{-1}$), dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$).
+We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound.\\
+
+b: The transition from prestroke to poststroke in the Winch paper is given by three transitions: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$), the power stroke itself ($k_{PS} = 5000 s^{-1}$) and ADP release ($k_{-ADP} = 1000 s^{-1}$).\\
+
 \subsection{Stalk and tail length}

### 2016-09-19 thesis_stuff/thesis_stuff.tex
Add right equilibrium angle figures and cool crystal structures to thesis_stuff.tex.

--- 2016-09-18 thesis_stuff/thesis_stuff.tex
@@
   \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
+    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomograph.jpg}
     \caption{Post-powerstroke equilibrium angles from EM tomography.}
@@
   \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
+    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomograph.jpg}
     \caption{Pre-powerstroke equilibrium angles from EM tomography.}

### 2016-09-20 thesis_stuff/thesis_stuff.tex
Add todo to thesis_stuff.tex.

--- 2016-09-18 thesis_stuff/thesis_stuff.tex
@@
 
+\section{Todo}
+\begin{itemize}
+\item Add dt testing figure to thesis\_stuff.tex.
+\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
+\item Check out kinetic parameters papers in the Winch model, see how they are aquired
+\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
+\item Make a figure with PyMol visualizations with and without our model superimposed
+\end{itemize}
 \end{document}

### 2016-09-20 thesis_stuff/thesis_stuff.tex
Add minor change to thesis_stuff.tex.

@@
     & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
-    Ls & 12nm & & & &\\ \hline
-    Lt &  & & & &\\ \hline
+    $L_s$ & 12nm & & & &\\ \hline
+    $L_t$ &  & & & &\\ \hline
+    $R_b$ &  & & & &\\ \hline
+    $R_m$ &  & & & &\\ \hline
+    $R_t$ &  & & & &\\ \hline
     $\theta_{m}^{Pre}$ & & & & &\\ \hline
@@
     $\theta_{t}$ & 0 & & & &\\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
-    $k_b$ & $1000 s^{-1,b}$ & & & &\\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$? review & & & &\\ \hline
+    $k_b$ & $1000 s^{-1,b}$? review & & & &\\ \hline
   \end{tabular}
@@
 \item Make a figure with PyMol visualizations with and without our model superimposed
+\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
 \end{itemize}

### 2016-09-22 thesis_stuff/thesis_stuff.tex
Figure out the Winch paper angle scheme and get a couple more equilibrium angles for thesis_stuff.pdf!

--- 2016-09-19 thesis_stuff/thesis_stuff.tex
@@
 \section{Physical Parameters}
+
+\begin{center}
+  \begin{tabular}{| l | l | l | l | l | l |}
+    \hline
+    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
+    $L_s$ & 12nm & & & &\\ \hline
+    $L_t$ &  7nm & & & &\\ \hline
+    $R_b$ &  & & & &\\ \hline
+    $R_m$ &  7nm & & & &\\ \hline
+    $R_t$ &  & & & &\\ \hline
+    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
+    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
+    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
+    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
+  \end{tabular}
+\end{center}
+
+---- not sure if the Lin angles are right, since measuring the angle that the tail makes is \textit{not} necessarily the angle the angle the linker makes ----\\
+
+a: Sarlah \textit{et al} gives us two different rate constants which could represent the bothbound to onebound transition: motor dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$).
+We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound since it is the slower of the two.\\
+
+b: There are several Sarlah \textit{et al} rate constants we could use for the onebound to bothbound rate constant: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$) or the power stroke itself ($k_{PS} = 5000 s^{-1}$).
+We choose to represent the transition with $k_{-Pi} = 5000 s^{-1}$ because all these rates are fairly similar.
+We do not want to use the MT-binding rate because it could include both binding kinetics as well as MT-search kinetics, the latter of which we do not want to include in our binding rate.\\
+
 \subsection{Stalk and tail length}
@@
 \textbf{Physical Parameters from Winch Model paper}:\\
-Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm, $L_t = 14$nm, binding angle: 34 degrees from vertical, motor
-domain radius: 7nm, motor domain angle from vertical: 30 degrees, tail angle: 0 degrees between linkers when poststroke, 40 degrees when prestroke.
+Sarlah et al. use the following physical parameters for Dynein: $L_s = 12$nm binding angle: 34 degrees from vertical, motor
+domain radius: 7nm. Their angle scheme is different than ours in that it has the linker/tail facing towards the MT, which looks different
+from our facing-up tail.
+This might be a confusion on our part in the difference between the linker and the tail, but it may not.
+By assuming the linker starts at the top of the head and points downwards, we can calculate an estimate for tail length as $L_t = 7nm$.
 
@@
   \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomograph.jpg}
+    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
     \caption{Post-powerstroke equilibrium angles from EM tomography.}
@@
   \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomograph.jpg}
-    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
+    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
+    \caption{Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
   \end{minipage}
@@
 
+\subsection{2012 Kon Crystal Structure (3VKH)}
+This paper crystallizes a full-length and MTBD-truncation mutants. 3VKH is the full-length, but one MTBD of the dimer did not come out in the crystal structure.
+
+\section{Todo}
+\begin{itemize}
+\item Add dt testing figure to thesis\_stuff.tex.
+\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
+\item Check out kinetic parameters papers in the Winch model, see how they are aquired
+\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
+\item Make a figure with PyMol visualizations with and without our model superimposed
+\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
+\item Fix generate-stepping-data non-printing bug.
+\end{itemize}
 \end{document}

### 2016-09-23 thesis_stuff/thesis_stuff.tex
Fix rate constants from Winch paper in thesis_stuff.tex.

--- 2016-09-20 thesis_stuff/thesis_stuff.tex
@@
 
-a: The transition from post-stroke to prestroke in the Winch paper is given by three transitions: the binding of ATP ($k_{+ATP} = 2.2*10^{6} M^{-1}s^{-1}$), dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$).
-We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound.\\
+a: Sarlah \textit{et al} gives us two different rate constants which could represent the bothbound to onebound transition: motor dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$).
+We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound since it is the slower of the two.\\
 
-b: The transition from prestroke to poststroke in the Winch paper is given by three transitions: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$), the power stroke itself ($k_{PS} = 5000 s^{-1}$) and ADP release ($k_{-ADP} = 1000 s^{-1}$).\\
+b: There are several Sarlah \textit{et al} rate constants we could use for the onebound to bothbound rate constant: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$) or the power stroke itself ($k_{PS} = 5000 s^{-1}$).
+We choose to represent the transition with $k_{-Pi} = 5000 s^{-1}$ because all these rates are fairly similar.
+We do not want to use the MT-binding rate because it could include both binding kinetics as well as MT-search kinetics, the latter of which we do not want to include in our binding rate.\\
 
@@
 \item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
+\item Fix generate-stepping-data non-printing bug.
 \end{itemize}

### 2016-09-23 thesis_stuff/thesis_stuff.tex
Add a bit more to thesis_stuff.tex.

@@
     $R_t$ &  & & & &\\ \hline
-    $\theta_{m}^{Pre}$ & & & & &\\ \hline
-    $\theta_{m}^{Post}$ & & & & &\\ \hline
-    $\theta_{b}$ & 56 & & & &\\ \hline
-    $\theta_{t}$ & 0 & & & &\\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$? review & & & &\\ \hline
-    $k_b$ & $1000 s^{-1,b}$? review & & & &\\ \hline
+    $\theta_{m}^{Pre}$ & & & 171$^{\circ}$ & &\\ \hline
+    $\theta_{m}^{Post}$ & & & 137.5$^{\circ}$ & &\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
+    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
+    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
   \end{tabular}
@@
     \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
-    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
+    \caption{Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
   \end{minipage}

### 2016-09-23 thesis_stuff/thesis_stuff.tex
Add more measurements to thesis_stuff.pdf.

--- 2016-09-22 thesis_stuff/thesis_stuff.tex
@@
     & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
-    $L_s$ & 12nm & & & &\\ \hline
-    $L_t$ &  7nm & & & &\\ \hline
-    $R_b$ &  & & & &\\ \hline
-    $R_m$ &  7nm & & & &\\ \hline
+    $L_s$ & 12nm & & 21.0nm & &\\ \hline
+    $L_t$ &  7nm & & 11.15nm & &\\ \hline
+    $R_b$ &  & & 1.57nm & &\\ \hline
+    $R_m$ &  7nm & & 7.36nm & &\\ \hline
     $R_t$ &  & & & &\\ \hline
@@
 \subsection{Stalk and tail length}
-Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and XXXX (pre and post-powerstroke) to find
-these values.
+Sarlah et.
+al use stalk and tail lengths of 12 and 14 nm, respectively.
+We used PyMol to examine the crystal structures 3VKH and 4RH7 (pre and post-powerstroke) to find these values.
+The linker is roughly residues 1250-1510, calculated by eye.\\
 
 \section{Interesting Crystal Structures}
-\textbf{3VKH} - 2.8A x-ray resolution full dynein motor, from Kon 2012 (2.8A crystal structure of the dynein motor domain).
+\textbf{3VKH} 2.8A x-ray resolution full dynein motor, from Kon 2012 (2.8A crystal structure of the dynein motor domain).
 Probably what we'll use to get some equilibrium angles and lengths, though not sure if crystal structures are identical to in vivo structures.

### 2016-09-24 thesis_stuff/thesis_stuff.tex
Add last measurements from PyMol.

@@
     & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
-    $L_s$ & 12nm & & 21.0nm & &\\ \hline
-    $L_t$ &  7nm & & 11.15nm & &\\ \hline
-    $R_b$ &  & & 1.57nm & &\\ \hline
-    $R_m$ &  7nm & & 7.36nm & &\\ \hline
-    $R_t$ &  & & & &\\ \hline
+    $L_s$ & 12nm & & & 21.0nm & 22.1nm\\ \hline
+    $L_t$ &  7nm & & & & 11.15nm\\ \hline
+    $R_b$ &  & & & 1.57nm & 1.45nm\\ \hline
+    $R_m$ &  7nm & & & 7.36nm & 6.3nm\\ \hline
+    $R_t$ &  & & & & 2.16nm \\ \hline
     $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline

### 2016-09-29 thesis_stuff/thesis_stuff.tex
Minor changes to thesis_stuff.pdf

--- 2016-09-23 thesis_stuff/thesis_stuff.tex
@@
     & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
-    $L_s$ & 12nm & & 21.0nm & &\\ \hline
-    $L_t$ &  7nm & & 11.15nm & &\\ \hline
-    $R_b$ &  & & 1.57nm & &\\ \hline
-    $R_m$ &  7nm & & 7.36nm & &\\ \hline
-    $R_t$ &  & & & &\\ \hline
+    $L_s$ & 12nm & & & 21.0nm & 22.1nm\\ \hline
+    $L_t$ &  7nm & & & & 11.15nm\\ \hline
+    $R_b$ &  & & & 1.57nm & 1.45nm\\ \hline
+    $R_m$ &  7nm & & & 7.36nm & 6.3nm\\ \hline
+    $R_t$ &  & & & & 2.16nm \\ \hline
     $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
     $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & &\\ \hline
     $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline

### 2016-09-30 thesis_stuff/thesis_stuff.tex
Add brief Imamula paper notes to tehsis_stuff.pdf.

@@
 
+\subsection{Imamula Stepping Model}
+This is an older (2007) paper presenting a chemical model.
+It gives more MT dissociation constants for several different dyneins, and averages them as: $K_{d,pre} = 0.2uM$, $K_{d,post} > 10uM$.
+They determine these by adding a known concentration of Dynein apo, ATP, ADP-Pi or ADP, adding microtubules, removing MT-Dynein dimers and remeasuring concentration.
+These parameters are good in that equilibrium constants (as opposed to rate constants) \textit{don't} take into account kinetics, only free energy change...right?\\
+
 \section{Todo}
@@
 \item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
-\item Fix generate-stepping-data non-printing bug.
+\item Make Dynein binding rate diagram showing how our model relates to the Imamula one
+\item Make pretty dynein visualization in PyMol (or some software) showing how dimerization happens AND how docking to the MT happens; ask David what this should look like
 \end{itemize}

### 2016-09-30 thesis_stuff/thesis_stuff.tex
make figure use references

@@
 
-These figures show different measurements for equilibrium angles from the data in this paper:\\
-
+Figure~\ref{fig:em_tomography_eq_angles} shows different measurements
+for equilibrium angles from the data in this paper.
 \begin{figure}[h!]
   \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
-    \caption{Post-powerstroke equilibrium angles from EM tomography.}
-  \end{minipage}
-  \hspace{5mm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
-    \caption{Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
-  \end{minipage}
+  \includegraphics[width=.45\textwidth]{../figures/Post_powerstroke_tomography.jpg}
+  \includegraphics[width=.45\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
+  \caption{Post- and Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
   \label{fig:em_tomography_eq_angles}

### 2016-10-01 thesis_stuff/thesis_stuff.tex
teach make to build figures I hope and add pretty figure
Add new rate scheme based on Winch paper.

--- 2016-09-30 thesis_stuff/thesis_stuff.tex
@@
 
+\subsection{Arrhenius Rate}
+Papers often supply rate constants for various transitions.
+Our model uses Arhennius-type rates which take into account the change in conformational energy from switching equilibrium angles, so we must
+convert between these two systems:
+
+\begin{align*}
+  k_{bind} &= Ae^{-\beta(\Delta G_{bind} + \Delta G_{conf})}\\
+  k_{bind} &= \left(Ae^{-\beta\Delta G_{bind}}\right)e^{-\beta\Delta G_{conf}}\\
+  k_{bind} &= Be^{-\beta\Delta G_{conf})}\hspace{2cm}\mbox{B constant at constant T}\\
+  \left<k_{bind}\right> &= \left<Be^{-\beta\Delta G_{conf}}\right>\\
+  \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
+  \left<\Delta G_{conf}\right> &= \left(4-2\right)\left(\frac{1}{2}k_BT\right) = \beta^{-1}\\
+  \left<k_{bind}\right> &= Be^{-1}\\
+  \rightarrow B &= \frac{k_{bind}}{e}\\
+\end{align*}
+
 \section{Interesting Crystal Structures}
@@
 \subsection{Imamula Stepping Model}
-This is an older (2007) paper presenting a chemical model.
-It gives more MT dissociation constants for several different dyneins, and averages them as: $K_{d,pre} = 0.2uM$, $K_{d,post} > 10uM$.
-They determine these by adding a known concentration of Dynein apo, ATP, ADP-Pi or ADP, adding microtubules, removing MT-Dynein dimers and remeasuring concentration.
+This is an older (2007) paper presenting a chemical model and giving rate constants for MT un/binding.
+Averages are: $K_{d,pre} = 0.2uM$, $K_{d,post} > 10uM$.
+They determine these by adding a known concentration of monomeric Dynein apo, ATP, ADP-Pi or ADP, adding microtubules, removing MT-Dynein dimers and remeasuring concentration.
 These parameters are good in that equilibrium constants (as opposed to rate constants) \textit{don't} take into account kinetics, only free energy change...right?\\
+
+Also, the paper says that axonemal dyneins have multiple motor domains, i.e aren't dimers, so that changes the results from the Lin paper. The binding angle is probably valid, though.\\
 

### 2016-10-06 thesis_stuff/thesis_stuff.tex

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=.45\textwidth]{../figures/equilibrium-onebound}
+  \caption{Definition of equilibrium angles.}
+  \label{fig:eq_angles}
+\end{figure}
+
 \begin{center}

### 2016-11-17 thesis_stuff/thesis_stuff.tex
tweak thesis version of estimate for rate (but not code)
add note about time between steps to thesis_stuff

@@
   \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
-  \left<\Delta G_{conf}\right> &= \left(4-2\right)\left(\frac{1}{2}k_BT\right) = \beta^{-1}\\
-  \left<k_{bind}\right> &= Be^{-1}\\
-  \rightarrow B &= \frac{k_{bind}}{e}\\
+  \left<\Delta G_{conf}\right> &= \frac{1}{2}k_BT = \frac12\beta^{-1}\\
+  \left<k_{bind}\right> &= Be^{-1/2}\\
+  \rightarrow B &= \frac{k_{bind}}{\sqrt{e}}
 \end{align*}
@@
 
+\section{Notes by David}
+(This stuff can be deleted or edited or moved elsewhere...)
+
+The mean speed of dynein is $134\pm 60$~nm~s$^{-1}$.
+
+Its average step 1D displacement is 8~nm. (See page 194 of Weihong's \emph{Nature} paper.)
+
+Together this means that the mean time between steps is about 60~ms.
+Note milliseconds.  Thus we really need to be careful about how small
+our $\Delta t$ is.
+
 \section{Todo}

### 2016-11-18 thesis_stuff/thesis_stuff.tex
add a citation to thesis_stuff
use bibtex for a couple of examples
Add program scaling information to thesis_stuff.tex. We can generate a single step in 6.5 hours at dt=10^-11s!

@@
 
+\subsection{Program Scaling}
+Program runtimes, as of commit 62c4d:
+
+\begin{verbatim}
+elliotc12@bennet:~/dynein_walk$ grep "dt" default_parameters.h 
+double dt = 1e-11;
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-5
+Running for 1e-05 s
+
+real	0m5.001s
+user	0m4.972s
+sys	0m0.000s
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-5
+Running for 1e-05 s
+
+real	0m7.121s
+user	0m7.072s
+sys	0m0.000s
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-4
+Running for 0.0001 s
+
+real	0m26.666s
+user	0m26.608s
+sys	0m0.000s
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-4
+Running for 0.0001 s
+
+real	0m29.479s
+user	0m29.428s
+sys	0m0.000s
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-3
+Running for 0.001 s
+
+real	4m47.224s
+user	4m46.832s
+sys	0m0.000s
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-3
+Running for 0.001 s
+
+real	4m56.207s
+user	4m55.776s
+sys	0m0.000s
+elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-2
+Running for 0.01 s
+
+real	61m44.302s
+user	61m35.264s
+sys	0m0.120s
+\end{verbatim}
+
+The average time per iteration is ~3.9 microseconds, or 3.9e5 real seconds per simulated second at $dt=10^{-11}s$.
+Thus we can generate one 60-millisecond step in 23,400 seconds, or 6.5 hours.
+A thousand-step simulation would thus take, very roughly, 8 months.\\
+
 \section{Todo}

### 2016-11-18 thesis_stuff/thesis_stuff.tex

@@
 
-The mean speed of dynein is $134\pm 60$~nm~s$^{-1}$.
+The mean speed of dynein is $134\pm 60$~nm~s$^{-1}$.  It looks like
+perhaps the speed should be more like 80 or 80 nm/s~\cite{reck2006single}.
 
@@
 
-\subsection{Program Scaling}
+Note also another paper that is very similar to that of Weihong~\cite{dewitt2012cytoplasmic}.
+
+\section{Program Scaling}
 Program runtimes, as of commit 62c4d:
@@
 \end{itemize}
+
+\bibliographystyle{plain}
+\bibliography{thesis_stuff}
+
 \end{document}

### 2016-12-16 thesis_stuff/thesis_stuff.tex
Add calculations for ct and free energy of binding from Redwine et. al.

@@
 \usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins
-
-\usepackage{marvosym} % Required for symbols in the colored box
 
@@
 \begin{center}
-  \begin{tabular}{| l | l | l | l | l | l |}
+  \begin{tabular}{| l | l | l | l | l | l | l |}
     \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
-    $L_s$ & 12nm & & & 21.0nm & 22.1nm\\ \hline
-    $L_t$ &  7nm & & & & 11.15nm\\ \hline
-    $R_b$ &  & & & 1.57nm & 1.45nm\\ \hline
-    $R_m$ &  7nm & & & 7.36nm & 6.3nm\\ \hline
-    $R_t$ &  & & & & 2.16nm \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & &\\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
-    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
+    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine\\\hline
+    $L_s$ & 12nm & & & 21.0nm & 22.1nm &\\ \hline
+    $L_t$ &  7nm & & & & 11.15nm &\\ \hline
+    $R_b$ &  & & & 1.57nm & 1.45nm &\\ \hline
+    $R_m$ &  7nm & & & 7.36nm & 6.3nm &\\ \hline
+    $R_t$ &  & & & & 2.16nm & \\ \hline
+    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & \\ \hline
+    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & &\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & &\\ \hline
+    $\theta_{t}$ & 0$^{\circ}$ & & & & &\\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ & & & & &\\ \hline
+    $k_b$ & $5000 s^{-1,b}$ & & & & &\\ \hline
+    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol\\ \hline
+    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol\\ \hline
+    $c_t$ & & & & & & \\ \hline
+    $c_m$ & & & & & & \\ \hline
+    $c_b$ & & & & & & 140 kJ/mol\\ \hline
   \end{tabular}
@@
 
-\subsection{Arrhenius Rate}
+\subsection{Finding Arrhenius preexpontential from k}
 Papers often supply rate constants for various transitions.
-Our model uses Arhennius-type rates which take into account the change in conformational energy from switching equilibrium angles, so we must
-convert between these two systems:
+Our model uses Arhennius-type rates which take into account the change in conformational energy from switching equilibrium angles, so we must convert between free energy and rates:
 
@@
 
-\section{Interesting Crystal Structures}
+\subsection{Calculating $\Delta G_{bind}$}
+Based on Van der Spoel \textit{et. al.}, $\Delta H_{HB} = 10.6kJ/mol$ for water molecules forming a single hydrogen bond. Based on another paper (Anderson \textit{et al}), the
+``stabilizing energy'' of a single salt bridge (H-bond between charged molecules) is about 16 kJ/mol.\\
+
+Based on the interpreted bonds from crystal structures of the MTBD-MT complex shown in Redwine \textit{et. al}, there are 5.9 salt bridges in the high-affinity MTBD-MT
+complex and 3.1 in the low-affinity complex. Thus if we guess the free energy of a salt bridge as 12 kJ/mol, we can estimate binding energies as:
+
+\begin{align*}
+  \Delta G_{bind, high-affinity} &= -71 \mbox{ kJ/mol}\\
+  \Delta G_{bind, low-affinity} &= -37 \mbox{ kJ/mol}\\
+\end{align*}
+
+\subsection{Estimating $c_b$ spring constant}
+If the energy of binding of the MTBD foot to the MT is -71 kJ/mol, we can get a rough estimate of the spring constant for the binding domain. We say that
+$\Delta \theta \approx 0$ corresponds to being fully bound and $\Delta \theta \approx 1$ corresponds to breaking all salt bridges and being unbound. Thus:
+
+\begin{align*}
+  \frac 12 c_b \Delta \theta_{ba} = \Delta G_{bind, high} &\rightarrow c_b = 2\Delta G_{bind, high} \approx 140 \mbox{ kJ/mol}\\
+\end{align*}
+
+\section{Papers}
+
+\subsection{Interesting Crystal Structures}
 \textbf{3VKH} 2.8A x-ray resolution full dynein motor, from Kon 2012 (2.8A crystal structure of the dynein motor domain).
@@
 
-\section{Papers}
+\subsection{H-bond $\Delta G$ calculation paper}
+van der Spoel, D., J. van Maaren, P., Larsson, P., Timneanu, N. ``Thermodynamics of Hydrogen Bonding in Hydrophilic and Hydrophobic Media'' \textit{J. Phys. Chem. B} 2006: 110, 4393-4398.\\
+
+This paper uses classical simulations of water and alcohols to calculate thermodynamic parameters for the transition state and equilibrium state of water-water and water-alcohol
+hydrogen bonds. It uses H-bond lifetime and the Eyring rate equation to calculate transition state $\Delta G$ and number of H bond pairs / unbonded pairs to find equilibrium
+$\Delta G$. It then uses a Van't Hoff calculation to find enthalpies and entropies. Raman spectroscopy is shown to find a different enthalpy for water-water H-bonds. Findings:
+
+\begin{center}
+  \begin{tabular}{| l | l | l | l | l | l |}
+    \hline
+    & $\Delta G$ & $\Delta H$ & $T\Delta S$ \\\hline
+    Simulation & 5.11 kJ/mol & 9.0 kJ/mol & 4.1 kJ/mol\\ \hline
+    Experimental & 10.6 kJ/mol & & \\ \hline
+  \end{tabular}
+\end{center}
+
+where T = 298.15K.\\
+
+Another study (pH-Induced denaturation of proteins: a single salt bridge contributes 3-5 kcal/mol to the free energy of folding of T4 lysozyme by D. Anderson) found that
+a single salt bridge contributes about 16 kJ/mol to stabilizing a protein. We can use these numbers as estimates of the binding energy of the motor.\\
+
+\subsection{MTBD-Tubulin complex}
+Redwine, W.B. \textit{et. al.} ``Structural basis for microtubule binding and release by dynein. '' Science 2012, 337(6101): 1532–1536.
+
+This is a sub-nanometer MTBD-tubulin complex structure which shows how the complex forms. A cryo-EM structure was acquired, atomic-resolution structures for the high-affinity
+MTBD and tubulin dimers were superimposed.  Rigid body docking and molecular dynamics was then used to optimize this structure. Another technique was used to figure out how
+the low-affinity MTBD would bind, and yet another technique was used to translate between the low and high-affinity MTBDs to make an animation. Also did this with the Kon
+vanadium onebound crystal structure and not much changed.\\
+
+The MTBD-tubulin dimers are on the PDB as 3J1T for the high-affinity and 3J1U for the low-affinity structures.\\
+
+After finding the high- and low-affinity structures for the complexes, the authors guess at what salt bridges form in the two states between MT and MTBD.
+The reported values are shown in the tables below.\\
+
+\begin{table}
+  \parbox{.45\linewidth}{
+    \centering
+    \begin{tabular}{| l | l |}
+      \hline
+      Residue & Occupancy \\\hline
+      R3382-αE417 & 23\% \\\hline
+      R3382-αE420 & 79\% \\\hline
+      R3382-αG416 & 40\% \\\hline
+      K3299-βE431 & 60\% \\\hline
+      K3299-βD427 & 53\% \\\hline
+      R3342-βE159 & 51\% \\\hline
+      N3310-αG410 & 38\% \\\hline
+      L3385-αE415 & 48\% \\\hline
+      S3384-αG415 & 27\% \\\hline
+      A3383-αE415 & 49\% \\\hline
+      R3306-βE196 & 86\%*\\\hline
+      R3337-βD199 & 2\%* \\\hline
+      R3342-βN197 & 36\%*\\\hline
+    \end{tabular}
+    \caption{High-affinity MTBD-MT complex salt bridges. RH column is bonds between MTBD and MT, respectively.}
+  }
+  \hfill
+  \parbox{.45\linewidth}{
+    \centering
+    \begin{tabular}{| l | l |}
+      \hline
+      Residue & Occupancy \\\hline
+      A3383-αE415  & 45\% \\ \hline
+      R3382-αG416  & 44\% \\ \hline
+      R3382-αE417  & 61\% \\ \hline
+      R3382-αE420  & 79\% \\ \hline
+      K3299-βE196  & 27\% \\ \hline
+      S3307-βR253  & 16\% \\ \hline
+      L3385-αE415  & 34\% \\ \hline
+      N3310-αK112  & 10\% \\ \hline
+    \end{tabular}
+    \caption{Low-affinity MTBD-MT complex salt bridges. RH column is bonds between MTBD and MT, respectively.}
+  }
+\end{table}
+
+From this table we count the number of effective salt bridges in the high/low affinity complexes: 5.9 and 3.1, respectively.\\
+
+Some \textbf{really} cool videos of the MTBD switching from high/low affinity states. If you could get a similar video of the AAA domains binding ATP, these would be really
+cool videos to put in a presentation.\\
+
 \subsection{Winch Model (dx.doi.org/10.1016/j.bpj.2014.06.022)}
@@
 
+\subsection{Further reading}
+\begin{itemize}
+\item The dynein family at a glance. Höök P, Vallee RB J Cell Sci. 2006 Nov 1; 119(Pt 21):4369-71. The actual differences between axonemal/cytoplasmic dynein.
+\end{itemize}
+
 \section{Notes by David}

### 2016-12-17 thesis_stuff/thesis_stuff.tex
Add better calculations ftions for binding rate from Sarlah paper, and a script to help in this calculation

@@
 \usepackage{amssymb}
+\usepackage{verbatim}
 \pagestyle{fancy}
 \fancyhf{}
-% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
-% Example footer:
-%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}
 
@@
 \end{align*}
+
+\subsection{Properly implementing binding rates}
+To determine if it is time to do a state transition, we calculate the per-timestep
+transition probability $k_b/dt$, pick a number between zero and one, and transition
+if our number was the lower of the two.\\
+
+One issue with this is the rate constant $k_b$ is calculated experimentally from an
+ensemble of dynein, and doesn't take into account how transitions are much more likely in some orientations than others. In reality, dynein will only bind to the MT when
+its binding domain is less than 0.2nm away from a binding site.\\
+
+To fix this, we define a parameter $n$, the time fraction onebound dynein is capable
+of binding. Then a weighted average of the bindable and non-bindable rate constants
+looks like:
+
+\begin{equation*}
+  nk_{bindable} + (n-1)k_{nonbindable} = k_b
+\end{equation*}
+
+Since we say $k_{nonbindable} = 0$, $k_{bindable}$, our effective rate constant of
+binding, is $k_b/n$. Thus our preexponential Arrenhius factor is (see above):
+
+\begin{equation*}
+  B = \frac{k_{b}}{n\sqrt{e}}
+\end{equation*}
+
+\subsubsection{Calculating $n$}
+A script, \verb|simulations/get_binding_time_fraction.py|, calculates how often
+a onebound dynein spends in a bindable state:
+
+\verbatiminput{../simulations/simulation_results/binding_time_fraction.txt}
 

### 2016-12-22 thesis_stuff/thesis_stuff.tex
Minor change to preexponential factor thesis_stuff.pdf calc.
Fix previous fix of thesis_stuff.pdf.
Add work on [ATP] from Weihong's paper.

@@
 \end{align*}
+
+\subsection{ATP Concentration from Weihong's Paper}
+Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.
+Thus we need to calculate the equilibrium concentration of ATP:\\
+
+\begin{align*}
+  \Delta G^\cdot' &= \Delta G^\cdot + RT\ln Q\\
+  \rightarrow Q &= e^{-\frac{\Delta G^\cdot}{RT}}\\
+  \frac{[ADP][Pi]}{[ATP]} = \frac{n^2}{0.001 - n} &= e^{\frac{30.5}{0.008134*298}} = 2.915 * 10^{5}\\
+  \rightarrow n \approx 0.001
+\end{align*}
+
+Thus we see that $[ADP] = [Pi] \approx 0.001$, $[ATP] = 3.4*10^{-12}$. What's more, we see that, since the [ATP] and [ADP] are at equilibrium, there is no energy to be gained
+from hydrolysing ATP. Thus, dynein can't move. Maybe something is wrong...\\
 

### 2016-12-23 thesis_stuff/thesis_stuff.tex
Remove bad dG calculation.

--- 2016-12-17 thesis_stuff/thesis_stuff.tex
@@
   \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
-  \left<\Delta G_{conf}\right> &= \frac{1}{2}k_BT = \frac12\beta^{-1}\\
+  \left<\Delta G_{conf}\right> &= \frac{1}{2}k_BT = \frac12\beta^{-1}\hspace{2cm}\mbox{David, what was the justification for this again?}\\
   \left<k_{bind}\right> &= Be^{-1/2}\\
-  \rightarrow B &= \frac{k_{bind}}{\sqrt{e}}
+  \rightarrow B &= k_{bind}\sqrt{e}
 \end{align*}
@@
 \begin{equation*}
-  B = \frac{k_{b}}{n\sqrt{e}}
+  B = \frac{k_{b}\sqrt{e}}{n}
 \end{equation*}
@@
 \end{align*}
+
+\subsection{ATP Concentration from Weihong's Paper}
+Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.
 

### 2016-12-26 thesis_stuff/thesis_stuff.tex
Add parameter finding run log to thesis_stuff.tex with progress of runs.

@@
 \begin{align*}
-  \frac 12 c_b \Delta \theta_{ba} = \Delta G_{bind, high} &\rightarrow c_b = 2\Delta G_{bind, high} \approx 140 \mbox{ kJ/mol}\\
+  \frac 12 c_b \Delta \theta_{ba}^2 = \Delta G_{bind, high} &\rightarrow c_b = 2\Delta G_{bind, high} \approx 140 \mbox{ kJ/mol}\\
 \end{align*}
@@
 \subsection{ATP Concentration from Weihong's Paper}
-Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.
+Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.\\
+
+\subsection{Parameter fitting}
+Lots of different manual simulations and their outcomes.
+
+\begin{center}
+  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
+    \hline
+    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
+  \end{tabular}
+\end{center}
 

### 2016-12-27 thesis_stuff/thesis_stuff.tex
Add minor change to thesis_stuff.tex.

@@
 
-\subsection{Parameter fitting}
+\subsection{Parameter hunt}
 Lots of different manual simulations and their outcomes.
@@
     22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
   \end{tabular}

### 2016-12-29 thesis_stuff/thesis_stuff.tex
Add feature to save disc space by only printing movie data when program crashes.

@@
     22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
     22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & trying to find good springs for binding & this one seems to keel over, not strong enough springs\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, but this one seems to also keel over, so springs not strong enough\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & trying to find good springs for binding & Looks good, takes lots of steps! Too many?\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 4.65 & 4.65 & 4.65 & trying to find good springs for binding & Seems very rigid, but might have the right probabilities\\\hline
   \end{tabular}

### 2016-12-30 thesis_stuff/thesis_stuff.tex
Add spring constant finding stuff to thesis_stuff.tex.

--- 2016-12-27 thesis_stuff/thesis_stuff.tex
@@
     \hline
-    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
+    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind})\Big>$  & errors\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & & \\\hline
   \end{tabular}
 \end{center}
+
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-32786885246,cm-0.0232786885246,ct-0.0232786885246,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-6393442623,cm-0.116393442623,ct-0.116393442623,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-6229508197,cm-0.186229508197,ct-0.186229508197,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-2786885246,cm-0.232786885246,ct-0.232786885246,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-1967213115,cm-0.581967213115,ct-0.581967213115,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-393442623,cm-1.16393442623,ct-1.16393442623,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-590163934,cm-1.74590163934,ct-1.74590163934,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-786885246,cm-2.32786885246,ct-2.32786885246,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-983606557,cm-2.90983606557,ct-2.90983606557,T-310.15.out
+findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-180327869,cm-3.49180327869,ct-3.49180327869,T-310.15.out
 

### 2016-12-30 thesis_stuff/thesis_stuff.tex
Make stepping data files slightly prettier.

--- 2016-12-27 thesis_stuff/thesis_stuff.tex
@@
     \hline
-    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
+    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ $ steps / second & errors\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & ??      & & keeled over after ns \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & & keeled over after ns\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & & no error yet\\\hline
   \end{tabular}
 \end{center}
+
+If the mean stepping rate from Weihong's paper is ~ 1 step / .1 seconds, then at a dt of $1e-11$s would lead to a desired unbinding
+probability of $1e-11/.1 = 1e-10$.
 

### 2016-12-30 thesis_stuff/thesis_stuff.tex
Add average length/time to stepping histograms.

--- 2016-12-29 thesis_stuff/thesis_stuff.tex
@@
 \begin{center}
-  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
+  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
     \hline
-    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & trying to find good springs for binding & this one seems to keel over, not strong enough springs\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, but this one seems to also keel over, so springs not strong enough\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & trying to find good springs for binding & Looks good, takes lots of steps! Too many?\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 4.65 & 4.65 & 4.65 & trying to find good springs for binding & Seems very rigid, but might have the right probabilities\\\hline
+    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 7.8e-3 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & ?? & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
+    22.1 & 11.1 & 2500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 1500 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 &  500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 &  100 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
   \end{tabular}
 \end{center}
+
+If the mean stepping rate from Weihong's paper is about 1 step / .1 seconds, then at a dt of $1e-11$s would lead to a desired unbinding
+probability of $1e-11s/.1s = 1e-10$. The stepping probability was determined by printing out a random subset of unbinding probabilities
+for the bothbound case, then averaging.\\
+
+A more reliable step time determiner is $\Big<\mbox{step time}\Big>$. This number can be determined from the step time histograms.\\
 

### 2016-12-30 make_stepping_plots.py

@@ -48,7 +48,7 @@ plt.hist(step_lengths,
 plt.title("Stepping length histogram " + data_name)
 plt.xlabel("Step length (nm)")
 plt.ylabel("Frequency")
-add_config_info(config_txt)
+add_config_info(config_txt + "\n\n<step length>: %.2e" % np.mean(step_lengths))
 plt.savefig("plots/stepping_length_histogram_" + data_name + ".pdf", format="pdf")
 plt.close(fig)
 
@@ -59,6 +59,6 @@ plt.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
 plt.title("Stepping time histogram " + data_name)
 plt.xlabel("Step time (s)")
 plt.ylabel("Frequency")
-add_config_info(config_txt)
+add_config_info(config_txt + "\n\n<step times>: %.2e" % np.mean(step_times))
 plt.savefig("plots/stepping_time_histogram_" + data_name + ".pdf", format="pdf")
 plt.close(fig)

### 2016-12-31 thesis_stuff/thesis_stuff.tex
Add a paper on linker movement to thesis_stuff.tex.

@@
 
+\subsection{Linker position in Post-powerstroke dynein, two Post-PS states?}
+Insights into dynein motor domain function from a 3.3A crystal structure, Hugo Schmidt, Andrew P. Carter\\
+
+A crystal structure of just the motor domain in a low-ATP-affinity conformation.
+Suggests that differences between their structure and a Dictyostelium ADP-bound structure suggest there is a difference between AAA1 apo/ADP states, suggesting at least two post-powerstroke states.
+The paper postulates that linker interacting with AAA5 is what kicks out ADP.
+They say that linker-AAA5 complex creates a low-nucleotide-affinity state.\\
+
+They further suggest that nucleotide binding causes the linker to unbind AAA5 and rebind AAA2 on nucleotide binding.
+Thus AAA5-linker is post-powerstroke apo and AAA2-linker is ATP-bound (pre or post powerstroke?)\\
+
+ATPases 2, 3, 4 mutation leads to decreased velocity.\\
+
+\subsection{Linker pre-powerstroke conformation}
+ATP hydrolysis cycle-dependent tail motions in cytoplasmic dynein
+Kon T, Sutoh K
+
+This paper supposedly talks about how the linker changes conformation on ATP binding.\\
+
 Figure~\ref{fig:em_tomography_eq_angles} shows different measurements

### 2016-12-31 thesis_stuff/thesis_stuff.tex
Add yet another paper to thesis_stuff.tex, which says that maybe cm changes between one/bothbound.

@@
 \begin{center}
-  \begin{tabular}{| l | l | l | l | l | l | l |}
+  \begin{tabular}{| l | l | l | l | l | l | l | l |}
     \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine\\\hline
-    $L_s$ & 12nm & & & 21.0nm & 22.1nm &\\ \hline
-    $L_t$ &  7nm & & & & 11.15nm &\\ \hline
-    $R_b$ &  & & & 1.57nm & 1.45nm &\\ \hline
-    $R_m$ &  7nm & & & 7.36nm & 6.3nm &\\ \hline
-    $R_t$ &  & & & & 2.16nm & \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & \\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & &\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & &\\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ & & & & &\\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & & &\\ \hline
-    $k_b$ & $5000 s^{-1,b}$ & & & & &\\ \hline
-    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol\\ \hline
-    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol\\ \hline
-    $c_t$ & & & & & & \\ \hline
-    $c_m$ & & & & & & \\ \hline
-    $c_b$ & & & & & & 140 kJ/mol\\ \hline
+    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess\\\hline
+    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
+    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
+    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
+    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
+    $R_t$ &  & & & & 2.16nm & & & \\ \hline
+    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
+    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
+    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
+    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
+    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
+    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
+    $c_t$ & & & & & & & & \\ \hline
+    $c_m$ & & & & & & & & \\ \hline
+    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
   \end{tabular}
@@
     22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
+    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
+    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
     22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
     22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 7.8e-3 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & ?? & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 9.0e-3 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & 7.2e-2 & no error yet\\\hline
     22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
-    22.1 & 11.1 & 2500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
-    22.1 & 11.1 & 1500 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
-    22.1 & 11.1 &  500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
-    22.1 & 11.1 &  100 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
   \end{tabular}
@@
 
-\subsection{Linker position in Post-powerstroke dynein, two Post-PS states?}
-Insights into dynein motor domain function from a 3.3A crystal structure, Hugo Schmidt, Andrew P. Carter\\
-
-A crystal structure of just the motor domain in a low-ATP-affinity conformation.
-Suggests that differences between their structure and a Dictyostelium ADP-bound structure suggest there is a difference between AAA1 apo/ADP states, suggesting at least two post-powerstroke states.
-The paper postulates that linker interacting with AAA5 is what kicks out ADP.
-They say that linker-AAA5 complex creates a low-nucleotide-affinity state.\\
-
-They further suggest that nucleotide binding causes the linker to unbind AAA5 and rebind AAA2 on nucleotide binding.
-Thus AAA5-linker is post-powerstroke apo and AAA2-linker is ATP-bound (pre or post powerstroke?)\\
-
-ATPases 2, 3, 4 mutation leads to decreased velocity.\\
-
-\subsection{Linker pre-powerstroke conformation}
-ATP hydrolysis cycle-dependent tail motions in cytoplasmic dynein
-Kon T, Sutoh K
-
-This paper supposedly talks about how the linker changes conformation on ATP binding.\\
-
 Figure~\ref{fig:em_tomography_eq_angles} shows different measurements
@@
 \end{figure}
+
+\subsection{Linker position in Post-powerstroke dynein, two Post-PS states?}
+Insights into dynein motor domain function from a 3.3A crystal structure, Hugo Schmidt, Andrew P. Carter\\
+
+A crystal structure of just the motor domain in a low-ATP-affinity conformation.
+Suggests that differences between their structure and a Dictyostelium ADP-bound structure suggest there is a difference between AAA1 apo/ADP states, suggesting at least two post-powerstroke states.
+The paper postulates that linker interacting with AAA5 is what kicks out ADP.
+They say that linker-AAA5 complex creates a low-nucleotide-affinity state.\\
+
+They further suggest that nucleotide binding causes the linker to unbind AAA5 and rebind AAA2 on nucleotide binding.
+Thus AAA5-linker is post-powerstroke apo and AAA2-linker is ATP-bound (pre or post powerstroke?)\\
+
+ATPases 2, 3, 4 mutation leads to decreased velocity.\\
+
+\subsection{Linker pre-powerstroke conformation}
+ATP hydrolysis cycle-dependent tail motions in cytoplasmic dynein
+Kon T, Sutoh K
+
+This paper supposedly talks about how the linker changes conformation on ATP binding.\\
+
+A FRET study on how ATP changes the distance of domains.
+They label the C-terminal tail and different regions on the motor, then calculate the FRET efficiency.
+FRETY efficiency is higher when ATP is present, indicating two different states based on ATP presence.
+They try to trap dynein in different states (apo, ATP, ADP-Pi, ADP) using different trapping nucleotide analogs.
+ADP-Vi dynein stayed in state II, while nonhydrolyzable ATP, apo, and ADP additions caused the motor to stay in state I.\\
+
+The interpretation is that the dynein's tail moves from a state where it is near the C-terminus (AAA5) to one where it is near AAA2.
+5->2 is prestroke on hydrolysis, 2->5 is poststroke on Pi rejection.
+ATP binding is what causes the conformation change, since they have trapped ATP-ish bound dyneins in both state I and II.
+The powerstroke happens during the ADP state, since they have an ADP-dynein in state II and another in state I.\\
+
+They also report an ATPase $k_{cat} = 90.2 \pm 4.5$, meaning roughly 100 ATP are cycled per second.\\
+
+\subsection{Possibly more equilibrium motor angles}
+Dynein structure and power stroke
+Nature 2003, Burgess and Oiwa
+
+EM microscopy of apo/ADP-Vi flagellar dynein shows that the stem and stalk don't change length between two states, only the angle/position changes.
+The paper claims ``the origin of the movement is a displacement of the stem relative to the head and stalk.''.
+
+Paper claims motor angle is \textbf{160 degrees in pre-stroke and 136 degrees in powerstroke}.\\
+
+There is a difference in standard deviation of angles in pre/post-stroke.
+Pre-stroke has a stdev of 20 degrees, Post-stroke has a stdev of 11.
+The authors indicate this is due to stiffening of the stalk/foot domain.
+This seems like it would indicate changes in the motor spring constants between the pre/post-powerstroke states.
 

### 2017-01-02 thesis_stuff/thesis_stuff.tex

@@
 \begin{center}
-  \begin{tabular}{| l | l | l | l | l | l | l | l |}
+  \begin{tabular}{| l | l | l | l | l | l | l |}
     \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess\\\hline
-    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
-    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
-    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
-    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
-    $R_t$ &  & & & & 2.16nm & & & \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
-    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
-    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
-    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
-    $c_t$ & & & & & & & & \\ \hline
-    $c_m$ & & & & & & & & \\ \hline
-    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
+    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine\\\hline
+    $L_s$ & 12nm & & & 21.0nm & 22.1nm &\\ \hline
+    $L_t$ &  7nm & & & & 11.15nm &\\ \hline
+    $R_b$ &  & & & 1.57nm & 1.45nm &\\ \hline
+    $R_m$ &  7nm & & & 7.36nm & 6.3nm &\\ \hline
+    $R_t$ &  & & & & 2.16nm & \\ \hline
+    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & \\ \hline
+    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & &\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & &\\ \hline
+    $\theta_{t}$ & 0$^{\circ}$ & & & & &\\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ & & & & &\\ \hline
+    $k_b$ & $5000 s^{-1,b}$ & & & & &\\ \hline
+    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol\\ \hline
+    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol\\ \hline
+    $c_t$ & & & & & & \\ \hline
+    $c_m$ & & & & & & \\ \hline
+    $c_b$ & & & & & & 140 kJ/mol\\ \hline
   \end{tabular}
@@
 
-\subsection{Possibly more equilibrium motor angles}
-Dynein structure and power stroke
-Nature 2003, Burgess and Oiwa
-
-EM microscopy of apo/ADP-Vi flagellar dynein shows that the stem and stalk don't change length between two states, only the angle/position changes.
-The paper claims ``the origin of the movement is a displacement of the stem relative to the head and stalk.''.
-
-Paper claims motor angle is \textbf{160 degrees in pre-stroke and 136 degrees in powerstroke}.\\
-
-There is a difference in standard deviation of angles in pre/post-stroke.
-Pre-stroke has a stdev of 20 degrees, Post-stroke has a stdev of 11.
-The authors indicate this is due to stiffening of the stalk/foot domain.
-This seems like it would indicate changes in the motor spring constants between the pre/post-powerstroke states.
-
 \subsection{2012 Kon Crystal Structure (3VKH)}

### 2017-01-08 thesis_stuff/thesis_stuff.tex
minor commit on finding spring constants from an experimental motor angle distribution.

--- 2016-12-31 thesis_stuff/thesis_stuff.tex
@@
 \begin{center}
-  \begin{tabular}{| l | l | l | l | l | l | l | l |}
+  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
     \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess\\\hline
+    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
     $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
@@
 
+\textbf{Could we use the angle distribution histograms in \ref{fig:EM-angles-burgess} fit to a boltzmann factor with a spring energy to get cm?}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=.45\textwidth]{../figures/axonemal-motor-angles.jpg}
+  \caption{Angle histograms from EM microscopy on axonemal (not cytoplasmic) dynein.}
+  \label{fig:EM-angles-burgess}
+\end{figure}
+
 There is a difference in standard deviation of angles in pre/post-stroke.

### 2017-01-12 thesis_stuff/thesis_stuff.tex
Add new simulation runs showing too quick steps.

@@
   \end{tabular}
+  \textbf{Old probably wrong angle scheme run data}
+\end{center}
+
+\begin{center}
+  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | l | p{5cm} |}
+    \hline
+    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & run & errors\\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & & & NaN! tail crashes into MT \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & & & NaN! motor crashes into MT \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & & & NaN! tail crashes into MT \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & $3.7e-4$ & & NaN! tail crashes into MT \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & $9.1e-4$ & & NaN! motor crashes into MT \\\hline
+    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
+    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
+    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
+    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & $4.6e-14$ & & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $2.7e-13$ & $6.8e-4$ & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
+    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
+    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
+    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
+    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & $5.4e-18$ & & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $9.5e-32$ & & & \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $2.7e-35$ & & & \\\hline
+  \end{tabular}
+  \textbf{New possibly right angle scheme run data}
 \end{center}
@@
 
-A more reliable step time determiner is $\Big<\mbox{step time}\Big>$. This number can be determined from the step time histograms.\\
+A more reliable step time determiner is $\Big<\mbox{step time}\Big>$, which should be around 0.1. This number can be determined from the step time histograms.\\
 

### 2017-01-14 thesis_stuff/thesis_stuff.tex
Add in new parameters from hunt

--- 2017-01-02 thesis_stuff/thesis_stuff.tex
@@
     Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns \\\hline
+    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns\\\hline
     22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
@@
     22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
-    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
-    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
-    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & 6.8e-4 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & 1.6e-3 & weirdly stepped so L is around zero (0.04), maybe write a nudge to prevent this?\\\hline
+    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & 1.9e-3 & weirdly stepped so L is around zero (0.04), maybe write a nudge to prevent this?\\\hline
+    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & 7.9e-3 & no error yet\\\hline
     22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
@@
     22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 9.0e-3 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
-    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
-    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
-    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
+    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & 1.3e-2 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & 1.3e-2 & no error yet\\\hline
+    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & 4.6e-2 & no error yet\\\hline
+    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & no error yet\\\hline
     22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & 7.2e-2 & no error yet\\\hline
@@
 \end{center}
+
+ARE THESE ANGLES RIGHT??????????????\\
 

### 2017-01-19 thesis_stuff/thesis_stuff.tex

--- 2017-01-14 thesis_stuff/thesis_stuff.tex
@@
 \end{align*}
-
-\subsection{ATP Concentration from Weihong's Paper}
-Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.\\
-
-\subsection{Parameter hunt}
-Lots of different manual simulations and their outcomes.
-
-\begin{center}
-  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
-    \hline
-    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & 6.8e-4 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & 1.6e-3 & weirdly stepped so L is around zero (0.04), maybe write a nudge to prevent this?\\\hline
-    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & 1.9e-3 & weirdly stepped so L is around zero (0.04), maybe write a nudge to prevent this?\\\hline
-    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & 7.9e-3 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 9.0e-3 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & 1.3e-2 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & 1.3e-2 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & 4.6e-2 & no error yet\\\hline
-    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & 7.2e-2 & no error yet\\\hline
-    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
-  \end{tabular}
-\end{center}
-
-ARE THESE ANGLES RIGHT??????????????\\
-
-If the mean stepping rate from Weihong's paper is about 1 step / .1 seconds, then at a dt of $1e-11$s would lead to a desired unbinding
-probability of $1e-11s/.1s = 1e-10$. The stepping probability was determined by printing out a random subset of unbinding probabilities
-for the bothbound case, then averaging.\\
-
-A more reliable step time determiner is $\Big<\mbox{step time}\Big>$. This number can be determined from the step time histograms.\\
 
@@
 
-\subsection{Linker position in Post-powerstroke dynein, two Post-PS states?}
-Insights into dynein motor domain function from a 3.3A crystal structure, Hugo Schmidt, Andrew P. Carter\\
-
-A crystal structure of just the motor domain in a low-ATP-affinity conformation.
-Suggests that differences between their structure and a Dictyostelium ADP-bound structure suggest there is a difference between AAA1 apo/ADP states, suggesting at least two post-powerstroke states.
-The paper postulates that linker interacting with AAA5 is what kicks out ADP.
-They say that linker-AAA5 complex creates a low-nucleotide-affinity state.\\
-
-They further suggest that nucleotide binding causes the linker to unbind AAA5 and rebind AAA2 on nucleotide binding.
-Thus AAA5-linker is post-powerstroke apo and AAA2-linker is ATP-bound (pre or post powerstroke?)\\
-
-ATPases 2, 3, 4 mutation leads to decreased velocity.\\
-
-\subsection{Linker pre-powerstroke conformation}
-ATP hydrolysis cycle-dependent tail motions in cytoplasmic dynein
-Kon T, Sutoh K
-
-This paper supposedly talks about how the linker changes conformation on ATP binding.\\
-
-A FRET study on how ATP changes the distance of domains.
-They label the C-terminal tail and different regions on the motor, then calculate the FRET efficiency.
-FRETY efficiency is higher when ATP is present, indicating two different states based on ATP presence.
-They try to trap dynein in different states (apo, ATP, ADP-Pi, ADP) using different trapping nucleotide analogs.
-ADP-Vi dynein stayed in state II, while nonhydrolyzable ATP, apo, and ADP additions caused the motor to stay in state I.\\
-
-The interpretation is that the dynein's tail moves from a state where it is near the C-terminus (AAA5) to one where it is near AAA2.
-5->2 is prestroke on hydrolysis, 2->5 is poststroke on Pi rejection.
-ATP binding is what causes the conformation change, since they have trapped ATP-ish bound dyneins in both state I and II.
-The powerstroke happens during the ADP state, since they have an ADP-dynein in state II and another in state I.\\
-
-They also report an ATPase $k_{cat} = 90.2 \pm 4.5$, meaning roughly 100 ATP are cycled per second.\\
-
 \subsection{2012 Kon Crystal Structure (3VKH)}

### 2017-01-21 thesis/latex/thesis.tex

\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins
\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

\usepackage{listings}
\lstset{escapechar=\&}

% Fonts and tweaks for XeLaTeX
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
%\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Colors for links, text and headings
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
\definecolor{shade}{HTML}{F5DD9D} % Peach color for the contact information box
\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
\definecolor{headings}{HTML}{701112} % Dark red color for headings
% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080

\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors

\usepackage{titlesec}
\setcounter{secnumdepth}{4}

\setlength{\emergencystretch}{3cm} % somehow helps prevent hboxes from overflowing

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsmath}
\pagestyle{fancy}
\fancyhf{}

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

\bibliographystyle{plain}

\begin{document}

\tableofcontents
\newpage

\section{Chapter: Introduction}
\subsection{What is dynein?}
\subsubsection{Basics}

Dynein is a cellular structure which converts chemical energy to mechanical energy. It does so by reacting with adenosine triphosphate (ATP) to take steps along long cellular tracks known as microtubules (MTs). Dynein's mechanical energy is used to transport molecules around the cell, pull chromosomes during division, move cellular propellers known as cilia and various other functions \cite{cianfroccoreview}.\\

Dynein is a protein with many smaller domains. A depiction of the protein and its labeled subdomains is shown in Figure (\ref{dynein-artist-rendition}). Each motor is a homodimer made up of two identical monomer proteins. Each monomer has a binding domain which binds to the microtubule, a motor domain which binds ATP, a tail domain which connects to the other monomer, a stalk which connects the binding and motor domains, and a linker which connects the motor and tail domains. The tail domain is also responsible for binding to cargo.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

Dynein is believed to move by using the energy of ATP to cycle through a ring of states, each with different spatial relations to the microtubule. By cycling forward through this ring, the molecule can end up in the same state it began, but moved forward a small amount. This ring of states is known as the mechanochemical cycle \cite{cianfroccoreview}. The goal of this project is to create a mathematical model of the mechanochemical cycle and verify that it can reproduce experimental dynein stepping data. There are several types of dynein which all behave differently. This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\

\subsubsection{Glossary}
\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate. This reaction is used to power many energy-requiring mechanisms within the cell. This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.\\

\subsubsection{Why do cells need motor transport?}
Cells are organized, heretogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving components to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2) \textbf{((is this the best way to cite this?))}, a $10^3$ factor difference in size.\\

Diffusion, or random motion of molecules due to collisions with solvent (i.e. Brownian motion), is one possible process cells could use to transport biomolecules. Diffusion has two problems: it is slow and nondirected. The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \textbf{cite here}:

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}

where D is the diffusion constant describing the diffusability of the biomolecule. For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ %% \cite{diffusionconstants}
, it would take about a month to travel across a millimeter-sized cell. In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
  \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

\textit{Maybe use the more reasonable 2$\mu m / s$ number for dynein velocity, in-vitro speed may not be applicable since [ATP]-limited}

Another advantage of motor transport is that microtubules can be highly specific in their location in the cell. During cell division chromosomes line up at the center of each cell in a plane. Such a geometrically precise shape requires some sort of directed motion which a random process could never provide.\\

\textit{maybe decorate the above plot with pictures of cells of each size, or how long certain cellular events take? That could be cool and make it actually an interesting plot}
\textit{this argument would be much better if you could find examples of things which need to be done quickly in the cell, like responding to foreign particles or signalling
  molecules or cell division or neural events}

\subsubsection{What role does it play in the cell?}
Some of dynein's primary roles in the cell are to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins. Dynein also plays a role in positioning and breaking down the nucleus, cell death, spindle formation and the placement of other important cellular structures \cite{valetoolbox}.

Microtubules are long polymers of alternating $\alpha-$ and $\beta-$ tubulin subunits. MTs are polar, meaning they have a distinct directionality based on the orientation of thetubulin proteins which comprise them. One pole, the minus end, is where they initiate formation, typically at a MTOC (microtubule organizing center) around the center of the cell. The other pole, the plus end, is where they grow and shrink from. Kinesin and myosin, two other families of motor protein, typically walk towards the plus end of the MT. Dynein is unique in that it walks towards the minus end, making it a minus end-directed motor. This lends it to a particularly important function inside neurons known as retrograde transport.\\

Neurons have cell bodies at their centers and axons which grow outwards. Axons are long, narrow structures extending up to a meter in length in humans. Cell bodies contain nuclei and important organelles for synthesizing proteins, but growth of axon tips is vital for neuron function. This means bidirectional motor transport between axon tips and cell bodies is very important in neurons, since diffusion would not be quick enough. Retrograde transport is transport from the axon tip to the cell body. Cargo includes vesicles full of proteins ready to be broken down in the cell body and microtubule fragments to be returned from the axon tip \cite{neuroanatomy}. Because microtubule minus ends are found in the cell body, dynein's minus end-directed nature makes it the only protein capable of retrograde transport. An interesting question is, if proteins like dynein are synthesized in the cell body but needed at the axon tip to perform retrograde transport, how do dynein get to the tip? The answer is shown in \ref{retrograde-transport}: kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/retrograde_transport.jpg}
  \caption{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

\subsubsection{Dynein structure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition-2}
\end{figure}

\textit{eventually find a different figure}

As shown in \ref{dynein-artist-rendition-2}, a dynein motor is a fusion of to identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.

\textbf{Binding domain}
Microtubule binding domains (MTBDs) allow dynein to bind to the microtubule.

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mtbd-complex.png}
  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
  \label{dynein-artist-rendition-2}
\end{figure}

\subsubsection{How does it behave?}
Talk about its stepping behavior using Weihong's figures (as well as the new paper David found?)\\

Also possibly talk about the other things Dynein has been found to do, such as hydrolyse ATP and
move its subdomains around. This may be better in a different section than the introduction though,
since its a lot of biochemistry for the second section in an intro? maybe not, it has to go somewhere.

\subsubsection{Why is dynein special and interesting?}
Compare the processive motion of dynein to kinesin in \textbf{a.)} directionality, \textbf{b.)}
stepping pattern and \textbf{c.)} size (like how it can step over roadblocks kinesin cannot).\\

Talk about why a random stepping motor is interesting compared to a orderly-stepping motor: what
is different about dynein's structure that makes it step differently? Compare the crystal structures
and ask lots of questions. Build interest in the motors here.\\

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
%%   \caption{Crystal structures of cytoplasmic dynein 1 and kinesin KIF5B (PDB IDs 4RH7 and 1BG2).}
%%   \label{kin_n_dyn}
%% \end{figure}

\textit{make this figure good -- find a full length kinesin crystal structure, not 1BG2. Use kindyn.pse as a template.}

\subsection{How does dynein walk?}

Cianfrocco \textit{et. al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig. \ref{mech-cycle}. This model will hereon be referred to as the Cianfrocco model. The model claims the primary events in the dynein step are as follows. First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation. ATP hydrolysis to ADP-Pi causes further conformation changes. These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound. The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT. Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle. The exact order of these events is not precisely known. More detail on each step of the cycle is given below.\\

Maybe show the Cianfrocco model in a section \textit{after} talking about all the things which happen for sure in dynein, since it's more theoretical? Talk about the Cianfrocco model, but other interpretations?

\textbf{Things which are known about dynein which support the Cianfrocco model}
\begin{itemize}
\item AAA1 only ATPase necessary for motility, which is why we don't include the other ATPases in our model \cite{cianfroccoreview}
\item AAA5 mediates stalk register changes Schmidt H, Zalyte R, Urnavicius L, Carter AP. 2014. Structure of human cytoplasmic dynein-2 primed for
  its power stroke. Nature 518:435–38
\item Linker moves as response to AAA1 nucleotide binding Burgess SA, Walker ML, Sakakibara H, Knight PJ, Oiwa K. 2003. Dynein structure and power stroke. Nature
  421:715–8
\item Crystal structures with Vanadium-Adp show dynein in the pre-powerstroke state, hinting that ADP-Pi-bound dynein takes on a different conformation than ADP-Pi free dynein
\end{itemize}

Make a figure of pre/post-powerstroke dynein with the linker hilighted? Can you get what residues correspond to the linker somewhere?

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

\subsubsection{ATP binding / unbinding effects}
\subsubsection{Microtubule un/rebinding}
\subsubsection{Conformation change of motor (``priming stroke'')}
A FRET (fluorescent resonance energy transfer) study, which probes the closeness of different labeled domains on a protein, showed that dynein is found in two different major conformations, depending on the nucleotide bound to its AAA1 ATPase site \cite{FRETstatepaper}. When no nucleotide, ATP or ADP is bound, the authors label the protein ``state I.'' When ADP-Pi bound, the motor is said to be in ``state II,'' as shown in Fig \ref{nucleotide-state}. In addition, motors in the presence of the unhydrolyzable ATP analog were found in state II, indicating the transition from state I to II occurs during ATP binding. Similar reasoning shows that the state II to I transition occurs when the protein is ADP bound. This allows the authors to create the state diagram shown in Fig \ref{nucleotide-state-diagram}.\\

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/two-state-em-diagram}
%%   \caption{}
%%   \label{nuecleotide-state}
%% \end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/nucleotide-state-cycle}
%%   \caption{}
%%   \label{nucleotide-state-diagram}
%% \end{figure}

This single FRET study illustrates how the conformational aspect of the mechanochemical cycle works. Dynein begins in state I and binds ATP into its AAA1 ATPase, changing into state II by changing its stalk-tail angle to move the tail outward. ATP is then hydrolized into ADP-Pi. Pi is then ejected from the AAA1 site, leaving ADP behind. This causes the reverse state transition, moving the tail inward. When combined with microtubule affinity changes, this primitive model of the dynein cycle could explain how dynein walks.\\

\textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}. The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I. Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\

\textbf{more on how ATP actually causes the conformation change, if that's available. The change from an open/closed ATPase is what changes the nucleotide affinity, go into depth on that, but actual info on how ATP binding causes conformation change would be good. Something about going from a planar to nonplanar conformation?}\\

also how crystal structures are in different positions

\subsubsection{Experimental results on dynein’s step}
Weihong's figures go here.\\

\subsubsection{c What is still needed to support theory}
Where our simulation fits in. Why we need this kind of information.
There are many different things which might be important for dynein's walk which we don't take into account: springiness of tail/stalk, changes in spring constants, repulsion between the heads, multiple pre/post powerstroke conformations. We are trying to see if these things are actually important.

\subsubsection{Other theories?}
Imamula model: how it is different from Cianfrocco model, and why we chose the Cianfrocco model.\\
	\subsection{Past Simulations}
		\subsubsection{Sarlah Winch Model}
		\subsubsection{-x Other models}
	\subsection{Brownian motion}
                \subsubsection{Introduction/derivation}
                \subsubsection{Justification}

\subsection{Simulation}
Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
aren't high resolution enough to make good videos of the walk, and even if they were, in some sense
knowing that dynein behaves identically to a simple mathematical model is more informative than
a video, since there is lots of information in a video and really precise info in a simulation.\\

\textbf{Not sure where this goes:} The 'goal' of our experiment, at a very high level, is to
understand how dynein works. We can know this if we can come up with the minimum set of characteristics a physical system needs to act like dynein. This information is the same thing as knowing
``how dynein walks.'' We don't need to know all the complex dynamics of every single amino acid in
dynein, we only need to know our rough model.\\

\subsection{Our model}
Talk about what the important parts of the mechanochemical cycle from the introduction are, and how
we take those and model them.\\
\subsubsection{Rigid point model}
Talk about two things: reducing bulky circular domains to points (is this the same as unified atom
model?) with a certain drag constant based on radius, and acting like the domains are rigid in
distance from each other. Talk about why this is valid (is it? it's an assumption, David may know
more).
\subsubsection{Harmonic energies}
How we're modeling the complicated folding and adjusting of a massive protein as a harmonic
oscillator. Why this is valid. Also other approaches...what else could we have modelled it as?
\subsubsection{Two-state model}
The mechanochemical cycle has eight states. We choose two as representative because \textbf{a.)}
many of the states are identically conformationally or \textbf{b.)} the transitions happen so fast
the intermediate states don't matter. Talk about rate constants here.
\subsubsection{Limitations}
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information,
other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into
account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be
springy...

Mention the Burgess paper, which says spring constants might change between apo/ADP states.

\paragraph{Euler’s method}
Show how Euler's method is arrived at, how its error scales, why we use it.

\paragraph{Vs other methods (Runge Kutta, etc)}
Talk about why our differential equation is most conducive to Euler's method. Euler's is more
efficient -- is there a way to show how our differential equation is smooth, not jagged?

\paragraph{Gibbs energy of transition}
Do some stuff with Gibb's here? Why our energies are Gibb's and not internal energy?\\

\section{Chapter: Methods}

\subsection{Dynein Models}
In order to simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state. The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\

\subsubsection{Prestroke onebound model}
Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound. A spatial representation of onebound dynein is shown in Figure \ref{ob_fig}.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/ob_fig.pdf}
  \caption{Spatial representation of onebound model.}
  \label{ob_fig}
\end{figure}

TODO: make figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\

Each domain is represented by a point, and is connected to other domains via fixed-length rods. Angles represent the degrees of freedom of the model. Since the protein is a dimer, there are two copies of the MTB, motor and tail domains. The tails are fused together and so represented as a single point. The motor and MTB domains are given a ``bound'' and ``unbound'' designation to differentiate them. The ``bound'' domains are the MTBD attached to the MT and its corresponding motor domain. The unbound domains are the unbound MTBD and its corresponding motor domain.\\

\paragraph{Angular and Cartesian coordinates}

The four angles $\Theta_{bb}, \Theta_{bm}, \Theta_{um}$ and $\Theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on. The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$. Each angle is defined relative to the horizontal axis.\\

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      class Dynein_onebound{
        double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
        double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
        double &$X_{bb}$&
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Pseudocode of the onebound Dynein model.}
  \label{ob_struct}
\end{figure}

Pseudocode for the numerical onebound model representation is shown in Figure \ref{ob_struct}. The position of the bound binding domain $X_{bb}$ and the four domain angles are all the values needed to determine the position of the protein at any time.\\

\paragraph{$\dot{\Theta}_{ub}, \dot{\Theta}_{um}, \dot{\Theta}_{bm}, \dot{\Theta}_{bb}$ calculation}

The following equations allow recursive calculation of the positions of each domain in cartesian coordinates:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}
  Y_{bb} &= 0 \\
  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
\end{align}
\end{minipage}
\vspace{.5cm}

$L_s$ and $L_t$ correspond to lengths of each interdomain rod, and the $t$ subscripts refer to tail domain coordinates.\\

\paragraph{Angular and Cartesian velocities}
The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities. To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\vspace{.5cm}

Another way to express these cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:

\begin{align}  
  \dot{X}_{bm} &= \frac{1}{\gamma_m} \Big(F_{xml} + - \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \label{brownian-bmx}\\
  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
\end{align}

where $\gamma_n$ is a drag coefficient for the binding, motor or tail domain with units of mass per second. $F_{xn}$ is the x component of external force on each domain $n$ due to various factors. $\lambda_{12}\left(X_1 - X_2\right)$ is the x component of internal force on domain $2$ due to domain $1$, where $\lambda$ is a tension coefficient with units of mass per second per second. $R_{xn}$ is the Brownian coefficient representing motion due to solvent collision, with units of velocity.\\

These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations. For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated. This equating, combined with expanding the recursive velocity definitions leads to:

\begin{align}
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} &= \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
\end{align}

\begin{align}
  L_s\cos(\theta_{bb})\dot{\theta}_{bm} &= \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
\end{align}

These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$. This system is more compactly represented as:
{\small
  \[
  \hspace{-1.0cm}
  \resizebox{0.85\linewidth}{!}{%
  $\begin{pmatrix}
    L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um})\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um})\\
    -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um})\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})\\
  \end{pmatrix}$%
  }
  \begin{pmatrix}
    \dot{\theta}_{bb}\\
    \dot{\theta}_{bm}\\
    \dot{\theta}_{um}\\
    \dot{\theta}_{ub}\\
    \lambda_{bs}\\
    \lambda_{bt}\\
    \lambda_{ut}\\
    \lambda_{us}\\
  \end{pmatrix}
  =
  \begin{pmatrix}
    -F_{bmx} + \gamma_m R_{bmx}\\
    -F_{tx} + \gamma_t R_{tx}\\
    -F_{umx} + \gamma_m R_{umx}\\
    -F_{ubx} + \gamma_b R_{ubx}\\
    -F_{bmy} + \gamma_m R_{bmy}\\
    -F_{ty} + \gamma_t R_{ty}\\
    -F_{umy} + \gamma_m R_{umy}\\
    -F_{uby} + \gamma_b R_{uby}\\
  \end{pmatrix}
  \]
}

This matrix is then solved using the Mathematica computer algebra system, resulting in a set of $\dot{\Theta}_n$ equations shown in Appendix (\ref{ob-motion-equations]}).

\subsubsection{Poststroke bothbound model}
The main difference between the prestroke and poststroke mathematical models is that the latter has a further constraint: both its MTB domains are attached to the MT. This has the effect of diminishing the degrees of freedom of the system from four to two, assuming the motor remains above the MT. A spatial representation of the bothbound model is shown in Figure (\ref{bb_fig}).\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/code-bothbound.pdf}
  \caption{Definition of equilibrium angles.}
  \label{bb_fig}
\end{figure}

The bothbound model is very similar in assumptions to the onebound: domains are represented as points connected by rigid rods, and the tails are still fused into a single point. The main differences are the naming scheme and spatial constraints. Dimers can no longer be differentiated by being un/bound, so are now differentiated by their z-position: being near or far from the ``camera.'' This is similar to labeling them as the right or left dimer. Thus there are the near binding (nb), near motor (nm), tail (t), far motor (fm) and far binding (fb) domains. Both the near and far binding domains have their x-coordinate fixed at zero. The system is described completely by two angles: $\Theta_{nm}$ and $\Theta_{fm}$. Angles $\Theta_t, \Theta_{nb}$ and $\Theta_{fb}$ are dependent on these two motor angles.\\

The second MTBD constraint adds another required piece of information the model must track: the x position of the second MTBD. This position is described by $L$, the distance between the near and far binding domains. The pseudocode used to describe the bothbound model are shown in Figure (\ref{bb_struct}).\\

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      class Dynein_bothbound{
        double &$\Theta_{nm}, \Theta_{fm}$&
        double &$\dot{\Theta}_{nm}, \dot{\Theta}_{fm}$&
        double &$X_{nb, L}$&
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Pseudocode of the bothbound Dynein model.}
  \label{ob_struct}
\end{figure}

\paragraph{$\dot{\Theta}_{nm}, \dot{\Theta}_{fm}$ calculation}

The first step in calculating angular velocities is to define new variables $L_n$ and $L_f$ using the Law of Cosines:

\begin{align}
  L_n &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{nm}}} \\
  L_f &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{fm}}}
\end{align}

These new artificial stalks are not physically relevant, but allow the definition of new angles $\Theta_n, \Theta_{ns}, \Theta_{f}$ and $\Theta_{fs}$, which are useful for calculating the position of the motor domain. The treatment of the near and far versions of these angles is very similar, so only the near angles will be dealt with here. The angles themselves are never dealt with, only their $\sin$s and $\cos$s:

\begin{align}
  \cos\theta_n &= \frac{L^2 + L_n^2 - L_f^2}{2L L_n} \\
  \sin\theta_{n} &= \sqrt{1 - \cos^2\theta_{n}} \\
  \cos\theta_{ns} &= \frac{L_s^2 + L_n^2 - L_t^2}{2L_s L_n} \\
  \sin\theta_{ns} &=
  \begin{cases}
    +\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} < \pi \\
    -\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} > \pi
  \end{cases}
\end{align}

These values are arrived at through the Law of Cosines and a trigonometric identity. The sign of $\sin\left(\Theta_n\right)$ is restricted to positive values due to the angle's $[0,\pi]$ domain. $\Theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted. The partial derivatives of these values are useful:

\begin{align}
  \frac{\partial \cos\theta_n}{\partial L_n} &= \frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\\
  \frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{LL_n}\\
  \frac{\partial \sin\theta_n}{\partial L_n} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
  \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  \left(\frac{-L_f}{LLn}\right)\\
  \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
  - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
  \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
  \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
  \begin{cases}
    \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
  \end{cases}\\
  \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
\end{align}

The position of the motor and tail domains is calculated as follws, using the angle addition trigonometric identity:

\begin{align}
  X_{nm} &= L_s\left(
  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
  \right)
  \\
  Y_{nm} &= L_s\left(
  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
  \right)
  \\
  X_{t} &= L_n\cos\theta_n\\
  Y_{t} &= L_n\sin\theta_n\\
\end{align}

The partial derivatives of these values are:

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}\Big)\\
  \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)\\
  \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
  \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
  \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
  \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
  \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
\end{align}

These partial derivatives are then used in a system of equations very similar to that in Equations (\ref{ob_system_first}-\ref{ob_system_last}), combining Brownian and coordinate system definitions of domain velocities:

\begin{align}
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} - \lambda_{ns}(X_{bm} - X_{bb})
  + \lambda_{nt}(X_{t } - X_{bm}) \Big) + R_{xml}
  &=& \frac{\partial X_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{nm}}{\partial L_f}\dot{L}_f\\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } - \lambda_{nt}(X_{t } - X_{bm})
  + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
  &=& \frac{\partial X_{t}}{\partial L_n}\dot{L}_n + \frac{\partial X_{t}}{\partial L_f}\dot{L}_f\\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} - \lambda_{ft}(X_{fm} - X_{t })
  + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
  &=& \frac{\partial X_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{fm}}{\partial L_f}\dot{L}_f
\end{align}

\begin{align}
  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} - \lambda_{ns}(Y_{bm} - Y_{bb})
  + \lambda_{nt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
  &= \frac{\partial Y_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{nm}}{\partial L_f}\dot{L}_f\\
  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } - \lambda_{nt}(Y_{t } - Y_{bm})
  + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
  &= \frac{\partial Y_{t}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{t}}{\partial L_f}\dot{L}_f\\
  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} - \lambda_{ft}(Y_{fm} - Y_{t })
  + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
  &= \frac{\partial Y_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{fm}}{\partial L_f}\dot{L}_f
\end{align}

The matrix version of this system looks like:

\[
\begin{pmatrix}
  -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
  & -\frac{X_{nm}-X_{nb}}{\gamma} & \frac{X_{t}-X_{nm}}{\gamma} & 0 & 0\\
  -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
  & 0 & -\frac{X_{t}-X_{nm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
  -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
  & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
  -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
  & -\frac{Y_{nm}-Y_{nb}}{\gamma} & \frac{Y_{t}-Y_{nm}}{\gamma} & 0 & 0\\
  -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
  & 0 & -\frac{Y_{t}-Y_{nm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
  -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}
  & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
\end{pmatrix}
\begin{pmatrix}
  \dot{L}_n\\
  \dot{L}_f\\
  \lambda_{ns}\\
  \lambda_{nt}\\
  \lambda_{ft}\\
  \lambda_{fs}\\
\end{pmatrix}
=
\begin{pmatrix}
  -\frac{1}{\gamma}F_{nmx} - R_{nmx}\\
  -\frac{1}{\gamma}F_{tx}  - R_{tx}\\
  -\frac{1}{\gamma}F_{fmx} - R_{fmx}\\
  -\frac{1}{\gamma}F_{nmy} - R_{nmy}\\
  -\frac{1}{\gamma}F_{ty}  - R_{ty}\\
  -\frac{1}{\gamma}F_{fmy} - R_{fmy}\\
\end{pmatrix}
\]

This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{both-motion-equations}).

\subsection{Simulation}
To generate stepping data, the models were coded in \verb|C++| and time-evolved using Euler's method to generate reasonable dynamical behavior. When in a position deemed worthy of a state transition a conversion, the model was converted to the respective other model, representing part of a ``step'' through the mechanochemical cycle. Some unphysical but minor corrections at points in the simulation were needed to rescue the model from entering incalculable positions.\\

Code is available at \verb|https://github.com/elliotc12/dynein_walk.git|.

\textit{todo: come up with a better word than ``model'' to describe the state of the system at any time}
\subsubsection{Time evolution}
Euler's method for solving differential equations was used to calculate domain positions through time. Because each model is a set of multiple coupled differential equations, care was taken to update each domain position at the same time, and not in a cascade. A code snippet is shown in Figure (\ref{euler-code-snippet}) for the onebound updating scheme.

\begin{figure}[h!]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=python]
      def simulate(dyn_ob):
      t = 0
      while (t < runtime):
      double temp_bba = dyn_ob->get_bba() + dyn_ob->get_d_bba() * dt
      double temp_bma = dyn_ob->get_bma() + dyn_ob->get_d_bma() * dt
      double temp_uma = dyn_ob->get_uma() + dyn_ob->get_d_uma() * dt
      double temp_uba = dyn_ob->get_uba() + dyn_ob->get_d_uba() * dt

      dyn_ob->set_bba(temp_bba)
      dyn_ob->set_bma(temp_bma)
      dyn_ob->set_uma(temp_uma)
      dyn_ob->set_uba(temp_uba)

      t += dt
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
  \label{ob_struct}
\end{figure}

The \verb|dt| used to update was $10^{-11}$ seconds.

\subsubsection{Transitioning between states}

\paragraph{Transition rate}
\label{sec:transitioning-states}
Onebound and bothbound models transition between each other based on rate constants $k_b$, the binding constant, and $k_{ub}$, the unbinding constant, respectively. These values are calculated using the Arrhenius equation, and are given as:

\begin{equation}
  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
\end{equation}

where $\Delta G_{conf}$ is the change in spring energy in going from bothbound to onebound, $\Delta G_{bind}$ is the energy gained from binding to the microtubule, and A is a constant known as the preexponential factor with units of $s^{-1}$.\\

Transitions from one state to another are accomplished by calculating the probability of a transition at a given timestep, given by $P_{ob\rightarrow bb} = k_bdt$. Each timestep a value in $[0,1]$ is sampled from a random number generator and, if lower than $P$, the respective transition is made. A code snippet illustrating how unbinding occurs is shown in Figure (\ref{transition-rate-snippet}).

\begin{figure}[h!]
  \begin{tabular}{c}
    \begin{lstlisting}[language=python]
      def get_near_unbinding_rate(dyn_bb) {
        dyn_ob_test = make_onebound_from_bothbound(dyn_bb) // do a fake unbind to find energy
        dG_spring = dyn_ob_test.get_PE() - dyn_bb.get_PE()
        low_affinity_unbinding_preexponential_factor = low_affinity_unbinding_rate / exp(1.0)
        return low_affinity_unbinding_preexponential_factor*exp(-dG_spring/kb/T)
      }
      def transition_bothbound_to_onebound(dyn_bb) {
        random_number = rand(0,1)
        if (random_number < get_unbinding_rate(dyn_bb)) {
          return make_onebound_from_bothbound(dyn_bb)
        }
        else return 0
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of transition rate calculation using the Arrhenius equation.}
  \label{transition-rate-snippet}
\end{figure}

\paragraph{OB $\rightarrow$ BB Transition calculation}
When binding occurs, conversion between OB and BB models is done by creating a bothbound dynein which is as similar in terms of domain position as possible to the onebound dynein.\\

Due to the nature of the simulation, binding attempts must occur above, but very close to, the microtubule. This is because \textit{in vivo}, electrostatic interactions between MTBD and MT bring the two together when they are near. These electrostatic interactions are not present in the model, and so are simulated by allowing binding attempts to occur when $Y_{ub} \leq 0.2nm$ above the MT. When a binding attempt is successful, the unbound binding domain of the OB dynein is ``teleported'' such that $Y_{ub} = 0.0$. This is to enforce the constraint that both binding domains of the BB model are directly on the MT.\\

To create a BB model from OB, the following intermediate variables are first computed:\\

\begin{align}
  L_n^2 &= \left(X_t - X_{nb}\right)^2 + Y_t^2\\
  L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
  \cos(\Theta_{nm}) = \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
  \cos(\Theta_{fm}) = \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}\\
\end{align}

\textbf{todo: figure out why this new method is used instead of just computing the bad nma angles}

\paragraph{BB $\rightarrow$ OB Transition calculation}
Similar to the binding transition, unbinding involves creating a new onebound dynein from the old bothbound. To accomplish a transition to the farbound state, the following equations are used:\\

\begin{align}
  \Theta_{new,bba} &= \Theta_{old,nba}\\
  \Theta_{new,bma} &= \Theta_{old,nma} + \Theta_{old,nba} - \pi\\
  \Theta_{new,uma} &= \Theta_{old,fma} + \Theta_{old,fba} - \pi\\
  \Theta_{new,uba} &= \Theta_{old,fba}\\
\end{align}

To do a nearbound transition, the ``f'' and ``n'' subscripts in the above equations are swapped.\\

As shown in Section \ref{final-parameter-table}, the MT binding rate is much quicker than the unbinding rate. This means that, when just unbound, the rate of rebinding is very high. To prevent immediate rebinding, the model is given a ``rebinding immunity'' of a single timestep. During this immunity period, rebinding is not allowed.\\

\subsubsection{Corrections}
\label{corrections-section}
Certain configurations of the model, such as in the bothbound model when $\Theta_{nm} = \pi$ or $\Theta_{fm} = \pi$, it becomes impossible to calculate intermediate variables due to values going to infinity (name for this??). For example when $\Theta_{nm} = \pi$, $Ln = Ls + Lt$ and so:

\begin{align}
  \cos\theta_{ns} &= 1 \\
  \sin\theta_{ns} &= 0 \\
  \mbox{some val?} &\rightarrow \infty
\end{align}

Alternative problem states are when $L = 0$ and ???. These states are corrected similarly.\\

\subsubsection{Forces}
Spring and Brownian forces are used to properly move the model through time. Appendices (\ref{onebound-motion-equatons}-\ref{bothbound-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.

\paragraph{Brownian forces}
Each Brownian force $R_{n,m}$ on domain $n$ in direction $m$ is sampled from a Gaussian with standard deviation $\sqrt{\frac{2k_BT\gamma_n}{dt}}$.\\

\paragraph{Spring forces}
Spring forces are calculated by first finding the torque $\tau$ on each angle, then converting this to a force. For example, the onebound near motor angle feels a force $\tau_{nm} = c_m(\Theta_{nm}-\Theta_{nm,eq})$, where $c_n$ is the spring constant of the motor domain and $\Theta_{nm,eq}$ the equilibrium angle. The magnitude of force on the adjacent binding and tail domains is thus $\tau/Ls$ and $\tau/Lt$, pointing in the direction adjacent the Ls and Lt rods, respectively. The force on the motor domain is found as the equal-and-opposite force to these two imposed forces. In code:

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      T = cm*(nma - nma_eq);
      f1 = T/Ls;
      f2 = T/Lt;
      f1x = f1 * sin(bba);
      f1y = f1 * -cos(bba);
      f2x = f2 * sin(bma);
      f2y = f2 * -cos(bma);
      f.bbx += f1x;
      f.bby += f1y;
      f.tx  += f2x;
      f.ty  += f2y;
      f.bmx += -(f1x + f2x); // equal and opposite forces
      f.bmy += -(f1y + f2y);
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of internal force calculation.}
  \label{transition-rate-snippet}
\end{figure}

\subsection{Verifying the model}
The models were verified to follow physical laws by checking their behavior in various tests: general conformational tests, energy conservation and obeying the equipartition theorem. The purpose of these tests was to verify that equations had been entered properly (primarily the conformational and energy conservation tests), and that the model obeyed the laws of physics (all tests).

\subsubsection{Conformational tests}
The models were tested in the following different conformations to verify they behaved as expected:\\

\textbf{Onebound tests}
\begin{itemize}
\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths. Also checks that all angular velocities are zero. This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or cartesian) without forces.
\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths. Also check that all velocities are zero. This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that cartesian x-velocities are positive and y-velocities are zero. Verifies that the cartesian velocities have the expected sign.
\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all cartesian velocities are zero. Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite. Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
\end{itemize}
*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\

These tests together verify that the onebound model's internal coordinate system's directions match the XY coordinate system directions, that the angular directions in the model properly align with the $\pm x$ and $\pm y$ directions of the XY coordinate system, that velocities have the proper magnitude at zero force and proper sign at nonzero force, and that Brownian and internal forces are in the same unit system. There are still errors which could exist in the model pertaining to magnitude of velocity, which will be tested for in the energy conservation section.\\

\textbf{Bothbound tests}
\begin{itemize}
\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^(-25)$) and motor domains nearly vertical ($\Theta_{n/f} = \pi \pm 10^(-15)$). Equilibrium angles set to have a vertical line as the lowest energy point. Model is not exactly vertical for NaN concerns explained in section \ref{corrections-section}. Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero. Verifies that the domains are properly oriented by the angles, the angles are defined properly and forces are calculated from angles properly.
\item \textbf{Bothbound:} \textit{Equilateral house conformation with outward x-forces.} The model forms the shape of a square with an equilateral triangle on top, with the tail domain as the triangle. Checks if all domains are at the desired locations and the derivatives are the proper sign and are equal and opposite to their counterparts on the opposing side of the house. This test verifies that the angular system behaves as expected and forces are symmetric about the two dimers.
\item \textbf{Bothbound:} \textit{Two table conformations with near/far domains flipped.} Two models are put in the same table-like conformation, but the near/far domains are flipped. Checks if opposite domains have the same positions and forces. Re-verifies that the model is symmetric in position and force between the two dimers.
\end{itemize}

These tests verify the bothbound model's angle system behaves as expected, forces are zero when expected and have the proper signs, and that the whole system is symmetric with either dimer.

\subsubsection{Energy conservation}
To verify that the magnitudes of forces are calculated properly, a conservation of energy test was performed. A very slight angular nudge was applied to either model. This nudge caused a small change in energy. This change in energy was compared with the work the forces on each domain caused over the nudge. In order for energy to be conserved, these values were required to be very similar. Mathematically the test required the following:

\begin{equation}
  \sum_n \frac12 \left(\Theta_{nudge} - \Theta_{n} - \Theta_{n,eq}\right) = \sum_n \vec{F}_n \cdot \vec{r}_{n,nudge}
\end{equation}

where $\Theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the cartesian displacement of each domain $n$ due to the nudge. This test is powerful since it links the force-calculation system of either model to the energy calculation system. Energy is calculated by looking at displacements of angles from equilibrium, whereas forces are calculated using displacement of angles from equilibrium, but also orientation and position of each domain. Having the force system and energy system calculate the same results indicates that they are both likely correct.. \textbf{make this more precise.}

\textbf{is there a test to be run which could verify the velocity calculation is correct?}

\subsubsection{Equipartition theorem}
The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $<E> = \frac N2 k_bT$. In order for the dynein models to display ET behavior, they would have to both properly calculate forces and properly calculate velocities from forces. Brownian forces are also required to properly explore the different states of the system, but they need not be the correct magnitude for ET agreement.\\

To test if the models obey the ET, the total potential energy of each model was logged over \textbf{ten million} (???) timesteps of simulation. The results are reported in Figure \ref{equipartition_agreement}, where the PE scale is in units of $\frac12 k_bT$. Energies are reported as a running average over the simulation from 0 to time $t$. As shown, both models have their average potential energy converge to the expected amount, where the onebound model has four degrees of freedom and the bothbound two.\\

This test verifies both force and velocity are calculated properly for either model. If either force or velocity was wrong, then the model would not obey the Boltzmann hypothesis $P(s) = e^{-\Delta G_{s}/K_BT}$, where $s$ is a state of the system. The transition rate from $s_1$ to $s_2$ is $P(s_1\rightarrow s_2) = e^{-{\Delta G_2 - \Delta G_1}/K_BT}$. Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.\\

\textbf{would it be a stronger test to also calculate the standard deviation of <PE>? It seems like <PE> would still equal N/2KbT as long as the forces/velocities were symmetrically wrong. Calculating the stdev would require the state occupation to actually the ET. Or, maybe just plot the angle occupation and show that it is what it should be?}

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{equipartition_agreement}
%% \end{figure}

\textbf{Possibly do mutations on motion equations to show that tests are no longer behaved}
\subsubsection{Finding proper $dt$}

\subsubsection{Equipartition theorem obeyed}
%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{fig:equipartition_agreement}
%% \end{figure}

\subsection{Parameter fitting}
There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$. Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}. Others are more difficult to find.\\

What's more, using exact literature values for each parameter does not necessarily create the simulation most similar to \textit{in vivo} dynein. Defects and simplifications in the model may cause slightly less physical values for individual parameters to lead to a more physical simulation. For this reason, fitting model parameters to experiment is necessary. This process is chronicled below.

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Table of literature values for various free parameters in dynein model.}
  \label{parameter-table}
\end{figure}

\subsubsection{Fitting rate constants}
Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively. As shown in Section \ref{sec:transitioning-states}, these values can be calculated using the Arrhenius equation:

\begin{equation*}
  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
\end{equation*}

One issue is that $\Delta G_{conf}$ is based on the current conformation of the model, whereas $k_b$ is a macroscopic parameter representative of all conformations of dynein. This is resolved by replacing $\Delta G_{conf}$ with $\left<\Delta G_{conf}\right>$, the expectation value of energy change in going from onebound to bothbound states. This expected energy, by the equipartition theorem, is $2k_BT$ for onebound and $k_BT$ for bothbound. Conversely $\Delta G_{bind}$ is a constant. Thus the rates can be rewritten:

\begin{equation*}
  k_b = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-k_BT\left(1-2\right)}{k_BT}} = \frac{A_b}{e}
\end{equation*}

where $A_b = Ae^{\frac{-\Delta G_{bind}}{k_BT}}$. Thus literature values on MT binding rate can be used in our model to calculate $A_b$.

\textbf{now explain what literature values were used, and why those are reasonable guesses.}

\subsubsection{Fitting spring constants}
\subsubsection{Finding parameters from PyMol}
\subsubsection{Finding values from literature}
\subsubsection{Final parameter guess table}
\subsubsection{Finding the right timestep}

\subsection{Data collection}

\subsubsection{Outputting positions, step locations}
\subsubsection{Reconstructing steps from step locations}
\subsubsection{Job management}

------------------------------------------

\section{Chapter: Results}

\subsection{Simulation parameters}
The ideal set of parameters used to generate data were found to be:

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
    \hline
    $L_s$ & $L_t$ & $R_b$ & $R_m$ & $R_t$ & $\theta_{m}^{Pre}$ & $\theta_{m}^{Post}$ & $\theta_{b}$ & $\theta_{t}$ & $A_{ub}$ & $A_b$ & $c_t$ & $c_m$  &$c_b$\\ \hline
    21.0nm & 22.0nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ & 90 & 2000 & 0.5 & 2.2  & 3.1\\ \hline
  \end{tabular}
  \caption{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
  \label{final-parameter-table}
\end{figure}

\subsection{Histograms}
\subsubsection{Step length histograms}
\subsubsection{Step time histograms}
\subsection{Other ways to represent data?}

\section{Chapter: Discussion}
\subsection{Why our model worked, didn’t work}
Fill this out over winter when you know more.\\
\subsection{Future work on this project}
If setbacks happen, this'll be a big section. Or, further simulations which could be done.

\subsubsection{Experiments to verify our model}
Talk about how FRET could be used to verify our model. We have domain distance info over long
timescales in our model - this is something we could compare to a FRET experiment exploring
the distance between domains in dynein.\\

Other biophysics experiments which could verify our model?\\

Do our spring constants seem to indicate that the protein does about one ATP's worth of work through its cycle? I wonder if the motor cools down its surroundings when it walks...\\

Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using
vanadium? Maybe...\\
\subsection{Possible further projects}
\subsection{Difference between dynein and kinesin}
Our project un/successfully predicted how dynein behaved. How would we modify it to describe kinesin?
Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion? This
would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility
and get its crystal structure to do some comparisons.

\bibliography{thesis-articles}

%% \bibliography{thesis-webpages}

\section{Appendix}

\subsection{Motion equations}

\subsubsection{Onebound equations}
\label{onebound-motion-equations}
The following is a continuation of the derivation for the full motion equations used to time evolve the onebound model:

\begin{align*}
AA &= L_s\sin\theta_{bb}      &   LL &= -L_s\cos(\theta_{bb})\\
BB &= L_t\sin(\theta_{bm})    &	 MM &= -L_t\cos(\theta_{bm})\\
CC &= -L_t\sin(\theta_{um})   &	 NN &= L_t\cos(\theta_{um})\\
DD &= -L_s\sin(\theta_{ub})   &	 OO &= L_s\cos(\theta_{ub})\\
\\
EE &= -\gamma_m (X_{bm} - X_{bb})       &  PP &= -\gamma_m (Y_{bm} - Y_{bb})\\
FF &= \gamma_m (X_{t } - X_{bm})        &	 QQ &= \gamma_m (Y_{t } - Y_{bm})\\ 
GG &= -\gamma_t (X_{t } - X_{bm})       &	 RR &= -\gamma_t (Y_{t } - Y_{bm})\\
HH &= \gamma_t (X_{um} - X_{t })        &	 SS &= \gamma_t (Y_{um} - Y_{t })\\ 
II &= -\gamma_m (X_{um} - X_{t })       &	 TT &= -\gamma_m (Y_{um} - Y_{t })\\
JJ &= \gamma_m (X_{ub} - X_{um})        &	 UU &= \gamma_m (Y_{ub} - Y_{um})\\ 
KK &= -\gamma_b (X_{ub} - X_{um})       &	 VV &= -\gamma_b (Y_{ub} - Y_{um})\\
\end{align*}%
%
\[
\begin{pmatrix}
  AA & 0 & 0 & 0 & EE & FF & 0 & 0\\
  AA & BB & 0 & 0 & 0 & GG & HH & 0\\
  AA & BB & CC & 0 & 0 & 0 & II & JJ\\
  AA & BB & CC & DD & 0 & 0 & 0 & KK\\
  LL & 0 & 0 & 0 & PP & QQ & 0 & 0\\
  LL & MM & 0 & 0 & 0 & RR & SS & 0\\
  LL & MM & NN & 0 & 0 & 0 & TT & UU\\
  LL & MM & NN & OO & 0 & 0 & 0 & VV\\
\end{pmatrix}
\begin{pmatrix}
    \dot{\theta}_{bb}\\
    \dot{\theta}_{bm}\\
    \dot{\theta}_{um}\\
    \dot{\theta}_{ub}\\
    \lambda_{bs}\\
    \lambda_{bt}\\
    \lambda_{ut}\\
    \lambda_{us}\\
  \end{pmatrix}
=
\begin{pmatrix}
  X1\\
  X2\\
  X3\\
  X4\\
  X5\\
  X6\\
  X7\\
  X8\\
\end{pmatrix}
\]

Solving the above system for $\dot{\Theta}_{bb}, \dot{\Theta}_{bm}, \dot{\Theta}_{um}$ and $\dot{\Theta}_{ub}$ gives the desired velocities. Solution was done via Mathematica.

%% $\dot{\Theta}_{bb}$ =
%% {\tiny
%% ( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
%% } \break

%% $\dot{\Theta}_{bm}$ =
%% {\tiny
%%   (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
%% }\break

%% $\dot{\Theta}_{um}$ =
%% {\tiny
%%   ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
%% }\break

%% $\dot{\Theta}_{ub}$ =
%% {\tiny
%%   ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
%% }

\subsubsection{Bothbound equations}
\label{bothbound-motion-equations}
The following are the full motion equations used to time evolve the bothbound model:

\begin{center}
  \begin{minipage}{0.3\textwidth}
    \begin{align*}
      a &= \frac{-dXnm}{dLn}\\
       b &= \frac{-dXnm}{dLf}\\
       c &= -(x_{nm} - x_{nb}) / \gamma_m\\
       d &= (x_t - x_{nm}) / \gamma_m\\
       e &= \frac{-dXt}{dLn}\\
       f &= \frac{-dXt}{dLf}\\
       g &= -(x_t - x_{nm}) / \gamma_t\\
       h &= (x_{fm} - x_t) / \gamma_t\\
       i &= \frac{-dXfm}{dLn}\\
       j &= \frac{-dXfm}{dLf}\\
       k &= -(x_{fm} - x_t) / \gamma_m\\
       l &= (x_{fb} - x_{fm}) / \gamma_m\\
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
    \begin{align*}
       m &= \frac{-dYnm}{dLn}\\
       n &= \frac{-dYnm}{dLf}\\
       p &= -(y_{nm} - y_{nb}) / \gamma_m\\
       q &= (y_t - y_{nm}) / \gamma_m\\
       r &= \frac{-dYt}{dLn}\\
       s &= \frac{-dYt}{dLf}\\
       t &= -(y_t - y_{nm}) / \gamma_t\\
       u &= (y_{fm} - y_t) / \gamma_t\\
       v &= \frac{-dYfm}{dLn}\\
       w &= \frac{-dYfm}{dLf}\\
       x &= -(y_{fm} - y_t) / \gamma_m\\
       y &= (y_{fb} - y_{fm}) / \gamma_m
    \end{align*}
  \end{minipage}
\end{center}

Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.

%% $\dot{Ln}$ =
%% {\tiny
%%     (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
%%      d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
%%      c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
%%      c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
%%      c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
%%      d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
%%      c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
%%      g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
%%      d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
%%      d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
%%      c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
%%      b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
%%      c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
%%      d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
%% }\break

%% $\dot{Lf}$ =
%% {\tiny
%%     (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
%%      d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
%%      c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
%%      c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
%%      c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
%%      d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
%%      c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
%%      g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
%%      d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
%%      d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
%%      c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
%%      a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
%%      c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
%%      d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
%% }

\section{Questions for Tate/Nicole}
\begin{itemize}
\item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
\item Is it appropriate to cite web pages in a thesis? In a separate citation section?
\item When is a fact ``common knowledge'' enough that it doesn't need a citation?
\item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
\end{itemize}

\section{Questions for David}
\begin{itemize}
\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be? Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
\item What is the value of $\left<\Delta G_{conf}\right>$ in going from bothbound to onebound?
\end{itemize}
\end{document}

### 2017-01-22 thesis/latex/thesis.tex
Add all thesis figures to root figures directory and make thesis build.

@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
   \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
   \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/retrograde_transport.jpg}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
   \caption{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mtbd-complex.png}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
@@
 %%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
 %%   \caption{Crystal structures of cytoplasmic dynein 1 and kinesin KIF5B (PDB IDs 4RH7 and 1BG2).}
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
   \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
@@
 %%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/two-state-em-diagram}
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/two-state-em-diagram}
 %%   \caption{}
@@
 %%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/nucleotide-state-cycle}
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/nucleotide-state-cycle}
 %%   \caption{}
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../figures/ob_fig.pdf}
+  \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
   \caption{Spatial representation of onebound model.}
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../figures/code-bothbound.pdf}
+  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
   \caption{Definition of equilibrium angles.}
@@
 %%   \begin{minipage}[b]{0.49\textwidth}
-%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
+%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
 %%     \caption{Onebound PE vs time.}
@@
 %%   \begin{minipage}[b]{0.49\textwidth}
-%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
+%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
 %%     \caption{Bothbound PE vs time.}

### 2017-01-22 thesis/latex/thesis.tex
Add work on rate constant fitting and add sample histograms to results.

@@
 Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
+
+\textit{Add figure somewhere of this cycle superimposed with markings of what states are considered onebound and bothbound}\\
 
@@
 
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
+    \caption{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
+  \end{minipage}
+  \hspace{.2cm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
+    \caption{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
+  \end{minipage}
+  \label{fig:equipartition_agreement}
+\end{figure}
+
 \textbf{would it be a stronger test to also calculate the standard deviation of <PE>?
@@
 
-%% \begin{figure}[h!]
-%%   \centering
-%%   \begin{minipage}[b]{0.49\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
-%%     \caption{Onebound PE vs time.}
-%%   \end{minipage}
-%%   \begin{minipage}[b]{0.49\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
-%%     \caption{Bothbound PE vs time.}
-%%   \end{minipage}
-%%   \label{equipartition_agreement}
-%% \end{figure}
-
 \textbf{Possibly do mutations on motion equations to show that tests are no longer behaved}
-\subsubsection{Finding proper $dt$}
-
-\subsubsection{Equipartition theorem obeyed}
-%% \begin{figure}[h!]
-%%   \centering
-%%   \begin{minipage}[b]{0.49\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
-%%     \caption{Onebound PE vs time.}
-%%   \end{minipage}
-%%   \begin{minipage}[b]{0.49\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
-%%     \caption{Bothbound PE vs time.}
-%%   \end{minipage}
-%%   \label{fig:equipartition_agreement}
-%% \end{figure}
 
@@
 This process is chronicled below.
+Table \ref{table:parameter-table} concisely lists literature values for various parameters.
 
@@
     $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
-    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
-    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
     $c_t$ & & & & & & & & \\ \hline
@@
   \caption{Table of literature values for various free parameters in dynein model.}
-  \label{parameter-table}
+  \label{table:parameter-table}
+\end{figure}
+
+In addition, the physical conditions the simulations were run at are shown in Table \ref{table:simulation-conditions}.
+These conditions are meant to reflect the conditions found inside a typical cell.
+\textbf{of what species?}\\
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| l | l |}
+    \hline
+    T & [ATP] \\ \hline
+    310.15 K & $1.54*10^{-3}$ M \cite{cellular-atp}\\ \hline
+  \end{tabular}
+  \caption{Table of physical constants used in simulation.}
+  \label{table:parameter-table}
 \end{figure}
@@
 \subsubsection{Fitting rate constants}
+\paragraph{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
 Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
-As shown in Section \ref{sec:transitioning-states}, these values can be calculated using the Arrhenius equation:
-
-\begin{equation*}
-  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
-\end{equation*}
-
-One issue is that $\Delta G_{conf}$ is based on the current conformation of the model, whereas $k_b$ is a macroscopic parameter representative of all conformations of dynein.
-This is resolved by replacing $\Delta G_{conf}$ with $\left<\Delta G_{conf}\right>$, the expectation value of energy change in going from onebound to bothbound states.
-This expected energy, by the equipartition theorem, is $2k_BT$ for onebound and $k_BT$ for bothbound.
-Conversely $\Delta G_{bind}$ is a constant.
-Thus the rates can be rewritten:
-
-\begin{equation*}
-  k_b = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-k_BT\left(1-2\right)}{k_BT}} = \frac{A_b}{e}
-\end{equation*}
-
-where $A_b = Ae^{\frac{-\Delta G_{bind}}{k_BT}}$. Thus literature values on MT binding rate can be used in our model to calculate $A_b$.
-
-\textbf{now explain what literature values were used, and why those are reasonable guesses.}
+One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations.
+In contrast, the rates the model uses represent the probability of unbinding of a specific conformation.
+Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$.
+As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:
+
+\begin{align*}
+  k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
+  k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
+\end{align*}
+
+where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
+The experimental values are calculated the same way, with the free energy changes replaced with expectation values.
+Since by the equipartition theorem $\left<G_{conf}^{ob}\right> = 2k_BT$ and $\left<G_{conf}^{bb}\right> = k_BT$, the equations can be simplified:
+
+\begin{align*}
+  k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
+  k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
+\end{align*}
+
+Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
+
+\paragraph{Literature values for experimental binding rates}
+Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
+  \caption{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
+  \label{fig:sarlah-rate-table}
+\end{figure}
+
+The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
+Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound.
+These states are roughly grouped as MT-bound and MT-unbound states in the Cianfrocco mechanochemical cycle \cite{cianfroccoreview}.\\
+
+The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
+That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\
+
+\paragraph{Fitting rate constants by simulation}
+\textit{Add in a plot of the binding rate fitting search}
 
 \subsubsection{Fitting spring constants}
+\paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
+\paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
+\paragraph{Fitting rate constants by simulation}
+
 \subsubsection{Finding parameters from PyMol}
-\subsubsection{Finding values from literature}
-\subsubsection{Final parameter guess table}
+
 \subsubsection{Finding the right timestep}
@@
 \subsubsection{Job management}
-
-------------------------------------------
 
@@
 \subsection{Histograms}
-\subsubsection{Step length histograms}
-\subsubsection{Step time histograms}
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
+    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
+  \end{minipage}
+  \hspace{.1cm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
+    \caption{Histogram of simulated stepping times using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
+  \end{minipage}
+  \label{fig:equipartition_agreement}
+\end{figure}
+
 \subsection{Other ways to represent data?}

### 2017-01-23 thesis/latex/thesis.tex
Fix k_ub parameter.

@@
     $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
-    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
+    $k_b$ & $460 s^{-1,b}$ & & & & & & & \\ \hline
     $c_t$ & & & & & & & & \\ \hline

### 2017-01-23 thesis_stuff/thesis_stuff.tex
Add results of latest runs. Looks like unbinding probability still too high.
Fix k_ub parameter.

--- 2017-01-15 thesis_stuff/thesis_stuff.tex
@@
 
-\begin{center}
-  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
-    \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
-    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
-    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
-    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
-    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
-    $R_t$ &  & & & & 2.16nm & & & \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
-    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
-    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
-    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
-    $c_t$ & & & & & & & & \\ \hline
-    $c_m$ & & & & & & & & \\ \hline
-    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
-  \end{tabular}
-\end{center}
+%% \begin{center}
+%%   \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
+%%     \hline
+%%     & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
+%%     $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
+%%     $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
+%%     $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
+%%     $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
+%%     $R_t$ &  & & & & 2.16nm & & & \\ \hline
+%%     $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
+%%     $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
+%%     $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
+%%     $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
+%%     $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
+%%     $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
+%%     $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
+%%     $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
+%%     $c_t$ & & & & & & & & \\ \hline
+%%     $c_m$ & & & & & & & & \\ \hline
+%%     $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
+%%   \end{tabular}
+%% \end{center}
+
+\textbf{Table moved to real elliott thesis!}
 
@@
     22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & $9.1e-4$ & & NaN! motor crashes into MT \\\hline
-    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
-    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
-    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
-    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & $4.6e-14$ & & & \\\hline
     22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $2.7e-13$ & $6.8e-4$ & & \\\hline
@@
     22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
-    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
-    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
-    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
-    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & $5.4e-18$ & & & \\\hline
     22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $9.5e-32$ & & & \\\hline
     22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $2.7e-35$ & & & \\\hline
+    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & $2.7e-12$ & $1.7e-3$ & & NaN! motor crashes into MT\\\hline
+    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & $4.1e-18$ & $5.5e-3$ & & \\\hline
+    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & $1.5e-12$ & $2.2e-4$ & & \\\hline
+    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & $2.2e-18$ & & & \\\hline
+    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & & & & \\\hline
+    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 1.00 & 1.00 & 1.00 & & $1.8^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 1.30 & 1.30 & 1.30 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 1.60 & 1.60 & 1.60 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 1.90 & 1.90 & 1.90 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 2.10 & 2.10 & 2.10 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 2.25 & 2.25 & 2.25 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 2.55 & 2.55 & 2.55 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 2.70 & 2.70 & 2.70 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 5000 &  180 & 3.10 & 3.10 & 3.10 & & $1.9^{-2}$ & & \\\hline
   \end{tabular}
@@
 
-A more reliable step time determiner is $\Big<\mbox{step time}\Big>$, which should be around 0.1. This number can be determined from the step time histograms.\\
+A more reliable step time determiner is $\Big<\mbox{step time}\Big>$, which should be around 0.1. This number can be determined from our step time histograms.\\
 

### 2017-01-23 default_parameters.h
Add precision to stepping data printout.

@@ -47,7 +47,7 @@ double binding_fraction = 1e-6;
 double MICROTUBULE_REPULSION_FORCE = 30.0; // N/nm
 double MICROTUBULE_BINDING_DISTANCE = 0.2; // nm
 
-double REBINDING_IMMUNITY_TIME = 2e-11; // s
+double REBINDING_IMMUNITY_TIME = 2*dt; // s
 
 double RAND_INIT_SEED = 0;
 

### 2017-01-23 thesis/latex/thesis.tex

@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
+  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
   \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
@@
 
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
-    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
-  \end{minipage}
-  \hspace{.1cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
-    \caption{Histogram of simulated stepping times using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
-  \end{minipage}
-  \label{fig:equipartition_agreement}
-\end{figure}
+%% \begin{figure}[h!]
+%%   \centering
+%%   \begin{minipage}[b]{0.45\textwidth}
+%%     \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
+%%     \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
+%%   \end{minipage}
+%%   \hspace{.1cm}
+%%   \begin{minipage}[b]{0.45\textwidth}
+%%     \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
+%%     \caption{Histogram of simulated stepping times using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
+%%   \end{minipage}
+%%   \label{fig:final-histograms}
+%% \end{figure}
 
@@
 
-%% $\dot{\Theta}_{bb}$ =
-%% {\tiny
-%% ( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% } \break
-
-%% $\dot{\Theta}_{bm}$ =
-%% {\tiny
-%%   (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% }\break
-
-%% $\dot{\Theta}_{um}$ =
-%% {\tiny
-%%   ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }\break
-
-%% $\dot{\Theta}_{ub}$ =
-%% {\tiny
-%%   ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }
+$\dot{\Theta}_{bb}$ =
+{\tiny
+( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
+} \break
+
+$\dot{\Theta}_{bm}$ =
+{\tiny
+  (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
+}\break
+
+$\dot{\Theta}_{um}$ =
+{\tiny
+  ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
+}\break
+
+$\dot{\Theta}_{ub}$ =
+{\tiny
+  ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
+}
 
@@
 
-%% $\dot{Ln}$ =
-%% {\tiny
-%%     (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
-%%      d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
-%%      c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
-%%      c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
-%%      c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
-%%      d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
-%%      c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
-%%      g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
-%%      d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
-%%      d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
-%%      c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
-%%      b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
-%%      c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
-%%      d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }\break
-
-%% $\dot{Lf}$ =
-%% {\tiny
-%%     (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
-%%      d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
-%%      c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
-%%      c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
-%%      c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
-%%      d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
-%%      c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
-%%      g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
-%%      d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
-%%      d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
-%%      c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
-%%      a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
-%%      c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
-%%      d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }
+$\dot{Ln}$ =
+{\tiny
+    (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
+     d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
+     c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
+     c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
+     c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
+     d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
+     c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
+     g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
+     d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
+     d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
+     c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
+     b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
+     c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
+     d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
+     (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
+     c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
+     d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
+     c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
+     c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
+     c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
+     c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
+     c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
+     c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
+     d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
+     c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
+     b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
+     c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
+     d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
+}\break
+
+$\dot{Lf}$ =
+{\tiny
+    (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
+     d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
+     c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
+     c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
+     c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
+     d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
+     c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
+     g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
+     d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
+     d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
+     c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
+     a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
+     c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
+     d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
+     (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
+     c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
+     d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
+     c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
+     c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
+     c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
+     c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
+     c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
+     c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
+     d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
+     c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
+     b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
+     c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
+     d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
+}
 
@@
 \item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
-\item Is it appropriate to cite web pages in a thesis? In a separate citation section?
+\item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
 \item When is a fact ``common knowledge'' enough that it doesn't need a citation?
 \item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
+\item Is 25 pages too long for a thesis? What makes a thesis too long?
+\item What details belong in a thesis, and which are too much?
+ex going in-depth on what tests do, describing how we came up with guess numbers for parameter hunt, describing function of dynein in the cell, showing why motor proteins are necessary.
+\item Supplemental info?
 \end{itemize}

### 2017-01-27 thesis/latex/thesis.tex
table written while meeting with Elliott

@@
   \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
+  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
+  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
+  \newcommand\transition{\textcolor{green}{transition?}}
+  \begin{tabular}{rll}
+    \bothbound &
+    1 & \begin{minipage}{5in}
+      Bound to microtubule and waiting for ATP to arrive.  The
+      conformation is ``post-powerstroke''.
+    \end{minipage}\vspace{0.5em}\\
+    \bothbound &
+    2 & \begin{minipage}{5in}
+      ATP has bound to the motor at AAA1, but nothing else has changed.
+    \end{minipage}\vspace{0.5em}\\
+    \transition &
+    3 & \begin{minipage}{5in}
+      ``The ring has closed'' in the motor, whatever that means.
+    \end{minipage}\vspace{0.5em}\\
+    \bothbound &
+    4 & \begin{minipage}{5in}
+      The affinity to the microtubule is dropped, so it is likely to pop off soon.
+    \end{minipage}\vspace{0.5em}\\
+    \onebound &
+    5 & \begin{minipage}{5in} It has popped off of the microtubule!
+      Onebound! The equilibrium angle is also changed.  The ATP has
+      been hydrolized, but the phosphate is still bound to the motor.
+      ``Priming stroke?''
+    \end{minipage}\vspace{0.5em}\\
+    \onebound &
+    6 & \begin{minipage}{5in} It is now bound to the microtubule, but
+      with low affinity, and without any loss of phosphate. Question:
+      does this happen many times? If so it may still be onebound.
+      Otherwise it is probably bothbound.
+    \end{minipage}\vspace{0.5em}\\
+    \bothbound &
+    7 & \begin{minipage}{5in}
+      Now it is seriously bound to the microtubule, and the motor
+      domain has changed conformation.  This is now ``high affinity.''
+    \end{minipage}\vspace{0.5em}\\
+    \bothbound &
+    8 & \begin{minipage}{5in}
+      Phosphate has been released, and our equilibrium angles have
+      been changed.  This is the ``power stroke.''
+    \end{minipage}\vspace{0.5em}\\
+    \bothbound &
+    1 & \begin{minipage}{5in}
+      The ADP has been released from the motor domain, so it can now
+      bind ATP.  Still ``high affinity,'' and still in the
+      ``power-stroke'' conformation.
+    \end{minipage}\vspace{0.5em}\\
+    \bothbound &
+    9 & \begin{minipage}{5in}
+      While stuck in this ``normal bound'' state, another site on the
+      motor AAA3 can lose its ADP, which leaves the motor in a state
+      where it cannot directly move on to step 2 (until after
+      reversing this).  Controversial?
+    \end{minipage}
+  \end{tabular}
   \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}

### 2017-01-27 thesis/latex/thesis.tex
Thesis: Add intro suggestions and a todo list.

--- 2017-01-23 thesis/latex/thesis.tex
@@
 \section{Chapter: Introduction}
+Begin with a paper-like introduction which talks about:
+
+\begin{itemize}
+\item How dynein is a structure which turns chemical energy into motion
+\item How it's weird that a cellular structure can generate directed motion
+\item Other cool stuff - make dynein mysterious and cool.
+\end{itemize}
+
 \subsection{What is dynein?}
@@
 \end{itemize}
+
+\section{Todo for project}
+\begin{itemize}
+\item Do calculations to turn processivity into state time ratios
+\item Fit the state times to above number by tweaking un/binding rates
+\item Fit spring constants to step length histograms
+\end{itemize}
 \end{document}

### 2017-01-28 thesis_stuff/thesis_stuff.tex
Add precision to stepping data printout.
Add few numbers from Weihong's paper to thesis.

@@
     22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & & & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 1.00 & 1.00 & 1.00 & & $1.8^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 1.30 & 1.30 & 1.30 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 1.60 & 1.60 & 1.60 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 1.90 & 1.90 & 1.90 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 2.10 & 2.10 & 2.10 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 1.00 & 1.00 & 1.00 & & $1.8^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 1.30 & 1.30 & 1.30 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 1.60 & 1.60 & 1.60 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 1.90 & 1.90 & 1.90 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 2.10 & 2.10 & 2.10 & & $1.9^{-2}$ & & \\\hline
     22.1 & 11.1 & 5000 &  180 & 2.25 & 2.25 & 2.25 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 2.55 & 2.55 & 2.55 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 2.70 & 2.70 & 2.70 & & $1.9^{-2}$ & & \\\hline
-    22.1 & 11.1 & 5000 &  180 & 3.10 & 3.10 & 3.10 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 2.55 & 2.55 & 2.55 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 2.70 & 2.70 & 2.70 & & $1.9^{-2}$ & & \\\hline
+    %% 22.1 & 11.1 & 5000 &  180 & 3.10 & 3.10 & 3.10 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 300 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
+    22.1 & 11.1 & 100 &  180 & 2.40 & 2.40 & 2.40 & & $1.9^{-2}$ & & \\\hline
   \end{tabular}
@@
 \section{Papers}
+
+\subsection{A Simple Theoretical Model Explains Dynein’s Response to Load}
+Yi Qin Gao 2006
+
+Two reaction coordinates. First is where it is in the ATP, ADP-Pi, ADP, Apo cycle. Second is domain orientation and MT binding status position.\\
+
+Stalling force increases by 4-fold when [ATP] goes from 0.1 to 1mM, a much more dramatic change than seen in kinesin.
+(they cite this claim).
+Dynein's step size also varies a lot with load -- we could easily test if our model behaves this way, as well.\\
+
+ATP binding rate to apo dynein: $7*1-^5/m/s$
+
+This seems like a good paper to finish eventually. It would be something to compare our results to.\\
 
@@
 
-Has the stepping histograms we are trying to reproduce computationally.
+Has the stepping histograms we are trying to reproduce computationally.\\
+
+Velocities reported here are probably bad, but the step lengths are good. Step length not influenced by [ATP].\\
+
+At Weihong's 1mM [ATP], the stepping rate for their dynein is $k = 1.78 ± 0.13 s−1$.
+Thus dynein takes a step roughly every $0.58s$ when in low-ATP conditions.
+Average velocity at this concentration si $134 ± 60.4 nm s−1$.
+Run length of $1.06 ± 0.044 µm$.\\
+
+Seems to be a difference between different types of steps: tail steps are a single motion of the tail, and Weihong says are about 10nm (2d).
+Motions of each motor are 14-16nm.
+77\% are forward steps.\\
+
+It's potentially important to note the dynein species used, though probably not since Weihong didn't mention it much in the paper.\\
 

### 2017-02-02 thesis/latex/thesis.tex
Add few numbers from Weihong's paper to thesis.

@@
 \item How dynein is a structure which turns chemical energy into motion
+\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
 \item How it's weird that a cellular structure can generate directed motion
@@
 
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| c | c | c | c |}
+    \hline
+    Author & Conditions & Velocity & Run length\\\hline
+    Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
+    Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
+  \end{tabular}
+  \caption{Table of literature values for dynein behavior}
+  \label{table:parameter-table}
+\end{figure}
+
 \subsection{Parameter fitting}

### 2017-02-04 thesis/latex/thesis.tex
Thesis: Add method for estimating time in one/bothbound from today's meeting.

@@
 
+\paragraph{Fitting rate constants to processivity and step times}
+Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
+
+\newcommand\tbb{\left<t_{bb}\right>}
+\newcommand\tob{\left<t_{ob}\right>}
+\newcommand\tstep{\left<t_{step}\right>}
+\newcommand\tproc{\left<t_{processivity}\right>}
+\newcommand\kub{k_{ub}}
+\newcommand\kb{k_{b}}
+\newcommand\ko{k_{dis}}
+
+\begin{itemize}
+\item $\tbb$: Time in bothbound per step
+\item $\tob$: Time in onebound per step
+\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+\end{itemize}
+
+$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
+
+\begin{align*}
+  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  \tbb &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tob &= \tstep-\tbb\\
+  &= \tstep - \frac{\tstep\tbb}{\tstep-\tbb}\\
+  &= \frac{\left(\tstep-\tbb\right)\tstep\tbb}{\tstep-\tbb}\\
+  &= \frac{\tstep\left(\tstep-\tbb\right) - \tstep\tbb}{\tstep-\tbb}\\
+  &= \frac{\tstep^2}{\tstep-\tbb}\\
+\end{align*}
+
+Thus, by the above equations and using data from (put right paper here), values for $\tbb$ and $\tob$ can be found:
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| c | c | c | c | c | c |}
+    \hline
+    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    100nm/s & 8nm & 0.08 & 3s & 0.08 & 0.002 \\ \hline
+  \end{tabular}
+  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
+  \label{table:parameter-table}
+\end{figure}
+
+Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATp concentration.\\
+
 \paragraph{Fitting rate constants by simulation}

### 2017-02-04 thesis/latex/thesis.tex
Thesis: clean up, add comments frok Nicole.

--- 2017-02-02 thesis/latex/thesis.tex
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
-  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
-  \label{dynein-artist-rendition-2}
-\end{figure}
+%% \begin{figure}[h]
+%%   \centering
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
+%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
+%%   \label{dynein-artist-rendition-2}
+%% \end{figure}
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
   \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
-  \caption{Spatial representation of onebound model.}
-  \label{ob_fig}
-\end{figure}
-
-TODO: make figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\
+%% \begin{figure}[h]
+%%   \centering
+%%   \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
+%%   \caption{Spatial representation of onebound model.}
+%%   \label{ob_fig}
+%% \end{figure}
+
+TODO: make onebound model figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\
 
@@
 \begin{align}
-  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} &= \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
-  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
-  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
-  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
-\end{align}
-
-\begin{align}
-  L_s\cos(\theta_{bb})\dot{\theta}_{bm} &= \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
-  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
-  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
-  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
+  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
+  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
+  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
+  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
+\end{align}
+
+\begin{align}
+  &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
+  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
+  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
+  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
 \end{align}
@@
 
+%% \subsection{Data collection}
+%% Time evolution of the system has the potential to create a huge amount of data, so care has to be taken to only collect what is necessary.
+For the purposes of testing stepping behavior of the model the geometry and per-domain forces and energies can be safely ignored.
+All that is needed to determine model fitness is the size and duration of each step.\\
+
+%% \subsubsection{Stepping data output and calculation}
+%% A step is defined as a complete cycle of
+
+%% \subsubsection{Simulation running via SLURM}
+
 \subsection{Parameter fitting}
@@
 
-\paragraph{Fitting rate constants by simulation}
-\textit{Add in a plot of the binding rate fitting search}
-
-\subsubsection{Fitting spring constants}
-\paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
-\paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
-\paragraph{Fitting rate constants by simulation}
-
-\subsubsection{Finding parameters from PyMol}
-
-\subsubsection{Finding the right timestep}
-
-\subsection{Data collection}
-
-\subsubsection{Outputting positions, step locations}
-\subsubsection{Reconstructing steps from step locations}
-\subsubsection{Job management}
+%% \paragraph{Fitting rate constants by simulation}
+%% \textit{Add in a plot of the binding rate fitting search}
+
+%% \subsubsection{Fitting spring constants}
+%% \paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
+%% \paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
+%% \paragraph{Fitting rate constants by simulation}
+
+%% \subsubsection{Finding parameters from PyMol}
+
+%% \subsubsection{Finding the right timestep}
 
@@
 
-$\dot{\Theta}_{bb}$ =
-{\tiny
-( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-} \break
-
-$\dot{\Theta}_{bm}$ =
-{\tiny
-  (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-}\break
-
-$\dot{\Theta}_{um}$ =
-{\tiny
-  ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-}\break
-
-$\dot{\Theta}_{ub}$ =
-{\tiny
-  ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-}
-
-\subsubsection{Bothbound equations}
-\label{bothbound-motion-equations}
-The following are the full motion equations used to time evolve the bothbound model:
-
-\begin{center}
-  \begin{minipage}{0.3\textwidth}
-    \begin{align*}
-      a &= \frac{-dXnm}{dLn}\\
-       b &= \frac{-dXnm}{dLf}\\
-       c &= -(x_{nm} - x_{nb}) / \gamma_m\\
-       d &= (x_t - x_{nm}) / \gamma_m\\
-       e &= \frac{-dXt}{dLn}\\
-       f &= \frac{-dXt}{dLf}\\
-       g &= -(x_t - x_{nm}) / \gamma_t\\
-       h &= (x_{fm} - x_t) / \gamma_t\\
-       i &= \frac{-dXfm}{dLn}\\
-       j &= \frac{-dXfm}{dLf}\\
-       k &= -(x_{fm} - x_t) / \gamma_m\\
-       l &= (x_{fb} - x_{fm}) / \gamma_m\\
-    \end{align*}
-  \end{minipage}
-  \begin{minipage}{0.3\textwidth}
-    \begin{align*}
-       m &= \frac{-dYnm}{dLn}\\
-       n &= \frac{-dYnm}{dLf}\\
-       p &= -(y_{nm} - y_{nb}) / \gamma_m\\
-       q &= (y_t - y_{nm}) / \gamma_m\\
-       r &= \frac{-dYt}{dLn}\\
-       s &= \frac{-dYt}{dLf}\\
-       t &= -(y_t - y_{nm}) / \gamma_t\\
-       u &= (y_{fm} - y_t) / \gamma_t\\
-       v &= \frac{-dYfm}{dLn}\\
-       w &= \frac{-dYfm}{dLf}\\
-       x &= -(y_{fm} - y_t) / \gamma_m\\
-       y &= (y_{fb} - y_{fm}) / \gamma_m
-    \end{align*}
-  \end{minipage}
-\end{center}
-
-Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
-
-$\dot{Ln}$ =
-{\tiny
-    (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
-     d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
-     c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
-     c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
-     c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
-     d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
-     c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
-     g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
-     d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
-     d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
-     c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
-     b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
-     c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
-     d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
-     (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-     c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-     d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-     c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-     c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-     c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-     c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-     c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-     c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-     d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-     c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-     b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-     c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-     d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-}\break
-
-$\dot{Lf}$ =
-{\tiny
-    (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
-     d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
-     c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
-     c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
-     c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
-     d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
-     c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
-     g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
-     d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
-     d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
-     c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
-     a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
-     c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
-     d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
-     (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-     c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-     d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-     c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-     c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-     c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-     c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-     c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-     c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-     d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-     c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-     b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-     c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-     d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-}
+%% $\dot{\Theta}_{bb}$ =
+%% {\tiny
+%% ( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
+%% } \break
+
+%% $\dot{\Theta}_{bm}$ =
+%% {\tiny
+%%   (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
+%% }\break
+
+%% $\dot{\Theta}_{um}$ =
+%% {\tiny
+%%   ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
+%% }\break
+
+%% $\dot{\Theta}_{ub}$ =
+%% {\tiny
+%%   ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
+%% }
+
+%% \subsubsection{Bothbound equations}
+%% \label{bothbound-motion-equations}
+%% The following are the full motion equations used to time evolve the bothbound model:
+
+%% \begin{center}
+%%   \begin{minipage}{0.3\textwidth}
+%%     \begin{align*}
+%%       a &= \frac{-dXnm}{dLn}\\
+%%        b &= \frac{-dXnm}{dLf}\\
+%%        c &= -(x_{nm} - x_{nb}) / \gamma_m\\
+%%        d &= (x_t - x_{nm}) / \gamma_m\\
+%%        e &= \frac{-dXt}{dLn}\\
+%%        f &= \frac{-dXt}{dLf}\\
+%%        g &= -(x_t - x_{nm}) / \gamma_t\\
+%%        h &= (x_{fm} - x_t) / \gamma_t\\
+%%        i &= \frac{-dXfm}{dLn}\\
+%%        j &= \frac{-dXfm}{dLf}\\
+%%        k &= -(x_{fm} - x_t) / \gamma_m\\
+%%        l &= (x_{fb} - x_{fm}) / \gamma_m\\
+%%     \end{align*}
+%%   \end{minipage}
+%%   \begin{minipage}{0.3\textwidth}
+%%     \begin{align*}
+%%        m &= \frac{-dYnm}{dLn}\\
+%%        n &= \frac{-dYnm}{dLf}\\
+%%        p &= -(y_{nm} - y_{nb}) / \gamma_m\\
+%%        q &= (y_t - y_{nm}) / \gamma_m\\
+%%        r &= \frac{-dYt}{dLn}\\
+%%        s &= \frac{-dYt}{dLf}\\
+%%        t &= -(y_t - y_{nm}) / \gamma_t\\
+%%        u &= (y_{fm} - y_t) / \gamma_t\\
+%%        v &= \frac{-dYfm}{dLn}\\
+%%        w &= \frac{-dYfm}{dLf}\\
+%%        x &= -(y_{fm} - y_t) / \gamma_m\\
+%%        y &= (y_{fb} - y_{fm}) / \gamma_m
+%%     \end{align*}
+%%   \end{minipage}
+%% \end{center}
+
+%% Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
+
+%% $\dot{Ln}$ =
+%% {\tiny
+%%     (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
+%%      d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
+%%      c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
+%%      c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
+%%      c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
+%%      d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
+%%      c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
+%%      g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
+%%      d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
+%%      d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
+%%      c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
+%%      b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
+%%      c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
+%%      d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
+%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
+%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
+%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
+%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
+%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
+%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
+%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
+%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
+%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
+%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
+%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
+%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
+%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
+%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
+%% }\break
+
+%% $\dot{Lf}$ =
+%% {\tiny
+%%     (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
+%%      d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
+%%      c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
+%%      c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
+%%      c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
+%%      d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
+%%      c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
+%%      g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
+%%      d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
+%%      d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
+%%      c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
+%%      a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
+%%      c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
+%%      d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
+%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
+%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
+%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
+%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
+%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
+%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
+%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
+%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
+%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
+%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
+%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
+%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
+%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
+%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
+%% }
 
 \section{Questions for Tate/Nicole}
-\begin{itemize}
-\item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
-\item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
-\item When is a fact ``common knowledge'' enough that it doesn't need a citation?
-\item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
-\item Is 25 pages too long for a thesis? What makes a thesis too long?
-\item What details belong in a thesis, and which are too much?
+%%\begin{itemize}
+%% \item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
+%% \item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
+%% \item When is a fact ``common knowledge'' enough that it doesn't need a citation?
+%% \item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
+%% \item Is 25 pages too long for a thesis? What makes a thesis too long?
+%% \item What details belong in a thesis, and which are too much?
 ex going in-depth on what tests do, describing how we came up with guess numbers for parameter hunt, describing function of dynein in the cell, showing why motor proteins are necessary.
-\item Supplemental info?
-\end{itemize}
+%% \item Supplemental info?
+%%\end{itemize}
 

### 2017-02-04 thesis/latex/thesis.tex

@@
 
-%% \paragraph{Fitting rate constants by simulation}
+\paragraph{Fitting rate constants to processivity and step times}
+Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
+
+\newcommand\tbb{\left<t_{bb}\right>}
+\newcommand\tob{\left<t_{ob}\right>}
+\newcommand\tstep{\left<t_{step}\right>}
+\newcommand\tproc{\left<t_{processivity}\right>}
+\newcommand\kub{k_{ub}}
+\newcommand\kb{k_{b}}
+\newcommand\ko{k_{dis}}
+
+\begin{itemize}
+\item $\tbb$: Time in bothbound per step
+\item $\tob$: Time in onebound per step
+\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+\end{itemize}
+
+$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
+
+\begin{align*}
+  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  \tbb &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tob &= \tstep-\tbb\\
+  &= \tstep - \frac{\tstep\tbb}{\tstep-\tbb}\\
+  &= \frac{\left(\tstep-\tbb\right)\tstep\tbb}{\tstep-\tbb}\\
+  &= \frac{\tstep\left(\tstep-\tbb\right) - \tstep\tbb}{\tstep-\tbb}\\
+  &= \frac{\tstep^2}{\tstep-\tbb}\\
+\end{align*}
+
+Thus, by the above equations and using data from (put right paper here), values for $\tbb$ and $\tob$ can be found:
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| c | c | c | c | c | c |}
+    \hline
+    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    100nm/s & 8nm & 0.08 & 3s & 0.08 & 0.002 \\ \hline
+  \end{tabular}
+  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
+  \label{table:parameter-table}
+\end{figure}
+
+Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATP concentration.\\
+
 %% \textit{Add in a plot of the binding rate fitting search}
+
+\paragraph{Fitting rate constants by simulation}
+\textit{Add in a plot of the binding rate fitting search}
+
+\subsubsection{Fitting spring constants}
+\paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
+\paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
+\paragraph{Fitting rate constants by simulation}
 

### 2017-02-05 thesis_stuff/thesis_stuff.tex
Thesis: Add a little bit of new dynein stepping behavior stuff.
Thesis: Apparently 1mM ATP is a good estimate for in vivo conditions, so Weihong's stepping conditions are what we want.

@@
 \section{Papers}
-
 \subsection{A Simple Theoretical Model Explains Dynein’s Response to Load}
@@
 Could be another good place to get angles for pre-stroke, since 3VKH is post-stroke.\\
+
+\subsection{Single-Molecule Analysis of Dynein processivity and Stepping Behavior}
+2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.
+
+Cool asside: Dynein can be dissociated from microtubules by adding 5mM ATP. This makes sense, since unbinding rate is proportional to ATP concentration.\\
+
+Report a velocity of $85\pm30$ nm/s. Run length of $1.9\pm0.2\mu m$. Measurements done at $1mM ATP$.\\
+
+Required for walking: two motor domains, but not cargo binding or associated chains.\\
+
+Step length assay conducted at $4 \mu M$ ATP, roughly three orders of magnitude less than \textit{in vivo} ATP concentration.\\
+
+Head steps are roughly 8nm, but motor movements per step are 0 for nonmoving and 16-18 for moving motor. This means that our average step size should be about 16nm.\\
+
+Dwell time: probably the average time a domain is bound to the MT?
+IE the total step time?
+Although perhaps they only measure dwell times when they are especially long, since the average looks to be around 2s, or ten dynein steps.\\
+
+Stepping rate of 0.13 per second per $\mu M$ ATP. Ten steps per second, consistent with velocity.\\
+
+Forward stepping probability: 0.8\\
+
+Propose the original ``alternate shuffling''/''hand-over-hand'' mechanism, where each head moves past the other, and the tail/centroid moves a half of each motor domain's movement.\\
+
+\subsection{ATP concentration papers}
+\paragraph{The Contents of Adenine Nucleotides, Phsphagens and some Glycolytic Intermediates in Resting Muscles from Vertebrates and Invertebrates -- 1975}
+
+Found the following:
+
+\begin{center}
+  \begin{tabular}{| l | l |}
+    \hline
+    Organism & ATP\\ \hline
+    Locust flight muscle & 5.8mM\\ \hline
+    Rosechafer flight muscle & 8.5mM\\ \hline
+    Dogfish white muscle & 4.18mM\\ \hline
+    Lab rat thigh & 6.23mM\\ \hline
+    Lab rat kidney & 1.71mM\\ \hline
+  \end{tabular}
+\end{center}
+
+\paragraph{Diversity in ATP concentrations in a single bacterial cell population revealed b quantitate single-cell imaging}
+
+Report $1.54\pm1.22$ mM\\
+
+\paragraph{Bionumbers: http://bionumbers.hms.harvard.edu/search.aspx?log=y&task=searchbytrmorg&trm=atp+concentration&org=}
+
+Growing E. coli: 9.6 mM\\
+human blood cell: 1.61 mM\\
+Maize: 0.5-1.2 mM\\
 
@@
 
+Head moves half as fast as either motor, suggesting motors move every other step, tail moves each step.\\
+
 It's potentially important to note the dynein species used, though probably not since Weihong didn't mention it much in the paper.\\
+
+\subsection{}
 

### 2017-02-05 thesis/latex/thesis.tex
Thesis: add updated calculation for step time, bb/ob time.

@@
 \subsubsection{Microtubule un/rebinding}
+\subsubsection{Domain movement}
+Dynein domains have been shown to move in an alternating fashion, with motor domains moving twice the distance of head domains. This indicates an alternate shuffling-type movement.\\
+
+Flesh this out? Make a table of lots of different experiments and what they indicate?\\
+
 \subsubsection{Conformation change of motor (``priming stroke'')}
@@
     T & [ATP] \\ \hline
-    310.15 K & $1.54*10^{-3}$ M \cite{cellular-atp}\\ \hline
+    310.15 K & $1mM$\\ \hline
   \end{tabular}
@@
   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  \tbb &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
   \tob &= \tstep-\tbb\\
-  &= \tstep - \frac{\tstep\tbb}{\tstep-\tbb}\\
-  &= \frac{\left(\tstep-\tbb\right)\tstep\tbb}{\tstep-\tbb}\\
-  &= \frac{\tstep\left(\tstep-\tbb\right) - \tstep\tbb}{\tstep-\tbb}\\
-  &= \frac{\tstep^2}{\tstep-\tbb}\\
+  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
+  &= \frac{\tstep^2}{\tstep+\tproc}\\
 \end{align*}
 
-Thus, by the above equations and using data from (put right paper here), values for $\tbb$ and $\tob$ can be found:
+Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
 
@@
     Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    100nm/s & 8nm & 0.08 & 3s & 0.08 & 0.002 \\ \hline
+    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
   \end{tabular}
@@
 \end{figure}
-
-Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATP concentration.\\
 

### 2017-02-07 thesis/latex/thesis.tex
Thesis: Add another paper to thesis_stuff.tex.

--- 2017-02-04 thesis/latex/thesis.tex
@@
 \section{Chapter: Introduction}
-Begin with a paper-like introduction which talks about:
-
-\begin{itemize}
-\item How dynein is a structure which turns chemical energy into motion
-\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
-\item How it's weird that a cellular structure can generate directed motion
-\item Other cool stuff - make dynein mysterious and cool.
-\end{itemize}
+%% Begin with a paper-like introduction which talks about:
+
+%% \begin{itemize}
+%% \item How dynein is a structure which turns chemical energy into motion
+%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
+%% \item How it's weird that a cellular structure can generate directed motion
+%% \item Other cool stuff - make dynein mysterious and cool.
+%% \end{itemize}
 
@@
 This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\
-
-\subsubsection{Glossary}
-\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate.
-This reaction is used to power many energy-requiring mechanisms within the cell.
-This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
-\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.\\
 
@@
 Microtubule binding domains (MTBDs) allow dynein to bind to the microtubule.
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
-%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
-%%   \label{dynein-artist-rendition-2}
-%% \end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
   \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
@@
 \subsubsection{Microtubule un/rebinding}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
+  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
+  \label{dynein-artist-rendition-2}
+\end{figure}
+
 \subsubsection{Conformation change of motor (``priming stroke'')}
@@
 
-\section{Chapter: Methods}
-
+\section{Chapter: Theory}
 \subsection{Dynein Models}
@@
 
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
-%%   \caption{Spatial representation of onebound model.}
-%%   \label{ob_fig}
-%% \end{figure}
-
-TODO: make onebound model figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
+  \caption{Spatial representation of onebound model.}
+  \label{ob_fig}
+\end{figure}
+
+TODO: make figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\
 
@@
 \begin{align}
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
-\end{align}
-
-\begin{align}
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
+  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} &= \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
+  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
+  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
+  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
+\end{align}
+
+\begin{align}
+  L_s\cos(\theta_{bb})\dot{\theta}_{bm} &= \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
+  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
+  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
+  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
 \end{align}
@@
 
+\section{Chapter: Methods}
+This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\
+
 \subsection{Verifying the model}
@@
 \end{figure}
-
-%% \subsection{Data collection}
-%% Time evolution of the system has the potential to create a huge amount of data, so care has to be taken to only collect what is necessary.
-For the purposes of testing stepping behavior of the model the geometry and per-domain forces and energies can be safely ignored.
-All that is needed to determine model fitness is the size and duration of each step.\\
-
-%% \subsubsection{Stepping data output and calculation}
-%% A step is defined as a complete cycle of
-
-%% \subsubsection{Simulation running via SLURM}
 
@@
 
-Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATP concentration.\\
-
-%% \textit{Add in a plot of the binding rate fitting search}
+Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATp concentration.\\
 
@@
 
-%% \subsubsection{Fitting spring constants}
-%% \paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
-%% \paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
-%% \paragraph{Fitting rate constants by simulation}
-
-%% \subsubsection{Finding parameters from PyMol}
-
-%% \subsubsection{Finding the right timestep}
+\subsubsection{Finding parameters from PyMol}
+
+\subsubsection{Finding the right timestep}
+
+\subsection{Data collection}
+
+\subsubsection{Outputting positions, step locations}
+\subsubsection{Reconstructing steps from step locations}
+\subsubsection{Job management}
 
@@
 \section{Appendix}
+
+\subsubsection{Glossary}
+\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate.
+This reaction is used to power many energy-requiring mechanisms within the cell.
+This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
+\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.\\
 
@@
 
-%% $\dot{\Theta}_{bb}$ =
-%% {\tiny
-%% ( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% } \break
-
-%% $\dot{\Theta}_{bm}$ =
-%% {\tiny
-%%   (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% }\break
-
-%% $\dot{\Theta}_{um}$ =
-%% {\tiny
-%%   ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }\break
-
-%% $\dot{\Theta}_{ub}$ =
-%% {\tiny
-%%   ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }
-
-%% \subsubsection{Bothbound equations}
-%% \label{bothbound-motion-equations}
-%% The following are the full motion equations used to time evolve the bothbound model:
-
-%% \begin{center}
-%%   \begin{minipage}{0.3\textwidth}
-%%     \begin{align*}
-%%       a &= \frac{-dXnm}{dLn}\\
-%%        b &= \frac{-dXnm}{dLf}\\
-%%        c &= -(x_{nm} - x_{nb}) / \gamma_m\\
-%%        d &= (x_t - x_{nm}) / \gamma_m\\
-%%        e &= \frac{-dXt}{dLn}\\
-%%        f &= \frac{-dXt}{dLf}\\
-%%        g &= -(x_t - x_{nm}) / \gamma_t\\
-%%        h &= (x_{fm} - x_t) / \gamma_t\\
-%%        i &= \frac{-dXfm}{dLn}\\
-%%        j &= \frac{-dXfm}{dLf}\\
-%%        k &= -(x_{fm} - x_t) / \gamma_m\\
-%%        l &= (x_{fb} - x_{fm}) / \gamma_m\\
-%%     \end{align*}
-%%   \end{minipage}
-%%   \begin{minipage}{0.3\textwidth}
-%%     \begin{align*}
-%%        m &= \frac{-dYnm}{dLn}\\
-%%        n &= \frac{-dYnm}{dLf}\\
-%%        p &= -(y_{nm} - y_{nb}) / \gamma_m\\
-%%        q &= (y_t - y_{nm}) / \gamma_m\\
-%%        r &= \frac{-dYt}{dLn}\\
-%%        s &= \frac{-dYt}{dLf}\\
-%%        t &= -(y_t - y_{nm}) / \gamma_t\\
-%%        u &= (y_{fm} - y_t) / \gamma_t\\
-%%        v &= \frac{-dYfm}{dLn}\\
-%%        w &= \frac{-dYfm}{dLf}\\
-%%        x &= -(y_{fm} - y_t) / \gamma_m\\
-%%        y &= (y_{fb} - y_{fm}) / \gamma_m
-%%     \end{align*}
-%%   \end{minipage}
-%% \end{center}
-
-%% Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
-
-%% $\dot{Ln}$ =
-%% {\tiny
-%%     (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
-%%      d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
-%%      c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
-%%      c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
-%%      c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
-%%      d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
-%%      c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
-%%      g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
-%%      d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
-%%      d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
-%%      c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
-%%      b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
-%%      c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
-%%      d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }\break
-
-%% $\dot{Lf}$ =
-%% {\tiny
-%%     (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
-%%      d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
-%%      c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
-%%      c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
-%%      c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
-%%      d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
-%%      c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
-%%      g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
-%%      d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
-%%      d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
-%%      c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
-%%      a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
-%%      c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
-%%      d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }
+$\dot{\Theta}_{bb}$ =
+{\tiny
+( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
+} \break
+
+$\dot{\Theta}_{bm}$ =
+{\tiny
+  (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
+}\break
+
+$\dot{\Theta}_{um}$ =
+{\tiny
+  ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
+}\break
+
+$\dot{\Theta}_{ub}$ =
+{\tiny
+  ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
+}
+
+\subsubsection{Bothbound equations}
+\label{bothbound-motion-equations}
+The following are the full motion equations used to time evolve the bothbound model:
+
+\begin{center}
+  \begin{minipage}{0.3\textwidth}
+    \begin{align*}
+      a &= \frac{-dXnm}{dLn}\\
+       b &= \frac{-dXnm}{dLf}\\
+       c &= -(x_{nm} - x_{nb}) / \gamma_m\\
+       d &= (x_t - x_{nm}) / \gamma_m\\
+       e &= \frac{-dXt}{dLn}\\
+       f &= \frac{-dXt}{dLf}\\
+       g &= -(x_t - x_{nm}) / \gamma_t\\
+       h &= (x_{fm} - x_t) / \gamma_t\\
+       i &= \frac{-dXfm}{dLn}\\
+       j &= \frac{-dXfm}{dLf}\\
+       k &= -(x_{fm} - x_t) / \gamma_m\\
+       l &= (x_{fb} - x_{fm}) / \gamma_m\\
+    \end{align*}
+  \end{minipage}
+  \begin{minipage}{0.3\textwidth}
+    \begin{align*}
+       m &= \frac{-dYnm}{dLn}\\
+       n &= \frac{-dYnm}{dLf}\\
+       p &= -(y_{nm} - y_{nb}) / \gamma_m\\
+       q &= (y_t - y_{nm}) / \gamma_m\\
+       r &= \frac{-dYt}{dLn}\\
+       s &= \frac{-dYt}{dLf}\\
+       t &= -(y_t - y_{nm}) / \gamma_t\\
+       u &= (y_{fm} - y_t) / \gamma_t\\
+       v &= \frac{-dYfm}{dLn}\\
+       w &= \frac{-dYfm}{dLf}\\
+       x &= -(y_{fm} - y_t) / \gamma_m\\
+       y &= (y_{fb} - y_{fm}) / \gamma_m
+    \end{align*}
+  \end{minipage}
+\end{center}
+
+Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
+
+$\dot{Ln}$ =
+{\tiny
+    (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
+     d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
+     c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
+     c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
+     c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
+     d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
+     c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
+     g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
+     d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
+     d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
+     c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
+     b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
+     c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
+     d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
+     (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
+     c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
+     d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
+     c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
+     c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
+     c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
+     c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
+     c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
+     c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
+     d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
+     c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
+     b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
+     c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
+     d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
+}\break
+
+$\dot{Lf}$ =
+{\tiny
+    (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
+     d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
+     c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
+     c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
+     c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
+     d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
+     c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
+     g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
+     d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
+     d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
+     c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
+     a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
+     c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
+     d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
+     (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
+     c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
+     d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
+     c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
+     c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
+     c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
+     c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
+     c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
+     c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
+     d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
+     c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
+     b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
+     c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
+     d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
+}
 
 \section{Questions for Tate/Nicole}
-%%\begin{itemize}
-%% \item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
-%% \item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
-%% \item When is a fact ``common knowledge'' enough that it doesn't need a citation?
-%% \item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
-%% \item Is 25 pages too long for a thesis? What makes a thesis too long?
-%% \item What details belong in a thesis, and which are too much?
+\begin{itemize}
+\item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
+\item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
+\item When is a fact ``common knowledge'' enough that it doesn't need a citation?
+\item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
+\item Is 25 pages too long for a thesis? What makes a thesis too long?
+\item What details belong in a thesis, and which are too much?
 ex going in-depth on what tests do, describing how we came up with guess numbers for parameter hunt, describing function of dynein in the cell, showing why motor proteins are necessary.
-%% \item Supplemental info?
-%%\end{itemize}
+\item Supplemental info?
+\end{itemize}
 

### 2017-02-07 thesis_stuff/thesis_stuff.tex
fix typo in latex file
Thesis: Add another paper to thesis_stuff.tex.

--- 2017-01-28 thesis_stuff/thesis_stuff.tex
@@
 a single salt bridge contributes about 16 kJ/mol to stabilizing a protein. We can use these numbers as estimates of the binding energy of the motor.\\
+
+\subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
+Discuss how other work has shown that MT affinity is controlled by registry.
+They do this study in vivo, and show that there is a coupling between ATPase activity and MT binding which is destroyed by locking the coiled coils into registries.
+
+\textbf{Key findings}
+\begin{itemize}
+\item CC being unlocked is necessary for MT-affinity sensitivity to ATP, showing ATP-state influences MT-affinity
+\item high MT affinity causes high ATPase rate, low MT affinity causes low ATPase rate (presumably bc ATP cannot bind)
+\end{itemize}
+
+WT: No ATP -> strong binding, ATP: weak binding\\
+Locked in a register: ATP insensitivity\\
+MT increases ATPase rate 25x\\
+MT doesn't increase locked-register ATPase rate\\
+(Thus unlocked registers are necessary for ATPase/MT-binding coupling)\\
+
+They then did a FRET study to show that locking a registry \textit{induces} a change in linker conformation, pre/poststroke.\\
+
+They provide the following explanation of dynein mechanochemical cycle:
+
+\begin{itemize}
+\item (apo): strong MT-binding, in $\alpha$ conformation
+\item (ATP binding): causes a shift towards the $\Beta+$ conformation, causing MT dissociation by lowering affinity
+\item (before ATP hydrolysis): dynein performs prestroke, \textit{then} hydrolyzes ATP
+\item (during Phosphate or ADP release): MTBD rebinds to MT, returns to $\alpha$ registry, increasing the rate of product release, increasing MT affiniy, AND causing the powerstroke
+\item (full release): turns back to apo dynein
+\end{itemize}
+
+ATPase and MT cycles are interestingly coupled.
+
+\textbf{ATPase cycle}
+\begin{itemize}
+\item apo $\rightarrow$ ATP: this is somehow influenced by MT state
+\item ATP $\rightarrow$ ADP+Pi: This happens after prestroke, somehow coupled to it or no?
+\item ADP+Pi $\rightarrow$ ADP: This ejection (or the ADP ejection) is sped up by MTBD rebinding
+\item ADP $\rightarrow$ apo: This ejection doesn't do anything structurally, according to Cianfrocco model
+\end{itemize}
 

### 2017-02-07 thesis/latex/thesis.tex

--- 2017-02-05 thesis/latex/thesis.tex
@@
 \subsubsection{Microtubule un/rebinding}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
+  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
+  \label{dynein-artist-rendition-2}
+\end{figure}
+
 \subsubsection{Domain movement}

### 2017-02-08 thesis_stuff/thesis_stuff.tex

@@
 Could be another good place to get angles for pre-stroke, since 3VKH is post-stroke.\\
+
+\subsection{Single-Molecule Analysis of Dynein processivity and Stepping Behavior}
+2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.
+
+Cool asside: Dynein can be dissociated from microtubules by adding 5mM ATP. This makes sense, since unbinding rate is proportional to ATP concentration.\\
+
+Report a velocity of $85\pm30$ nm/s. Run length of $1.9\pm0.2\mu m$. Measurements done at $1mM ATP$.\\
+
+Required for walking: two motor domains, but not cargo binding or associated chains.\\
+
+Step length assay conducted at $4 \mu M$ ATP, roughly three orders of magnitude less than \textit{in vivo} ATP concentration.\\
+
+Head steps are roughly 8nm, but motor movements per step are 0 for nonmoving and 16-18 for moving motor. This means that our average step size should be about 16nm.\\
+
+Dwell time: probably the average time a domain is bound to the MT?
+IE the total step time?
+Although perhaps they only measure dwell times when they are especially long, since the average looks to be around 2s, or ten dynein steps.\\
+
+Stepping rate of 0.13 per second per $\mu M$ ATP. Ten steps per second, consistent with velocity.\\
+
+Forward stepping probability: 0.8\\
+
+Propose the original ``alternate shuffling''/''hand-over-hand'' mechanism, where each head moves past the other, and the tail/centroid moves a half of each motor domain's movement.\\
+
+\subsection{ATP concentration papers}
+\paragraph{The Contents of Adenine Nucleotides, Phsphagens and some Glycolytic Intermediates in Resting Muscles from Vertebrates and Invertebrates -- 1975}
+
+Found the following:
+
+\begin{center}
+  \begin{tabular}{| l | l |}
+    \hline
+    Organism & ATP\\ \hline
+    Locust flight muscle & 5.8mM\\ \hline
+    Rosechafer flight muscle & 8.5mM\\ \hline
+    Dogfish white muscle & 4.18mM\\ \hline
+    Lab rat thigh & 6.23mM\\ \hline
+    Lab rat kidney & 1.71mM\\ \hline
+  \end{tabular}
+\end{center}
+
+\paragraph{Diversity in ATP concentrations in a single bacterial cell population revealed b quantitate single-cell imaging}
+
+Report $1.54\pm1.22$ mM\\
+
+\paragraph{Bionumbers: http://bionumbers.hms.harvard.edu/search.aspx?log=y\&task=searchbytrmorg\&trm=atp+concentration\&org=}
+
+Growing E. coli: 9.6 mM\\
+human blood cell: 1.61 mM\\
+Maize: 0.5-1.2 mM\\
 

### 2017-02-08 thesis/latex/thesis.tex
Add feature for printing only onebound states, to debug why they're behaving weird.

@@
 \section{Chapter: Introduction}
+
 %% Begin with a paper-like introduction which talks about:
@@
 \subsubsection{Microtubule un/rebinding}
+Microtubule binding and unbinding play an important role in the dynein mechanochemical cycle.
+The MTBD/stalk system has two conformational states: a high-MT-affinity state where MT binding occurs at a fast rate, and a low-affinity state with a slower binding rate \.
+The MTBD/stalk alternates between these two states as the motor progresses through the mechanochemical cycle
 
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
-  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
+  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}. Is this figure actually useful, or would a diagram be better?}
   \label{dynein-artist-rendition-2}
@@
 		\subsubsection{Sarlah Winch Model}
-		\subsubsection{-x Other models}
-	\subsection{Brownian motion}
-                \subsubsection{Introduction/derivation}
-                \subsubsection{Justification}
-
-\subsection{Simulation}
+		\subsubsection{Other models}
+
+\subsection{Moving forward}
 Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
@@
 
-\subsection{Our model}
+\section{Chapter: Theory}
+\subsection{Model features}
 Talk about what the important parts of the mechanochemical cycle from the introduction are, and how
@@
 the intermediate states don't matter. Talk about rate constants here.
-\subsubsection{Limitations}
-Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information,
-other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into
-account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be
-springy...
-
-Mention the Burgess paper, which says spring constants might change between apo/ADP states.
-
-\paragraph{Euler’s method}
-Show how Euler's method is arrived at, how its error scales, why we use it.
-
-\paragraph{Vs other methods (Runge Kutta, etc)}
-Talk about why our differential equation is most conducive to Euler's method. Euler's is more
-efficient -- is there a way to show how our differential equation is smooth, not jagged?
-
-\paragraph{Gibbs energy of transition}
-Do some stuff with Gibb's here? Why our energies are Gibb's and not internal energy?\\
-
-\section{Chapter: Theory}
-\subsection{Dynein Models}
+
+\subsection{Brownian motion}
+\subsubsection{Introduction/derivation}
+\subsubsection{Justification}
+
+\subsection{Mathematical models}
 In order to simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state.
@@
 
+\paragraph{Euler’s method}
+Show how Euler's method is arrived at, how its error scales, why we use it.
+
+\paragraph{Vs other methods (Runge Kutta, etc)}
+Talk about why our differential equation is most conducive to Euler's method. Euler's is more
+efficient -- is there a way to show how our differential equation is smooth, not jagged?
+
 \textit{todo: come up with a better word than ``model'' to describe the state of the system at any time}
@@
 
-\subsection{Other ways to represent data?}
-
 \section{Chapter: Discussion}
-\subsection{Why our model worked, didn’t work}
-Fill this out over winter when you know more.\\
+\subsubsection{Limitations}
+Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information,
+other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into
+account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be
+springy...
+
+Mention the Burgess paper, which says spring constants might change between apo/ADP states.
 \subsection{Future work on this project}

### 2017-02-08 dynein_struct_onebound.cpp

@@ -286,7 +286,7 @@ void Dynein_onebound::update_velocities() {
   }
 
   //******* Checking for sub-MT dynein ********
-  if (get_bmy() < -1e-3 or get_ty() < -1e-3 or get_umy() < -1e-3 or get_uby() < -1e-3) {
+  if (get_bmy() < -1e-3 or get_ty() < -1e-3 or get_umy() < -1e-3) {
     printf("A domain is under the MT! bmy, ty, umy, uby: : %g, %g, %g, %g\n", get_bmy(), get_ty(), get_umy(), get_uby());
     if (am_only_writing_on_crash) on_crash_write_movie_buffer();
     exit(1);

### 2017-02-15 thesis/latex/thesis.tex
Thesis: microcommit.
Thesis: Add work to Theory.

@@
 %% \end{itemize}
+
+Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
 
@@
 \subsection{Model features}
-Talk about what the important parts of the mechanochemical cycle from the introduction are, and how
-we take those and model them.\\
-\subsubsection{Rigid point model}
-Talk about two things: reducing bulky circular domains to points (is this the same as unified atom
-model?) with a certain drag constant based on radius, and acting like the domains are rigid in
-distance from each other. Talk about why this is valid (is it? it's an assumption, David may know
-more).
-\subsubsection{Harmonic energies}
-How we're modeling the complicated folding and adjusting of a massive protein as a harmonic
-oscillator. Why this is valid. Also other approaches...what else could we have modelled it as?
+The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior.
+To test this hypothesis, these features are put into a model and simulated.
+The features are as follows:
+
+\begin{itemize}
+\item Dynein is a collection of spherical domains joined together by massless rods
+\item These rods are rigid
+\item Each joint in the motor feels a spring force about some equilibrium joint angle
+\item Dynein can be in two states: onebound and bothbound
+\item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
+\item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
+\item Transitions between the two states are based solely on spring energies between the two models
+\item Brownian dynamics describes the behavior of the domains in time
+\item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
+\item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
+\end{itemize}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/onebound-model}
+  \caption{}
+  \label{fig:model-intro}
+\end{figure}
+
+\subsubsection{Spherical domains connected by massless rods}
+A key feature of the model is that each domain of the protein (two feet, twp motors and a tail) is treated as a sphere.
+Each sphere is connected to one or two other spheres, as shown in Figure (\ref{fig:model-intro}).
+This simplification is made to make the math easier and allow a simple definition of dynein's conformation.\\
+
+One quickly notices by glancing at Figure (\ref{fig:crystal-structure-model-imposed}), a visualization of actual dynein, that modelling the tail and feet domains as spheres is a stretch.
+The main point of the simplification is not to capture the shape of dynein, but the conformation.
+It is undefined to discuss the distance between the two motor domains in real dynein, because the motors are made up of hundreds of amino acids, and the average inter-domain distance between amino acids is comparable to the intra-domain distance.
+However it is very easy to describe the difference between two spheres.\\
+
+Each sphere has an associated drag factor $\gamma$, which describes the resistance it feels to motion.
+This drag factor is calculated based on the radius $R$ of the spheres, and is given by Stoke's Law:
+
+\begin{equation}
+  \gamma = 6\pi\nu R
+\end{equation}
+
+Thus R becomes a parameter input to the model.\\
+
+\subsubsection{Rigid rods}
+The model assumes connected domains are rigidly attached to one another by rods.
+This assumption makes the math easier, and is not necessarily based on biology.
+One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \ref{burgess-paper}.
+However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \ref{myosin-cc-elasticity}.
+
+\subsubsection{Angular springs}
+Each domain has a spring constant, $c_b, c_m$ or $c_t$ for binding, motor or tail, which decides the energy associated with that domain's angle. For example, the tail domain's energy is given by
+
+\begin{equation}
+  \Delta G_t = \frac12c_t\left(\theta_t - \theta_t^{eq}\right)^2
+\end{equation}
+
 \subsubsection{Two-state model}
+The model assumes MT-bound dynein can assume one of two states: one where both MTBDs are bound, and one where only one MTBD is bound to the MT.
+The states are also differentiated by different motor equilibrium angles and different transition rates.
+
 The mechanochemical cycle has eight states. We choose two as representative because \textbf{a.)}
@@
 
-\subsection{Brownian motion}
-\subsubsection{Introduction/derivation}
-\subsubsection{Justification}
+\subsubection{Onebound state}
+
+\subsubsection{Bothbound state}
+
+\subsubsection{Transitioning between states}
+
+\subsubsection{Brownian dynamics}
+
+\subsubsection{$\alpha-\beta$ binding unnecessary}
+
+\subsubsection{2D model}
 

### 2017-02-17 thesis/latex/thesis.tex

@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/onebound-model}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
   \caption{}
@@
 The model assumes MT-bound dynein can assume one of two states: one where both MTBDs are bound, and one where only one MTBD is bound to the MT.
-The states are also differentiated by different motor equilibrium angles and different transition rates.
-
-The mechanochemical cycle has eight states. We choose two as representative because \textbf{a.)}
-many of the states are identically conformationally or \textbf{b.)} the transitions happen so fast
-the intermediate states don't matter. Talk about rate constants here.
-
-\subsubection{Onebound state}
-
-\subsubsection{Bothbound state}
+These states are also differentiated by different motor equilibrium angles, $\Theta_{m}^{bb}$ and $\Theta_{m}^{ob}$, and different transition rates.
+Biological dynein likely passes through a series of permutations of nucleotide, MT affinity and conformational states as it travels through its mechanochemical cycle.
+This model makes the assumption that the mechanochemical cycle can be broken down into a cycle of prestroking to move the unbound foot forward, brownian walking to place the foot on the microtubule, then powerstroking to move the other domains forward.\\
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
+  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
+  \caption{Representations of onebound (left) and bothbound (right) dynein models.}
+  \label{ob_fig}
+\end{figure}
 
 \subsubsection{Transitioning between states}
+The model transitions between states with a probability dependent on both the energy difference between the two states and the physical separation between the MT and binding MTBD.
+Energy difference between states A and B is given by:
+
+\begin{equation}
+  \Delta G_{A\rightarrow B} = \sum_{i=0...N_B}^{B} \frac{1}{2}c_i\left(\theta_i-\Theta_i^B\right)^2 - \sum_{j=0...N_A}^{A} \frac{1}{2}c_j\left(\theta_j-\Theta_j^A\right)^2
+\end{equation}
+
+Transition energies are used to calculate transition rates, as given by the Arhennius equation $k=Ae^{-\beta\Delta G}$, where $\beta = (k_BT)^{-1}$.
+In this equation $\Delta G$ is the total energy of transition between states and A is a constant known as the preexponential factor with units of $s^{-1}$.\\
+
+\begin{equation}
+  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
+\end{equation}
+
+where $\Delta G_{conf}$ is the change in spring energy in going from bothbound to onebound and $\Delta G_{bind}$ is the energy gained from binding to the microtubule.
+Because binding energy for the MT-MTBD complex is hard to find, the following substitution is made:
+
+\begin{equation}
+  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Be^{\frac{-\Delta G_{conf}}{k_BT}}
+\end{equation}
+
+Thus $B$ becomes a parameter of the model.\\
 
 \subsubsection{Brownian dynamics}
+The Brownian dynamics equation describes the motion of high-drag objects which spend most of their time at terminal velocity, and is given by:
+
+\begin{equation}
+  \dot{x} = \frac{1}{\gamma}\left(F_{net} + R\right)
+\end{equation}
+
+where $\gamma$ is the drag constant of the object and R is a random Brownian force which describes the effects of water particle collision.
+R a Gaussian-sampled zero-centered force with variance given by:
+
+\begin{equation}
+  R_{\sigma^2} = \sqrt{\frac{2*kb*T*\gamma}{dt}}
+\end{equation}
+
+Dynein is in the range of objects which BD describes well. (citation needed)
 
 \subsubsection{$\alpha-\beta$ binding unnecessary}
+Dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
+By this, all dynein steps should be multiples of $8$nm.
+This model ignores this requirement and allows stepping to occur at any length.
+This assumption is not based on biology, but to simplify the model.
+The assumption is that \textit{in vivo} dynein is tuned to take 8nm steps based on its size and stepping angle, and doesn't search along the MT for a binding site.\\
 
 \subsubsection{2D model}
+The coordinate system for this model is two-dimensional.
+Thus interactions between the two motors and MTBDs are ignored.
+This assumption is made to simplify the model.
+Other dynein models, like the winch model \ref{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions.
+It is not clear why such forces are necessary for dynein motion, and so they are omitted.\\
+
+Side stepping of dynein is ignored by this model.
+Stepping perpendicular to the MT occurs in dynein \cite{weihongppaer}, as shown in Figure \ref{fig:weihong-side-stepping}.
+This model assumes it is a symptom, and not an influencer of, of dynein's forward-backward stepping mechanism.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/weihong-side-stepping}
+  \caption{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}. 0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right. Modified.}
+  \label{fig:weihong-side-stepping}
+\end{figure}
 
@@
 \label{sec:transitioning-states}
-Onebound and bothbound models transition between each other based on rate constants $k_b$, the binding constant, and $k_{ub}$, the unbinding constant, respectively.
-These values are calculated using the Arrhenius equation, and are given as:
-
-\begin{equation}
-  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
-\end{equation}
-
-where $\Delta G_{conf}$ is the change in spring energy in going from bothbound to onebound, $\Delta G_{bind}$ is the energy gained from binding to the microtubule, and A is a constant known as the preexponential factor with units of $s^{-1}$.\\
-
 Transitions from one state to another are accomplished by calculating the probability of a transition at a given timestep, given by $P_{ob\rightarrow bb} = k_bdt$.

### 2017-02-19 thesis/latex/thesis.tex
Add beginnings of Intro-2 section.

@@
 
-Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
+%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
 
@@
 
+\section{Chapter: Introduction II}
+
+\subsection{Dynein Stepping Background}
+Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
+The full mechanism is not known, but results of such experiments suggest a certain vague picture of how dynein generates motion.\\
+
+\subsubsection{Different conformational states}
+Dynein is known to occupy multiple discrete conformational states depending on its environment.
+In particular, the concentration of ATP and microtubules is known to alter the shape dynein takes on.
+A FRET (fluorescence resonance energy transfer) study attached fluorophores to dynein's motor and tail and measured the average distance between the two \cite{FRETstatepaper}.
+It was found that average distance increased or decreased depending on the nucleotide bound to dynein, indicating the motor takes on different conformations for different bound nucleotides.
+Dynein unbound to nucleotide, or frozen in ATP or ADP-bound states, had a similar tail-motor distance.
+However, when the motor was stuck in an ADP-Pi state, with ATP hydrolyzed but phosphate not yet released, the tail-motor distance was increased.
+This suggests that dynein starts its cycle with no nucleotide, binds ATP, hydrolyzes ATP, enters the ADP-Pi state and changes conformation to a far tail-motor distance, then releases phosphate, moves back to its original close tail-motor conformation, then ejects ADP and starts over.\\
+
 \section{Chapter: Theory}

### 2017-02-19 thesis/latex/thesis.tex
Thesis: clean up.

--- 2017-02-17 thesis/latex/thesis.tex
@@
   \newcommand\transition{\textcolor{green}{transition?}}
-  \begin{tabular}{rll}
-    \bothbound &
-    1 & \begin{minipage}{5in}
-      Bound to microtubule and waiting for ATP to arrive.  The
-      conformation is ``post-powerstroke''.
-    \end{minipage}\vspace{0.5em}\\
-    \bothbound &
-    2 & \begin{minipage}{5in}
-      ATP has bound to the motor at AAA1, but nothing else has changed.
-    \end{minipage}\vspace{0.5em}\\
-    \transition &
-    3 & \begin{minipage}{5in}
-      ``The ring has closed'' in the motor, whatever that means.
-    \end{minipage}\vspace{0.5em}\\
-    \bothbound &
-    4 & \begin{minipage}{5in}
-      The affinity to the microtubule is dropped, so it is likely to pop off soon.
-    \end{minipage}\vspace{0.5em}\\
-    \onebound &
-    5 & \begin{minipage}{5in} It has popped off of the microtubule!
-      Onebound! The equilibrium angle is also changed.  The ATP has
-      been hydrolized, but the phosphate is still bound to the motor.
-      ``Priming stroke?''
-    \end{minipage}\vspace{0.5em}\\
-    \onebound &
-    6 & \begin{minipage}{5in} It is now bound to the microtubule, but
-      with low affinity, and without any loss of phosphate. Question:
-      does this happen many times? If so it may still be onebound.
-      Otherwise it is probably bothbound.
-    \end{minipage}\vspace{0.5em}\\
-    \bothbound &
-    7 & \begin{minipage}{5in}
-      Now it is seriously bound to the microtubule, and the motor
-      domain has changed conformation.  This is now ``high affinity.''
-    \end{minipage}\vspace{0.5em}\\
-    \bothbound &
-    8 & \begin{minipage}{5in}
-      Phosphate has been released, and our equilibrium angles have
-      been changed.  This is the ``power stroke.''
-    \end{minipage}\vspace{0.5em}\\
-    \bothbound &
-    1 & \begin{minipage}{5in}
-      The ADP has been released from the motor domain, so it can now
-      bind ATP.  Still ``high affinity,'' and still in the
-      ``power-stroke'' conformation.
-    \end{minipage}\vspace{0.5em}\\
-    \bothbound &
-    9 & \begin{minipage}{5in}
-      While stuck in this ``normal bound'' state, another site on the
-      motor AAA3 can lose its ADP, which leaves the motor in a state
-      where it cannot directly move on to step 2 (until after
-      reversing this).  Controversial?
-    \end{minipage}
-  \end{tabular}
+  %% \begin{tabular}{rll}
+  %%   \bothbound &
+  %%   1 & \begin{minipage}{5in}
+  %%     Bound to microtubule and waiting for ATP to arrive.  The
+  %%     conformation is ``post-powerstroke''.
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \bothbound &
+  %%   2 & \begin{minipage}{5in}
+  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \transition &
+  %%   3 & \begin{minipage}{5in}
+  %%     ``The ring has closed'' in the motor, whatever that means.
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \bothbound &
+  %%   4 & \begin{minipage}{5in}
+  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \onebound &
+  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
+  %%     Onebound! The equilibrium angle is also changed.  The ATP has
+  %%     been hydrolized, but the phosphate is still bound to the motor.
+  %%     ``Priming stroke?''
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \onebound &
+  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
+  %%     with low affinity, and without any loss of phosphate. Question:
+  %%     does this happen many times? If so it may still be onebound.
+  %%     Otherwise it is probably bothbound.
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \bothbound &
+  %%   7 & \begin{minipage}{5in}
+  %%     Now it is seriously bound to the microtubule, and the motor
+  %%     domain has changed conformation.  This is now ``high affinity.''
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \bothbound &
+  %%   8 & \begin{minipage}{5in}
+  %%     Phosphate has been released, and our equilibrium angles have
+  %%     been changed.  This is the ``power stroke.''
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \bothbound &
+  %%   1 & \begin{minipage}{5in}
+  %%     The ADP has been released from the motor domain, so it can now
+  %%     bind ATP.  Still ``high affinity,'' and still in the
+  %%     ``power-stroke'' conformation.
+  %%   \end{minipage}\vspace{0.5em}\\
+  %%   \bothbound &
+  %%   9 & \begin{minipage}{5in}
+  %%     While stuck in this ``normal bound'' state, another site on the
+  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
+  %%     where it cannot directly move on to step 2 (until after
+  %%     reversing this).  Controversial?
+  %%   \end{minipage}
+  %% \end{tabular}
   \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}

### 2017-02-19 thesis_stuff/thesis_stuff.tex
Thesis: clean up.

@@
 \subsection{Single-Molecule Analysis of Dynein processivity and Stepping Behavior}
-2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.
+Vale RD\\
+2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.\\
 
@@
 \subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
+Takahide Kon, Kenji Imamula, Anthony J Roberts, Reiko Ohkura, Peter J Knight, I R Gibbons, Stan A Burgess & Kazuo Sutoh\\
 Discuss how other work has shown that MT affinity is controlled by registry.
@@
 \item (apo): strong MT-binding, in $\alpha$ conformation
-\item (ATP binding): causes a shift towards the $\Beta+$ conformation, causing MT dissociation by lowering affinity
+\item (ATP binding): causes a shift towards the $\beta+$ conformation, causing MT dissociation by lowering affinity
 \item (before ATP hydrolysis): dynein performs prestroke, \textit{then} hydrolyzes ATP

### 2017-02-21 thesis/latex/thesis.tex

@@
 
-\subsubsection{Different conformational states}
+\subsubsection{ATP cycle influences conformational state}
 Dynein is known to occupy multiple discrete conformational states depending on its environment.
@@
 This suggests that dynein starts its cycle with no nucleotide, binds ATP, hydrolyzes ATP, enters the ADP-Pi state and changes conformation to a far tail-motor distance, then releases phosphate, moves back to its original close tail-motor conformation, then ejects ADP and starts over.\\
+
+Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the trail \cite{FRETstatepaper} \cite{burgess-paper}.
+Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.\\
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/literature/burgess-dynein-angles}
+  \caption{Cryo-electron microscopy images of dynein in two different nucleotide states.
+Left: dynein frozen in ADP-Pi state.
+Middle: dynein without nucleotide.
+Right: two states superimposed on one another.
+Bottom: cartoons representing how dynein may bind to the MT in either state.
+From \cite{burgess-paper}.}
+  \label{fig:cryo-em-angles}
+\end{figure}
+
+Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}.
+Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.
+This movement might cause a net forward motion of the motor domain.\\
+
+\textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
+
+\subsubsection{Microtubule and nucleotide states are coupled}
+Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
+This site occurs roughly every 8nm, indicating dynein is restricted to step sizes which are multiples of 8nm.\\
+
+The nucleotide state of the motor is not the only determiner of dynein conformation; microtubule binding state has also been shown to influence conformation.
+A study on the MTBD-MT complex indicates the stalk connecting the motor and MTBD can take on two major conformations, depending on whether the MTBD is bound to the MT or not \cite{mt-atp-coupling}.
+The conformation of the stalk has been shown to communicate information between the motor and MTBD.
+In the presence of microtubules, the ATPase rate of the motor is increased 25-fold.
+This indicates the stalk communicates MT-binding state of the MTBD to the motor, increasing its ATP hydrolysis rate.
+The communication happens the other way, as well.
+Treating dynein with ATP causes MT-binding rate to drop 15-fold, indicating ATP-binding at the motor decreases MT-binding rate at the MTBD.\\
+
+In addition to a bidirectional linking between ATPase rate and MT-binding, stalk state has been shown to directly influence motor conformation \cite{mt-atp-coupling}.
+When the stalk is allowed to freely transition between bound and unbound states, the motor can also transition between near and far tail/motor states.
+However, when the stalk is frozen in a particular conformation, the motor loses its transitioning ability.
+This suggests that the conformations of the two systems are tightly linked.\\
+
+\subsubsection{Stepping pattern}
+Several studies have been done on the dynein motor's stepping pattern using selectively-labeled motor domains \cite{reck2006single} \cite{weihongpaper}. These studies suggest that dynein has a
 
@@
 Mention the Burgess paper, which says spring constants might change between apo/ADP states.
+
+Computational limitations: Our project is computational, not experimental.
+Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
+
 \subsection{Future work on this project}

### 2017-02-23 thesis/latex/thesis.tex

@@
 
-\subsection{How does dynein walk?}
-
+\subsection{Dynein Stepping Background}
+Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
+The full mechanism is not known, but results of such experiments suggest a certain vague picture of how dynein generates motion.\\
+
+\subsubsection{ATP cycle influences conformational state}
+Dynein is known to occupy multiple discrete conformational states depending on its environment.
+In particular, the concentration of ATP and microtubules is known to alter the shape dynein takes on.
+A FRET (fluorescence resonance energy transfer) study attached fluorophores to dynein's motor and tail and measured the average distance between the two \cite{FRETstatepaper}.
+It was found that average distance increased or decreased depending on the nucleotide bound to dynein, indicating the motor takes on different conformations for different bound nucleotides.
+Dynein unbound to nucleotide, or frozen in ATP or ADP-bound states, had a similar tail-motor distance.
+However, when the motor was stuck in an ADP-Pi state, with ATP hydrolyzed but phosphate not yet released, the tail-motor distance was increased.
+This suggests that dynein starts its cycle with no nucleotide, binds ATP, hydrolyzes ATP, enters the ADP-Pi state and changes conformation to a far tail-motor distance, then releases phosphate, moves back to its original close tail-motor conformation, then ejects ADP and starts over.\\
+
+Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the trail \cite{FRETstatepaper} \cite{burgess-paper}.
+Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.\\
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures//burgess-dynein-angles}
+  \caption{Cryo-electron microscopy images of dynein in two different nucleotide states.
+Left: dynein frozen in ADP-Pi state.
+Middle: dynein without nucleotide.
+Right: two states superimposed on one another.
+Bottom: cartoons representing how dynein may bind to the MT in either state.
+From \cite{burgess-paper}.}
+  \label{fig:cryo-em-angles}
+\end{figure}
+
+Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}.
+Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.
+This movement might cause a net forward motion of the motor domain.\\
+
+\textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
+
+\subsubsection{Microtubule and nucleotide states are coupled}
+Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
+This site occurs roughly every 8nm, indicating dynein is restricted to step sizes which are multiples of 8nm.\\
+
+The nucleotide state of the motor is not the only determiner of dynein conformation; microtubule binding state has also been shown to influence conformation.
+A study on the MTBD-MT complex indicates the stalk connecting the motor and MTBD can take on two major conformations, depending on whether the MTBD is bound to the MT or not \cite{mt-atp-coupling}.
+The conformation of the stalk has been shown to communicate information between the motor and MTBD.
+In the presence of microtubules, the ATPase rate of the motor is increased 25-fold.
+This indicates the stalk communicates MT-binding state of the MTBD to the motor, increasing its ATP hydrolysis rate.
+The communication happens the other way, as well.
+Treating dynein with ATP causes MT-binding rate to drop 15-fold, indicating ATP-binding at the motor decreases MT-binding rate at the MTBD.\\
+
+In addition to a bidirectional linking between ATPase rate and MT-binding, stalk state has been shown to directly influence motor conformation \cite{mt-atp-coupling}.
+When the stalk is allowed to freely transition between bound and unbound states, the motor can also transition between near and far tail/motor states.
+However, when the stalk is frozen in a particular conformation, the motor loses its transitioning ability.
+This suggests that the conformations of the two systems are tightly linked.\\
+
+\subsubsection{Stepping pattern}
+Several studies have been done on the dynein motor's stepping pattern using selectively-labeled motor domains \cite{reck2006single} \cite{weihongpaper}.
+These studies show dynein's stepping pattern to be stochastic and weakly forward-directed.
+As shown in Figure (\ref{fig:weihong-steps}), dynein takes many backwards steps, and also many steps with components perpendicular to the microtubule.
+This indicates the process dynein uses to generate motion has a stochastic component to it.
+It is likely that the physical states of subcomponents in the motor, and/or the effects of Brownian motion due to water particle collision, play a role in dynein's stepping mechanism.\\
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/weihong-step-size}
+    \caption{Size of steps taken by dynein motor parallel to microtubule. Positive axis corresponds to steps towards the microtubule minus-end. Figure modified from \cite{weihongpaper}.}
+  \end{minipage}
+  \hspace{.2cm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/weihong-off-axis-steps}
+    \caption{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
+  \end{minipage}
+  \label{fig:weihong-steps}
+\end{figure}
+
+\subsection{Dynein models}
+Data presented in the previous sections paints a
+
+\subsubsection{Cianfrocco Model}
 Cianfrocco \textit{et.
@@
 Talk about the Cianfrocco model, but other interpretations?
-
-\textbf{Things which are known about dynein which support the Cianfrocco model}
-\begin{itemize}
-\item AAA1 only ATPase necessary for motility, which is why we don't include the other ATPases in our model \cite{cianfroccoreview}
-\item AAA5 mediates stalk register changes Schmidt H, Zalyte R, Urnavicius L, Carter AP. 2014. Structure of human cytoplasmic dynein-2 primed for
-  its power stroke. Nature 518:435–38
-\item Linker moves as response to AAA1 nucleotide binding Burgess SA, Walker ML, Sakakibara H, Knight PJ, Oiwa K. 2003. Dynein structure and power stroke. Nature
-  421:715–8
-\item Crystal structures with Vanadium-Adp show dynein in the pre-powerstroke state, hinting that ADP-Pi-bound dynein takes on a different conformation than ADP-Pi free dynein
-\end{itemize}
 
@@
 
-\subsubsection{ATP binding / unbinding effects}
-\subsubsection{Microtubule un/rebinding}
-Microtubule binding and unbinding play an important role in the dynein mechanochemical cycle.
-The MTBD/stalk system has two conformational states: a high-MT-affinity state where MT binding occurs at a fast rate, and a low-affinity state with a slower binding rate \.
-The MTBD/stalk alternates between these two states as the motor progresses through the mechanochemical cycle
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
-  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}. Is this figure actually useful, or would a diagram be better?}
-  \label{dynein-artist-rendition-2}
-\end{figure}
-
-\subsubsection{Domain movement}
-Dynein domains have been shown to move in an alternating fashion, with motor domains moving twice the distance of head domains. This indicates an alternate shuffling-type movement.\\
-
-Flesh this out? Make a table of lots of different experiments and what they indicate?\\
-
-\subsubsection{Conformation change of motor (``priming stroke'')}
-A FRET (fluorescent resonance energy transfer) study, which probes the closeness of different labeled domains on a protein, showed that dynein is found in two different major conformations, depending on the nucleotide bound to its AAA1 ATPase site \cite{FRETstatepaper}.
-When no nucleotide, ATP or ADP is bound, the authors label the protein ``state I.'' When ADP-Pi bound, the motor is said to be in ``state II,'' as shown in Fig \ref{nucleotide-state}.
-In addition, motors in the presence of the unhydrolyzable ATP analog were found in state II, indicating the transition from state I to II occurs during ATP binding.
-Similar reasoning shows that the state II to I transition occurs when the protein is ADP bound.
-This allows the authors to create the state diagram shown in Fig \ref{nucleotide-state-diagram}.\\
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/two-state-em-diagram}
-%%   \caption{}
-%%   \label{nuecleotide-state}
-%% \end{figure}
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/nucleotide-state-cycle}
-%%   \caption{}
-%%   \label{nucleotide-state-diagram}
-%% \end{figure}
-
-This single FRET study illustrates how the conformational aspect of the mechanochemical cycle works.
-Dynein begins in state I and binds ATP into its AAA1 ATPase, changing into state II by changing its stalk-tail angle to move the tail outward.
-ATP is then hydrolized into ADP-Pi.
-Pi is then ejected from the AAA1 site, leaving ADP behind.
-This causes the reverse state transition, moving the tail inward.
-When combined with microtubule affinity changes, this primitive model of the dynein cycle could explain how dynein walks.\\
-
-\textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}.
+\subsubsection{Other models}
+If there are other models which conflict with Cianfrocco, here would be a place to put them.\\
+
+\subsection{This work}
+\subsubsection{Our model}
+what we're trying to do with our project
+
+\textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
+It would basically show all events occuring at two times: unbinding or rebinding.}\\
+
+\subsubsection{Goals}
+What we hope to gain by simulating such a model, and what it would contribute to the current literature
+
+%% \textbf{Things which are known about dynein which support the Cianfrocco model}
+%% \begin{itemize}
+%% \item AAA1 only ATPase necessary for motility, which is why we don't include the other ATPases in our model \cite{cianfroccoreview}
+%% \item AAA5 mediates stalk register changes Schmidt H, Zalyte R, Urnavicius L, Carter AP. 2014. Structure of human cytoplasmic dynein-2 primed for
+%%   its power stroke. Nature 518:435–38
+%% \item Linker moves as response to AAA1 nucleotide binding Burgess SA, Walker ML, Sakakibara H, Knight PJ, Oiwa K. 2003. Dynein structure and power stroke. Nature
+%%   421:715–8
+%% \item Crystal structures with Vanadium-Adp show dynein in the pre-powerstroke state, hinting that ADP-Pi-bound dynein takes on a different conformation than ADP-Pi free dynein
+%% \end{itemize}
+
+%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}.
 The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I.
 Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
-
-\textit{Add figure somewhere of this cycle superimposed with markings of what states are considered onebound and bothbound}\\
-
-\textbf{more on how ATP actually causes the conformation change, if that's available.
-The change from an open/closed ATPase is what changes the nucleotide affinity, go into depth on that, but actual info on how ATP binding causes conformation change would be good.
-Something about going from a planar to nonplanar conformation?}\\
-
-also how crystal structures are in different positions
-
-\subsubsection{Experimental results on dynein’s step}
-Weihong's figures go here.\\
-
-\subsubsection{c What is still needed to support theory}
-Where our simulation fits in. Why we need this kind of information.
-There are many different things which might be important for dynein's walk which we don't take into account: springiness of tail/stalk, changes in spring constants, repulsion between the heads, multiple pre/post powerstroke conformations.
-We are trying to see if these things are actually important.
-
-\subsubsection{Other theories?}
-Imamula model: how it is different from Cianfrocco model, and why we chose the Cianfrocco model.\\
-	\subsection{Past Simulations}
-		\subsubsection{Sarlah Winch Model}
-		\subsubsection{Other models}
-
-\subsection{Moving forward}
-Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
-aren't high resolution enough to make good videos of the walk, and even if they were, in some sense
-knowing that dynein behaves identically to a simple mathematical model is more informative than
-a video, since there is lots of information in a video and really precise info in a simulation.\\
-
-\textbf{Not sure where this goes:} The 'goal' of our experiment, at a very high level, is to
-understand how dynein works. We can know this if we can come up with the minimum set of characteristics a physical system needs to act like dynein. This information is the same thing as knowing
-``how dynein walks.'' We don't need to know all the complex dynamics of every single amino acid in
-dynein, we only need to know our rough model.\\
-
-\section{Chapter: Introduction II}
-
-\subsection{Dynein Stepping Background}
-Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
-The full mechanism is not known, but results of such experiments suggest a certain vague picture of how dynein generates motion.\\
-
-\subsubsection{ATP cycle influences conformational state}
-Dynein is known to occupy multiple discrete conformational states depending on its environment.
-In particular, the concentration of ATP and microtubules is known to alter the shape dynein takes on.
-A FRET (fluorescence resonance energy transfer) study attached fluorophores to dynein's motor and tail and measured the average distance between the two \cite{FRETstatepaper}.
-It was found that average distance increased or decreased depending on the nucleotide bound to dynein, indicating the motor takes on different conformations for different bound nucleotides.
-Dynein unbound to nucleotide, or frozen in ATP or ADP-bound states, had a similar tail-motor distance.
-However, when the motor was stuck in an ADP-Pi state, with ATP hydrolyzed but phosphate not yet released, the tail-motor distance was increased.
-This suggests that dynein starts its cycle with no nucleotide, binds ATP, hydrolyzes ATP, enters the ADP-Pi state and changes conformation to a far tail-motor distance, then releases phosphate, moves back to its original close tail-motor conformation, then ejects ADP and starts over.\\
-
-Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the trail \cite{FRETstatepaper} \cite{burgess-paper}.
-Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/literature/burgess-dynein-angles}
-  \caption{Cryo-electron microscopy images of dynein in two different nucleotide states.
-Left: dynein frozen in ADP-Pi state.
-Middle: dynein without nucleotide.
-Right: two states superimposed on one another.
-Bottom: cartoons representing how dynein may bind to the MT in either state.
-From \cite{burgess-paper}.}
-  \label{fig:cryo-em-angles}
-\end{figure}
-
-Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}.
-Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.
-This movement might cause a net forward motion of the motor domain.\\
-
-\textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
-
-\subsubsection{Microtubule and nucleotide states are coupled}
-Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
-This site occurs roughly every 8nm, indicating dynein is restricted to step sizes which are multiples of 8nm.\\
-
-The nucleotide state of the motor is not the only determiner of dynein conformation; microtubule binding state has also been shown to influence conformation.
-A study on the MTBD-MT complex indicates the stalk connecting the motor and MTBD can take on two major conformations, depending on whether the MTBD is bound to the MT or not \cite{mt-atp-coupling}.
-The conformation of the stalk has been shown to communicate information between the motor and MTBD.
-In the presence of microtubules, the ATPase rate of the motor is increased 25-fold.
-This indicates the stalk communicates MT-binding state of the MTBD to the motor, increasing its ATP hydrolysis rate.
-The communication happens the other way, as well.
-Treating dynein with ATP causes MT-binding rate to drop 15-fold, indicating ATP-binding at the motor decreases MT-binding rate at the MTBD.\\
-
-In addition to a bidirectional linking between ATPase rate and MT-binding, stalk state has been shown to directly influence motor conformation \cite{mt-atp-coupling}.
-When the stalk is allowed to freely transition between bound and unbound states, the motor can also transition between near and far tail/motor states.
-However, when the stalk is frozen in a particular conformation, the motor loses its transitioning ability.
-This suggests that the conformations of the two systems are tightly linked.\\
-
-\subsubsection{Stepping pattern}
-Several studies have been done on the dynein motor's stepping pattern using selectively-labeled motor domains \cite{reck2006single} \cite{weihongpaper}. These studies suggest that dynein has a
 

### 2017-03-01 thesis_stuff/thesis_stuff.tex

@@
 \subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
-Takahide Kon, Kenji Imamula, Anthony J Roberts, Reiko Ohkura, Peter J Knight, I R Gibbons, Stan A Burgess & Kazuo Sutoh\\
+Takahide Kon, Kenji Imamula, Anthony J Roberts, Reiko Ohkura, Peter J Knight, I R Gibbons, Stan A Burgess \& Kazuo Sutoh\\
 Discuss how other work has shown that MT affinity is controlled by registry.
@@
 
+\textbf{The supplemental movies could be used in a presentation, along with the molecular dynamics simulations in the MTBD-MT complex paper.}
+
 \subsection{3D Pre/Post-PS structures, there are two Pre-PS states!}

### 2017-03-08 thesis/latex/thesis.tex

@@
 
-As shown in \ref{dynein-artist-rendition-2}, a dynein motor is a fusion of to identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
+As shown in \ref{dynein-artist-rendition-2}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
 Each of these subunits has a unique purpose for the motor.
@@
 This drag factor is calculated based on the radius $R$ of the spheres, and is given by Stoke's Law:
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Thus R becomes a parameter input to the model.\\
@@
 \subsubsection{Angular springs}
-Each domain has a spring constant, $c_b, c_m$ or $c_t$ for binding, motor or tail, which decides the energy associated with that domain's angle. For example, the tail domain's energy is given by
-
+Each domain has a spring constant, $c_b, c_m$ or $c_t$ for binding, motor or tail, which decides the energy associated with that domain angle. For example, the tail domain energy is given by
+%
 \begin{equation}
@@
 The model transitions between states with a probability dependent on both the energy difference between the two states and the physical separation between the MT and binding MTBD.
-Energy difference between states A and B is given by:
-
+The energy difference between states A and B is given by:
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Transition energies are used to calculate transition rates, as given by the Arhennius equation $k=Ae^{-\beta\Delta G}$, where $\beta = (k_BT)^{-1}$.
 In this equation $\Delta G$ is the total energy of transition between states and A is a constant known as the preexponential factor with units of $s^{-1}$.\\
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 where $\Delta G_{conf}$ is the change in spring energy in going from bothbound to onebound and $\Delta G_{bind}$ is the energy gained from binding to the microtubule.
 Because binding energy for the MT-MTBD complex is hard to find, the following substitution is made:
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Thus $B$ becomes a parameter of the model.\\
@@
 The Brownian dynamics equation describes the motion of high-drag objects which spend most of their time at terminal velocity, and is given by:
-
+%
 \begin{equation}
@@
 \end{equation}
-
-where $\gamma$ is the drag constant of the object and R is a random Brownian force which describes the effects of water particle collision.
-R a Gaussian-sampled zero-centered force with variance given by:
-
+%
+where $\gamma$ is the drag constant of the object and $R$ is a random Brownian force which describes the effects of water particle collision.
+$R$ is a Gaussian-sampled zero-centered force with variance given by:
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Dynein is in the range of objects which BD describes well. (citation needed)
@@
 Dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
-By this, all dynein steps should be multiples of $8$nm.
+Thus, all dynein steps should be multiples of $8$nm.
 This model ignores this requirement and allows stepping to occur at any length.
@@
 
-Side stepping of dynein is ignored by this model.
+Side stepping of dynein is ignored in this model.
 Stepping perpendicular to the MT occurs in dynein \cite{weihongppaer}, as shown in Figure \ref{fig:weihong-side-stepping}.
@@
 \subsection{Mathematical models}
-In order to simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state.
+To simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state.
 The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\
@@
 This change in energy was compared with the work the forces on each domain caused over the nudge.
-In order for energy to be conserved, these values were required to be very similar.
+For energy to be conserved, these values were required to be very similar.
 Mathematically the test required the following:
@@
 The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $<E> = \frac N2 k_bT$.
-In order for the dynein models to display ET behavior, they would have to both properly calculate forces and properly calculate velocities from forces.
+For the dynein models to display ET behavior, they would have to both properly calculate forces and properly calculate velocities from forces.
 Brownian forces are also required to properly explore the different states of the system, but they need not be the correct magnitude for ET agreement.\\

### 2017-03-14 thesis/latex/thesis.tex
Thesis: minor commit.

@@
 \tableofcontents
+\listoffigures
 \newpage
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
+  \caption{Artist's rendition of dynein.}{Artist rendition of the dynein motor bound to a microtubule.
+One monomer is bound to the MT, and one is raised up.
+Modified.
+Source: Lander Lab, The Scripps Research Institute.}
   \label{dynein-artist-rendition}
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
-  \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
+  \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
   \label{diffusion_vs_dynein}
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
-  \caption{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
+  \caption{Dynein localization to axon growth cones.}{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport.
+Modified from \cite{valetoolbox}.}
   \label{retrograde-transport}
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
+  \caption{Artist's rendition of motor-MT complex.}{Artist rendition of the dynein motor bound to a microtubule.
+One monomer is bound to the MT, and one is raised up.
+Modified.
+Source: Lander Lab, The Scripps Research Institute.}
   \label{dynein-artist-rendition-2}
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures//burgess-dynein-angles}
-  \caption{Cryo-electron microscopy images of dynein in two different nucleotide states.
+  \caption{Cryo-EM microscopy of dynein conformational states.}{Cryo-electron microscopy images of dynein in two different nucleotide states.
 Left: dynein frozen in ADP-Pi state.
@@
 
-Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}.
-Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.
-This movement might cause a net forward motion of the motor domain.\\
+Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper} (make a Chimaera figure where the pre/poststroke motors are docked showing this).
+Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\
 
@@
     \includegraphics[width=\textwidth]{../../figures/weihong-step-size}
-    \caption{Size of steps taken by dynein motor parallel to microtubule. Positive axis corresponds to steps towards the microtubule minus-end. Figure modified from \cite{weihongpaper}.}
+    \caption{Experimental dynein step size histogram.}{Size of steps taken by dynein motor parallel to microtubule.
+Positive axis corresponds to steps towards the microtubule minus-end.
+Figure modified from \cite{weihongpaper}.}
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{../../figures/weihong-off-axis-steps}
-    \caption{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
+    \caption{Dynein experimental off-axis stepping size.}{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
   \end{minipage}
@@
 \subsection{Dynein models}
-Data presented in the previous sections paints a
+Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts.
+Somehow the protein itneracts with nucleotides and microtubules in a way that allows it to reliably move through the cell.
+Models presented below take these facts and string them together into cohesive cycles which might explain how dynein walks.
+It is important to note that these models are hypotheses.\\
 
@@
 Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle.
-The exact order of these events is not precisely known.
-More detail on each step of the cycle is given below.\\
-
-Maybe show the Cianfrocco model in a section \textit{after} talking about all the things which happen for sure in dynein, since it's more theoretical?
-Talk about the Cianfrocco model, but other interpretations?
-
-Make a figure of pre/post-powerstroke dynein with the linker hilighted? Can you get what residues correspond to the linker somewhere?
+The exact order of these events is not precisely known.\\
 
@@
   %% \end{tabular}
-  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
+  \caption{Cianfrocco mechanochemical cycle.}{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
   \label{mech-cycle}
@@
 
-\subsubsection{Other models}
-If there are other models which conflict with Cianfrocco, here would be a place to put them.\\
-
-\subsection{This work}
+%% \subsubsection{Other models}
+%% Find other models and put them here
+
+\subsection{Necessary and sufficient criteria for motion}
+Each of the models described above postulates a series of chemical events which occur during the dynein step. Testing such hypotheses can be done in a variety of ways.
+
 \subsubsection{Our model}
@@
 To test this hypothesis, these features are put into a model and simulated.
-The features are as follows:
-
-\begin{itemize}
-\item Dynein is a collection of spherical domains joined together by massless rods
-\item These rods are rigid
-\item Each joint in the motor feels a spring force about some equilibrium joint angle
-\item Dynein can be in two states: onebound and bothbound
-\item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
-\item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
-\item Transitions between the two states are based solely on spring energies between the two models
-\item Brownian dynamics describes the behavior of the domains in time
-\item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
-\item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
-\end{itemize}
+A schematic of the model is pictured in Figure \ref{fig:model-intro} and described below.\\
 
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
-  \caption{}
-  \label{fig:model-intro}
-\end{figure}
+  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
+  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
+  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
+  \label{ob_fig}
+\end{figure}
+
+%% \begin{itemize}
+%% \item Dynein is a collection of spherical domains joined together by massless rods
+%% \item These rods are rigid
+%% \item Each joint in the motor feels a spring force about some equilibrium joint angle
+%% \item Dynein can be in two states: onebound and bothbound
+%% \item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
+%% \item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
+%% \item Transitions between the two states are based solely on spring energies between the two models
+%% \item Brownian dynamics describes the behavior of the domains in time
+%% \item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
+%% \item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
+%% \end{itemize}
+
+%% \begin{figure}[h]
+%%   \centering
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
+%%   \caption{Onebound dynein model.}{}
+%%   \label{fig:model-intro}
+%% \end{figure}
 
@@
 This model makes the assumption that the mechanochemical cycle can be broken down into a cycle of prestroking to move the unbound foot forward, brownian walking to place the foot on the microtubule, then powerstroking to move the other domains forward.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
-  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
-  \caption{Representations of onebound (left) and bothbound (right) dynein models.}
-  \label{ob_fig}
-\end{figure}
 
@@
 
-\subsubsection{$\alpha-\beta$ binding unnecessary}
-Dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
+\subsubsection{Binding to microtubule}
+The model ``steps'' whenever an MTBD diffuses near the microtubule.
+\textit{In vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
 Thus, all dynein steps should be multiples of $8$nm.
 This model ignores this requirement and allows stepping to occur at any length.
-This assumption is not based on biology, but to simplify the model.
-The assumption is that \textit{in vivo} dynein is tuned to take 8nm steps based on its size and stepping angle, and doesn't search along the MT for a binding site.\\
+The assumption is that \textit{in vivo} dynein takes 8nm steps because of its size and stepping angle.
+Thus the 8nm step length should be reproduced by the model without explicit coding.\\
 
@@
   \includegraphics[width=.45\textwidth]{../../figures/weihong-side-stepping}
-  \caption{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}. 0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right. Modified.}
+  \caption{Dynein experimental off-axis stepping histogram.}{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}.
+0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right.
+Modified.}
   \label{fig:weihong-side-stepping}
@@
 The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$.
-Each angle is defined relative to the horizontal axis.\\
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=C++]
-      class Dynein_onebound{
-        double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
-        double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
-        double &$X_{bb}$&
-      }
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Pseudocode of the onebound Dynein model.}
-  \label{ob_struct}
-\end{figure}
-
-Pseudocode for the numerical onebound model representation is shown in Figure \ref{ob_struct}.
-The position of the bound binding domain $X_{bb}$ and the four domain angles are all the values needed to determine the position of the protein at any time.\\
+Each angle is defined relative to the horizontal axis.
+The position of the bound binding domain $X_{bb}$ and the four domain angles are all that is needed to determine the position of the protein at any time.\\
+
+%% \begin{figure}[h]
+%%   \centering
+%%   \begin{tabular}{c}
+%%     \begin{lstlisting}[language=C++]
+%%       class Dynein_onebound{
+%%         double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
+%%         double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
+%%         double &$X_{bb}$&
+%%       }
+%%     \end{lstlisting}
+%%   \end{tabular}
+%%   \caption{Pseudocode of the onebound Dynein model.}
+%%   \label{ob_struct}
+%% \end{figure}
 
@@
   \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
-  \caption{Definition of equilibrium angles.}
+  \caption{Model bothbound equilibrium angle defintion.}{}
   \label{bb_fig}
@@
   \end{tabular}
-  \caption{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
+  \caption{Code snippet}{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
   \label{ob_struct}
@@
   \end{tabular}
-  \caption{Code snippet of transition rate calculation using the Arrhenius equation.}
+  \caption{Code snip}{Code snippet of transition rate calculation using the Arrhenius equation.}
   \label{transition-rate-snippet}
@@
   \end{tabular}
-  \caption{Code snippet of internal force calculation.}
+  \caption{Snip}{Code snippet of internal force calculation.}
   \label{transition-rate-snippet}
@@
     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
-    \caption{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
+    \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
-    \caption{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
+    \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
   \end{minipage}
@@
   \end{tabular}
-  \caption{Table of literature values for dynein behavior}
+  \caption{Literature values for experimental dynein stepping behavior.}{Table of literature values for dynein behavior}
   \label{table:parameter-table}
@@
   \end{tabular}
-  \caption{Table of literature values for various free parameters in dynein model.}
+  \caption{Literature values for dynein model parameters.}{Table of literature values for various free parameters in dynein model.}
   \label{table:parameter-table}
@@
   \end{tabular}
-  \caption{Table of physical constants used in simulation.}
+  \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
   \label{table:parameter-table}
@@
   \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
-  \caption{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
+  \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
   \label{fig:sarlah-rate-table}
@@
   \end{tabular}
-  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
+  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
   \label{table:parameter-table}
@@
   \end{tabular}
-  \caption{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
+  \caption{Ideal parameters for model stepping.}{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
   \label{final-parameter-table}

### 2017-03-16 thesis/latex/thesis.tex
Thesis: small commit.

@@
 \textit{maybe decorate the above plot with pictures of cells of each size, or how long certain cellular events take? That could be cool and make it actually an interesting plot}
-\textit{this argument would be much better if you could find examples of things which need to be done quickly in the cell, like responding to foreign particles or signalling
-  molecules or cell division or neural events}
+\textit{this argument would be much better if you could find examples of things which need to be done quickly in the cell, like responding to foreign particles or signalling molecules or cell division or neural events}
 
@@
 
-Also possibly talk about the other things Dynein has been found to do, such as hydrolyse ATP and
-move its subdomains around. This may be better in a different section than the introduction though,
-since its a lot of biochemistry for the second section in an intro? maybe not, it has to go somewhere.
+Also possibly talk about the other things Dynein has been found to do, such as hydrolyse ATP and move its subdomains around.
+This may be better in a different section than the introduction though, since its a lot of biochemistry for the second section in an intro?
+maybe not, it has to go somewhere.
 
 \subsubsection{Why is dynein special and interesting?}
-Compare the processive motion of dynein to kinesin in \textbf{a.)} directionality, \textbf{b.)}
-stepping pattern and \textbf{c.)} size (like how it can step over roadblocks kinesin cannot).\\
-
-Talk about why a random stepping motor is interesting compared to a orderly-stepping motor: what
-is different about dynein's structure that makes it step differently? Compare the crystal structures
-and ask lots of questions. Build interest in the motors here.\\
+Compare the processive motion of dynein to kinesin in \textbf{a.)} directionality, \textbf{b.)} stepping pattern and \textbf{c.)} size (like how it can step over roadblocks kinesin cannot).\\
+
+Talk about why a random stepping motor is interesting compared to a orderly-stepping motor: what is different about dynein's structure that makes it step differently?
+Compare the crystal structures and ask lots of questions.
+Build interest in the motors here.\\
 
@@
 
-\subsection{Necessary and sufficient criteria for motion}
-Each of the models described above postulates a series of chemical events which occur during the dynein step. Testing such hypotheses can be done in a variety of ways.
-
-\subsubsection{Our model}
-what we're trying to do with our project
-
-\textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
-It would basically show all events occuring at two times: unbinding or rebinding.}\\
+%% \subsection{Brownian dynamics}
+%% New section which describes how BD works.
+
+\subsection{This work}
+\subsubsection{Necessary and sufficient criteria for motion}
+One of the principle goals of researchers studying the dynein motor is establishing how it walks.
+This can be a difficult task, since direct observation of the motor walking is not currently experimentally possible.
+The next best thing, then, is building a model which both only does all the things dynein does, and generates motion.
+Finding such a system would be very useful for forming hypotheses on how dynein walks.
+Another requirement of the system would be that it be as simple as possible while still explaining all the data.
+By Occam's Razor, such systems are the most likely to represent real dynein.
+Thus, finding the necessary and sufficient criteria for dynein's motion is a big goal in the field.\\
+
+A good starting place for finding the minimum set of motile criteria would be preexisting models, like the Cianfrocco model.
+This model describes a set of states which logically lead to each other and are supported by experiment.
+It seems intuitive that a motor which obeyed the Cianfrocco cycle would walk.
+There are multiple ways to verify this.
+A completely synthetic biological motor could be designed which obeys the cycle, and its motile properties could be studied.
+This seems incredibly difficult.
+Much easier would be to create a physical model of such a cycle, simulate it, and see if it obeys similarly to experimentally observed dynein.
+If the physical model both behaves according to the laws of physics and captures experimental dynein behavior well, this would be good evidence that such a model describes how dynein actually walks.\\
 
 \subsubsection{Goals}
-What we hope to gain by simulating such a model, and what it would contribute to the current literature
+The goal of this work is to construct a minimum physical model of dynein protein based on the theoretical Cianfrocco model.
+The model should behave as physics predicts a protein to behave; namely, it should obey Brownian dynamics and conservation of energy.
+It should also roughly capture the state transitions and conformation changes of the Cianfrocco model.
+Also the model should be as simple as possible, to assure that each part of the model is necessary.
+If too many extra features are added, the model will not be minimal and not achieve its purpose.\\
+
+This model will then be converted into a computer program, tested for compliance with the laws of physics, and simulated.
+Information on the long-term behavior of such a simulation will then be used to evaluate how well the model describe's experimental dynein's behavior.\\
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
-  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
-  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
-  \label{ob_fig}
-\end{figure}
+\textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
+It would basically show all events occuring at two times: unbinding or rebinding.}\\
 
@@
 This model makes the assumption that the mechanochemical cycle can be broken down into a cycle of prestroking to move the unbound foot forward, brownian walking to place the foot on the microtubule, then powerstroking to move the other domains forward.\\
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
+  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
+  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
+  \label{ob_fig}
+\end{figure}
+
+\textbf{todo: Add springs to joints!}
 
@@
 The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities.
-To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner:
+To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner.
+A subset of the equations are shown here:
 
@@
   \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
-  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
-  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
+  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
+  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
+  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
 \end{align}
@@
   \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
-  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
+  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
+  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
+  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
 \end{align}
@@
   \dot{X}_{bm} &= \frac{1}{\gamma_m} \Big(F_{xml} + - \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \label{brownian-bmx}\\
-  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
-  \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
-  \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
+  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
+  %% \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
+  %% \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
 \end{align}
 
-\begin{align}  
-  \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
-  \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
-  \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-  \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
-\end{align}
+%% \begin{align}  
+%%   \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
+%%   \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
+%%   \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
+%%   \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
+%% \end{align}
 
@@
 For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated.
-This equating, combined with expanding the recursive velocity definitions leads to:
+This equating, combined with expanding the recursive velocity definitions leads to new equations, some of which are shown here:
 
@@
   &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
+  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx}
+  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
+  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
 \end{align}
 
-\begin{align}
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
-  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
-\end{align}
-
+%% \begin{align}
+%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
+%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
+%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
+%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
+%% \end{align}
+
+A total of eight coupled differential equations are formed from this procedure.
 These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$.
@@
 
-This matrix is then solved using the Mathematica computer algebra system, resulting in a set of $\dot{\Theta}_n$ equations shown in Appendix (\ref{ob-motion-equations]}).
+This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\Theta_{bm}}(\Theta_{bb}, \Theta_{bm}, \Theta_{um}, \Theta_{ub})$.
+These motion equations are further described in (\ref{sec:ob-motion-equations}).\\
 
@@
 $\Theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted.
-The partial derivatives of these values are useful:
+The partial derivatives of these values are used in future calculations, and some are shown here:
 
@@
   \frac{\partial \sin\theta_n}{\partial L_n} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
-  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
-  \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
-  \left(\frac{-L_f}{LLn}\right)\\
-  \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
-  - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
-  \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
-  \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
-  \begin{cases}
-    \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
-    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
-    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
-    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
-  \end{cases}\\
-  \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
+  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)
+  %% \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
+  %% \left(\frac{-L_f}{LLn}\right)\\
+  %% \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
+  %% - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
+  %% \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
+  %% \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
+  %% \begin{cases}
+  %%   \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
+  %%   \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
+  %%   \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
+  %%   \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
+  %% \end{cases}\\
+  %% \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
 \end{align}
@@
 
-The partial derivatives of these values are:
+The partial derivatives of these values are used later. A selection are shown here:
 
@@
   \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)\\
-  \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
-  \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
-  \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
-  \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
-  \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
+  %% \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
+  %% \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
+  %% \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
+  %% \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
+  %% \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
 \end{align}
@@
 
-This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{both-motion-equations}).
+This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{sec:bb-motion-equations}).
 
@@
 
-\paragraph{Euler’s method}
-Show how Euler's method is arrived at, how its error scales, why we use it.
-
-\paragraph{Vs other methods (Runge Kutta, etc)}
-Talk about why our differential equation is most conducive to Euler's method. Euler's is more
-efficient -- is there a way to show how our differential equation is smooth, not jagged?
+%% \paragraph{Euler’s method}
+%% Show how Euler's method is arrived at, how its error scales, why we use it.
+
+%% \paragraph{Vs other methods (Runge Kutta, etc)}
+%% Talk about why our differential equation is most conducive to Euler's method. Euler's is more
+%% efficient -- is there a way to show how our differential equation is smooth, not jagged?
 
@@
   L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
-  \cos(\Theta_{nm}) = \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
-  \cos(\Theta_{fm}) = \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}\\
+  \cos(\Theta_{nm}) &= \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
+  \cos(\Theta_{fm}) &= \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}
 \end{align}
@@
   \Theta_{new,uma} &= \Theta_{old,fma} + \Theta_{old,fba} - \pi\\
-  \Theta_{new,uba} &= \Theta_{old,fba}\\
+  \Theta_{new,uba} &= \Theta_{old,fba}
 \end{align}
@@
 Spring and Brownian forces are used to properly move the model through time.
-Appendices (\ref{onebound-motion-equatons}-\ref{bothbound-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
+Appendices (\ref{sec:ob-motion-equatons}-\ref{sec:bb-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
 
@@
 
-\subsubsection{Fitting spring constants}
-\paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
-\paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
-\paragraph{Fitting rate constants by simulation}
-
 %% \subsubsection{Fitting spring constants}
@@
 \subsection{Future work on this project}
-If setbacks happen, this'll be a big section. Or, further simulations which could be done.
+If setbacks happen, this'll be a big section.
+Or, further simulations which could be done.
+Namely taking our model and giving it lots more states and seeing if this model even better fits experimental data.\\
 
@@
 \subsubsection{Onebound equations}
-\label{onebound-motion-equations}
+\label{sec:ob-motion-equations}
 The following is a continuation of the derivation for the full motion equations used to time evolve the onebound model:
@@
 
-%% \subsubsection{Bothbound equations}
-%% \label{bothbound-motion-equations}
-%% The following are the full motion equations used to time evolve the bothbound model:
-
-%% \begin{center}
-%%   \begin{minipage}{0.3\textwidth}
-%%     \begin{align*}
-%%       a &= \frac{-dXnm}{dLn}\\
-%%        b &= \frac{-dXnm}{dLf}\\
-%%        c &= -(x_{nm} - x_{nb}) / \gamma_m\\
-%%        d &= (x_t - x_{nm}) / \gamma_m\\
-%%        e &= \frac{-dXt}{dLn}\\
-%%        f &= \frac{-dXt}{dLf}\\
-%%        g &= -(x_t - x_{nm}) / \gamma_t\\
-%%        h &= (x_{fm} - x_t) / \gamma_t\\
-%%        i &= \frac{-dXfm}{dLn}\\
-%%        j &= \frac{-dXfm}{dLf}\\
-%%        k &= -(x_{fm} - x_t) / \gamma_m\\
-%%        l &= (x_{fb} - x_{fm}) / \gamma_m\\
-%%     \end{align*}
-%%   \end{minipage}
-%%   \begin{minipage}{0.3\textwidth}
-%%     \begin{align*}
-%%        m &= \frac{-dYnm}{dLn}\\
-%%        n &= \frac{-dYnm}{dLf}\\
-%%        p &= -(y_{nm} - y_{nb}) / \gamma_m\\
-%%        q &= (y_t - y_{nm}) / \gamma_m\\
-%%        r &= \frac{-dYt}{dLn}\\
-%%        s &= \frac{-dYt}{dLf}\\
-%%        t &= -(y_t - y_{nm}) / \gamma_t\\
-%%        u &= (y_{fm} - y_t) / \gamma_t\\
-%%        v &= \frac{-dYfm}{dLn}\\
-%%        w &= \frac{-dYfm}{dLf}\\
-%%        x &= -(y_{fm} - y_t) / \gamma_m\\
-%%        y &= (y_{fb} - y_{fm}) / \gamma_m
-%%     \end{align*}
-%%   \end{minipage}
-%% \end{center}
-
-%% Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
+\subsubsection{Bothbound equations}
+\label{sec:bb-motion-equations}
+The following are the full motion equations used to time evolve the bothbound model:
+
+\begin{center}
+  \begin{minipage}{0.3\textwidth}
+    \begin{align*}
+      a &= \frac{-dXnm}{dLn}\\
+       b &= \frac{-dXnm}{dLf}\\
+       c &= -(x_{nm} - x_{nb}) / \gamma_m\\
+       d &= (x_t - x_{nm}) / \gamma_m\\
+       e &= \frac{-dXt}{dLn}\\
+       f &= \frac{-dXt}{dLf}\\
+       g &= -(x_t - x_{nm}) / \gamma_t\\
+       h &= (x_{fm} - x_t) / \gamma_t\\
+       i &= \frac{-dXfm}{dLn}\\
+       j &= \frac{-dXfm}{dLf}\\
+       k &= -(x_{fm} - x_t) / \gamma_m\\
+       l &= (x_{fb} - x_{fm}) / \gamma_m\\
+    \end{align*}
+  \end{minipage}
+  \begin{minipage}{0.3\textwidth}
+    \begin{align*}
+       m &= \frac{-dYnm}{dLn}\\
+       n &= \frac{-dYnm}{dLf}\\
+       p &= -(y_{nm} - y_{nb}) / \gamma_m\\
+       q &= (y_t - y_{nm}) / \gamma_m\\
+       r &= \frac{-dYt}{dLn}\\
+       s &= \frac{-dYt}{dLf}\\
+       t &= -(y_t - y_{nm}) / \gamma_t\\
+       u &= (y_{fm} - y_t) / \gamma_t\\
+       v &= \frac{-dYfm}{dLn}\\
+       w &= \frac{-dYfm}{dLf}\\
+       x &= -(y_{fm} - y_t) / \gamma_m\\
+       y &= (y_{fb} - y_{fm}) / \gamma_m
+    \end{align*}
+  \end{minipage}
+\end{center}
+
+Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
 

### 2017-03-24 thesis/latex/thesis.tex
Thesis: do some shufflin

@@
 
+\usepackage{tocbibind}
+\usepackage{tocloft}
+\usepackage{xpatch}
+
 \renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
@@
 \begin{document}
+\newcommand{\listequationsname}{List of Equations}
+\newlistof{myequations}{equ}{\listequationsname}
+\newcommand{\myequations}[1]{%
+\addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}
+
+\xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}
 
@@
 \listoffigures
+\clearpage
+\listofmyequations
 \newpage
@@
 \subsubsection{Basics}
-
 Dynein is a cellular structure which converts chemical energy to mechanical energy.
 It does so by reacting with adenosine triphosphate (ATP) to take steps along long cellular tracks known as microtubules (MTs).
-Dynein's mechanical energy is used to transport molecules around the cell, pull chromosomes during division, move cellular propellers known as cilia and various other functions \cite{cianfroccoreview}.\\
+Dynein's mechanical energy is used for various cellular functions, including to transport molecules around the cell, pull chromosomes during division, and move cellular propellers known as cilia \cite{cianfroccoreview}.\\
 
@@
 Dynein is believed to move by using the energy of ATP to cycle through a ring of states, each with different spatial relations to the microtubule.
-By cycling forward through this ring, the molecule can end up in the same state it began, but moved forward a small amount.
+By cycling forward through this ring, the molecule will end up in the same state it began, but moved forward a small amount.
 This ring of states is known as the mechanochemical cycle \cite{cianfroccoreview}.
@@
 A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter.
-In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2) \textbf{((is this the best way to cite this?))}, a $10^3$ factor difference in size.\\
+In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\
 
@@
 \end{equation}
+\myequations{some equation}
 
 where D is the diffusion constant describing the diffusability of the biomolecule.
-For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ %% \cite{diffusionconstants}
-, it would take about a month to travel across a millimeter-sized cell.
+For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell.
 In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.
+Figure (\ref{fig:diffusion_vs_dynein}) demonstrates how motor transport quickly outstrips diffusion in a cell.\\
 
@@
   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
-  \label{diffusion_vs_dynein}
+  \label{fig:diffusion_vs_dynein}
 \end{figure}
@@
   X_{t} &= L_n\cos\theta_n\\
-  Y_{t} &= L_n\sin\theta_n\\
+  Y_{t} &= L_n\sin\theta_n
 \end{align}
@@
   \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
-  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)\\
+  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)
   %% \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
@@
 
+\section{Chapter: Methods}
+This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\
+
 \subsection{Simulation}
@@
 \end{figure}
-
-\section{Chapter: Methods}
-This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\
 

### 2017-03-25 thesis/latex/thesis.tex
Thesis: partial commit of kb-kub testing.

@@
 
-\usepackage{tocbibind}
-\usepackage{tocloft}
+%% \usepackage{tocbibind}
+%% \usepackage{tocloft}
 \usepackage{xpatch}
@@
 \begin{document}
-\newcommand{\listequationsname}{List of Equations}
-\newlistof{myequations}{equ}{\listequationsname}
-\newcommand{\myequations}[1]{%
-\addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}
-
-\xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}
-
-\tableofcontents
+%% \newcommand{\listequationsname}{List of Equations}
+%% \newlistof{myequations}{equ}{\listequationsname}
+%% \newcommand{\myequations}[1]{%
+%% \addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}
+
+%% \xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}
+
+%% \tableofcontents
 \listoffigures
 \clearpage
-\listofmyequations
-\newpage
+%% \listofmyequations
+%% \newpage
 
@@
 \end{equation}
-\myequations{some equation}
+%% \myequations{some equation}
 
@@
   \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
-  \label{table:parameter-table}
+  \label{table:simulation-std-conditions}
 \end{figure}
@@
   \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
-  \label{table:parameter-table}
-\end{figure}
-
-%% \textit{Add in a plot of the binding rate fitting search}
+  \label{table:time-parameter-table}
+\end{figure}
 
 \paragraph{Fitting rate constants by simulation}
-\textit{Add in a plot of the binding rate fitting search}
+\textit{Add in a plot of the binding rate fitting search}\\
+
+To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
+The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}.
+Simulation behavior for a wide range of $k_b$ and $k_{ub}$ values is shown as a heat map in Figure \ref{fig:kb-kub-heatmap}.\\
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
+  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
+Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
+  \label{fig:kb-kub-heatmap}
+\end{figure}
 

### 2017-03-26 thesis/latex/thesis.tex
Thesis: small commit.

@@
 
-%% \usepackage{tocbibind}
-%% \usepackage{tocloft}
-\usepackage{xpatch}
-
 \renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
@@
 \begin{document}
-%% \newcommand{\listequationsname}{List of Equations}
-%% \newlistof{myequations}{equ}{\listequationsname}
-%% \newcommand{\myequations}[1]{%
-%% \addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}
-
-%% \xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}
-
-%% \tableofcontents
+
+\tableofcontents
 \listoffigures
-\clearpage
-%% \listofmyequations
-%% \newpage
+\newpage
 
@@
 
-%% Begin with a paper-like introduction which talks about:
-
-%% \begin{itemize}
-%% \item How dynein is a structure which turns chemical energy into motion
-%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
-%% \item How it's weird that a cellular structure can generate directed motion
-%% \item Other cool stuff - make dynein mysterious and cool.
-%% \end{itemize}
-
-%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
+Begin with a paper-like introduction which talks about:
+
+\begin{itemize}
+\item How dynein is a structure which turns chemical energy into motion
+\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
+\item How it's weird that a cellular structure can generate directed motion
+\item Other cool stuff - make dynein mysterious and cool.
+\end{itemize}
+
+Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
 

### 2017-03-29 thesis/latex/thesis.tex
Thesis: mini commit.

@@
 
+\usepackage{csquotes}
+
 \renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
@@
 \section{Chapter: Introduction}
-
+\blockquote{An embryo in its spherical blastula stage has spherical symmetry [...].
+But a system which has spherical symmetry, and whose state is changing because of chemical reactions and diffusion, will remain spherically symmetrical for ever [...].
+It certainly cannot result in an organism such as a horse, which is not spherically symmetrical.
+\textbf{Alan Turing, The Chemical Basis of Morphogenesis, 1952}}
+
+Cells need to create asymmetric, heterogeneous structures inside themselves in order to function.
+However, as per the above quote, diffusive processes cannot create this asymmetry.
+How then do cells create heterogeneity?
+Motor proteins are part of the answer.
+Motor proteins are structures which use energy to create directed motion in cells.
+In broad terms, they are creators of asymmetry.
+This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\
+
+\subsection{Interest builder}
 Begin with a paper-like introduction which talks about:

### 2017-03-29 thesis/latex/thesis.tex

--- 2017-03-26 thesis/latex/thesis.tex
@@
 
+\usepackage{epigraph}
+
 \renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
@@
 \section{Chapter: Introduction}
-
+\subsection{Grabber}
+
+\epigraph{An embryo in its spherical blastula stage has spherical symmetry [...].
+But a system which has spherical symmetry, and whose state is changing because of chemical reactions and diffusion, will remain spherically symmetrical for ever [...].
+It certainly cannot result in an organism such as a horse, which is not spherically symmetrical.}{Alan Turing, The Chemical Basis of Morphogenesis, 1952}
+
+A fundamental faculty cells require to control their internal environments is the ability to create and maintain asymmetry.
+Diffusion, as per above, is an undirected process which cannot create asymmetry.
+How, then, do cells meet this need?\\
+
+Motor proteins are structures which use energy to create directed motion in cells.
+In broad terms, they are creators of asymmetry.
+This thesis will explore a hypothesis on how one such motor protein, Dynein, achieves this.\\
+
+\subsection{Interest builder}
 Begin with a paper-like introduction which talks about:

### 2017-03-29 thesis/latex/thesis.tex
Thesis: another minor commit.

--- 2017-03-29 thesis/latex/thesis.tex
@@
 \usepackage{csquotes}
+
+\usepackage{float}
 
@@
 
+\subsection{Data interpretation}
+Metrics for quality are required to assess how well the model fits reality. These metrics include time spent in one/bothbound states and average step size. These metrics are developed here.\\
+
+\subsubsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
+Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
+One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations.
+In contrast, the rates the model uses represent the probability of unbinding of a specific conformation.
+Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$.
+As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:
+
+\begin{align*}
+  k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
+  k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
+\end{align*}
+
+where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
+The experimental values are calculated the same way, with the free energy changes replaced with expectation values.
+Since by the equipartition theorem $\left<G_{conf}^{ob}\right> = 2k_BT$ and $\left<G_{conf}^{bb}\right> = k_BT$, the equations can be simplified:
+
+\begin{align*}
+  k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
+  k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
+\end{align*}
+
+Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
+
+\subsubsection{Literature values for experimental binding rates}
+Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
+  \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
+  \label{fig:sarlah-rate-table}
+\end{figure}
+
+The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
+Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound.
+These states are roughly grouped as MT-bound and MT-unbound states in the Cianfrocco mechanochemical cycle \cite{cianfroccoreview}.\\
+
+The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
+That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\
+
+\subsubsection{Calculating one/bothbound times of experimental dynein}
+Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
+
+\newcommand\tbb{\left<t_{bb}\right>}
+\newcommand\tob{\left<t_{ob}\right>}
+\newcommand\tstep{\left<t_{step}\right>}
+\newcommand\tproc{\left<t_{processivity}\right>}
+\newcommand\kub{k_{ub}}
+\newcommand\kb{k_{b}}
+\newcommand\ko{k_{dis}}
+
+\begin{itemize}
+\item $\tbb$: Time in bothbound per step
+\item $\tob$: Time in onebound per step
+\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+\end{itemize}
+
+$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
+
+\begin{align*}
+  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
+  \tob &= \tstep-\tbb\\
+  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
+  &= \frac{\tstep^2}{\tstep+\tproc}\\
+\end{align*}
+
+Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| c | c | c | c | c | c |}
+    \hline
+    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+  \end{tabular}
+  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
+  \label{table:time-parameter-table}
+\end{figure}
+
 \section{Chapter: Methods}
@@
 There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
-Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.
-Others are more difficult to find.\\
-
-What's more, using exact literature values for each parameter does not necessarily create the simulation most similar to \textit{in vivo} dynein.
-Defects and simplifications in the model may cause slightly less physical values for individual parameters to lead to a more physical simulation.
-For this reason, fitting model parameters to experiment is necessary.
+Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.\\
+
+Others are more difficult to find.
+These values, including $k_b$, $k_ub$ and the three spring constants, are fit by an optimization process.
+First un/binding rates are fit to one/bothbound times, then spring constants are fit to average step length.
 This process is chronicled below.
-Table \ref{table:parameter-table} concisely lists literature values for various parameters.
 
@@
 \subsubsection{Fitting rate constants}
-\paragraph{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
-Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
-One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations.
-In contrast, the rates the model uses represent the probability of unbinding of a specific conformation.
-Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$.
-As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:
-
-\begin{align*}
-  k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
-  k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
-\end{align*}
-
-where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
-The experimental values are calculated the same way, with the free energy changes replaced with expectation values.
-Since by the equipartition theorem $\left<G_{conf}^{ob}\right> = 2k_BT$ and $\left<G_{conf}^{bb}\right> = k_BT$, the equations can be simplified:
-
-\begin{align*}
-  k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
-  k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
-\end{align*}
-
-Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
-
-\paragraph{Literature values for experimental binding rates}
-Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
-  \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
-  \label{fig:sarlah-rate-table}
-\end{figure}
-
-The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
-Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound.
-These states are roughly grouped as MT-bound and MT-unbound states in the Cianfrocco mechanochemical cycle \cite{cianfroccoreview}.\\
-
-The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
-That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\
-
-\paragraph{Fitting rate constants to processivity and step times}
-Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
-
-\newcommand\tbb{\left<t_{bb}\right>}
-\newcommand\tob{\left<t_{ob}\right>}
-\newcommand\tstep{\left<t_{step}\right>}
-\newcommand\tproc{\left<t_{processivity}\right>}
-\newcommand\kub{k_{ub}}
-\newcommand\kb{k_{b}}
-\newcommand\ko{k_{dis}}
-
-\begin{itemize}
-\item $\tbb$: Time in bothbound per step
-\item $\tob$: Time in onebound per step
-\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
-\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
-\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
-\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
-\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
-\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
-\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
-\end{itemize}
-
-$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
-
-\begin{align*}
-  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
-  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
-  \tob &= \tstep-\tbb\\
-  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
-  &= \frac{\tstep^2}{\tstep+\tproc}\\
-\end{align*}
-
-Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| c | c | c | c | c | c |}
-    \hline
-    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
-  \end{tabular}
-  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
-  \label{table:time-parameter-table}
-\end{figure}
-
-\paragraph{Fitting rate constants by simulation}
-\textit{Add in a plot of the binding rate fitting search}\\
-
 To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
@@
 
-\begin{figure}[h!]
+\begin{figure}[H]
   \centering
@@
 
-%% \subsubsection{Fitting spring constants}
-%% \paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
-%% \paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
-%% \paragraph{Fitting rate constants by simulation}
-
-%% \subsubsection{Finding parameters from PyMol}
-
-%% \subsubsection{Finding the right timestep}
+\subsubsection{Fitting spring constants}
+This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
 
 \section{Chapter: Results}
-
-\subsection{Simulation parameters}
-The ideal set of parameters used to generate data were found to be:
-
-\begin{figure}[h]
+The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\
+
+\begin{figure}[H]
   \centering
@@
     $L_s$ & $L_t$ & $R_b$ & $R_m$ & $R_t$ & $\theta_{m}^{Pre}$ & $\theta_{m}^{Post}$ & $\theta_{b}$ & $\theta_{t}$ & $A_{ub}$ & $A_b$ & $c_t$ & $c_m$  &$c_b$\\ \hline
-    21.0nm & 22.0nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ & 90 & 2000 & 0.5 & 2.2  & 3.1\\ \hline
+    21.0nm & 11.15nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ &  &  &  &   & \\ \hline
   \end{tabular}
   \caption{Ideal parameters for model stepping.}{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
-  \label{final-parameter-table}
-\end{figure}
-
-\subsection{Histograms}
-
-%% \begin{figure}[h!]
-%%   \centering
-%%   \begin{minipage}[b]{0.45\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
-%%     \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
-%%   \end{minipage}
-%%   \hspace{.1cm}
-%%   \begin{minipage}[b]{0.45\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
-%%     \caption{Histogram of simulated stepping times using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
-%%   \end{minipage}
-%%   \label{fig:final-histograms}
-%% \end{figure}
+  \label{table:final-parameter-table}
+\end{figure}
+
+Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\
+
+\begin{figure}[H]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
+    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: make these figures compare better.}
+  \end{minipage}
+  \hspace{.1cm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
+    \caption{Histogram of simulated stepping times using ideal dynein parameters.}
+  \end{minipage}\\
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/weihong-step-size.pdf}
+    \caption{Experimental dynein step size from \cite{weihongpaper}.}
+  \end{minipage}
+  \hspace{.1cm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/weihong-velocity.pdf}
+    \caption{Experimental dynein step time from \cite{weihongpaper}}
+  \end{minipage}
+  \label{fig:final-histograms}
+\end{figure}
 
@@
 \subsubsection{Limitations}
-Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information,
-other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into
-account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be
-springy...
+Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy...
 

### 2017-03-30 thesis/latex/thesis.tex
Thesis: add work on intro. Also add figures-to-make list.

@@
 Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
+
+\subsection{Interest builder}
+Motor proteins are cellular structures which use chemical energy to do work and generate motion.
+Kinesin, myosin and dynein are the three main motor proteins in cells.
+Though these proteins have significantly different ancestors [cite], they all evolved into a single similar structure.
+In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem.
+How, then, do motor proteins work?\\
+
+The basic form is simple.
+Kinesin, myosin and dynein each have two foot domains which each alternatingly act as levers.
+One foot will bind to a surface and apply a force, levering the whole motor forward.
+This causes the other foot to bind and the cycle to repeat.
+This design is simple, but the ways each motor implement it are very different.
+Binding to the .........
+
+Dynein:
+feet which bind to track
+motor connected to feet which generates the force
+-----------
+ATP binding causes dissociation
+Also causes forward kick
+ATP hydrolysis
+rebinding causes ADP rejection and forward lurch
+restart
+
+Kinesin:
+feet which bind to track
+connected via lever arm to cargo binding domain
+-----------
+ATP binding causes forward kick
+ATP hydrolysis
+MT binding, ADP, Pi rejection
+Other foot unbinds
+
+Myosin:
+Feet which bind to track
+connected via lever arm to cargo binding domain
+----------
+actin binding causes Pi rejection, strengthening binding
+binding causes foot to change relative to lever, shifting the motor forward
+ATP binding causes dissocaition and undoing the powerstroke
+
+Todo:
+figure out how myosin works
+explain how the motors are all really similar in structure
+also how they're all kind of carnot-like engines which take in energy and do work
+explain how dynein is much more stochastic than kinesin, and how this is interesting, since it hints at a Brownian component, which isn't present in kinesin
+Talk about how confirming brownian component of the cycle would be good
 

### 2017-04-01 thesis/latex/thesis.tex
Thesis: minor additions.

@@
 The basic form is simple.
-Kinesin, myosin and dynein each have two foot domains which each alternatingly act as levers.
-One foot will bind to a surface and apply a force, levering the whole motor forward.
-This causes the other foot to bind and the cycle to repeat.
-This design is simple, but the ways each motor implement it are very different.
-Binding to the .........
+Kinesin, myosin and dynein each use two binding domains to attach to a surface.
+These binding domains are connected via a linker domain.
+Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface.
+In a cycle a binding domain will unbind from a surface, tense its foot to kick forward, rebind, then untense its foot to pull the whole motor forward.
+This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\
 

### 2017-04-01 thesis/latex/thesis.tex
Thesis: finish attn grabber.

--- 2017-03-29 thesis/latex/thesis.tex
@@
 Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
+
+\subsection{Interest builder}
+Motor proteins are cellular structures which use chemical energy to do work and generate motion.
+Kinesin, myosin and dynein are the three main motor proteins in cells.
+Though these proteins have significantly different ancestors [cite], they all evolved into a single similar structure.
+In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem.
+How, then, do motor proteins work?\\
+
+The basic form is simple.
+Kinesin, myosin and dynein each use two binding domains to attach to a surface.
+These binding domains are connected via a linker domain.
+Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface.
+In a single cycle a binding domain will unbind from a surface, tense its foot to kick forward, rebind, then untense its foot to pull the whole motor forward.
+This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\
+
+Although the three motor protein families operate using the same stepping cycle, their behavior differs significantly.
+Kinesin and myosin are predictable motors which step in the forwards direction with a regular step size [get kinesin, myosin stepping papers].
+In contrast, dynein's stepping pattern varies wildly in both size and direction.
+The motor steps forward on average, but takes steps backwards and to the side quite regularly \cite{weihongpaper}.
+How can motors which implement the same release, lever, bind, lurch stepping mechanism behave so differently?\\
+
+One possibility is that dynein's size and organization are responsible for the motor's odd stepping pattern.
+Dynein is much larger than kinesin or myosin, meaning its feet may need to move significantly further over each cycle.
+Due to the random nature of Brownian motion from water particle collisions, there may be significantly more variance in the path taken by dynein's feet compared to other motor feet.
+This could explain the large variance in step size.
+Another contributing factor could be that dynein is so large that it can twist and contort during its step, allowing varying and even backwards steps, which a small motor would be too tense to achieve.\\
+
+This thesis aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern.
+To do this, an artificial motor model is created which exhibits flexibility and is affected by Brownian motion.
+This model is then simulated, and its behavior are compared to the behavior of real dynein.
+
+%% Dynein:
+%% feet which bind to track
+%% motor connected to feet which generates the force
+%% -----------
+%% ATP binding causes dissociation
+%% Also causes forward kick
+%% ATP hydrolysis
+%% rebinding causes ADP rejection and forward lurch
+%% restart
+
+%% Kinesin:
+%% feet which bind to track
+%% connected via lever arm to cargo binding domain
+%% -----------
+%% ATP binding causes forward kick
+%% ATP hydrolysis
+%% MT binding, ADP, Pi rejection
+%% Other foot unbinds
+
+%% Myosin:
+%% Feet which bind to track
+%% connected via lever arm to cargo binding domain
+%% ----------
+%% actin binding causes Pi rejection, strengthening binding
+%% binding causes foot to change relative to lever, shifting the motor forward
+%% ATP binding causes dissocaition and undoing the powerstroke
 
@@
 Mention the Burgess paper, which says spring constants might change between apo/ADP states.
+Also dynein may move helically: Bidirectional helical motility of cytoplasmic dynein around microtubules
 

### 2017-04-04 thesis/latex/thesis.tex
Thesis: small touchup.

@@
 
-\subsection{Interest builder}
-Begin with a paper-like introduction which talks about:
-
-\begin{itemize}
-\item How dynein is a structure which turns chemical energy into motion
-\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
-\item How it's weird that a cellular structure can generate directed motion
-\item Other cool stuff - make dynein mysterious and cool.
-\end{itemize}
-
-Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
+%% \subsection{Interest builder}
+%% Begin with a paper-like introduction which talks about:
+
+%% \begin{itemize}
+%% \item How dynein is a structure which turns chemical energy into motion
+%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
+%% \item How it's weird that a cellular structure can generate directed motion
+%% \item Other cool stuff - make dynein mysterious and cool.
+%% \end{itemize}
+
+%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
 
@@
 
-This thesis aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern.
-To do this, an artificial motor model is created which exhibits flexibility and is affected by Brownian motion.
-This model is then simulated, and its behavior are compared to the behavior of real dynein.
+This thesis describes an experiment which aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern.
+To do this, a mathematical model of a dynein-like motor is constructed which exhibits flexibility and feels Brownian forces.
+This model is then simulated, and its behavior is compared to the behavior of real dynein.\\
 
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of dynein.}{Artist rendition of the dynein motor bound to a microtubule.
-One monomer is bound to the MT, and one is raised up.
-Modified.
-Source: Lander Lab, The Scripps Research Institute.}
+  \caption{Artist's rendition of dynein bound to a microtubule.}{One monomer is bound to the MT, and the other is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
   \label{dynein-artist-rendition}
@@
 Diffusion has two problems: it is slow and nondirected.
-The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \textbf{cite here}:
+The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \cite{einstein-paper}:
 
@@
 \end{equation}
-%% \myequations{some equation}
 

### 2017-04-04 thesis/latex/thesis.tex
Thesis: very small commit.

@@
 
-\subsubsection{What role does it play in the cell?}
+\subsubsection{What role does dynein play in the cell?}
 Some of dynein's primary roles in the cell are to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins.
-Dynein also plays a role in positioning and breaking down the nucleus, cell death, spindle formation and the placement of other important cellular structures \cite{valetoolbox}.
+Dynein also plays a role in positioning and breaking down the nucleus, cell death, spindle formation and the placement of other important cellular structures \cite{valetoolbox}.\\
 

### 2017-04-10 thesis/latex/thesis.tex
Make build.

@@
   \centering
-  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
+  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
@@
 \subsubsection{Limitations}
+The accuracy of correspondence between model dynein and physical dynein is very relevant when assessing the meaningfulness of the simulation results.
+Reducing a megaDalton weight protein to a five-coordinate kinematic model with springy hinges is bound to have low resolution.
+However, the point of this model is to predict gross stepping behavior over large timescales.
+Thus, only assumptions which possibly add large systematic errors to stepping behavior are of interest.
+These possible limitations are listed below.\\
+
+\paragraph{Spherical domains}
+Domain shape influences primarily the drag coefficients $\gamma$ of the model.
+These in turn affect the diffusion rate of different domains.
+Reducing domains to spheres adds a systematic error to the diffusion speed of each domain, which could bias step size.
+However, spring constants $c_b$, $c_m$ and $c_t$ also have an influence on the diffusion rate of spheres.
+Thus by fitting spring constants to the proper step length, the systematic error of domain size can be reduced -- ???\\
+
+-------------------------------------
 Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy...
@@
 Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
+-------------------------------------
 

### 2017-04-12 thesis/latex/thesis.tex

@@
 
+In reality, all molecules have a degree of elasticity.
+A dynein model by Sarlah \textit{et.
+al.} models the dynein stalk as an elastic rod \cite{sarlahpaper}.
+However, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.\\
+
 \subsubsection{Angular springs}
@@
 
-\paragraph{Spherical domains}
 Domain shape influences primarily the drag coefficients $\gamma$ of the model.
@@
 Thus by fitting spring constants to the proper step length, the systematic error of domain size can be reduced -- ???\\
+
+Treating the conformational dynamics of the domains as harmonic energies is a simplification, but
 

### 2017-04-12 thesis_stuff/thesis_stuff.tex

@@
 
-\subsection{}
-
 \subsection{Pre-powerstroke structure, linker remodel details}
@@
 Also, the paper says that axonemal dyneins have multiple motor domains, i.e aren't dimers, so that changes the results from the Lin paper. The binding angle is probably valid, though.\\
+
+\subsection{Chemical Basis of Morphogenesis}
+Turing paper on how asymmetry comes about in biology\\
+
+\subsection{Coarge-grained modeling of the structural states and transition underlying the powerstroke of dynein motor domain}
+Models six AAA+ domains, CC, C-term, pre/post-powerstroke\\
+
+Modelling the motor domain, using the post-powerstroke crystal structure, and using ``normal mode analysis'' to create a fluid transition into the pre-powerstroke state.
+This involves taking a crystal structure and somehow calculating the number of normal mode angle changes necessary to get it from one state to another.\\
+
+MD is hard on molecular motors, because their kinetic timescale is fairly slow.\\
+
+Discusses Elastic Network Model - treating atoms as springs, then finding low-frequency normal modes of the whole protein\\
+
+Choosing just a couple modes gets lots of information
 

### 2017-04-12 thesis/latex/thesis.tex
Thesis: minor commit.

--- 2017-04-04 thesis/latex/thesis.tex
@@
 
-As shown in \ref{dynein-artist-rendition-2}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
+As shown in the crystal structure in Figure XXX, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
 Each of these subunits has a unique purpose for the motor.
@@
 
+This could be fixed up...probably remove multiple of these sections
+
 \subsubsection{How does it behave?}
-Talk about its stepping behavior using Weihong's figures (as well as the new paper David found?)\\
-
-Also possibly talk about the other things Dynein has been found to do, such as hydrolyse ATP and move its subdomains around.
-This may be better in a different section than the introduction though, since its a lot of biochemistry for the second section in an intro?
-maybe not, it has to go somewhere.
+Dynein's stepping pattern is distinct from its partner, kinesin. Kinesin takes very precise 8-nm steps \cite{kinesin-step-size}. In contrast, dynein takes a large range of steps, as shown in Figure \\
 
@@
 
+In reality, all molecules have a degree of elasticity.
+A dynein model by Sarlah \textit{et.
+al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.
+However, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.\\
+
 \subsubsection{Angular springs}
@@
 Side stepping of dynein is ignored in this model.
-Stepping perpendicular to the MT occurs in dynein \cite{weihongppaer}, as shown in Figure \ref{fig:weihong-side-stepping}.
+Stepping perpendicular to the MT occurs in dynein \cite{weihongpaper}, as shown in Figure \ref{fig:weihong-side-stepping}.
 This model assumes it is a symptom, and not an influencer of, of dynein's forward-backward stepping mechanism.
@@
 
+\textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
+
 \subsubsection{Fitting spring constants}
@@
 
-\section{Chapter: Results}
+\section{Chapter: Results \& Discussion}
+\subsection{Stepping behavior of fit model}
 The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\
@@
 
-\section{Chapter: Discussion}
+Do our spring constants seem to indicate that the protein does about one ATP's worth of work through its cycle? I wonder if the motor cools down its surroundings when it walks...\\
+
+Our project un/successfully predicted how dynein behaved.
+How would we modify it to describe kinesin?
+Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion?
+This would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility and get its crystal structure to do some comparisons.
+
+\subsection{Next Steps}
 \subsubsection{Limitations}
-Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy...
+
+-------------------------------------
+Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy, 2D model...
 
@@
 Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
-
-\subsection{Future work on this project}
-If setbacks happen, this'll be a big section.
-Or, further simulations which could be done.
-Namely taking our model and giving it lots more states and seeing if this model even better fits experimental data.\\
-
-\subsubsection{Experiments to verify our model}
-Talk about how FRET could be used to verify our model. We have domain distance info over long
-timescales in our model - this is something we could compare to a FRET experiment exploring
-the distance between domains in dynein.\\
+-------------------------------------
+
+\subsubsection{Improvements to model}
+
+\subsubsection{\textit{Experiments to verify our model}}
+Talk about how FRET could be used to verify our model.
+We have domain distance info over long timescales in our model - this is something we could compare to a FRET experiment exploring the distance between domains in dynein.\\
 
@@
 
-Do our spring constants seem to indicate that the protein does about one ATP's worth of work through its cycle? I wonder if the motor cools down its surroundings when it walks...\\
-
-Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using
-vanadium? Maybe...\\
-\subsection{Possible further projects}
-\subsection{Difference between dynein and kinesin}
-Our project un/successfully predicted how dynein behaved. How would we modify it to describe kinesin?
-Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion? This
-would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility
-and get its crystal structure to do some comparisons.
+Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using vanadium? Maybe...\\
+
+\section{Conclusion}
+Does anything actually go here?
 

### 2017-04-19 thesis/latex/thesis.tex

@@
 
-\subsubsection{Why is dynein special and interesting?}
-Compare the processive motion of dynein to kinesin in \textbf{a.)} directionality, \textbf{b.)} stepping pattern and \textbf{c.)} size (like how it can step over roadblocks kinesin cannot).\\
-
-Talk about why a random stepping motor is interesting compared to a orderly-stepping motor: what is different about dynein's structure that makes it step differently?
-Compare the crystal structures and ask lots of questions.
-Build interest in the motors here.\\
+\subsubsection{Why is dynein interesting?}
+Studying how nature creates directed motion is interesting in itself.
+Another interesting question is how, given the large number of similarities between motors kinesin and dynein, does dynein achieve such a radically different stepping pattern than kinesin?
+Elucidating how the structural differences between the motors give rise to the differences in dynamics would provide lots of important information on how the machines fine-tune their stepping.\\
+
+The major difference between kinesin and dynein is their size.
+Kinesin proteins are generally 100-200 kD in mass, whereas dynein is roughly 1mD.
+As shown in Figure \ref{fig:kinesin-vs-dynein}, the size and volume differences between proteins is very apparent.
+Dynein is about 20nm from MTBD to tail, whereas kinesin is ----.
+Another key difference is the separation between active sites on either protein.
+Kinesin binds to the MT with a foot domain, colored blue in Figure \ref{fig:kinesin-vs-dynein}.
+It hydrolyzes ATP at the residues colored pink.
+The separation between these domains is roughly ---nm.
+In contrast, Dynein binds to the MT with its MTBD, colored blue, and hydrolyses ATP in its motor domain, residues colored pink.
+This distance is close to 20nm in length - much longer than kinesin.
+Another difference is the way the motors interact with the microtubule.
+Both motors bind to the MT using domains.
+However, for dynein the motor-MTBD-MT angle is ---, whereas for kinesin, it is ---.\\
+
+Despite these differences, the two motors implement very similar chemical cycles to achieve motion.
+Both motors begin bound to the microtubule, then bind ATP, causing them to lift one foot off.
+They then hydrolyse the ATP, causing their feet to kick forward and rebind.
+They then
 
@@
 %%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
-%%   \caption{Crystal structures of cytoplasmic dynein 1 and kinesin KIF5B (PDB IDs 4RH7 and 1BG2).}
-%%   \label{kin_n_dyn}
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/kinesin-vs-dynein}
+%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
+%%   \label{fig:kinesin-vs-dynein}
 %% \end{figure}
-
-\textit{make this figure good -- find a full length kinesin crystal structure, not 1BG2. Use kindyn.pse as a template.}
 

### 2017-04-25 thesis/latex/thesis.tex
Thesis: stuff.

@@
-\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt
+\documentclass[defaultstyle,11pt]{article}
+%% \documentclass[defaultstyle,11pt]{thesis}
 
@@
 
+%% \title{Simulating a Brownian model of the dynein motor protein}
+%% \author{E. L.}{Capek}
+
+%% \otherdegrees{B.A., North Dakota State University, 2005 \\
+%% 	      M.S., University of Reno, 2007}
+
+%% \degree{Doctor of Philosophy}		%  #1 {long descr.}
+%% 	{Ph.D., Rocket Science}		%  #2 {short descr.}
+
+%% \dept{Department of}			%  #1 {designation}
+%% 	{Rocket Science}		%  #2 {name}
+
+%% \advisor{Prof.}				%  #1 {title}
+%% 	{Ed Visor}			%  #2 {name}
+
+%% \reader{Prof.~Rachel Goddard}		%  2nd person to sign thesis
+%% \readerThree{Ms.~Thora Nea}		%  3rd person to sign thesis
+
+%% \abstract{Yet to come.}
+
+%% \dedication{Yet to come.}
+
+%% \acknowledgements{Yet to come.}
+
 \begin{document}
@@
 However, as per the above quote, diffusive processes cannot create this asymmetry.
-How then do cells create heterogeneity?
+How then do cells create heterogeneous structures they need in order to exist?
 Motor proteins are part of the answer.
 Motor proteins are structures which use energy to create directed motion in cells.
-In broad terms, they are creators of asymmetry.
+In broad terms, they are mechanical creators of asymmetry.
 This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\
@@
 
-\subsection{Interest builder}
+\subsection{Motivation}
 Motor proteins are cellular structures which use chemical energy to do work and generate motion.
 Kinesin, myosin and dynein are the three main motor proteins in cells.
-Though these proteins have significantly different ancestors [cite], they all evolved into a single similar structure.
+Though these proteins have significantly different ancestors \ref{cite}, they all evolved into a single similar structure.
 In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem.
@@
 Despite these differences, the two motors implement very similar chemical cycles to achieve motion.
-Both motors begin bound to the microtubule, then bind ATP, causing them to lift one foot off.
-They then hydrolyse the ATP, causing their feet to kick forward and rebind.
-They then
+Both feet begin bound to the microtubule, then one unbinds.
+This foot diffuses forward, then rebinds to the microtubule
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
-    \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
-  \end{minipage}
-  \hspace{.2cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
-    \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
-  \end{minipage}
-  \label{fig:equipartition_agreement}
-\end{figure}
-
 \textbf{would it be a stronger test to also calculate the standard deviation of <PE>?
@@
 
+\textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
+
+\subsubsection{Fitting spring constants}
+This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
+
+\newpage
+\section{Chapter: Results \& Discussion}
+\subsection{Validating model}
+The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
+Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over time.\\
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
+    \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
+  \end{minipage}
+  \hspace{.2cm}
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
+    \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
+  \end{minipage}
+  \label{fig:equipartition_agreement}
+\end{figure}
+
+\subsection{Exploring the parameter space}
+Once validated, the model was fit to experimental data.
+Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values.
+The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment.
+As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.
+
 \begin{figure}[H]
@@
   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
-Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
+Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.
+The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right.
+Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
   \label{fig:kb-kub-heatmap}
@@
 
-\textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
-
-\subsubsection{Fitting spring constants}
-This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
-
-\section{Chapter: Results \& Discussion}
 \subsection{Stepping behavior of fit model}

### 2017-04-26 thesis/latex/thesis.tex
Thesis: Add a bit of changes to Results.

@@
 
-\subsection{Exploring the parameter space}
-Once validated, the model was fit to experimental data.
-Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values.
-The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment.
-As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.
+\subsection{Model achieves processivity}
+At certain input parameters, the model can successfully take steps.
+Figure \ref{fig:stepping-ghosts} shows snapshots of the model at various times throughout a simulation.
+The model steps back and forth, taking both forwards and backwards steps.\\
 
@@
   \centering
-  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
-  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
-Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.
-The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right.
-Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
-  \label{fig:kb-kub-heatmap}
-\end{figure}
-
-\subsection{Stepping behavior of fit model}
-The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\
+  \includegraphics[width=\textwidth]{../../figures/stepping-ghosts}
+  \caption{Snapshots of model over the course of a simulation.
+Bothbound states are depicted immediately after binding events.
+Onebound states depict the conformation with the highest unbound binding domain between binding events.
+Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
+  \label{fig:stepping-ghosts}
+\end{figure}
+
+More detailed stepping information is shown in Figure \ref{fig:stepping-trajectory}. The model steps both forwards and backwards, but has a definite forward bias.
 
@@
   \centering
-  \begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
-    \hline
-    $L_s$ & $L_t$ & $R_b$ & $R_m$ & $R_t$ & $\theta_{m}^{Pre}$ & $\theta_{m}^{Post}$ & $\theta_{b}$ & $\theta_{t}$ & $A_{ub}$ & $A_b$ & $c_t$ & $c_m$  &$c_b$\\ \hline
-    21.0nm & 11.15nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ &  &  &  &   & \\ \hline
-  \end{tabular}
-  \caption{Ideal parameters for model stepping.}{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
-  \label{table:final-parameter-table}
-\end{figure}
-
+  \includegraphics[width=\textwidth]{../../figures/stepping-trajectory}
+  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
+  \label{fig:stepping-trajectory}
+\end{figure}
+
+--------------------------
 Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\
@@
 This would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility and get its crystal structure to do some comparisons.
+
+\subsection{Current work: Refining model parameters}
+Once validated, the model was fit to experimental data.
+Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values.
+The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment.
+As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
+  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
+Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.
+The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right.
+Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
+  \label{fig:kb-kub-heatmap}
+\end{figure}
 

### 2017-04-26 thesis/latex/thesis.tex
Add y-trajectory plot.

@@
 
-More detailed stepping information is shown in Figure \ref{fig:stepping-trajectory}. The model steps both forwards and backwards, but has a definite forward bias.
+More detailed stepping information is shown in Figure \ref{fig:stepping-x-trajectory}.a.
+The model steps both forwards and backwards, but has a definite forward bias.
+The model's behavior can be contrasted with experimental behavior in Figure \ref{fig:stepping-trajectory}.b.
+The two trajectory plots look very different, but share major key features: forwards and backwards steps, a directional bias, and varying step sizes.
+At a minimum, the two-state stepping model
 
@@
   \centering
-  \includegraphics[width=\textwidth]{../../figures/stepping-trajectory}
+  \includegraphics[width=\textwidth]{../../figures/stepping-x-trajectory}
   \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
-  \label{fig:stepping-trajectory}
-\end{figure}
-
---------------------------
-Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\
+  \label{fig:stepping-x-trajectory}
+\end{figure}
+
+\subsection{Model steps reasonably}
 
@@
 
+\subsection{Model does not drag as it steps}
+The model lifts its foot up and lowers it as it is about to step; it doesn't drag along the microtubule searching for the binding site.
+This behavior is shown in Figure \ref{fig:stepping-y-trajectory}.\\
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{../../figures/stepping-y-trajectory}
+  \caption{Unbound binding domain position over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
+  \label{fig:stepping-y-trajectory}
+\end{figure}
+
 Do our spring constants seem to indicate that the protein does about one ATP's worth of work through its cycle? I wonder if the motor cools down its surroundings when it walks...\\
@@
 
+\section{Conclusion}
+
 \subsection{Next Steps}
@@
 Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using vanadium? Maybe...\\
-
-\section{Conclusion}
-Does anything actually go here?
 

### 2017-04-30 dynein_simulate.cpp
Remove old variable-ts code from project.

@@ -74,33 +74,12 @@ void simulate(double runtime, double rand_seed, State init_state, double* init_p
 	printf("Running for %g s\n", runtime);
   }
 
-  if (using_variable_timestep) {
-    variable_ts_checkpoint_onebound = (Dynein_onebound*) malloc(sizeof(Dynein_onebound));
-    variable_ts_checkpoint_bothbound = (Dynein_bothbound*) malloc(sizeof(Dynein_bothbound));
-    variable_ts_checkpoint_time = 0;
-    variable_ts_stepping_print_buffer = (char*) malloc(4096*sizeof(char));
-    variable_ts_stepping_print_buffer[0] = 0;
-    variable_ts_stepping_print_buffer_index = 0;
-    variable_ts_base_dt = dt;
-    variable_ts_rewinding_state = false;
-  }
-
   double near_unbinding_prob_printing_average = 0;
   int unbinding_prob_printing_n = 0;
 
   while( t < runtime or run_indefinite) {
     if (current_state == NEARBOUND or current_state == FARBOUND)
       while (t < runtime or run_indefinite) { // loop as long as it is onebound
-	if (using_variable_timestep and t > variable_ts_checkpoint_time + variable_ts_checkpoint_interval) { // if we are due for a new checkpoint
-	  variable_ts_checkpoint_time = t;
-	  if (dyn_ob != NULL) memcpy(variable_ts_checkpoint_onebound, dyn_ob, sizeof(Dynein_onebound));
-	  if (dyn_bb != NULL) memcpy(variable_ts_checkpoint_bothbound, dyn_bb, sizeof(Dynein_bothbound));
-	  fprintf(variable_ts_stepping_data_file, "%s", variable_ts_stepping_print_buffer);
-	  variable_ts_stepping_print_buffer_index = 0;
-	  variable_ts_rewinding_state = false;
-	  dt = variable_ts_base_dt;
-	}
-
         if (am_debugging_time) printf("\n==== t = %8g/%8g ====\n", t, runtime);
 	
         double unbinding_prob = dyn_ob->get_unbinding_rate()*dt;
@@ -148,35 +127,11 @@ void simulate(double runtime, double rand_seed, State init_state, double* init_p
 	    printf("Onebound velocity calculation generated a NaN, exiting.\n");
 	    exit(1);
 	  }
-
[…]

### 2017-04-30 dynein_struct_bothbound.cpp

@@ -440,13 +440,7 @@ int Dynein_bothbound::update_velocities() {
     if (nmy < -1.5 or ty < -1.5 or fmy < -1.5) {
       printf("A domain is under the MT! nmy, ty, fmy: %g, %g, %g\n", nmy, ty, fmy);
       if (am_only_writing_on_crash) on_crash_write_movie_buffer();
-      if (using_variable_timestep) {
-	printf("Going to last checkpoint.\n");
-	return VARIABLE_TS_REWIND_RETURN;
-      }
-      else {
-	exit(1);
-      }
+      exit(1);
     }
   }
 
@@ -639,7 +633,7 @@ int Dynein_bothbound::update_velocities() {
 
   if (am_debugging_nans) printf("d_Ln is %g\n", d_Ln);
   if (am_debugging_nans) printf("d_Lf is %g\n--------------\n", d_Lf);
-  return RETURN_OKAY;
+  return 0;
 }
 
 double Dynein_bothbound::get_near_unbinding_rate() {

### 2017-04-30 trajectory-plt.py

@@ -1,58 +1,0 @@
-#! /usr/bin/env python2.7
-
-import numpy as np
-import time, signal, sys, os, matplotlib, subprocess
-
-if 'show' not in sys.argv:
-    matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-
-tail = 'tail' in sys.argv
-
-usage = '''
-Usage: python2 TITLE %s [show] [tail]"
-       show: show animation in a window while generating movie
-	     omitting show makes %s faster but less exciting to watch
-''' % (sys.argv[0], sys.argv[0])
-
-if len(sys.argv) < 2:
-  print usage
-  sys.exit(1)
-
-data_filename = sys.argv[1]
-title = data_filename[data_filename.index("data/")+5:-4]
-
-if tail:
-    data = np.genfromtxt(data_filename, delimiter="\t", invalid_raise=False, skip_header=skiplen)
-else:
-    data = np.genfromtxt(data_filename, delimiter="\t", invalid_raise=False)
-
-if tail and sys.stdin.isatty():
-    skiplen = sum(1 for line in open(data_filename)) - 100
-    if skiplen < 0:
-	skiplen = 1
-
-if len(data) == 0:
-       print "Very short run!"
-       exit(1)
-
-nbxs = data[:,7]
-fbxs = data[:,15]
-
-x_min = np.min([np.min(nbxs), np.min(fbxs)])
-x_max = np.max([np.max(nbxs), np.max(fbxs)])
-
-plt.title("Trajectories of two feet")
-plt.xlabel("time (s)")
-plt.ylabel("foot position")
-
-plt.gca().set_ylim(x_min-1,x_max+1)
-
-plt.plot(nbxs, label="nbx")
-plt.plot(fbxs, label="fbx")
-
-plt.legend()
-plt.tight_layout()
-
-os.system('mkdir -p plots')
-plt.savefig("plots/x-trajectory-" + title + ".pdf")

### 2017-04-30 trajectory-y-plt.py

@@ -47,12 +47,12 @@ for i in range(timesteps):
         fbys[i] = data[i,16]
     elif int(data[i,0]) == 1:
         nbys[i] = data[i,16]
-    times[i] = data[i,1]
+    times[i] = data[i,1]*1000
 
 y_min = np.min([np.min(nbys), np.min(fbys)])
 y_max = np.max([np.max(nbys), np.max(fbys)])
 
-plt.xlabel("time (s)")
+plt.xlabel("time (ms)")
 plt.ylabel("binding domain y-projection (nm)")
 
 plt.gca().set_ylim(y_min-1,y_max+1)

### 2017-04-30 thesis/latex/thesis.tex
Remove old variable-ts code from project.
Improve how thesis figures are generated.

@@
   \centering
-  \includegraphics[width=\textwidth]{../../figures/stepping-ghosts}
+  \includegraphics[width=0.2\textwidth]{../../plots/stepping-ghost}
   \caption{Snapshots of model over the course of a simulation.
@@
   \centering
-  \includegraphics[width=\textwidth]{../../figures/stepping-x-trajectory}
+  \includegraphics[width=0.5\textwidth]{../../plots/x-trajectory_thesis}
+  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
   \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
@@
   \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
-    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: make these figures compare better.}
-  \end{minipage}
-  \hspace{.1cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
-    \caption{Histogram of simulated stepping times using ideal dynein parameters.}
-  \end{minipage}\\
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/weihong-step-size.pdf}
-    \caption{Experimental dynein step size from \cite{weihongpaper}.}
-  \end{minipage}
-  \hspace{.1cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/weihong-velocity.pdf}
+    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
+    \includegraphics[width=0.5\textwidth]{../../plots/stepping_time_histogram_thesis}
+    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}%%
+    \includegraphics[width=0.5\textwidth]{../../figures/weihong-velocity.pdf}
     \caption{Experimental dynein step time from \cite{weihongpaper}}
-  \end{minipage}
     \label{fig:final-histograms}
@@
   \centering
-  \includegraphics[width=\textwidth]{../../figures/stepping-y-trajectory}
+  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
   \caption{Unbound binding domain position over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}

### 2017-04-30 thesis/latex/thesis.tex
Add input parameters to thesis.

@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.2\textwidth]{../../plots/stepping-ghost}
-  \caption{Snapshots of model over the course of a simulation.
-Bothbound states are depicted immediately after binding events.
-Onebound states depict the conformation with the highest unbound binding domain between binding events.
-Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
-  \label{fig:stepping-ghosts}
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| l | l | l | l | l |}
+    \hline
+    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$\\\hline
+    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$\\ \hline
+  \end{tabular}
+  \caption{Parameters used in simulations.}
+  \label{table:thesis-parameters}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
-    \includegraphics[width=0.5\textwidth]{../../plots/stepping_time_histogram_thesis}
-    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}%%
-    \includegraphics[width=0.5\textwidth]{../../figures/weihong-velocity.pdf}
-    \caption{Experimental dynein step time from \cite{weihongpaper}}
+    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
+    \caption{Model vs experimental step sizes.
+\textbf{a.)} Step sizes model took at parameters in \ref{table:thesis-parameters}.
+\textbf{b.)} Experimental stepping behavior of dynein \cite{weihongpaper}.}
     \label{fig:final-histograms}

### 2017-05-02 thesis/latex/thesis.tex
Thesis: Add title and abstract.

@@
 
-\titleformat{\paragraph}
-{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-\titlespacing*{\paragraph}
-{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+%% \titleformat{\paragraph}
+%% {\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+%% \titlespacing*{\paragraph}
+%% {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
 
@@
 
+% Format of the section titles
+\titleformat{\section}{\color{headings}
+\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]
+
+\title{Simulating dynein's powerstroke using Brownian dynamics}
+\author{Elliott Capek}
+\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles
+
 \usepackage{csquotes}
@@
 
+\maketitle{}
 \tableofcontents
@@
 \newpage
+
+\textbf{Abstract}
+\blockquote{Dynein is a motor protein which uses cellular energy to transport cargo around the cell.
+Like related motor proteins kinesin and myosin, dynein uses ATP bond breaking to alternatingly kick its two foot domains forward and generate motion.
+Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60\textit{nm} in both the forwards and backwards directions.
+It is believed that dynein takes broad, stochastic steps because it is large and has several elastic regions, making it more affected by Brownian motion.
+To test this, we model the motor as a 2D system of springy hinges, then simulate this model using Brownian dynamics.
+Preliminary results indicate such a model is capable of taking steps between 0 and 25nm.
+These results give hope that, with further tweaking, the model may be able to generate both larger and backwards steps.}
 

### 2017-05-02 run_scripts/generate-thesis-data.py

@@ -8,7 +8,7 @@ simrunner.avoid_slurm = True
 
 basename = simrunner.run_sim(**{"k_b": 1e18, "k_ub": 1e20, "cb": 2.0, "cm": 2.0, "ct": 1.0, "dt": 1e-10, "label": l,
                                 "seed": 8,
-                                "runtime": 1e-2,
+                                "runtime": 1e-4,
                                 "constant-write": True,
                                 "no-slurm": True})
 

### 2017-05-02 thesis/latex/thesis.tex
Add results section. Todo: think about Next Steps part (heat map?)

@@
 These results give hope that, with further tweaking, the model may be able to generate both larger and backwards steps.}
+
+\textbf{Keywords}: Dynein, powerstroke, Brownian dynamics, coarse-grained, dynamics simulation\\
 
@@
 \subsubsection{Conformational tests}
+\label{sec:conformational-tests}
 The models were tested in the following different conformations to verify they behaved as expected:\\
@@
 \subsubsection{Energy conservation}
+\label{sec:energy-conservation}
 To verify that the magnitudes of forces are calculated properly, a conservation of energy test was performed.
@@
 The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
-Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over time.\\
+Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over a long time.
+This is evidence that both the forces and velocities of the model are properly calculated.
+Grossly inncorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy.
+The model's force calculations are further validated in Section \ref{sec:conformational-tests}, and energy conservation is validated in Section \ref{sec:energy-conservation}.\\
 
@@
 \subsection{Model achieves processivity}
-At certain input parameters, the model can successfully take steps.
-Figure \ref{fig:stepping-ghosts} shows snapshots of the model at various times throughout a simulation.
-The model steps back and forth, taking both forwards and backwards steps.\\
+When run at the proper parameters, the dynein model can step processively.
+Figure \ref{fig:stepping-trajectory} shows the dynamics of a motor when run at the parameters shown in Table \ref{table:thesis-parameters}.
 
@@
   \centering
-  \begin{tabular}{| l | l | l | l | l |}
+  \begin{tabular}{| l | l | l | l | l | l |}
     \hline
-    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$\\\hline
-    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$\\ \hline
+    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
+    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
   \end{tabular}
-  \caption{Parameters used in simulations.}
+  \caption{Parameters used in processive simulations in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
   \label{table:thesis-parameters}
 \end{figure}
-
-More detailed stepping information is shown in Figure \ref{fig:stepping-x-trajectory}.a.
-The model steps both forwards and backwards, but has a definite forward bias.
-The model's behavior can be contrasted with experimental behavior in Figure \ref{fig:stepping-trajectory}.b.
-The two trajectory plots look very different, but share major key features: forwards and backwards steps, a directional bias, and varying step sizes.
-At a minimum, the two-state stepping model
 
@@
   \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
-  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
-  \label{fig:stepping-x-trajectory}
-\end{figure}
-
-\subsection{Model steps reasonably}
+  \caption{Near and far binding domains over the course of several microseconds of simulation.
+Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
+  \label{fig:stepping-trajectory}
+\end{figure}
+
+Figures \ref{fig:stepping-trajectory}.b and \ref{fig:stepping-trajectory}.c demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time.
+This behavior indicates that a springy hinge model with shifting equilibrium angles is capable of generating processive stepping behavior.
+Now that the model has demonstrated stepping behavior, it must be seen if it can generate steps at a size- and time-scale similar to that which real dynein takes in experiment.\\
+
+Another important determination from Figure \ref{fig:stepping-trajectory}.c is the average position of the unbound foot is about 30\textit{nm} above the microtubule.
+This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible.
+However, it does initially suggest how dynein searches for the microtubule.
+Instead of hovering near the microtubule looking for a binding site, the motor pulls its foot away from the microtubule, diffusing until pushed downward far enough to bind.
+This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30\textit{nm} would allow significant x-diffusion along the microtubule.
+This could be contrasted with kinesin, which is smaller and could not move its foot so high off the microtubule.\\
+
+Importantly, the physical parameters causing processive motion are reasonable physically.
+The spring constants are roughly the same size as the energy of hydrolysis of ATP, which is reasonable.
+By a very rough argument, the dynein must move its tail angle by roughly one radian to diffuse enough for a step.
+This would correspond to a $\Delta G_{spring} = \frac{1}{2}c_t\Delta \theta_t \approx \Delta G_{ATP}$, which is very reasonable.
+In addition, the tail spring constant is less than the motor and binding spring constants, which is in line with the notion that the tail is much more elastic than the motor or binding domains.
+CITE\\
+
+\subsection{Model step size is highly variant}
+Figure \ref{fig:final-histograms}.a shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}.
+This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\
 
@@
 
-\subsection{Model does not drag as it steps}
-The model lifts its foot up and lowers it as it is about to step; it doesn't drag along the microtubule searching for the binding site.
-This behavior is shown in Figure \ref{fig:stepping-y-trajectory}.\\
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
-  \caption{Unbound binding domain position over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
-  \label{fig:stepping-y-trajectory}
-\end{figure}
-
-Do our spring constants seem to indicate that the protein does about one ATP's worth of work through its cycle? I wonder if the motor cools down its surroundings when it walks...\\
-
-Our project un/successfully predicted how dynein behaved.
-How would we modify it to describe kinesin?
-Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion?
-This would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility and get its crystal structure to do some comparisons.
-
-\subsection{Current work: Refining model parameters}
-Once validated, the model was fit to experimental data.
+Figure \ref{fig:final-histograms}.a shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
+This is a very important result, since it indicates that the model is capable of taking a varied step size.
+This behavior is characteristic of dynein, and hence very important to reproduce.\\
+
+The preference for $<5nm$ steps is very un-dynein-like.
+One explanation is that steps may be defined differently between experimental and modeled dynein.
+In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram.
+This may not be how the experiment in \ref{fig:final-histograms}.b records steps.
+Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely.
+A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out.
+This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\
+
+The ability of the model to generate near-experiment stepping behavior is imperative if the model is to be considered a proper explanation of dynein's stepping.
+In the case that changing the binding rate does not remove the small-step preference of the model, it may be necessary to change how the model works.
+For example, using the total spring-energy-of-binding change to calculate the binding probability may be invalid, or perhaps the entire two-state model will need to be thrown out.
+The inability of either of these assumptions to predict dynein's behavior would themselves be important findings.\\
+
+Another issue with the simulated histogram is that it shows no steps over $30nm$.
+This is a problem, since taking $40+nm$ steps is characteristic of dynein.
+Ideally, tuning the parameters of dynein would increase the step size.
+However, in the case that it can't, this might be an important result.
+The current model assumes connections between domains are rigid.
+This may not be a valid assumption, since the coiled coil region connecting the binding and motor domains has some elasticity to it CITE.
+Thus it may be necessary to add in elasticity to the model to reproduce long steps.\\
+
+Comparing the simulation results in \ref{fig:final-histograms}.a with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein.
+However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein.
+It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically.
+Lowering the binding rate may even out the histogram and prevent instant rebinding.
+It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm.
+Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\
+
+%% \subsection{Current work: Refining model parameters}
+%% Once validated, the model was fit to experimental data.
 Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
-  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
+%% \begin{figure}[H]
+%%   \centering
+%%   \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
+%%   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
 Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.
@@
 Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
-  \label{fig:kb-kub-heatmap}
-\end{figure}
+%%   \label{fig:kb-kub-heatmap}
+%% \end{figure}
 

### 2017-05-03 thesis/latex/thesis.tex
Thesis: change abstract to be more detailed+informative, but also more complicated. It'll need some simplificaiton.

@@
 \textbf{Abstract}
-\blockquote{Dynein is a motor protein which uses cellular energy to transport cargo around the cell.
-Like related motor proteins kinesin and myosin, dynein uses ATP bond breaking to alternatingly kick its two foot domains forward and generate motion.
+\blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell.
+Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
 Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60\textit{nm} in both the forwards and backwards directions.
-It is believed that dynein takes broad, stochastic steps because it is large and has several elastic regions, making it more affected by Brownian motion.
-To test this, we model the motor as a 2D system of springy hinges, then simulate this model using Brownian dynamics.
-Preliminary results indicate such a model is capable of taking steps between 0 and 25nm.
-These results give hope that, with further tweaking, the model may be able to generate both larger and backwards steps.}
+It is believed that dynein takes such broad, stochastic steps because of its large size and several elastic regions, which make it more influenced by Brownian motion.
+To test this diffusion-dominated hypothesis for dynein stepping, we create a minimal model of dynein with elastic regions which feels Brownian forces, and simulate the model's stepping behavior in a cellular environment.
+The model treats dynein's domains as ``point hinges'' connected by rigid rods, and accomplishes steps by changing the openness of its hinges.
+The model's behavior is found using Brownian dynamics equations.
+Preliminary data indicate such a model is capable of taking steps between 0 and 25nm.
+These results affirm that the Brownian hinge model of dynein is capable of stepping, and give hope that, with further tweaking, the model may be able to generate both larger and backwards steps, supporting the notion of a diffusion-dominated dynein step.}
 

### 2017-05-03 thesis/latex/thesis.tex
Thesis: Add most of Conclusion section.

@@
 \section{Conclusion}
-
-\subsection{Next Steps}
-\subsubsection{Limitations}
-
--------------------------------------
-Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy, 2D model...
-
-Mention the Burgess paper, which says spring constants might change between apo/ADP states.
-Also dynein may move helically: Bidirectional helical motility of cytoplasmic dynein around microtubules
-
-Computational limitations: Our project is computational, not experimental.
-Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
--------------------------------------
-
-\subsubsection{Improvements to model}
-
-\subsubsection{\textit{Experiments to verify our model}}
-Talk about how FRET could be used to verify our model.
-We have domain distance info over long timescales in our model - this is something we could compare to a FRET experiment exploring the distance between domains in dynein.\\
-
-Other biophysics experiments which could verify our model?\\
-
-Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using vanadium? Maybe...\\
+\subsection{Findings}
+The most important findings of this work are that a springy hinge model of dynein can take steps of a similar size to real dynein.
+What's more, it is likely further tweaking of the model will improve the model's behavior to the point of generating backwards and large steps.
+This would be a very important result which would strongly support the linker-swing/diffusive-step model of dynein stepping and guide further research.\\
+
+Many studies have been done on dynein, resulting in a large body of literature about the motor's behavior and features.
+Sifting through this information to find what is important for the motor's step is a difficult task.
+Mutational studies can remove traits of the motor, deducing what traits are necessary for stepping.
+However, this process is slow, and it can be difficult to remove large traits of the motor while keeping the engineered dynein representative of the natural motor.
+This is where simulations come in.
+Minimal features can be put into a physical model, which can then be tested for behavior similar to real dynein.
+In this study, we created a mathematical model which simplifies the motor to a rigid hinge structure with harmonic spring energies between the hinges.
+The equilibrium angles change dynamically to reflect structural changes during dynein's mechanochemical cycle.
+The model was then subjected to Brownian forces and evolved.
+If the model generates a stepping pattern similar to real dynein, this would demonstrate that dynein can be thought of as a rigid hinged structure.
+This would mean that many other traits of dynein may not be vital for stepping, such as stalk elasticity \cite{sarlahmodel}, motor-motor interaction \cite{sarlahmodel}, nucleotide state \cite{cianfroccoreview}, nucleotide state of non-AAA1 nuclease sites \cite{cianfroccoreview}, and changing stiffness of the foot domain \cite{burgess-paper}.
+Thus future research may want to focus more on linker swing and binding interactions, and less on these other traits.\\
+
+Other findings cast doubt on some aspects of the model.
+The vast preference of the model for $<5nm$ steps suggests that the model may handle binding events unlike real dynein.
+When binding, the total spring energy of the transition from a onebound to a bothbound state is calculated, then used to calculate the likelihood of transition via a Boltzmann factor.
+This approach may be overly simple, or take into account the wrong information.
+It may be that it is necessary to expand the two-state model into a three-state model with a low-microtubule-affinity onebound state immediately after unbinding, to prevent instant rebinding.
+This state would eventually transition to the high-microtubule-affinity state after some time.
+If this proves to be necessary to decrease small steps, this would be an interesting result showing that the motor might rely on its low-microtule-affinity ADP-Pi state to prevent early binding.\\
+
+\subsection{Further work}
+The goal of studying dynein's mechanochemical cycle is to find an explanation for how it work.
+That is, to find the necessary and sufficient properties of dynein that cause the cycle to happen.
+Simulations are only part of the recipe for creating a scientific theory.
+Simulations are easy to implement and can study phenomena which are difficult to design experiments for.
+However, when experimental data is available, it is generally more reliable than a simulation of the same system.
+This is because a simulation is only as good as the strength of correspondence between the mathematical model and the system it represents.
+With dynein, this correspondence can be hard to achieve because the protein is complicated.
+The model predicts, according to the laws of physics for small objects, how a small machine composed of springy hinges would behave in an aqueous environment.
+This machine can be made the same size and general shape as dynein, and its conformational angles can be made the same as dynein's, and its state transitions can happen in the same way dynein's do.
+However, it is never possible to say that this machine ``is'' dynein or represents how dynein actually behaves.
+Thus, it is only possible to say that the simulation provides sufficient criteria for dynein stepping, not necessary criteria.
+The simulation shows that the linker-swing/diffusive-step model is sufficient for motion, but it cannot show that this is needed for dynein's walk.\\
+
+To more strongly support the linker-swing/diffusive step model of dynein motion, more experiments should be done.
+Demonstrating that dynein requires flexible domain connections in order to take such broad steps would be one powerful experiment.
+Mutating the foot and tail domains to be more rigid, then examining stepping behavior would be one way to see if rigidity is necessary for random steps.
+Another experiment could use FRET (Forster Resonance Energy Transfer) and fluorophores on the microtubule and foot domain to track how the distance between the two regions evolves with time.
+This could provide information about the average distance between the MTBD and MT, which would validate this work's finding that the MTBD mostly hovers.
+More importantly, FRET data could be fit to models to predict the amount of diffusion the foot domain undergoes over the course of a step.
+Significant diffusion would indicate that diffusion may be very important for the step.
+Experiments with both feet labeled could get similarly good information.\\
+
+\textbf{Talk to Dr. Hsu about this sort of thing...what experiments could be used to validate the model?}
+
+If the model were validated by FRET and rigidity mutation studies, then there are many other interesting things which could be found from it.
+First, the amount of work done by the motor could be found by inducing an artificial drag force pulling the protein's motor domains against its direction of travel.
+This force could be integrated over dynein's trajectory to find the work the model exerted on its artificial cargo.
+This could be used to estimate the efficiency of the motor.
+Another interesting study would be to add binding sites to the model, only allowing it to bind at $\alpha-\beta$ tubulin dimerization sites, like real dynein.
+This would mandate re-fitting the binding constants to the new environment.
+It would be interesting to know if this model behaves more, or less dynein-like than the original.
+This would help answer the question of whether dynein searches for a binding site on the microtubule, or if it is naturally tuned to bind at the right site.\\
+
+Another very interesting simulation which could be run could help answer the open question of why kinesin and dynein, though using similar mechanisms, produce such different steps.
+Kinesin, unlike dynein, conducts all of its chemistry directly on its foot.
+This translates to effectively having two fewer joints than dynein.
+Kinesin's stroke is believed to involves a similar foot unbinding, kicking forward, rebinding, then lurching the motor forward mechanism.
+The dynein model could be used to construct a very rough model of kinesin by shrinking the tail linkers and increasing the motor domain spring constant $c_m$ high enough to simulate a rigid hinge.
+This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics.
+If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating.
+This result would show that the differences betwen kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants.
+This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\
+
+Next: add Big Questions to introduction, then answer them here.\\
 

### 2017-05-10 thesis/latex/thesis.tex

@@
 \textbf{Abstract}
-\blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell.
+%% \blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell.
 Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
@@
 The model's behavior is found using Brownian dynamics equations.
-Preliminary data indicate such a model is capable of taking steps between 0 and 25nm.
+Preliminary data indicate such a model is capable of taking steps between 0 and 25nm, though it vastly prefers <5nm steps.
 These results affirm that the Brownian hinge model of dynein is capable of stepping, and give hope that, with further tweaking, the model may be able to generate both larger and backwards steps, supporting the notion of a diffusion-dominated dynein step.}
+
+\blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell.
+Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
+Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60nm in both the forwards and backwards directions.
+It is believed that dynein takes such broad, stochastic steps because of its large size and several elastic regions, which make it more influenced by Brownian motion.
+To test this, we model the motor as a 2D system of springy hinges, then simulate this model using Brownian dynamics.
+Preliminary results indicate such a model is capable of taking steps between zero and 25nm.
+These results give hope that, with further tweaking, the model may be able to generate both larger and backwards steps.}
 

### 2017-05-10 trajectory-x-plt.py
Hopefully fix the date in index.html to be in our timezone?

@@ -43,15 +43,20 @@ plot_length = int(min(1e5,len(data)))
 
 nbxs =  np.zeros(plot_length)
 fbxs =  np.zeros(plot_length)
+nbys =  np.zeros(plot_length)
+fbys =  np.zeros(plot_length)
+
 times = np.empty(plot_length)
 
 for i in range(plot_length):
     if int(data[i,0]) == 0 or int(data[i,0]) == 2:
         nbxs[i] = data[i,7]
         fbxs[i] = data[i,15]
+        fbys[i] = data[i,16]
     elif int(data[i,0]) == 1:
         nbxs[i] = data[i,15]
         fbxs[i] = data[i,7]
+        nbys[i] = data[i,16]
     times[i] = data[i,1]*1e6
 
 avging_window_width = 300
@@ -59,15 +64,20 @@ num_windows = plot_length // avging_window_width # floor division
 
 avg_nbxs = np.array([np.mean(nbxs[avging_window_width*i:avging_window_width*(i+1)]) for i in range(num_windows)])
 avg_fbxs = np.array([np.mean(fbxs[avging_window_width*i:avging_window_width*(i+1)]) for i in range(num_windows)])
+avg_nbys = np.array([np.mean(nbys[avging_window_width*i:avging_window_width*(i+1)]) for i in range(num_windows)])
+avg_fbys = np.array([np.mean(fbys[avging_window_width*i:avging_window_width*(i+1)]) for i in range(num_windows)])
+
 avg_times = np.array([times[int(np.floor((i+0.5)*avging_window_width))] for i in range(num_windows)])
 
-y_min = np.min([np.min(avg_nbxs), np.min(avg_fbxs)])
-y_max = np.max([np.max(avg_nbxs), np.max(avg_fbxs)])
+y_min_xproj = np.min([np.min(avg_nbxs), np.min(avg_fbxs)])
+y_max_xproj = np.max([np.max(avg_nbxs), np.max(avg_fbxs)])
 
+# x projection
+plt.subplot(2, 1, 1)
 plt.xlabel("time ($\mu$s)")
 plt.ylabel("Binding domain x-projection (nm)")
 
-plt.gca().set_ylim(y_min-1,y_max+1)
+plt.gca().set_ylim(y_min_xproj-1,y_max_xproj+1)
 
[…]

### 2017-05-11 thesis/latex/thesis-old.tex
Thesis: Move over to a template. thesis-old.tex has the old thesis in it.

--- 2017-05-10 thesis/latex/thesis.tex
@@
 Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
-Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60nm in both the forwards and backwards directions.
-It is believed that dynein takes such broad, stochastic steps because of its large size and several elastic regions, which make it more influenced by Brownian motion.
-To test this, we model the motor as a 2D system of springy hinges, then simulate this model using Brownian dynamics.
+Unlike kinesin or myosin, dynein's stepping pattern is highly varied: it can take steps between zero and 60nm in both the forwards and backwards directions.
+It is believed that dynein takes such broad, stochastic steps because its large size and several elastic regions make it more influenced by Brownian motion.
+To test this, we model the motor as a 2D system of elastic hinges, then simulate this model using Brownian dynamics.
 Preliminary results indicate such a model is capable of taking steps between zero and 25nm.
-These results give hope that, with further tweaking, the model may be able to generate both larger and backwards steps.}
+These results give hope that, with further tweaking, the model may be able to generate both larger steps and backwards steps.}
 
@@
 
+\newpage
 \section{Chapter: Introduction}
@@
 Cells need to create asymmetric, heterogeneous structures inside themselves in order to function.
-However, as per the above quote, diffusive processes cannot create this asymmetry.
-How then do cells create heterogeneous structures they need in order to exist?
+However, diffusive processes cannot create this asymmetry.
+How then do cells create the heterogeneous structures they need to exist?
 Motor proteins are part of the answer.
@@
 In broad terms, they are mechanical creators of asymmetry.
-This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\
+This thesis explores a hypothesis about how one such motor protein, dynein, generates directed motion.\\
 
@@
 Though these proteins have significantly different ancestors \ref{cite}, they all evolved into a single similar structure.
-In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem.
+In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way of solving a problem.
 How, then, do motor proteins work?\\
 
-The basic form is simple.
+The basic process is simple.
 Kinesin, myosin and dynein each use two binding domains to attach to a surface.
@@
 Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface.
-In a single cycle a binding domain will unbind from a surface, tense its foot to kick forward, rebind, then untense its foot to pull the whole motor forward.
+In a single cycle a binding domain unbinds from a surface, tenses its foot to kick forward, rebinds, then untenses its foot to pull the whole motor forward.
 This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\
 
-Although the three motor protein families operate using the same stepping cycle, their behavior differs significantly.
-Kinesin and myosin are predictable motors which step in the forwards direction with a regular step size [get kinesin, myosin stepping papers].
-In contrast, dynein's stepping pattern varies wildly in both size and direction.
-The motor steps forward on average, but takes steps backwards and to the side quite regularly \cite{weihongpaper}.
+Although the three motor protein families operate using the same stepping cycle, their behaviors differ significantly.
+Kinesin and myosin are predictable motors which step in the forward direction with a regular step size [get kinesin, myosin stepping papers].
+In contrast, dynein's stepping pattern varies in both size and direction.
+The motor can take 64nm steps forward or 32nm steps backward, and often steps sideways as well \cite{weihongpaper}.
 How can motors which implement the same release, lever, bind, lurch stepping mechanism behave so differently?\\
@@
 One possibility is that dynein's size and organization are responsible for the motor's odd stepping pattern.
-Dynein is much larger than kinesin or myosin, meaning its feet may need to move significantly further over each cycle.
+Dynein is much larger than kinesin or myosin, so its feet may need to move significantly further during each cycle.
 Due to the random nature of Brownian motion from water particle collisions, there may be significantly more variance in the path taken by dynein's feet compared to other motor feet.
 This could explain the large variance in step size.
-Another contributing factor could be that dynein is so large that it can twist and contort during its step, allowing varying and even backwards steps, which a small motor would be too tense to achieve.\\
-
-This thesis describes an experiment which aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern.
-To do this, a mathematical model of a dynein-like motor is constructed which exhibits flexibility and feels Brownian forces.
-This model is then simulated, and its behavior is compared to the behavior of real dynein.\\
+Another contributing factor could be that dynein is so large that it can twist and contort during its step, allowing varying and even backwards steps, which a small motor would be too stiff to achieve.\\
+
+This thesis describes an experiment which aims to test whether Brownian motion and flexibility cause dynein's unique stepping pattern.
+To do this, we construct a mathematical model of the dynein motor which exhibits flexibility and feels Brownian forces.
+We then simulate the model and compare its behavior to real dynein.\\
 
@@
 
+\newpage
 \section{Chapter: Theory}
@@
 
+\newpage
 \section{Chapter: Methods}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{../../plots/x-trajectory_thesis}
-  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
+  \includegraphics[width=0.5\textwidth]{../../plots/trajectory-plot_thesis}
   \caption{Near and far binding domains over the course of several microseconds of simulation.
@@
 
-\section{Conclusion}
+\newpage
+\section{Chapter: Conclusion}
 \subsection{Findings}

### 2017-05-11 thesis/latex/thesis.tex
Hopefully fix the date in index.html to be in our timezone?
Fix up trajectory-plt to look thesis-worthy.
Thesis: Add .cls file.

--- 2017-05-03 thesis/latex/thesis.tex
@@
-\documentclass[defaultstyle,11pt]{article}
-%% \documentclass[defaultstyle,11pt]{thesis}
-
-\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins
-\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Masters/Doctoral Thesis 
+% LaTeX Template
+% Version 2.4 (22/11/16)
+%
+% This template has been downloaded from:
+% http://www.LaTeXTemplates.com
+%
+% Version 2.x major modifications by:
+% Vel (vel@latextemplates.com)
+%
+% This template is based on a template by:
+% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
+% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
+%
+% Template license:
+% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%----------------------------------------------------------------------------------------
+%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
+%----------------------------------------------------------------------------------------
+
+\documentclass[
+12pt, % The default document font size, options: 10pt, 11pt, 12pt
+%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
+english, % ngerman for German
+singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
+%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
+%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
+%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
+%toctotoc, % Uncomment to add the main table of contents to the table of contents
+%parskip, % Uncomment to add space between paragraphs
+%nohyperref, % Uncomment to not load the hyperref package
+headsepline, % Uncomment to get a line under the header
+chapterinoneline, % Uncomment to place the chapter title next to the number on one line
+%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
+]{MastersDoctoralThesis} % The class file specifying the document structure
+
+\usepackage[utf8]{inputenc} % Required for inputting international characters
+\usepackage[T1]{fontenc} % Output font encoding for international characters
+
+\usepackage{palatino} % Use the Palatino font by default
+
+\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+
+\addbibresource{thesis-articles.bib} % The filename of the bibliography
+
+\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
+
+% Elliott-added packages
+\usepackage{amsmath}
 \usepackage{listings}
-\lstset{escapechar=\&}
-
-% Fonts and tweaks for XeLaTeX
-\usepackage{fontspec,xltxtra,xunicode}
-\defaultfontfeatures{Mapping=tex-text}
-%\setmonofont[Scale=MatchLowercase]{Andale Mono}
-
-% Colors for links, text and headings
-\usepackage{hyperref}
-\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
-\definecolor{shade}{HTML}{F5DD9D} % Peach color for the contact information box
-\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
-\definecolor{headings}{HTML}{701112} % Dark red color for headings
-% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080
-
-\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors
-
-\usepackage{titlesec}
-\setcounter{secnumdepth}{4}
-
-\setlength{\emergencystretch}{3cm} % somehow helps prevent hboxes from overflowing
-
-%% \titleformat{\paragraph}
-%% {\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-%% \titlespacing*{\paragraph}
-%% {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
-
-\usepackage{fancyhdr}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\pagestyle{fancy}
-\fancyhf{}
-
-% Format of the section titles
-\titleformat{\section}{\color{headings}
-\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]
-
-\title{Simulating dynein's powerstroke using Brownian dynamics}
-\author{Elliott Capek}
-\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles
-
-\usepackage{csquotes}
-
 \usepackage{float}
 
-\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
-
-\bibliographystyle{plain}
-
-%% \title{Simulating a Brownian model of the dynein motor protein}
-%% \author{E. L.}{Capek}
-
-%% \otherdegrees{B.A., North Dakota State University, 2005 \\
-%% 	      M.S., University of Reno, 2007}
-
-%% \degree{Doctor of Philosophy}		%  #1 {long descr.}
-%% 	{Ph.D., Rocket Science}		%  #2 {short descr.}
-
-%% \dept{Department of}			%  #1 {designation}
-%% 	{Rocket Science}		%  #2 {name}
-
-%% \advisor{Prof.}				%  #1 {title}
-%% 	{Ed Visor}			%  #2 {name}
-
-%% \reader{Prof.~Rachel Goddard}		%  2nd person to sign thesis
-%% \readerThree{Ms.~Thora Nea}		%  3rd person to sign thesis
-
-%% \abstract{Yet to come.}
-
-%% \dedication{Yet to come.}
-
-%% \acknowledgements{Yet to come.}
+%----------------------------------------------------------------------------------------
+%	MARGIN SETTINGS
+%----------------------------------------------------------------------------------------
+
+\geometry{
+	paper=a4paper, % Change to letterpaper for US letter
+	inner=2.5cm, % Inner margin
+	outer=2.5cm, % Outer margin
+	bindingoffset=.5cm, % Binding offset
+	top=1.5cm, % Top margin
+	bottom=1.5cm, % Bottom margin
+	%showframe, % Uncomment to show how the type block is set on the page
+}
+
+%----------------------------------------------------------------------------------------
+%	THESIS INFORMATION
+%----------------------------------------------------------------------------------------
+
+\thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\supervisor{Dr. David \textsc{Roundy}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
+\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
+\degree{Bachelor of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
+\author{Elliott \textsc{Capek}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
+\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
+
+\subject{Physics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
+\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
+\university{\href{http://www.university.com}{Oregon State University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
+\department{\href{http://physics.oregonstate.edu}{Physics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\group{\href{http://physics.oregonstate.edu/~roundyd/}{Roundy Research Group}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
+\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
+
+\AtBeginDocument{
+\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
+\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
+\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
+}
 
@@
 
-\maketitle{}
-\tableofcontents
-\listoffigures
-\newpage
-
-\textbf{Abstract}
-\blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell.
+\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages
+
+\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content
+
+%----------------------------------------------------------------------------------------
+%	TITLE PAGE
+%----------------------------------------------------------------------------------------
+
+\begin{titlepage}
+\begin{center}
+
+\vspace*{.06\textheight}
+{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
+\textsc{\Large Undergraduate Thesis}\\[0.5cm] % Thesis type
+
+\HRule \\[0.4cm] % Horizontal line
+{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
+\HRule \\[1.5cm] % Horizontal line
+
+\begin{minipage}[t]{0.4\textwidth}
+\begin{flushleft} \large
+\emph{Author:}\\
+{\authorname} % Author name - remove the \href bracket to remove the link
+\end{flushleft}
+\end{minipage}
+\begin{minipage}[t]{0.4\textwidth}
+\begin{flushright} \large
+\emph{Supervisor:} \\
+{\supname} % Supervisor name - remove the \href bracket to remove the link  
+\end{flushright}
+\end{minipage}\\[3cm]
+
+\vfill
+
+\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
+\textit{in the}\\[0.4cm]
+\groupname\\\deptname\\[2cm] % Research group name and department name
+
+\vfill
+
+{\large \today}\\[4cm] % Date
+%\includegraphics{Logo} % University/department logo - uncomment to place it
+
+\vfill
+\end{center}
+\end{titlepage}
+
+%----------------------------------------------------------------------------------------
+%	ABSTRACT PAGE
+%----------------------------------------------------------------------------------------
+
+\begin{abstract}
+\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
+Dynein is a motor protein which transports cargo along tracks inside the cell.
 Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
-Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60\textit{nm} in both the forwards and backwards directions.
-It is believed that dynein takes such broad, stochastic steps because of its large size and several elastic regions, which make it more influenced by Brownian motion.
-To test this diffusion-dominated hypothesis for dynein stepping, we create a minimal model of dynein with elastic regions which feels Brownian forces, and simulate the model's stepping behavior in a cellular environment.
-The model treats dynein's domains as ``point hinges'' connected by rigid rods, and accomplishes steps by changing the openness of its hinges.
-The model's behavior is found using Brownian dynamics equations.
-Preliminary data indicate such a model is capable of taking steps between 0 and 25nm.
-These results affirm that the Brownian hinge model of dynein is capable of stepping, and give hope that, with further tweaking, the model may be able to generate both larger and backwards steps, supporting the notion of a diffusion-dominated dynein step.}
-
-\textbf{Keywords}: Dynein, powerstroke, Brownian dynamics, coarse-grained, dynamics simulation\\
-
-\section{Chapter: Introduction}
+Unlike kinesin or myosin, dynein's stepping pattern is highly varied: it can take steps between zero and 60nm in both the forwards and backwards directions.
+It is believed that dynein takes such broad, stochastic steps because its large size and several elastic regions make it more influenced by Brownian motion.
+To test this, we model the motor as a 2D system of elastic hinges, then simulate this model using Brownian dynamics.
+Preliminary results indicate such a model is capable of taking steps between zero and 25nm.
+These results give hope that, with further tweaking, the model may be able to generate both larger steps and backwards steps.
+\end{abstract}
+
+%% %----------------------------------------------------------------------------------------
+%% %	ACKNOWLEDGEMENTS
+%% %----------------------------------------------------------------------------------------
+
+%% \begin{acknowledgements}
+%% \addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+%% The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
+%% \end{acknowledgements}
+
+%----------------------------------------------------------------------------------------
+%	LIST OF CONTENTS/FIGURES/TABLES PAGES
+%----------------------------------------------------------------------------------------
+
+\tableofcontents % Prints the main table of contents
+
+\listoffigures % Prints the list of figures
+
+\listoftables % Prints the list of tables
+
+%----------------------------------------------------------------------------------------
+%	ABBREVIATIONS
+%----------------------------------------------------------------------------------------
+
+\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+
+\textbf{MT} & \textbf{M}icro\textbf{t}ubule\\
+\textbf{MTBD} & \textbf{M}icro\textbf{t}ubule \textbf{B}inding \textbf{D}omain\\
+
+\end{abbreviations}
+
+%% %----------------------------------------------------------------------------------------
+%% %	PHYSICAL CONSTANTS/OTHER DEFINITIONS
+%% %----------------------------------------------------------------------------------------
+
+%% \begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
+
+%% % The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
+
+%% Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
+%% %Constant Name & $Symbol$ & $Constant Value$ with units\\
+
+%% \end{constants}
+
+%% %----------------------------------------------------------------------------------------
+%% %	SYMBOLS
+%% %----------------------------------------------------------------------------------------
+
+%% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
+
+%% $a$ & distance & \si{\meter} \\
+%% $P$ & power & \si{\watt} (\si{\joule\per\second}) \\
+%% %Symbol & Name & Unit \\
+
+%% \addlinespace % Gap to separate the Roman symbols from the Greek
+
+%% $\omega$ & angular frequency & \si{\radian} \\
+
+%% \end{symbols}
+
+%% %----------------------------------------------------------------------------------------
+%% %	DEDICATION
+%% %----------------------------------------------------------------------------------------
+
+%% \dedicatory{For/Dedicated to/To my\ldots}
+
+%----------------------------------------------------------------------------------------
+%	THESIS CONTENT - CHAPTERS
+%----------------------------------------------------------------------------------------
+
+\mainmatter % Begin numeric (1,2,3...) page numbering
+
+\pagestyle{thesis} % Return the page headers back to the "thesis" style
+
+% Include the chapters of the thesis as separate files from the Chapters folder
+% Uncomment the lines as you write the chapters
+
+%----------------------------------------------------------------------------------------
+%	THESIS CONTENT - CHAPTERS
+%----------------------------------------------------------------------------------------
+\chapter{Introduction}
+\label{chap:Introduction}
+
 \blockquote{An embryo in its spherical blastula stage has spherical symmetry [...].
@@
 In broad terms, they are mechanical creators of asymmetry.
-This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\
-
-%% \subsection{Interest builder}
+This thesis explores a hypothesis about how one such motor protein, dynein, generates directed motion.\\
+
+%% \section{Interest builder}
 %% Begin with a paper-like introduction which talks about:
@@
 
-\subsection{Motivation}
+\section{Motivation}
 Motor proteins are cellular structures which use chemical energy to do work and generate motion.
@@
 
-\subsection{What is dynein?}
-\subsubsection{Basics}
+\section{What is dynein?}
+\subsection{Basics}
 Dynein is a cellular structure which converts chemical energy to mechanical energy.
@@
 
-\subsubsection{Why do cells need motor transport?}
+\subsection{Why do cells need motor transport?}
 Cells are organized, heretogenous structures which respond quickly to their environments.
@@
 
-\subsubsection{What role does dynein play in the cell?}
+\subsection{What role does dynein play in the cell?}
 Some of dynein's primary roles in the cell are to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins.
@@
 
-\subsubsection{Dynein structure}
+\subsection{Dynein structure}
 
@@
 
-\subsubsection{How does it behave?}
+\subsection{How does it behave?}
 Dynein's stepping pattern is distinct from its partner, kinesin. Kinesin takes very precise 8-nm steps \cite{kinesin-step-size}. In contrast, dynein takes a large range of steps, as shown in Figure \\
 
-\subsubsection{Why is dynein interesting?}
+\subsection{Why is dynein interesting?}
 Studying how nature creates directed motion is interesting in itself.
@@
 
-\subsection{Dynein Stepping Background}
+\section{Dynein Stepping Background}
 Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
@@
 
-\subsubsection{ATP cycle influences conformational state}
+\subsection{ATP cycle influences conformational state}
 Dynein is known to occupy multiple discrete conformational states depending on its environment.
@@
 
-\subsubsection{Microtubule and nucleotide states are coupled}
+\subsection{Microtubule and nucleotide states are coupled}
 Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
@@
 
-\subsubsection{Stepping pattern}
+\subsection{Stepping pattern}
 Several studies have been done on the dynein motor's stepping pattern using selectively-labeled motor domains \cite{reck2006single} \cite{weihongpaper}.
@@
 
-\subsection{Dynein models}
+\section{Dynein models}
 Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts.
@@
 
-\subsubsection{Cianfrocco Model}
+\subsection{Cianfrocco Model}
 Cianfrocco \textit{et.
@@
 
-%% \subsubsection{Other models}
+%% \subsection{Other models}
 %% Find other models and put them here
 
-%% \subsection{Brownian dynamics}
+%% \section{Brownian dynamics}
 %% New section which describes how BD works.
 
-\subsection{This work}
-\subsubsection{Necessary and sufficient criteria for motion}
+\section{This work}
+\subsection{Necessary and sufficient criteria for motion}
 One of the principle goals of researchers studying the dynein motor is establishing how it walks.
@@
 
-\subsubsection{Goals}
+\subsection{Goals}
 The goal of this work is to construct a minimum physical model of dynein protein based on the theoretical Cianfrocco model.
@@
 
-\section{Chapter: Theory}
-\subsection{Model features}
+\chapter{Theory}
+\label{chap:Theory}
+
+\section{Model features}
 The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior.
@@
 
-\subsubsection{Spherical domains connected by massless rods}
+\subsection{Spherical domains connected by massless rods}
 A key feature of the model is that each domain of the protein (two feet, twp motors and a tail) is treated as a sphere.
@@
 
-\subsubsection{Rigid rods}
+\subsection{Rigid rods}
 The model assumes connected domains are rigidly attached to one another by rods.
@@
 
-\subsubsection{Angular springs}
+\subsection{Angular springs}
 Each domain has a spring constant, $c_b, c_m$ or $c_t$ for binding, motor or tail, which decides the energy associated with that domain angle. For example, the tail domain energy is given by
@@
 
-\subsubsection{Two-state model}
+\subsection{Two-state model}
 The model assumes MT-bound dynein can assume one of two states: one where both MTBDs are bound, and one where only one MTBD is bound to the MT.
@@
 
-\subsubsection{Transitioning between states}
+\subsection{Transitioning between states}
 The model transitions between states with a probability dependent on both the energy difference between the two states and the physical separation between the MT and binding MTBD.
@@
 
-\subsubsection{Brownian dynamics}
+\subsection{Brownian dynamics}
 The Brownian dynamics equation describes the motion of high-drag objects which spend most of their time at terminal velocity, and is given by:
@@
 
-\subsubsection{Binding to microtubule}
+\subsection{Binding to microtubule}
 The model ``steps'' whenever an MTBD diffuses near the microtubule.
@@
 
-\subsubsection{2D model}
+\subsection{2D model}
 The coordinate system for this model is two-dimensional.
@@
 
-\subsection{Mathematical models}
+\section{Mathematical models}
 To simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state.
@@
 
-\subsubsection{Prestroke onebound model}
+\subsection{Prestroke onebound model}
 Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound.
@@
 
-\subsubsection{Poststroke bothbound model}
+\subsection{Poststroke bothbound model}
 The main difference between the prestroke and poststroke mathematical models is that the latter has a further constraint: both its MTB domains are attached to the MT.
@@
 
-\subsection{Data interpretation}
+\section{Data interpretation}
 Metrics for quality are required to assess how well the model fits reality. These metrics include time spent in one/bothbound states and average step size. These metrics are developed here.\\
 
-\subsubsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
+\subsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
 Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
@@
 
-\subsubsection{Literature values for experimental binding rates}
+\subsection{Literature values for experimental binding rates}
 Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
@@
 
-\subsubsection{Calculating one/bothbound times of experimental dynein}
+\subsection{Calculating one/bothbound times of experimental dynein}
 Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
@@
 
-\section{Chapter: Methods}
+\chapter{Methods}
+\label{chap:Methods}
 This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\
 
-\subsection{Simulation}
+\section{Simulation}
 To generate stepping data, the models were coded in \verb|C++| and time-evolved using Euler's method to generate reasonable dynamical behavior.
@@
 \textit{todo: come up with a better word than ``model'' to describe the state of the system at any time}
-\subsubsection{Time evolution}
+\subsection{Time evolution}
 Euler's method for solving differential equations was used to calculate domain positions through time.
@@
 
-\subsubsection{Transitioning between states}
+\subsection{Transitioning between states}
 
@@
 
-\subsubsection{Corrections}
+\subsection{Corrections}
 \label{corrections-section}
@@
 
-\subsubsection{Forces}
+\subsection{Forces}
 Spring and Brownian forces are used to properly move the model through time.
@@
 
-\subsection{Verifying the model}
+\section{Verifying the model}
 The models were verified to follow physical laws by checking their behavior in various tests: general conformational tests, energy conservation and obeying the equipartition theorem.
@@
 
-\subsubsection{Conformational tests}
+\subsection{Conformational tests}
 \label{sec:conformational-tests}
@@
 
-\subsubsection{Energy conservation}
+\subsection{Energy conservation}
 \label{sec:energy-conservation}
@@
 
-\subsubsection{Equipartition theorem}
+\subsection{Equipartition theorem}
 The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $<E> = \frac N2 k_bT$.
@@
 
-%% \subsection{Data collection}
+%% \section{Data collection}
 %% Time evolution of the system has the potential to create a huge amount of data, so care has to be taken to only collect what is necessary.
@@
 
-%% \subsubsection{Stepping data output and calculation}
+%% \subsection{Stepping data output and calculation}
 %% A step is defined as a complete cycle of
 
-%% \subsubsection{Simulation running via SLURM}
-
-\subsection{Parameter fitting}
+%% \subsection{Simulation running via SLURM}
+
+\section{Parameter fitting}
 There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
@@
 
-\subsubsection{Fitting rate constants}
+\subsection{Fitting rate constants}
 To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
@@
 
-\subsubsection{Fitting spring constants}
+\subsection{Fitting spring constants}
 This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
 
-\newpage
-\section{Chapter: Results \& Discussion}
-\subsection{Validating model}
+\chapter{Results \& Discussion}
+\label{chap:ResultsAndDiscussion}
+
+\section{Validating model}
 The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
@@
 
-\subsection{Model achieves processivity}
+\section{Model achieves processivity}
 When run at the proper parameters, the dynein model can step processively.
@@
 
-\subsection{Model step size is highly variant}
+\section{Model step size is highly variant}
 Figure \ref{fig:final-histograms}.a shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}.
@@
 
-%% \subsection{Current work: Refining model parameters}
+%% \section{Current work: Refining model parameters}
 %% Once validated, the model was fit to experimental data.
@@
 
-\section{Conclusion}
-\subsection{Findings}
+\chapter{Conclusion}
+\label{chap:Conclusion}
+
+\section{Findings}
 The most important findings of this work are that a springy hinge model of dynein can take steps of a similar size to real dynein.
@@
 
-\subsection{Further work}
+\section{Further work}
 The goal of studying dynein's mechanochemical cycle is to find an explanation for how it work.
@@
 
-\bibliography{thesis-articles}
-
-%% \bibliography{thesis-webpages}
-
-\section{Appendix}
-
-\subsubsection{Glossary}
-\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate.
-This reaction is used to power many energy-requiring mechanisms within the cell.
-This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
-\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.\\
-
-\subsection{Motion equations}
-
-\subsubsection{Onebound equations}
-\label{sec:ob-motion-equations}
+%----------------------------------------------------------------------------------------
+%	THESIS CONTENT - APPENDICES
+%----------------------------------------------------------------------------------------
+
+\appendix % Cue to tell LaTeX that the following "chapters" are Appendices
+
+% Include the appendices of the thesis as separate files from the Appendices folder
+% Uncomment the lines as you write the Appendices
+
+\chapter{Onebound equations} % Main appendix title
+\label{sec:AppendixOneboundEquations}
+
 The following is a continuation of the derivation for the full motion equations used to time evolve the onebound model:
@@
 
-%% $\dot{\Theta}_{bb}$ =
-%% {\tiny
-%% ( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% } \break
-
-%% $\dot{\Theta}_{bm}$ =
-%% {\tiny
-%%   (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% }\break
-
-%% $\dot{\Theta}_{um}$ =
-%% {\tiny
-%%   ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }\break
-
-%% $\dot{\Theta}_{ub}$ =
-%% {\tiny
-%%   ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }
-
-\subsubsection{Bothbound equations}
-\label{sec:bb-motion-equations}
+\chapter{Bothbound equations} % Main appendix title
+\label{sec:AppendixBothboundEquations}
+
 The following are the full motion equations used to time evolve the bothbound model:
@@
 
-%% $\dot{Ln}$ =
-%% {\tiny
-%%     (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
-%%      d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
-%%      c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
-%%      c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
-%%      c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
-%%      d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
-%%      c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
-%%      g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
-%%      d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
-%%      d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
-%%      c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
-%%      b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
-%%      c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
-%%      d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }\break
-
-%% $\dot{Lf}$ =
-%% {\tiny
-%%     (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
-%%      d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
-%%      c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
-%%      c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
-%%      c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
-%%      d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
-%%      c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
-%%      g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
-%%      d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
-%%      d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
-%%      c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
-%%      a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
-%%      c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
-%%      d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }
-
-\section{Questions for Tate/Nicole}
-%%\begin{itemize}
-%% \item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
-%% \item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
-%% \item When is a fact ``common knowledge'' enough that it doesn't need a citation?
-%% \item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
-%% \item Is 25 pages too long for a thesis? What makes a thesis too long?
-%% \item What details belong in a thesis, and which are too much?
-ex going in-depth on what tests do, describing how we came up with guess numbers for parameter hunt, describing function of dynein in the cell, showing why motor proteins are necessary.
-%% \item Supplemental info?
-%%\end{itemize}
-
-\section{Questions for David}
-\begin{itemize}
-\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be?
-Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
-\item What is the value of $\left<\Delta G_{conf}\right>$ in going from bothbound to onebound?
-\end{itemize}
-
-\section{Todo for project}
-\begin{itemize}
-\item Do calculations to turn processivity into state time ratios
-\item Fit the state times to above number by tweaking un/binding rates
-\item Fit spring constants to step length histograms
-\end{itemize}
+%----------------------------------------------------------------------------------------
+%	BIBLIOGRAPHY
+%----------------------------------------------------------------------------------------
+
+\printbibliography[heading=bibintoc]
+
+%----------------------------------------------------------------------------------------
+
 \end{document}

### 2017-05-11 thesis/latex/thesis.tex
Thesis: Mess around with latex header / .cls to make things look better.

@@
 \documentclass[
-12pt, % The default document font size, options: 10pt, 11pt, 12pt
+11pt, % The default document font size, options: 10pt, 11pt, 12pt
 %oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
@@
 
-\usepackage{palatino} % Use the Palatino font by default
-
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage{lmodern} % Use the Palatino font by default
+
+\usepackage[backend=bibtex,style=numeric,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 
@@
 % Elliott-added packages
-\usepackage{amsmath}
+\usepackage{amsmath} % for align and other environments
 \usepackage{listings}
-\usepackage{float}
+\usepackage{float}   % for H figure specifier
+\usepackage{indentfirst} % to indent after sections
 
@@
 	outer=2.5cm, % Outer margin
-	bindingoffset=.5cm, % Binding offset
+	bindingoffset=.0cm, % Binding offset
 	top=1.5cm, % Top margin
@@
 \university{\href{http://www.university.com}{Oregon State University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{http://physics.oregonstate.edu}{Physics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\department{\href{http://physics.oregonstate.edu}{Oregon State University Department of Physics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
 \group{\href{http://physics.oregonstate.edu/~roundyd/}{Roundy Research Group}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
@@
 \end{abstract}
+\newpage
 
@@
 \tableofcontents % Prints the main table of contents
+\newpage
 
 \listoffigures % Prints the list of figures
+\newpage
 
 \listoftables % Prints the list of tables
-
-%----------------------------------------------------------------------------------------
-%	ABBREVIATIONS
-%----------------------------------------------------------------------------------------
-
-\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
-
-\textbf{MT} & \textbf{M}icro\textbf{t}ubule\\
-\textbf{MTBD} & \textbf{M}icro\textbf{t}ubule \textbf{B}inding \textbf{D}omain\\
-
-\end{abbreviations}
+\newpage
+
+%% %----------------------------------------------------------------------------------------
+%% %	ABBREVIATIONS
+%% %----------------------------------------------------------------------------------------
+
+%% \begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+
+%% \textbf{MT} & \textbf{M}icro\textbf{t}ubule\\
+%% \textbf{MTBD} & \textbf{M}icro\textbf{t}ubule \textbf{B}inding \textbf{D}omain\\
+
+%% \end{abbreviations}
 
@@
 
+\newpage
 \chapter{Theory}
@@
 
+\newpage
 \chapter{Methods}
@@
 
+\newpage
 \chapter{Results \& Discussion}
@@
 
+\newpage
 \chapter{Conclusion}

### 2017-05-11 thesis/latex/thesis.tex
Thesis: Add a citation.

@@
 Kinesin, myosin and dynein are the three main motor proteins in cells.
-Though these proteins have significantly different ancestors \ref{cite}, they all evolved into a single similar structure.
+Though these proteins have significantly different ancestors \ref{hook-family}, they all evolved into a single similar structure.
 In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way of solving a problem.
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of dynein bound to a microtubule.}{One monomer is bound to the MT, and the other is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
+  \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (green/blue) and several tail proteins (pink) come together to form the dynein motor complex.
+One monomer's binding domain is bound to the microtubule, and the other is diffusing.
+ATP hydrolysis sites are labeled glowing green.
+Figure modified.
+Source: Lander Lab, The Scripps Research Institute \cite{landerartistsrendition}.}
   \label{dynein-artist-rendition}
@@
 In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.
-Figure (\ref{fig:diffusion_vs_dynein}) demonstrates how motor transport quickly outstrips diffusion in a cell.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
-  \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
-  \label{fig:diffusion_vs_dynein}
-\end{figure}
-
-\textit{Maybe use the more reasonable 2$\mu m / s$ number for dynein velocity, in-vitro speed may not be applicable since [ATP]-limited}
+\\%% Figure (\ref{fig:diffusion_vs_dynein}) demonstrates how motor transport quickly outstrips diffusion in a cell.\\
+
+%% \begin{figure}[h]
+%%   \centering
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
+%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
+%%   \label{fig:diffusion_vs_dynein}
+%% \end{figure}
 
@@
 
-\textit{maybe decorate the above plot with pictures of cells of each size, or how long certain cellular events take? That could be cool and make it actually an interesting plot}
-\textit{this argument would be much better if you could find examples of things which need to be done quickly in the cell, like responding to foreign particles or signalling molecules or cell division or neural events}
-
 \subsection{What role does dynein play in the cell?}
-Some of dynein's primary roles in the cell are to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins.
+One of dynein's primary jobs is to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins from place to place in the cell.
 Dynein also plays a role in positioning and breaking down the nucleus, cell death, spindle formation and the placement of other important cellular structures \cite{valetoolbox}.\\
 
-Microtubules are long polymers of alternating $\alpha-$ and $\beta-$ tubulin subunits.
-MTs are polar, meaning they have a distinct directionality based on the orientation of thetubulin proteins which comprise them.
-One pole, the minus end, is where they initiate formation, typically at a MTOC (microtubule organizing center) around the center of the cell.
+Dynein walks along cellular tracks called microtubules (MTs).
+MTs are long polymers of alternating $\alpha-$ and $\beta-$ tubulin subunits.
+MTs are polar, meaning they have a distinct directionality based on the orientation of the tubulin proteins which comprise them.
+One pole, called the minus end, is where they initiate formation, typically at a MTOC (microtubule organizing center) around the center of the cell.
 The other pole, the plus end, is where they grow and shrink from.
-Kinesin and myosin, two other families of motor protein, typically walk towards the plus end of the MT.
+Kinesin, another type of motor protein, typically walks towards the plus end of the MT.
 Dynein is unique in that it walks towards the minus end, making it a minus end-directed motor.
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
-  \caption{Dynein localization to axon growth cones.}{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport.
-Modified from \cite{valetoolbox}.}
+  \caption{Dynein transport to neuron growth cones.}{Dynein and kinesin collaborate to move cargo between the neuron body and axon tip.
+The oppositely-directed motors take turns transporting each other, along with cargo for building the axon growth cone.
+Borrowed from \cite{valetoolbox}.}
   \label{retrograde-transport}
@@
 \subsection{Dynein structure}
+As shown in the crystal structure in Figure \ref{fig:pdb-motm-dynein}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
+Each of these subunits has a unique purpose for the motor.
+
+Dynein is a fusion of two identical proteins, referred to as monomers.
+A single monomer, depicted in \ref{fig:pdb-motm-dynein}, is composed of a microtubule-binding domain (MTBD), a stalk, a buttress, a motor domain, a linker and a tail.
+The MTBD is responsible for binding to the microtubule.
+The stalk links the motor domain to the MTBD and carries information about the state of the motor to the MTBD.
+The motor domain hydrolyses ATP and performs the main conformation changes involved in the step \cite{FRETstatepaper}.
+The linker connects the tail to the motor and also changes conformation during the step.
+The tail is a binding site which interacts with several binding partners, including the tail of a twin monomer.\\
 
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of motor-MT complex.}{Artist rendition of the dynein motor bound to a microtubule.
-One monomer is bound to the MT, and one is raised up.
-Modified.
-Source: Lander Lab, The Scripps Research Institute.}
-  \label{dynein-artist-rendition-2}
-\end{figure}
-
-\textit{eventually find a different figure}
-
-As shown in the crystal structure in Figure XXX, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
-Each of these subunits has a unique purpose for the motor.
-
-\textbf{Binding domain}
-Microtubule binding domains (MTBDs) allow dynein to bind to the microtubule.
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
-%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
-%%   \label{dynein-artist-rendition-2}
-%% \end{figure}
-
-This could be fixed up...probably remove multiple of these sections
-
-\subsection{How does it behave?}
-Dynein's stepping pattern is distinct from its partner, kinesin. Kinesin takes very precise 8-nm steps \cite{kinesin-step-size}. In contrast, dynein takes a large range of steps, as shown in Figure \\
+  \includegraphics[width=.5\textwidth,keepaspectratio]{../../figures/pdb-motm-dynein}
+  \caption{Structure of a dynein monomer.}{A cryo-electron microscopy-inspired image detailing the subcomponents of a single dynein monomer.
+The microtubule-binding domain (MTBD) connects to the motor domain via a coiled coil known as the stalk.
+The six AAA regions provide structure for the motor domain, and AAA2 conducts the ATP hydrolysis.
+The linker is a flexible region which connects the motor domain to the tail.
+One of the main roles of the tail is connecting a monomer to its twin to form the dynein complex.
+Image borrowed from \cite{pdb-motm-dynein}.}
+  \label{fig:pdb-motm-dynein}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures//burgess-dynein-angles}
-  \caption{Cryo-EM microscopy of dynein conformational states.}{Cryo-electron microscopy images of dynein in two different nucleotide states.
-Left: dynein frozen in ADP-Pi state.
-Middle: dynein without nucleotide.
-Right: two states superimposed on one another.
-Bottom: cartoons representing how dynein may bind to the MT in either state.
-From \cite{burgess-paper}.}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/burgess-dynein-angles}\\
+  \hspace{1cm}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/linker-swing}
+  \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states.
+Top left: dynein frozen in ADP-Pi state.
+Top middle: dynein without nucleotide.
+Top right: two states superimposed on one another.
+Figures borrowed from \cite{burgess-paper}.
+Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states.
+Bottom left: motor in ADP-Pi state.
+Bottom right: Motor in ADP state.
+The linker undergoes an approximately 40 degree swing between these two states.
+Figure borrowed from \cite{bhabha-paper}.}
   \label{fig:cryo-em-angles}
@@
 
-\textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
+%% \textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
 
@@
   \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/weihong-step-size}
-    \caption{Experimental dynein step size histogram.}{Size of steps taken by dynein motor parallel to microtubule.
+  \includegraphics[width=0.49\textwidth]{../../figures/weihong-step-size}
+  \includegraphics[width=0.49\textwidth]{../../figures/weihong-off-axis-steps}
+    \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule.
 Positive axis corresponds to steps towards the microtubule minus-end.
+Right: Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule.
 Figure modified from \cite{weihongpaper}.}
-  \end{minipage}
-  \hspace{.2cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/weihong-off-axis-steps}
-    \caption{Dynein experimental off-axis stepping size.}{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
-  \end{minipage}
   \label{fig:weihong-steps}

### 2017-05-12 thesis/latex/thesis.tex
Thesis: Next commit.

@@
 
-%% \section{Interest builder}
-%% Begin with a paper-like introduction which talks about:
-
-%% \begin{itemize}
-%% \item How dynein is a structure which turns chemical energy into motion
-%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
-%% \item How it's weird that a cellular structure can generate directed motion
-%% \item Other cool stuff - make dynein mysterious and cool.
-%% \end{itemize}
-
-%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
-
 \section{Motivation}
@@
 \subsection{Why is dynein interesting?}
-Studying how nature creates directed motion is interesting in itself.
-Another interesting question is how, given the large number of similarities between motors kinesin and dynein, does dynein achieve such a radically different stepping pattern than kinesin?
+Selective domain labeling indicates dynein's stepping pattern is highly varied \cite{reck2006single} \cite{weihongpaper}.
+These studies show dynein's stepping pattern to be stochastic and weakly forward-directed.
+As shown in Figure (\ref{fig:weihong-steps}), dynein takes many backwards steps, and also many steps with components perpendicular to the microtubule.
+This indicates the process dynein uses to generate motion has a stochastic component to it.
+In contrast, kinesin is known to take very regular 8nm steps in the absence of large forces \cite{kinesin-step-size}.\\
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.49\textwidth]{../../figures/weihong-step-size}
+  \includegraphics[width=0.49\textwidth]{../../figures/weihong-off-axis-steps}
+    \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule.
+Positive axis corresponds to steps towards the microtubule minus-end.
+Right: Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule.
+Figure modified from \cite{weihongpaper}.}
+  \label{fig:weihong-steps}
+\end{figure}
+
+Kinesin and dynein, although of very different evolutionary origin \cite{hook-family}, have very similar stepping cycles.
+Both proteins bind bipedally to microtubules.
+Both proteins use ATP hydrolysis to leverage against a linker domain, pushing the motor domain forward.
+Both proteins couple their nucleotide and MT-binding states \cite{vale-kinesin-cycle}.
+How, given the large number of similarities between these motors, does dynein achieve such a radically different stepping pattern than kinesin?
 Elucidating how the structural differences between the motors give rise to the differences in dynamics would provide lots of important information on how the machines fine-tune their stepping.\\
 
-The major difference between kinesin and dynein is their size.
-Kinesin proteins are generally 100-200 kD in mass, whereas dynein is roughly 1mD.
-As shown in Figure \ref{fig:kinesin-vs-dynein}, the size and volume differences between proteins is very apparent.
-Dynein is about 20nm from MTBD to tail, whereas kinesin is ----.
-Another key difference is the separation between active sites on either protein.
-Kinesin binds to the MT with a foot domain, colored blue in Figure \ref{fig:kinesin-vs-dynein}.
-It hydrolyzes ATP at the residues colored pink.
-The separation between these domains is roughly ---nm.
-In contrast, Dynein binds to the MT with its MTBD, colored blue, and hydrolyses ATP in its motor domain, residues colored pink.
+A major factor which could contribute to differences in stepping is each protein's size.
+Kinesin proteins are generally 100-200 kD in mass, whereas dynein is on the order of 1mD.
+As shown in Figure \ref{fig:kinesin-vs-dynein}, the dynein motor domain is much bigger than the kinesin motor domain.
+Another key difference is the separation between ATP hydrolysis sites on either protein.
+Kinesin's ATP hydrolysis site is inside the globular microtubule-binding domain.
+In contrast, Dynein binds to the MT with its MTBD, colored yellow in Figure \ref{fig:kinesin-vs-dynein}, and hydrolyses ATP in its motor domain, which is colored cyan.
 This distance is close to 20nm in length - much longer than kinesin.
-Another difference is the way the motors interact with the microtubule.
-Both motors bind to the MT using domains.
-However, for dynein the motor-MTBD-MT angle is ---, whereas for kinesin, it is ---.\\
-
-Despite these differences, the two motors implement very similar chemical cycles to achieve motion.
-Both feet begin bound to the microtubule, then one unbinds.
-This foot diffuses forward, then rebinds to the microtubule
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/kinesin-vs-dynein}
-%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
-%%   \label{fig:kinesin-vs-dynein}
-%% \end{figure}
+This large separation might act like a loose ``leash,'' allowing the binding domain to diffuse freely around the microtubule.
+Kinesin has a much more rigid leash, as shown in the bottom pane of \ref{fig:kinesin-vs-dynein}.
+This more rigid leash may prevent diffusion from happening as much.\\
+
+\begin{figure}[H]
+  \centering
+  \begin{minipage}{0.3\textwidth}
+    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein}
+  \end{minipage}
+  \begin{minipage}{0.65\textwidth}
+    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein_2}
+  \end{minipage}
+  \caption{Structural comparison of dynein and kinesin}{Left: Comparison of crystal structures of the motor domains of dynein and kinesin bound to a microtubule.
+Image from \cite{kinesin-vs-dynein}.
+Right: Full motor complexes of dynein and kinesin.
+The blue regions of either protein are the motor domains, which are pictured in the above crystal structures.
+Image from \cite{kinesin-vs-dynein-2}.}
+  \label{fig:kinesin-vs-dynein}
+\end{figure}
 
@@
 Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
-The full mechanism is not known, but results of such experiments suggest a certain vague picture of how dynein generates motion.\\
+The full mechanism is not known, but several known behaviors of dynein can be taken together to construct a model for how the motor walks.\\
 
@@
   \hspace{1cm}
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/linker-swing}
+  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/linker-swing}
   \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states.
@@
 
-\subsection{Stepping pattern}
-Several studies have been done on the dynein motor's stepping pattern using selectively-labeled motor domains \cite{reck2006single} \cite{weihongpaper}.
-These studies show dynein's stepping pattern to be stochastic and weakly forward-directed.
-As shown in Figure (\ref{fig:weihong-steps}), dynein takes many backwards steps, and also many steps with components perpendicular to the microtubule.
-This indicates the process dynein uses to generate motion has a stochastic component to it.
-It is likely that the physical states of subcomponents in the motor, and/or the effects of Brownian motion due to water particle collision, play a role in dynein's stepping mechanism.\\
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../../figures/weihong-step-size}
-  \includegraphics[width=0.49\textwidth]{../../figures/weihong-off-axis-steps}
-    \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule.
-Positive axis corresponds to steps towards the microtubule minus-end.
-Right: Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule.
-Figure modified from \cite{weihongpaper}.}
-  \label{fig:weihong-steps}
-\end{figure}
-
-\section{Dynein models}
+\section{Cianfrocco model for dynein stepping}
 Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts.
-Somehow the protein itneracts with nucleotides and microtubules in a way that allows it to reliably move through the cell.
-Models presented below take these facts and string them together into cohesive cycles which might explain how dynein walks.
-It is important to note that these models are hypotheses.\\
-
-\subsection{Cianfrocco Model}
+Somehow the protein interacts with nucleotides and microtubules in a way that allows it to reliably move through the cell.
+The Cianfrocco model presented below takes these facts and string them together into cohesive cycles which might explain how dynein walks.\\
+
 Cianfrocco \textit{et.

### 2017-05-12 thesis/latex/thesis.tex
Thesis: Add work to introduction.

@@
 \ref{mech-cycle}.
-This model will hereon be referred to as the Cianfrocco model.
 The model claims the primary events in the dynein step are as follows.
@@
 
-\section{This work}
-\subsection{Necessary and sufficient criteria for motion}
-One of the principle goals of researchers studying the dynein motor is establishing how it walks.
-This can be a difficult task, since direct observation of the motor walking is not currently experimentally possible.
-The next best thing, then, is building a model which both only does all the things dynein does, and generates motion.
-Finding such a system would be very useful for forming hypotheses on how dynein walks.
-Another requirement of the system would be that it be as simple as possible while still explaining all the data.
-By Occam's Razor, such systems are the most likely to represent real dynein.
-Thus, finding the necessary and sufficient criteria for dynein's motion is a big goal in the field.\\
-
-A good starting place for finding the minimum set of motile criteria would be preexisting models, like the Cianfrocco model.
-This model describes a set of states which logically lead to each other and are supported by experiment.
-It seems intuitive that a motor which obeyed the Cianfrocco cycle would walk.
-There are multiple ways to verify this.
-A completely synthetic biological motor could be designed which obeys the cycle, and its motile properties could be studied.
-This seems incredibly difficult.
-Much easier would be to create a physical model of such a cycle, simulate it, and see if it obeys similarly to experimentally observed dynein.
-If the physical model both behaves according to the laws of physics and captures experimental dynein behavior well, this would be good evidence that such a model describes how dynein actually walks.\\
-
-\subsection{Goals}
-The goal of this work is to construct a minimum physical model of dynein protein based on the theoretical Cianfrocco model.
-The model should behave as physics predicts a protein to behave; namely, it should obey Brownian dynamics and conservation of energy.
-It should also roughly capture the state transitions and conformation changes of the Cianfrocco model.
-Also the model should be as simple as possible, to assure that each part of the model is necessary.
-If too many extra features are added, the model will not be minimal and not achieve its purpose.\\
-
-This model will then be converted into a computer program, tested for compliance with the laws of physics, and simulated.
-Information on the long-term behavior of such a simulation will then be used to evaluate how well the model describe's experimental dynein's behavior.\\
+\section{Testing the Cianfrocco model}
+One of the main goals of studying dynein is establishing how the motor walks.
+This can be a difficult task, since direct observation of the protein walking is not currently experimentally possible.
+Given the experimental challenges, a computational approach seems promising.
+This approach involves creating a hypothesis on how the motor walks, creating a model which behaves according to this hypothesis, simulating that model, and comparing the simulation's behavior to experimental data.
+This process can be an efficient way to support hypotheses and guide future research.\\
+
+\subsection{Computational approach}
+This project seeks to create a dynamic model of dynein and use it to answer questions.
+The Cianfrocco model provides a rough framework for the events that go on during the dynein mechanochemical cycle.
+By augmenting this model with information about dynein's structure and conformation changes occuring during the cycle, a new dynamic model which takes into account both temporal and spatial information can be constructed.
+This dynamic model can then be simulated under cellular conditions to test how it behaves.
+Such a model would be ideal, since it would make very precise predictions about how real dynein walks.
+This simulation would act as an experiment testing the validity of the Cianfrocco model.\\
+
+\subsection{Questions to answer}
+The biggest question such a simulation would answer is: does the Cianfrocco model, when applied to a dynein-sized motor with elastic hinges, produce dynein-like stepping?
+High similarity between simulation behavior and experimental dynein behavior would be a strong positive result supporting the Cianfrocco model.
+If confirmed to be dynein-like, the simulation could then be used to answer many other questions.\\
+
+Dynein has both angular and linear elasticity between its domains.
+Angular elasticity, or the flexibility of protein domains relative to each other, may play a large role in dynein's stepping.
+It is possible that dynein requires its foot domain to diffuse to a high-energy conformation in order to take a step.
+It is postulated by \textit{Burgess et.
+al.} \cite{burgess-paper} that changes in angular elasticity may be important for dynein's ability to step at key points in the mechanochemical cycle.
+Alternatively, it is possible that elasticity is not required, and the angular changes caused by the powerstroke are enough for stepping.
+By varying the angular elasticity of the model, this simulation could determine the importance of angular elasticity for dynein's step.\\
+
+Another question this simulation could answer is how dynein localizes to its binding site.
+Microtubules are regular tubulin polymers with MTBD binding sites roughly every 8nm.
+Dynein can take steps at integer multiples of this length, but the 8nm step is its most favored.
+Why is this?
+Does the MTBD drag along the microtubule until it hits a binding site?
+Or, does it diffuse high above the microtubule, randomly descending until it finds a place to bind.
+This simulation could answer that question by outputting MTBD positions over time.\\
+
+Why does dynein step differently than kinesin?
+Kinesin follows a similar mechanochemical cycle to dynein.
+By modifying the stepping cycle, shrinking inter-domain distance and changing conformation angles of the dynein model, it may be possible to create a rough kinesin dynamic model.
+This model could then be tested for similarity to experimental kinesin.
+If kinesin behavior was replicable, then comparisons between the models could be readily made.
+Does kinesin step like dynein when its size is increased?
+Does dynein step like kinesin when its conformation angles are made rigid?
+By varying the spatial representation of the two models, it might be possible to determine why the two motors step differently.\\
+
+Kinesin and dynein generally travel in opposite directions along the microtubule.
+Why is this?
+Both proteins bind to the same place on the microtubule \cite{kinesin-dynein-mt-overlap}, so the binding site can't determine directionality.
+It is possible that not the binding site, but the angle at which the protein binds to the microtubule is what determines its stepping direction.
+If it turns out that kinesin can be successfully modelled using the same dynamic model, then this question could possibly be answered.
+If altering the microtubule binding angles of dynein and kinesin reverses their directionality, it may be that binding angle is all it takes to determine motor directionality.\\
 

### 2017-05-12 thesis/latex/thesis.tex
Thesis: Begin work on theory section.

@@
 \section{Cianfrocco model for dynein stepping}
+\label{sec:cianfrocco-model}
 Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts.
@@
 
-%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}.
-The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I.
-Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
-
 \newpage
@@
 
-\section{Model features}
-The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior.
-To test this hypothesis, these features are put into a model and simulated.
-A schematic of the model is pictured in Figure \ref{fig:model-intro} and described below.\\
-
-\textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
+\section{Building the model}
+The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell.
+In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation.
+Creating such a model is a balance between accuracy and computational efficiency.
+The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time.
+Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be infeasibly computationally expensive to simulate a dynein step.
+Thus, many approximations are made about dynein to simplify the simulation.\\
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.45\textwidth]{../../figures/theory-onebound}
+  \includegraphics[width=.45\textwidth]{../../figures/theory-bothbound}
+  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to a two-dimensional point-particle system.
+Five points in total represent the two MTBDs, two motor domains and one tail domain.
+These points are connected by rigid rods.
+Although approximated as points, each domain has a radius $R$ associated with it used for drag calculations.}
+  \label{fig:theory-intro}
+\end{figure}
+
+%% \textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
 It would basically show all events occuring at two times: unbinding or rebinding.}\\
@@
 This model makes the assumption that the mechanochemical cycle can be broken down into a cycle of prestroking to move the unbound foot forward, brownian walking to place the foot on the microtubule, then powerstroking to move the other domains forward.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
-  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
-  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
-  \label{ob_fig}
-\end{figure}
 
@@
 \label{chap:Conclusion}
+
+%thoughts
+%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}.
+The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I.
+Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
 

### 2017-05-12 thesis/latex/thesis.tex
Thesis: Add theory overview.

@@
 
-\section{Building the model}
+\section{Model overview}
 The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell.
@@
   \includegraphics[width=.45\textwidth]{../../figures/theory-bothbound}
-  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to a two-dimensional point-particle system.
+  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to two two-dimensional point-particle systems.
+The left ``onebound'' system represents dynein when one MTBD is unbound, and the right ``bothbound'' system represents dynein with both MTBDs bound.
 Five points in total represent the two MTBDs, two motor domains and one tail domain.
+Each model's orientation is defined by a set of angles, four in the onebound case and two in the bothbound case.
 These points are connected by rigid rods.
@@
 \end{figure}
+
+\subsection{Summary}
+The model is composed of two separate systems of five point particles, with each point representing a domain of dynein: two binding domains, two motor domains and one tail domain.
+Physical representations of these two systems are shown in Figure \ref{fig:theory-intro}.
+The points are connected together by rigid rods, and the sytems are defined by the angles the rods make at each point.
+These angles are free to swivel.
+Each point thus acts somewhat like a ``hinge'' which can open or close.
+These two systems represent different modes dynein can be in.
+The Cianfrocco model is simplified to two states: onebound, when one MTBD (Microtubule Binding Domain) is diffusively searching for a binding site, and bothbound, where both MTBDs are MT-bound.
+The model can be in one of these two states at any time, and can transition between them if the right conditions are met.
+For example, if the model is in the onebound state but drifts such that both of its MTBDs are near the microtubule, the model can ``bind'' the MT and transition to the bothbound state.\\
+
+The model is subject to two forces, each of which is meant to simulate the effects real dynein domains feel.
+The first is a Brownian force which constantly changes.
+This force is meant to mimic the force of water particles colliding with the domains and causing diffusion.
+The second force is called a conformational force, and is meant to mimic the conformation and elasticity of dynein.
+Each hinge is somewhat like a spring with an equilibrium resting angle.
+At this angle, the domain feels no force.
+However, when the angle deviates from this equilibrium, a harmonic restoring force proportional to the displacement angle is applied to the involved domains to push the angle back to equilibrium.
+Thus these two forces oppose each other during a simulation, with Brownian forces pushing the model out of equilibrium and conformational forces trying to restore equilibrium.\\
+
+How this system is used to generate data is covered later in the section.
+In brief, this system is then converted into a computer program.
+A technique known as Brownian dynamics, described below, is used by the program to evolve the model through time.
+Models are started in one state and evolved, occasionally transitioning from one state to another.
+The positions of each domain in time are stored as data.
+Each time a model transitions from onebound to bothbound, the model registers a ``step'' having occured.
+Thus long simulations can be used to find the stepping behavior of a model.\\
 
@@
 
+\section{Model assumptions}
 \subsection{Spherical domains connected by massless rods}

### 2017-05-12 thesis/latex/thesis.tex
Thesis: Do work on methods section.

@@
 A key feature of the model is that each domain of the protein (two feet, twp motors and a tail) is treated as a sphere.
-Each sphere is connected to one or two other spheres, as shown in Figure (\ref{fig:model-intro}).
+Each sphere is connected to one or two other spheres, as shown in Figure (\ref{fig:theory-intro}).
 This simplification is made to make the math easier and allow a simple definition of dynein's conformation.\\
 
-One quickly notices by glancing at Figure (\ref{fig:crystal-structure-model-imposed}), a visualization of actual dynein, that modelling the tail and feet domains as spheres is a stretch.
-The main point of the simplification is not to capture the shape of dynein, but the conformation.
-It is undefined to discuss the distance between the two motor domains in real dynein, because the motors are made up of hundreds of amino acids, and the average inter-domain distance between amino acids is comparable to the intra-domain distance.
-However it is very easy to describe the difference between two spheres.\\
+As shown in Figure \ref{fig:pdb-motm-dynein}, dynein's motor and tail domains are fairly spherical.
+Though the stalk and tail connecting these domains is definitely not massless, it is small enough that approximating it as massless should be reasonable.
+Making the radii of the spherical domains slightly larger should account for any drag caused by the rigid rods.
 
@@
 %
-Thus R becomes a parameter input to the model.\\
-
-\subsection{Rigid rods}
+This drag factor $\gamma$ is used later to calculate the velocity of each domain.\\
+
+\subsection{Rods connecting domains are rigid}
 The model assumes connected domains are rigidly attached to one another by rods.
-This assumption makes the math easier, and is not necessarily based on biology.
+This assumption makes the math easier.
 One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \ref{burgess-paper}.
 However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \ref{myosin-cc-elasticity}.
-
-In reality, all molecules have a degree of elasticity.
-A dynein model by Sarlah \textit{et.
-al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.
-However, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.\\
+Another dynein simulation done by Sarlah \textit{et.
+al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.\\
+
+In defense of rigid rods, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.
+Either way, it is then an assumption of the model that inter-domain elasticity is not necessary for stepping.\\
 
 \subsection{Angular springs}
-Each domain has a spring constant, $c_b, c_m$ or $c_t$ for binding, motor or tail, which decides the energy associated with that domain angle. For example, the tail domain energy is given by
+Each domain has a spring constant $c_b, c_m$ or $c_t$, for binding, motor or tail domains respectively, which decides the energy associated with that domain angle.
+For example, the tail domain energy is given by
 %
@@
 
+This energy represents the conformational energy of that particular domain.
+This energy can be used to calculate a return force which pushes the domain back to equilibrium.
+A depiction of this is shown in Figure \ref{fig:angular-spring}.\\
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.65\textwidth]{../../figures/angular-spring}
+  \caption{Angular spring return force when out of equilibrium.}{The $\theta_{bb}$ angle shown is greater than the equilibrium angle $\theta_{bb}^{eq}$, and thus the $bb$ domain has conformational energy $\frac{1}{2}c_b\left(\theta_{bb}-\theta_{bb}^{eq}\right)^2$, and feels a force pulling the motor domain towards the microtubule.}
+  \label{fig:angular-spring}
+\end{figure}
+
 \subsection{Two-state model}
-The model assumes MT-bound dynein can assume one of two states: one where both MTBDs are bound, and one where only one MTBD is bound to the MT.
-These states are also differentiated by different motor equilibrium angles, $\Theta_{m}^{bb}$ and $\Theta_{m}^{ob}$, and different transition rates.
-Biological dynein likely passes through a series of permutations of nucleotide, MT affinity and conformational states as it travels through its mechanochemical cycle.
-This model makes the assumption that the mechanochemical cycle can be broken down into a cycle of prestroking to move the unbound foot forward, brownian walking to place the foot on the microtubule, then powerstroking to move the other domains forward.\\
-
-\textbf{todo: Add springs to joints!}
+According to the Cianfrocco model, dynein takes on a total of eight states during a single step.
+Many of these states are conformationally very similar, eg the ADP- vs apo-bound or ATP- vs ADP-bound.
+Others involve quick transitions, eg from the just-MT-bound state to the post-powerstroke state.
+The transitions which take the most time according to reaction rate calculations are MT-binding and MT-release \cite{sarlahmodel}.
+Thus, these two states are taken to be the most important, and the Cianfrocco model is approximated by transitioning between these two states.\\
+
+The main difference between these two states is that onebound has one diffusing MTBD, whereas bothbound has both its MTBDs MT-bound.
+Another key difference is equilibrium angles of the motor domains.
+During powerstroke, according to the Cianfrocco model, the dynein linker shifts, causing the tail-MTBD angle to shift.
+In this model, the conformation change caused by ATP hydrolysis is modelled as shifting the bothbound equilibrium angle $\theta_{xm}^{bb,eq}$ to $\theta_{xm}^{ob,eq}$.\\
 
 \subsection{Transitioning between states}
-The model transitions between states with a probability dependent on both the energy difference between the two states and the physical separation between the MT and binding MTBD.
-The energy difference between states A and B is given by:
+The model transitions between states with a probability dependent on both the conformational energy difference between the two states and the physical separation between the MT and binding MTBD.
+This transition can be tricky.
+To unbind, or convert from a bothbound to onebound model, a onebound structure can be constructed with the exact same domain positions, except the unbound MTBD is allowed to diffuse.
+To bind, or convert from a onebound to bothbound model, the unbound MTBD must be projected onto the microtubule.
+This is because the bothbound state is defined as having both MTBDs at $y=0$.
+Once projected, a bothbound model can be constructed with domains in the same places as the projected onebound model.\\
+
+The rates of such transitions are based on the conformational energy change between the new and old states. The energy difference between states A and B is given by:
 %
 \begin{equation}
-  \Delta G_{A\rightarrow B} = \sum_{i=0...N_B}^{B} \frac{1}{2}c_i\left(\theta_i-\Theta_i^B\right)^2 - \sum_{j=0...N_A}^{A} \frac{1}{2}c_j\left(\theta_j-\Theta_j^A\right)^2
+  \Delta G_{A\rightarrow B} = \sum_{i=0...N_B}^{B} \frac{1}{2}c_i\left(\theta_i-\theta_i^B\right)^2 - \sum_{j=0...N_A}^{A} \frac{1}{2}c_j\left(\theta_j-\Theta_j^A\right)^2
 \end{equation}
 %
+where B is the transitioned version of state A.
 Transition energies are used to calculate transition rates, as given by the Arhennius equation $k=Ae^{-\beta\Delta G}$, where $\beta = (k_BT)^{-1}$.
@@
 \begin{equation}
-  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
+  k_b = Ae^{-\beta\Delta G} = Ae^{-\beta\Delta G_{conf}}e^{-\beta\Delta G_{bind}}
 \end{equation}
@@
 %
-Thus $B$ becomes a parameter of the model.\\
+Thus the transition rate is only dependent on the change in conformational energy of transitioning and the preexponential factor $B$.
+To prevent binding events from happening when the MTBD is high above the MT, the following step function correction is added to the rate equation: \\
+
+\begin{equation}
+  k_b = Be^{\frac{-\Delta G_{conf}}{k_BT}}\left(1-H\left(X_{uby}-0.1\right)\right)
+\end{equation}
+
+where H is the Heaviside function, a step function of value 1 for $x>0$. Thus the binding rate is zero when the unbound MTBD is over $0.1$nm from the MT.\\
 
 \subsection{Brownian dynamics}
+\label{sec:bd}
 The Brownian dynamics equation describes the motion of high-drag objects which spend most of their time at terminal velocity, and is given by:
@@
 %
-Dynein is in the range of objects which BD describes well. (citation needed)
+which is calculated from the Einstein relation.\\
 
@@
 This model ignores this requirement and allows stepping to occur at any length.
-The assumption is that \textit{in vivo} dynein takes 8nm steps because of its size and stepping angle.
-Thus the 8nm step length should be reproduced by the model without explicit coding.\\
+The assumption is that \textit{in vivo} dynein takes 8nm steps because it is tuned to take 8nm steps, not because it drags along the microtubule searching for a binding site.
+Thus the 8nm step length should be reproduced by the model even if stepping is allowed anywhere.\\
 
@@
 Other dynein models, like the winch model \ref{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions.
-It is not clear why such forces are necessary for dynein motion, and so they are omitted.\\
-
-Side stepping of dynein is ignored in this model.
-Stepping perpendicular to the MT occurs in dynein \cite{weihongpaper}, as shown in Figure \ref{fig:weihong-side-stepping}.
-This model assumes it is a symptom, and not an influencer of, of dynein's forward-backward stepping mechanism.
+This model ignores such effects.\\
+
+\section{Deriving motion equations}
+To simulate a protein's passage through the above mechanochemical cycle, equations are needed to describe the position of dynein at an arbitrary time.
+Using Euler's method, a position equation can be found given a velocity equation like so:
+
+\begin{align}
+  f(t+\delta t) &= f(t)+f'(t)\delta t
+\end{align}
+
+Thus, if velocity equations can be found for the individual domains, then dynein's dynamic behavior can be solved for using numerical integration.
+The Brownian dynamics equation shown in Section \ref{sec:bd} provides velocity at time t from forces at time t.
+All that needs to be done is to come up with expressions for the forces on each domain, which is done in the next two sections.\\
+
+One complication arises from the choice of coordinate system.
+Angular coordinates are nice, since they automatically enforce the rigid rod constraint.
+However, forces are more easily calculated in Cartesian coordinates.
+In addition, forces on the $ith$ domain depend on domains $i\pm1$.
+Thus, solving for forces requires solving a large system of equations.
+Mathematica is used for this purpose, as outlined below.\\
+
+\subsection{Prestroke onebound model}
+Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound.
+A spatial representation of onebound dynein is shown in Figure \ref{fig:derivation-onebound}.
 
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../../figures/weihong-side-stepping}
-  \caption{Dynein experimental off-axis stepping histogram.}{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}.
-0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right.
-Modified.}
-  \label{fig:weihong-side-stepping}
+  \includegraphics[width=.45\textwidth]{../../figures/derivation-onebound}
+  \caption{Spatial representation of the onebound dynein model.}{The coordinate system used for derivation of onebound forces.}
+  \label{fig:derivation-onebound}
 \end{figure}
 
-\section{Mathematical models}
-To simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state.
-The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\
-
-\subsection{Prestroke onebound model}
-Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound.
-A spatial representation of onebound dynein is shown in Figure \ref{ob_fig}.
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
-%%   \caption{Spatial representation of onebound model.}
-%%   \label{ob_fig}
-%% \end{figure}
-
-TODO: make onebound model figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\
-
-Each domain is represented by a point, and is connected to other domains via fixed-length rods.
-Angles represent the degrees of freedom of the model.
-Since the protein is a dimer, there are two copies of the MTB, motor and tail domains.
-The tails are fused together and so represented as a single point.
-The motor and MTB domains are given a ``bound'' and ``unbound'' designation to differentiate them.
-The ``bound'' domains are the MTBD attached to the MT and its corresponding motor domain.
-The unbound domains are the unbound MTBD and its corresponding motor domain.\\
-
-\paragraph{Angular and Cartesian coordinates}
-
-The four angles $\Theta_{bb}, \Theta_{bm}, \Theta_{um}$ and $\Theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on.
-The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$.
+The coordinate system for this model is as follows.
+The bound MTBD is referred to as the ``bound binding domain'' $bb$.
+Its coordinates take the form, for example, $X_{bb}$.
+The motor domain adjacent to $bb$ is the ``bound motor'' $bm$.
+Next is the tail $t$, then the ``unbound motor'' $um$ and finally $ub$.\\
+
+The four angles $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on.
+The domain of $\theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$.
 Each angle is defined relative to the horizontal axis.
@@
 
-%% \begin{figure}[h]
-%%   \centering
-%%   \begin{tabular}{c}
-%%     \begin{lstlisting}[language=C++]
-%%       class Dynein_onebound{
-%%         double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
-%%         double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
-%%         double &$X_{bb}$&
-%%       }
-%%     \end{lstlisting}
-%%   \end{tabular}
-%%   \caption{Pseudocode of the onebound Dynein model.}
-%%   \label{ob_struct}
-%% \end{figure}
-
-\paragraph{$\dot{\Theta}_{ub}, \dot{\Theta}_{um}, \dot{\Theta}_{bm}, \dot{\Theta}_{bb}$ calculation}
-
-The following equations allow recursive calculation of the positions of each domain in cartesian coordinates:
+\subsubsection{Onebound velocity calculations}
+
+The following equations allow recursive calculation of the positions of each domain in Cartesian coordinates:
 
@@
 \begin{align}
-  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
-  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
-  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
-  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
+  X_{bm} &= X_{bb}+L_{s}\cos(\theta_{bb}) \\
+  X_{t}  &= X_{bm}+L_{t}\cos(\theta_{bm}) \\
+  X_{fm} &= X_{t} - L_{t}\cos(\theta_{fm}) \\
+  X_{fb} &= X_{fm} - L_{s}\cos(\theta_{fb})
 \end{align}
@@
   Y_{bb} &= 0 \\
-  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
-  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
-  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
-  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
+  Y_{bm} &= Y_{bb}+L_{s}\sin(\theta_{bb}) \\
+  Y_{t}  &= Y_{bm}+L_{t}\sin(\theta_{bm}) \\
+  Y_{fm} &= Y_{t} - L_{t}\sin(\theta_{fm}) \\
+  Y_{fb} &= Y_{fm} - L_{s}\sin(\theta_{fb})
 \end{align}
@@
 
-\paragraph{Angular and Cartesian velocities}
-The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities.
+The goal is to express angular velocities $\dot{\theta}_{bb}, \dot{\theta}_{bb}, \dot{\theta}_{bb}$ and $\dot{\theta}_{bb}$ in terms of known quantities.
 To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner.
@@
   \dot{X}_{bb} &= 0 \\
-  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
-  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
-  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
+  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\theta_{bb})\dot{\theta}_{bb} \label{cartesian-bmx}\\
+  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\theta_{bm})\dot{\theta}_{bm}
+  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\theta_{fm})\dot{\theta}_{fm} \\
+  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\theta_{fb})\dot{\theta}_{fb}
 \end{align}
@@
   \dot{Y}_{bb} &= 0 \\                                                        
-  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
-  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
+  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\theta_{bb})\dot{\theta}_{bb} \\
+  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\theta_{bm})\dot{\theta}_{bm}
+  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\theta_{fm})\dot{\theta}_{fm} \\
+  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\theta_{fb})\dot{\theta}_{fb}
 \end{align}
@@
 \vspace{.5cm}
-
+%
 Another way to express these cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:
@@
 \end{align}
-
-%% \begin{align}  
-%%   \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
-%%   \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
-%%   \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-%%   \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
-%% \end{align}
-
+%
 where $\gamma_n$ is a drag coefficient for the binding, motor or tail domain with units of mass per second.
@@
   &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx}
-  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
-  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
+  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx}\label{ob_system_second}
 \end{align}
-
-%% \begin{align}
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
-%% \end{align}
-
+%
 A total of eight coupled differential equations are formed from this procedure.
-These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$.
+These eight equations form a system of equations with eight unknowns: $\dot{\theta}_{bb}, \dot{\theta}_{bb}, \dot{\theta}_{bb}$ and $\dot{\theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$.
 This system is more compactly represented as:
@@
 
-This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\Theta_{bm}}(\Theta_{bb}, \Theta_{bm}, \Theta_{um}, \Theta_{ub})$.
-These motion equations are further described in (\ref{sec:ob-motion-equations}).\\
+This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\theta_{bm}}(\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub})$.
+These motion equations are further described in (\ref{sec:AppendixOneboundEquations}).\\
 
 \subsection{Poststroke bothbound model}
-The main difference between the prestroke and poststroke mathematical models is that the latter has a further constraint: both its MTB domains are attached to the MT.
+The main difference between the prestroke and poststroke mathematical models is that the latter has a further constraint: both of its MTBDs are attached to the MT.
 This has the effect of diminishing the degrees of freedom of the system from four to two, assuming the motor remains above the MT.
-A spatial representation of the bothbound model is shown in Figure (\ref{bb_fig}).\\
+A spatial representation of the bothbound model is shown in Figure (\ref{fig:derivation-botbound}).\\
 
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
-  \caption{Model bothbound equilibrium angle defintion.}{}
-  \label{bb_fig}
+  \includegraphics[width=.45\textwidth]{../../figures/derivation-bothbound}
+  \caption{Spatial representation of the bothbound dynein model.}{The coordinate system used for derivation of bothbound forces.}
+  \label{fig:derivation-bothbound}
 \end{figure}
 
-The bothbound model is very similar in assumptions to the onebound: domains are represented as points connected by rigid rods, and the tails are still fused into a single point.
-The main differences are the naming scheme and spatial constraints.
+The main differences between onebound and bothbound are the naming scheme and spatial constraints.
 Dimers can no longer be differentiated by being un/bound, so are now differentiated by their z-position: being near or far from the ``camera.'' This is similar to labeling them as the right or left dimer.
-Thus there are the near binding (nb), near motor (nm), tail (t), far motor (fm) and far binding (fb) domains.
-Both the near and far binding domains have their x-coordinate fixed at zero.
-The system is described completely by two angles: $\Theta_{nm}$ and $\Theta_{fm}$.
-Angles $\Theta_t, \Theta_{nb}$ and $\Theta_{fb}$ are dependent on these two motor angles.\\
-
+Thus there is the near binding domain $nb$, near motor $nm$, tail $t$, far motor $fm$ and far binding domain $fb$.
+Both the near and far binding domains have their y-coordinate fixed at zero.
+The system is described completely by two angles: $\theta_{nm}$ and $\theta_{fm}$.
+Angles $\theta_t, \theta_{nb}$ and $\theta_{fb}$ are dependent on these two motor angles.
+Intermediate variables $L_{n}$ and $L_{f}$ are computed to ease calculations.
 The second MTBD constraint adds another required piece of information the model must track: the x position of the second MTBD.
-This position is described by $L$, the distance between the near and far binding domains.
-The pseudocode used to describe the bothbound model are shown in Figure (\ref{bb_struct}).\\
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=C++]
-      class Dynein_bothbound{
-        double &$\Theta_{nm}, \Theta_{fm}$&
-        double &$\dot{\Theta}_{nm}, \dot{\Theta}_{fm}$&
-        double &$X_{nb, L}$&
-      }
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Pseudocode of the bothbound Dynein model.}
-  \label{ob_struct}
-\end{figure}
-
-\paragraph{$\dot{\Theta}_{nm}, \dot{\Theta}_{fm}$ calculation}
-
-The first step in calculating angular velocities is to define new variables $L_n$ and $L_f$ using the Law of Cosines:
+This position is described by $L$, the distance between the near and far binding domains.\\
+
+\subsubsection{Bothbound velocity calculations}
+
+The first step in calculating angular velocities is to define intermediate variables $L_n$ and $L_f$ using the law of cosines:
 
@@
 
-These new artificial stalks are not physically relevant, but allow the definition of new angles $\Theta_n, \Theta_{ns}, \Theta_{f}$ and $\Theta_{fs}$, which are useful for calculating the position of the motor domain.
+These new artificial stalks are not physically relevant, but allow the definition of new angles $\theta_n, \theta_{ns}, \theta_{f}$ and $\theta_{fs}$, which are useful for calculating the position of the motor domain.
 The treatment of the near and far versions of these angles is very similar, so only the near angles will be dealt with here.
@@
 These values are arrived at through the Law of Cosines and a trigonometric identity.
-The sign of $\sin\left(\Theta_n\right)$ is restricted to positive values due to the angle's $[0,\pi]$ domain.
-$\Theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted.
+The sign of $\sin\left(\theta_n\right)$ is restricted to positive values due to the angle's $[0,\pi]$ domain.
+$\theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted.
 The partial derivatives of these values are used in future calculations, and some are shown here:
@@
 
-The position of the motor and tail domains is calculated as follws, using the angle addition trigonometric identity:
+The position of the motor and tail domains is calculated as follows, using the angle addition trigonometric identity:
 
@@
 
-These partial derivatives are then used in a system of equations very similar to that in Equations (\ref{ob_system_first}-\ref{ob_system_last}), combining Brownian and coordinate system definitions of domain velocities:
+These partial derivatives are then used in a system of equations very similar to that in Equations (\ref{ob_system_first}-\ref{ob_system_second}), combining Brownian and coordinate system definitions of domain velocities:
 
@@
 
-This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{sec:bb-motion-equations}).
-
-\section{Data interpretation}
-Metrics for quality are required to assess how well the model fits reality. These metrics include time spent in one/bothbound states and average step size. These metrics are developed here.\\
-
-\subsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
-Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
+This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{sec:AppendixBothboundEquations}).
+These intermediate velocities can then be used to calculate $\dot{\theta_{nm}}$ and $\dot{\theta_{fm}}$.\\
+
+%% \subsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
+%% Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
 One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations.
@@
 
-\begin{align*}
-  k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
-  k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
-\end{align*}
-
-where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
+%% \begin{align*}
+%%   k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
+%%   k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
+%% \end{align*}
+
+%% where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
 The experimental values are calculated the same way, with the free energy changes replaced with expectation values.
@@
 
-\begin{align*}
-  k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
-  k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
-\end{align*}
-
-Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
-
-\subsection{Literature values for experimental binding rates}
-Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
-  \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
-  \label{fig:sarlah-rate-table}
-\end{figure}
-
-The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
+%% \begin{align*}
+%%   k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
+%%   k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
+%% \end{align*}
+
+%% Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
+
+%% \subsection{Literature values for experimental binding rates}
+%% Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
+
+%% \begin{figure}[h]
+%%   \centering
+%%   \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
+%%   \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
+%%   \label{fig:sarlah-rate-table}
+%% \end{figure}
+
+%% The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
 Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound.
@@
 
-The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
+%% The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
 That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\
-
-\subsection{Calculating one/bothbound times of experimental dynein}
-Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
-
-\newcommand\tbb{\left<t_{bb}\right>}
-\newcommand\tob{\left<t_{ob}\right>}
-\newcommand\tstep{\left<t_{step}\right>}
-\newcommand\tproc{\left<t_{processivity}\right>}
-\newcommand\kub{k_{ub}}
-\newcommand\kb{k_{b}}
-\newcommand\ko{k_{dis}}
-
-\begin{itemize}
-\item $\tbb$: Time in bothbound per step
-\item $\tob$: Time in onebound per step
-\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
-\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
-\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
-\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
-\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
-\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
-\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
-\end{itemize}
-
-$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
-
-\begin{align*}
-  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
-  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
-  \tob &= \tstep-\tbb\\
-  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
-  &= \frac{\tstep^2}{\tstep+\tproc}\\
-\end{align*}
-
-Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| c | c | c | c | c | c |}
-    \hline
-    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
-  \end{tabular}
-  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
-  \label{table:time-parameter-table}
-\end{figure}
 
@@
 \label{chap:Methods}
-This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\
+This section will go into detail on how the model was implemented in C++ and verified for accuracy and physicality.\\
 
@@
 To generate stepping data, the models were coded in \verb|C++| and time-evolved using Euler's method to generate reasonable dynamical behavior.
-When in a position deemed worthy of a state transition a conversion, the model was converted to the respective other model, representing part of a ``step'' through the mechanochemical cycle.
-Some unphysical but minor corrections at points in the simulation were needed to rescue the model from entering incalculable positions.\\
+When in a position deemed worthy of a state transition, the model was converted to the respective other model, representing part of a ``step'' through the mechanochemical cycle.\\
 
@@
 
-%% \paragraph{Euler’s method}
-%% Show how Euler's method is arrived at, how its error scales, why we use it.
-
-%% \paragraph{Vs other methods (Runge Kutta, etc)}
-%% Talk about why our differential equation is most conducive to Euler's method. Euler's is more
-%% efficient -- is there a way to show how our differential equation is smooth, not jagged?
-
-\textit{todo: come up with a better word than ``model'' to describe the state of the system at any time}
 \subsection{Time evolution}
@@
 Because each model is a set of multiple coupled differential equations, care was taken to update each domain position at the same time, and not in a cascade.
-A code snippet is shown in Figure (\ref{euler-code-snippet}) for the onebound updating scheme.
+A code snippet is shown in Figure (\ref{snip:euler-code-snippet}) for the onebound updating scheme.
 
@@
   \caption{Code snippet}{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
-  \label{ob_struct}
+  \label{snip:euler-code-snippet}
 \end{figure}
@@
 
-\paragraph{Transition rate}
+\subsubsection{Transition rate}
 \label{sec:transitioning-states}
-Transitions from one state to another are accomplished by calculating the probability of a transition at a given timestep, given by $P_{ob\rightarrow bb} = k_bdt$.
-Each timestep a value in $[0,1]$ is sampled from a random number generator and, if lower than $P$, the respective transition is made.
-A code snippet illustrating how unbinding occurs is shown in Figure (\ref{transition-rate-snippet}).
-
-\begin{figure}[h!]
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=python]
-      def get_near_unbinding_rate(dyn_bb) {
-        dyn_ob_test = make_onebound_from_bothbound(dyn_bb) // do a fake unbind to find energy
-        dG_spring = dyn_ob_test.get_PE() - dyn_bb.get_PE()
-        low_affinity_unbinding_preexponential_factor = low_affinity_unbinding_rate / exp(1.0)
-        return low_affinity_unbinding_preexponential_factor*exp(-dG_spring/kb/T)
-      }
-      def transition_bothbound_to_onebound(dyn_bb) {
-        random_number = rand(0,1)
-        if (random_number < get_unbinding_rate(dyn_bb)) {
-          return make_onebound_from_bothbound(dyn_bb)
-        }
-        else return 0
-      }
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Code snip}{Code snippet of transition rate calculation using the Arrhenius equation.}
-  \label{transition-rate-snippet}
-\end{figure}
-
-\paragraph{OB $\rightarrow$ BB Transition calculation}
+Transitions from one state to another are accomplished by calculating the probability of a transition $t$ at a given timestep, given by $P_{t} = k_tdt$.
+Each timestep a value in $[0,1]$ is sampled from a random number generator and, if lower than $k_tdt$, the respective transition is made.
+The following sections describe how transitions are done.\\
+
+\subsubsection{Onebound to bothbound transition calculation}
 When binding occurs, conversion between OB and BB models is done by creating a bothbound dynein which is as similar in terms of domain position as possible to the onebound dynein.\\
@@
   L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
-  \cos(\Theta_{nm}) &= \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
-  \cos(\Theta_{fm}) &= \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}
+  \cos(\theta_{nm}) &= \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
+  \cos(\theta_{fm}) &= \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}
 \end{align}
 
-\textbf{todo: figure out why this new method is used instead of just computing the bad nma angles}
-
-\paragraph{BB $\rightarrow$ OB Transition calculation}
+\subsubsection{Bothbound to onebound transition calculation}
 Similar to the binding transition, unbinding involves creating a new onebound dynein from the old bothbound. To accomplish a transition to the farbound state, the following equations are used:\\
@@
 \begin{align}
-  \Theta_{new,bba} &= \Theta_{old,nba}\\
-  \Theta_{new,bma} &= \Theta_{old,nma} + \Theta_{old,nba} - \pi\\
-  \Theta_{new,uma} &= \Theta_{old,fma} + \Theta_{old,fba} - \pi\\
-  \Theta_{new,uba} &= \Theta_{old,fba}
+  \theta_{new,bba} &= \theta_{old,nba}\\
+  \theta_{new,bma} &= \theta_{old,nma} + \theta_{old,nba} - \pi\\
+  \theta_{new,uma} &= \theta_{old,fma} + \theta_{old,fba} - \pi\\
+  \theta_{new,uba} &= \theta_{old,fba}
 \end{align}
@@
 
-\subsection{Corrections}
-\label{corrections-section}
-Certain configurations of the model, such as in the bothbound model when $\Theta_{nm} = \pi$ or $\Theta_{fm} = \pi$, it becomes impossible to calculate intermediate variables due to values going to infinity (name for this??).
-For example when $\Theta_{nm} = \pi$, $Ln = Ls + Lt$ and so:
-
-\begin{align}
-  \cos\theta_{ns} &= 1 \\
-  \sin\theta_{ns} &= 0 \\
-  \mbox{some val?} &\rightarrow \infty
-\end{align}
-
-Alternative problem states are when $L = 0$ and ???. These states are corrected similarly.\\
-
-\subsection{Forces}
+%% \subsection{Corrections}
+%% \label{corrections-section}
+%% Certain configurations of the model, such as in the bothbound model when $\theta_{nm} = \pi$ or $\theta_{fm} = \pi$, it becomes impossible to calculate intermediate variables due to values going to infinity (name for this??).
+For example when $\theta_{nm} = \pi$, $Ln = Ls + Lt$ and so:
+
+%% \begin{align}
+%%   \cos\theta_{ns} &= 1 \\
+%%   \sin\theta_{ns} &= 0 \\
+%%   \mbox{some val?} &\rightarrow \infty
+%% \end{align}
+
+%% Alternative problem states are when $L = 0$ and ???. These states are corrected similarly.\\
+
+\subsection{Calculating forces}
 Spring and Brownian forces are used to properly move the model through time.
@@
 
-\paragraph{Brownian forces}
 Each Brownian force $R_{n,m}$ on domain $n$ in direction $m$ is sampled from a Gaussian with standard deviation $\sqrt{\frac{2k_BT\gamma_n}{dt}}$.\\
 
-\paragraph{Spring forces}
 Spring forces are calculated by first finding the torque $\tau$ on each angle, then converting this to a force.
-For example, the onebound near motor angle feels a force $\tau_{nm} = c_m(\Theta_{nm}-\Theta_{nm,eq})$, where $c_n$ is the spring constant of the motor domain and $\Theta_{nm,eq}$ the equilibrium angle.
-The magnitude of force on the adjacent binding and tail domains is thus $\tau/Ls$ and $\tau/Lt$, pointing in the direction adjacent the Ls and Lt rods, respectively.
+For example, the onebound near motor angle feels a force $\tau_{nm} = c_m(\theta_{nm}-\theta_{nm,eq})$, where $c_n$ is the spring constant of the motor domain and $\theta_{nm,eq}$ the equilibrium angle.
+The magnitude of force on the adjacent binding and tail domains is thus $\tau/L_s$ and $\tau/L_t$, pointing in the direction adjacent the Ls and Lt rods, respectively.
 The force on the motor domain is found as the equal-and-opposite force to these two imposed forces.
-In code:
+A sample calculation is shown in Snippet (\ref{snip:transition-rate-snippet}).\\
 
@@
     \begin{lstlisting}[language=C++]
+      def get_onebound_restoring_forces():
           T = cm*(nma - nma_eq);
@@
   \end{tabular}
-  \caption{Snip}{Code snippet of internal force calculation.}
-  \label{transition-rate-snippet}
+  \caption{Code snippet of restoring force calculation for near motor domain displacement.}{Torque is calculated the near motor's angular displacement from equilibrium.
+This is converted to force exerted on adjacent domains.
+Finally, the equal and opposite force is exerted on the near motor domain.}
+  \label{snip:transition-rate-snippet}
 \end{figure}
@@
 The models were verified to follow physical laws by checking their behavior in various tests: general conformational tests, energy conservation and obeying the equipartition theorem.
-The purpose of these tests was to verify that equations had been entered properly (primarily the conformational and energy conservation tests), and that the model obeyed the laws of physics (all tests).
-
-\subsection{Conformational tests}
-\label{sec:conformational-tests}
-The models were tested in the following different conformations to verify they behaved as expected:\\
-
-\textbf{Onebound tests}
-\begin{itemize}
-\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths.
-Also checks that all angular velocities are zero.
-This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or cartesian) without forces.
-\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths.
-Also check that all velocities are zero.
-This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that cartesian x-velocities are positive and y-velocities are zero.
-Verifies that the cartesian velocities have the expected sign.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all cartesian velocities are zero.
-Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
-  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite.
-Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
-\end{itemize}
-*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
-
-These tests together verify that the onebound model's internal coordinate system's directions match the XY coordinate system directions, that the angular directions in the model properly align with the $\pm x$ and $\pm y$ directions of the XY coordinate system, that velocities have the proper magnitude at zero force and proper sign at nonzero force, and that Brownian and internal forces are in the same unit system.
-There are still errors which could exist in the model pertaining to magnitude of velocity, which will be tested for in the energy conservation section.\\
-
-\textbf{Bothbound tests}
-\begin{itemize}
-\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^(-25)$) and motor domains nearly vertical ($\Theta_{n/f} = \pi \pm 10^(-15)$).
-Equilibrium angles set to have a vertical line as the lowest energy point.
-Model is not exactly vertical for NaN concerns explained in section \ref{corrections-section}.
-Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero.
-Verifies that the domains are properly oriented by the angles, the angles are defined properly and forces are calculated from angles properly.
-\item \textbf{Bothbound:} \textit{Equilateral house conformation with outward x-forces.} The model forms the shape of a square with an equilateral triangle on top, with the tail domain as the triangle.
-Checks if all domains are at the desired locations and the derivatives are the proper sign and are equal and opposite to their counterparts on the opposing side of the house.
-This test verifies that the angular system behaves as expected and forces are symmetric about the two dimers.
-\item \textbf{Bothbound:} \textit{Two table conformations with near/far domains flipped.} Two models are put in the same table-like conformation, but the near/far domains are flipped.
-Checks if opposite domains have the same positions and forces.
-Re-verifies that the model is symmetric in position and force between the two dimers.
-\end{itemize}
-
-These tests verify the bothbound model's angle system behaves as expected, forces are zero when expected and have the proper signs, and that the whole system is symmetric with either dimer.
+The purpose of these tests was to verify that equations had been entered properly (primarily the conformational and energy conservation tests), and that the model obeyed the laws of physics (all tests).\\
+
+A series of conformational tests were done. These are listed in Appendix \ref{sec:conformational-tests}.\\
 
@@
 \begin{equation}
-  \sum_n \frac12 \left(\Theta_{nudge} - \Theta_{n} - \Theta_{n,eq}\right) = \sum_n \vec{F}_n \cdot \vec{r}_{n,nudge}
+  \sum_n \frac12 \left(\theta_{nudge} - \theta_{n} - \theta_{n,eq}\right) = \sum_n \vec{F}_n \cdot \vec{r}_{n,nudge}
 \end{equation}
 
-where $\Theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the cartesian displacement of each domain $n$ due to the nudge.
+where $\theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the cartesian displacement of each domain $n$ due to the nudge.
 This test is powerful since it links the force-calculation system of either model to the energy calculation system.
 Energy is calculated by looking at displacements of angles from equilibrium, whereas forces are calculated using displacement of angles from equilibrium, but also orientation and position of each domain.
-Having the force system and energy system calculate the same results indicates that they are both likely correct..
-\textbf{make this more precise.}
-
-\textbf{is there a test to be run which could verify the velocity calculation is correct?}
+Having the force system and energy system calculate the same results indicates that they are both likely correct.\\
 
@@
 
-To test if the models obey the ET, the total potential energy of each model was logged over \textbf{ten million} (???) timesteps of simulation.
+To test if the models obey the ET, the total potential energy of each model was logged over $10^7$ timesteps of simulation.
 The results are reported in Figure \ref{equipartition_agreement}, where the PE scale is in units of $\frac12 k_bT$.
@@
 
-\textbf{would it be a stronger test to also calculate the standard deviation of <PE>?
-It seems like <PE> would still equal N/2KbT as long as the forces/velocities were symmetrically wrong.
-Calculating the stdev would require the state occupation to actually the ET.
-Or, maybe just plot the angle occupation and show that it is what it should be?}
-
-\textbf{Possibly do mutations on motion equations to show that tests are no longer behaved}
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| c | c | c | c |}
-    \hline
-    Author & Conditions & Velocity & Run length\\\hline
-    Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
-    Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
-  \end{tabular}
-  \caption{Literature values for experimental dynein stepping behavior.}{Table of literature values for dynein behavior}
-  \label{table:parameter-table}
-\end{figure}
+%% \begin{figure}[h]
+%%   \centering
+%%   \begin{tabular}{| c | c | c | c |}
+%%     \hline
+%%     Author & Conditions & Velocity & Run length\\\hline
+%%     Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
+%%     Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
+%%   \end{tabular}
+%%   \caption{Literature values for experimental dynein stepping behavior.}{Table of literature values for dynein behavior}
+%%   \label{table:parameter-table}
+%% \end{figure}
 
@@
 \section{Parameter fitting}
-There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
+There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\theta_{m,eq}^{Pre}$, $\theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
 Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.\\
@@
   \centering
-  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
+  \begin{tabular}{| l | l | l | l | l | l | l | l |}
     \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
-    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
-    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
-    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
-    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
-    $R_t$ &  & & & & 2.16nm & & & \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
-    $k_b$ & $460 s^{-1,b}$ & & & & & & & \\ \hline
-    $c_t$ & & & & & & & & \\ \hline
-    $c_m$ & & & & & & & & \\ \hline
-    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
+    & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
+    $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
+    $L_t$ &  7nm && & 11.15nm & & & \\ \hline
+    $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
+    $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
+    $R_t$ &  & & &2.16nm & & & \\ \hline
+    $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
+    $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & & & \\ \hline
+    $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
+    $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
+    $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
+    $c_t$ & & && & & & \\ \hline
+    $c_m$ & & && & & & \\ \hline
+    $c_b$ & & && & 140 kJ/mol & & \\ \hline
   \end{tabular}
-  \caption{Literature values for dynein model parameters.}{Table of literature values for various free parameters in dynein model.}
+  \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
   \label{table:parameter-table}
@@
 
-In addition, the physical conditions the simulations were run at are shown in Table \ref{table:simulation-conditions}.
-These conditions are meant to reflect the conditions found inside a typical cell.
-\textbf{of what species?}\\
+\subsection{Calculating one/bothbound times of experimental dynein}
+In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
+
+\newcommand\tbb{\left<t_{bb}\right>}
+\newcommand\tob{\left<t_{ob}\right>}
+\newcommand\tstep{\left<t_{step}\right>}
+\newcommand\tproc{\left<t_{processivity}\right>}
+\newcommand\kub{k_{ub}}
+\newcommand\kb{k_{b}}
+\newcommand\ko{k_{dis}}
+
+\begin{itemize}
+\item $\tbb$: Time in bothbound per step
+\item $\tob$: Time in onebound per step
+\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+\end{itemize}
+
+$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
+
+\begin{align*}
+  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
+  \tob &= \tstep-\tbb\\
+  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
+  &= \frac{\tstep^2}{\tstep+\tproc}\\
+\end{align*}
+
+Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
 
@@
   \centering
-  \begin{tabular}{| l | l |}
+  \begin{tabular}{| c | c | c | c | c | c |}
     \hline
-    T & [ATP] \\ \hline
-    310.15 K & $1mM$\\ \hline
+    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
   \end{tabular}
-  \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
-  \label{table:simulation-std-conditions}
+  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
+  \label{table:time-parameter-table}
 \end{figure}
 
-\subsection{Fitting rate constants}
-To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
+%% \subsection{Fitting rate constants}
+%% To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
 The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}.
@@
 
-\textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
-
-\subsection{Fitting spring constants}
-This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
+%% \textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
+
+%% \subsection{Fitting spring constants}
+%% This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
 
@@
 
-Solving the above system for $\dot{\Theta}_{bb}, \dot{\Theta}_{bm}, \dot{\Theta}_{um}$ and $\dot{\Theta}_{ub}$ gives the desired velocities. Solution was done via Mathematica.
+Solving the above system for $\dot{\theta}_{bb}, \dot{\theta}_{bm}, \dot{\theta}_{um}$ and $\dot{\theta}_{ub}$ gives the desired velocities. Solution was done via Mathematica.
 
@@
 
-Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
+Solving the above system for $\dot{\theta}_{nm}$ and $\dot{\theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
+
+\chapter{Conformational tests}
+\label{sec:conformational-tests}
+The models were tested in the following different conformations to verify they behaved as expected:\\
+
+\textbf{Onebound tests}
+\begin{itemize}
+\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths.
+Also checks that all angular velocities are zero.
+This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or cartesian) without forces.
+\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths.
+Also check that all velocities are zero.
+This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
+\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that cartesian x-velocities are positive and y-velocities are zero.
+Verifies that the cartesian velocities have the expected sign.
+\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all cartesian velocities are zero.
+Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
+  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite.
+Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
+\end{itemize}
+*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
+
+These tests together verify that the onebound model's internal coordinate system's directions match the XY coordinate system directions, that the angular directions in the model properly align with the $\pm x$ and $\pm y$ directions of the XY coordinate system, that velocities have the proper magnitude at zero force and proper sign at nonzero force, and that Brownian and internal forces are in the same unit system.
+There are still errors which could exist in the model pertaining to magnitude of velocity, which will be tested for in the energy conservation section.\\
+
+\textbf{Bothbound tests}
+\begin{itemize}
+\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^(-25)$) and motor domains nearly vertical ($\theta_{n/f} = \pi \pm 10^(-15)$).
+Equilibrium angles set to have a vertical line as the lowest energy point.
+Model is not exactly vertical for NaN concerns explained in section \ref{corrections-section}.
+Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero.
+Verifies that the domains are properly oriented by the angles, the angles are defined properly and forces are calculated from angles properly.
+\item \textbf{Bothbound:} \textit{Equilateral house conformation with outward x-forces.} The model forms the shape of a square with an equilateral triangle on top, with the tail domain as the triangle.
+Checks if all domains are at the desired locations and the derivatives are the proper sign and are equal and opposite to their counterparts on the opposing side of the house.
+This test verifies that the angular system behaves as expected and forces are symmetric about the two dimers.
+\item \textbf{Bothbound:} \textit{Two table conformations with near/far domains flipped.} Two models are put in the same table-like conformation, but the near/far domains are flipped.
+Checks if opposite domains have the same positions and forces.
+Re-verifies that the model is symmetric in position and force between the two dimers.
+\end{itemize}
+
+These tests verify the bothbound model's angle system behaves as expected, forces are zero when expected and have the proper signs, and that the whole system is symmetric with either dimer.
 

### 2017-05-12 thesis/latex/thesis.tex

@@
 Transitions from one state to another are accomplished by calculating the probability of a transition $t$ at a given timestep, given by $P_{t} = k_tdt$.
-Each timestep a value in $[0,1]$ is sampled from a random number generator and, if lower than $k_tdt$, the respective transition is made.
+Each timestep a value in $[0,1]$ is sampled from a random number generator and, if the roll is lower than $k_tdt$, the respective transition is made.
 The following sections describe how transitions are done.\\
@@
 \subsubsection{Bothbound to onebound transition calculation}
-Similar to the binding transition, unbinding involves creating a new onebound dynein from the old bothbound. To accomplish a transition to the farbound state, the following equations are used:\\
+Similar to the binding transition, unbinding involves creating a new onebound dynein from the old bothbound. To accomplish a transition to the farbound state, the following equations are used:
 
@@
     \begin{lstlisting}[language=C++]
-      def get_onebound_restoring_forces():
+      def set_onebound_restoring_forces():
           T = cm*(nma - nma_eq);
@@
 
-A series of conformational tests were done. These are listed in Appendix \ref{sec:conformational-tests}.\\
+A series of conformational tests were done to test if the coordinate systems of either model worked. These are listed in Appendix \ref{sec:conformational-tests}.\\
 
@@
 There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\theta_{m,eq}^{Pre}$, $\theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
-Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.\\
-
+Each of these values influences the stepping behavior of the model, and so must be chosen wisely.
+Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.
 Others are more difficult to find.
-These values, including $k_b$, $k_ub$ and the three spring constants, are fit by an optimization process.
-First un/binding rates are fit to one/bothbound times, then spring constants are fit to average step length.
-This process is chronicled below.
+These values, including $k_b$, $k_ub$ and the three spring constants, must be found via fitting the model to experiment.\\
+
+The process entails running simulations at various binding rates and spring constants, checking the output, and optimizing the input parameters until physical stepping behavior is achieved.
+Fitting these parameters to experiment is an active area of work on this project, but has shown tentative positive results, as shown in the Results section.\\
 
@@
 
-\subsection{Calculating one/bothbound times of experimental dynein}
-In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
-
-\newcommand\tbb{\left<t_{bb}\right>}
-\newcommand\tob{\left<t_{ob}\right>}
-\newcommand\tstep{\left<t_{step}\right>}
-\newcommand\tproc{\left<t_{processivity}\right>}
-\newcommand\kub{k_{ub}}
-\newcommand\kb{k_{b}}
-\newcommand\ko{k_{dis}}
-
-\begin{itemize}
-\item $\tbb$: Time in bothbound per step
-\item $\tob$: Time in onebound per step
-\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
-\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
-\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
-\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
-\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
-\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
-\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
-\end{itemize}
-
-$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
-
-\begin{align*}
-  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
-  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
-  \tob &= \tstep-\tbb\\
-  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
-  &= \frac{\tstep^2}{\tstep+\tproc}\\
-\end{align*}
-
-Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| c | c | c | c | c | c |}
-    \hline
-    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
-  \end{tabular}
-  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
-  \label{table:time-parameter-table}
-\end{figure}
+%% \subsection{Calculating one/bothbound times of experimental dynein}
+%% In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
+
+%% \newcommand\tbb{\left<t_{bb}\right>}
+%% \newcommand\tob{\left<t_{ob}\right>}
+%% \newcommand\tstep{\left<t_{step}\right>}
+%% \newcommand\tproc{\left<t_{processivity}\right>}
+%% \newcommand\kub{k_{ub}}
+%% \newcommand\kb{k_{b}}
+%% \newcommand\ko{k_{dis}}
+
+%% \begin{itemize}
+%% \item $\tbb$: Time in bothbound per step
+%% \item $\tob$: Time in onebound per step
+%% \item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+%% \item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+%% \item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+%% \item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+%% \item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+%% \item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+%% \item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+%% \end{itemize}
+
+%% $\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
+
+%% \begin{align*}
+%%   \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+%%   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+%%   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+%%   \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+%%   \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
+%%   \tob &= \tstep-\tbb\\
+%%   &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
+%%   &= \frac{\tstep^2}{\tstep+\tproc}\\
+%% \end{align*}
+
+%% Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
+
+%% \begin{figure}[h]
+%%   \centering
+%%   \begin{tabular}{| c | c | c | c | c | c |}
+%%     \hline
+%%     Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+%%     134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+%%   \end{tabular}
+%%   \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
+%%   \label{table:time-parameter-table}
+%% \end{figure}
 
@@
 
-\section{Validating model}
-The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
+%% \section{Validating model}
+%% The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
 Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over a long time.
@@
 
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
-    \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
-  \end{minipage}
-  \hspace{.2cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
-    \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
-  \end{minipage}
-  \label{fig:equipartition_agreement}
-\end{figure}
+%% \begin{figure}[h!]
+%%   \centering
+%%   \begin{minipage}[b]{0.45\textwidth}
+%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
+%%     \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
+%%   \end{minipage}
+%%   \hspace{.2cm}
+%%   \begin{minipage}[b]{0.45\textwidth}
+%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
+%%     \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
+%%   \end{minipage}
+%%   \label{fig:equipartition_agreement}
+%% \end{figure}
 
 \section{Model achieves processivity}
-When run at the proper parameters, the dynein model can step processively.
-Figure \ref{fig:stepping-trajectory} shows the dynamics of a motor when run at the parameters shown in Table \ref{table:thesis-parameters}.
+When the simulation is run at the parameters shown in \ref{table:thesis-parameters}, the model exhibits stepping behavior, as shown in Figure \ref{fig:stepping-trajectory}.\\
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{../../plots/trajectory-plot_thesis}
+  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
   \caption{Near and far binding domains over the course of several microseconds of simulation.
@@
 This state would eventually transition to the high-microtubule-affinity state after some time.
-If this proves to be necessary to decrease small steps, this would be an interesting result showing that the motor might rely on its low-microtule-affinity ADP-Pi state to prevent early binding.\\
+If this proves to be necessary to decrease small steps, this would be an interesting result showing that the motor might rely on its low-microtubule-affinity ADP-Pi state to prevent early binding.\\
 
@@
 
+\subsection{Experimental validation}
 To more strongly support the linker-swing/diffusive step model of dynein motion, more experiments should be done.
@@
 
-\textbf{Talk to Dr. Hsu about this sort of thing...what experiments could be used to validate the model?}
-
-If the model were validated by FRET and rigidity mutation studies, then there are many other interesting things which could be found from it.
+%% \textbf{Talk to Dr. Hsu about this sort of thing...what experiments could be used to validate the model?}
+
+\subsection{Further questions}
+If the model were validated by FRET and rigidity mutation studies, there are many other interesting things which could be found from it.
 First, the amount of work done by the motor could be found by inducing an artificial drag force pulling the protein's motor domains against its direction of travel.
@@
 
-Next: add Big Questions to introduction, then answer them here.\\
+\subsection{The future of dynein research}
+The motor protein field has come a long way over the past two decades.
+Theoretical papers in the 90s, such as \textit{Bhaba et.
+al.} \cite{bhabha-paper},  opened up many questions about how cells can use proteins and simple chemical reactions to generate directed, finely-controlled motion.
+Following these papers came low-resolution structures and experiments testing the stepping behavior, directionality, conformation changes and chemical affinities of these motors.
+As structural technology got better, resolution got better, until eventually amino-acid resolution structures were found \cite{schmidt-carter}.
+These structures allowed more informed hypotheses to integrate experimental data and structures into well-advised theories on motor motility, such as \textit{Andreasson et.
+al.} for kinesin \cite{kinesin-cycle} and \textit{Cianfrocco et.
+al.} for dynein \cite{cianfroccoreview}.
+These theories are now being tested using state of the art methods.
+For example, a lab at Penn State is currently exploring kinesin dynamics using gold nanoparticles, and is capable of getting 2nm spatial resolution and 1ms temporal resolution \cite{kinesin-gold-nanoparticle}.
+This level of detail would provide intra-step information about the kinesin mechanochemical cycle, confirming or rejecting hypotheses about how the motor steps.
+If such technology were applied to dynein, the accuracy of the Cianfrocco model and the role of diffusion would be definitively determined.
+However, such experiments take time to design and implement.
+In the meantime, modelling projects like the one in this thesis can be used to provide rough windows into the nanoscale world, guiding future experimental work.
+They sanity-check theories and help scientists form new questions, such as if dynein drags along the microtubule or diffuses above it.
+It is uncertain what direction the field will go over the coming decade, but it is clear that now is a very exciting time for dynein research.\\
 

### 2017-05-13 thesis/latex/thesis.tex
Thesis: spellcheck

@@
 
-\listoftables % Prints the list of tables
+%% \listoftables % Prints the list of tables
 \newpage
@@
 \subsection{Why do cells need motor transport?}
-Cells are organized, heretogenous structures which respond quickly to their environments.
+Cells are organized, heterogenous structures which respond quickly to their environments.
 This means that cells require a mechanism for rapidly moving components to precise locations within the cell.
@@
 %%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
-%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
+%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion constant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
 %%   \label{fig:diffusion_vs_dynein}
@@
 As shown in the crystal structure in Figure \ref{fig:pdb-motm-dynein}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
-Each of these subunits has a unique purpose for the motor.
+Each of these subunits has a unique purpose for the motor.\\
 
@@
 The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time.
-Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be infeasibly computationally expensive to simulate a dynein step.
+Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be prohibitively expensive to simulate a dynein step.
 Thus, many approximations are made about dynein to simplify the simulation.\\
@@
 The positions of each domain in time are stored as data.
-Each time a model transitions from onebound to bothbound, the model registers a ``step'' having occured.
+Each time a model transitions from onebound to bothbound, the model registers a ``step'' having occurred.
 Thus long simulations can be used to find the stepping behavior of a model.\\
@@
 According to the Cianfrocco model, dynein takes on a total of eight states during a single step.
-Many of these states are conformationally very similar, eg the ADP- vs apo-bound or ATP- vs ADP-bound.
-Others involve quick transitions, eg from the just-MT-bound state to the post-powerstroke state.
+Many of these states are conformationally very similar, e.g.
+the ADP- vs apo-bound or ATP- vs ADP-bound.
+Others involve quick transitions, e.g.
+from the just-MT-bound state to the post-powerstroke state.
 The transitions which take the most time according to reaction rate calculations are MT-binding and MT-release \cite{sarlahmodel}.
@@
 The model ``steps'' whenever an MTBD diffuses near the microtubule.
-\textit{In vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
+\textit{in vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
 Thus, all dynein steps should be multiples of $8$nm.
@@
 The goal is to express angular velocities $\dot{\theta}_{bb}, \dot{\theta}_{bb}, \dot{\theta}_{bb}$ and $\dot{\theta}_{bb}$ in terms of known quantities.
-To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner.
+To begin, the Cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner.
 A subset of the equations are shown here:
@@
 %
-Another way to express these cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:
+Another way to express these Cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:
 
@@
 
-These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations.
+These two sets of equations, Cartesian and Brownian, can be equated to get more interesting equations.
 For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated.
@@
 
-This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\theta_{bm}}(\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub})$.
+This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, e.g.
+$\dot{\theta_{bm}}(\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub})$.
 These motion equations are further described in (\ref{sec:AppendixOneboundEquations}).\\
@@
   \end{tabular}
-  \caption{Code snippet}{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
+  \caption{Euler's method code snippet.}{This code calculates domain velocities for onebound dynein and uses them to find position displacements.
+These values are stored in temporary variables first, then updated all at once.}
   \label{snip:euler-code-snippet}
@@
   \end{tabular}
-  \caption{Code snippet of restoring force calculation for near motor domain displacement.}{Torque is calculated the near motor's angular displacement from equilibrium.
+  \caption{Code snippet of restoring force calculation.}{Torque is calculated the near motor's angular displacement from equilibrium.
 This is converted to force exerted on adjacent domains.
@@
 
-where $\theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the cartesian displacement of each domain $n$ due to the nudge.
+where $\theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the Cartesian displacement of each domain $n$ due to the nudge.
 This test is powerful since it links the force-calculation system of either model to the energy calculation system.
@@
 This is evidence that both the forces and velocities of the model are properly calculated.
-Grossly inncorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy.
+Grossly incorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy.
 The model's force calculations are further validated in Section \ref{sec:conformational-tests}, and energy conservation is validated in Section \ref{sec:energy-conservation}.\\
@@
   \end{tabular}
-  \caption{Parameters used in processive simulations in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
+  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
   \label{table:thesis-parameters}
@@
   \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
-  \caption{Near and far binding domains over the course of several microseconds of simulation.
-Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
+  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation.
+The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer.
+Top: x-projection of binding domains over time.
+The motor steps roughly 50nm in 10 $\mu s$.
+Middle: cartoon depictions of the model during simulation.
+In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots.
+That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$.
+The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model.
+Bottom: y-projection of binding domains over time.
+Notice that only one binding domain is above 0nm at any time.}
   \label{fig:stepping-trajectory}
@@
 \section{Model step size is highly variant}
-Figure \ref{fig:final-histograms}.a shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}.
+Figure \ref{fig:final-histograms} shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}.
 This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\
@@
     \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
-    \caption{Model vs experimental step sizes.
-\textbf{a.)} Step sizes model took at parameters in \ref{table:thesis-parameters}.
-\textbf{b.)} Experimental stepping behavior of dynein \cite{weihongpaper}.}
+    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model.
+Note the model can generate 25nm steps, but has a high preference for <5nm steps.
+Also note that no backward steps are generated by the model.
+Simulation run at conditions in \ref{table:thesis-parameters}.
+Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
     \label{fig:final-histograms}
@@
 
-Figure \ref{fig:final-histograms}.a shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
+Figure \ref{fig:final-histograms} shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
 This is a very important result, since it indicates that the model is capable of taking a varied step size.
@@
 In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram.
-This may not be how the experiment in \ref{fig:final-histograms}.b records steps.
+This may not be how the experiment in \ref{fig:final-histograms} records steps.
 Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely.
@@
 
-Comparing the simulation results in \ref{fig:final-histograms}.a with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein.
+Comparing the simulation results in \ref{fig:final-histograms} with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein.
 However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein.
@@
 If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating.
-This result would show that the differences betwen kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants.
+This result would show that the differences between kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants.
 This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\
@@
 Also checks that all angular velocities are zero.
-This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or cartesian) without forces.
+This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or Cartesian) without forces.
 \item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths.
@@
 This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that cartesian x-velocities are positive and y-velocities are zero.
-Verifies that the cartesian velocities have the expected sign.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all cartesian velocities are zero.
+\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that Cartesian x-velocities are positive and y-velocities are zero.
+Verifies that the Cartesian velocities have the expected sign.
+\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all Cartesian velocities are zero.
 Verifies that upwards forces in an already-vertical stalk have no effect on velocity.

### 2017-05-13 thesis/latex/thesis.tex
Thesis: minor cleanup.

@@
 Kinesin, myosin and dynein are the three main motor proteins in cells.
-Though these proteins have significantly different ancestors \ref{hook-family}, they all evolved into a single similar structure.
+Though these proteins have significantly different ancestors \cite{hook-family}, they all evolved into a single similar structure.
 In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way of solving a problem.
@@
 An interesting question is, if proteins like dynein are synthesized in the cell body but needed at the axon tip to perform retrograde transport, how do dynein get to the tip?
-The answer is shown in \ref{retrograde-transport}: kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\
+The answer is shown in Figure (\ref{retrograde-transport}): kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\
 
@@
 \subsection{Dynein structure}
-As shown in the crystal structure in Figure \ref{fig:pdb-motm-dynein}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
+As shown in the crystal structure in Figure (\ref{fig:pdb-motm-dynein}), a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
 Each of these subunits has a unique purpose for the motor.\\
@@
 Dynein is a fusion of two identical proteins, referred to as monomers.
-A single monomer, depicted in \ref{fig:pdb-motm-dynein}, is composed of a microtubule-binding domain (MTBD), a stalk, a buttress, a motor domain, a linker and a tail.
+A single monomer, depicted in (\ref{fig:pdb-motm-dynein}), is composed of a microtubule-binding domain (MTBD), a stalk, a buttress, a motor domain, a linker and a tail.
 The MTBD is responsible for binding to the microtubule.
@@
 Kinesin proteins are generally 100-200 kD in mass, whereas dynein is on the order of 1mD.
-As shown in Figure \ref{fig:kinesin-vs-dynein}, the dynein motor domain is much bigger than the kinesin motor domain.
+As shown in Figure (\ref{fig:kinesin-vs-dynein}), the dynein motor domain is much bigger than the kinesin motor domain.
 Another key difference is the separation between ATP hydrolysis sites on either protein.
 Kinesin's ATP hydrolysis site is inside the globular microtubule-binding domain.
-In contrast, Dynein binds to the MT with its MTBD, colored yellow in Figure \ref{fig:kinesin-vs-dynein}, and hydrolyses ATP in its motor domain, which is colored cyan.
+In contrast, Dynein binds to the MT with its MTBD, colored yellow in Figure (\ref{fig:kinesin-vs-dynein}), and hydrolyses ATP in its motor domain, which is colored cyan.
 This distance is close to 20nm in length - much longer than kinesin.
 This large separation might act like a loose ``leash,'' allowing the binding domain to diffuse freely around the microtubule.
-Kinesin has a much more rigid leash, as shown in the bottom pane of \ref{fig:kinesin-vs-dynein}.
+Kinesin has a much more rigid leash, as shown in the bottom pane of (\ref{fig:kinesin-vs-dynein}).
 This more rigid leash may prevent diffusion from happening as much.\\
@@
 Image from \cite{kinesin-vs-dynein}.
-Right: Full motor complexes of dynein and kinesin.
-The blue regions of either protein are the motor domains, which are pictured in the above crystal structures.
-Image from \cite{kinesin-vs-dynein-2}.}
+Right: Full motor complexes of dynein and kinesin inspired by cryo-EM microscopy.
+The blue regions on the right image of either protein are the motor domains, which are pictured in the left crystal structures.
+Not present in the left cyrstal structures are the tail and intermediate chains of either protein.
+Right image from \cite{kinesin-vs-dynein-2}.}
   \label{fig:kinesin-vs-dynein}
@@
 
-Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the trail \cite{FRETstatepaper} \cite{burgess-paper}.
-Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.\\
+Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the tail \cite{FRETstatepaper} \cite{burgess-paper}.
+Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.
+The shifting of the linker domain in the ADP state is known as the powerstroke, and is believed to be the principle cause for dynein's forward step.\\
 
@@
   \hspace{1cm}
-  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/linker-swing}
+  \includegraphics[width=.95\textwidth,keepaspectratio]{../../figures/linker-swing}
   \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states.
@@
 Bottom right: Motor in ADP state.
-The linker undergoes an approximately 40 degree swing between these two states.
+The linker undergoes an approximately 40 degree swing between these two states known as the powerstroke.
 Figure borrowed from \cite{bhabha-paper}.}
@@
 
-Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper} (make a Chimaera figure where the pre/poststroke motors are docked showing this).
+Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}.
 Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\
@@
 al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig.
-\ref{mech-cycle}.
+(\ref{mech-cycle}).
 The model claims the primary events in the dynein step are as follows.
@@
 Given the experimental challenges, a computational approach seems promising.
-This approach involves creating a hypothesis on how the motor walks, creating a model which behaves according to this hypothesis, simulating that model, and comparing the simulation's behavior to experimental data.
+This approach involves forming a hypothesis on how the motor walks, creating a model which behaves according to this hypothesis, simulating that model, and comparing the simulation's behavior to experimental data.
 This process can be an efficient way to support hypotheses and guide future research.\\
@@
 \section{Model overview}
-The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell.
+The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model (\ref{sec:cianfrocco-model}) would behave in a cell.
 In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation.
@@
 The model is composed of two separate systems of five point particles, with each point representing a domain of dynein: two binding domains, two motor domains and one tail domain.
-Physical representations of these two systems are shown in Figure \ref{fig:theory-intro}.
+Physical representations of these two systems are shown in Figure (\ref{fig:theory-intro}).
 The points are connected together by rigid rods, and the sytems are defined by the angles the rods make at each point.
@@
 
-As shown in Figure \ref{fig:pdb-motm-dynein}, dynein's motor and tail domains are fairly spherical.
+As shown in Figure (\ref{fig:pdb-motm-dynein}), dynein's motor and tail domains are fairly spherical.
 Though the stalk and tail connecting these domains is definitely not massless, it is small enough that approximating it as massless should be reasonable.
-Making the radii of the spherical domains slightly larger should account for any drag caused by the rigid rods.
+Making the radii of the spherical domains slightly larger should account for any drag caused by the rigid rods.\\
 
@@
 This assumption makes the math easier.
-One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \ref{burgess-paper}.
-However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \ref{myosin-cc-elasticity}.
+One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \cite{burgess-paper}.
+However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \cite{myosin-cc-elasticity}.
 Another dynein simulation done by Sarlah \textit{et.
@@
 This energy can be used to calculate a return force which pushes the domain back to equilibrium.
-A depiction of this is shown in Figure \ref{fig:angular-spring}.\\
+A depiction of this is shown in Figure (\ref{fig:angular-spring}).\\
 
@@
 This assumption is made to simplify the model.
-Other dynein models, like the winch model \ref{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions.
+Other dynein models, like the winch model (\ref{sarlahmodel}), add in attractive and repulsive forces between the two motors which act in three dimensions.
 This model ignores such effects.\\
@@
 Thus, if velocity equations can be found for the individual domains, then dynein's dynamic behavior can be solved for using numerical integration.
-The Brownian dynamics equation shown in Section \ref{sec:bd} provides velocity at time t from forces at time t.
+The Brownian dynamics equation shown in Section (\ref{sec:bd}) provides velocity at time t from forces at time t.
 All that needs to be done is to come up with expressions for the forces on each domain, which is done in the next two sections.\\
@@
 Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound.
-A spatial representation of onebound dynein is shown in Figure \ref{fig:derivation-onebound}.
+A spatial representation of onebound dynein is shown in Figure (\ref{fig:derivation-onebound}).
 
@@
 
-As shown in Section \ref{final-parameter-table}, the MT binding rate is much quicker than the unbinding rate.
+As shown in Section (\ref{final-parameter-table}), the MT binding rate is much quicker than the unbinding rate.
 This means that, when just unbound, the rate of rebinding is very high.
@@
 
-A series of conformational tests were done to test if the coordinate systems of either model worked. These are listed in Appendix \ref{sec:conformational-tests}.\\
+A series of conformational tests were done to test if the coordinate systems of either model worked. These are listed in Appendix (\ref{sec:conformational-tests}).\\
 
@@
 To test if the models obey the ET, the total potential energy of each model was logged over $10^7$ timesteps of simulation.
-The results are reported in Figure \ref{equipartition_agreement}, where the PE scale is in units of $\frac12 k_bT$.
+The results are reported in Figure (\ref{equipartition_agreement}), where the PE scale is in units of $\frac12 k_bT$.
 Energies are reported as a running average over the simulation from 0 to time $t$.
@@
 Each of these values influences the stepping behavior of the model, and so must be chosen wisely.
-Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.
+Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table (\ref{parameter-table}).
 Others are more difficult to find.
@@
 \section{Model achieves processivity}
-When the simulation is run at the parameters shown in \ref{table:thesis-parameters}, the model exhibits stepping behavior, as shown in Figure \ref{fig:stepping-trajectory}.\\
+When the simulation is run at the parameters shown in (\ref{table:thesis-parameters}), the model exhibits stepping behavior, as shown in Figure (\ref{fig:stepping-trajectory}).\\
 
@@
   \end{tabular}
-  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
+  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures (\ref{fig:stepping-trajectory}) and (\ref{fig:final-histograms}).}
   \label{table:thesis-parameters}
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
   \centering
@@
 
-Figures \ref{fig:stepping-trajectory}.b and \ref{fig:stepping-trajectory}.c demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time.
+Figures (\ref{fig:stepping-trajectory}) and (\ref{fig:stepping-trajectory}) demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time.
 This behavior indicates that a springy hinge model with shifting equilibrium angles is capable of generating processive stepping behavior.
@@
 
-Another important determination from Figure \ref{fig:stepping-trajectory}.c is the average position of the unbound foot is about 30\textit{nm} above the microtubule.
+Another important determination from Figure (\ref{fig:stepping-trajectory}) is the average position of the unbound foot is about 30\textit{nm} above the microtubule.
 This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible.
@@
 \section{Model step size is highly variant}
-Figure \ref{fig:final-histograms} shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}.
+Figure (\ref{fig:final-histograms}) shows the stepping pattern of the model at the parameters shown in Table (\ref{table:thesis-parameters}).
 This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\
@@
 Also note that no backward steps are generated by the model.
-Simulation run at conditions in \ref{table:thesis-parameters}.
+Simulation run at conditions in (\ref{table:thesis-parameters}).
 Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
@@
 
-Figure \ref{fig:final-histograms} shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
+Figure (\ref{fig:final-histograms}) shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
 This is a very important result, since it indicates that the model is capable of taking a varied step size.
@@
 In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram.
-This may not be how the experiment in \ref{fig:final-histograms} records steps.
+This may not be how the experiment in (\ref{fig:final-histograms}) records steps.
 Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely.
@@
 
-Comparing the simulation results in \ref{fig:final-histograms} with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein.
+Comparing the simulation results in (\ref{fig:final-histograms}) with the experimental results in (\ref{fig:final-histograms}), it is clear that the model is still far from experimental dynein.
 However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein.
@@
 Equilibrium angles set to have a vertical line as the lowest energy point.
-Model is not exactly vertical for NaN concerns explained in section \ref{corrections-section}.
+Model is not exactly vertical for NaN concerns explained in section (\ref{corrections-section}).
 Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero.

### 2017-05-31 thesis/latex/thesis.tex
Thesis: add column to literature values tbale.

@@
     \hline
-    & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
+    & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Leschziner \cite{leschziner} & Kon & Burgess \\\hline
     $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
@@
     $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & & & \\ \hline
+    $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & 60 & & \\ \hline
     $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
@@
     $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
-    $c_t$ & & && & & & \\ \hline
-    $c_m$ & & && & & & \\ \hline
-    $c_b$ & & && & 140 kJ/mol & & \\ \hline
   \end{tabular}
@@
 \end{figure}
+
+%% \begin{figure}[h]
+%%   \centering
+%%   \begin{tabular}{| l | l | l | l | l | l | l | l |}
+%%     \hline
+%%     & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
+%%     $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
+%%     $L_t$ &  7nm && & 11.15nm & & & \\ \hline
+%%     $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
+%%     $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
+%%     $R_t$ &  & & &2.16nm & & & \\ \hline
+%%     $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
+%%     $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
+%%     $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & & & \\ \hline
+%%     $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
+%%     $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
+%%     $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
+%%     $c_t$ & & && & & & \\ \hline
+%%     $c_m$ & & && & & & \\ \hline
+%%     $c_b$ & & && & 140 kJ/mol & & \\ \hline
+%%   \end{tabular}
+%%   \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
+%%   \label{table:parameter-table}
+%% \end{figure}
 

### 2017-06-08 thesis/latex/thesis.tex
Thesis: Incoroprate first two pages of David's suggestions.

@@
 Although the three motor protein families operate using the same stepping cycle, their behaviors differ significantly.
-Kinesin and myosin are predictable motors which step in the forward direction with a regular step size [get kinesin, myosin stepping papers].
+Kinesin and myosin are predictable motors which step in the forward direction with a regular step size.
 In contrast, dynein's stepping pattern varies in both size and direction.
@@
   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (green/blue) and several tail proteins (pink) come together to form the dynein motor complex.
-One monomer's binding domain is bound to the microtubule, and the other is diffusing.
+  \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (cyan and blue) and several tail proteins (pink) come together to form the dynein motor complex.
+One monomer's binding domain is bound to the microtubule (green), and the other is diffusing.
 ATP hydrolysis sites are labeled glowing green.
@@
 
-Dynein is believed to move by using the energy of ATP to cycle through a ring of states, each with different spatial relations to the microtubule.
-By cycling forward through this ring, the molecule will end up in the same state it began, but moved forward a small amount.
-This ring of states is known as the mechanochemical cycle \cite{cianfroccoreview}.
+Dynein is believed to move by using the energy of ATP to cycle through a sequence of states, each with different spatial relations to the microtubule.
+By cycling forward through this sequence, the molecule will end up in the same state it began, but moved forward a small amount.
+This sequence of states is known as the mechanochemical cycle \cite{cianfroccoreview}.
 The goal of this project is to create a mathematical model of the mechanochemical cycle and verify that it can reproduce experimental dynein stepping data.
-There are several types of dynein which all behave differently.
+There are several types of dynein which all behave slightly differently.
 This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\
@@
 This can be a challenge, since cells are fairly large compared to the proteins which compose them.
-A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter.
+A human fibroblast cell has a volume of roughly 2000 $\mu\text{m}^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter.
 In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\
@@
   \end{tabular}
-  \caption{Euler's method code snippet.}{This code calculates domain velocities for onebound dynein and uses them to find position displacements.
+  \caption{Domain time evolution via Euler's method code snippet.}{This code calculates domain velocities for onebound dynein and uses them to find position displacements.
 These values are stored in temporary variables first, then updated all at once.}

### 2017-08-12 timeCorrelationTests/fft_speedup/convolution_theorem.tex
changes for adding fft

\documentclass[11pt]{article}

\usepackage{amsmath, amsthm, amssymb}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Real}{mathbb{R}}

\begin{document}

\title{Convolution Theorem for Autocorrelation Speedup} 
\author{John Waczak} 
\date{\today}
\maketitle

\paragraph{Motivation} 	
	In order to validate the $dt$ usage in our dynein simulation, I have run multiple simulations for the bound and unbound states (by choice of parameters) at different values of $dt$. To compare the simulations, an autocorrelation function was generated for the potential energy data by dynein domain (tail, motor, binding). This function is of the form:

	\begin{align}
		\rho(\tau) &= \frac{\int_{-\infty}^{\infty} [(f(t)-\mu)(f(t+\tau)-\mu)]dt}
		{\int_{-\infty}^{\infty}(f(t)-\mu)^2}dt \\ 
		\rho(k) &= \frac{\sum_{0}^{t_{max}-k} (f(t)-\mu)(f(t+k)-\mu)}
		{\sum_{0}^{t_{max}-k}(f(t)-\mu)^2}
	\end{align}

	Where (1) is the continuous version and (2) the discrete. The problem with this formula though is that it is slow. For a data set of n values we want to compute n different k's in order to generate our autocorrelation function. This is of order $n^2$ computations.

\end{document}

### 2017-08-12 timeCorrelationTests/autocorrelation.py

@@ -69,6 +69,9 @@ def autoCorrelate2(data, Nmax = None, skipIndex = 1, verbose = False):
         rho[k] = R/N
     return rho
 
+def autoCorrelateFFT():
+    pass 
+
 if __name__ == "__main__":
     A = np.random.rand(1000)
     rho10 = autoCorrelate2(A, Nmax = 500, skipIndex = 10)

### 2017-09-21 reorganize/papers/fft_speedup/convolution_theorem.tex
reorganizing

\documentclass[11pt]{article}

\usepackage{amsmath, amsthm, amssymb}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Real}{mathbb{R}}

\begin{document}

\title{Convolution Theorem for Autocorrelation Speedup} 
\author{John Waczak} 
\date{\today}
\maketitle

\paragraph{Motivation} 	
	In order to validate the $dt$ usage in our dynein simulation, I have run multiple simulations for the bound and unbound states (by choice of parameters) at different values of $dt$. To compare the simulations, an autocorrelation function was generated for the potential energy data by dynein domain (tail, motor, binding). This function is of the form:

	\begin{align}
		\rho(\tau) &= \frac{\int_{-\infty}^{\infty} [(f(t)-\mu)(f(t+\tau)-\mu)]dt}
		{\int_{-\infty}^{\infty}(f(t)-\mu)^2}dt \\ 
		\rho(k) &= \frac{\sum_{0}^{t_{max}-k} (f(t)-\mu)(f(t+k)-\mu)}
		{\sum_{0}^{t_{max}-k}(f(t)-\mu)^2}
	\end{align}

	Where (1) is the continuous version and (2) the discrete. The problem with this formula though is that it is slow. For a data set of n values we want to compute n different k's in order to generate our autocorrelation function. This is of order $n^2$ computations. To speed this up, we can employ the convolution theorem to allow us to make use of the speed Fast Fourier Transform (FFT). The following is a derivation of the equations necessary to perform this mathematical trick.

\paragraph{Derivation}	
To begin, we will forget about the normalization term in the denominator and focus on the numerator of (1), redefining the functions involved and then redefining them again using the Fourier transform. Let $\F$ denote the Fourier transform and $\F^{-1}$ its inverse.

\begin{align*}
	\rho(\tau) &= \int_{-\infty}^{\infty}[(f(t)-\mu)(f(t+\tau)-\mu)] dt \\
	g(t) &\equiv f(t)-\mu \\ 
	\rho(\tau) &= \int_{-\infty}^{\infty}g(t)\cdot g(t+\tau) dt \\ 
	g(t) &= \F^{-1}[\widetilde{g}(\omega)] = \int_{-\infty}^{\infty} \widetilde{g}(\omega) e^{i\omega t} d\omega \\ 
	\rho(\tau) &= \int \int \widetilde{g}(\omega) e^{i \omega t} d\omega \int \widetilde{g}(\omega') e^{i \omega' (t+\tau)} d\omega'
\end{align*}

I have stopped including the bounds for ease of typing. They will remain the same. Notice that because $\omega$ is an arbitrary choice of 'name' for the dependent variable after the transformation, we can differentiated between the transformed $g(t)$ and $g(t+\tau)$. This enables us to manipulate the integrals in the following way:

\begin{align*}
	\rho(\tau) &= \int \int \widetilde{g}(\omega)\widetilde{g}(\omega') d\omega d\omega' \int e^{i\omega t}e^{i\omega'(t+\tau)} dt \\ 
	&= \int \int \widetilde{g}(\omega)\widetilde{g}(\omega') e^{i \omega' \tau} d\omega d\omega' \int e^{i t (\omega + \omega')} dt \\ 
	&= \int \int \widetilde{g}(\omega)\widetilde{g}(\omega') \delta(\omega+\omega') d\omega d\omega' \\ 
	&= \int \widetilde{g}(\omega') \widetilde{g}(-\omega')e^{i \omega' \tau} d\omega'
\end{align*}

\end{document}

### 2017-09-21 reorganize/scripts/comparison.py

@@ -1,0 +1,102 @@
+import subprocess, os
+import argparse 
+import numpy as np
+import matplotlib.pyplot as plt
+import dynein.run as run 
+
+
+def act(data, Nmax = None): #generate autocorrelation function
+    if Nmax is not None:
+        f_t = data[:Nmax]
+    else:
+        f_t = data[::]
+    mu = np.mean(f_t)
+    f_w = np.fft.fft(f_t-mu)
+    f_w_conj = np.conjugate(f_w)
+    norm2 = f_w*f_w_conj
+    rho = np.fftifft(norm2)
+    rho = rho/rho[0] #normalize by first element
+    return rho
+
+if __name__ == '__main__':
+    
+    parser = argparse.ArgumentParser(description = 'A script to test simulation performance at various values of dt')
+
+    parser.add_argument("-L", "--label", dest = 'label', default = 'compare', help = 'label for output graphs')
+    parser.add_argument("-v", "--verbose", action = 'store_true', dest = 'verbose', default = False, help = 'print extra status messages')
+    group = parser.add_mutually_exclusive_group()
+    group.add_argument("-o", "--onebound", action = "store_true", dest = 'onebound', default = False, help = 'check dt behavior for onebound state')
+    group.add_argument("-b", "--bothbound", action = "store_true", dest = 'bothbound', default = False, help = 'check dt behavior for bothbound state')
+
+    args = parser.parse_args()
+
+    LABEL = args.label
+    VERBOSE = args.verbose
+    ONEBOUND = args.onebound
+    BOTHBOUND = args.bothbound
+
+    if ONEBOUND is False and BOTHBOUND is False:    # make onebound default while keeping them mutually exclusives args 
+        ONEBOUND = True 
+    
+    if VERBOSE:
+        print "Running simulations..."
+
+    os.chdir("../")   # change to folder with generate_stepping_data
+
+    data_files = []   # 
+    
+    if ONEBOUND:
+        if VERBOSE:
+            print "ONEBOUND - dt 1e-10"
+            print "ONEBOUND - dt 1e-11"
+            print "ONEBOUND - dt 1e-11"
+
+        l = 'oneboundAC'
+        
+        basename1 = run.sim(**{"k_b": 10e-10, "k_ub": 10e20, "cb": 2.0, "cm": 2.0, "ct": 1.0, "dt": 1e-10, "label": l,
[…]

### 2017-09-22 thesis/latex/thesis.tex
random tehsis commit?

@@
 In a single cycle a binding domain unbinds from a surface, tenses its foot to kick forward, rebinds, then untenses its foot to pull the whole motor forward.
-This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\
+This pattern is repeated by both feet to generate motion \cite{kinesin-cycle, myosin-cycle}.\\
 
@@
 This can be a challenge, since cells are fairly large compared to the proteins which compose them.
-A human fibroblast cell has a volume of roughly 2000 $\mu\text{m}^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter.
-In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\
+A human fibroblast cell has a volume of roughly 2000 $\mu\text{m}^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu \text{m}$ in diameter.
+In comparison, human hemoglobin has a diameter of roughly $5 \text{nm}$ (PDB id 5ME2), a $10^3$ factor decrease in size.\\
 
@@
   \label{diffusion-equation}
-  <x> = \sqrt{2Dt}
+  \langle x\rangle = \sqrt{2Dt}
 \end{equation}
-
+%
 where D is the diffusion constant describing the diffusability of the biomolecule.
-For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell.
+For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu \text{m}^2/\text{s}$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell.
 In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.
@@
 The oppositely-directed motors take turns transporting each other, along with cargo for building the axon growth cone.
-Borrowed from \cite{valetoolbox}.}
+Image from \cite{valetoolbox}.}
   \label{retrograde-transport}
@@
 One of the main roles of the tail is connecting a monomer to its twin to form the dynein complex.
-Image borrowed from \cite{pdb-motm-dynein}.}
+Image from \cite{pdb-motm-dynein}.}
   \label{fig:pdb-motm-dynein}
@@
 \subsection{Why is dynein interesting?}
-Selective domain labeling indicates dynein's stepping pattern is highly varied \cite{reck2006single} \cite{weihongpaper}.
+Selective domain labeling indicates dynein's stepping pattern is highly varied \cite{reck2006single, weihongpaper}.
 These studies show dynein's stepping pattern to be stochastic and weakly forward-directed.
@@
 This indicates the process dynein uses to generate motion has a stochastic component to it.
-In contrast, kinesin is known to take very regular 8nm steps in the absence of large forces \cite{kinesin-step-size}.\\
+In contrast, kinesin is known to take very regular 8nm steps in the absence of large forces \cite{kinesin-step-size}.
+For reference, the diameter of a microtubule is roughly 25nm.\\
 
@@
 
-Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the tail \cite{FRETstatepaper} \cite{burgess-paper}.
+Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the tail \cite{FRETstatepaper, burgess-paper}.
 Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.
@@
 Top right: two states superimposed on one another.
-Figures borrowed from \cite{burgess-paper}.
+Figures from \cite{burgess-paper}.
 Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states.
@@
 The linker undergoes an approximately 40 degree swing between these two states known as the powerstroke.
-Figure borrowed from \cite{bhabha-paper}.}
+Figure from \cite{bhabha-paper}.}
   \label{fig:cryo-em-angles}
@@
 Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
-This site occurs roughly every 8nm, indicating dynein is restricted to step sizes which are multiples of 8nm.\\
+This site occurs roughly every 8nm, indicating dynein is restricted to forward step sizes which are multiples of 8nm.
+The motor is also capable of stepping sideways \cite{weihongpaper}, indicating total displacements which are not multiples of 8nm.\\
 
@@
 \section{Model overview}
-The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model (\ref{sec:cianfrocco-model}) would behave in a cell.
+The model constructed in this thesis is meant to approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model (\ref{sec:cianfrocco-model}) would behave in a cell.
 In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation.
@@
 At this angle, the domain feels no force.
-However, when the angle deviates from this equilibrium, a harmonic restoring force proportional to the displacement angle is applied to the involved domains to push the angle back to equilibrium.
+However, when the angle deviates from this equilibrium, a harmonic restoring torque proportional to the displacement angle is applied to the involved domains to push the angle back to equilibrium.
 Thus these two forces oppose each other during a simulation, with Brownian forces pushing the model out of equilibrium and conformational forces trying to restore equilibrium.\\
@@
 \subsection{Spherical domains connected by massless rods}
-A key feature of the model is that each domain of the protein (two feet, twp motors and a tail) is treated as a sphere.
+A key feature of the model is that each domain of the protein (two feet, two motors and a tail) is treated as a sphere.
 Each sphere is connected to one or two other spheres, as shown in Figure (\ref{fig:theory-intro}).
@@
 %
-This drag factor $\gamma$ is used later to calculate the velocity of each domain.\\
+where this drag factor $\gamma$ is used later to calculate the velocity of each domain.\\
 
@@
 This assumption makes the math easier.
-One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \cite{burgess-paper}.
+One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1\text{nm}$ \cite{burgess-paper}.
 However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \cite{myosin-cc-elasticity}.
@@
 \end{equation}
-
+%
 This energy represents the conformational energy of that particular domain.
@@
 
-where H is the Heaviside function, a step function of value 1 for $x>0$. Thus the binding rate is zero when the unbound MTBD is over $0.1$nm from the MT.\\
+where H is the Heaviside step function and $X_{uby}$ is the y position of the unbound MTBD. Thus the binding rate is zero when the unbound MTBD is over $0.1$nm from the MT.\\
 
@@
 \begin{equation}
-  R_{\sigma^2} = \sqrt{\frac{2*kb*T*\gamma}{dt}}
+  R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}
 \end{equation}
@@
 This assumption is made to simplify the model.
-Other dynein models, like the winch model (\ref{sarlahmodel}), add in attractive and repulsive forces between the two motors which act in three dimensions.
+Other dynein models, like the winch model \cite{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions.
 This model ignores such effects.\\
@@
 \vspace{.5cm}
-%
+
 Another way to express these Cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:
@@
 $F_{xn}$ is the x component of external force on each domain $n$ due to various factors.
-$\lambda_{12}\left(X_1 - X_2\right)$ is the x component of internal force on domain $2$ due to domain $1$, where $\lambda$ is a tension coefficient with units of mass per second per second.
+$\lambda_{12}\left(X_1 - X_2\right)$ is the x component of internal force on domain $2$ due to domain $1$, where $\lambda$ is a tension coefficient with units of mass per second squared, also known as a Lagrange multiplier.
 $R_{xn}$ is the Brownian coefficient representing motion due to solvent collision, with units of velocity.\\
@@
 $\dot{\theta_{bm}}(\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub})$.
-These motion equations are further described in (\ref{sec:AppendixOneboundEquations}).\\
+These motion equations are further described in Appendix (\ref{sec:AppendixOneboundEquations}).\\
 
@@
 This has the effect of diminishing the degrees of freedom of the system from four to two, assuming the motor remains above the MT.
-A spatial representation of the bothbound model is shown in Figure (\ref{fig:derivation-botbound}).\\
+A spatial representation of the bothbound model is shown in Figure (\ref{fig:derivation-bothbound}).\\
 
@@
 Dimers can no longer be differentiated by being un/bound, so are now differentiated by their z-position: being near or far from the ``camera.'' This is similar to labeling them as the right or left dimer.
-Thus there is the near binding domain $nb$, near motor $nm$, tail $t$, far motor $fm$ and far binding domain $fb$.
+Thus there is the near binding domain $nb$, near motor $\text{nm}$, tail $t$, far motor $fm$ and far binding domain $fb$.
 Both the near and far binding domains have their y-coordinate fixed at zero.
@@
 The second MTBD constraint adds another required piece of information the model must track: the x position of the second MTBD.
-This position is described by $L$, the distance between the near and far binding domains.\\
+This position is described by $L$, the displacement between the near and far binding domains.\\
 
@@
 The treatment of the near and far versions of these angles is very similar, so only the near angles will be dealt with here.
-The angles themselves are never dealt with, only their $\sin$s and $\cos$s:
+The angles themselves are never dealt with, only their sines and cosines:
 
@@
 \end{align}
-
+%
 The position of the motor and tail domains is calculated as follows, using the angle addition trigonometric identity:
@@
 \end{align}
-
+%
 These partial derivatives are then used in a system of equations very similar to that in Equations (\ref{ob_system_first}-\ref{ob_system_second}), combining Brownian and coordinate system definitions of domain velocities:
@@
 \end{align}
-
+%
 The matrix version of this system looks like:
@@
 \]
-
+%
 This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{sec:AppendixBothboundEquations}).
@@
 
-Code is available at \verb|https://github.com/elliotc12/dynein_walk.git|.
-
 \subsection{Time evolution}
@@
 A code snippet is shown in Figure (\ref{snip:euler-code-snippet}) for the onebound updating scheme.
+This code calculates domain velocities for onebound dynein and uses them to find position displacements.
+These values are stored in temporary variables first, then updated all at once.
+The \verb|dt| used to update was $10^{-11}$ seconds.
 
@@
   \end{tabular}
-  \caption{Domain time evolution via Euler's method code snippet.}{This code calculates domain velocities for onebound dynein and uses them to find position displacements.
-These values are stored in temporary variables first, then updated all at once.}
+  \caption{Domain time evolution via Euler's method code snippet.}{}
   \label{snip:euler-code-snippet}
@@
 
-The \verb|dt| used to update was $10^{-11}$ seconds.
-
 \subsection{Transitioning between states}
@@
 \label{sec:transitioning-states}
-Transitions from one state to another are accomplished by calculating the probability of a transition $t$ at a given timestep, given by $P_{t} = k_tdt$.
+Transitions from one state to another are accomplished by calculating the probability of a transition $t$ at a given timestep, given by $P_{t} = k_t\delta t$.
 Each timestep a value in $[0,1]$ is sampled from a random number generator and, if the roll is lower than $k_tdt$, the respective transition is made.
@@
 This is because \textit{in vivo}, electrostatic interactions between MTBD and MT bring the two together when they are near.
-These electrostatic interactions are not present in the model, and so are simulated by allowing binding attempts to occur when $Y_{ub} \leq 0.2nm$ above the MT.
+These electrostatic interactions are not present in the model, and so are simulated by allowing binding attempts to occur when $Y_{ub} \leq 0.1\text{nm}$ above the MT.
 When a binding attempt is successful, the unbound binding domain of the OB dynein is ``teleported'' such that $Y_{ub} = 0.0$.
@@
 \end{align}
-
+%
 To do a nearbound transition, the ``f'' and ``n'' subscripts in the above equations are swapped.\\
 
-As shown in Section (\ref{final-parameter-table}), the MT binding rate is much quicker than the unbinding rate.
-This means that, when just unbound, the rate of rebinding is very high.
-To prevent immediate rebinding, the model is given a ``rebinding immunity'' of a single timestep.
-During this immunity period, rebinding is not allowed.\\
+As shown in Section (\ref{table:thesis-parameters}), the MT binding rate is much quicker than the unbinding rate. This means that, when just unbound, the rate of rebinding is very high.\\
 
@@
 Spring and Brownian forces are used to properly move the model through time.
-Appendices (\ref{sec:ob-motion-equatons}-\ref{sec:bb-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
-
+Appendices (\ref{sec:AppendixOneboundEquations}-\ref{sec:AppendixBothboundEquations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
 Each Brownian force $R_{n,m}$ on domain $n$ in direction $m$ is sampled from a Gaussian with standard deviation $\sqrt{\frac{2k_BT\gamma_n}{dt}}$.\\
@@
 The force on the motor domain is found as the equal-and-opposite force to these two imposed forces.
-A sample calculation is shown in Snippet (\ref{snip:transition-rate-snippet}).\\
+A sample calculation is shown in Snippet (\ref{snip:transition-rate-snippet}).
+Torque is calculated the near motor's angular displacement from equilibrium.
+This is converted to force exerted on adjacent domains.
+Finally, the equal and opposite force is exerted on the near motor domain.\\
 
@@
   \end{tabular}
-  \caption{Code snippet of restoring force calculation.}{Torque is calculated the near motor's angular displacement from equilibrium.
-This is converted to force exerted on adjacent domains.
-Finally, the equal and opposite force is exerted on the near motor domain.}
+  \caption{Code snippet of restoring force calculation.}{}
   \label{snip:transition-rate-snippet}
@@
 \subsection{Equipartition theorem}
-The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $<E> = \frac N2 k_bT$.
+The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $\langle E\rangle = \frac N2 k_bT$.
 For the dynein models to display ET behavior, they would have to both properly calculate forces and properly calculate velocities from forces.
@@
 To test if the models obey the ET, the total potential energy of each model was logged over $10^7$ timesteps of simulation.
-The results are reported in Figure (\ref{equipartition_agreement}), where the PE scale is in units of $\frac12 k_bT$.
 Energies are reported as a running average over the simulation from 0 to time $t$.
@@
 The transition rate from $s_1$ to $s_2$ is $P(s_1\rightarrow s_2) = e^{-{\Delta G_2 - \Delta G_1}/K_BT}$.
-Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.\\
+Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.
+Another simulation feature this test verifies is that Brownian forces are calculated properly.\\
 
@@
 Each of these values influences the stepping behavior of the model, and so must be chosen wisely.
-Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table (\ref{parameter-table}).
+Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table (\ref{table:thesis-parameters}).
 Others are more difficult to find.
-These values, including $k_b$, $k_ub$ and the three spring constants, must be found via fitting the model to experiment.\\
-
-The process entails running simulations at various binding rates and spring constants, checking the output, and optimizing the input parameters until physical stepping behavior is achieved.
+These values, including $k_b$, $k_ub$ and the three spring constants, must be found via fitting the predictions of the model to experiment.
+This process entails running simulations at various binding rates and spring constants, checking the output, and optimizing the input parameters until physical stepping behavior is achieved.
 Fitting these parameters to experiment is an active area of work on this project, but has shown tentative positive results, as shown in the Results section.\\
@@
   \end{tabular}
-  \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
+  \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources, other simulations and crystal structures.}
   \label{table:parameter-table}
@@
 
-Another important determination from Figure (\ref{fig:stepping-trajectory}) is the average position of the unbound foot is about 30\textit{nm} above the microtubule.
+Another important determination from Figure (\ref{fig:stepping-trajectory}) is the average position of the unbound foot is about 30nm above the microtubule.
 This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible.
@@
 Instead of hovering near the microtubule looking for a binding site, the motor pulls its foot away from the microtubule, diffusing until pushed downward far enough to bind.
-This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30\textit{nm} would allow significant x-diffusion along the microtubule.
+This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30nm would allow significant x-diffusion along the microtubule.
 This could be contrasted with kinesin, which is smaller and could not move its foot so high off the microtubule.\\
 
-Importantly, the physical parameters causing processive motion are reasonable physically.
+Importantly, the parameters causing processive motion are physically reasonable.
 The spring constants are roughly the same size as the energy of hydrolysis of ATP, which is reasonable.
@@
 This would correspond to a $\Delta G_{spring} = \frac{1}{2}c_t\Delta \theta_t \approx \Delta G_{ATP}$, which is very reasonable.
-In addition, the tail spring constant is less than the motor and binding spring constants, which is in line with the notion that the tail is much more elastic than the motor or binding domains.
-CITE\\
+In addition, the tail spring constant is less than the motor and binding spring constants, which is in line with the notion that the tail is much more elastic than the motor or binding domains.\\
 
@@
 Figure (\ref{fig:final-histograms}) shows the stepping pattern of the model at the parameters shown in Table (\ref{table:thesis-parameters}).
-This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\
+This simulation was run over a much longer time period than that shown in Figure (\ref{fig:stepping-trajectory}), and hence shows much more significant information on the model's stepping behavior.\\
 
@@
 Note the model can generate 25nm steps, but has a high preference for <5nm steps.
-Also note that no backward steps are generated by the model.
+Also note that few backward steps are generated by the model.
 Simulation run at conditions in (\ref{table:thesis-parameters}).
@@
 
-Figure (\ref{fig:final-histograms}) shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
+Figure (\ref{fig:final-histograms}) shows the model has a strong preference for $<5$nm steps, but is capable of generating steps up to $25$nm in length, with a fairly even distribution of step frequency between $5$ and $25$nm.
 This is a very important result, since it indicates that the model is capable of taking a varied step size.
@@
 
-The preference for $<5nm$ steps is very un-dynein-like.
+The preference for $<5$nm steps is very un-dynein-like.
 One explanation is that steps may be defined differently between experimental and modeled dynein.
@@
 Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely.
-A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out.
-This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\
+A solution may thus be to lower the microtubule binding rate and see if the stepping histogram would level out.\\
 
@@
 
-Another issue with the simulated histogram is that it shows no steps over $30nm$.
-This is a problem, since taking $40+nm$ steps is characteristic of dynein.
+Another issue with the simulated histogram is that it shows no steps over $30$nm.
+This is a problem, since taking $40+$nm steps is characteristic of dynein.
 Ideally, tuning the parameters of dynein would increase the step size.
@@
 The current model assumes connections between domains are rigid.
-This may not be a valid assumption, since the coiled coil region connecting the binding and motor domains has some elasticity to it CITE.
+This may not be a valid assumption, since coiled coils are generally elastic \cite{myosin-cc-elasticity}.
 Thus it may be necessary to add in elasticity to the model to reproduce long steps.\\
@@
 It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm.
-Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\
+Another issue is the lack of backwards steps, which may also be solved by reducing the spring constants or lowering binding rate.\\
 
@@
 Other findings cast doubt on some aspects of the model.
-The vast preference of the model for $<5nm$ steps suggests that the model may handle binding events unlike real dynein.
+The vast preference of the model for $<5$nm steps suggests that the model may handle binding events unlike real dynein.
 When binding, the total spring energy of the transition from a onebound to a bothbound state is calculated, then used to calculate the likelihood of transition via a Boltzmann factor.
@@
 This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics.
-If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating.
+If this new model even roughly manages to mimic experimental kinesin stepping, that would be fascinating.
 This result would show that the differences between kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants.
@@
 Following these papers came low-resolution structures and experiments testing the stepping behavior, directionality, conformation changes and chemical affinities of these motors.
-As structural technology got better, resolution got better, until eventually amino-acid resolution structures were found \cite{schmidt-carter}.
+As structural technology got better, resolution got better, until eventually amino-acid resolution structures were found~\cite{schmidt-carter}.
 These structures allowed more informed hypotheses to integrate experimental data and structures into well-advised theories on motor motility, such as \textit{Andreasson et.
-al.} for kinesin \cite{kinesin-cycle} and \textit{Cianfrocco et.
+al.} for kinesin~\cite{kinesin-cycle} and \textit{Cianfrocco et.
 al.} for dynein \cite{cianfroccoreview}.
 These theories are now being tested using state of the art methods.
-For example, a lab at Penn State is currently exploring kinesin dynamics using gold nanoparticles, and is capable of getting 2nm spatial resolution and 1ms temporal resolution \cite{kinesin-gold-nanoparticle}.
+For example, a lab at Penn State is currently exploring kinesin dynamics using gold nanoparticles, and is capable of getting 2nm spatial resolution and 1ms temporal resolution~\cite{kinesin-gold-nanoparticle}.
 This level of detail would provide intra-step information about the kinesin mechanochemical cycle, confirming or rejecting hypotheses about how the motor steps.
@@
 % Uncomment the lines as you write the Appendices
+
+\allowdisplaybreaks
 
@@
   \begin{pmatrix}
-  X1\\
-  X2\\
-  X3\\
-  X4\\
-  X5\\
-  X6\\
-  X7\\
-  X8\\
+    -F_{bmx} + \gamma_m R_{bmx}\\
+    -F_{tx} + \gamma_t R_{tx}\\
+    -F_{umx} + \gamma_m R_{umx}\\
+    -F_{ubx} + \gamma_b R_{ubx}\\
+    -F_{bmy} + \gamma_m R_{bmy}\\
+    -F_{ty} + \gamma_t R_{ty}\\
+    -F_{umy} + \gamma_m R_{umy}\\
+    -F_{uby} + \gamma_b R_{uby}\\
   \end{pmatrix}
@@
 \end{center}
+%
+\[
+\begin{pmatrix}
+  a & b & c & d & 0 & 0\\
+  e & f & 0 & g & h & 0\\
+  i & j & 0 & 0 & k & l\\
+  m & n & p & q & 0 & 0\\
+  r & s & 0 & t & u & 0\\
+  v & w & 0 & 0 & x & y\\
+\end{pmatrix}
+\begin{pmatrix}
+    \dot{L}_{n}\\
+    \dot{L}_{f}\\
+    \lambda_{ns}\\
+    \lambda_{nt}\\
+    \lambda_{ft}\\
+    \lambda_{fs}\\
+  \end{pmatrix}
+=
+\begin{pmatrix}
+  -\frac{1}{\gamma}F_{nmx} - R_{nmx}\\
+  -\frac{1}{\gamma}F_{tx}  - R_{tx}\\
+  -\frac{1}{\gamma}F_{fmx} - R_{fmx}\\
+  -\frac{1}{\gamma}F_{nmy} - R_{nmy}\\
+  -\frac{1}{\gamma}F_{ty}  - R_{ty}\\
+  -\frac{1}{\gamma}F_{fmy} - R_{fmy}\\
+\end{pmatrix}
+\]
 
@@
 \end{itemize}
-*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
+
+These checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
 
@@
 \begin{itemize}
-\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^(-25)$) and motor domains nearly vertical ($\theta_{n/f} = \pi \pm 10^(-15)$).
+\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^{-25}$) and motor domains nearly vertical ($\theta_{n/f} = \pi \pm 10^{-15}$).
 Equilibrium angles set to have a vertical line as the lowest energy point.
-Model is not exactly vertical for NaN concerns explained in section (\ref{corrections-section}).
 Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero.

### 2017-09-30 thesis_stuff/thesis_stuff.tex
Add a good candidate set of run parameters to generate_exploration-data.py

@@
 \section{Papers}
+\subsection{Tension on the Linker Gates the ATP-Dependent Release of Dynein from Microtubules - Yildiz 2014}
+Yildiz shows that dynein only requires one functional head, and an MTBD linker, to walk.
+He claims that this shows dynein relies on high bb/ob time, not from communication.
+He does say that linker tension increases ATP hydrolysis rate, which isn't really inter-head connection.\\
+Takeaway: linker tension inhibits MT release. Stepping happens lots when the active head is low-tension (near its partner), but not when it is far away.\\
+
 \subsection{A Simple Theoretical Model Explains Dynein’s Response to Load}

### 2017-09-30 thesis_stuff/thesis_stuff.tex
mini commit.

@@
 Takeaway: linker tension inhibits MT release. Stepping happens lots when the active head is low-tension (near its partner), but not when it is far away.\\
+
+Yildiz found that processivity and velocity are inversely related.
+This means that the MT-bound to unbound ratio is related to how far the motor can walk.
+Thus, tuning k_b and k_ub may be a way to alter dynein processivity.\\
+
+A ring domain can be substituted with another protein and still walks, so ring-ring interactions aren't necessary for motion, either.\\
+
+This result means that stalk registry changes aren't necessary for MT unbinding.\\
+
+Abolishing linker swing by making weird constructs inhibits stepping when the linked head is mutated, but not when the unlinked head is muated.\\
+
+There's a better stall-force measurement here than in other assays.\\
 

### 2017-10-08 reorganize/papers/elliott-thesis/latex/thesis.tex
Add stuff which should have been in previous commit

--- 2017-09-22 thesis/latex/thesis.tex
@@
 
-\thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+%% \newcommand{\ttitle}{Simulating dynein's powerstroke using Brownian dynamics}
+%% \newcommand{\title}{Simulating dynein's powerstroke using Brownian dynamics}
+%% \thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+
+\newcommand{\ttitle}{Thesis title}
+\makeatletter
+\renewcommand{\@title}{Thesis title}
+\makeatother
+
 \supervisor{Dr. David \textsc{Roundy}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \AtBeginDocument{
-\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
+%% \hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
 \hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
@@
 \HRule \\[0.4cm] % Horizontal line
-{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
+%% {\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
 \HRule \\[1.5cm] % Horizontal line
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
   \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (cyan and blue) and several tail proteins (pink) come together to form the dynein motor complex.
@@
 %%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
 %%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion constant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/retrograde_transport.jpg}
   \caption{Dynein transport to neuron growth cones.}{Dynein and kinesin collaborate to move cargo between the neuron body and axon tip.
@@
   \centering
-  \includegraphics[width=.5\textwidth,keepaspectratio]{../../figures/pdb-motm-dynein}
+  \includegraphics[width=.5\textwidth,keepaspectratio]{../figures/pdb-motm-dynein}
   \caption{Structure of a dynein monomer.}{A cryo-electron microscopy-inspired image detailing the subcomponents of a single dynein monomer.
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{../../figures/weihong-step-size}
-  \includegraphics[width=0.49\textwidth]{../../figures/weihong-off-axis-steps}
+  \includegraphics[width=0.49\textwidth]{../figures/weihong-step-size}
+  \includegraphics[width=0.49\textwidth]{../figures/weihong-off-axis-steps}
     \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule.
@@
   \begin{minipage}{0.3\textwidth}
-    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein}
+    \includegraphics[width=\textwidth,keepaspectratio]{../figures/kinesin_vs_dynein}
   \end{minipage}
   \begin{minipage}{0.65\textwidth}
-    \includegraphics[width=\textwidth,keepaspectratio]{../../figures/kinesin_vs_dynein_2}
+    \includegraphics[width=\textwidth,keepaspectratio]{../figures/kinesin_vs_dynein_2}
   \end{minipage}
@@
   \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/burgess-dynein-angles}\\
+  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/burgess-dynein-angles}\\
   \hspace{1cm}
-  \includegraphics[width=.95\textwidth,keepaspectratio]{../../figures/linker-swing}
+  \includegraphics[width=.95\textwidth,keepaspectratio]{../figures/linker-swing}
   \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states.
@@
   \centering
-  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
+  \includegraphics[width=.90\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
   \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../../figures/theory-onebound}
-  \includegraphics[width=.45\textwidth]{../../figures/theory-bothbound}
+  \includegraphics[width=.45\textwidth]{../figures/theory-onebound}
+  \includegraphics[width=.45\textwidth]{../figures/theory-bothbound}
   \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to two two-dimensional point-particle systems.
@@
 %%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
+%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/ob_fig}
 %%   \caption{Onebound dynein model.}{}
@@
   \centering
-  \includegraphics[width=.65\textwidth]{../../figures/angular-spring}
+  \includegraphics[width=.65\textwidth]{../figures/angular-spring}
   \caption{Angular spring return force when out of equilibrium.}{The $\theta_{bb}$ angle shown is greater than the equilibrium angle $\theta_{bb}^{eq}$, and thus the $bb$ domain has conformational energy $\frac{1}{2}c_b\left(\theta_{bb}-\theta_{bb}^{eq}\right)^2$, and feels a force pulling the motor domain towards the microtubule.}
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../../figures/derivation-onebound}
+  \includegraphics[width=.45\textwidth]{../figures/derivation-onebound}
   \caption{Spatial representation of the onebound dynein model.}{The coordinate system used for derivation of onebound forces.}
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../../figures/derivation-bothbound}
+  \includegraphics[width=.45\textwidth]{../figures/derivation-bothbound}
   \caption{Spatial representation of the bothbound dynein model.}{The coordinate system used for derivation of bothbound forces.}
@@
 %%   \centering
-%%   \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
+%%   \includegraphics[width=.45\textwidth]{../figures/SarlahParameterTable.png}
 %%   \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
@@
 %%   \begin{minipage}[b]{0.45\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
+%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
 %%     \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
@@
 %%   \begin{minipage}[b]{0.45\textwidth}
-%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
+%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
 %%     \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
+  \includegraphics[width=0.9\textwidth]{../../../plots/trajectory-plot_thesis}
   \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation.
@@
   \centering
-    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
-    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
+    \includegraphics[width=0.5\textwidth]{../../../plots/stepping_length_histogram_thesis}%%
+    \includegraphics[width=0.5\textwidth]{../figures/weihong-step-size.pdf}
     \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model.
@@
 %%   \centering
-%%   \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
+%%   \includegraphics[width=\textwidth]{../figures/kb-kub-contour}
 %%   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.

### 2017-10-09 reorganize/papers/elliott-thesis/latex/thesis.tex

@@
 
-%% \newcommand{\ttitle}{Simulating dynein's powerstroke using Brownian dynamics}
-%% \newcommand{\title}{Simulating dynein's powerstroke using Brownian dynamics}
-%% \thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-
-\newcommand{\ttitle}{Thesis title}
-\makeatletter
-\renewcommand{\@title}{Thesis title}
-\makeatother
-
+\thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Dr. David \textsc{Roundy}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 \AtBeginDocument{
-%% \hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
+\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
 \hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
@@
 \HRule \\[0.4cm] % Horizontal line
-%% {\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
+{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
 \HRule \\[1.5cm] % Horizontal line

### 2017-10-10 reorganize/papers/elliott-thesis/latex/thesis.tex
Make stuff build on lab computers.

@@
 
-%% \subsection{Calculating one/bothbound times of experimental dynein}
-%% In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
-
-%% \newcommand\tbb{\left<t_{bb}\right>}
-%% \newcommand\tob{\left<t_{ob}\right>}
-%% \newcommand\tstep{\left<t_{step}\right>}
-%% \newcommand\tproc{\left<t_{processivity}\right>}
-%% \newcommand\kub{k_{ub}}
-%% \newcommand\kb{k_{b}}
-%% \newcommand\ko{k_{dis}}
-
-%% \begin{itemize}
-%% \item $\tbb$: Time in bothbound per step
-%% \item $\tob$: Time in onebound per step
-%% \item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
-%% \item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
-%% \item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
-%% \item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
-%% \item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
-%% \item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
-%% \item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
-%% \end{itemize}
-
-%% $\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
-
-%% \begin{align*}
-%%   \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
-%%   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-%%   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-%%   \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
-%%   \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
-%%   \tob &= \tstep-\tbb\\
-%%   &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
-%%   &= \frac{\tstep^2}{\tstep+\tproc}\\
-%% \end{align*}
-
-%% Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \begin{tabular}{| c | c | c | c | c | c |}
-%%     \hline
-%%     Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-%%     134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
-%%   \end{tabular}
-%%   \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
-%%   \label{table:time-parameter-table}
-%% \end{figure}
+\subsection{Calculating one/bothbound times of experimental dynein}
+In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
+
+\newcommand\tbb{\left<t_{bb}\right>}
+\newcommand\tob{\left<t_{ob}\right>}
+\newcommand\tstep{\left<t_{step}\right>}
+\newcommand\tproc{\left<t_{processivity}\right>}
+\newcommand\kub{k_{ub}}
+\newcommand\kb{k_{b}}
+\newcommand\ko{k_{dis}}
+
+\begin{itemize}
+\item $\tbb$: Time in bothbound per step
+\item $\tob$: Time in onebound per step
+\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+\end{itemize}
+
+$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
+
+\begin{align*}
+  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
+  \tob &= \tstep-\tbb\\
+  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
+  &= \frac{\tstep^2}{\tstep+\tproc}\\
+\end{align*}
+
+Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
+
+\begin{figure}[h]
+  \centering
+  \begin{tabular}{| c | c | c | c | c | c |}
+    \hline
+    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+  \end{tabular}
+  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
+  \label{table:time-parameter-table}
+\end{figure}
 

### 2017-10-10 reorganize/scripts/exploration-plt.py

@@ -1,0 +1,214 @@
+#! /usr/bin/env python3
+
+from __future__ import division
+import numpy as np
+import time, signal, sys, os, matplotlib, subprocess, re
+
+if 'show' not in sys.argv:
+    matplotlib.use('Agg')
+
+#import draw.balls as cartoon
+import draw.cartoon as cartoon
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+from matplotlib.patches import Rectangle
+
+import io
+
+tail = 'tail' in sys.argv
+
+usage = '''
+Usage: python2 %s MOVIE_FILENAME STEPS_FILENAME [show]"
+       show: show plot in a window
+''' % (sys.argv[0])
+
+if len(sys.argv) < 3:
+  print(usage)
+  sys.exit(1)
+
+data_filename = sys.argv[1]
+title = data_filename[data_filename.index("data/")+5:-4]
+
+raw_lines = open(data_filename, 'r').readlines()
+lines = sum(1 for l in raw_lines)
+start_line = 0
+end_line = int(min(1e6, lines))
+plot_length = end_line - start_line - 1
+
+raw_data = "".join(raw_lines[start_line:end_line])
+
+run_conditions = open("data/exploration_stepping_parameters.tex").read()
+raw_run_conditions = run_conditions.replace("\n", " ").replace("\\\\", "\\")
+
+data = np.genfromtxt(io.BytesIO(raw_data.encode()), delimiter="\t", invalid_raise=False)
+
+avging_window_width = 300
+if len(data) < avging_window_width:
+       print("Need at least ", avging_window_width, " data points!")
+       exit(1)
+
+nbxs =  np.zeros(plot_length)
+fbxs =  np.zeros(plot_length)
+nbys =  np.zeros(plot_length)
+fbys =  np.zeros(plot_length)
+
+times = np.empty(plot_length)
+
+for i in range(plot_length):
+    if int(data[i,0]) == 0 or int(data[i,0]) == 2:
+        nbxs[i] = data[i,7]
+        fbxs[i] = data[i,15]
+        fbys[i] = data[i,16]
+    elif int(data[i,0]) == 1:
+        nbxs[i] = data[i,15]
+        fbxs[i] = data[i,7]
+        nbys[i] = data[i,16]
[…]

### 2017-10-10 reorganize/scripts/trajectory-movie-old.py

@@ -1,188 +1,0 @@
-#! /usr/bin/env python3
-
-from __future__ import division
-import numpy as np
-import time, signal, sys, os, matplotlib, subprocess
-
-if 'show' not in sys.argv:
-    matplotlib.use('Agg')
-
-import draw.balls as cartoon
-import matplotlib.pyplot as plt
-from matplotlib import gridspec
-from matplotlib.patches import Rectangle
-
-import io
-
-usage = '''
-Usage: python2 %s FILENAME [show]"
-       show: show animation in a window while generating movie
-	     omitting show makes %s faster but less exciting to watch
-''' % (sys.argv[0], sys.argv[0])
-
-if len(sys.argv) < 2:
-  print(usage)
-  sys.exit(1)
-
-os.system("rm -rf PNGs") # ensure the PNGs directory is empty.
-os.system("mkdir -p PNGs") # ensure the PNGs directory exists.
-
-data_filename = sys.argv[1]
-title = data_filename[data_filename.index("data/")+5:-4]
-
-raw_lines = open(data_filename, 'r').readlines()
-lines = sum(1 for l in raw_lines)
-start_line = 0
-end_line = int(min(1e5,lines))
-plot_length = end_line - start_line - 1
-
-raw_data = "".join(raw_lines[start_line:end_line])
-
-data = np.genfromtxt(io.BytesIO(raw_data.encode()), delimiter="\t", invalid_raise=False)
-
-if len(data) == 0:
-       print("Very short run!")
-       exit(1)
-
-nbxs =  np.zeros(plot_length)
-fbxs =  np.zeros(plot_length)
-nbys =  np.zeros(plot_length)
-fbys =  np.zeros(plot_length)
-
-times = np.empty(plot_length)
-
-for i in range(plot_length):
-    if int(data[i,0]) == 0 or int(data[i,0]) == 2:
-        nbxs[i] = data[i,7]
-        fbxs[i] = data[i,15]
-        fbys[i] = data[i,16]
-    elif int(data[i,0]) == 1:
-        nbxs[i] = data[i,15]
-        fbxs[i] = data[i,7]
-        nbys[i] = data[i,16]
-    times[i] = data[i,1]*1e6
-
-avging_window_width = 300
[…]

### 2017-10-13 reorganize/papers/elliott-thesis/latex/thesis.tex

@@
 
-\subsection{Calculating one/bothbound times of experimental dynein}
-In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
-
-\newcommand\tbb{\left<t_{bb}\right>}
-\newcommand\tob{\left<t_{ob}\right>}
-\newcommand\tstep{\left<t_{step}\right>}
-\newcommand\tproc{\left<t_{processivity}\right>}
-\newcommand\kub{k_{ub}}
-\newcommand\kb{k_{b}}
-\newcommand\ko{k_{dis}}
-
-\begin{itemize}
-\item $\tbb$: Time in bothbound per step
-\item $\tob$: Time in onebound per step
-\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
-\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
-\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
-\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
-\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
-\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
-\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
-\end{itemize}
-
-$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
-
-\begin{align*}
-  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
-  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
-  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
-  \tob &= \tstep-\tbb\\
-  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
-  &= \frac{\tstep^2}{\tstep+\tproc}\\
-\end{align*}
-
-Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| c | c | c | c | c | c |}
-    \hline
-    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
-  \end{tabular}
-  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
-  \label{table:time-parameter-table}
-\end{figure}
-
 %% \subsection{Fitting rate constants}

### 2017-10-13 reorganize/papers/param-calculation/param-calc.tex

--- 2017-05-03 thesis/latex/thesis.tex
@@
-\documentclass[defaultstyle,11pt]{article}
-%% \documentclass[defaultstyle,11pt]{thesis}
+\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt
+
+\nonstopmode
 
 \usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins
+
+\usepackage{amsmath}
+
 \usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors
-
-\usepackage{listings}
-\lstset{escapechar=\&}
 
@@
 
-\usepackage{titlesec}
-\setcounter{secnumdepth}{4}
-
-\setlength{\emergencystretch}{3cm} % somehow helps prevent hboxes from overflowing
-
-%% \titleformat{\paragraph}
-%% {\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-%% \titlespacing*{\paragraph}
-%% {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
-
 \usepackage{fancyhdr}
 \usepackage{amssymb}
-\usepackage{amsmath}
 \pagestyle{fancy}
 \fancyhf{}
+% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
+% Example footer:
+%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}
+
+\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
+
+\usepackage{titlesec} % Allows creating custom \section's
 
@@
 
-\title{Simulating dynein's powerstroke using Brownian dynamics}
+\title{Electromagnetism Assignment One}
 \author{Elliott Capek}
 \titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles
-
-\usepackage{csquotes}
-
-\usepackage{float}
-
-\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
-
-\bibliographystyle{plain}
-
-%% \title{Simulating a Brownian model of the dynein motor protein}
-%% \author{E. L.}{Capek}
-
-%% \otherdegrees{B.A., North Dakota State University, 2005 \\
-%% 	      M.S., University of Reno, 2007}
-
-%% \degree{Doctor of Philosophy}		%  #1 {long descr.}
-%% 	{Ph.D., Rocket Science}		%  #2 {short descr.}
-
-%% \dept{Department of}			%  #1 {designation}
-%% 	{Rocket Science}		%  #2 {name}
-
-%% \advisor{Prof.}				%  #1 {title}
-%% 	{Ed Visor}			%  #2 {name}
-
-%% \reader{Prof.~Rachel Goddard}		%  2nd person to sign thesis
-%% \readerThree{Ms.~Thora Nea}		%  3rd person to sign thesis
-
-%% \abstract{Yet to come.}
-
-%% \dedication{Yet to come.}
-
-%% \acknowledgements{Yet to come.}
 
@@
 \maketitle{}
-\tableofcontents
-\listoffigures
-\newpage
 
-\textbf{Abstract}
-\blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell.
-Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
-Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60\textit{nm} in both the forwards and backwards directions.
-It is believed that dynein takes such broad, stochastic steps because of its large size and several elastic regions, which make it more influenced by Brownian motion.
-To test this diffusion-dominated hypothesis for dynein stepping, we create a minimal model of dynein with elastic regions which feels Brownian forces, and simulate the model's stepping behavior in a cellular environment.
-The model treats dynein's domains as ``point hinges'' connected by rigid rods, and accomplishes steps by changing the openness of its hinges.
-The model's behavior is found using Brownian dynamics equations.
-Preliminary data indicate such a model is capable of taking steps between 0 and 25nm.
-These results affirm that the Brownian hinge model of dynein is capable of stepping, and give hope that, with further tweaking, the model may be able to generate both larger and backwards steps, supporting the notion of a diffusion-dominated dynein step.}
-
-\textbf{Keywords}: Dynein, powerstroke, Brownian dynamics, coarse-grained, dynamics simulation\\
-
-\section{Chapter: Introduction}
-\blockquote{An embryo in its spherical blastula stage has spherical symmetry [...].
-But a system which has spherical symmetry, and whose state is changing because of chemical reactions and diffusion, will remain spherically symmetrical for ever [...].
-It certainly cannot result in an organism such as a horse, which is not spherically symmetrical.
-\textbf{Alan Turing, The Chemical Basis of Morphogenesis, 1952}}
-
-Cells need to create asymmetric, heterogeneous structures inside themselves in order to function.
-However, as per the above quote, diffusive processes cannot create this asymmetry.
-How then do cells create heterogeneous structures they need in order to exist?
-Motor proteins are part of the answer.
-Motor proteins are structures which use energy to create directed motion in cells.
-In broad terms, they are mechanical creators of asymmetry.
-This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\
-
-%% \subsection{Interest builder}
-%% Begin with a paper-like introduction which talks about:
-
-%% \begin{itemize}
-%% \item How dynein is a structure which turns chemical energy into motion
-%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
-%% \item How it's weird that a cellular structure can generate directed motion
-%% \item Other cool stuff - make dynein mysterious and cool.
-%% \end{itemize}
-
-%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
-
-\subsection{Motivation}
-Motor proteins are cellular structures which use chemical energy to do work and generate motion.
-Kinesin, myosin and dynein are the three main motor proteins in cells.
-Though these proteins have significantly different ancestors \ref{cite}, they all evolved into a single similar structure.
-In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem.
-How, then, do motor proteins work?\\
-
-The basic form is simple.
-Kinesin, myosin and dynein each use two binding domains to attach to a surface.
-These binding domains are connected via a linker domain.
-Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface.
-In a single cycle a binding domain will unbind from a surface, tense its foot to kick forward, rebind, then untense its foot to pull the whole motor forward.
-This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\
-
-Although the three motor protein families operate using the same stepping cycle, their behavior differs significantly.
-Kinesin and myosin are predictable motors which step in the forwards direction with a regular step size [get kinesin, myosin stepping papers].
-In contrast, dynein's stepping pattern varies wildly in both size and direction.
-The motor steps forward on average, but takes steps backwards and to the side quite regularly \cite{weihongpaper}.
-How can motors which implement the same release, lever, bind, lurch stepping mechanism behave so differently?\\
-
-One possibility is that dynein's size and organization are responsible for the motor's odd stepping pattern.
-Dynein is much larger than kinesin or myosin, meaning its feet may need to move significantly further over each cycle.
-Due to the random nature of Brownian motion from water particle collisions, there may be significantly more variance in the path taken by dynein's feet compared to other motor feet.
-This could explain the large variance in step size.
-Another contributing factor could be that dynein is so large that it can twist and contort during its step, allowing varying and even backwards steps, which a small motor would be too tense to achieve.\\
-
-This thesis describes an experiment which aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern.
-To do this, a mathematical model of a dynein-like motor is constructed which exhibits flexibility and feels Brownian forces.
-This model is then simulated, and its behavior is compared to the behavior of real dynein.\\
-
-%% Dynein:
-%% feet which bind to track
-%% motor connected to feet which generates the force
-%% -----------
-%% ATP binding causes dissociation
-%% Also causes forward kick
-%% ATP hydrolysis
-%% rebinding causes ADP rejection and forward lurch
-%% restart
-
-%% Kinesin:
-%% feet which bind to track
-%% connected via lever arm to cargo binding domain
-%% -----------
-%% ATP binding causes forward kick
-%% ATP hydrolysis
-%% MT binding, ADP, Pi rejection
-%% Other foot unbinds
-
-%% Myosin:
-%% Feet which bind to track
-%% connected via lever arm to cargo binding domain
-%% ----------
-%% actin binding causes Pi rejection, strengthening binding
-%% binding causes foot to change relative to lever, shifting the motor forward
-%% ATP binding causes dissocaition and undoing the powerstroke
-
-\subsection{What is dynein?}
-\subsubsection{Basics}
-Dynein is a cellular structure which converts chemical energy to mechanical energy.
-It does so by reacting with adenosine triphosphate (ATP) to take steps along long cellular tracks known as microtubules (MTs).
-Dynein's mechanical energy is used for various cellular functions, including to transport molecules around the cell, pull chromosomes during division, and move cellular propellers known as cilia \cite{cianfroccoreview}.\\
-
-Dynein is a protein with many smaller domains.
-A depiction of the protein and its labeled subdomains is shown in Figure (\ref{dynein-artist-rendition}).
-Each motor is a homodimer made up of two identical monomer proteins.
-Each monomer has a binding domain which binds to the microtubule, a motor domain which binds ATP, a tail domain which connects to the other monomer, a stalk which connects the binding and motor domains, and a linker which connects the motor and tail domains.
-The tail domain is also responsible for binding to cargo.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of dynein bound to a microtubule.}{One monomer is bound to the MT, and the other is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
-  \label{dynein-artist-rendition}
-\end{figure}
-
-Dynein is believed to move by using the energy of ATP to cycle through a ring of states, each with different spatial relations to the microtubule.
-By cycling forward through this ring, the molecule will end up in the same state it began, but moved forward a small amount.
-This ring of states is known as the mechanochemical cycle \cite{cianfroccoreview}.
-The goal of this project is to create a mathematical model of the mechanochemical cycle and verify that it can reproduce experimental dynein stepping data.
-There are several types of dynein which all behave differently.
-This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\
-
-\subsubsection{Why do cells need motor transport?}
-Cells are organized, heretogenous structures which respond quickly to their environments.
-This means that cells require a mechanism for rapidly moving components to precise locations within the cell.
-This can be a challenge, since cells are fairly large compared to the proteins which compose them.
-A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter.
-In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\
-
-Diffusion, or random motion of molecules due to collisions with solvent (i.e.
-Brownian motion), is one possible process cells could use to transport biomolecules.
-Diffusion has two problems: it is slow and nondirected.
-The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \cite{einstein-paper}:
-
-\begin{equation}
-  \label{diffusion-equation}
-  <x> = \sqrt{2Dt}
-\end{equation}
-
-where D is the diffusion constant describing the diffusability of the biomolecule.
-For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell.
-In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.
-Figure (\ref{fig:diffusion_vs_dynein}) demonstrates how motor transport quickly outstrips diffusion in a cell.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
-  \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
-  \label{fig:diffusion_vs_dynein}
-\end{figure}
-
-\textit{Maybe use the more reasonable 2$\mu m / s$ number for dynein velocity, in-vitro speed may not be applicable since [ATP]-limited}
-
-Another advantage of motor transport is that microtubules can be highly specific in their location in the cell.
-During cell division chromosomes line up at the center of each cell in a plane.
-Such a geometrically precise shape requires some sort of directed motion which a random process could never provide.\\
-
-\textit{maybe decorate the above plot with pictures of cells of each size, or how long certain cellular events take? That could be cool and make it actually an interesting plot}
-\textit{this argument would be much better if you could find examples of things which need to be done quickly in the cell, like responding to foreign particles or signalling molecules or cell division or neural events}
-
-\subsubsection{What role does dynein play in the cell?}
-Some of dynein's primary roles in the cell are to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins.
-Dynein also plays a role in positioning and breaking down the nucleus, cell death, spindle formation and the placement of other important cellular structures \cite{valetoolbox}.\\
-
-Microtubules are long polymers of alternating $\alpha-$ and $\beta-$ tubulin subunits.
-MTs are polar, meaning they have a distinct directionality based on the orientation of thetubulin proteins which comprise them.
-One pole, the minus end, is where they initiate formation, typically at a MTOC (microtubule organizing center) around the center of the cell.
-The other pole, the plus end, is where they grow and shrink from.
-Kinesin and myosin, two other families of motor protein, typically walk towards the plus end of the MT.
-Dynein is unique in that it walks towards the minus end, making it a minus end-directed motor.
-This lends it to a particularly important function inside neurons known as retrograde transport.\\
-
-Neurons have cell bodies at their centers and axons which grow outwards.
-Axons are long, narrow structures extending up to a meter in length in humans.
-Cell bodies contain nuclei and important organelles for synthesizing proteins, but growth of axon tips is vital for neuron function.
-This means bidirectional motor transport between axon tips and cell bodies is very important in neurons, since diffusion would not be quick enough.
-Retrograde transport is transport from the axon tip to the cell body.
-Cargo includes vesicles full of proteins ready to be broken down in the cell body and microtubule fragments to be returned from the axon tip \cite{neuroanatomy}.
-Because microtubule minus ends are found in the cell body, dynein's minus end-directed nature makes it the only protein capable of retrograde transport.
-An interesting question is, if proteins like dynein are synthesized in the cell body but needed at the axon tip to perform retrograde transport, how do dynein get to the tip?
-The answer is shown in \ref{retrograde-transport}: kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
-  \caption{Dynein localization to axon growth cones.}{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport.
-Modified from \cite{valetoolbox}.}
-  \label{retrograde-transport}
-\end{figure}
-
-\subsubsection{Dynein structure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of motor-MT complex.}{Artist rendition of the dynein motor bound to a microtubule.
-One monomer is bound to the MT, and one is raised up.
-Modified.
-Source: Lander Lab, The Scripps Research Institute.}
-  \label{dynein-artist-rendition-2}
-\end{figure}
-
-\textit{eventually find a different figure}
-
-As shown in the crystal structure in Figure XXX, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
-Each of these subunits has a unique purpose for the motor.
-
-\textbf{Binding domain}
-Microtubule binding domains (MTBDs) allow dynein to bind to the microtubule.
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
-%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
-%%   \label{dynein-artist-rendition-2}
-%% \end{figure}
-
-This could be fixed up...probably remove multiple of these sections
-
-\subsubsection{How does it behave?}
-Dynein's stepping pattern is distinct from its partner, kinesin. Kinesin takes very precise 8-nm steps \cite{kinesin-step-size}. In contrast, dynein takes a large range of steps, as shown in Figure \\
-
-\subsubsection{Why is dynein interesting?}
-Studying how nature creates directed motion is interesting in itself.
-Another interesting question is how, given the large number of similarities between motors kinesin and dynein, does dynein achieve such a radically different stepping pattern than kinesin?
-Elucidating how the structural differences between the motors give rise to the differences in dynamics would provide lots of important information on how the machines fine-tune their stepping.\\
-
-The major difference between kinesin and dynein is their size.
-Kinesin proteins are generally 100-200 kD in mass, whereas dynein is roughly 1mD.
-As shown in Figure \ref{fig:kinesin-vs-dynein}, the size and volume differences between proteins is very apparent.
-Dynein is about 20nm from MTBD to tail, whereas kinesin is ----.
-Another key difference is the separation between active sites on either protein.
-Kinesin binds to the MT with a foot domain, colored blue in Figure \ref{fig:kinesin-vs-dynein}.
-It hydrolyzes ATP at the residues colored pink.
-The separation between these domains is roughly ---nm.
-In contrast, Dynein binds to the MT with its MTBD, colored blue, and hydrolyses ATP in its motor domain, residues colored pink.
-This distance is close to 20nm in length - much longer than kinesin.
-Another difference is the way the motors interact with the microtubule.
-Both motors bind to the MT using domains.
-However, for dynein the motor-MTBD-MT angle is ---, whereas for kinesin, it is ---.\\
-
-Despite these differences, the two motors implement very similar chemical cycles to achieve motion.
-Both feet begin bound to the microtubule, then one unbinds.
-This foot diffuses forward, then rebinds to the microtubule
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/kinesin-vs-dynein}
-%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
-%%   \label{fig:kinesin-vs-dynein}
-%% \end{figure}
-
-\subsection{Dynein Stepping Background}
-Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
-The full mechanism is not known, but results of such experiments suggest a certain vague picture of how dynein generates motion.\\
-
-\subsubsection{ATP cycle influences conformational state}
-Dynein is known to occupy multiple discrete conformational states depending on its environment.
-In particular, the concentration of ATP and microtubules is known to alter the shape dynein takes on.
-A FRET (fluorescence resonance energy transfer) study attached fluorophores to dynein's motor and tail and measured the average distance between the two \cite{FRETstatepaper}.
-It was found that average distance increased or decreased depending on the nucleotide bound to dynein, indicating the motor takes on different conformations for different bound nucleotides.
-Dynein unbound to nucleotide, or frozen in ATP or ADP-bound states, had a similar tail-motor distance.
-However, when the motor was stuck in an ADP-Pi state, with ATP hydrolyzed but phosphate not yet released, the tail-motor distance was increased.
-This suggests that dynein starts its cycle with no nucleotide, binds ATP, hydrolyzes ATP, enters the ADP-Pi state and changes conformation to a far tail-motor distance, then releases phosphate, moves back to its original close tail-motor conformation, then ejects ADP and starts over.\\
-
-Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the trail \cite{FRETstatepaper} \cite{burgess-paper}.
-Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures//burgess-dynein-angles}
-  \caption{Cryo-EM microscopy of dynein conformational states.}{Cryo-electron microscopy images of dynein in two different nucleotide states.
-Left: dynein frozen in ADP-Pi state.
-Middle: dynein without nucleotide.
-Right: two states superimposed on one another.
-Bottom: cartoons representing how dynein may bind to the MT in either state.
-From \cite{burgess-paper}.}
-  \label{fig:cryo-em-angles}
-\end{figure}
-
-Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper} (make a Chimaera figure where the pre/poststroke motors are docked showing this).
-Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\
-
-\textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
-
-\subsubsection{Microtubule and nucleotide states are coupled}
-Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
-This site occurs roughly every 8nm, indicating dynein is restricted to step sizes which are multiples of 8nm.\\
-
-The nucleotide state of the motor is not the only determiner of dynein conformation; microtubule binding state has also been shown to influence conformation.
-A study on the MTBD-MT complex indicates the stalk connecting the motor and MTBD can take on two major conformations, depending on whether the MTBD is bound to the MT or not \cite{mt-atp-coupling}.
-The conformation of the stalk has been shown to communicate information between the motor and MTBD.
-In the presence of microtubules, the ATPase rate of the motor is increased 25-fold.
-This indicates the stalk communicates MT-binding state of the MTBD to the motor, increasing its ATP hydrolysis rate.
-The communication happens the other way, as well.
-Treating dynein with ATP causes MT-binding rate to drop 15-fold, indicating ATP-binding at the motor decreases MT-binding rate at the MTBD.\\
-
-In addition to a bidirectional linking between ATPase rate and MT-binding, stalk state has been shown to directly influence motor conformation \cite{mt-atp-coupling}.
-When the stalk is allowed to freely transition between bound and unbound states, the motor can also transition between near and far tail/motor states.
-However, when the stalk is frozen in a particular conformation, the motor loses its transitioning ability.
-This suggests that the conformations of the two systems are tightly linked.\\
-
-\subsubsection{Stepping pattern}
-Several studies have been done on the dynein motor's stepping pattern using selectively-labeled motor domains \cite{reck2006single} \cite{weihongpaper}.
-These studies show dynein's stepping pattern to be stochastic and weakly forward-directed.
-As shown in Figure (\ref{fig:weihong-steps}), dynein takes many backwards steps, and also many steps with components perpendicular to the microtubule.
-This indicates the process dynein uses to generate motion has a stochastic component to it.
-It is likely that the physical states of subcomponents in the motor, and/or the effects of Brownian motion due to water particle collision, play a role in dynein's stepping mechanism.\\
-
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/weihong-step-size}
-    \caption{Experimental dynein step size histogram.}{Size of steps taken by dynein motor parallel to microtubule.
-Positive axis corresponds to steps towards the microtubule minus-end.
-Figure modified from \cite{weihongpaper}.}
-  \end{minipage}
-  \hspace{.2cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/weihong-off-axis-steps}
-    \caption{Dynein experimental off-axis stepping size.}{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
-  \end{minipage}
-  \label{fig:weihong-steps}
-\end{figure}
-
-\subsection{Dynein models}
-Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts.
-Somehow the protein itneracts with nucleotides and microtubules in a way that allows it to reliably move through the cell.
-Models presented below take these facts and string them together into cohesive cycles which might explain how dynein walks.
-It is important to note that these models are hypotheses.\\
-
-\subsubsection{Cianfrocco Model}
-Cianfrocco \textit{et.
-al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig.
-\ref{mech-cycle}.
-This model will hereon be referred to as the Cianfrocco model.
-The model claims the primary events in the dynein step are as follows.
-First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation.
-ATP hydrolysis to ADP-Pi causes further conformation changes.
-These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound.
-The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT.
-Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle.
-The exact order of these events is not precisely known.\\
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
-  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
-  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
-  \newcommand\transition{\textcolor{green}{transition?}}
-  %% \begin{tabular}{rll}
-  %%   \bothbound &
-  %%   1 & \begin{minipage}{5in}
-  %%     Bound to microtubule and waiting for ATP to arrive.  The
-  %%     conformation is ``post-powerstroke''.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   2 & \begin{minipage}{5in}
-  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \transition &
-  %%   3 & \begin{minipage}{5in}
-  %%     ``The ring has closed'' in the motor, whatever that means.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   4 & \begin{minipage}{5in}
-  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \onebound &
-  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
-  %%     Onebound! The equilibrium angle is also changed.  The ATP has
-  %%     been hydrolized, but the phosphate is still bound to the motor.
-  %%     ``Priming stroke?''
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \onebound &
-  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
-  %%     with low affinity, and without any loss of phosphate. Question:
-  %%     does this happen many times? If so it may still be onebound.
-  %%     Otherwise it is probably bothbound.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   7 & \begin{minipage}{5in}
-  %%     Now it is seriously bound to the microtubule, and the motor
-  %%     domain has changed conformation.  This is now ``high affinity.''
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   8 & \begin{minipage}{5in}
-  %%     Phosphate has been released, and our equilibrium angles have
-  %%     been changed.  This is the ``power stroke.''
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   1 & \begin{minipage}{5in}
-  %%     The ADP has been released from the motor domain, so it can now
-  %%     bind ATP.  Still ``high affinity,'' and still in the
-  %%     ``power-stroke'' conformation.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   9 & \begin{minipage}{5in}
-  %%     While stuck in this ``normal bound'' state, another site on the
-  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
-  %%     where it cannot directly move on to step 2 (until after
-  %%     reversing this).  Controversial?
-  %%   \end{minipage}
-  %% \end{tabular}
-  \caption{Cianfrocco mechanochemical cycle.}{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
-  \label{mech-cycle}
-\end{figure}
-
-%% \subsubsection{Other models}
-%% Find other models and put them here
-
-%% \subsection{Brownian dynamics}
-%% New section which describes how BD works.
-
-\subsection{This work}
-\subsubsection{Necessary and sufficient criteria for motion}
-One of the principle goals of researchers studying the dynein motor is establishing how it walks.
-This can be a difficult task, since direct observation of the motor walking is not currently experimentally possible.
-The next best thing, then, is building a model which both only does all the things dynein does, and generates motion.
-Finding such a system would be very useful for forming hypotheses on how dynein walks.
-Another requirement of the system would be that it be as simple as possible while still explaining all the data.
-By Occam's Razor, such systems are the most likely to represent real dynein.
-Thus, finding the necessary and sufficient criteria for dynein's motion is a big goal in the field.\\
-
-A good starting place for finding the minimum set of motile criteria would be preexisting models, like the Cianfrocco model.
-This model describes a set of states which logically lead to each other and are supported by experiment.
-It seems intuitive that a motor which obeyed the Cianfrocco cycle would walk.
-There are multiple ways to verify this.
-A completely synthetic biological motor could be designed which obeys the cycle, and its motile properties could be studied.
-This seems incredibly difficult.
-Much easier would be to create a physical model of such a cycle, simulate it, and see if it obeys similarly to experimentally observed dynein.
-If the physical model both behaves according to the laws of physics and captures experimental dynein behavior well, this would be good evidence that such a model describes how dynein actually walks.\\
-
-\subsubsection{Goals}
-The goal of this work is to construct a minimum physical model of dynein protein based on the theoretical Cianfrocco model.
-The model should behave as physics predicts a protein to behave; namely, it should obey Brownian dynamics and conservation of energy.
-It should also roughly capture the state transitions and conformation changes of the Cianfrocco model.
-Also the model should be as simple as possible, to assure that each part of the model is necessary.
-If too many extra features are added, the model will not be minimal and not achieve its purpose.\\
-
-This model will then be converted into a computer program, tested for compliance with the laws of physics, and simulated.
-Information on the long-term behavior of such a simulation will then be used to evaluate how well the model describe's experimental dynein's behavior.\\
-
-%% \textbf{Things which are known about dynein which support the Cianfrocco model}
-%% \begin{itemize}
-%% \item AAA1 only ATPase necessary for motility, which is why we don't include the other ATPases in our model \cite{cianfroccoreview}
-%% \item AAA5 mediates stalk register changes Schmidt H, Zalyte R, Urnavicius L, Carter AP. 2014. Structure of human cytoplasmic dynein-2 primed for
-%%   its power stroke. Nature 518:435–38
-%% \item Linker moves as response to AAA1 nucleotide binding Burgess SA, Walker ML, Sakakibara H, Knight PJ, Oiwa K. 2003. Dynein structure and power stroke. Nature
-%%   421:715–8
-%% \item Crystal structures with Vanadium-Adp show dynein in the pre-powerstroke state, hinting that ADP-Pi-bound dynein takes on a different conformation than ADP-Pi free dynein
-%% \end{itemize}
-
-%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}.
-The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I.
-Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
-
-\section{Chapter: Theory}
-\subsection{Model features}
-The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior.
-To test this hypothesis, these features are put into a model and simulated.
-A schematic of the model is pictured in Figure \ref{fig:model-intro} and described below.\\
-
-\textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
-It would basically show all events occuring at two times: unbinding or rebinding.}\\
-
-%% \begin{itemize}
-%% \item Dynein is a collection of spherical domains joined together by massless rods
-%% \item These rods are rigid
-%% \item Each joint in the motor feels a spring force about some equilibrium joint angle
-%% \item Dynein can be in two states: onebound and bothbound
-%% \item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
-%% \item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
-%% \item Transitions between the two states are based solely on spring energies between the two models
-%% \item Brownian dynamics describes the behavior of the domains in time
-%% \item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
-%% \item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
-%% \end{itemize}
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
-%%   \caption{Onebound dynein model.}{}
-%%   \label{fig:model-intro}
-%% \end{figure}
-
-\subsubsection{Spherical domains connected by massless rods}
-A key feature of the model is that each domain of the protein (two feet, twp motors and a tail) is treated as a sphere.
-Each sphere is connected to one or two other spheres, as shown in Figure (\ref{fig:model-intro}).
-This simplification is made to make the math easier and allow a simple definition of dynein's conformation.\\
-
-One quickly notices by glancing at Figure (\ref{fig:crystal-structure-model-imposed}), a visualization of actual dynein, that modelling the tail and feet domains as spheres is a stretch.
-The main point of the simplification is not to capture the shape of dynein, but the conformation.
-It is undefined to discuss the distance between the two motor domains in real dynein, because the motors are made up of hundreds of amino acids, and the average inter-domain distance between amino acids is comparable to the intra-domain distance.
-However it is very easy to describe the difference between two spheres.\\
-
-Each sphere has an associated drag factor $\gamma$, which describes the resistance it feels to motion.
-This drag factor is calculated based on the radius $R$ of the spheres, and is given by Stoke's Law:
-%
-\begin{equation}
-  \gamma = 6\pi\nu R
-\end{equation}
-%
-Thus R becomes a parameter input to the model.\\
-
-\subsubsection{Rigid rods}
-The model assumes connected domains are rigidly attached to one another by rods.
-This assumption makes the math easier, and is not necessarily based on biology.
-One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1nm$ \ref{burgess-paper}.
-However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \ref{myosin-cc-elasticity}.
-
-In reality, all molecules have a degree of elasticity.
-A dynein model by Sarlah \textit{et.
-al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.
-However, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.\\
-
-\subsubsection{Angular springs}
-Each domain has a spring constant, $c_b, c_m$ or $c_t$ for binding, motor or tail, which decides the energy associated with that domain angle. For example, the tail domain energy is given by
-%
-\begin{equation}
-  \Delta G_t = \frac12c_t\left(\theta_t - \theta_t^{eq}\right)^2
-\end{equation}
-
-\subsubsection{Two-state model}
-The model assumes MT-bound dynein can assume one of two states: one where both MTBDs are bound, and one where only one MTBD is bound to the MT.
-These states are also differentiated by different motor equilibrium angles, $\Theta_{m}^{bb}$ and $\Theta_{m}^{ob}$, and different transition rates.
-Biological dynein likely passes through a series of permutations of nucleotide, MT affinity and conformational states as it travels through its mechanochemical cycle.
-This model makes the assumption that the mechanochemical cycle can be broken down into a cycle of prestroking to move the unbound foot forward, brownian walking to place the foot on the microtubule, then powerstroking to move the other domains forward.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
-  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
-  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
-  \label{ob_fig}
-\end{figure}
-
-\textbf{todo: Add springs to joints!}
-
-\subsubsection{Transitioning between states}
-The model transitions between states with a probability dependent on both the energy difference between the two states and the physical separation between the MT and binding MTBD.
-The energy difference between states A and B is given by:
-%
-\begin{equation}
-  \Delta G_{A\rightarrow B} = \sum_{i=0...N_B}^{B} \frac{1}{2}c_i\left(\theta_i-\Theta_i^B\right)^2 - \sum_{j=0...N_A}^{A} \frac{1}{2}c_j\left(\theta_j-\Theta_j^A\right)^2
-\end{equation}
-%
-Transition energies are used to calculate transition rates, as given by the Arhennius equation $k=Ae^{-\beta\Delta G}$, where $\beta = (k_BT)^{-1}$.
-In this equation $\Delta G$ is the total energy of transition between states and A is a constant known as the preexponential factor with units of $s^{-1}$.\\
-%
-\begin{equation}
-  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Ae^{\frac{-\Delta G_{conf}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}}
-\end{equation}
-%
-where $\Delta G_{conf}$ is the change in spring energy in going from bothbound to onebound and $\Delta G_{bind}$ is the energy gained from binding to the microtubule.
-Because binding energy for the MT-MTBD complex is hard to find, the following substitution is made:
-%
-\begin{equation}
-  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Be^{\frac{-\Delta G_{conf}}{k_BT}}
-\end{equation}
-%
-Thus $B$ becomes a parameter of the model.\\
-
-\subsubsection{Brownian dynamics}
-The Brownian dynamics equation describes the motion of high-drag objects which spend most of their time at terminal velocity, and is given by:
-%
-\begin{equation}
-  \dot{x} = \frac{1}{\gamma}\left(F_{net} + R\right)
-\end{equation}
-%
-where $\gamma$ is the drag constant of the object and $R$ is a random Brownian force which describes the effects of water particle collision.
-$R$ is a Gaussian-sampled zero-centered force with variance given by:
-%
-\begin{equation}
-  R_{\sigma^2} = \sqrt{\frac{2*kb*T*\gamma}{dt}}
-\end{equation}
-%
-Dynein is in the range of objects which BD describes well. (citation needed)
-
-\subsubsection{Binding to microtubule}
-The model ``steps'' whenever an MTBD diffuses near the microtubule.
-\textit{In vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
-Thus, all dynein steps should be multiples of $8$nm.
-This model ignores this requirement and allows stepping to occur at any length.
-The assumption is that \textit{in vivo} dynein takes 8nm steps because of its size and stepping angle.
-Thus the 8nm step length should be reproduced by the model without explicit coding.\\
-
-\subsubsection{2D model}
-The coordinate system for this model is two-dimensional.
-Thus interactions between the two motors and MTBDs are ignored.
-This assumption is made to simplify the model.
-Other dynein models, like the winch model \ref{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions.
-It is not clear why such forces are necessary for dynein motion, and so they are omitted.\\
-
-Side stepping of dynein is ignored in this model.
-Stepping perpendicular to the MT occurs in dynein \cite{weihongpaper}, as shown in Figure \ref{fig:weihong-side-stepping}.
-This model assumes it is a symptom, and not an influencer of, of dynein's forward-backward stepping mechanism.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/weihong-side-stepping}
-  \caption{Dynein experimental off-axis stepping histogram.}{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}.
-0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right.
-Modified.}
-  \label{fig:weihong-side-stepping}
-\end{figure}
-
-\subsection{Mathematical models}
-To simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state.
-The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\
-
-\subsubsection{Prestroke onebound model}
-Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound.
-A spatial representation of onebound dynein is shown in Figure \ref{ob_fig}.
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
-%%   \caption{Spatial representation of onebound model.}
-%%   \label{ob_fig}
-%% \end{figure}
-
-TODO: make onebound model figure, label domain names (MTBD motor tail), Ls, Lt, microtubule\\
-
-Each domain is represented by a point, and is connected to other domains via fixed-length rods.
-Angles represent the degrees of freedom of the model.
-Since the protein is a dimer, there are two copies of the MTB, motor and tail domains.
-The tails are fused together and so represented as a single point.
-The motor and MTB domains are given a ``bound'' and ``unbound'' designation to differentiate them.
-The ``bound'' domains are the MTBD attached to the MT and its corresponding motor domain.
-The unbound domains are the unbound MTBD and its corresponding motor domain.\\
-
-\paragraph{Angular and Cartesian coordinates}
-
-The four angles $\Theta_{bb}, \Theta_{bm}, \Theta_{um}$ and $\Theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on.
-The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$.
-Each angle is defined relative to the horizontal axis.
-The position of the bound binding domain $X_{bb}$ and the four domain angles are all that is needed to determine the position of the protein at any time.\\
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \begin{tabular}{c}
-%%     \begin{lstlisting}[language=C++]
-%%       class Dynein_onebound{
-%%         double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
-%%         double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
-%%         double &$X_{bb}$&
-%%       }
-%%     \end{lstlisting}
-%%   \end{tabular}
-%%   \caption{Pseudocode of the onebound Dynein model.}
-%%   \label{ob_struct}
-%% \end{figure}
-
-\paragraph{$\dot{\Theta}_{ub}, \dot{\Theta}_{um}, \dot{\Theta}_{bm}, \dot{\Theta}_{bb}$ calculation}
-
-The following equations allow recursive calculation of the positions of each domain in cartesian coordinates:
-
-\noindent\begin{minipage}{0.49\linewidth}
-\begin{align}
-  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
-  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
-  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
-  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
-\end{align}
-\end{minipage}
-\begin{minipage}{0.49\linewidth}
-\begin{align}
-  Y_{bb} &= 0 \\
-  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
-  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
-  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
-  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
-\end{align}
-\end{minipage}
-\vspace{.5cm}
-
-$L_s$ and $L_t$ correspond to lengths of each interdomain rod, and the $t$ subscripts refer to tail domain coordinates.\\
-
-\paragraph{Angular and Cartesian velocities}
-The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities.
-To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner.
-A subset of the equations are shown here:
-
-\noindent\begin{minipage}{0.49\linewidth}
-\begin{align}
-  \dot{X}_{bb} &= 0 \\
-  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
-  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
-  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
-  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
-\end{align}
-\end{minipage}
-\begin{minipage}{0.49\linewidth}
-\begin{align}                                                                          
-  \dot{Y}_{bb} &= 0 \\                                                        
-  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
-  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
-  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
-  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
-\end{align}
-\end{minipage}
-\vspace{.5cm}
-
-Another way to express these cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:
-
-\begin{align}  
-  \dot{X}_{bm} &= \frac{1}{\gamma_m} \Big(F_{xml} + - \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \label{brownian-bmx}\\
-  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
-  %% \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
-  %% \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
-\end{align}
-
-%% \begin{align}  
-%%   \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
-%%   \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
-%%   \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
-%%   \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
-%% \end{align}
-
-where $\gamma_n$ is a drag coefficient for the binding, motor or tail domain with units of mass per second.
-$F_{xn}$ is the x component of external force on each domain $n$ due to various factors.
-$\lambda_{12}\left(X_1 - X_2\right)$ is the x component of internal force on domain $2$ due to domain $1$, where $\lambda$ is a tension coefficient with units of mass per second per second.
-$R_{xn}$ is the Brownian coefficient representing motion due to solvent collision, with units of velocity.\\
-
-These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations.
-For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated.
-This equating, combined with expanding the recursive velocity definitions leads to new equations, some of which are shown here:
-
-\begin{align}
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
-  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx}
-  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
-  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
-\end{align}
-
-%% \begin{align}
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
-%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
-%% \end{align}
-
-A total of eight coupled differential equations are formed from this procedure.
-These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$.
-This system is more compactly represented as:
-{\small
-  \[
-  \hspace{-1.0cm}
-  \resizebox{0.85\linewidth}{!}{%
-  $\begin{pmatrix}
-    L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0\\
-    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0\\
-    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um})\\
-    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um})\\
-    -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0\\
-    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0\\
-    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um})\\
-    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})\\
-  \end{pmatrix}$%
-  }
-  \begin{pmatrix}
-    \dot{\theta}_{bb}\\
-    \dot{\theta}_{bm}\\
-    \dot{\theta}_{um}\\
-    \dot{\theta}_{ub}\\
-    \lambda_{bs}\\
-    \lambda_{bt}\\
-    \lambda_{ut}\\
-    \lambda_{us}\\
-  \end{pmatrix}
-  =
-  \begin{pmatrix}
-    -F_{bmx} + \gamma_m R_{bmx}\\
-    -F_{tx} + \gamma_t R_{tx}\\
-    -F_{umx} + \gamma_m R_{umx}\\
-    -F_{ubx} + \gamma_b R_{ubx}\\
-    -F_{bmy} + \gamma_m R_{bmy}\\
-    -F_{ty} + \gamma_t R_{ty}\\
-    -F_{umy} + \gamma_m R_{umy}\\
-    -F_{uby} + \gamma_b R_{uby}\\
-  \end{pmatrix}
-  \]
-}
-
-This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\Theta_{bm}}(\Theta_{bb}, \Theta_{bm}, \Theta_{um}, \Theta_{ub})$.
-These motion equations are further described in (\ref{sec:ob-motion-equations}).\\
-
-\subsubsection{Poststroke bothbound model}
-The main difference between the prestroke and poststroke mathematical models is that the latter has a further constraint: both its MTB domains are attached to the MT.
-This has the effect of diminishing the degrees of freedom of the system from four to two, assuming the motor remains above the MT.
-A spatial representation of the bothbound model is shown in Figure (\ref{bb_fig}).\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
-  \caption{Model bothbound equilibrium angle defintion.}{}
-  \label{bb_fig}
-\end{figure}
-
-The bothbound model is very similar in assumptions to the onebound: domains are represented as points connected by rigid rods, and the tails are still fused into a single point.
-The main differences are the naming scheme and spatial constraints.
-Dimers can no longer be differentiated by being un/bound, so are now differentiated by their z-position: being near or far from the ``camera.'' This is similar to labeling them as the right or left dimer.
-Thus there are the near binding (nb), near motor (nm), tail (t), far motor (fm) and far binding (fb) domains.
-Both the near and far binding domains have their x-coordinate fixed at zero.
-The system is described completely by two angles: $\Theta_{nm}$ and $\Theta_{fm}$.
-Angles $\Theta_t, \Theta_{nb}$ and $\Theta_{fb}$ are dependent on these two motor angles.\\
-
-The second MTBD constraint adds another required piece of information the model must track: the x position of the second MTBD.
-This position is described by $L$, the distance between the near and far binding domains.
-The pseudocode used to describe the bothbound model are shown in Figure (\ref{bb_struct}).\\
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=C++]
-      class Dynein_bothbound{
-        double &$\Theta_{nm}, \Theta_{fm}$&
-        double &$\dot{\Theta}_{nm}, \dot{\Theta}_{fm}$&
-        double &$X_{nb, L}$&
-      }
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Pseudocode of the bothbound Dynein model.}
-  \label{ob_struct}
-\end{figure}
-
-\paragraph{$\dot{\Theta}_{nm}, \dot{\Theta}_{fm}$ calculation}
-
-The first step in calculating angular velocities is to define new variables $L_n$ and $L_f$ using the Law of Cosines:
-
-\begin{align}
-  L_n &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{nm}}} \\
-  L_f &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{fm}}}
-\end{align}
-
-These new artificial stalks are not physically relevant, but allow the definition of new angles $\Theta_n, \Theta_{ns}, \Theta_{f}$ and $\Theta_{fs}$, which are useful for calculating the position of the motor domain.
-The treatment of the near and far versions of these angles is very similar, so only the near angles will be dealt with here.
-The angles themselves are never dealt with, only their $\sin$s and $\cos$s:
-
-\begin{align}
-  \cos\theta_n &= \frac{L^2 + L_n^2 - L_f^2}{2L L_n} \\
-  \sin\theta_{n} &= \sqrt{1 - \cos^2\theta_{n}} \\
-  \cos\theta_{ns} &= \frac{L_s^2 + L_n^2 - L_t^2}{2L_s L_n} \\
-  \sin\theta_{ns} &=
-  \begin{cases}
-    +\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} < \pi \\
-    -\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} > \pi
-  \end{cases}
-\end{align}
-
-These values are arrived at through the Law of Cosines and a trigonometric identity.
-The sign of $\sin\left(\Theta_n\right)$ is restricted to positive values due to the angle's $[0,\pi]$ domain.
-$\Theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted.
-The partial derivatives of these values are used in future calculations, and some are shown here:
-
-\begin{align}
-  \frac{\partial \cos\theta_n}{\partial L_n} &= \frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\\
-  \frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{LL_n}\\
-  \frac{\partial \sin\theta_n}{\partial L_n} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
-  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)
-  %% \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
-  %% \left(\frac{-L_f}{LLn}\right)\\
-  %% \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
-  %% - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
-  %% \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
-  %% \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
-  %% \begin{cases}
-  %%   \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
-  %%   \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
-  %%   \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
-  %%   \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
-  %% \end{cases}\\
-  %% \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
-\end{align}
-
-The position of the motor and tail domains is calculated as follws, using the angle addition trigonometric identity:
-
-\begin{align}
-  X_{nm} &= L_s\left(
-  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
-  \right)
-  \\
-  Y_{nm} &= L_s\left(
-  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
-  \right)
-  \\
-  X_{t} &= L_n\cos\theta_n\\
-  Y_{t} &= L_n\sin\theta_n
-\end{align}
-
-The partial derivatives of these values are used later. A selection are shown here:
-
-\begin{align}
-  \frac{dX_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}\Big)\\
-  \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
-  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)
-  %% \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
-  %% \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
-  %% \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
-  %% \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
-  %% \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
-\end{align}
-
-These partial derivatives are then used in a system of equations very similar to that in Equations (\ref{ob_system_first}-\ref{ob_system_last}), combining Brownian and coordinate system definitions of domain velocities:
-
-\begin{align}
-  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} - \lambda_{ns}(X_{bm} - X_{bb})
-  + \lambda_{nt}(X_{t } - X_{bm}) \Big) + R_{xml}
-  &=& \frac{\partial X_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{nm}}{\partial L_f}\dot{L}_f\\
-  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } - \lambda_{nt}(X_{t } - X_{bm})
-  + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
-  &=& \frac{\partial X_{t}}{\partial L_n}\dot{L}_n + \frac{\partial X_{t}}{\partial L_f}\dot{L}_f\\
-  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} - \lambda_{ft}(X_{fm} - X_{t })
-  + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
-  &=& \frac{\partial X_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{fm}}{\partial L_f}\dot{L}_f
-\end{align}
-
-\begin{align}
-  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} - \lambda_{ns}(Y_{bm} - Y_{bb})
-  + \lambda_{nt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
-  &= \frac{\partial Y_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{nm}}{\partial L_f}\dot{L}_f\\
-  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } - \lambda_{nt}(Y_{t } - Y_{bm})
-  + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
-  &= \frac{\partial Y_{t}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{t}}{\partial L_f}\dot{L}_f\\
-  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} - \lambda_{ft}(Y_{fm} - Y_{t })
-  + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
-  &= \frac{\partial Y_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{fm}}{\partial L_f}\dot{L}_f
-\end{align}
-
-The matrix version of this system looks like:
-
-\[
-\begin{pmatrix}
-  -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
-  & -\frac{X_{nm}-X_{nb}}{\gamma} & \frac{X_{t}-X_{nm}}{\gamma} & 0 & 0\\
-  -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
-  & 0 & -\frac{X_{t}-X_{nm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
-  -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
-  & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
-  -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
-  & -\frac{Y_{nm}-Y_{nb}}{\gamma} & \frac{Y_{t}-Y_{nm}}{\gamma} & 0 & 0\\
-  -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
-  & 0 & -\frac{Y_{t}-Y_{nm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
-  -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}
-  & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
-\end{pmatrix}
-\begin{pmatrix}
-  \dot{L}_n\\
-  \dot{L}_f\\
-  \lambda_{ns}\\
-  \lambda_{nt}\\
-  \lambda_{ft}\\
-  \lambda_{fs}\\
-\end{pmatrix}
-=
-\begin{pmatrix}
-  -\frac{1}{\gamma}F_{nmx} - R_{nmx}\\
-  -\frac{1}{\gamma}F_{tx}  - R_{tx}\\
-  -\frac{1}{\gamma}F_{fmx} - R_{fmx}\\
-  -\frac{1}{\gamma}F_{nmy} - R_{nmy}\\
-  -\frac{1}{\gamma}F_{ty}  - R_{ty}\\
-  -\frac{1}{\gamma}F_{fmy} - R_{fmy}\\
-\end{pmatrix}
-\]
-
-This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{sec:bb-motion-equations}).
-
-\subsection{Data interpretation}
-Metrics for quality are required to assess how well the model fits reality. These metrics include time spent in one/bothbound states and average step size. These metrics are developed here.\\
-
-\subsubsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
-Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
-One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations.
-In contrast, the rates the model uses represent the probability of unbinding of a specific conformation.
-Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$.
-As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:
-
-\begin{align*}
-  k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
-  k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
-\end{align*}
-
-where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
-The experimental values are calculated the same way, with the free energy changes replaced with expectation values.
-Since by the equipartition theorem $\left<G_{conf}^{ob}\right> = 2k_BT$ and $\left<G_{conf}^{bb}\right> = k_BT$, the equations can be simplified:
-
-\begin{align*}
-  k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
-  k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
-\end{align*}
-
-Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
-
-\subsubsection{Literature values for experimental binding rates}
-Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
-  \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
-  \label{fig:sarlah-rate-table}
-\end{figure}
-
-The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
-Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound.
-These states are roughly grouped as MT-bound and MT-unbound states in the Cianfrocco mechanochemical cycle \cite{cianfroccoreview}.\\
-
-The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
-That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\
-
-\subsubsection{Calculating one/bothbound times of experimental dynein}
-Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:
+\subsection{Calculating one/bothbound times of experimental dynein}
+In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
 
@@
   &= \frac{\tstep^2}{\tstep+\tproc}\\
+  \frac\tob\tbb &= \frac{\tstep}{\tproc}
 \end{align*}
 
-Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:
+Thus, by the above equations and data from various sources, estimates on $\tbb$ and $\tob$ can be made.\\
 
@@
   \centering
-  \begin{tabular}{| c | c | c | c | c | c |}
+  \begin{tabular}{| c | c | c | c | c | c | c |}
     \hline
-    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+    Source & Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    Weihong 2012 & 134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+    Higuchi 2006 & 800nm/s & 8nm & 0.01s &  7.9? &  9.9e-3 & 1.2e-5\\ \hline
   \end{tabular}
@@
 
-\section{Chapter: Methods}
-This section will go into detail on how the model was implemented in code, verified for accuracy, and how its parameters were fit to experiment.\\
-
-\subsection{Simulation}
-To generate stepping data, the models were coded in \verb|C++| and time-evolved using Euler's method to generate reasonable dynamical behavior.
-When in a position deemed worthy of a state transition a conversion, the model was converted to the respective other model, representing part of a ``step'' through the mechanochemical cycle.
-Some unphysical but minor corrections at points in the simulation were needed to rescue the model from entering incalculable positions.\\
-
-Code is available at \verb|https://github.com/elliotc12/dynein_walk.git|.
-
-%% \paragraph{Euler’s method}
-%% Show how Euler's method is arrived at, how its error scales, why we use it.
-
-%% \paragraph{Vs other methods (Runge Kutta, etc)}
-%% Talk about why our differential equation is most conducive to Euler's method. Euler's is more
-%% efficient -- is there a way to show how our differential equation is smooth, not jagged?
-
-\textit{todo: come up with a better word than ``model'' to describe the state of the system at any time}
-\subsubsection{Time evolution}
-Euler's method for solving differential equations was used to calculate domain positions through time.
-Because each model is a set of multiple coupled differential equations, care was taken to update each domain position at the same time, and not in a cascade.
-A code snippet is shown in Figure (\ref{euler-code-snippet}) for the onebound updating scheme.
-
-\begin{figure}[h!]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=python]
-      def simulate(dyn_ob):
-      t = 0
-      while (t < runtime):
-      double temp_bba = dyn_ob->get_bba() + dyn_ob->get_d_bba() * dt
-      double temp_bma = dyn_ob->get_bma() + dyn_ob->get_d_bma() * dt
-      double temp_uma = dyn_ob->get_uma() + dyn_ob->get_d_uma() * dt
-      double temp_uba = dyn_ob->get_uba() + dyn_ob->get_d_uba() * dt
-
-      dyn_ob->set_bba(temp_bba)
-      dyn_ob->set_bma(temp_bma)
-      dyn_ob->set_uma(temp_uma)
-      dyn_ob->set_uba(temp_uba)
-
-      t += dt
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Code snippet}{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
-  \label{ob_struct}
-\end{figure}
-
-The \verb|dt| used to update was $10^{-11}$ seconds.
-
-\subsubsection{Transitioning between states}
-
-\paragraph{Transition rate}
-\label{sec:transitioning-states}
-Transitions from one state to another are accomplished by calculating the probability of a transition at a given timestep, given by $P_{ob\rightarrow bb} = k_bdt$.
-Each timestep a value in $[0,1]$ is sampled from a random number generator and, if lower than $P$, the respective transition is made.
-A code snippet illustrating how unbinding occurs is shown in Figure (\ref{transition-rate-snippet}).
-
-\begin{figure}[h!]
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=python]
-      def get_near_unbinding_rate(dyn_bb) {
-        dyn_ob_test = make_onebound_from_bothbound(dyn_bb) // do a fake unbind to find energy
-        dG_spring = dyn_ob_test.get_PE() - dyn_bb.get_PE()
-        low_affinity_unbinding_preexponential_factor = low_affinity_unbinding_rate / exp(1.0)
-        return low_affinity_unbinding_preexponential_factor*exp(-dG_spring/kb/T)
-      }
-      def transition_bothbound_to_onebound(dyn_bb) {
-        random_number = rand(0,1)
-        if (random_number < get_unbinding_rate(dyn_bb)) {
-          return make_onebound_from_bothbound(dyn_bb)
-        }
-        else return 0
-      }
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Code snip}{Code snippet of transition rate calculation using the Arrhenius equation.}
-  \label{transition-rate-snippet}
-\end{figure}
-
-\paragraph{OB $\rightarrow$ BB Transition calculation}
-When binding occurs, conversion between OB and BB models is done by creating a bothbound dynein which is as similar in terms of domain position as possible to the onebound dynein.\\
-
-Due to the nature of the simulation, binding attempts must occur above, but very close to, the microtubule.
-This is because \textit{in vivo}, electrostatic interactions between MTBD and MT bring the two together when they are near.
-These electrostatic interactions are not present in the model, and so are simulated by allowing binding attempts to occur when $Y_{ub} \leq 0.2nm$ above the MT.
-When a binding attempt is successful, the unbound binding domain of the OB dynein is ``teleported'' such that $Y_{ub} = 0.0$.
-This is to enforce the constraint that both binding domains of the BB model are directly on the MT.\\
-
-To create a BB model from OB, the following intermediate variables are first computed:\\
-
-\begin{align}
-  L_n^2 &= \left(X_t - X_{nb}\right)^2 + Y_t^2\\
-  L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
-  \cos(\Theta_{nm}) &= \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
-  \cos(\Theta_{fm}) &= \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}
-\end{align}
-
-\textbf{todo: figure out why this new method is used instead of just computing the bad nma angles}
-
-\paragraph{BB $\rightarrow$ OB Transition calculation}
-Similar to the binding transition, unbinding involves creating a new onebound dynein from the old bothbound. To accomplish a transition to the farbound state, the following equations are used:\\
-
-\begin{align}
-  \Theta_{new,bba} &= \Theta_{old,nba}\\
-  \Theta_{new,bma} &= \Theta_{old,nma} + \Theta_{old,nba} - \pi\\
-  \Theta_{new,uma} &= \Theta_{old,fma} + \Theta_{old,fba} - \pi\\
-  \Theta_{new,uba} &= \Theta_{old,fba}
-\end{align}
-
-To do a nearbound transition, the ``f'' and ``n'' subscripts in the above equations are swapped.\\
-
-As shown in Section \ref{final-parameter-table}, the MT binding rate is much quicker than the unbinding rate.
-This means that, when just unbound, the rate of rebinding is very high.
-To prevent immediate rebinding, the model is given a ``rebinding immunity'' of a single timestep.
-During this immunity period, rebinding is not allowed.\\
-
-\subsubsection{Corrections}
-\label{corrections-section}
-Certain configurations of the model, such as in the bothbound model when $\Theta_{nm} = \pi$ or $\Theta_{fm} = \pi$, it becomes impossible to calculate intermediate variables due to values going to infinity (name for this??).
-For example when $\Theta_{nm} = \pi$, $Ln = Ls + Lt$ and so:
-
-\begin{align}
-  \cos\theta_{ns} &= 1 \\
-  \sin\theta_{ns} &= 0 \\
-  \mbox{some val?} &\rightarrow \infty
-\end{align}
-
-Alternative problem states are when $L = 0$ and ???. These states are corrected similarly.\\
-
-\subsubsection{Forces}
-Spring and Brownian forces are used to properly move the model through time.
-Appendices (\ref{sec:ob-motion-equatons}-\ref{sec:bb-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
-
-\paragraph{Brownian forces}
-Each Brownian force $R_{n,m}$ on domain $n$ in direction $m$ is sampled from a Gaussian with standard deviation $\sqrt{\frac{2k_BT\gamma_n}{dt}}$.\\
-
-\paragraph{Spring forces}
-Spring forces are calculated by first finding the torque $\tau$ on each angle, then converting this to a force.
-For example, the onebound near motor angle feels a force $\tau_{nm} = c_m(\Theta_{nm}-\Theta_{nm,eq})$, where $c_n$ is the spring constant of the motor domain and $\Theta_{nm,eq}$ the equilibrium angle.
-The magnitude of force on the adjacent binding and tail domains is thus $\tau/Ls$ and $\tau/Lt$, pointing in the direction adjacent the Ls and Lt rods, respectively.
-The force on the motor domain is found as the equal-and-opposite force to these two imposed forces.
-In code:
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=C++]
-      T = cm*(nma - nma_eq);
-      f1 = T/Ls;
-      f2 = T/Lt;
-      f1x = f1 * sin(bba);
-      f1y = f1 * -cos(bba);
-      f2x = f2 * sin(bma);
-      f2y = f2 * -cos(bma);
-      f.bbx += f1x;
-      f.bby += f1y;
-      f.tx  += f2x;
-      f.ty  += f2y;
-      f.bmx += -(f1x + f2x); // equal and opposite forces
-      f.bmy += -(f1y + f2y);
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Snip}{Code snippet of internal force calculation.}
-  \label{transition-rate-snippet}
-\end{figure}
-
-\subsection{Verifying the model}
-The models were verified to follow physical laws by checking their behavior in various tests: general conformational tests, energy conservation and obeying the equipartition theorem.
-The purpose of these tests was to verify that equations had been entered properly (primarily the conformational and energy conservation tests), and that the model obeyed the laws of physics (all tests).
-
-\subsubsection{Conformational tests}
-\label{sec:conformational-tests}
-The models were tested in the following different conformations to verify they behaved as expected:\\
-
-\textbf{Onebound tests}
-\begin{itemize}
-\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths.
-Also checks that all angular velocities are zero.
-This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or cartesian) without forces.
-\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths.
-Also check that all velocities are zero.
-This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that cartesian x-velocities are positive and y-velocities are zero.
-Verifies that the cartesian velocities have the expected sign.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all cartesian velocities are zero.
-Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
-  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite.
-Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
-\end{itemize}
-*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
-
-These tests together verify that the onebound model's internal coordinate system's directions match the XY coordinate system directions, that the angular directions in the model properly align with the $\pm x$ and $\pm y$ directions of the XY coordinate system, that velocities have the proper magnitude at zero force and proper sign at nonzero force, and that Brownian and internal forces are in the same unit system.
-There are still errors which could exist in the model pertaining to magnitude of velocity, which will be tested for in the energy conservation section.\\
-
-\textbf{Bothbound tests}
-\begin{itemize}
-\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^(-25)$) and motor domains nearly vertical ($\Theta_{n/f} = \pi \pm 10^(-15)$).
-Equilibrium angles set to have a vertical line as the lowest energy point.
-Model is not exactly vertical for NaN concerns explained in section \ref{corrections-section}.
-Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero.
-Verifies that the domains are properly oriented by the angles, the angles are defined properly and forces are calculated from angles properly.
-\item \textbf{Bothbound:} \textit{Equilateral house conformation with outward x-forces.} The model forms the shape of a square with an equilateral triangle on top, with the tail domain as the triangle.
-Checks if all domains are at the desired locations and the derivatives are the proper sign and are equal and opposite to their counterparts on the opposing side of the house.
-This test verifies that the angular system behaves as expected and forces are symmetric about the two dimers.
-\item \textbf{Bothbound:} \textit{Two table conformations with near/far domains flipped.} Two models are put in the same table-like conformation, but the near/far domains are flipped.
-Checks if opposite domains have the same positions and forces.
-Re-verifies that the model is symmetric in position and force between the two dimers.
-\end{itemize}
-
-These tests verify the bothbound model's angle system behaves as expected, forces are zero when expected and have the proper signs, and that the whole system is symmetric with either dimer.
-
-\subsubsection{Energy conservation}
-\label{sec:energy-conservation}
-To verify that the magnitudes of forces are calculated properly, a conservation of energy test was performed.
-A very slight angular nudge was applied to either model.
-This nudge caused a small change in energy.
-This change in energy was compared with the work the forces on each domain caused over the nudge.
-For energy to be conserved, these values were required to be very similar.
-Mathematically the test required the following:
-
-\begin{equation}
-  \sum_n \frac12 \left(\Theta_{nudge} - \Theta_{n} - \Theta_{n,eq}\right) = \sum_n \vec{F}_n \cdot \vec{r}_{n,nudge}
-\end{equation}
-
-where $\Theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the cartesian displacement of each domain $n$ due to the nudge.
-This test is powerful since it links the force-calculation system of either model to the energy calculation system.
-Energy is calculated by looking at displacements of angles from equilibrium, whereas forces are calculated using displacement of angles from equilibrium, but also orientation and position of each domain.
-Having the force system and energy system calculate the same results indicates that they are both likely correct..
-\textbf{make this more precise.}
-
-\textbf{is there a test to be run which could verify the velocity calculation is correct?}
-
-\subsubsection{Equipartition theorem}
-The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $<E> = \frac N2 k_bT$.
-For the dynein models to display ET behavior, they would have to both properly calculate forces and properly calculate velocities from forces.
-Brownian forces are also required to properly explore the different states of the system, but they need not be the correct magnitude for ET agreement.\\
-
-To test if the models obey the ET, the total potential energy of each model was logged over \textbf{ten million} (???) timesteps of simulation.
-The results are reported in Figure \ref{equipartition_agreement}, where the PE scale is in units of $\frac12 k_bT$.
-Energies are reported as a running average over the simulation from 0 to time $t$.
-As shown, both models have their average potential energy converge to the expected amount, where the onebound model has four degrees of freedom and the bothbound two.\\
-
-This test verifies both force and velocity are calculated properly for either model.
-If either force or velocity was wrong, then the model would not obey the Boltzmann hypothesis $P(s) = e^{-\Delta G_{s}/K_BT}$, where $s$ is a state of the system.
-The transition rate from $s_1$ to $s_2$ is $P(s_1\rightarrow s_2) = e^{-{\Delta G_2 - \Delta G_1}/K_BT}$.
-Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.\\
-
-\textbf{would it be a stronger test to also calculate the standard deviation of <PE>?
-It seems like <PE> would still equal N/2KbT as long as the forces/velocities were symmetrically wrong.
-Calculating the stdev would require the state occupation to actually the ET.
-Or, maybe just plot the angle occupation and show that it is what it should be?}
-
-\textbf{Possibly do mutations on motion equations to show that tests are no longer behaved}
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| c | c | c | c |}
-    \hline
-    Author & Conditions & Velocity & Run length\\\hline
-    Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
-    Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
-  \end{tabular}
-  \caption{Literature values for experimental dynein stepping behavior.}{Table of literature values for dynein behavior}
-  \label{table:parameter-table}
-\end{figure}
-
-%% \subsection{Data collection}
-%% Time evolution of the system has the potential to create a huge amount of data, so care has to be taken to only collect what is necessary.
-For the purposes of testing stepping behavior of the model the geometry and per-domain forces and energies can be safely ignored.
-All that is needed to determine model fitness is the size and duration of each step.\\
-
-%% \subsubsection{Stepping data output and calculation}
-%% A step is defined as a complete cycle of
-
-%% \subsubsection{Simulation running via SLURM}
-
-\subsection{Parameter fitting}
-There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
-Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.\\
-
-Others are more difficult to find.
-These values, including $k_b$, $k_ub$ and the three spring constants, are fit by an optimization process.
-First un/binding rates are fit to one/bothbound times, then spring constants are fit to average step length.
-This process is chronicled below.
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
-    \hline
-    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
-    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
-    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
-    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
-    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
-    $R_t$ &  & & & & 2.16nm & & & \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
-    $k_b$ & $460 s^{-1,b}$ & & & & & & & \\ \hline
-    $c_t$ & & & & & & & & \\ \hline
-    $c_m$ & & & & & & & & \\ \hline
-    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
-  \end{tabular}
-  \caption{Literature values for dynein model parameters.}{Table of literature values for various free parameters in dynein model.}
-  \label{table:parameter-table}
-\end{figure}
-
-In addition, the physical conditions the simulations were run at are shown in Table \ref{table:simulation-conditions}.
-These conditions are meant to reflect the conditions found inside a typical cell.
-\textbf{of what species?}\\
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| l | l |}
-    \hline
-    T & [ATP] \\ \hline
-    310.15 K & $1mM$\\ \hline
-  \end{tabular}
-  \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
-  \label{table:simulation-std-conditions}
-\end{figure}
-
-\subsubsection{Fitting rate constants}
-To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
-The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}.
-Simulation behavior for a wide range of $k_b$ and $k_{ub}$ values is shown as a heat map in Figure \ref{fig:kb-kub-heatmap}.\\
-
-\textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
-
-\subsubsection{Fitting spring constants}
-This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
-
-\newpage
-\section{Chapter: Results \& Discussion}
-\subsection{Validating model}
-The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
-Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over a long time.
-This is evidence that both the forces and velocities of the model are properly calculated.
-Grossly inncorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy.
-The model's force calculations are further validated in Section \ref{sec:conformational-tests}, and energy conservation is validated in Section \ref{sec:energy-conservation}.\\
-
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
-    \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
-  \end{minipage}
-  \hspace{.2cm}
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
-    \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
-  \end{minipage}
-  \label{fig:equipartition_agreement}
-\end{figure}
-
-\subsection{Model achieves processivity}
-When run at the proper parameters, the dynein model can step processively.
-Figure \ref{fig:stepping-trajectory} shows the dynamics of a motor when run at the parameters shown in Table \ref{table:thesis-parameters}.
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| l | l | l | l | l | l |}
-    \hline
-    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
-    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
-  \end{tabular}
-  \caption{Parameters used in processive simulations in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
-  \label{table:thesis-parameters}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\textwidth]{../../plots/x-trajectory_thesis}
-  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
-  \caption{Near and far binding domains over the course of several microseconds of simulation.
-Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
-  \label{fig:stepping-trajectory}
-\end{figure}
-
-Figures \ref{fig:stepping-trajectory}.b and \ref{fig:stepping-trajectory}.c demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time.
-This behavior indicates that a springy hinge model with shifting equilibrium angles is capable of generating processive stepping behavior.
-Now that the model has demonstrated stepping behavior, it must be seen if it can generate steps at a size- and time-scale similar to that which real dynein takes in experiment.\\
-
-Another important determination from Figure \ref{fig:stepping-trajectory}.c is the average position of the unbound foot is about 30\textit{nm} above the microtubule.
-This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible.
-However, it does initially suggest how dynein searches for the microtubule.
-Instead of hovering near the microtubule looking for a binding site, the motor pulls its foot away from the microtubule, diffusing until pushed downward far enough to bind.
-This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30\textit{nm} would allow significant x-diffusion along the microtubule.
-This could be contrasted with kinesin, which is smaller and could not move its foot so high off the microtubule.\\
-
-Importantly, the physical parameters causing processive motion are reasonable physically.
-The spring constants are roughly the same size as the energy of hydrolysis of ATP, which is reasonable.
-By a very rough argument, the dynein must move its tail angle by roughly one radian to diffuse enough for a step.
-This would correspond to a $\Delta G_{spring} = \frac{1}{2}c_t\Delta \theta_t \approx \Delta G_{ATP}$, which is very reasonable.
-In addition, the tail spring constant is less than the motor and binding spring constants, which is in line with the notion that the tail is much more elastic than the motor or binding domains.
-CITE\\
-
-\subsection{Model step size is highly variant}
-Figure \ref{fig:final-histograms}.a shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}.
-This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\
-
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
-    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
-    \caption{Model vs experimental step sizes.
-\textbf{a.)} Step sizes model took at parameters in \ref{table:thesis-parameters}.
-\textbf{b.)} Experimental stepping behavior of dynein \cite{weihongpaper}.}
-    \label{fig:final-histograms}
-\end{figure}
-
-Figure \ref{fig:final-histograms}.a shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$.
-This is a very important result, since it indicates that the model is capable of taking a varied step size.
-This behavior is characteristic of dynein, and hence very important to reproduce.\\
-
-The preference for $<5nm$ steps is very un-dynein-like.
-One explanation is that steps may be defined differently between experimental and modeled dynein.
-In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram.
-This may not be how the experiment in \ref{fig:final-histograms}.b records steps.
-Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely.
-A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out.
-This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\
-
-The ability of the model to generate near-experiment stepping behavior is imperative if the model is to be considered a proper explanation of dynein's stepping.
-In the case that changing the binding rate does not remove the small-step preference of the model, it may be necessary to change how the model works.
-For example, using the total spring-energy-of-binding change to calculate the binding probability may be invalid, or perhaps the entire two-state model will need to be thrown out.
-The inability of either of these assumptions to predict dynein's behavior would themselves be important findings.\\
-
-Another issue with the simulated histogram is that it shows no steps over $30nm$.
-This is a problem, since taking $40+nm$ steps is characteristic of dynein.
-Ideally, tuning the parameters of dynein would increase the step size.
-However, in the case that it can't, this might be an important result.
-The current model assumes connections between domains are rigid.
-This may not be a valid assumption, since the coiled coil region connecting the binding and motor domains has some elasticity to it CITE.
-Thus it may be necessary to add in elasticity to the model to reproduce long steps.\\
-
-Comparing the simulation results in \ref{fig:final-histograms}.a with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein.
-However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein.
-It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically.
-Lowering the binding rate may even out the histogram and prevent instant rebinding.
-It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm.
-Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\
-
-%% \subsection{Current work: Refining model parameters}
-%% Once validated, the model was fit to experimental data.
-Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values.
-The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment.
-As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.
-
-%% \begin{figure}[H]
-%%   \centering
-%%   \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
-%%   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
-Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.
-The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right.
-Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
-%%   \label{fig:kb-kub-heatmap}
-%% \end{figure}
-
-\section{Conclusion}
-\subsection{Findings}
-The most important findings of this work are that a springy hinge model of dynein can take steps of a similar size to real dynein.
-What's more, it is likely further tweaking of the model will improve the model's behavior to the point of generating backwards and large steps.
-This would be a very important result which would strongly support the linker-swing/diffusive-step model of dynein stepping and guide further research.\\
-
-Many studies have been done on dynein, resulting in a large body of literature about the motor's behavior and features.
-Sifting through this information to find what is important for the motor's step is a difficult task.
-Mutational studies can remove traits of the motor, deducing what traits are necessary for stepping.
-However, this process is slow, and it can be difficult to remove large traits of the motor while keeping the engineered dynein representative of the natural motor.
-This is where simulations come in.
-Minimal features can be put into a physical model, which can then be tested for behavior similar to real dynein.
-In this study, we created a mathematical model which simplifies the motor to a rigid hinge structure with harmonic spring energies between the hinges.
-The equilibrium angles change dynamically to reflect structural changes during dynein's mechanochemical cycle.
-The model was then subjected to Brownian forces and evolved.
-If the model generates a stepping pattern similar to real dynein, this would demonstrate that dynein can be thought of as a rigid hinged structure.
-This would mean that many other traits of dynein may not be vital for stepping, such as stalk elasticity \cite{sarlahmodel}, motor-motor interaction \cite{sarlahmodel}, nucleotide state \cite{cianfroccoreview}, nucleotide state of non-AAA1 nuclease sites \cite{cianfroccoreview}, and changing stiffness of the foot domain \cite{burgess-paper}.
-Thus future research may want to focus more on linker swing and binding interactions, and less on these other traits.\\
-
-Other findings cast doubt on some aspects of the model.
-The vast preference of the model for $<5nm$ steps suggests that the model may handle binding events unlike real dynein.
-When binding, the total spring energy of the transition from a onebound to a bothbound state is calculated, then used to calculate the likelihood of transition via a Boltzmann factor.
-This approach may be overly simple, or take into account the wrong information.
-It may be that it is necessary to expand the two-state model into a three-state model with a low-microtubule-affinity onebound state immediately after unbinding, to prevent instant rebinding.
-This state would eventually transition to the high-microtubule-affinity state after some time.
-If this proves to be necessary to decrease small steps, this would be an interesting result showing that the motor might rely on its low-microtule-affinity ADP-Pi state to prevent early binding.\\
-
-\subsection{Further work}
-The goal of studying dynein's mechanochemical cycle is to find an explanation for how it work.
-That is, to find the necessary and sufficient properties of dynein that cause the cycle to happen.
-Simulations are only part of the recipe for creating a scientific theory.
-Simulations are easy to implement and can study phenomena which are difficult to design experiments for.
-However, when experimental data is available, it is generally more reliable than a simulation of the same system.
-This is because a simulation is only as good as the strength of correspondence between the mathematical model and the system it represents.
-With dynein, this correspondence can be hard to achieve because the protein is complicated.
-The model predicts, according to the laws of physics for small objects, how a small machine composed of springy hinges would behave in an aqueous environment.
-This machine can be made the same size and general shape as dynein, and its conformational angles can be made the same as dynein's, and its state transitions can happen in the same way dynein's do.
-However, it is never possible to say that this machine ``is'' dynein or represents how dynein actually behaves.
-Thus, it is only possible to say that the simulation provides sufficient criteria for dynein stepping, not necessary criteria.
-The simulation shows that the linker-swing/diffusive-step model is sufficient for motion, but it cannot show that this is needed for dynein's walk.\\
-
-To more strongly support the linker-swing/diffusive step model of dynein motion, more experiments should be done.
-Demonstrating that dynein requires flexible domain connections in order to take such broad steps would be one powerful experiment.
-Mutating the foot and tail domains to be more rigid, then examining stepping behavior would be one way to see if rigidity is necessary for random steps.
-Another experiment could use FRET (Forster Resonance Energy Transfer) and fluorophores on the microtubule and foot domain to track how the distance between the two regions evolves with time.
-This could provide information about the average distance between the MTBD and MT, which would validate this work's finding that the MTBD mostly hovers.
-More importantly, FRET data could be fit to models to predict the amount of diffusion the foot domain undergoes over the course of a step.
-Significant diffusion would indicate that diffusion may be very important for the step.
-Experiments with both feet labeled could get similarly good information.\\
-
-\textbf{Talk to Dr. Hsu about this sort of thing...what experiments could be used to validate the model?}
-
-If the model were validated by FRET and rigidity mutation studies, then there are many other interesting things which could be found from it.
-First, the amount of work done by the motor could be found by inducing an artificial drag force pulling the protein's motor domains against its direction of travel.
-This force could be integrated over dynein's trajectory to find the work the model exerted on its artificial cargo.
-This could be used to estimate the efficiency of the motor.
-Another interesting study would be to add binding sites to the model, only allowing it to bind at $\alpha-\beta$ tubulin dimerization sites, like real dynein.
-This would mandate re-fitting the binding constants to the new environment.
-It would be interesting to know if this model behaves more, or less dynein-like than the original.
-This would help answer the question of whether dynein searches for a binding site on the microtubule, or if it is naturally tuned to bind at the right site.\\
-
-Another very interesting simulation which could be run could help answer the open question of why kinesin and dynein, though using similar mechanisms, produce such different steps.
-Kinesin, unlike dynein, conducts all of its chemistry directly on its foot.
-This translates to effectively having two fewer joints than dynein.
-Kinesin's stroke is believed to involves a similar foot unbinding, kicking forward, rebinding, then lurching the motor forward mechanism.
-The dynein model could be used to construct a very rough model of kinesin by shrinking the tail linkers and increasing the motor domain spring constant $c_m$ high enough to simulate a rigid hinge.
-This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics.
-If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating.
-This result would show that the differences betwen kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants.
-This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\
-
-Next: add Big Questions to introduction, then answer them here.\\
-
-\bibliography{thesis-articles}
-
-%% \bibliography{thesis-webpages}
-
-\section{Appendix}
-
-\subsubsection{Glossary}
-\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate.
-This reaction is used to power many energy-requiring mechanisms within the cell.
-This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
-\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.\\
-
-\subsection{Motion equations}
-
-\subsubsection{Onebound equations}
-\label{sec:ob-motion-equations}
-The following is a continuation of the derivation for the full motion equations used to time evolve the onebound model:
-
-\begin{align*}
-AA &= L_s\sin\theta_{bb}      &   LL &= -L_s\cos(\theta_{bb})\\
-BB &= L_t\sin(\theta_{bm})    &	 MM &= -L_t\cos(\theta_{bm})\\
-CC &= -L_t\sin(\theta_{um})   &	 NN &= L_t\cos(\theta_{um})\\
-DD &= -L_s\sin(\theta_{ub})   &	 OO &= L_s\cos(\theta_{ub})\\
-\\
-EE &= -\gamma_m (X_{bm} - X_{bb})       &  PP &= -\gamma_m (Y_{bm} - Y_{bb})\\
-FF &= \gamma_m (X_{t } - X_{bm})        &	 QQ &= \gamma_m (Y_{t } - Y_{bm})\\ 
-GG &= -\gamma_t (X_{t } - X_{bm})       &	 RR &= -\gamma_t (Y_{t } - Y_{bm})\\
-HH &= \gamma_t (X_{um} - X_{t })        &	 SS &= \gamma_t (Y_{um} - Y_{t })\\ 
-II &= -\gamma_m (X_{um} - X_{t })       &	 TT &= -\gamma_m (Y_{um} - Y_{t })\\
-JJ &= \gamma_m (X_{ub} - X_{um})        &	 UU &= \gamma_m (Y_{ub} - Y_{um})\\ 
-KK &= -\gamma_b (X_{ub} - X_{um})       &	 VV &= -\gamma_b (Y_{ub} - Y_{um})\\
-\end{align*}%
-%
-\[
-\begin{pmatrix}
-  AA & 0 & 0 & 0 & EE & FF & 0 & 0\\
-  AA & BB & 0 & 0 & 0 & GG & HH & 0\\
-  AA & BB & CC & 0 & 0 & 0 & II & JJ\\
-  AA & BB & CC & DD & 0 & 0 & 0 & KK\\
-  LL & 0 & 0 & 0 & PP & QQ & 0 & 0\\
-  LL & MM & 0 & 0 & 0 & RR & SS & 0\\
-  LL & MM & NN & 0 & 0 & 0 & TT & UU\\
-  LL & MM & NN & OO & 0 & 0 & 0 & VV\\
-\end{pmatrix}
-\begin{pmatrix}
-    \dot{\theta}_{bb}\\
-    \dot{\theta}_{bm}\\
-    \dot{\theta}_{um}\\
-    \dot{\theta}_{ub}\\
-    \lambda_{bs}\\
-    \lambda_{bt}\\
-    \lambda_{ut}\\
-    \lambda_{us}\\
-  \end{pmatrix}
-=
-\begin{pmatrix}
-  X1\\
-  X2\\
-  X3\\
-  X4\\
-  X5\\
-  X6\\
-  X7\\
-  X8\\
-\end{pmatrix}
-\]
-
-Solving the above system for $\dot{\Theta}_{bb}, \dot{\Theta}_{bm}, \dot{\Theta}_{um}$ and $\dot{\Theta}_{ub}$ gives the desired velocities. Solution was done via Mathematica.
-
-%% $\dot{\Theta}_{bb}$ =
-%% {\tiny
-%% ( - (GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 - BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 + BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 + FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 - BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 - CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 + EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 + EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 - BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 - CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 + BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 - BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 - BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 - BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/(( - (EE*GG*II*LL*MM*NN) - BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP - AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ - BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ + CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR - AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR - CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS - AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS - BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT - BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT + BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT + AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% } \break
-
-%% $\dot{\Theta}_{bm}$ =
-%% {\tiny
-%%   (GG*II*LL*NN*PP*X1 - CC*HH*LL*PP*RR*X1 + AA*HH*NN*PP*RR*X1 - AA*II*NN*PP*RR*X1 + CC*GG*LL*PP*SS*X1 - AA*GG*NN*PP*SS*X1 - CC*GG*LL*PP*TT*X1 + AA*CC*PP*RR*TT*X1 - FF*II*LL*NN*PP*X2 + EE*II*LL*NN*QQ*X2 - EE*II*LL*NN*RR*X2 + AA*II*NN*PP*RR*X2 - CC*FF*LL*PP*SS*X2 + AA*FF*NN*PP*SS*X2 + CC*EE*LL*QQ*SS*X2 - AA*EE*NN*QQ*SS*X2 + CC*FF*LL*PP*TT*X2 - CC*EE*LL*QQ*TT*X2 + CC*EE*LL*RR*TT*X2 - AA*CC*PP*RR*TT*X2 + FF*HH*LL*NN*PP*X3 - EE*HH*LL*NN*QQ*X3 + EE*HH*LL*NN*RR*X3 - AA*HH*NN*PP*RR*X3 - EE*GG*LL*NN*SS*X3 - AA*FF*NN*PP*SS*X3 + AA*GG*NN*PP*SS*X3 + AA*EE*NN*QQ*SS*X3 - EE*GG*II*LL*NN*X5 + CC*EE*HH*LL*RR*X5 - AA*EE*HH*NN*RR*X5 + AA*EE*II*NN*RR*X5 - CC*EE*GG*LL*SS*X5 + AA*EE*GG*NN*SS*X5 + CC*EE*GG*LL*TT*X5 - AA*CC*EE*RR*TT*X5 + EE*GG*II*LL*NN*X6 + CC*FF*HH*LL*PP*X6 - AA*FF*HH*NN*PP*X6 + AA*FF*II*NN*PP*X6 - AA*GG*II*NN*PP*X6 - CC*EE*HH*LL*QQ*X6 + AA*EE*HH*NN*QQ*X6 - AA*EE*II*NN*QQ*X6 - CC*EE*GG*LL*TT*X6 - AA*CC*FF*PP*TT*X6 + AA*CC*GG*PP*TT*X6 + AA*CC*EE*QQ*TT*X6 - CC*FF*HH*LL*PP*X7 + CC*EE*HH*LL*QQ*X7 - CC*EE*HH*LL*RR*X7 + AA*CC*HH*PP*RR*X7 + CC*EE*GG*LL*SS*X7 + AA*CC*FF*PP*SS*X7 - AA*CC*GG*PP*SS*X7 - AA*CC*EE*QQ*SS*X7)/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) + (( - (FF*HH*LL*PP) + EE*HH*LL*QQ - EE*HH*LL*RR + AA*HH*PP*RR + EE*GG*LL*SS + AA*FF*PP*SS - AA*GG*PP*SS - AA*EE*QQ*SS)*(JJ*NN - CC*UU)*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/((EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)*( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV)))
-%% }\break
-
-%% $\dot{\Theta}_{um}$ =
-%% {\tiny
-%%   ( - X2 + X3)/CC + (GG*( - (BB*LL*PP*X1) + AA*MM*PP*X1 + EE*LL*MM*X2 - AA*MM*PP*X2 + BB*EE*LL*X5 - AA*EE*MM*X5 - BB*EE*LL*X6 + AA*BB*PP*X6))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)) - ((( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT) - ((JJ/CC + ((EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*(( - HH + II)/CC - (GG*(EE*LL - AA*PP)*( - (HH*MM) + BB*SS))/(CC*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)))*( - (JJ*NN) + CC*UU))/(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }\break
-
-%% $\dot{\Theta}_{ub}$ =
-%% {\tiny
-%%   ( - X3 + X4)/DD + (II*( - (BB*GG*LL*NN*PP*X1) + AA*GG*MM*NN*PP*X1 + BB*CC*LL*PP*RR*X1 - AA*CC*MM*PP*RR*X1 + BB*FF*LL*NN*PP*X2 - AA*FF*MM*NN*PP*X2 - BB*EE*LL*NN*QQ*X2 + AA*EE*MM*NN*QQ*X2 - CC*EE*LL*MM*RR*X2 + BB*EE*LL*NN*RR*X2 + AA*CC*MM*PP*RR*X2 - AA*BB*NN*PP*RR*X2 + EE*GG*LL*MM*NN*X3 - BB*FF*LL*NN*PP*X3 + AA*FF*MM*NN*PP*X3 - AA*GG*MM*NN*PP*X3 + BB*EE*LL*NN*QQ*X3 - AA*EE*MM*NN*QQ*X3 - BB*EE*LL*NN*RR*X3 + AA*BB*NN*PP*RR*X3 + BB*EE*GG*LL*NN*X5 - AA*EE*GG*MM*NN*X5 - BB*CC*EE*LL*RR*X5 + AA*CC*EE*MM*RR*X5 + CC*EE*GG*LL*MM*X6 - BB*EE*GG*LL*NN*X6 - BB*CC*FF*LL*PP*X6 + AA*CC*FF*MM*PP*X6 - AA*CC*GG*MM*PP*X6 + AA*BB*GG*NN*PP*X6 + BB*CC*EE*LL*QQ*X6 - AA*CC*EE*MM*QQ*X6 - CC*EE*GG*LL*MM*X7 + BB*CC*FF*LL*PP*X7 - AA*CC*FF*MM*PP*X7 + AA*CC*GG*MM*PP*X7 - BB*CC*EE*LL*QQ*X7 + AA*CC*EE*MM*QQ*X7 + BB*CC*EE*LL*RR*X7 - AA*BB*CC*PP*RR*X7))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)) - ((( - JJ + KK)/DD - (II*(EE*GG*LL*MM - BB*FF*LL*PP + AA*FF*MM*PP - AA*GG*MM*PP + BB*EE*LL*QQ - AA*EE*MM*QQ - BB*EE*LL*RR + AA*BB*PP*RR)*( - (JJ*NN) + CC*UU))/(DD*(EE*GG*II*LL*MM*NN + BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP + AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ + BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ - CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR + AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR + CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS + AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS + BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT + BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT - BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT - AA*BB*CC*PP*RR*TT)))*( - ((( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( - ((( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*NN*X2 +  Power(AA,4)* Power(BB,2)*NN*X3 -  Power(AA,4)* Power(BB,2)*CC*X7)))) + ( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( - ((( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,3)* Power(BB,2)*CC*LL*X1 -  Power(AA,4)*BB*CC*MM*X1 +  Power(AA,4)*BB*CC*MM*X2 -  Power(AA,4)* Power(BB,2)*CC*X6))) + ( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (LL*X1) + AA*X5)) + ( - (EE*LL) + AA*PP)*( Power(AA,5)* Power(BB,3)*CC*DD*LL*X1 -  Power(AA,6)* Power(BB,2)*CC*DD*MM*X1 +  Power(AA,6)* Power(BB,2)*CC*DD*MM*X2 -  Power(AA,6)* Power(BB,3)*DD*NN*X2 +  Power(AA,6)* Power(BB,3)*DD*NN*X3 -  Power(AA,6)* Power(BB,3)*CC*OO*X3 +  Power(AA,6)* Power(BB,3)*CC*OO*X4 -  Power(AA,6)* Power(BB,3)*CC*DD*X8)))))/( - (( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*(( Power(AA,6)* Power(BB,2)*CC*DD*HH*MM -  Power(AA,6)* Power(BB,3)*DD*HH*NN +  Power(AA,6)* Power(BB,3)*DD*II*NN -  Power(AA,6)* Power(BB,3)*CC*II*OO)*( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR))) - ( - (EE*LL) + AA*PP)*(( Power(AA,5)* Power(BB,3)*CC*DD*FF*LL -  Power(AA,6)* Power(BB,2)*CC*DD*FF*MM +  Power(AA,6)* Power(BB,2)*CC*DD*GG*MM -  Power(AA,6)* Power(BB,3)*DD*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,5)* Power(BB,3)*CC*DD*EE*LL -  Power(AA,6)* Power(BB,2)*CC*DD*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS))*( Power(AA,4)* Power(BB,2)*JJ*NN -  Power(AA,4)* Power(BB,2)*CC*UU)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( - (( - (EE*LL) + AA*PP)*(( Power(AA,3)* Power(BB,2)*CC*FF*LL -  Power(AA,4)*BB*CC*FF*MM +  Power(AA,4)*BB*CC*GG*MM -  Power(AA,4)* Power(BB,2)*GG*NN)*( - (EE*LL) + AA*PP) - ( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*CC*SS)) + ( - (EE*LL) + AA*PP)*( - (( Power(AA,3)* Power(BB,2)*CC*EE*LL -  Power(AA,4)*BB*CC*EE*MM)*( - (FF*LL) + AA*QQ)) + ( - (EE*LL) + AA*PP)*( Power(AA,4)*BB*CC*GG*MM -  Power(AA,2)*BB*CC*( - (AA*BB*FF*LL) +  Power(AA,2)*FF*MM +  Power(AA,2)*BB*RR)))*( Power(AA,4)*BB*CC*HH*MM -  Power(AA,4)* Power(BB,2)*HH*NN +  Power(AA,4)* Power(BB,2)*II*NN -  Power(AA,4)* Power(BB,2)*CC*TT))*( Power(AA,6)* Power(BB,3)*DD*JJ*NN -  Power(AA,6)* Power(BB,3)*CC*JJ*OO +  Power(AA,6)* Power(BB,3)*CC*KK*OO -  Power(AA,6)* Power(BB,3)*CC*DD*VV))
-%% }
-
-\subsubsection{Bothbound equations}
-\label{sec:bb-motion-equations}
-The following are the full motion equations used to time evolve the bothbound model:
-
-\begin{center}
-  \begin{minipage}{0.3\textwidth}
-    \begin{align*}
-      a &= \frac{-dXnm}{dLn}\\
-       b &= \frac{-dXnm}{dLf}\\
-       c &= -(x_{nm} - x_{nb}) / \gamma_m\\
-       d &= (x_t - x_{nm}) / \gamma_m\\
-       e &= \frac{-dXt}{dLn}\\
-       f &= \frac{-dXt}{dLf}\\
-       g &= -(x_t - x_{nm}) / \gamma_t\\
-       h &= (x_{fm} - x_t) / \gamma_t\\
-       i &= \frac{-dXfm}{dLn}\\
-       j &= \frac{-dXfm}{dLf}\\
-       k &= -(x_{fm} - x_t) / \gamma_m\\
-       l &= (x_{fb} - x_{fm}) / \gamma_m\\
-    \end{align*}
-  \end{minipage}
-  \begin{minipage}{0.3\textwidth}
-    \begin{align*}
-       m &= \frac{-dYnm}{dLn}\\
-       n &= \frac{-dYnm}{dLf}\\
-       p &= -(y_{nm} - y_{nb}) / \gamma_m\\
-       q &= (y_t - y_{nm}) / \gamma_m\\
-       r &= \frac{-dYt}{dLn}\\
-       s &= \frac{-dYt}{dLf}\\
-       t &= -(y_t - y_{nm}) / \gamma_t\\
-       u &= (y_{fm} - y_t) / \gamma_t\\
-       v &= \frac{-dYfm}{dLn}\\
-       w &= \frac{-dYfm}{dLf}\\
-       x &= -(y_{fm} - y_t) / \gamma_m\\
-       y &= (y_{fb} - y_{fm}) / \gamma_m
-    \end{align*}
-  \end{minipage}
-\end{center}
-
-Solving the above system for $\dot{\Theta}_{nm}$ and $\dot{\Theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
-
-%% $\dot{Ln}$ =
-%% {\tiny
-%%     (h*l*p*t*w*x1 - g*l*p*u*w*x1 + g*l*p*s*x*x1 - f*l*p*t*x*x1 +
-%%      d*l*p*u*w*x2 - c*l*q*u*w*x2 - d*l*p*s*x*x2 + c*l*q*s*x*x2 -
-%%      c*l*n*t*x*x2 + b*l*p*t*x*x2 - c*h*l*t*w*x4 + c*g*l*u*w*x4 -
-%%      c*g*l*s*x*x4 + c*f*l*t*x*x4 - d*h*l*p*w*x5 + c*h*l*q*w*x5 +
-%%      c*g*l*n*x*x5 + d*f*l*p*x*x5 - b*g*l*p*x*x5 - c*f*l*q*x*x5 +
-%%      d*h*l*p*s*x6 - c*h*l*q*s*x6 + c*h*l*n*t*x6 - b*h*l*p*t*x6 -
-%%      c*g*l*n*u*x6 - d*f*l*p*u*x6 + b*g*l*p*u*x6 + c*f*l*q*u*x6 -
-%%      g*k*p*s*x1*y - h*j*p*t*x1*y + f*k*p*t*x1*y + g*j*p*u*x1*y +
-%%      d*k*p*s*x2*y - c*k*q*s*x2*y + c*k*n*t*x2*y - b*k*p*t*x2*y -
-%%      d*j*p*u*x2*y + c*j*q*u*x2*y - d*h*p*s*x3*y + c*h*q*s*x3*y -
-%%      c*h*n*t*x3*y + b*h*p*t*x3*y + c*g*n*u*x3*y + d*f*p*u*x3*y -
-%%      b*g*p*u*x3*y - c*f*q*u*x3*y + c*g*k*s*x4*y + c*h*j*t*x4*y -
-%%      c*f*k*t*x4*y - c*g*j*u*x4*y - c*g*k*n*x5*y + d*h*j*p*x5*y -
-%%      d*f*k*p*x5*y + b*g*k*p*x5*y - c*h*j*q*x5*y + c*f*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }\break
-
-%% $\dot{Lf}$ =
-%% {\tiny
-%%     (-(h*l*p*t*v*x1) + g*l*p*u*v*x1 - g*l*p*r*x*x1 + e*l*p*t*x*x1 -
-%%      d*l*p*u*v*x2 + c*l*q*u*v*x2 + d*l*p*r*x*x2 - c*l*q*r*x*x2 +
-%%      c*l*m*t*x*x2 - a*l*p*t*x*x2 + c*h*l*t*v*x4 - c*g*l*u*v*x4 +
-%%      c*g*l*r*x*x4 - c*e*l*t*x*x4 + d*h*l*p*v*x5 - c*h*l*q*v*x5 -
-%%      c*g*l*m*x*x5 - d*e*l*p*x*x5 + a*g*l*p*x*x5 + c*e*l*q*x*x5 -
-%%      d*h*l*p*r*x6 + c*h*l*q*r*x6 - c*h*l*m*t*x6 + a*h*l*p*t*x6 +
-%%      c*g*l*m*u*x6 + d*e*l*p*u*x6 - a*g*l*p*u*x6 - c*e*l*q*u*x6 +
-%%      g*k*p*r*x1*y + h*i*p*t*x1*y - e*k*p*t*x1*y - g*i*p*u*x1*y -
-%%      d*k*p*r*x2*y + c*k*q*r*x2*y - c*k*m*t*x2*y + a*k*p*t*x2*y +
-%%      d*i*p*u*x2*y - c*i*q*u*x2*y + d*h*p*r*x3*y - c*h*q*r*x3*y +
-%%      c*h*m*t*x3*y - a*h*p*t*x3*y - c*g*m*u*x3*y - d*e*p*u*x3*y +
-%%      a*g*p*u*x3*y + c*e*q*u*x3*y - c*g*k*r*x4*y - c*h*i*t*x4*y +
-%%      c*e*k*t*x4*y + c*g*i*u*x4*y + c*g*k*m*x5*y - d*h*i*p*x5*y +
-%%      d*e*k*p*x5*y - a*g*k*p*x5*y + c*h*i*q*x5*y - c*e*k*q*x5*y)/
-%%      (d*h*l*p*s*v - c*h*l*q*s*v + c*h*l*n*t*v - b*h*l*p*t*v -
-%%      c*g*l*n*u*v - d*f*l*p*u*v + b*g*l*p*u*v + c*f*l*q*u*v -
-%%      d*h*l*p*r*w + c*h*l*q*r*w - c*h*l*m*t*w + a*h*l*p*t*w +
-%%      c*g*l*m*u*w + d*e*l*p*u*w - a*g*l*p*u*w - c*e*l*q*u*w +
-%%      c*g*l*n*r*x + d*f*l*p*r*x - b*g*l*p*r*x - c*f*l*q*r*x -
-%%      c*g*l*m*s*x - d*e*l*p*s*x + a*g*l*p*s*x + c*e*l*q*s*x +
-%%      c*f*l*m*t*x - c*e*l*n*t*x + b*e*l*p*t*x - a*f*l*p*t*x -
-%%      c*g*k*n*r*y + d*h*j*p*r*y - d*f*k*p*r*y + b*g*k*p*r*y -
-%%      c*h*j*q*r*y + c*f*k*q*r*y + c*g*k*m*s*y - d*h*i*p*s*y +
-%%      d*e*k*p*s*y - a*g*k*p*s*y + c*h*i*q*s*y - c*e*k*q*s*y +
-%%      c*h*j*m*t*y - c*f*k*m*t*y - c*h*i*n*t*y + c*e*k*n*t*y +
-%%      b*h*i*p*t*y - a*h*j*p*t*y - b*e*k*p*t*y + a*f*k*p*t*y -
-%%      c*g*j*m*u*y + c*g*i*n*u*y + d*f*i*p*u*y - b*g*i*p*u*y -
-%%      d*e*j*p*u*y + a*g*j*p*u*y - c*f*i*q*u*y + c*e*j*q*u*y)
-%% }
-
-\section{Questions for Tate/Nicole}
-%%\begin{itemize}
-%% \item How responsible am I for the papers I cite? Should I have read them, know their methodologies?
-%% \item Is it appropriate to cite web pages in a thesis? In a separate citation section? For images
-%% \item When is a fact ``common knowledge'' enough that it doesn't need a citation?
-%% \item Some papers have 'Request permission to reuse' links for figures - do I need to do this for copying figures?
-%% \item Is 25 pages too long for a thesis? What makes a thesis too long?
-%% \item What details belong in a thesis, and which are too much?
-ex going in-depth on what tests do, describing how we came up with guess numbers for parameter hunt, describing function of dynein in the cell, showing why motor proteins are necessary.
-%% \item Supplemental info?
-%%\end{itemize}
-
-\section{Questions for David}
-\begin{itemize}
-\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be?
-Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
-\item What is the value of $\left<\Delta G_{conf}\right>$ in going from bothbound to onebound?
-\end{itemize}
-
-\section{Todo for project}
-\begin{itemize}
-\item Do calculations to turn processivity into state time ratios
-\item Fit the state times to above number by tweaking un/binding rates
-\item Fit spring constants to step length histograms
-\end{itemize}
 \end{document}

### 2017-10-15 reorganize/papers/notes/notes.tex
Add PNAS template and new stepping velocity papers.

--- 2017-09-30 thesis_stuff/thesis_stuff.tex
@@
 
-\title{Dynein project log}
+\title{Dynein notes}
 \author{Elliott Capek}
@@
 
-\section{Equipartition Theorem}
-The Equipartition Theorem (ET) predicts the average energy per degree of freedom of a system with energy which depends on the square of each degree of freedom. Mathematically is is expressed as:
+\subsection{Calculating one/bothbound times of experimental dynein}
+In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\
+
+\newcommand\tbb{\left<t_{bb}\right>}
+\newcommand\tob{\left<t_{ob}\right>}
+\newcommand\tstep{\left<t_{step}\right>}
+\newcommand\tproc{\left<t_{processivity}\right>}
+\newcommand\kub{k_{ub}}
+\newcommand\kb{k_{b}}
+\newcommand\ko{k_{dis}}
+
+\begin{itemize}
+\item $\tbb$: Time in bothbound per step
+\item $\tob$: Time in onebound per step
+\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
+\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
+\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
+\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
+\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
+\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
+\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
+\end{itemize}
+
+$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:
 
 \begin{align*}
-  Z &= \int_{-\infty}^{\infty} e^{-\beta Ax^2}dx = \sqrt{\frac{\pi}{\beta A}}\\
-  <E> &= - \frac{d\ln Z}{d\beta} = -\left(\sqrt{\frac{\beta A}{\pi}}\right)\left(\frac{\sqrt{\beta A}}{2\sqrt{\pi}}\right)\frac{-\pi}{A\beta^2}\\
-  &= \frac{1}{2}k_BT\\
+  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
+  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
+  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
+  \tob &= \tstep-\tbb\\
+  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
+  &= \frac{\tstep^2}{\tstep+\tproc}\\
+  \frac\tob\tbb &= \frac{\tstep}{\tproc}
 \end{align*}
 
-where Z is the partition function and x a degree of freedom.\\
-
-For our model, each domain feels three separate forces:
-
-\textbf{Brownian forces}: Random forces due to water particle collisions. Gaussian-sampled with a
-variance $\sqrt{\frac{\gamma k_BT}{dt}}$. Brownian forces are somehow necessary for the ET energy
-to be realized.\\
-
-\textbf{Conformational forces}: Spring forces from the molecule deviating from its lowest-energy
-conformation. The energy from these forces is quadratic with respect to angle, and so each free
-angle should contribute to the average energy by ET.\\
-
-\textbf{Internal forces}. Tension forces (constraint forces) felt between domains which keep
-the protein rigid. These are not quadratic, so it is unclear how they contribute to energy!\\
-
-\subsection{Onebound case}
-The conformational forces are:\\
-\begin{align*}
-  |\vec{F_{ub}}| &\approx \frac{c_m\theta_{um}}{L_s}\\
-  |\vec{F_{um}}| &\approx \frac{c_m\theta_{um}}{L_s} + \frac{c_m\theta_{um}}{L_t} + \frac{c_t\theta_{t}}{L_t}\\
-  |\vec{F_{t}}| &\approx \frac{c_m\theta_{um}}{L_t} + 2\frac{c_t\theta_t}{L_t} + \frac{c_m\theta_{bm}}{L_t}\\
-  |\vec{F_{bm}}| &\approx \frac{c_t\theta_t}{L_t} + \frac{c_m\theta_{bm}}{L_t} + \frac{c_m\theta_{bm}}{L_s} + \frac{c_b\theta_{bb}}{L_s}\\
-  |\vec{F_{bb}}| &\approx \frac{c_m\theta_{bm}}{L_s} + \frac{c_b\theta_{bb}}{L_s}\\
-\end{align*}
-
-From this we can come up with rough order-of-magnitude estimates of the energy of each domain is:
-
-\begin{align*}
-  PE_{ub} &\approx \frac{c_m}{L_s}\theta_{um}^2 + \frac{c_m}{L_t}\theta_{um}^2\\
-  PE_{t} &\approx \frac{c_t}{L_t}\theta_{t}^2\\
-  PE_{bm} &\approx \frac{c_m}{L_s}\theta_{bm}^2 + \frac{c_m}{L_t}\theta_{bm}^2\\
-  PE_{bb} &\approx \frac{c_m}{L_s}\theta_{um}^2\\
-\end{align*}
-
-From this we can see that the conformational PE of each domain depends on different combinations of
-stalk/tail length and spring constants.
-
-\textbf{When is equipartition behaved?}
-It seems like ET should be behaved when we have an even balance of Brownian and conformational forces:
-
-\begin{align*}
-  F_{conf} &\approx F_{Brownian}\\
-  \frac{c}{L}\theta &\approx \sqrt{\frac{k_BT\gamma}{dt}}\\
-\end{align*}
-
-Is this reflected in our simulation? Well take a look at %% Fig ($\ref{fig:latent-heat}$)
-...
-
-%% \begin{figure}[h!]
-%%   \centering
-%%   \includegraphics[width=0.5\textwidth]{../figures/ob_equipartition_vs_force_ratio.pdf}
-%%   \caption{Onebound conformational energy follows equipartition best when the ratio of conformational
-%%   forces to Brownian forces is one.}
-%%   \label{fig:equipartition_vs_force_ratio}
-%% \end{figure}
-
-\section{Brownian motion}
-\subsection{Derivation} \label{sec:bmotion-derivation}
-We can derive the equation for the position of a particle using the simple Newtonian mechanics. We
-start with the general $2^{nd}$ law equation for a particle with random forces and drag (the
-Langevin equation). We then take the time-averages of all variables (using expectation value signs)
-to eliminate the effect of random Brownian forces. After some algebra we arrive at a differential
-equation for squared position. We solve it and simplify its expression for limits when $t >> \tau$
-and $t << \tau$.\\
-
-\begin{align*}
-  \frac{d\vec{v}}{dt} &= \frac{1}{m}\left(\frac{-mv}{\tau} + R\right)\\
-  \frac{d\vec{v}}{dt} &= \frac{-v}{\tau} + \frac{R}{m}\\
-  <\vec{r} \cdot \frac{d\vec{v}}{dt} > &+ \frac{1}{\tau}<\vec{r} \cdot \vec{v}> = 0\\
-  \frac{1}{2}\frac{d^2}{dt^2}(r^2) &+ \frac{1}{2\tau}\frac{d}{dt}(r^2) - v^2 = 0 \hspace{1cm} \Bigg(\mbox{b/c }\frac{d}{dt}\left(\vec{r} \cdot \vec{v}\right) = v^2 + \left(\vec{r} \cdot \frac{d\vec{v}}{dt}\right)
-  \mbox{ and }
-  \frac{d}{dt}\left(\vec{r} \cdot \vec{r}\right) = 2\left(\vec{r} \cdot \vec{v}\right) \Bigg)\\
-  \frac{d^2}{dt^2}(<r^2>) + &\frac{1}{\tau}\frac{d}{dt}(<r^2>) = 2<v^2> = \frac{6k_BT}{m} \hspace{1cm}\left(\mbox{Equipartition Theorem}\right)\\
-  <r^2> &= \frac{6k_BT\tau^2}{m}\left(e^{-t/\tau}-1+\frac{t}{\tau}\right)\\
-\end{align*}
-
-so...
-
-\begin{align*}
-  \left(t << \tau \right) \rightarrow <r^2> = \frac{3k_BT}{m}t^2 \hspace{2cm}\mbox{free particle motion}\\
-  \left(t >> \tau \right) \rightarrow <r^2> = \frac{6k_BT\tau}{m}t \hspace{2cm}\mbox{motion proportional to }\sqrt{t}\\
-\end{align*}
-
-\textbf{Averaging over time?}
-In the above derivation we use time averaging to eliminate the effect of Brownian forces. This is
-essentially just discussing the motion of a particle on a timescale where Brownian forces go to
-zero. The variance of the Brownian force R is:
-
-\begin{align*}
-  \sigma_R^2 &= \sqrt{\frac{2k_BTm}{\tau dt}}\\
-\end{align*}
-
-(TODO: further justify the dt in the variance)\\
-Thus over larger timescales (bigger dt's) the Brownian force is smaller. When time averaging, all
-we are saying is that our dt is large enough that Brownian forces are negligible.\\
-
-An interesting observation is that the motion equation for a particle feeling Brownian forces is
-identical to the equation for a macroscopic object feeling drag forces, which makes sense, since
-to solve the Brownian motion equation we just eliminate R.\\
-
-\section{Brownian dynamics}
-We use Brownian dynamics as our equation of motion. BD is just the special case of Langevin dynamics
-
-\begin{align*}
-  m\frac{d\vec{v}}{dt} &= -\frac{m}{\tau}\vec{v} + \vec{F} + \vec{R}\\
-\end{align*}
-
-where $m\rightarrow0$:
-
-\begin{align*}
-  \vec{v} &= \frac{\tau}{m}\vec{F} + \frac{\tau}{m}\vec{R}\\
-\end{align*}
-
-where m is the mass, $\tau$ the time constant, $\vec{F}$ a generic force and $\vec{R}$ the Brownian
-force. Mass ``going to zero'' means we are discussing particles where $m << $ any other variable.
-Because m is tiny the particle effectively has no net force on it, so the drag force must cancel
-out the other forces. From this we can find velocity.\\
-
-\subsection{What is $\tau$?}
-Tau is a time constant that describes the behavior of a system with respect to time. By looking at
-the motion equations for Brownian systems in Section (\ref{sec:bmotion-derivation}), we see that the
-size of t with respect to $\tau$ decides what type of motion the particle will feel. On the ``small''
-timescale the system displays free particle motion, but on the ``large'' timescale, the system
-displays Brownian motion. $\tau$ can be thought of as the time the system switches from free to
-Brownian motion.\\
-
-\section{Finding a reasonable dt}
-TODO: describe the relationship between diffusion constant D, time constant $\tau$ and dt.\\
-
-\subsection{Relating D to $\tau$}
-
-I don't really understand this derivation:
-
-\begin{align*}
-  \sin\left(\Delta\theta\right) &\approx \Delta\theta = \frac{x}{L}\\
-  \Delta\theta^2 &= \frac{x^2}{L^2} = \frac{Dt}{L^2}\\
-\end{align*}
-
-We set our $\tau$ to be the time when $<\Delta\theta^2> \approx 1$, so:
-
-\begin{align*}
-  \tau = \frac{L^2}{D}\\
-\end{align*}
-
-\subsection{Finding D}
-For a particle feeling Brownian forces:
-
-\begin{align*}
-  \frac{\Delta x}{\Delta t} &= \frac{\tau}{m} R\\
-\end{align*}
-
-We say the magnitude of R is the standard deviation of a Gaussian process:
-
-\begin{align*}
-  \frac{\Delta x}{\Delta t} &= \frac{\tau}{m}\sqrt{\frac{2k_BTm}{\tau \Delta t}}\\
-  \Delta x &= \sqrt{\frac{2k_BT\tau}{m\Delta t}}\Delta t\\
-  <\Delta x^2> &= \frac{2k_BT\tau}{m}\Delta t\\
-\end{align*}
-
-We then use the Brownian motion equation for $t >> \tau$ to find D:\\
-
-\begin{align*}
-  <\Delta x^2> &= D\Delta t = \frac{2k_BT\tau}{m}\Delta t\\
-  D = \frac{2k_BT\tau}{m} = \frac{2k_BT}{\gamma}\\
-\end{align*}
-
-\subsection{Alternative derivation of D (Einstein relation)}
-We can also arrive at an expression for D through an equilibrium argument. There are two forces which cause currents in solutions: drift and diffusion.
-Drift is motion due to a force acting on particles. Diffusion is current due to random, natural motions of particles. Our equilibrium condition is when
-the flux of particles due to both effects is equal, so there is no net particle flow. We first need to describe these fluxes:\\
-
-\textbf{Drift flux}\\
-Our particles obey Brownian dynamics, so $\gamma\dot{x} = F$, where $\gamma$ is the drag force constant. Flux J, or particles per second-area, can be
-found by multiplying the velocity of particles by the concentration $\rho$:
-
-\begin{align*}
-  J_{drift} &= \frac{1}{\gamma}F(x)\rho(x)\\
-  &= -\frac{1}{\gamma}\rho(x)\nabla U\\
-\end{align*}
-
-\textbf{Diffusion flux}\\
-Flux due to diffusion is proportional to the negative gradient in concentration and D:
-
-\begin{align*}
-  J_{diff} &= -D\nabla \rho(x)\\
-\end{align*}
-
-\textbf{Solving for D}\\
-The concentration gradient in a solution is proportional to the energy gradient. By the chain rule:
-
-\begin{align*}
-  \nabla \rho &= \frac{\partial\rho}{\partial U} \nabla U\\
-\end{align*}
-
-We then set the sum of our two fluxes to zero and solve for the equilibrium condition:
-
-\begin{align*}
-  J_{diff} + J_{drift} &= 0\\
-  -\frac{1}{\gamma}\rho(x)\nabla U - D\nabla \rho(x) &= 0\\
-  \frac{1}{\gamma}\rho(x)\nabla U + D \frac{\partial\rho}{\partial U} \nabla U&= 0\\
-  \left(\frac{1}{\gamma}\rho(x) + D\frac{\partial\rho}{\partial U}\right)\nabla U &= 0\\
-\end{align*}
-
-because $\nabla U$ is not guarenteed to be zero everywhere, it must be the case that:
-
-\begin{align*}
-  \frac{1}{\gamma}\rho(x) &= -D\frac{\partial\rho}{\partial U}\\
-  \frac{-\rho(x)}{\gamma\frac{\partial\rho}{\partial U}} &= D\\
-\end{align*}
-
-\textbf{Finding d$\rho$/dU}\\
-To simplify this value, we note that, because the particles do not interact, energy is purely a function of position. Thus, by
-Maxwell-Boltzman statistics, the probability of being at a location x (i.e $\rho(x)$) is proportional to $e^{-\beta U(x)}$.
-From this we can find an expression for concentration and d$\rho(x)/dU(x)$:
-
-\begin{align*}
-  \rho(x) &= Ae^{-\beta U(x)}\\
-  \frac{\partial \rho(x)}{\partial U} &= \frac{-1}{k_BT}Ae^{-\beta U(x)}\\
-\end{align*}
-
-Plugging these expressions into our D equation, in addition to our definition for $\gamma$, we can see that:
-
-\begin{align*}
-  \frac{-1}{\gamma\frac{-1}{k_BT}} &= D\\
-  D &= \frac{k_BT}{\gamma} = \frac{k_BT\tau}{m}\\
-\end{align*}
-
-\section{Equipartition Theorem for quadratic energies}
-\begin{align*}
-  Z &= \int_{-\infty}^{\infty} e^{-\beta Ax^2}dx = \sqrt{\frac{\pi}{\beta A}}\\
-  <E> &= - \frac{d\ln Z}{d\beta} = -\left(\sqrt{\frac{\beta A}{\pi}}\right)\left(\frac{\sqrt{\beta A}}{2\sqrt{\pi}}\right)\frac{-\pi}{A\beta^2}\\
-  &= \frac{k_BT}{2}\\
-\end{align*}
-
-\section{Gamma derivation}
-
-Stoke's Law states that the relationship between viscosity, force, and
-velocity for a spherical particle is given by:
-\begin{align}
-  \mathbf{v} &= \frac{\mathbf{F}}{6\pi \mu R}
-\end{align}
-where $\mu$ is the viscosity of the fluid, and $R$ is the radius of
-the particle.  Thus in our terminology:
-\begin{align}
-  \gamma &= 6\pi \mu R.
-\end{align}
-Note that the viscosity of water is temperature-dependent and around
-0.7~mPa~s at body temperature.  However, the viscosity of cytoplasm
-may be rather different, and will of course depend on length scale.
-But for our purposes we can probably get away with this value.
-
-The random force $\mathbf{R}(t)$ should have a Gaussian distribution
-with variance~1, but then be divided by $\sqrt{\Delta t}$.  Thus, the
-smaller the time step, the larger the random force we will apply.  We
-can understand this in the backwards direction.  When we observe a
-larger time step, the ``random force'' results from many smaller
-random forces added together, and these smaller forces often cancel,
-leading to this reduction in the total force over that time period.
-
-Finally, we will need estimates for the radii of each domain (to go
-into the $\gamma$ parameter, the equilibrium angles for each hinge, and
-the spring constants for each hinge.  The first two we can estimate
-from the structure of dynein.  The third will require a rough guess.
-We can get a ball-park guess by deciding how much we want the angle to
-fluctuate (e.g. $\ll \pi$ for each angle!), and then take our spring
-constant to be $kT$ divided by that anglular fluctuation squared.
-
-\section{Background of Correlation function}
-This is based on the Autocorrelation procedure (see Convolution on Wikipedia).
-In our correlation function code, we take the autocorrelation function of our
-potential and time-translate it to get the time at which there is zero correlation
-between the functions. Flesh this out sometime!\\
-
-\section{CLT (and/or Brownian distribution is Gaussian?) Derivation}
-Here we show that, given an initial PDF as a delta function $P(t_0,x) = \delta(x)$
-and any transition likelihood $W(s)$ for some step size s and 1 timestep, P
-eventually evolves into a Gaussian function.\\
-
-We use a discrete time, continuous position model:\\
-
-\begin{align}
-  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx
-\end{align}
-
-This matches the form of a convolution integral:
-
-\begin{align*}
-  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx
-\end{align*}
-
-By the Convolution Theorem (prove?) we can simplify the above expression:
-
-\begin{align}
-  F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
-  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)
-\end{align}
-
-We now let our initial time $t_0$ be zero and note that, because
-$W_n(\Delta x) = W(\Delta x)^n$, we can simplify our expression to:
-
-\begin{align}
-  \widetilde{P}(n,k) &= \widetilde{W}(k)^n\widetilde{P}(t_0,k)
-\end{align}
-
-We then take the Inverse Fourier Transform of this expression, yielding:
-
-\begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\widetilde{P}(n,k)e^{2\pi ikx}dk
-  = \int_{-\infty}^{\infty}\widetilde{W}(k)^n\widetilde{P}(t_0,k)e^{2\pi ikx}dk
-\end{align}
-
-Since $P(0,x)$ is a delta function, we know that $\widetilde{P}(0,x) = 1$, so:
-
-\begin{align}
-  P(n,x) &=  \int_{-\infty}^{\infty}\widetilde{W}(k)^ne^{2\pi ikx}dk
-\end{align}
-
-The Taylor Series for $\widetilde{W}(k)$ is:
-
-\begin{align*}
-  \widetilde{W}(k) &= \widetilde{W}(0) + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_3}(0) + ...\\
-  &= 1 + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_3}(0) ...\\
-\end{align*}
-
-We define a variable $\widetilde{W}$ such that:
-
-\begin{align*}
-  \widetilde{W}(k) &= 1 - \widetilde{C}\\
-  \widetilde{C} &= -(k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_3}(0) ...)\\
-\end{align*}
-
-This allows us to substitute in $\widetilde{C}$ and use the Binomial Expansion:
-
-\begin{align}
-  P(n,x) &=  \int_{-\infty}^{\infty}\left(1 - \widetilde{C}\right)^ne^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n {}_nC_\alpha\left(-\widetilde{C}\right)^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!(-1)^\alpha}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
-\end{align}
-
-The Taylor Series of our goal, the Gaussian function, is:\\
-
-\begin{align*}
-  e^{\frac{-x^2}{2\sigma^2}} &= \sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\left(\frac{x}{\sqrt{2}\sigma}\right)^{2\alpha}
-\end{align*}
-
-We want to make our expression for $P(n,x)$ resemble this. We begin by saying that, for sufficiently large $n$, the higher-order
-$\alpha$ terms in the sum go to zero due to the $1/\alpha!$. Thus, we can extend our sum to infinity:\\
-
-\begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
-\end{align}
-
-We then apply Sterling's Approximation in the form $Z! = e^{Z\ln(Z)-Z}$:
-
-\begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{e^{n\ln(n)-n}}{e^{(n-\alpha)\ln(n-\alpha)-(n-\alpha)}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk
-\end{align}
-
-Because n is large, we can get rid of its decaying exponentials and simplify:\\
-
-\begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}e^{\alpha}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\frac{n^\alpha}{(1-\frac{\alpha}{n})^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
-\end{align}
-
-%% We now use the following simplification, assuming that $\alpha/n < 1$:
-
-%% \begin{align*}
-%%   \left(1-\frac{\alpha}{n}\right)^{n-\alpha} &= \sum_{x=0}^{n-\alpha} \frac{(n-\alpha)!}{(n-\alpha-x)!x!} \left(\frac{\alpha}{n}\right)^x\\
-%%   &= 1 - (n-\alpha)\left(\frac{\alpha}{n}\right) + (n-\alpha)(n-\alpha-1)\left(\frac{\alpha}{n}\right)^2\\
-%%   &= 1 - \alpha + \frac{\alpha^2}{n} + \alpha^2 + \frac{-\alpha^3}{n} + \frac{-\alpha^2}{n} + \frac{-\alpha^3}{n} + \frac{\alpha^4}{n^2} + \frac{\alpha^3}{n^2}\\
-%%   &= 1 - \alpha + \alpha^2 + \frac{-2\alpha^3}{n} + \frac{\alpha^4}{n^2} + \frac{\alpha^3}{n^2}\\
-%% \end{align*}
-
-We then supply the middle factorial fraction with a name, $m = \frac{1}{(1-\frac{\alpha}{n})^{n-\alpha}}$:
-
-\begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{m(-1)^\alpha}{\alpha!}\sqrt{\frac{n\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk
-\end{align}
-
-\textbf{TODO: figure out why m is there}
-
-We then are \textit{almost} in a form where we can invert the Gaussian Taylor Expansion. We try it anyway, ignoring m. We also make the assumptions
-that our second $\widetilde{W}_1(0)$ Taylor Expansion term in $\widetilde{C}$ is zero and the third term is negative.\\
-
-\begin{align}
-  P(n,x) &= \int_{-\infty}^{\infty}e^{\frac{-k^2}{\sqrt{2}\frac{e}{|nW_2(0)|}}}e^{2\pi ikx}dk\\
-  &= \int_{-\infty}^{\infty}e^{\frac{-k^2}{\sqrt{2}\sigma^2}}e^{2\pi ikx}dk
-\end{align}
-
-We finally use the fact that Gaussians take the same form in real and Fourier space to undo the transform:
-
-\begin{align}
-  P(n,x) &= e^{\frac{-k^2}{\sqrt{2}\sigma^2}}\\
-\end{align}
-
-where
-
-\begin{align}
-  \sigma^2 = \frac{e}{n|W_2(0)|}\\
-\end{align}
-
-%% We then solve for $\widetilde{W}_2(0)$ to find our variance:
-
-%% \begin{align}
-%%   \widetilde{W}_2(0) &= \frac{d^2}{dk^2}\widetilde{W}(0)\\
-%%   &= \left(\frac{d^2}{dk^2}\int_{-\infty}^{\infty}W(x)e^{2\pi ikx}dx\right)_{k=0}\\
-%% \end{align}
-
-\section{Alternative CLT Derivation}
-Here we show that, given an initial PDF as a delta function $P(t_0,x) = \delta(x)$
-and any transition likelihood $W(s)$ for some step size s and 1 timestep, P
-eventually evolves into a Gaussian function.\\
-
-We use a discrete time, continuous position model:\\
-
-\begin{align}
-  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx
-\end{align}
-
-This matches the form of a convolution integral:
-
-\begin{align*}
-  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx
-\end{align*}
-
-By the Convolution Theorem (prove?) we can simplify the above expression:
-
-\begin{align}
-  F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
-  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)
-\end{align}
-
-We see that in general, the transformed probability distribution after n
-timsteps is given by:\\
-
-\begin{align}
-  \widetilde{P}(t_0+n,k) &= \widetilde{W}(k)\widetilde{P}(t_0+n-1,k)
-\end{align}
-
-Thus our distribution after n timesteps can be expressed as:
-
-\begin{align}
-  \widetilde{P}(t_0+n,k) &= \widetilde{W}^n(k)\widetilde{P}(t_0,k)
-\end{align}
-
-We wish to solve for the non-transformed probability distribution, so we
-apply the inverse Fourier Transform:
-
-\begin{align}
-  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}\widetilde{W}^n(k)\widetilde{P}(t_0,k)e^{ikx}dk
-\end{align}
-
-We specified our initial probability as a delta function, which Fourier Transforms to unity:
-
-\begin{align}
-  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}\widetilde{W}^n(k)e^{ikx}dk
-\end{align}
-
-We now introduce a new definition $\widetilde{W} = e^{\widetilde{L}}$:\\
-
-\begin{align}
-  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{n\widetilde{L}}e^{ikx}dk
-\end{align}
-
-We now need to expand $\widetilde{L}$. We use a Taylor Series:
-
-\begin{align*}
-  \widetilde{L}(k) &= \ln(\widetilde{W}) = \sum\frac{k^n\frac{d^n}{dk^n}\ln(\widetilde{W})}{n!}\\
-  &= \ln\left(\widetilde{W}(0)\right) + k\frac{\widetilde{W}_1(0)}{\widetilde{W}(0)}
-  + \frac{k^2}{2}\left(\frac{\widetilde{W}_2(0)}{\widetilde{W}(0)} - \frac{\widetilde{W}_1(0)^2}{\widetilde{W}_0(0)^2}\right)
-  + \frac{k^3}{6}\left(\frac{2\widetilde{W}_1(0)^3}{\widetilde{W}_(0)^3} + \frac{\widetilde{W}_3(0)}{\widetilde{W}(0)}
-     - \frac{3\widetilde{W}_1(0)\widetilde{W}_2(0)}{\widetilde{W}(0)^2}\right)\\
-  &+ \frac{k^4}{24}\left(\frac{6\widetilde{W}_1(0)^2\widetilde{W}_2(0)}{\widetilde{W}(0)^3} - \frac{6\widetilde{W}_1(0)^4}{\widetilde{W}(0)^4}
-  - \frac{3\widetilde{W}_2(0)^2}{\widetilde{W}(0)^2} - \frac{3\widetilde{W}_1(0)\widetilde{W}_3(0)}{\widetilde{W}(0)^2}
-  + \frac{6\widetilde{W}_1(0)^2\widetilde{W}_2(0)}{\widetilde{W}(0)^3} + \frac{\widetilde{W}_4(0)}{\widetilde{W}(0)}
-  - \frac{\widetilde{W}_1(0)\widetilde{W}_3(0)}{\widetilde{W}(0)^2}\right) + O(5)
-\end{align*}
-
-We then make the following assumption: \textbf{Assume all odd terms in $\widetilde{W}$'s expansion are zero}. We justify this by imposing that
-$\widetilde{W}$ must be symmetric about the y-axis. We also say that $\widetilde{W}_1(0)=1$, which I don't know how to justify -- (just because
-W is normalized to one doesn't mean its maximum point equals one?). These assumptions allow us to simplify $\widetilde{L}$:\\
-
-\begin{align*}
-  \widetilde{L}(k) &= \frac{k^2}{2}\widetilde{W}_2(0) + \frac{k^4}{24}\left(\widetilde{W}_4(0) - 3\widetilde{W}_2(0)\right)
-\end{align*}
-
-I'm not really sure how to justify this part either:
-
-\begin{align}
-  \widetilde{L}(k) &\approx \frac{k^2}{2}\widetilde{W}_2(0)
-\end{align}
-
-We then plug this into our definition for $P(t_0+n,k)$:
-
-\begin{align}
-  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{n\frac{k^2}{2}\widetilde{W}_2(0)}e^{ikx}dk
-\end{align}
-
-In order to be normalizable, all derivatives of $\widetilde{W}$ must be negative. Thus we rewrite
-$\widetilde{W}_2$:
-
-\begin{align}
-  P(t_0+n,k) &= \frac{1}{2\pi}\int_{-\infty}^{\infty}e^{-n\frac{k^2}{2}|\widetilde{W}_2(0)|}e^{ikx}dk
-\end{align}
-
-This takes the form of a Gaussian. We know that Gaussians are invariant under Fourier Transform,
-so:\\
-
-\begin{align}
-  P(t_0+n,k) &= e^{\frac{k^2}{2\sigma^2}}
-\end{align}
-
-where $\sigma = \sqrt{\frac{1}{n\widetilde{W}_2(0)}}$. As expected by the CLT, the standard deviation of our
-new probability depends on $\frac{1}{\sqrt{n}}$!\\
-
-We now try and find more out about $|\widetilde{W}_2(k)|$:
-
-\begin{align*}
-  \widetilde{W}_2(k) &= \frac{d^2}{dk^2}\widetilde{W}(k)\\
-  &= \frac{d^2}{dk^2}\int_{-\infty}^\infty W(x)e^{-ikx}dx\\
-  &= \frac{d}{dk}\int_{-\infty}^\infty -ixW(x)e^{-ikx}dx\\
-  &= -\int_{-\infty}^\infty x^2W(x)e^{-ikx}dx\\
-\end{align*}
-
-We are specifically interested in the case where $k=0$:
-
-\begin{align*}
-  \widetilde{W}_2(0) &= -\int_{-\infty}^\infty x^2W(x)dx
-\end{align*}
-
-We explicitly denote $\widetilde{W}_2$'s negativity:
-
-\begin{align*}
-  |\widetilde{W}_2(0)| &= \int_{-\infty}^\infty x^2W(x)dx
-\end{align*}
-
-and finally note that, since W is the transition probability per timestep, this looks like the expected squared deviation in a single timestep:
-
-\begin{align*}
-  |\widetilde{W}_2(0)| &= \int_{-\infty}^\infty x^2W(x)dx = <\Delta x>
-\end{align*}
-
-We plug this back into our Gaussian to get our final answer:
-
-\begin{align}
-  P(t_0+n,k) &= e^{\frac{k^2}{2\frac{1}{n<\Delta x>}}}
-\end{align}
-
-A $\sigma = \sqrt{\frac{1}{n<W>}}$ does not make sense. For one, $\sqrt{<\Delta x>}$ should be in the numerator, since it is the
-single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
-$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...\\
-\\
-
-\section{Un/binding constants}
-We let our un/binding rates $k_b$ and $k_u$ be, according to the Arrhenius equation:
-
-\begin{align}
-  k_b &= A_be^{\Delta G_{u\rightarrow b}\beta}\\
-  k_u &= A_ue^{\Delta G_{b\rightarrow u}\beta}
-\end{align}
-
-Our Gibb's free energy changes are given as functions of angular state $\theta$:
-
-\begin{align}
-  \Delta G_{u\rightarrow b}(\theta) &= \sum_i \frac{1}{2}c_{bi}\Delta\theta_{bi}^2 - \sum_i \frac{1}{2}c_{ui}\Delta\theta_{ui}^2 + G_{bind}\\
-  \Delta G_{u\rightarrow b}(\theta) &= \sum_i \frac{1}{2}c_{ui}\Delta\theta_{ui}^2 - \sum_i \frac{1}{2}c_{bi}\Delta\theta_{bi}^2 + G_{unbind}\\
-\end{align}
-
-\section{Equipartition Theorem}
-Both bothbound and onebound states show good agreement with the equipartition theorem. Horizontal dashed line represents Equipartition Thorem energy $\frac{1}{2}k_BT$.
-
-\begin{figure}[h!]
+Thus, by the above equations and data from various sources, estimates on $\tbb$ and $\tob$ can be made.\\
+
+\begin{figure}[h]
   \centering
-
-  \begin{minipage}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
-    \caption{Onebound PE vs time.}
-  \end{minipage}
-  \begin{minipage}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
-    \caption{Bothbound PE vs time.}
-  \end{minipage}
-  \label{fig:equipartition_agreement}
+  \begin{tabular}{| c | c | c | c | c | c | c |}
+    \hline
+    Source & Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
+    Weihong 2012 GST-dimerized & 134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+    Higuchi 2006 & 800nm/s &  &  &   &   & \\ \hline
+    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s &  & 0.011s & 1s    & 0.011s & 1.3e-4\\ \hline
+    Schroer 2000 native 2mM ATP w/ 210nm beads + dynactin & 700nm/s &  & 0.011s & 2.14s & 0.011s & 6e-5\\ \hline
+    Vale    2006 GST-dimerized 1mM + qdots                & 87 nm/s &  & 0.09s  & 13.8s & &\\ \hline
+    Schroer 2000 organic dye-labelled full-length dynein & 120nm/s &  &  &  &  & \\ \hline
+
+  \end{tabular}
+  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
+  \label{table:time-parameter-table}
 \end{figure}
@@
   \centering
-  \includegraphics[width=.45\textwidth]{../figures/equilibrium-onebound}
+  \includegraphics[width=.45\textwidth]{figures/equilibrium-onebound}
   \caption{Definition of equilibrium angles.}
@@
 This means that the MT-bound to unbound ratio is related to how far the motor can walk.
-Thus, tuning k_b and k_ub may be a way to alter dynein processivity.\\
+Thus, tuning $k_b$ and $k_ub$ may be a way to alter dynein processivity.\\
 
@@
 
-Figure~\ref{fig:em_tomography_eq_angles} shows different measurements
-for equilibrium angles from the data in this paper.
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=.45\textwidth]{../figures/Post_powerstroke_tomography.jpg}
-  \includegraphics[width=.45\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
-  \caption{Post- and Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
-  \label{fig:em_tomography_eq_angles}
-\end{figure}
+%% Figure~\ref{fig:em_tomography_eq_angles} shows different measurements
+%% for equilibrium angles from the data in this paper.
+%% \begin{figure}[h!]
+%%   \centering
+%%   \includegraphics[width=.45\textwidth]{../figures/Post_powerstroke_tomography.jpg}
+%%   \includegraphics[width=.45\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
+%%   \caption{Post- and Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
+%%   \label{fig:em_tomography_eq_angles}
+%% \end{figure}
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=.45\textwidth]{../figures/axonemal-motor-angles.jpg}
-  \caption{Angle histograms from EM microscopy on axonemal (not cytoplasmic) dynein.}
-  \label{fig:EM-angles-burgess}
-\end{figure}
+%% \begin{figure}[h!]
+%%   \centering
+%%   \includegraphics[width=.45\textwidth]{../figures/axonemal-motor-angles.jpg}
+%%   \caption{Angle histograms from EM microscopy on axonemal (not cytoplasmic) dynein.}
+%%   \label{fig:EM-angles-burgess}
+%% \end{figure}
 

### 2017-10-15 reorganize/papers/paper/paper.tex
Add PNAS template and new stepping velocity papers.

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} = Template for a one-column mathematics article
% {pnasinvited} = Template for a PNAS invited submission

\title{Dynein walks like an Imperial AT-ST}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,c,1]{Author One}

\affil[a]{Oregon State University}

% Please give the surname of the lead author for the running footer
\leadauthor{Lead author last name}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any conflict of interest here.}
\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{dynein $|$ Brownian dynamics $|$ powerstroke $|$ modeling}

\begin{abstract}
Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

\dropcap{D}ynein is a motor protein used to generate directed force in cells. The protein is a homodimer which binds to cellular filaments known as microtubules (MTs). Each monomer uses ATP hydrolysis to step along the MT. ... \\

Compared to other motors kinesin and myosin, dynein is unique in that it has a widely varied step size. Dynein's average step is 8nm in the forwards direction, but it is capable of taking 32nm steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.

\subsubsection*{SI Figures}

Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.
Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.

% \pnasbreak splits and balances the columns before the references.
% If you see unexpected formatting errors, try commenting out this line
% as it can run into problems with floats and footnotes on the final page.
\pnasbreak

\bibliography{paper}

\end{document}

### 2017-10-16 reorganize/papers/paper/paper.tex
minor changes to paper.

@@
 The protein is a homodimer which binds to cellular filaments known as microtubules (MTs).
-Each monomer uses ATP hydrolysis to step along the MT.
-...
-\\
+Each monomer has several ATPase domains arranged in a larger globular domain known as the head.
+This head is the site which hydrolyzes ATP and undergoes the conformational changes responsible for dynein's step.
+The head is attached via a long chain to the microtubule binding domain (MTBD).
+Dynein is an interesting structure in that it manages to coordinate ATPase chemistry at its head with MT-releasing chemistry at its MTBD, some 20nm away \cite{mt-atp-coupling}.
+The head has a long tail domain coming off it, which eventually dimerizes to the other monomer.\\
 
-Compared to other motors kinesin and myosin, dynein is unique in that it has a widely varied step size.
-Dynein's average step is 8nm in the forwards direction, but it is capable of taking 32nm steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.
+Dynein is unique in that it has a widely varied step size.
+Dynein's average step is 8 \textit{nm} in the forwards direction, but it is capable of taking 32 \textit{nm} steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.
+This stochastic, varied stepping is contrasted with the much more regular 8 \textit{nm} step size of kinesin, another bipedal motor protein \cite{kinesin-step-size}.
+It has been suggested that dynein's long separation between its head
+
+Dynein is known to change stepping behavior and direction as a response to forwards or backwards load \cite{responsetoload}.
 
@@
 
-Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.
-Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Mauris in aliquet quam, a cursus orci.
+Fusce vitae faucibus tortor, vel molestie nibh.
+Proin condimentum cursus mollis.
+Praesent euismod ligula sit amet libero elementum, sed commodo velit suscipit.
+Integer sed nisl vitae nibh dapibus sagittis.
+Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Nullam et semper sem.
+Nulla fringilla lacus quis justo tincidunt venenatis.
+Vestibulum aliquet ante diam, nec accumsan augue rutrum id.
+Nam sollicitudin magna vitae mauris pellentesque, et rhoncus felis accumsan.\\
+
+Etiam ullamcorper elit a interdum molestie.
+Phasellus aliquam nulla nec orci sodales, sit amet bibendum odio pulvinar.
+Nullam at pulvinar lectus.
+Nulla facilisi.
+Phasellus ut magna ut nunc vehicula posuere non ac ligula.
+Nulla facilisi.
+Duis ultrices ornare turpis, eget tempus mauris pulvinar interdum.\\
+
+Curabitur eget nisi tellus.
+Nullam bibendum et dolor et rutrum.
+Sed tincidunt quam nec laoreet tincidunt.
+Etiam quam erat, tempus in posuere eget, pellentesque vel ex.
+Nunc non turpis sagittis, condimentum ante porttitor, pulvinar risus.
+Proin sodales, odio vel efficitur porta, nunc ligula ornare leo, ut lobortis elit ante bibendum mauris.
+Sed molestie nisl at elit efficitur interdum.\\
+
+Nam ultricies efficitur nunc, in tristique tellus auctor vitae.
+Aliquam ante leo, varius a ante sit amet, pretium efficitur elit.
+Nulla suscipit, nunc eget mollis blandit, nulla lorem venenatis ipsum, lobortis ultricies leo justo eu diam.
+Proin fringilla, purus non hendrerit vulputate, eros est ultrices massa, vel faucibus mi risus ac magna.
+Ut varius justo maximus finibus aliquam.
+Nullam rutrum vestibulum eros sed accumsan.
+Vestibulum a porttitor urna, porttitor tempus sem.
+Quisque dapibus aliquam pulvinar.
+Fusce vehicula nisl a tellus semper vulputate.\\
+
+Nunc lobortis, tellus sit amet interdum maximus, justo elit faucibus turpis, quis volutpat magna lorem id purus.
+Donec urna erat, semper non egestas eget, sodales at quam.
+Etiam interdum tincidunt purus, eu tempor mauris consequat consequat.
+Aenean feugiat sapien enim, et cursus sem ultrices vitae.
+Vivamus enim purus, malesuada sit amet turpis sed, porta consequat tellus.
+Orci varius natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+Aenean vitae nisl convallis, venenatis magna et, aliquet sem.
+Proin diam est, rutrum at auctor vel, gravida nec magna.
+Aliquam erat volutpat.
+Nunc eu tempus ex.
+Praesent eget aliquam metus, ut faucibus sapien.
+Donec porttitor, dolor et accumsan volutpat, est neque sagittis libero, eu lobortis lacus lorem sed diam.\\
 

### 2017-10-17 reorganize/papers/paper/paper.tex
Add introduction to PNAS template.

--- 2017-10-15 reorganize/papers/paper/paper.tex
@@
 The protein is a homodimer which binds to cellular filaments known as microtubules (MTs).
-Each monomer uses ATP hydrolysis to step along the MT.
-...
-\\
+Each monomer has several ATPase domains arranged in a larger globular domain known as the ``head''.
+This head is the site which hydrolyzes ATP and undergoes the conformational changes responsible for dynein's step.
+The head is attached via a long chain to the microtubule binding domain (MTBD).
+Dynein is an interesting structure in that it manages to coordinate ATPase chemistry at its head with MT-releasing chemistry at its MTBD, some 20nm away \cite{mt-atp-coupling}.
+The head has a long tail domain coming off it, which eventually dimerizes to the other monomer.\\
 
-Compared to other motors kinesin and myosin, dynein is unique in that it has a widely varied step size.
-Dynein's average step is 8nm in the forwards direction, but it is capable of taking 32nm steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.
+Dynein is unique in that it has a widely varied step size.
+Dynein's average step is 8 \textit{nm} in the forwards direction, but it is capable of taking 32 \textit{nm} steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.
+This stochastic, varied stepping is contrasted with the much more regular 8 \textit{nm} step size of kinesin, another bipedal motor protein \cite{kinesin-step-size}.
+It has been suggested that the long separation between dynein's MTBD and dimerization sites facilitates larger diffusive searches, allowing dynein to take larger steps than kinesin \cite{cargotransport}.\\
 
-\subsubsection*{SI Figures}
+A simple explanation for dynein's stepping pattern can be given based on only a few facts about the protein.
+It is known that on treatment with ATP, the tail-head-MTBD angle of a dynein monomer alters, moving the MTBD closer to the tail \cite{carteradpprimed} \cite{burgess-paper}.
+It is also known that the nucleotide state of the head communicates with the MTBD.
+ATP binding at a head ATPase shifts the MTBD from a strong to weak MT-bound state.
+And vice-versa, whether the MTBD is bound or unbound from the MT changes the ATPase rate at the head.
+From this it is possible to infer a simple model for the dynein stepping cycle.
+This model, known as the mechanochemical cycle \cite{cianfroccoreview}, has dynein unbind MT, kick forward, diffuse to the next MT binding site, rebind MT, then repeat.
+Whether a model this simple can explain dynein's behavior needs to be tested.\\
 
-Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.
-Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.Provide a brief legend for each supporting figure after the supporting text.
-Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text.
-When saving TIFF files, use only LZW compression; do not use JPEG compression.
-Do not save figure numbers, legends, or author names as part of the image.
-Composite figures must be pre-assembled.
+There are many relevant details about dynein which this simple model doesn't account for.
+Dynein is known to have low interhead communication at low separation, but to have a tension-gated stepping pattern at high separations \cite{yildizpaper}.
+It is also suggested that dynein's MTBD doesn't conduct an undirected search for its next MT binding site, but rather is guided by long-range electrostatic interactions from each MT binding site \cite{longrangemt}.
+Dynein has several cofactors which alter its dynamics.
+For example, the motor's stall force is tripled when exposed to dynactin and Bic2D \cite{yildizdynactin}.
+This is odd, since the dynactin- and Bic2D-binding site on dynein is on the tail, far from the motor heads.
+Many of these details suggest a complicated picture of dynein motility than a simple forward kick and pull mechanism.\\
+
+Several computational models have been created to explain dynein's motility.
+\textit{Imamula et.
+al.} define a chemical transition model which defines all the MT- and nucleotide-bound states dynein goes through as it walks \cite{imamulamodel}.
+\textit{Sarlah et.
+al} simulate a model obeying rate constants from \textit{Imamula}, and replicate dynein's stepping trajectory \cite{sarlahmodel}.
+\textit{Zheng} uses normal mode analysis to simulate the dynein motor's transition from pre to post-powerstroke \cite{normalmodes}.
+To our knowledge, no computational model exists which takes into account the microscopic dynamics of protein-water interactions to test whether diffusion is enough for dynein motility.
+Here we show how a simple Brownian dynamics model can be used to test the mechanochemical cycle picture of dynein processivity.\\
 

### 2017-10-17 reorganize/papers/paper/pnas-template-main.tex
Make elliott-thesis make?

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} = Template for a one-column mathematics article
% {pnasinvited} = Template for a PNAS invited submission

\title{Template for preparing your research report submission to PNAS using Overleaf}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,c,1]{Author One}
\author[b,1,2]{Author Two} 
\author[a]{Author Three}

\affil[a]{Affiliation One}
\affil[b]{Affiliation Two}
\affil[c]{Affiliation Three}

% Please give the surname of the lead author for the running footer
\leadauthor{Lead author last name}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any conflict of interest here.}
\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}

\begin{abstract}
Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{T}his PNAS journal template is provided to help you write your work in the correct journal format.  Instructions for use are provided below.

Note: please start your introduction without including the word ``Introduction'' as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.

\section*{Guide to using this template on Overleaf}

Please note that whilst this template provides a preview of the typeset manuscript for submission, to help in this preparation, it will not necessarily be the final publication layout. For more detailed information please see the \href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information for Authors}.

If you have a question while using this template on Overleaf, please use the help menu (``?'') on the top bar to search for \href{https://www.overleaf.com/help}{help and tutorials}. You can also \href{https://www.overleaf.com/contact}{contact the Overleaf support team} at any time with specific questions about your manuscript or feedback on the template.

\subsection*{Author Affiliations}

Include department, institution, and complete address, with the ZIP/postal code, for each author. Use lower case letters to match authors with institutions, as shown in the example. Authors with an ORCID ID may supply this information at submission.

\subsection*{Submitting Manuscripts}

All authors must submit their articles at \href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you are using Overleaf to write your article, you can use the ``Submit to PNAS'' option in the top bar of the editor window.

\subsection*{Format}

Many authors find it useful to organize their manuscripts with the following order of sections;  Title, Author Affiliation, Keywords, Abstract, Significance Statement, Results, Discussion, Materials and methods, Acknowledgments, and References. Other orders and headings are permitted.

\subsection*{Manuscript Length}

PNAS generally uses a two-column format averaging 67 characters, including spaces, per line. The maximum length of a Direct Submission research article is six pages and a PNAS PLUS research article is ten pages including all text, spaces, and the number of characters displaced by figures, tables, and equations.  When submitting tables, figures, and/or equations in addition to text, keep the text for your manuscript under 39,000 characters (including spaces) for Direct Submissions and 72,000 characters (including spaces) for PNAS PLUS.

\subsection*{References}

References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric}. All references, including for the SI, should be included in the main manuscript file. References appearing in both sections should not be duplicated.  SI references included in tables should be included with the main reference section.

\subsection*{Data Archival}

PNAS must be able to archive the data essential to a published article. Where such archiving is not possible, deposition of data in public databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata, and others outlined in the Information for Authors, is acceptable.

\subsection*{Language-Editing Services}
Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at www.pnas.org/site/authors/language-editing.xhtml). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{frog}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:frog}
\end{figure}

\subsection*{Digital Figures}
\label{sec:figures}

Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for figures that will appear in the main text, and images must be final size. Authors may submit U3D or PRC files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format.  Color images must be in RGB (red, green, blue) mode. Include the font files for any text.

Figures and Tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

Figure \ref{fig:frog} shows an example of how to insert a column-wide figure. To insert a figure wider than one column, please use the \verb|\begin{figure*}...\end{figure*}| environment. Figures wider than one column should be sized to 11.4 cm or 17.8 cm wide.

\subsection*{Single column equations}

Authors may use 1- or 2-column equations in their article, according to their preference.

To allow an equation to span both columns, options are to use the \verb|\begin{figure*}...\end{figure*}| environment mentioned above for figures, or to use the \verb|\begin{widetext}...\end{widetext}| environment as shown in equation \ref{eqn:example} below.

Please note that this option may run into problems with floats and footnotes, as mentioned in the \href{http://texdoc.net/pkg/cuted}{cuted package documentation}. In the case of problems with footnotes, it may be possible to correct the situation using commands \verb|\footnotemark| and \verb|\footnotetext|.

%% Do not use widetext if paper is in single column.
\begin{widetext}
\begin{align*}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \numberthis \label{eqn:example} \\
       &=x^3+3x^2y+3xy^3+x^3. 
\end{align*}
\end{widetext}

\begin{table}%[tbhp]
\centering
\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
\begin{tabular}{lrrr}
Species & CBS & CV & G3 \\
\midrule
1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
\bottomrule
\end{tabular}

\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

\subsection*{Supporting Information (SI)}

The main text of the paper must stand on its own without the SI. Refer to SI in the manuscript at an appropriate point in the text. Number supporting figures and tables starting with S1, S2, etc. Authors are limited to no more than 10 SI files, not including movie files. Authors who place detailed materials and methods in SI must provide sufficient detail in the main text methods to enable a reader to follow the logic of the procedures and results and also must reference the online methods. If a paper is fundamentally a study of a new method or technique, then the methods must be described completely in the main text. Because PNAS edits SI and composes it into a single PDF, authors must provide the following file formats only.

\subsubsection*{SI Text}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a PDF with the same file name for visual reference).

\subsubsection*{SI Figures}

Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.

\subsubsection*{3D Figures}

Supply a composable U3D or PRC file so that it may be edited and composed. Authors may submit a PDF file but please note it will be published in raw format and will not be edited or composed.

\subsubsection*{SI Tables}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a PDF with the same file name for visual reference); include only one table per file. Do not use tabs or spaces to separate columns in Word tables.

\subsubsection*{SI Datasets}

Supply Excel (.xls), RTF, or PDF files. This file type will be published in raw format and will not be edited or composed.

\subsubsection*{SI Movies}

Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media (wmv), animated GIF (gif), or MPEG files and submit a brief legend for each movie in a Word or RTF file. All movies should be submitted at the desired reproduction size and length. Movies should be no more than 10 MB in size.

\subsubsection*{Still images}

Authors must provide a still image from each video file. Supply TIFF, EPS, high-resolution PDF, JPEG, or GIF files.

\subsubsection*{Appendices}

PNAS prefers that authors submit individual source files to ensure readability. If this is not possible, supply a single PDF file that contains all of the SI associated with the paper. This file type will be published in raw format and will not be edited or composed.

\matmethods{Please describe your materials and methods here. This can be more than one paragraph, and may contain subsections and equations as required. Authors should include a statement in the methods section describing how readers will be able to access the data in the paper.

\subsection*{Subsection for Method}
Example text for subsection.
}

\showmatmethods % Display the Materials and Methods section

\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}

\showacknow % Display the acknowledgments section

% \pnasbreak splits and balances the columns before the references.
% If you see unexpected formatting errors, try commenting out this line
% as it can run into problems with floats and footnotes on the final page.
\pnasbreak

% Bibliography
\bibliography{pnas-sample}

\end{document}

### 2017-10-17 reorganize/scripts/generate-exploration-data.py

@@ -10,7 +10,7 @@ basename  = run.sim(**{"k_b": 1e15,
                        "cb": 0.4,
                        "cm": 1.3,
                        "ct": 0.5,
-                       "dt": 1e-10, "label": l, "seed": 1, "runtime": 5e-2,
+                       "dt": 1e-10, "label": l, "seed": 1, "runtime": 1e-3,
                        "framerate": 1e-8, "constant-write": True,
                        "no-slurm": True})
 

### 2017-10-21 reorganize/papers/notes/notes.tex
Add schmidt paper to notes.tex

@@
 \section{Papers}
+\subsection{Structure of human cytoplasmic dynein-2 primed for its power stroke}
+Schmidt, Carter et al\\
+
+Paper on crystallizing dynein-2 (cytoplasmic) with and without ADP-Vanadate to find the pre- and post-powerstroke structures.
+They find a different foot-head-tail angle than the Burgess paper (possibly because Burgess crystallized axonemal dynein).
+Burgess found a ~20 degree shift for axonemal, and schmidt found a 90 degree shift in angle on pre-stroking.\\
+
 \subsection{Tension on the Linker Gates the ATP-Dependent Release of Dynein from Microtubules - Yildiz 2014}

### 2017-10-30 reorganize/papers/notes/notes.tex
Notes: Add paper about how our model should currently step in the proper direction

@@
+\errorstopmode
+
 \documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt
@@
 \section{Papers}
+\subsection{Paper on our model stepping in the proper direction given our angle scheme}
+Figure 7 of 'Three-dimensional structure of cytoplasmic dynein bound to microtubules' shows a cartoon interpretation of a dynein-MT crystal structure indicating that a model which has its tail-load towards the + end will step towards the - end of the MT.\\
+
 \subsection{Structure of human cytoplasmic dynein-2 primed for its power stroke}

### 2017-11-07 reorganize/papers/notes/notes.tex
Add two new papers to notes.tex.

@@
 \section{Papers}
+\subsection{Native dynein cryo-EM structure}
+Full structure of dynein.\\
+
+\subsection{HC dimerization}
+The structure of the dynactin complex and its interaction with dynein -- stuff about HC dimerization, NOT structure\\
+
+Structure of dynactin-dynein.
+Paper says that ct is pretty loose; loose enough that the angle can rotate 180 to take on the in-vivo state (originally the two motors are 180 degrees apart, but rotate to be parallel).
+It seems that there is only one dimerization domain at the very N-term of the heavy chain (1-178).\\
+
+Paper says that dynactin may work by separating the two HCs, allowing them to take on an active, bipedal legs-unlocked conformation.
+Perhaps without this, the two HC legs wrap around each other, or somethign.\\
+
 \subsection{Paper on our model stepping in the proper direction given our angle scheme}

### 2017-11-07 reorganize/papers/paper/supplemental-figs.tex
Add supplemental figures doc with one model figure.

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\begin{document}

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-1-cryoem}
   \caption{AAAAAAAA}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-1-superimposed}
   \caption{AAAAAAAA}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-1-model}
   \caption{AAAAAAAA}
   \label{fig:explengths}
 \end{minipage}
 \begin{minipage}{.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/ob_fig}
   \caption{AAAAAAAA}
   \label{fig:modangles}
 \end{minipage}%
 \begin{minipage}{.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/ob_fig}
   \caption{AAAAAAAA}
   \label{fig:expangles}
 \end{minipage}
\caption{\textbf{Experimental values used to determine model parameters.}}
\label{fig:modelparams}
\end{figure}

\end{document}

### 2017-11-07 reorganize/papers/paper/supplemental-figs.tex
Add another subfigure to supplemental-figs.pdf

@@
    \includegraphics[width=\linewidth]{figures/schematic-1-cryoem}
-   \caption{AAAAAAAA}
    \label{fig:modlengths}
@@
    \includegraphics[width=\linewidth]{figures/schematic-1-superimposed}
-   \caption{AAAAAAAA}
    \label{fig:modlengths}
@@
    \includegraphics[width=\linewidth]{figures/schematic-1-model}
-   \caption{AAAAAAAA}
    \label{fig:explengths}
  \end{minipage}
- \begin{minipage}{.5\textwidth}
+ %
+ \begin{minipage}{.3\textwidth}
    \centering
-   \includegraphics[width=\linewidth]{figures/ob_fig}
-   \caption{AAAAAAAA}
-   \label{fig:modangles}
+   \includegraphics[width=\linewidth]{figures/schematic-2-cryoem}
+   \label{fig:modlengths}
  \end{minipage}%
- \begin{minipage}{.5\textwidth}
+ \begin{minipage}{.3\textwidth}
    \centering
-   \includegraphics[width=\linewidth]{figures/ob_fig}
-   \caption{AAAAAAAA}
-   \label{fig:expangles}
+   \includegraphics[width=\linewidth]{figures/schematic-2-superimposed}
+   \label{fig:modlengths}
+ \end{minipage}%
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-2-model}
+   \label{fig:explengths}
  \end{minipage}
-\caption{\textbf{Experimental values used to determine model parameters.}}
+\caption{\textbf{Model schematic superimposed on cryo-EM images of native dynein.} Native cryo-EM images of the full dimerized dynein complex composed of light, intermediate and heavy chains, from \cite{nativestructure}.
+Model schematics are superimposed for illustrative purpose; shown angles to not represent expected \textit{in vivo} equilibria.
+Schematics are shown docked to a microtubule for illustrative purposes.}
 \label{fig:modelparams}

### 2017-11-07 reorganize/papers/paper/supplemental-figs.tex
Add another supplemental figure on equilibrium angles.

@@
 \usepackage{graphicx}
+\usepackage[margin=0.5in]{geometry}
 
@@
 
+\begin{figure}%[tbhp]
+\centering
+ \begin{minipage}{0.5\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-prestroke}
+   \label{fig:prestrokeangle}
+ \end{minipage}%
+ \begin{minipage}{0.5\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-poststroke}
+   \label{fig:poststrokeangle}
+ \end{minipage}
+ %
+ \begin{minipage}{\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-binding-angle}
+   \label{fig:bindingangle}
+ \end{minipage}
+\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}.
+\textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}.}
+\label{fig:modelangles}
+\end{figure}
+
 \end{document}

### 2017-11-07 reorganize/papers/paper/supplemental-figs.tex
Add new supplemental figure.

@@
  \end{minipage}
+ \begin{minipage}{\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-full}
+   \label{fig:allangles}
+ \end{minipage}
 \caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}.
-\textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}.}
+\textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}.
+\textbf{d.} Full native dynein cryo-EM image bound to an MT with model superimposed, from \textbf{nativestructure}.}
 \label{fig:modelangles}

### 2017-11-15 reorganize/papers/paper/paper.tex
demo wide figure
Add current parameter table to paper.
remove watermark from paper
Add two new papers to notes.tex.
fail more nicely when latex fails

@@
 % may affect the guide line number alignment.
+
+% the follow ing causes latex to not wait interactively
+\nonstopmode
+
+\setboolean{displaywatermark}{false}
 
@@
 \doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+
+\input{../../data/paper_stepping_parameters.tex}
 
@@
 
+\subsection*{Results}
+
+\begin{figure*}%[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
+\caption{Placeholder image of a frog with a long example caption to show justification setting.}
+\label{fig:trajectory}
+\end{figure*}
+
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
+\caption{Placeholder image of a frog with a long example caption to show justification setting.}
+\label{fig:trajectory}
+\end{figure}
+
+\begin{table}%[tbhp]
+\centering
+\caption{Parameters used in model simulation.}
+\begin{tabular}{lrrr}
+Parameter & Model & Experimental & Source \\
+\midrule
+$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
+$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
+$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
+$k_b$ & $\kb s^{-1}$&  & \\
+$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
+$L_s$ & $\ls nm$ & \cite{nativestructure} & \\
+$L_t$ & $\lt nm$ & \cite{nativestructure} & \\
+$\theta_b$ & $\eqb$ &  & \\
+$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
+$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
+$\theta_t$ & $\eqt$ &  & \\
+
+\bottomrule
+\end{tabular}
+
+%% \addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
+\end{table}
+
+\begin{figure}%[tbhp]
+\centering
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-1-cryoem}
+   \label{fig:modlengths}
+ \end{minipage}%
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-1-superimposed}
+   \label{fig:modlengths}
+ \end{minipage}%
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-1-model}
+   \label{fig:explengths}
+ \end{minipage}
+ %
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-2-cryoem}
+   \label{fig:modlengths}
+ \end{minipage}%
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-2-superimposed}
+   \label{fig:modlengths}
+ \end{minipage}%
+ \begin{minipage}{.3\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-2-model}
+   \label{fig:explengths}
+ \end{minipage}
+\caption{\textbf{Model schematic superimposed on cryo-EM images of native dynein.} Native cryo-EM images of the full dimerized dynein complex composed of light, intermediate and heavy chains, from \cite{nativestructure}.
+Model schematics are superimposed for illustrative purpose; shown angles to not represent expected \textit{in vivo} equilibria.
+Schematics are shown docked to a microtubule for illustrative purposes.}
+\label{fig:modelparams}
+\end{figure}
+
+\begin{figure}%[tbhp]
+\centering
+ \begin{minipage}{0.5\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-prestroke}
+   \label{fig:prestrokeangle}
+ \end{minipage}%
+ \begin{minipage}{0.5\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-poststroke}
+   \label{fig:poststrokeangle}
+ \end{minipage}
+ %
+ \begin{minipage}{\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-binding-angle}
+   \label{fig:bindingangle}
+ \end{minipage}
+ \begin{minipage}{\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{figures/schematic-full}
+   \label{fig:allangles}
+ \end{minipage}
+\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}.
+\textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}.
+\textbf{d.} Full native dynein cryo-EM image bound to an MT with model superimposed, from \textbf{nativestructure}.}
+\label{fig:modelangles}
+\end{figure}
+
 % \pnasbreak splits and balances the columns before the references.

### 2017-11-15 reorganize/papers/paper/paper.tex
Many more filename changes.

@@
 
-\input{../../data/paper_stepping_parameters.tex}
+\input{../../data/paper_histogram_stepping_parameters.tex}
 
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
-\caption{Placeholder image of a frog with a long example caption to show justification setting.}
-\label{fig:trajectory}
+\includegraphics[width=\linewidth]{../../plots/stepping_length_histogram_paper.pdf}
+\caption{Histogram of size of steps taken by model.}
+\label{fig:lengthhist}
+\end{figure}
+
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/stepping_time_histogram_paper.pdf}
+\caption{Histogram of duration of steps taken by model.}
+\label{fig:timehist}
 \end{figure}

### 2017-11-15 reorganize/scripts/generate-paper-histogram-data.py

@@ -18,7 +18,7 @@ else:
 
 label = "paperhisto"
 
-run.cmd(**{"k_b": 1e9,
+basename = run.cmd(**{"k_b": 1e9,
           "k_ub": 100,
           "cb": 0.1,
           "cm": 0.5,
@@ -30,8 +30,10 @@ run.cmd(**{"k_b": 1e9,
           "eqmpost": 224, # from burgess 2002, 360-136
           "eqt": 0,
           "dt": 1e-10, "label": label, "seed": seed, "runtime": runtime,
-          "framerate": 1e-5, "crash-movie": False,
-          "no-slurm": True})
+          "framerate": 1, "crash-movie": False})
 
-os.system("rm data/stepping_movie_config_paperhisto*.txt")
-os.system("rm data/stepping_config_paperhisto*.txt")
+os.system("mv data/stepping_data_paperhisto_%s.txt data/paper_histogram_stepping_data-%s.txt", basename, seed)
+os.system("mv data/stepping_parameters_paperhisto_%s.txt data/paper_histogram_stepping_parameters.tex", basename, seed)
+os.system("rm data/stepping_movie_config_paperhisto_%s.txt", basename)
+os.system("rm data/stepping_movie_data_paperhisto_%s.txt", basename)
+os.system("rm data/stepping_config_paperhisto_%s.txt", basename)

### 2017-11-15 reorganize/scripts/generate-paper-trajectory-data.py

@@ -3,11 +3,7 @@ import os, sys
 import numpy as np
 import dynein.run as run
 
-runtime = 1e-2
-l = "paper"
-if 'long' in sys.argv:
-    runtime = 100e-3
-    l = 'long_paper'
+runtime = 1e-3
 
 basename  = run.sim(**{"k_b": 1e9,
                        "k_ub": 100,
@@ -20,13 +16,13 @@ basename  = run.sim(**{"k_b": 1e9,
                        "eqmpre": 200, # from burgess 2002, 360-160
                        "eqmpost": 224, # from burgess 2002, 360-136
                        "eqt": 0,
-                       "dt": 1e-10, "label": l, "seed": 1, "runtime": runtime,
-                       "framerate": 1e-4, "crash-movie": False,
+                       "dt": 1e-10, "label": "paper", "seed": 1, "runtime": runtime,
+                       "framerate": 1e-8, "crash-movie": False,
                        "no-slurm": True})
 
-os.rename("data/stepping_movie_data_%s.txt" % (basename), "data/%s_movie_data.txt" % l)
-os.rename("data/stepping_data_%s.txt" % (basename), "data/%s_stepping_data.txt" % l)
-os.rename("data/stepping_parameters_%s.tex" % (basename), "data/%s_stepping_parameters.tex" % l)
+os.rename("data/stepping_movie_data_%s.txt" % (basename), "data/paper_trajectory_movie_data.txt")
+os.rename("data/stepping_data_%s.txt" % (basename), "data/paper_trajectory_stepping_data.txt")
+os.rename("data/stepping_parameters_%s.tex" % (basename), "data/paper_trajectory_stepping_parameters.tex")
 
 os.unlink("data/stepping_movie_config_%s.txt" % basename)
 os.unlink("data/stepping_config_%s.txt" % basename)

### 2017-11-15 reorganize/scripts/paper-histogram-plt.py
Fix up paper histogram script

@@ -29,113 +29,15 @@ if len(sys.argv) < 2:
   sys.exit(1)
 
 base_filename = sys.argv[1]
-data_filename = base_filename+'_movie_data.txt'
 step_filename = base_filename+'_stepping_data.txt'
 parameters_filename = base_filename+'_stepping_parameters.tex'
-title = data_filename[data_filename.index("data/")+5:-4]
 
 run_conditions = open(parameters_filename).read()
 raw_run_conditions = run_conditions.replace("\n", " ").replace("\\\\", "\\")
 
-data = np.loadtxt(data_filename)
-plot_length = min(int(5e6), len(data[:,0]))
-data = data[:plot_length, :]
-
-nbxs =  np.zeros(plot_length)
-fbxs =  np.zeros(plot_length)
-nbys =  np.zeros(plot_length)
-fbys =  np.zeros(plot_length)
-
-times = np.empty(plot_length)
-
-for i in range(plot_length-1):
-    if int(data[i,0]) == 0 or int(data[i,0]) == 2:
-        nbxs[i] = data[i,7]
-        fbxs[i] = data[i,15]
-        fbys[i] = data[i,16]
-    elif int(data[i,0]) == 1:
-        nbxs[i] = data[i,15]
-        fbxs[i] = data[i,7]
-        nbys[i] = data[i,16]
-    times[i] = data[i,1]
-
-# avging_window_width = 0.5
-# if len(data) < avging_window_width:
-#        print("Need at least ", avging_window_width, " data points!")
-#        exit(1)
-# num_points = 1000
-# sample_points = np.floor(np.linspace(avging_window_width+1, plot_length-avging_window_width-1, num_points))
-
-# if (plot_length-2*avging_window_width-2 < num_points):
-#     print("Error, need more data points to make trajectory plot.")
-#     exit(1)
-
-# avg_nbxs = np.array([np.mean(nbxs[int(t-avging_window_width):int(t+avging_window_width)]) for t in sample_points])
-# avg_fbxs = np.array([np.mean(fbxs[int(t-avging_window_width):int(t+avging_window_width)]) for t in sample_points])
-# avg_nbys = np.array([np.mean(nbys[int(t-avging_window_width):int(t+avging_window_width)]) for t in sample_points])
[…]

### 2017-11-21 old_stuff/old_simulations/simulation_defaults.h
turned reorganize into root

@@ -1,0 +1,9 @@
+#ifndef SIMULATION_DEFAULTS_H
+#define SIMULATION_DEFAULTS_H
+
+const long long iterations = 1e7;
+const long long data_generation_skip_iterations = 1e5;
+
+const int MOVIE_BUFFER_SIZE = 1000;
+
+#endif

### 2017-11-21 old_stuff/old_simulations/simulations.cpp

@@ -1,0 +1,612 @@
+#include <cassert>
+#include <limits>
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <time.h>
+
+#include "../dynein_struct.h"
+#include "simulation_defaults.h"
+#include "plotting_defaults.h"
+
+/** create_ob/bb_plots .txt generation code **/
+
+struct simple_msg {
+  long long max_iteration;
+  double start_time;
+  char* run_msg;
+};
+
+void generate_force_data(double* times, double* f, int len, const char* legend, char* fname_base, const char* annotation) {
+  char fname[200];
+  sprintf(fname, "%s_%s.txt", fname_base, annotation);
+
+  char buf[256];
+  sprintf(buf, "--legend='%s'", legend);
+  prepare_data_file(buf, fname);
+
+  double* f_local_ave = new double[num_generate_force_datapoints];
+  double* sampled_times = new double[num_generate_force_datapoints];
+
+  int avging_width;
+  if (custom_generate_averaging_width != 0)
+    avging_width = custom_generate_averaging_width;
+  else
+    avging_width = len / num_generate_force_datapoints;
+  
+  for (int i=0; i < num_generate_force_datapoints; i++) {
+    f_local_ave[i] = get_average(&f[i*avging_width], avging_width);
+    sampled_times[i] = times[i*avging_width + avging_width/2];
+  }
+
+  printf("Finished %s                        \n", fname);
+
+  FILE* file = fopen(fname, "a");
+  append_data_to_file(sampled_times, f_local_ave, num_generate_force_datapoints, file);
+  fclose(file);
+
+  delete[] f_local_ave;
+  delete[] sampled_times;
+}
+
+void generate_correlation_fn_data(double* pe, int iters, const char* legend, char* fname_base){
+  int max_tau_iter;
+  if (iters*tau_runtime_fraction > num_corr_datapoints) {
+    max_tau_iter = iters*tau_runtime_fraction;
+  }
+  else {
+    max_tau_iter = num_corr_datapoints;
+  }
+  int d_tau_iter = max_tau_iter / num_corr_datapoints;
+
+  char fname[200];
+  strcpy(fname, fname_base);
+  strcat(fname, "_correlation_fn.txt");
+
+  char buf[256];
[…]

### 2017-11-21 scripts/dynein/draw/balls.py

@@ -1,0 +1,39 @@
+#! /usr/bin/env python3
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
+
+def draw_cartoon(near_foot_figure_coords, state, x_coords, y_coords, x_scaling, y_scaling, alpha=1):
+    if (state == 0):
+        figure_xs = near_foot_figure_coords[0] + x_scaling*(np.array(x_coords) - x_coords[0]) + x_coords[0]
+    else:
+        figure_xs = near_foot_figure_coords[0] + x_scaling*(np.array(x_coords) - x_coords[4]) + x_coords[4]
+
+    figure_ys = near_foot_figure_coords[1] + y_scaling*np.array(y_coords)
+
+    # print("figure_xs", figure_xs)
+    # print("x_coords", x_coords)
+
+    plt.plot([figure_xs[0], figure_xs[1]], [figure_ys[0], figure_ys[1]], color="black", zorder=4, linewidth=0.5, alpha=alpha)
+    plt.plot([figure_xs[1], figure_xs[2]], [figure_ys[1], figure_ys[2]], color="black", zorder=4, linewidth=0.5, alpha=alpha)
+    plt.plot([figure_xs[2], figure_xs[3]], [figure_ys[2], figure_ys[3]], color="black", zorder=1, linewidth=0.5, linestyle=":", alpha=alpha)
+    plt.plot([figure_xs[3], figure_xs[4]], [figure_ys[3], figure_ys[4]], color="black", zorder=1, linewidth=0.5, linestyle=":", alpha=alpha)
+
+    plt.plot([figure_xs[4]], [figure_ys[4]], marker='o', markeredgecolor='k', markeredgewidth=0.4, zorder=2, color="red",   markersize=6*x_scaling, alpha=alpha)
+    plt.plot([figure_xs[3]], [figure_ys[3]], marker='o', markeredgecolor='k', markeredgewidth=0.4, zorder=3, color="white", markersize=18*x_scaling, alpha=alpha)
+    plt.plot([figure_xs[2]], [figure_ys[2]], marker='o', markeredgecolor='k', markeredgewidth=0.4, zorder=4, color="white", markersize=6*x_scaling, alpha=alpha)
[…]

### 2017-11-21 scripts/generate-paper-histogram-data.py

@@ -1,0 +1,39 @@
+#!/usr/bin/python3
+import argparse
+import os, sys
+import numpy as np
+import dynein.run as run
+
+runtime = 1
+
+os.system("make generate_stepping_data")
+
+parser = argparse.ArgumentParser()
+parser.add_argument("-s", "--seed", type=int, help="Manually set the seed value, default=1")
+args = parser.parse_args()
+if args.seed:
+    seed = args.seed
+else:
+    seed = 1
+
+label = "paperhisto"
+
+basename = run.sim(**{"k_b": 1e9,
+                      "k_ub": 100,
+                      "cb": 0.1,
+                      "cm": 0.5,
+                      "ct": 0.2,
+                      "ls": 10.49, # from urnavicius 2015 (paper.bib)
+                      "lt": 23.8,  # from urnavicius 2015
+                      "eqb": 120,  # from redwine 2012 supplemental
+                      "eqmpre": 200, # from burgess 2002, 360-160
+                      "eqmpost": 224, # from burgess 2002, 360-136
+                      "eqt": 0,
+                      "dt": 1e-10, "label": label, "seed": seed, "runtime": runtime,
+                      "framerate": 1, "crash-movie": False})
+
+os.system("mv data/stepping_data_%s.txt data/paper_histogram_stepping_data-%s.txt" % (basename, seed))
+os.system("mv data/stepping_parameters_%s.tex data/paper_histogram_stepping_parameters.tex" % basename)
+os.system("rm data/stepping_movie_config_%s.txt" % basename)
+os.system("rm data/stepping_movie_data_%s.txt" % basename)
+os.system("rm data/stepping_config_%s.txt" % basename)

### 2017-11-21 scripts/histogram-helper.py

@@ -1,0 +1,7 @@
+#!/usr/bin/env python
+import os
+
+seeds = [1, 2, 3, 4, 5]
+
+for s in seeds:
+    os.system("rq run python3 scripts/generate-paper-histogram-data.py --seed " + str(s))

### 2017-11-21 scripts/make_stepping_plots.py

@@ -1,0 +1,60 @@
+#!/usr/bin/python3
+from __future__ import division, print_function
+
+import matplotlib
+matplotlib.use("PDF") # use PDF generating backend bc it can handle bigger datasets
+import matplotlib.pyplot as plt
+import os
+import numpy as np
+import sys
+
+from matplotlib.offsetbox import AnchoredOffsetbox, TextArea
+
+file_string = sys.argv[1]
+data_files = []
+
+for fname in os.listdir("data/"):
+    if os.path.isfile("data/" + fname):
+        if (file_string in "data/" + fname) and ("stepping_data" in "data/" + fname):
+            data_files.append("data/" + fname)
+
+step_times = []
+step_lengths = []
+onebound_times = []
+bothbound_times = []
+
+for data_file in data_files:
+    data = np.loadtxt(data_file)
+    if len(data) < 3 or str(type(data[0])) == "<type 'numpy.float64'>":
+        continue
+
+    bind_times = np.array(data[:,1])
+    unbind_times = np.array(data[:,0])
+    near_positions = -1*np.array(data[:,2])
+    far_positions = -1*np.array(data[:,3])
+    near_step_idxs = near_positions[1:] != near_positions[:-1]
+    far_step_idxs = far_positions[1:] != far_positions[:-1]
+    near_step_lens = (near_positions[1:] - near_positions[:-1])[near_step_idxs]
+    far_step_lens = (far_positions[1:] - far_positions[:-1])[far_step_idxs]
+
+    step_times = np.concatenate((step_times, np.array(bind_times[1:] - bind_times[:-1])))
+    onebound_times = np.concatenate((onebound_times, bind_times - unbind_times))
+    bothbound_times = np.concatenate((bothbound_times, bind_times[1:] - unbind_times[:-1]))
+    step_lengths = np.concatenate((step_lengths, near_step_lens, far_step_lens))
+
+#step length histogram
+fig = plt.figure()
+plt.hist(step_lengths, bins=50)
+plt.xlabel("Step length (nm)")
+plt.ylabel("Frequency")
+plt.savefig("plots/stepping_length_histogram.pdf", format="pdf")
+plt.close(fig)
+
+#step time histogram
+fig = plt.figure()
+plt.hist(step_times, bins=50)
+plt.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+plt.xlabel("Step time (s)")
+plt.ylabel("Frequency")
[…]

### 2017-11-21 src/generate_stepping_data.cpp

@@ -1,0 +1,561 @@
+#include <cassert>
+#include <cstdlib>
+#include <cstdio>
+#include <cstring>
+#include <limits>
+
+#include <errno.h>
+#include <fcntl.h>
+#include <getopt.h>
+#include <sys/mman.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <unistd.h>
+
+#include "version-info.h"
+#include "default_parameters.h"
+#include "dynein_struct.h"
+#include "simulation_defaults.h"
+
+const bool display_step_info = false;
+const bool display_progress = false;
+
+extern movie_data_struct* on_crash_old_movie_data_global_ptr;
+extern movie_data_struct* on_crash_new_movie_data_global_ptr;
+extern char* crash_movie_file_name_global;
+
+bool am_making_movie = true;
+bool am_debugging_onebound = false;
+
+long num_movie_writes = 1e7;
+// bytes per movie write: 213, 2000Mb bytes max movie size
+
+static const long MAX_FILESIZE_PERMITTED = 1<<30; // <- bit shift 
+static int NUM_STEPS = 0;
+
+void on_crash_write_movie_buffer();
+
+struct job_msg_t {
+  long long max_iteration;
+  double start_time;
+  char *run_msg;
+  FILE *stepping_data_file;
+  FILE *movie_data_file;
+};
+
+void check_for_quitting_conditions(double time_run, FILE* data_file, double first_binding_time, double last_unbinding_time) {
+  // P(stepping k times in t seconds) = ((t/0.06)^k*e^(t/0.06)) / k!
+  if (time_run > 0.3 and NUM_STEPS == 0 and am_exiting_on_improbable_stepping) {
+    printf("Zero steps in 0.3 seconds. There's a 0.67%% chance of real dynein doing this. Exiting successfully\n");
+    fprintf(data_file, "#EXIT SUCCESSFULLY!\n");
+    fprintf(data_file, "#First binding time: %g\n", first_binding_time);
+    fprintf(data_file, "#Last unbinding time: %g\n", last_unbinding_time);
+    fprintf(data_file, "#Runtime: %g\n", time_run);
+    exit(0);
+  }
[…]

### 2017-11-21 src/ob_PE_equipartition_ratio_vs_time.cpp

@@ -1,0 +1,92 @@
+#include <cassert>
+#include <stdio.h>
+#include <string.h>
+
+#include "../dynein_struct.h"
+#include "../default_parameters.h"
+
+int main(int argc, char** argv) {
+  if (FP_EXCEPTION_FATAL) {
+    feenableexcept(FE_ALL_EXCEPT); // NaN generation kills program
+    signal(SIGFPE, FPE_signal_handler);
+  }
+
+  T = 100;
+  int max_eq_iter = 1e6;
+  int min_eq_iter = 0.1*max_eq_iter;
+  int d_runtime_iter = 1e5;
+  
+  int num_eq_datapoints = (max_eq_iter - min_eq_iter) / d_runtime_iter;
+
+  const char* bba_eq_title = "Bound binding";
+  const char* bma_eq_title = "Bound motor";
+  const char* ta_eq_title =  "Tail domain";
+  const char* uma_eq_title = "Unbound motor";
+
+  if (argc != 2) {
+    printf("Error, TITLE variable must have underscores, not spaces.\n");
+    exit(1);
+  }
+  char* f_appended_name = argv[1];
+  char bba_eq_fname[200];
+  char bma_eq_fname[200];
+  char ta_eq_fname[200];
+  char uma_eq_fname[200];
+  char config_eq_fname[200];
+
+  strcpy(bba_eq_fname, "data/bba_pe_equipartition_ratio_");
+  strcpy(bma_eq_fname, "data/bma_pe_equipartition_ratio_");
+  strcpy(ta_eq_fname,  "data/ta_pe_equipartition_ratio_");
+  strcpy(uma_eq_fname, "data/uma_pe_equipartition_ratio_");
+  strcpy(config_eq_fname, "data/config_pe_equipartition_ratio_");
+
+  strcat(bba_eq_fname, f_appended_name);
+  strcat(bma_eq_fname, f_appended_name);
+  strcat(ta_eq_fname, f_appended_name);
+  strcat(uma_eq_fname, f_appended_name);
+  strcat(config_eq_fname, f_appended_name);
+
+  strcat(bba_eq_fname, ".txt");
+  strcat(bma_eq_fname, ".txt");
+  strcat(ta_eq_fname, ".txt");
+  strcat(uma_eq_fname, ".txt");
+  strcat(config_eq_fname, ".txt");
+
+  prepare_data_file(bba_eq_title, bba_eq_fname);
+  prepare_data_file(bma_eq_title, bma_eq_fname);
[…]

### 2017-12-05 papers/paper/paper.tex
clean up figures and add new color plot to paper

--- 2017-11-15 reorganize/papers/paper/paper.tex
@@
-\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
+\documentclass[9pt,twocolumn,twoside]{pnas-new}
 % Use the lineno option to display guide line numbers if required.
@@
 
-\begin{figure*}%[tbhp]
+\begin{figure}%[tbhp]
 \centering
-\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
+\includegraphics[width=\linewidth]{../../plots/paper-trajectory-plot.pdf}
 \caption{Placeholder image of a frog with a long example caption to show justification setting.}
 \label{fig:trajectory}
-\end{figure*}
+\end{figure}
 
@@
 \caption{Histogram of duration of steps taken by model.}
+\label{fig:timehist}
+\end{figure}
+
+\begin{figure}%[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/total_step_time_vs_step_length_multiple_seeds}
+\caption{Histogram of duration and length of steps taken by model.}
 \label{fig:timehist}
@@
   \centering
- \begin{minipage}{.3\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-1-cryoem}
-   \label{fig:modlengths}
- \end{minipage}%
- \begin{minipage}{.3\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-1-superimposed}
-   \label{fig:modlengths}
- \end{minipage}%
- \begin{minipage}{.3\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-1-model}
-   \label{fig:explengths}
- \end{minipage}
- %
- \begin{minipage}{.3\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-2-cryoem}
-   \label{fig:modlengths}
- \end{minipage}%
- \begin{minipage}{.3\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-2-superimposed}
-   \label{fig:modlengths}
- \end{minipage}%
- \begin{minipage}{.3\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-2-model}
-   \label{fig:explengths}
- \end{minipage}
-\caption{\textbf{Model schematic superimposed on cryo-EM images of native dynein.} Native cryo-EM images of the full dimerized dynein complex composed of light, intermediate and heavy chains, from \cite{nativestructure}.
-Model schematics are superimposed for illustrative purpose; shown angles to not represent expected \textit{in vivo} equilibria.
-Schematics are shown docked to a microtubule for illustrative purposes.}
+   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
+   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
+   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}
+
+   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
+   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
+   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
+   \caption{\textbf{Model schematic superimposed on cryo-EM images of
+       native dynein.} Native cryo-EM images of the full dimerized
+     dynein complex composed of light, intermediate and heavy chains,
+     from \cite{nativestructure}. Model schematics are superimposed
+     for illustrative purpose; shown angles to not represent expected
+     \textit{in vivo} equilibria. Schematics are shown docked to a
+     microtubule for illustrative purposes.}
    \label{fig:modelparams}
@@
   \centering
- \begin{minipage}{0.5\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-prestroke}
-   \label{fig:prestrokeangle}
- \end{minipage}%
- \begin{minipage}{0.5\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-poststroke}
-   \label{fig:poststrokeangle}
- \end{minipage}
- %
- \begin{minipage}{\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-binding-angle}
-   \label{fig:bindingangle}
- \end{minipage}
- \begin{minipage}{\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{figures/schematic-full}
-   \label{fig:allangles}
- \end{minipage}
-\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}.
-\textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}.
-\textbf{d.} Full native dynein cryo-EM image bound to an MT with model superimposed, from \textbf{nativestructure}.}
+\includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
+\includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
+\includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
+\includegraphics[width=0.5\columnwidth]{figures/schematic-full}
+  \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
+      images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
+    dynein heavy chains superimposed with model motor angles, both
+    from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
+    MT with model binding angle superimposed, from
+    \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
+    bound to an MT with model superimposed, from
+    \textbf{nativestructure}.}
 \label{fig:modelangles}
 \end{figure}
+
+See schematic in Figure~\ref{fig:modelangles}.
 

### 2017-12-05 scripts/color_hist.py

@@ -2,7 +2,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import argparse
-import os
+import os, glob
 
 parser = argparse.ArgumentParser(description = 'Script to generate 2 dimensional histogram from dynein stepping data')
 
@@ -59,13 +59,11 @@ if not ALL:
     step_times = onebound_times + bothbound_times
 else:
     data_files = []
-    for fname in os.listdir("data/"):
-        if os.path.isfile("data/" + fname):
-            if ("data/paper_histogram_stepping_data" in "data/" + fname):
-                data_files.append("data/" + fname)
-                if len(data_files) == 0:
-                    print("Error, no files of form data/paper_histogram_stepping_data*.txt found. Exiting.")
-                    exit(1)
+    for fname in glob.glob("data/paper_histogram_stepping_data*.txt"):
+        data_files.append(fname)
+    if len(data_files) == 0:
+        print("Error, no files of form data/paper_histogram_stepping_data*.txt found. Exiting.")
+        exit(1)
 
 
     for data_file in data_files:
@@ -130,7 +128,7 @@ def plotCounts(x, y, graph_label, x_label, y_label):
 
 seed_label = ''
 if ALL:
-    seed_label = '(multiple seeds)'
+    seed_label = 'multiple_seeds'
 plotCounts(step_times, step_lengths,
            "total step time vs step length {}".format(seed_label),
            'step time', 'step length')

### 2017-12-05 papers/paper/paper.tex
shorten title and change filename
reorder figure slightly

@@
 
-\subsection*{Results}
+\section{Results}
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../../plots/time-vs-length-multiple-seeds}
+\caption{Histogram of duration and length of steps taken by model.}
+\label{fig:duration-length}
+\end{figure}
+
+Figure~\ref{fig:duration-length} shows the frequency of steps with
+various combination of step length and step time.  We can see that...
 
@@
 \caption{Histogram of duration of steps taken by model.}
-\label{fig:timehist}
-\end{figure}
-
-\begin{figure}%[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/total_step_time_vs_step_length_multiple_seeds}
-\caption{Histogram of duration and length of steps taken by model.}
 \label{fig:timehist}
@@
 
-See schematic in Figure~\ref{fig:modelangles}.
-
 % \pnasbreak splits and balances the columns before the references.

### 2018-02-13 papers/notes/notes.tex
turned reorganize into root
add a small notes

--- 2017-11-07 reorganize/papers/notes/notes.tex
@@
   \centering
-  \includegraphics[width=.45\textwidth]{figures/equilibrium-onebound}
+  \includegraphics[width=.45\textwidth]{../elliott-thesis/figures/equilibrium-onebound}
   \caption{Definition of equilibrium angles.}
@@
 \subsection{Native dynein cryo-EM structure}
+Structural organization of the dynein-dynactin complex bound to microtubules\\
+
 Full structure of dynein.\\
@@
 There's a better stall-force measurement here than in other assays.\\
+
+to discuss:
+        gibbs-bd transitions look much better
+        hard to run simulations with the current nan-unbinding code - is there a better way? could we just sample from a positive gaussian instead?
+        yildiz-inspired transition model: at low separation atpase unbinding rate; at high internhead, feel 1pN force per 12nm
+                        Could use the release rate modifiers from the Yildiz rate vs separation plots
 

### 2018-02-26 papers/paper/paper.tex
Add step alternation/passing plot to paper
Make paper.pdf build.
New data file scheme: static and exponential data files hold data from respective trials, and are used to make plots for paper.pdf.

--- 2017-12-05 papers/paper/paper.tex
@@
 % may affect the guide line number alignment.
+
+\usepackage{subcaption}
 
@@
 
-\input{../../data/paper_histogram_stepping_parameters.tex}
+\input{../../data/paper_static_stepping_parameters.tex}
 
@@
 
-\subsection*{Results}
+\section{Results}
 
-\begin{figure}%[tbhp]
+\begin{figure}[tbhp]
 \centering
-\includegraphics[width=\linewidth]{../../plots/paper-trajectory-plot.pdf}
+\includegraphics[width=\linewidth]{../../plots/paper_static_time_vs_length}
+\caption{Heatmap of relationship between step length and time.}
+\label{fig:duration-length}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
 \caption{Placeholder image of a frog with a long example caption to show justification setting.}
@@
 
-\begin{figure}%[tbhp]
+%% \begin{figure}%[tbhp]
+%% \centering
+%% \includegraphics[width=\linewidth]{../../plots/stepping_analysis_paper.pdf}
+%% \caption{Histogram of duration of steps taken by model.}
+%% \label{fig:timehist}
+%% \end{figure}
+
+\begin{figure*}[tbhp]
+  \begin{subfigure}{0.5\textwidth}
     \centering
-\includegraphics[width=\linewidth]{../../plots/stepping_length_histogram_paper.pdf}
+    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
+    \subcaption{Static unbinding rate}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
+    \subcaption{Exponential unbinding rate}
+  \end{subfigure}
 \caption{Histogram of size of steps taken by model.}
 \label{fig:lengthhist}
-\end{figure}
+\end{figure*}
 
-\begin{figure}%[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/stepping_time_histogram_paper.pdf}
-\caption{Histogram of duration of steps taken by model.}
-\label{fig:timehist}
-\end{figure}
-
-\begin{figure}%[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/total_step_time_vs_step_length_multiple_seeds}
-\caption{Histogram of duration and length of steps taken by model.}
-\label{fig:timehist}
-\end{figure}
-
-\begin{table}%[tbhp]
+\begin{table}[tbhp]
 \centering
@@
 
-\begin{figure}%[tbhp]
+\begin{figure}[tbhp]
   \centering

### 2018-02-28 papers/paper/paper.tex

@@
   \end{subfigure}
-\caption{Histogram of size of steps taken by model.}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_static_foot_order_histogram}
+    \subcaption{Static unbinding rate}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_exponential_foot_order_histogram}
+    \subcaption{Exponential unbinding rate}
+  \end{subfigure}
+\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
 \label{fig:lengthhist}
@@
 \caption{Parameters used in model simulation.}
+\label{tab:staticparams}
 \begin{tabular}{lrrr}
@@
 $k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
-$L_s$ & $\ls nm$ & \cite{nativestructure} & \\
-$L_t$ & $\lt nm$ & \cite{nativestructure} & \\
+$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
+$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
 $\theta_b$ & $\eqb$ &  & \\

### 2018-03-22 papers/paper/paper.tex

@@
     \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
+  \end{subfigure}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
     \subcaption{Static unbinding rate}
@@
     \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
-    \subcaption{Exponential unbinding rate}
-  \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_static_foot_order_histogram}
-    \subcaption{Static unbinding rate}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_exponential_foot_order_histogram}
+    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
     \subcaption{Exponential unbinding rate}
@@
 \label{fig:lengthhist}
+\end{figure*}
+
+\begin{figure*}[tbhp]
+    \includegraphics[width=0.5\linewidth]{../../plots/paper_static_foot_order_histogram}
+    \includegraphics[width=0.5\linewidth]{../../plots/paper_exponential_foot_order_histogram}
+\caption{The left plot is the $C=0$ case where the unbinding rate is
+  independent of angle.  Here ``alternating'' means that the binding
+  domain which did not move last time moved this time.  Passing means
+  that the moving foot was behind, and ended up in front.}
+\label{fig:steppingorder}
 \end{figure*}

### 2018-04-06 papers/paper/paper.tex
Add leading/lagging histogram to paper.pdf
Minor add to paper.

@@
 
+\section*{Model}
+\subsection*{Model layout}
+The dynein model used in this paper consists of two systems meant to mimic the motor's dynamics in its post-powerstroke and pre-powerstroke states.
+These systems, shown in Figure \ref{fig:model-cartoon},
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}
+\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
+\caption{Cartoon representation of model systems. \textbf{Left}: Post-powerstroke, \textbf{right}: pre-powerstroke.}
+\label{fig:duration-length}
+\end{figure}
+
 \section{Results}
@@
     \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
+  \end{subfigure}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
   \end{subfigure}

### 2018-04-08 scripts/make_all_stepping_plots.py
Add trajectory plot from histogram files

@@ -364,3 +364,37 @@ if args.parameters_filename != "":
 
 plt.savefig("plots/displacement_histogram.pdf", format="pdf")
 plt.close(fig)
+
+plt.figure()
+
+data = np.loadtxt(data_files[0], dtype = np.float64)
+bind_times = np.array(data[:,1])
+near_foot_positions = np.around(np.array(data[:,2]), decimals=12)
+far_foot_positions = np.around(np.array(data[:,3]), decimals=12)
+
+bind_times_duplicated = np.zeros(len(bind_times)*2-1)
+near_positions_duplicated = np.zeros(len(bind_times)*2-1)
+far_positions_duplicated = np.zeros(len(bind_times)*2-1)
+
+for t in range(1, len(bind_times)):
+    bind_times_duplicated[2*t-1] = bind_times[t]
+    bind_times_duplicated[2*t] = bind_times[t]
+    near_positions_duplicated[2*t-1] = near_foot_positions[t-1]
+    near_positions_duplicated[2*t] = near_foot_positions[t]
+    far_positions_duplicated[2*t-1] = far_foot_positions[t-1]
+    far_positions_duplicated[2*t] = far_foot_positions[t]
+
+bind_times_duplicated[0] = bind_times[0]
+near_positions_duplicated[0] = near_foot_positions[0]
+far_positions_duplicated[0] = far_foot_positions[0]
+
+plt.plot(bind_times_duplicated, near_positions_duplicated, 'o-', label="Near BD", markersize=1)
+plt.plot(bind_times_duplicated, far_positions_duplicated, 'o-', label="Far BD", markersize=1)
+
+plt.xlabel("time (s)")
+plt.ylabel("Position (nm)")
+
+plt.legend()
+
+plt.savefig("plots/stepping_trajectory.pdf", format="pdf")
+plt.close(fig)

### 2018-04-15 scripts/movie.py
Clean up some data files manually

@@ -47,7 +47,7 @@ if sys.argv[2][:6] != 'speed=':
 speed =  float(sys.argv[2][6:])
 
 if tail and sys.stdin.isatty():
-    skiplen = sum(1 for line in open(data_file)) - 10000
+    skiplen = sum(1 for line in open(data_file)) - 100000
     if skiplen < 0:
 	skiplen = 1
 

### 2018-05-01 papers/notes/notes.tex
Add brief change to notes.tex about expected ob/bb time

@@
     Source & Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
-    Weihong 2012 GST-dimerized & 134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
+    Weihong 2012 GST-dimerized & 134nm/s & 3.5nm? &  & 7.9s & 0.0595s & \\ \hline
     Higuchi 2006 & 800nm/s &  &  &   &   & \\ \hline
-    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s &  & 0.011s & 1s    & 0.011s & 1.3e-4\\ \hline
-    Schroer 2000 native 2mM ATP w/ 210nm beads + dynactin & 700nm/s &  & 0.011s & 2.14s & 0.011s & 6e-5\\ \hline
+    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s & 3.5nm? & 0.005s & 1s    & 5e-3s & 2.5e-5\\ \hline
+    Schroer 2000 native 2mM ATP w/ 210nm beads + dynactin & 700nm/s & 3.5nm? &  & 2.14s &  & 6e-5\\ \hline
     Vale    2006 GST-dimerized 1mM + qdots                & 87 nm/s &  & 0.09s  & 13.8s & &\\ \hline

### 2018-05-01 scripts/make_all_stepping_plots.py

@@ -247,9 +247,9 @@ plt.close(fig)
 # OB_time vs step_length scatter
 assert len(onebound_times) == len(step_lengths)
 fig = plt.figure()
-plt.scatter(onebound_times, step_lengths)
+plt.scatter(onebound_times, step_lengths, alpha=0.3)
 plt.gca().set_xscale('log')
-plt.xlabel("Onebound time (s)")
+plt.xlabel("Onebound time (s), theory= 2.5e-5s")
 plt.ylabel("Step length (nm)")
 
 plt.gca().set_xlim((1e-7, 1e-2))
@@ -263,9 +263,9 @@ plt.close(fig)
 # BB_time vs step_length scatter
 assert len(bothbound_times) == len(step_lengths)
 fig = plt.figure()
-plt.scatter(bothbound_times, step_lengths)
+plt.scatter(bothbound_times, step_lengths, alpha=0.3)
 plt.gca().set_xscale('log')
-plt.xlabel("Bothbound time (s)")
+plt.xlabel("Bothbound time (s), theory= 5e-3s")
 plt.ylabel("Step length (nm)")
 
 plt.gca().set_xlim((1e-5, 1))

### 2018-05-03 papers/notes/notes.tex
very minor change

@@
     Higuchi 2006 & 800nm/s &  &  &   &   & \\ \hline
-    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s & 3.5nm? & 0.005s & 1s    & 5e-3s & 2.5e-5\\ \hline
+    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s & 1.7nm? & 0.0025s & 1s    & 2.5e-3s & 6e-6\\ \hline
     Schroer 2000 native 2mM ATP w/ 210nm beads + dynactin & 700nm/s & 3.5nm? &  & 2.14s &  & 6e-5\\ \hline

### 2018-05-03 scripts/make_all_stepping_plots.py

@@ -247,9 +247,9 @@ plt.close(fig)
 # OB_time vs step_length scatter
 assert len(onebound_times) == len(step_lengths)
 fig = plt.figure()
-plt.scatter(onebound_times, step_lengths, alpha=0.3)
+plt.scatter(onebound_times, step_lengths, alpha=0.1)
 plt.gca().set_xscale('log')
-plt.xlabel("Onebound time (s), theory= 2.5e-5s")
+plt.xlabel("Onebound time (s), theory= 6e-6s")
 plt.ylabel("Step length (nm)")
 
 plt.gca().set_xlim((1e-7, 1e-2))
@@ -263,7 +263,7 @@ plt.close(fig)
 # BB_time vs step_length scatter
 assert len(bothbound_times) == len(step_lengths)
 fig = plt.figure()
-plt.scatter(bothbound_times, step_lengths, alpha=0.3)
+plt.scatter(bothbound_times, step_lengths, alpha=0.1)
 plt.gca().set_xscale('log')
 plt.xlabel("Bothbound time (s), theory= 5e-3s")
 plt.ylabel("Step length (nm)")

### 2018-05-31 papers/notes/notes.tex
Add very rough model section to paper.tex

@@
 
+\subsection{Angular measurements of the dynein ring reveal a stepping mechanism dependent on a flexible stalk}
+Imaging study using polTIRF which shows that the dynein motor doesn't rotate
+
 \subsection{Further reading}
@@
 
-\section{Program Scaling}
-Program runtimes, as of commit 62c4d:
-
-\begin{verbatim}
-elliotc12@bennet:~/dynein_walk$ grep "dt" default_parameters.h 
-double dt = 1e-11;
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-5
-Running for 1e-05 s
-
-real	0m5.001s
-user	0m4.972s
-sys	0m0.000s
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-5
-Running for 1e-05 s
-
-real	0m7.121s
-user	0m7.072s
-sys	0m0.000s
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-4
-Running for 0.0001 s
-
-real	0m26.666s
-user	0m26.608s
-sys	0m0.000s
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-4
-Running for 0.0001 s
-
-real	0m29.479s
-user	0m29.428s
-sys	0m0.000s
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-3
-Running for 0.001 s
-
-real	4m47.224s
-user	4m46.832s
-sys	0m0.000s
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-3
-Running for 0.001 s
-
-real	4m56.207s
-user	4m55.776s
-sys	0m0.000s
-elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-2
-Running for 0.01 s
-
-real	61m44.302s
-user	61m35.264s
-sys	0m0.120s
-\end{verbatim}
-
-The average time per iteration is ~3.9 microseconds, or 3.9e5 real seconds per simulated second at $dt=10^{-11}s$.
-Thus we can generate one 60-millisecond step in 23,400 seconds, or 6.5 hours.
-A thousand-step simulation would thus take, very roughly, 8 months.\\
-
 \section{Todo}

### 2018-05-31 papers/paper/paper.tex
Add very rough model section to paper.tex

@@
 \usepackage{subcaption}
+\usepackage{breqn}
 
@@
 \section*{Model}
-\subsection*{Model layout}
-The dynein model used in this paper consists of two systems meant to mimic the motor's dynamics in its post-powerstroke and pre-powerstroke states.
-These systems, shown in Figure \ref{fig:model-cartoon},
+
+%% Figure X.1 - poststroke
+%% FIgure X.2 - prestroke
+%% Figure X.A: Model of the protein superimposed over cryo-EM data (with length data)
+%% Figure X.B: Cryo-EM visualizations of how we get equilibrium angles
+%% Add rod vectors connecting each domain
 
@@
 \end{figure}
+
+\subsection*{Elastic hinge model}~\\
+Our model is designed to capture the course-grained dynamics of the dynein protein while remaining mathematically tractable.
+We capture the structure of the full dynein complex by treating the protein as a set of spheres connected by rigid rods.
+Geometric properties of the model, such as rod length $L_s$ and $L_t$, and sphere radii $R_b$, $R_m$ and $R_t$, are calculated from electron microscopy and crystallography data, as pictured in Fig X.A.
+Each sphere acts as a hinge, and the angle between connected rods, or the MT, is free to vary.
+The model is constrained to remain in the plane of the microtubule, so transverse motion is not allowed.
+The model exists in two states: one called the poststroke state with both binding domain positions constant, as in Figure X.1, and one called the prestroke state with one binding domain free to move, as in Figure X.2.
+
+\subsection*{Model dynamics}~\\
+The model experiences internal and external forces.
+The internal forces are due to elastic restoring forces for each hinge angle ($\left[\theta_{bb}, \theta_{bm}, \theta_{t}, \theta_{um},\right]$ for prestroke, $\left[\theta_{nb}, \theta_{nm}, \theta_{t}, \theta_{fm}, \theta_{fb},\right]$ for poststroke) compared to its equilibrium ($\left[\Theta_{bb}, \Theta_{bm}, \Theta_{t}, \Theta_{um},\right]$ for prestroke, $\left[\Theta_{nb}, \Theta_{nm}, \Theta_{t}, \Theta_{fm}, \Theta_{fb},\right]$ for postsroke).
+These equilibrium angles are determined from cryo-EM micrographs of ATP-Vi-bound and ADP-bound dynein monomers, indicated in Figure X.B.\\
+
+The torque on each domain is given by:
+%
+\begin{equation}
+  \vec{\tau}_{i} = c_i\left(\theta_{i}-\Theta_{i}\right)\hat{z}
+\end{equation}
+%
+The external forces on the model are random Brownian forces $\vec{R_i} = R_i\hat{x} + R_i\hat{y}$, where $R_i$ is a Gaussian random variable with $\mu_R = 0$ and $\sigma^2_R = 2kbT\gamma_i/dt$, where drag factor $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$.
+Brownian dynamics is used to calculate the velocity on each domain, where velocity is given by:
+%
+\begin{dmath}
+  \vec{v}_i = \gamma_i^{-1}\left(\frac{\vec{\tau}_{i-1}}{L_{i-1}}\left(\hat{z}\times\hat{r}_{i-1}\right)
+  + \frac{\vec{\tau}_{i+1}}{L_{i+1}}\left(\hat{z}\times\hat{r}_{i+1}\right)
+  - \vec{\tau}_{i}\left(\frac{\hat{z}\times\hat{r}_{i-1}}{L_{i-1}}+\frac{\hat{z}\times\hat{r}_{i+1}}{L_{i+1}}\right) + \vec{R_i}\right)
+  \label{eq:motionequation}
+\end{dmath}
+%
+\subsection*{Powerstroke model}~\\
+The dynein powerstroke is the hypothetical process whereby a motor unbinds from the microtubule, undergoes a linker remodel which pushes the motor forward, binds to the microtubule, and undergoes the opposite linker remodel, pulling the rest of the motor forward in a ``powerstroke.'' Our model simplifies the powerstroke cycle by alternating between two states: a two-foot-bound post-powerstroke state similar to the apo dynein, and a one-foot-bound pre-powerstroke state similar to the post-hydrolysis ADP-Pi dynein.
+Our model captures the prestroke kick of the unbound MTBD through different motor hinge equilibrium angles, as calculated from Figure X.B.
+The larger prestroke motor hinge angle causes a forward diffusion of the unbound binding domain on transition to one-foot-bound, followed by another forward diffusion of the whole motor as the MTBD binds and transitions back to post-stroke hinge angles.\\
+
+Dynein's MTBD unbinding dynamics are known to be tension-dependent, where at high interhead separations unbinding favors the lagging MTBD, but no preference between leading and lagging is seen for small interhead separations \cite{yildizpaper}.
+To capture this, the microtubule unbinding rate $k_{ub}$ takes into account absolute binding angle:
+%
+\begin{equation}
+  k_{ub} = k_{ub}^0e^{-c\left(\theta_{xb}-\Theta{xb}\right)}
+\end{equation}
+%
+where $k_{ub}^0$ is the default unbinding rate and $c$ the unbinding exponential factor.
+Each timestep unbinding occurs with probability $k_{ub}dt$.
+On unbinding, the both-foot-bound model transitions to a one-foot-bound model with identical domain positions, but new equilibrium hinge angles.
+Microtubule binding occurs with probability $k_{b}^0dt$ if the binding domain is within $D$ nm of the microtubule.
+On binding, the one-foot-bound model transitions to a both-feet-bound with identical domain positions, but with both MTBDs constrained on the microtubule.\\
+
+\subsection*{Simulating the model}~\\
+The model was simulated using Euler's method to time evolve Equation \ref{eq:motionequation} using a timestep $dt$, transitioning freely between the poststroke and prestroke states.
 
@@
 $\theta_t$ & $\eqt$ &  & \\
+$D$ & 0.2 nm &  & \\
 

### 2018-05-31 papers/paper/paper.tex
Add initial work on dynamic model+cryoem micrograph figure

@@
 
-\begin{figure}[tbhp]
+\begin{figure*}[tbhp]
 \centering
-\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}
-\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
-\caption{Cartoon representation of model systems. \textbf{Left}: Post-powerstroke, \textbf{right}: pre-powerstroke.}
+\includegraphics[width=0.3\linewidth]{figures/onebound-cartoon.pdf}%
+\includegraphics[width=0.3\linewidth]{figures/bothbound-cartoon.pdf}%
+\includegraphics[width=0.3\linewidth]{figures/schematic-1-superimposed}\\
+\includegraphics[width=0.15\linewidth]{../../plots/poststroke-figure.pdf}%
+\includegraphics[width=0.15\linewidth]{../../plots/prestroke-figure.pdf}%
+\includegraphics[width=0.3\linewidth]{figures/schematic-binding-angle}
+\caption{}
 \label{fig:duration-length}
-\end{figure}
+\end{figure*}
 
@@
 The model exists in two states: one called the poststroke state with both binding domain positions constant, as in Figure X.1, and one called the prestroke state with one binding domain free to move, as in Figure X.2.
+
+\begin{table}[tbhp]
+\centering
+\caption{Parameters used in model simulation.}
+\label{tab:staticparams}
+\begin{tabular}{lrrr}
+Parameter & Model & Experimental & Source \\
+\midrule
+$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
+$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
+$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
+$k_b$ & $\kb s^{-1}$&  & \\
+$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
+$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
+$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
+$\theta_b$ & $\eqb$ &  & \\
+$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
+$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
+$\theta_t$ & $\eqt$ &  & \\
+$D$ & 0.2 nm &  & \\
+
+\bottomrule
+\end{tabular}
+
+%% \addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
+\end{table}
 
@@
 
-\begin{table}[tbhp]
-\centering
-\caption{Parameters used in model simulation.}
-\label{tab:staticparams}
-\begin{tabular}{lrrr}
-Parameter & Model & Experimental & Source \\
-\midrule
-$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
-$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
-$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
-$k_b$ & $\kb s^{-1}$&  & \\
-$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
-$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
-$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
-$\theta_b$ & $\eqb$ &  & \\
-$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
-$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
-$\theta_t$ & $\eqt$ &  & \\
-$D$ & 0.2 nm &  & \\
-
-\bottomrule
-\end{tabular}
-
-%% \addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
-\end{table}
-
 \begin{figure}[tbhp]
@@
 
+\section{To do items}
+
+\subsection{Elliott}
+\begin{enumerate}
+\item Document carefully where all figures and data comes from.
+\item Make our cool figures presentable, e.g. trajectory plot.
+\item Describe our algorithm in sufficient detail.
+\item Ensure our experimental figures have at least one version with
+  scale bars.
+\item Write script to generate figures with cartoon on top of
+  microscopy images.
+\item Store our preferred geometric (and non-geometric) parameters in
+  a python module, which is used both for creating figures (see above)
+  and for running simulations.
+\item Python script to write out latex with parameters.
+\item Fix stepping analysis python module to categorize zero-length
+  steps separately from other steps, particularly in terms of stepping
+  times.  Alternately, change C++ to make it possible to identify
+  which foot lifted if it didn't move.
+\item Update plotting scripts to use stepping analysis python module,
+  or other modules.
+\item Write up how we estimate one-bound/bothbound time ratio from
+  processivity.  Ensure simulation obeys this?
+\item Keep trying to get data from Yildiz.
+\end{enumerate}
+
+\subsection{John}
+\begin{enumerate}
+\item Proofread the algorithm description, improve its writing, and
+  check against code.
+\item Figure out how to do no-unbinding simulations to get Yildiz
+  comparison data.  Also this gives us unbinding rates that will agree
+  with our stepping time, etc. \verb!src/simulate_unbinding_rates.cpp!
+\item Play with parameters to get stepping length histogram more
+  reasonable (this automatically gives us the velocity).
+\item Run long/many simulations with final parameters.
+\item Run a low-ATP simulation for comparison data.
+\item Nice final version of stepping length histogram.
+\item Nice final version of tension-gating Yildiz comparison.
+\item Consider a no-binding simulation and a separable model.  Create
+  a figure demonstrating/testing whether the histogram of final
+  displacement is independent of initial displacement.
+\item Consider a simple Monte Carlo that just uses our no-unbinding
+  and no-binding simulations to model dynein (like Yildiz).
+\end{enumerate}
+
+\section{Papers we should cite}
+This paper says something interesting~\cite{leschziner}.
+
 % \pnasbreak splits and balances the columns before the references.

### 2018-06-21 scripts/generate-paper-model-figures.py
Add progress on model-cryoem figure script

@@ -3,30 +3,58 @@
 from __future__ import division
 import numpy as np
 import time, signal, sys, os, matplotlib, subprocess, re
+
+if 'show' not in sys.argv:
+    matplotlib.use('Agg')
+
 import dynein.draw.cartoon as cartoon
 
 sys.path.insert(0, os.getcwd() + "/data/")
 import paper_params as params
-
-if 'show' not in sys.argv:
-    matplotlib.use('Agg')
 
 import argparse
 import datetime
 import dynein.draw.cartoon as cartoon
 import matplotlib.pyplot as plt
 import matplotlib.image as mpimg
+from scipy import ndimage
 
-poststroke = mpimg.imread('papers/paper/figures/schematic-poststroke.png')
-prestroke = mpimg.imread('papers/paper/figures/schematic-prestroke.png')
+
+def plot_dynein_equilibrium_onebound(fig, start_x_px, start_y_px, px_per_nm, start_bb_angle):
+    print(px_per_nm)
+    Xs = [0, 0, 0, 0, 0]
+    Ys = [0, 0, 0, 0, 0]
+    bba_abs = params.eqb
+    bma_abs = params.eqb + params.eqmpost - np.pi
+    ta_abs = bma_abs + np.pi
+    uma_abs = params.eqb + params.eqmpre - np.pi
+
+    Xs[0] = start_x_px
+    Xs[1] = Xs[0] + params.ls*np.cos(start_bb_angle+bba_abs)*px_per_nm
+    Xs[2] = Xs[1] + params.lt*np.cos(start_bb_angle+bma_abs)*px_per_nm
+    Xs[3] = Xs[2] + params.lt*np.cos(start_bb_angle+ta_abs) *px_per_nm
+    Xs[4] = Xs[3] + params.ls*np.cos(start_bb_angle+uma_abs)*px_per_nm
+
+    Ys[0] = start_y_px
+    Ys[1] = Ys[0] + params.ls*np.sin(start_bb_angle+bba_abs)*px_per_nm
+    Ys[2] = Ys[1] + params.lt*np.sin(start_bb_angle+bma_abs)*px_per_nm
+    Ys[3] = Ys[2] + params.lt*np.sin(start_bb_angle+ta_abs) *px_per_nm
+    Ys[4] = Ys[3] + params.ls*np.sin(start_bb_angle+uma_abs)*px_per_nm
+
[…]

### 2018-06-22 scripts/generate-paper-model-figures.py
mini commit

@@ -44,10 +44,12 @@ def plot_dynein_equilibrium_onebound(fig, start_x_px, start_y_px, px_per_nm, sta
     Rs = np.array([params.radius_b, params.radius_m, params.radius_t, params.radius_m, params.radius_b])*px_per_nm
 
     plt.figure(fig.number)
-    plt.plot(Xs, Ys)
-    plt.scatter(Xs, Ys, s=Rs*Rs)
+    plt.plot(Xs, Ys, c="black", zorder=1)
+    plt.scatter(Xs, Ys, s=Rs*Rs, zorder=2)
 
 merged_burgess_img = mpimg.imread('papers/paper/figures/model-raw-images/burgess-fig-4-cropped.png')
+merged_chowdhury_img = mpimg.imread('papers/paper/figures/model-raw-images/chowdhury-fig-1-cropped.png')
+merged_redwine_img = mpimg.imread('papers/paper/figures/model-raw-images/redwine-supplemental-cropped.png')
 
 px_per_nm = 4.13
 
@@ -58,3 +60,27 @@ plt.plot([57, 57+15*px_per_nm], [10, 10])
 
 plt.axis('off')
 plt.savefig("plots/burgess-model-figure.pdf", bbox_inches='tight', format="pdf")
+
+
+
+
+px_per_nm = 4.13
+
+fig = plt.figure()
+plt.imshow(merged_chowdhury_img)
+plot_dynein_equilibrium_onebound(fig, 50, 25, px_per_nm, np.pi*1.23)
+
+plt.axis('off')
+plt.savefig("plots/chowdhury-model-figure.pdf", bbox_inches='tight', format="pdf")
+
+
+
+
+px_per_nm = 4.13
+
+fig = plt.figure()
+plt.imshow(merged_redwine_img)
+plot_dynein_equilibrium_onebound(fig, 50, 25, px_per_nm, np.pi*1.23)
+
+plt.axis('off')
+plt.savefig("plots/redwine-model-figure.pdf", bbox_inches='tight', format="pdf")

### 2018-06-23 data/parameters.py
finish up model figure

@@ -1,18 +1,0 @@
-#! /usr/bin/env python3
-
-kb = 9e7
-kub = 100
-runtime = 1.0
-c = -0.35
-seed = 1.0
-cb = 0.1
-cm = 0.4
-ct = 0.2
-
-eqb = 116.5
-eqmpre = 200
-eqmpost = 224
-eqt = 0
-
-lt = 10
-ls = 22.1

### 2018-06-26 data/paper_params.py
Fix minor bug in parameters-to-latex script

@@ -6,7 +6,7 @@ k_ub = 75 # s^-1
 trajectory_k_b  = 1e25 # s^-1
 trajectory_k_ub = 1e9 # s^-1
 
-c = -0.35
+cexp = -0.35
 
 cb = 0.1 # kbT
 cm = 0.4 # kbT

### 2018-06-26 scripts/parameters-to-latex.py

@@ -29,8 +29,6 @@ def latex_format(x):
             if m == '1':
                 return r'10^{'+e+'}'
             return m + r'\times 10^{' + e+ '}'
-    if isinstance(x, str):
-        x = x.replace('-', '_')
     return x
 
 parameters = {
@@ -38,7 +36,7 @@ parameters = {
 "k_ub" :              params.k_ub,
 "trajectory_k_b" :    params.trajectory_k_b,
 "trajectory_k_ub" :   params.trajectory_k_ub,
-"c" :                 params.c,
+"cexp" :              params.cexp,
 "cb" :                params.cb,
 "cm" :                params.cm,
 "ct" :                params.ct,

### 2018-06-29 papers/paper/paper.tex
Add progress on model-cryoem figure script
mini commit
finish up model figure
Fix minor bug in parameters-to-latex script
Make new crystal structure superimposed figure work (sort of) - still needs work

@@
 
-\input{../../data/paper_static_stepping_parameters.tex}
+\input{../../data/paper_params.tex}
 
@@
 
-\begin{figure*}[tbhp]
+\begin{figure}[tbhp]
 \centering
-\includegraphics[width=0.3\linewidth]{figures/onebound-cartoon.pdf}%
-\includegraphics[width=0.3\linewidth]{figures/bothbound-cartoon.pdf}%
-\includegraphics[width=0.3\linewidth]{figures/schematic-1-superimposed}\\
-\includegraphics[width=0.15\linewidth]{../../plots/poststroke-figure.pdf}%
-\includegraphics[width=0.15\linewidth]{../../plots/prestroke-figure.pdf}%
-\includegraphics[width=0.3\linewidth]{figures/schematic-binding-angle}
+\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}%
+\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
 \caption{}
+\end{figure}
+
+\begin{figure}[tbhp]
+\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
+%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
+\includegraphics[width=0.5\linewidth]{../../plots/chowdhury-model-figure.pdf}\\
+\includegraphics[width=0.5\linewidth]{../../plots/crystal-model-figure.pdf}%
+\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over ---maybe the burgess paper is bad since it uses dynein c, which seems like an axonemal dynein}
 \label{fig:duration-length}
-\end{figure*}
+\end{figure}
 
@@
 $L_t$ & $\lt nm$ & & \cite{nativestructure}\\
+$c$ & $\cexp$ & & \\
 $\theta_b$ & $\eqb$ &  & \\
@@
 \item Keep trying to get data from Yildiz.
+\item Add force-dependent plots to compare with yildiz?
 \end{enumerate}

### 2018-06-29 scripts/generate-paper-model-figures.py

@@ -43,37 +43,39 @@ def plot_dynein_equilibrium_onebound(fig, start_x_px, start_y_px, px_per_nm, sta
     Rs = np.array([params.radius_b, params.radius_m, params.radius_t, params.radius_m, params.radius_b])*px_per_nm
 
     plt.figure(fig.number)
-    plt.plot(Xs, Ys, c="black", zorder=1)
-    plt.scatter(Xs, Ys, s=Rs*Rs, c="#aeaae5", zorder=2, edgecolor='black')
+    plt.plot(Xs, Ys, c="white", zorder=1)
+    plt.scatter(Xs, Ys, s=Rs, c="#aeaae5", zorder=2, edgecolor='white')
 
 merged_burgess_img = mpimg.imread('papers/paper/figures/model-raw-images/burgess-fig-4-cropped.png')
 merged_chowdhury_img = mpimg.imread('papers/paper/figures/model-raw-images/chowdhury-fig-1-cropped.png')
 merged_redwine_img = mpimg.imread('papers/paper/figures/model-raw-images/redwine-supplemental-cropped.png')
+merged_crystalstruct_img = mpimg.imread('papers/paper/figures/model-raw-images/pymol-cytoplasmic-superimpose.png')
 
 px_per_nm = 4.13
-
 fig = plt.figure()
 plt.imshow(merged_burgess_img, origin="lower") # angles rotate ccw
 plot_dynein_equilibrium_onebound(fig, 57, 29, px_per_nm, 60*np.pi/180.0-params.eqb*np.pi/180.0)
 plt.plot([57, 57+15*px_per_nm], [10, 10])
-
 plt.axis('off')
 plt.savefig("plots/burgess-model-figure.pdf", bbox_inches='tight', format="pdf")
 
 
-
-
 px_per_nm = 2.78
-
 fig = plt.figure()
 plt.imshow(merged_chowdhury_img) # angles rotate cw
 plot_dynein_equilibrium_onebound(fig, 68, 122, px_per_nm, np.pi)
 plt.plot([142, 142+25*px_per_nm], [175, 175])
-
 plt.axis('off')
 plt.savefig("plots/chowdhury-model-figure.pdf", bbox_inches='tight', format="pdf")
 
 
+px_per_nm = 25
+fig = plt.figure()
+plt.imshow(merged_crystalstruct_img) # angles rotate cw
[…]

### 2018-07-29 papers/paper/paper.tex
Add more descriptive caption to model figure

@@
 \includegraphics[width=0.5\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over ---maybe the burgess paper is bad since it uses dynein c, which seems like an axonemal dynein}
+\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}.
+\textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}.
+\textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound monomer (ID 4RH7), yellow being apo monomer (ID 3VKH), docked together using linkers as a reference point.
+Orange indicates the linker region used to dock the two monomers.}
 \label{fig:duration-length}

### 2018-07-30 papers/paper/paper.tex
Add citation about axonemal and cytoplasmic dynein having similar structures

--- 2018-06-29 papers/paper/paper.tex
@@
 
-\begin{figure}[tbhp]
-\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
+\begin{figure*}[tbhp]
+\includegraphics[width=0.3\linewidth]{../../plots/burgess-model-figure.pdf}%
 %% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
-\includegraphics[width=0.5\linewidth]{../../plots/chowdhury-model-figure.pdf}\\
-\includegraphics[width=0.5\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over ---maybe the burgess paper is bad since it uses dynein c, which seems like an axonemal dynein}
+\includegraphics[width=0.3\linewidth]{../../plots/chowdhury-model-figure.pdf}%
+\includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
+\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
+\textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}.
+\textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point.
+Orange indicates the linker region used to dock the two monomers.}
 \label{fig:duration-length}
-\end{figure}
+\end{figure*}
 

### 2018-08-05 papers/paper/paper.tex
Add new caption to paper.tex
Change paper_params eq angles and lengths to better match the burgess cryo-em figure; using model fitting in lieu of values reported from paper

@@
 \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point.
-Orange indicates the linker region used to dock the two monomers.}
+Orange indicates the linker region used to dock the two monomers.
+Left figure has a scale bar of 15nm, middle 25nm and right 28.8nm between the two binding domains.}
 \label{fig:duration-length}
@@
 $k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
-$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
-$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
+$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
+$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
 $c$ & $\cexp$ & & \\
@@
 \item Describe our algorithm in sufficient detail.
-\item Ensure our experimental figures have at least one version with
-  scale bars.
-\item Write script to generate figures with cartoon on top of
-  microscopy images.
-\item Store our preferred geometric (and non-geometric) parameters in
-  a python module, which is used both for creating figures (see above)
-  and for running simulations.
-\item Python script to write out latex with parameters.
 \item Fix stepping analysis python module to categorize zero-length
@@
 \item Add force-dependent plots to compare with yildiz?
+\item Figure out which of the model-em subfigures to include/remove
 \end{enumerate}

### 2018-08-06 papers/paper/paper.tex
Make the paper trajectory plot look prettier

@@
 
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
-\caption{Placeholder image of a frog with a long example caption to show justification setting.}
-\label{fig:trajectory}
-\end{figure}
-
 %% \begin{figure}%[tbhp]
@@
 
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
+\caption{\textbf{Model processive trajectory.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$.
+\textit{Middle view:} Cartoon snapshot of model at time indicated by bottom foot.
+\textit{Bottom view:} y-projection.}
+\label{fig:trajectory}
+\end{figure}
+
 \section{To do items}
@@
 \item Figure out which of the model-em subfigures to include/remove
+\item add cartoon back to trajectory plot
 \end{enumerate}

### 2018-08-06 scripts/generate-stepping-data.py

@@ -4,8 +4,6 @@ import os, sys
 import numpy as np
 import dynein.run as run
 
-runtime = 1e-1
-
 os.system("make generate_stepping_data")
 
 parser = argparse.ArgumentParser()
@@ -15,6 +13,12 @@ parser.add_argument("-m", "--cm", type=float, help="Manually set the cm value, d
 parser.add_argument("-t", "--ct", type=float, help="Manually set the ct value, default=0.2", default=0.2)
 parser.add_argument("-k", "--kb", type=float, help="Manually set the binding rate", default=3e9)
 parser.add_argument("-u", "--kub", type=float, help="Manually set the unbinding rate", default=1000)
+parser.add_argument("-y", "--ls", type=float, help="", default=10)
+parser.add_argument("-w", "--lt", type=float, help="", default=10)
+parser.add_argument("-aa", "--eqb", type=float, help="", default=10)
+parser.add_argument("-bb", "--eqt", type=float, help="", default=10)
+parser.add_argument("-cc", "--eqmpre", type=float, help="", default=10)
+parser.add_argument("-dd", "--eqmpost", type=float, help="", default=10)
 parser.add_argument("-x", "--unbindingconst", type=float, help="Manually set the unbinding const", default=0.0)
 parser.add_argument("-r", "--runtime", type=float, help="Manually set the runtime value, default=0.1", default=0.1)
 parser.add_argument("-f", "--framerate", type=float, help="Manually set the frame rate, default=1e-10", default=1)
@@ -35,12 +39,12 @@ basename = run.sim(**{"k_b": args.kb,
                       "cb": args.cb, # 0.1?
                       "cm": args.cm, # 0.4?
                       "ct": args.ct, # 0.2?
-                      "ls": 10.49, # from urnavicius 2015 (paper.bib)
-                      "lt": 23.8,  # from urnavicius 2015
-                      "eqb": 120,  # from redwine 2012 supplemental
-                      "eqmpre": 200, # from burgess 2002, 360-160
-                      "eqmpost": 224, # from burgess 2002, 360-136
-                      "eqt": 0,
+                      "ls": args.ls,
+                      "lt": args.lt,
+                      "eqb": args.eqb,  # from redwine 2012 supplemental
+                      "eqmpre": args.eqmpre, # from burgess 2002, 360-160
+                      "eqmpost": args.eqmpost, # from burgess 2002, 360-136
+                      "eqt": args.eqt,
[…]

### 2018-08-06 scripts/paper-trajectory-plt.py

@@ -12,6 +12,7 @@ import dynein.draw.cartoon as cartoon
 import matplotlib.pyplot as plt
 from matplotlib import gridspec
 from matplotlib.patches import Rectangle
+from matplotlib.ticker import ScalarFormatter
 
 import io
 
@@ -89,27 +90,37 @@ ax0.set_ylabel("x-projection (nm)")
 ax0.set_ylim(-150,150)
 plt.setp(ax0.get_xticklabels(), visible=False)
 
-ax0.plot(times, nbxs, label="near foot", c='b')
-ax0.plot(times, fbxs, label="far foot", c='r')
+ax0.plot(times*1e6, nbxs, label="near foot", c='b')
+ax0.plot(times*1e6, fbxs, label="far foot", c='r')
 
-ax0.legend(loc="upper right")
+ax0.legend(loc="lower right")
+ax0.axes.get_xaxis().set_visible(False)
+
+# ax = plt.gca().xaxis
+# ax.set_major_formatter(ScalarFormatter()) 
+# ax0.set_xticklabels([])
 
 # y projection
-ax1.set_xlabel("time (s)")
+ax1.set_xlabel("time ($\mu s$)")
 ax1.set_ylabel("y-projection (nm)")
 
 ax1.set_ylim(y_min_yproj-1,y_max_yproj+1)
 
-ax1.plot(times, nbys, label="near foot", c='b')
-ax1.plot(times, fbys, label="far foot", c='r')
-ax1.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+ax1.plot(times*1e6, nbys, label="near foot", c='b')
+ax1.plot(times*1e6, fbys, label="far foot", c='r')
+
+ax1.set_ylim(-20,65)
+
+# ax = plt.gca().xaxis
+# ax.set_major_formatter(ScalarFormatter())
+# ax1.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
 
 gs.tight_layout(fig, pad=2)
 
-plt.gcf().suptitle(
-    raw_run_conditions +
-    r' $k_{b}: \kb, k_{ub}: \kub$',
-    fontsize=14)
+# plt.gcf().suptitle(
+#     raw_run_conditions +
+#     r' $k_{b}: \kb, k_{ub}: \kub$',
+#     fontsize=14)
 
 os.system('mkdir -p plots')
 plt.savefig("plots/paper_trajectory_plot.pdf")

### 2018-08-07 papers/paper/paper.tex
Add cartoon snapshot back to trajectory plot.

--- 2018-08-05 papers/paper/paper.tex
@@
 
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
+\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$.
+\textit{Middle view:} Cartoon snapshot of model at time indicated by bound binding domain.
+Teal lines correspond to the microtubule.
+\textit{Bottom view:} y-projection.}
+\label{fig:trajectory}
+\end{figure}
+
 \section{To do items}
@@
 \item Document carefully where all figures and data comes from.
-\item Make our cool figures presentable, e.g. trajectory plot.
 \item Describe our algorithm in sufficient detail.

### 2018-08-07 scripts/paper-trajectory-plt.py

@@ -77,17 +77,17 @@ y_max_yproj = np.max([np.max(nbys), np.max(fbys)])
 fig = plt.figure()
 plt.rc('text', usetex=True)
 
-gs = gridspec.GridSpec(2, 1, height_ratios=[2, 1])
+gs = gridspec.GridSpec(3, 1, height_ratios=[4, 1, 4])
 ax0 = fig.add_subplot(gs[0])
 ax1 = fig.add_subplot(gs[1], sharex=ax0)
-plt.setp([ax0.get_xticklabels()], visible=False)
+ax2 = fig.add_subplot(gs[2], sharex=ax0)
+plt.setp([ax0.get_xticklabels(), ax1.get_xticklabels()], visible=False)
 
 ### Trajectory plots
 
 # x projection
 ax0.set_ylabel("x-projection (nm)")
-# ax0.set_ylim(y_min_xproj-1,y_max_xproj+1)
-ax0.set_ylim(-150,150)
+ax0.set_ylim(-50,150)
 plt.setp(ax0.get_xticklabels(), visible=False)
 
 ax0.plot(times*1e6, nbxs, label="near foot", c='b')
@@ -96,31 +96,53 @@ ax0.plot(times*1e6, fbxs, label="far foot", c='r')
 ax0.legend(loc="lower right")
 ax0.axes.get_xaxis().set_visible(False)
 
-# ax = plt.gca().xaxis
-# ax.set_major_formatter(ScalarFormatter()) 
-# ax0.set_xticklabels([])
+# cartoons
+# ax1.axis('off')
+ax1.set_aspect('equal', 'datalim')
+plt.setp(ax1.get_xticklabels(), visible=False)
+plt.setp(ax1.get_yticklabels(), visible=False)
+
+x_axes_size = ax1.get_xlim()[1] - ax1.get_xlim()[0]
+y_axes_size = ax1.get_ylim()[1] - ax1.get_ylim()[0]
+
+x_scaling = 2e-2 #
+y_scaling = 2e-2
+
+cartoon_draw_times_x_proj = np.array([9.241e-07, 3.0*1e-6, 4.899*1e-6, 7.0155e-06, 9.0*1e-6])
+
+plt.sca(ax1)
+for t in cartoon_draw_times_x_proj:
+    idx = np.where(data[:,1] >= t)[0][0]
+    Xs = np.abs(x_scaling*data[idx,7:16:2])
[…]

### 2018-08-08 scripts/paper-trajectory-plt.py
Slightly perfect arrow placement for trajectory plot.

@@ -148,9 +148,9 @@ ax2.set_ylim(-10,75)
 for t in cartoon_draw_times_x_proj:
     idx = np.where(data[:,1] >= t)[0][0]
     X = np.min([data[idx,7], data[idx,15]])
-    Y = np.max([data[idx,8], data[idx,16]])
-    ax0.annotate('', xy=(t*1e6, X-10), xytext=(t*1e6, X-10.01), arrowprops=dict(facecolor='black', width=1, headwidth=3, headlength=3, shrink=0))
-    ax2.annotate('', xy=(t*1e6, Y+10), xytext=(t*1e6, Y+10.01), arrowprops=dict(facecolor='black', width=1, headwidth=3, headlength=3, shrink=0))
+    Y = np.min([data[idx,8], data[idx,16]])
+    ax0.annotate('', xy=(t*1e6, X-7), xytext=(t*1e6, X-7.01), arrowprops=dict(facecolor='black', width=1, headwidth=3, headlength=3, shrink=0))
+    ax2.annotate('', xy=(t*1e6, Y-3), xytext=(t*1e6, Y-3.01), arrowprops=dict(facecolor='black', width=1, headwidth=3, headlength=3, shrink=0))
 
 gs.tight_layout(fig, pad=0.01)
 

### 2018-08-09 scripts/make_paper_unbinding_probability_plot.py
Add unbinding rate vs L plot to paper.tex.

@@ -1,0 +1,85 @@
+#! /usr/bin/env python3
+
+from __future__ import division
+import numpy as np
+import time, signal, sys, os, matplotlib, subprocess, re
+
+if 'show' not in sys.argv:
+    matplotlib.use('Agg')
+
+import argparse
+import datetime
+import dynein.draw.cartoon as cartoon
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+from matplotlib.patches import Rectangle
+
+import io
+
+EPSILON = 1e-7
+
+def equal(f1, f2):
+    return abs(f1-f2) < EPSILON
+
+data_files = []
+for fname in os.listdir("data"):
+    if os.path.isfile("data/" + fname):
+        if ("paper_unbinding_probability__" in fname and ".txt" in fname):
+            if ("~" not in fname):
+                data_files.append("data/" + fname)
+
+if len(data_files) == 0:
+    print("No files of form data/*.txt found. Exiting.")
+    exit(1)
+
+Ls = []
+mean_lagging_probability_per_L = []
+mean_leading_probability_per_L = []
+leading_probabilities_vs_time = []
+lagging_probabilities_vs_time = []
+
+for data_file in data_files:
+    data = np.loadtxt(data_file, dtype = np.float64)
+    if len(data) == 15:
+        continue
+    start_L_idx = data_file.find('L-')+2
+    end_L_idx = data_file[start_L_idx:].find(',') + start_L_idx
+    L = float(data_file[start_L_idx:end_L_idx])
+
+    times = data[:,0]
+    near_unbinding_probabilities = data[:,1]
+    far_unbinding_probabilities = data[:,2]
+
+    near_binding_xs = data[:,5]
+    far_binding_xs = data[:,9]
+
+    lagging_unbinding_probabilities = np.array([far_unbinding_probabilities[s] if near_binding_xs[s] > far_binding_xs[s] else near_unbinding_probabilities[s] for s in range(len(times))])
+    leading_unbinding_probabilities = np.array([near_unbinding_probabilities[s] if near_binding_xs[s] > far_binding_xs[s] else far_unbinding_probabilities[s] for s in range(len(times))])
+    
+    Ls.append(L)
+    mean_lagging_probability_per_L.append(np.mean(lagging_unbinding_probabilities))
[…]

### 2018-08-10 papers/paper/paper.tex
Add trajectory seed # specification in paper_params; add arrows to trajectory plot
Slightly perfect arrow placement for trajectory plot.
Add unbinding rate vs L plot to paper.tex.
Change up makefile and paper.tex to make room for new figures, remove old figures

@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/paper_static_time_vs_length}
+\includegraphics[width=\linewidth]{../../plots/paper_time_vs_length}
 \caption{Heatmap of relationship between step length and time.}
@@
 
-\begin{figure*}[tbhp]
-  \begin{subfigure}{0.5\textwidth}
+%% \begin{figure*}[tbhp]
+%%   \begin{subfigure}{0.5\textwidth}
+%%     \centering
+%%     \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
+%%   \end{subfigure}%
+%%   \begin{subfigure}{0.5\textwidth}
+%%     \centering
+%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
+%%   \end{subfigure}
+%%   \begin{subfigure}{0.5\textwidth}
+%%     \centering
+%%     \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
+%%   \end{subfigure}%
+%%   \begin{subfigure}{0.5\textwidth}
+%%     \centering
+%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
+%%   \end{subfigure}
+%%   \begin{subfigure}{0.5\textwidth}
+%%     \centering
+%%     \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
+%%     \subcaption{Static unbinding rate}
+%%   \end{subfigure}%
+%%   \begin{subfigure}{0.5\textwidth}
+%%     \centering
+%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
+%%     \subcaption{Exponential unbinding rate}
+%%   \end{subfigure}
+%% \caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
+%% \label{fig:lengthhist}
+%% \end{figure*}
+
+\begin{figure}[tbhp]
   \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_dwell_time_histogram}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
+\caption{\textbf{Basic behavior of our model}}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[tbhp]
   \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
-  \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
-  \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
-    \subcaption{Static unbinding rate}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
-    \subcaption{Exponential unbinding rate}
-  \end{subfigure}
-\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
-\label{fig:lengthhist}
-\end{figure*}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_histogram.pdf}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
+\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
+\label{fig:}
+\end{figure}
 
 \begin{figure*}[tbhp]
-    \includegraphics[width=0.5\linewidth]{../../plots/paper_static_foot_order_histogram}
-    \includegraphics[width=0.5\linewidth]{../../plots/paper_exponential_foot_order_histogram}
+    \includegraphics[width=0.5\linewidth]{../../plots/paper_foot_order_histogram.pdf}
 \caption{The left plot is the $C=0$ case where the unbinding rate is
@@
 Teal lines correspond to the microtubule.
-\textit{Bottom view:} y-projection.}
+\textit{Bottom view:} y-projection.
+Arrows on top and bottom plots correspond to respective snapshot times.}
 \label{fig:trajectory}
@@
 \item Figure out which of the model-em subfigures to include/remove
-\item add cartoon back to trajectory plot
 \end{enumerate}

### 2018-08-10 scripts/color_hist.py

@@ -11,7 +11,7 @@ import glob
 
 parser = argparse.ArgumentParser(description='Script to generate 2 dimensional histogram from dynein stepping data')
 
-parser.add_argument('-d', '--datafile', dest='data_file', action='store', default='data/paper_static_stepping_data-1.txt',
+parser.add_argument('-d', '--datafile', dest='data_file', action='store', default='data/paper_exponential_stepping_data-1.txt',
                     help='path to data file', type=str)
 parser.add_argument('-b', '--bins', dest='bins', action='store', default=20,
                     help='number of bins for x and y axes', type=int)
@@ -20,7 +20,7 @@ parser.add_argument('-v', '--verbose', dest='verbose', action='store_true', defa
 parser.add_argument('-s', '--show', dest='show', action='store_true', default=False,
                     help='show graphs in matplotib windows')
 parser.add_argument('-a', '--all', dest='All', action='store_true', default=False,
-                    help='generate plots for all paper_static_stepping_data files')
+                    help='generate plots for all paper_exponential_stepping_data files')
 parser.add_argument('-c', '--colormap', dest='cmap', action='store', type=str,
                     default=None, help='set color map for plots')
 
@@ -80,10 +80,10 @@ if not ALL:
     step_times = onebound_times + bothbound_times
 else:
     data_files = []
-    for fname in glob.glob("data/paper_static_stepping_data*.txt"):
+    for fname in glob.glob("data/paper_exponential_stepping_data*.txt"):
         data_files.append(fname)
     if len(data_files) == 0:
-        print("Error, no files of form data/paper_static_stepping_data*.txt found. Exiting.")
+        print("Error, no files of form data/paper_exponential_stepping_data*.txt found. Exiting.")
         exit(1)
 
     for data_file in data_files:

### 2018-08-10 papers/paper/paper.tex
Add new plots to paper. TODO: make them look nicer

@@
   \centering
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}%
   \includegraphics[width=0.5\linewidth]{../../plots/paper_dwell_time_histogram}
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}%
   \includegraphics[width=0.5\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
@@
   \centering
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
+  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}%
   \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_histogram.pdf}

### 2018-08-10 scripts/make_all_stepping_plots.py

@@ -200,7 +200,7 @@ plt.savefig("plots/stepping_length_histogram.pdf", format="pdf")
 plt.close(fig)
 
 #step time histogram
-fig = plt.figure(figsize=(8, 8), dpi=300)
+fig = plt.figure(dpi=300)
 plt.rc('text', usetex=True)
 
 gs = gridspec.GridSpec(4, 1, height_ratios=[1, 1, 1, 1])
@@ -242,6 +242,46 @@ plt.subplots_adjust(hspace=0.6)
 
 plt.show()
 plt.savefig("plots/stepping_time_histogram.pdf", format="pdf")
+plt.close(fig)
+
+# OB time histogram
+fig = plt.figure(dpi=300)
+plt.rc('text', usetex=True)
+
+if len(step_times) > 0:
+    plt.gca().hist(onebound_times, bins=np.logspace(np.log10(1e-10),np.log10(1e-2), 50))
+else:
+    print("Error, no step_times")
+    exit(1)
+
+plt.gca().set_title("onebound times (theory: 6e-5)")
+plt.gca().set_ylabel("Frequency")
+plt.gca().set_xscale('log')
+# ax1.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+
+if args.parameters_filename != "":
+    plt.gcf().suptitle(run_conditions + r' $k_{b}: \kb, k_{ub}: \kub, cb: \cb, cm: \cm, ct: \ct, runtime: \runtime$', fontsize=14)
+
+plt.show()
+plt.savefig("plots/onebound_time_histogram.pdf", format="pdf")
+plt.close(fig)
+
+# BB (dwell) time histogram
+fig = plt.figure(dpi=300)
+plt.rc('text', usetex=True)
+
+if len(step_times) > 0:
+    plt.gca().hist(bothbound_times, bins=np.logspace(np.log10(1e-10),np.log10(1e-2), 50))
+
+plt.gca().set_title("bothbound times")
+plt.gca().set_ylabel("Frequency")
+plt.gca().set_xscale('log')
+# ax1.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+
+if args.parameters_filename != "":
+    plt.gcf().suptitle(run_conditions + r' $k_{b}: \kb, k_{ub}: \kub, cb: \cb, cm: \cm, ct: \ct, runtime: \runtime$', fontsize=14)
+
[…]

### 2018-08-10 papers/paper/paper.tex
Make paper plots look better

--- 2018-08-10 papers/paper/paper.tex
@@
   \centering
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_dwell_time_histogram}
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_stepping_length_histogram}
+  \includegraphics[width=\linewidth]{../../plots/paper_dwell_time_histogram}
+  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
 \caption{\textbf{Basic behavior of our model}}
@@
   \centering
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_histogram.pdf}
-  \includegraphics[width=0.5\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_onebound_histogram.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
 \caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}

### 2018-08-10 scripts/make_paper_unbinding_probability_plot.py

@@ -81,5 +81,8 @@ plt.xlabel("|L| (nm)")
 plt.ylabel("Lagging $k_{ub}$ fraction")
 plt.legend()
 
+plt.gca().spines["top"].set_visible(False)
+plt.gca().spines["right"].set_visible(False)
+plt.tight_layout()
 plt.savefig("plots/paper_unbinding_probability_vs_L.pdf", format="pdf")
 plt.close(fig)

### 2018-08-14 scripts/color_hist2.py
change up color_hist2 to work with multiple files

@@ -13,8 +13,8 @@ import dynein.data as data
 
 parser = argparse.ArgumentParser(description='Script to generate 2 dimensional histogram from dynein stepping data')
 
-parser.add_argument('-d', '--datafile', dest='data_file', action='store', default='data/paper_exponential_stepping_data-1.txt',
-                    help='path to data file', type=str)
+parser.add_argument('-d', '--datawildcard', dest='data_wc', action='store', default='paper_main',
+                    help='data file wildcard', type=str)
 parser.add_argument('-b', '--bins', dest='bins', action='store', default=20,
                     help='number of bins for x and y axes', type=int)
 parser.add_argument('-v', '--verbose', dest='verbose', action='store_true', default=False,
@@ -30,24 +30,31 @@ parser.add_argument('-c', '--colormap', dest='cmap', action='store', type=str,
 args = parser.parse_args()
 
 VERBOSE = args.verbose
-DATAFILE = args.data_file
+DATAWC = args.data_wc
 NUM_BINS = args.bins
 SHOW = args.show
 #ALL = args.All
 CMAP = args.cmap
 
-if os.path.exists('color_hist.py'):
+if os.path.exists('color_hist2.py'):
     if VERBOSE: print("navigating to root directory")
     os.chdir('../')
 
+data_files = []
+for fname in os.listdir("data/"):
+    if os.path.isfile("data/" + fname):
+        if (DATAWC in fname and "stepping_data" in fname and ".txt" in fname and "~" not in fname):
+            data_files.append("data/" + fname)
 
-if not os.path.isfile(DATAFILE):
-    print("Could not find data file. Please specify path using -d")
+if len(data_files) == 0:
+    print("No files matching wildcard " + args.data_wc)
     exit(1)
-        # load in data
+
+# load in data
 if VERBOSE: print("Data file found- loading data...")
-Data = data.SteppingData(DATAFILE)
-   
+datasets = []
+for df in data_files:
+    datasets.append(data.SteppingData(df))
 
 
 #--------------------------------------------------------------------------------------#
@@ -126,8 +133,13 @@ seed_label = ''
 #            yIsTimeValue=False,
 #            filename='plots/time-vs-length{}.pdf'.format(seed_label))
 
-plotCounts(Data.initial_displacements,
-           Data.final_displacements,
+initial_displacements = np.concatenate([s.initial_displacements for s in datasets])
[…]

### 2018-08-15 papers/paper/paper.tex
Move to use color_hist2.py to generate 2d histograms
Slight change to eqb

@@
 $c$ & $\cexp$ & & \\
-$\theta_b$ & $\eqb$ &  & \\
+$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
 $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
@@
 \section{Results}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/paper_time_vs_length}
-\caption{Heatmap of relationship between step length and time.}
-\label{fig:duration-length}
-\end{figure}
 

### 2018-08-16 papers/paper/paper.tex
Add experimental values to paper table

@@
 $k_b$ & $\kb s^{-1}$&  & \\
-$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
-$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
-$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
+$k_{ub}$ & $\kub s^{-1}$ & & \\
+$L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
+$L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
 $c$ & $\cexp$ & & \\
 $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
-$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
-$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
+$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
+$\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
 $\theta_t$ & $\eqt$ &  & \\
-$D$ & 0.2 nm &  & \\
+$R_t$ & $\radius_t$ & 8nm & \cite{burgess-paper}\\
+$R_m$ & $\radius_m$ & 11nm & \cite{burgess-paper}\\
+$R_b$ & $\radius_b$ & 3.5nm & \cite{burgess-paper}\\
 

### 2018-08-16 papers/paper/paper.tex
Add new better model figure which shows realistic dynein full-length structure from Grotjahn et al 2018

--- 2018-08-15 papers/paper/paper.tex
@@
 
-\begin{figure*}[tbhp]
-\includegraphics[width=0.3\linewidth]{../../plots/burgess-model-figure.pdf}%
-%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
-\includegraphics[width=0.3\linewidth]{../../plots/chowdhury-model-figure.pdf}%
-\includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
+\begin{figure}[tbhp]
+\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
+\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
+%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
 \caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
-\textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}.
-\textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point.
+\textit{Grey bg:} Model superimposed over full-length dimerized dynein bound to accessory proteins \cite{grotjahn}.
+}
+\label{fig:duration-length}
+\end{figure}
+
+%% \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point.
 Orange indicates the linker region used to dock the two monomers.
-Left figure has a scale bar of 15nm, middle 25nm and right 28.8nm between the two binding domains.}
-\label{fig:duration-length}
-\end{figure*}
+Left figure has a scale bar of 15nm, middle 26.3nm and right 28.8nm between the two binding domains.
 
@@
 $k_b$ & $\kb s^{-1}$&  & \\
-$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
-$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
-$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
+$k_{ub}$ & $\kub s^{-1}$ & & \\
+$L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
+$L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
 $c$ & $\cexp$ & & \\
 $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
-$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
-$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
+$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
+$\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
 $\theta_t$ & $\eqt$ &  & \\
-$D$ & 0.2 nm &  & \\
+$R_t$ & $\radiust$ & 8nm & \cite{burgess-paper}\\
+$R_m$ & $\radiusm$ & 11nm & \cite{burgess-paper}\\
+$R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\
 

### 2018-08-16 scripts/generate-paper-model-figures.py

@@ -22,13 +22,20 @@ import matplotlib.image as mpimg
 from scipy import ndimage
 
 
-def plot_dynein_equilibrium_onebound(fig, start_x_units, start_y_units, units_per_nm, mt_angle):
+def plot_dynein_equilibrium_onebound(fig, start_x_units, start_y_units, units_per_nm, mt_angle, flipx=False):
     Xs = [0, 0, 0, 0, 0]
     Ys = [0, 0, 0, 0, 0]
+
     bba_abs = mt_angle + params.eqb*np.pi/180.0
     bma_abs = bba_abs - np.pi + params.eqmpost*np.pi/180.0
     ta_abs = bma_abs - np.pi
     uma_abs = bma_abs - params.eqmpre*np.pi/180.0
+
+    if flipx:
+        bba_abs = np.pi - bba_abs
+        bma_abs = np.pi - bma_abs
+        ta_abs = np.pi - ta_abs
+        uma_abs = np.pi - uma_abs
 
     Xs[0] = start_x_units
     Xs[1] = Xs[0] + params.ls*np.cos(bba_abs)*units_per_nm
@@ -73,7 +80,8 @@ def plot_image(img, org, dpi):
     return fig
 
 merged_burgess_img = mpimg.imread('papers/paper/figures/model-raw-images/burgess-fig-4-cropped.png')
-merged_chowdhury_img = mpimg.imread('papers/paper/figures/model-raw-images/chowdhury-fig-1-cropped.png')
+# merged_chowdhury_img = mpimg.imread('papers/paper/figures/model-raw-images/chowdhury-fig-1-cropped.png')
+grotjahn_img = mpimg.imread('papers/paper/figures/model-raw-images/grotjahn-model-figure.png')
 merged_redwine_img = mpimg.imread('papers/paper/figures/model-raw-images/redwine-supplemental-cropped.png')
 merged_crystalstruct_img = mpimg.imread('papers/paper/figures/model-raw-images/pymol-cytoplasmic-superimpose.png')
 
@@ -86,15 +94,15 @@ plt.axis('off')
 plot_dynein_equilibrium_onebound(fig, 57, 29, units_per_nm, -np.pi*0.31)
 plt.savefig("plots/burgess-model-figure.pdf", format="pdf", interpolation='none', dpi=100, bbox_inches='tight')
 
-# chowdhury fig
-units_per_nm = 2.78
-scalebar_nm = 25
[…]

### 2018-08-16 papers/paper/paper.tex
Minor change to model fig caption

@@
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
-\textit{Grey bg:} Model superimposed over full-length dimerized dynein bound to accessory proteins \cite{grotjahn}.
-}
+\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
+\textit{Right:} Model superimposed over full-length dimerized dynein bound to accessory proteins, (map ID EMD-7000) \cite{grotjahn}.
+Left figure has a scale bar of 15nm, right 26.3nm between MTBD and AAA1 of motor domain.}
 \label{fig:duration-length}
@@
 Orange indicates the linker region used to dock the two monomers.
-Left figure has a scale bar of 15nm, middle 26.3nm and right 28.8nm between the two binding domains.
 
@@
 
-\begin{figure}[tbhp]
-  \centering
-   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
-   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
-   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}
+%% \begin{figure}[tbhp]
+%%   \centering
+%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
+%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
+%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}
 
-   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
-   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
-   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
-   \caption{\textbf{Model schematic superimposed on cryo-EM images of
-       native dynein.} Native cryo-EM images of the full dimerized
-     dynein complex composed of light, intermediate and heavy chains,
-     from \cite{nativestructure}. Model schematics are superimposed
-     for illustrative purpose; shown angles to not represent expected
-     \textit{in vivo} equilibria. Schematics are shown docked to a
-     microtubule for illustrative purposes.}
-   \label{fig:modelparams}
-\end{figure}
+%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
+%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
+%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
+%%    \caption{\textbf{Model schematic superimposed on cryo-EM images of
+%%        native dynein.} Native cryo-EM images of the full dimerized
+%%      dynein complex composed of light, intermediate and heavy chains,
+%%      from \cite{nativestructure}. Model schematics are superimposed
+%%      for illustrative purpose; shown angles to not represent expected
+%%      \textit{in vivo} equilibria. Schematics are shown docked to a
+%%      microtubule for illustrative purposes.}
+%%    \label{fig:modelparams}
+%% \end{figure}
 
-\begin{figure}[tbhp]
-  \centering
-\includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
-\includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
-\includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
-\includegraphics[width=0.5\columnwidth]{figures/schematic-full}
-  \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
-      images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
-    dynein heavy chains superimposed with model motor angles, both
-    from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
-    MT with model binding angle superimposed, from
-    \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
-    bound to an MT with model superimposed, from
-    \textbf{nativestructure}.}
-\label{fig:modelangles}
-\end{figure}
+%% \begin{figure}[tbhp]
+%%   \centering
+%% \includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
+%% \includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
+%% \includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
+%% \includegraphics[width=0.5\columnwidth]{figures/schematic-full}
+%%   \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
+%%       images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
+%%     dynein heavy chains superimposed with model motor angles, both
+%%     from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
+%%     MT with model binding angle superimposed, from
+%%     \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
+%%     bound to an MT with model superimposed, from
+%%     \textbf{nativestructure}.}
+%% \label{fig:modelangles}
+%% \end{figure}
 

### 2018-08-16 papers/paper/paper.tex
Add theoretical OB and BB times to OB/BB histograms

@@
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
-\textit{Right:} Model superimposed over full-length dimerized dynein bound to accessory proteins, (map ID EMD-7000) \cite{grotjahn}.
+\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model at equilibrium angles superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
+\textit{Right:} Model at equilibrium superimposed over full-length dimerized dynein bound to accessory proteins, (map ID EMD-7000) \cite{grotjahn}.
 Left figure has a scale bar of 15nm, right 26.3nm between MTBD and AAA1 of motor domain.}
@@
 \item Add force-dependent plots to compare with yildiz?
-\item Figure out which of the model-em subfigures to include/remove
 \end{enumerate}

### 2018-08-20 papers/paper/paper.tex
Use gridspec to better format some figures
minor changes

@@
 \midrule
-$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
-$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
+$c_b$ & $\cb \Delta G_{ATP}$ &  & \\
+$c_m$ & $\cm \Delta G_{ATP}$ &  & \\
 $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
@@
   \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_stepping_length_histogram}
-  \includegraphics[width=\linewidth]{../../plots/paper_dwell_time_histogram}
-  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
   \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
@@
   \centering
+  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
   \includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
-  \includegraphics[width=\linewidth]{../../plots/paper_onebound_histogram.pdf}
   \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}

### 2018-08-20 scripts/make_all_stepping_plots.py

@@ -239,9 +239,10 @@ yildiz_step_lengths = np.append(yildiz_step_lengths, [47]*1)
 if len(step_lengths) == 0:
     print("No steps to put in histogram!")
 
-ax0.hist(yildiz_step_lengths, bins=20, alpha=0.5, label="Yildiz 2012", normed=True, stacked=True)
-if (len(step_lengths) > 0):
-    ax0.hist(step_lengths, bins=20, alpha=0.5, label="Model", normed=True, stacked=True)
+bins = np.histogram(np.hstack((yildiz_step_lengths, step_lengths)), bins=20)[1]
+
+ax0.hist(yildiz_step_lengths, bins, alpha=0.5, label="Yildiz 2012", normed=True, stacked=True)
+ax0.hist(step_lengths, bins, alpha=0.5, label="Model", normed=True, stacked=True)
 
 ax0.scatter([np.mean(step_lengths)], [0], label=r'$\overline{\Delta x} = ' + str(np.around(np.mean(step_lengths), decimals=2)) + r'$ \textit{nm}')
 

### 2018-08-20 papers/paper/paper.tex
Add (very rough) methods section with onebound equations derivation

@@
 
+\matmethods{
+
+  \subsection*{Onebound motion equations}
+  Brownian Dynamics was used to describe the motion of each domain:
+
+  \begin{equation}
+    \dot{X_i} = \frac{1}{\gamma_i}\left(F^x_i + R^x_i\right)
+  \end{equation}
+
+  where $F^x_i$ is the force projection on coordinate $x$ of domain $i$, and $R^x_i$ the Brownian force.
+Expanding the force term and transforming position variables to polar coordinates yields the following:
+
+  \begin{multline}
+    \dot{X_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F(\theta_1, ..., \theta_n) + \\
+    \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right)R^x_i\big)
+    \label{eq:ob-system}
+  \end{multline}
+
+  where the $\lambda$ terms are tension terms needed to maintain the rigid rod constraints.
+Each $X_i$ coordinate is related to the $\theta_j$ coordinates via the recursive formulas $X_1 = L_1\cos(\theta_1)$ and $X_{i>1} = L_i\cos(\theta_i)+L_{i-1}$ for x-coordinates and $Y_1 = 0$ and $Y_{i>1} = L_i\sin(\theta_i)+L_{i-1}$.
+Thus, each $\dot{X_i}$ term is linearly related to all $\dot{\theta_j}$ terms.\\
+
+  There are $n$ unknown $\theta_j$ values and n unknown $\lambda$ values, totaling $2n$ unknown variables.
+There are $2n$ equations linear in $\dot{theta_j}$ and $\lambda_q$, $n$ each from the X and Y equations.
+The system of equations provided by Equation $\ref{eq:ob-system}$ was solved in Matlab, yielding equations for all $\dot{\theta_j}$.
+}
+
 \section{Results}
@@
 
+\showmatmethods
+
 \section{To do items}

### 2018-08-21 papers/paper/paper-supplemental.tex
Add paper-suplemental.tex with more deptn on OB and BB derivations

--- 2017-10-13 reorganize/papers/elliott-thesis/latex/thesis.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Masters/Doctoral Thesis 
-% LaTeX Template
-% Version 2.4 (22/11/16)
-%
-% This template has been downloaded from:
-% http://www.LaTeXTemplates.com
-%
-% Version 2.x major modifications by:
-% Vel (vel@latextemplates.com)
-%
-% This template is based on a template by:
-% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
-% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
-%
-% Template license:
-% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[9pt,twoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
 
-%----------------------------------------------------------------------------------------
-%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
-%----------------------------------------------------------------------------------------
+\templatetype{pnassupportinginfo}
+% \readytosubmit %% Uncomment this line before submitting, so that the instruction page is removed.
 
-\documentclass[
-11pt, % The default document font size, options: 10pt, 11pt, 12pt
-%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
-english, % ngerman for German
-singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
-%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
-%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
-%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
-%toctotoc, % Uncomment to add the main table of contents to the table of contents
-%parskip, % Uncomment to add space between paragraphs
-%nohyperref, % Uncomment to not load the hyperref package
-headsepline, % Uncomment to get a line under the header
-chapterinoneline, % Uncomment to place the chapter title next to the number on one line
-%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
-]{MastersDoctoralThesis} % The class file specifying the document structure
-
-\usepackage[utf8]{inputenc} % Required for inputting international characters
-\usepackage[T1]{fontenc} % Output font encoding for international characters
-
-\usepackage{lmodern} % Use the Palatino font by default
-
-\usepackage[backend=bibtex,style=numeric,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
-
-\addbibresource{thesis-articles.bib} % The filename of the bibliography
-
-\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
-
-% Elliott-added packages
-\usepackage{amsmath} % for align and other environments
-\usepackage{listings}
-\usepackage{float}   % for H figure specifier
-\usepackage{indentfirst} % to indent after sections
-
-%----------------------------------------------------------------------------------------
-%	MARGIN SETTINGS
-%----------------------------------------------------------------------------------------
-
-\geometry{
-	paper=a4paper, % Change to letterpaper for US letter
-	inner=2.5cm, % Inner margin
-	outer=2.5cm, % Outer margin
-	bindingoffset=.0cm, % Binding offset
-	top=1.5cm, % Top margin
-	bottom=1.5cm, % Bottom margin
-	%showframe, % Uncomment to show how the type block is set on the page
-}
-
-%----------------------------------------------------------------------------------------
-%	THESIS INFORMATION
-%----------------------------------------------------------------------------------------
-
-\thesistitle{Simulating dynein'’s powerstroke using Brownian dynamics} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\supervisor{Dr. David \textsc{Roundy}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
-\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
-\degree{Bachelor of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
-\author{Elliott \textsc{Capek}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
-\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
-
-\subject{Physics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
-\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
-\university{\href{http://www.university.com}{Oregon State University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{http://physics.oregonstate.edu}{Oregon State University Department of Physics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
-\group{\href{http://physics.oregonstate.edu/~roundyd/}{Roundy Research Group}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
-\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
-
-\AtBeginDocument{
-\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
-\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
-\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
-}
+\title{Your Main Manuscript Title}
+\author{Author1, Author2 and Author3 (Complete author list)}
+\correspondingauthor{Corresponding Author Name.\\E-mail: author.two@email.com}
 
@@
 
-\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages
+%% Comment/remove this line before generating final copy for submission
+\instructionspage
 
-\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content
+\maketitle
 
-%----------------------------------------------------------------------------------------
-%	TITLE PAGE
-%----------------------------------------------------------------------------------------
+%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
+\SItext
 
-\begin{titlepage}
-\begin{center}
-
-\vspace*{.06\textheight}
-{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
-\textsc{\Large Undergraduate Thesis}\\[0.5cm] % Thesis type
-
-\HRule \\[0.4cm] % Horizontal line
-{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
-\HRule \\[1.5cm] % Horizontal line
-
-\begin{minipage}[t]{0.4\textwidth}
-\begin{flushleft} \large
-\emph{Author:}\\
-{\authorname} % Author name - remove the \href bracket to remove the link
-\end{flushleft}
-\end{minipage}
-\begin{minipage}[t]{0.4\textwidth}
-\begin{flushright} \large
-\emph{Supervisor:} \\
-{\supname} % Supervisor name - remove the \href bracket to remove the link  
-\end{flushright}
-\end{minipage}\\[3cm]
-
-\vfill
-
-\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
-\textit{in the}\\[0.4cm]
-\groupname\\\deptname\\[2cm] % Research group name and department name
-
-\vfill
-
-{\large \today}\\[4cm] % Date
-%\includegraphics{Logo} % University/department logo - uncomment to place it
-
-\vfill
-\end{center}
-\end{titlepage}
-
-%----------------------------------------------------------------------------------------
-%	ABSTRACT PAGE
-%----------------------------------------------------------------------------------------
-
-\begin{abstract}
-\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-Dynein is a motor protein which transports cargo along tracks inside the cell.
-Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains.
-Unlike kinesin or myosin, dynein's stepping pattern is highly varied: it can take steps between zero and 60nm in both the forwards and backwards directions.
-It is believed that dynein takes such broad, stochastic steps because its large size and several elastic regions make it more influenced by Brownian motion.
-To test this, we model the motor as a 2D system of elastic hinges, then simulate this model using Brownian dynamics.
-Preliminary results indicate such a model is capable of taking steps between zero and 25nm.
-These results give hope that, with further tweaking, the model may be able to generate both larger steps and backwards steps.
-\end{abstract}
-\newpage
-
-%% %----------------------------------------------------------------------------------------
-%% %	ACKNOWLEDGEMENTS
-%% %----------------------------------------------------------------------------------------
-
-%% \begin{acknowledgements}
-%% \addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-%% The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
-%% \end{acknowledgements}
-
-%----------------------------------------------------------------------------------------
-%	LIST OF CONTENTS/FIGURES/TABLES PAGES
-%----------------------------------------------------------------------------------------
-
-\tableofcontents % Prints the main table of contents
-\newpage
-
-\listoffigures % Prints the list of figures
-\newpage
-
-%% \listoftables % Prints the list of tables
-\newpage
-
-%% %----------------------------------------------------------------------------------------
-%% %	ABBREVIATIONS
-%% %----------------------------------------------------------------------------------------
-
-%% \begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
-
-%% \textbf{MT} & \textbf{M}icro\textbf{t}ubule\\
-%% \textbf{MTBD} & \textbf{M}icro\textbf{t}ubule \textbf{B}inding \textbf{D}omain\\
-
-%% \end{abbreviations}
-
-%% %----------------------------------------------------------------------------------------
-%% %	PHYSICAL CONSTANTS/OTHER DEFINITIONS
-%% %----------------------------------------------------------------------------------------
-
-%% \begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
-
-%% % The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
-
-%% Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
-%% %Constant Name & $Symbol$ & $Constant Value$ with units\\
-
-%% \end{constants}
-
-%% %----------------------------------------------------------------------------------------
-%% %	SYMBOLS
-%% %----------------------------------------------------------------------------------------
-
-%% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
-
-%% $a$ & distance & \si{\meter} \\
-%% $P$ & power & \si{\watt} (\si{\joule\per\second}) \\
-%% %Symbol & Name & Unit \\
-
-%% \addlinespace % Gap to separate the Roman symbols from the Greek
-
-%% $\omega$ & angular frequency & \si{\radian} \\
-
-%% \end{symbols}
-
-%% %----------------------------------------------------------------------------------------
-%% %	DEDICATION
-%% %----------------------------------------------------------------------------------------
-
-%% \dedicatory{For/Dedicated to/To my\ldots}
-
-%----------------------------------------------------------------------------------------
-%	THESIS CONTENT - CHAPTERS
-%----------------------------------------------------------------------------------------
-
-\mainmatter % Begin numeric (1,2,3...) page numbering
-
-\pagestyle{thesis} % Return the page headers back to the "thesis" style
-
-% Include the chapters of the thesis as separate files from the Chapters folder
-% Uncomment the lines as you write the chapters
-
-%----------------------------------------------------------------------------------------
-%	THESIS CONTENT - CHAPTERS
-%----------------------------------------------------------------------------------------
-\chapter{Introduction}
-\label{chap:Introduction}
-
-\blockquote{An embryo in its spherical blastula stage has spherical symmetry [...].
-But a system which has spherical symmetry, and whose state is changing because of chemical reactions and diffusion, will remain spherically symmetrical for ever [...].
-It certainly cannot result in an organism such as a horse, which is not spherically symmetrical.
-\textbf{Alan Turing, The Chemical Basis of Morphogenesis, 1952}}
-
-Cells need to create asymmetric, heterogeneous structures inside themselves in order to function.
-However, diffusive processes cannot create this asymmetry.
-How then do cells create the heterogeneous structures they need to exist?
-Motor proteins are part of the answer.
-Motor proteins are structures which use energy to create directed motion in cells.
-In broad terms, they are mechanical creators of asymmetry.
-This thesis explores a hypothesis about how one such motor protein, dynein, generates directed motion.\\
-
-\section{Motivation}
-Motor proteins are cellular structures which use chemical energy to do work and generate motion.
-Kinesin, myosin and dynein are the three main motor proteins in cells.
-Though these proteins have significantly different ancestors \cite{hook-family}, they all evolved into a single similar structure.
-In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way of solving a problem.
-How, then, do motor proteins work?\\
-
-The basic process is simple.
-Kinesin, myosin and dynein each use two binding domains to attach to a surface.
-These binding domains are connected via a linker domain.
-Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface.
-In a single cycle a binding domain unbinds from a surface, tenses its foot to kick forward, rebinds, then untenses its foot to pull the whole motor forward.
-This pattern is repeated by both feet to generate motion \cite{kinesin-cycle, myosin-cycle}.\\
-
-Although the three motor protein families operate using the same stepping cycle, their behaviors differ significantly.
-Kinesin and myosin are predictable motors which step in the forward direction with a regular step size.
-In contrast, dynein's stepping pattern varies in both size and direction.
-The motor can take 64nm steps forward or 32nm steps backward, and often steps sideways as well \cite{weihongpaper}.
-How can motors which implement the same release, lever, bind, lurch stepping mechanism behave so differently?\\
-
-One possibility is that dynein's size and organization are responsible for the motor's odd stepping pattern.
-Dynein is much larger than kinesin or myosin, so its feet may need to move significantly further during each cycle.
-Due to the random nature of Brownian motion from water particle collisions, there may be significantly more variance in the path taken by dynein's feet compared to other motor feet.
-This could explain the large variance in step size.
-Another contributing factor could be that dynein is so large that it can twist and contort during its step, allowing varying and even backwards steps, which a small motor would be too stiff to achieve.\\
-
-This thesis describes an experiment which aims to test whether Brownian motion and flexibility cause dynein's unique stepping pattern.
-To do this, we construct a mathematical model of the dynein motor which exhibits flexibility and feels Brownian forces.
-We then simulate the model and compare its behavior to real dynein.\\
-
-%% Dynein:
-%% feet which bind to track
-%% motor connected to feet which generates the force
-%% -----------
-%% ATP binding causes dissociation
-%% Also causes forward kick
-%% ATP hydrolysis
-%% rebinding causes ADP rejection and forward lurch
-%% restart
-
-%% Kinesin:
-%% feet which bind to track
-%% connected via lever arm to cargo binding domain
-%% -----------
-%% ATP binding causes forward kick
-%% ATP hydrolysis
-%% MT binding, ADP, Pi rejection
-%% Other foot unbinds
-
-%% Myosin:
-%% Feet which bind to track
-%% connected via lever arm to cargo binding domain
-%% ----------
-%% actin binding causes Pi rejection, strengthening binding
-%% binding causes foot to change relative to lever, shifting the motor forward
-%% ATP binding causes dissocaition and undoing the powerstroke
-
-\section{What is dynein?}
-\subsection{Basics}
-Dynein is a cellular structure which converts chemical energy to mechanical energy.
-It does so by reacting with adenosine triphosphate (ATP) to take steps along long cellular tracks known as microtubules (MTs).
-Dynein's mechanical energy is used for various cellular functions, including to transport molecules around the cell, pull chromosomes during division, and move cellular propellers known as cilia \cite{cianfroccoreview}.\\
-
-Dynein is a protein with many smaller domains.
-A depiction of the protein and its labeled subdomains is shown in Figure (\ref{dynein-artist-rendition}).
-Each motor is a homodimer made up of two identical monomer proteins.
-Each monomer has a binding domain which binds to the microtubule, a motor domain which binds ATP, a tail domain which connects to the other monomer, a stalk which connects the binding and motor domains, and a linker which connects the motor and tail domains.
-The tail domain is also responsible for binding to cargo.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
-  \caption{Artist's rendition of dynein bound to a microtubule.}{Two heavy chains (cyan and blue) and several tail proteins (pink) come together to form the dynein motor complex.
-One monomer's binding domain is bound to the microtubule (green), and the other is diffusing.
-ATP hydrolysis sites are labeled glowing green.
-Figure modified.
-Source: Lander Lab, The Scripps Research Institute \cite{landerartistsrendition}.}
-  \label{dynein-artist-rendition}
-\end{figure}
-
-Dynein is believed to move by using the energy of ATP to cycle through a sequence of states, each with different spatial relations to the microtubule.
-By cycling forward through this sequence, the molecule will end up in the same state it began, but moved forward a small amount.
-This sequence of states is known as the mechanochemical cycle \cite{cianfroccoreview}.
-The goal of this project is to create a mathematical model of the mechanochemical cycle and verify that it can reproduce experimental dynein stepping data.
-There are several types of dynein which all behave slightly differently.
-This project will focus on cytoplasmic dynein-1, hereby referred to as dynein.\\
-
-\subsection{Why do cells need motor transport?}
-Cells are organized, heterogenous structures which respond quickly to their environments.
-This means that cells require a mechanism for rapidly moving components to precise locations within the cell.
-This can be a challenge, since cells are fairly large compared to the proteins which compose them.
-A human fibroblast cell has a volume of roughly 2000 $\mu\text{m}^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu \text{m}$ in diameter.
-In comparison, human hemoglobin has a diameter of roughly $5 \text{nm}$ (PDB id 5ME2), a $10^3$ factor decrease in size.\\
-
-Diffusion, or random motion of molecules due to collisions with solvent (i.e.
-Brownian motion), is one possible process cells could use to transport biomolecules.
-Diffusion has two problems: it is slow and nondirected.
-The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \cite{einstein-paper}:
-
-\begin{equation}
-  \label{diffusion-equation}
-  \langle x\rangle = \sqrt{2Dt}
-\end{equation}
-%
-where D is the diffusion constant describing the diffusability of the biomolecule.
-For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu \text{m}^2/\text{s}$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell.
-In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.
-\\%% Figure (\ref{fig:diffusion_vs_dynein}) demonstrates how motor transport quickly outstrips diffusion in a cell.\\
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
-%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion constant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
-%%   \label{fig:diffusion_vs_dynein}
-%% \end{figure}
-
-Another advantage of motor transport is that microtubules can be highly specific in their location in the cell.
-During cell division chromosomes line up at the center of each cell in a plane.
-Such a geometrically precise shape requires some sort of directed motion which a random process could never provide.\\
-
-\subsection{What role does dynein play in the cell?}
-One of dynein's primary jobs is to transport cellular cargos such as organelles, vesicles, mRNA, cytoskeletal filaments and certain proteins from place to place in the cell.
-Dynein also plays a role in positioning and breaking down the nucleus, cell death, spindle formation and the placement of other important cellular structures \cite{valetoolbox}.\\
-
-Dynein walks along cellular tracks called microtubules (MTs).
-MTs are long polymers of alternating $\alpha-$ and $\beta-$ tubulin subunits.
-MTs are polar, meaning they have a distinct directionality based on the orientation of the tubulin proteins which comprise them.
-One pole, called the minus end, is where they initiate formation, typically at a MTOC (microtubule organizing center) around the center of the cell.
-The other pole, the plus end, is where they grow and shrink from.
-Kinesin, another type of motor protein, typically walks towards the plus end of the MT.
-Dynein is unique in that it walks towards the minus end, making it a minus end-directed motor.
-This lends it to a particularly important function inside neurons known as retrograde transport.\\
-
-Neurons have cell bodies at their centers and axons which grow outwards.
-Axons are long, narrow structures extending up to a meter in length in humans.
-Cell bodies contain nuclei and important organelles for synthesizing proteins, but growth of axon tips is vital for neuron function.
-This means bidirectional motor transport between axon tips and cell bodies is very important in neurons, since diffusion would not be quick enough.
-Retrograde transport is transport from the axon tip to the cell body.
-Cargo includes vesicles full of proteins ready to be broken down in the cell body and microtubule fragments to be returned from the axon tip \cite{neuroanatomy}.
-Because microtubule minus ends are found in the cell body, dynein's minus end-directed nature makes it the only protein capable of retrograde transport.
-An interesting question is, if proteins like dynein are synthesized in the cell body but needed at the axon tip to perform retrograde transport, how do dynein get to the tip?
-The answer is shown in Figure (\ref{retrograde-transport}): kinesin, a plus end-directed motor, takes dynein to the tip from the cell body.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/retrograde_transport.jpg}
-  \caption{Dynein transport to neuron growth cones.}{Dynein and kinesin collaborate to move cargo between the neuron body and axon tip.
-The oppositely-directed motors take turns transporting each other, along with cargo for building the axon growth cone.
-Image from \cite{valetoolbox}.}
-  \label{retrograde-transport}
-\end{figure}
-
-\subsection{Dynein structure}
-As shown in the crystal structure in Figure (\ref{fig:pdb-motm-dynein}), a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains.
-Each of these subunits has a unique purpose for the motor.\\
-
-Dynein is a fusion of two identical proteins, referred to as monomers.
-A single monomer, depicted in (\ref{fig:pdb-motm-dynein}), is composed of a microtubule-binding domain (MTBD), a stalk, a buttress, a motor domain, a linker and a tail.
-The MTBD is responsible for binding to the microtubule.
-The stalk links the motor domain to the MTBD and carries information about the state of the motor to the MTBD.
-The motor domain hydrolyses ATP and performs the main conformation changes involved in the step \cite{FRETstatepaper}.
-The linker connects the tail to the motor and also changes conformation during the step.
-The tail is a binding site which interacts with several binding partners, including the tail of a twin monomer.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.5\textwidth,keepaspectratio]{../figures/pdb-motm-dynein}
-  \caption{Structure of a dynein monomer.}{A cryo-electron microscopy-inspired image detailing the subcomponents of a single dynein monomer.
-The microtubule-binding domain (MTBD) connects to the motor domain via a coiled coil known as the stalk.
-The six AAA regions provide structure for the motor domain, and AAA2 conducts the ATP hydrolysis.
-The linker is a flexible region which connects the motor domain to the tail.
-One of the main roles of the tail is connecting a monomer to its twin to form the dynein complex.
-Image from \cite{pdb-motm-dynein}.}
-  \label{fig:pdb-motm-dynein}
-\end{figure}
-
-\subsection{Why is dynein interesting?}
-Selective domain labeling indicates dynein's stepping pattern is highly varied \cite{reck2006single, weihongpaper}.
-These studies show dynein's stepping pattern to be stochastic and weakly forward-directed.
-As shown in Figure (\ref{fig:weihong-steps}), dynein takes many backwards steps, and also many steps with components perpendicular to the microtubule.
-This indicates the process dynein uses to generate motion has a stochastic component to it.
-In contrast, kinesin is known to take very regular 8nm steps in the absence of large forces \cite{kinesin-step-size}.
-For reference, the diameter of a microtubule is roughly 25nm.\\
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.49\textwidth]{../figures/weihong-step-size}
-  \includegraphics[width=0.49\textwidth]{../figures/weihong-off-axis-steps}
-    \caption{Experimental dynein stepping behavior histograms.}{Left: Size of steps taken by dynein motor parallel to microtubule.
-Positive axis corresponds to steps towards the microtubule minus-end.
-Right: Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule.
-Figure modified from \cite{weihongpaper}.}
-  \label{fig:weihong-steps}
-\end{figure}
-
-Kinesin and dynein, although of very different evolutionary origin \cite{hook-family}, have very similar stepping cycles.
-Both proteins bind bipedally to microtubules.
-Both proteins use ATP hydrolysis to leverage against a linker domain, pushing the motor domain forward.
-Both proteins couple their nucleotide and MT-binding states \cite{vale-kinesin-cycle}.
-How, given the large number of similarities between these motors, does dynein achieve such a radically different stepping pattern than kinesin?
-Elucidating how the structural differences between the motors give rise to the differences in dynamics would provide lots of important information on how the machines fine-tune their stepping.\\
-
-A major factor which could contribute to differences in stepping is each protein's size.
-Kinesin proteins are generally 100-200 kD in mass, whereas dynein is on the order of 1mD.
-As shown in Figure (\ref{fig:kinesin-vs-dynein}), the dynein motor domain is much bigger than the kinesin motor domain.
-Another key difference is the separation between ATP hydrolysis sites on either protein.
-Kinesin's ATP hydrolysis site is inside the globular microtubule-binding domain.
-In contrast, Dynein binds to the MT with its MTBD, colored yellow in Figure (\ref{fig:kinesin-vs-dynein}), and hydrolyses ATP in its motor domain, which is colored cyan.
-This distance is close to 20nm in length - much longer than kinesin.
-This large separation might act like a loose ``leash,'' allowing the binding domain to diffuse freely around the microtubule.
-Kinesin has a much more rigid leash, as shown in the bottom pane of (\ref{fig:kinesin-vs-dynein}).
-This more rigid leash may prevent diffusion from happening as much.\\
-
-\begin{figure}[H]
-  \centering
-  \begin{minipage}{0.3\textwidth}
-    \includegraphics[width=\textwidth,keepaspectratio]{../figures/kinesin_vs_dynein}
-  \end{minipage}
-  \begin{minipage}{0.65\textwidth}
-    \includegraphics[width=\textwidth,keepaspectratio]{../figures/kinesin_vs_dynein_2}
-  \end{minipage}
-  \caption{Structural comparison of dynein and kinesin}{Left: Comparison of crystal structures of the motor domains of dynein and kinesin bound to a microtubule.
-Image from \cite{kinesin-vs-dynein}.
-Right: Full motor complexes of dynein and kinesin inspired by cryo-EM microscopy.
-The blue regions on the right image of either protein are the motor domains, which are pictured in the left crystal structures.
-Not present in the left cyrstal structures are the tail and intermediate chains of either protein.
-Right image from \cite{kinesin-vs-dynein-2}.}
-  \label{fig:kinesin-vs-dynein}
-\end{figure}
-
-\section{Dynein Stepping Background}
-Biophysicists and molecular biologists have conducted experiments over the past twenty years which shed light on how the dynein motor might walk.
-The full mechanism is not known, but several known behaviors of dynein can be taken together to construct a model for how the motor walks.\\
-
-\subsection{ATP cycle influences conformational state}
-Dynein is known to occupy multiple discrete conformational states depending on its environment.
-In particular, the concentration of ATP and microtubules is known to alter the shape dynein takes on.
-A FRET (fluorescence resonance energy transfer) study attached fluorophores to dynein's motor and tail and measured the average distance between the two \cite{FRETstatepaper}.
-It was found that average distance increased or decreased depending on the nucleotide bound to dynein, indicating the motor takes on different conformations for different bound nucleotides.
-Dynein unbound to nucleotide, or frozen in ATP or ADP-bound states, had a similar tail-motor distance.
-However, when the motor was stuck in an ADP-Pi state, with ATP hydrolyzed but phosphate not yet released, the tail-motor distance was increased.
-This suggests that dynein starts its cycle with no nucleotide, binds ATP, hydrolyzes ATP, enters the ADP-Pi state and changes conformation to a far tail-motor distance, then releases phosphate, moves back to its original close tail-motor conformation, then ejects ADP and starts over.\\
-
-Studies suggest that near/far tail-motor conformation changes are not due to lengthening of the stem linking the two domains, but rather a change in position of the head relative to the tail \cite{FRETstatepaper, burgess-paper}.
-Cryo-electron microscopy images of the dynein motor shown in Figure (\ref{fig:cryo-em-angles}) demonstrate the differences in conformation in the nucleotide-free and ADP-Pi state.
-The shifting of the linker domain in the ADP state is known as the powerstroke, and is believed to be the principle cause for dynein's forward step.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/burgess-dynein-angles}\\
-  \hspace{1cm}
-  \includegraphics[width=.95\textwidth,keepaspectratio]{../figures/linker-swing}
-  \caption{Dynein conformation change during a step.}{Top: Cryo-electron microscopy images of axonemal dynein in two different nucleotide states.
-Top left: dynein frozen in ADP-Pi state.
-Top middle: dynein without nucleotide.
-Top right: two states superimposed on one another.
-Figures from \cite{burgess-paper}.
-Bottom: X-ray diffraction-inspired image of a motor in two nucleotide states.
-Bottom left: motor in ADP-Pi state.
-Bottom right: Motor in ADP state.
-The linker undergoes an approximately 40 degree swing between these two states known as the powerstroke.
-Figure from \cite{bhabha-paper}.}
-  \label{fig:cryo-em-angles}
-\end{figure}
-
-Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}.
-Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\
-
-%% \textbf{TODO: look at \cite{nicastro} and \cite{schmidt-carter} to see if they can add to this discussion}
-
-\subsection{Microtubule and nucleotide states are coupled}
-Dynein is known to bind to the microtubule at a location known as the $\alpha$-$\beta$ polymerization site \cite{redwineMTBDcomplex}.
-This site occurs roughly every 8nm, indicating dynein is restricted to forward step sizes which are multiples of 8nm.
-The motor is also capable of stepping sideways \cite{weihongpaper}, indicating total displacements which are not multiples of 8nm.\\
-
-The nucleotide state of the motor is not the only determiner of dynein conformation; microtubule binding state has also been shown to influence conformation.
-A study on the MTBD-MT complex indicates the stalk connecting the motor and MTBD can take on two major conformations, depending on whether the MTBD is bound to the MT or not \cite{mt-atp-coupling}.
-The conformation of the stalk has been shown to communicate information between the motor and MTBD.
-In the presence of microtubules, the ATPase rate of the motor is increased 25-fold.
-This indicates the stalk communicates MT-binding state of the MTBD to the motor, increasing its ATP hydrolysis rate.
-The communication happens the other way, as well.
-Treating dynein with ATP causes MT-binding rate to drop 15-fold, indicating ATP-binding at the motor decreases MT-binding rate at the MTBD.\\
-
-In addition to a bidirectional linking between ATPase rate and MT-binding, stalk state has been shown to directly influence motor conformation \cite{mt-atp-coupling}.
-When the stalk is allowed to freely transition between bound and unbound states, the motor can also transition between near and far tail/motor states.
-However, when the stalk is frozen in a particular conformation, the motor loses its transitioning ability.
-This suggests that the conformations of the two systems are tightly linked.\\
-
-\section{Cianfrocco model for dynein stepping}
-\label{sec:cianfrocco-model}
-Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts.
-Somehow the protein interacts with nucleotides and microtubules in a way that allows it to reliably move through the cell.
-The Cianfrocco model presented below takes these facts and string them together into cohesive cycles which might explain how dynein walks.\\
-
-Cianfrocco \textit{et.
-al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig.
-(\ref{mech-cycle}).
-The model claims the primary events in the dynein step are as follows.
-First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation.
-ATP hydrolysis to ADP-Pi causes further conformation changes.
-These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound.
-The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT.
-Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle.
-The exact order of these events is not precisely known.\\
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=.90\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
-  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
-  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
-  \newcommand\transition{\textcolor{green}{transition?}}
-  %% \begin{tabular}{rll}
-  %%   \bothbound &
-  %%   1 & \begin{minipage}{5in}
-  %%     Bound to microtubule and waiting for ATP to arrive.  The
-  %%     conformation is ``post-powerstroke''.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   2 & \begin{minipage}{5in}
-  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \transition &
-  %%   3 & \begin{minipage}{5in}
-  %%     ``The ring has closed'' in the motor, whatever that means.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   4 & \begin{minipage}{5in}
-  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \onebound &
-  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
-  %%     Onebound! The equilibrium angle is also changed.  The ATP has
-  %%     been hydrolized, but the phosphate is still bound to the motor.
-  %%     ``Priming stroke?''
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \onebound &
-  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
-  %%     with low affinity, and without any loss of phosphate. Question:
-  %%     does this happen many times? If so it may still be onebound.
-  %%     Otherwise it is probably bothbound.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   7 & \begin{minipage}{5in}
-  %%     Now it is seriously bound to the microtubule, and the motor
-  %%     domain has changed conformation.  This is now ``high affinity.''
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   8 & \begin{minipage}{5in}
-  %%     Phosphate has been released, and our equilibrium angles have
-  %%     been changed.  This is the ``power stroke.''
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   1 & \begin{minipage}{5in}
-  %%     The ADP has been released from the motor domain, so it can now
-  %%     bind ATP.  Still ``high affinity,'' and still in the
-  %%     ``power-stroke'' conformation.
-  %%   \end{minipage}\vspace{0.5em}\\
-  %%   \bothbound &
-  %%   9 & \begin{minipage}{5in}
-  %%     While stuck in this ``normal bound'' state, another site on the
-  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
-  %%     where it cannot directly move on to step 2 (until after
-  %%     reversing this).  Controversial?
-  %%   \end{minipage}
-  %% \end{tabular}
-  \caption{Cianfrocco mechanochemical cycle.}{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
-  \label{mech-cycle}
-\end{figure}
-
-%% \subsection{Other models}
-%% Find other models and put them here
-
-%% \section{Brownian dynamics}
-%% New section which describes how BD works.
-
-\section{Testing the Cianfrocco model}
-One of the main goals of studying dynein is establishing how the motor walks.
-This can be a difficult task, since direct observation of the protein walking is not currently experimentally possible.
-Given the experimental challenges, a computational approach seems promising.
-This approach involves forming a hypothesis on how the motor walks, creating a model which behaves according to this hypothesis, simulating that model, and comparing the simulation's behavior to experimental data.
-This process can be an efficient way to support hypotheses and guide future research.\\
-
-\subsection{Computational approach}
-This project seeks to create a dynamic model of dynein and use it to answer questions.
-The Cianfrocco model provides a rough framework for the events that go on during the dynein mechanochemical cycle.
-By augmenting this model with information about dynein's structure and conformation changes occuring during the cycle, a new dynamic model which takes into account both temporal and spatial information can be constructed.
-This dynamic model can then be simulated under cellular conditions to test how it behaves.
-Such a model would be ideal, since it would make very precise predictions about how real dynein walks.
-This simulation would act as an experiment testing the validity of the Cianfrocco model.\\
-
-\subsection{Questions to answer}
-The biggest question such a simulation would answer is: does the Cianfrocco model, when applied to a dynein-sized motor with elastic hinges, produce dynein-like stepping?
-High similarity between simulation behavior and experimental dynein behavior would be a strong positive result supporting the Cianfrocco model.
-If confirmed to be dynein-like, the simulation could then be used to answer many other questions.\\
-
-Dynein has both angular and linear elasticity between its domains.
-Angular elasticity, or the flexibility of protein domains relative to each other, may play a large role in dynein's stepping.
-It is possible that dynein requires its foot domain to diffuse to a high-energy conformation in order to take a step.
-It is postulated by \textit{Burgess et.
-al.} \cite{burgess-paper} that changes in angular elasticity may be important for dynein's ability to step at key points in the mechanochemical cycle.
-Alternatively, it is possible that elasticity is not required, and the angular changes caused by the powerstroke are enough for stepping.
-By varying the angular elasticity of the model, this simulation could determine the importance of angular elasticity for dynein's step.\\
-
-Another question this simulation could answer is how dynein localizes to its binding site.
-Microtubules are regular tubulin polymers with MTBD binding sites roughly every 8nm.
-Dynein can take steps at integer multiples of this length, but the 8nm step is its most favored.
-Why is this?
-Does the MTBD drag along the microtubule until it hits a binding site?
-Or, does it diffuse high above the microtubule, randomly descending until it finds a place to bind.
-This simulation could answer that question by outputting MTBD positions over time.\\
-
-Why does dynein step differently than kinesin?
-Kinesin follows a similar mechanochemical cycle to dynein.
-By modifying the stepping cycle, shrinking inter-domain distance and changing conformation angles of the dynein model, it may be possible to create a rough kinesin dynamic model.
-This model could then be tested for similarity to experimental kinesin.
-If kinesin behavior was replicable, then comparisons between the models could be readily made.
-Does kinesin step like dynein when its size is increased?
-Does dynein step like kinesin when its conformation angles are made rigid?
-By varying the spatial representation of the two models, it might be possible to determine why the two motors step differently.\\
-
-Kinesin and dynein generally travel in opposite directions along the microtubule.
-Why is this?
-Both proteins bind to the same place on the microtubule \cite{kinesin-dynein-mt-overlap}, so the binding site can't determine directionality.
-It is possible that not the binding site, but the angle at which the protein binds to the microtubule is what determines its stepping direction.
-If it turns out that kinesin can be successfully modelled using the same dynamic model, then this question could possibly be answered.
-If altering the microtubule binding angles of dynein and kinesin reverses their directionality, it may be that binding angle is all it takes to determine motor directionality.\\
-
-%% \textbf{Things which are known about dynein which support the Cianfrocco model}
-%% \begin{itemize}
-%% \item AAA1 only ATPase necessary for motility, which is why we don't include the other ATPases in our model \cite{cianfroccoreview}
-%% \item AAA5 mediates stalk register changes Schmidt H, Zalyte R, Urnavicius L, Carter AP. 2014. Structure of human cytoplasmic dynein-2 primed for
-%%   its power stroke. Nature 518:435–38
-%% \item Linker moves as response to AAA1 nucleotide binding Burgess SA, Walker ML, Sakakibara H, Knight PJ, Oiwa K. 2003. Dynein structure and power stroke. Nature
-%%   421:715–8
-%% \item Crystal structures with Vanadium-Adp show dynein in the pre-powerstroke state, hinting that ADP-Pi-bound dynein takes on a different conformation than ADP-Pi free dynein
-%% \end{itemize}
-
-\newpage
-\chapter{Theory}
-\label{chap:Theory}
-
-\section{Model overview}
-The model constructed in this thesis is meant to approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model (\ref{sec:cianfrocco-model}) would behave in a cell.
-In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation.
-Creating such a model is a balance between accuracy and computational efficiency.
-The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time.
-Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be prohibitively expensive to simulate a dynein step.
-Thus, many approximations are made about dynein to simplify the simulation.\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../figures/theory-onebound}
-  \includegraphics[width=.45\textwidth]{../figures/theory-bothbound}
-  \caption{Spatial representation of the dynein dynamic model.}{Dynein is simplified to two two-dimensional point-particle systems.
-The left ``onebound'' system represents dynein when one MTBD is unbound, and the right ``bothbound'' system represents dynein with both MTBDs bound.
-Five points in total represent the two MTBDs, two motor domains and one tail domain.
-Each model's orientation is defined by a set of angles, four in the onebound case and two in the bothbound case.
-These points are connected by rigid rods.
-Although approximated as points, each domain has a radius $R$ associated with it used for drag calculations.}
-  \label{fig:theory-intro}
-\end{figure}
-
-\subsection{Summary}
-The model is composed of two separate systems of five point particles, with each point representing a domain of dynein: two binding domains, two motor domains and one tail domain.
-Physical representations of these two systems are shown in Figure (\ref{fig:theory-intro}).
-The points are connected together by rigid rods, and the sytems are defined by the angles the rods make at each point.
-These angles are free to swivel.
-Each point thus acts somewhat like a ``hinge'' which can open or close.
-These two systems represent different modes dynein can be in.
-The Cianfrocco model is simplified to two states: onebound, when one MTBD (Microtubule Binding Domain) is diffusively searching for a binding site, and bothbound, where both MTBDs are MT-bound.
-The model can be in one of these two states at any time, and can transition between them if the right conditions are met.
-For example, if the model is in the onebound state but drifts such that both of its MTBDs are near the microtubule, the model can ``bind'' the MT and transition to the bothbound state.\\
-
-The model is subject to two forces, each of which is meant to simulate the effects real dynein domains feel.
-The first is a Brownian force which constantly changes.
-This force is meant to mimic the force of water particles colliding with the domains and causing diffusion.
-The second force is called a conformational force, and is meant to mimic the conformation and elasticity of dynein.
-Each hinge is somewhat like a spring with an equilibrium resting angle.
-At this angle, the domain feels no force.
-However, when the angle deviates from this equilibrium, a harmonic restoring torque proportional to the displacement angle is applied to the involved domains to push the angle back to equilibrium.
-Thus these two forces oppose each other during a simulation, with Brownian forces pushing the model out of equilibrium and conformational forces trying to restore equilibrium.\\
-
-How this system is used to generate data is covered later in the section.
-In brief, this system is then converted into a computer program.
-A technique known as Brownian dynamics, described below, is used by the program to evolve the model through time.
-Models are started in one state and evolved, occasionally transitioning from one state to another.
-The positions of each domain in time are stored as data.
-Each time a model transitions from onebound to bothbound, the model registers a ``step'' having occurred.
-Thus long simulations can be used to find the stepping behavior of a model.\\
-
-%% \textit{Add a figure (maybe here?) of all the events which are known to happen in dynein, along with our mechanochemical cycle.
-It would basically show all events occuring at two times: unbinding or rebinding.}\\
-
-%% \begin{itemize}
-%% \item Dynein is a collection of spherical domains joined together by massless rods
-%% \item These rods are rigid
-%% \item Each joint in the motor feels a spring force about some equilibrium joint angle
-%% \item Dynein can be in two states: onebound and bothbound
-%% \item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
-%% \item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
-%% \item Transitions between the two states are based solely on spring energies between the two models
-%% \item Brownian dynamics describes the behavior of the domains in time
-%% \item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
-%% \item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
-%% \end{itemize}
-
-%% \begin{figure}[h]
-%%   \centering
-%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/ob_fig}
-%%   \caption{Onebound dynein model.}{}
-%%   \label{fig:model-intro}
-%% \end{figure}
-
-\section{Model assumptions}
-\subsection{Spherical domains connected by massless rods}
-A key feature of the model is that each domain of the protein (two feet, two motors and a tail) is treated as a sphere.
-Each sphere is connected to one or two other spheres, as shown in Figure (\ref{fig:theory-intro}).
-This simplification is made to make the math easier and allow a simple definition of dynein's conformation.\\
-
-As shown in Figure (\ref{fig:pdb-motm-dynein}), dynein's motor and tail domains are fairly spherical.
-Though the stalk and tail connecting these domains is definitely not massless, it is small enough that approximating it as massless should be reasonable.
-Making the radii of the spherical domains slightly larger should account for any drag caused by the rigid rods.\\
-
-Each sphere has an associated drag factor $\gamma$, which describes the resistance it feels to motion.
-This drag factor is calculated based on the radius $R$ of the spheres, and is given by Stoke's Law:
-%
-\begin{equation}
-  \gamma = 6\pi\nu R
-\end{equation}
-%
-where this drag factor $\gamma$ is used later to calculate the velocity of each domain.\\
-
-\subsection{Rods connecting domains are rigid}
-The model assumes connected domains are rigidly attached to one another by rods.
-This assumption makes the math easier.
-One study found that the standard deviation of stalk and stem lengths in \textit{in vitro} dynein was roughly $1\text{nm}$ \cite{burgess-paper}.
-However a contrasting piece of evidence showed the coiled coil, a common protein structure which links the MTBD and motor domains in dynein, can stretch in myosin, another motor protein, by 2.5x \cite{myosin-cc-elasticity}.
-Another dynein simulation done by Sarlah \textit{et.
-al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}.\\
-
-In defense of rigid rods, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.
-Either way, it is then an assumption of the model that inter-domain elasticity is not necessary for stepping.\\
-
-\subsection{Angular springs}
-Each domain has a spring constant $c_b, c_m$ or $c_t$, for binding, motor or tail domains respectively, which decides the energy associated with that domain angle.
-For example, the tail domain energy is given by
-%
-\begin{equation}
-  \Delta G_t = \frac12c_t\left(\theta_t - \theta_t^{eq}\right)^2
-\end{equation}
-%
-This energy represents the conformational energy of that particular domain.
-This energy can be used to calculate a return force which pushes the domain back to equilibrium.
-A depiction of this is shown in Figure (\ref{fig:angular-spring}).\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.65\textwidth]{../figures/angular-spring}
-  \caption{Angular spring return force when out of equilibrium.}{The $\theta_{bb}$ angle shown is greater than the equilibrium angle $\theta_{bb}^{eq}$, and thus the $bb$ domain has conformational energy $\frac{1}{2}c_b\left(\theta_{bb}-\theta_{bb}^{eq}\right)^2$, and feels a force pulling the motor domain towards the microtubule.}
-  \label{fig:angular-spring}
-\end{figure}
-
-\subsection{Two-state model}
-According to the Cianfrocco model, dynein takes on a total of eight states during a single step.
-Many of these states are conformationally very similar, e.g.
-the ADP- vs apo-bound or ATP- vs ADP-bound.
-Others involve quick transitions, e.g.
-from the just-MT-bound state to the post-powerstroke state.
-The transitions which take the most time according to reaction rate calculations are MT-binding and MT-release \cite{sarlahmodel}.
-Thus, these two states are taken to be the most important, and the Cianfrocco model is approximated by transitioning between these two states.\\
-
-The main difference between these two states is that onebound has one diffusing MTBD, whereas bothbound has both its MTBDs MT-bound.
-Another key difference is equilibrium angles of the motor domains.
-During powerstroke, according to the Cianfrocco model, the dynein linker shifts, causing the tail-MTBD angle to shift.
-In this model, the conformation change caused by ATP hydrolysis is modelled as shifting the bothbound equilibrium angle $\theta_{xm}^{bb,eq}$ to $\theta_{xm}^{ob,eq}$.\\
-
-\subsection{Transitioning between states}
-The model transitions between states with a probability dependent on both the conformational energy difference between the two states and the physical separation between the MT and binding MTBD.
-This transition can be tricky.
-To unbind, or convert from a bothbound to onebound model, a onebound structure can be constructed with the exact same domain positions, except the unbound MTBD is allowed to diffuse.
-To bind, or convert from a onebound to bothbound model, the unbound MTBD must be projected onto the microtubule.
-This is because the bothbound state is defined as having both MTBDs at $y=0$.
-Once projected, a bothbound model can be constructed with domains in the same places as the projected onebound model.\\
-
-The rates of such transitions are based on the conformational energy change between the new and old states. The energy difference between states A and B is given by:
-%
-\begin{equation}
-  \Delta G_{A\rightarrow B} = \sum_{i=0...N_B}^{B} \frac{1}{2}c_i\left(\theta_i-\theta_i^B\right)^2 - \sum_{j=0...N_A}^{A} \frac{1}{2}c_j\left(\theta_j-\Theta_j^A\right)^2
-\end{equation}
-%
-where B is the transitioned version of state A.
-Transition energies are used to calculate transition rates, as given by the Arhennius equation $k=Ae^{-\beta\Delta G}$, where $\beta = (k_BT)^{-1}$.
-In this equation $\Delta G$ is the total energy of transition between states and A is a constant known as the preexponential factor with units of $s^{-1}$.\\
-%
-\begin{equation}
-  k_b = Ae^{-\beta\Delta G} = Ae^{-\beta\Delta G_{conf}}e^{-\beta\Delta G_{bind}}
-\end{equation}
-%
-where $\Delta G_{conf}$ is the change in spring energy in going from bothbound to onebound and $\Delta G_{bind}$ is the energy gained from binding to the microtubule.
-Because binding energy for the MT-MTBD complex is hard to find, the following substitution is made:
-%
-\begin{equation}
-  k_b = Ae^{\frac{-\Delta G}{k_BT}} = Be^{\frac{-\Delta G_{conf}}{k_BT}}
-\end{equation}
-%
-Thus the transition rate is only dependent on the change in conformational energy of transitioning and the preexponential factor $B$.
-To prevent binding events from happening when the MTBD is high above the MT, the following step function correction is added to the rate equation: \\
-
-\begin{equation}
-  k_b = Be^{\frac{-\Delta G_{conf}}{k_BT}}\left(1-H\left(X_{uby}-0.1\right)\right)
-\end{equation}
-
-where H is the Heaviside step function and $X_{uby}$ is the y position of the unbound MTBD. Thus the binding rate is zero when the unbound MTBD is over $0.1$nm from the MT.\\
-
-\subsection{Brownian dynamics}
-\label{sec:bd}
-The Brownian dynamics equation describes the motion of high-drag objects which spend most of their time at terminal velocity, and is given by:
-%
-\begin{equation}
-  \dot{x} = \frac{1}{\gamma}\left(F_{net} + R\right)
-\end{equation}
-%
-where $\gamma$ is the drag constant of the object and $R$ is a random Brownian force which describes the effects of water particle collision.
-$R$ is a Gaussian-sampled zero-centered force with variance given by:
-%
-\begin{equation}
-  R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}
-\end{equation}
-%
-which is calculated from the Einstein relation.\\
-
-\subsection{Binding to microtubule}
-The model ``steps'' whenever an MTBD diffuses near the microtubule.
-\textit{in vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm.
-Thus, all dynein steps should be multiples of $8$nm.
-This model ignores this requirement and allows stepping to occur at any length.
-The assumption is that \textit{in vivo} dynein takes 8nm steps because it is tuned to take 8nm steps, not because it drags along the microtubule searching for a binding site.
-Thus the 8nm step length should be reproduced by the model even if stepping is allowed anywhere.\\
-
-\subsection{2D model}
-The coordinate system for this model is two-dimensional.
-Thus interactions between the two motors and MTBDs are ignored.
-This assumption is made to simplify the model.
-Other dynein models, like the winch model \cite{sarlahmodel}, add in attractive and repulsive forces between the two motors which act in three dimensions.
-This model ignores such effects.\\
-
-\section{Deriving motion equations}
-To simulate a protein's passage through the above mechanochemical cycle, equations are needed to describe the position of dynein at an arbitrary time.
-Using Euler's method, a position equation can be found given a velocity equation like so:
-
-\begin{align}
-  f(t+\delta t) &= f(t)+f'(t)\delta t
-\end{align}
-
-Thus, if velocity equations can be found for the individual domains, then dynein's dynamic behavior can be solved for using numerical integration.
-The Brownian dynamics equation shown in Section (\ref{sec:bd}) provides velocity at time t from forces at time t.
-All that needs to be done is to come up with expressions for the forces on each domain, which is done in the next two sections.\\
-
-One complication arises from the choice of coordinate system.
-Angular coordinates are nice, since they automatically enforce the rigid rod constraint.
-However, forces are more easily calculated in Cartesian coordinates.
-In addition, forces on the $ith$ domain depend on domains $i\pm1$.
-Thus, solving for forces requires solving a large system of equations.
-Mathematica is used for this purpose, as outlined below.\\
-
-\subsection{Prestroke onebound model}
-Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound.
-A spatial representation of onebound dynein is shown in Figure (\ref{fig:derivation-onebound}).
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../figures/derivation-onebound}
-  \caption{Spatial representation of the onebound dynein model.}{The coordinate system used for derivation of onebound forces.}
-  \label{fig:derivation-onebound}
-\end{figure}
-
-The coordinate system for this model is as follows.
-The bound MTBD is referred to as the ``bound binding domain'' $bb$.
-Its coordinates take the form, for example, $X_{bb}$.
-The motor domain adjacent to $bb$ is the ``bound motor'' $bm$.
-Next is the tail $t$, then the ``unbound motor'' $um$ and finally $ub$.\\
-
-The four angles $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on.
-The domain of $\theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$.
-Each angle is defined relative to the horizontal axis.
-The position of the bound binding domain $X_{bb}$ and the four domain angles are all that is needed to determine the position of the protein at any time.\\
-
-\subsubsection{Onebound velocity calculations}
-
+\section*{Deriving motion equations}
+\subsection*{Onebound case}
 The following equations allow recursive calculation of the positions of each domain in Cartesian coordinates:
@@
 
-\subsection{Poststroke bothbound model}
-The main difference between the prestroke and poststroke mathematical models is that the latter has a further constraint: both of its MTBDs are attached to the MT.
-This has the effect of diminishing the degrees of freedom of the system from four to two, assuming the motor remains above the MT.
-A spatial representation of the bothbound model is shown in Figure (\ref{fig:derivation-bothbound}).\\
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.45\textwidth]{../figures/derivation-bothbound}
-  \caption{Spatial representation of the bothbound dynein model.}{The coordinate system used for derivation of bothbound forces.}
-  \label{fig:derivation-bothbound}
-\end{figure}
-
-The main differences between onebound and bothbound are the naming scheme and spatial constraints.
-Dimers can no longer be differentiated by being un/bound, so are now differentiated by their z-position: being near or far from the ``camera.'' This is similar to labeling them as the right or left dimer.
-Thus there is the near binding domain $nb$, near motor $\text{nm}$, tail $t$, far motor $fm$ and far binding domain $fb$.
-Both the near and far binding domains have their y-coordinate fixed at zero.
-The system is described completely by two angles: $\theta_{nm}$ and $\theta_{fm}$.
-Angles $\theta_t, \theta_{nb}$ and $\theta_{fb}$ are dependent on these two motor angles.
-Intermediate variables $L_{n}$ and $L_{f}$ are computed to ease calculations.
-The second MTBD constraint adds another required piece of information the model must track: the x position of the second MTBD.
-This position is described by $L$, the displacement between the near and far binding domains.\\
-
-\subsubsection{Bothbound velocity calculations}
-
+\subsection*{Bothbound case}
 The first step in calculating angular velocities is to define intermediate variables $L_n$ and $L_f$ using the law of cosines:
@@
 
-%% \subsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
-%% Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively.
-One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations.
-In contrast, the rates the model uses represent the probability of unbinding of a specific conformation.
-Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$.
-As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:
-
-%% \begin{align*}
-%%   k_b &= A_b'e^{\frac{-\Delta G_{bind}}{k_BT}} = A_b'e^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}e^{\frac{-\Delta G_{bind}}{k_BT}} = A_be^{\frac{-\Delta G_{conf}^{ob\rightarrow bb}}{k_BT}}\\
-%%   k_{ub} &= A_{ub}'e^{\frac{-\Delta G_{unbind}}{k_BT}} = A_{ub}'e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}e^{\frac{\Delta G_{bind}}{k_BT}} = A_{ub}e^{\frac{-\Delta G_{conf}^{bb\rightarrow ob}}{k_BT}}
-%% \end{align*}
-
-%% where the constant Boltzmann factor for binding energy are hidden inside the unprimed preexponential factors.
-The experimental values are calculated the same way, with the free energy changes replaced with expectation values.
-Since by the equipartition theorem $\left<G_{conf}^{ob}\right> = 2k_BT$ and $\left<G_{conf}^{bb}\right> = k_BT$, the equations can be simplified:
-
-%% \begin{align*}
-%%   k_b^{exp} &= A_be^{\frac{-\left(2k_BT - k_BT\right)}{k_BT}} = \frac{A_b}{e}\\
-%%   k_{ub}^{exp} &= A_{ub}e^{\frac{-\left(k_BT-2k_BT\right)}{k_BT}} = A_{ub}e
-%% \end{align*}
-
-%% Thus experimental rates can be converted easily into the model parameters $A_b$ and $A_{ub}$.
-
-%% \subsection{Literature values for experimental binding rates}
-%% Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.
-
-%% \begin{figure}[h]
+%%% Each figure should be on its own page
+%% \begin{figure}
 %% \centering
-%%   \includegraphics[width=.45\textwidth]{../figures/SarlahParameterTable.png}
-%%   \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
-%%   \label{fig:sarlah-rate-table}
+%% \includegraphics[width=\textwidth]{example-image}
+%% \caption{First figure}
 %% \end{figure}
 
-%% The assumption of this project is that many of the states in this table can be combined into a single state without loss of predictive power of dynein behavior.
-Specifically, the assumption is that ejecting phosphate, conducting the powerstroke, releasing ADP, binding ATP and dissociating from the microtubule and all occur during the bothbound state, and hydrolyzing ATP, conducting the prestroke and rebinding the MT occur during onebound.
-These states are roughly grouped as MT-bound and MT-unbound states in the Cianfrocco mechanochemical cycle \cite{cianfroccoreview}.\\
-
-%% The rate-limiting transitions in the Cianfrocco model are used as the guess $k_b$ and $k_{ub}$ values.
-That means that, since ATP hydrolysis has the slowest rate constant in onebound and MT release has the slowest rate in bothbound, $k_b^{exp} = 180 s^{-1}$ and $k_{ub} = 460 s^{-1}$ serve as good initial guesses.\\
-
-\newpage
-\chapter{Methods}
-\label{chap:Methods}
-This section will go into detail on how the model was implemented in C++ and verified for accuracy and physicality.\\
-
-\section{Simulation}
-To generate stepping data, the models were coded in \verb|C++| and time-evolved using Euler's method to generate reasonable dynamical behavior.
-When in a position deemed worthy of a state transition, the model was converted to the respective other model, representing part of a ``step'' through the mechanochemical cycle.\\
-
-\subsection{Time evolution}
-Euler's method for solving differential equations was used to calculate domain positions through time.
-Because each model is a set of multiple coupled differential equations, care was taken to update each domain position at the same time, and not in a cascade.
-A code snippet is shown in Figure (\ref{snip:euler-code-snippet}) for the onebound updating scheme.
-This code calculates domain velocities for onebound dynein and uses them to find position displacements.
-These values are stored in temporary variables first, then updated all at once.
-The \verb|dt| used to update was $10^{-11}$ seconds.
-
-\begin{figure}[h!]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=python]
-      def simulate(dyn_ob):
-          t = 0
-          while (t < runtime):
-              double temp_bba = dyn_ob->get_bba() + dyn_ob->get_d_bba() * dt
-              double temp_bma = dyn_ob->get_bma() + dyn_ob->get_d_bma() * dt
-              double temp_uma = dyn_ob->get_uma() + dyn_ob->get_d_uma() * dt
-              double temp_uba = dyn_ob->get_uba() + dyn_ob->get_d_uba() * dt
-
-              dyn_ob->set_bba(temp_bba)
-              dyn_ob->set_bma(temp_bma)
-              dyn_ob->set_uma(temp_uma)
-              dyn_ob->set_uba(temp_uba)
-
-              t += dt
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Domain time evolution via Euler's method code snippet.}{}
-  \label{snip:euler-code-snippet}
-\end{figure}
-
-\subsection{Transitioning between states}
-
-\subsubsection{Transition rate}
-\label{sec:transitioning-states}
-Transitions from one state to another are accomplished by calculating the probability of a transition $t$ at a given timestep, given by $P_{t} = k_t\delta t$.
-Each timestep a value in $[0,1]$ is sampled from a random number generator and, if the roll is lower than $k_tdt$, the respective transition is made.
-The following sections describe how transitions are done.\\
-
-\subsubsection{Onebound to bothbound transition calculation}
-When binding occurs, conversion between OB and BB models is done by creating a bothbound dynein which is as similar in terms of domain position as possible to the onebound dynein.\\
-
-Due to the nature of the simulation, binding attempts must occur above, but very close to, the microtubule.
-This is because \textit{in vivo}, electrostatic interactions between MTBD and MT bring the two together when they are near.
-These electrostatic interactions are not present in the model, and so are simulated by allowing binding attempts to occur when $Y_{ub} \leq 0.1\text{nm}$ above the MT.
-When a binding attempt is successful, the unbound binding domain of the OB dynein is ``teleported'' such that $Y_{ub} = 0.0$.
-This is to enforce the constraint that both binding domains of the BB model are directly on the MT.\\
-
-To create a BB model from OB, the following intermediate variables are first computed:\\
-
-\begin{align}
-  L_n^2 &= \left(X_t - X_{nb}\right)^2 + Y_t^2\\
-  L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
-  \cos(\theta_{nm}) &= \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
-  \cos(\theta_{fm}) &= \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}
-\end{align}
-
-\subsubsection{Bothbound to onebound transition calculation}
-Similar to the binding transition, unbinding involves creating a new onebound dynein from the old bothbound. To accomplish a transition to the farbound state, the following equations are used:
-
-\begin{align}
-  \theta_{new,bba} &= \theta_{old,nba}\\
-  \theta_{new,bma} &= \theta_{old,nma} + \theta_{old,nba} - \pi\\
-  \theta_{new,uma} &= \theta_{old,fma} + \theta_{old,fba} - \pi\\
-  \theta_{new,uba} &= \theta_{old,fba}
-\end{align}
-%
-To do a nearbound transition, the ``f'' and ``n'' subscripts in the above equations are swapped.\\
-
-As shown in Section (\ref{table:thesis-parameters}), the MT binding rate is much quicker than the unbinding rate. This means that, when just unbound, the rate of rebinding is very high.\\
-
-%% \subsection{Corrections}
-%% \label{corrections-section}
-%% Certain configurations of the model, such as in the bothbound model when $\theta_{nm} = \pi$ or $\theta_{fm} = \pi$, it becomes impossible to calculate intermediate variables due to values going to infinity (name for this??).
-For example when $\theta_{nm} = \pi$, $Ln = Ls + Lt$ and so:
-
-%% \begin{align}
-%%   \cos\theta_{ns} &= 1 \\
-%%   \sin\theta_{ns} &= 0 \\
-%%   \mbox{some val?} &\rightarrow \infty
-%% \end{align}
-
-%% Alternative problem states are when $L = 0$ and ???. These states are corrected similarly.\\
-
-\subsection{Calculating forces}
-Spring and Brownian forces are used to properly move the model through time.
-Appendices (\ref{sec:AppendixOneboundEquations}-\ref{sec:AppendixBothboundEquations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
-Each Brownian force $R_{n,m}$ on domain $n$ in direction $m$ is sampled from a Gaussian with standard deviation $\sqrt{\frac{2k_BT\gamma_n}{dt}}$.\\
-
-Spring forces are calculated by first finding the torque $\tau$ on each angle, then converting this to a force.
-For example, the onebound near motor angle feels a force $\tau_{nm} = c_m(\theta_{nm}-\theta_{nm,eq})$, where $c_n$ is the spring constant of the motor domain and $\theta_{nm,eq}$ the equilibrium angle.
-The magnitude of force on the adjacent binding and tail domains is thus $\tau/L_s$ and $\tau/L_t$, pointing in the direction adjacent the Ls and Lt rods, respectively.
-The force on the motor domain is found as the equal-and-opposite force to these two imposed forces.
-A sample calculation is shown in Snippet (\ref{snip:transition-rate-snippet}).
-Torque is calculated the near motor's angular displacement from equilibrium.
-This is converted to force exerted on adjacent domains.
-Finally, the equal and opposite force is exerted on the near motor domain.\\
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{c}
-    \begin{lstlisting}[language=C++]
-      def set_onebound_restoring_forces():
-          T = cm*(nma - nma_eq);
-          f1 = T/Ls;
-          f2 = T/Lt;
-          f1x = f1 * sin(bba);
-          f1y = f1 * -cos(bba);
-          f2x = f2 * sin(bma);
-          f2y = f2 * -cos(bma);
-          f.bbx += f1x;
-          f.bby += f1y;
-          f.tx  += f2x;
-          f.ty  += f2y;
-          f.bmx += -(f1x + f2x); // equal and opposite forces
-          f.bmy += -(f1y + f2y);
-    \end{lstlisting}
-  \end{tabular}
-  \caption{Code snippet of restoring force calculation.}{}
-  \label{snip:transition-rate-snippet}
-\end{figure}
-
-\section{Verifying the model}
-The models were verified to follow physical laws by checking their behavior in various tests: general conformational tests, energy conservation and obeying the equipartition theorem.
-The purpose of these tests was to verify that equations had been entered properly (primarily the conformational and energy conservation tests), and that the model obeyed the laws of physics (all tests).\\
-
-A series of conformational tests were done to test if the coordinate systems of either model worked. These are listed in Appendix (\ref{sec:conformational-tests}).\\
-
-\subsection{Energy conservation}
-\label{sec:energy-conservation}
-To verify that the magnitudes of forces are calculated properly, a conservation of energy test was performed.
-A very slight angular nudge was applied to either model.
-This nudge caused a small change in energy.
-This change in energy was compared with the work the forces on each domain caused over the nudge.
-For energy to be conserved, these values were required to be very similar.
-Mathematically the test required the following:
-
-\begin{equation}
-  \sum_n \frac12 \left(\theta_{nudge} - \theta_{n} - \theta_{n,eq}\right) = \sum_n \vec{F}_n \cdot \vec{r}_{n,nudge}
-\end{equation}
-
-where $\theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the Cartesian displacement of each domain $n$ due to the nudge.
-This test is powerful since it links the force-calculation system of either model to the energy calculation system.
-Energy is calculated by looking at displacements of angles from equilibrium, whereas forces are calculated using displacement of angles from equilibrium, but also orientation and position of each domain.
-Having the force system and energy system calculate the same results indicates that they are both likely correct.\\
-
-\subsection{Equipartition theorem}
-The equipartition theorem (ET) is a thermodynamic statement which says that all systems with solely quadratic energy dependence on $N$ degrees of freedom will have $\langle E\rangle = \frac N2 k_bT$.
-For the dynein models to display ET behavior, they would have to both properly calculate forces and properly calculate velocities from forces.
-Brownian forces are also required to properly explore the different states of the system, but they need not be the correct magnitude for ET agreement.\\
-
-To test if the models obey the ET, the total potential energy of each model was logged over $10^7$ timesteps of simulation.
-Energies are reported as a running average over the simulation from 0 to time $t$.
-As shown, both models have their average potential energy converge to the expected amount, where the onebound model has four degrees of freedom and the bothbound two.\\
-
-This test verifies both force and velocity are calculated properly for either model.
-If either force or velocity was wrong, then the model would not obey the Boltzmann hypothesis $P(s) = e^{-\Delta G_{s}/K_BT}$, where $s$ is a state of the system.
-The transition rate from $s_1$ to $s_2$ is $P(s_1\rightarrow s_2) = e^{-{\Delta G_2 - \Delta G_1}/K_BT}$.
-Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.
-Another simulation feature this test verifies is that Brownian forces are calculated properly.\\
-
-%% \begin{figure}[h]
+%% \begin{figure}
 %% \centering
-%%   \begin{tabular}{| c | c | c | c |}
-%%     \hline
-%%     Author & Conditions & Velocity & Run length\\\hline
-%%     Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
-%%     Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
-%%   \end{tabular}
-%%   \caption{Literature values for experimental dynein stepping behavior.}{Table of literature values for dynein behavior}
-%%   \label{table:parameter-table}
+%% \includegraphics[width=\textwidth]{frog}
+%% \caption{Second figure}
 %% \end{figure}
 
-%% \section{Data collection}
-%% Time evolution of the system has the potential to create a huge amount of data, so care has to be taken to only collect what is necessary.
-For the purposes of testing stepping behavior of the model the geometry and per-domain forces and energies can be safely ignored.
-All that is needed to determine model fitness is the size and duration of each step.\\
+%% \begin{table}\centering
+%% \caption{This is a table}
 
-%% \subsection{Stepping data output and calculation}
-%% A step is defined as a complete cycle of
+%% \begin{tabular}{lrrr}
+%% Species & CBS & CV & G3 \\
+%% \midrule
+%% 1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
+%% 2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
+%% 3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
+%% \bottomrule
+%% \end{tabular}
+%% \end{table}
 
-%% \subsection{Simulation running via SLURM}
+%%% Add this line AFTER all your figures and tables
+\FloatBarrier
 
-\section{Parameter fitting}
-There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\theta_{m,eq}^{Pre}$, $\theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$.
-Each of these values influences the stepping behavior of the model, and so must be chosen wisely.
-Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table (\ref{table:thesis-parameters}).
-Others are more difficult to find.
-These values, including $k_b$, $k_ub$ and the three spring constants, must be found via fitting the predictions of the model to experiment.
-This process entails running simulations at various binding rates and spring constants, checking the output, and optimizing the input parameters until physical stepping behavior is achieved.
-Fitting these parameters to experiment is an active area of work on this project, but has shown tentative positive results, as shown in the Results section.\\
+%% \movie{Type caption for the movie here.}
 
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| l | l | l | l | l | l | l | l |}
-    \hline
-    & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Leschziner \cite{leschziner} & Kon & Burgess \\\hline
-    $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
-    $L_t$ &  7nm && & 11.15nm & & & \\ \hline
-    $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
-    $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
-    $R_t$ &  & & &2.16nm & & & \\ \hline
-    $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
-    $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
-    $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & 60 & & \\ \hline
-    $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
-    $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
-    $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
-  \end{tabular}
-  \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources, other simulations and crystal structures.}
-  \label{table:parameter-table}
-\end{figure}
+%% \movie{Type caption for the other movie here. Adding longer text to show what happens, to decide on alignment and/or indentations.}
 
-%% \begin{figure}[h]
-%%   \centering
-%%   \begin{tabular}{| l | l | l | l | l | l | l | l |}
-%%     \hline
-%%     & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
-%%     $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
-%%     $L_t$ &  7nm && & 11.15nm & & & \\ \hline
-%%     $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
-%%     $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
-%%     $R_t$ &  & & &2.16nm & & & \\ \hline
-%%     $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
-%%     $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
-%%     $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & & & \\ \hline
-%%     $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
-%%     $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
-%%     $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
-%%     $c_t$ & & && & & & \\ \hline
-%%     $c_m$ & & && & & & \\ \hline
-%%     $c_b$ & & && & 140 kJ/mol & & \\ \hline
-%%   \end{tabular}
-%%   \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
-%%   \label{table:parameter-table}
-%% \end{figure}
+%% \movie{A third movie, just for kicks.}
 
-%% \subsection{Fitting rate constants}
-%% To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions.
-The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}.
-Simulation behavior for a wide range of $k_b$ and $k_{ub}$ values is shown as a heat map in Figure \ref{fig:kb-kub-heatmap}.\\
+%% \dataset{dataset_one.txt}{Type or paste caption here.}
 
-%% \textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}
+%% \dataset{dataset_two.txt}{Type or paste caption here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}
 
-%% \subsection{Fitting spring constants}
-%% This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\
-
-\newpage
-\chapter{Results \& Discussion}
-\label{chap:ResultsAndDiscussion}
-
-%% \section{Validating model}
-%% The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem.
-Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over a long time.
-This is evidence that both the forces and velocities of the model are properly calculated.
-Grossly incorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy.
-The model's force calculations are further validated in Section \ref{sec:conformational-tests}, and energy conservation is validated in Section \ref{sec:energy-conservation}.\\
-
-%% \begin{figure}[h!]
-%%   \centering
-%%   \begin{minipage}[b]{0.45\textwidth}
-%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
-%%     \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
-%%   \end{minipage}
-%%   \hspace{.2cm}
-%%   \begin{minipage}[b]{0.45\textwidth}
-%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
-%%     \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
-%%   \end{minipage}
-%%   \label{fig:equipartition_agreement}
-%% \end{figure}
-
-\section{Model achieves processivity}
-When the simulation is run at the parameters shown in (\ref{table:thesis-parameters}), the model exhibits stepping behavior, as shown in Figure (\ref{fig:stepping-trajectory}).\\
-
-\begin{figure}[h]
-  \centering
-  \begin{tabular}{| l | l | l | l | l | l |}
-    \hline
-    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
-    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
-  \end{tabular}
-  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures (\ref{fig:stepping-trajectory}) and (\ref{fig:final-histograms}).}
-  \label{table:thesis-parameters}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.9\textwidth]{../../../plots/trajectory-plot_thesis}
-  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation.
-The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer.
-Top: x-projection of binding domains over time.
-The motor steps roughly 50nm in 10 $\mu s$.
-Middle: cartoon depictions of the model during simulation.
-In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots.
-That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$.
-The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model.
-Bottom: y-projection of binding domains over time.
-Notice that only one binding domain is above 0nm at any time.}
-  \label{fig:stepping-trajectory}
-\end{figure}
-
-Figures (\ref{fig:stepping-trajectory}) and (\ref{fig:stepping-trajectory}) demonstrate the model stepping five times, where a step constitutes lifting a binding domain off the microtubule for any amount of time.
-This behavior indicates that a springy hinge model with shifting equilibrium angles is capable of generating processive stepping behavior.
-Now that the model has demonstrated stepping behavior, it must be seen if it can generate steps at a size- and time-scale similar to that which real dynein takes in experiment.\\
-
-Another important determination from Figure (\ref{fig:stepping-trajectory}) is the average position of the unbound foot is about 30nm above the microtubule.
-This is a preliminary finding which may not represent how the model will behave once fit to stepping behavior, so drawing conclusive conclusions from it is impossible.
-However, it does initially suggest how dynein searches for the microtubule.
-Instead of hovering near the microtubule looking for a binding site, the motor pulls its foot away from the microtubule, diffusing until pushed downward far enough to bind.
-This behavior could explain why dynein's stepping pattern is so large: diffusing downward from 30nm would allow significant x-diffusion along the microtubule.
-This could be contrasted with kinesin, which is smaller and could not move its foot so high off the microtubule.\\
-
-Importantly, the parameters causing processive motion are physically reasonable.
-The spring constants are roughly the same size as the energy of hydrolysis of ATP, which is reasonable.
-By a very rough argument, the dynein must move its tail angle by roughly one radian to diffuse enough for a step.
-This would correspond to a $\Delta G_{spring} = \frac{1}{2}c_t\Delta \theta_t \approx \Delta G_{ATP}$, which is very reasonable.
-In addition, the tail spring constant is less than the motor and binding spring constants, which is in line with the notion that the tail is much more elastic than the motor or binding domains.\\
-
-\section{Model step size is highly variant}
-Figure (\ref{fig:final-histograms}) shows the stepping pattern of the model at the parameters shown in Table (\ref{table:thesis-parameters}).
-This simulation was run over a much longer time period than that shown in Figure (\ref{fig:stepping-trajectory}), and hence shows much more significant information on the model's stepping behavior.\\
-
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=0.5\textwidth]{../../../plots/stepping_length_histogram_thesis}%%
-    \includegraphics[width=0.5\textwidth]{../figures/weihong-step-size.pdf}
-    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model.
-Note the model can generate 25nm steps, but has a high preference for <5nm steps.
-Also note that few backward steps are generated by the model.
-Simulation run at conditions in (\ref{table:thesis-parameters}).
-Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
-    \label{fig:final-histograms}
-\end{figure}
-
-Figure (\ref{fig:final-histograms}) shows the model has a strong preference for $<5$nm steps, but is capable of generating steps up to $25$nm in length, with a fairly even distribution of step frequency between $5$ and $25$nm.
-This is a very important result, since it indicates that the model is capable of taking a varied step size.
-This behavior is characteristic of dynein, and hence very important to reproduce.\\
-
-The preference for $<5$nm steps is very un-dynein-like.
-One explanation is that steps may be defined differently between experimental and modeled dynein.
-In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram.
-This may not be how the experiment in (\ref{fig:final-histograms}) records steps.
-Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely.
-A solution may thus be to lower the microtubule binding rate and see if the stepping histogram would level out.\\
-
-The ability of the model to generate near-experiment stepping behavior is imperative if the model is to be considered a proper explanation of dynein's stepping.
-In the case that changing the binding rate does not remove the small-step preference of the model, it may be necessary to change how the model works.
-For example, using the total spring-energy-of-binding change to calculate the binding probability may be invalid, or perhaps the entire two-state model will need to be thrown out.
-The inability of either of these assumptions to predict dynein's behavior would themselves be important findings.\\
-
-Another issue with the simulated histogram is that it shows no steps over $30$nm.
-This is a problem, since taking $40+$nm steps is characteristic of dynein.
-Ideally, tuning the parameters of dynein would increase the step size.
-However, in the case that it can't, this might be an important result.
-The current model assumes connections between domains are rigid.
-This may not be a valid assumption, since coiled coils are generally elastic \cite{myosin-cc-elasticity}.
-Thus it may be necessary to add in elasticity to the model to reproduce long steps.\\
-
-Comparing the simulation results in (\ref{fig:final-histograms}) with the experimental results in (\ref{fig:final-histograms}), it is clear that the model is still far from experimental dynein.
-However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein.
-It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically.
-Lowering the binding rate may even out the histogram and prevent instant rebinding.
-It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm.
-Another issue is the lack of backwards steps, which may also be solved by reducing the spring constants or lowering binding rate.\\
-
-%% \section{Current work: Refining model parameters}
-%% Once validated, the model was fit to experimental data.
-Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values.
-The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment.
-As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.
-
-%% \begin{figure}[H]
-%%   \centering
-%%   \includegraphics[width=\textwidth]{../figures/kb-kub-contour}
-%%   \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state.
-Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.
-The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right.
-Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
-%%   \label{fig:kb-kub-heatmap}
-%% \end{figure}
-
-\newpage
-\chapter{Conclusion}
-\label{chap:Conclusion}
-
-%thoughts
-%% \textit{It is interesting to note that the hydrolysis of ATP is not actually used to directly power the motor -- binding AMP-PMP, a nonhydrolyzable analog of ATP, can also cause the motor to change from state I to state II \cite{FRETstatepaper}.
-The specialness of ATP is that it can be broken down into ADP, which causes another conformation change back to state I.
-Thus, something something the transfer of energy from nucleotide to motor is in its shape, not in its chemistry.}\\
-
-\section{Findings}
-The most important findings of this work are that a springy hinge model of dynein can take steps of a similar size to real dynein.
-What's more, it is likely further tweaking of the model will improve the model's behavior to the point of generating backwards and large steps.
-This would be a very important result which would strongly support the linker-swing/diffusive-step model of dynein stepping and guide further research.\\
-
-Many studies have been done on dynein, resulting in a large body of literature about the motor's behavior and features.
-Sifting through this information to find what is important for the motor's step is a difficult task.
-Mutational studies can remove traits of the motor, deducing what traits are necessary for stepping.
-However, this process is slow, and it can be difficult to remove large traits of the motor while keeping the engineered dynein representative of the natural motor.
-This is where simulations come in.
-Minimal features can be put into a physical model, which can then be tested for behavior similar to real dynein.
-In this study, we created a mathematical model which simplifies the motor to a rigid hinge structure with harmonic spring energies between the hinges.
-The equilibrium angles change dynamically to reflect structural changes during dynein's mechanochemical cycle.
-The model was then subjected to Brownian forces and evolved.
-If the model generates a stepping pattern similar to real dynein, this would demonstrate that dynein can be thought of as a rigid hinged structure.
-This would mean that many other traits of dynein may not be vital for stepping, such as stalk elasticity \cite{sarlahmodel}, motor-motor interaction \cite{sarlahmodel}, nucleotide state \cite{cianfroccoreview}, nucleotide state of non-AAA1 nuclease sites \cite{cianfroccoreview}, and changing stiffness of the foot domain \cite{burgess-paper}.
-Thus future research may want to focus more on linker swing and binding interactions, and less on these other traits.\\
-
-Other findings cast doubt on some aspects of the model.
-The vast preference of the model for $<5$nm steps suggests that the model may handle binding events unlike real dynein.
-When binding, the total spring energy of the transition from a onebound to a bothbound state is calculated, then used to calculate the likelihood of transition via a Boltzmann factor.
-This approach may be overly simple, or take into account the wrong information.
-It may be that it is necessary to expand the two-state model into a three-state model with a low-microtubule-affinity onebound state immediately after unbinding, to prevent instant rebinding.
-This state would eventually transition to the high-microtubule-affinity state after some time.
-If this proves to be necessary to decrease small steps, this would be an interesting result showing that the motor might rely on its low-microtubule-affinity ADP-Pi state to prevent early binding.\\
-
-\section{Further work}
-The goal of studying dynein's mechanochemical cycle is to find an explanation for how it work.
-That is, to find the necessary and sufficient properties of dynein that cause the cycle to happen.
-Simulations are only part of the recipe for creating a scientific theory.
-Simulations are easy to implement and can study phenomena which are difficult to design experiments for.
-However, when experimental data is available, it is generally more reliable than a simulation of the same system.
-This is because a simulation is only as good as the strength of correspondence between the mathematical model and the system it represents.
-With dynein, this correspondence can be hard to achieve because the protein is complicated.
-The model predicts, according to the laws of physics for small objects, how a small machine composed of springy hinges would behave in an aqueous environment.
-This machine can be made the same size and general shape as dynein, and its conformational angles can be made the same as dynein's, and its state transitions can happen in the same way dynein's do.
-However, it is never possible to say that this machine ``is'' dynein or represents how dynein actually behaves.
-Thus, it is only possible to say that the simulation provides sufficient criteria for dynein stepping, not necessary criteria.
-The simulation shows that the linker-swing/diffusive-step model is sufficient for motion, but it cannot show that this is needed for dynein's walk.\\
-
-\subsection{Experimental validation}
-To more strongly support the linker-swing/diffusive step model of dynein motion, more experiments should be done.
-Demonstrating that dynein requires flexible domain connections in order to take such broad steps would be one powerful experiment.
-Mutating the foot and tail domains to be more rigid, then examining stepping behavior would be one way to see if rigidity is necessary for random steps.
-Another experiment could use FRET (Forster Resonance Energy Transfer) and fluorophores on the microtubule and foot domain to track how the distance between the two regions evolves with time.
-This could provide information about the average distance between the MTBD and MT, which would validate this work's finding that the MTBD mostly hovers.
-More importantly, FRET data could be fit to models to predict the amount of diffusion the foot domain undergoes over the course of a step.
-Significant diffusion would indicate that diffusion may be very important for the step.
-Experiments with both feet labeled could get similarly good information.\\
-
-%% \textbf{Talk to Dr. Hsu about this sort of thing...what experiments could be used to validate the model?}
-
-\subsection{Further questions}
-If the model were validated by FRET and rigidity mutation studies, there are many other interesting things which could be found from it.
-First, the amount of work done by the motor could be found by inducing an artificial drag force pulling the protein's motor domains against its direction of travel.
-This force could be integrated over dynein's trajectory to find the work the model exerted on its artificial cargo.
-This could be used to estimate the efficiency of the motor.
-Another interesting study would be to add binding sites to the model, only allowing it to bind at $\alpha-\beta$ tubulin dimerization sites, like real dynein.
-This would mandate re-fitting the binding constants to the new environment.
-It would be interesting to know if this model behaves more, or less dynein-like than the original.
-This would help answer the question of whether dynein searches for a binding site on the microtubule, or if it is naturally tuned to bind at the right site.\\
-
-Another very interesting simulation which could be run could help answer the open question of why kinesin and dynein, though using similar mechanisms, produce such different steps.
-Kinesin, unlike dynein, conducts all of its chemistry directly on its foot.
-This translates to effectively having two fewer joints than dynein.
-Kinesin's stroke is believed to involves a similar foot unbinding, kicking forward, rebinding, then lurching the motor forward mechanism.
-The dynein model could be used to construct a very rough model of kinesin by shrinking the tail linkers and increasing the motor domain spring constant $c_m$ high enough to simulate a rigid hinge.
-This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics.
-If this new model even roughly manages to mimic experimental kinesin stepping, that would be fascinating.
-This result would show that the differences between kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants.
-This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\
-
-\subsection{The future of dynein research}
-The motor protein field has come a long way over the past two decades.
-Theoretical papers in the 90s, such as \textit{Bhaba et.
-al.} \cite{bhabha-paper},  opened up many questions about how cells can use proteins and simple chemical reactions to generate directed, finely-controlled motion.
-Following these papers came low-resolution structures and experiments testing the stepping behavior, directionality, conformation changes and chemical affinities of these motors.
-As structural technology got better, resolution got better, until eventually amino-acid resolution structures were found~\cite{schmidt-carter}.
-These structures allowed more informed hypotheses to integrate experimental data and structures into well-advised theories on motor motility, such as \textit{Andreasson et.
-al.} for kinesin~\cite{kinesin-cycle} and \textit{Cianfrocco et.
-al.} for dynein \cite{cianfroccoreview}.
-These theories are now being tested using state of the art methods.
-For example, a lab at Penn State is currently exploring kinesin dynamics using gold nanoparticles, and is capable of getting 2nm spatial resolution and 1ms temporal resolution~\cite{kinesin-gold-nanoparticle}.
-This level of detail would provide intra-step information about the kinesin mechanochemical cycle, confirming or rejecting hypotheses about how the motor steps.
-If such technology were applied to dynein, the accuracy of the Cianfrocco model and the role of diffusion would be definitively determined.
-However, such experiments take time to design and implement.
-In the meantime, modelling projects like the one in this thesis can be used to provide rough windows into the nanoscale world, guiding future experimental work.
-They sanity-check theories and help scientists form new questions, such as if dynein drags along the microtubule or diffuses above it.
-It is uncertain what direction the field will go over the coming decade, but it is clear that now is a very exciting time for dynein research.\\
-
-%----------------------------------------------------------------------------------------
-%	THESIS CONTENT - APPENDICES
-%----------------------------------------------------------------------------------------
-
-\appendix % Cue to tell LaTeX that the following "chapters" are Appendices
-
-% Include the appendices of the thesis as separate files from the Appendices folder
-% Uncomment the lines as you write the Appendices
-
-\allowdisplaybreaks
-
-\chapter{Onebound equations} % Main appendix title
-\label{sec:AppendixOneboundEquations}
-
-The following is a continuation of the derivation for the full motion equations used to time evolve the onebound model:
-
-\begin{align*}
-AA &= L_s\sin\theta_{bb}      &   LL &= -L_s\cos(\theta_{bb})\\
-BB &= L_t\sin(\theta_{bm})    &	 MM &= -L_t\cos(\theta_{bm})\\
-CC &= -L_t\sin(\theta_{um})   &	 NN &= L_t\cos(\theta_{um})\\
-DD &= -L_s\sin(\theta_{ub})   &	 OO &= L_s\cos(\theta_{ub})\\
-\\
-EE &= -\gamma_m (X_{bm} - X_{bb})       &  PP &= -\gamma_m (Y_{bm} - Y_{bb})\\
-FF &= \gamma_m (X_{t } - X_{bm})        &	 QQ &= \gamma_m (Y_{t } - Y_{bm})\\ 
-GG &= -\gamma_t (X_{t } - X_{bm})       &	 RR &= -\gamma_t (Y_{t } - Y_{bm})\\
-HH &= \gamma_t (X_{um} - X_{t })        &	 SS &= \gamma_t (Y_{um} - Y_{t })\\ 
-II &= -\gamma_m (X_{um} - X_{t })       &	 TT &= -\gamma_m (Y_{um} - Y_{t })\\
-JJ &= \gamma_m (X_{ub} - X_{um})        &	 UU &= \gamma_m (Y_{ub} - Y_{um})\\ 
-KK &= -\gamma_b (X_{ub} - X_{um})       &	 VV &= -\gamma_b (Y_{ub} - Y_{um})\\
-\end{align*}%
-%
-\[
-\begin{pmatrix}
-  AA & 0 & 0 & 0 & EE & FF & 0 & 0\\
-  AA & BB & 0 & 0 & 0 & GG & HH & 0\\
-  AA & BB & CC & 0 & 0 & 0 & II & JJ\\
-  AA & BB & CC & DD & 0 & 0 & 0 & KK\\
-  LL & 0 & 0 & 0 & PP & QQ & 0 & 0\\
-  LL & MM & 0 & 0 & 0 & RR & SS & 0\\
-  LL & MM & NN & 0 & 0 & 0 & TT & UU\\
-  LL & MM & NN & OO & 0 & 0 & 0 & VV\\
-\end{pmatrix}
-\begin{pmatrix}
-    \dot{\theta}_{bb}\\
-    \dot{\theta}_{bm}\\
-    \dot{\theta}_{um}\\
-    \dot{\theta}_{ub}\\
-    \lambda_{bs}\\
-    \lambda_{bt}\\
-    \lambda_{ut}\\
-    \lambda_{us}\\
-  \end{pmatrix}
-=
-  \begin{pmatrix}
-    -F_{bmx} + \gamma_m R_{bmx}\\
-    -F_{tx} + \gamma_t R_{tx}\\
-    -F_{umx} + \gamma_m R_{umx}\\
-    -F_{ubx} + \gamma_b R_{ubx}\\
-    -F_{bmy} + \gamma_m R_{bmy}\\
-    -F_{ty} + \gamma_t R_{ty}\\
-    -F_{umy} + \gamma_m R_{umy}\\
-    -F_{uby} + \gamma_b R_{uby}\\
-  \end{pmatrix}
-\]
-
-Solving the above system for $\dot{\theta}_{bb}, \dot{\theta}_{bm}, \dot{\theta}_{um}$ and $\dot{\theta}_{ub}$ gives the desired velocities. Solution was done via Mathematica.
-
-\chapter{Bothbound equations} % Main appendix title
-\label{sec:AppendixBothboundEquations}
-
-The following are the full motion equations used to time evolve the bothbound model:
-
-\begin{center}
-  \begin{minipage}{0.3\textwidth}
-    \begin{align*}
-      a &= \frac{-dXnm}{dLn}\\
-       b &= \frac{-dXnm}{dLf}\\
-       c &= -(x_{nm} - x_{nb}) / \gamma_m\\
-       d &= (x_t - x_{nm}) / \gamma_m\\
-       e &= \frac{-dXt}{dLn}\\
-       f &= \frac{-dXt}{dLf}\\
-       g &= -(x_t - x_{nm}) / \gamma_t\\
-       h &= (x_{fm} - x_t) / \gamma_t\\
-       i &= \frac{-dXfm}{dLn}\\
-       j &= \frac{-dXfm}{dLf}\\
-       k &= -(x_{fm} - x_t) / \gamma_m\\
-       l &= (x_{fb} - x_{fm}) / \gamma_m\\
-    \end{align*}
-  \end{minipage}
-  \begin{minipage}{0.3\textwidth}
-    \begin{align*}
-       m &= \frac{-dYnm}{dLn}\\
-       n &= \frac{-dYnm}{dLf}\\
-       p &= -(y_{nm} - y_{nb}) / \gamma_m\\
-       q &= (y_t - y_{nm}) / \gamma_m\\
-       r &= \frac{-dYt}{dLn}\\
-       s &= \frac{-dYt}{dLf}\\
-       t &= -(y_t - y_{nm}) / \gamma_t\\
-       u &= (y_{fm} - y_t) / \gamma_t\\
-       v &= \frac{-dYfm}{dLn}\\
-       w &= \frac{-dYfm}{dLf}\\
-       x &= -(y_{fm} - y_t) / \gamma_m\\
-       y &= (y_{fb} - y_{fm}) / \gamma_m
-    \end{align*}
-  \end{minipage}
-\end{center}
-%
-\[
-\begin{pmatrix}
-  a & b & c & d & 0 & 0\\
-  e & f & 0 & g & h & 0\\
-  i & j & 0 & 0 & k & l\\
-  m & n & p & q & 0 & 0\\
-  r & s & 0 & t & u & 0\\
-  v & w & 0 & 0 & x & y\\
-\end{pmatrix}
-\begin{pmatrix}
-    \dot{L}_{n}\\
-    \dot{L}_{f}\\
-    \lambda_{ns}\\
-    \lambda_{nt}\\
-    \lambda_{ft}\\
-    \lambda_{fs}\\
-  \end{pmatrix}
-=
-\begin{pmatrix}
-  -\frac{1}{\gamma}F_{nmx} - R_{nmx}\\
-  -\frac{1}{\gamma}F_{tx}  - R_{tx}\\
-  -\frac{1}{\gamma}F_{fmx} - R_{fmx}\\
-  -\frac{1}{\gamma}F_{nmy} - R_{nmy}\\
-  -\frac{1}{\gamma}F_{ty}  - R_{ty}\\
-  -\frac{1}{\gamma}F_{fmy} - R_{fmy}\\
-\end{pmatrix}
-\]
-
-Solving the above system for $\dot{\theta}_{nm}$ and $\dot{\theta}_{fm}$ gives the desired velocities. Solution was done via Mathematica.
-
-\chapter{Conformational tests}
-\label{sec:conformational-tests}
-The models were tested in the following different conformations to verify they behaved as expected:\\
-
-\textbf{Onebound tests}
-\begin{itemize}
-\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths.
-Also checks that all angular velocities are zero.
-This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or Cartesian) without forces.
-\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths.
-Also check that all velocities are zero.
-This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that Cartesian x-velocities are positive and y-velocities are zero.
-Verifies that the Cartesian velocities have the expected sign.
-\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all Cartesian velocities are zero.
-Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
-  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite.
-Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
-\end{itemize}
-
-These checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
-
-These tests together verify that the onebound model's internal coordinate system's directions match the XY coordinate system directions, that the angular directions in the model properly align with the $\pm x$ and $\pm y$ directions of the XY coordinate system, that velocities have the proper magnitude at zero force and proper sign at nonzero force, and that Brownian and internal forces are in the same unit system.
-There are still errors which could exist in the model pertaining to magnitude of velocity, which will be tested for in the energy conservation section.\\
-
-\textbf{Bothbound tests}
-\begin{itemize}
-\item \textbf{Bothbound:} \textit{Upwards line conformation with no Brownian forces.} Both MTB domains are very close together ($L=10^{-25}$) and motor domains nearly vertical ($\theta_{n/f} = \pi \pm 10^{-15}$).
-Equilibrium angles set to have a vertical line as the lowest energy point.
-Checks that domain x-values are zero$^*$, domain y-values are the correct combination of $L_s$ and $L_t$ lengths, all angles are at equilibrium and all forces are zero.
-Verifies that the domains are properly oriented by the angles, the angles are defined properly and forces are calculated from angles properly.
-\item \textbf{Bothbound:} \textit{Equilateral house conformation with outward x-forces.} The model forms the shape of a square with an equilateral triangle on top, with the tail domain as the triangle.
-Checks if all domains are at the desired locations and the derivatives are the proper sign and are equal and opposite to their counterparts on the opposing side of the house.
-This test verifies that the angular system behaves as expected and forces are symmetric about the two dimers.
-\item \textbf{Bothbound:} \textit{Two table conformations with near/far domains flipped.} Two models are put in the same table-like conformation, but the near/far domains are flipped.
-Checks if opposite domains have the same positions and forces.
-Re-verifies that the model is symmetric in position and force between the two dimers.
-\end{itemize}
-
-These tests verify the bothbound model's angle system behaves as expected, forces are zero when expected and have the proper signs, and that the whole system is symmetric with either dimer.
-
-%----------------------------------------------------------------------------------------
-%	BIBLIOGRAPHY
-%----------------------------------------------------------------------------------------
-
-\printbibliography[heading=bibintoc]
-
-%----------------------------------------------------------------------------------------
+%% \bibliography{pnas-sample}
 

### 2018-08-21 papers/paper/paper.tex
Add bothbound solution section (still needs lots of work)

--- 2018-08-20 papers/paper/paper.tex
@@
 
+\matmethods{
+
+  \section*{Onebound motion equations}
+  Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:
+
+  \begin{align}
+    \dot{X_i} &= \frac{1}{\gamma_i}\left(F^x_i + R^x_i\right)\\
+    \dot{Y_i} &= \frac{1}{\gamma_i}\left(F^y_i + R^y_i\right)
+  \end{align}
+
+  where $F^{x/y}_i$ is the force projection on coordinate $x/y$ of domain $i$, and $R^x_i$ the Brownian force.
+Expanding the force term and transforming position variables to polar coordinates yields the following:
+
+  \begin{multline}
+    \dot{X_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F_x(\theta_1, ..., \theta_n) + \\
+    \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right)R^x_i\big)
+    \label{eq:ob-system}
+  \end{multline}
+
+  \begin{multline}
+    \dot{Y_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F_y(\theta_1, ..., \theta_n) + \\
+    \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right)R^y_i\big)
+    \label{eq:ob-system}
+  \end{multline}
+
+  where the $\lambda$ terms are tension terms needed to maintain the rigid rod constraints.
+Each $X_i$ coordinate is related to the $\theta_j$ coordinates via the recursive formulas $X_1 = L_1\cos(\theta_1)$ and $X_{i>1} = L_i\cos(\theta_i)+X_{i-1}$ for x-coordinates and $Y_1 = 0$ and $Y_{i>1} = L_i\sin(\theta_i)+Y_{i-1}$ for y-coords.
+Thus, each $\dot{X_i}$ term is linearly related to one or more $\dot{\theta_j}$ terms.\\
+
+  There are $n$ unknown $\theta_j$ values and n unknown $\lambda$ values, totaling $2n$ unknown variables.
+There are $2n$ equations linear in $\dot{theta_j}$ and $\lambda_q$, $n$ each from the X and Y equations.
+The system of equations provided by Equation $\ref{eq:ob-system}$ was solved in Matlab, yielding equations for all $\dot{\theta_j}$.
+
+  \section*{Bothbound motion equations}
+  Brownian dynamics was also used for the bothbound case.
+Due to the added constraint of both binding domains being fixed to the microtubule, the model is fully described by angles $\theta_{nm}$ and $\theta_{fm}$; see Figure \ref{fig:model}.
+The positions of non-bound domains are defined by the following equation for $i \in \{nb, nm, t, fm, fb\}$, corresponding to near-binding, near-motor, tail, far-motor and far-binding domains:
+
+  \begin{multline}
+    \dot{X_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F_x(\theta_{nm}, \theta_{fm}) + \\
+    \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right) + R^x_i\big)
+    \label{eq:bb-system}
+  \end{multline}
+
+  \begin{multline}
+    \dot{Y_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F_y(\theta_{nm}, \theta_{fm}) + \\
+    \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right) + R^y_i\big)
+    \label{eq:bb-system}
+  \end{multline}
+
+  Coordinate velocities are similarly linear with $\dot{\theta_{nm}}$ and $\dot{\theta_{fm}}$.
+This system has six independent equations and six unknowns $\dot{\theta_{nm}}, \dot{\theta_{fm}}, \lambda_{ns}, \lambda_{nt}, \lambda_{ft}, \lambda_{fs}$.
+Analytic solutions were acquired using Mathematica.
+}
+
 \section{Results}

### 2018-08-22 papers/paper/paper-supplemental.tex
Add work from thesis to supplemental doc

@@
 % \readytosubmit %% Uncomment this line before submitting, so that the instruction page is removed.
+
+\usepackage{tabstackengine}
+\setstackEOL{\cr}
 
@@
 This system is more compactly represented as:
-{\small
+
+\setstacktabbedgap{4pt}
+{\tiny
   \[
@@
   \resizebox{0.85\linewidth}{!}{%
-  $\begin{pmatrix}
-    L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0\\
-    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0\\
-    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um})\\
-    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um})\\
-    -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0\\
-    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0\\
-    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um})\\
-    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})\\
-  \end{pmatrix}$%
+    $\parenMatrixstack{
+      L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0 \cr
+      L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0 \cr
+      L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um}) \cr
+      L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um}) \cr
+      -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0 \cr
+      -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0 \cr
+      -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um}) \cr
+      -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})
+      }$%
     }

### 2018-08-22 papers/paper/paper.tex
Add work from thesis to supplemental doc

@@
   where $F^{x/y}_i$ is the force projection on coordinate $x/y$ of domain $i$, and $R^x_i$ the Brownian force.
-Expanding the force term and transforming position variables to polar coordinates yields the following:
+Transforming position variables to polar coordinates results in four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um} and \theta_{ub}$.
+Performing this transformation and expanding the force term yields the following equations:
 
   \begin{multline}
-    \dot{X_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F_x(\theta_1, ..., \theta_n) + \\
+    \dot{X_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F^{spr}_x(\theta_1, ..., \theta_n) + \\
     \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right)R^x_i\big)
@@
   \begin{multline}
-    \dot{Y_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F_y(\theta_1, ..., \theta_n) + \\
+    \dot{Y_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F^{spr}_y(\theta_1, ..., \theta_n) + \\
     \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right)R^y_i\big)
@@
 
-  where the $\lambda$ terms are tension terms needed to maintain the rigid rod constraints.
-Each $X_i$ coordinate is related to the $\theta_j$ coordinates via the recursive formulas $X_1 = L_1\cos(\theta_1)$ and $X_{i>1} = L_i\cos(\theta_i)+X_{i-1}$ for x-coordinates and $Y_1 = 0$ and $Y_{i>1} = L_i\sin(\theta_i)+Y_{i-1}$ for y-coords.
+  where the $\lambda$ terms are tension terms needed to maintain the rigid rod constraints and $\vec{F}^{spr}$ the harmonic equilibrium forces felt by each domain.
+Each $X_i$ coordinate is related to the $\theta_j$ coordinates via the recursive formulas $X_{i>1} = L_i\cos(\theta_{i-1})+X_{i-1}$ and $Y_{i>1} = L_i\sin(\theta_{i-1})+Y_{i-1}$ for y-coords.
 Thus, each $\dot{X_i}$ term is linearly related to one or more $\dot{\theta_j}$ terms.\\
@@
   \begin{multline}
-    \dot{X_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F_x(\theta_{nm}, \theta_{fm}) + \\
+    \dot{X_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F^{spr}_x(\theta_{nm}, \theta_{fm}) + \\
     \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right) + R^x_i\big)
@@
   \begin{multline}
-    \dot{Y_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F_y(\theta_{nm}, \theta_{fm}) + \\
+    \dot{Y_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F^{spr}_y(\theta_{nm}, \theta_{fm}) + \\
     \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right) + R^y_i\big)
@@
   Coordinate velocities are similarly linear with $\dot{\theta_{nm}}$ and $\dot{\theta_{fm}}$.
-This system has six independent equations and six unknowns $\dot{\theta_{nm}}, \dot{\theta_{fm}}, \lambda_{ns}, \lambda_{nt}, \lambda_{ft}, \lambda_{fs}$.
+This system has six independent equations and six unknowns $\dot{\theta_{nm}}, \dot{\theta_{fm}}, \lambda_{nb}, \lambda_{nm}, \lambda_{t}, \lambda_{fm}$.
 Analytic solutions were acquired using Mathematica.

### 2018-08-22 papers/paper/paper-supplemental.tex
Add work to methods section

@@
 
+\section*{Simulation special cases}
+Model time evolution led to certain special cases which required attention:\\
+
+\textbf{Domain below microtubule:} When a domain's velocity would result in the domain's y value becoming negative, the velocity was rejected and a new one calculated.
+The stochastic nature of $R$ guarentees that eventually a velocity would be selected which doesn't lead to a negative y value.\\
+
+\textbf{$\theta_{nm}$ or $\theta_{fm}$ approach $\pi/2$:} Bothbound velocity calculations would yield NaNs when motor angles approached $\pi/2$.
+To prevent this, random perturbations of $1e-5$ were added to each motor angle when it was sufficiently close to $\pi/2$.
+
 %%% Each figure should be on its own page

### 2018-08-22 papers/paper/paper.tex
Add work to methods section

@@
 
-  \section*{Onebound motion equations}
+  \section*{Onebound motion equations derivation}
   Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:
@@
 
-  where $F^{x/y}_i$ is the force projection on coordinate $x/y$ of domain $i$, and $R^x_i$ the Brownian force.
+  where $F^{x/y}_i$ is the force projection on coordinate $x/y$ of domain $i$, and $R^x_i$ the Brownian force, a Gaussian zero-mean force with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ \cite{einstein}.
 Transforming position variables to polar coordinates results in four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um} and \theta_{ub}$.
@@
   \begin{multline}
-    \dot{X_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F^{spr}_x(\theta_1, ..., \theta_n) + \\
+    \dot{X_i}\left(\theta_{bb}, ..., \theta_{ub}, \dot{\theta}_{bb}, ..., \dot{\theta}_{ub}\right) = \frac{1}{\gamma_i}\big(F^{spr}_x(\theta_{bb}, ..., \theta_{ub}) + \\
     \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right)R^x_i\big)
@@
   \begin{multline}
-    \dot{Y_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F^{spr}_y(\theta_1, ..., \theta_n) + \\
+    \dot{Y_i}\left(\theta_{bb}, ..., \theta_{ub}, \dot{\theta}_{bb}, ..., \dot{\theta}_{ub}\right) = \frac{1}{\gamma_i}\big(F^{spr}_y(\theta_{bb}, ..., \theta_{ub}) + \\
     \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right)R^y_i\big)
@@
 
-  \section*{Bothbound motion equations}
+  \section*{Bothbound motion equations derivation}
   Brownian dynamics was also used for the bothbound case.
@@
 Analytic solutions were acquired using Mathematica.
+
+  \section*{Simulating the model}
+  Simulations began in the bothbound equilibrium state.
+The model was time-evolved via Euler's Method using analytic expressions for $\{\dot{\theta}_{bb}, \dot{\theta}_{bm}, \dot{\theta}_{um}, \dot{\theta}_{ub}\}$, using a timestep of $dt = 10^{-10}s$.
+In the onebound state, during each timestep the model had a $k_b*dt$ probability of transitioning into the bothbound state, where $k_b = k_b^0\left(1-H\left(X_{uby}-0.1\right)\right)$, where H is the Heaviside function.
+On transition to bothbound, proper $\theta_{nm}$ and $\theta_{fm}$ angles and proper interhead separation $L$ were calculated to yield a bothbound model with identical cartesian positions to the old bothbound, except with the previously unbound binding domain moved to $y=0$.
+Once in bothbound, the model was time-evolved via Euler's Method using analytic expressions for $\{\dot{\theta}_{nm}$ and $\dot{\theta}_{fm}\}$ and a timestep of $dt=10^{-10}s$.
+Each timestep, the bothbound model had a $k_{ub}*dt$ chance of transitioning to onebound, where $k_{ub} = k^0_{ub}e^{-c(\theta-\theta_{eq})}$.
+On transitioning, proper values of $\{\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub}\}$ were calculated to create a onebound model with identical cartesian positions to the old bothbound model.\\
 }

### 2018-08-22 papers/paper/paper.tex
Add work on model section replacing old work. This work is hopefully better.

@@
 
-%% Figure X.1 - poststroke
-%% FIgure X.2 - prestroke
-%% Figure X.A: Model of the protein superimposed over cryo-EM data (with length data)
-%% Figure X.B: Cryo-EM visualizations of how we get equilibrium angles
-%% Add rod vectors connecting each domain
-
 \begin{figure}[tbhp]
@@
 \includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
-\caption{}
+\caption{TODO: make this more schematic-y and add transition arrows with rates}
+\label{fig:model}
 \end{figure}
@@
 Left figure has a scale bar of 15nm, right 26.3nm between MTBD and AAA1 of motor domain.}
-\label{fig:duration-length}
+\label{fig:micrographs}
 \end{figure}
-
-%% \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point.
-Orange indicates the linker region used to dock the two monomers.
-
-\subsection*{Elastic hinge model}~\\
-Our model is designed to capture the course-grained dynamics of the dynein protein while remaining mathematically tractable.
-We capture the structure of the full dynein complex by treating the protein as a set of spheres connected by rigid rods.
-Geometric properties of the model, such as rod length $L_s$ and $L_t$, and sphere radii $R_b$, $R_m$ and $R_t$, are calculated from electron microscopy and crystallography data, as pictured in Fig X.A.
-Each sphere acts as a hinge, and the angle between connected rods, or the MT, is free to vary.
-The model is constrained to remain in the plane of the microtubule, so transverse motion is not allowed.
-The model exists in two states: one called the poststroke state with both binding domain positions constant, as in Figure X.1, and one called the prestroke state with one binding domain free to move, as in Figure X.2.
 
@@
 \caption{Parameters used in model simulation.}
-\label{tab:staticparams}
+\label{tab:params}
 \begin{tabular}{lrrr}
@@
 
-\subsection*{Model dynamics}~\\
-The model experiences internal and external forces.
-The internal forces are due to elastic restoring forces for each hinge angle ($\left[\theta_{bb}, \theta_{bm}, \theta_{t}, \theta_{um},\right]$ for prestroke, $\left[\theta_{nb}, \theta_{nm}, \theta_{t}, \theta_{fm}, \theta_{fb},\right]$ for poststroke) compared to its equilibrium ($\left[\Theta_{bb}, \Theta_{bm}, \Theta_{t}, \Theta_{um},\right]$ for prestroke, $\left[\Theta_{nb}, \Theta_{nm}, \Theta_{t}, \Theta_{fm}, \Theta_{fb},\right]$ for postsroke).
-These equilibrium angles are determined from cryo-EM micrographs of ATP-Vi-bound and ADP-bound dynein monomers, indicated in Figure X.B.\\
+\section{Model}
+This dynein model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex while remaining mathematically simple.
+The structural features of dynein are captured through a two-dimensional geometric model of circular domains connected by rigid rods, shown in Figure \ref{fig:model}.
+The dynamics of dynein are captured by imposing both equilibrium and Brownian forces on each circular domain of the model.
+The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse.
+Each state feels equilibrium forces meant to mimic the structural changes which occur through dynein's chemical cycle.
+This transitioning is meant to capture the powerstroke of dynein, between the apo ``post-powerstroke'' state and the ADP-Pi-bound ``pre-powerstroke'' state.
 
-The torque on each domain is given by:
-%
-\begin{equation}
-  \vec{\tau}_{i} = c_i\left(\theta_{i}-\Theta_{i}\right)\hat{z}
-\end{equation}
-%
-The external forces on the model are random Brownian forces $\vec{R_i} = R_i\hat{x} + R_i\hat{y}$, where $R_i$ is a Gaussian random variable with $\mu_R = 0$ and $\sigma^2_R = 2kbT\gamma_i/dt$, where drag factor $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$.
-Brownian dynamics is used to calculate the velocity on each domain, where velocity is given by:
-%
-\begin{dmath}
-  \vec{v}_i = \gamma_i^{-1}\left(\frac{\vec{\tau}_{i-1}}{L_{i-1}}\left(\hat{z}\times\hat{r}_{i-1}\right)
-  + \frac{\vec{\tau}_{i+1}}{L_{i+1}}\left(\hat{z}\times\hat{r}_{i+1}\right)
-  - \vec{\tau}_{i}\left(\frac{\hat{z}\times\hat{r}_{i-1}}{L_{i-1}}+\frac{\hat{z}\times\hat{r}_{i+1}}{L_{i+1}}\right) + \vec{R_i}\right)
-  \label{eq:motionequation}
-\end{dmath}
-%
-\subsection*{Powerstroke model}~\\
-The dynein powerstroke is the hypothetical process whereby a motor unbinds from the microtubule, undergoes a linker remodel which pushes the motor forward, binds to the microtubule, and undergoes the opposite linker remodel, pulling the rest of the motor forward in a ``powerstroke.'' Our model simplifies the powerstroke cycle by alternating between two states: a two-foot-bound post-powerstroke state similar to the apo dynein, and a one-foot-bound pre-powerstroke state similar to the post-hydrolysis ADP-Pi dynein.
-Our model captures the prestroke kick of the unbound MTBD through different motor hinge equilibrium angles, as calculated from Figure X.B.
-The larger prestroke motor hinge angle causes a forward diffusion of the unbound binding domain on transition to one-foot-bound, followed by another forward diffusion of the whole motor as the MTBD binds and transitions back to post-stroke hinge angles.\\
+\subsection*{Model geometry}
+The dynein model represents a full dynein complex consisting of two dynein heavy chains dimerized by a large tail domain.
+The model accounts for the following domains within the complex: two microtubule binding domains (``MTBD''), two AAA+ heptad motor domains, and a tail domain consisting of many dynein light chains and a dimerization site.
+MTBDs, motor domains and the tail are all represented by circles of radius $R_b$, $R_m$ and $R_t$, respectively.
+Each MTBD is connected to a motor domain via a rigid rod of length $L_s$, meant to represent the stalk domain.
+Each motor domain is connected to the tail domain via a rigid rod of length $L_t$; this rod represents the heavy chain linker and intermediate/light chains which connect the motor to the dimerization site.\\
 
-Dynein's MTBD unbinding dynamics are known to be tension-dependent, where at high interhead separations unbinding favors the lagging MTBD, but no preference between leading and lagging is seen for small interhead separations \cite{yildizpaper}.
-To capture this, the microtubule unbinding rate $k_{ub}$ takes into account absolute binding angle:
-%
-\begin{equation}
-  k_{ub} = k_{ub}^0e^{-c\left(\theta_{xb}-\Theta{xb}\right)}
-\end{equation}
-%
-where $k_{ub}^0$ is the default unbinding rate and $c$ the unbinding exponential factor.
-Each timestep unbinding occurs with probability $k_{ub}dt$.
-On unbinding, the both-foot-bound model transitions to a one-foot-bound model with identical domain positions, but new equilibrium hinge angles.
-Microtubule binding occurs with probability $k_{b}^0dt$ if the binding domain is within $D$ nm of the microtubule.
-On binding, the one-foot-bound model transitions to a both-feet-bound with identical domain positions, but with both MTBDs constrained on the microtubule.\\
+Values for $R$ and $L$ were acquired by aligning the dynein model with EM micrographs of the full dynein complex \cite{burgess-paper,grotjahn}, as shown in Figure \ref{fig:micrographs}.
+See Table \ref{table:params} for these values.\\
 
-\subsection*{Simulating the model}~\\
-The model was simulated using Euler's method to time evolve Equation \ref{eq:motionequation} using a timestep $dt$, transitioning freely between the poststroke and prestroke states.
+\subsection*{Equilibrium forces}
+The onebound model has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$.
+The bothbound model has two: $\theta_{nm}$ and $\theta_{fm}$.
+The model is free to vary across all of these degrees of freedom, barring steric interactions with the microtubule.
+These angles describe a planar model which is not capable of transverse motion.
+To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for onebound and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for bothbound.
+Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain.
+These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}.
+Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.\\
+
+\subsection*{Brownian dynamics}
+Brownian dynamics is used to study the model's dynamics in a biophysical manner.
+In the Brownian regime, protein motion is given by $\dot{\vec{X}} = \frac{1}{\gamma}\left(\vec{F}+\vec{R}\right)$.
+In the model, each circular domain has its own associated $\gamma$ factor given by Stokes' Law as $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$ \cite{stokeslaw}.
+The force on each domain is given by $\vec{F} = \vec{F}_{spr} + \vec{T}$, where $\vec{T}$ is the tension force between domains maintaining the rigid rod constraint.
+Each domain feels not only a harmonic restoring force, but also a Brownian force $\vec{R}$.
+This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ \cite{einstein} and uniformly random direction.
+
+\subsection*{Binding}
+Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the onebound and bothbound states.
+Binding can occur when the onebound model's unbound foot diffuses near enough the microtubule.
+When within a distance of $1 A$, binding occurs at a rate of $k_b$ (Table \ref{table:params}).
+On binding, the onebound model changes state to a bothbound model while retaining the positions of its domains.
+The previously unbound domain is transported to the microtubule.
+
+\subsection*{Unbinding}
+Unbinding occurs when a bothbound MTBD unbinds from the microtubule.
+This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$.
+To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildiz} to allow for interhead communication and bias the motor forward, the parameter $c$ is used to alter the unbinding rates of either MTBD.
+For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $k_{ub} = k^0_{ub}e^{-c\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$.
+This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head.
+Values used for parameters $k^0_{ub}$ and $c$, along with $k_b$, are shown in Table \ref{table:params}.\\
+
+The ``prestroke'' and ``powerstroke'' events in the mechanochemical cycle \cite{cianfrocco} are captured by different motor equilibrium angles between the onebound and bothbound states.
+The onebound ``prestroke'' state has an unbound motor angle closer to $\pi$ than the bothbound motor\cite{burgess-paper}; thus, on unbinding, the unbound MTBD should experience a restoring force effecting the ``prestroke'' conformational change.
+On rebinding, the motors transition back to the poststroke equilibrium, producing restoring forces in the direction of the ``powerstroke.''
 
 \matmethods{
+
+  \section*{Fitting $k_b$ and $k_{ub}$}
+  To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used.
+First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD.
+Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{<t_{ob}}{t_{step}} * \frac{1}{<t_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $<t_{ob}>$ and $<t_{bb}>$ are the expected durations for a onebound and bothbound state, and $<t_{step}> = <t_{ob}> + <t_{bb}>$ is the expected step duration.
+Plugging in the last definition yields $k_{dis} = \frac{<t_{step}> - <t_{bb}}{<t_{step}><t_{bb}>}$.
+Introducing a new variable $<t_{run}>$, the average run length of in vivo dynein, and using the relation $<t_{run}> = k_{dis}^{-1}$, a new relation is found for bothbound time: $<t_{bb}> = \frac{<t_{run}><t_{step}>}{<t_{run}>+<t_{step}>}$.
+Using the definition of $<t_{step}>$ a similar relation is found for onebound time: $<t_{ob}> = \frac{<t_{step}>^2}{<t_{step}>+<t_{run}>}$.
+Finally, using the relation $<t_{step}> = \frac{v}{<L_{step}>}$ for dynein velocity $v$ and expected step length $<L_{step}>$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:
+
+  \begin{align}
+    <t_{ob}> &= \frac{v^2}{L_{step}^2\left(v/L_{step}+<t_{run}>\right)}\\
+    <t_{bb}> &= \frac{v<t_{run}>}{L_{step}\left(<t_{run}>+v/L_{step}\right)}
+  \end{align}
 
@@
 \section{Results}
+-Briefly how we simulated the model
+-Model is forwards-directed and processive (trajectory plot)
+-Tuning the parameters to Yildiz data (kb/kub from theoretical OB/BB time and step length histograms for cm/cb/ct and leading/lagging fractions for c)
+-Does the tuned model walk similarly to Yildiz dynein? (also the lagging vs step length)
 
-%% \begin{figure}%[tbhp]
-%% \centering
-%% \includegraphics[width=\linewidth]{../../plots/stepping_analysis_paper.pdf}
-%% \caption{Histogram of duration of steps taken by model.}
-%% \label{fig:timehist}
-%% \end{figure}
-
-%% \begin{figure*}[tbhp]
-%%   \begin{subfigure}{0.5\textwidth}
-%%     \centering
-%%     \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
-%%   \end{subfigure}%
-%%   \begin{subfigure}{0.5\textwidth}
-%%     \centering
-%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
-%%   \end{subfigure}
-%%   \begin{subfigure}{0.5\textwidth}
-%%     \centering
-%%     \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
-%%   \end{subfigure}%
-%%   \begin{subfigure}{0.5\textwidth}
-%%     \centering
-%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
-%%   \end{subfigure}
-%%   \begin{subfigure}{0.5\textwidth}
-%%     \centering
-%%     \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
-%%     \subcaption{Static unbinding rate}
-%%   \end{subfigure}%
-%%   \begin{subfigure}{0.5\textwidth}
-%%     \centering
-%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
-%%     \subcaption{Exponential unbinding rate}
-%%   \end{subfigure}
-%% \caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
-%% \label{fig:lengthhist}
-%% \end{figure*}
+-Impact of initial unbinding position on step dynamics: whether we need geometry or could use a Markov model
 

### 2018-08-22 papers/paper/paper.tex
Small commit.

@@
 \section{Results}
--Briefly how we simulated the model
--Model is forwards-directed and processive (trajectory plot)
--Tuning the parameters to Yildiz data (kb/kub from theoretical OB/BB time and step length histograms for cm/cb/ct and leading/lagging fractions for c)
--Does the tuned model walk similarly to Yildiz dynein? (also the lagging vs step length)
 
--Impact of initial unbinding position on step dynamics: whether we need geometry or could use a Markov model
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
+\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$.
+\textit{Middle view:} Cartoon snapshot of model at time indicated by bound binding domain.
+Teal lines correspond to the microtubule.
+\textit{Bottom view:} y-projection.
+Arrows on top and bottom plots correspond to respective snapshot times.}
+\label{fig:trajectory}
+\end{figure}
+
+\textbf{Processive, forward-directed motility}\\
+The model was time-evolved using Euler's method.
+When simulated, the model produces processive, forward-directed motion.
+Figure \ref{fig:trajectory} shows a short time window of the model's dynamics.
+The model is capable of taking both forward and backwards steps, but is biased in the forward direction.\\
+
+\textbf{Stepping dynamics}
+The stepping dynamics of the model reproduce experimental results.
+The model is capable of producing a wide variety of step lengths, from 48nm forward to 40nm backwards, as in Figure \ref{fig:behavior}.a.
+The onebound and bothbound times correspond well to the theoretical values, as in \ref{fig:behavior}.b and c.
+The tension-gating mechanism is capable of producing a lagging-head favor, as shown in \ref{fig:behavior}.d.
+
+%% -Briefly how we simulated the model
+%% -Model is forwards-directed and processive (trajectory plot)
+%% -Tuning the parameters to Yildiz data (kb/kub from theoretical OB/BB time and step length histograms for cm/cb/ct and leading/lagging fractions for c)
+%% -Does the tuned model walk similarly to Yildiz dynein? (also the lagging vs step length)
+
+%% -Impact of initial unbinding position on step dynamics: whether we need geometry or could use a Markov model
 
@@
 \caption{\textbf{Basic behavior of our model}}
-\label{fig:}
+\label{fig:behavior}
 \end{figure}
@@
 
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
-\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$.
-\textit{Middle view:} Cartoon snapshot of model at time indicated by bound binding domain.
-Teal lines correspond to the microtubule.
-\textit{Bottom view:} y-projection.
-Arrows on top and bottom plots correspond to respective snapshot times.}
-\label{fig:trajectory}
-\end{figure}
-
 \showmatmethods

### 2018-08-23 papers/paper/paper.tex
minor commit

@@
 First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD.
-Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{<t_{ob}}{t_{step}} * \frac{1}{<t_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $<t_{ob}>$ and $<t_{bb}>$ are the expected durations for a onebound and bothbound state, and $<t_{step}> = <t_{ob}> + <t_{bb}>$ is the expected step duration.
-Plugging in the last definition yields $k_{dis} = \frac{<t_{step}> - <t_{bb}}{<t_{step}><t_{bb}>}$.
-Introducing a new variable $<t_{run}>$, the average run length of in vivo dynein, and using the relation $<t_{run}> = k_{dis}^{-1}$, a new relation is found for bothbound time: $<t_{bb}> = \frac{<t_{run}><t_{step}>}{<t_{run}>+<t_{step}>}$.
-Using the definition of $<t_{step}>$ a similar relation is found for onebound time: $<t_{ob}> = \frac{<t_{step}>^2}{<t_{step}>+<t_{run}>}$.
-Finally, using the relation $<t_{step}> = \frac{v}{<L_{step}>}$ for dynein velocity $v$ and expected step length $<L_{step}>$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:
+Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{\bar{t}_{ob}}{\bar{t}_{step}} * \frac{1}{\bar{t}_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $\bar{t}_{ob}$ and $\bar{t}_{bb}$ are the expected durations for a onebound and bothbound state, and $\bar{t}_{step} = \bar{t}_{ob} + \bar{t}_{bb}$ is the expected step duration.
+Plugging in the last definition yields $k_{dis} = \frac{\bar{t}_{step} - \bar{t}_{bb}}{\bar{t}_{step}\bar{t}_{bb}}$.
+Introducing a new variable $\bar{t}_{run}$, the average run length of in vivo dynein, and using the relation $\bar{t}_{run} = k_{dis}^{-1}$, a new relation is found for bothbound time: $\bar{t}_{bb} = \frac{\bar{t}_{run}\bar{t}_{step}}{\bar{t}_{run}+\bar{t}_{step}}$.
+Using the definition of $\bar{t}_{step}$ a similar relation is found for onebound time: $\bar{t}_{ob} = \frac{\bar{t}_{step}^2}{\bar{t}_{step}+\bar{t}_{run}}$.
+Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected step length $\bar{L}_{step}$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:
 
   \begin{align}
-    <t_{ob}> &= \frac{v^2}{L_{step}^2\left(v/L_{step}+<t_{run}>\right)}\\
-    <t_{bb}> &= \frac{v<t_{run}>}{L_{step}\left(<t_{run}>+v/L_{step}\right)}
+    \bar{t}_{ob} &= \frac{v^2}{\bar{L}_{step}^2\left(v/\bar{L}_{step}+\bar{t}_{run}\right)}\\
+    \bar{t}_{bb} &= \frac{v\bar{t}_{run}}{\bar{L}_{step}\left(\bar{t}_{run}+v/\bar{L}_{step}\right)}
   \end{align}

### 2018-08-27 scripts/color_hist2.py
Make make make remotely on cluster

@@ -2,7 +2,11 @@
 
 import numpy as np
 import matplotlib
-#matplotlib.use('Agg')
+import sys
+
+if 'show' not in sys.argv:
+    matplotlib.use('Agg')
+
 import matplotlib.pyplot as plt
 import argparse
 import os

### 2018-08-27 scripts/generate-paper-model-figures.py

@@ -4,8 +4,8 @@ from __future__ import division
 import numpy as np
 import time, signal, sys, os, matplotlib, subprocess, re
 
-# if 'show' not in sys.argv:
-#     matplotlib.use('Agg')
+if 'show' not in sys.argv:
+    matplotlib.use('Agg')
 
 import dynein.draw.cartoon as cartoon
 

### 2018-08-29 data/paper_params.py
Add new stepping data

@@ -1,7 +1,7 @@
 #!/usr/bin/python3
 
-k_b = 1.4e8 # s^-1
-k_ub = 120 # s^-1
+k_b = 3e7 # s^-1
+k_ub = 40 # s^-1
 
 trajectory_k_b  = 9.5e9 # s^-1
 trajectory_k_ub = 1e20 # s^-1

### 2018-08-29 papers/paper/paper.tex
Break up model figs into a simpler one for the main paper and a more detailed one for the supplemental

@@
 \centering
-\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}%
-\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
+\includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
 \caption{TODO: make this more schematic-y and add transition arrows with rates}
@@
 Using the definition of $\bar{t}_{step}$ a similar relation is found for onebound time: $\bar{t}_{ob} = \frac{\bar{t}_{step}^2}{\bar{t}_{step}+\bar{t}_{run}}$.
-Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected step length $\bar{L}_{step}$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:
+Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected tail step length $\bar{L}_{step}$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:
 
   \begin{align}
-    \bar{t}_{ob} &= \frac{v^2}{\bar{L}_{step}^2\left(v/\bar{L}_{step}+\bar{t}_{run}\right)}\\
-    \bar{t}_{bb} &= \frac{v\bar{t}_{run}}{\bar{L}_{step}\left(\bar{t}_{run}+v/\bar{L}_{step}\right)}
+    \bar{t}_{ob} &= \frac{\bar{L}^2}{\bar{v}^2\left(\bar{L}/v+\bar{t}_{run}\right)}\\
+    \bar{t}_{bb} &= \frac{\bar{L}\bar{t}_{run}}{v\left(\bar{t}_{run}+\bar{L}/v\right)}
   \end{align}
+
+  For estimating onebound and bothbound times from Yildiz \textit{et al}\cite{yildiz}, a velocity of $124 nm/s$ is used.
+A study with a similar velocity is used to estimate $\bar{t}_{run} = 1060 nm / 134 nm / s = 7.9s$ \cite{weihongpaper}.
+These observables, along with $\bar{L} = 8nm$, yield estimations $\bar{t}_{ob} = 5.2*10^{-4}s$ and $\bar{t}_{bb} = 6.4 * 10^{-2}s$.\\
 

### 2018-08-30 data/paper_params.py
Add new paper main data

@@ -1,7 +1,7 @@
 #!/usr/bin/python3
 
-k_b = 3e7 # s^-1
-k_ub = 40 # s^-1
+k_b = 3e6 # s^-1
+k_ub = 35 # s^-1
 
 trajectory_k_b  = 9.5e9 # s^-1
 trajectory_k_ub = 1e20 # s^-1

### 2018-08-30 scripts/generate-paper-unbinding-rate-data.py
Refactor make_all_stepping_plots.py to also make unbinding probability plots, be more modular

@@ -15,7 +15,7 @@ write_rate = 1e5
 runtime = 7e-4
 seed = 1
 
-for L in [10, 15, 20, 25, 30, 35, 40, 45, 50]:
+for L in [10, 20, 30, 40, 50]:
     basename = "paper_unbinding_probability__L-%s,s-%s" % (str(L), seed)
 
     cmd = ["./simulate_unbinding_rates",

### 2018-08-30 scripts/make_all_stepping_plots.py

@@ -25,402 +25,366 @@ EPSILON = 1e-7
 def equal(f1, f2):
     return abs(f1-f2) < EPSILON
 
-plt.rcParams.update({'font.size': 8})
+def get_stepping_data(args):
+    data_files = []
+    for fname in os.listdir(args.data_directory):
+        if os.path.isfile(args.data_directory + "/" + fname):
+            if (args.data_basename in fname and ".txt" in fname):
+                if ("~" not in fname and "movie" not in fname and "config" not in fname):
+                    data_files.append(args.data_directory + "/" + fname)
 
-parser = argparse.ArgumentParser(description = 'script to generate various histograms from stepping data.')
+    if len(data_files) == 0:
+        print("No files of form " + args.data_directory + "/*" + args.data_basename + "*.txt found. Exiting.")
+        exit(1)
 
-parser.add_argument('-d', '--data-directory', dest = 'data_directory', action='store', type = str,
-                    default="data/", help='data file directory', required = False)
-parser.add_argument('-b', '--data-basename', dest = 'data_basename', action='store', type = str,
-                    default="", help='data file basename', required = True)
-parser.add_argument('-p', '--param-file', dest = 'parameters_filename', action='store', type = str,
-                    default="", help='parameter filename (.tex)')
-parser.add_argument('-q', '--quick', dest='quick', action='store_true', default=False,
-                    help='Only make the stepping length histogram')
+    data_objects = []
 
-args = parser.parse_args()
+    for data_file in data_files:
+        data_objects.append(datalib.SteppingData(data_file))
 
-if args.parameters_filename != "":
-    run_conditions = open(args.parameters_filename).read().replace("\n", " ").replace("\\\\", "\\")
+    stepping_data = {}
 
-data_files = []
-for fname in os.listdir(args.data_directory):
-    if os.path.isfile(args.data_directory + "/" + fname):
-        if (args.data_basename in fname and ".txt" in fname):
-            if ("~" not in fname and "movie" not in fname and "config" not in fname):
-                data_files.append(args.data_directory + "/" + fname)
[…]

### 2018-08-31 data/paper_params.py
Add new papermain data

@@ -1,7 +1,7 @@
 #!/usr/bin/python3
 
 k_b = 3e6 # s^-1
-k_ub = 35 # s^-1
+k_ub = 30 # s^-1
 
 trajectory_k_b  = 9.5e9 # s^-1
 trajectory_k_ub = 1e20 # s^-1

### 2018-09-01 scripts/generate-paper-main-data.py
mini commit

@@ -8,7 +8,7 @@ sys.path.insert(0, os.getcwd() + "/data/")
 import paper_params as params
 
 runtime = 5
-seeds = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16]
+seeds = [17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]
 
 for s in seeds:
     os.system("rq run --job-name papermain-" + str(s) \

### 2018-09-02 papers/paper/paper.tex
Refactor make_all_stepping_plots.py to also make unbinding probability plots, be more modular
Add force vs velocity literature data

@@
 
-  \section*{Fitting $k_b$ and $k_{ub}$}
+  \section*{Fitting $k_b$ and $k_{ub}$}\\
   To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used.
@@
 
-  \section*{Onebound motion equations derivation}
+  \section*{Onebound motion equations derivation}\\
   Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:
@@
 
-  \section*{Bothbound motion equations derivation}
+  \section*{Bothbound motion equations derivation}\\
   Brownian dynamics was also used for the bothbound case.
@@
 
-  \section*{Simulating the model}
+  \section*{Simulating the model}\\
   Simulations began in the bothbound equilibrium state.
@@
 On transitioning, proper values of $\{\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub}\}$ were calculated to create a onebound model with identical cartesian positions to the old bothbound model.\\
+
+  \section*{Calculating leading/lagging probability vs displacement}\\
+
+  \section*{Calculating force-dependent velocities}\\
 }
@@
   \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
-  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
 \caption{\textbf{Basic behavior of our model}}
@@
 
+\begin{figure}[tbhp]
+  \centering
+  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
+\caption{}
+\label{fig:}
+\end{figure}
+
 \begin{figure*}[tbhp]
@@
 \end{figure*}
+
+\section{Discussion}
+
+\begin{enumerate}
+\item \cite{lippert} is a 2017 PNAS paper claiming the powerstroke model is wrong since angular displacement of the dynein ring is weak (+- 7 degrees) and weakly correlated with stepping.
+However, their camera records at 50ms resolution, which is 100x slower than our average onebound time.
+Thus their whole experiment is somewhat flawed.
+This is relevant since the oneboudn time duration may not be well known, and our theoretical results may be relevant.
+\item No need for being guided to Mt binding sites, the motor naturally can take 16nm steps through a powerstroke
+\item Is tension gating necessary for our model? Could run simulations without it to see how the model changes
+\item Dynein's adjacent step step length correlation is low; thus the motor is a memory-less process which could be simulated by a Markov model.
+Also look at ob and bb time covariance and displacement covariance
+\end{enumerate}
 

### 2018-09-03 papers/paper/paper.tex
Add randomsearchplot to supplemental pdf. Hard-adding the plot PDF because the data files are large.

@@
 
-  \section*{Fitting $k_b$ and $k_{ub}$}\\
+  \section*{Fitting $k_b$ and $k_{ub}$}
   To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used.
@@
 
-  \section*{Onebound motion equations derivation}\\
+  \section*{Onebound motion equations derivation}
   Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:
@@
 
-  \section*{Bothbound motion equations derivation}\\
+  \section*{Bothbound motion equations derivation}
   Brownian dynamics was also used for the bothbound case.
@@
 
-  \section*{Simulating the model}\\
+  \section*{Simulating the model}
   Simulations began in the bothbound equilibrium state.
@@
 
-  \section*{Calculating leading/lagging probability vs displacement}\\
+  \section*{Calculating leading/lagging probability vs displacement}
 
-  \section*{Calculating force-dependent velocities}\\
+  \section*{Calculating force-dependent velocities}
 }

### 2018-09-12 papers/paper/paper-supplemental.tex
Break up model figs into a simpler one for the main paper and a more detailed one for the supplemental

@@
 \section*{Deriving motion equations}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}
+\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
+\caption{}
+\label{fig:supp-model}
+\end{figure}
+
 \subsection*{Onebound case}
@@
 
+\section*{Fitting spring constants}
+How we fit spring constants; maybe plot the 3d correlation-color scatter plot for 3 springs
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=0.7\linewidth]{../../plots/randomsearchplot.pdf}
+\caption{\textbf{Fitting spring constants through homology to experimental stepping data.} \textit{A.} 3D scatter plot of simulations color-coded by the sum-of-squares error between the model and experimental stepping histograms.
+\textit{B-D:} Scatter plots of spring constants and error; orange dots indicate averages over nearest 25 points.}
+\label{fig:supp-model}
+\end{figure}
+
 %%% Each figure should be on its own page

### 2018-09-12 papers/paper/paper.tex

@@
 \begin{enumerate}
-\item Document carefully where all figures and data comes from.
-\item Describe our algorithm in sufficient detail.
 \item Fix stepping analysis python module to categorize zero-length
@@
   which foot lifted if it didn't move.
-\item Update plotting scripts to use stepping analysis python module,
-  or other modules.
-\item Write up how we estimate one-bound/bothbound time ratio from
-  processivity.  Ensure simulation obeys this?
-\item Keep trying to get data from Yildiz.
-\item Add force-dependent plots to compare with yildiz?
+\item When we have all data, write discussion
+\item Rewrite introduction
+\item Possibly sample stalk angles at high resolution and also 50ms, to show why the low time resolution in Lessinger prevented them from seeing the powerstroke?
+\item Test suite for paper plots to see if there aren't subtle bugs?
 \end{enumerate}
@@
   check against code.
-\item Figure out how to do no-unbinding simulations to get Yildiz
-  comparison data.  Also this gives us unbinding rates that will agree
-  with our stepping time, etc. \verb!src/simulate_unbinding_rates.cpp!
-\item Play with parameters to get stepping length histogram more
-  reasonable (this automatically gives us the velocity).
-\item Run long/many simulations with final parameters.
 \item Run a low-ATP simulation for comparison data.
-\item Nice final version of stepping length histogram.
-\item Nice final version of tension-gating Yildiz comparison.
 \item Consider a no-binding simulation and a separable model.  Create

### 2018-10-03 papers/paper/paper.tex
change figures and start converting to fac

@@
 \usepackage{breqn}
+\usepackage{color}
+
+\newcommand\davidsays[1]{{\em\color{blue} {\bf DR:} #1}}
 
@@
   \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
-  \includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
-  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
-\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
+  a)\includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+  b)\includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
+  c)\includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
+\caption{\davidsays{Look up Yildiz figure for (a)}\textbf{Does our model capture dynamics a markov model wouldn't?}}
 \label{fig:}

### 2018-10-28 papers/paper/paper.tex
Add a bit of new work to the intro

@@
 
-\title{Dynein walks like an Imperial AT-ST}
+\title{Brownian dynamics simulation of cytoplasmic dynein reproduces bidirectional stepping}
 
@@
 Here we show how a simple Brownian dynamics model can be used to test the mechanochemical cycle picture of dynein processivity.\\
+
+\textbf{New intro}\\
+
+--Background on dynein
+--Evidence for dynein's powerstroke
+
+However, to our knowledge, no work has been done to study dynein dynamics computationally.
+Existing models use chemical rate transitions and assume independence of steps \cite{sarlahmodel}.
+No models exist which account for the diffusion dynamics or conformational changes of dynein as it walks along the microtubule.
+Understanding the coordinated dynamics of dynein's domains is necessary to fully describe the protein's motility.
+Testing whether the current powerstroke model is capable of generating processive motion would be a good first step to understanding dynein's dynamics.\\
+
+Here we present a course-grained model of cytoplasmic dynein which treats its domains as connected rigid bodies.
+Chemical transitions and conformational changes consistent with the powerstroke model are accounted for via elastic forces.
+The dynamics are determined using Brownian dynamics.
+The model is capable of generating directed motility at rates similar to experiment.
+Further, we show that the model displays further complex behavior, such as tension gating and force-mediated bidirectionality.\\
 
@@
   \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
-\caption{}
+\caption{Gennerich et al \cite{responsetoload}}
 \label{fig:}
@@
 \item Test suite for paper plots to see if there aren't subtle bugs?
+\item Re-run velocity vs force simulation at a much lower rate to match the Gennerich velocity at pN=0
 \end{enumerate}

### 2018-10-31 papers/paper/paper.tex
Add new introduction rough draft

--- 2018-10-03 papers/paper/paper.tex
@@
 
-\title{Dynein walks like an Imperial AT-ST}
+\title{Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping}
 
@@
 
-\dropcap{D}ynein is a motor protein used to generate directed force in cells.
+%% \dropcap{C}ytoplasmic dynein-1 is a motor protein used to generate directed force in cells.
 The protein is a homodimer which binds to cellular filaments known as microtubules (MTs).
@@
 
-Dynein is unique in that it has a widely varied step size.
+%% Dynein is unique in that it has a widely varied step size.
 Dynein's average step is 8 \textit{nm} in the forwards direction, but it is capable of taking 32 \textit{nm} steps in the forwards and reverse directions \cite{weihongpaper} \cite{yildizpaper}.
@@
 
-A simple explanation for dynein's stepping pattern can be given based on only a few facts about the protein.
+%% A simple explanation for dynein's stepping pattern can be given based on only a few facts about the protein.
 It is known that on treatment with ATP, the tail-head-MTBD angle of a dynein monomer alters, moving the MTBD closer to the tail \cite{carteradpprimed} \cite{burgess-paper}.
@@
 
-There are many relevant details about dynein which this simple model doesn't account for.
-Dynein is known to have low interhead communication at low separation, but to have a tension-gated stepping pattern at high separations \cite{yildizpaper}.
-It is also suggested that dynein's MTBD doesn't conduct an undirected search for its next MT binding site, but rather is guided by long-range electrostatic interactions from each MT binding site \cite{longrangemt}.
-Dynein has several cofactors which alter its dynamics.
-For example, the motor's stall force is tripled when exposed to dynactin and Bic2D \cite{yildizdynactin}.
-This is odd, since the dynactin- and Bic2D-binding site on dynein is on the tail, far from the motor heads.
-Many of these details suggest a complicated picture of dynein motility than a simple forward kick and pull mechanism.\\
-
-Several computational models have been created to explain dynein's motility.
+%% Several computational models have been created to explain dynein's motility.
 \textit{Imamula et.
@@
 Here we show how a simple Brownian dynamics model can be used to test the mechanochemical cycle picture of dynein processivity.\\
+
+%% Dynein has several cofactors which alter its dynamics.
+For example, the motor's stall force is tripled when exposed to dynactin and Bic2D \cite{yildizdynactin}.
+This is odd, since the dynactin- and Bic2D-binding site on dynein is on the tail, far from the motor heads.
+
+\dropcap{D}ynein is a motor protein which generates motion for various cellular processes.
+Cytoplasmic dynein-1, here referred to as ``dynein,'' is a motor which performs cargo transport and aids in nuclear division.
+The protein consists of a ring structure of six AAA+ domains known as the ``head'' which connect via a long stalk to a microtubule binding domain (MTBD).
+The AAA+ region is responsible for hydrolyzing ATP to drive dynein's motion.
+The head is connected via a linker to a large tail domain responsible for binding various cargos and accessory proteins.
+The tail is also the site of dimerization, where two dynein monomers join to form a homodimeric unit capable of motion.\\
+
+Dynein's mechanism of motion generation is the least understood of all motor proteins.
+Kinesin and myosin both take periodic, consistent steps of 8nm.
+In contrast, dynein is known to take highly variant steps both forwards and backwards, but averaging 16nm \cite{yildizpaper, weihongpaper}.
+Another interesting feature of dynein is the 20nm separation between its ATP hydrolysis and the site and MT binding site \cite{3vkh-cite}.
+The protein must transmit information about ATP binding across this distance in order to coordinate its steps \cite{mt-atp-coupling}.
+Explaining these phenomena is necessary to fully understand dynein's mechanism.\\
+
+Studies over the past 15 years have shed much light on dynein's stepping mechanism.
+The motor is known to switch between two conformational states depending on its ATP hydrolysis state \cite{burgess-paper, FRETstatepaper, carter-paper, nicastro, schmidt-carter}.
+It is also known that ATP binding can induce structural changes within the motor which increase unbinding rate \cite{leschziner, carter-paper}, and similarly that microtubule rebinding can influence nucleotide unbinding rate \cite{mt-atp-coupling}.
+Taken together this evidence is synthesized into a powerstroke model \cite{cianfroccoreview, imamulamodel}.
+In the powerstroke model, dynein binds ATP, causing structural changes which eventually lead to microtubule unbinding at its MTBD.
+These structural changes transition the motor into a more open position, causing the MTBD to diffuse forwards on the microtubule.
+This biased search is known as the prestroke.
+Eventually the MTBD rebinds the microtubule, causing structural changes inducing the ejection of hydrolyzed ADP and transitioning back to the closed position.
+This causes the motor to lurch forward in a process called the powerstroke.
+The protein is now ready to re-bind ATP and take another step.\\
+
+Ample evidence exists that dynein engages in an ATP-induced prestroke and MT-binding-induced powerstroke.
+However, to our knowledge, no work has been done to test whether a structural model of dynein obeying the proposed mechanochemical cycle is sufficient to reproduce experimental stepping data.
+Existing computational models use chemical rate transitions and assume independence of steps, without simulating the entire mechanochemical cycle \cite{sarlahmodel}.
+No models have combined structural and kinetic data to simulate a dynein model in a biophysically realistic way.
+It is necessary to do so to properly test the powerstroke hypothesis.
+Such a study would determine if the powerstroke mechanism is sufficient to explain dynein's walk, or if further explanation is necessary.
+Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
+Such a study would be able to find the minimum criteria for generating dynein's motion.\\
+
+Here we present a course-grained model of cytoplasmic dynein which treats its domains as connected rigid bodies.
+Chemical transitions and conformational changes consistent with the powerstroke model are accounted for via elastic forces.
+The dynamics are determined using Brownian dynamics.
+The model is capable of generating directed motility at rates similar to experiment.
+Further, we show that the model displays more complex behavior, such as tension gating and force-mediated bidirectionality.\\
 
@@
 
-%% -Impact of initial unbinding position on step dynamics: whether we need geometry or could use a Markov model
-
 \begin{figure}[tbhp]
@@
 
-\begin{figure*}[tbhp]
-    \includegraphics[width=0.5\linewidth]{../../plots/paper_foot_order_histogram.pdf}
-\caption{The left plot is the $C=0$ case where the unbinding rate is
-  independent of angle.  Here ``alternating'' means that the binding
-  domain which did not move last time moved this time.  Passing means
-  that the moving foot was behind, and ended up in front.}
-\label{fig:steppingorder}
-\end{figure*}
+%% \begin{figure*}[tbhp]
+%%     \includegraphics[width=0.5\linewidth]{../../plots/paper_foot_order_histogram.pdf}
+%% \caption{The left plot is the $C=0$ case where the unbinding rate is
+%%   independent of angle.  Here ``alternating'' means that the binding
+%%   domain which did not move last time moved this time.  Passing means
+%%   that the moving foot was behind, and ended up in front.}
+%% \label{fig:steppingorder}
+%% \end{figure*}
 

### 2018-11-05 papers/johnWaczak-thesis/modelExplanation/model_explanation.tex
added folder for model explanation

\documentclass[a4paper, 11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}  
\usepackage{amsthm}
\usepackage{ulem} 
\usepackage{graphicx}
\usepackage{enumitem} % use for making lettered list 
\usepackage{bbm} % use for making the 1 identity operator EX: \mathbbm{1}
\usepackage{subfig} 
\graphicspath{ {images/} }

% format to allow bolded theorems, corollaries, etc... 
\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}
\newtheorem*{lemma}{Lemma}
\newtheorem*{definition}{Definition}
\newtheorem*{Example}{Example} 
\newtheorem*{Remark}{Remark}

% stop typing \mathbb a thousand times 
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Mat}[2]{\mathcal{M}_{#1\times#2}}

% change margins for solution
\newenvironment{solution}{%
	\begin{list}{}{%
			\setlength{\topsep}{0pt}%
			\setlength{\leftmargin}{1.5cm}%
			\setlength{\rightmargin}{1.5cm}%
			\setlength{\listparindent}{\parindent}%
			\setlength{\itemindent}{\parindent}%
			\setlength{\parsep}{\parskip}%
		}%
		\item[]}{\end{list}}

\begin{document}
%Header-Make sure you update this information!!!!
\noindent
\large\textbf{Dynein Model Explanation and Theory} \hfill \textbf{John Waczak} \\
\normalsize Physics Thesis \hfill  Date: \today \\
Dr. David Roundy 
\par\noindent\rule{\textwidth}{0.4pt} \\

\end{document}

### 2018-11-05 papers/paper/paper.tex
Move figures around and remove onebound-vs-steplen hist

@@
 \begin{figure}[tbhp]
+  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_displacement.pdf}
+  \caption{\textbf{Tension gating of model} \davidsays{Look up Yildiz figure}}
+  \label{fig:tensiongating}
+\end{figure}
+
+\begin{figure}[tbhp]
   \centering
-  a)\includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
-  b)\includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
-  c)\includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
-  \caption{\davidsays{Look up Yildiz figure for (a)}\textbf{Does our model capture dynamics a markov model wouldn't?}}
+  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
+  \caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
 \label{fig:}

### 2018-11-05 scripts/make_all_stepping_plots.py

@@ -159,13 +159,12 @@ def get_cli_arguments():
     return parser.parse_args()
 
 def make_behavior_plot(args, stepping_data, up_data):
-    fig = plt.figure(figsize=(4,8))
-    gs = gridspec.GridSpec(7, 2)
+    fig = plt.figure(figsize=(4,6))
+    gs = gridspec.GridSpec(5, 2)
     ax0 = fig.add_subplot(gs[0:2, 0:2])
     ax1 = fig.add_subplot(gs[2:4, 0:2])
     ax2 = fig.add_subplot(gs[4, 0])
     ax3 = fig.add_subplot(gs[4, 1], sharey=ax2)
-    ax4 = fig.add_subplot(gs[5:7, 0:2])
 
     data_files = []
     for fname in os.listdir(args.data_directory):
@@ -274,23 +273,27 @@ def make_behavior_plot(args, stepping_data, up_data):
     ax3.spines["top"].set_visible(False)
     ax3.spines["right"].set_visible(False)
 
+    plt.tight_layout(w_pad=2, h_pad=0.5)
+    plt.savefig("plots/model_behavior.pdf", format="pdf")
+
     # unbinding probability vs L plot
+    fig = plt.figure(figsize=(4,2))
     yildiz_displacements = [10, 20, 30, 40, 50]
     yildiz_lagging_fractions = [0.525, 0.545, 0.61, 0.59, 0.67]
     yildiz_lagging_uncertainty = [0.06, 0.04, 0.035, 0.045, 0.075]
 
-    ax4.errorbar(yildiz_displacements, yildiz_lagging_fractions, yerr=yildiz_lagging_uncertainty, label="Experiment", fmt='o-', c='C0', markersize=4, linestyle='', capsize=1, elinewidth=0.3, markeredgewidth=0.3)
+    plt.errorbar(yildiz_displacements, yildiz_lagging_fractions, yerr=yildiz_lagging_uncertainty, label="Experiment", fmt='o-', c='C0', markersize=4, linestyle='', capsize=1, elinewidth=0.3, markeredgewidth=0.3)
 
-    ax4.scatter(up_data["Ls"], up_data["mean_lagging_probability_per_L"] / (up_data["mean_lagging_probability_per_L"] + up_data["mean_leading_probability_per_L"]), c='C1', label="Model", zorder=2, s=4**2)
-    ax4.set_xlabel("Binding domain separation (nm)")
-    ax4.set_ylabel("P(lagging step)")
-    ax4.legend()
[…]

### 2018-11-06 papers/paper/paper.tex
Add captions to all figures.

@@
 \includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
-\caption{TODO: make this more schematic-y and add transition arrows with rates}
+\caption{\textbf{Basic geometric model in pre-powerstroke and post-powerstroke states.} \textit{Left: } Pre-powerstroke model of dynein with one MTBD bound to microtubule and the other free.
+Angles are measured from the $+\hat{x}$ direction.
+\textit{Right: } Post-powerstroke model with both MTBDs bound to microtubule.
+MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail.
+Lengths and radii not to scale.}
 \label{fig:model}
@@
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model at equilibrium angles superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
-\textit{Right:} Model at equilibrium superimposed over full-length dimerized dynein bound to accessory proteins, (map ID EMD-7000) \cite{grotjahn}.
-Left figure has a scale bar of 15nm, right 26.3nm between MTBD and AAA1 of motor domain.}
+\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-powerstroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-powerstroke ADP-Vi-bound state \cite{burgess-paper}.
+Interdomain lengths and radii scaled to micrograph scale bar.
+No microtubule is present, so $\theta_{nb}$ is arbitrary.
+\textit{Right: } Model with angles at pre-powerstroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}.
+Interdomain lengths and radii scaled to density map.}
 \label{fig:micrographs}
@@
 
-\begin{table}[tbhp]
+%% Model at equilibrium angles superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}.
+\textit{Right:} Model at equilibrium superimposed over full-length dimerized dynein bound to accessory proteins,  Left figure has a scale bar of 15nm, right 26.3nm between MTBD and AAA1 of motor domain.
+
+\begin{minipage}{\linewidth}%% [tbhp]
   \centering
-\caption{Parameters used in model simulation.}
-\label{tab:params}
   \begin{tabular}{lrrr}
@@
     $R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\
-
     \bottomrule
@@
 
-%% \addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
-\end{table}
+  \begin{minipage}{\linewidth}
+    \small
+    \textbf{Table 1.
+Parameters used in simulation.} $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
+$k_b$ and $k_{ub}$ are the rates of pre-powerstroke to post-powerstroke and post-powerstroke to pre-powerstroke transitions, respectively.
+$L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
+$c$ is the tension-gating factor.
+The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-powerstroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-powerstroke motor and both post-powerstroke motors.
+$R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
+Parameters used for all simulations unless otherwise noted.
+  \end{minipage}
+  \label{tab:params}
+
+\end{minipage}
 
@@
   \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
-\caption{\textbf{Basic behavior of our model}}
+\caption{\textbf{Stepping dynamics of model.} \textit{Top: } Average position of near and far MTBDs over 5 seconds of simulation and 8 random seeds.
+Trajectory compared with single-motor-labelled cytoplasmic dynein from DeWitt \textit{et.
+al.} \cite{yildizpaper}.
+\textit{Middle: } Model step size distribution from 32 5 second simulations.
+Step length is defined as the change in an MTBD position during a full step cycle.
+Also plotted is the head step size distribution from DeWitt \textit{et.
+al.} \cite{yildizpaper}.
+\textit{Bottom left: } Distribution of time spent in the pre-powerstroke state during a full mechanochemical cycle from the same dataset.
+\textit{Bottom right: } Time in the post-powerstroke state.
+Both bottom plots have the theoretical values for pre-powerstroke and post-powerstoke times from the DeWitt \textit{et.
+al.} stepping trajectory.}
 \label{fig:behavior}
@@
   \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_displacement.pdf}
-  \caption{\textbf{Tension gating of model} \davidsays{Look up Yildiz figure}}
+  \caption{\textbf{Analysis of foot order on unbinding.} \textit{Top: } Heatmap of initial foot position vs length of ensuing step.
+Initial displacement defined as position of the stepping MTBD minus the position of the stationary MTBD, before the step takes place.
+Line of best fit calculated with equation shown in legend.
+\textit{Bottom: } Likelihood of a lagging-MTBD unbinding event vs the absolute value of initial displacement for model.
+The lagging-MTBD is the MTBD with more negative x position.
+Probability calculated as P(lagging step)$ = k_{ub}^{\text{lag}} / \left(k_{ub}^{\text{lag}} + k_{ub}^{\text{lead}}\right)$, where $k_{ub}^{\text{lag}}$ is the lagging-MTBD unbinding rate and $k_{ub}^{\text{lead}}$ the leading-MTBD unbinding rate.
+Lagging step probability also shown for DeWitt \textit{et.
+al.} cytoplasmic dynein \cite{yildizpaper}.}
   \label{fig:tensiongating}
@@
   \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
-  \caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
+  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
+\caption{\textbf{Impact of force on model velocity.} Model response to force in the $+\hat{x}$ direction applied to tail domain.
+Velocity calculated using displacement after 2 seconds of simulation at standard parameters.
+Behavior compared with a similar experiment on a cytoplasmic dynein construct using optical tweezers from Gennerich \textit{et.
+al.} \cite{responsetoload}.}
 \label{fig:}
@@
   \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
-\caption{Gennerich et al \cite{responsetoload}}
+  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
+  \caption{\textbf{Analysis of stepping independence.} Heatmap of MTBD displacement before and after a stepping cycle.
+Displacement defined as the unbinding MTBD's x coordinate minus the stationary MTBD's x coordinate, calculated before and after the step.
+Structure in the heat map suggests steps are not independent, but rather that correlation exists between starting position and step size.}
 \label{fig:}
@@
 \item Re-run velocity vs force simulation at a much lower rate to match the Gennerich velocity at pN=0
+\item \davidsays{Look up Yildiz figure} for initial displacement vs step length fig
+\item Calculate mutual information or pearson's R for initial/final displacement
 \end{enumerate}

### 2018-11-07 papers/johnWaczak-thesis/modelExplanation/model_explanation.tex
began write up for model physics

@@
 \large\textbf{Dynein Model Explanation and Theory} \hfill \textbf{John Waczak} \\
-\normalsize Physics Thesis \hfill  Date: \today \\
-Dr. David Roundy 
+\normalsize Dr. David Roundy \hfill  Date: \today \\
 \par\noindent\rule{\textwidth}{0.4pt} \\
 
+\section*{General Theory}
+\noindent Our model for dyenin consists of a system of domains treated as spheres connected by massless rigid rods.
+Because dynein works inside of cells, it's aqueous environment exaggerates the forces due to drag and adds an extra random force due to collisions with water molecules.
+This results in the following equation of motion known as the Langevin equation:
+\begin{equation}
+  m\ddot{\mathbf{x}} = \mathbf{F}_\text{interact} -\gamma\dot{\mathbf{x}}+\mathbf{R} 
+\end{equation}
+In our simulation, we use Brownian dynamics which assumes that the drag great enough so that acceleration may be neglected and, therefore, equation (1) reduces to
+\begin{equation}
+  \dot{\mathbf{x}} = \frac{1}{\gamma}\left(\mathbf{F}_\text{interact}+\mathbf{R}\right) 
+\end{equation}
+where $\mathbf{x}$ is the position of the Brownian particle and $\mathbf{R}$ is the random force due to water molecule collisions.
+$\gamma$ is the drag coefficient and depends on the radius of the Brownian particle.
+$\mathbf{F}_\text{interact}$ is the force of interaction between the particles.
+For our purposes, this interaction is composed of two separate forces.
+Our massless rods are rigid and therefore there is a tension force between adjacent domains responsible for maintaining the length constraint.
+We also apply a Hooke's law restorative torque with a magnitude given by
+\begin{equation}
+  \Gamma_i = c_i(\varphi_i - \varphi_{i, \text{eq}})
+\end{equation}
+where $c_i$ is a constant and $\varphi_{i,\text{eq}}$ the equilibrium angle for the $i^\text{th}$ domain.
+The forces that these torques exert move the protein towards a preferred configuration and helps generate directed motility.
+Given this information, we can now discuss how these forces are determined for each of the simulation's possible states.
+\pagebreak
+
+\section*{One bound Model}
+The following figure shows the model in the one bound configuration.\\
+\begin{figure}[!hbt]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{onebound}
+  \caption{The dynein model in the one bound state } 
+\end{figure}
+
+\noindent Here $\ell_S, \ell_T$ are fixed stalk and tail lengths.
+We have chosen the angles $\{\theta_i\}$ as they are the most convenient and lead to a description of the position of each domain that requires only one angle and an adjacent position, that is
+\begin{align}
+  x's \quad &\begin{cases}
+    x_0 = x_\text{bound} \\
+    x_1 = x_0 + \ell_S \cos\theta_0 \\
+    x_2 = x_1 + \ell_T \cos\theta_1 \\
+    x_3 = x_2 + \ell_T \cos(\pi-\theta_3) = x_2 - \ell_T\cos\theta_3 \\
+    x_4 = x_3 + \ell_S \cos(\pi-\theta_4) = x_3 - \ell_S\cos\theta_4
+  \end{cases} \\
+  y's \quad &\begin{cases}
+    y_0 = 0 \\
+    y_1 = y_0 + \ell_S\sin\theta_0 \\
+    y_2 = y_1 + \ell_T\sin\theta_1 \\
+    y_3 = y_2 - \ell_T\sin\theta_3 \\
+    y_4 = y_3 - \ell_S\sin\theta_4 
+  \end{cases}
+\end{align}
+
+ \noindent Because equation (2) relates the forces on each domain to its velocity we need the time derivative of the above equations. 
+ \begin{equation}
+   \dot{x}'s \quad \begin{cases}
+     \dot{x}_0 = 0 \\
+     \dot{x}_1 = \dot{x}_0-\ell_S\sin\theta_0 \dot{\theta}_0 \\
+     \dot{x}_2 = \dot{x}_1-\ell_T\sin\theta_1 \dot{\theta}_1 \\
+     \dot{x}_3 = \dot{x}_2+\ell_T\sin\theta_3 \dot{\theta}_3 \\
+     \dot{x}_4 = \dot{x}_3+\ell_S\sin\theta_4 \dot{\theta}_4
+   \end{cases} \\
+ \end{equation}
+ \begin{equation}
+   \dot{y}'s \quad \begin{cases}
+     \dot{y}_0 = 0 \\
+     \dot{y}_1 = \dot{y}_0 + \ell_S\cos\theta_0\dot{\theta}_0 \\
+     \dot{y}_2 = \dot{y}_1 + \ell_T\cos\theta_1\dot{\theta}_1 \\
+     \dot{y}_3 = \dot{y}_2 - \ell_T\cos\theta_3\dot{\theta}_3 \\
+     \dot{y}_4 = \dot{y}_3 - \ell_S\cos\theta_4\dot{\theta}_4
+   \end{cases} 
+ \end{equation}
+
 \end{document}

### 2018-11-07 papers/paper/paper.tex

@@
 
+Motion equations were derived for the pre-powerstroke and post-powerstroke states of the model.
+The model was simulated by starting in the equilibrium post-powerstroke position and using Euler's method to time-evolve the model, using a timestep of 1e-10 \textit{s}.
+The model was transitioned between post-powerstroke and pre-powerstroke states using unbinding and binding rates.
+Model parameters were estimated from various experimental results.
+Spring constants were chosen to fit the model stepping size to experiment, as outlined in Figure S\ref{fig:supp-model-fit}.
+Model rate constants were fit to theoretical calculations outlined in the Methods section.
+The tension-gating parameter c was fit as shown in Figure \ref{fig:tensiongating}.
+32 5-second simulations were run, each initialized with a different random seed.
+Each simulation was forward directed, took both forward and backward steps, and displayed stepping dynamics similar to that seen in experiment.\\
+
+  As seen in Figure \ref{fig:trajectory}, the model is highly variant in trajectory, but biased to moving in the $+\hat{x}$ direction, corresponding to the microtubule minus-end.
+When unbound the free MTBD diffuses both parallel and perpendicular to the microtubule, reaching up to 50 \textit{nm} above the track.
+Though the unbound MTBD freely approaches the microtubule, it does not always bind, as seen in the $7-9 \mu s$ part of the simulation.
+The cartoons in Figure \ref{fig:trajectory} reveal the model taking on many conformations, revealing the model's structural flexibility.
+The model seems to prefer alternating hand-over-hand stepping, but occasionally takes steps in a semi-inchworm fashion, as seen at time $5.3 \mu s$ in Figure \ref{fig:trajectory}.\\
+
 \begin{figure}[tbhp]
@@
 
-\textbf{Processive, forward-directed motility}\\
-The model was time-evolved using Euler's method.
-When simulated, the model produces processive, forward-directed motion.
-Figure \ref{fig:trajectory} shows a short time window of the model's dynamics.
-The model is capable of taking both forward and backwards steps, but is biased in the forward direction.\\
-
-\textbf{Stepping dynamics}
-The stepping dynamics of the model reproduce experimental results.
-The model is capable of producing a wide variety of step lengths, from 48nm forward to 40nm backwards, as in Figure \ref{fig:behavior}.a.
-The onebound and bothbound times correspond well to the theoretical values, as in \ref{fig:behavior}.b and c.
-The tension-gating mechanism is capable of producing a lagging-head favor, as shown in \ref{fig:behavior}.d.
-
-%% -Briefly how we simulated the model
-%% -Model is forwards-directed and processive (trajectory plot)
-%% -Tuning the parameters to Yildiz data (kb/kub from theoretical OB/BB time and step length histograms for cm/cb/ct and leading/lagging fractions for c)
-%% -Does the tuned model walk similarly to Yildiz dynein? (also the lagging vs step length)
+The model was then compared to TIRF studies of dynein stepping in DeWitt \textit{et.
+al.} \cite{yildizpaper}.
+Figure \ref{fig:behavior}.a shows 8 representative model trajectories compared to experimental dynein.
+The eight simulations track experimental very well over 5 seconds, and average to the same position.
+The eight simulations end up distributed over a 200 \textit{nm} area, showing the variation in the model stepping extends to a variation in velocity in the long term.
+The step size distribution for the 32 simulations are shown in Figure \ref{fig:behavior}.b).
+The model is capable of taking both positive and negative steps, with steps extending from -40 \textit{nm} to 50 \textit{nm}, matching experimental dynein.
+The most probable step is 12 \textit{nm}, with an average step size of 6.2 \textit{nm}.
+This matches the peak experimental step size window of 7-13 \textit{nm}.
+The major deviation in model and experiment is the density of model steps around 0nm, which is possibly caused by an inability of the step detection algorithm to detect small steps.
+The pre-powerstroke and post-powerstroke state occupation times are shown in Figure \ref{fig:behavior}.c and d.).
+The model prefers long pre-powerstroke times, but is capable of taking very fast steps.
+The post-powerstroke time has a heavy-tailed distribution.
+Experimental technique does not resolve time spent in pre- and post-powerstroke, but we outline a technique for calculating these values for experimental trajectories in Methods.
+These theoretical values correspond well to model behavior.\\
 
@@
 
+Dependence of the unbinding MTBD on its relation to its partner MTBD is studied in Figure \ref{fig:tensiongating}.
+Figure \ref{fig:tensiongating}.a shows a heat map of initial displacement, defined as how much the stepping MTBD is ahead of the stationary MTBD, vs the step size.
+A line of best fit is constructed with intercept $b=5.7$ and slope $m=-1$.
+This indicates a negative trend where large positive displacements are likely to cause backwards steps, and negative displacements are likely to cause forward steps.
+This is consistent with the idea of tension gating, where tension between the two motor heads drives unbinding to relieve tension.
+The negative trend is reproduced in DeWitt \textit{et.
+al}, which shows a slope of $m=-0.4$.
+Figure \ref{fig:tensiongating}.b shows the unbinding probability of the lagging head with distance to the leading head.
+As the distance becomes greater the lagging head is more and more likely to unbind, again consistent with tension gating.
+This trend also very closely tracks DeWitt \textit{et.
+al}.\\
+
 \begin{figure}[tbhp]
@@
 
+The effect of force on the model was then assessed by applying an artificial force on the tail domain of the model in the $+\hat{x}$ direction.
+The results of this study are shown in Figure \ref{fig:force}.
+An expected decrease in velocity is seen as stronger and stronger negative forces are applied to the model, pulling it against its natural walking direction.
+Unlike experiment, a reversal in velocity is not seen for this trial, indicating that perhaps the dynamics of force-mediated velocity reversal are more complicated than what this simplified model can handle.
+The results are consistent with an experiment done by Grotjahn \textit{et.
+al} where force is applied via optical tweezers to dynein constructs and their velocity is assayed.
+It will need to be studied why odd behavior is seen in the mdoel for positive forces.\\
+
 \begin{figure}[tbhp]
@@
 al.} \cite{responsetoload}.}
-\label{fig:}
+\label{fig:force}
 \end{figure}
+
+The independence of dynein steps is then studied in Figure \ref{fig:independence}.
+Whether dynein works like a Markovian process, where each step is a history-free, is an interesting question.
+Figure \ref{fig:independence} demonstrates the impact of initial displacement of MTBDs to their final displacement, before and after a step is taken.
+The asymmetry in the plot is indicative that the initial configuration of the motor does have significant impact on the later state.
+The Brownian forces act to mitigate momentum and prevent information transfer through motion.
+However, the binding orientation of the dynein model to the microtubule is stable through time, and can influence the binding orientation of dynein to the microtubule at a later time.
+There seems to be a roughly tension-gated process occurring where negative displacements initially lead to positive displacements later.\\
 
@@
 Structure in the heat map suggests steps are not independent, but rather that correlation exists between starting position and step size.}
-\label{fig:}
+\label{fig:independence}
 \end{figure}

### 2018-11-13 papers/paper/paper.tex
Add notes to paper.bib on new papers

@@
 Such a study would determine if the powerstroke mechanism is sufficient to explain dynein's walk, or if further explanation is necessary.
-Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
+Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
 Such a study would be able to find the minimum criteria for generating dynein's motion.\\
@@
 Further, we show that the model displays more complex behavior, such as tension gating and force-mediated bidirectionality.\\
+
+%% just say that we included tension gating
 
@@
   To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used.
-First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD.
+First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD, that is, that there is no inter-head coordination.
 Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{\bar{t}_{ob}}{\bar{t}_{step}} * \frac{1}{\bar{t}_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $\bar{t}_{ob}$ and $\bar{t}_{bb}$ are the expected durations for a onebound and bothbound state, and $\bar{t}_{step} = \bar{t}_{ob} + \bar{t}_{bb}$ is the expected step duration.
@@
 \begin{enumerate}
-\item Fix stepping analysis python module to categorize zero-length
-  steps separately from other steps, particularly in terms of stepping
-  times.  Alternately, change C++ to make it possible to identify
-  which foot lifted if it didn't move.
+\item Fix stepping analysis python module to categorize zero-length steps separately from other steps, particularly in terms of stepping imes.
+Alternately, change C++ to make it possible to identify which foot lifted if it didn't move.
 \item When we have all data, write discussion
@@
 \item Calculate mutual information or pearson's R for initial/final displacement
+\item Add spring symbols to angles to make it more obvious where the springs are
+\item Add more stuff to supplemental methods, like how our drag forces and stuff are calculated and how we calculate unbinding rate
+\item Make clear that we are comparing to artificially-dimerized molecules in our experiment
+\item Run simulations with/without interhead coordination, use a passing/no-passing chart with both models and experiment to demonstrate that tension-gating helps
 \end{enumerate}
@@
 \end{document}
+
+-Dynein's two feet take different steps according to yildiz/qiu
+-Carter 2008 says that dynein's MTBD decides directionaolity, whereas Redwine 2012 thinks its linker motion (clarify)
+-Imai 2015 has lots to say criticizing the step length studies of qiu/yildiz and have something to say about domain movement MT search
+-Someone else referred to the Cianfrocco model, so maybe it's a good one to refer to (well accepted)
+-The winch model is also referred to as the

### 2018-11-14 papers/paper/paper.tex
Add simulation printing mode to generate a new data file with tx, ty, motor and binding angle info in bothbound. This is for a new figure.

@@
 -Someone else referred to the Cianfrocco model, so maybe it's a good one to refer to (well accepted)
--The winch model is also referred to as the
+-It's important that our model doesn't have the powerstroke mechanism in, only observations from experiment

### 2018-11-14 data/paper_params.py

@@ -7,6 +7,10 @@ trajectory_k_b  = 9.5e9 # s^-1
 trajectory_k_ub = 1e20 # s^-1
 trajectory_seed = 14 # 1 and 10 and 14 and 17 20 are okay
 
+stroke_angle_k_b  = 9.5e9 # s^-1
+stroke_angle_k_ub = 1e5   # s^-1
+stroke_angle_seed = 1
+
 cexp = -0.35
 
 cb = 0.08 # kbT

### 2018-11-14 scripts/generate-stepping-data.py

@@ -35,6 +35,8 @@ parser.add_argument("-v", "--movie", help="Movie flag", action="store_true")
 parser.add_argument("-n", "--renametrajectory", help="Rename outputs to paper trajectory files", action="store_true")
 parser.add_argument("-o", "--renamepaper", help="Rename outputs to paper exponential histogram files", action="store_true")
 parser.add_argument("-R", "--renameforce", help="Rename outputs to force files", action="store_true")
+parser.add_argument("-M", "--renameangles", help="Rename outputs to angles files", action="store_true")
+parser.add_argument("-T", "--anglemode", help="Rename outputs to angles files", action="store_true", default=False)
 args = parser.parse_args()
 
 if args.movie:
@@ -44,14 +46,14 @@ if args.movie:
 
 basename = run.sim(**{"k_b": args.kb,
                       "k_ub": args.kub,
-                      "cb": args.cb, # 0.1?
-                      "cm": args.cm, # 0.4?
-                      "ct": args.ct, # 0.2?
+                      "cb": args.cb,
+                      "cm": args.cm,
+                      "ct": args.ct,
                       "ls": args.ls,
                       "lt": args.lt,
-                      "eqb": args.eqb,  # from redwine 2012 supplemental
-                      "eqmpre": args.eqmpre, # from burgess 2002, 360-160
-                      "eqmpost": args.eqmpost, # from burgess 2002, 360-136
+                      "eqb": args.eqb,
+                      "eqmpre": args.eqmpre,
+                      "eqmpost": args.eqmpost,
                       "eqt": args.eqt,
                       "rt": args.rt,
                       "rm": args.rm,
@@ -59,7 +61,8 @@ basename = run.sim(**{"k_b": args.kb,
                       "force": args.force,
                       "exp-unbinding-constant": args.unbindingconst,
                       "dt": 1e-10, "label": args.label, "seed": args.seed, "runtime": args.runtime,
-                      "framerate": args.framerate, "crash-movie": False, "nomovie": not args.movie})
+                      "framerate": args.framerate, "crash-movie": False, "nomovie": not args.movie,
+                      "angle-logging-mode": args.anglemode})
 
 if args.renamepaper:
     os.system("mv data/stepping_data_%s.txt data/paper_main_stepping_data-%s.txt" % (basename, args.seed))
[…]

### 2018-11-14 src/default_parameters.h

@@ -60,6 +60,8 @@ TRANSITION_MODES binding_mode = EXPONENTIAL_UNBINDING;
 bool am_only_writing_on_crash = false;
 double stepping_movie_framerate = 1e-10;
 
+bool angle_logging_mode = false;
+
 double tail_force = 0;
 
 /* onebound_equilibrium_angles onebound_post_powerstroke_internal_angles = { */

### 2018-11-21 papers/paper/paper.tex

@@
 
-%% \begin{figure}[tbhp]
-%%   \centering
-%% \includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
-%% \includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
-%% \includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
-%% \includegraphics[width=0.5\columnwidth]{figures/schematic-full}
-%%   \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
-%%       images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
-%%     dynein heavy chains superimposed with model motor angles, both
-%%     from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
-%%     MT with model binding angle superimposed, from
-%%     \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
-%%     bound to an MT with model superimposed, from
-%%     \textbf{nativestructure}.}
-%% \label{fig:modelangles}
-%% \end{figure}
+\begin{figure}[tbhp]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{figures/model-cartoon-simple}%
+  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_angles_bd.pdf}\\
+  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_taily_positions}%
+  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\\
+  \includegraphics[width=0.5\columnwidth]{../../plots/onebound_stroke_tailx_positions}%
+  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_angles_md}\\
+  \caption{\textbf{Model behavior during power stroke.}}
+\label{fig:stroke}
+\end{figure}
 

### 2018-11-23 papers/paper/paper.tex
Add winch vs ps cartoon to angle figure, along with caption.

@@
 
+\usepackage{caption}
 \usepackage{subcaption}
@@
 \setboolean{displaywatermark}{false}
+
+\captionsetup[subfigure]{singlelinecheck=off,justification=raggedright, margin=0pt, parskip=0, skip=0pt}
 
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{figures/model-cartoon-simple}%
-  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_angles_bd.pdf}\\
-  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_taily_positions}%
-  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\\
-  \includegraphics[width=0.5\columnwidth]{../../plots/onebound_stroke_tailx_positions}%
-  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_angles_md}\\
-  \caption{\textbf{Model behavior during power stroke.}}
+  \begin{subfigure}[]{0.8\columnwidth}\caption{}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd.pdf}\end{subfigure}%
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}
+  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A.
+left: } Schematic of the winch mechanism.
+On free MTBD binding, linker swing in the just-bound head pulls the tail and cargo in the direction of the just-bound MTBD.
+\textit{A.
+right: } Schematic of the powerstroke mechanism.
+On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT.
+\textit{b.) } Just-bound MTBD angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line).
+\textit{c.) } Just-bound head angle, along with prestroke equilibrium (red dotted line) and poststroke equilibrium (blue dotted line).
+\textit{d.) } Change in tail domain x coordinate since MTBD binding.
+\textit{e.) } Value of tail domain y coordinate.
+All values sampled every $10 ns$ and plotted as mean $\pm$ SD.}
 \label{fig:stroke}

### 2018-11-24 papers/paper/paper.tex
minor commit

@@
   \centering
-  \begin{subfigure}[]{0.8\columnwidth}\caption{}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
+  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
   \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd.pdf}\end{subfigure}%

### 2018-11-26 papers/paper/paper.tex
Make make make on bingley
Add rough draft of discussion section.

@@
 
-\usepackage{caption}
 \usepackage{subcaption}
@@
 
-\captionsetup[subfigure]{singlelinecheck=off,justification=raggedright, margin=0pt, parskip=0, skip=0pt}
+\captionsetup[subfigure]{singlelinecheck=off,justification=raggedright, margin=0pt, parskip=0pt, skip=0pt}
 
@@
 
-%% \begin{figure*}[tbhp]
-%%     \includegraphics[width=0.5\linewidth]{../../plots/paper_foot_order_histogram.pdf}
-%% \caption{The left plot is the $C=0$ case where the unbinding rate is
-%%   independent of angle.  Here ``alternating'' means that the binding
-%%   domain which did not move last time moved this time.  Passing means
-%%   that the moving foot was behind, and ended up in front.}
-%% \label{fig:steppingorder}
-%% \end{figure*}
-
-\section{Discussion}
-
-\begin{enumerate}
-\item \cite{lippert} is a 2017 PNAS paper claiming the powerstroke model is wrong since angular displacement of the dynein ring is weak (+- 7 degrees) and weakly correlated with stepping.
-However, their camera records at 50ms resolution, which is 100x slower than our average onebound time.
-Thus their whole experiment is somewhat flawed.
-This is relevant since the oneboudn time duration may not be well known, and our theoretical results may be relevant.
-\item No need for being guided to Mt binding sites, the motor naturally can take 16nm steps through a powerstroke
-\item Is tension gating necessary for our model? Could run simulations without it to see how the model changes
-\item Dynein's adjacent step step length correlation is low; thus the motor is a memory-less process which could be simulated by a Markov model.
-Also look at ob and bb time covariance and displacement covariance
-\end{enumerate}
-
-%% \begin{figure}[tbhp]
-%%   \centering
-%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
-%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
-%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}
-
-%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
-%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
-%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
-%%    \caption{\textbf{Model schematic superimposed on cryo-EM images of
-%%        native dynein.} Native cryo-EM images of the full dimerized
-%%      dynein complex composed of light, intermediate and heavy chains,
-%%      from \cite{nativestructure}. Model schematics are superimposed
-%%      for illustrative purpose; shown angles to not represent expected
-%%      \textit{in vivo} equilibria. Schematics are shown docked to a
-%%      microtubule for illustrative purposes.}
-%%    \label{fig:modelparams}
-%% \end{figure}
-
 \begin{figure}[tbhp]
@@
 \end{figure}
+
+%% \begin{figure*}[tbhp]
+%%     \includegraphics[width=0.5\linewidth]{../../plots/paper_foot_order_histogram.pdf}
+%% \caption{The left plot is the $C=0$ case where the unbinding rate is
+%%   independent of angle.  Here ``alternating'' means that the binding
+%%   domain which did not move last time moved this time.  Passing means
+%%   that the moving foot was behind, and ended up in front.}
+%% \label{fig:steppingorder}
+%% \end{figure*}
+
+\section{Discussion}
+In this study we sought to study dynein's dynamics using a simple model.
+We used imaging data to construct a structurally realistic goemetric model for the motor, then used Brownian dynamics to explore how such a model would behave in a cell.
+We used experimental data on dynein's step length distribution and unbinding likelihood to fit the model's spring and tension-gating constants.
+We used arguments about dynein's run length and velocity to predict the average time the motor spent in the pre-powerstroke and post-powerstroke states, and fit the model's binding and unbinding rates to these predictions.
+We tested the dynamics of this fit model, and found that the model displayed a high level of agreement with the data used to fit; the simulation's velocity and stepping histogram in Figure \ref{fig:behavior} match experiment quite well.
+In addition the model can predict new data it was not fit with, such as force output in Figure \ref{fig:force} and effects of foot displacement on step length in Figure \ref{fig:tensiongating}.
+We then examined the mechanism our model used to walk by studying domain positions over many steps.
+We found that the majority of forward displacement occured immediately after a free binding domain bound to the microtubule, when the just-bound stalk swung forward, pulling the attached motor and tail domains toward the minus-end of the microtubule.\\
+
+One of the main advantages of our study is that it provides high spatial and temporal information about the model's behavior, which is currently unavailable for real dynein.
+This allows us to study mechanistic questions about how dynein walks.
+Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps} (CITE MORE).
+As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
+This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY CITATIONS HERE}.
+Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.\\
+
+This model contrasts with another theory on the dynein step called the winch mechanism \cite{uenoem, sarlahmodel}.
+According to this model, on MTBD rebinding, linker swing puts the just-bound head in a high energy state, just like in the powerstroke mdoel.
+However, to relieve this tension the motor instead ``winches'' its tail domain downwards in the direction of the stalk, resulting in a tail which is closer to the MT and further forward.
+To our knowledge, no previous simulation has tested the physical feasibility of either the winch or powerstroke models.
+Although our model is a minimal depiction which does not take into account the acute dynamics of the whole motor, its ability to reproduce the dynamics of the real dynein suggests that it may have some bearing on how the real dynein walks.
+In particular, this model spontaneously exhibits the powerstroke mechanism, suggesting that the powerstroke mechanism is both feasible for the dynein complex to generate and sufficient to explain much experimental data.
+Although this does not rule out the winch mechanism as an explanation, we believe that the lack of any winch-like behavior in our simulation is meaningful.
+Indeed during displacement our model's tail domain actually moves away from the microtubule, the opposite of the winch's prediction.
+Further theoretical studies demonstrating the feasibility and sufficiency of the winch mechanism are needed.\\
+
+Recent experimental studies have had strong implications for the winch vs powerstroke mechanisms.
+A key question is whether the just-bound stalk experiences angular displacement as the motor moves forward, as this is necessary for the powerstroke and not the winch.
+This angular displacement was not found by Lippert \textit{et.
+al.} \cite{lippert}, who used polTIRF to study the angle dynein's stalk made with the MT in freely-walking dynein.
+Another study showed that there is no difference in stalk angle between motors locked in the pre- and post-powerstroke state using special nucleotides and cryo-electron microscopy \cite{uenoem}.
+One key finding of our study which reconciles the powerstroke mechanism with these experimental findings is the timescale on which it occurs.
+We find that the average duration of the angular displacement of the just-bound stalk is XYZ $\mu s$ (see Figure \ref{fig:stroke}).
+This time is much faster than the 50 $ms$ time resolution of the polTIRF experiment of Lippert \textit{et.
+al.} \cite{lippert}, which may explain why the angular displacement was not detected.
+Furthermore we note that in our model the stalk angle deviates from equilibrium as the motor and tail move forwards; only much later does the stalk return to equilibrium.
+This suggests that the stsalk angular displacement is a non-equilibrium phenomena which could not be detected through cryo-EM, which resolves equilibrium structures.
+This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem}.
+We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast XYZ $\mu s$ phenomena.\\
+
+Our study demonstrates other interesting findings.
+Similar to past simulation work \cite{sarlahmodel}, we demonstrate that our model is capable of achieving minus-end directed motility merely through the way it binds to the microtubule.
+Also interestingly, we demonstrate that our model is capable of taking 12$nm$ (CHANGE ON RERUN) steps in the absence of explicit microtubule binding sites.
+Merely through the size of its stalk and tail and through the magnitude of angular displacement induced by linker swing, our model is capable of taking the right step size.
+It is interesting that in our model a single step is slightly shorter than the experimental 16nm step \cite{find citation}.
+This suggests that perhaps the motor requires a diffusive search along the microtubule to find the next binding site.
+Alternatively, as has been recently demonstrated, perhaps an electrostatic mechanism is used to guide the MTBD to the next binding site using long-range interactions \cite{longrangemt}.\\
+
+Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel}.
+This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency.
+Our minimal assumptions simplify the model and rule out overfitting.
+However, our model neglects many features which may be important for real dynein's walk.
+For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find that other possibly burgess paper}.
+Other features like microtubule electrostatic interactions \cite{longrangemt}, X, Y and Z are also neglected.
+Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\
+
+In conclusion, our study demonstrates that the powerstroke mechanism is sufficient to explain dynein's velocity, step length histogram, displacement-vs-step length relationship, and force output.
+We demonstrate that the powerstroke arises naturally from minimal structural information about the protein, suggesting it is likely possible for real dynein to exhibit a powerstroke.
+Further, we explain why past studies may have failed to detect this powerstroke.
+We hope that this evidence is sufficient to maintain the powerstroke mechanism as a viable hypothesis for how dynein walks.
+We further hope that experiments with higher spatial and temporal resolution can be conducted in the near future to shed more light on the precise nature of dynein's stepping mechanism.\\
 

### 2018-11-26 papers/paper/paper.tex
minor change to paper to make it build

@@
 As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
-This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY CITATIONS HERE}.
+This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY-CITATIONS-HERE}.
 Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.\\
@@
 Merely through the size of its stalk and tail and through the magnitude of angular displacement induced by linker swing, our model is capable of taking the right step size.
-It is interesting that in our model a single step is slightly shorter than the experimental 16nm step \cite{find citation}.
+It is interesting that in our model a single step is slightly shorter than the experimental 16nm step \cite{find-citation}.
 This suggests that perhaps the motor requires a diffusive search along the microtubule to find the next binding site.
@@
 However, our model neglects many features which may be important for real dynein's walk.
-For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find that other possibly burgess paper}.
+For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find-that-other-possibly-burgess-paper}.
 Other features like microtubule electrostatic interactions \cite{longrangemt}, X, Y and Z are also neglected.

### 2018-11-27 papers/paper/paper.tex

@@
   \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd.pdf}\end{subfigure}%
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
   \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
   \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
+  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
   \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A.
@@
 On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT.
-\textit{b.) } Just-bound MTBD angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line).
+\textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line).
 \textit{c.) } Just-bound head angle, along with prestroke equilibrium (red dotted line) and poststroke equilibrium (blue dotted line).
@@
 \textit{e.) } Value of tail domain y coordinate.
-All values sampled every $10 ns$ and plotted as mean $\pm$ SD.}
+All values sampled every $10 ns$.
+\textit{f.) } Just-bound MTBD stalk angle over the entirety of the post-powerstroke state, sampled every 1 $\mu s$.
+All values plotted as mean $\pm$ SD.}
 \label{fig:stroke}

### 2018-11-27 papers/paper/paper.tex
Minor tweak to paper

@@
 This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY-CITATIONS-HERE}.
+The stalk angle remains displaced from equilibrium until the next unbinding.
 Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.\\
@@
 Another study showed that there is no difference in stalk angle between motors locked in the pre- and post-powerstroke state using special nucleotides and cryo-electron microscopy \cite{uenoem}.
-One key finding of our study which reconciles the powerstroke mechanism with these experimental findings is the timescale on which it occurs.
-We find that the average duration of the angular displacement of the just-bound stalk is XYZ $\mu s$ (see Figure \ref{fig:stroke}).
+One key finding of our study which reconciles the powerstroke mechanism with these experimental findings is the timescale on which the predicted stalk angular displacement occurs.
+We find that the average duration of the angular displacement of the just-bound stalk is on the order of 1 $ms s$ from the prestroke diffusive search, as the actual angular displacement during the powerstroke is negligibly small (see Figure \ref{fig:stroke}).
 This time is much faster than the 50 $ms$ time resolution of the polTIRF experiment of Lippert \textit{et.
-al.} \cite{lippert}, which may explain why the angular displacement was not detected.
+al.} \cite{lippert}, which may explain why an angular displacement was not detected.
 Furthermore we note that in our model the stalk angle deviates from equilibrium as the motor and tail move forwards; only much later does the stalk return to equilibrium.
@@
 This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem}.
-We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast XYZ $\mu s$ phenomena.\\
+We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast millisecond phenomena.\\
 

### 2018-12-02 scripts/color_hist2.py
Add line of best fit from Yildiz data to our initial displacement vs step length plot.

@@ -114,7 +114,7 @@ def getCounts(X, Y, xIsTimeValue, yIsTimeValue):
 
 # x_name, x_units, y_name, y_units
 def plotCounts(x, y, graph_label, x_label, y_label,
-               xIsTimeValue, yIsTimeValue,filename=None, drawline=False):
+               xIsTimeValue, yIsTimeValue,filename=None, drawline=False, drawyildizline=False):
 
     x_bins, y_bins, counts = getCounts(x, y, xIsTimeValue, yIsTimeValue)
     if VERBOSE: print("graphing")
@@ -136,10 +136,17 @@ def plotCounts(x, y, graph_label, x_label, y_label,
     if drawline:
         A = np.vstack([x, np.ones(len(x))]).T
         m, c = np.linalg.lstsq(A, y)[0]
-        eq = "y = {:.2} + {:.2}x".format(c, m)
+        eq = "Model: y = {:.2} + {:.2}x".format(c, m)
         if m < 0:
-            eq = "y = {:.2} - {:.2}x".format(c, -m)
-        plt.plot([x_bins[0], x_bins[-1]], [x_bins[0]*m, x_bins[-1]*m]+c, label=eq, linestyle=":", color='w')
+            eq = "Model: y = {:.2} - {:.2}x".format(c, -m)
+        plt.plot([x_bins[0], x_bins[-1]], [x_bins[0]*m, x_bins[-1]*m]+c, label=eq, linestyle=":", color='C1')
+        plt.legend()
+
+    if drawyildizline:
+        m = -0.4 # yildiz 2012
+        c = 9.05 # yildiz 2012
+        eq = "Experiment: y = {:.2} - {:.2}x".format(c, -m)
+        plt.plot(np.array([x_bins[0], x_bins[-1]]), np.array([x_bins[0]*m, x_bins[-1]*m])+c, label=eq, linestyle=":", color='C0')
         plt.legend()
 
     if filename is None:
@@ -202,6 +209,7 @@ plotCounts(initial_displacements,
            xIsTimeValue=False,
            yIsTimeValue=False,
            drawline=True,
+           drawyildizline=True,
            filename='plots/initial-displacement-vs-step-length{}.pdf'.format(seed_label))
 
 if SHOW:

### 2018-12-12 papers/paper/paper.tex
Add line of best fit from Yildiz data to our initial displacement vs step length plot.

@@
 Initial displacement defined as position of the stepping MTBD minus the position of the stationary MTBD, before the step takes place.
-Line of best fit calculated with equation shown in legend.
+Line of best fit calculated with equation shown in legend in orange.
+Line of best fit from the same plot in DeWitt \textit{et al} \cite{yildizpaper} on cytoplasmic dynein shown in blue.
 \textit{Bottom: } Likelihood of a lagging-MTBD unbinding event vs the absolute value of initial displacement for model.
@@
 Lagging step probability also shown for DeWitt \textit{et.
-al.} cytoplasmic dynein \cite{yildizpaper}.}
+al.} cytoplasmic dynein.}
   \label{fig:tensiongating}
@@
 This allows us to study mechanistic questions about how dynein walks.
-Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps} (CITE MORE).
+Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps, burgessknight} (CITE MORE).
 As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
@@
 
-This model contrasts with another theory on the dynein step called the winch mechanism \cite{uenoem, sarlahmodel}.
+This model contrasts with another theory on the dynein step called the winch mechanism \cite{uenoem, sarlahmodel, nicastro}.
 According to this model, on MTBD rebinding, linker swing puts the just-bound head in a high energy state, just like in the powerstroke mdoel.
@@
 This suggests that the stsalk angular displacement is a non-equilibrium phenomena which could not be detected through cryo-EM, which resolves equilibrium structures.
-This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem}.
+This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem, nicastro}.
 We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast millisecond phenomena.\\

### 2018-12-27 papers/paper/paper.tex
Add 2 citations.

@@
 Such a study would determine if the powerstroke mechanism is sufficient to explain dynein's walk, or if further explanation is necessary.
-Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
+Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary, imaiburgess}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
 Such a study would be able to find the minimum criteria for generating dynein's motion.\\
@@
   \section*{Fitting $k_b$ and $k_{ub}$}
-  To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$, a simple theoretical model for stepping was used.
+  To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$ a simple theoretical model for stepping was used, similar to one previously published \cite{myosindutyratio}.
 First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD, that is, that there is no inter-head coordination.
@@
 The tension-gating parameter c was fit as shown in Figure \ref{fig:tensiongating}.
-32 5-second simulations were run, each initialized with a different random seed.
+Thirty-two 5-second simulations were run, each initialized with a different random seed.
 Each simulation was forward directed, took both forward and backward steps, and displayed stepping dynamics similar to that seen in experiment.\\
@@
 This matches the peak experimental step size window of 7-13 \textit{nm}.
-The major deviation in model and experiment is the density of model steps around 0nm, which is possibly caused by an inability of the step detection algorithm to detect small steps.
 The pre-powerstroke and post-powerstroke state occupation times are shown in Figure \ref{fig:behavior}.c and d.).
@@
 Experimental technique does not resolve time spent in pre- and post-powerstroke, but we outline a technique for calculating these values for experimental trajectories in Methods.
-These theoretical values correspond well to model behavior.\\
+These theoretical values correspond well to model behavior, and square with experimental findings that dynein is almost always in the post-stroke state \cite{imaiburgess}.\\
 
@@
 In addition the model can predict new data it was not fit with, such as force output in Figure \ref{fig:force} and effects of foot displacement on step length in Figure \ref{fig:tensiongating}.
+The major deviation in model and experiment is the density of model steps around 0nm, which is possibly caused by an inability of the step detection algorithm to detect small steps in experimental dynein.
 We then examined the mechanism our model used to walk by studying domain positions over many steps.
@@
 Furthermore we note that in our model the stalk angle deviates from equilibrium as the motor and tail move forwards; only much later does the stalk return to equilibrium.
-This suggests that the stsalk angular displacement is a non-equilibrium phenomena which could not be detected through cryo-EM, which resolves equilibrium structures.
+This suggests that the stalk angular displacement is a non-equilibrium phenomena which could not be detected through cryo-EM, which resolves equilibrium structures.
 This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem, nicastro}.

### 2018-12-29 papers/paper/paper.tex
Add work on paper justifying our 2-state model with kinetic data

@@
 The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse.
-Each state feels equilibrium forces meant to mimic the structural changes which occur through dynein's chemical cycle.
-This transitioning is meant to capture the powerstroke of dynein, between the apo ``post-powerstroke'' state and the ADP-Pi-bound ``pre-powerstroke'' state.
+The bothbound state is meant to represent the post-powerstroke pre-ADP release state, and the onebound state represents the post pre-stroke pre-MT binding state, during which ATP is hydrolyzed and phosphate is rejected.
+These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the recovery stroke is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-recovery conformation should dominate when unbound from MT.
+We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, neglecting other possible cycles.
+Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the recovery stroke and powerstroke \cite{burgess-paper, burgessknight}.
+In particular, the equilibrium angles controlling a motor's tail-motor-MTBD angle change to kick the stalk-MTBD further from the tail.\\
 
@@
 This allows us to study mechanistic questions about how dynein walks.
-Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps, burgessknight} (CITE MORE).
+Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps, burgessknight, robertspowerstroke, burgess-paper} (CITE MORE).
 As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
@@
 
-This model contrasts with another theory on the dynein step called the winch mechanism \cite{uenoem, sarlahmodel, nicastro}.
+This model contrasts with another theory on the dynein step called the winch mechanism \cite{uenoem, sarlahmodel, nicastro} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
+al} \cite{lippert}).
 According to this model, on MTBD rebinding, linker swing puts the just-bound head in a high energy state, just like in the powerstroke mdoel.
@@
 One key finding of our study which reconciles the powerstroke mechanism with these experimental findings is the timescale on which the predicted stalk angular displacement occurs.
-We find that the average duration of the angular displacement of the just-bound stalk is on the order of 1 $ms s$ from the prestroke diffusive search, as the actual angular displacement during the powerstroke is negligibly small (see Figure \ref{fig:stroke}).
-This time is much faster than the 50 $ms$ time resolution of the polTIRF experiment of Lippert \textit{et.
-al.} \cite{lippert}, which may explain why an angular displacement was not detected.
+We find that the average duration of the angular displacement period of the just-bound stalk is on the order of 1 $ms s$ from the prestroke diffusive search, as the actual angular displacement during the powerstroke is negligibly small (see Figure \ref{fig:stroke}).
+According to the powerstroke model the stalk should be displaced after the recovery stroke, during ATP hydrolysis and Pi release, after binding the MT, and during the powerstroke, in the most likely progression through the mechanochemical cycle \cite{tsygankovscheme}.
+Our calculations for the time only one head is bound predict this period to last roughly 1 $ms$.
+Thus, assuming the MT-bound prestroke period is short enough \cite{mogamirate}, it is possible the entire displacement period should be on the order of milliseconds.
+This time could be faster than the 50 $ms$ time resolution of the polTIRF experiment of Lippert \textit{et.
+al.}, which may explain why an angular displacement was not detected.
 Furthermore we note that in our model the stalk angle deviates from equilibrium as the motor and tail move forwards; only much later does the stalk return to equilibrium.
@@
 For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find-that-other-possibly-burgess-paper}.
-Other features like microtubule electrostatic interactions \cite{longrangemt}, X, Y and Z are also neglected.
+Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, Y and Z are also neglected.
 Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\

### 2018-12-29 papers/paper/paper.tex
Add two new papers

@@
 It is also known that ATP binding can induce structural changes within the motor which increase unbinding rate \cite{leschziner, carter-paper}, and similarly that microtubule rebinding can influence nucleotide unbinding rate \cite{mt-atp-coupling}.
-Taken together this evidence is synthesized into a powerstroke model \cite{cianfroccoreview, imamulamodel}.
+Taken together this evidence is synthesized into a powerstroke model \cite{cianfroccoreview, imamulamodel, tsygankovscheme}.
 In the powerstroke model, dynein binds ATP, causing structural changes which eventually lead to microtubule unbinding at its MTBD.
@@
 These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the recovery stroke is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-recovery conformation should dominate when unbound from MT.
-We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, neglecting other possible cycles.
+We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-powerstroke state while the other head goers through the entire mechanochemical cycle, neglecting other possible cycles.
 Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the recovery stroke and powerstroke \cite{burgess-paper, burgessknight}.
@@
 We used arguments about dynein's run length and velocity to predict the average time the motor spent in the pre-powerstroke and post-powerstroke states, and fit the model's binding and unbinding rates to these predictions.
+From fitting we found that relatively loose tail and MTBD spring constants and a stiff tail produced the best stepping histogram; this agrees with another simulation which found tail and MTBD flexibility is necessary for large steps \cite{tsygankovemsimulation}.
 We tested the dynamics of this fit model, and found that the model displayed a high level of agreement with the data used to fit; the simulation's velocity and stepping histogram in Figure \ref{fig:behavior} match experiment quite well.
@@
 
-This model contrasts with another theory on the dynein step called the winch mechanism \cite{uenoem, sarlahmodel, nicastro} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
+This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
 al} \cite{lippert}).
@@
 
-Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel}.
+Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel, tsygankovemsimulation}.
 This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency.
@@
 For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find-that-other-possibly-burgess-paper}.
-Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, Y and Z are also neglected.
+Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, inter-head interactions \cite{tsygankovscheme, tsygankovemsimulation}, Y and Z are also neglected.
 Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\

### 2018-12-30 papers/paper/paper.tex
Add another modeling paper to paper

@@
 The dynamics of dynein are captured by imposing both equilibrium and Brownian forces on each circular domain of the model.
-The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse.
+The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse, as has been done before \cite{zhaomodel}.
 The bothbound state is meant to represent the post-powerstroke pre-ADP release state, and the onebound state represents the post pre-stroke pre-MT binding state, during which ATP is hydrolyzed and phosphate is rejected.
@@
 
-Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel, tsygankovemsimulation}.
-This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency.
+Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel, tsygankovemsimulation, zhaomodel}.
+This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency, and to our knowledge is the first model to combine imaging and kinetics data with Brownian dynamics to quantify the influences of drag on the dynein motor.
 Our minimal assumptions simplify the model and rule out overfitting.
@@
 For example, some have proposed that stalk flexibility is an important aspect of dynein's mechanism \cite{mdstalk, lippert, find-that-other-possibly-burgess-paper}.
-Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, inter-head interactions \cite{tsygankovscheme, tsygankovemsimulation}, Y and Z are also neglected.
+Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, inter-head coordination \cite{tsygankovscheme, tsygankovemsimulation}, stalk flexibility???, Y and Z are also neglected.
 Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\

### 2018-12-30 papers/paper/paper.tex
Add more on previous models

@@
 
-This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
+This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
 al} \cite{lippert}).
@@
 This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency, and to our knowledge is the first model to combine imaging and kinetics data with Brownian dynamics to quantify the influences of drag on the dynein motor.
-Our minimal assumptions simplify the model and rule out overfitting.
+We believe that taking into account diffusion dynamics and drag is necessary to understand dynein's dynamics, and not doing so may explain why previous studies found the winch model to replicate experimental results \cite{sarlahmodel}.
+Our minimal assumptions simplify the model and allow analytical solutions to motion equations.
 However, our model neglects many features which may be important for real dynein's walk.

### 2019-01-03 papers/paper/paper.tex
Remove unused references from paper.bib and add some more.

@@
 Dynein's mechanism of motion generation is the least understood of all motor proteins.
-Kinesin and myosin both take periodic, consistent steps of 8nm.
+Kinesin and myosin both take consistent steps of the same size \cite{kinesin-step-size, myosin-step-size}.
 In contrast, dynein is known to take highly variant steps both forwards and backwards, but averaging 16nm \cite{yildizpaper, weihongpaper}.
@@
 These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}.
+These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}.
 Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.\\
@@
 Each domain feels not only a harmonic restoring force, but also a Brownian force $\vec{R}$.
-This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ \cite{einstein} and uniformly random direction.
+This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ and uniformly random direction.
 
@@
 
+Describe fig:stroke results here.
+The transition rate from pre->post powerstroke compares roughly with MD simulations of the powerstroke \cite{mdstroke}. - is this actually true?
+
 %% \begin{figure*}[tbhp]

### 2019-01-03 papers/paper/paper.tex
Add 2 paragraphs to results section on angle plots

@@
 On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT.
+Data used for subfigures b-e are for all steps with a positive step size.
 \textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line).
@@
 
-Describe fig:stroke results here.
-The transition rate from pre->post powerstroke compares roughly with MD simulations of the powerstroke \cite{mdstroke}. - is this actually true?
+We then examined how the model took its forward steps.
+Two existing theories for motion generation are depicted in Figure \ref{fig:stroke}.a.
+The winch model \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch, lippert}, on the left, predicts that the prestroke to poststroke transition causes the just-bound motor's head to act like a winch, pulling the tail domain down and forwards toward the microtubule.
+The powerstroke model \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}, on the right, predicts that the transition will cause a lever-like action of the just bound stalk, pulling the just bound motor's head and tail forward.
+The most notable differences between these two models are whether the stalk angle changes during the stroke \cite{lippert}, and whether the tail domain moves closer or further from the microtubule.
+Arrows indicate these predictions in Figure \ref{fig:stroke}.a.\\
+
+The average change of motor angles and positions during the prestroke-to-poststroke transition is shown in subfigures \ref{fig:stroke}.b-e.
+Only positive steps were used for clarity.
+Subfigure \ref{fig:stroke}.b indicates the model's just-bound stalk experiences a consistent angular displacement after binding, rotating to point more towards the minus end of the MT.
+Interestingly, this transition takes the binding angle out of equilibrium.
+This transition is permanent once made, as shown in \ref{fig:stroke}.f, which shows the no change even up to a millisecond after binding.
+This forward transition of the head domain is accompanied by a forward displacement of the tail domain by roughly 12 $nm$, as shown in Figure \ref{fig:stroke}.d, and a displacement away from the microtubule by 5-8 $nm$, as shown in Figure \ref{fig:stroke}.e.
+This tail displacement takes roughly 300ns, which corresponds roughly to the prestroke-to-powerstroke transition time from MD \cite{mdstroke} (DOES IT ACTUALLY THOUGH?
+LOOK AGAIN).
+The motor angle is shown in Figure \ref{fig:stroke}.c to transition from the pre-stroke equilibrium to the post-stroke equilibrium in time with the stalk angle change.
+Taken together, this data indicates that our simulated dynein moves through a powerstroke-, not a winch-type mechanism.
+We hypothesize that the out of equilibrium state of the motor angle post-transition is highly energetic, and it is quicker for the model to re-equilibrate the high-energy state through pushing the motor forward in a powerstroke than winching the faraway bulky tail downwards.\\
 
@@
 This allows us to study mechanistic questions about how dynein walks.
-Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps, burgessknight, robertspowerstroke, burgess-paper} (CITE MORE).
+Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}.
 As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
@@
 
-This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
+This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch, lippert} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
 al} \cite{lippert}).

### 2019-01-03 papers/paper/paper.tex
Slight edits to paper text.

@@
 The head is connected via a linker to a large tail domain responsible for binding various cargos and accessory proteins.
-The tail is also the site of dimerization, where two dynein monomers join to form a homodimeric unit capable of motion.\\
+The tail is also the site of dimerization, where two dynein monomers join to form a homodimeric unit capable of motion.
 
@@
 The protein must transmit information about ATP binding across this distance in order to coordinate its steps \cite{mt-atp-coupling}.
-Explaining these phenomena is necessary to fully understand dynein's mechanism.\\
+Explaining these phenomena is necessary to fully understand dynein's mechanism.
 
@@
 This causes the motor to lurch forward in a process called the powerstroke.
-The protein is now ready to re-bind ATP and take another step.\\
+The protein is now ready to re-bind ATP and take another step.
 
@@
 Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary, imaiburgess}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
-Such a study would be able to find the minimum criteria for generating dynein's motion.\\
+Such a study would be able to find the minimum criteria for generating dynein's motion.
 
@@
 The model is capable of generating directed motility at rates similar to experiment.
-Further, we show that the model displays more complex behavior, such as tension gating and force-mediated bidirectionality.\\
+Further, we show that the model displays more complex behavior, such as tension gating and force-mediated bidirectionality.
 
 %% just say that we included tension gating
-
-\section*{Model}
 
@@
 Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the recovery stroke and powerstroke \cite{burgess-paper, burgessknight}.
-In particular, the equilibrium angles controlling a motor's tail-motor-MTBD angle change to kick the stalk-MTBD further from the tail.\\
+In particular, the equilibrium angles controlling a motor's tail-motor-MTBD angle change to kick the stalk-MTBD further from the tail.
 
@@
 Each MTBD is connected to a motor domain via a rigid rod of length $L_s$, meant to represent the stalk domain.
-Each motor domain is connected to the tail domain via a rigid rod of length $L_t$; this rod represents the heavy chain linker and intermediate/light chains which connect the motor to the dimerization site.\\
+Each motor domain is connected to the tail domain via a rigid rod of length $L_t$; this rod represents the heavy chain linker and intermediate/light chains which connect the motor to the dimerization site.
 
 Values for $R$ and $L$ were acquired by aligning the dynein model with EM micrographs of the full dynein complex \cite{burgess-paper,grotjahn}, as shown in Figure \ref{fig:micrographs}.
-See Table \ref{table:params} for these values.\\
+See Table \ref{table:params} for these values.
 
@@
 These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}.
-Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.\\
+Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.
 
@@
 This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head.
-Values used for parameters $k^0_{ub}$ and $c$, along with $k_b$, are shown in Table \ref{table:params}.\\
+Values used for parameters $k^0_{ub}$ and $c$, along with $k_b$, are shown in Table \ref{table:params}.
 
@@
 A study with a similar velocity is used to estimate $\bar{t}_{run} = 1060 nm / 134 nm / s = 7.9s$ \cite{weihongpaper}.
-These observables, along with $\bar{L} = 8nm$, yield estimations $\bar{t}_{ob} = 5.2*10^{-4}s$ and $\bar{t}_{bb} = 6.4 * 10^{-2}s$.\\
+These observables, along with $\bar{L} = 8nm$, yield estimations $\bar{t}_{ob} = 5.2*10^{-4}s$ and $\bar{t}_{bb} = 6.4 * 10^{-2}s$.
 
@@
 Each $X_i$ coordinate is related to the $\theta_j$ coordinates via the recursive formulas $X_{i>1} = L_i\cos(\theta_{i-1})+X_{i-1}$ and $Y_{i>1} = L_i\sin(\theta_{i-1})+Y_{i-1}$ for y-coords.
-Thus, each $\dot{X_i}$ term is linearly related to one or more $\dot{\theta_j}$ terms.\\
+Thus, each $\dot{X_i}$ term is linearly related to one or more $\dot{\theta_j}$ terms.
 
@@
 Each timestep, the bothbound model had a $k_{ub}*dt$ chance of transitioning to onebound, where $k_{ub} = k^0_{ub}e^{-c(\theta-\theta_{eq})}$.
-On transitioning, proper values of $\{\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub}\}$ were calculated to create a onebound model with identical cartesian positions to the old bothbound model.\\
+On transitioning, proper values of $\{\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub}\}$ were calculated to create a onebound model with identical cartesian positions to the old bothbound model.
 
@@
 Thirty-two 5-second simulations were run, each initialized with a different random seed.
-Each simulation was forward directed, took both forward and backward steps, and displayed stepping dynamics similar to that seen in experiment.\\
+Each simulation was forward directed, took both forward and backward steps, and displayed stepping dynamics similar to that seen in experiment.
 
@@
 The cartoons in Figure \ref{fig:trajectory} reveal the model taking on many conformations, revealing the model's structural flexibility.
-The model seems to prefer alternating hand-over-hand stepping, but occasionally takes steps in a semi-inchworm fashion, as seen at time $5.3 \mu s$ in Figure \ref{fig:trajectory}.\\
+The model seems to prefer alternating hand-over-hand stepping, but occasionally takes steps in a semi-inchworm fashion, as seen at time $5.3 \mu s$ in Figure \ref{fig:trajectory}.
 
@@
 Experimental technique does not resolve time spent in pre- and post-powerstroke, but we outline a technique for calculating these values for experimental trajectories in Methods.
-These theoretical values correspond well to model behavior, and square with experimental findings that dynein is almost always in the post-stroke state \cite{imaiburgess}.\\
+These theoretical values correspond well to model behavior, and square with experimental findings that dynein is almost always in the post-stroke state \cite{imaiburgess}.
 
@@
 This trend also very closely tracks DeWitt \textit{et.
-al}.\\
+al}.
 
@@
 al} where force is applied via optical tweezers to dynein constructs and their velocity is assayed.
-It will need to be studied why odd behavior is seen in the mdoel for positive forces.\\
+It will need to be studied why odd behavior is seen in the mdoel for positive forces.
 
@@
 However, the binding orientation of the dynein model to the microtubule is stable through time, and can influence the binding orientation of dynein to the microtubule at a later time.
-There seems to be a roughly tension-gated process occurring where negative displacements initially lead to positive displacements later.\\
+There seems to be a roughly tension-gated process occurring where negative displacements initially lead to positive displacements later.
 
@@
 The most notable differences between these two models are whether the stalk angle changes during the stroke \cite{lippert}, and whether the tail domain moves closer or further from the microtubule.
-Arrows indicate these predictions in Figure \ref{fig:stroke}.a.\\
+Arrows indicate these predictions in Figure \ref{fig:stroke}.a.
 
@@
 Taken together, this data indicates that our simulated dynein moves through a powerstroke-, not a winch-type mechanism.
-We hypothesize that the out of equilibrium state of the motor angle post-transition is highly energetic, and it is quicker for the model to re-equilibrate the high-energy state through pushing the motor forward in a powerstroke than winching the faraway bulky tail downwards.\\
+We hypothesize that the out of equilibrium state of the motor angle post-transition is highly energetic, and it is quicker for the model to re-equilibrate the high-energy state through pushing the motor forward in a powerstroke than winching the faraway bulky tail downwards.
 
@@
 We then examined the mechanism our model used to walk by studying domain positions over many steps.
-We found that the majority of forward displacement occured immediately after a free binding domain bound to the microtubule, when the just-bound stalk swung forward, pulling the attached motor and tail domains toward the minus-end of the microtubule.\\
+We found that the majority of forward displacement occured immediately after a free binding domain bound to the microtubule, when the just-bound stalk swung forward, pulling the attached motor and tail domains toward the minus-end of the microtubule.
 
@@
 The stalk angle remains displaced from equilibrium until the next unbinding.
-Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.\\
+Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.
 
@@
 Indeed during displacement our model's tail domain actually moves away from the microtubule, the opposite of the winch's prediction.
-Further theoretical studies demonstrating the feasibility and sufficiency of the winch mechanism are needed.\\
+Further theoretical studies demonstrating the feasibility and sufficiency of the winch mechanism are needed.
 
@@
 This suggests that the stalk angular displacement is a non-equilibrium phenomena which could not be detected through cryo-EM, which resolves equilibrium structures.
-This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem, nicastro}.
-We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast millisecond phenomena.\\
+This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem, nicastro} (REREAD THE UENOEM PAPER TO MAKE SURE THIS IS RIGHT).
+We further hypothesize that previous simulation results \cite{sarlahmodel}, which have shown a winch-like mechanism is capable of generating motion, have only done so because they do not account for drag and diffusion dynamics.
+Our data demonstrate that pushing forward the motor domain in a powerstroke is a more likely means of relieving the high-energy poststroke state than winching down the far off tail.
+We hypothesize that further models which also account for diffusion would find the same.
+We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast microsecond phenomena.
 
@@
 This suggests that perhaps the motor requires a diffusive search along the microtubule to find the next binding site.
-Alternatively, as has been recently demonstrated, perhaps an electrostatic mechanism is used to guide the MTBD to the next binding site using long-range interactions \cite{longrangemt}.\\
+Alternatively, as has been recently demonstrated, perhaps an electrostatic mechanism is used to guide the MTBD to the next binding site using long-range interactions \cite{longrangemt}.
 
@@
 Other features like microtubule electrostatic interactions \cite{longrangemt}, binding angle dependent MTBD binding \cite{responsetoload} - ACTUALLY LOOK AT PAPER THOUGH, inter-head coordination \cite{tsygankovscheme, tsygankovemsimulation}, stalk flexibility???, Y and Z are also neglected.
-Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.\\
+Although our work successfully demonstrates the sufficiency of our minimal set of assumptions for generating motion, a more biologically realistic model would need to take these listed features into account.
 
@@
 We hope that this evidence is sufficient to maintain the powerstroke mechanism as a viable hypothesis for how dynein walks.
-We further hope that experiments with higher spatial and temporal resolution can be conducted in the near future to shed more light on the precise nature of dynein's stepping mechanism.\\
+We further hope that experiments with higher spatial and temporal resolution can be conducted in the near future to shed more light on the precise nature of dynein's stepping mechanism.
 
@@
 \item Run simulations with/without interhead coordination, use a passing/no-passing chart with both models and experiment to demonstrate that tension-gating helps
+\end{enumerate}
+
+\subsection{Anyone tasks}
+\begin{enumerate}
+\item Movie of dynein walking as a supplemental figure
+\item Put most likely step length in stepping histogram
 \end{enumerate}

### 2019-01-12 papers/paper/paper.tex
Make various changes to angle figure to look better, including modifying the cartoon and downsampling one plot

@@
   \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A.
-left: } Schematic of the winch mechanism.
+left: } Schematic of winch model for dynamics during conformation changes associated with right monomer binding.
 On free MTBD binding, linker swing in the just-bound head pulls the tail and cargo in the direction of the just-bound MTBD.
 \textit{A.
-right: } Schematic of the powerstroke mechanism.
+right: } Schematic of the powerstroke model for dynamics during during conformation changes associated with right monomer binding.
 On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT.
-Data used for subfigures b-e are for all steps with a positive step size.
+Subfigures b-e describe dynamics for the right monomer during post-binding conformation change; only data for steps with a positive step size is shown.
 \textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line).
@@
 All values sampled every $10 ns$.
-\textit{f.) } Just-bound MTBD stalk angle over the entirety of the post-powerstroke state, sampled every 1 $\mu s$.
+\textit{f.) } Just-bound MTBD stalk angle for the millisecond after binding, sampled every 20 $\mu s$.
 All values plotted as mean $\pm$ SD.}

### 2019-01-13 papers/waczak-thesis/thesis/thesis.tex

\documentclass[a4paper, 11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}  
\usepackage{amsthm}
\usepackage{ulem} 
\usepackage{graphicx}
\usepackage{enumitem} % use for making lettered list 
\usepackage{subfig} 
\graphicspath{ {images/} }
\usepackage{titletoc}

\title{Simulating the Brownian Dynamics of a Two-Dimensional Model for the Dynein Motor Protein}
\author{John Waczak}
\date{\today}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Introduction}
	\subsection{Cellular Processes}
		\subsubsection{The Cytoskeleton}
		\subsubsection{Mitosis} 
	\subsection{Motor Proteins}
\subsection{Dynein}
	\subsubsection{Directed Motion}
	\subsubsection{Drunken Walking}
	\subsubsection{Transporting Cargo}
	\subsubsection{Experimental Stepping Statistics}

\section{The Model} 
	\subsection{Brownian Motion}
	\subsection{A Simplified Model for Dynein}
	\subsection{Equations of Motion}
		\subsubsection{The one bound state}
		\subsubsection{The both bound state}
		\subsubsection{Calculating Forces and Torques}
	\subsection{The Code}

\section{Results}
	\subsection{Model Tests}
		\subsubsection{Determining an Appropriate dt}
		\subsubsection{Conservation of Energy}
	\subsection{Parameter Fitting}
	\subsection{Model Stepping Statistics}
	\subsection{Simulating External Forces}

\section{Discussion}
	\subsection{Comparison to Experimental Results}
	\subsection{Consequences of the Simple Model}
		\subsubsection{Do we need a Two State Model?}
		test text 
\section{Conclusions}
	\subsection{Summary}
	\subsection{Future Work}
		\subsubsection{Simulating Multiple Dynein}
		\subsubsection{Forces on the Binding Domain} 
		\vspace{2em}
		\textbf{NOTE: I still need to figure out how to organize the information I already wrote within the sections of the introduction I list in the table of contents.}\\

		The dynein motor protein is a unique molecule among the family of motor proteins. Unrelated to similar motors of the kinesin family, dynein consists of heavy chains which include a large motor domain \cite{alberts_molecular_2002}. Dynein’s cellular environment means that the it is constantly bombarded by water molecules which impart random pushes to the protein. The resulting kinematics are called Brownian dynamics. Dynein has a mass on the order of 1 MDa whereas other motors like kinesin are of the scale of a few hundred kDa \cite{johnson_structure_1983}. This exaggerates the effects of the Brownian forces on dynein and has led the motor to be dubbed  as the “drunken-walker” due its tendency to take steps forward, backwards, diagonally, and in no particular order. The many forms of dynein play critical roles in everything from cell division to the movement of flagella. Its occasional mutation can lead to critical cell malfunctions and has even been linked to neurodegenerative diseases \cite{cleary_tension_2014}.

		To date, research on the protein has investigated the chemical cycle required for dynein to convert ATP into usable mechanical energy \cite{cianfrocco_mechanism_2015}. Other studies have tested the extent to which mechanical information is stored between the legs of the protein, that is, how much previous steps and the steps of opposite legs affect future stepping behavior \cite{puls_mutant_2003}. Somehow, despite all of this investigation, there is no accepted model that explains the motion of this system as a physical object moving through space. Through direct simulation of the Brownian dynamics on a simplified two-dimensional structure, we propose a physical model for the movement of dynein that can replicate many of its famous behaviors including the drunken walk. Individual domains are allowed to pass through one another to account for the truly 3-dimensional structure. During each time step of the simulation, a random diffusive force is applied to each domain as well as a restorative torque that pushes the domains towards an equilibrium angle.

		\newpage

		\begin{figure}[!hbt]
			\centering
			\includegraphics[width=0.65\columnwidth]{paper_trajectory_plot}
			\caption{Horizontal(x) and vertical(y) projections for the binding domain as a function of time. Between each image we show a cartoon of dynein illustrating its configuration corresponding to the black marker in each graph}
			\label{fig:trajectory}
		\end{figure}

		In figure \ref{fig:trajectory} we can see the horizontal and vertical projections for the dynein motor protein throughout a simulation. From this graph we can make a number of interesting conclusions. First, we can clearly see the stepping behavior: while one foot (say red) is chaotically diffusing, the other (blue) is fixed on the microtubule. Furthermore, the x-projection graph demonstrates that the motor is, on average, forward directed. Interestingly, the cartoons show that the model assumes a wide range of configurations throughout the simulation. Neither the hind-leg nor human leg shape appears to be preferred.

		\noindent\textbf{NOTE2: Need to fix bibliography style in latex to match the physical review letters style}

\bibliography{references}
\bibliographystyle{acm}
\end{document}

### 2019-01-15 papers/paper/paper.tex
Add potentially fit kb/kub to paper_params.py for gennerich force/velocity plot. Still need to re-run the force data gen script with new params.

@@
 Model parameters were estimated from various experimental results.
-Spring constants were chosen to fit the model stepping size to experiment, as outlined in Figure S\ref{fig:supp-model-fit}.
-Model rate constants were fit to theoretical calculations outlined in the Methods section.
-The tension-gating parameter c was fit as shown in Figure \ref{fig:tensiongating}.
+Spring constants were chosen to fit the model stepping size to single-molecule head-labelled experiments\cite{yildizpaper}, as outlined in Figure S\ref{fig:supp-model-fit}.
+Model rate constants were fit to motor velocities from the same experiment, along with theoretical calculations for the prestroke and poststroke times outlined in the Methods section.
+The tension-gating parameter $c$ was fit to the leading/lagging unbinding likelihood versus interhead separation from the same experiment, as shown in Figure \ref{fig:tensiongating}.
 Thirty-two 5-second simulations were run, each initialized with a different random seed.

### 2019-01-15 data/paper_params.py

@@ -11,8 +11,8 @@ stroke_angle_k_b  = k_b # s^-1
 stroke_angle_k_ub = k_ub # s^-1
 stroke_angle_seed = 1
 
-force_k_b  = k_b # s^-1
-force_k_ub = 10 # s^-1
+force_k_b  = 3e6 # s^-1
+force_k_ub = 10 # s^-1, 5 was about 1/2 the velocity we want
 
 cexp = -0.35
 

### 2019-01-15 scripts/generate-paper-force_vs_velocity_data.py

@@ -12,7 +12,6 @@ sys.path.insert(0, os.getcwd() + "/data/")
 import paper_params as params
 
 runtime = 2
-
 for f in [4, 0, -1, -2, -3, -4, -5, -6, -7, -8, -10]:
     for s in [1, 2, 3, 4]:
         basename = "paper_force__F-%s,s-%s" % (str(f), str(s))

### 2019-01-16 papers/paper/paper.tex
Add very rough additions to introduction

@@
 
-Dynein's mechanism of motion generation is the least understood of all motor proteins.
-Kinesin and myosin both take consistent steps of the same size \cite{kinesin-step-size, myosin-step-size}.
-In contrast, dynein is known to take highly variant steps both forwards and backwards, but averaging 16nm \cite{yildizpaper, weihongpaper}.
+Dynein's mechanism of motion generation is the least understood of all motor proteins \cite{}.
+Kinesin and myosin both take consistent steps of the same size \cite{kinesin-step-size, myosin-step-size, is-this-true-in-general-i-thought-only-types-of-myosin}.
+In contrast, dynein is known to take highly variant steps both forwards and backwards, averaging 16nm \cite{yildizpaper, weihongpaper}.
 Another interesting feature of dynein is the 20nm separation between its ATP hydrolysis and the site and MT binding site \cite{3vkh-cite}.
@@
 It is also known that ATP binding can induce structural changes within the motor which increase unbinding rate \cite{leschziner, carter-paper}, and similarly that microtubule rebinding can influence nucleotide unbinding rate \cite{mt-atp-coupling}.
-Taken together this evidence is synthesized into a powerstroke model \cite{cianfroccoreview, imamulamodel, tsygankovscheme}.
-In the powerstroke model, dynein binds ATP, causing structural changes which eventually lead to microtubule unbinding at its MTBD.
+Taken together this evidence is synthesized into a mechanochemical cycle \cite{cianfroccoreview, imamulamodel, tsygankovscheme}.
+In this scheme, dynein binds ATP, causing structural changes which eventually lead to microtubule unbinding at its MTBD.
 These structural changes transition the motor into a more open position, causing the MTBD to diffuse forwards on the microtubule.
@@
 Eventually the MTBD rebinds the microtubule, causing structural changes inducing the ejection of hydrolyzed ADP and transitioning back to the closed position.
-This causes the motor to lurch forward in a process called the powerstroke.
+This puts the motor in the post-stroke state, moved forward slightly.
 The protein is now ready to re-bind ATP and take another step.
 
-Ample evidence exists that dynein engages in an ATP-induced prestroke and MT-binding-induced powerstroke.
-However, to our knowledge, no work has been done to test whether a structural model of dynein obeying the proposed mechanochemical cycle is sufficient to reproduce experimental stepping data.
-Existing computational models use chemical rate transitions and assume independence of steps, without simulating the entire mechanochemical cycle \cite{sarlahmodel}.
-No models have combined structural and kinetic data to simulate a dynein model in a biophysically realistic way.
-It is necessary to do so to properly test the powerstroke hypothesis.
-Such a study would determine if the powerstroke mechanism is sufficient to explain dynein's walk, or if further explanation is necessary.
-Others have theorized that elements such as electrostatic interactions with the microtubule \cite{longrangemt}, tension-gating between the two heads \cite{yildizcleary, imaiburgess}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are important for dynein's walk.
-Such a study would be able to find the minimum criteria for generating dynein's motion.
+This mechanochemical cycle of chemical transitions is well supported by evidence \cite{citemore}.
+However, there is still relatively little known about the dynamic mechanism of domain motion dynein uses to achieve its forward motion by transitioning between these states \cite{lippert}.
+There exist models theorizing how dynein's domains move during its forward step, such as the winch \cite{} and powerstroke \cite{} models, which can reproduce experimental data \cite{}.
+However, to our knowledge, no studies exist which study if either of these dynamic mechanisms is feasible for the dynein motor to produce.
+Existing computational models of walking use chemical rate transitions and assume independence of steps, without simulating the precise protein dynamics \cite{}.
+Molecular dynamics simulations exist, but are of too short a timescale to describe dynein's forward stroke \cite{}.
+It is necessary to model dynein dynamically at a large timescale to fully understand how feasible models like the winch and powerstroke are.
+Further, such long-timescale dynamic models could be used to find what elements of dynein are sufficient to produce forward motion.
+Further, an accurate dynamical model would allow us to test if certain dynamical elements, such as electrostatic interactions with the microtubule \cite{longrangemt}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are necessary for dynein's walk.
 
-Here we present a course-grained model of cytoplasmic dynein which treats its domains as connected rigid bodies.
-Chemical transitions and conformational changes consistent with the powerstroke model are accounted for via elastic forces.
-The dynamics are determined using Brownian dynamics.
-The model is capable of generating directed motility at rates similar to experiment.
-Further, we show that the model displays more complex behavior, such as tension gating and force-mediated bidirectionality.
-
-%% just say that we included tension gating
+Here we present a course-grained model of cytoplasmic dynein which reduces the mechanochemical cycle down to pre- and post-stroke states.
+We use cryo-EM data to create rough structural models of these conformers, and impose inter-domain tension and elastic restoring forces to describe the dynamics within each conformer.
+We then model the state transition as a transition between two equilibria, and use Brownian dynamics to simulate the model's behavior in physically realistic drag and diffusion conditions.
+This minimal model spontaneously generates a powerstroke-like dynamic mechanism, and uses it to produce bidirectional motion.
+The model also reproduces several experimental measures, such as step size, velocity and force-mediated directionality control.
 
@@
 This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$.
-To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildiz} to allow for interhead communication and bias the motor forward, the parameter $c$ is used to alter the unbinding rates of either MTBD.
+To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildiz, yildizcleary} to allow for interhead communication and bias the motor forward, the parameter $c$ is used to alter the unbinding rates of either MTBD.
 For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $k_{ub} = k^0_{ub}e^{-c\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$.

### 2019-01-17 papers/paper/paper.tex
Make some additions to paper text, and replace the onebound/bothbound formalism with prestroke and poststroke to fit better with other papers

@@
 al} simulate a model obeying rate constants from \textit{Imamula}, and replicate dynein's stepping trajectory \cite{sarlahmodel}.
-\textit{Zheng} uses normal mode analysis to simulate the dynein motor's transition from pre to post-powerstroke \cite{normalmodes}.
+\textit{Zheng} uses normal mode analysis to simulate the dynein motor's transition from pre to post-stroke \cite{normalmodes}.
 To our knowledge, no computational model exists which takes into account the microscopic dynamics of protein-water interactions to test whether diffusion is enough for dynein motility.
@@
 There exist models theorizing how dynein's domains move during its forward step, such as the winch \cite{} and powerstroke \cite{} models, which can reproduce experimental data \cite{}.
-However, to our knowledge, no studies exist which study if either of these dynamic mechanisms is feasible for the dynein motor to produce.
+However, to our knowledge, no studies exist which use protein dynamics to study if either of these dynamic mechanisms is feasible for the dynein motor to produce.
 Existing computational models of walking use chemical rate transitions and assume independence of steps, without simulating the precise protein dynamics \cite{}.
 Molecular dynamics simulations exist, but are of too short a timescale to describe dynein's forward stroke \cite{}.
-It is necessary to model dynein dynamically at a large timescale to fully understand how feasible models like the winch and powerstroke are.
+It is necessary to model dynein dynamically at a large timescale using physically realistic protein dynamics to fully understand how feasible models like the winch and powerstroke are.
 Further, such long-timescale dynamic models could be used to find what elements of dynein are sufficient to produce forward motion.
@@
 \includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
-\caption{\textbf{Basic geometric model in pre-powerstroke and post-powerstroke states.} \textit{Left: } Pre-powerstroke model of dynein with one MTBD bound to microtubule and the other free.
+\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.} \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free.
 Angles are measured from the $+\hat{x}$ direction.
-\textit{Right: } Post-powerstroke model with both MTBDs bound to microtubule.
+\textit{Right: } Post-stroke model with both MTBDs bound to microtubule.
 MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail.
@@
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-powerstroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-powerstroke ADP-Vi-bound state \cite{burgess-paper}.
+\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-stroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state \cite{burgess-paper}.
 Interdomain lengths and radii scaled to micrograph scale bar.
 No microtubule is present, so $\theta_{nb}$ is arbitrary.
-\textit{Right: } Model with angles at pre-powerstroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}.
+\textit{Right: } Model with angles at pre-stroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}.
 Interdomain lengths and radii scaled to density map.}
@@
 Parameters used in simulation.} $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
-$k_b$ and $k_{ub}$ are the rates of pre-powerstroke to post-powerstroke and post-powerstroke to pre-powerstroke transitions, respectively.
+$k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
 $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
 $c$ is the tension-gating factor.
-The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-powerstroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-powerstroke motor and both post-powerstroke motors.
+The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
 $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
@@
 The dynamics of dynein are captured by imposing both equilibrium and Brownian forces on each circular domain of the model.
-The chemical properties of dynein are captured by sporadically transitioning the model between two states: a ``bothbound'' state where both binding domains are fixed to the microtubule, and a ``onebound'' state where one foot is free to diffuse, as has been done before \cite{zhaomodel}.
-The bothbound state is meant to represent the post-powerstroke pre-ADP release state, and the onebound state represents the post pre-stroke pre-MT binding state, during which ATP is hydrolyzed and phosphate is rejected.
-These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the recovery stroke is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-recovery conformation should dominate when unbound from MT.
-We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-powerstroke state while the other head goers through the entire mechanochemical cycle, neglecting other possible cycles.
-Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the recovery stroke and powerstroke \cite{burgess-paper, burgessknight}.
-In particular, the equilibrium angles controlling a motor's tail-motor-MTBD angle change to kick the stalk-MTBD further from the tail.
+The chemical properties of dynein are captured by sporadically transitioning the model between two states: a poststroke state where both binding domains are fixed to the microtubule, and a prestroke state where one foot is free to diffuse, as has been done before \cite{zhaomodel}.
+The poststroke state is meant to represent dynein after rebinding free MTBD and undergoing the motor-MTBD conformational change, but before releasing ADP, according to the Tsygankov scheme \cite{tsygankovscheme}.
+The prestroke state represents the dynein after binding ATP, unbinding from the MT and undergoing a motor conformational change, but before rebinding the MT.
+ATP hydrolysis and Pi rejection are ignored by the model.
+These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the post-unbinding conformational change is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-unbinding conformation should dominate when unbound from MT.
+We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-stroke state while the other head goes through the entire mechanochemical cycle, neglecting other possible cycles.
+Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the cycle \cite{burgess-paper, burgessknight}.
+In particular, the equilibrium angles governing a motor's tail-motor-MTBD angle change to cause a displacement of the free MTBD towards the MT minus end, producing a forward step.
 
@@
 See Table \ref{table:params} for these values.
+$L_t$, the stem length between motor domain and tail, was calculated as the distance between the center of the EM motor domains and identified dimerization site in the tail domain \cite{}.
+However, studies which compare truncated GST-linked dynein lacking a tail and native dynein find the two step with similar dynamics \cite{weihongpaper-i-think}, suggesting that our model with an $L_t$ value from native dynein should be comparable with studies on truncated dynein constructs as well.
 
 \subsection*{Equilibrium forces}
-The onebound model has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$.
-The bothbound model has two: $\theta_{nm}$ and $\theta_{fm}$.
-The model is free to vary across all of these degrees of freedom, barring steric interactions with the microtubule.
+The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$.
+The poststroke state has two: $\theta_{nm}$ and $\theta_{fm}$.
+The model is free to vary across all of these degrees of freedom, depending on its state, barring steric interactions with the microtubule.
 These angles describe a planar model which is not capable of transverse motion.
-To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for onebound and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for bothbound.
+To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke.
 Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain.
@@
 These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}.
-Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.
+Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.
 
@@
 \subsection*{Binding}
-Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the onebound and bothbound states.
-Binding can occur when the onebound model's unbound foot diffuses near enough the microtubule.
+Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the prestroke and poststroke states.
+Binding can occur when the prestroke model's unbound foot diffuses near enough the microtubule.
 When within a distance of $1 A$, binding occurs at a rate of $k_b$ (Table \ref{table:params}).
-On binding, the onebound model changes state to a bothbound model while retaining the positions of its domains.
+On binding, the prestroke model changes state to a poststroke model while retaining the positions of its domains.
 The previously unbound domain is transported to the microtubule.
@@
 \subsection*{Unbinding}
-Unbinding occurs when a bothbound MTBD unbinds from the microtubule.
+Unbinding occurs when a poststroke MTBD unbinds from the microtubule.
 This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$.
-To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildiz, yildizcleary} to allow for interhead communication and bias the motor forward, the parameter $c$ is used to alter the unbinding rates of either MTBD.
-For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $k_{ub} = k^0_{ub}e^{-c\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$.
+To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildizcleary} to allow for interhead communication and bias the motor forward, we use a scheme where an MTBD is more likely to unbind based on its distance behind the other MT, which accords with experiments \cite{yildiz}.
+For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $k_{ub} = k^0_{ub}e^{-c\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$, where $c$ is a parameter of the model.
 This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head.
@@
 
-The ``prestroke'' and ``powerstroke'' events in the mechanochemical cycle \cite{cianfrocco} are captured by different motor equilibrium angles between the onebound and bothbound states.
-The onebound ``prestroke'' state has an unbound motor angle closer to $\pi$ than the bothbound motor\cite{burgess-paper}; thus, on unbinding, the unbound MTBD should experience a restoring force effecting the ``prestroke'' conformational change.
-On rebinding, the motors transition back to the poststroke equilibrium, producing restoring forces in the direction of the ``powerstroke.''
+The transitions between prestroke and poststroke events in the mechanochemical cycle \cite{cianfrocco} are captured by changing the motor equilibrium angles when a state transition occurs.
+The prestroke state has an unbound motor angle closer to $\pi$ than the prestroke motor\cite{burgess-paper}; thus, on unbinding, the unbound MTBD should experience a restoring force effecting the post-to-pre conformational change.
+On rebinding, the motors transition back to the poststroke equilibrium, producing restoring forces causing the pre-to-post conformational change.
+This shifting of equilibria, coupled with alternating the freedom of the active MTBD, meant to mimic the coupling of ATPase activity and MTBD affinity in the real dynein motor.
 
@@
 First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD, that is, that there is no inter-head coordination.
-Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{\bar{t}_{ob}}{\bar{t}_{step}} * \frac{1}{\bar{t}_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the onebound state, $\bar{t}_{ob}$ and $\bar{t}_{bb}$ are the expected durations for a onebound and bothbound state, and $\bar{t}_{step} = \bar{t}_{ob} + \bar{t}_{bb}$ is the expected step duration.
+Then the dissociation rate of the whole complex from the microtubule, $k_{dis}$, is estimated as $k_{dis} = P(ob)*k_{ub} = \frac{\bar{t}_{ob}}{\bar{t}_{step}} * \frac{1}{\bar{t}_{bb}}$, where $P(ob)$ is the probability of a dynein complex being in the prestroke state, $\bar{t}_{ob}$ and $\bar{t}_{bb}$ are the expected durations for a prestroke and poststroke state, and $\bar{t}_{step} = \bar{t}_{ob} + \bar{t}_{bb}$ is the expected step duration.
 Plugging in the last definition yields $k_{dis} = \frac{\bar{t}_{step} - \bar{t}_{bb}}{\bar{t}_{step}\bar{t}_{bb}}$.
-Introducing a new variable $\bar{t}_{run}$, the average run length of in vivo dynein, and using the relation $\bar{t}_{run} = k_{dis}^{-1}$, a new relation is found for bothbound time: $\bar{t}_{bb} = \frac{\bar{t}_{run}\bar{t}_{step}}{\bar{t}_{run}+\bar{t}_{step}}$.
-Using the definition of $\bar{t}_{step}$ a similar relation is found for onebound time: $\bar{t}_{ob} = \frac{\bar{t}_{step}^2}{\bar{t}_{step}+\bar{t}_{run}}$.
-Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected tail step length $\bar{L}_{step}$, the following equations are found for onebound and bothbound time in terms of experimental observables of velocity, run time and step length:
+Introducing a new variable $\bar{t}_{run}$, the average run length of in vivo dynein, and using the relation $\bar{t}_{run} = k_{dis}^{-1}$, a new relation is found for poststroke time: $\bar{t}_{bb} = \frac{\bar{t}_{run}\bar{t}_{step}}{\bar{t}_{run}+\bar{t}_{step}}$.
+Using the definition of $\bar{t}_{step}$ a similar relation is found for prestroke time: $\bar{t}_{ob} = \frac{\bar{t}_{step}^2}{\bar{t}_{step}+\bar{t}_{run}}$.
+Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected tail step length $\bar{L}_{step}$, the following equations are found for prestroke and poststroke time in terms of experimental observables of velocity, run time and step length:
 
@@
 
-  For estimating onebound and bothbound times from Yildiz \textit{et al}\cite{yildiz}, a velocity of $124 nm/s$ is used.
+  For estimating prestroke and poststroke times from Yildiz \textit{et al}\cite{yildiz}, a velocity of $124 nm/s$ is used.
 A study with a similar velocity is used to estimate $\bar{t}_{run} = 1060 nm / 134 nm / s = 7.9s$ \cite{weihongpaper}.
@@
 
-  \section*{Onebound motion equations derivation}
+  \section*{Prestroke motion equations derivation}
   Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:
@@
 
-  \section*{Bothbound motion equations derivation}
-  Brownian dynamics was also used for the bothbound case.
+  \section*{Poststroke motion equations derivation}
+  Brownian dynamics was also used for the poststroke case.
 Due to the added constraint of both binding domains being fixed to the microtubule, the model is fully described by angles $\theta_{nm}$ and $\theta_{fm}$; see Figure \ref{fig:model}.
@@
   \section*{Simulating the model}
-  Simulations began in the bothbound equilibrium state.
+  Simulations began in the poststroke equilibrium state.
 The model was time-evolved via Euler's Method using analytic expressions for $\{\dot{\theta}_{bb}, \dot{\theta}_{bm}, \dot{\theta}_{um}, \dot{\theta}_{ub}\}$, using a timestep of $dt = 10^{-10}s$.
-In the onebound state, during each timestep the model had a $k_b*dt$ probability of transitioning into the bothbound state, where $k_b = k_b^0\left(1-H\left(X_{uby}-0.1\right)\right)$, where H is the Heaviside function.
-On transition to bothbound, proper $\theta_{nm}$ and $\theta_{fm}$ angles and proper interhead separation $L$ were calculated to yield a bothbound model with identical cartesian positions to the old bothbound, except with the previously unbound binding domain moved to $y=0$.
-Once in bothbound, the model was time-evolved via Euler's Method using analytic expressions for $\{\dot{\theta}_{nm}$ and $\dot{\theta}_{fm}\}$ and a timestep of $dt=10^{-10}s$.
-Each timestep, the bothbound model had a $k_{ub}*dt$ chance of transitioning to onebound, where $k_{ub} = k^0_{ub}e^{-c(\theta-\theta_{eq})}$.
-On transitioning, proper values of $\{\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub}\}$ were calculated to create a onebound model with identical cartesian positions to the old bothbound model.
+In the prestroke state, during each timestep the model had a $k_b*dt$ probability of transitioning into the poststroke state, where $k_b = k_b^0\left(1-H\left(X_{uby}-0.1\right)\right)$, where H is the Heaviside function.
+On transition to poststroke, proper $\theta_{nm}$ and $\theta_{fm}$ angles and proper interhead separation $L$ were calculated to yield a poststroke model with identical cartesian positions to the old poststroke, except with the previously unbound binding domain moved to $y=0$.
+Once in poststroke, the model was time-evolved via Euler's Method using analytic expressions for $\{\dot{\theta}_{nm}$ and $\dot{\theta}_{fm}\}$ and a timestep of $dt=10^{-10}s$.
+Each timestep, the poststroke model had a $k_{ub}*dt$ chance of transitioning to prestroke, where $k_{ub} = k^0_{ub}e^{-c(\theta-\theta_{eq})}$.
+On transitioning, proper values of $\{\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub}\}$ were calculated to create a prestroke model with identical cartesian positions to the old poststroke model.
 
@@
 
-Motion equations were derived for the pre-powerstroke and post-powerstroke states of the model.
-The model was simulated by starting in the equilibrium post-powerstroke position and using Euler's method to time-evolve the model, using a timestep of 1e-10 \textit{s}.
-The model was transitioned between post-powerstroke and pre-powerstroke states using unbinding and binding rates.
+Motion equations were derived for the pre-stroke and post-stroke states of the model.
+The model was simulated by starting in the equilibrium post-stroke position and using Euler's method to time-evolve the model, using a timestep of 1e-10 \textit{s}.
+The model was transitioned between post-stroke and pre-stroke states using unbinding and binding rates.
 Model parameters were estimated from various experimental results.
@@
 This matches the peak experimental step size window of 7-13 \textit{nm}.
-The pre-powerstroke and post-powerstroke state occupation times are shown in Figure \ref{fig:behavior}.c and d.).
-The model prefers long pre-powerstroke times, but is capable of taking very fast steps.
-The post-powerstroke time has a heavy-tailed distribution.
-Experimental technique does not resolve time spent in pre- and post-powerstroke, but we outline a technique for calculating these values for experimental trajectories in Methods.
+The pre-stroke and post-stroke state occupation times are shown in Figure \ref{fig:behavior}.c and d.).
+The model prefers long pre-stroke times, but is capable of taking very fast steps.
+The post-stroke time has a heavy-tailed distribution.
+Experimental technique does not resolve time spent in pre- and post-stroke, but we outline a technique for calculating these values for experimental trajectories in Methods.
 These theoretical values correspond well to model behavior, and square with experimental findings that dynein is almost always in the post-stroke state \cite{imaiburgess}.
@@
 al.} \cite{yildizpaper}.
-\textit{Bottom left: } Distribution of time spent in the pre-powerstroke state during a full mechanochemical cycle from the same dataset.
-\textit{Bottom right: } Time in the post-powerstroke state.
-Both bottom plots have the theoretical values for pre-powerstroke and post-powerstoke times from the DeWitt \textit{et.
+\textit{Bottom left: } Distribution of time spent in the pre-stroke state during a full mechanochemical cycle from the same dataset.
+\textit{Bottom right: } Time in the post-stroke state.
+Both bottom plots have the theoretical values for pre-stroke and post-powerstoke times from the DeWitt \textit{et.
 al.} stepping trajectory.}
@@
 We used experimental data on dynein's step length distribution and unbinding likelihood to fit the model's spring and tension-gating constants.
-We used arguments about dynein's run length and velocity to predict the average time the motor spent in the pre-powerstroke and post-powerstroke states, and fit the model's binding and unbinding rates to these predictions.
-From fitting we found that relatively loose tail and MTBD spring constants and a stiff tail produced the best stepping histogram; this agrees with another simulation which found tail and MTBD flexibility is necessary for large steps \cite{tsygankovemsimulation}.
+We used arguments about dynein's run length and velocity to predict the average time the motor spent in the pre-stroke and post-stroke states, and fit the model's binding and unbinding rates to these predictions.
+From fitting we found that relatively loose tail and MTBD spring constants and a stiff motor domain produced the best stepping histogram; this agrees with another simulation which found tail and MTBD flexibility is necessary for large steps \cite{tsygankovemsimulation}.
 We tested the dynamics of this fit model, and found that the model displayed a high level of agreement with the data used to fit; the simulation's velocity and stepping histogram in Figure \ref{fig:behavior} match experiment quite well.
 In addition the model can predict new data it was not fit with, such as force output in Figure \ref{fig:force} and effects of foot displacement on step length in Figure \ref{fig:tensiongating}.
-The major deviation in model and experiment is the density of model steps around 0nm, which is possibly caused by an inability of the step detection algorithm to detect small steps in experimental dynein.
+The model also displays both inchworm and hand-over-hand stepping, as in real dynein \cite{weihongpaper}.
+The ability of our model to replicate basic experimental features indicates that the core of dynein's step is its ability to couple conformational transitions with MT affinity, and no other aspects are needed.
+The major deviation in model and experiment is the step length density of model steps around 0nm, which is possibly caused by an inability of the step detection algorithm to detect small steps in experimental dynein.
 We then examined the mechanism our model used to walk by studying domain positions over many steps.
@@
 
-One of the main advantages of our study is that it provides high spatial and temporal information about the model's behavior, which is currently unavailable for real dynein.
-This allows us to study mechanistic questions about how dynein walks.
-Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}.
-As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
+One of the main advantages of our study is that it makes predictions with high spatial and temporal resolution using dynamics realistic for a protein of dynein's size and environment.
+This allows us to study mechanistic questions about how dynein walks, which has not been done before.
+Interestingly, our minimal model, with no assumptions about the dynamics of dynein's forward step, appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}.
+As our model transitions from the so-called pre-stroke to post-stroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
 This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY-CITATIONS-HERE}.
@@
 Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.
+The fact that our model only assumes a harmonic restoring energy and a transition in equilibrium angles when switching states, yet produces a robust powerstroke, supports the idea that the powerstroke is feasible for a protein of dynein's general shape and size.
+The fact that a winch-like mechanism was not the dominant mechanism may indicate that the winch is more infeasible for a dynein-like protein.
+This may be due to the fact that the winch requires dragging a potentially large tail domain, whereas the powerstroke only requires pushing the motor domain forward.
+(Not sure if this makes sense, re-check).
 
@@
 al.} \cite{lippert}, who used polTIRF to study the angle dynein's stalk made with the MT in freely-walking dynein.
-Another study showed that there is no difference in stalk angle between motors locked in the pre- and post-powerstroke state using special nucleotides and cryo-electron microscopy \cite{uenoem}.
+Another study showed that there is no difference in stalk angle between motors locked in the pre- and post-stroke state using special nucleotides and cryo-electron microscopy \cite{uenoem}.
 One key finding of our study which reconciles the powerstroke mechanism with these experimental findings is the timescale on which the predicted stalk angular displacement occurs.
@@
 
-\subsection{Elliott}
-\begin{enumerate}
-\item Fix stepping analysis python module to categorize zero-length steps separately from other steps, particularly in terms of stepping imes.
-Alternately, change C++ to make it possible to identify which foot lifted if it didn't move.
-\item When we have all data, write discussion
-\item Rewrite introduction
-\item Possibly sample stalk angles at high resolution and also 50ms, to show why the low time resolution in Lessinger prevented them from seeing the powerstroke?
-\item Test suite for paper plots to see if there aren't subtle bugs?
-\item Re-run velocity vs force simulation at a much lower rate to match the Gennerich velocity at pN=0
-\item \davidsays{Look up Yildiz figure} for initial displacement vs step length fig
-\item Calculate mutual information or pearson's R for initial/final displacement
-\item Add spring symbols to angles to make it more obvious where the springs are
-\item Add more stuff to supplemental methods, like how our drag forces and stuff are calculated and how we calculate unbinding rate
-\item Make clear that we are comparing to artificially-dimerized molecules in our experiment
-\item Run simulations with/without interhead coordination, use a passing/no-passing chart with both models and experiment to demonstrate that tension-gating helps
-\end{enumerate}
-
 \subsection{Anyone tasks}
@@
 \item Movie of dynein walking as a supplemental figure
-\item Put most likely step length in stepping histogram
 \end{enumerate}
@@
   and no-binding simulations to model dynein (like Yildiz).
+\item Debug initial/final displacement plot - it looks like there's a weird
+  threshold at final displacement = 0, is that normal?
 \end{enumerate}
@@
 \end{document}
-
--Dynein's two feet take different steps according to yildiz/qiu
--Carter 2008 says that dynein's MTBD decides directionaolity, whereas Redwine 2012 thinks its linker motion (clarify)
--Imai 2015 has lots to say criticizing the step length studies of qiu/yildiz and have something to say about domain movement MT search
--Someone else referred to the Cianfrocco model, so maybe it's a good one to refer to (well accepted)
--It's important that our model doesn't have the powerstroke mechanism in, only observations from experiment

### 2019-01-22 papers/waczak-thesis/thesis/chapters/dynein.tex
updates to thesis

\section{Directed Motion}
\section{Drunken Walking}
\section{Transporting Cargo}
\section{Experimental Stepping Statistics}

### 2019-01-22 papers/waczak-thesis/thesis/chapters/introduction.tex
updates to thesis

\section{Cellular Processes}
	\subsection{The Cytoskeleton}
	\subsection{Mitosis} 
\section{Motor Proteins}

### 2019-01-22 papers/waczak-thesis/thesis/chapters/methods.tex
updates to thesis

\section{Theory}
Now that I have established some facts about motor proteins as well as specifics about dynein's many odd behaviors, we may begin our discussion of how to construct and test a physical model for its motion. First, we note that dynein's large mass of roughly 2MDa \cite{johnson_structure_1983} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao_kinesin_1998} exaggerates the effect of interactions with the  aqueous environment of the cell. This results in a much more significant drag force as well as a random element from water molecule collisions that changes the overall dynamics of the system. The set of equations governing this motion is called Brownian dynamics and is what we use to simulate the trajectory of dynein along the microtubule. 
	\subsection{Brownian dynamics}
	To model dynein we treat its various domains (binding, motor, and tail) as spheres held together by massless rigid-rods. In general, the dynamics of a constant mass particle are governed by Newton's second law
	\begin{equation}
		\sum_i \mathbf{F}_i = \dot{\mathbf{p}} = m\ddot{\mathbf{x}}
	\end{equation}
	Thus, determining the dynamics of a system boils down to describing the various forces which act upon it and then solving the resulting differential equation. For particles in a solvent, there are three important forces to consider. The first is linear drag, which we write as 
	\begin{equation}
		F_\text{drag} = -\gamma\dot{\mathbf{x}}
	\end{equation}
	where $\gamma$ is the constant of proportionality. For a spherical particle of radius $a$ moving through a solvent with liquid viscosity $\eta$ this was derived by Stoke to be 
	\begin{equation}
		\gamma = 6\pi\eta a
	\end{equation}

	The second characteristic force of Brownian dynamics is a random force due to density fluctuations in the solvent which we denote $F_\text{rand}$. Finally, might also consider how individual particles interact with each other. For us, this will be accomplished through the rigid rods that outline the structure of the protein. Putting all of these forces together results in what is often called the \textit{Langevin Equation}.
	\begin{equation}
		m\ddot{\mathbf{x}} + \gamma\dot{\mathbf{x}}+\mathbf{F}_\text{rand} = 0 
	\end{equation}

	If we assume further that $|\gamma\dot{\mathbf{x}}|\gg |m\ddot{\mathbf{x}}|$, or in other words, we take the limit of strong drag, then we arrive at the definition of Brownian Dynamics. This allows us to neglect the acceleration term resulting in the following differential equation:
	\begin{equation}
		\dot{\mathbf{x}} = \frac{1}{\gamma}\left( \mathbf{F}_\text{interact} + \mathbf{F}_\text{rand} \right)
	\end{equation}
	To complete the model, we must specify how we calculate and apply the random force as well as the force due to the interactions between domains.

	\subsection{A Simplified Model for Dynein}
	As previously mentioned, we model dynein as a system of spherical domains held together by massless rigid-rods with the whole system moving according to Brownian Dynamics. The random forces on each domain are responsible for diffusing the system and creating the chaotic motion, but in order to have dynein prefer one side of the microtubule on average (as is the case for real dynein) we need to impose some \textit{extra} structure on the protein.

	To do this we steer each domain towards an equilibrium configuration by a Hooke's law restorative torque of the following form
	\begin{equation}
		\Gamma_i = c_i\left(\phi_i-\phi_{i,\text{eq}}\right)
	\end{equation}
	where the $c_i$ are spring constants (a free parameter of the model) and the set $\{\phi_i\}$ are the angles measured between the $i-1$ and $i+1$ domains. Note that for binding domains this angle may be measured to the microtubule or not measured if the domain is unbound from the microtubule. The angles $\{\phi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}

	\begin{figure}[hbt!]
		\centering
		\includegraphics[angle=-90, width=0.75\columnwidth]{torque_angles}
		\caption{Example of dynein in the onebound configuration with torque angles $\{\phi_i\}$ shown. \textbf{NOTE: double check w/ David on how we select the angles e.g. do we take min of the two possible angles? How do we define the equilibrium angles?}}
		\label{fig:torque angles}
	\end{figure}

	\subsection{Determining constants of the model}
	I will insert discussion here about how we determined rod lengths and equilibrium angles from microscopy images. \\

	\begin{figure}[hbt!]
		\centering
		\includegraphics[width=0.3\columnwidth]{schematic-2-superimposed}
		\caption{Our model superimposed over microscopy image of Dynein \textbf{NOTE: add source} for determining lengths and equilibrium angles} 
		\label{fig:superimpmosed}
	\end{figure}
	\subsection{Equations of Motion}
	This is where I will discuss how we calculate the equations of motion for our two states-- One bound and both bound as well as how we algorithmically determine the interaction forces from the torques.

		\subsubsection{The one bound state}
		The following figure shows the model in the one bound configuration.\\
		\begin{figure}[!hbt]
			\centering
			\includegraphics[width=0.6\columnwidth]{onebound}
			\caption{The dynein model in the one bound state } 
		\end{figure}

		\noindent Here $\ell_S, \ell_T$ are fixed stalk and tail lengths. We have chosen the angles $\{\theta_i\}$ as they are the most convenient and lead to a description of the position of each domain that requires only one angle and an adjacent position, that is
		\begin{align}
		x's \quad &\begin{cases}
		x_0 = x_\text{bound} \\
		x_1 = x_0 + \ell_S \cos\theta_0 \\
		x_2 = x_1 + \ell_T \cos\theta_1 \\
		x_3 = x_2 + \ell_T \cos(\pi-\theta_3) = x_2 - \ell_T\cos\theta_3 \\
		x_4 = x_3 + \ell_S \cos(\pi-\theta_4) = x_3 - \ell_S\cos\theta_4
		\end{cases} \\
		y's \quad &\begin{cases}
		y_0 = 0 \\
		y_1 = y_0 + \ell_S\sin\theta_0 \\
		y_2 = y_1 + \ell_T\sin\theta_1 \\
		y_3 = y_2 - \ell_T\sin\theta_3 \\
		y_4 = y_3 - \ell_S\sin\theta_4 
		\end{cases}
		\end{align}

		\noindent Because equation (2) relates the forces on each domain to its velocity we need the time derivative of the above equations. 
		\begin{equation}
		\dot{x}'s \quad \begin{cases}
		\dot{x}_0 = 0 \\
		\dot{x}_1 = \dot{x}_0-\ell_S\sin\theta_0 \dot{\theta}_0 \\
		\dot{x}_2 = \dot{x}_1-\ell_T\sin\theta_1 \dot{\theta}_1 \\
		\dot{x}_3 = \dot{x}_2+\ell_T\sin\theta_3 \dot{\theta}_3 \\
		\dot{x}_4 = \dot{x}_3+\ell_S\sin\theta_4 \dot{\theta}_4
		\end{cases} \\
		\end{equation}
		\begin{equation}
		\dot{y}'s \quad \begin{cases}
		\dot{y}_0 = 0 \\
		\dot{y}_1 = \dot{y}_0 + \ell_S\cos\theta_0\dot{\theta}_0 \\
		\dot{y}_2 = \dot{y}_1 + \ell_T\cos\theta_1\dot{\theta}_1 \\
		\dot{y}_3 = \dot{y}_2 - \ell_T\cos\theta_3\dot{\theta}_3 \\
		\dot{y}_4 = \dot{y}_3 - \ell_S\cos\theta_4\dot{\theta}_4
		\end{cases} 
		\end{equation}

		\subsubsection{The both bound state}
		\subsubsection{Calculating Forces and Torques}
			Here I will discuss in detail how we calculate the forces and show how this is done in code 
	\subsection{The Code}
		\subsubsection{The Random Force}
\section{Testing the model} 
	\subsection{Sanity Checks}
	This sub section will be for the various methods we used to ensure our model is behaving reasonably 
		\subsubsection{Verifying size of time step} 
		Here I will talk about how we found autocorrelations functions for each domain energy at various values of dt in order to verify our time step is as large as can be
		\subsubsection{Energy conservation and the Equipartion theorem} 
		talk about code to check that we satisfy energy 
	\subsection{Fitting to other studies}

### 2019-01-22 papers/waczak-thesis/thesis/thesis.tex
updates to thesis

@@
-\documentclass[a4paper, 11pt]{article}
-\usepackage{geometry}
-\geometry{letterpaper, margin=1in}
+\documentclass[12pt]{report}
+\usepackage{graphicx} % make it easy to load in images
+\graphicspath{{./images/}} % where to find images
+\usepackage[a4paper, margin=1in]{geometry} % change margins 
+\usepackage{fancyhdr} % add a header / footer 
+\pagestyle{fancy}
+
 \usepackage{amsmath}
@@
 \usepackage{ulem}
-\usepackage{graphicx}
-\usepackage{enumitem} % use for making lettered list 
-\usepackage{subfig} 
-\graphicspath{ {images/} }
-\usepackage{titletoc}
 
-\title{Simulating the Brownian Dynamics of a Two-Dimensional Model for the Dynein Motor Protein}
+\usepackage{caption}  % for creating simple subfigures
+\usepackage{subcaption}
+\title{
+	{Simulating the Brownian Dynamics of a Two-Dimensional Model for the Dynein Motor Protein}\vspace{1.5em}\\
+	\includegraphics[width=0.5\columnwidth]{OSU_logo.png}\vspace{0.5em}\\
+	\large{Oregon State University}
+}
 \author{John Waczak}
@@
 	\maketitle
-\newpage
+
+	\chapter*{Abstract}
+	test
+	\chapter*{Acknowledgments}
+	I want to thank ...
+
 	\tableofcontents
-\newpage
 
-\section{Introduction}
-	\subsection{Cellular Processes}
-		\subsubsection{The Cytoskeleton}
-		\subsubsection{Mitosis} 
-	\subsection{Motor Proteins}
-\subsection{Dynein}
-	\subsubsection{Directed Motion}
-	\subsubsection{Drunken Walking}
-	\subsubsection{Transporting Cargo}
-	\subsubsection{Experimental Stepping Statistics}
-
-\section{The Model} 
-	\subsection{Brownian Motion}
-	\subsection{A Simplified Model for Dynein}
-	\subsection{Equations of Motion}
-		\subsubsection{The one bound state}
-		\subsubsection{The both bound state}
-		\subsubsection{Calculating Forces and Torques}
-	\subsection{The Code}
-
-\section{Results}
-	\subsection{Model Tests}
-		\subsubsection{Determining an Appropriate dt}
-		\subsubsection{Conservation of Energy}
-	\subsection{Parameter Fitting}
-	\subsection{Model Stepping Statistics}
-	\subsection{Simulating External Forces}
-
-\section{Discussion}
-	\subsection{Comparison to Experimental Results}
-	\subsection{Consequences of the Simple Model}
-		\subsubsection{Do we need a Two State Model?}
-		test text 
-\section{Conclusions}
-	\subsection{Summary}
-	\subsection{Future Work}
-		\subsubsection{Simulating Multiple Dynein}
-		\subsubsection{Forces on the Binding Domain} 
-		\vspace{2em}
-		\textbf{NOTE: I still need to figure out how to organize the information I already wrote within the sections of the introduction I list in the table of contents.}\\
-
-		The dynein motor protein is a unique molecule among the family of motor proteins.
-Unrelated to similar motors of the kinesin family, dynein consists of heavy chains which include a large motor domain \cite{alberts_molecular_2002}.
-Dynein’s cellular environment means that the it is constantly bombarded by water molecules which impart random pushes to the protein.
-The resulting kinematics are called Brownian dynamics.
-Dynein has a mass on the order of 1 MDa whereas other motors like kinesin are of the scale of a few hundred kDa \cite{johnson_structure_1983}.
-This exaggerates the effects of the Brownian forces on dynein and has led the motor to be dubbed  as the “drunken-walker” due its tendency to take steps forward, backwards, diagonally, and in no particular order.
-The many forms of dynein play critical roles in everything from cell division to the movement of flagella.
-Its occasional mutation can lead to critical cell malfunctions and has even been linked to neurodegenerative diseases \cite{cleary_tension_2014}.
-
-		To date, research on the protein has investigated the chemical cycle required for dynein to convert ATP into usable mechanical energy \cite{cianfrocco_mechanism_2015}.
-Other studies have tested the extent to which mechanical information is stored between the legs of the protein, that is, how much previous steps and the steps of opposite legs affect future stepping behavior \cite{puls_mutant_2003}.
-Somehow, despite all of this investigation, there is no accepted model that explains the motion of this system as a physical object moving through space.
-Through direct simulation of the Brownian dynamics on a simplified two-dimensional structure, we propose a physical model for the movement of dynein that can replicate many of its famous behaviors including the drunken walk.
-Individual domains are allowed to pass through one another to account for the truly 3-dimensional structure.
-During each time step of the simulation, a random diffusive force is applied to each domain as well as a restorative torque that pushes the domains towards an equilibrium angle.
-
-		\newpage
-
-		\begin{figure}[!hbt]
-			\centering
-			\includegraphics[width=0.65\columnwidth]{paper_trajectory_plot}
-			\caption{Horizontal(x) and vertical(y) projections for the binding domain as a function of time.
-Between each image we show a cartoon of dynein illustrating its configuration corresponding to the black marker in each graph}
-			\label{fig:trajectory}
-		\end{figure}
-
-		In figure \ref{fig:trajectory} we can see the horizontal and vertical projections for the dynein motor protein throughout a simulation.
-From this graph we can make a number of interesting conclusions.
-First, we can clearly see the stepping behavior: while one foot (say red) is chaotically diffusing, the other (blue) is fixed on the microtubule.
-Furthermore, the x-projection graph demonstrates that the motor is, on average, forward directed.
-Interestingly, the cartoons show that the model assumes a wide range of configurations throughout the simulation.
-Neither the hind-leg nor human leg shape appears to be preferred.
-
-		\noindent\textbf{NOTE2: Need to fix bibliography style in latex to match the physical review letters style}
+	\chapter{Introduction}
+	\input{./chapters/introduction}
+	\chapter{Dynein}
+	\input{./chapters/dynein}
+	\chapter{Methods}
+	\input{./chapters/methods}
 

### 2019-01-29 papers/waczak-thesis/thesis/chapters/introduction.tex
more thesis stuff

@@
-\section{Cellular Processes}
-	\subsection{The Cytoskeleton}
-	\subsection{Mitosis} 
-\section{Motor Proteins}
+\textbf{NOTE:} Empty brackets [] indicate fields where I intend to add references. \\
+
+The cell is the basic structural component for all life on Earth.
+Each is comprised of a cocktail of complicated molecules that when working together enable these small units to perform their many biological functions-- often in collections, but also as individuals.
+Most cells must be magnified tens or hundreds of times just to be seen.
+How then do the constituent components of cells maneuver through their environment with only their aqueous surroundings and a slew of proteins at their disposal?
+As cells replicate, how do the newly copied parts find their way to opposite sides of the cell before it finally divides?
+
+The answer lies in part with motor proteins.
+Within each cell there is a vast network of interweaving protein filaments called the cytoskeleton that functions as a system of  highways to a particular class of proteins that have evolved to tackle the problem of cellular transport.
+These \textit{motor proteins} move along the cytoplasm by converting chemical energy into mechanical work through the hydrolysis of Adenosine triphosphate (ATP).
+
+Why should we study motor proteins and why should this interest a physicist?
+To answer first question we need only consider the vast array of cellular processes in which motor proteins are critically involved.
+Among these include muscle contraction, axonal transprot, mitosis, meiosis, and the movement of flagella to name a few \cite{}.
+When motor proteins fail, these fundamental processes are jeopardized and can result in disease\cite{hirokawa_biochemical_2003}.
+Therefore, understanding the workings of motor proteins is vital if we are to understand how and why they fail.
+
+The answer to the second question is a little more complicated.
+Naturally, one might wonder at how such small motors can be studied in the laboratory.
+Kinesin and Dynein have masses of a few hundred kDa and  $\sim2$ MDa respectively \cite{liao_kinesin_1998, johnson_structure_1983}.
+Recalling that 1 Dalton (Da) corresponds to one atomic mass unit means these proteins consist of, at most, a few million atoms.
+This small scale poses a unique experimental challenge.
+One way this is approached here at OSU by Prof.
+Weihong Qiu's group is by attaching small fluorescent beads called fluorophores to the binding sites that motor proteins use to grab on to their cargo.
+Then, the individual movement of motors is tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in figure \ref{fig:weihong tirf} from \cite{qiu_dynein_2012}.
+
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[width=0.25\columnwidth]{weihong_motor}
+	\caption{\textbf{TIRF Microscopy Imaging} individual kinesin proteins are imaged as small green dots and tracked as they move.
+Slices at different times are stacked so that the slope of each green line indicates the velocity of the protein.
+Taken from \cite{qiu_dynein_2012}.}
+	\label{fig:weihong tirf}
+\end{figure}
+
+My interest lies in how these motor proteins move as physical objects through space.
+Remarkably, life has evolved to make use of three primary motor proteins: myosin, kinesin, and dynein; all perform similar but slightly varied functions.
+This thesis is concerned specifically with dynein-- a protein unique not only for its status as the largest of the motor proteins, but also for its unique motion as drunken walker.
+In this thesis I continue the analysis of a proposed model for the motion of dynein along the microtublule.

### 2019-02-13 papers/paper/paper.tex
Add capability to make the model/experimental stacked histogram plot for initial vs final displacement to make_all_stepping_plots.py.

@@
   \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
-  \caption{\textbf{Analysis of stepping independence.} Heatmap of MTBD displacement before and after a stepping cycle.
+  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}\\
+  \includegraphics[width=\linewidth]{../../plots/stacked_displacement_histogram.pdf}
+  \caption{\textbf{Analysis of stepping independence.} \textbf{a.)} Heatmap of MTBD displacement before and after a stepping cycle.
 Displacement defined as the unbinding MTBD's x coordinate minus the stationary MTBD's x coordinate, calculated before and after the step.
-Structure in the heat map suggests steps are not independent, but rather that correlation exists between starting position and step size.}
+Structure in the heat map suggests steps are not independent, but rather that correlation exists between starting position and step size.
+\textbf{b.)} Compound histogram of final displacement for different ranges of initial displacement.}
 \label{fig:independence}

### 2019-02-13 papers/waczak-thesis/thesis/chapters/methods.tex

@@
-\section{Theory}
-Now that I have established some facts about motor proteins as well as specifics about dynein's many odd behaviors, we may begin our discussion of how to construct and test a physical model for its motion.
-First, we note that dynein's large mass of roughly 2MDa \cite{johnson_structure_1983} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao_kinesin_1998} exaggerates the effect of interactions with the  aqueous environment of the cell.
-This results in a much more significant drag force as well as a random element from water molecule collisions that changes the overall dynamics of the system.
-The set of equations governing this motion is called Brownian dynamics and is what we use to simulate the trajectory of dynein along the microtubule.
-	\subsection{Brownian dynamics}
-	To model dynein we treat its various domains (binding, motor, and tail) as spheres held together by massless rigid-rods.
-In general, the dynamics of a constant mass particle are governed by Newton's second law
-	\begin{equation}
-		\sum_i \mathbf{F}_i = \dot{\mathbf{p}} = m\ddot{\mathbf{x}}
-	\end{equation}
-	Thus, determining the dynamics of a system boils down to describing the various forces which act upon it and then solving the resulting differential equation.
-For particles in a solvent, there are three important forces to consider.
-The first is linear drag, which we write as
-	\begin{equation}
-		F_\text{drag} = -\gamma\dot{\mathbf{x}}
-	\end{equation}
-	where $\gamma$ is the constant of proportionality. For a spherical particle of radius $a$ moving through a solvent with liquid viscosity $\eta$ this was derived by Stoke to be 
-	\begin{equation}
-		\gamma = 6\pi\eta a
-	\end{equation}
-
-	The second characteristic force of Brownian dynamics is a random force due to density fluctuations in the solvent which we denote $F_\text{rand}$.
-Finally, might also consider how individual particles interact with each other.
-For us, this will be accomplished through the rigid rods that outline the structure of the protein.
-Putting all of these forces together results in what is often called the \textit{Langevin Equation}.
-	\begin{equation}
-		m\ddot{\mathbf{x}} + \gamma\dot{\mathbf{x}}+\mathbf{F}_\text{rand} = 0 
-	\end{equation}
-
-	If we assume further that $|\gamma\dot{\mathbf{x}}|\gg |m\ddot{\mathbf{x}}|$, or in other words, we take the limit of strong drag, then we arrive at the definition of Brownian Dynamics.
-This allows us to neglect the acceleration term resulting in the following differential equation:
-	\begin{equation}
-		\dot{\mathbf{x}} = \frac{1}{\gamma}\left( \mathbf{F}_\text{interact} + \mathbf{F}_\text{rand} \right)
-	\end{equation}
-	To complete the model, we must specify how we calculate and apply the random force as well as the force due to the interactions between domains.
-
-	\subsection{A Simplified Model for Dynein}
-	As previously mentioned, we model dynein as a system of spherical domains held together by massless rigid-rods with the whole system moving according to Brownian Dynamics.
-The random forces on each domain are responsible for diffusing the system and creating the chaotic motion, but in order to have dynein prefer one side of the microtubule on average (as is the case for real dynein) we need to impose some \textit{extra} structure on the protein.
-
-	To do this we steer each domain towards an equilibrium configuration by a Hooke's law restorative torque of the following form
-	\begin{equation}
-		\Gamma_i = c_i\left(\phi_i-\phi_{i,\text{eq}}\right)
-	\end{equation}
-	where the $c_i$ are spring constants (a free parameter of the model) and the set $\{\phi_i\}$ are the angles measured between the $i-1$ and $i+1$ domains.
-Note that for binding domains this angle may be measured to the microtubule or not measured if the domain is unbound from the microtubule.
-The angles $\{\phi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}
-
-	\begin{figure}[hbt!]
-		\centering
-		\includegraphics[angle=-90, width=0.75\columnwidth]{torque_angles}
-		\caption{Example of dynein in the onebound configuration with torque angles $\{\phi_i\}$ shown.
-\textbf{NOTE: double check w/ David on how we select the angles e.g.
-do we take min of the two possible angles?
-How do we define the equilibrium angles?}}
-		\label{fig:torque angles}
-	\end{figure}
-
-	\subsection{Determining constants of the model}
-	I will insert discussion here about how we determined rod lengths and equilibrium angles from microscopy images. \\
-
-	\begin{figure}[hbt!]
-		\centering
-		\includegraphics[width=0.3\columnwidth]{schematic-2-superimposed}
-		\caption{Our model superimposed over microscopy image of Dynein \textbf{NOTE: add source} for determining lengths and equilibrium angles} 
-		\label{fig:superimpmosed}
-	\end{figure}
-	\subsection{Equations of Motion}
-	This is where I will discuss how we calculate the equations of motion for our two states-- One bound and both bound as well as how we algorithmically determine the interaction forces from the torques.
-
-		\subsubsection{The one bound state}
-		The following figure shows the model in the one bound configuration.\\
-		\begin{figure}[!hbt]
-			\centering
-			\includegraphics[width=0.6\columnwidth]{onebound}
-			\caption{The dynein model in the one bound state } 
-		\end{figure}
-
-		\noindent Here $\ell_S, \ell_T$ are fixed stalk and tail lengths.
-We have chosen the angles $\{\theta_i\}$ as they are the most convenient and lead to a description of the position of each domain that requires only one angle and an adjacent position, that is
-		\begin{align}
-		x's \quad &\begin{cases}
-		x_0 = x_\text{bound} \\
-		x_1 = x_0 + \ell_S \cos\theta_0 \\
-		x_2 = x_1 + \ell_T \cos\theta_1 \\
-		x_3 = x_2 + \ell_T \cos(\pi-\theta_3) = x_2 - \ell_T\cos\theta_3 \\
-		x_4 = x_3 + \ell_S \cos(\pi-\theta_4) = x_3 - \ell_S\cos\theta_4
-		\end{cases} \\
-		y's \quad &\begin{cases}
-		y_0 = 0 \\
-		y_1 = y_0 + \ell_S\sin\theta_0 \\
-		y_2 = y_1 + \ell_T\sin\theta_1 \\
-		y_3 = y_2 - \ell_T\sin\theta_3 \\
-		y_4 = y_3 - \ell_S\sin\theta_4 
-		\end{cases}
-		\end{align}
-
-		\noindent Because equation (2) relates the forces on each domain to its velocity we need the time derivative of the above equations. 
-		\begin{equation}
-		\dot{x}'s \quad \begin{cases}
-		\dot{x}_0 = 0 \\
-		\dot{x}_1 = \dot{x}_0-\ell_S\sin\theta_0 \dot{\theta}_0 \\
-		\dot{x}_2 = \dot{x}_1-\ell_T\sin\theta_1 \dot{\theta}_1 \\
-		\dot{x}_3 = \dot{x}_2+\ell_T\sin\theta_3 \dot{\theta}_3 \\
-		\dot{x}_4 = \dot{x}_3+\ell_S\sin\theta_4 \dot{\theta}_4
-		\end{cases} \\
-		\end{equation}
-		\begin{equation}
-		\dot{y}'s \quad \begin{cases}
-		\dot{y}_0 = 0 \\
-		\dot{y}_1 = \dot{y}_0 + \ell_S\cos\theta_0\dot{\theta}_0 \\
-		\dot{y}_2 = \dot{y}_1 + \ell_T\cos\theta_1\dot{\theta}_1 \\
-		\dot{y}_3 = \dot{y}_2 - \ell_T\cos\theta_3\dot{\theta}_3 \\
-		\dot{y}_4 = \dot{y}_3 - \ell_S\cos\theta_4\dot{\theta}_4
-		\end{cases} 
-		\end{equation}
-
-		\subsubsection{The both bound state}
-		\subsubsection{Calculating Forces and Torques}
-			Here I will discuss in detail how we calculate the forces and show how this is done in code 
-	\subsection{The Code}
-		\subsubsection{The Random Force}
 \section{Testing the model} 

### 2019-02-13 papers/waczak-thesis/thesis/chapters/theory.tex

Now that I have established some facts about motor proteins as well as specifics about dynein's many odd behaviors, we may begin our discussion of how to construct and test a physical model for its motion. First, we note that dynein's large mass of roughly 2MDa \cite{johnson_structure_1983} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao_kinesin_1998} exaggerates the effect of interactions with the  aqueous environment of the cell. This results in a much more significant drag force as well as a random element from water molecule collisions that changes the overall dynamics of the system. The set of equations governing this motion is called Brownian dynamics and is what we use to simulate the trajectory of dynein along the microtubule. 
	\section{Brownian dynamics}
	To model dynein we treat its various domains (binding, motor, and tail) as spheres held together by massless rigid-rods. In general, the dynamics of a constant mass particle are governed by Newton's second law
	\begin{equation}
		\sum_i \mathbf{F}_i = \dot{\mathbf{p}} = m\ddot{\mathbf{x}}
	\end{equation}
	Thus, determining the dynamics of a system boils down to describing the various forces which act upon it and then solving the resulting differential equation for some set of initial conditions. For particles in a solvent, there are three important forces to consider. The first is linear drag, which we write as 
	\begin{equation}
		F_\text{drag} = -\gamma\dot{\mathbf{x}}
	\end{equation}
	so that the force is proportional to the velocity by a factor $\gamma$s. For a spherical particle of radius $a$ moving through a solvent with liquid viscosity $\eta$ this was derived by Stoke to be 
	\begin{equation}
		\gamma = 6\pi\eta a
	\end{equation}

	The second characteristic force of Brownian dynamics is a random force due to density fluctuations in the solvent which we denote $F_\text{rand}$. Finally, we might also consider how individual particles interact with each other through some interaction force. For us, this will be accomplished through the rigid rods that outline the structure of the protein by fixing the inter-domain distances via tension. Putting all of these forces together results in what is often called the \textit{Langevin Equation}.
	\begin{equation}
		 -\gamma\dot{\mathbf{x}}+\mathbf{F}_\text{rand} + \mathbf{F}_\text{interact} = m\ddot{\mathbf{x}} 
	\end{equation}

	If we assume further that $|\gamma\dot{\mathbf{x}}|\gg |m\ddot{\mathbf{x}}|$, or in other words, we take the limit of strong drag, then we arrive at the definition of Brownian Dynamics. This allows us to neglect the acceleration term resulting in the following differential equation:
	\begin{equation}
		\dot{\mathbf{x}} = \frac{1}{\gamma}\left( \mathbf{F}_\text{interact} + \mathbf{F}_\text{rand} \right)
	\end{equation}
	We must now solve the above for equations of motion.

	\section{A Simplified Model for Dynein}
	As mentioned, we model dynein as a system of spherical domains held together by massless rigid-rods with the whole system moving according to Brownian dynamics. The random forces on each domain are responsible for diffusing the system and creating the expected chaotic motion, but in order to have dynein prefer one side of the microtubule on average (as is the case for real dynein) we need to impose some \textit{extra} structure on the protein.

	\begin{figure}[hbt!]
		\centering
		\includegraphics[angle=-90, width=0.6\columnwidth]{torque_angles}
		\caption{Example of dynein in the onebound configuration with torque angles $\{\phi_i\}$ shown. \textbf{NOTE: double check w/ David on how we select the angles e.g. do we take min of the two possible angles? How do we define the equilibrium angles?}}
		\label{fig:torque angles}
	\end{figure}

	To do this we steer each domain towards an equilibrium configuration by a Hooke's law restorative torque with magnitude of the following form
	\begin{equation}
		\Gamma_i = -c_i\left(\varphi_i-\varphi_{i,\text{eq}}\right)
	\end{equation}
	Here the $c_i$ are spring constants (a free parameter of the model) and the set $\{\varphi_i\}$ are the angles measured between the $i-1$ and $i+1$ domains. Perhaps more useful is the harmonic energy associated with each torque given as 
	\begin{equation}
		U_i = \frac{1}{2}c_i(\varphi_i-\varphi_{i,\text{eq}})^2
	\end{equation} 
	Note that for binding domains this angle may be measured to the microtubule or not measured if the domain is unbound from the microtubule. The angles $\{\varphi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}. Torques are related to forces by 
	\begin{equation}
		\mathbf{\Gamma} = \mathbf{r}\times\mathbf{F}
	\end{equation}
	so that knowing the distance between each domains means that we have specified each of the $\mathbf{\Gamma}_i$ and $\mathbf{r}_i$. We desire to determine $\mathbf{F}_i$ from this information however there is no unique way to invert a cross product. Therefore we must specify an algorithm for determining the forces that result from each torque.

	\section{Equations of Motion}
	To model how dynein steps we introduce two states hereafter referred to as the one bound state and the both bound state. In the one bound state, all but one of the domains are free to diffuse whilst the last is attached to the microtubule. In the both bound state, both binding domains are attached. The slight difference in geometry between the two scenarios leads to two sets of equations for motion that differ slightly. The following section details their derivation.

		\subsection{The one bound state}
		Figure \ref{fig:one bound} illustrates dynein in the one bound state with new angles $\{\theta_i\}$ chosen for convenience of calculation and computation.\\
		\begin{figure}[!hbt]
			\centering
			\includegraphics[angle=-90,width=0.75\columnwidth]{onebound}
			\caption{The dynein model in the one bound state }
			\label{fig:one bound}  
		\end{figure}

		\noindent Here $\ell_S, \ell_T$ are fixed stalk and tail lengths. With some simple trigonometry, the positions of each domain are given by
		\begin{align}
		x's \quad &\begin{cases}
		x_0 = x_\text{bound} \\
		x_1 = x_0 + \ell_S \cos\theta_0 \\
		x_2 = x_1 + \ell_T \cos\theta_1 \\
		x_3 = x_2 + \ell_T \cos(\pi-\theta_3) = x_2 - \ell_T\cos\theta_3 \\
		x_4 = x_3 + \ell_S \cos(\pi-\theta_4) = x_3 - \ell_S\cos\theta_4
		\end{cases} &
		y's \quad &\begin{cases}
		y_0 = 0 \\
		y_1 = y_0 + \ell_S\sin\theta_0 \\
		y_2 = y_1 + \ell_T\sin\theta_1 \\
		y_3 = y_2 - \ell_T\sin\theta_3 \\
		y_4 = y_3 - \ell_S\sin\theta_4 
		\end{cases}
		\end{align}

		\noindent Because equation (3.5) relates the forces on each domain to its velocity we need the time derivative of the above equations. 
		\begin{align}
		\dot{x}'s \quad \begin{cases}
		\dot{x}_0 = 0 \\
		\dot{x}_1 = \dot{x}_0-\ell_S\sin\theta_0 \dot{\theta}_0 \\
		\dot{x}_2 = \dot{x}_1-\ell_T\sin\theta_1 \dot{\theta}_1 \\
		\dot{x}_3 = \dot{x}_2+\ell_T\sin\theta_3 \dot{\theta}_3 \\
		\dot{x}_4 = \dot{x}_3+\ell_S\sin\theta_4 \dot{\theta}_4
		\end{cases} &
		\dot{y}'s \quad \begin{cases}
		\dot{y}_0 = 0 \\
		\dot{y}_1 = \dot{y}_0 + \ell_S\cos\theta_0\dot{\theta}_0 \\
		\dot{y}_2 = \dot{y}_1 + \ell_T\cos\theta_1\dot{\theta}_1 \\
		\dot{y}_3 = \dot{y}_2 - \ell_T\cos\theta_3\dot{\theta}_3 \\
		\dot{y}_4 = \dot{y}_3 - \ell_S\cos\theta_4\dot{\theta}_4
		\end{cases} 
		\end{align}

		The Brownian motion equation (3.5) also defines the velocity on domain.

		\section{The both bound state}
		\section{Calculating Forces and Torques}
			Here I will discuss in detail how we calculate the forces and show how this is done in code 
		\section{Determining constants of the model}
		The stalk and tail lengths $\ell_S, \ell_T$ as well as a set of equilibrium angles $\{\varphi_{i,\text{eq}}\}$ were determined by examining microscopy images of dynein in various configurations. 
		\begin{figure}[hbt!]
			\centering
			\includegraphics[width=0.3\columnwidth]{schematic-2-superimposed}
			\caption{Our model superimposed over microscopy image of Dynein \textbf{NOTE: add source} for determining lengths and equilibrium angles} 
			\label{fig:superimpmosed}
		\end{figure}
	\section{The Code}
		\subsection{The Random Force}

### 2019-02-22 papers/waczak-thesis/thesis/chapters/introduction.tex
thesis updates
thesis update

--- 2019-01-22 papers/waczak-thesis/thesis/chapters/introduction.tex
@@
-\section{Cellular Processes}
-	\subsection{The Cytoskeleton}
-	\subsection{Mitosis} 
-\section{Motor Proteins}
+Cells are the fundamental unit for all life on Earth. In order
+for them to perform their biological tasks, the complex structures they contain
+must be able to replicate and move within their aqueous environment. This
+transport problem  poses a unique challenge as diffusion alone is far to slow,
+and random, a process to be able to produce movement on cellular timescales[].
+Nature's solution to this problem is twofold.
+Within each cell there is a vast network of interweaving filaments called the \textit{cytoskeleton} that spans the gaps between the substructures of the cell.
+This cytoskeleton serves as a highway to a class of proteins called \textit{molecular motors} which can be distinguished into three types: kinesin, myosin, and dynein.
+Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing Adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work\cite{alberts_molecular_2002}.
+Correct operation of these motors results in processes such as cell division, muscle contraction, and axonal transport; failure can lead to debilitating diseases such as ALS \cite{boillee_als:_2006}.
+
+\begin{figure}[!hbt]
+	\centering 
+	\includegraphics[width=0.5\columnwidth]{motor_comparison}
+	\caption{Comparison of the three primary motor proteins (from left to right): myosin, kinesin, dynein. Image taken from \cite{philips__nodate}.}
+	\label{fig:motor proteins} 
+\end{figure}
+
+Astonishingly, each of these motors is composed of two legs that combine to form a bipedal structure (see figure \ref{fig:motor proteins}).
+that steps like a human as it moves along the cytoskeleton.
+Myosin and kinesin behave like a normal person; their steps alternate between opposing domains.
+This motion is called \textit{hand over hand} stepping \cite{noauthor_drunk_nodate}.
+Dynein, however, is unique in its motion as it takes hand-over-hand steps but also \textit{inchworms} meaning that it often steps twice with the same foot.
+Furthermore, dynein even takes frequent backwards steps as shown in the stepping histogram in figure \ref{fig:weihong histogram} \cite{qiu_dynein_2012}.
+Collectively this behavior has earned dynein the title of \textit{drunken walker} which compactly summarizes its peculiar tendencies \cite{noauthor_drunk_nodate}.
+\\
+
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[width=0.5\columnwidth]{weihong_histogram}
+	\caption{Stepping histogram showing the distribution of step sizes for \textit{in vitro} dynein.
+1-D data corresponds to the projection of the step along the axis of the microtubule.
+2-D data corresponds to the total step size over the two-dimensional structure.
+Figure taken form \cite{qiu_dynein_2012}.}
+	\label{fig:weihong histogram} 
+\end{figure}
+
+This unique stepping behavior makes dynein an interesting subject to study.
+There have been significant efforts aimed at characterizing the complex, multi-phase chemical cycle involved in the hydrolysis of ATP\cite{cianfrocco_mechanism_2015}.
+However, the dynamics of dynein's physical motion through space remains an open question.
+In this thesis, we examine a simplified physical model for the motion of dynein using Brownian dynamics.
+By simulating this model, we demonstrate it's ability to replicate of many observed properties of the protein.
+We will also use the model to comment a proposed mechanism for how dynein generates most of its movement, namely the powerstroke model.

### 2019-02-22 papers/waczak-thesis/thesis/chapters/theory.tex
thesis update

@@
 	Thus, determining the dynamics of a system boils down to describing the various forces which act upon it and then solving the resulting differential equation for some set of initial conditions.
-For particles in a solvent, there are three important forces to consider.
+For small particles in a solvent, there are three important forces to consider.
 The first is linear drag, which we write as
@@
 	\end{equation}
-	so that the force is proportional to the velocity by a factor $\gamma$s. For a spherical particle of radius $a$ moving through a solvent with liquid viscosity $\eta$ this was derived by Stoke to be 
+	so that the drag force is proportional to the velocity by a factor $\gamma$.
+For a spherical particle of radius $a$ moving through a solvent with liquid viscosity $\eta$ this was derived by Stoke to be
 	\begin{equation}
@@
 	If we assume further that $|\gamma\dot{\mathbf{x}}|\gg |m\ddot{\mathbf{x}}|$, or in other words, we take the limit of strong drag, then we arrive at the definition of Brownian Dynamics.
-This allows us to neglect the acceleration term resulting in the following differential equation:
+This allows us to neglect the acceleration term resulting in the following differential equation
 	\begin{equation}
@@
 	\end{equation}
-	We must now solve the above for equations of motion.
+	which we must now solve for the equations of motion of our model.
 
@@
 	As mentioned, we model dynein as a system of spherical domains held together by massless rigid-rods with the whole system moving according to Brownian dynamics.
-The random forces on each domain are responsible for diffusing the system and creating the expected chaotic motion, but in order to have dynein prefer one side of the microtubule on average (as is the case for real dynein) we need to impose some \textit{extra} structure on the protein.
+The random forces on each domain are responsible for diffusing the system and creating the expected chaotic motion, but in order to have dynein prefer walking towards one side of the microtubule, as is the case for real dynein, we need to impose some \textit{extra} structure on the protein.
 
@@
 		\includegraphics[angle=-90, width=0.6\columnwidth]{torque_angles}
-		\caption{Example of dynein in the onebound configuration with torque angles $\{\phi_i\}$ shown.
-\textbf{NOTE: double check w/ David on how we select the angles e.g.
-do we take min of the two possible angles?
-How do we define the equilibrium angles?}}
+		\caption{Example of dynein in the one bound configuration with torque angles $\{\varphi_i\}$ shown.}
 		\label{fig:torque angles}
@@
 	Here the $c_i$ are spring constants (a free parameter of the model) and the set $\{\varphi_i\}$ are the angles measured between the $i-1$ and $i+1$ domains.
-Perhaps more useful is the harmonic energy associated with each torque given as
+Equally useful is the harmonic energy associated with each torque.
+These are given by
 	\begin{equation}
@@
 	\end{equation}
-	Note that for binding domains this angle may be measured to the microtubule or not measured if the domain is unbound from the microtubule.
-The angles $\{\varphi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}.
-Torques are related to forces by
+
+	Real dynein is composed of a pair of identical heavy chains.
+Therefore, our angle convention is chosen starting at the $0^{th}$ domain in figure \ref{fig:torque angles}.
+The same convention is then repeated for the second leg with the following correspondence
+	\begin{align}
+		\varphi_{0,eq} &\longleftrightarrow \varphi_{4,eq} \\ 
+		\varphi_{1,eq} &\longleftrightarrow \varphi_{3,eq}
+	\end{align}
+	where the angles $\{\varphi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}. The torques on each domain are related to forces by 
 	\begin{equation}
@@
 	so that knowing the distance between each domains means that we have specified each of the $\mathbf{\Gamma}_i$ and $\mathbf{r}_i$.
-We desire to determine $\mathbf{F}_i$ from this information however there is no unique way to invert a cross product.
-Therefore we must specify an algorithm for determining the forces that result from each torque.
+In order to dynamically move each domain we must invert equation 4.10 to determine $\mathbf{F}_i$, however there is no unique way to invert such a cross product.
+Therefore, we must specify an algorithm for determining the forces that result from each torque.
+
+	\section{Calculating Forces and Torques}
+	Here I will discuss in detail how we calculate the forces and show how this is done in code
 
 	\section{Equations of Motion}
-	To model how dynein steps we introduce two states hereafter referred to as the one bound state and the both bound state.
-In the one bound state, all but one of the domains are free to diffuse whilst the last is attached to the microtubule.
+	Now that we have specified the forces, the dynamics of each domain are determined by equation 4.5 so that in order to simulate the complicated structure we must solve a system of coupled first order differential equations.
+In doing so, it is convenient to introduce two states to distinguish between dynein's stepping and when both of its binding domains are attached to the microtubule.
+We shall refer to these configurations hereafter as the one bound state and the both bound state.
+
+	In the one bound state, all but one of the domains are free to diffuse while the last is attached to the microtubule.
 In the both bound state, both binding domains are attached.
-The slight difference in geometry between the two scenarios leads to two sets of equations for motion that differ slightly.
-The following section details their derivation.
+This slight difference in geometry between the two scenarios leads to two sets of equations for motion that differ slightly.
+The following section details the derivation of these equations of motion.
 
@@
 
-		\section{The both bound state}
-		\section{Calculating Forces and Torques}
-			Here I will discuss in detail how we calculate the forces and show how this is done in code 
+		\subsection{The both bound state}
+
 		\section{Determining constants of the model}

### 2019-03-08 papers/waczak-thesis/thesis/chapters/dynein.tex
more thesis stuff

@@
-\section{Directed Motion}
-\section{Drunken Walking}
-\section{Transporting Cargo}
-\section{Experimental Stepping Statistics}
+\section{The microtubule}
+I am going to add more description of the microtubule here. \\
+
+Dynein walks along a particular cyctoskeleton filament called a microtubule which has an inherent structural polarity identified as the plus ($+$) and minus ($-$) ends \cite{lodish_microtubule_2000}.
+Most(not all) variations of the kinesin molecular motor are plus-end directed whereas dynein is only minus-end directed \cite{alberts_molecular_2002}.
+\\
+
+I intend to discuss how our model may elucidate why dynein is specifically directed towards the minus end.
+
+\section{The powerstroke model} 
+Here I will talk about the powerstroke vs winch mechanism debate.
+
+\section{Observations \textit{in vitro}} 
+Here I will talk about how single-molecule observations are made as well as their limitations (e.g. can't observe stutter steps of $0$ $nm$.) \\\\
+
+Naturally, one might wonder at how such small motors can be studied in the laboratory.
+Kinesin and Dynein have masses of a few hundred kDa and  $\sim2$ MDa respectively \cite{liao_kinesin_1998, johnson_structure_1983}.
+Recalling that 1 Dalton (Da) corresponds to one atomic mass unit means these proteins consist of, at most, a few million atoms.
+This small scale poses a unique experimental challenge.
+One way this is approached at OSU by Prof.
+Weihong Qiu's group is by attaching small fluorescent molecules called fluorophores to the binding sites that motor proteins use to latch onto their cargo.
+Then, the individual movement of motors is tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in figure \ref{fig:weihong tirf} from \cite{qiu_dynein_2012}.
+
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[angle=90, width=0.75\columnwidth]{weihong_motor}
+	\caption{\textbf{TIRF Microscopy Imaging} individual kinesin proteins are imaged as small green dots and tracked as they move.
+Slices at different times are stacked so that the slope of each green line indicates the velocity of the protein.
+Image taken from \cite{qiu_dynein_2012}.}
+	\label{fig:weihong tirf}
+\end{figure}
+
+Although the individual binding domains of the molecule can not be resolved, 
+\section{Transporting cargo}
+\section{Experimental stepping statistics}
+Here I will include the various stepping statistics (distribution, binding/unbinding rates, etc...) that we hope to
+
+\section{More motivation} 
+Here I will discuss other simulation efforts that, in our opinion, make far to many assumptions or are purely monte carlo and don't actually simulate the motion of the protein.
+I will also discuss why our simulation is a happy medium between a full on molecular dynamics simulation (time expensive but accurate) and monte carlo (very fast but doesn't dynamically simulate the protein and instead just selects steps from a distribution).

### 2019-03-20 papers/waczak-thesis/thesis/chapters/dynein.tex
big thesis update

--- 2019-01-22 papers/waczak-thesis/thesis/chapters/dynein.tex
@@
-\section{Directed Motion}
-\section{Drunken Walking}
-\section{Transporting Cargo}
-\section{Experimental Stepping Statistics}
+\section{The microtubule}
+We've already mentioned that cells employ motor proteins and the cytoskeleton to solve the cellular transport problem.
+The following figure demonstrates the complexity of this network of cellular highways within endothelial cells.
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[width=0.5\columnwidth]{cytoskeleton}
+	\caption{Endothelial cells with their cytoskeleton structures shown.
+The nucleus of each cell is colored in blue.
+Actin filaments are shown in red and tubulin is shown in green.
+Image taken from \cite{cytoskeleton}}
+	\label{fig:cytoskeleton}
+\end{figure}
+
+Dynein walks along a particular cyctoskeleton filament called a microtubule.
+Microtubules are cytoskeletal structures formed by self assembly of $\alpha$ and $\beta$ tubulin heterodimers (shown as green in Figure \ref{fig:cytoskeleton}).
+\cite{downing_tubulin_1998} These molecular structures are typically comprised of 13 protofilaments each of which is a periodic arrangement of the $\alpha$ and $\beta$ dimers.
+
+Microtubules exhibit an inherent polarity identified as the plus ($+$) and minus ($-$) ends \cite{lodish_microtubule_2000}.
+This polarity is both function and structural.
+One end of the microtubule experiences much faster addition of tubulin making it easy to identify\cite{heidemann_visualization_1980}.
+For our purposes though, the structural polarity of the microtubule is more important as the formation of the microtubule results in a helical structure that has definite chirality \cite{microtubule_chirality}.
+Two possible microtubule configurations are shown in Figure \ref{fig:chirality}.
+Note that even though there is a deviation by angle $\theta$ between the two microtubules, the overall handedness of the helix is the same.
+
+\begin{figure}[!hbt]
+	\centering 
+	\includegraphics[width=.5\columnwidth]{microtubule_chirality}
+	\caption{Two possible microtubule structures illustrating the chirality of the helix as well as the skew angle of the dimers of which only one is shown for illustrative purposes.
+Image taken from \cite{microtubule_chirality}.}
+	\label{fig:chirality}
+\end{figure}
+
+As Figure \ref{fig:cytoskeleton} shows, microtubules foliate the entire cell with paths that enable motor proteins to move cargo.
+Most(not all) variations of the kinesin molecular motor are plus-end directed.
+They are almost always observed to walk towards the plus-end of the microtubule.
+Dynein is strictly a minus-end directed motor \cite{alberts_molecular_2002}.
+How this directed motion is derived from the symmetric dynein structure is still an open question.\\
+
+\section{The powerstroke model} 
+Take another look at Figure \ref{fig:motor proteins}.
+How does this complicated structure perform complex locomotion using only the resources of its aqueous environment?
+How can a highly symmetric structure lead to directed motion?
+The chemical resolution to this problem arises from the interaction of ATP with each of the motor domains of dynein.
+The cycle of converting the chemical energy of  ATP into useful mechanical energy for motion is called the \textit{mechanochemical cycle}\cite{cianfrocco_mechanism_2015}.
+Describing all of the chemical interactions involved in a single dynein step has been an active area of research.
+The currently accepted model was proposed by Cianfrocco et al.
+and is summarized in the following graphic shown in Figure \ref{fig:mechanochemical_cycle}.
+
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[width=1\columnwidth]{mechanochemical_cycle}
+	\caption{The mechanochemical cycle of dynein.
+Dynein goes through many identifiable stages as ATP from the environment interacts with the motor domain and changes the conformation of the protein.
+Image taken from \cite{cianfrocco_mechanism_2015}.}
+	\label{fig:mechanochemical_cycle}
+\end{figure}
+
+The important takeaway from Figure \ref{fig:mechanochemical_cycle} is that we can identify a ``pre-stroke" and a ``post-stroke" state corresponding to the conformational change that occurs in the purple linker between steps 7 and 8.
+These states are again illustrated in the following figure to make the physical change in shape clear.
+
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[width=1\columnwidth]{pre_post_powerstroke}
+	\caption{An illustration of the pre and post stroke states of dynein in relation to the microtubule and the cargo that they carry.
+This two-dimensional illustration shows only one of legs of dynein.
+Image taken from \cite{dynein_powerstroke}.}
+\end{figure}
+
+Scientists have determined the steps of this chemical cycle by carefully isolating and analyzing the resulting structures via cryo-electron microscopy \cite{cryo_em}.
+While this is useful for determining the conformation before and after a chemical process occurs, it does note describe the actual motion along the microtubule-- only intermittent states.
+All of the information about how flexible each domain is during binding and to what extent the protein diffuses in its search for the microtubule require alternative methods to establish.
+
+\section{Other observational techniques} 
+ Kinesin and Dynein have masses of a few hundred kDa and  $\sim2$ MDa respectively \cite{liao_kinesin_1998, johnson_structure_1983}.
+Recalling that 1 Dalton (Da) corresponds to one atomic mass unit means these proteins consist of, at most, a few million atoms.
+This small scale poses a unique experimental challenge.
+One way this is approached at Prof.
+Weihong Qiu's group is by attaching small fluorescent molecules called fluorophores to the binding sites that motor proteins use to latch onto their cargo.
+Then, the individual movement of motors can be tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in figure \ref{fig:weihong tirf} from \cite{qiu_dynein_2012}.
+
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[angle=90, width=0.75\columnwidth]{weihong_motor}
+	\caption{\textbf{TIRF Microscopy Imaging} individual kinesin proteins are imaged as small green dots and tracked as they move.
+Slices at different times are stacked so that the slope of each green line indicates the velocity of the protein.
+Image taken from \cite{qiu_dynein_2012}.}
+	\label{fig:weihong tirf}
+\end{figure}
+
+Figure \ref{fig:weihong tirf} demonstrates fluorescence microscopy enables observation of protein speed, how far it walks along the microtubule, which direction is preferred.
+Furthermore, by tagging a motor domain instead of the tail, this technique can resolve step sizes and as shown in Figure \ref{fig:weihong histogram}.
+\cite{qiu_dynein_2012} Taking into account these studies as well as the delicate cryo-em analysis forms a rough sketch for dynein's motion.
+Unfortunately though, this is the limit of current experimental methods; observing the individual motions of each of the binding domains of a dynein protein is not yet possible.
+
+\todo[inline]{TODO: Add in discussion of using gold particles + scattering to observe Brownian wiggling. This was a result of conversations with Colloquium speaker Kazuhiro Oiwa.}
+
+\section{Experimental stepping statistics}
+Here I will include the various stepping statistics (distribution, binding/unbinding rates, etc...) that we hope to fit our simulation to.
+
+\section{More motivation} 
+Here I will discuss other simulation efforts that, in our opinion, make far to many assumptions or are purely monte carlo and don't actually simulate the motion of the protein.
+I will also discuss why our simulation is a happy medium between a full on molecular dynamics simulation (time expensive but accurate) and monte carlo (very fast but doesn't dynamically simulate the protein and instead just selects steps from a distribution).

### 2019-03-20 papers/waczak-thesis/thesis/chapters/introduction.tex
big thesis update

@@
 This cytoskeleton serves as a highway to a class of proteins called \textit{molecular motors} which can be distinguished into three types: kinesin, myosin, and dynein.
-Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing Adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work\cite{alberts_molecular_2002}.
+Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work\cite{alberts_molecular_2002}.
 Correct operation of these motors results in processes such as cell division, muscle contraction, and axonal transport; failure can lead to debilitating diseases such as ALS \cite{boillee_als:_2006}.
@@
 
-Astonishingly, each of these motors is composed of two legs that combine to form a bipedal structure (see figure \ref{fig:motor proteins}).
+Astonishingly, each of these motors is composed of two legs that combine to form a bipedal structure (see Figure \ref{fig:motor proteins}).
 that steps like a human as it moves along the cytoskeleton.
@@
 This motion is called \textit{hand over hand} stepping \cite{noauthor_drunk_nodate}.
-Dynein, however, is unique in its motion as it takes hand-over-hand steps but also \textit{inchworms} meaning that it often steps twice with the same foot.
+Dynein, however, is unique in its motion as it takes hand-over-hand steps and also \textit{inchworms}.
+This alternative behavior is a scenario in which one motor consistently leads the opposite resulting in a shuffling motion.
 Furthermore, dynein even takes frequent backwards steps as shown in the stepping histogram in figure \ref{fig:weihong histogram} \cite{qiu_dynein_2012}.
@@
 There have been significant efforts aimed at characterizing the complex, multi-phase chemical cycle involved in the hydrolysis of ATP\cite{cianfrocco_mechanism_2015}.
-However, the dynamics of dynein's physical motion through space remains an open question.
+However, the dynamics of dynein's physical motion through space remains an open question as current optical techniques have difficulty resolving the individual motion of each dimer.
 In this thesis, we examine a simplified physical model for the motion of dynein using Brownian dynamics.
-By simulating this model, we demonstrate it's ability to replicate of many observed properties of the protein.
-We will also use the model to comment a proposed mechanism for how dynein generates most of its movement, namely the powerstroke model.
+By simulating this model, we demonstrate it's ability to replicate many of the observed properties of the protein.
+We will also use the model to comment a proposed mechanism for how dynein generates its movement, namely the powerstroke model.

### 2019-03-20 papers/waczak-thesis/thesis/chapters/results.tex
big thesis update

\todo[inline]{TODO: I plan to add description and section headings over break}
\todo[inline]{TODO: add discussion of powerstroke vs winch models. Discuss simple modifications to simulation parameters to try and fit for this alternate mechanochemical model}

\begin{figure}[!hbt]
	\centering
	\includegraphics[width=0.75\columnwidth]{paper_displacement_vs_step_length}
	\caption{\textbf{Two dimensional histogram} comparing the total signed step length to
			the signed initial displacement between the binding domains. A positive value
			indicates that the front foot made the step (leading). A negative value
			indicates the rear foot (lagging) made the step. Simulations show a strong,
			negative correlation. A similar fit from an experimental paper is plotted for comparison.}
\end{figure}

\begin{figure}[!hbt]
	\centering
	\includegraphics[angle=-90, width=1\columnwidth]{leading_vs_lagging}
	\caption{Diagram illustrating a leading foot step (a) and a lagging foot step (b).}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1\columnwidth]{paper_trajectory_plot}
	\caption{}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1\columnwidth]{paper_model_behavior}
	\caption{}
\end{figure}
\vspace{10em}

\todo[inline]{TODO: combine 5.1 with 5.2 to explain leading vs lagging}
\todo[inline]{TODO: consider removing leading lagging axis labels in 5.1 if redundant with figure caption} 
\todo[inline]{NOTE: it looks like there may be an issue with the middle most cartoon in 5.3. The tail does not appear to be the correct size}
\todo[inline]{TODO decrease overall width of tail in cartoon dynein. Increase thickness of stalk} 
\todo[inline]{TODO: Check to make sure time axis in final panel of fig 5.4 is actually a log scale}

### 2019-03-20 papers/waczak-thesis/thesis/chapters/theory.tex
big thesis update

@@
 
-	To do this we steer each domain towards an equilibrium configuration by a Hooke's law restorative torque with magnitude of the following form
+	To do this we steer each domain towards an equilibrium configuration by a Hooke's law restorative torque with signed magnitude of the following form
 	\begin{equation}
@@
 	\section{Calculating Forces and Torques}
-	Here I will discuss in detail how we calculate the forces and show how this is done in code
+	However we decide to choose the forces on each domain, we would like them to satisfy  conservation angular momentum as this condition serves to keep the energy of the structure in check (add some stuff here) \todo[inline]{TODO: double check for other conditions on torques with David}
+
+	Ultimately, we must specify the forces for three cases: a motor domain, and a tail domain, and the unbound binding domain.
+Having decided upon an algorithm for determining these forces, we could also calculate the force on a bound binding domain (attached to the microtubule) in order to estimate the maximum possible strain before unbinding occurs.
+This may prove interesting for future work but currently we do not care to calculate these forces as a bound binding domain is static and therefore, we do not need to evolve it's position.
+
+	\begin{figure}[!hbt]
+		\centering
+		\includegraphics[angle =-90, width=0.65\columnwidth]{torque_forces.pdf}
+		\caption{Toy model for three arbitrary domains.
+The force applied to adjacent domains due to the torque on the $i^{th}$ domain is shown.
+Forces are chosen to be perpendicular the inter-domain separation and in the direction that would move $\varphi_i$ towards its equilibrium configuration.}
+		\label{fig:torque_force}
+	\end{figure}
+
+	Figure \ref{fig:torque_force} illustrates how the force on the motor domain due to the torque on the binding domain is chosen.
+In general, equation (3.10) suggests we should pick the magnitude of the force on the $i^{th}$ domain due to the torque on the $j=i\pm1$ domains to be
+	\begin{equation}
+		F_{ij} = \Gamma_j / \ell_{ij}
+	\end{equation}
+	where $\ell_{ij}$ is the distance between the $i$ and $j$ domains.
+We then make the choice to apply the force perpendicular to the inter-domain separation and in the direction of the equilibrium angle.
+Making this choice makes it clear that angular momentum will be conserved for the case where $\ell_{i\;i-1}=\ell_{i\;i+1}$.
+Finally to simplify computational complexity, we transform these two forces into forces on the $i^{th}$ domain by instead applying an equal and opposite force to each $\mathbf{F}_{ij}$ on the $i^{th}$ domain.
+
+	With this algorithm, we can loop through each domain and calculate the torque-related forces on each domain. For binding domains, there is only one adjacent domain to consider. 
+	\todo[inline]{TODO: add another figure or update above to indicate the equal-and-opposite forces that are actually kept.
+It may look nice to turn force arrows into dotted arrow and then add the force on the $i^{th}$ domain with a solid line}
+
+	We are now armed with a way to calculate the forces on each domain due to the restorative torque.
+The only force which we are unable to calculate directly is the force due to tension.
+We will deal with these forces by applying the method Lagrange multipliers as we solve for the equations of motion.
 
 	\section{Equations of Motion}
-	Now that we have specified the forces, the dynamics of each domain are determined by equation 4.5 so that in order to simulate the complicated structure we must solve a system of coupled first order differential equations.
+	The dynamics of each domain are determined by equation 3.5 so that in order to simulate the complicated structure we must solve a system of coupled first order differential equations.
 In doing so, it is convenient to introduce two states to distinguish between dynein's stepping and when both of its binding domains are attached to the microtubule.
-We shall refer to these configurations hereafter as the one bound state and the both bound state.
+We shall refer to these configurations hereafter as the one bound state and the both bound state with the idea being that they directly correspond to the pre and post-stroke states defined by the mechanochemical cycle of \cite{cianfrocco_mechanism_2015}.
 
@@
 In the both bound state, both binding domains are attached.
-This slight difference in geometry between the two scenarios leads to two sets of equations for motion that differ slightly.
-The following section details the derivation of these equations of motion.
+This slight difference in geometry between the two scenarios leads to two independent equations motion motion that require careful consideration when transitioning between states.
+The following sections detail the derivation of these equations of motion for each configuration.
 
@@
 
-		The Brownian motion equation (3.5) also defines the velocity on domain.
+		The Brownian motion equation (3.5) also defines the velocity on each domain allowing us to write
+		\begin{align}
+			\dot{x}_i &= \frac{1}{\gamma_i}\Big(F_{i,\Gamma_i}^x+ \lambda_{i,i-1}(x_i-x_{i-1})+\lambda_{i,i+1}(x_i-x_{i+1})-F_{i,\text{rand}}^x\Big)\\
+			\dot{y}_i &= \frac{1}{\gamma_i}\Big(F_{i,\Gamma_i}^y+ \lambda_{i,i-1}(y_i-y_{i-1})+\lambda_{i,i+1}(y_i-y_{i+1})-F_{i,\text{rand}}^y\Big) \notag
+		\end{align}
+		where superscript $x$ and $y$ denote the force components.
+
+		\todo[inline]{Double check this calculation with David to make sure I have accounted for the tension terms correctly.
+For some reason, Elliott uses x's in both the x and y equations...
+Is this a typo?}
+
+		 At this point, comparing equations 3.13 with 3.14 reveals we have identified 8 nontrivial equations (x and y derivatives; ignoring bound binding domain 0).
+There are four unknown derivatives $\{\dot\theta_i\}$ and four unknown Lagrange multipliers $\{\lambda_{ij}\}$ which altogether form a linear system which we solve using Mathematica.
+For a detailed calculation see the appendices.
+
+		 \todo[inline]{TODO: add appendices with full matrix equations}
 
@@
 		\end{figure}
-	\section{The Code}
-		\subsection{The Random Force}
+
+	\section{Binding and Unbinding}
+
+	\todo[inline]{Add theoretical description of binding and unbinding probabilities and their relation to tension and torque on binding domain.
+Explain the use of our exponential factor and why it is reasonable.
+Discuss potential to add in exponential factor to binding rate.}

### 2019-03-20 papers/waczak-thesis/thesis/thesis.tex
thesis update
more thesis stuff
big thesis update

@@
 \usepackage{graphicx} % make it easy to load in images
-\graphicspath{{./images/}} % where to find images
+\graphicspath{{./images/},{../../../plots/}} % where to find images
 \usepackage[a4paper, margin=1in]{geometry} % change margins 
@@
 \usepackage{subcaption}
+
+\usepackage{titlesec} % redefine headings to remove "Chapter X"
+
+\usepackage[labelfont=bf, textfont=md]{caption}
+
+\usepackage{setspace}
+
+\usepackage{hyperref}
+
+\usepackage[color=cyan]{todonotes}
+
+\usepackage[labelfont=bf]{caption}
+
 \title{
-	{Simulating the Brownian Dynamics of a Two-Dimensional Model for the Dynein Motor Protein}\vspace{1.5em}\\
+	{Simulating the Brownian Dynamics of a Two-dimensional Model for the Dynein Motor Protein}\vspace{1.5em}\\
 	\includegraphics[width=0.5\columnwidth]{OSU_logo.png}\vspace{0.5em}\\
@@
 \begin{document}
+	\onehalfspacing
+
 	\maketitle
@@
 	\input{./chapters/dynein}
+	\chapter{Theory}
+	\input{./chapters/theory}
 	\chapter{Methods}
 	\input{./chapters/methods}
-
+	\chapter{Results}
+	\input{./chapters/results}
 \bibliography{references}
-\bibliographystyle{acm}
+\bibliographystyle{prl_like.bst}
 \end{document}

### 2019-04-16 papers/waczak-thesis/thesis/chapters/results.tex
added some rough figures to results and drafted the abstract

@@
 
+\todo[inline]{TODO: combine 5.1 with 5.2 to explain leading vs lagging}
+\todo[inline]{TODO: consider removing leading lagging axis labels in 5.1 if redundant with figure caption} 
+\todo[inline]{NOTE: it looks like there may be an issue with the middle most cartoon in 5.3. The tail does not appear to be the correct size}
+\todo[inline]{TODO decrease overall width of tail in cartoon dynein. Increase thickness of stalk} 
+\todo[inline]{TODO: Check to make sure time axis in final panel of fig 5.4 is actually a log scale}
+
+\section{Stepping}
+\begin{figure}
+	\centering
+	\includegraphics[width=1\columnwidth]{paper_trajectory_plot}
+	\caption{\textbf{Trajectory Plot} Vertical and horizontal projections of each of binding domains.
+Directed motion is clearly seen in the positive slope of the x-projection graph.
+Dynein's conformation is illustrated for a selection of times.}
+	\label{fig:trajectory}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.85\columnwidth]{paper_model_behavior}
+	\caption{\textbf{Stepping statistics} trajectories run with different random number seeds all show forward directed motion.
+Step lengths have a similar distribution to experiment although steps of zero length are not measured experimentally.
+}
+	\label{Fig:statistics}
+\end{figure}
+
+\section{One bound and both bound correlations}
 \begin{figure}[!hbt]
@@
 			negative correlation. A similar fit from an experimental paper is plotted for comparison.}
+	\label{fig:displacement_vs_step_length}
 \end{figure}
@@
 
-\begin{figure}
+\section{Possible Monte Carlo}
+\begin{figure}[!hbt]
 	\centering
-	\includegraphics[width=1\columnwidth]{paper_trajectory_plot}
-	\caption{}
+	\includegraphics[width=1\columnwidth]{energy_landscape}
+	\caption{\textbf{Energy Landscape} graph showing the total energy of the dynein for a given binding domain displacement $L$.
+The yellow and red dots correspond to the minimum and maximum energy configurations for which a cartoon is shown on the right.}
+	\label{fig:energy_landscape}
 \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\columnwidth]{paper_model_behavior}
-	\caption{}
-\end{figure}
 \vspace{10em}
-
-\todo[inline]{TODO: combine 5.1 with 5.2 to explain leading vs lagging}
-\todo[inline]{TODO: consider removing leading lagging axis labels in 5.1 if redundant with figure caption} 
-\todo[inline]{NOTE: it looks like there may be an issue with the middle most cartoon in 5.3. The tail does not appear to be the correct size}
-\todo[inline]{TODO decrease overall width of tail in cartoon dynein. Increase thickness of stalk} 
-\todo[inline]{TODO: Check to make sure time axis in final panel of fig 5.4 is actually a log scale}

### 2019-04-16 papers/waczak-thesis/thesis/thesis.tex
fix failure to build in john thesis
added some rough figures to results and drafted the abstract

@@
 	\chapter*{Abstract}
-	test
+	\vspace{-3 em}word count: \textbf{345}\\
+
+	Cells are complicated structures whose components must perform controlled motion in order for the cell to execute its functions.
+Diffusion alone is far to slow of an action to produce the observed motions of cellular structures.
+The solution to this problem comes in the form of a class of proteins known as molecular motors that carry cargo throughout the cell by hydrolyzing adenosine triphosphate.
+Among these motors, the dynein protein is recognized for its odd stepping behaviors.
+Sometimes it steps forwards.
+Other times it steps backwards-- even been observed to occasionally shuffle.
+This peculiar motion makes dynein an interesting object of study, but its status as one a select few minus-end directed motors makes understanding the mechanics of dynein’s motion vital to our understanding of the cell.
+When these motors misbehave, fundamental processes like axonal transport and muscle contraction fail.
+
+	Current observational techniques for studying biomolecules include techniques for imaging such as cryo-electron microscopy and x-ray crystallography, and techniques for tracking a protein’s motion such as fluorescent tagging combined with fluorescence microscopy.
+These methods have revealed much about the different conformational states achieved by dynein during a step and have established a base of statistics for step lengths, velocities, generated forces, etc… Despite these advancements, the ability to image the full molecule for an entire stepping cycle remains beyond the capabilities of the current experimental apparatus.
+
+	To address this gap, we have developed a simplified, two-dimensional model for the dynein molecule.
+We treat the protein as a system of massive domains held together by rigid rods steered towards equilibrium configurations by spring like torques and time evolved using Brownian dynamics.
+With our current set of parameters, the model displays directed motion with step length and velocity distributions ( give statistics here ) in agreement with experiment.
+Simulations also suggest that there is no correlation between the conformation of dynein before and after a step.
+These results indicate that a more computationally efficient simulation can be achieved with a Monte Carlo simulation for the both bound state coupled with the full Brownian simulation for the one bound state.
+
 	\chapter*{Acknowledgments}

### 2019-04-23 papers/waczak-thesis/thesis/chapters/dynein.tex
big thesis update 1

@@
 Microtubules are cytoskeletal structures formed by self assembly of $\alpha$ and $\beta$ tubulin heterodimers (shown as green in Figure \ref{fig:cytoskeleton}).
-\cite{downing_tubulin_1998} These molecular structures are typically comprised of 13 protofilaments each of which is a periodic arrangement of the $\alpha$ and $\beta$ dimers.
+\cite{downing1998tubulin} These molecular structures are typically comprised of 13 protofilaments each of which is a periodic arrangement of the $\alpha$ and $\beta$ dimers.
 
-Microtubules exhibit an inherent polarity identified as the plus ($+$) and minus ($-$) ends \cite{lodish_microtubule_2000}.
+Microtubules exhibit an inherent polarity identified as the plus ($+$) and minus ($-$) ends \cite{berk2000molecular}.
 This polarity is both function and structural.
-One end of the microtubule experiences much faster addition of tubulin making it easy to identify\cite{heidemann_visualization_1980}.
-For our purposes though, the structural polarity of the microtubule is more important as the formation of the microtubule results in a helical structure that has definite chirality \cite{microtubule_chirality}.
+One end of the microtubule experiences much faster addition of tubulin making it easy to identify\cite{heidemann1980visualization}.
+For our purposes though, the structural polarity of the microtubule is more important as the formation of the microtubule results in a helical structure that has definite chirality \cite{hunyadi2007microtubule}.
 Two possible microtubule configurations are shown in Figure \ref{fig:chirality}.
@@
 They are almost always observed to walk towards the plus-end of the microtubule.
-Dynein is strictly a minus-end directed motor \cite{alberts_molecular_2002}.
+Dynein is strictly a minus-end directed motor \cite{alberts2002molecular}.
 How this directed motion is derived from the symmetric dynein structure is still an open question.\\
@@
 The chemical resolution to this problem arises from the interaction of ATP with each of the motor domains of dynein.
-The cycle of converting the chemical energy of  ATP into useful mechanical energy for motion is called the \textit{mechanochemical cycle}\cite{cianfrocco_mechanism_2015}.
+The cycle of converting the chemical energy of  ATP into useful mechanical energy for motion is called the \textit{mechanochemical cycle}\cite{cianfrocco2015mechanism}.
 Describing all of the chemical interactions involved in a single dynein step has been an active area of research.
@@
 Dynein goes through many identifiable stages as ATP from the environment interacts with the motor domain and changes the conformation of the protein.
-Image taken from \cite{cianfrocco_mechanism_2015}.}
+Image taken from \cite{cianfrocco2015mechanism}.}
 	\label{fig:mechanochemical_cycle}
@@
 This two-dimensional illustration shows only one of legs of dynein.
-Image taken from \cite{dynein_powerstroke}.}
+Image taken from \cite{lin2014structural}.}
 \end{figure}
 
-Scientists have determined the steps of this chemical cycle by carefully isolating and analyzing the resulting structures via cryo-electron microscopy \cite{cryo_em}.
-While this is useful for determining the conformation before and after a chemical process occurs, it does note describe the actual motion along the microtubule-- only intermittent states.
+Scientists have determined the steps of this chemical cycle by carefully isolating and analyzing the resulting structures via cryo-electron microscopy \cite{burgess2003dynein}.
+While this is useful for determining the conformation before and after a chemical process occurs, it does not describe the actual motion along the microtubule-- only intermittent states.
 All of the information about how flexible each domain is during binding and to what extent the protein diffuses in its search for the microtubule require alternative methods to establish.
@@
 \section{Other observational techniques} 
- Kinesin and Dynein have masses of a few hundred kDa and  $\sim2$ MDa respectively \cite{liao_kinesin_1998, johnson_structure_1983}.
+ Kinesin and Dynein have masses of a few hundred kDa and  $\sim2$ MDa respectively \cite{liao1998kinesin, johnson1983structure}.
 Recalling that 1 Dalton (Da) corresponds to one atomic mass unit means these proteins consist of, at most, a few million atoms.
@@
 Weihong Qiu's group is by attaching small fluorescent molecules called fluorophores to the binding sites that motor proteins use to latch onto their cargo.
-Then, the individual movement of motors can be tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in figure \ref{fig:weihong tirf} from \cite{qiu_dynein_2012}.
+Then, the individual movement of motors can be tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in figure \ref{fig:weihong tirf} from \cite{qiu2012dynein}.
 
@@
 Slices at different times are stacked so that the slope of each green line indicates the velocity of the protein.
-Image taken from \cite{qiu_dynein_2012}.}
+Image taken from \cite{qiu2012dynein}.}
 	\label{fig:weihong tirf}
@@
 Furthermore, by tagging a motor domain instead of the tail, this technique can resolve step sizes and as shown in Figure \ref{fig:weihong histogram}.
-\cite{qiu_dynein_2012} Taking into account these studies as well as the delicate cryo-em analysis forms a rough sketch for dynein's motion.
+\cite{qiu2012dynein} Taking into account these studies as well as the delicate cryo-em analysis forms a rough sketch for dynein's motion.
 Unfortunately though, this is the limit of current experimental methods; observing the individual motions of each of the binding domains of a dynein protein is not yet possible.

### 2019-04-23 papers/waczak-thesis/thesis/chapters/introduction.tex
big thesis update 1

@@
 This cytoskeleton serves as a highway to a class of proteins called \textit{molecular motors} which can be distinguished into three types: kinesin, myosin, and dynein.
-Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work\cite{alberts_molecular_2002}.
-Correct operation of these motors results in processes such as cell division, muscle contraction, and axonal transport; failure can lead to debilitating diseases such as ALS \cite{boillee_als:_2006}.
+Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work\cite{alberts2002molecular}.
+Correct operation of these motors results in processes such as cell division, muscle contraction, and axonal transport; failure can lead to debilitating diseases such as ALS \cite{boillee2006disease}.
 
@@
 Myosin and kinesin behave like a normal person; their steps alternate between opposing domains.
-This motion is called \textit{hand over hand} stepping \cite{noauthor_drunk_nodate}.
+This motion is called \textit{hand over hand} stepping \cite{goldman2009drunk}.
 Dynein, however, is unique in its motion as it takes hand-over-hand steps and also \textit{inchworms}.
 This alternative behavior is a scenario in which one motor consistently leads the opposite resulting in a shuffling motion.
-Furthermore, dynein even takes frequent backwards steps as shown in the stepping histogram in figure \ref{fig:weihong histogram} \cite{qiu_dynein_2012}.
-Collectively this behavior has earned dynein the title of \textit{drunken walker} which compactly summarizes its peculiar tendencies \cite{noauthor_drunk_nodate}.
+Furthermore, dynein even takes frequent backwards steps as shown in the stepping histogram in figure \ref{fig:weihong histogram} \cite{qiu2012dynein}.
+Collectively this behavior has earned dynein the title of \textit{drunken walker} which compactly summarizes its peculiar tendencies \cite{goldman2009drunk}.
 \\
@@
 2-D data corresponds to the total step size over the two-dimensional structure.
-Figure taken form \cite{qiu_dynein_2012}.}
+Figure taken form \cite{qiu2012dynein}.}
 	\label{fig:weihong histogram} 
@@
 This unique stepping behavior makes dynein an interesting subject to study.
-There have been significant efforts aimed at characterizing the complex, multi-phase chemical cycle involved in the hydrolysis of ATP\cite{cianfrocco_mechanism_2015}.
+There have been significant efforts aimed at characterizing the complex, multi-phase chemical cycle involved in the hydrolysis of ATP\cite{cianfrocco2015mechanism}.
 However, the dynamics of dynein's physical motion through space remains an open question as current optical techniques have difficulty resolving the individual motion of each dimer.

### 2019-04-23 papers/waczak-thesis/thesis/chapters/methods.tex
big thesis update
big thesis update 1

@@
+	
+\section{The Code}
+	\section{Time evolution: Euler's method}
+	\subsection{The Random Force}
+\section{Determining constants of the model}
+The stalk and tail lengths $\ell_S, \ell_T$ as well as a set of equilibrium angles $\{\varphi_{i,\text{eq}}\}$ were determined by examining microscopy images of dynein in various configurations. 
+\begin{figure}[hbt!]
+	\centering
+	\includegraphics[width=0.3\columnwidth]{schematic-2-superimposed}
+	\caption{Our model superimposed over microscopy image of Dynein \textbf{NOTE: add source} for determining lengths and equilibrium angles} 
+	\label{fig:superimpmosed}
+\end{figure}
+
 \section{Testing the model} 

### 2019-04-23 papers/waczak-thesis/thesis/chapters/theory.tex
big thesis update 1

@@
 Now that I have established some facts about motor proteins as well as specifics about dynein's many odd behaviors, we may begin our discussion of how to construct and test a physical model for its motion.
-First, we note that dynein's large mass of roughly 2MDa \cite{johnson_structure_1983} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao_kinesin_1998} exaggerates the effect of interactions with the  aqueous environment of the cell.
+First, we note that dynein's large mass of roughly 2MDa \cite{johnson1983structure} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao1998kinesin} amplifies the effect of interactions with the  aqueous environment of the cell.
 This results in a much more significant drag force as well as a random element from water molecule collisions that changes the overall dynamics of the system.
@@
 	\end{equation} 
+	Bead-and-spring models such as this are common in molecular dynamics simulations as a way to model the interactions of high weight molecules.\cite{bead-spring-model}.
 
@@
 In doing so, it is convenient to introduce two states to distinguish between dynein's stepping and when both of its binding domains are attached to the microtubule.
-We shall refer to these configurations hereafter as the one bound state and the both bound state with the idea being that they directly correspond to the pre and post-stroke states defined by the mechanochemical cycle of \cite{cianfrocco_mechanism_2015}.
+We shall refer to these configurations hereafter as the one bound state and the both bound state with the idea being that they directly correspond to the pre and post-stroke states defined by the mechanochemical cycle of \cite{cianfrocco2015mechanism}.
 
@@
 			\centering
-			\includegraphics[angle=-90,width=0.75\columnwidth]{onebound}
+			\includegraphics[angle=-90,width=0.8\columnwidth]{onebound}
 			\caption{The dynein model in the one bound state }
@@
 		\subsection{The both bound state}
+		For the both bound state, we no longer have a notion of bound and unbound domains.
+We therefore introduce a new notation, near and far, to identify each dimer.
+This is not purely for convenience of notation, but rather is important for storing data.
+We will want the ability to calculate the total step length.
+Doing this requires knowledge of which motor domain initiates the stepping cycle.
+\\
 
-		\section{Determining constants of the model}
-		The stalk and tail lengths $\ell_S, \ell_T$ as well as a set of equilibrium angles $\{\varphi_{i,\text{eq}}\}$ were determined by examining microscopy images of dynein in various configurations. 
-		\begin{figure}[hbt!]
+		In this state, both binding domains are attached to the microtubule and therefore, a degree of freedom has been removed from our system.
+This enables us to simplify the dynamic equations in order to take advantage of the new, constrained geometry.
+To that end, we define a new coordinate system as shown in the following figure.
+
+		\begin{figure}[!hbt]
 			\centering
-			\includegraphics[width=0.3\columnwidth]{schematic-2-superimposed}
-			\caption{Our model superimposed over microscopy image of Dynein \textbf{NOTE: add source} for determining lengths and equilibrium angles} 
-			\label{fig:superimpmosed}
+			\includegraphics[width=0.75\columnwidth, angle=-90]{bothbound.pdf}
+			\caption{\textbf{Both bound} state with the new angles and lengths shown.}
+			\label{fig:bothbound}
 		\end{figure}
+
+		Here, $\theta_{nm}$ and $\theta_{fm}$ can be obtained from the one bound state by 
+		\begin{equation}
+			\theta_{nm} = \theta_1+(\pi-\theta_0) \qquad \theta_{fm}= \theta_3 + (\pi-\theta_4) 
+		\end{equation}
+		Because the near and far binding domains are fixed, the only domains that we need to time evolve for the both bound state are the two motors (nm, fm) and the tail (T).
+Therefore, specifying $\theta_{nm}, \theta_{fm}$, and $\ell$ is enough to determine the geometry of the system.
+The intermediate variables are calculated by wild application of the law of cosines.
+		\begin{align}
+			\ell_n &= \sqrt{\ell_s^2+\ell_T^2-2\ell_s\ell_T\cos(2\pi-\theta_{nm})} \\
+			\ell_f &=  \sqrt{\ell_s^2+\ell_T^2-2\ell_s\ell_T\cos(2\pi-\theta_{fm})} \\
+			\text{}\nonumber\\
+			 \theta_n &= \arccos\left(\frac{\ell_n^2+\ell^2-\ell_f^2}{2\ell_n\ell}\right)\\
+			\theta_f &= \pi-\arccos\left(\frac{\ell_f^2+\ell^2-\ell_n^2}{2\ell_f\ell}\right)\\
+			\text{}\nonumber\\
+			\theta_{n'} &= \arccos\left(\frac{\ell_n^2+\ell_s^2-\ell_t^2}{2\ell_n\ell_s}\right) \\
+			\theta_{f'} &= \arccos\left(\frac{\ell_f^2+\ell_s^2-\ell_t^2}{2\ell_f\ell_s}\right) \\ 
+			\text{}\nonumber \\ 
+			\theta_{nb} &\equiv \theta_{n}-\theta_{n'} \\ 
+			\theta_{fb} &\equiv \theta_{f}-\theta_{f'} 
+		\end{align}
+	   	with these angles and lengths defined, we can now easily define the positions 
+	   		\begin{align}
+	   	{x}'s \quad \begin{cases}
+	   	{x}_{nm} = x_n+\ell_s\cos(\theta_{nb}) \\
+	   	{x}_{fm} = x_f+\ell_s\cos(\theta_{fb}) \\
+	   	{x}_{T} = x_{nm}+\ell_n\cos(\theta_n) 
+	   	\end{cases} &
+	   	{y}'s \quad \begin{cases}
+	   	{y}_{nm} = \ell_s\sin(\theta_{nb}) \\
+	   	{y}_{fm} = \ell_s\sin(\theta_{fb}) \\
+	   	{y}_{t} = \ell_n\sin(\theta_n) 
+	   	\end{cases} 
+	   	\end{align}
+		Now we have everything we need in order to repeat the process for the one bound state.
+Differentiating these equations will give us explicit formulas for the time derivative of the coordinates of each domain which we can then compare to the forces acting on each domain via the Brownian motion equation.
+Fortunately, the effort was well spent as we've reduced (3.14) to a system of six equation with 6 unknowns (one angle and one Lagrange multiplier for each \textit{moving} domain).
 
@@
 Discuss potential to add in exponential factor to binding rate.}
+
+	\begin{equation}
+	\rho_{ub} = k_{ub}e^{-c(\theta_i-\theta_{i,eq})}
+	\end{equation}

### 2019-04-23 papers/waczak-thesis/thesis/thesis.tex
big thesis update 1

--- 2019-03-20 papers/waczak-thesis/thesis/thesis.tex
@@
 	\maketitle
+	\todo[inline]{TODO: Fix formatting of title page}
+	\chapter*{Abstract}
+	\vspace{-3 em}word count: \textbf{345}\\
 
-	\chapter*{Abstract}
-	test
+	The dynein molecule is a peculiar motor protein recognized for its odd stepping behavior.
+Sometimes it steps forwards.
+Other times it steps backwards.
+It has even been observed to occasionally shuffle by beginning a step with the same domain many times in row.
+These unique motions make dynein an interesting object of study, but its status as one of a select few minus-end directed motors makes understanding the mechanics of dynein’s motion vital to our understanding of the cell.
+When these motors misbehave, fundamental processes like axonal transport and muscle contraction fail.
+Observational techniques for studying biomolecules have revealed much about the different conformational states achieved by dynein during its stepping cycle and have established a base of relevant statistics such step lengths, velocities, and generated forces among others.
+Despite these advancements, the ability to image the full molecule for an entire stepping cycle remains beyond the capabilities of the current experimental apparatus.
+
+	To address this gap, we have developed a simplified, two-dimensional model for the dynein molecule.
+We treat the protein as a system of massive domains held together by rigid rods steered towards equilibrium configurations by spring like torques and time evolved using Brownian dynamics.
+With our current set of parameters, the model displays directed motion with step length and velocity distributions ( give statistics here ) in agreement with experiment.
+Our simulations also suggest that there is no correlation between the conformation of dynein before and after a step.
+Our results indicate that a more computationally efficient simulation can be achieved with a two state system where a post power stroke state is selected from a distribution via a Monte Carlo simulation and binding is then simulated with the full Brownian dynamics.
+We are optimistic that our simulations will be able to address the power stroke versus winch model debate.
+
+	\todo[inline]{TODO: Add in specific data to results}
+	\todo[inline]{TODO: Fix formatting to include "a thesis submitted in completion of..." etc.}
+
 	\chapter*{Acknowledgments}

### 2019-04-23 papers/waczak-thesis/thesis/chapters/theory.tex
thesis update 2

@@
 	\section{Binding and Unbinding}
+	To keep the simulation simple, we have chosen a very physically reasonable and uncomplicated binding model with a minimum amount of assumptions.
+The two key processes, binding and unbinding, are controlled by two parameters called the binding rates.
+For binding, we simply assume that a binding event occurs when a binding domain is close enough to the microtubule.
+In other words
+	\begin{equation}
+		\rho_{b} = k_b
+	\end{equation}
+	where $\rho_b$ is a probability per second and $k_b$ is a constant. \\
 
-	\todo[inline]{Add theoretical description of binding and unbinding probabilities and their relation to tension and torque on binding domain.
-Explain the use of our exponential factor and why it is reasonable.
-Discuss potential to add in exponential factor to binding rate.}
+	Recently there has been evidence to show that dynein's step length depends on the tension applied at the linker between the two motor domains (e.g.
+the tail).\cite{cleary2014tension} This tension is high when the motor domains are far apart and small when they are together as illustrated in the following figure.
+\\
+	\begin{figure}[!hbt]
+		\centering
+		\includegraphics[width=0.8\columnwidth]{yildiz_tension_dependence}
+		\caption{\textbf{Tension dependent stepping} is shown for a typical dynein (non-mutated).
+There is a clear, negative correlation between the step size and interhead separation.
+Data is clustered around trailing steps indicating that a higher tension leads to more stepping.
+Image taken from \cite{cleary2014tension}}
+		\label{fig:yildiz_tension}
+	\end{figure} 	
+	As figure \ref{fig:yildiz_tension} indicates, a large interhead separation leads to more likely stepping.
+Furthermore, trailing steps are favored-- this means steps where the back foot begins the motion (like a normal step) are more likely.
+To capture this behavior, we use an angle dependent exponential factor in the binding rate.
+That is
 
 	\begin{equation}
-	\rho_{ub} = k_{ub}e^{-c(\theta_i-\theta_{i,eq})}
+	\rho_{ub} = k_{ub}e^{-c(\theta_b-\theta_{b,eq})}
 	\end{equation}
+	i.e.
+unbinding depends on the angular separation of the binding domain from it's equilibrium position.
+If the $\theta_b$ is large and positive, then the unbinding rate is very small.
+If $\theta_b$ is less than $\theta_{b,eq}$, then the unbinding rate is very large.
+This will favor the lagging foot because when dynein has a large interhead separation, the lagging $\theta_b$ is very small and the leading $\theta_b$ is very large as shown in the following figure.
+
+	\begin{figure}[!hbt]
+		\centering
+		\includegraphics[width=0.7\columnwidth, angle=-90]{tension_dependence_edge_case}
+		\caption{\textbf{A Stretched dynein} illustrates the angular dependence of the unbinding model.
+In this configuration $\theta_{nb}$ is very small and is therefore much more likely to unbind than $\theta_{fb}$.}
+	\end{figure}

### 2019-04-30 papers/waczak-thesis/thesis/chapters/theory.tex
thesis update

@@
 The two key processes, binding and unbinding, are controlled by two parameters called the binding rates.
-For binding, we simply assume that a binding event occurs when a binding domain is close enough to the microtubule.
-In other words
+For binding, we simply assume that a binding event occurs at a certain rate whenever a binding domain is close enough to the microtubule.
+That is,
+
 	\begin{equation}
-		\rho_{b} = k_b
+	\begin{cases}
+		\rho_{b} = k_b; & y_b < \varepsilon \\ 
+		\rho_{b} = 0; & y_b > \varepsilon
+	\end{cases}
 	\end{equation}
+
 	where $\rho_b$ is a probability per second and $k_b$ is a constant. \\

### 2019-05-07 papers/waczak-thesis/thesis/chapters/dynein.tex
thesis update

@@
 	\includegraphics[width=0.5\columnwidth]{cytoskeleton}
-	\caption{Endothelial cells with their cytoskeleton structures shown.
+	\caption[The cytoskeleton]{Endothelial cells with their cytoskeleton structures shown.
 The nucleus of each cell is colored in blue.
@@
 Dynein walks along a particular cyctoskeleton filament called a microtubule.
-Microtubules are cytoskeletal structures formed by self assembly of $\alpha$ and $\beta$ tubulin heterodimers (shown as green in Figure \ref{fig:cytoskeleton}).
-\cite{downing1998tubulin} These molecular structures are typically comprised of 13 protofilaments each of which is a periodic arrangement of the $\alpha$ and $\beta$ dimers.
+Microtubules are cytoskeletal structures formed by self assembly of $\alpha$ and $\beta$ tubulin heterodimers (shown as green in Figure \ref{fig:cytoskeleton}) \cite{downing1998tubulin}.
+These molecular structures are typically comprised of 13 protofilaments each of which is a periodic arrangement of the $\alpha$ and $\beta$ dimers.
 
@@
 	\includegraphics[width=.5\columnwidth]{microtubule_chirality}
-	\caption{Two possible microtubule structures illustrating the chirality of the helix as well as the skew angle of the dimers of which only one is shown for illustrative purposes.
-Image taken from \cite{microtubule_chirality}.}
+	\caption[Motor protein structures]{Two possible microtubule structures illustrating the chirality of the helix as well as the skew angle of the dimers of which only one is shown for illustrative purposes.
+Image taken from \cite{hunyadi2007microtubule}.}
 	\label{fig:chirality}
@@
 As Figure \ref{fig:cytoskeleton} shows, microtubules foliate the entire cell with paths that enable motor proteins to move cargo.
-Most(not all) variations of the kinesin molecular motor are plus-end directed.
+Most (not all) variations of the kinesin molecular motor are plus-end directed.
 They are almost always observed to walk towards the plus-end of the microtubule.
@@
 The chemical resolution to this problem arises from the interaction of ATP with each of the motor domains of dynein.
-The cycle of converting the chemical energy of  ATP into useful mechanical energy for motion is called the \textit{mechanochemical cycle}\cite{cianfrocco2015mechanism}.
+The cycle of converting the chemical energy of  ATP into useful mechanical energy for motion is called the \textit{mechanochemical cycle} \cite{cianfrocco2015mechanism}.
 Describing all of the chemical interactions involved in a single dynein step has been an active area of research.
@@
 	\includegraphics[width=1\columnwidth]{mechanochemical_cycle}
-	\caption{The mechanochemical cycle of dynein.
+	\caption[Cianfrocco's mechanochemical cycle]{The mechanochemical cycle of dynein.
 Dynein goes through many identifiable stages as ATP from the environment interacts with the motor domain and changes the conformation of the protein.
@@
 	\includegraphics[width=1\columnwidth]{pre_post_powerstroke}
-	\caption{An illustration of the pre and post stroke states of dynein in relation to the microtubule and the cargo that they carry.
+	\caption[Powerstroke illustration]{An illustration of the pre and post stroke states of dynein in relation to the microtubule and the cargo that they carry.
 This two-dimensional illustration shows only one of legs of dynein.
@@
 This small scale poses a unique experimental challenge.
-One way this is approached at Prof.
-Weihong Qiu's group is by attaching small fluorescent molecules called fluorophores to the binding sites that motor proteins use to latch onto their cargo.
-Then, the individual movement of motors can be tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in figure \ref{fig:weihong tirf} from \cite{qiu2012dynein}.
+One way this is approached Qiu \textit{et al} group is by attaching small fluorescent molecules called fluorophores to the binding sites that motor proteins use to latch onto their cargo.
+Then, the individual movement of motors can be tracked using total internal reflection fluorescence microscopy to produce video of the proteins in action as illustrated in the following figure from \cite{qiu2012dynein}.
 
@@
 	\includegraphics[angle=90, width=0.75\columnwidth]{weihong_motor}
-	\caption{\textbf{TIRF Microscopy Imaging} individual kinesin proteins are imaged as small green dots and tracked as they move.
+	\caption[Stepping histogram]{\textbf{TIRF Microscopy Imaging} individual kinesin proteins are imaged as small green dots and tracked as they move.
 Slices at different times are stacked so that the slope of each green line indicates the velocity of the protein.
@@
 Figure \ref{fig:weihong tirf} demonstrates fluorescence microscopy enables observation of protein speed, how far it walks along the microtubule, which direction is preferred.
-Furthermore, by tagging a motor domain instead of the tail, this technique can resolve step sizes and as shown in Figure \ref{fig:weihong histogram}.
-\cite{qiu2012dynein} Taking into account these studies as well as the delicate cryo-em analysis forms a rough sketch for dynein's motion.
-Unfortunately though, this is the limit of current experimental methods; observing the individual motions of each of the binding domains of a dynein protein is not yet possible.
+Furthermore, by tagging a motor domain instead of the tail, this technique can resolve step sizes and as shown in figure \ref{fig:weihong histogram}.
+Data from these techniques and the more delicate cryo-em analyses form a rough sketch for dynein's motion.
+Unfortunately, this is the limit of current experimental methods; resolving the motion of the entire protein is not yet possible.
 
-\todo[inline]{TODO: Add in discussion of using gold particles + scattering to observe Brownian wiggling. This was a result of conversations with Colloquium speaker Kazuhiro Oiwa.}
+\section{Other simulations} 
+Others have created codes for simulating the dynein motor protein.
+Typically these simulations are strictly Monte Carlo, and therefore, must make a large number of assumptions in order to reproduce similar stepping statistics.
+For example, Singh \textit{et al} have created a Monte Carlo code to simulate single-molecule cytoplasmic dynein \cite{singh2005monte}.
+Despite trying to "limit the number of ad hoc assumptions", the authors still concede to making six of them which effectively remove considerations for the physical orientation of dynein in space as it steps.
 
-\section{Experimental stepping statistics}
-Here I will include the various stepping statistics (distribution, binding/unbinding rates, etc...) that we hope to fit our simulation to.
+For example, their first assumption is that dynein can only take steps of 4 distinct sizes (multiples of 8 nm)  \cite{singh2005monte}.
+The intention of this assumption is to capture the structure of the microtubule which has an 8 nm periodicity (see figure \ref{fig:chirality}).
+However there are multiple issues with making this assumption.
+First, dynein step sizes are measured by attaching fluorophores to the motor domains.
+These tags are then tracked using fluorescence microscopy so that the trajectory of the protein can be observed.
+The distance that the motor domains travel \textit{is not} necessarily the same distance that the binding domains travel so that even though reasonable stepping statistics can be achieved by manipulating simulation parameters, such codes neglect the behavior of dynein as a physical system and reduce stepping entirely to chemical exchanges at the motor domain.
+This in turn means that these codes are hard to extend to other modeling questions.
+How would you add tugging forces on dynein from cargo to this model?
+You would have to introduce more assumptions about typical force distributions to the model!
 
-\section{More motivation} 
-Here I will discuss other simulation efforts that, in our opinion, make far to many assumptions or are purely monte carlo and don't actually simulate the motion of the protein.
-I will also discuss why our simulation is a happy medium between a full on molecular dynamics simulation (time expensive but accurate) and monte carlo (very fast but doesn't dynamically simulate the protein and instead just selects steps from a distribution).
+For this work, we take the opposite approach  by instead assuming that the chemistry of ATP exchange at the motor domain has more or less been solved.
+We introduce a physical model for the structure of dynein and explore how such a structure will move along the microtubule under an angle dependent binding/unbinding model.
+We shall see that this affords us greater flexibility in addressing questions about the dynamics of dynein's stepping cycle and makes it easy to extend simulations to scenarios where dynein pulls some cargo through the cell.

### 2019-05-07 papers/waczak-thesis/thesis/chapters/introduction.tex
thesis update

@@
 must be able to replicate and move within their aqueous environment. This
-transport problem  poses a unique challenge as diffusion alone is far to slow,
-and random, a process to be able to produce movement on cellular timescales[].
+transport problem  poses a unique challenge as diffusion alone is far to slow
+and random a process to be able to produce movement on cellular timescales.
 Nature's solution to this problem is twofold.
@@
 This cytoskeleton serves as a highway to a class of proteins called \textit{molecular motors} which can be distinguished into three types: kinesin, myosin, and dynein.
-Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work\cite{alberts2002molecular}.
-Correct operation of these motors results in processes such as cell division, muscle contraction, and axonal transport; failure can lead to debilitating diseases such as ALS \cite{boillee2006disease}.
-
+Molecular motors attach to cellular cargo and drag it along the cytoskeleton by hydrolyzing adenosine triphosphate (ATP) in order to convert stored chemical energy into mechanical work \cite{alberts2002molecular}.
+Correct operation of these motors results in processes such as cell division, muscle contraction, and axonal transport; failure can lead to debilitating diseases such as Amyotrophic Lateral Sclerosis (ALS) \cite{boillee2006disease}.
 \begin{figure}[!hbt]
 	\centering 
-	\includegraphics[width=0.5\columnwidth]{motor_comparison}
-	\caption{Comparison of the three primary motor proteins (from left to right): myosin, kinesin, dynein. Image taken from \cite{philips__nodate}.}
+	\includegraphics[width=0.4\columnwidth]{motor_comparison}
+	\caption[Motor protein structure]{Comparison of the three primary motor proteins (from left to right): myosin, kinesin, dynein. Image taken from \cite{philips__nodate}.}
 	\label{fig:motor proteins} 
 \end{figure}
+{}\\
 
-Astonishingly, each of these motors is composed of two legs that combine to form a bipedal structure (see Figure \ref{fig:motor proteins}).
-that steps like a human as it moves along the cytoskeleton.
+Astonishingly, each of these motors is composed of two legs that combine to form a bipedal structure (see Figure \ref{fig:motor proteins}) that steps like a human as it moves along the cytoskeleton.
 Myosin and kinesin behave like a normal person; their steps alternate between opposing domains.
@@
 	\includegraphics[width=0.5\columnwidth]{weihong_histogram}
-	\caption{Stepping histogram showing the distribution of step sizes for \textit{in vitro} dynein.
+	\caption[Step size distribution]{Stepping histogram showing the distribution of step sizes for \textit{in vitro} dynein.
 1-D data corresponds to the projection of the step along the axis of the microtubule.
@@
 By simulating this model, we demonstrate it's ability to replicate many of the observed properties of the protein.
-We will also use the model to comment a proposed mechanism for how dynein generates its movement, namely the powerstroke model.
+We also use the model to comment on the proposed mechanism for how dynein generates its movement: the power stroke model.

### 2019-05-07 papers/waczak-thesis/thesis/chapters/theory.tex
thesis update

@@
-Now that I have established some facts about motor proteins as well as specifics about dynein's many odd behaviors, we may begin our discussion of how to construct and test a physical model for its motion.
-First, we note that dynein's large mass of roughly 2MDa \cite{johnson1983structure} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao1998kinesin} amplifies the effect of interactions with the  aqueous environment of the cell.
+Having established some facts about motor proteins as well as specifics about dynein's many odd behaviors, we may begin our discussion of how to construct and test a physical model for its motion.
+First, we note that dynein's large cross section and mass (roughly 2 MDa) \cite{johnson1983structure} as compared to similar motor proteins such as Kinesin (a few hundred kDa) \cite{liao1998kinesin} amplifies the effect of interactions with the  aqueous environment of the cell.
 This results in a much more significant drag force as well as a random element from water molecule collisions that changes the overall dynamics of the system.
@@
 		\includegraphics[angle=-90, width=0.6\columnwidth]{torque_angles}
-		\caption{Example of dynein in the one bound configuration with torque angles $\{\varphi_i\}$ shown.}
+		\caption[One bound state]{Example of dynein in the one bound configuration with torque angles $\{\varphi_i\}$ shown.}
 		\label{fig:torque angles}
@@
 	\end{equation} 
-	Bead-and-spring models such as this are common in molecular dynamics simulations as a way to model the interactions of high weight molecules.\cite{bead-spring-model}.
+	Bead-and-spring models such as this are common in molecular dynamics simulations as a way to model the interactions of the components of large molecules.\cite{bead-spring-model}.
 
-	Real dynein is composed of a pair of identical heavy chains.
+	Real dynein is composed of a pair of identical heavy chain legs.
 Therefore, our angle convention is chosen starting at the $0^{th}$ domain in figure \ref{fig:torque angles}.
-The same convention is then repeated for the second leg with the following correspondence
+The same convention is then repeated for the second leg with the following correspondences as the two legs are identical.
 	\begin{align}
-		\varphi_{0,eq} &\longleftrightarrow \varphi_{4,eq} \\ 
-		\varphi_{1,eq} &\longleftrightarrow \varphi_{3,eq}
+		\varphi_{0,eq} = \varphi_{4,eq} \\ 
+		\varphi_{1,eq} = \varphi_{3,eq}
 	\end{align}
-	where the angles $\{\varphi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}. The torques on each domain are related to forces by 
+	where the angles $\{\varphi_{i, \text{eq}}\}$ are the preferred angles of the system as illustrated in figure \ref{fig:torque angles}.\\
+
+	 The torques on each domain are related to forces by 
 	\begin{equation}
@@
 	so that knowing the distance between each domains means that we have specified each of the $\mathbf{\Gamma}_i$ and $\mathbf{r}_i$.
-In order to dynamically move each domain we must invert equation 4.10 to determine $\mathbf{F}_i$, however there is no unique way to invert such a cross product.
-Therefore, we must specify an algorithm for determining the forces that result from each torque.
+In order to dynamically move each domain, we must invert equation 3.10 to determine $\mathbf{F}_i$.
+However, there is no unique way to invert such a cross product.
+We must specify an algorithm for determining the forces that result from the torque on each domain.
 
 	\section{Calculating Forces and Torques}
-	However we decide to choose the forces on each domain, we would like them to satisfy  conservation angular momentum as this condition serves to keep the energy of the structure in check (add some stuff here) \todo[inline]{TODO: double check for other conditions on torques with David}
+	We would like our choice of forces to satisfy momentum conservation (linear and angular) as this condition is a physical requirement and serves to keep the energy of the structure in check across long simulations.
+Physically, this also imposes a requirement that no spring can move the entire molecule.
+To that end we must specify the spring forces for three cases: a motor domain, a tail domain, and an unbound binding domain.
+Having decided upon an algorithm for determining these forces, we can also calculate the force on a bound binding domain (attached to the microtubule) to estimate the maximum possible strain before unbinding occurs.
+This may prove interesting for future work but currently we do calculate these forces as a bound binding domain is static and therefore does not change its position while bound.
+\\
 
-	Ultimately, we must specify the forces for three cases: a motor domain, and a tail domain, and the unbound binding domain.
-Having decided upon an algorithm for determining these forces, we could also calculate the force on a bound binding domain (attached to the microtubule) in order to estimate the maximum possible strain before unbinding occurs.
-This may prove interesting for future work but currently we do not care to calculate these forces as a bound binding domain is static and therefore, we do not need to evolve it's position.
+	To help us devise a reasonable method for applying the forces due to each torque, consider a small portion of dynein consisting of only three domains under the influence of \textbf{no} external forces.
+\\
 
@@
 		\centering
-		\includegraphics[angle =-90, width=0.65\columnwidth]{torque_forces.pdf}
-		\caption{Toy model for three arbitrary domains.
-The force applied to adjacent domains due to the torque on the $i^{th}$ domain is shown.
-Forces are chosen to be perpendicular the inter-domain separation and in the direction that would move $\varphi_i$ towards its equilibrium configuration.}
+		\includegraphics[angle =-90, width=0.475\columnwidth]{torque_forces.pdf}
+		\caption[Torque related forces]{Toy model for three arbitrary domains.
+The force applied on each domain due to the torque on the $i^{th}$ domain is shown.
+Forces are chosen to be perpendicular the inter-domain separation and in the direction that would move $\varphi_i$ towards its equilibrium configuration.
+Equal and opposite forces are applied to the $i^{th}$.}
 		\label{fig:torque_force}
@@
 
-	Figure \ref{fig:torque_force} illustrates how the force on the motor domain due to the torque on the binding domain is chosen.
+	 Figure \ref{fig:torque_force} illustrates how the torque related forces on the $i^{th}$ domain and its two neighbors can be determined in this scenario.
 In general, equation (3.10) suggests we should pick the magnitude of the force on the $i^{th}$ domain due to the torque on the $j=i\pm1$ domains to be
 	\begin{equation}
-		F_{ij} = \Gamma_j / \ell_{ij}
+		F_{ij} \propto \Gamma_j / \ell_{ij}
 	\end{equation}
 	where $\ell_{ij}$ is the distance between the $i$ and $j$ domains.
-We then make the choice to apply the force perpendicular to the inter-domain separation and in the direction of the equilibrium angle.
-Making this choice makes it clear that angular momentum will be conserved for the case where $\ell_{i\;i-1}=\ell_{i\;i+1}$.
-Finally to simplify computational complexity, we transform these two forces into forces on the $i^{th}$ domain by instead applying an equal and opposite force to each $\mathbf{F}_{ij}$ on the $i^{th}$ domain.
-
-	With this algorithm, we can loop through each domain and calculate the torque-related forces on each domain. For binding domains, there is only one adjacent domain to consider. 
-	\todo[inline]{TODO: add another figure or update above to indicate the equal-and-opposite forces that are actually kept.
-It may look nice to turn force arrows into dotted arrow and then add the force on the $i^{th}$ domain with a solid line}
+To make our lives easier, we can make the choice to apply the force perpendicular to the interdomain separation and in the direction of the equilibrium angle so that (3.11) is really an equality.
+If the $i^{th}$ domain were fixed in space, then we would be done.
+However, it is also free to move which means we should expect a force on it as well.
+We define the force on the $i^{th}$ domain to be the sum of the equal-and-opposite forces to the $i+1$ and $i-1$ domains.
+This results in the following properties
+	\begin{equation}
+		\sum\limits_{j=i-1}^{i+1}\mathbf{F}_j=0 \qquad\qquad \sum\limits_{j=i-1}^{i+1}\mathbf{\Gamma}_j = 0
+	\end{equation}
+	which indicate that the center of mass does not move (linear momentum conservation) and that angular momentum is conserved in the case of equal masses and equal distances (as desired).
+With this algorithm, we can loop through each domain and calculate the torque-related forces.
+For binding domains, there is only one neighboring domain to consider.
 
@@
 The only force which we are unable to calculate directly is the force due to tension.
-We will deal with these forces by applying the method Lagrange multipliers as we solve for the equations of motion.
+We will deal with this force via the method Lagrange multipliers as we solve for the equations of motion.
 
@@
 In doing so, it is convenient to introduce two states to distinguish between dynein's stepping and when both of its binding domains are attached to the microtubule.
-We shall refer to these configurations hereafter as the one bound state and the both bound state with the idea being that they directly correspond to the pre and post-stroke states defined by the mechanochemical cycle of \cite{cianfrocco2015mechanism}.
+We shall refer to these configurations hereafter as the \textbf{one bound state} and the \textbf{both bound state} with the idea being that they directly correspond to the pre and post-stroke states defined by the mechanochemical cycle of \cite{cianfrocco2015mechanism}.
 
@@
 			\includegraphics[angle=-90,width=0.8\columnwidth]{onebound}
-			\caption{The dynein model in the one bound state }
+			\caption[One bound angles]{The dynein model in the one bound state }
 			\label{fig:one bound}  
@@
 
-		\todo[inline]{Double check this calculation with David to make sure I have accounted for the tension terms correctly.
-For some reason, Elliott uses x's in both the x and y equations...
-Is this a typo?}
-
 		 At this point, comparing equations 3.13 with 3.14 reveals we have identified 8 nontrivial equations (x and y derivatives; ignoring bound binding domain 0).
@@
 For a detailed calculation see the appendices.
-
-		 \todo[inline]{TODO: add appendices with full matrix equations}
 
@@
 This is not purely for convenience of notation, but rather is important for storing data.
-We will want the ability to calculate the total step length.
+We want the ability to calculate the total step length.
 Doing this requires knowledge of which motor domain initiates the stepping cycle.
@@
 
-		In this state, both binding domains are attached to the microtubule and therefore, a degree of freedom has been removed from our system.
+		In the both bound state, both binding domains are attached to the microtubule and therefore, some degrees of freedom have been removed from our system.
 This enables us to simplify the dynamic equations in order to take advantage of the new, constrained geometry.
@@
 			\includegraphics[width=0.75\columnwidth, angle=-90]{bothbound.pdf}
-			\caption{\textbf{Both bound} state with the new angles and lengths shown.}
+			\caption[The both bound state]{\textbf{Both bound} state with the new angles and lengths shown.}
 			\label{fig:bothbound}
@@
 Therefore, specifying $\theta_{nm}, \theta_{fm}$, and $\ell$ is enough to determine the geometry of the system.
-The intermediate variables are calculated by wild application of the law of cosines.
+The intermediate variables are calculated by multiple applications of the law of cosines.
 		\begin{align}
@@
 	\section{Binding and Unbinding}
-	To keep the simulation simple, we have chosen a very physically reasonable and uncomplicated binding model with a minimum amount of assumptions.
-The two key processes, binding and unbinding, are controlled by two parameters called the binding rates.
+	To keep the simulation simple, we have chosen an uncomplicated binding model which requires a minimum amount of assumptions.
+The two key processes, binding and unbinding, are controlled by two parameters called the binding rates (probability per unit time).
 For binding, we simply assume that a binding event occurs at a certain rate whenever a binding domain is close enough to the microtubule.
@@
 
-	where $\rho_b$ is a probability per second and $k_b$ is a constant. \\
+	where $\rho_b$ is the rate and $k_b$ is a constant. \\
 
@@
 		\includegraphics[width=0.8\columnwidth]{yildiz_tension_dependence}
-		\caption{\textbf{Tension dependent stepping} is shown for a typical dynein (non-mutated).
+		\caption[Tension dependent stepping]{\textbf{Tension dependent stepping} is shown for a typical dynein (non-mutated).
 There is a clear, negative correlation between the step size and interhead separation.
@@
 	As figure \ref{fig:yildiz_tension} indicates, a large interhead separation leads to more likely stepping.
-Furthermore, trailing steps are favored-- this means steps where the back foot begins the motion (like a normal step) are more likely.
+Furthermore, trailing steps are favored-- this means steps where the back foot begins the motion (like a normal human step) are more likely.
 To capture this behavior, we use an angle dependent exponential factor in the binding rate.
@@
 	\begin{equation}
-	\rho_{ub} = k_{ub}e^{-c(\theta_b-\theta_{b,eq})}
+	\rho_{ub} = k_{ub}e^{c(\theta_b-\theta_{b,eq})}
 	\end{equation}
@@
 unbinding depends on the angular separation of the binding domain from it's equilibrium position.
-If the $\theta_b$ is large and positive, then the unbinding rate is very small.
-If $\theta_b$ is less than $\theta_{b,eq}$, then the unbinding rate is very large.
+This means that for negative values of this constant, a large $\theta_b$ should yields a very small unbinding rate.
+Similarly, if $\theta_b$ is less than $\theta_{b,eq}$, then the unbinding rate is very large.
 This will favor the lagging foot because when dynein has a large interhead separation, the lagging $\theta_b$ is very small and the leading $\theta_b$ is very large as shown in the following figure.
@@
 		\includegraphics[width=0.7\columnwidth, angle=-90]{tension_dependence_edge_case}
-		\caption{\textbf{A Stretched dynein} illustrates the angular dependence of the unbinding model.
+		\caption[Stretched dynein]{\textbf{A Stretched dynein} illustrates the angular dependence of the unbinding model.
 In this configuration $\theta_{nb}$ is very small and is therefore much more likely to unbind than $\theta_{fb}$.}

### 2019-05-07 papers/waczak-thesis/thesis/chapters/conclusion.tex

We have developed a Brownian dynamics simulation which effectively models the locomotion of the dynein motor protein. By manipulating our binding and unbinding rate parameters together with the spring constants for each domain, we are able to reproduce step length and velocity distributions as measured experimentally. Furthermore, directed motion towards the same end of the microtubule was achieved across all random number seeds without the need to introduce a separate model for the structure of the microtubule.

In an effort to corroborate the results of research on the tension dependence of dynein stepping, we introduced an angle dependent unbinding rate which favors lagging foot steps at large inter-domain separations. Simulations with this unbinding model indicate that the one bound and both bound configurations are largely uncorrelated. In other words, the initial configuration of dynein does factor in to which domain steps, but it does not correlate with the final state after the next binding event. This unexpected result is contrary to experiment and has led us to begin developing a new simulation for which we only dynamically simulate the one bound state and use Monte Carlo methods to analyze distributions of possible both bound states. We anticipate that this new simulation will be significantly easier to implement and should lead to faster simulations.

The flexible design and fast computation time relative to other simulation methods mean that our model can be easily applied to test other experimental hypotheses. For example, a popular mode of research is to use an optical tweezer to test how much force a dynein generates when pulling cargo. Our simulation can easily accommodate additional forces and will allow us to examine how the motion deviates from the case of a free dynein on a microtubule. Future work may also integrate a second dimension into the dynamics enabling us to simulate how dynein navigates around obstacles on it's 3 dimensional surface. By making small additions and adjustments like this, we believe that our simulation will help shed light on exactly how dynein moves throughout the cell.

### 2019-05-07 papers/waczak-thesis/thesis/chapters/methods.tex

--- 2019-02-13 papers/waczak-thesis/thesis/chapters/methods.tex
@@
+\section{The Code}
+The simulation code was written in C++ in order to take advantage of the language's speed and object-oriented programming features.
+The equations of motion for our model in each state form a linear system of coupled first order differential equations for the domain velocities which we solved directly using Mathematica.
+We employed git version control to log changes to the code base-- our digital lab notebook.
+Data sets were stored locally and data used for our analysis was added to an online repository.
+An up-to-date version can be found at \url{https://github.com/droundy/dynein_walk}.\\
+
+Armed with equations for each domain velocity, we can now describe how the simulation evolves our model through time, that is, how we integrate for the time evolution of each state \textit{and} how we negotiate binding and unbinding events.
+
+	\section{Time evolution: Euler's method}
+	There are countless numerical methods for integrating differential equations.
+Popular methods for molecular dynamics simulations typically include Verlet integration or $n^{th}$ order Runge-Kutta.
+The first is valuable as it preserves time-reversal symmetry and the second integrates to a high level of precision.
+These properties are nice, but the randomness of Brownian motion means that there is little sense in running a simulation backwards and the degree of extra precision afforded is meaningless.
+We therefore employ perhaps the simplest integration scheme: Euler's method.
+\\
+
+	Euler's method assumes that a function $f$ can be treated as locally linear so that the tangent line is a good approximation for the value of the function.
+Therefore, if we know the value of $f$ at some time $t$, then the value of the function at a nearby time $t+\Delta t$ can be approximated by
+	\begin{equation}
+		f(t+\Delta t) = f(t)+f'(t)\Delta t
+	\end{equation}
+	where $\Delta t$ is understood to be small. We apply this scheme to the system of equations given by equation (3.15) to adjust the positions of each domain and \textit{move} the protein.
+
+	\subsection{The Random Force}
+	As noted in section 3.1, dynein experiences a frequent, random interaction force due to collisions between each domain and the surrounding water molecules.
+To simulate this extra force, we sample from a zero centered Gaussian distribution for each domain during each time step.
+
+	\subsection{Putting it all together}
+	The last piece of the simulation is deciding when dynein has binds to or unbinds from the microtubule.
+This is accomplished via turning the binding (eq 3.26) and unbinding rates (eq 3.27) into probabilities, e.g.
+	\begin{align}
+		P_{\text{bind}} &= \rho_b\; \Delta t \\ 
+		P_{\text{unbind}} &= \rho_{ub}\;\Delta t
+	\end{align}
+
+	During each time step, we first update the velocity of each domain and then use equation (4.1) to evolve their positions.
+Next, we calculate the binding/unbinding probabilities for equations (4.2) and (4.3).
+Finally, we \textit{roll a die} to select a random number in the interval $[0,1]$.
+If this number is below the binding/unbinding probability, we record the step and then change dynein's state.
+If it is above, we repeat the process and time evolve the protein again.
+\\
+
+	This process is outlined for the one bound state in the following flowchart.
+
+	\begin{figure}[!hbt]
+		\centering
+		\includegraphics[width=0.39\columnwidth]{One_bound_sim_flowchart.pdf}
+		\caption[One bound simulation flow chart]{\textbf{One bound simulation flow chart} showing how the simulation is performed for the one bound state.
+Note that we do not allow dynein to pass through the microtubule as this is a 2-dimensional simulation.}
+	\end{figure}
+
+	 \newpage
+
+\section{Determining constants of the model}
+In order to determine the stalk and tail lengths $\ell_S, \ell_T$, domain radii, and the set of equilibrium angles $\{\varphi_{i,\text{eq}}\}$, we examined microscopy images of dynein in various configurations.
+The following figure shows a cartoon of the model superimposed on images of real dynein in what we identify as the both bound and one bound states.
+\begin{figure}[hbt!]
+	\centering
+	\includegraphics[width=0.3\columnwidth]{burgess-model-figure.pdf}
+	\includegraphics[width=0.5\columnwidth]{grotjahn-model-figure.pdf}%
+	\caption[Model parameters determined from experiment ]{\textbf{Model parameters determined from experiment} Left: the both bound model is superimposed over dynein micrograph.
+The arrow indicates 15nm.
+Image taken from \cite{burgess2003dynein}.
+Right: cryo-electron tomograph of dynein with the one-bound model overlaid.
+Image taken from \cite{grotjahn}.}
+	\label{fig:superimpmosed}
+\end{figure}
+Figure \ref{fig:superimpmosed} shows example images of micrographs used to determine the model constants.
+In order to account for the fact that we idealize the stalks and tail as thin, massless rods, we slightly increase the size of each domain to account for any extra drag.
+Interestingly, these images suggest an angle of $0^\circ$ for both states.
+
 \section{Testing the model} 
-\subsection{Sanity Checks}
-This sub section will be for the various methods we used to ensure our model is behaving reasonably 
-\subsubsection{Verifying size of time step} 
-Here I will talk about how we found autocorrelations functions for each domain energy at various values of dt in order to verify our time step is as large as can be
-\subsubsection{Energy conservation and the Equipartion theorem} 
-talk about code to check that we satisfy energy 
-\subsection{Fitting to other studies}
+To test the model we ran multiple simulations varying the spring constants and binding / unbinding rates.
+Having so many degrees of freedom makes using any kind of minimization process challenging to implement and far too long to simulate.
+Nevertheless, we can still be clever by using reported velocities (for example \cite{dewitt2012cytoplasmic} reports 124 nm/sec) to estimate the time spent in the one bound and both bound states.
+With this information we can set the binding and unbinding rates in such a way as to simulate only the both bound state \textit{or} the one bound state.
+With these simulations we can get good estimates for the rate constants.
+
+With good estimates for these constants, we then refine the values by fitting our stepping statistics to those of experiments such as shown in figures \ref{fig:weihong histogram} and \ref{fig:yildiz_tension}.

### 2019-05-07 papers/waczak-thesis/thesis/chapters/results.tex
big thesis update 1
thesis update 2
thesis update

@@
-\todo[inline]{TODO: I plan to add description and section headings over break}
-\todo[inline]{TODO: add discussion of powerstroke vs winch models. Discuss simple modifications to simulation parameters to try and fit for this alternate mechanochemical model}
+\section{Best-fit parameters}
+After running multiple simulations as discussed in section 4.4, the current set of best parameters for our model are shown in the table below
+\begin{table}[!hbt]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+		\hline
+		$\mathbf{k_b}$&  $\mathbf{k_{ub}}$ &  $\mathbf{c_b}$&  $\mathbf{c_m}$& $\mathbf{c_t}$ & $\mathbf{\ell_s}$ & $\mathbf{\ell_t}$ & $\mathbf{r_t}$ & $\mathbf{r_m}$ &$\mathbf{r_b}$ & $\mathbf{dt}$ & $\mathbf{c}$\\
+		$s^{-1}$ & $s^{-1}$ & $k_bT$ & $k_bT$ & $k_bT$& nm & nm & nm & nm & nm & $s$ &  \\
+		\hline \hline
+		$9.5e9$ & $1e20$ & $0.08$ & $1.05$ & $0.36$ & $20.75$ & $23.0$ & $6.0$ & $5.5$ & $1.75$ & $1e10$ & $0.35$\\ 
+		\hline
+	\end{tabular}
+\caption[Best parameters]{Current set of best fit parameters}
+\label{table:params}
+\end{table}
 
-\todo[inline]{TODO: combine 5.1 with 5.2 to explain leading vs lagging}
-\todo[inline]{TODO: consider removing leading lagging axis labels in 5.1 if redundant with figure caption} 
-\todo[inline]{NOTE: it looks like there may be an issue with the middle most cartoon in 5.3. The tail does not appear to be the correct size}
-\todo[inline]{TODO decrease overall width of tail in cartoon dynein. Increase thickness of stalk} 
-\todo[inline]{TODO: Check to make sure time axis in final panel of fig 5.4 is actually a log scale}
+With these parameters, the following analysis was performed for multiple simulations with a variety of different random number seeds.
 
 \section{Stepping}
-\begin{figure}
+
+Our model is able to achieve directed motion with clear evidence of the desired Brownian jiggling. All simulations show a net displacement in the positive x direction.
+\begin{figure}[!hbt]
 	\centering
 	\includegraphics[width=1\columnwidth]{paper_trajectory_plot}
-	\caption{\textbf{Trajectory Plot} Vertical and horizontal projections of each of binding domains.
+	\caption[Trajectory plot]{\textbf{Trajectory Plot} for a small subset of steps.
+Vertical and horizontal projections for the trajectory of each binding domain are plotted in red and blue.
 Directed motion is clearly seen in the positive slope of the x-projection graph.
@@
 
+As y-projection plot in figure \ref{fig:trajectory} indicates, the model performs a wide diffusive search for the microtubule, assuming a wide range of configurations along the way.
+The cartoons corresponding to the black triangles in the x and y projection plots show the motor domains travel around the tail linker during the stepping cycle.
+This behavior is suggestive of the power-stroke model proposed by \cite{burgess2003dynein} and others.
+It is also worth noting that the y-projection plot suggests an average binding domain height $>0$.
+This is contrary to the popular depictions of dynein with the binding domains nearly scrubbing the microtubule until binding.\\
+
+Dynein's stepping velocity can be seen in the positive slope of figure \ref{fig:trajectory}.
+This velocity is directly related to the stepping rates.
+To increase the model's velocity, simply increase both the binding and unbinding rates.
+\\
+
+Running a longer simulations at multiple random number seeds allows us to gather more stepping statistics. A sample of these are shown in figure \ref{fig:statistics}.
+
 \begin{figure}
@@
 	\includegraphics[width=0.85\columnwidth]{paper_model_behavior}
-	\caption{\textbf{Stepping statistics} trajectories run with different random number seeds all show forward directed motion.
+	\caption[Model Stepping Statistics]{\textbf{Stepping statistics} trajectories run with different random number seeds all show forward directed motion.
 Step lengths have a similar distribution to experiment although steps of zero length are not measured experimentally.
 }
-	\label{Fig:statistics}
+	\label{fig:statistics}
 \end{figure}
 
-\section{One bound and both bound correlations}
+The first graph in figure \ref{fig:statistics} shows the x position trajectory plot for the same simulation run with many different random seeds.
+An experimental trajectory plot is shown in blue with data taken from \cite{dewitt2012cytoplasmic}.
+This figure illustrates that even for long simulations, the model shows directed motion despite occasionally stepping backwards.
+Furthermore, we can see that average velocity across each of the model simulations agrees well with the experiment.
+
+The second graph in figure \ref{fig:statistics} shows a signed step length histogram comparing the model with data from \cite{qiu2012dynein}.
+Here negative values of step length indicate a backwards step.
+The shape of the histogram matches well with the experiment despite missing the notable dip at zero step length.
+This is likely due to the fact that a step of zero length (i.e.
+a stutter step) can not be distinguished experimentally from the typical Brownian motion.
+\\
+
+Finally, we plot histograms for the time spent in the one bound and both bound states during each simulation.
+The red line indicates our estimates for these values based off of experimental stepping velocities.
+It is interesting to note that in both cases, the average time spent in each state is below this estimate.
+Despite this, we can clearly see that the median one bound time is around $0.0015-0.003$ seconds while the both bound time is between lies somewhere between $0.015-0.03$ seconds-- an order of magnitude higher.
+This suggests that dynein spends most of its time in the both bound state.
+
+\section{State correlations}
+If the both bound time is significantly higher than the one bound time, perhaps the two states are uncorrelated.
+In other words, does our model predict that the configuration of dynein before a step is unrelated to the final configuration when it rebinds again?
+To investigate this possible result, we plot the initial displacement versus the step length for the steps taken during all of the simulations.
+We consider these quantities as signed distances.
+For the step length, this indicates whether or not the model steps forwards or backwards.
+For the initial displacement, the sign indicates which binding domain initiates the step as indicated in the following figure.
+\begin{figure}[!hbt]
+	\centering
+	\includegraphics[angle=-90, width=1\columnwidth]{leading_vs_lagging}
+	\caption[Leading vs Lagging Steps]{Diagram illustrating a leading foot step (a) and a lagging foot step (b).}
+\end{figure}
+
 \begin{figure}[!hbt]
@@
 	\includegraphics[width=0.75\columnwidth]{paper_displacement_vs_step_length}
-	\caption{\textbf{Two dimensional histogram} comparing the total signed step length to
+	\caption[Initial displacement vs Step Length]{\textbf{Two dimensional histogram} comparing the total signed step length to
 			the signed initial displacement between the binding domains. A positive value
@@
 
-\begin{figure}[!hbt]
-	\centering
-	\includegraphics[angle=-90, width=1\columnwidth]{leading_vs_lagging}
-	\caption{Diagram illustrating a leading foot step (a) and a lagging foot step (b).}
-\end{figure}
+Figure \ref{fig:displacement_vs_step_length} is a two-dimensional histogram for which step lengths are binned against initial displacements.
+A linear fit through the data (orange dashed line) indicates that the distribution is shifted vertically.
+This reflects the model's preference for stepping in the positive direction.
+Interestingly though, the slope of this fit appears much stepper than the same fit for experimental data from \cite{dewitt2012cytoplasmic}.
 
-\section{Possible Monte Carlo}
+If we define the final step length to be 
+\begin{equation}
+\text{final displacement} = \text{initial displacement} + \text{step length },
+\end{equation}	
+then clearly our model indicates that the final displacement is roughly the same regardless of the initial displacement-- a conclusion at odds with the experimental data.
+This discrepancy may be due to the low number of data points in \cite{dewitt2012cytoplasmic}, but it can not be explained away by the expected lack of zero nm step observations.
+
+\section{Simulating states separately}
+Our simulations appear to predict that the one bound and both bound states are uncorrelated with each other. Therefore, one reasonable conclusion is: Why simulate them together in the first place? \\
+
+We are now developing a simplified simulation code for our model which still performs the full Brownian dynamics for the short lived one bound state but takes advantage of this result by removing the both bound portion of the simulation all together.
+Instead, we seek to use Monte Carlo methods to generate both bound stepping statistics by determining unbinding based on the distribution of possible both bound configurations for a given initial displacement.
+\\
+
 \begin{figure}[!hbt]
@@
 	\includegraphics[width=1\columnwidth]{energy_landscape}
-	\caption{\textbf{Energy Landscape} graph showing the total energy of the dynein for a given binding domain displacement $L$.
+	\caption[Energy Landscape]{\textbf{Energy Landscape} graph showing the total energy of the dynein for a given binding domain displacement $L$.
 The yellow and red dots correspond to the minimum and maximum energy configurations for which a cartoon is shown on the right.}
@@
 \end{figure}
+In figure \ref{fig:energy_landscape} we can see a contour plot of the energy associated with dynein in the both bound state for all possible allowed combinations of near motor and far motor angles given an interhead separation of $16$ nm.
+Indicated on the graph are the minimum and maximum energy configurations (orange and red respectfully).
+The total energy appears to increase monotonically outwards from the minimum suggesting that the orange configuration shown to the right of the figure is a reasonable representative for the typical both bound state with this interhead separation.
+
+We anticipate that a simulation distinguishing between the two states will significantly improve the computation time and enable us to fit simulation parameters more tactfully.
 

### 2019-05-07 papers/waczak-thesis/thesis/thesis.tex
thesis update 2
make thesis compile

@@
 \graphicspath{{./images/},{../../../plots/}} % where to find images
-\usepackage[a4paper, margin=1in]{geometry} % change margins 
+\usepackage[letterpaper, margin=1in]{geometry} % change margins 
 \usepackage{fancyhdr} % add a header / footer 
@@
 \title{
-	{Simulating the Brownian Dynamics of a Two-dimensional Model for the Dynein Motor Protein}\vspace{1.5em}\\
+	\large{Drunken Walking: A Novel Brownian Dynamics Simulation for the Mechanochemical Cycle of the Dynein Motor Protein}\vspace{1.5em}\\
+	\normalsize{by}\\
+	\large{John Waczak} \vspace{2em}\\ 
+	\normalsize{an undergraduate thesis advised by David Roundy submitted to \\ 
+		Department of Physics, Oregon State University}\vspace{2em}\\
+	\normalsize{in partial fulfillment of the requirements for the degree of}\\
+	\normalsize{Baccalaureate of Science in Physics}\vspace{1.5 em}\\
+	\normalsize{Submitted \today}\vspace{3em}\\
 	\includegraphics[width=0.5\columnwidth]{OSU_logo.png}\vspace{0.5em}\\
-	\large{Oregon State University}
 }
-\author{John Waczak}
-\date{\today}
+\date{}
 
@@
 	\maketitle
-	\todo[inline]{TODO: Fix formatting of title page}
 	\chapter*{Abstract}
-	\vspace{-3 em}word count: \textbf{345}\\
+	\vspace{-3 em}word count: \textbf{282}\\
 
@@
 When these motors misbehave, fundamental processes like axonal transport and muscle contraction fail.
-Observational techniques for studying biomolecules have revealed much about the different conformational states achieved by dynein during its stepping cycle and have established a base of relevant statistics such step lengths, velocities, and generated forces among others.
-Despite these advancements, the ability to image the full molecule for an entire stepping cycle remains beyond the capabilities of the current experimental apparatus.
+Experimental techniques for studying biomolecules have revealed much about the different conformational states achieved by dynein during its stepping cycle and have established a base of relevant statistics such step lengths, velocities, and generated forces among others.
+Despite these advancements, the ability to image the full molecule for an entire stepping cycle remains beyond current experimental capabilities.
 
@@
 We treat the protein as a system of massive domains held together by rigid rods steered towards equilibrium configurations by spring like torques and time evolved using Brownian dynamics.
-With our current set of parameters, the model displays directed motion with step length and velocity distributions ( give statistics here ) in agreement with experiment.
-Our simulations also suggest that there is no correlation between the conformation of dynein before and after a step.
+With our current set of parameters, the model displays directed motion with step length and velocity distributions in agreement with experiment.
+Our simulations also suggest that there is no correlation between the conformation of dynein before and after it takes a step.
 Our results indicate that a more computationally efficient simulation can be achieved with a two state system where a post power stroke state is selected from a distribution via a Monte Carlo simulation and binding is then simulated with the full Brownian dynamics.
-We are optimistic that our simulations will be able to address the power stroke versus winch model debate.
-
-	\todo[inline]{TODO: Add in specific data to results}
-	\todo[inline]{TODO: Fix formatting to include "a thesis submitted in completion of..." etc.}
-
-	\chapter*{Acknowledgments}
-	I want to thank ...
 
 	\tableofcontents
+	\listoffigures
+	%\listoftables
 
@@
 	\input{./chapters/methods}
-	\chapter{Results}
+	\chapter{Results \& Discussion}
 	\input{./chapters/results}
+	\chapter{Conclusion}
+	\input{./chapters/conclusion}
 \bibliography{references}
-\bibliographystyle{prl_like.bst}
+\bibliographystyle{plain}
 \end{document}

### 2020-07-30 papers/paper/paper.tex
make it all build on my new computer

@@
-\documentclass[9pt,twocolumn,twoside]{pnas-new}
+\documentclass[9pt,twocolumn,twoside]{article}
 % Use the lineno option to display guide line numbers if required.
@@
 % the follow ing causes latex to not wait interactively
-\nonstopmode
-
-\setboolean{displaywatermark}{false}
+% \nonstopmode
 
@@
 
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} = Template for a one-column mathematics article
-% {pnasinvited} = Template for a PNAS invited submission
-
 \title{Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping}
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[a,c,1]{Author One}
+\input{../../data/paper_params.tex}
 
-\affil[a]{Oregon State University}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Lead author last name}
-
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{Please provide details of author contributions here.}
-\authordeclaration{Please declare any conflict of interest here.}
-\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
-\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}
-
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{dynein $|$ Brownian dynamics $|$ powerstroke $|$ modeling}
+\begin{document}
+\maketitle
 
@@
 \end{abstract}
-
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\input{../../data/paper_params.tex}
-
-\begin{document}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-\verticaladjustment{-2pt}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
 
@@
 
-\dropcap{D}ynein is a motor protein which generates motion for various cellular processes.
+Dynein is a motor protein which generates motion for various cellular processes.
 Cytoplasmic dynein-1, here referred to as ``dynein,'' is a motor which performs cargo transport and aids in nuclear division.
@@
 
-\begin{minipage}{\linewidth}%% [tbhp]
+\begin{table}
   \centering
   \begin{tabular}{lrrr}
-    Parameter & Model & Experimental & Source \\
-    \midrule
+    Param & Model & Experimental & Source \\
+    \hline
     $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
@@
     $R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\
-    \bottomrule
+    \hline
   \end{tabular}
-
-  \begin{minipage}{\linewidth}
-    \small
-    \textbf{Table 1.
-Parameters used in simulation.} $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
+  \caption{Parameters used in simulation.
+$c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
 $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
@@
 $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
-Parameters used for all simulations unless otherwise noted.
-  \end{minipage}
+Parameters used for all simulations unless otherwise noted}
   \label{tab:params}
-
-\end{minipage}
+\end{table}
 
@@
 
-\matmethods{
-
   \section*{Fitting $k_b$ and $k_{ub}$}
@@
     \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right)R^y_i\big)
-    \label{eq:ob-system}
+    \label{eq:ob-system-other}
   \end{multline}
@@
   \section*{Calculating force-dependent velocities}
-}
 
@@
   \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}\\
-  \includegraphics[width=\linewidth]{../../plots/stacked_displacement_histogram.pdf}
+  \includegraphics[width=\linewidth]{../../plots/paper_stacked_displacement_histogram.pdf}
   \caption{\textbf{Analysis of stepping independence.} \textbf{a.)} Heatmap of MTBD displacement before and after a stepping cycle.
@@
 
-\showmatmethods
-
 \section{To do items}
@@
 
-% \pnasbreak splits and balances the columns before the references.
-% If you see unexpected formatting errors, try commenting out this line
-% as it can run into problems with floats and footnotes on the final page.
-\pnasbreak
-
+\bibliographystyle{plain}
 \bibliography{paper}

### 2020-07-30 papers/paper/figures/fac-svgs.py

@@ -2,4 +2,4 @@ import glob
 
 for svg in glob.glob('*.svg'):
     basename = svg[:-4]
-    print('| inkscape -D --export-pdf {basename}.pdf {basename}.svg'.format(basename=basename))
+    print('| cairosvg -o {basename}.pdf {basename}.svg'.format(basename=basename))

### 2020-07-30 papers/paper/paper.tex
remove obsolete todo and unsrt the bibliography

@@
 
-\section{To do items}
-
-\subsection{Anyone tasks}
-\begin{enumerate}
-\item Movie of dynein walking as a supplemental figure
-\end{enumerate}
-
-\subsection{John}
-\begin{enumerate}
-\item Proofread the algorithm description, improve its writing, and
-  check against code.
-\item Run a low-ATP simulation for comparison data.
-\item Consider a no-binding simulation and a separable model.  Create
-  a figure demonstrating/testing whether the histogram of final
-  displacement is independent of initial displacement.
-\item Consider a simple Monte Carlo that just uses our no-unbinding
-  and no-binding simulations to model dynein (like Yildiz).
-\item Debug initial/final displacement plot - it looks like there's a weird
-  threshold at final displacement = 0, is that normal?
-\end{enumerate}
-
 \section{Papers we should cite}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{paper}

### 2020-08-13 papers/paper/paper.tex
Make papers/paper/paper.pdf build on Bennet from a fresh dynein_walk clone. Needed to add amsmath and graphicx packages. Not sure how this was building before??
add TODO stuff to paper

@@
 
+\usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage{subcaption}
@@
 \end{abstract}
+
+\section*{TODO August 2020}
+\begin{enumerate}
+  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
+  \item Articulate data we fit to
+  \begin{enumerate}
+    \item Velocity -> unbinding rate
+    \item Ratio of leading vs trailing steps -> exponential parameter
+    \item Average step length -> other parameters
+    \item Yildiz weird slope -> sticky rate + binding rate
+    \item Avoid instant rebinds -> sticky rate
+    \item Time to kick from MD??
+    \item efficiency (affects instant rebind)
+  \end{enumerate}
+  \item Do the fit (requires 1 above)
+  \item Could have a fixed binding immunity time rather than sticky rate
+  \paragraph{Advantages of immunity time}
+  \begin{enumerate}
+    \item Might accurately reflect a diffusive escape from an energy well
+  \end{enumerate}
+  \paragraph{Advantages of sticky rate}
+  \begin{enumerate}
+    \item Accurately reflects the dynamics of a chemical process
+  \end{enumerate}
+\end{enumerate}
 

### 2020-08-20 papers/paper/paper.tex
Add section on how we fit parameters to paper.tex

@@
 
-  \section*{Calculating leading/lagging probability vs displacement}
+  %% \section*{Calculating leading/lagging probability vs displacement}
 
-  \section*{Calculating force-dependent velocities}
+  %% \section*{Calculating force-dependent velocities}
+
+\section*{Fitting model parameters}
+
+\subsection*{$L_t$, $L_s$, $R_b$, $R_m$, $R_s$, $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$}
+Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}.
+In the class average image from Burgess \textit{et.
+al.} \cite{burgess} the different tail-motor-MTBD angles were taken to indicate that left stalk's motor domain was in the apo post-powerstroke state, and the right stalk's motor domain in the ADP-bound pre-powerstroke state.
+In the Grotjahn \textit{et.
+al} \cite{grotjahn} density map, both motor domains were taken to be in the post-powerstroke state.
+
+\subsection*{$c_b$, $c_m$, $c_t$}
+Spring constants $c_b$, $c_m$ and $c_t$ were fit using the dynein step length distribution from \cite{yildizpaper}.
+Three spring constants were drawn uniformly from range $[0.0, 4.0]$ and a simulation was run for 10s simulation time with $k_b=X$, $k_{ub}=Y$, $k_{stk}=Z$, and other parameters noted in Table \ref{tab:params}.
+One thousand simulations total were run, and the set of spring constants which yielded the lowest root-mean-squared histogram error between the simulation and experimental step length distributions was chosen.
+\textbf{Probably need to rerun this using our final $k_b$, $k_{ub}$ and $k_{stk}$.}
+
+\subsection*{$k_{ub}$}
+The unbinding rate $k_{ub}$ was estimated from velocity data in the Yildiz \textit{et.
+al.} experiment.
+The $k_{ub}$ value which led to an average velocity of 124 nm/s was chosen, as shown in Figure \ref{fig:behavior}.
+
+\subsection*{$c$}
+The exponential unbinding parameter $c$ was estimated using the likelihood of leading/lagging head unbinding vs interhead separation data provided in DeWitt \textit{et.
+al.} \cite{dewitt}.
+The value of $c$ was chosen which led to the lowest root-mean-squared error in P(lagging step) vs interhead separation between the experiment and the model, as shown in Figure \ref{fig:tensiongating}.
+All other parameters were held at the values in Table \ref{tab:params}.
+
+\subsection*{$k_b$, $k_{stk}$}
+The sticky rate and binding rate were chosen ... based on the Yildiz initial-vs-final displacement slope?
 

### 2020-09-19 papers/paper/paper.tex
Added plots to front page of paper

@@
 \end{enumerate}
+
+\section*{Plots from MC}
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09.pdf}
+\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+\label{fig:final_disp_prob}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09.pdf}
+\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+\label{fig:step_length_prob}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09.pdf}
+\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
+\label{fig:step_length_prob_den}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_5.50e+09_1.00e+09.pdf}
+\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
+\label{fig:prob_lagging}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_5.50e+09_1.00e+09.pdf}
+\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
+\label{fig:bothbound_time}
+\end{figure}
+
+\newpage
 

### 2020-10-12 papers/paper/paper.tex
Added ob time plot on paper
Added small edits to plotting script
Fixed fac because of renaming

@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
 \caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
 \caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
 \caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_5.50e+09_1.00e+09.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563.pdf}
 \caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_5.50e+09_1.00e+09.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
+\caption{\textbf{Onebounnd Time} Dimentions: $s$.}
+\label{fig:ob_time}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563.pdf}
 \caption{\textbf{Bothbound Time.} Dimentions: $s$ .}

### 2020-10-13 papers/paper/paper.tex
Changed naming and worked on paper

@@
 
-Here we present a course-grained model of cytoplasmic dynein which reduces the mechanochemical cycle down to pre- and post-stroke states.
+Here we use a Monte Carlo simulation that investigates dynein's inter-step correlations as it moves along the MT.
+We model cytoplasmic dynein by reducing the mechanochemical cycle into two states: the pre-stroke and post-stroke states.
 We use cryo-EM data to create rough structural models of these conformers, and impose inter-domain tension and elastic restoring forces to describe the dynamics within each conformer.
@@
 This minimal model spontaneously generates a powerstroke-like dynamic mechanism, and uses it to produce bidirectional motion.
-The model also reproduces several experimental measures, such as step size, velocity and force-mediated directionality control.
+The model also reproduces several experimental measures, such as step length and the probability of stepping.
+%% velocity and force-mediated directionality control.
 
@@
 \section*{Poststroke motion equations derivation}
-  Brownian dynamics was also used for the poststroke case.
+Brownian dynamics was initially used for the postroke case but was later changed to be simulated with Monte Carlo methods.
+After running simulations undergoing Brownian dynamics for both states, we saw a large time spent in this poststroke state causing it to frequently reach equilibrium and be independent of our dynein's stepping pattern.
+We decided to shorten this process by simulating this state with Monte Carlo algorithms that sample from a Boltzmann distribution of the dynein's total energy.
+*Talk about choosing random configuration of dynein and calculating its total energy from each conformer. 
+%% Brownian dynamics was also used for the poststroke case.
 Due to the added constraint of both binding domains being fixed to the microtubule, the model is fully described by angles $\theta_{nm}$ and $\theta_{fm}$; see Figure \ref{fig:model}.
@@
 
-  \begin{multline}
-    \dot{X_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F^{spr}_x(\theta_{nm}, \theta_{fm}) + \\
-    \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right) + R^x_i\big)
-    \label{eq:bb-system}
-  \end{multline}
+%%  \begin{multline}
+%%    \dot{X_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F^{spr}_x(\theta_{nm}, \theta_{fm}) + \\
+%%    \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right) + R^x_i\big)
+%%    \label{eq:bb-system}
+%%  \end{multline}
 
-  \begin{multline}
-    \dot{Y_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F^{spr}_y(\theta_{nm}, \theta_{fm}) + \\
-    \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right) + R^y_i\big)
-    \label{eq:bb-system}
-  \end{multline}
+%%  \begin{multline}
+%%    \dot{Y_{i\neq\{nb, fb\}}}\left(\theta_{nm},\theta_{fm}, \dot{\theta_{nm}}, \dot{\theta_{fm}}\right) = \frac{1}{\gamma_i}\big(F^{spr}_y(\theta_{nm}, \theta_{fm}) + \\
+%%    \lambda_i\left(Y_{i+1}-Y_i\right) + \lambda_{i-1}\left(Y_i-Y_{i-1}\right) + R^y_i\big)
+%%    \label{eq:bb-system}
+%%  \end{multline}
 
-  Coordinate velocities are similarly linear with $\dot{\theta_{nm}}$ and $\dot{\theta_{fm}}$.
+%%  Coordinate velocities are similarly linear with $\dot{\theta_{nm}}$ and $\dot{\theta_{fm}}$.
 This system has six independent equations and six unknowns $\dot{\theta_{nm}}, \dot{\theta_{fm}}, \lambda_{nb}, \lambda_{nm}, \lambda_{t}, \lambda_{fm}$.

### 2020-11-24 papers/paper/paper.tex
remove file name extensions to make build work again

@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36}
 \caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36}
 \caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09_0.08_1.05_0.36}
 \caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
 \caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_5.50e+09_1.00e+09_0.08_1.05_0.36}
 \caption{\textbf{Onebounnd Time} Dimentions: $s$.}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563.pdf}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563}
 \caption{\textbf{Bothbound Time.} Dimentions: $s$ .}

### 2020-11-29 papers/paper/paper.tex
Coded picture data for mc dynein for every 50 steps

@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
 \caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
 \caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
 \caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
 \caption{\textbf{Onebounnd Time} Dimentions: $s$.}

### 2021-01-05 papers/jin-thesis/Chapters/2Dynein.tex
Added my thesis to repo

\section{What is dynein?}
\textit{Introduce dynein as motor protein . Maybe just a quick single paragraph or two of background knowledge on motor proteins and compare it to kinesin and myosin. Basic functions}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/dynein_on_MT.png}
	\caption[Dynein on Microtubule]{\textbf{Dynein on Microtubule} Artist’s illustration of a dimer of cytoplasmic dynein heavy chains bounded to microtubule. This rendition similarly illustrates dynein’s structure as a domain-rod system, where the unlabeled linker domain connects the two AAA+ domains to the tail. \cite{TheTrappistArt}}
	\label{fig:final_disp}
\end{figure}

\section{Functions}
\textit{Purpose in the cell. What does dynein do that helps the cell operate? It walks on microtubule towards minus end. It uses chemical energy from ATP hydrolysis to convert into mechanical energy to walk and transport cargo with information along the cell. }

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/retrograde_transport.jpg}
	\caption[Retrograde Transport]{\textbf{Retrograde Transport} \cite{Vale2003molecular}}
	\label{fig:transport}
\end{figure}

\section{Architecture}
\textit{In-detail background knowledge on structure of dynein. Talk about each domain and their roles. Binding domain, six AAA+ domains, tail, and cargo. Stalk and linker that attaches things together. How the structure is so much larger than that of kinesin. dynein has flexibility because of its linker and in order to compensate for its huge domains. }

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/dynein_polypeptide.jpg}
	\caption[Polypeptide Structure]{\textbf{Polypeptide Structure} \cite{GoodsellArt}}
	\label{fig:polypeptide}
\end{figure}

\section{Stepping}
\textit{Biology and chemistry of stepping. What is actually causing it to step? ATP hydrolysis. Maybe short introduction on stepping and go more in detail in Power Stroke model. Say there are multiple theories and models of how dynein steps. Powerstroke, Winch, etc. Power stroke is most accepted. It can step on microtubule that is made up of tubulin dimers, $\alpha$ and $\beta$ tubulins. They are normally 8nm apart and so experimentalists believe dynein average step is always factor of 8nm. }

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\columnwidth]{Figures/Onaxis.png}
	\caption[Stepping Axis]{\textbf{Stepping axis}  \cite{Dewitt2012} }
	\label{fig:YildizCorrelation}
\end{figure}

\subsection{Powerstroke Model}
\textit{Theorized model of stepping. Mechanochemical Cycle. Talk about ATP hydrolysis. Different conformational changes within a step. Look at linker and how it changes angles. Physically, it looks like it unbinds, stretches leg, then kicks forward, then diffuse back to MT.}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\columnwidth]{Figures/mechanochemical_cycle.jpeg}
	\caption[Mechanochemical Cycle]{\textbf{Mechanochemical Cycle}  \cite{Cianfrocco2015mechanism}}
	\label{fig:MechanochemicalCycle}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\columnwidth]{Figures/powerstroke.jpeg}
	\caption[Powerstroke]{\textbf{Powerstroke}  \cite{Carter2010communication} }
	\label{fig:Powerstroke}
\end{figure}

\section{Experimental Research on Dynein}
\textit{Most likely just short sections on experiments done on dynein.}
\subsection{Measuring}
\textit{How are experimentalists measuring dyneins stepping? Quantum dots on motor domains or quantum rod on tail, etc. }

\subsection{Interhead Coordination}
\textit{Purpose of my research. Trying to make model and fit to Yildiz analysis of dynein having interstep correlation. Dependency between step length and initial inter head separation.}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\columnwidth]{Figures/Yildiz_stepping.png}
	\caption[Stepping Correlation]{\textbf{Stepping Correlation}  \cite{Dewitt2012} }
	\label{fig:YildizCorrelation}
\end{figure}

### 2021-01-07 papers/jin-thesis/Chapters/1Introduction.tex

\textit{Introduce topic by talking about cells. Attention grabber, relate biophysics study to cancer reserach and many areas where we need to focus our research. Short and sweet, maybe 1 or 2 short paragraphs.}

	Neuroegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States. Scientists all over the world struggle to find the leading causes of these diseases and continue to hope for a breakthrough in science in attempt to prevent or even cure these fatal diseases. Although this breakthrough has yet to come, researchers discovered that one of the central causes of cell degeneration is motor protein failure. More specifically, defects in the motor protein dynein has been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties. However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and unpredicatable in nature. Thus, fully understandding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to solving the breakthrough.

\section{Background}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/dynein_walking_art.jpg}
	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} \cite{JohnsonArt}}
	\label{fig:final_disp}
\end{figure}

Cells are complicated. Despite their degeneracies, cells have the ability to move, perfectly divide, and spatially organize themselves. They are constructed by organelles surrdounded by a network of protein filaments called the cytoskeleton. The cytoskeleton is composed of microtubules (MT) that act as a walkway for motor protein soldiers to carry out the functions of the cell. These motor proteins consists of kinesin, myosin, and dynein.

\textit{THIS IS STRAIGHT FROM PROPOSAL, NEED TO FIX THIS AND ADJUST SO THAT MORE DYNEIN DETAILS GOES INTO CHAPTER 2}

In a eukaryotic cell, dynein is one of the three motor proteins that are responsible for the cell’s ability to move, divide, and spatially organize itself. Similar to the more researched kinesin, dynein conveys cargo along the microtubule track by using ATP to power its two binding domains (its “feet”). However, its walking-like movements along the track are very unpredictable and can vary in terms of distance and direction. Dynein’s two feet can also act independently from each other causing much more erratic and stochastic steps. However, despite dynein’s stochastic nature, dynein is still able to achieve processive motion due to the functions of its structure. Structurally, dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains. These domains are the tail domain, the linker domain, the six AAA+ domains, and the microtubule binding domains (See Figure 1). The AAA+ domains are responsible for ATP hydrolysis, in which converts chemical energy stored in ATP into mechanical work causing dynein’s motility.

Because dynein’s stepping is unpredictable in nature, its stepping mechanism has not been intensely studied as compared to its structure. Questions regarding the electrostatic interactions with the microtubule, ring stacking, discrete microtubule binding sites, or elasticity of the stalk are yet to be answered. A known and supported model to describe dynein’s motion is the powerstroke model, where ATP binding to an AAA+ domain triggers conformational changes that lowers the affinity of the binding domain for the microtubule, causing it to unbind and take a step . While the powerstroke model and other theorized stepping models exists, there are no such studies which use molecular dynamics to verify if these theorized mechanisms are feasible for the dynein motor to produce. There are studies that incorporate a computational model of dynein, but many use chemical rate transitions and assume independence of steps without simulating the precise protein dynamics within its step.

\section{Motivation}
\textit{Briefly write about the importance of dynein, how dynein is researched when studying neurological diseases, dynein stepping is understudied compared to other motor proteins, hard to model dynein because of random walking, there are almost no computational models of dynein that uses molecular dynamics, modelling dyenin can give us better understanding of why it moves the way it does, specific motivation for model: new research found that there is interhead coordination when stepping so maybe we can use that to base our model off of.}
\par

To bridge this gap, we propose a coarse-grained model of dynein that assumes a particle-rod structure for its various domains and uses Brownian motion to simulate the model’s behavior in physically realistic drag and diffusion conditions, while efficiently collecting a wide ensemble of statistics using Monte Carlo methods. We chose to use Brownian inspired motion to simulate dynein’s molecular dynamics in order to replicate dynein’s stochastic behavior under realistic conditions and produce its unpredictable stepping patterns observed from experiment. We call this process Brownian dynamics, as it replaces interactions the domains have with solvent molecules with a stochastic force and allows us to simulate large time scales compared to other molecular dynamics simulation. Likewise, Monte Carlo methods will allow us to visualize dynein as a system and associate its possible configurations as states. With our simulation following these methods, we can generate an ensemble of statistics and compare measured quantities with experiment. We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism. One of which being a question regarding dynein’s inter-step correlation.

### 2021-01-07 papers/jin-thesis/Chapters/5Results.tex

\section{Optimized Parameters}
\textit{Talk about best-fit parameters that matched experimentalists data. Include table with all parameters.}

\section{Stepping Patterns}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\columnwidth]{/../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0.png}
	\caption[Final Displacement Probability Distribution]{\textbf{Final Displacement Probability Distribution}}
	\label{fig:final_disp}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{Figures/step_length_hist.png}
	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
	\label{fig:step_length}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{Figures/prob_lagging_vs_init_L.png}
	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
	\label{fig:step_length}
\end{figure}

\textit{Analysis on stepping patterns and what the parameters of our model indicate. Does dynein take a lot of fast steps?}

\section{Agree with Experiment?}
\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job?}

### 2021-01-07 papers/jin-thesis/main.tex

\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage{float}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}

\usepackage{caption}
\usepackage{subcaption}

\usepackage{titlesec}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage[labelfont=bf, textfont=md]{caption}

\usepackage[square,numbers]{natbib}
\usepackage{indentfirst}

\title{
	\Huge{Modeling the mechanisms of dynein's step using Monte Carlo simulations and Brownian dynamics}\vspace{1em}\\
	\Large{Jin Kiatvongcharoen} \vspace{0.5em}\\ 
	\normalsize{Department of Physics, Oregon State University}\vspace{2em}\\
	\includegraphics[width=0.4\columnwidth]{OSU_logo.png}\vspace{1em}\\
	\normalsize{An undergraduate thesis advised by Dr. David Roundy}\\
	\normalsize{in partial fulfillment of the requirements for the degree of}\\
	\normalsize{Baccalaureate of Science in Physics}\vspace{1.5 em}\\
	\normalsize{Submitted \today}\\

}
\date{}

\begin{document}
    \maketitle
    \onehalfspacing

	\chapter*{Abstract}
	Molecular motor proteins are responsible for the cell’s ability to move, divide, and spatially organize itself. A defect within any of the three motor proteins can cause severe damage to the cell’s functionality and lead to neurological diseases. In order to fully understand the cause of such possible diseases, the motor protein dynein and more specifically its structure has been extensively studied. However, there has been limited research focused on the motion of dynein. To investigate this, we will simulate dynein’s stepping mechanisms using Monte Carlo methods and Brownian dynamics. The dynein will be computationally replicated with a particle-rod model undergoing Brownian motion in a fluid, where its stepping will be repeatedly simulated to generate an ensemble of statistics, via the Monte Carlo. The program will optimize dynein’s stepping patterns by fitting parameters according to experimental results of dynein’s step length, time, and probability of stepping.

    \begin{spacing}{1.2}
	\tableofcontents
	\listoffigures
	\end{spacing}

	\chapter{Introduction}
	\input{./Chapters/1Introduction}
	\chapter{Dynein}
	\input{./Chapters/2Dynein}
	\chapter{Theory}
	\input{./Chapters/3Theory}
	\chapter{Methods}
	\input{./Chapters/4Methods}
	\chapter{Results \& Discussion}
	\input{./Chapters/5Results}
	\chapter{Conclusion}
	\input{./Chapters/6Conclusion}

\newpage
\cite{Burgess2003} \cite{Cianfrocco2015mechanism} \cite{Dewitt2012} \cite{Capek2017}
\bibliographystyle{unsrt}
\bibliography{references}

\end{document}

### 2021-01-07 papers/jin-thesis/Chapters/5Results.tex
Bug fixes

@@
 \textit{Talk about best-fit parameters that matched experimentalists data. Include table with all parameters.}
-
 \section{Stepping Patterns}
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{/../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0.png}
-	\caption[Final Displacement Probability Distribution]{\textbf{Final Displacement Probability Distribution}}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
+	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
+Displacement is defined as the unbounded binding domain x position minus the binded binding domain x position, calculated before and after a step.
+Linear regression of the probability distribution indicates a dependence the final displacement of the step and its initial displacement, similarly to experiment.
+\textit{Bottom:} One dimensional probability density of step length.
+Step length defined as final displacement minus the initial displacement.
+Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
 	\label{fig:final_disp}
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\columnwidth]{Figures/step_length_hist.png}
-	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
-	\label{fig:step_length}
-\end{figure}
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/%u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
+%	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
+%	\label{fig:step_length}
+%\end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{Figures/prob_lagging_vs_init_L.png}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
 	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}

### 2021-01-07 src/dynein_struct.h

@@ -90,10 +90,10 @@ const bool am_debugging_naive_corrections = true;
 
 const bool am_exiting_on_improbable_stepping = false;
 
-const bool am_crashing_on_unphysical_behavior = false; // crash when model under MT, etc
+const bool am_crashing_on_unphysical_behavior = true; // crash when model under MT, etc
 const bool am_naively_correcting_nan_errors = false; // "nudges" nan states into good states, eg if cosAn > 1, cosAn = 0.9999
 
-const bool am_avoiding_sub_MT = false;
+const bool am_avoiding_sub_MT = true;
 
 const bool crash_on_nan = true;
 

### 2021-01-07 src/dynein_struct_onebound.cpp

@@ -1049,7 +1049,7 @@ bool Dynein_onebound::update_velocities() {
 
   // printf("specs: nby: %g, nmy: %g, ty: %g, umy: %g, uby: %g\n", get_bby(), get_bmy(), get_ty(), get_umy(), get_uby());
 
-  if (am_avoiding_sub_MT and (get_bmy() < 0.0 or get_ty() < 0.0 or get_umy() < 0.0 or get_uby() < 0.0)) {
+  if (am_avoiding_sub_MT and (get_bmy() < 0.0 or get_ty() < 0.0 or get_umy() < 0.0 or )) {  	//get_uby() < 0.0)) {
   // if (am_avoiding_sub_MT and (get_bmy() < 0.0 or get_ty() < 0.0 or get_umy() < 0.0)) {
     // printf("Onebound domain under MT, retrying...\n");
     // fprintf(stderr, "Onebound domain under MT, retrying...\n");

### 2021-01-13 papers/paper/paper.tex
Added fac command to build my thesis

--- 2020-11-24 papers/paper/paper.tex
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
 \caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
 \caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09_0.08_1.05_0.36}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
 \caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
@@
 
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_5.50e+09_1.00e+09_0.08_1.05_0.36}
-\caption{\textbf{Onebounnd Time} Dimentions: $s$.}
-\label{fig:ob_time}
-\end{figure}
+%% \begin{figure}[tbhp]
+%% \centering
+%% \includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
+%% \caption{\textbf{Onebounnd Time} Dimentions: $s$.}
+%% \label{fig:ob_time}
+%% \end{figure}
 

### 2021-01-17 papers/jin-thesis/Chapters/1Introduction.tex
Added a lot to my thesis directory

@@
 
-	Neuroegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States.
+	Neurodegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States.
 Scientists all over the world struggle to find the leading causes of these diseases and continue to hope for a breakthrough in science in attempt to prevent or even cure these fatal diseases.
-Although this breakthrough has yet to come, researchers discovered that one of the central causes of cell degeneration is motor protein failure.
+Although this breakthrough has yet to come, research suggests that motor protein failure is a main cause of cell degeneration.
 More specifically, defects in the motor protein dynein has been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties.
-However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and unpredicatable in nature.
-Thus, fully understandding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to solving the breakthrough.
+However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredicatable in nature.
+Thus, fully understanding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to discovering the major breakthrough for neurodegenerative research.
+In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation in order to reproduce the steping behavior observed from experiment.
+that reproduces the stepping behavior of experiment using Monte Carlo methods and a Brownian dynamics simulation.
 
@@
 	\centering
-	\includegraphics[width=0.6\columnwidth]{Figures/dynein_walking_art.jpg}
+	\includegraphics[width=0.5\columnwidth]{Figures/dynein_walking_art.jpg}
 	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} \cite{JohnsonArt}}
-	\label{fig:final_disp}
+	\label{fig:ArtDynein}
 \end{figure}
@@
 Cells are complicated.
-Despite their degeneracies, cells have the ability to move, perfectly divide, and spatially organize themselves.
-They are constructed by organelles surrdounded by a network of protein filaments called the cytoskeleton.
-The cytoskeleton is composed of microtubules (MT) that act as a walkway for motor protein soldiers to carry out the functions of the cell.
+Despite their fatal degeneracies, cells have the ability to move, perfectly divide, and spatially organize themselves.
+They can do so because tiny, two-legged molecular proteins, named \textit{motor proteins}, carry cargo containing information that outlines the blueprint for different functions within the cell.
 These motor proteins consists of kinesin, myosin, and dynein.
+They can travel all around the cell on a cytoskeleton composed of microtubules (MT) that act as a walkway for the proteins.
+A depiction of dynein walking along the microtubule is shown above in Figure (\ref{fig:ArtDynein}).
+Microtubules are constructed from negatively charged $\alpha$ and positively charged $\beta$ tubulin dimers that polarizes the microtubule depending on which tubulin is left hanging at the ends.
+In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a positive end that pulls kinesin and myosin.
+However, dynein opposes kinesin and myosin by walking towards the nucleus cell body where the MT is negatively charged.
+This attraction to both ends drives the directed stepping motion for each motor protein and is shown in Figure (\ref{fig:transport}).
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.6\columnwidth]{Figures/retrograde_transport.jpg}
+	\caption[Retrograde Transport]{\textbf{Retrograde Transport} \cite{Vale2003molecular}}
+	\label{fig:transport}
+\end{figure}
+
+Both kinesin and myosin exhibit hand-over-hand stepping, where their ``legs" take turns alternating steps like a human.
+Due to dynein's massive size compared to its motor protein siblings, dynein does not step uniformly but rather inchworms its ``feet" like a drunk human.
+This unique property makes dynein difficult to study when analyzing possible sources of molecular failure, but utters the importance of understanding the physical structure of the entire motor protein.
+
+\section{Structure}
+\textit{In-detail background knowledge on structure of dynein.
+Talk about each domain and their roles.
+Binding domain, six AAA+ domains, tail, and cargo.
+Stalk and linker that attaches things together.
+How the structure is so much larger than that of kinesin.
+dynein has flexibility because of its linker and in order to compensate for its huge domains.
+}
+
+Dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains.
+These domains are the tail domain, the six AAA+ domains (which creates a ring and is often called the motor domain), and the microtubule binding domains, where a linker connects the tail to the AAA+ ring and a stalk connects the AAA+ ring to the binding domain.
+Figure (\ref{fig:structure}) displays a simplified dynein where both subunits are connected to the tail with separate linkers.
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.6\columnwidth]{Figures/dynein_polypeptide.jpg}
+%	\caption[Polypeptide Structure]{\textbf{Polypeptide Structure} \cite{GoodsellArt}}
+%	\label{fig:polypeptide}
+%\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.6\columnwidth]{Figures/dynein_on_MT.png}
+	\caption[Dynein on Microtubule]{\textbf{Dynein on Microtubule} Artist’s illustration of a dimer of cytoplasmic dynein heavy chains bounded to microtubule.
+This rendition similarly illustrates dynein’s structure as a domain-rod system.
+\cite{TheTrappistArt}}
+	\label{fig:structure}
+\end{figure}
+
+Dynein's crystal structure has been intensely studied because of the pivotal role it plays in dyneins unpredictable stepping nature.
+Its inability to step uniformly is largely due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
+This is unique when commpared to kinesin and myosin, as their motor domains are much closer to the MT causing their center of mass to keep the protein controlled and steady when stepping.
+Despite dynein's large structure, dynein can still achieve processive stepping towards the negative end of the MT by the interaction of ATP with the AAA+ domains, thus is why the AAA+ domains are referred to as the motor domains.
+
+\section{Stepping}
+\textit{Biology and chemistry of stepping.
+What is actually causing it to step?
+ATP hydrolysis.
+Maybe short introduction on stepping and go more in detail in Power Stroke model.
+Say there are multiple theories and models of how dynein steps.
+Powerstroke, Winch, etc.
+Power stroke is most accepted.
+It can step on microtubule that is made up of tubulin dimers, $\alpha$ and $\beta$ tubulins.
+They are normally 8nm apart and so experimentalists believe dynein average step is always factor of 8nm.
+}
+
+Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis with its motor domains.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.3\columnwidth]{Figures/Onaxis.png}
+	\caption[Stepping Axis]{\textbf{Stepping axis}  \cite{Dewitt2012} }
+	\label{fig:YildizCorrelation}
+\end{figure}
 
@@
 
+\subsection{Powerstroke Model}
+\textit{Theorized model of stepping.
+Mechanochemical Cycle.
+Talk about ATP hydrolysis.
+Different conformational changes within a step.
+Look at linker and how it changes angles.
+Physically, it looks like it unbinds, stretches leg, then kicks forward, then diffuse back to MT.}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\columnwidth]{Figures/mechanochemical_cycle.jpeg}
+	\caption[Mechanochemical Cycle]{\textbf{Mechanochemical Cycle}  \cite{Cianfrocco2015mechanism}}
+	\label{fig:MechanochemicalCycle}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\columnwidth]{Figures/powerstroke.jpeg}
+	\caption[Powerstroke]{\textbf{Powerstroke}  \cite{Carter2010communication} }
+	\label{fig:Powerstroke}
+\end{figure}
+
+\section{Experimental Research on Dynein}
+\textit{Most likely just short sections on experiments done on dynein.}
+\subsection{Measuring}
+\textit{How are experimentalists measuring dyneins stepping? Quantum dots on motor domains or quantum rod on tail, etc. }
+
+\subsection{Interhead Coordination}
+\textit{Purpose of my research. Trying to make model and fit to Yildiz analysis of dynein having interstep correlation. Dependency between step length and initial inter head separation.}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\columnwidth]{Figures/Yildiz_stepping.png}
+	\caption[Stepping Correlation]{\textbf{Stepping Correlation}  \cite{Dewitt2012} }
+	\label{fig:YildizCorrelation}
+\end{figure}
+
 \section{Motivation}

### 2021-01-17 papers/jin-thesis/Chapters/2Theory.tex
Added a lot to my thesis directory

\section{Model}
In order to reliably reproduce experimental observations of dynein's stepping, a model of dynein should responsibly conserve dynein's spatial information and complex structure under an aqueous environment. Doing so computationally introduces a strict balance between model accuracy and computational efficiency. In an attempt to best satisfy this difficult balance, we propose a coarse-grained model of dynein under a series of assumptions that benefits quick simulations of dynein taking a step.

\subsection{2D Rigid Rod Model}
Since our goal is to investigate dynein's inter-step correlation during its forward directed stepping, we decided to model dynein as a 2-dimensional system of circular domains held together by massless rigid rods. These domains entitle two binding domains, two motor domains, and one tail domain, where each domain act as independent angular springs with their own spring constants.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{Figures/model-cartoon.png}
	\caption[Dynein Model]{\textbf{Dynein Model} \cite{Capek2017}}
	\label{fig:model}
\end{figure}

Despite dynein's complexity allowing its step to vary in both length and direction, we limit our model to one direction to eliminate a dimension (the off-axis) when analyzing the forward stepping pattern of dynein. This would also simplify the asymmetry of the microtubule when the dynein is stepping either on the $\alpha$ or $\beta$ tubulin. We also simplify the stalk and linker to be massless because we are assuming the drag force to be much larger than the mass of the rods and domains. The reasoning for this will be later discussed in Section \hyperref[sec:BrownianDynamics]{3.3} when we introduce Brownian dynamics. Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with its environment by increasing the radii of the domains to be slightly larger than experimental measurements.

\subsection{Domains as Angular Springs}
In order to best simulate the stretching and forward kicking motion of the power stroke, we defined our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain. This can be analogous to how humans walk using their knees and ankles to bend and stretch accordingly when taking a step. Defining our domains as springs will allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law: 
\begin{equation}
    F_i=-c_i(\theta_i-\theta_{i,eq})
\end{equation}
where $c_i$ is the spring constant, $\theta_i$ is angle corresponding to the $i^{th}$ domain, and $\theta_{i,eq}$ is the equilibrium angle in which biases the motion. Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
\begin{equation}
    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})
\end{equation}
Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e. $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains. This equation would then be used throughout the entirety of the simulation to determine the total energy of our dynein at a given conformation.

\subsection{Two-State System}
According to the Mechanochemical Cycle (\hyperref[fig:MechanochemicalCycle]{Figure 2.5}), dynein can be in eight states over the course of a single step. However, many of these states possess similar conformations, where the dynein has either one binding domain bounded with the other diffusing above the microtubule or both binding domains bounded. Since the states that take the most time are during binding and unbinding \cite{}, we categorized the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\columnwidth]{Figures/OB_vs_BB.PNG}
	\caption[One Bound vs. Both Bound]{\textbf{One Bound vs. Both Bound} Figure on left: Prestroke one bound state with labeling scheme ‘bounded’ and ‘unbouded’ for bounded leg and unbounded leg. Figure on the right: Poststroke both bound state with labeling scheme ‘near’ and ‘far’ for identifying heavy chain subunits \cite{Capek2017}.}
	\label{fig:final_disp}
\end{figure}

Differentiating the two allows us to more conveniently bias the conformational change by defining different equilibrium angles for both states.

\subsection{Transitioning Between States}
\textit{Physics about conformational energy changes. How we model transitioning between BB state and OB state using transitioning rates and spring energies.}

\section{Simulation}
\textit{Pulled from Methods section. Maybe add a little intro to simulation process}
\par
These quick simulations are governed by a Monte Carlo algorithm, while the movement of the model is dictated by equations of motion describing domains interacting with a force of drag and a random force. This type of molecular simulations are more commonly known as Brownian dynamics. (\textbf{Possible take out sentence introducing MC and Brownian dynamics for later})

\subsection{Monte Carlo Algorithm}
\textit{Physics background on Monte Carlo. Stat Mech. }

\subsection{Brownian Dynamics}
\label{sec:BrownianDynamics}
\textit{Physics background on Brownian dynemaics. Newton's second law. What forces will we use? How do we determine the random force? etc.}

\subsection{Equations of Motion}
\textit{Derived equations of motion for each domain of our dynein from Brownian dynamics.}

\textit{STRAIGHT FROM PROPOSAL. FIXME}

Our entire model of dynein will be coded with a combination of both Python and C++. The structural features of dynein will be captured with a two-dimensional geometric model of circular domains connected by rigid rods. The dynamics of dynein will be captured by imposing both equilibrium and Brownian forces on each circular domain of the model, while the chemical properties will be modeled by sporadically transitioning between two states: a poststroke both bound state, and a prestroke one bound state. These two states are shown below in Figure 2.

The simulation for stepping will consist of running multiple independent steps that starts in a both bound configuration and transitions into the Brownian dynamics one bound state. In this state, each domain will undergo Brownian forces until the unbounded leg diffuses back onto the microtubule, thus completing a step. The Brownian dynamics only affects the one bound state since that is the only time (in our model) the domains undergo molecular interaction with its surroundings to achieve processive motion. This Monte Carlo method of collecting an ensemble of statistics after many simulations will lead to probability distributions of measured variables that can be compared with experimental results. The common experimental results analyzed in this field are the distribution of step lengths (defined as the final displacement of the “stepping” leg minus the initial displacement), stepping times, probability of the binding domain unbinding, and the velocity of a step. Once sufficient data is collected for each listed variable, plotting scripts on Python will be used to visualize the possible relationships between these variables and generate analysis for our model’s stepping patterns. Currently, a paper published by Dr. Ahmet Yildiz from the University of Berkeley proposed a possible relationship within dynein’s stepping, implying inter-step correlation [3]. Our model aims to reproduce these results by finding a set of parameters that matches Yildiz’s observation in the form of a linear regression of the step lengths against the initial binding domain separation. We hope to either support Yildiz’s claim or infer some new property of dynein that generated Yildiz’s observation.

### 2021-01-17 papers/jin-thesis/Chapters/3Methods.tex
Added a lot to my thesis directory

\textit{All code for simulation can be accessed from GitHub through this link:}

\section{Simulation}
\textit{Picking Random angles to create random distribution of dynein configurations. Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound. It is done this way in order for MC to generate ensemble of data rather quickly.}\\
\textit{Include a flow chart.}

\section{Time Evolution}
\textit{Simulate over a delta t during one bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}

\section{Constants}
\textit{How we defined our constants based on experiment and pictures.  Need to include figures here of experiment dynein and how we measure the pre and post stroke equilibrium angles.}

\section{Parameter Fitting}
\textit{How we will fit our parameters to agree with Yildiz' experimental data of dynein stepping.}

\subsection{Rate Constants}
\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results.}

\section{Model Validation}
\textit{Any tests of our model to make sure the code is reasonably sound and that the physics makes sense. Make sure there is no bugs in code. What was the bug testing procedure.}

### 2021-01-17 papers/jin-thesis/Chapters/5Conclusion.tex
Added a lot to my thesis directory

\section{Findings}
\textit{What do our results indicate? Do we think our model correctly represents real dynein and its stepping patterns?}

\section{Further Work}
\textit{How can we improve our model?}

### 2021-01-18 papers/jin-thesis/Chapters/1Introduction.tex
Worked on thesis

@@
-\textit{Introduce topic by talking about cells.
+%\textit{Introduce topic by talking about cells.
 Attention grabber, relate biophysics study to cancer reserach and many areas where we need to focus our research.
@@
 	Neurodegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States.
-Scientists all over the world struggle to find the leading causes of these diseases and continue to hope for a breakthrough in science in attempt to prevent or even cure these fatal diseases.
+Scientists all over the world struggle to find a solution for these diseases and continue to hope for a breakthrough in science in attempt to prevent or even cure these fatal diseases.
 Although this breakthrough has yet to come, research suggests that motor protein failure is a main cause of cell degeneration.
@@
 In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation in order to reproduce the steping behavior observed from experiment.
-that reproduces the stepping behavior of experiment using Monte Carlo methods and a Brownian dynamics simulation.
 
@@
 A depiction of dynein walking along the microtubule is shown above in Figure (\ref{fig:ArtDynein}).
-Microtubules are constructed from negatively charged $\alpha$ and positively charged $\beta$ tubulin dimers that polarizes the microtubule depending on which tubulin is left hanging at the ends.
+Microtubules are constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulin dimers that polarizes the microtubule depending on which tubulin is left hanging at the ends.
 In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a positive end that pulls kinesin and myosin.
@@
 \section{Structure}
-\textit{In-detail background knowledge on structure of dynein.
+%\textit{In-detail background knowledge on structure of dynein.
 Talk about each domain and their roles.
@@
 Dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains.
-These domains are the tail domain, the six AAA+ domains (which creates a ring and is often called the motor domain), and the microtubule binding domains, where a linker connects the tail to the AAA+ ring and a stalk connects the AAA+ ring to the binding domain.
+These domains are the tail domain, the motor domain (constructed from six AAA+ domains that form a ring), and the microtubule binding domains, where a linker connects the tail to the AAA+ ring and a stalk connects the AAA+ ring to the binding domain.
 Figure (\ref{fig:structure}) displays a simplified dynein where both subunits are connected to the tail with separate linkers.
@@
 
-Dynein's crystal structure has been intensely studied because of the pivotal role it plays in dyneins unpredictable stepping nature.
+Dynein's crystal structure has been intensively studied because of the pivotal role it plays in dyneins unpredictable stepping nature.
 Its inability to step uniformly is largely due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
 This is unique when commpared to kinesin and myosin, as their motor domains are much closer to the MT causing their center of mass to keep the protein controlled and steady when stepping.
-Despite dynein's large structure, dynein can still achieve processive stepping towards the negative end of the MT by the interaction of ATP with the AAA+ domains, thus is why the AAA+ domains are referred to as the motor domains.
+Despite dynein's large structure, dynein can still achieve processive stepping towards the negative end of the MT due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, thus is why the AAA+ domains are referred to as the motor domains.
 
 \section{Stepping}
-\textit{Biology and chemistry of stepping.
+%\textit{Biology and chemistry of stepping.
 What is actually causing it to step?
@@
 Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis with its motor domains.
+The ATP provides dynein chemical energy which converts into mechanical energy for the dynein to transition between differenet conformational states during a step.
+Currently, there are many models being explored that discusses how dynein uses the ATP to step, such as the powerstroke model or the winch model, but this paper will be influenced by the more accepted powerstroke model.
+For either case, it is best to define an axis on the MT for where dynein can step.
+
+The on-axis is defined to be the axis parallel to the direction of forward stepping towards the negative end of the MT, while the off-axis is defined to be the axis perpendicular towards the side, as shown in Figure (\ref{fig:axis}).
+Figure (\ref{fig:axis}) also displays the alternative helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.
 
@@
 	\caption[Stepping Axis]{\textbf{Stepping axis}  \cite{Dewitt2012} }
-	\label{fig:YildizCorrelation}
+	\label{fig:axis}
 \end{figure}
 
-\textit{THIS IS STRAIGHT FROM PROPOSAL, NEED TO FIX THIS AND ADJUST SO THAT MORE DYNEIN DETAILS GOES INTO CHAPTER 2}
-
-In a eukaryotic cell, dynein is one of the three motor proteins that are responsible for the cell’s ability to move, divide, and spatially organize itself.
-Similar to the more researched kinesin, dynein conveys cargo along the microtubule track by using ATP to power its two binding domains (its “feet”).
-However, its walking-like movements along the track are very unpredictable and can vary in terms of distance and direction.
-Dynein’s two feet can also act independently from each other causing much more erratic and stochastic steps.
-However, despite dynein’s stochastic nature, dynein is still able to achieve processive motion due to the functions of its structure.
-Structurally, dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains.
-These domains are the tail domain, the linker domain, the six AAA+ domains, and the microtubule binding domains (See Figure 1).
-The AAA+ domains are responsible for ATP hydrolysis, in which converts chemical energy stored in ATP into mechanical work causing dynein’s motility.
-
-Because dynein’s stepping is unpredictable in nature, its stepping mechanism has not been intensely studied as compared to its structure.
-Questions regarding the electrostatic interactions with the microtubule, ring stacking, discrete microtubule binding sites, or elasticity of the stalk are yet to be answered.
-A known and supported model to describe dynein’s motion is the powerstroke model, where ATP binding to an AAA+ domain triggers conformational changes that lowers the affinity of the binding domain for the microtubule, causing it to unbind and take a step .
-While the powerstroke model and other theorized stepping models exists, there are no such studies which use molecular dynamics to verify if these theorized mechanisms are feasible for the dynein motor to produce.
-There are studies that incorporate a computational model of dynein, but many use chemical rate transitions and assume independence of steps without simulating the precise protein dynamics within its step.
+\textit{Maybe add a transition here. Seems awkward to go straight into next section...}
 
 \subsection{Powerstroke Model}
-\textit{Theorized model of stepping.
+%\textit{Theorized model of stepping.
 Mechanochemical Cycle.
@@
 Physically, it looks like it unbinds, stretches leg, then kicks forward, then diffuse back to MT.}
+
+As mentioned earlier, there are many theorized models for dynein's stepping, but the widely accepted model is the powerstroke model within the mechenochemical cycle introduced by Cianfrocco et al.
+\cite{Cianfrocco2015mechanism}.
+A summary of the eight step cycle is shown below in Figure (\ref{fig:MechanochemicalCycle}).
 
@@
 \end{figure}
+
+The cycle utilizes the conformational transition between high affinity and low affinity to explain dynein's unbinding and rebinding process.
+This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward.
+This key detail within the transition of stretching the linker distinguishes a ``pre-stroke" and a ``post-stroke" state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step.
+A closer visualization of this transition between pre- and post- stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.
 
@@
 \section{Experimental Research on Dynein}
-\textit{Most likely just short sections on experiments done on dynein.}
+
+Although the mechanochemical cycle provides a reasonable model for dynein's step, the model fails to analyze the precise movements of each domain and how different configurations alter the conformational transitions.
+To what extent does the linker stretch when exhibiting the powerstroke and is it angle dependent?
+How does the separation between the two subunits of dynein affect the step length of the powerstroke?
+Consequently, these questions inspire experimentalists to measure dynein's step and study correlations between different parameters within a step.
+
 \subsection{Measuring}
-\textit{How are experimentalists measuring dyneins stepping? Quantum dots on motor domains or quantum rod on tail, etc. }
+%\textit{How are experimentalists measuring dyneins stepping? Quantum dots on motor domains or quantum rod on tail, etc. }
+
+Experimentalists approach measuring dynein in various ways involving electron microscopy and quantum measuring techniques.
+Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod.
+However, all experimental procedures suffer with one major limitation: undetectable steps close to 0nm.
+\textit{This bit is akward.
+Maybe just combine with next part to and label it Interstep coordination or something.}
 
 \subsection{Interhead Coordination}
-\textit{Purpose of my research. Trying to make model and fit to Yildiz analysis of dynein having interstep correlation. Dependency between step length and initial inter head separation.}
+%\textit{Purpose of my research. Trying to make model and fit to Yildiz analysis of dynein having interstep correlation. Dependency between step length and initial inter head separation.}
+
+Dynein's large size and stochastic nature implies completely independent stepping from the initial conformational state before the step.
+However, in 2012, Yildiz et al.
+observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}.
+This discovery challenged established views on dynein's stepping processivity and poses the question around the existence of interhead coordination between the motor domains when stepping.
+Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.
 
@@
 
+This correlation implies a connection between the physical state of dynein and its stepping behavior, inferring that dynein's step is not only ATP dependent.
+Unfortunately, experiment is inherently limited and can massively benefit from accurate models that can simulate dynein's stepping under realistic circumstances.
+
 \section{Motivation}
-\textit{Briefly write about the importance of dynein, how dynein is researched when studying neurological diseases, dynein stepping is understudied compared to other motor proteins, hard to model dynein because of random walking, there are almost no computational models of dynein that uses molecular dynamics, modelling dyenin can give us better understanding of why it moves the way it does, specific motivation for model: new research found that there is interhead coordination when stepping so maybe we can use that to base our model off of.}
-\par
+%\textit{Briefly write about the importance of dynein, how dynein is researched when studying neurological diseases, dynein stepping is understudied compared to other motor proteins, hard to model dynein because of random walking, there are almost no computational models of dynein that uses molecular dynamics, modelling dyenin can give us better understanding of why it moves the way it does, specific motivation for model: new research found that there is interhead coordination when stepping so maybe we can use that to base our model off of.}
 
-To bridge this gap, we propose a coarse-grained model of dynein that assumes a particle-rod structure for its various domains and uses Brownian motion to simulate the model’s behavior in physically realistic drag and diffusion conditions, while efficiently collecting a wide ensemble of statistics using Monte Carlo methods.
+Simulations that model dynein's step exists, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
+Because of this, these simulations suffer from numerous assumptions made about the physical aspects of dynein's step.
+(\textit{Should reference a simulation here and be more detailed}) Some assume that dynein can only step in increments of 8nm or that the rebinding process is constrained to a certain time frame.
+These limitations make it impossible for the models to replicate unique discoveries about dyneins stepping, such as Yildiz's correlation from above.
+A perfect simulation ought to lift these physical constraints and accurately reproduce experimental data.
+
+To bridge this gap, Roundy et al.
+constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment.
+Instead of making assumptions about the physical properties of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes that the force applied from the ATP is incorporated within the forces on the domains (???
+weird wording need to FIXME).
+Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experiences Brownian motion during a step to mimic stochastic movement \cite{Capek2017, Burgess2003}.
+They were able to track dynein's precise movement along a walk and compare their stepping results to experiment.
+However, their simulation suffered from immense computaiton time and lacked the ability to optimize model parameters for a better fit to experiment.
+For this work, we will use their simulation as a foundation and implement a Monte Carlo method for reproducing data fast and generating an ensemble of statistics.
+We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism.
+More specifically, we want reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.
+
+%\textit{THIS IS STRAIGHT FROM PROPOSAL, NEED TO FIX THIS AND ADJUST SO THAT MORE DYNEIN DETAILS GOES INTO CHAPTER 2}
+%
+%In a eukaryotic cell, dynein is one of the three motor proteins that are responsible for the cell’s ability to move, divide, and spatially organize itself.
+Similar to the more researched kinesin, dynein conveys cargo along the microtubule track by using ATP to power its two binding domains (its “feet”).
+However, its walking-like movements along the track are very unpredictable and can vary in terms of distance and direction.
+Dynein’s two feet can also act independently from each other causing much more erratic and stochastic steps.
+However, despite dynein’s stochastic nature, dynein is still able to achieve processive motion due to the functions of its structure.
+Structurally, dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains.
+These domains are the tail domain, the linker domain, the six AAA+ domains, and the microtubule binding domains (See Figure 1).
+The AAA+ domains are responsible for ATP hydrolysis, in which converts chemical energy stored in ATP into mechanical work causing dynein’s motility.
+%
+%Because dynein’s stepping is unpredictable in nature, its stepping mechanism has not been intensely studied as compared to its structure.
+Questions regarding the electrostatic interactions with the microtubule, ring stacking, discrete microtubule binding sites, or elasticity of the stalk are yet to be answered.
+A known and supported model to describe dynein’s motion is the powerstroke model, where ATP binding to an AAA+ domain triggers conformational changes that lowers the affinity of the binding domain for the microtubule, causing it to unbind and take a step .
+While the powerstroke model and other theorized stepping models exists, there are no such studies which use molecular dynamics to verify if these theorized mechanisms are feasible for the dynein motor to produce.
+There are studies that incorporate a computational model of dynein, but many use chemical rate transitions and assume independence of steps without simulating the precise protein dynamics within its step.
+%
+%To bridge this gap, we propose a coarse-grained model of dynein that assumes a particle-rod structure for its various domains and uses Brownian motion to simulate the model’s behavior in physically realistic drag and diffusion conditions, while efficiently collecting a wide ensemble of statistics using Monte Carlo methods.
 We chose to use Brownian inspired motion to simulate dynein’s molecular dynamics in order to replicate dynein’s stochastic behavior under realistic conditions and produce its unpredictable stepping patterns observed from experiment.

### 2021-01-18 papers/jin-thesis/Chapters/2Theory.tex
Worked on thesis

@@
 \section{Model}
-In order to reliably reproduce experimental observations of dynein's stepping, a model of dynein should responsibly conserve dynein's spatial information and complex structure under an aqueous environment.
+In order to reliably reproduce experimental observations of dynein's step, a model of dynein should responsibly conserve dynein's spatial information and complex structure.
 Doing so computationally introduces a strict balance between model accuracy and computational efficiency.
-In an attempt to best satisfy this difficult balance, we propose a coarse-grained model of dynein under a series of assumptions that benefits quick simulations of dynein taking a step.
+In an attempt to best satisfy this difficult balance, we propose a simple model of dynein under a series of assumptions that benefits quick simulations of dynein taking a step.
 
 \subsection{2D Rigid Rod Model}
-Since our goal is to investigate dynein's inter-step correlation during its forward directed stepping, we decided to model dynein as a 2-dimensional system of circular domains held together by massless rigid rods.
-These domains entitle two binding domains, two motor domains, and one tail domain, where each domain act as independent angular springs with their own spring constants.
+Since our goal is to investigate dynein's interhead coordination during its forward directed stepping, we decided to model dynein as a 2-dimensional system of circular domains held together by massless rigid rods.
+These cirular domains embody the two binding domains, two motor domains, and one tail domain, where each domain act as independent angular springs with their own spring constants.
+A labeled picture of the model is shown below in Figure (\ref{fig:model}).
 
@@
 \subsection{Domains as Angular Springs}
-In order to best simulate the stretching and forward kicking motion of the power stroke, we defined our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain.
-This can be analogous to how humans walk using their knees and ankles to bend and stretch accordingly when taking a step.
-Defining our domains as springs will allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law:
+In order to best simulate the stretching and forward kicking motion of the power stroke, we define our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain.
+This can be analogous to how humans walk as the domains are used as flexible joints when taking a step.
+Defining our domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law:
 \begin{equation}
@@
 \begin{equation}
-    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})
+    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
 \end{equation}
-Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e.
+%Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e.
 $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
@@
 \subsection{Two-State System}
-According to the Mechanochemical Cycle (\hyperref[fig:MechanochemicalCycle]{Figure 2.5}), dynein can be in eight states over the course of a single step.
-However, many of these states possess similar conformations, where the dynein has either one binding domain bounded with the other diffusing above the microtubule or both binding domains bounded.
-Since the states that take the most time are during binding and unbinding \cite{}, we categorized the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.
+According to the Mechanochemical Cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step.
+However, many of these states possess similar conformations, where the dynein either has one binding domain bounded while the other diffuses above the microtubule or has both binding domains bounded to the microtubule.
+Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.
 
@@
 Differentiating the two allows us to more conveniently bias the conformational change by defining different equilibrium angles for both states.
+Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both bound state will be identical for both binding and motor domain pairs, i.e.
+$\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
+However, in the one bound state, the unbounded leg wants to exhibit the powerstroke and kick out.
+Therefore, the equilibrium angles for the motor domains will differ in order to bias the unbound leg to straighten and perform the powerstroke.
 
 \subsection{Transitioning Between States}
-\textit{Physics about conformational energy changes. How we model transitioning between BB state and OB state using transitioning rates and spring energies.}
+%\textit{Physics about conformational energy changes. How we model transitioning between BB state and OB state using transitioning rates and spring energies.}
+
+Similar to other simulations, the binding and unbinding process will be governed by a rate-limiting step, where each process will be associated with binding rates.
+These binding rates will be model parameters defined by binding constants with units of probability per time.
+When the dynein is in the one bound state, we assume that the unbound binding domain can only bind when it is within a vertical range of the microtubule, i.e.
+\begin{equation}
+	\rho_b=k_b(1-H(r_{ub,y}-\epsilon)).
+\end{equation} 
+Here, the $\rho_b$ is the binding rate, $k_b$ is the rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
+
+When the dynein is in the both bound state and wants to unbind, we incorporate a stepping bias in the unbinding rate.
+As supported from Yildiz in Figure (\ref{fig:trailingbias}), the likelihood of the trailing leg unbinding is greater than the leading leg when the distance between the two legs increase.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.6\columnwidth]{Figures/trailingbias.png}
+	\caption[Probability of Unbinding Bias]{\textbf{Probability of Unbinding Bias}\cite{Dewitt2012}.}
+	\label{fig:trailingbias}
+\end{figure}
+
+To favor trailing steps, we define an angle dependent exponential factor within the binding domains and mathematically express this as,
+\begin{equation}
+	\rho_{ub}=k_{ub}e^{C(\theta_b-theta_{b,eq})}.
+\end{equation}
+We introduce a new model parameter $C$, the exponential unbinding constant, that allows us to control this bias.
+For the trailing step bias we want to achieve, we define $C$ to be negative because the trailing $\theta_b$ tends to be less than the leading $\theta_b$ and  when $\theta_b$ is less than $\theta_{b,eq}$, the unbinding rate becomes large.
 
 \section{Simulation}
-\textit{Pulled from Methods section. Maybe add a little intro to simulation process}
-\par
-These quick simulations are governed by a Monte Carlo algorithm, while the movement of the model is dictated by equations of motion describing domains interacting with a force of drag and a random force.
+
+The key difference between the works discussed in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state.
+Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk.
+However, they noticed that their simulation took significant computation time because of dynein being stuck in the both bound state inbetween steps.
+We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step when in the one bound state.
+
+%These quick simulations are governed by a Monte Carlo algorithm, while the movement of the model is dictated by equations of motion describing domains interacting with a force of drag and a random force.
 This type of molecular simulations are more commonly known as Brownian dynamics.
@@
 
+\subsection{Brownian Dynamics for One Bound}
+\label{sec:BrownianDynamics}
+
+When simulating dynein's one bound motion
+
 \subsection{Monte Carlo Algorithm}
-\textit{Physics background on Monte Carlo. Stat Mech. }
-
-\subsection{Brownian Dynamics}
-\label{sec:BrownianDynamics}
-\textit{Physics background on Brownian dynemaics. Newton's second law. What forces will we use? How do we determine the random force? etc.}
-
-\subsection{Equations of Motion}
-\textit{Derived equations of motion for each domain of our dynein from Brownian dynamics.}
 
@@
 
-Our entire model of dynein will be coded with a combination of both Python and C++.
+%Our entire model of dynein will be coded with a combination of both Python and C++.
 The structural features of dynein will be captured with a two-dimensional geometric model of circular domains connected by rigid rods.
@@
 These two states are shown below in Figure 2.
-
-The simulation for stepping will consist of running multiple independent steps that starts in a both bound configuration and transitions into the Brownian dynamics one bound state.
+%
+%The simulation for stepping will consist of running multiple independent steps that starts in a both bound configuration and transitions into the Brownian dynamics one bound state.
 In this state, each domain will undergo Brownian forces until the unbounded leg diffuses back onto the microtubule, thus completing a step.

### 2021-01-18 papers/jin-thesis/Chapters/4Results.tex
Added a lot to my thesis directory
Worked on thesis

--- 2021-01-07 papers/jin-thesis/Chapters/5Results.tex
@@
 
-\section{Stepping Patterns}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{/../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0.png}
-	\caption[Final Displacement Probability Distribution]{\textbf{Final Displacement Probability Distribution}}
-	\label{fig:final_disp}
-\end{figure}
+%\section{Stepping Patterns}
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
+%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
+%	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
+Displacement is defined as the unbounded binding domain x position minus the binded binding domain x position, calculated before and after a step.
+Linear regression of the probability distribution indicates a dependence the final displacement of the step and its initial displacement, similarly to experiment.
+\textit{Bottom:} One dimensional probability density of step length.
+Step length defined as final displacement minus the initial displacement.
+Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
+%	\label{fig:final_disp}
+%\end{figure}
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/%u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0}
+%	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
+%	\label{fig:step_length}
+%\end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{Figures/step_length_hist.png}
-	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
-	\label{fig:step_length}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\columnwidth]{Figures/prob_lagging_vs_init_L.png}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
 	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}

### 2021-01-18 scripts/monte_carlo_simulation.py

@@ -141,20 +141,31 @@ while Z < N:
             Z += P
             rate_trailing = np.exp(args.C*(dynein.nba - eqb_angle))
             rate_leading = np.exp(args.C*(dynein.fba - eqb_angle))
+            print(dynein.E_t)
+            print(dynein.E_nm)
+            print(dynein.E_fm)
 
             prob_trailing = P*rate_trailing*P_factor
             prob_leading = P*rate_leading*P_factor
+
+            print('Energy: ', dynein.E_total)
+            print('P: ', P)
+            print('rate: ', rate_trailing, rate_leading)
+            print(P_factor)
+            print('probs: ', prob_trailing, prob_leading)
+            print('')
             # if (len(trailing_data['L'])) == 7:
             #     print('nba: {}, nma: {}, ta: {}, fma: {}, fba: {}'.format(dynein.nba*57.3, dynein.ob_nma*57.3, dynein.ta*57.3, dynein.ob_fma*57.3, dynein.fba*57.3))
             #     print('nba: {}, bb_nma: {}, ta: {}, bb_fma: {}, fba: {}'.format(dynein.nba*57.3, dynein.bb_nma*57.3, dynein.ta*57.3, dynein.bb_fma*57.3, dynein.fba*57.3))
             #     print('nb: {}, nm: {}, t: {}, fm: {}, fb: {}'.format(dynein.r_nb, dynein.r_nm, dynein.r_t, dynein.r_fm, dynein.r_fb))
 
             if prob_trailing > 1 or prob_leading > 1:
-                P_factor = P_factor - 0.05
+                P_factor = P_factor*0.99
                 # k[0] = 0
                 # Z = 0
                 continue
             if np.random.random() < prob_trailing:
+                    print('About to t step!')
                     # FARBOUND State
                     state = 1
                     if k[0] % 50 == 0:
@@ -167,6 +178,7 @@ while Z < N:
                                             L, trailing_data)
 
             if np.random.random() < prob_leading:
+                    print('About to l step!')
                     # NEARBOUND State
                     state = 0
                     if k[0] % 50 == 0:

### 2021-01-19 papers/jin-thesis/Chapters/2Theory.tex
Paper edits

@@
 \section{Model}
-In order to reliably reproduce experimental observations of dynein's step, a model of dynein should responsibly conserve dynein's spatial information and complex structure.
+In order to reliably reproduce experimental observations of dynein's step, a model of dynein should responsibly conserve dynein's spatial information and complex structure without limiting the physical interactions with its environment.
 Doing so computationally introduces a strict balance between model accuracy and computational efficiency.
@@
 	\includegraphics[width=0.6\columnwidth]{Figures/model-cartoon.png}
-	\caption[Dynein Model]{\textbf{Dynein Model} \cite{Capek2017}}
+	\caption[Dynein Model]{\textbf{Dynein Model.} A model of the dynein in the both bound state where both binding domains are bounded to the microtubule.
+The springs are only a visualization of how they control the domains and are not a part of the model geometry.
+\cite{Capek2017}}
 	\label{fig:model}
@@
 We also simplify the stalk and linker to be massless because we are assuming the drag force to be much larger than the mass of the rods and domains.
-The reasoning for this will be later discussed in Section \hyperref[sec:BrownianDynamics]{3.3} when we introduce Brownian dynamics.
+The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics.
 Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with its environment by increasing the radii of the domains to be slightly larger than experimental measurements.
@@
 Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
-\begin{equation}
+\begin{equation} \label{eq:energy}
     U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{Figures/OB_vs_BB.PNG}
+	\includegraphics[width=0.9\columnwidth]{Figures/OB_vs_BB.PNG}
 	\caption[One Bound vs.
 Both Bound]{\textbf{One Bound vs.
-Both Bound} Figure on left: Prestroke one bound state with labeling scheme ‘bounded’ and ‘unbouded’ for bounded leg and unbounded leg.
-Figure on the right: Poststroke both bound state with labeling scheme ‘near’ and ‘far’ for identifying heavy chain subunits \cite{Capek2017}.}
-	\label{fig:final_disp}
+Both Bound} \textit{Figure on left}: Prestroke one bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg.
+\textit{Figure on the right}: Poststroke both bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg.
+\cite{Capek2017}.}
+	\label{fig:OBvsBB}
 \end{figure}
@@
 $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
-However, in the one bound state, the unbounded leg wants to exhibit the powerstroke and kick out.
+However, in the one bound state, the unbound leg wants to exhibit the powerstroke and kick out.
 Therefore, the equilibrium angles for the motor domains will differ in order to bias the unbound leg to straighten and perform the powerstroke.
@@
 	\includegraphics[width=0.6\columnwidth]{Figures/trailingbias.png}
-	\caption[Probability of Unbinding Bias]{\textbf{Probability of Unbinding Bias}\cite{Dewitt2012}.}
+	\caption[Probability of Unbinding Bias]{\textbf{Probability of Unbinding Bias.} The probability of either trailing or leading steps which correspond to the model's ``near" or ``far" leg unbinding, respectively.
+\cite{Dewitt2012}.}
 	\label{fig:trailingbias}
@@
 Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk.
-However, they noticed that their simulation took significant computation time because of dynein being stuck in the both bound state inbetween steps.
-We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step when in the one bound state.
+However, they noticed that their simulation took significant computation time because of the unbinding process taking a large amount of time relative to the total stepping time.
+They also noticed that the both bound configuration of dynein does not impact the final step length.
+We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.
 
@@
 
-When simulating dynein's one bound motion
+When simulating dynein's one bound motion, the domains of constant mass must still obey classical Newtonian physics and follow Newton's laws of motion.
+Knowing this, we can use Newton's second law to derive the equations of motion for each domain when experiencing various forces.
+That is,
+\begin{equation}
+	\sum_{i}\textbf{F}_i=m\ddot{\textbf{r}}.
+\end{equation}
+
+For our domains experiencing the aqueous environment in the cell, the first force we can identify is the force of linear drag:
+\begin{equation}
+	\textbf{F}_{drag}=-\gamma \dot{\textbf{r}}
+\end{equation}
+where $\gamma$ is the drag coefficient defined from Stokes' law to be:
+\begin{equation}
+	\gamma=6\pi\eta a.
+\end{equation}
+This equation specifies the drag term by a given radius $a$ and liquid viscocity $\eta$.
+
+The secondary force that we can easily identify is the random force inspiring the Brownian motion.
+This force describes the random interactions the domains experience with the paticles making the solvent and will be denoted as \textbf{F}$_{rand}$.
+The ``randomness" will be sampled from a zero-centered Gaussian with variance:
+\begin{equation}
+	\sigma^2=\sqrt{\frac{2\gamma}{\beta\Delta t}}.
+\end{equation}
+where $\beta$ is the thermodynamic beta and $\Delta t$ is a time-step.
+
+The final existing force on the domains will be the tension force the domains have on each other \textit{via} their connecting rods.
+We will name this \textbf{F}$_T$.
+Incorporting all these forces with Newton's second law, we can produce an equation otherwise known as the \textit{Langevin Equation}:
+\begin{equation}
+	-\gamma \dot{\textbf{r}} + \textbf{F}_{rand} + \textbf{F}_T = m\ddot{\textbf{r}}.
+\end{equation}
+As mentioned earlier, in order to properly demonstrate Brownian dynamics, we must assume strong drag where $|\gamma \dot{\textbf{r}}|\ll |m\ddot{\textbf{r}}|$.
+Or in otherwords, we assume that the immense viscosity in the environment stricts the ability for our domains to accelerate.
+Simplifying the \textit{Langevin Equation} and solving for $\dot{\textbf{r}}$, we get:
+\begin{equation}
+	\dot{\textbf{r}}=\frac{1}{\gamma}(\textbf{F}_{rand} + \textbf{F}_T)
+\end{equation}
+which is a differential equation we can solve for the equations of motion for the domains in the one bound state. The derivation and final equations of motion can be found in \cite{Capek2017, W}
 
 \subsection{Monte Carlo Algorithm}
+Since research and Waczak/Capek suggests that the dynein spends the majority of the stepping time in the both bound state, we can safely assume that the dynein equilibriates before unbinding.
+This allows us to use Monte Carlo methods for analyzing a single step by interpreting our model as a system.
+Typically, Monte Carlo methods are used to analyze equilibrium theromodynamics of fluids where a system of atoms can possess many different microstates.
+For this model, the dynein is the system and the different possible microstates are the both bound configurations our model can achieve.
+Each both bound configuration are independent from one another and can produce different total energy values.
+The benefit of this method is the ability to sample a large ensemble of both bound states and quickly generate statitics about the step.
+Eventually, this will allow us to create probability distributions for important variables.
+The algorithm is as follows:
+\begin{algorithm}[H]
+	\caption{Monte Carlo}
+	\label{alg:MonteCarlo}
 
-\textit{STRAIGHT FROM PROPOSAL. FIXME}
+	\begin{alg}
+	\item Initialize an unsigned distance, L, between the binding domains.
+
+	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space. (\textit{Include picture})
+
+	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.
+
+	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate both bound state angles with the naming convention in Figure (\ref{fig:OBvsBB}).
+
+	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eq:energy})).
+	\begin{equation}
+		E_{total, n}=\sum_{i}\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
+	\end{equation}
+	Here, $n$ refers to the specific both bound configuration.
+
+	\item Define a Boltzmann distribution for the relative probability of unbinding and a partition function, $Z$.
+	\begin{equation}
+		P_{ub}\propto e^{-\beta E_{total, n}}
+	\end{equation}
+	\begin{equation}
+		Z=\sum_{n}e^{\beta E_{total, n}}
+	\end{equation}
+
+	\item Calculate the probability of unbinding with the unbinding rate and Boltzmann distribution.
+	\begin{equation}
+		P_{ub} = \rho_{ub}e^{-\beta E_{total, n}}
+	\end{equation}
+
+	\item ``Roll a die" for a value within the range of $[0,1]$ and check if the value is less than $P_{ub}$. If not, repeat algorithm from step 1.
+
+	\item If dynein unbinds, run one bound Brownian dynamics simulation of the step and wait until rebinding.
+
+	\item Collect statistics about final displacement and one bound time.
+
+	\end{alg}
+
+\end{algorithm}
+
+%\textit{STRAIGHT FROM PROPOSAL. FIXME}
 

### 2021-01-20 papers/jin-thesis/Chapters/1Introduction.tex

@@
 	\includegraphics[width=0.5\columnwidth]{Figures/dynein_walking_art.jpg}
-	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} \cite{JohnsonArt}}
+	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} walking along a microtubule in a weary cell. \cite{JohnsonArt}}
 	\label{fig:ArtDynein}
@@
 	\includegraphics[width=0.6\columnwidth]{Figures/retrograde_transport.jpg}
-	\caption[Retrograde Transport]{\textbf{Retrograde Transport} \cite{Vale2003molecular}}
+	\caption[Charge Influenced Transport]{\textbf{Charge Influenced Transport}.
+Dynein and kinesin transporting cargo on the axon of a neuron cell for building the axon growth cone.
+They share cargo and take turns delivering each other to opposite ends of the cell.
+\cite{Vale2003molecular}}
 	\label{fig:transport}
@@
 	\includegraphics[width=0.6\columnwidth]{Figures/dynein_on_MT.png}
-	\caption[Dynein on Microtubule]{\textbf{Dynein on Microtubule} Artist’s illustration of a dimer of cytoplasmic dynein heavy chains bounded to microtubule.
+	\caption[Structure of Dynein]{\textbf{Structure of Dynein.} Illustration of cytoplasmic dynein's heavy chain subunits bounded to the microtubule.
+The large size of the AAA+ rings are blocking the view of the independent linkers connecting to the tail.
 This rendition similarly illustrates dynein’s structure as a domain-rod system.
@@
 	\includegraphics[width=0.3\columnwidth]{Figures/Onaxis.png}
-	\caption[Stepping Axis]{\textbf{Stepping axis}  \cite{Dewitt2012} }
+	\caption[Stepping Axis]{\textbf{Stepping axis.} Birds-eye view of the microtubule with the green areas identifying the microtubule binding domains.
+For the on-axis, positive displacement is defined towards the minus end of the microtubule.
+Dark and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers.
+\cite{Dewitt2012} }
 	\label{fig:axis}
@@
 	\includegraphics[width=1\columnwidth]{Figures/mechanochemical_cycle.jpeg}
-	\caption[Mechanochemical Cycle]{\textbf{Mechanochemical Cycle}  \cite{Cianfrocco2015mechanism}}
+	\caption[Mechanochemical Cycle]{\textbf{Mechanochemical Cycle.} The proposed series of conformational stages dynein undergoes during a step.
+The interaction of ATP with the motor domain is the main factor causing the powerstroke.
+\cite{Cianfrocco2015mechanism}}
 	\label{fig:MechanochemicalCycle}
@@
 This key detail within the transition of stretching the linker distinguishes a ``pre-stroke" and a ``post-stroke" state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step.
-A closer visualization of this transition between pre- and post- stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.
+A closer visualization of this transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.
 
@@
 	\includegraphics[width=1\columnwidth]{Figures/powerstroke.jpeg}
-	\caption[Powerstroke]{\textbf{Powerstroke}  \cite{Carter2010communication} }
+	\caption[Powerstroke]{\textbf{Powerstroke.} A more detailed visualization of the linker during the transition from pre- to post-stroke states.
+The linker is initially bent inwards during the pre-stroke state, then stretches backwards to extend the binding domain forward and land during the post-stroke state.
+\cite{Carter2010communication} }
 	\label{fig:Powerstroke}
@@
 	\includegraphics[width=1\columnwidth]{Figures/Yildiz_stepping.png}
-	\caption[Stepping Correlation]{\textbf{Stepping Correlation}  \cite{Dewitt2012} }
+	\caption[Stepping Correlation]{\textbf{Stepping Correlation.} A scatter plot of step sizes vs.
+on-axis separation which hints at a functional dependency between the step  length and the initial distance between the binding domains.
+The 1D histogram for the trailing head on the left only generalizes the step lengths for negative on-axis separation, while the histogram for the leading head does the same for positive on-axis separation.
+\cite{Dewitt2012} }
 	\label{fig:YildizCorrelation}

### 2021-01-25 papers/jin-thesis/Chapters/2Theory.tex
Progress on thesis and reverted changes for generate paper model figures

@@
 Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
-\begin{equation} \label{eq:energy}
+\begin{equation} \label{eqn:energy}
     U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
@@
 Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk.
-However, they noticed that their simulation took significant computation time because of the unbinding process taking a large amount of time relative to the total stepping time.
+However, they noticed that the unbinding process took a large amount of computation time relative to the total stepping time.
 They also noticed that the both bound configuration of dynein does not impact the final step length.
@@
 The secondary force that we can easily identify is the random force inspiring the Brownian motion.
-This force describes the random interactions the domains experience with the paticles making the solvent and will be denoted as \textbf{F}$_{rand}$.
-The ``randomness" will be sampled from a zero-centered Gaussian with variance:
+This force describes the random interactions the domains experience with the paticles making the solvent.
+It will be denoted as \textbf{F}$_{rand}$, and the ``randomness" will be sampled from a zero-centered Gaussian with variance:
 \begin{equation}
@@
 
-\subsection{Monte Carlo Algorithm}
+\subsection{Monte Carlo for Both Bound}
 Since research and Waczak/Capek suggests that the dynein spends the majority of the stepping time in the both bound state, we can safely assume that the dynein equilibriates before unbinding.
-This allows us to use Monte Carlo methods for analyzing a single step by interpreting our model as a system.
+This inspired us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system.
 Typically, Monte Carlo methods are used to analyze equilibrium theromodynamics of fluids where a system of atoms can possess many different microstates.
-For this model, the dynein is the system and the different possible microstates are the both bound configurations our model can achieve.
-Each both bound configuration are independent from one another and can produce different total energy values.
-The benefit of this method is the ability to sample a large ensemble of both bound states and quickly generate statitics about the step.
+For this model, the dynein is the system and the different possible microstates are the many both bound configurations our model can achieve.
+However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values.
+The benefit of this method is the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics.
 Eventually, this will allow us to create probability distributions for important variables.
-The algorithm is as follows:
-\begin{algorithm}[H]
-	\caption{Monte Carlo}
-	\label{alg:MonteCarlo}
 
-	\begin{alg}
-	\item Initialize an unsigned distance, L, between the binding domains.
-
-	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space. (\textit{Include picture})
-
-	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.
-
-	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate both bound state angles with the naming convention in Figure (\ref{fig:OBvsBB}).
-
-	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eq:energy})).
+With the assumption of thermodyamic equilibrium during the both bound state, we can define the probability of dynein being in that configuration from a Boltzmann distribution and calculate the relative probability of unbinding for that specifc configuration by using a proportionality expression.
+That is,
 \begin{equation}
-		E_{total, n}=\sum_{i}\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
+	P_{ub}\propto e^{-\beta E_{total}}.
 \end{equation}
-	Here, $n$ refers to the specific both bound configuration.
-
-	\item Define a Boltzmann distribution for the relative probability of unbinding and a partition function, $Z$.
+With this Boltzmann factor, we can also generate a partition function, 
+\begin{equation} \label{eqn:partition}
+	Z=\sum_{i}e^{-\beta E_{total,i}},
+\end{equation}
+where $i$ refers to the specific both bound configuration.
+In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well.
+The thermodynamic ensemble can then generate an ensemble of steps that can eventually produce smooth statictics.
+With the partition function defined in Equation (\ref{eqn:partition}), we can also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time.
+The equations to do so are all shown below in that order:
 \begin{equation}
-		P_{ub}\propto e^{-\beta E_{total, n}}
+	\langle\rho_{ub, n}\rangle=\frac{\sum_{i}\rho_{ub, n} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, f}\rangle=\frac{\sum_{i}\rho_{ub, f} e^{-\beta E_{total,i}}}{Z}
 \end{equation}
 \begin{equation}
-		Z=\sum_{n}e^{\beta E_{total, n}}
+	\langle P_{ub, n}(L)\rangle = \frac{\langle\rho_{ub, n}\rangle}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}
 \end{equation}
-
-	\item Calculate the probability of unbinding with the unbinding rate and Boltzmann distribution.
 \begin{equation}
-		P_{ub} = \rho_{ub}e^{-\beta E_{total, n}}
+	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}.
 \end{equation}
-
-	\item ``Roll a die" for a value within the range of $[0,1]$ and check if the value is less than $P_{ub}$. If not, repeat algorithm from step 1.
-
-	\item If dynein unbinds, run one bound Brownian dynamics simulation of the step and wait until rebinding.
-
-	\item Collect statistics about final displacement and one bound time.
-
-	\end{alg}
-
-\end{algorithm}
 

### 2021-01-25 papers/jin-thesis/Chapters/3Methods.tex
Progress on thesis and reverted changes for generate paper model figures

@@
-\textit{All code for simulation can be accessed from GitHub through this link:}
+%\textit{All code for simulation can be accessed from GitHub through this link:}
+
+The entire model and simulation code can be found here on \url{https://github.com/kiatvonj/dynein_walk}, where the model and simulation were coded using both Python and C++.
+The both bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous and time independent, while the one bound Brownian dynamics was coded on C++ to utilize the faster computation speed for the time  dependent Brownian motion.
 
 \section{Simulation}
-\textit{Picking Random angles to create random distribution of dynein configurations.
+%\textit{Picking Random angles to create random distribution of dynein configurations.
 Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound.
 It is done this way in order for MC to generate ensemble of data rather quickly.}\\
-\textit{Include a flow chart.}
+%\textit{Include a flow chart.}
+Since we want to generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk.
+This allows us to simplify the code into two respective parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycles repeatedly after the model takes a step.
+The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculate the total energy.
+If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one bound simulation and execute the Brownian dynamics.
+Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step.
+However, the big caveat with this method is that we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations.
+This will force the measured probabilities to be a function of $L$ and will be addressed later in Section (\ref{sec:DataAna}).
+The algorithm for the both bound process is shown below:
 
-\section{Time Evolution}
-\textit{Simulate over a delta t during one bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}
+\begin{algorithm}[H]
+	\caption{Monte Carlo Both Bound}
+	\label{alg:MonteCarlo}
+
+	\begin{alg}
+	\item Initialize an unsigned distance, $L$, between the binding domains.
+
+	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space. (\textit{Include picture})
+
+	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.
+
+	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate angles with the naming convention in Figure (\ref{fig:OBvsBB}).
+
+	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eqn:energy})),
+	\begin{equation}
+		E_{total, i}=\sum_{k}\frac{1}{2}c_k(\theta_k-\theta_{k,eq})^2.
+	\end{equation}
+	Here, $i$ refers to the specific both bound configuration and $k$ is the domain.
+
+	\item Calculate the relative unbinding probability from a Boltzmann distribution and add a term to the partition function:
+	\begin{equation}
+		P_{ub} \propto \rho_{ub}e^{-\beta E_{total, n}}\kappa,
+	\end{equation}
+	\begin{equation}
+		Z=\sum_{n}e^{\beta E_{total, n}}.
+	\end{equation}
+	We defined a $\kappa$ to normalize the relative unbinding probability and keep it less than 1.
+
+	\item ``Roll a die" for a value within the range of $[0,1]$ and check if the value is less than $P_{ub}$. If not, repeat algorithm from step 2.
+
+	\item If dynein unbinds, initialize the one bound state with the both bound configuration, run the Brownian dynamics simulation of the step, and wait until it rebinds.
+
+	\item Collect statistics about final displacement and one bound time. Repeat algorithm from step 2.
+
+	\end{alg}
+
+\end{algorithm}
+
+A more in-depth explanation and rigorous flow chart for the one bound Brownian dynamics simulation can be found here \cite{Capek2017, }.
+
+%\section{Time Evolution}
+%\textit{Simulate over a delta t during one bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}
 
@@
 \textit{How we defined our constants based on experiment and pictures.  Need to include figures here of experiment dynein and how we measure the pre and post stroke equilibrium angles.}
+
+\begin{figure}[hbt!]
+	\centering
+	\includegraphics[width=0.3\columnwidth]{../../plots/burgess-model-figure.pdf}
+	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
+	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} Left: the both bound model is superimposed over dynein micrograph.
+The arrow indicates 15nm.
+Image taken from \cite{burgess2003dynein}.
+Right: cryo-electron tomograph of dynein with the one-bound model overlaid.
+Image taken from \cite{grotjahn}.}
+	\label{fig:ModelParams}
+\end{figure}
 
@@
 \textit{Any tests of our model to make sure the code is reasonably sound and that the physics makes sense. Make sure there is no bugs in code. What was the bug testing procedure.}
+
+\section{Data Analysis} \label{sec:DataAna}
+\begin{equation}
+	p(x_i,x_f)=p(x_f|x_i)p(x_i)
+\end{equation}
+Bayes' Theorem
+\begin{equation}
+	p(x_i|L_i)=\frac{p(L_i|x_i)p(x_i)}{p(L_i)}
+\end{equation}
+\[
+	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)} 
+\]\[
+	p(x_i)=p(x_i|L_i)p(L_i)
+\]
+Detailed Balance Equation:
+\begin{equation}
+	p^n(L_i)=T^n(L_f|L_i)p^0(L_i)
+\end{equation}
+\begin{align}
+	T(L_f|L_i)&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
+	&=p(L_f|x_i)p(x_i|L_i)\\
+	&=p(L_f|L_i)
+\end{align}

### 2021-01-29 papers/jin-thesis/Chapters/2Theory.tex
Edited thesis

@@
 Both Bound]{\textbf{One Bound vs.
-Both Bound} \textit{Figure on left}: Prestroke one bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg.
-\textit{Figure on the right}: Poststroke both bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg.
+Both Bound} \textit{Left}: Prestroke one bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg.
+\textit{Right}: Poststroke both bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg.
 \cite{Capek2017}.}
@@
 \begin{equation}
-	\langle\rho_{ub, n}\rangle=\frac{\sum_{i}\rho_{ub, n} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, f}\rangle=\frac{\sum_{i}\rho_{ub, f} e^{-\beta E_{total,i}}}{Z}
+	\langle\rho_{ub, trail.}\rangle=\frac{\sum_{i}\rho_{ub, trail.} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, lead.}\rangle=\frac{\sum_{i}\rho_{ub, lead.} e^{-\beta E_{total,i}}}{Z}
+\end{equation}
+\begin{equation} \label{eqn:ProbTrail}
+	\langle P_{ub, trail.}(L)\rangle = \frac{\langle\rho_{ub, trail.}\rangle}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle}
 \end{equation}
 \begin{equation}
-	\langle P_{ub, n}(L)\rangle = \frac{\langle\rho_{ub, n}\rangle}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}
+	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle},
 \end{equation}
-\begin{equation}
-	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}.
-\end{equation}
+where $trail.$ and $lead.$ signifies a trailing or leading step.
 

### 2021-01-29 papers/jin-thesis/Chapters/3Methods.tex
Edited thesis

@@
 This allows us to simplify the code into two respective parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycles repeatedly after the model takes a step.
-The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculate the total energy.
+The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculates the total energy.
 If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one bound simulation and execute the Brownian dynamics.
 Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step.
-However, the big caveat with this method is that we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations.
-This will force the measured probabilities to be a function of $L$ and will be addressed later in Section (\ref{sec:DataAna}).
+However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations.
+This will force the measured probabilities to be a function of $L$ and will be addressed later in the Data Analysis section (Section \ref{sec:DataAna}).
 The algorithm for the both bound process is shown below:
@@
 	\begin{equation}
-		Z=\sum_{n}e^{\beta E_{total, n}}.
+		Z=\sum_{i}e^{\beta E_{total, i}}.
 	\end{equation}
-	We defined a $\kappa$ to normalize the relative unbinding probability and keep it less than 1.
+	We defined $\kappa$ to normalize the relative unbinding probability to keep it less than 1.
 
@@
 
-	\item Collect statistics about final displacement and one bound time. Repeat algorithm from step 2.
+	\item Collect statistics about the final position and one bound time. Repeat algorithm from step 2.
 
@@
 
-\section{Constants}
-\textit{How we defined our constants based on experiment and pictures.  Need to include figures here of experiment dynein and how we measure the pre and post stroke equilibrium angles.}
+\section{Model Parameters}
+%\textit{How we defined our constants based on experiment and pictures.  Need to include figures here of experiment dynein and how we measure the pre and post stroke equilibrium angles.}
+
+We match model paramters concerning dynein's geometry based on experiment by analyzing electron microscopy pictures of dynein.
+These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both bound and one bound states.
+The parameters we can measure from these figures are the domain radii, equilibrium angles, and the stalk and tail lengths.
 
@@
 	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
-	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} Left: the both bound model is superimposed over dynein micrograph.
-The arrow indicates 15nm.
-Image taken from \cite{burgess2003dynein}.
-Right: cryo-electron tomograph of dynein with the one-bound model overlaid.
-Image taken from \cite{grotjahn}.}
-	\label{fig:ModelParams}
+	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles \cite{burgess2003dynein}.
+\textit{Right:} Cryo-electron tomograph of one bound dynein for pre-stroke equilbrium angles \cite{grotjahn}.}
+	\label{fig:ParamsPics}
 \end{figure}
 
-\section{Parameter Fitting}
-\textit{How we will fit our parameters to agree with Yildiz' experimental data of dynein stepping.}
+However, these pictures do not help identify the binding rates ($k_b$, $k_{ub}$) and spring constants ($c_b$, $c_m$, $c_t$), thus making these parameters \textit{free variables} in the model.
+Fortunately, the Monte Carlo simulation can quickly optimize these free variables and fit different combinations of parameters to  different sets of experimental data.
+Since we want to replicate Yildiz's observations from Figure (\ref{fig:YildizCorrelation}), the free variables will be optimized according to the slope and y-intercept of the correlation.
 
 \subsection{Rate Constants}
-\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results.}
+\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results. Maybe bring up sticky rate???}
 
@@
 \section{Data Analysis} \label{sec:DataAna}
+As mentioned earlier, the simulation can only collect statistics for a given initial binding domain distance, $L$.
+This limits the probability data of landing at a final position to be a function of $L$.
+However, the unsigned distance is insignificant when calculating the step length of either a trailing or leading step.
+This promotes the new naming scheme of using initial displacement, $x_i$, and final displacement $x_f$, when identifying the distance between the binding domains before and after the step.
+The displacement is the $x$ position of the unbounded binding domain during the step, where the origin is defined at the bounded binding domain.
+This implies a negative initial displacement for a trailing step and a positive initial displacement for a leading step.
+
+However, we still suffer with the simulation outputting a probability distribution of final displacements as a function of initial displacements.
+To properly reproduce Yildiz's stepping plot, we need a joint probability distribution with both $x_i$ and $x_f$ as variables.
+Using probability notation, we want $p(x_i,x_f)$ (the probability of $x_i$ \textit{and} $x_f$) but we have $p(x_f|x_i)$ (the probability of $x_f$ \textit{given} $x_i$).
+To solve this problem, we can use conditional probability and solve for $p(x_i,x_f)$, as shown below:
+
+\[
+	p(x_f|x_i)=\frac{p(x_i,x_f)}{p(x_i)},
+\]
 \begin{equation}
-	p(x_i,x_f)=p(x_f|x_i)p(x_i)
+	p(x_i,x_f)=p(x_f|x_i)p(x_i).
 \end{equation}
-Bayes' Theorem
+Now, we only need to find the probability density of initial displacements, $p(x_i)$.
+Since the initial displacement is simply a signed distance $L$, we can use the probability of unbinding for a trailing or leading step as a function of $L$ from Equation (\ref{eqn:ProbTrail}) to generate $p(x_i)$.
+In otherwords, Equation (\ref{eqn:ProbTrail}) gives us $p(x_i|L_i)$.
+We can relate the two by using Bayes' Theorem:
+
 \begin{equation}
-	p(x_i|L_i)=\frac{p(L_i|x_i)p(x_i)}{p(L_i)}
+	p(x_i|L_i)=\frac{p(L_i|x_i)p(x_i)}{p(L_i)}.
 \end{equation}
+Since the probability of an initial distance given the initial displacement, $p(L_i|x_i)$, is always 1, we can simplify further,
 \[
 	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)} 
-\]\[
-	p(x_i)=p(x_i|L_i)p(L_i)
 \]
-Detailed Balance Equation:
+
 \begin{equation}
-	p^n(L_i)=T^n(L_f|L_i)p^0(L_i)
+	p(x_i)=p(x_i|L_i)p(L_i).
 \end{equation}
+Now, the final step is to solve for the probability density of initial distance, $p(L_i)$.
+We can do so by solving a Detailed Balance Equation, where we define a transition matrix, $T=p(L_f|L_i)$.
+This equation will have the form,
+\begin{equation}
+	p(L_i)=T^np^0(L_i),
+\end{equation}
+where $T$ is raised to the $n$ number of steps to signify equilibrium for the probability of all distances $L$.
+$n$ is chosen to be arbitrarily large to ensure equilibrium after enough steps (???
+FIXME this reasoning needs to be clearer.
+Ask Roundy.) To solve for $T$, we can use the previous probability distributions $p(x_f|x_i)$ and $p(x_i|L_i)$ to convert the probabilities to distances, as shown below:
 \begin{align}
-	T(L_f|L_i)&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
+	T&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
 	&=p(L_f|x_i)p(x_i|L_i)\\
-	&=p(L_f|L_i)
+	&=p(L_f|L_i),
 \end{align}
+where $I(L_f|x_i)$ is the identity matrix for converting $x_f$ into $L_f$.
+We have now solved for all the unknowns to generate a joint probability distribution of initial and final displacements, $p(x_i,x_f)$.

### 2021-01-31 papers/jin-thesis/Chapters/1Introduction.tex
Edited thesis
Edited thesis by adding refs and adjusted transition matrix part

@@
 Thus, fully understanding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to discovering the major breakthrough for neurodegenerative research.
-In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation in order to reproduce the steping behavior observed from experiment.
+In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce the steping behavior observed from experiment.
+\textit{ADD CLARIFIER}
 
@@
 Cells are complicated.
-Despite their fatal degeneracies, cells have the ability to move, perfectly divide, and spatially organize themselves.
-They can do so because tiny, two-legged molecular proteins, named \textit{motor proteins}, carry cargo containing information that outlines the blueprint for different functions within the cell.
+They have the ability to move, perfectly divide, and spatially organize themselves when they are functional, but can also be responsible for death when they are not.
+They can function because tiny, two-legged molecular proteins, named \textit{motor proteins}, carry cargo with information around the cell.
 These motor proteins consists of kinesin, myosin, and dynein.
@@
 Due to dynein's massive size compared to its motor protein siblings, dynein does not step uniformly but rather inchworms its ``feet" like a drunk human.
-This unique property makes dynein difficult to study when analyzing possible sources of molecular failure, but utters the importance of understanding the physical structure of the entire motor protein.
+This unique property makes dynein difficult to study when analyzing possible sources of molecular failure, but illustrates the importance of understanding the physical structure of the entire motor protein.
 
@@
 The large size of the AAA+ rings are blocking the view of the independent linkers connecting to the tail.
-This rendition similarly illustrates dynein’s structure as a domain-rod system.
+This rendition depicts dynein’s structure as a domain-rod system.
 \cite{TheTrappistArt}}
@@
 
-Dynein's crystal structure has been intensively studied because of the pivotal role it plays in dyneins unpredictable stepping nature.
+Dynein's crystal structure has been rigorously studied because of the pivotal role it plays in dyneins unpredictable stepping nature.
 Its inability to step uniformly is largely due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
@@
 The ATP provides dynein chemical energy which converts into mechanical energy for the dynein to transition between differenet conformational states during a step.
-Currently, there are many models being explored that discusses how dynein uses the ATP to step, such as the powerstroke model or the winch model, but this paper will be influenced by the more accepted powerstroke model.
+Currently, there are many models being explored that discuss how dynein uses the ATP to step, such as the powerstroke model or the winch model, but this paper will be influenced by the more accepted powerstroke model.
 For either case, it is best to define an axis on the MT for where dynein can step.
@@
 Simulations that model dynein's step exists, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
-Because of this, these simulations suffer from numerous assumptions made about the physical aspects of dynein's step.
+These simulations suffer from numerous assumptions made about the physical aspects of dynein's step.
 (\textit{Should reference a simulation here and be more detailed}) Some assume that dynein can only step in increments of 8nm or that the rebinding process is constrained to a certain time frame.

### 2021-01-31 papers/jin-thesis/Chapters/3Methods.tex
Edited thesis by adding refs and adjusted transition matrix part

@@
 
-The entire model and simulation code can be found here on \url{https://github.com/kiatvonj/dynein_walk}, where the model and simulation were coded using both Python and C++.
+The entire model and simulation code can be found at \url{https://github.com/kiatvonj/dynein_walk}, where the model and simulation were coded using both Python and C++.
 The both bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous and time independent, while the one bound Brownian dynamics was coded on C++ to utilize the faster computation speed for the time  dependent Brownian motion.
@@
 %\textit{Include a flow chart.}
-Since we want to generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk.
-This allows us to simplify the code into two respective parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycles repeatedly after the model takes a step.
+To generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk.
+This simplifies the code into two parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycle repeatedly after the model takes a step.
 The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculates the total energy.
@@
 However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations.
-This will force the measured probabilities to be a function of $L$ and will be addressed later in the Data Analysis section (Section \ref{sec:DataAna}).
+This forces the measured probabilities to be a function of $L$ and will be addressed later in the Data Analysis section (Section \ref{sec:DataAna}).
 The algorithm for the both bound process is shown below:
@@
 	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
-	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles \cite{burgess2003dynein}.
-\textit{Right:} Cryo-electron tomograph of one bound dynein for pre-stroke equilbrium angles \cite{grotjahn}.}
+	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles \cite{Burgess2003}.
+\textit{Right:} Cryo-electron tomograph of one bound dynein for pre-stroke equilbrium angles \cite{grotjahn2018cryo}.}
 	\label{fig:ParamsPics}
@@
 This limits the probability data of landing at a final position to be a function of $L$.
-However, the unsigned distance is insignificant when calculating the step length of either a trailing or leading step.
-This promotes the new naming scheme of using initial displacement, $x_i$, and final displacement $x_f$, when identifying the distance between the binding domains before and after the step.
+However, we can not calculate the step length for a trailing or leading step with an unsigned distance.
+This promotes the new naming scheme of using initial displacement, $x_i$, and final displacement $x_f$, when identifying the distances between the binding domains before and after the step.
 The displacement is the $x$ position of the unbounded binding domain during the step, where the origin is defined at the bounded binding domain.
@@
 Since the initial displacement is simply a signed distance $L$, we can use the probability of unbinding for a trailing or leading step as a function of $L$ from Equation (\ref{eqn:ProbTrail}) to generate $p(x_i)$.
-In otherwords, Equation (\ref{eqn:ProbTrail}) gives us $p(x_i|L_i)$.
+In other words, Equation (\ref{eqn:ProbTrail}) gives us $p(x_i|L_i)$.
 We can relate the two by using Bayes' Theorem:
@@
 \end{equation}
-Now, the final step is to solve for the probability density of initial distance, $p(L_i)$.
-We can do so by solving a Detailed Balance Equation, where we define a transition matrix, $T=p(L_f|L_i)$.
-This equation will have the form,
+Now, the final step is to solve for the probability distribution of distances, $p(L_i)$.
+Since we want the probability of absolute differences, we can neglect the distinction between `initial' and `final' and calculate an equilibrium distribution of distances, $p(L)$.
+To do so, we used a reoccurence relation, where we defined an initial $p^0(L)$ that is not in equilibrium and multiplied it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
+That is,
+\begin{align*}
+	p^1(L)= & p(L'|L)p^0(L) \\
+	p^2(L)= & p(L'|L)p^1(L)=p(L'|L)^2p^0(L)\\
+	&\vdots \\
+	p^n(L)= & p(L'|L)p^{n-1}(L)=p(L'|L)^np^0(L) 
+\end{align*}
 \begin{equation}
-	p(L_i)=T^np^0(L_i),
+	p^n(L)=p(L'|L)^np^0(L) 	
 \end{equation}
-where $T$ is raised to the $n$ number of steps to signify equilibrium for the probability of all distances $L$.
-$n$ is chosen to be arbitrarily large to ensure equilibrium after enough steps (???
-FIXME this reasoning needs to be clearer.
-Ask Roundy.) To solve for $T$, we can use the previous probability distributions $p(x_f|x_i)$ and $p(x_i|L_i)$ to convert the probabilities to distances, as shown below:
-\begin{align}
-	T&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
-	&=p(L_f|x_i)p(x_i|L_i)\\
-	&=p(L_f|L_i),
-\end{align}
-where $I(L_f|x_i)$ is the identity matrix for converting $x_f$ into $L_f$.
+where $n$ is an arbitrarily large number of steps to ensure the dynein is in equilibrium.
+This process can be thought of as a large row of dyneins all starting with the probability of an initial distance $p^0(L)$.
+Once they all take a step, their probability of having another distance $L'$ is $p(L'|L)p(L)$, and after a significant number of $n$ steps, the probability of having a distance $L$ would be the same for all the dyneins, thus being a equilibirum distribution of $L$.
+To solve for $p(L'|L)$, we can use the previous probability distributions $p(x_f|x_i)$ and $p(x_i|L_i)$ to convert these probabilities into distances, as shown below:
+\begin{equation}
+	p(L'|L)=I(L'|x_i)p(x_f|x_i)p(x_i|L),
+\end{equation}
+where $I(L'|x_i)$ is the identity matrix for converting $x_f$ into $L'$.
 We have now solved for all the unknowns to generate a joint probability distribution of initial and final displacements, $p(x_i,x_f)$.

### 2021-01-31 papers/jin-thesis/main.tex
Added a lot to my thesis directory
Paper edits
Edited thesis by adding refs and adjusted transition matrix part

@@
 \usepackage{indentfirst}
+
+\floatstyle{plaintop}
+\newfloat{algorithm}{thb}{lop}
+\floatname{algorithm}{Algorithm}
+\newenvironment{alg}
+{\hrulefill\begin{enumerate}}
+{\end{enumerate}\hrulefill}
 
@@
 	\input{./Chapters/1Introduction}
-	\chapter{Dynein}
-	\input{./Chapters/2Dynein}
 	\chapter{Theory}
-	\input{./Chapters/3Theory}
+	\input{./Chapters/2Theory}
 	\chapter{Methods}
-	\input{./Chapters/4Methods}
+	\input{./Chapters/3Methods}
 	\chapter{Results \& Discussion}
-	\input{./Chapters/5Results}
+	\input{./Chapters/4Results}
 	\chapter{Conclusion}
-	\input{./Chapters/6Conclusion}
+	\input{./Chapters/5Conclusion}
 
 \newpage
-\cite{Burgess2003} \cite{Cianfrocco2015mechanism} \cite{Dewitt2012} \cite{Capek2017}
+\cite{Burgess2003} \cite{Cianfrocco2015mechanism} \cite{Dewitt2012} \cite{Capek2017, waczak2019drunken}
+\cite{GoodsellArt} \cite{eschbach2011cytoplasmic}
+\cite{rao2019molecular} \cite{manna2020mechanistic} \cite{desantis2017lis1} 
+\cite{elshenawy2020lis1} \cite{ando2020small} \cite{kinoshita2018step} \cite{qiu2012dynein} \cite{muller1973dynamic} \cite{lim2007vorticity} \cite{fehr2008kinesin} \cite{trott2018mathematical}
+
 \bibliographystyle{unsrt}

### 2021-02-01 papers/jin-thesis/Chapters/2Theory.tex

@@
 
-Similar to other simulations, the binding and unbinding process will be governed by a rate-limiting step, where each process will be associated with binding rates.
-These binding rates will be model parameters defined by binding constants with units of probability per time.
+Similar to other simulations, the binding and unbinding process is governed by a rate-limiting step, where each process is associated with binding rates.
+These binding rates are model parameters defined by binding constants with units of probability per time.
 When the dynein is in the one bound state, we assume that the unbound binding domain can only bind when it is within a vertical range of the microtubule, i.e.

### 2021-02-01 papers/jin-thesis/Chapters/4Results.tex
Added to thesis and changed params defaults

--- 2021-01-07 papers/jin-thesis/Chapters/5Results.tex
@@
 \section{Optimized Parameters}
-\textit{Talk about best-fit parameters that matched experimentalists data. Include table with all parameters.}
+The set of parameters that best fit Yildiz's data are shown in the table below
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|l | r | r | r|}
+  	\hline
+    Param & Model & Experimental & Source \\
+    \hline
+    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
+    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
+    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
+    $k_b$ & $\kb s^{-1}$&  & \\
+    $k_{ub}$ & $\kub s^{-1}$ & & \\
+    $C$ & $\cexp$ & & \\
+    $L_s$ & $\ls nm$ & $21nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
+    $L_t$ & $\lt nm$ & $23nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
+    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
+    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
+    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
+    $\theta_t$ & $\eqt$ &  & \\
+    $R_t$ & $\radiust$ & $8nm$ & \cite{Burgess2003}\\
+    $R_m$ & $\radiusm$ & $11nm$ & \cite{Burgess2003}\\
+    $R_b$ & $\radiusb$ & $3.5nm$ & \cite{Burgess2003}\\
+    \hline
+  \end{tabular}
+  \caption{Optimized model parameters for following data sets. }
+%  \caption{Parameters used in simulation.
+$c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
+$k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
+$L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
+$c$ is the tension-gating factor.
+The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
+$R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
+Parameters used for all simulations unless otherwise noted}
+  \label{tab:params}
+\end{table}
+
+After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's geometric constants.
+\textit{FIXME: Plots are wrong, need to fix and ask which plots to finalize}
 
 \section{Stepping Patterns}
+The plots that were used to compare with experiment and optimize our parameters are shown below
 \begin{figure}[H]
 	\centering
-	\includegraphics[width=0.8\columnwidth]{/../../plots/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.2_1.05_0.0_90.0_197.0_242.0.png}
-	\caption[Final Displacement Probability Distribution]{\textbf{Final Displacement Probability Distribution}}
-	\label{fig:final_disp}
+	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.6\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
+Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement.
+\textit{Bottom:} One dimensional probability density of step length.
+Step length defined as final displacement minus the initial displacement.
+Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
+	\label{fig:DataStep}
 \end{figure}
+The first plot in Figure (\ref{fig:DataStep}) displayed the joint probability density of having a specific final displacement and initial displacement.
+The linear regression from experiment indicated the functionality between the two with an average final displacement of 9.1nm, indicated from the y-intercept.
+The second plot in Figure (\ref{fig:DataStep}) displayed the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement.
+The limitation of experiment was made very obvious here due to their inability to record short step lengths.
+This factor heavily influenced the parameter fitting because in order to best fit the linear correlation within steps, the model dynein had to take very fast and short steps.
+Since Yildiz observed a linear regression that averaged 0nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding.
+The step lengths close to 0nm from Experiment Fig 3A in Figure (\ref{fig:DataStep}) were large step lengths in the off-axis.
+
+We fit the pre-exponential unbinding factor, $C$, based on experimental probability of having a trailing (lagging) step, as shown below
 
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{Figures/step_length_hist.png}
-	\caption[Step Length Histogram]{\textbf{Step Length Histogram}}
-	\label{fig:step_length}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
+	\label{fig:ProbTrail}
 \end{figure}
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\columnwidth]{Figures/prob_lagging_vs_init_L.png}
-	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
-	\label{fig:step_length}
-\end{figure}
-
-\textit{Analysis on stepping patterns and what the parameters of our model indicate. Does dynein take a lot of fast steps?}
+\textit{Need to include time plots and maybe more figures. Talk about the short time step.}
 
 \section{Agree with Experiment?}
-\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job?}
+\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job? }
+
+\textit{Need to eventually bring up the issue of being able to fit both the 2d hist linear regression and step length plot: If we want to fit linear regression, we must have short steps, but if we have short steps, the step length plot will not match at steps $>$ 20nm.
+Hard to agree with experiment when our dynein is forced to take short steps.
+Mention time too.}

### 2021-02-01 papers/jin-thesis/Chapters/5Conclusion.tex
Added to thesis and changed params defaults

@@
 
+The model has the flexibility to replicate many sets of experimental data.
+The most unique set is Yildiz and we were able to reproduce his observations to the best of our ability with the set of parameters we used.
+We discovered an inherent problem when trying to fit to data that cannot observe 0nm steps.
+We usec Monte Carlo that produces a smooth probability distribution because of running large numbers of simulations and law of large numbers.
+However, In order to best fit the linear regression, the simulation must average 0nm step lengths, meaning we need to force parameters so that model dynein takes very quick and short steps.
+But, if we do this, the average step length will be a lot less than what they observe and the model will not be able to achieve large steps.
+
 \section{Further Work}
 \textit{How can we improve our model?}
+
+We can improve our model by implementing a third dimension that utilizes the off-axis.
+We could always run more simulations with different sets of parameters until we find the perfect set.
+We could implement a optimization process of maximizing and minimizing all parameters so that we get a large range of combinations and eventually narrow down to a parameter space that cleany replicates data.

### 2021-02-01 papers/paper/paper.tex
Added to thesis and changed params defaults

@@
 \section*{Plots from MC}
+%\begin{figure}[tbhp]
+%\centering
+%\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
+%\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+%\label{fig:final_disp_prob}
+%\end{figure}
+
+%\begin{figure}[tbhp]
+%\centering
+%\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
+%\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+%\label{fig:step_length_prob}
+%\end{figure}
+
+%\begin{figure}[tbhp]
+%\centering
+%\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
+%\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
+%\label{fig:step_length_prob_den}
+%\end{figure}
+%
 \begin{figure}[tbhp]
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
-\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:final_disp_prob}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
-\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:step_length_prob}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0_-0.3563}
-\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
-\label{fig:step_length_prob_den}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
 \caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.5}
 \caption{\textbf{Bothbound Time.} Dimentions: $s$ .}

### 2021-02-01 scripts/make_mc_plots.py

@@ -476,7 +476,7 @@ def make_bothbound_plots(args, plotpath, bb_L, bb_P_trailing, bb_avg_t, **_):
     plt.plot(bb_L, bb_avg_t,color='C0')
     plt.xlabel('initial L (nm)')
     plt.ylabel('Average time (s)')
-    plt.ylim(0,0.02)
+    plt.ylim(0,0.04)
     plt.legend()
     plt.title('C = {}'.format(args.C))
     plt.savefig(plotpath+'bb_time_{}.png'.format(args.C))

### 2021-02-02 papers/jin-thesis/Chapters/2Theory.tex
Added to thesis and changed params defaults
Edited thesis and added sticky rate to params to latex

@@
 The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics.
-Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with its environment by increasing the radii of the domains to be slightly larger than experimental measurements.
+Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with its environment by increasing the radii of the domains slightly larger than experimental measurements.
 
@@
 In order to best simulate the stretching and forward kicking motion of the power stroke, we define our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain.
-This can be analogous to how humans walk as the domains are used as flexible joints when taking a step.
+This can be analogous to how humans walk, where the domains correspond to flexible joints when taking a step.
 Defining our domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law:
@@
 According to the Mechanochemical Cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step.
-However, many of these states possess similar conformations, where the dynein either has one binding domain bounded while the other diffuses above the microtubule or has both binding domains bounded to the microtubule.
+However, many of these states possess similar conformations, where the dynein either has one foot bounded while the other diffuses above the microtubule or has both feet bounded to the microtubule.
 Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.
@@
 Therefore, the equilibrium angles for the motor domains will differ in order to bias the unbound leg to straighten and perform the powerstroke.
+This straightening mechanic resembles the linker being primed before allowing the binding domain to rebind.
 
@@
 These binding rates are model parameters defined by binding constants with units of probability per time.
-When the dynein is in the one bound state, we assume that the unbound binding domain can only bind when it is within a vertical range of the microtubule, i.e.
+When the dynein is in the one bound state, the binding domain depends on two rebinding rates: the linker priming rate ($\rho_p$) and the binding rate ($\rho_b$).
+We assume that the unbound binding domain can only bind when the linker is primed and the unbound binding domain is within a vertical range of the microtubule, i.e.
+\begin{equation}
+	\rho_p=k_p
+\end{equation}
 \begin{equation}
@@
 \end{equation} 
-Here, the $\rho_b$ is the binding rate, $k_b$ is the rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
+Here, the $k_p$ is the priming rate constant, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
 
@@
 \begin{equation}
-	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle},
+	\langle t_{bb}(L) \rangle =\frac{1}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle},
 \end{equation}

### 2021-02-03 papers/jin-thesis/Chapters/1Introduction.tex

@@
 
-	Neurodegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States.
+	Neurodegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States \cite{eschbach2011cytoplasmic}.
 Scientists all over the world struggle to find a solution for these diseases and continue to hope for a breakthrough in science in attempt to prevent or even cure these fatal diseases.
@@
 However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredicatable in nature.
-Thus, fully understanding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to discovering the major breakthrough for neurodegenerative research.
-In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce the steping behavior observed from experiment.
-\textit{ADD CLARIFIER}
+Thus, fully understanding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to discovering a major breakthrough in neurodegenerative research.
+In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior.
+What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which we seek to replicate Yildiz's observation of correlated stepping.
 
@@
 Dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains.
-These domains are the tail domain, the motor domain (constructed from six AAA+ domains that form a ring), and the microtubule binding domains, where a linker connects the tail to the AAA+ ring and a stalk connects the AAA+ ring to the binding domain.
-Figure (\ref{fig:structure}) displays a simplified dynein where both subunits are connected to the tail with separate linkers.
+Figure (\ref{fig:structure}) displays these domains and labels them as the tail domain, motor domains (constructed from six AAA+ domains that form a ring), and the microtubule binding domains.
+The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by the stalks.
 
@@
 Its inability to step uniformly is largely due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
-This is unique when commpared to kinesin and myosin, as their motor domains are much closer to the MT causing their center of mass to keep the protein controlled and steady when stepping.
-Despite dynein's large structure, dynein can still achieve processive stepping towards the negative end of the MT due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, thus is why the AAA+ domains are referred to as the motor domains.
+This is unique when commpared to kinesin and myosin, as their motor domains are much closer to the MT causing a more controlled and consistent step due to their low center of mass.
+Despite dynein's large structure, dynein can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, thus is why the AAA+ domains are referred to as the motor domains.
 
@@
 
-Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis with its motor domains.
-The ATP provides dynein chemical energy which converts into mechanical energy for the dynein to transition between differenet conformational states during a step.
-Currently, there are many models being explored that discuss how dynein uses the ATP to step, such as the powerstroke model or the winch model, but this paper will be influenced by the more accepted powerstroke model.
-For either case, it is best to define an axis on the MT for where dynein can step.
+Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis.
+The ATP binds to the motor domain and converts chemical energy into mechanical energy for the dynein to transition between differenet conformational states during a step.
+This process allows the binding domains to let go and reattach to the microtubule at different locations causing varying step sizes.
+We can measure dynein's step length by definined an axis on the microtubule for where dynein can step.
 
-The on-axis is defined to be the axis parallel to the direction of forward stepping towards the negative end of the MT, while the off-axis is defined to be the axis perpendicular towards the side, as shown in Figure (\ref{fig:axis}).
+The on-axis is defined to be the axis parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is defined to be the axis perpendicular, as shown in Figure (\ref{fig:axis}).
 Figure (\ref{fig:axis}) also displays the alternative helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.
@@
 
-\textit{Maybe add a transition here. Seems awkward to go straight into next section...}
+While ATP hydrolysis dictates the forward stepping during dynein's walk, the geometry of the domains is still a question for experimentalists.
+How exactly does the motor, tail, and linker  coorperate (\textit{find a better word}) to achieve processive motion?
+Do the motor domains act as knees and stretch out for a step?
+Or do the knees stay bent, while the tail swings forward?
+Despite ongoing debates, researchers suggest the former and named this process the powerestroke model.
 
@@
 
-As mentioned earlier, there are many theorized models for dynein's stepping, but the widely accepted model is the powerstroke model within the mechenochemical cycle introduced by Cianfrocco et al.
+The widely accepted powerstroke model was best exhibted within the mechanochemical cycle introduced by Cianfrocco et al.
 \cite{Cianfrocco2015mechanism}.
@@
 This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward.
-This key detail within the transition of stretching the linker distinguishes a ``pre-stroke" and a ``post-stroke" state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step.
+This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step.
 A closer visualization of this transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.
@@
 
+Although the mechanochemical cycle provides a reasonable model for dynein's step and illustrates the motion between the domains, the model still generalizes the dependencies of the step and fails to analyze different geometric factors that can alter the conformations.
+
 \section{Experimental Research on Dynein}
 
-Although the mechanochemical cycle provides a reasonable model for dynein's step, the model fails to analyze the precise movements of each domain and how different configurations alter the conformational transitions.
+Experimental research investigates the correlations within dynein's stepping pattern and how different parameters may affect the step.
+These consists of the angle dependency during the stretching of the linker, the affect of the initial conformation when taking a step, the ATP concentration for hydrolysis, etc.
+However, due to dynein's small scale, experiment often disagrees with one another and differs depending on the technique of measuring dynein.
+
+%Although the mechanochemical cycle provides a reasonable model for dynein's step, the model fails to analyze the precise movements of each domain and how different configurations alter the conformational transitions.
 To what extent does the linker stretch when exhibiting the powerstroke and is it angle dependent?
@@
 
-Experimentalists approach measuring dynein in various ways involving electron microscopy and quantum measuring techniques.
+Experimentalists approach measuring dynein in various ways, which can involve electron microscopy or quantum measuring techniques.
 Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod.
-However, all experimental procedures suffer with one major limitation: undetectable steps close to 0nm.
-\textit{This bit is akward.
-Maybe just combine with next part to and label it Interstep coordination or something.}
+Despite the different procedures, all measuring techniques suffer from their inability to measure small (\textit{change word}) movement.
+This causes steps with short step lengths to be undetectable, such as if dynein quickly rebinds at the same spot after unbinding.
+The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables.
+In this paper, we will focus on Yildiz et al.
+unique finding of observing a stepping correlation between the initial interhead separation and step length.
 
-\subsection{Interhead Coordination}
+\subsection{Yildiz's Stepping Correlation}
 %\textit{Purpose of my research. Trying to make model and fit to Yildiz analysis of dynein having interstep correlation. Dependency between step length and initial inter head separation.}
@@
 observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}.
-This discovery challenged established views on dynein's stepping processivity and poses the question around the existence of interhead coordination between the motor domains when stepping.
+This discovery challenged established views on dynein's stepping processivity and poses the question if there exists interhead coordination between the motor domains when stepping.
 Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.
@@
 
-Simulations that model dynein's step exists, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
+We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results.
+Currently, other simulations that model dynein's step exists, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
 These simulations suffer from numerous assumptions made about the physical aspects of dynein's step.
@@
 constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment.
-Instead of making assumptions about the physical properties of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes that the force applied from the ATP is incorporated within the forces on the domains (???
-weird wording need to FIXME).
-Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experiences Brownian motion during a step to mimic stochastic movement \cite{Capek2017, Burgess2003}.
+Instead of making assumptions about the physical properties of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes that the energy transfer from the ATP is incorporated within the binding processes.
+Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experiences Brownian motion during a step to mimic stochastic movement \cite{Capek2017, }.
 They were able to track dynein's precise movement along a walk and compare their stepping results to experiment.

### 2021-02-03 papers/jin-thesis/Chapters/3Methods.tex
Added to thesis and changed params defaults

@@
 These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both bound and one bound states.
-The parameters we can measure from these figures are the domain radii, equilibrium angles, and the stalk and tail lengths.
+The parameters we can measure from these figures are the domain radii \{$R_i$\}, equilibrium angles \{$\theta_{i,eq}$\}, and the stalk and tail lengths ($L_s$, $L_t$).
 
@@
 
-However, these pictures do not help identify the binding rates ($k_b$, $k_{ub}$) and spring constants ($c_b$, $c_m$, $c_t$), thus making these parameters \textit{free variables} in the model.
+However, these pictures do not help identify the binding rates ($k_p$, $k_b$, $k_{ub}$) and spring constants ($c_b$, $c_m$, $c_t$), making these parameters \textit{free variables} in the model.
 Fortunately, the Monte Carlo simulation can quickly optimize these free variables and fit different combinations of parameters to  different sets of experimental data.
@@
 
-\subsection{Rate Constants}
-\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results. Maybe bring up sticky rate???}
+\subsection{Validation for Model Parameters}
+%\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results. Maybe bring up sticky rate???}
 
-\section{Model Validation}
-\textit{Any tests of our model to make sure the code is reasonably sound and that the physics makes sense. Make sure there is no bugs in code. What was the bug testing procedure.}
+Despite simulating many combinations of parameters, the number of free variables still produce many degrees of freedom.
+This makes it difficult to test the entire parameter space and truly invesitage the relationships between different sets of parameters.
+We approach this problem by individually attributing the parameters to a specific data set from exerpiment.
+For instance, the exponential unbinding constant, $C$, will be fitted specifically to Figure (\ref{fig:trailingbias}).
+We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, since the units are $s^{-1}$ and the inverse will yield the average time it takes to unbind, i.e.
+the both bound time.
+The rebinding rates, $k_p$ and $k_b$, can also be fitted to experiment's one bound time, but these rates are directly correlated to dynein's step length.
+The ability for dynein to take long steps are dependent on how long dynein diffuses above the microtubule.
+Therefore, the rebinding rates will have a much larger parameter space due to the flexibility of optimizing according to the one bound time or step length.
+Since we are interested in Yildiz's step lengths, we will match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}).
+The last set of parameters are the spring constants.
+The spring constants also influence the step length because they dictate the strength of the restoring force.
+We fit the spring constants last to control the variance of step lengths.
+
+%An increase in the binding rate will cause fast steps and significantly shorter step lengths that approach 0nm (rebinds where foot unbinded).
+This causes a dilemma because experiments cannot record step lengths close to 0nm.
 

### 2021-02-03 papers/jin-thesis/Chapters/4Results.tex

@@
     $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
+    $k_p$ & $\kstk s^{-1}$&  & \\
     $k_b$ & $\kb s^{-1}$&  & \\

### 2021-02-24 papers/jin-thesis/Chapters/2Theory.tex
Editted thesis

@@
 \section{Model}
-In order to reliably reproduce experimental observations of dynein's step, a model of dynein should responsibly conserve dynein's spatial information and complex structure without limiting the physical interactions with its environment.
+To reliably reproduce experimental observations of dynein's step, a model of dynein should responsibly conserve dynein's spatial information and complex structure without limiting the physical interactions with its environment.
 Doing so computationally introduces a strict balance between model accuracy and computational efficiency.
@@
 
-Despite dynein's complexity allowing its step to vary in both length and direction, we limit our model to one direction to eliminate a dimension (the off-axis) when analyzing the forward stepping pattern of dynein.
+Despite dynein's complexity allowing its step to vary in both length and direction, we limit our model to one direction to eliminate the off-axis dimension when analyzing the forward stepping pattern of dynein.
 This would also simplify the asymmetry of the microtubule when the dynein is stepping either on the $\alpha$ or $\beta$ tubulin.
@@
 The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics.
-Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with its environment by increasing the radii of the domains slightly larger than experimental measurements.
+Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains slightly larger than experimental measurements.
 
 \subsection{Domains as Angular Springs}
-In order to best simulate the stretching and forward kicking motion of the power stroke, we define our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain.
+To best simulate the stretching and forward kicking motion of the power stroke, we define the domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ for each domain.
 This can be analogous to how humans walk, where the domains correspond to flexible joints when taking a step.
-Defining our domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law:
+Defining the domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law:
 \begin{equation}
@@
 $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
-This equation would then be used throughout the entirety of the simulation to determine the total energy of our dynein at a given conformation.
+This equation is used throughout the simulation to determine the total energy of our dynein at a given conformation.
 
 \subsection{Two-State System}
-According to the Mechanochemical Cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step.
+According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step.
 However, many of these states possess similar conformations, where the dynein either has one foot bounded while the other diffuses above the microtubule or has both feet bounded to the microtubule.
@@
 Differentiating the two allows us to more conveniently bias the conformational change by defining different equilibrium angles for both states.
-Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both bound state will be identical for both binding and motor domain pairs, i.e.
+Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both bound state is identical for both binding and motor domain pairs, i.e.
 $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
-However, in the one bound state, the unbound leg wants to exhibit the powerstroke and kick out.
-Therefore, the equilibrium angles for the motor domains will differ in order to bias the unbound leg to straighten and perform the powerstroke.
+However, in the one bound state, the unbound leg exhibits the powerstroke and kick out.
+Therefore, the equilibrium angles for the motor domains differ in order to bias the unbound leg to straighten and perform the powerstroke.
 This straightening mechanic resembles the linker being primed before allowing the binding domain to rebind.
@@
 When the dynein is in the both bound state and wants to unbind, we incorporate a stepping bias in the unbinding rate.
-As supported from Yildiz in Figure (\ref{fig:trailingbias}), the likelihood of the trailing leg unbinding is greater than the leading leg when the distance between the two legs increase.
+As supported from Yildiz in Figure (\ref{fig:trailingbias}), the likelihood of the trailing leg unbinding is greater than the leading leg when the distance between the two legs increases.
 
@@
 \end{equation}
-We introduce a new model parameter $C$, the exponential unbinding constant, that allows us to control this bias.
-For the trailing step bias we want to achieve, we define $C$ to be negative because the trailing $\theta_b$ tends to be less than the leading $\theta_b$ and  when $\theta_b$ is less than $\theta_{b,eq}$, the unbinding rate becomes large.
+We introduce a new model parameter $C$, the exponential unbinding constant, that controls this bias.
+To achieve trailing step bias, we define $C$ to be negative because the trailing $\theta_b$ tends to be less than the leading $\theta_b$ and  when $\theta_b$ is less than $\theta_{b,eq}$, the unbinding rate becomes large.
 
@@
 
-When simulating dynein's one bound motion, the domains of constant mass must still obey classical Newtonian physics and follow Newton's laws of motion.
-Knowing this, we can use Newton's second law to derive the equations of motion for each domain when experiencing various forces.
-That is,
+When simulating dynein's one bound motion, the domains of constant mass must obey classical Newtonian physics and follow Newton's laws of motion. That is,
 \begin{equation}
@@
 \end{equation} 
-
-For our domains experiencing the aqueous environment in the cell, the first force we can identify is the force of linear drag:
+For the domains in the aqueous environment of the cell, linear drag force is
 \begin{equation}
-	\textbf{F}_{drag}=-\gamma \dot{\textbf{r}}
+	\textbf{F}_{drag}=-\gamma \dot{\textbf{r}},
 \end{equation}
-where $\gamma$ is the drag coefficient defined from Stokes' law to be:
+where $\gamma$ is the drag coefficient defined by Stokes' law,
 \begin{equation}
@@
 
-The secondary force that we can easily identify is the random force inspiring the Brownian motion.
-This force describes the random interactions the domains experience with the paticles making the solvent.
-It will be denoted as \textbf{F}$_{rand}$, and the ``randomness" will be sampled from a zero-centered Gaussian with variance:
+A second force is the random force inspiring the Brownian motion.
+\textbf{F}$_{rand}$ describes the random interactions between the domains and the solvent paticles.
+\textbf{F}$_{rand}$ is sampled from a zero-centered Gaussian with variance
 \begin{equation}
-	\sigma^2=\sqrt{\frac{2\gamma}{\beta\Delta t}}.
+	\sigma^2=\sqrt{\frac{2\gamma}{\beta\Delta t}},
 \end{equation}
-where $\beta$ is the thermodynamic beta and $\Delta t$ is a time-step.
+where $\beta=\frac{1}{k_bT}$  and $\Delta t$ is a time-step.
 
-The final existing force on the domains will be the tension force the domains have on each other \textit{via} their connecting rods.
-We will name this \textbf{F}$_T$.
-Incorporting all these forces with Newton's second law, we can produce an equation otherwise known as the \textit{Langevin Equation}:
+The final force is the tension force, \textbf{F}$_T$, between the domains \textit{via} their connecting rods. Incorporting all these forces, we produce the \textit{Langevin Equation}:
 \begin{equation}
@@
 \end{equation}
-As mentioned earlier, in order to properly demonstrate Brownian dynamics, we must assume strong drag where $|\gamma \dot{\textbf{r}}|\ll |m\ddot{\textbf{r}}|$.
-Or in otherwords, we assume that the immense viscosity in the environment stricts the ability for our domains to accelerate.
+To properly demonstrate Brownian dynamics, we must assume strong drag where $|\gamma \dot{\textbf{r}}|\ll |m\ddot{\textbf{r}}|$.
+In other words, we assume that the immense viscosity in the environment restricts the ability for the domains to accelerate.
 Simplifying the \textit{Langevin Equation} and solving for $\dot{\textbf{r}}$, we get:

### 2021-02-24 papers/jin-thesis/Chapters/3Methods.tex
Editted thesis

@@
 We approach this problem by individually attributing the parameters to a specific data set from exerpiment.
-For instance, the exponential unbinding constant, $C$, will be fitted specifically to Figure (\ref{fig:trailingbias}).
-We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, since the units are $s^{-1}$ and the inverse will yield the average time it takes to unbind, i.e.
+For instance, the exponential unbinding constant, $C$, is fitted specifically to Figure (\ref{fig:trailingbias}).
+We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, and the inverse yields the average time it takes to unbind, i.e.
 the both bound time.
-The rebinding rates, $k_p$ and $k_b$, can also be fitted to experiment's one bound time, but these rates are directly correlated to dynein's step length.
-The ability for dynein to take long steps are dependent on how long dynein diffuses above the microtubule.
-Therefore, the rebinding rates will have a much larger parameter space due to the flexibility of optimizing according to the one bound time or step length.
-Since we are interested in Yildiz's step lengths, we will match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}).
-The last set of parameters are the spring constants.
+The rebinding rates, $k_p$ and $k_b$, are fit to experiment's one bound time, and these rates are directly correlated to dynein's step length.
+The ability for dynein to take long steps is dependent on how long dynein diffuses above the microtubule.
+Therefore, the rebinding rates have a much larger parameter space due to the flexibility of optimizing according to the one bound time or step length.
+Since we are interested in Yildiz's step lengths, we match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}).
+The last parameters are the spring constants.
 The spring constants also influence the step length because they dictate the strength of the restoring force.
@@
 \section{Data Analysis} \label{sec:DataAna}
-As mentioned earlier, the simulation can only collect statistics for a given initial binding domain distance, $L$.
+As mentioned earlier, the simulation can collect statistics only for a given initial binding domain distance, $L$.
 This limits the probability data of landing at a final position to be a function of $L$.
@@
 
-However, we still suffer with the simulation outputting a probability distribution of final displacements as a function of initial displacements.
+However, the simulation still outputs a probability distribution of final displacements as a function of initial displacements.
 To properly reproduce Yildiz's stepping plot, we need a joint probability distribution with both $x_i$ and $x_f$ as variables.
@@
 Since we want the probability of absolute differences, we can neglect the distinction between `initial' and `final' and calculate an equilibrium distribution of distances, $p(L)$.
-To do so, we used a reoccurence relation, where we defined an initial $p^0(L)$ that is not in equilibrium and multiplied it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
+To do so, we used a reccurence relation, where we define an initial $p^0(L)$ that is not in equilibrium and multiply it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
 That is,

### 2021-03-01 papers/jin-thesis/Chapters/1Introduction.tex

@@
 Although this breakthrough has yet to come, research suggests that motor protein failure is a main cause of cell degeneration.
-More specifically, defects in the motor protein dynein has been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties.
-However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredicatable in nature.
-Thus, fully understanding the mechanisms of dynein can allow us to further conclude causes of its failure, putting us one step closer to discovering a major breakthrough in neurodegenerative research.
+More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties.
+However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature.
+Thus, fully understanding the mechanisms of dynein can allow us to further understand causes of its failure.
 In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior.
@@
 	\includegraphics[width=0.5\columnwidth]{Figures/dynein_walking_art.jpg}
-	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} walking along a microtubule in a weary cell. \cite{JohnsonArt}}
+	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} walking along a microtubule in a cell. \cite{JohnsonArt}}
 	\label{fig:ArtDynein}
@@
 They can function because tiny, two-legged molecular proteins, named \textit{motor proteins}, carry cargo with information around the cell.
-These motor proteins consists of kinesin, myosin, and dynein.
-They can travel all around the cell on a cytoskeleton composed of microtubules (MT) that act as a walkway for the proteins.
+These motor proteins are kinesin, myosin, and dynein.
+They travel around the cell on a cytoskeleton composed of microtubules (MT) that act as a walkway for the proteins.
 A depiction of dynein walking along the microtubule is shown above in Figure (\ref{fig:ArtDynein}).
-Microtubules are constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulin dimers that polarizes the microtubule depending on which tubulin is left hanging at the ends.
+Microtubules are constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulin dimers that polarize the microtubule depending on which tubulin is left hanging at the ends.
 In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a positive end that pulls kinesin and myosin.
-However, dynein opposes kinesin and myosin by walking towards the nucleus cell body where the MT is negatively charged.
-This attraction to both ends drives the directed stepping motion for each motor protein and is shown in Figure (\ref{fig:transport}).
+However, dynein walks toward the nucleus cell body where the MT is negatively charged.
+This attraction to drives the directed stepping motion for each motor protein and is shown in Figure (\ref{fig:transport}).
 
@@
 	\caption[Structure of Dynein]{\textbf{Structure of Dynein.} Illustration of cytoplasmic dynein's heavy chain subunits bounded to the microtubule.
-The large size of the AAA+ rings are blocking the view of the independent linkers connecting to the tail.
+The AAA+ rings block the view of the independent linkers connecting to the tail.
 This rendition depicts dynein’s structure as a domain-rod system.
@@
 
-Dynein's crystal structure has been rigorously studied because of the pivotal role it plays in dyneins unpredictable stepping nature.
+Dynein's crystal structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature.
 Its inability to step uniformly is largely due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
-This is unique when commpared to kinesin and myosin, as their motor domains are much closer to the MT causing a more controlled and consistent step due to their low center of mass.
-Despite dynein's large structure, dynein can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, thus is why the AAA+ domains are referred to as the motor domains.
+In kinesin and myosin, the motor domains are much closer to the MT, causing a more controlled and consistent step due to their low center of mass.
+Despite dynein's large structure, it can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, which is why the AAA+ domains are referred to as the motor domains.
 
@@
 This process allows the binding domains to let go and reattach to the microtubule at different locations causing varying step sizes.
-We can measure dynein's step length by definined an axis on the microtubule for where dynein can step.
+We can measure dynein's step length by definining an axis on the microtubule for where dynein can step.
 
@@
 For the on-axis, positive displacement is defined towards the minus end of the microtubule.
-Dark and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers.
+Dark grey and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers.
 \cite{Dewitt2012} }
@@
 While ATP hydrolysis dictates the forward stepping during dynein's walk, the geometry of the domains is still a question for experimentalists.
-How exactly does the motor, tail, and linker  coorperate (\textit{find a better word}) to achieve processive motion?
+How exactly do the motor, tail, and linker achieve processive motion?
 Do the motor domains act as knees and stretch out for a step?
@@
 observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}.
-This discovery challenged established views on dynein's stepping processivity and poses the question if there exists interhead coordination between the motor domains when stepping.
+This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping.
 Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.
@@
 We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results.
-Currently, other simulations that model dynein's step exists, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
+Currently, other simulations that model dynein's step exist, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
 These simulations suffer from numerous assumptions made about the physical aspects of dynein's step.
-(\textit{Should reference a simulation here and be more detailed}) Some assume that dynein can only step in increments of 8nm or that the rebinding process is constrained to a certain time frame.
+(\textit{Should reference a simulation here}) Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame.
 These limitations make it impossible for the models to replicate unique discoveries about dyneins stepping, such as Yildiz's correlation from above.
-A perfect simulation ought to lift these physical constraints and accurately reproduce experimental data.
 

### 2021-03-03 papers/jin-thesis/Chapters/1Introduction.tex
Thesis work

@@
 
-	Neurodegenerative diseases, such as Alzheimer's and Huntinton's disease, have consistently been one of the leading causes of death in the United States \cite{eschbach2011cytoplasmic}.
-Scientists all over the world struggle to find a solution for these diseases and continue to hope for a breakthrough in science in attempt to prevent or even cure these fatal diseases.
-Although this breakthrough has yet to come, research suggests that motor protein failure is a main cause of cell degeneration.
+	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, is a leading cause of death in the United States \cite{eschbach2011cytoplasmic}.
+Scientists have yet to find a prevention or cure to these fatal diseases but suggests that motor protein failure directly contributes to cell degeneration.
 More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties.
-However, unlike dynein's motor protein siblings, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature.
+However, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature.
 Thus, fully understanding the mechanisms of dynein can allow us to further understand causes of its failure.
 In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior.
-What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which we seek to replicate Yildiz's observation of correlated stepping.
+What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which we seek to replicate Yildiz's observation of correlated stepping \cite{Dewitt2012}.
 
@@
 	\centering
-	\includegraphics[width=0.5\columnwidth]{Figures/dynein_walking_art.jpg}
+	\includegraphics[width=0.3\columnwidth]{Figures/dynein_walking_art.jpg}
 	\caption[Artist Rendition of Dynein]{\textbf{Artist Rendition of Dynein} walking along a microtubule in a cell. \cite{JohnsonArt}}
@@
 Cells are complicated.
-They have the ability to move, perfectly divide, and spatially organize themselves when they are functional, but can also be responsible for death when they are not.
-They can function because tiny, two-legged molecular proteins, named \textit{motor proteins}, carry cargo with information around the cell.
-These motor proteins are kinesin, myosin, and dynein.
-They travel around the cell on a cytoskeleton composed of microtubules (MT) that act as a walkway for the proteins.
-A depiction of dynein walking along the microtubule is shown above in Figure (\ref{fig:ArtDynein}).
-Microtubules are constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulin dimers that polarize the microtubule depending on which tubulin is left hanging at the ends.
-In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a positive end that pulls kinesin and myosin.
-However, dynein walks toward the nucleus cell body where the MT is negatively charged.
-This attraction to drives the directed stepping motion for each motor protein and is shown in Figure (\ref{fig:transport}).
+They have the ability to move, perfectly divide, and spatially organize themselves but are also responsible for fatal diseases when these functions fail.
+Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information to different parts of the cell.
+They travel around the cell on a cytoskeleton composed of microtubules that act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})).
+These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}).
+Because of kinesin and myosin's compact structure being close to the microtubule, they exhibit a uniform ``hand-over-hand" stepping pattern where their legs take turns alternating steps like a human.
+On the other hand, dynein's structure involves two autonomous motors that cause inconsistent steps.
+Dynein exhibits an inchworm pattern while walking where one leg consistently stays ahead of the other, emulating a limping motion.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.4\columnwidth]{Figures/motor_comparison.png}
+	\caption[Motor Proteins]{\textbf{Motor Proteins} Structure of myosin, kinesin, and dynein. \cite{JohnsonArt}}
+	\label{fig:Compare}
+\end{figure}
+
+In addition to their structural differences, dynein walks in the oppposite direction of its motor protein siblings and towards the negative end of the microtubule.
+Because microtubules are protein dimers constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulins, the microtubule track is polarized depending on which tubulin dominates at the end points.
+In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a negative end at the nucleus and influencing dynein's directionality.
+Figure (\ref{fig:transport}) displays kinesin and dynein experiencing a charged attraction to the end points, while they share a cargo to deliver information during axonal transport.
 
@@
 	\caption[Charge Influenced Transport]{\textbf{Charge Influenced Transport}.
-Dynein and kinesin transporting cargo on the axon of a neuron cell for building the axon growth cone.
+Dynein and kinesin transporting cargo with information on the axon of a neuron cell for building the axon growth cone.
 They share cargo and take turns delivering each other to opposite ends of the cell.
@@
 
-Both kinesin and myosin exhibit hand-over-hand stepping, where their ``legs" take turns alternating steps like a human.
-Due to dynein's massive size compared to its motor protein siblings, dynein does not step uniformly but rather inchworms its ``feet" like a drunk human.
-This unique property makes dynein difficult to study when analyzing possible sources of molecular failure, but illustrates the importance of understanding the physical structure of the entire motor protein.
+These unique properties make dynein difficult to study when analyzing possible sources of molecular failure, but illustrates the importance of understanding its entire physical structure and the chemical interactions with ATP to produce motion.
 
+\newpage
 \section{Structure}
@@
 
-Dynein is composed of two motor heavy chain subunits of linked amino acids, called polypeptides, each which are separated into domains.
-Figure (\ref{fig:structure}) displays these domains and labels them as the tail domain, motor domains (constructed from six AAA+ domains that form a ring), and the microtubule binding domains.
-The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by the stalks.
+Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains.
+Figure (\ref{fig:structure}) displays these as the tail, the AAA+ rings (or motor), and the microtubule binding domain.
+The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks.
 
@@
 
-Dynein's crystal structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature.
-Its inability to step uniformly is largely due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
+Dynein's physical structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature.
+Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
 In kinesin and myosin, the motor domains are much closer to the MT, causing a more controlled and consistent step due to their low center of mass.
@@
 Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis.
-The ATP binds to the motor domain and converts chemical energy into mechanical energy for the dynein to transition between differenet conformational states during a step.
+The ATP binds to the motor domain and converts chemical energy into mechanical energy for the dynein to transition between different conformational states (physicial arrangements) during a step.
 This process allows the binding domains to let go and reattach to the microtubule at different locations causing varying step sizes.
-We can measure dynein's step length by definining an axis on the microtubule for where dynein can step.
+To measure dynein's step length, an axis is defined on the microtubule for where dynein can step.
 
-The on-axis is defined to be the axis parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is defined to be the axis perpendicular, as shown in Figure (\ref{fig:axis}).
-Figure (\ref{fig:axis}) also displays the alternative helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.
+The on-axis is defined to be parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is perpendicular, as shown in Figure (\ref{fig:axis}).
+Figure (\ref{fig:axis}) also displays the alternating helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.
 
@@
 	\caption[Mechanochemical Cycle]{\textbf{Mechanochemical Cycle.} The proposed series of conformational stages dynein undergoes during a step.
-The interaction of ATP with the motor domain is the main factor causing the powerstroke.
+The interaction of ATP with the motor domain is the main cause of the powerstroke, and high and low affinity indicated by the tightness of yellow polypeptides in the stalk.
 \cite{Cianfrocco2015mechanism}}
@@
 
-The cycle utilizes the conformational transition between high affinity and low affinity to explain dynein's unbinding and rebinding process.
+Here, affinity refers to the tendency and strength of the binding domain binding to the microtubule - high affinity being a secure attachment to the microtubule and low affinity being loose.
+The cycle utilizes the conformational transition between high and low affinity to explain dynein's unbinding and rebinding process.
 This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward.
@@
 
-Although the mechanochemical cycle provides a reasonable model for dynein's step and illustrates the motion between the domains, the model still generalizes the dependencies of the step and fails to analyze different geometric factors that can alter the conformations.
+Although the mechanochemical cycle provides a reasonable model for dynein's step and illustrates the motion between the domains, the model still generalizes the dependence on the configuration of the entire dynein (not just one motor) before the step and fails to analyze different geometric factors that can alter the conformations.
 
@@
 
-Experimental research investigates the correlations within dynein's stepping pattern and how different parameters may affect the step.
-These consists of the angle dependency during the stretching of the linker, the affect of the initial conformation when taking a step, the ATP concentration for hydrolysis, etc.
-However, due to dynein's small scale, experiment often disagrees with one another and differs depending on the technique of measuring dynein.
+Experimental research investigates the correlations within dynein's step and how different parameters may affect the pattern.
+These consist of the angle dependency during the stretching of the linker, the effect of the initial domain distance before the step, the ATP concentration for hydrolysis, etc.
+However, due to dynein's small scale, experiment often disagrees with one another and differs depending on the measuring technique.
 
@@
 
-Experimentalists approach measuring dynein in various ways, which can involve electron microscopy or quantum measuring techniques.
+Experimentalists approach measuring dynein in various ways, which involve electron microscopy or quantum measuring techniques.
 Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod.
-Despite the different procedures, all measuring techniques suffer from their inability to measure small (\textit{change word}) movement.
-This causes steps with short step lengths to be undetectable, such as if dynein quickly rebinds at the same spot after unbinding.
+Despite the different procedures, all measuring techniques suffer from their inability to measure steps within $\sim 0.4$ nm of where the binding domain lifted off.
+This causes short step lengths, where the binding domain quickly rebinds after unbinding, to be undetectable.
 The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables.
@@
 
-Dynein's large size and stochastic nature implies completely independent stepping from the initial conformational state before the step.
+Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step.
 However, in 2012, Yildiz et al.
@@
 on-axis separation which hints at a functional dependency between the step  length and the initial distance between the binding domains.
-The 1D histogram for the trailing head on the left only generalizes the step lengths for negative on-axis separation, while the histogram for the leading head does the same for positive on-axis separation.
+The 1D histogram for the trailing head on the left records the step lengths for the negative on-axis separation, while the histogram for the leading head does the same for positive on-axis separation.
 \cite{Dewitt2012} }
@@
 This correlation implies a connection between the physical state of dynein and its stepping behavior, inferring that dynein's step is not only ATP dependent.
-Unfortunately, experiment is inherently limited and can massively benefit from accurate models that can simulate dynein's stepping under realistic circumstances.
+Because of the limited sample size from experiment producing a unique correlation, observations like Yildiz's can massively benefit from accurate computational models that can simulate dynein's stepping under realistic circumstances.
 

### 2021-03-04 papers/jin-thesis/Chapters/1Introduction.tex
A lot of thesis progress !

@@
 They have the ability to move, perfectly divide, and spatially organize themselves but are also responsible for fatal diseases when these functions fail.
-Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information to different parts of the cell.
-They travel around the cell on a cytoskeleton composed of microtubules that act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})).
+Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track.
+These microtubules form the cytoskeleton in the cell and act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})).
 These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}).
@@
 The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks.
+Both lengths measuring greater than 20 nm in length causing dynein to stand up to 50 nm high.
 
@@
 	\caption[Structure of Dynein]{\textbf{Structure of Dynein.} Illustration of cytoplasmic dynein's heavy chain subunits bounded to the microtubule.
-The AAA+ rings block the view of the independent linkers connecting to the tail.
-This rendition depicts dynein’s structure as a domain-rod system.
+The AAA+ rings block the view of the linkers connecting them to the tail.
+For simplicity, this rendition depicts dynein’s structure as a domain-rod system.
 \cite{TheTrappistArt}}
@@
 Dynein's physical structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature.
-Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are about a factor of a half larger than the diameter of the AAA+ ring.
+Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are a factor of a half larger than the diameter of the AAA+ ring.
 In kinesin and myosin, the motor domains are much closer to the MT, causing a more controlled and consistent step due to their low center of mass.
@@
 Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis.
-The ATP binds to the motor domain and converts chemical energy into mechanical energy for the dynein to transition between different conformational states (physicial arrangements) during a step.
-This process allows the binding domains to let go and reattach to the microtubule at different locations causing varying step sizes.
-To measure dynein's step length, an axis is defined on the microtubule for where dynein can step.
+The ATP binds onto the motor domain and converts chemical energy into mechanical energy for the dynein to transition between different conformational states (physicial arrangements) during a step.
+This process allows the binding domains to unbind and reattach at different locations on the microtubule and thus, permit varying step sizes.
+To measure dynein's step, an axis is defined on the microtubule.
 
-The on-axis is defined to be parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is perpendicular, as shown in Figure (\ref{fig:axis}).
+The on-axis is defined parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is perpendicular, as shown in Figure (\ref{fig:axis}).
 Figure (\ref{fig:axis}) also displays the alternating helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.
@@
 For the on-axis, positive displacement is defined towards the minus end of the microtubule.
-Dark grey and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers.
+Dark grey and light blue helix structure indicates $\alpha-$ and $\beta-$tubulin dimers, which are on average 8 nm apart in the on-axis.
 \cite{Dewitt2012} }
@@
 
-Here, affinity refers to the tendency and strength of the binding domain binding to the microtubule - high affinity being a secure attachment to the microtubule and low affinity being loose.
-The cycle utilizes the conformational transition between high and low affinity to explain dynein's unbinding and rebinding process.
+Here, affinity refers to the tendency and strength of the domain binding to the microtubule - high affinity being a secure attachment to the microtubule, while low affinity is more relaxed.
+The cycle utilizes the conformational transitions between high and low affinity to explain dynein's unbinding and rebinding process.
 This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward.
@@
 These consist of the angle dependency during the stretching of the linker, the effect of the initial domain distance before the step, the ATP concentration for hydrolysis, etc.
-However, due to dynein's small scale, experiment often disagrees with one another and differs depending on the measuring technique.
+However, due to dynein's small scale, experiment often disagrees with one another and differ depending on the various measuring techniques.
 
@@
 
-Experimentalists approach measuring dynein in various ways, which involve electron microscopy or quantum measuring techniques.
+Experimentalists measures dynein in various ways that utilizes electron microscopy and quantum measuring devices.
 Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod.
@@
 The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables.
-In this paper, we will focus on Yildiz et al.
-unique finding of observing a stepping correlation between the initial interhead separation and step length.
+In this paper, we focus on Yildiz et al.
+unique observation of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping.
 
@@
 This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping.
-Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.
+Figure (\ref{fig:YildizCorrelation}) below displays this correlation with a linear regression, where an existing non-zero slope indicates a dependence between the step and the initial on-axis separation.
 
@@
 (\textit{Should reference a simulation here}) Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame.
-These limitations make it impossible for the models to replicate unique discoveries about dyneins stepping, such as Yildiz's correlation from above.
+These limitations make it impossible for their models to replicate mechanical phenomenon observed in dynein's stepping, such as Yildiz's correlation from above.
 
@@
 constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment.
-Instead of making assumptions about the physical properties of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes that the energy transfer from the ATP is incorporated within the binding processes.
-Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experiences Brownian motion during a step to mimic stochastic movement \cite{Capek2017, }.
+Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes.
+Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experienced Brownian motion to mimic stochastic movement \cite{Capek2017, }.
 They were able to track dynein's precise movement along a walk and compare their stepping results to experiment.
-However, their simulation suffered from immense computaiton time and lacked the ability to optimize model parameters for a better fit to experiment.
-For this work, we will use their simulation as a foundation and implement a Monte Carlo method for reproducing data fast and generating an ensemble of statistics.
+However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbinded while $>20$ ms binded).
+Because of this, their simulation suffered from immense computaiton time and lacked the ability to optimize model parameters for a better fit to experiment.
+For this work, we will use their simulation as a foundation but replace the dynamical bounded state with a Monte Carlo algorithm.
+This allows us to only simulate the stepping motion, as the Monte Carlo will initially test equilibrium configurations before the step.
+This new method will drastically shorten computation time and generate larger ensembles of statistics.
 We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism.

### 2021-03-04 papers/jin-thesis/Chapters/2Theory.tex
A lot of thesis progress !

@@
 The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics.
-Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains slightly larger than experimental measurements.
+Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains abitrarily 10\% larger than experimental measurements.
 
 \subsection{Domains as Angular Springs}
-To best simulate the stretching and forward kicking motion of the power stroke, we define the domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ for each domain.
+To best simulate the stretching and forward kicking motion of the power stroke, we define the domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$.
 This can be analogous to how humans walk, where the domains correspond to flexible joints when taking a step.
-Defining the domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law:
+Defining the domains as springs also allows us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law,
 \begin{equation}
-    F_i=-c_i(\theta_i-\theta_{i,eq})
+    F_i=-c_i(\theta_i-\theta_{i,eq}),
 \end{equation}
 where $c_i$ is the spring constant, $\theta_i$ is angle corresponding to the $i^{th}$ domain, and $\theta_{i,eq}$ is the equilibrium angle in which biases the motion.
-Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
+Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy:
 \begin{equation} \label{eqn:energy}
-    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
+    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2.
 \end{equation}
@@
 According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step.
-However, many of these states possess similar conformations, where the dynein either has one foot bounded while the other diffuses above the microtubule or has both feet bounded to the microtubule.
+However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity.
 Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.
@@
 
-Similar to other simulations, the binding and unbinding process is governed by a rate-limiting step, where each process is associated with binding rates.
+Similar to other simulations, the binding and unbinding process is governed by rate-limiting steps, where each process is associated with binding rates.
 These binding rates are model parameters defined by binding constants with units of probability per time.
-When the dynein is in the one bound state, the binding domain depends on two rebinding rates: the linker priming rate ($\rho_p$) and the binding rate ($\rho_b$).
-We assume that the unbound binding domain can only bind when the linker is primed and the unbound binding domain is within a vertical range of the microtubule, i.e.
+When the dynein is in the one bound state, the binding domain depends on two rebinding parameters: the affinity transition time ($t_a$) and the binding rate ($\rho_b$).
+We assume that the unbound binding domain can only bind when high affinity completely transitions into low affinity and when the domain is within a vertical range of the microtubule, i.e.
 \begin{equation}
-	\rho_p=k_p
+	t>t_a=\frac{1}{k_a}
 \end{equation}
+and
 \begin{equation}
@@
 \end{equation} 
-Here, the $k_p$ is the priming rate constant, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
+Here, $t$ is the total one bound time, $k_a$ is the affinity transition rate, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
 
@@
 \begin{equation}
-	\rho_{ub}=k_{ub}e^{C(\theta_b-theta_{b,eq})}.
+	\rho_{ub}=k_{ub}e^{C(\theta_b-\theta_{b,eq})}.
 \end{equation}
@@
 
-The key difference between the works discussed in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state.
-Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk.
-However, they noticed that the unbinding process took a large amount of computation time relative to the total stepping time.
-They also noticed that the both bound configuration of dynein does not impact the final step length.
-We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.
+The key difference between the works in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state.
+In addition to the large both bound time mentioned earlier, they also noticed that the initial both bound configuration of the domains does not impact the stepping, giving a better incentive to apply a Monte Carlo approach.
+This new method of analyzing the both bound state will significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.
 
@@
 \subsection{Monte Carlo for Both Bound}
-Since research and Waczak/Capek suggests that the dynein spends the majority of the stepping time in the both bound state, we can safely assume that the dynein equilibriates before unbinding.
-This inspired us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system.
-Typically, Monte Carlo methods are used to analyze equilibrium theromodynamics of fluids where a system of atoms can possess many different microstates.
-For this model, the dynein is the system and the different possible microstates are the many both bound configurations our model can achieve.
-However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values.
-The benefit of this method is the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics.
-Eventually, this will allow us to create probability distributions for important variables.
+Since dynein spends the majority of time in the both bound state, we can safely assume that the dynein equilibriates before unbinding.
+This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system.
+Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids where a system of atoms possess many different microstates.
+For this model, dynein is the system and the many possible both bound configurations is analogous to the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values.
+The enables the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics.
+Eventually, this allows us to create probability distributions for important variables.
 
-With the assumption of thermodyamic equilibrium during the both bound state, we can define the probability of dynein being in that configuration from a Boltzmann distribution and calculate the relative probability of unbinding for that specifc configuration by using a proportionality expression.
+With the assumption of thermodyamic equilibrium during the both bound state, we define the probability of a configuration from a Boltzmann distribution and calculate the relative unbinding probability for that configuration by using a proportionality expression.
 That is,
@@
 In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well.
-The thermodynamic ensemble can then generate an ensemble of steps that can eventually produce smooth statictics.
-With the partition function defined in Equation (\ref{eqn:partition}), we can also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time.
+The thermodynamic ensemble then generates an ensemble of steps that can eventually produce smooth statictics.
+With the partition function defined in Equation (\ref{eqn:partition}), we also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time.
 The equations to do so are all shown below in that order:
 \begin{equation}
-	\langle\rho_{ub, trail.}\rangle=\frac{\sum_{i}\rho_{ub, trail.} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, lead.}\rangle=\frac{\sum_{i}\rho_{ub, lead.} e^{-\beta E_{total,i}}}{Z}
+	\langle\rho_{\textit{ub, trail.}}\rangle=\frac{\sum_{i}\rho_{\textit{ub, trail.}} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{\textit{ub, lead.}}\rangle=\frac{\sum_{i}\rho_{\textit{ub, lead.}} e^{-\beta E_{total,i}}}{Z}
 \end{equation}
 \begin{equation} \label{eqn:ProbTrail}
-	\langle P_{ub, trail.}(L)\rangle = \frac{\langle\rho_{ub, trail.}\rangle}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle}
+	\langle P_{\textit{ub, trail.}}(L)\rangle = \frac{\langle\rho_{\textit{ub, trail.}}\rangle}{\langle\rho_{\textit{ub, trail.}}\rangle + \langle\rho_{\textit{ub, lead.}}\rangle}
 \end{equation}
 \begin{equation}
-	\langle t_{bb}(L) \rangle =\frac{1}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle},
+	\langle t_{bb}(L) \rangle =\frac{1}{\langle\rho_{\textit{ub, trail.}}\rangle + \langle\rho_{\textit{ub, lead.}}\rangle},
 \end{equation}

### 2021-03-04 papers/jin-thesis/Chapters/3Methods.tex
Made algorithm figure
A lot of thesis progress !

@@
 Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step.
-However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations.
+However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, to ensure that our ensemble covers the whole sample space of possible both bound configurations.
 This forces the measured probabilities to be a function of $L$ and will be addressed later in the Data Analysis section (Section \ref{sec:DataAna}).
@@
 
-\begin{algorithm}[H]
-	\caption{Monte Carlo Both Bound}
-	\label{alg:MonteCarlo}
+\newpage
+\begin{center}\label{alg:MonteCarlo}
+	\textbf{\underline{Monte Carlo Algorithm}}
+\end{center}
 
-	\begin{alg}
+\begin{enumerate}
 	\item Initialize an unsigned distance, $L$, between the binding domains.
 
-	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space. (\textit{Include picture})
+	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space.
 
 	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.
+\end{enumerate}
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\columnwidth]{Figures/montecarlo2.png}
+%\caption[Dynein Model]{\textbf{Dynein Model.} }
+\label{fig:mc2}
+\end{figure}
+
+\begin{enumerate}
+	\setcounter{enumi}{3}
 	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate angles with the naming convention in Figure (\ref{fig:OBvsBB}).
+\end{enumerate}
 
-	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eqn:energy})),
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\columnwidth]{Figures/montecarlo3.png}
+%\caption[Dynein Model]{\textbf{Dynein Model.} }
+\label{fig:mc3}
+\end{figure}
+
+\begin{enumerate}
+	\setcounter{enumi}{4}
+	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eqn:energy})) and the relative unbinding probability from a Boltzmann distribution,
 	\begin{equation}
-		E_{total, i}=\sum_{k}\frac{1}{2}c_k(\theta_k-\theta_{k,eq})^2.
+		E_{total, i}=\sum_{k}\frac{1}{2}c_k(\theta_k-\theta_{k,eq})^2,
 	\end{equation}
-	Here, $i$ refers to the specific both bound configuration and $k$ is the domain.
-
-	\item Calculate the relative unbinding probability from a Boltzmann distribution and add a term to the partition function:
 	\begin{equation}
-		P_{ub} \propto \rho_{ub}e^{-\beta E_{total, n}}\kappa,
+		P_{ub} \propto \rho_{ub}e^{-\beta E_{total, i}}\kappa.
 	\end{equation}
+	Then, add a term to the partition function,
 	\begin{equation}
@@
 	\end{equation}
-	We defined $\kappa$ to normalize the relative unbinding probability to keep it less than 1.
+	Here, $i$ refers to the specific both bound configuration and $k$ is the domain. We also defined $\kappa$ to normalize the relative unbinding probability to keep it less than 1.
 
 	\item ``Roll a die" for a value within the range of $[0,1]$ and check if the value is less than $P_{ub}$. If not, repeat algorithm from step 2.
+\end{enumerate}
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\columnwidth]{Figures/montecarlo4.png}
+%\caption[Dynein Model]{\textbf{Dynein Model.} }
+\label{fig:mc4}
+\end{figure}
+
+\newpage
+
+\begin{enumerate}
+	\setcounter{enumi}{6}
 	\item If dynein unbinds, initialize the one bound state with the both bound configuration, run the Brownian dynamics simulation of the step, and wait until it rebinds.
+\end{enumerate}
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/montecarlo5.png}
+%\caption[Dynein Model]{\textbf{Dynein Model.} }
+\label{fig:mc4}
+\end{figure}
+
+\begin{enumerate}
+	\setcounter{enumi}{7}
 	\item Collect statistics about the final position and one bound time. Repeat algorithm from step 2. 
+\end{enumerate}
 
-	\end{alg}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/montecarlo6.png}
+%\caption[Dynein Model]{\textbf{Dynein Model.} }
+\label{fig:mc4}
+\end{figure}
 
-\end{algorithm}
+\noindent\rule{16.5cm}{0.4pt}
 
@@
 These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both bound and one bound states.
-The parameters we can measure from these figures are the domain radii \{$R_i$\}, equilibrium angles \{$\theta_{i,eq}$\}, and the stalk and tail lengths ($L_s$, $L_t$).
+We can measure the domain radii \{$R_i$\}, equilibrium angles \{$\theta_{i,eq}$\}, and the stalk and tail lengths ($L_s$, $L_t$) from these figures (refer to Section \ref{sec:Params} for measurements).
 
@@
 	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
-	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles \cite{Burgess2003}.
+	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles.
+The arrow indicates 15 nm \cite{Burgess2003}.
 \textit{Right:} Cryo-electron tomograph of one bound dynein for pre-stroke equilbrium angles \cite{grotjahn2018cryo}.}
@@
 
-However, these pictures do not help identify the binding rates ($k_p$, $k_b$, $k_{ub}$) and spring constants ($c_b$, $c_m$, $c_t$), making these parameters \textit{free variables} in the model.
+However, these pictures do not help identify the binding rates ($k_a$, $k_b$, $k_{ub}$) and spring constants ($c_b$, $c_m$, $c_t$), making these parameters \textit{free variables} in the model.
 Fortunately, the Monte Carlo simulation can quickly optimize these free variables and fit different combinations of parameters to  different sets of experimental data.
@@
 For instance, the exponential unbinding constant, $C$, is fitted specifically to Figure (\ref{fig:trailingbias}).
-We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, and the inverse yields the average time it takes to unbind, i.e.
+We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, because the inverse yields the average time it takes to unbind, i.e.
 the both bound time.
-The rebinding rates, $k_p$ and $k_b$, are fit to experiment's one bound time, and these rates are directly correlated to dynein's step length.
+The rebinding rates, $k_a$ and $k_b$, are harder to optimize because they directly correlate to step length.
 The ability for dynein to take long steps is dependent on how long dynein diffuses above the microtubule.
 Therefore, the rebinding rates have a much larger parameter space due to the flexibility of optimizing according to the one bound time or step length.
-Since we are interested in Yildiz's step lengths, we match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}).
+Since we are interested in Yildiz's step lengths, we match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}) and Yildiz's step length plots.
 The last parameters are the spring constants.
@@
 \section{Data Analysis} \label{sec:DataAna}
-As mentioned earlier, the simulation can collect statistics only for a given initial binding domain distance, $L$.
+As mentioned earlier, the simulation collects statistics only for a given initial binding domain distance, $L$.
 This limits the probability data of landing at a final position to be a function of $L$.
 However, we can not calculate the step length for a trailing or leading step with an unsigned distance.
-This promotes the new naming scheme of using initial displacement, $x_i$, and final displacement $x_f$, when identifying the distances between the binding domains before and after the step.
-The displacement is the $x$ position of the unbounded binding domain during the step, where the origin is defined at the bounded binding domain.
+This promotes the new naming scheme of using initial and final displacement, $x_i$ and $x_f$, when identifying the distances between the binding domains before and after the step.
+The displacement is the $x$ position of the unbounded binding domain, where the origin is defined at the bounded binding domain.
 This implies a negative initial displacement for a trailing step and a positive initial displacement for a leading step.
@@
 In other words, Equation (\ref{eqn:ProbTrail}) gives us $p(x_i|L_i)$.
-We can relate the two by using Bayes' Theorem:
+We can relate the two by using Bayes' Theorem,
 
@@
 \[
-	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)} 
+	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)},
 \]
@@
 Since we want the probability of absolute differences, we can neglect the distinction between `initial' and `final' and calculate an equilibrium distribution of distances, $p(L)$.
-To do so, we used a reccurence relation, where we define an initial $p^0(L)$ that is not in equilibrium and multiply it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
+To do so, we use a reccurence relation, where we define an initial $p^0(L)$ that is not in equilibrium and multiply it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
 That is,
@@
 This process can be thought of as a large row of dyneins all starting with the probability of an initial distance $p^0(L)$.
-Once they all take a step, their probability of having another distance $L'$ is $p(L'|L)p(L)$, and after a significant number of $n$ steps, the probability of having a distance $L$ would be the same for all the dyneins, thus being a equilibirum distribution of $L$.
+Once they all take a step, their probability of having another distance $L'$ is $p(L'|L)p(L)$, and after a significant number of $n$ steps, the probability of having a distance $L$ would be the same for all the dyneins, thus being an equilibirum distribution of $L$.
 To solve for $p(L'|L)$, we can use the previous probability distributions $p(x_f|x_i)$ and $p(x_i|L_i)$ to convert these probabilities into distances, as shown below:

### 2021-03-04 papers/jin-thesis/Chapters/4Results.tex
A lot of thesis progress !
Thesis work

@@
-\section{Optimized Parameters}
-The set of parameters that best fit Yildiz's data are shown in the table below
+\section{Optimized Parameters}\label{sec:Params}
+The set of parameters that best fit Yildiz's data are shown in Table (\ref{tab:params}) below.
 
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\includegraphics[width=0.6\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.7\textwidth]{/mc_plots/thesis_u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.6\textwidth]{/mc_plots/thesis_u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/thesis_prob_lagging_vs_init_L_-0.5}
 	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}

### 2021-03-05 papers/jin-thesis/Chapters/4Results.tex
Thesis work

--- 2021-02-03 papers/jin-thesis/Chapters/4Results.tex
@@
 After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's geometric constants.
-\textit{FIXME: Plots are wrong, need to fix and ask which plots to finalize}
+\textit{FIXME: Not finalized yet!!
+Still a WIP, need to fix and wait for simulations to finish}
 
-\section{Stepping Patterns}
-The plots that were used to compare with experiment and optimize our parameters are shown below
+\section{Stepping Plots}
+The final displacement and step lengths are plotted against experiment and shown below.
+
 \begin{figure}[H]
@@
 \end{figure}
-The first plot in Figure (\ref{fig:DataStep}) displayed the joint probability density of having a specific final displacement and initial displacement.
-The linear regression from experiment indicated the functionality between the two with an average final displacement of 9.1nm, indicated from the y-intercept.
-The second plot in Figure (\ref{fig:DataStep}) displayed the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement.
+\newpage
+The top plot in Figure (\ref{fig:DataStep}) displays the joint probability density of having a specific final displacement and initial displacement.
+The linear regression from Yildiz's experiment indicates the functionality between the two with an average final displacement of 9.1 nm, shown from the y-intercept.
+The bottom plot in Figure (\ref{fig:DataStep}) displays the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement.
 The limitation of experiment was made very obvious here due to their inability to record short step lengths.
-This factor heavily influenced the parameter fitting because in order to best fit the linear correlation within steps, the model dynein had to take very fast and short steps.
-Since Yildiz observed a linear regression that averaged 0nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding.
-The step lengths close to 0nm from Experiment Fig 3A in Figure (\ref{fig:DataStep}) were large step lengths in the off-axis.
+This factor heavily influenced the parameter fitting because in order to best fit the linear correlation, the model dynein had to take very fast and short steps.
+Since Yildiz observed a linear regression that averaged close to 0 nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding.
+The step lengths close to 0 nm from Experiment Fig 3A were lateral steps in the off-axis.
 
-We fit the pre-exponential unbinding factor, $C$, based on experimental probability of having a trailing (lagging) step, as shown below
+We fit the pre-exponential unbinding factor, $C$, based on experimental probability of having a trailing (lagging) step, as shown below.
 
@@
 
-\textit{Need to include time plots and maybe more figures. Talk about the short time step.}
+\textit{Need to include time plots and maybe more figures. Talk about the short time step. Sorry this is also still a WIP}
 
@@
 Mention time too.}
+
+\textit{\textbf{Note for Assignment 9.1:} I apologize that this section is still incomplete and a skeleton, but there were some hiccups in the code that delayed the simulations and may change the agreement based on how we solve the bug.
+I felt it was best to occupy my time trying to polish the code instead of writing a generalized version of this section.}

### 2021-03-05 papers/jin-thesis/Chapters/5Conclusion.tex
Thesis work

@@
 The most unique set is Yildiz and we were able to reproduce his observations to the best of our ability with the set of parameters we used.
-We discovered an inherent problem when trying to fit to data that cannot observe 0nm steps.
-We usec Monte Carlo that produces a smooth probability distribution because of running large numbers of simulations and law of large numbers.
+We discovered an inherent problem when trying to fit to data that cannot observe 0n m steps.
+We use Monte Carlo that produces a smooth probability distribution because of running large numbers of simulations and law of large numbers.
 However, In order to best fit the linear regression, the simulation must average 0nm step lengths, meaning we need to force parameters so that model dynein takes very quick and short steps.

### 2021-03-05 scripts/make_mc_plots.py

@@ -190,16 +190,16 @@ def make_probability_distribution(args, hist, normalized_hist, bb_P_leading, bb_
     plt.plot(initial_L, p_den_L)
     plt.xlabel('L (nm)')
     plt.ylabel('Probability density')
-    plt.title('kb = {0:.2e}, kstk = {1:.2e}, cb = {2}, cm = {3}, ct = {4}, eqb = {5}, eqmpre = {6}, eqmpost = {7}, C = {8}'.format(args.k_b,
-                args.k_stk, args.cb, args.cm, args.ct, args.eqb, args.eqmpre, args.eqmpost, args.C), fontsize=7)
+    # plt.title('kb = {0:.2e}, kstk = {1:.2e}, cb = {2}, cm = {3}, ct = {4}, eqb = {5}, eqmpre = {6}, eqmpost = {7}, C = {8}'.format(args.k_b,
+                # args.k_stk, args.cb, args.cm, args.ct, args.eqb, args.eqmpre, args.eqmpost, args.C), fontsize=7)
 
     p_den_disp = L_to_initial_displacement(P_ub_leading, P_ub_trailing).dot(p_den_L)   # Dimensions: 1/distance
     plt.figure('p_den_disp')
     plt.plot(initial_disp, p_den_disp)
     plt.xlabel('L (nm)')
     plt.ylabel('Probability density')
-    plt.title('kb = {0:.2e}, kstk = {1:.2e}, cb = {2}, cm = {3}, ct = {4}, eqb = {5}, eqmpre = {6}, eqmpost = {7}, C = {8}'.format(args.k_b,
-    args.k_stk, args.cb, args.cm, args.ct, args.eqb, args.eqmpre, args.eqmpost, args.C), fontsize=7)
+    # plt.title('kb = {0:.2e}, kstk = {1:.2e}, cb = {2}, cm = {3}, ct = {4}, eqb = {5}, eqmpre = {6}, eqmpost = {7}, C = {8}'.format(args.k_b,
+    # args.k_stk, args.cb, args.cm, args.ct, args.eqb, args.eqmpre, args.eqmpost, args.C), fontsize=7)
 
     # Probability Distribution is the normalized histogram multiplied by the probability density
     probability_distribution = np.zeros_like(normalized_hist)   # Dimensions: 1/distance**2
[…]

### 2021-03-09 papers/jin-thesis/Chapters/1Introduction.tex
Thesis work

@@
 However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbinded while $>20$ ms binded).
-Because of this, their simulation suffered from immense computaiton time and lacked the ability to optimize model parameters for a better fit to experiment.
+Because of this, their simulation suffered from immense computation time and lacked the ability to optimize model parameters for a better fit to experiment.
 For this work, we will use their simulation as a foundation but replace the dynamical bounded state with a Monte Carlo algorithm.

### 2021-04-05 papers/jin-thesis/Chapters/4Results.tex
Slight edits to plots to remove right and top borders

@@
 	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\includegraphics[width=0.6\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.65\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
 	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
+	\label{fig:ProbTrail}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[One-bound times]{\textbf{One-bound times}}
+	\label{fig:ProbTrail}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_trajectory_plot_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Stepping Trace]{\textbf{Stepping Trace}}
 	\label{fig:ProbTrail}
@@
 Mention time too.}
-
-\textit{\textbf{Note for Assignment 9.1:} I apologize that this section is still incomplete and a skeleton, but there were some hiccups in the code that delayed the simulations and may change the agreement based on how we solve the bug.
-I felt it was best to occupy my time trying to polish the code instead of writing a generalized version of this section.}

### 2021-04-19 papers/jin-thesis/Chapters/1Introduction.tex
Content to thesis

@@
 
-	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, is a leading cause of death in the United States \cite{eschbach2011cytoplasmic}.
+	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, are a leading cause of death in the United States \cite{eschbach2011cytoplasmic}.
 Scientists have yet to find a prevention or cure to these fatal diseases but suggests that motor protein failure directly contributes to cell degeneration.
@@
 Cells are complicated.
-They have the ability to move, perfectly divide, and spatially organize themselves but are also responsible for fatal diseases when these functions fail.
+They have the ability to move, perfectly divide, and spatially organize themselves but are responsible for fatal diseases when these functions fail.
 Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track.
@@
 These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}).
-Because of kinesin and myosin's compact structure being close to the microtubule, they exhibit a uniform ``hand-over-hand" stepping pattern where their legs take turns alternating steps like a human.
+Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern.
 On the other hand, dynein's structure involves two autonomous motors that cause inconsistent steps.
-Dynein exhibits an inchworm pattern while walking where one leg consistently stays ahead of the other, emulating a limping motion.
+As opposed to kinesin and myosin's uniform stepping, dynein exhibits an inchworm walk with one leg consistently ahead of the other, emulating a limping motion.
 
@@
 
-In addition to their structural differences, dynein walks in the oppposite direction of its motor protein siblings and towards the negative end of the microtubule.
+In addition to their structural differences, dynein walks towards the negative end of the microtubule while its motor protein siblings walk towards the positive end.
 Because microtubules are protein dimers constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulins, the microtubule track is polarized depending on which tubulin dominates at the end points.
@@
 The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks.
-Both lengths measuring greater than 20 nm in length causing dynein to stand up to 50 nm high.
+Both the linker and stalk measures greater than 20 nm in length, causing dynein to stand up to 50 nm high.
 
@@
 Dynein's physical structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature.
-Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are a factor of a half larger than the diameter of the AAA+ ring.
-In kinesin and myosin, the motor domains are much closer to the MT, causing a more controlled and consistent step due to their low center of mass.
+Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are 1.5x larger than the diameter of the AAA+ ring.
+In kinesin and myosin, the motor domains are much closer to the microtubule, causing a more controlled and consistent step due to their low center of mass.
 Despite dynein's large structure, it can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, which is why the AAA+ domains are referred to as the motor domains.
@@
 Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis.
-The ATP binds onto the motor domain and converts chemical energy into mechanical energy for the dynein to transition between different conformational states (physicial arrangements) during a step.
+The ATP binds onto the motor domain and converts chemical energy into mechanical energy for dynein to transition between different conformational states (physicial arrangements) during a step.
 This process allows the binding domains to unbind and reattach at different locations on the microtubule and thus, permit varying step sizes.
@@
 The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables.
-In this paper, we focus on Yildiz et al.
-unique observation of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping.
+In this paper, we focus on the unique observation by Yildiz \textit{et al.} of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping.
 
@@
 Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step.
-However, in 2012, Yildiz et al.
-observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}.
+However, in 2012, Yildiz \textit{et al.} observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}.
 This discovery challenged established views on dynein's stepping processivity and pose the question of whether there exists interhead coordination between the motor domains when stepping.
@@
 
-To bridge this gap, Roundy et al.
-constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment.
+To bridge this gap, Roundy \textit{et al.} constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment.
 Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes.
@@
 They were able to track dynein's precise movement along a walk and compare their stepping results to experiment.
-However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbinded while $>20$ ms binded).
+However, they also discovered that dynein spends less than 5\% of its total stepping time in the low affinity state where the dynein exhibits the actual stepping motion ($<1$ ms unbound while $>20$ ms bound).
 Because of this, their simulation suffered from immense computation time and lacked the ability to optimize model parameters for a better fit to experiment.

### 2021-04-19 papers/jin-thesis/Chapters/3Methods.tex
add comment
Content to thesis

@@
 
-	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.
+	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small. If not, repeat step 2.
+	   \davidsays{Mention going back to 2 if the distance isn't in range.}
 \end{enumerate}
@@
 	\setcounter{enumi}{3}
-	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate angles with the naming convention in Figure (\ref{fig:OBvsBB}).
+	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate angles with the naming convention from Figure (\ref{fig:OBvsBB}).
 \end{enumerate}

### 2021-04-19 papers/jin-thesis/Chapters/4Results.tex
Content to thesis

--- 2021-03-05 papers/jin-thesis/Chapters/4Results.tex
@@
 \section{Optimized Parameters}\label{sec:Params}
-The set of parameters that best fit Yildiz's data are shown in Table (\ref{tab:params}) below.
+The set of parameters that best fit Yildiz's observed stepping correlation is shown below in Table (\ref{tab:params}).
 
@@
     $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
-    $k_p$ & $\kstk s^{-1}$&  & \\
+    $k_a$ & $\kstk s^{-1}$&  & \\
     $k_b$ & $\kb s^{-1}$&  & \\
@@
   \end{tabular}
-  \caption{Optimized model parameters for following data sets. }
-%  \caption{Parameters used in simulation.
-$c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
-$k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
-$L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
-$c$ is the tension-gating factor.
-The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
-$R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
-Parameters used for all simulations unless otherwise noted}
+  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:Trajectory}).}
   \label{tab:params}
@@
 
-After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's geometric constants.
-\textit{FIXME: Not finalized yet!!
-Still a WIP, need to fix and wait for simulations to finish}
+After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving forward directionality with positive step lengths.
 
-\section{Stepping Plots}
 The final displacement and step lengths are plotted against experiment and shown below.
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\includegraphics[width=0.6\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.8\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.8\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
@@
 Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
-	\label{fig:DataStep}
+	\label{fig:DataFitYildiz}
 \end{figure}
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
+Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
+	\label{fig:OBtime}
+\end{figure}
+
 We fit the pre-exponential unbinding factor, $C$, based on experimental probability of having a trailing (lagging) step, as shown below.
@@
 	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
-	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
+	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step.} Likelihood of a trailing step vs.
+the initial binding domain distance, i.e.
+$P_{trail.}(L)$ calculated with Equation (\ref{eqn:ProbTrail}).
+Experimental data from Yildiz \textit{et al.} \cite{Dewitt2012}.}
 	\label{fig:ProbTrail}
+\end{figure}
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/bb_time_-0.5}
+%	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
+%	\label{fig:ProbTrail}
+%\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Stepping Trace]{\textbf{Stepping Trace.} Trajectory of binding domains over 24 seconds of walking.
+Red and blue lines distinguishing binding domains, and experimental data from Yildiz \textit{et al.} \cite{Dewitt2012}}
+	\label{fig:Trajectory}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.65\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
+Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement.
+\textit{Bottom:} One dimensional probability density of step length.
+Step length defined as final displacement minus the initial displacement.
+Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
+	\label{fig:DataFitYildiz}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
+Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
+	\label{fig:OBtime}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=0.65\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
+Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement.
+\textit{Bottom:} One dimensional probability density of step length.
+Step length defined as final displacement minus the initial displacement.
+Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
+	\label{fig:DataFitYildiz}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
+Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
+	\label{fig:OBtime}
 \end{figure}

### 2021-04-19 papers/jin-thesis/main.tex
Added to thesis and changed params defaults
Thesis work
add comment
Content to thesis

@@
 \usepackage{graphicx}
+\graphicspath{{./Figures/},{../../plots/}}
 \usepackage{geometry}
@@
 
+\input{../../data/paper_params.tex}
+
 \floatstyle{plaintop}
@@
 
+\newcommand\davidsays[1]{\textbf{\it [D: #1]}}
+
 \title{
 	\Huge{Modeling the mechanisms of dynein's step using Monte Carlo simulations and Brownian dynamics}\vspace{1em}\\
-	\Large{Jin Kiatvongcharoen} \vspace{0.5em}\\ 
-	\normalsize{Department of Physics, Oregon State University}\vspace{2em}\\
-	\includegraphics[width=0.4\columnwidth]{OSU_logo.png}\vspace{1em}\\
+	\Large{Jin Kiatvongcharoen} \vspace{0.5em}\\[2in] 
+%	\includegraphics[width=0.4\columnwidth]{OSU_logo.png}\vspace{1em}\\
 	\normalsize{An undergraduate thesis advised by Dr. David Roundy}\\
+	\normalsize{submitted to the Department of Physics, Oregon State University}\\%\vspace{2em}\\
 	\normalsize{in partial fulfillment of the requirements for the degree of}\\
-	\normalsize{Baccalaureate of Science in Physics}\vspace{1.5 em}\\
-	\normalsize{Submitted \today}\\
+	\normalsize{B.S. in Physics}\vspace{1.5 em}\\
+	\normalsize{Draft submitted \today}\\
 
@@
 	\chapter*{Abstract}
-	Molecular motor proteins are responsible for the cell’s ability to move, divide, and spatially organize itself.
+	Molecular motor proteins are the working soldiers within a cell.
+More specifically, the motor protein dynein delivers vital information along the microtubule for cellular processes like axonal transport and cell division.
+A failed delivery can cause severe damage to the cell’s functionality and lead to neurological diseases.
+Despite dynein's rich history in cellular research, the mechanisms of its motility remains poorly understood and is spectulated to be a cause for defects.
+In contrary to dynein having completely stochastic stepping, experimentalist Ahmet Yildiz and colleagues observed a dependence of dynein's stepping behavior as a function of interhead separation.
+To investigate this, we developed a two-dimensional, particle-rod model of dynein and simulated its stepping mechanisms using Monte Carlo methods and Brownian dynamics.
+The simulation optimized stepping patterns by fitting parameters according to Yildiz's results.
+In order to replicate the correlation observed by Yildiz, the binding rate was increased to encourage fast steps.
+Our results indicate that dynein takes many short and immediate steps that are undetectable to experimentalists in order to achieve stepping dependence on the initial domain separation.
+%	
+%	 However, dynein's walk is unpredictable in nature and can vary in length and direction.
+%	
+%	 cargo that allows the cell to 
+%	Molecular motor proteins are responsible for the cell’s ability to move, divide, and spatially organize itself.
 A defect within any of the three motor proteins can cause severe damage to the cell’s functionality and lead to neurological diseases.

### 2021-04-19 papers/jin-thesis/Chapters/4Results.tex
Thesis content

@@
 
-After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving forward directionality with positive step lengths.
-
-The final displacement and step lengths are plotted against experiment and shown below.
+After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's forward directionality.
+The two main stepping statistics used to compare with experiment are shown below, where the affinity transition rate ($k_a$) and binding rate ($k_b$) heavily influenced the statistics.
 
@@
 	\includegraphics[width=0.8\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
-Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement.
-\textit{Bottom:} One dimensional probability density of step length.
-Step length defined as final displacement minus the initial displacement.
-Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
+	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a step.
+Linear regression of the probability distribution indicates a dependence between the final displacement ($x_f$) and initial displacement ($x_i$).
+\textit{Bottom:} One dimensional probability density of step length (step length = $x_f-x_i$).
+Model compared with experimental figures from \citep{Dewitt2012}.}
 	\label{fig:DataFitYildiz}
@@
 \newpage
-The top plot in Figure (\ref{fig:DataStep}) displays the joint probability density of having a specific final displacement and initial displacement.
-The linear regression from Yildiz's experiment indicates the functionality between the two with an average final displacement of 9.1 nm, shown from the y-intercept.
-The bottom plot in Figure (\ref{fig:DataStep}) displays the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement.
-The limitation of experiment was made very obvious here due to their inability to record short step lengths.
-This factor heavily influenced the parameter fitting because in order to best fit the linear correlation, the model dynein had to take very fast and short steps.
-Since Yildiz observed a linear regression that averaged close to 0 nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding.
-The step lengths close to 0 nm from Experiment Fig 3A were lateral steps in the off-axis.
+The first plot in Figure (\ref{fig:DataFitYildiz}) displays the joint probability distribution of having a specific initial displacement and final displacement ($P(x_i,x_f)$).
+The linear regression from Yildiz's experiment indicates a functionality between the two with an average final displacement of 9.1 nm, shown from the y-intercept, and a slope of 0.6.
+The model produced steps with an average final displacement of 6.28 nm and a slope of 0.501.
+Despite the $16.5\%$ percent error in the slope, the model dynein was able to reproduce Yildiz's interhead correlation only if dynein prefers fast stutter steps with step lengths close to 0 nm.
+This is apparent from the diagonal shaded region with a slope of 1, indicating a step where $x_f\approx x_i$.
+
+The bottom plot in Figure (\ref{fig:DataFitYildiz}) displays the one-dimensional probability density of step lengths, defined as final displacement ($x_f$) minus initial displacement ($x_i$).
+The accumulative density from the diagonal shaded region is evident in this plot due to the peak at 0 nm.
+However, experiment was unable to detect 0 nm steps and is shown within the dip from Experiment Fig 3A (small density at 0 nm were lateral steps on the off-axis with little change on the on-axis).
+Our model suggests that dynein can still achieve forward directed motion with more positive steps than negatives ones but prefers short stuttered steps with fast one-bound times.
+A distribution of said one-bound times is shown below in Figure (\ref{fig:OBtime})
 
@@
 	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
-Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
+Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0068$.}
 	\label{fig:OBtime}
@@
 
-We fit the pre-exponential unbinding factor, $C$, based on experimental probability of having a trailing (lagging) step, as shown below.
+As the distribution of times in Figure (\ref{fig:OBtime}) indicates, the model dynein frequently spends $<$ 0.1 $\mu s$ in the one-bound state, with the dynein most likely to rebind immediately after the affinity transitions.
+This demonstrates the importance of a buffer time when the dynein unbinds in order to avoid instantaneous rebinding and still achieve large positive step lengths.
+A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCases}).
+
+We also fit the pre-exponential unbinding factor ($C$) and unbinding rate ($k_{ub}$) based on the following experimental plots shown below.
 
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
-	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step.} Likelihood of a trailing step vs.
-the initial binding domain distance, i.e.
-$P_{trail.}(L)$ calculated with Equation (\ref{eqn:ProbTrail}).
-Experimental data from Yildiz \textit{et al.} \cite{Dewitt2012}.}
-	\label{fig:ProbTrail}
+	\includegraphics[width=0.6\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Fitting Bothbound Parameters]{\textbf{Fitting Bothbound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
+the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
+\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
+Experimental data from \cite{Dewitt2012}.}
+	\label{fig:BBPlots}
 \end{figure}
+
+By measuring the unbinding rates of the ensemble of both-bound configurations, we were able to accurately reproduce the experiments unbinding probability for the trailing leg as a function of initial binding domain separation.
+This result forces the model to prefer trailing steps for large initial distances and influence forward directed stepping from the trailing leg's powerstroke.
+The model dynein could also replicate observed velocities over a long walk by modifying the unbinding rate ($k_{ub}$) and comparing the slopes of the binding domain trajectories.
+
+\section{Limiting Cases}\label{sec:LimitingCases}
+
+As mentioned previously, the
 
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Stepping Trace]{\textbf{Stepping Trace.} Trajectory of binding domains over 24 seconds of walking.
-Red and blue lines distinguishing binding domains, and experimental data from Yildiz \textit{et al.} \cite{Dewitt2012}}
-	\label{fig:Trajectory}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
 	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
@@
 Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
-	\label{fig:DataFitYildiz}
+	\label{fig:DataFitYildiz99}
 \end{figure}
@@
 Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
-	\label{fig:OBtime}
+	\label{fig:OBtime99}
 \end{figure}
@@
 Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
-	\label{fig:DataFitYildiz}
+	\label{fig:DataFitYildiz09}
 \end{figure}
@@
 Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
-	\label{fig:OBtime}
+	\label{fig:OBtime09}
 \end{figure}
 
-\textit{Need to include time plots and maybe more figures. Talk about the short time step. Sorry this is also still a WIP}
-
-\section{Agree with Experiment?}
-\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job? }
-
-\textit{Need to eventually bring up the issue of being able to fit both the 2d hist linear regression and step length plot: If we want to fit linear regression, we must have short steps, but if we have short steps, the step length plot will not match at steps $>$ 20nm.
+%\section{Agree with Experiment?}
+%\textit{Whole point of parameter fitting was to agree with Yildiz and/or other experimental data. Did we do a good job? }
+%
+%\textit{Need to eventually bring up the issue of being able to fit both the 2d hist linear regression and step length plot: If we want to fit linear regression, we must have short steps, but if we have short steps, the step length plot will not match at steps $>$ 20nm.
 Hard to agree with experiment when our dynein is forced to take short steps.

### 2021-04-20 papers/jin-thesis/Chapters/3Methods.tex
Added to thesis and changed sizes of plots

@@
 The entire model and simulation code can be found at \url{https://github.com/kiatvonj/dynein_walk}, where the model and simulation were coded using both Python and C++.
-The both bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous and time independent, while the one bound Brownian dynamics was coded on C++ to utilize the faster computation speed for the time  dependent Brownian motion.
+The both bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous, while the time dependent one-bound Brownian dynamics was coded on C++ to utilize faster computation speed.
 
@@
 We match model paramters concerning dynein's geometry based on experiment by analyzing electron microscopy pictures of dynein.
-These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both bound and one bound states.
+These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both-bound and one-bound states.
 We can measure the domain radii \{$R_i$\}, equilibrium angles \{$\theta_{i,eq}$\}, and the stalk and tail lengths ($L_s$, $L_t$) from these figures (refer to Section \ref{sec:Params} for measurements).
@@
 Fortunately, the Monte Carlo simulation can quickly optimize these free variables and fit different combinations of parameters to  different sets of experimental data.
-Since we want to replicate Yildiz's observations from Figure (\ref{fig:YildizCorrelation}), the free variables will be optimized according to the slope and y-intercept of the correlation.
+Since we want to replicate Yildiz's observations from Figure (\ref{fig:YildizCorrelation}), the free variables will be optimized according to Yildiz's data.
+%the slope and y-intercept of the correlation.
 
@@
 As mentioned earlier, the simulation collects statistics only for a given initial binding domain distance, $L$.
-This limits the probability data of landing at a final position to be a function of $L$.
+This limits the probability of landing at a final position to be a function of $L$.
 However, we can not calculate the step length for a trailing or leading step with an unsigned distance.

### 2021-04-20 papers/jin-thesis/Chapters/4Results.tex
Added to thesis and changed sizes of plots

@@
 After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's forward directionality.
-The two main stepping statistics used to compare with experiment are shown below, where the affinity transition rate ($k_a$) and binding rate ($k_b$) heavily influenced the statistics.
+The two main stepping statistics used to compare with experiment are shown below, where the affinity transition rate ($k_a$) and binding rate ($k_b$) heavily influenced these statistics.
 
@@
 	\includegraphics[width=0.8\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\includegraphics[width=0.8\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=17cm, height = 9.5cm]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a step.
@@
 \newpage
-The first plot in Figure (\ref{fig:DataFitYildiz}) displays the joint probability distribution of having a specific initial displacement and final displacement ($P(x_i,x_f)$).
+The first plot in Figure (\ref{fig:DataFitYildiz}) displays the joint probability distribution of having a specific initial displacement and final displacement ($p(x_i,x_f)$).
 The linear regression from Yildiz's experiment indicates a functionality between the two with an average final displacement of 9.1 nm, shown from the y-intercept, and a slope of 0.6.
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=14cm, height = 10cm]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
@@
 
-We also fit the pre-exponential unbinding factor ($C$) and unbinding rate ($k_{ub}$) based on the following experimental plots shown below.
+We also fit the pre-exponential unbinding factor ($C$) and unbinding rate ($k_{ub}$) based on the following experimental plots.
 
@@
 	\centering
-	\includegraphics[width=0.6\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
-	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=15.5cm, height = 6cm]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=15cm, height = 10cm]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 	\caption[Fitting Bothbound Parameters]{\textbf{Fitting Bothbound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
@@
 
-By measuring the unbinding rates of the ensemble of both-bound configurations, we were able to accurately reproduce the experiments unbinding probability for the trailing leg as a function of initial binding domain separation.
-This result forces the model to prefer trailing steps for large initial distances and influence forward directed stepping from the trailing leg's powerstroke.
-The model dynein could also replicate observed velocities over a long walk by modifying the unbinding rate ($k_{ub}$) and comparing the slopes of the binding domain trajectories.
+By measuring the unbinding rates from the ensemble of both-bound configurations, we were able to accurately reproduce the experiments unbinding probability for the trailing leg as a function of the initial binding domain separation (L).
+This result forced the model to prefer trailing steps for large initial distances and influenced forward directed stepping from the trailing leg's powerstroke.
+The model dynein also replicated experiment's velocities over a long walk by modifying the unbinding rate ($k_{ub}$) and comparing the slopes of the binding position trajectories.
+Both the experiment and model were able to record dynein's average velocity to be $v\approx25$ nm/s.
+Additionally, the bottom plot in Figure (\ref{fig:BBPlots}) displays the model's ability to replicate dynein's ``drunken" walk, with steps that vary forward and backwards.
 
+Based off the resemblence with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein.
+In our spring model, we assumed each domain to act as springs to influence the powerstroke.
+However, the simulations displayed more consistent forward stepping when we turned off the binding domain spring and only allowed the motor and tail to have non-zero spring constants.
+This adjustment displays the flexibility within the model and the potential to fine-tune paramters to fit different sets of data.
+
+\newpage
 \section{Limiting Cases}\label{sec:LimitingCases}
 
-As mentioned previously, the
+As mentioned previously, the model dynein had to take very rapid steps in order to closely generate Yildiz's stepping correlation.
+To achieve a slope closer to Yildiz's value of 0.6, the binding rate ($k_b$) and affinity transition rate ($k_a$) must both increase significantly.
+This led to instantaneous rebinding, as we investigated the limiting case of $k_a\gg k_b$ (affinity transition time $t_a\to 0$) and is shown in Figure (\ref{fig:DataFitYildiz99})
+
+\begin{figure}[H]
+	\begin{minipage}[b]{0.5\textwidth}
+	\includegraphics[width=8.5cm, height=6.5cm]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\end{minipage}
+	\begin{minipage}[b]{0.6\textwidth}		
+	\includegraphics[width=9.2cm, height = 6cm]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\end{minipage}	
+	\begin{center}
+	\includegraphics[width=12cm, height = 7.5cm]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\end{center}	
+	\caption[Limiting Case]{\textbf{Limiting Case for Instant Rebinding.} Each plot closely resembled the plots shown before but with the limiting case of $k_a\gg k_b$.
+The steps exhibited instantaneous rebinding, where the lifted domain landed at the same position immediately after unbinding off of the microtubule ($x_f\approx x_i$).
+The one-bound times were recorded within the first time-step where $dt<5$ ns.}
+	\label{fig:DataFitYildiz99}
+\end{figure}
+
+When fitting to Yildiz's slope, we avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (on Figure \ref{fig:DataFitYildiz}).
+The binding and affinity transition rate can be modified to fit the large step lengths better, but doing so would decrease the correlation between the displacements and thus, the value for the slope.
+This created a balance between fitting according to the slope or the step length plot.
+We believe that the parameters shown in Table (\ref{tab:params}) best demonstrates the functionality of the displacements while maintaining dynein's forward directionality with a similar step length trend.
 
@@
 %	\centering
-%	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/bb_time_-0.5}
-%	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
-%	\label{fig:ProbTrail}
-%\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\includegraphics[width=0.65\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
+%	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+%	\includegraphics[width=0.65\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+%	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
 Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement.
@@
 Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
-	\label{fig:DataFitYildiz99}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_9.00e+99_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
+%	\label{fig:DataFitYildiz09}
+%\end{figure}
+%
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+%	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
 Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
-	\label{fig:OBtime99}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\includegraphics[width=0.65\textwidth]{/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle.
-Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement.
-\textit{Bottom:} One dimensional probability density of step length.
-Step length defined as final displacement minus the initial displacement.
-Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.}
-	\label{fig:DataFitYildiz09}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[One-bound times]{\textbf{One-bound times.} Distribution of time spent in the one-bound state from either a trailing or leading step for an initial distance $L=16$.
-Average affinity time labeled at $\langle t_a \rangle \approx 0.01 \mu s$, and probability outside the time range is $P(t>0.5\mu s) \approx 0.0066$.}
-	\label{fig:OBtime09}
-\end{figure}
+%	\label{fig:OBtime09}
+%\end{figure}
 

### 2021-04-20 papers/jin-thesis/main.tex
Added to thesis and changed sizes of plots

@@
 	\chapter*{Abstract}
-	Molecular motor proteins are the working soldiers within a cell.
-More specifically, the motor protein dynein delivers vital information along the microtubule for cellular processes like axonal transport and cell division.
+	The motor protein dynein is responsible for cellular processes such as axonal transport and cell division by delivering vital information along the microtubule track.
 A failed delivery can cause severe damage to the cell’s functionality and lead to neurological diseases.
-Despite dynein's rich history in cellular research, the mechanisms of its motility remains poorly understood and is spectulated to be a cause for defects.
-In contrary to dynein having completely stochastic stepping, experimentalist Ahmet Yildiz and colleagues observed a dependence of dynein's stepping behavior as a function of interhead separation.
+Despite dynein's rich history in cellular research, the mechanisms of its motility remains poorly understood due to its large size, flexible structure, and stochastic stepping.
+Therefore, recent studies attempts to further understand dynein's stepping mechanism in hopes to prevent motility failure.
+Experimentalist Ahmet Yildiz and colleagues observed a dependence within dynein's stepping behavior varying as a function of interhead separation.
 To investigate this, we developed a two-dimensional, particle-rod model of dynein and simulated its stepping mechanisms using Monte Carlo methods and Brownian dynamics.
-The simulation optimized stepping patterns by fitting parameters according to Yildiz's results.
+We emulated the powerstroke by simulating rate limiting steps that transition the model dynein between a both-bound and one-bound state.
+The simulation optimized parameter sets by fitting probability distributions to Yildiz's observations.
 In order to replicate the correlation observed by Yildiz, the binding rate was increased to encourage fast steps.

### 2021-04-27 papers/jin-thesis/Chapters/1Introduction.tex
THESIS DONE (first fully complete draft)

@@
 In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior.
-What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which we seek to replicate Yildiz's observation of correlated stepping \cite{Dewitt2012}.
+What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which seeks to replicate an inter head stepping correlation observed by experimentalist Ahmet Yildiz \textit{et al.} \cite{Dewitt2012}.
 
@@
 Cells are complicated.
-They have the ability to move, perfectly divide, and spatially organize themselves but are responsible for fatal diseases when these functions fail.
+They are the fundamental unit of life and have the ability to move, perfectly divide, and spatially organize themselves.
+When these functions fail, cell degeneration can cause fatal diseases within their host.
 Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track.
@@
 Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern.
-On the other hand, dynein's structure involves two autonomous motors that cause inconsistent steps.
+On the contrary, dynein's structure involves two autonomous motors that cause inconsistent steps.
 As opposed to kinesin and myosin's uniform stepping, dynein exhibits an inchworm walk with one leg consistently ahead of the other, emulating a limping motion.
@@
 
-These unique properties make dynein difficult to study when analyzing possible sources of molecular failure, but illustrates the importance of understanding its entire physical structure and the chemical interactions with ATP to produce motion.
+These unique properties make dynein difficult to study when analyzing possible sources of molecular failure, but illustrates the importance of understanding its entire physical structure and chemical interaction with ATP to produce motion.
 
@@
 In kinesin and myosin, the motor domains are much closer to the microtubule, causing a more controlled and consistent step due to their low center of mass.
-Despite dynein's large structure, it can still achieve processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, which is why the AAA+ domains are referred to as the motor domains.
+Despite dynein's large structure, it still achieves processive stepping due to the interaction of adenosine triphosphate (ATP) with the AAA+ domains, which is why the AAA+ domains are referred to as the motor domains.
 
@@
 Or do the knees stay bent, while the tail swings forward?
-Despite ongoing debates, researchers suggest the former and named this process the powerestroke model.
+Despite ongoing debates, recent studies suggest the former and named this process the powerestroke model.
 
@@
 The cycle utilizes the conformational transitions between high and low affinity to explain dynein's unbinding and rebinding process.
-This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the MT (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the MT (steps 6 to 7), pulling the whole protein forward.
+This transition is governed by the addition of an ATP unit, which loosens the ``foot" from the microtubule (steps 3 to 4), stretches the linker (steps 5 to 6), and tightens the ``foot" back onto the microtubule (steps 6 to 7), pulling the whole protein forward.
 This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step.

### 2021-04-27 papers/jin-thesis/Chapters/2Theory.tex
THESIS DONE (first fully complete draft)

@@
 \subsection{2D Rigid Rod Model}
-Since our goal is to investigate dynein's interhead coordination during its forward directed stepping, we decided to model dynein as a 2-dimensional system of circular domains held together by massless rigid rods.
+Since our goal is to investigate dynein's interhead coordination during its forward directed stepping, we decided to model dynein as a two-dimensional system of circular domains held together by massless rigid rods.
 These cirular domains embody the two binding domains, two motor domains, and one tail domain, where each domain act as independent angular springs with their own spring constants.
@@
 	\includegraphics[width=0.6\columnwidth]{Figures/model-cartoon.png}
-	\caption[Dynein Model]{\textbf{Dynein Model.} A model of the dynein in the both bound state where both binding domains are bounded to the microtubule.
+	\caption[Dynein Model]{\textbf{Dynein Model.} A model of the dynein in the both-bound state where both binding domains are bounded to the microtubule.
 The springs are only a visualization of how they control the domains and are not a part of the model geometry.
@@
 
-Despite dynein's complexity allowing its step to vary in both length and direction, we limit our model to one direction to eliminate the off-axis dimension when analyzing the forward stepping pattern of dynein.
-This would also simplify the asymmetry of the microtubule when the dynein is stepping either on the $\alpha$ or $\beta$ tubulin.
-We also simplify the stalk and linker to be massless because we are assuming the drag force to be much larger than the mass of the rods and domains.
+Despite dynein's step varying in both length and direction, we limit our model in one direction to eliminate the off-axis and only focus on dynein's forward stepping.
+This would simplify the asymmetry of the microtubule when dynein is stepping on the $\alpha$ or $\beta$ tubulin.
+We also assume massless stalks and linkers due to the strong drag force terms dominating the mass of the rods and domains in the equations of motion.
 The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics.
@@
 To best simulate the stretching and forward kicking motion of the power stroke, we define the domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$.
-This can be analogous to how humans walk, where the domains correspond to flexible joints when taking a step.
-Defining the domains as springs also allows us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law,
+This is analogous to how humans walk, where the domains correspond to flexible joints when taking a step.
+Defining the domains as springs influences forward bias walking by introducing a restoring force in each domain using Hooke's law,
 \begin{equation}
@@
 However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity.
-Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one bound state and the post-stroke both bound state.
+Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one-bound state and the post-stroke both-bound state.
 
@@
 	\includegraphics[width=0.9\columnwidth]{Figures/OB_vs_BB.PNG}
-	\caption[One Bound vs.
-Both Bound]{\textbf{One Bound vs.
-Both Bound} \textit{Left}: Prestroke one bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg.
-\textit{Right}: Poststroke both bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg.
+	\caption[One-Bound vs.
+Both-Bound]{\textbf{One-Bound vs.
+Both-Bound} \textit{Left}: Prestroke one-bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg.
+\textit{Right}: Poststroke both-bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg.
 \cite{Capek2017}.}
@@
 
-Differentiating the two allows us to more conveniently bias the conformational change by defining different equilibrium angles for both states.
-Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both bound state is identical for both binding and motor domain pairs, i.e.
+Differentiating the two conveniently biases the conformational changes by defining different equilibrium angles for both states.
+Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both-bound state is identical for both binding and motor domain pairs, i.e.
 $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
-However, in the one bound state, the unbound leg exhibits the powerstroke and kick out.
+However, in the one-bound state, the unbound leg exhibits the powerstroke and kicks out.
 Therefore, the equilibrium angles for the motor domains differ in order to bias the unbound leg to straighten and perform the powerstroke.
@@
 These binding rates are model parameters defined by binding constants with units of probability per time.
-When the dynein is in the one bound state, the binding domain depends on two rebinding parameters: the affinity transition time ($t_a$) and the binding rate ($\rho_b$).
-We assume that the unbound binding domain can only bind when high affinity completely transitions into low affinity and when the domain is within a vertical range of the microtubule, i.e.
+When the dynein is in the one-bound state, the binding domain depends on two rebinding parameters: the affinity transition time ($t_a$) and the binding rate ($\rho_b$).
+We assume that the one-bound can only bind when high affinity completely transitions into low affinity and when the domain is within a vertical range of the microtubule, i.e.
 \begin{equation}
@@
 \end{equation} 
-Here, $t$ is the total one bound time, $k_a$ is the affinity transition rate, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
+Here, $t$ is the total one-bound time, $k_a$ is the affinity transition rate, $k_b$ is the binding rate constant, $H$ is the Heaviside step function, $r_{ub,y}$ is the y position of the unbound binding domain, and $\epsilon$ is the range within the microtubule.
 
-When the dynein is in the both bound state and wants to unbind, we incorporate a stepping bias in the unbinding rate.
+When the dynein is in the both-bound state and wants to unbind, we incorporate a stepping bias in the unbinding rate.
 As supported from Yildiz in Figure (\ref{fig:trailingbias}), the likelihood of the trailing leg unbinding is greater than the leading leg when the distance between the two legs increases.
@@
 
-The key difference between the works in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state.
-In addition to the large both bound time mentioned earlier, they also noticed that the initial both bound configuration of the domains does not impact the stepping, giving a better incentive to apply a Monte Carlo approach.
-This new method of analyzing the both bound state will significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.
+The key difference between the works in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both-bound state.
+In addition to the large both-bound time mentioned earlier, they noticed that the initial both-bound configuration of the motor and tail domains do not impact the stepping, giving a better incentive to apply a Monte Carlo approach.
+This new method of analyzing the both-bound state will significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one-bound state.
 
@@
 
-\subsection{Brownian Dynamics for One Bound}
+\subsection{Brownian Dynamics for One-Bound}
 \label{sec:BrownianDynamics}
 
-When simulating dynein's one bound motion, the domains of constant mass must obey classical Newtonian physics and follow Newton's laws of motion. That is,
+When simulating dynein's one-bound motion, the domains of constant mass must obey classical Newtonian physics and follow Newton's laws of motion. That is,
 \begin{equation}
@@
 \end{equation}
-which is a differential equation we can solve for the equations of motion for the domains in the one bound state. The derivation and final equations of motion can be found in \cite{Capek2017, W}
+which is a differential equation we can solve for the equations of motion for the domains in the one-bound state. The derivation and final equations of motion can be found in \cite{Capek2017, W}
 
-\subsection{Monte Carlo for Both Bound}
-Since dynein spends the majority of time in the both bound state, we can safely assume that the dynein equilibriates before unbinding.
+\subsection{Monte Carlo for Both-Bound}
+Since dynein spends most of its stepping time in the both-bound state, we safely assume dynein equilibriates before unbinding.
 This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system.
-Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids where a system of atoms possess many different microstates.
-For this model, dynein is the system and the many possible both bound configurations is analogous to the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values.
-The enables the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics.
-Eventually, this allows us to create probability distributions for important variables.
+Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids, where a system of atoms possess many different microstates.
+For this model, dynein is the system and the many possible both-bound configurations are the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both-bound configuration is independent and can generate different total energy values.
+This produces a large ensemble of of both-bound configurations, which we sample to create stepping statistics.
+Eventually, these statistics will reduce to probability distributions for important variables.
 
-With the assumption of thermodyamic equilibrium during the both bound state, we define the probability of a configuration from a Boltzmann distribution and calculate the relative unbinding probability for that configuration by using a proportionality expression.
+With the assumption of thermodyamic equilibrium during the both-bound state, we use a Boltzmann distribution to define the probability of a configuration and calculate the relative unbinding probability with a proportionality expression.
 That is,
@@
 \end{equation}
-where $i$ refers to the specific both bound configuration.
-In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well.
+where $i$ refers to the specific both-bound configuration.
+In order to guarantee an accurate thermodynamic ensemble of both-bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well.
 The thermodynamic ensemble then generates an ensemble of steps that can eventually produce smooth statictics.
-With the partition function defined in Equation (\ref{eqn:partition}), we also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time.
+With the partition function defined in Equation (\ref{eqn:partition}), we also define ensemble averages for both-bound statistics, such as the average unbinding rates, unbinding probability, and both-bound time.
 The equations to do so are all shown below in that order:

### 2021-04-27 papers/jin-thesis/Chapters/3Methods.tex
THESIS DONE (first fully complete draft)

@@
 The entire model and simulation code can be found at \url{https://github.com/kiatvonj/dynein_walk}, where the model and simulation were coded using both Python and C++.
-The both bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous, while the time dependent one-bound Brownian dynamics was coded on C++ to utilize faster computation speed.
+The both-bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous, while the time dependent one-bound Brownian dynamics was coded on C++ to utilize faster computation speed.
 
@@
 %\textit{Picking Random angles to create random distribution of dynein configurations.
-Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound.
+Make sure to clarify that the simulation is split into two parts, the monte carlo both-bound and brownian one-bound.
 It is done this way in order for MC to generate ensemble of data rather quickly.}\\
@@
 To generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk.
-This simplifies the code into two parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycle repeatedly after the model takes a step.
-The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculates the total energy.
-If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one bound simulation and execute the Brownian dynamics.
-Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step.
-However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, to ensure that our ensemble covers the whole sample space of possible both bound configurations.
+This simplifies the code into two parts (the Monte Carlo both-bound and the Brownian dynamics one-bound) that cycle repeatedly after the model takes a step.
+The simulation starts in the both-bound state, where the Monte Carlo randomly picks a both-bound configuration and calculates the total energy.
+If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one-bound simulation and execute the Brownian dynamics.
+Once the one-bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both-bound configuration for another step.
+However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, to ensure that our ensemble covers the whole sample space of possible both-bound configurations.
 This forces the measured probabilities to be a function of $L$ and will be addressed later in the Data Analysis section (Section \ref{sec:DataAna}).
-The algorithm for the both bound process is shown below:
+The algorithm for the both-bound process is shown below:
 
@@
 	\end{equation}
-	Here, $i$ refers to the specific both bound configuration and $k$ is the domain. We also defined $\kappa$ to normalize the relative unbinding probability to keep it less than 1.
+	Here, $i$ refers to the specific both-bound configuration and $k$ is the domain. We also defined $\kappa$ to normalize the relative unbinding probability to keep it less than 1.
 
@@
 	\setcounter{enumi}{6}
-	\item If dynein unbinds, initialize the one bound state with the both bound configuration, run the Brownian dynamics simulation of the step, and wait until it rebinds.
+	\item If dynein unbinds, initialize the one-bound state with the both-bound configuration, run the Brownian dynamics simulation of the step, and wait until it rebinds.
 \end{enumerate}
@@
 	\setcounter{enumi}{7}
-	\item Collect statistics about the final position and one bound time. Repeat algorithm from step 2. 
+	\item Collect statistics about the final position and one-bound time. Repeat algorithm from step 2. 
 \end{enumerate}
@@
 
-A more in-depth explanation and rigorous flow chart for the one bound Brownian dynamics simulation can be found here \cite{Capek2017, }.
+A more in-depth explanation and rigorous flow chart for the one-bound Brownian dynamics simulation can be found here \cite{Capek2017, }.
 
 %\section{Time Evolution}
-%\textit{Simulate over a delta t during one bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}
+%\textit{Simulate over a delta t during one-bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}
 
@@
 	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
-	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles.
+	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both-bound dynein with model domains to identify post-stroke equilbrium angles.
 The arrow indicates 15 nm \cite{Burgess2003}.
-\textit{Right:} Cryo-electron tomograph of one bound dynein for pre-stroke equilbrium angles \cite{grotjahn2018cryo}.}
+\textit{Right:} Cryo-electron tomograph of one-bound dynein for pre-stroke equilbrium angles \cite{grotjahn2018cryo}.}
 	\label{fig:ParamsPics}
@@
 We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, because the inverse yields the average time it takes to unbind, i.e.
-the both bound time.
+the both-bound time.
 The rebinding rates, $k_a$ and $k_b$, are harder to optimize because they directly correlate to step length.
 The ability for dynein to take long steps is dependent on how long dynein diffuses above the microtubule.
-Therefore, the rebinding rates have a much larger parameter space due to the flexibility of optimizing according to the one bound time or step length.
+Therefore, the rebinding rates have a much larger parameter space due to the flexibility of optimizing according to the one-bound time or step length.
 Since we are interested in Yildiz's step lengths, we match these rates to the linear regression from Figure (\ref{fig:YildizCorrelation}) and Yildiz's step length plots.

### 2021-04-27 papers/jin-thesis/Chapters/4Results.tex
THESIS DONE (first fully complete draft)

@@
     $\theta_t$ & $\eqt$ &  & \\
-    $R_t$ & $\radiust$ & $8nm$ & \cite{Burgess2003}\\
-    $R_m$ & $\radiusm$ & $11nm$ & \cite{Burgess2003}\\
-    $R_b$ & $\radiusb$ & $3.5nm$ & \cite{Burgess2003}\\
+    $R_t$ & $\radiust nm$ & $4nm$ & \cite{Burgess2003}\\
+    $R_m$ & $\radiusm nm$ & $5.5nm$ & \cite{Burgess2003}\\
+    $R_b$ & $\radiusb nm$ & $1.25nm$ & \cite{Burgess2003}\\
     \hline
@@
 The accumulative density from the diagonal shaded region is evident in this plot due to the peak at 0 nm.
-However, experiment was unable to detect 0 nm steps and is shown within the dip from Experiment Fig 3A (small density at 0 nm were lateral steps on the off-axis with little change on the on-axis).
+However, experiment was unable to detect 0 nm steps and is shown from the dip in Experiment Fig 3A (small density at 0 nm were lateral steps on the off-axis with little change on the on-axis).
 Our model suggests that dynein can still achieve forward directed motion with more positive steps than negatives ones but prefers short stuttered steps with fast one-bound times.
@@
 As the distribution of times in Figure (\ref{fig:OBtime}) indicates, the model dynein frequently spends $<$ 0.1 $\mu s$ in the one-bound state, with the dynein most likely to rebind immediately after the affinity transitions.
-This demonstrates the importance of a buffer time when the dynein unbinds in order to avoid instantaneous rebinding and still achieve large positive step lengths.
-A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCases}).
+This demonstrates the importance of a buffer time when the dynein unbinds to avoid instantaneous rebinding while still achieving large positive step lengths.
+A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCase}).
 
@@
 
-Based off the resemblence with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein.
+Based on the resemblence with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein.
 In our spring model, we assumed each domain to act as springs to influence the powerstroke.
 However, the simulations displayed more consistent forward stepping when we turned off the binding domain spring and only allowed the motor and tail to have non-zero spring constants.
+That is, $c_b=0$ while $c_m=c_t=1$ from Table (\ref{tab:params}).
 This adjustment displays the flexibility within the model and the potential to fine-tune paramters to fit different sets of data.
@@
 \newpage
-\section{Limiting Cases}\label{sec:LimitingCases}
+\section{Limiting Case}\label{sec:LimitingCase}
 
 As mentioned previously, the model dynein had to take very rapid steps in order to closely generate Yildiz's stepping correlation.
-To achieve a slope closer to Yildiz's value of 0.6, the binding rate ($k_b$) and affinity transition rate ($k_a$) must both increase significantly.
+To lessen the error and achieve a slope closer to Yildiz's value of 0.6, the binding rate ($k_b$) and affinity transition rate ($k_a$) must both increase significantly.
 This led to instantaneous rebinding, as we investigated the limiting case of $k_a\gg k_b$ (affinity transition time $t_a\to 0$) and is shown in Figure (\ref{fig:DataFitYildiz99})
@@
 The steps exhibited instantaneous rebinding, where the lifted domain landed at the same position immediately after unbinding off of the microtubule ($x_f\approx x_i$).
-The one-bound times were recorded within the first time-step where $dt<5$ ns.}
+The large majority of one-bound times were recorded within the first time-step where $dt<5$ ns.}
 	\label{fig:DataFitYildiz99}
@@
 When fitting to Yildiz's slope, we avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (on Figure \ref{fig:DataFitYildiz}).
-The binding and affinity transition rate can be modified to fit the large step lengths better, but doing so would decrease the correlation between the displacements and thus, the value for the slope.
-This created a balance between fitting according to the slope or the step length plot.
-We believe that the parameters shown in Table (\ref{tab:params}) best demonstrates the functionality of the displacements while maintaining dynein's forward directionality with a similar step length trend.
+The binding and affinity transition rates can be better optimizied to fit the larger step lengths (we classified ``large'' steps as $> 40$ nm), but doing so would decrease the correlation between the displacements and thus, the value for the slope.
+This caused an optimization problem of whether to fit according to the slope or the step lengths.
+We believed that the parameters shown in Table (\ref{tab:params}) best demonstrated the functionality of the displacements from the slope, while maintaining dynein's forward directionality with a similar step length trend towards large steps.
 

### 2021-04-27 papers/jin-thesis/Chapters/5Conclusion.tex
THESIS DONE (first fully complete draft)

--- 2021-01-17 papers/jin-thesis/Chapters/5Conclusion.tex
@@
-\section{Findings}
-\textit{What do our results indicate? Do we think our model correctly represents real dynein and its stepping patterns?}
+%\textit{What do our results indicate? Do we think our model correctly represents real dynein and its stepping patterns?}
 
-\section{Further Work}
-\textit{How can we improve our model?}
+We successfully incorporated a Monte Carlo algorithm when dynamically simulating dynein's unique stepping mechanism.
+By modelling dynein as a two-dimensional particle-rod system, we separated the conformations of the mechanochemical cycle into a both-bound and one-bound state and emulated the powerstroke with springs in each domain.
+With various degrees of freedom controlling the properties of a step, the model was able to flexibly optimize according to experimental results and provide further conclusions for observations.
+More specifically, we replicated experimentalist Ahmet Yildiz's unique result of an observered stepping correlation between the initial domain separation and final displacement with a 16.5\% error.
+
+Despite experiments inability to observe step lengths close to 0 nm, we conclude that dynein must take short and fast steps in order to achieve strong stepping dependence.
+After many tests with different combinations of parameters, the set of parameters shown in Table (\ref{tab:params}) demonstrated Yildiz's stepping correlation while still preserving directed motion with similar positive step length trends.
+Dynein also preferred larger positive steps when only the motor and tail domains acted as springs.
+Furthermore, the model achieved dynein's stepping tendencies with biased trailing steps and identical walking trajectories, all while being more computationally efficient and faster than previous simulations.
+
+If time provides, the flexbility of the model allows for a more sufficient optimization process that can minimize the parameter space when replicating experiment.
+Further work can apply this to other experimental hypotheses regarding dynein's stepping pattern and provide further support for new observations.
+As mentioned earlier, most simulations model the ATP transitions during the mechanochemical cycle, while this model focuses on the dynamics within the step.
+Thus, a combined model that incorporates both features may describe natural dynein perfectly and bring us one step closer to engineering a reliable prevention for cell failure.

### 2021-04-27 papers/jin-thesis/main.tex
THESIS DONE (first fully complete draft)

@@
 \title{
-	\Huge{Modeling the mechanisms of dynein's step using Monte Carlo simulations and Brownian dynamics}\vspace{1em}\\
+	\Large{Simulating Dynein: A Monte Carlo Improvement to a Dynamical Model of the Dynein Motor Protein}\vspace{1em}\\
+	\large{by} \\ 
 	\Large{Jin Kiatvongcharoen} \vspace{0.5em}\\[2in] 
@@
 Despite dynein's rich history in cellular research, the mechanisms of its motility remains poorly understood due to its large size, flexible structure, and stochastic stepping.
-Therefore, recent studies attempts to further understand dynein's stepping mechanism in hopes to prevent motility failure.
-Experimentalist Ahmet Yildiz and colleagues observed a dependence within dynein's stepping behavior varying as a function of interhead separation.
+Unlike its motor protein siblings which posses uniform stepping, dynein's step is unpredictable and can vary in size and direction.
+However, experimentalist Ahmet Yildiz and colleagues observed a stepping dependence within the interhead separation, indicating a possible correlation during dynein's step.
 To investigate this, we developed a two-dimensional, particle-rod model of dynein and simulated its stepping mechanisms using Monte Carlo methods and Brownian dynamics.
-We emulated the powerstroke by simulating rate limiting steps that transition the model dynein between a both-bound and one-bound state.
-The simulation optimized parameter sets by fitting probability distributions to Yildiz's observations.
-In order to replicate the correlation observed by Yildiz, the binding rate was increased to encourage fast steps.
-Our results indicate that dynein takes many short and immediate steps that are undetectable to experimentalists in order to achieve stepping dependence on the initial domain separation.
+We simplified the mechanochemical cycle by simulating rate limiting steps that transitions between a both-bound and one-bound state and emulated the powerstroke by defining springs in each domain.
+After optimizing parameters sets, the model achieved Yildiz's stepping correlation only when the binding rates were significantly large.
+Our simulations indicate that dynein must take many short ($\langle t \rangle < 0.1 \mu s$) and immediate steps, with step lengths close to 0 nm, in order to reproduce a stepping dependence within the interhead domain separation.
+These results demonstrates the model's ability to capture dynamic properties from experimental observations and provide further support for other experimental hypotheses regarding dynein's step.
+
 %	

### 2021-04-27 scripts/make_mc_plots.py

@@ -327,7 +327,7 @@ def make_step_length_plots(args, plotpath, probability_distribution, initial_dis
 
     norm_length_min = 7.75
     if args.k_stk == 9e99:
-        norm_length_min = 3
+        norm_length_min = 0
 
     norm_1B = np.sum(step_length_count_fig_1B[step_length_bin_center_fig_1B>norm_length_min])
     yildiz_normalized_prob_fig_1B = step_length_count_fig_1B/norm_1B
@@ -452,6 +452,11 @@ def make_ob_time_plot(args, plotpath, time_hists, avg_affinity_time, **_):
     time_bin_center = np.arange(increment/2, max_time, increment, dtype=float)
     x_upper_lim = 0.5e-6
     x_increment = 0.1e-6
+    decimal = 1
+    if args.k_stk == 9e99:
+        x_upper_lim = 0.05e-6
+        x_increment = 0.01e-6
+        decimal = 2
     ind = 1
     for j in time_bin_center:
         if j < x_upper_lim:
@@ -484,7 +489,7 @@ def make_ob_time_plot(args, plotpath, time_hists, avg_affinity_time, **_):
                 xticks = np.arange(0.0, x_upper_lim+x_increment, x_increment)
                 labels = np.arange(0.0, (x_upper_lim+x_increment)*1e6, x_increment*1e6)
                 plt.xlim(-increment,x_upper_lim)
-                plt.xticks(xticks, np.around(labels,decimals=1))
+                plt.xticks(xticks, np.around(labels,decimals=decimal))
                 plt.legend()
                 plt.subplots_adjust(top=0.93)
                 plt.gca().spines['right'].set_visible(False)

### 2021-05-05 papers/jin-thesis/Chapters/1Introduction.tex
Thesis edits

@@
 
-	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, are a leading cause of death in the United States \cite{eschbach2011cytoplasmic}.
+	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, are a leading cause of death in the United States \cite{gammon2014neurodegenerative}.
 Scientists have yet to find a prevention or cure to these fatal diseases but suggests that motor protein failure directly contributes to cell degeneration.
-More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties.
+More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties \cite{eschbach2011cytoplasmic}.
 However, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature.
@@
 These motor proteins are myosin, kinesin, and dynein and are shown below in Figure (\ref{fig:Compare}).
-Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern.
+Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern \cite{fehr2008kinesin}.
 On the contrary, dynein's structure involves two autonomous motors that cause inconsistent steps.
@@
 	\includegraphics[width=0.4\columnwidth]{Figures/motor_comparison.png}
-	\caption[Motor Proteins]{\textbf{Motor Proteins} Structure of myosin, kinesin, and dynein. \cite{JohnsonArt}}
+	\caption[Motor Proteins]{\textbf{Motor Proteins} Structure of myosin, kinesin, and dynein. \cite{RonArt}}
 	\label{fig:Compare}
@@
 Because microtubules are protein dimers constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulins, the microtubule track is polarized depending on which tubulin dominates at the end points.
-In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a negative end at the nucleus and influencing dynein's directionality.
+In a eukaryotic cell, microtubules typically stem outwards from the cell's nucleus to the cell walls where the $\beta$ tubulin is exposed, generating a negative end at the nucleus and influencing dynein's directionality \cite{paschal1987retrograde}.
 Figure (\ref{fig:transport}) displays kinesin and dynein experiencing a charged attraction to the end points, while they share a cargo to deliver information during axonal transport.
@@
 
-Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains.
+Dynein's ``leg" is a complex protein assembly composed of linked amino acids subunits, called polypeptides, separated into three main domains \cite{Burgess2003}.
 Figure (\ref{fig:structure}) displays these as the tail, the AAA+ rings (or motor), and the microtubule binding domain.
 The tail and the motor domains are connected by separate linkers, while the motor and the binding domains are connected by stalks.
-Both the linker and stalk measures greater than 20 nm in length, causing dynein to stand up to 50 nm high.
+Both the linker and stalk measures greater than 20 nm in length, causing dynein to stand up to 50 nm high \cite{Burgess2003}.
 
@@
 
-Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis.
+Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis \cite{manna2020mechanistic, elshenawy2020lis1}.
 The ATP binds onto the motor domain and converts chemical energy into mechanical energy for dynein to transition between different conformational states (physicial arrangements) during a step.
@@
 Or do the knees stay bent, while the tail swings forward?
-Despite ongoing debates, recent studies suggest the former and named this process the powerestroke model.
+Despite ongoing debates, recent studies suggest the former and named this process the powerestroke model \cite{Burgess2003}.
 
@@
 This key detail within the transition of stretching the linker distinguishes a ``pre-" and a ``post-" stroke state during the powerstroke model and can be analogous to bending a knee upwards and kicking the foot forwards to stretch the knee and take a step.
-A closer visualization of this transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.
+A closer visualization of the powerstroke and the transition between pre- and post-stroke states can be seen in Figure (\ref{fig:Powerstroke}), where the linker is highlighted in yellow.
 
@@
 
-Experimentalists measures dynein in various ways that utilizes electron microscopy and quantum measuring devices.
-Some attach quantum dots to dynein's motor domains, while others replace the tail with an artificial quantum rod.
+Experimentalists measures dynein in various ways that utilizes electron microscopy or quantum measuring devices.
+Some use optical tweezers to track dynein's motor domains, while others replace the tail with an artificial quantum rod \cite{kinoshita2018step, Dewitt2012}.
 Despite the different procedures, all measuring techniques suffer from their inability to measure steps within $\sim 0.4$ nm of where the binding domain lifted off.
@@
 The various measuring procedures and experimental limitations leads to different results and unique findings when observing different variables.
-In this paper, we focus on the unique observation by Yildiz \textit{et al.} of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping.
+In this paper, we focus on the unique observation by Yildiz \textit{et al.} of a stepping correlation between the initial interhead separation and step length because of the results contradicting previously accepted theories of independent stepping \cite{Dewitt2012}.
 
@@
 
-Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step.
+Due to dynein's large size and stochastic nature, dynein's step was previously hypothesized to be independent from the initial conformational before the step \cite{wang1995single}.
 However, in 2012, Yildiz \textit{et al.} observed a correlation between the initial on-axis separation and the step length, indicating a dependence on the interhead separation \cite{Dewitt2012}.
@@
 These simulations suffer from numerous assumptions made about the physical aspects of dynein's step.
-(\textit{Should reference a simulation here}) Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame.
+Some assume that dynein can step only in increments of 8nm or that the rebinding process is constrained to a certain time frame \cite{singh2005monte, trott2018mathematical}.
 These limitations make it impossible for their models to replicate mechanical phenomenon observed in dynein's stepping, such as Yildiz's correlation from above.
 
-To bridge this gap, Roundy \textit{et al.} constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment.
+To bridge this gap, Roundy \textit{et al.} constructed a physical model of dynein that explores the molecular interactions between the domains of dynein and its aqueous environment \cite{Capek2017, waczak2019drunken}.
 Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes.

### 2021-05-05 papers/jin-thesis/Chapters/2Theory.tex
Thesis edits

@@
 However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity.
-Since we assume simple ATP exchange and that the two physical states are during binding and unbinding \cite{}, we categorize the cycle into two main conformations: the pre-stroke one-bound state and the post-stroke both-bound state.
+Since we assume simple ATP exchange and that the two physical states are during binding and unbinding, we categorize the cycle into two main conformations: the pre-stroke one-bound state and the post-stroke both-bound state.
 
@@
 
-The key difference between the works in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both-bound state.
+The key difference between the works in \cite{Capek2017, waczak2019drunken} and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both-bound state.
 In addition to the large both-bound time mentioned earlier, they noticed that the initial both-bound configuration of the motor and tail domains do not impact the stepping, giving a better incentive to apply a Monte Carlo approach.
@@
 \end{equation}
-which is a differential equation we can solve for the equations of motion for the domains in the one-bound state. The derivation and final equations of motion can be found in \cite{Capek2017, W}
+which is a differential equation we can solve for the equations of motion for the domains in the one-bound state. The derivation and final equations of motion can be found in \cite{Capek2017}
 
@@
 This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system.
-Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids, where a system of atoms possess many different microstates.
+Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids, where a system of atoms possess many different microstates \cite{lim2007vorticity}.
 For this model, dynein is the system and the many possible both-bound configurations are the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both-bound configuration is independent and can generate different total energy values.

### 2021-05-05 papers/jin-thesis/Chapters/3Methods.tex
Thesis edits

@@
 	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small. If not, repeat step 2.
-	   \davidsays{Mention going back to 2 if the distance isn't in range.}
 \end{enumerate}
@@
 
-A more in-depth explanation and rigorous flow chart for the one-bound Brownian dynamics simulation can be found here \cite{Capek2017, }.
+A more in-depth explanation and rigorous flow chart for the one-bound Brownian dynamics simulation can be found here \cite{waczak2019drunken}.
 
@@
 For instance, the exponential unbinding constant, $C$, is fitted specifically to Figure (\ref{fig:trailingbias}).
-We use time data (\textit{cite paper for time data}\cite{}) to fit the unbinding rate constant, $k_{ub}$, because the inverse yields the average time it takes to unbind, i.e.
-the both-bound time.
+We fit the unbinding rate constant, $k_{ub}$, according to velocities for dynein's walk by matching to experimental trajectory data.
 The rebinding rates, $k_a$ and $k_b$, are harder to optimize because they directly correlate to step length.

### 2021-05-05 papers/jin-thesis/Chapters/4Results.tex
Thesis edits

@@
   \end{tabular}
-  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:Trajectory}).}
+  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:BBPlots}).}
   \label{tab:params}
@@
 The accumulative density from the diagonal shaded region is evident in this plot due to the peak at 0 nm.
-However, experiment was unable to detect 0 nm steps and is shown from the dip in Experiment Fig 3A (small density at 0 nm were lateral steps on the off-axis with little change on the on-axis).
-Our model suggests that dynein can still achieve forward directed motion with more positive steps than negatives ones but prefers short stuttered steps with fast one-bound times.
+However, experiment was unable to detect 0 nm steps.
+This was shown from the dip in Experiment Fig 3A, where the small density at 0 nm were lateral steps in the off-axis.
+Figure (\ref{fig:DataFitYildiz}) suggests that dynein can still achieve forward directed motion from favoring positive steps rather than negative ones, but prefers short stuttered steps with fast one-bound times.
 A distribution of said one-bound times is shown below in Figure (\ref{fig:OBtime})
@@
 This demonstrates the importance of a buffer time when the dynein unbinds to avoid instantaneous rebinding while still achieving large positive step lengths.
-A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCase}).
+A deeper analysis of this will be discussed in the Limiting Cases section (Section \ref{sec:LimitingCases}).
 
@@
 In our spring model, we assumed each domain to act as springs to influence the powerstroke.
-However, the simulations displayed more consistent forward stepping when we turned off the binding domain spring and only allowed the motor and tail to have non-zero spring constants.
+However, the simulations displayed more consistent forward stepping when we ``turned off" the binding domain spring and only allowed the motor and tail to have non-zero spring constants.
 That is, $c_b=0$ while $c_m=c_t=1$ from Table (\ref{tab:params}).
@@
 \newpage
-\section{Limiting Case}\label{sec:LimitingCase}
+\section{Limiting Cases}\label{sec:LimitingCases}
 
-As mentioned previously, the model dynein had to take very rapid steps in order to closely generate Yildiz's stepping correlation.
-To lessen the error and achieve a slope closer to Yildiz's value of 0.6, the binding rate ($k_b$) and affinity transition rate ($k_a$) must both increase significantly.
-This led to instantaneous rebinding, as we investigated the limiting case of $k_a\gg k_b$ (affinity transition time $t_a\to 0$) and is shown in Figure (\ref{fig:DataFitYildiz99})
+As mentioned previously, the model dynein took very rapid steps in order to closely generate Yildiz's stepping correlation.
+To lessen the error and achieve a slope closer to Yildiz's value, dynein would have to take even faster steps.
+We investigated this by increasing the affinity transition rate ($k_a$) significantly, which nullified the buffer period after unbinding.
+This limiting case of $k_a\gg k_b$ (affinity transition time $t_a\to 0$) is shown in Figure (\ref{fig:DataFitYildiz99})
 
@@
 
-When fitting to Yildiz's slope, we avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (on Figure \ref{fig:DataFitYildiz}).
-The binding and affinity transition rates can be better optimizied to fit the larger step lengths (we classified ``large'' steps as $> 40$ nm), but doing so would decrease the correlation between the displacements and thus, the value for the slope.
-This caused an optimization problem of whether to fit according to the slope or the step lengths.
+As Figure (\ref{fig:DataFitYildiz99}) showed, dynein exhibited instantaneous rebinding.
+If we ignored the transition period between low and high affinity, the model dynein would immediately rebind with an average one-bound time of 5 ns.
+The step length plot in Figure (\ref{fig:DataFitYildiz99}) also displayed a lack of directionality when stepping.
+
+We avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (we classifed ``large'' steps as $> 40$ nm).
+By lowering the binding and affinity transition rates,  the model dynein recorded larger step lengths better and achieved processive motion.
+However, decreasing the rates would subsequently decrease the correlation between the displacements and thus, the value for the slope.
+This caused an optimization problem of whether to fit according to the slope or the large step lengths.
 We believed that the parameters shown in Table (\ref{tab:params}) best demonstrated the functionality of the displacements from the slope, while maintaining dynein's forward directionality with a similar step length trend towards large steps.

### 2021-05-05 papers/jin-thesis/Chapters/5Conclusion.tex
Thesis edits

@@
 By modelling dynein as a two-dimensional particle-rod system, we separated the conformations of the mechanochemical cycle into a both-bound and one-bound state and emulated the powerstroke with springs in each domain.
-With various degrees of freedom controlling the properties of a step, the model was able to flexibly optimize according to experimental results and provide further conclusions for observations.
+With various degrees of freedom controlling the properties of a step, the model was able to flexibly optimize according to experimental results and provide further conclusions for correlated stepping.
 More specifically, we replicated experimentalist Ahmet Yildiz's unique result of an observered stepping correlation between the initial domain separation and final displacement with a 16.5\% error.

### 2021-05-05 papers/jin-thesis/main.tex
Thesis edits

@@
 \newpage
-\cite{Burgess2003} \cite{Cianfrocco2015mechanism} \cite{Dewitt2012} \cite{Capek2017, waczak2019drunken}
-\cite{GoodsellArt} \cite{eschbach2011cytoplasmic}
-\cite{rao2019molecular} \cite{manna2020mechanistic} \cite{desantis2017lis1} 
-\cite{elshenawy2020lis1} \cite{ando2020small} \cite{kinoshita2018step} \cite{qiu2012dynein} \cite{muller1973dynamic} \cite{lim2007vorticity} \cite{fehr2008kinesin} \cite{trott2018mathematical}
 
-\bibliographystyle{unsrt}
+\bibliographystyle{plain}
 \bibliography{references}

### 2021-05-05 scripts/make_mc_plots.py

@@ -327,7 +327,7 @@ def make_step_length_plots(args, plotpath, probability_distribution, initial_dis
 
     norm_length_min = 7.75
     if args.k_stk == 9e99:
-        norm_length_min = 0
+        norm_length_min = 3.5
 
     norm_1B = np.sum(step_length_count_fig_1B[step_length_bin_center_fig_1B>norm_length_min])
     yildiz_normalized_prob_fig_1B = step_length_count_fig_1B/norm_1B

### 2021-05-07 papers/jin-thesis/Chapters/1Introduction.tex
Finished thesis! kind of...

@@
 
-	Neurodegenerative diseases, such as Alzheimer's or Huntinton's disease, are a leading cause of death in the United States \cite{gammon2014neurodegenerative}.
+	Neurodegenerative diseases, such as Alzheimer's or Huntington's disease, are a leading cause of death in the United States \cite{gammon2014neurodegenerative}.
 Scientists have yet to find a prevention or cure to these fatal diseases but suggests that motor protein failure directly contributes to cell degeneration.
-More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's funtional dependence on dynein and its mechanical properties \cite{eschbach2011cytoplasmic}.
-However, dynein possesses a unique structure causing it to stochasitcally move around the cell and be unpredictable in nature.
-Thus, fully understanding the mechanisms of dynein can allow us to further understand causes of its failure.
-In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique steping behavior.
-What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which seeks to replicate an inter head stepping correlation observed by experimentalist Ahmet Yildiz \textit{et al.} \cite{Dewitt2012}.
+More specifically, defects in the motor protein dynein have been linked to neurodegeneration due to the cell's functional dependence on dynein and its mechanical properties \cite{eschbach2011cytoplasmic}.
+However, dynein possesses a unique structure causing it to stochastically move around the cell and be unpredictable in nature.
+Fully understanding the mechanisms of dynein can allow us to further understand causes of its failure.
+In this paper, we propose a model of dynein that uses Monte Carlo methods and a Brownian dynamics simulation to reproduce dynein's unique stepping behavior.
+What follows is a brief introduction to the dynein motor protein, a review of the powerstroke model, and the framework for a computational simulation of the powerstroke, which seeks to replicate the inter head stepping correlation observed by experimentalist Ahmet Yildiz \textit{et al.} \cite{Dewitt2012}.
 
@@
 
-Cells are complicated.
-They are the fundamental unit of life and have the ability to move, perfectly divide, and spatially organize themselves.
-When these functions fail, cell degeneration can cause fatal diseases within their host.
-Their functionality entirely depends on two-legged molecular proteins, named \textit{motor proteins}, that carry information along a microtubule track.
+Cells are the building blocks of all living organisms.
+Their biological responsibilities depend on their ability to move, perfectly divide, and spatially organize themselves.
+If these functions fail, cell degeneration can cause fatal diseases for their host.
+Thus, life depends on the working soldiers of the cell: motor proteins.
+Motor proteins are two-legged molecular proteins that carry information along a microtubule track.
 These microtubules form the cytoskeleton in the cell and act as a walkway for the proteins (see Figure (\ref{fig:ArtDynein})).
@@
 Because of kinesin and myosin's compact structure being close to the microtubule, their legs take turns alternating steps like a human and exhibit a uniform ``hand-over-hand" stepping pattern \cite{fehr2008kinesin}.
-On the contrary, dynein's structure involves two autonomous motors that cause inconsistent steps.
-As opposed to kinesin and myosin's uniform stepping, dynein exhibits an inchworm walk with one leg consistently ahead of the other, emulating a limping motion.
+Dynein's structure involves two autonomous motors that cause inconsistent steps.
+As opposed to kinesin and myosin's uniform stepping, dynein closely exhibits an inchworm walk with one leg consistently ahead of the other, emulating a limping motion.
 
@@
 
-In addition to their structural differences, dynein walks towards the negative end of the microtubule while its motor protein siblings walk towards the positive end.
+In addition to their structural differences, dynein walks towards the negative end of the microtubule, while its motor protein siblings walk towards the positive end.
 Because microtubules are protein dimers constructed from negatively charged $\alpha$- and positively charged $\beta$-tubulins, the microtubule track is polarized depending on which tubulin dominates at the end points.
@@
 
-These unique properties make dynein difficult to study when analyzing possible sources of molecular failure, but illustrates the importance of understanding its entire physical structure and chemical interaction with ATP to produce motion.
+These unique properties make dynein difficult to study when analyzing possible sources of molecular failure, but also illustrates the importance of understanding dynein's physical structure and chemical interaction with ATP to produce motion.
 
@@
 Dynein's physical structure has been rigorously studied because of the pivotal role it plays in dynein's unpredictable stepping nature.
-Its inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are 1.5x larger than the diameter of the AAA+ ring.
+Dynein's inability to step uniformly is due to the large lengths between each major domain site, as the linker and stalk are 1.5x larger than the diameter of the AAA+ ring.
 In kinesin and myosin, the motor domains are much closer to the microtubule, causing a more controlled and consistent step due to their low center of mass.
@@
 Dynein's ability to step is entirely ATP driven under the process of ATP hydrolysis \cite{manna2020mechanistic, elshenawy2020lis1}.
-The ATP binds onto the motor domain and converts chemical energy into mechanical energy for dynein to transition between different conformational states (physicial arrangements) during a step.
-This process allows the binding domains to unbind and reattach at different locations on the microtubule and thus, permit varying step sizes.
+ATP units bind onto the motor domain and converts chemical energy into mechanical energy, enabling dynein to transition between different conformational states (physical arrangements) during a step.
+This process allows the binding domains to unbind and reattach at different locations on the microtubule and permit varying step sizes.
 To measure dynein's step, an axis is defined on the microtubule.
@@
 The on-axis is defined parallel to the direction of forward stepping towards the negative end of the microtubule, while the off-axis is perpendicular, as shown in Figure (\ref{fig:axis}).
-Figure (\ref{fig:axis}) also displays the alternating helix structure of the $\alpha$- and $\beta$-tubulin dimers, in which act as the landing zones for dynein's binding domain.
+Figure (\ref{fig:axis}) also displays the alternating helix structure of the $\alpha$- and $\beta$-tubulin dimers, which act as the landing zones for dynein's binding domain.
 
@@
 Or do the knees stay bent, while the tail swings forward?
-Despite ongoing debates, recent studies suggest the former and named this process the powerestroke model \cite{Burgess2003}.
+Recent studies suggest the former and named this process the powerstroke model \cite{Burgess2003}.
+
+\newpage
 
@@
 
-The widely accepted powerstroke model was best exhibted within the mechanochemical cycle introduced by Cianfrocco et al.
-\cite{Cianfrocco2015mechanism}.
-A summary of the eight step cycle is shown below in Figure (\ref{fig:MechanochemicalCycle}).
+Experimentalists Cianfrocco \textit{et al.} introduced dynein's mechanochemical cycle, which best exhibits the powerstroke model.
+A summary of the eight-step cycle is shown below in Figure (\ref{fig:MechanochemicalCycle}).
 
@@
 
-Here, affinity refers to the tendency and strength of the domain binding to the microtubule - high affinity being a secure attachment to the microtubule, while low affinity is more relaxed.
+In this paper, affinity refers to the tendency and strength of the domain binding to the microtubule - high affinity being a secure attachment to the microtubule, while low affinity is more relaxed.
 The cycle utilizes the conformational transitions between high and low affinity to explain dynein's unbinding and rebinding process.
@@
 
-Although the mechanochemical cycle provides a reasonable model for dynein's step and illustrates the motion between the domains, the model still generalizes the dependence on the configuration of the entire dynein (not just one motor) before the step and fails to analyze different geometric factors that can alter the conformations.
+The mechanochemical cycle provides a reasonable model for dynein's step and illustrates the motion between the domains.
+However, the model still generalizes the dependence on the configuration of the entire dynein (not just one motor) before the step and fails to analyze different geometric factors that can alter the conformations.
 
@@
 
-Experimental research investigates the correlations within dynein's step and how different parameters may affect the pattern.
-These consist of the angle dependency during the stretching of the linker, the effect of the initial domain distance before the step, the ATP concentration for hydrolysis, etc.
-However, due to dynein's small scale, experiment often disagrees with one another and differ depending on the various measuring techniques.
+Experimental research investigates the correlations within dynein's step and how different parameters may affect dynein's behavior.
+Some experiments investigate the angle dependency during the stretching of the linker \cite{can2019directionality}, while others test ATP concentrations for hydrolysis \cite{manna2020mechanistic, elshenawy2020lis1}.
+Recent studies concerning dynein's stepping pattern further support dynein's stochastic behavior when the motors are close together but suggests coordinated stepping when the distance increases \cite{qiu2012dynein, Dewitt2012}.
+However, dynein's small scale makes experiments difficult to replicate, where their results may differ depending on various measuring techniques.
 
@@
 
-We want to further investigate Yildiz's unique stepping correlation by creating a compuational simulation of dynein and analyze the specific conditions that are required to replicate their results.
+We want to further investigate Yildiz's unique stepping correlation by creating a computational simulation of dynein and analyze the specific conditions that are required to replicate their results.
 Currently, other simulations that model dynein's step exist, but all of them are used to investigate the ATP hydrolysis mechanism during the mechanochemical cycle.
@@
 Instead of making assumptions about the physical mechanics of the step, Roundy's model neglects the chemistry of the ATP exchange and assumes the energy transfer from ATP is incorporated within the binding processes.
-Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experienced Brownian motion to mimic stochastic movement \cite{Capek2017, }.
+Researchers John Waczak and Elliott Capek successfully incorporated this model under an angle-dependent Brownian dynamics simulation, where each domain experienced Brownian motion to mimic stochastic movement.
 They were able to track dynein's precise movement along a walk and compare their stepping results to experiment.
@@
 We intend to use this model to reproduce experimental measures and help verify existing understandings concerning the properties of dynein’s stepping mechanism.
-More specifically, we want reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.
+More specifically, we want to reproduce Yildiz's unique findings and investigate the stepping dependence on the interhead separation.
 

### 2021-05-07 papers/jin-thesis/Chapters/2Theory.tex
Finished thesis! kind of...

@@
 Since our goal is to investigate dynein's interhead coordination during its forward directed stepping, we decided to model dynein as a two-dimensional system of circular domains held together by massless rigid rods.
-These cirular domains embody the two binding domains, two motor domains, and one tail domain, where each domain act as independent angular springs with their own spring constants.
+These circular domains embody the two binding domains, two motor domains, and one tail domain, where each domain act as independent angular springs with their own spring constants.
 A labeled picture of the model is shown below in Figure (\ref{fig:model}).
@@
 The reasoning for this will be later discussed in Section \ref{sec:BrownianDynamics} when we introduce Brownian dynamics.
-Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains abitrarily 10\% larger than experimental measurements.
+Although the stalk and linker of real dynein definitely have mass, we counteract the loss of interactions the rods experience with the environment by increasing the radii of the domains arbitrarily 10\% larger than experimental measurements.
 
@@
 According to the mechanochemical cycle (Figure \ref{fig:MechanochemicalCycle}), dynein can be in eight states over the course of a single step.
-However, many of these states possess similar conformations, where the dynein either has low affinity (unbinded domain diffusing above microtubule) or high affinity.
+However, many of these states possess similar conformations, where the dynein either has low affinity (unbound binding domain diffusing above microtubule) or high affinity.
 Since we assume simple ATP exchange and that the two physical states are during binding and unbinding, we categorize the cycle into two main conformations: the pre-stroke one-bound state and the post-stroke both-bound state.
@@
 Differentiating the two conveniently biases the conformational changes by defining different equilibrium angles for both states.
-Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both-bound state is identical for both binding and motor domain pairs, i.e.
+Since dynein is symmetric for each heavy chain leg, the equilibrium angles for the both-bound state are identical for both binding and motor domain pairs, i.e.
 $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains.
 However, in the one-bound state, the unbound leg exhibits the powerstroke and kicks out.
-Therefore, the equilibrium angles for the motor domains differ in order to bias the unbound leg to straighten and perform the powerstroke.
+Therefore, the equilibrium angles for the motor domains differs to bias the unbound leg and perform the powerstroke.
 This straightening mechanic resembles the linker being primed before allowing the binding domain to rebind.
@@
 \end{equation}
-This equation specifies the drag term by a given radius $a$ and liquid viscocity $\eta$.
+This equation specifies the drag term by a given radius $a$ and liquid viscosity $\eta$.
 
 A second force is the random force inspiring the Brownian motion.
-\textbf{F}$_{rand}$ describes the random interactions between the domains and the solvent paticles.
+\textbf{F}$_{rand}$ describes the random interactions between the domains and the solvent particles.
 \textbf{F}$_{rand}$ is sampled from a zero-centered Gaussian with variance
@@
 
-The final force is the tension force, \textbf{F}$_T$, between the domains \textit{via} their connecting rods. Incorporting all these forces, we produce the \textit{Langevin Equation}:
+The final force is the tension force, \textbf{F}$_T$, between the domains \textit{via} their connecting rods. Incorporating all these forces, we produce the \textit{Langevin Equation}:
 \begin{equation}
@@
 \subsection{Monte Carlo for Both-Bound}
-Since dynein spends most of its stepping time in the both-bound state, we safely assume dynein equilibriates before unbinding.
+Since dynein spends most of its stepping time in the both-bound state, we safely assume dynein equilibrates before unbinding.
 This allows us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system.
-Typically, Monte Carlo methods analyze equilibrium theromodynamics of fluids, where a system of atoms possess many different microstates \cite{lim2007vorticity}.
+Typically, Monte Carlo methods analyze equilibrium thermodynamics of fluids, where a system of atoms possess many different microstates \cite{lim2007vorticity}.
 For this model, dynein is the system and the many possible both-bound configurations are the ``microstates." However, unlike the more commonly known Markov Chain Monte Carlo, each both-bound configuration is independent and can generate different total energy values.
-This produces a large ensemble of of both-bound configurations, which we sample to create stepping statistics.
+This produces a large ensemble of both-bound configurations, which we sample to create stepping statistics.
 Eventually, these statistics will reduce to probability distributions for important variables.
 
-With the assumption of thermodyamic equilibrium during the both-bound state, we use a Boltzmann distribution to define the probability of a configuration and calculate the relative unbinding probability with a proportionality expression.
+With the assumption of thermodynamic equilibrium during the both-bound state, we use a Boltzmann distribution to define the probability of a configuration and calculate the relative unbinding probability with a proportionality expression.
 That is,
@@
 In order to guarantee an accurate thermodynamic ensemble of both-bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well.
-The thermodynamic ensemble then generates an ensemble of steps that can eventually produce smooth statictics.
+The thermodynamic ensemble then generates an ensemble of steps that can eventually produce smooth statistics.
 With the partition function defined in Equation (\ref{eqn:partition}), we also define ensemble averages for both-bound statistics, such as the average unbinding rates, unbinding probability, and both-bound time.

### 2021-05-07 papers/jin-thesis/Chapters/3Methods.tex
Finished thesis! kind of...

@@
 
-We match model paramters concerning dynein's geometry based on experiment by analyzing electron microscopy pictures of dynein.
+We match model parameters concerning dynein's geometry based on experiment by analyzing electron microscopy pictures of dynein.
 These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both-bound and one-bound states.
@@
 	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
-	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both-bound dynein with model domains to identify post-stroke equilbrium angles.
+	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both-bound dynein with model domains to identify post-stroke equilibrium angles.
 The arrow indicates 15 nm \cite{Burgess2003}.
-\textit{Right:} Cryo-electron tomograph of one-bound dynein for pre-stroke equilbrium angles \cite{grotjahn2018cryo}.}
+\textit{Right:} Cryo-electron tomograph of one-bound dynein for pre-stroke equilibrium angles \cite{grotjahn2018cryo}.}
 	\label{fig:ParamsPics}
@@
 Despite simulating many combinations of parameters, the number of free variables still produce many degrees of freedom.
-This makes it difficult to test the entire parameter space and truly invesitage the relationships between different sets of parameters.
-We approach this problem by individually attributing the parameters to a specific data set from exerpiment.
+This makes it difficult to test the entire parameter space and truly investigate the relationships between different sets of parameters.
+We approach this problem by individually attributing the parameters to a specific data set from experiment.
 For instance, the exponential unbinding constant, $C$, is fitted specifically to Figure (\ref{fig:trailingbias}).
@@
 This limits the probability of landing at a final position to be a function of $L$.
-However, we can not calculate the step length for a trailing or leading step with an unsigned distance.
+However, we cannot calculate the step length for a trailing or leading step with an unsigned distance.
 This promotes the new naming scheme of using initial and final displacement, $x_i$ and $x_f$, when identifying the distances between the binding domains before and after the step.
@@
 Since we want the probability of absolute differences, we can neglect the distinction between `initial' and `final' and calculate an equilibrium distribution of distances, $p(L)$.
-To do so, we use a reccurence relation, where we define an initial $p^0(L)$ that is not in equilibrium and multiply it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
+To do so, we use a recurrence relation, where we define an initial $p^0(L)$ that is not in equilibrium and multiply it by the conditional probability distribution for arbitrary $L$'s, $p(L'|L)$, until it reaches equilibrium.
 That is,
@@
 This process can be thought of as a large row of dyneins all starting with the probability of an initial distance $p^0(L)$.
-Once they all take a step, their probability of having another distance $L'$ is $p(L'|L)p(L)$, and after a significant number of $n$ steps, the probability of having a distance $L$ would be the same for all the dyneins, thus being an equilibirum distribution of $L$.
+Once they all take a step, their probability of having another distance $L'$ is $p(L'|L)p(L)$, and after a significant number of $n$ steps, the probability of having a distance $L$ would be the same for all the dyneins, thus being an equilibrium distribution of $L$.
 To solve for $p(L'|L)$, we can use the previous probability distributions $p(x_f|x_i)$ and $p(x_i|L_i)$ to convert these probabilities into distances, as shown below:

### 2021-05-07 papers/jin-thesis/Chapters/4Results.tex
Finished thesis! kind of...

@@
 \section{Optimized Parameters}\label{sec:Params}
-The set of parameters that best fit Yildiz's observed stepping correlation is shown below in Table (\ref{tab:params}).
+The set of parameters that best fit Yildiz's observed stepping correlation is shown below.
 
@@
     $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
-    $k_a$ & $\kstk s^{-1}$&  & \\
-    $k_b$ & $\kb s^{-1}$&  & \\
-    $k_{ub}$ & $\kub s^{-1}$ & & \\
+    $k_a$ & $\kstk$  $s^{-1}$ &  & \\
+    $k_b$ & $\kb$  nm $s^{-1}$ &  & \\
+    $\epsilon$ &  $\MTbindingdistance$ nm & & \\
+    $k_{ub}$ & $\kub$ $s^{-1}$ & & \\
     $C$ & $\cexp$ & & \\
-    $L_s$ & $\ls nm$ & $21nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
-    $L_t$ & $\lt nm$ & $23nm$ & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
+    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
+    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
     $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
@@
     $\theta_t$ & $\eqt$ &  & \\
-    $R_t$ & $\radiust nm$ & $4nm$ & \cite{Burgess2003}\\
-    $R_m$ & $\radiusm nm$ & $5.5nm$ & \cite{Burgess2003}\\
-    $R_b$ & $\radiusb nm$ & $1.25nm$ & \cite{Burgess2003}\\
+    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
+    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
+    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
     \hline
   \end{tabular}
-  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:BBPlots}).}
+  \caption{Optimized model parameters for Figures (\ref{fig:DataFitYildiz}-\ref{fig:BBPlots}).
+Binding rates ($k_a$, $k_{ub}$) have dimensions probability per time, while $k_b$ has dimensions probability of vertical height per time, depending on the binding distance threshold, $\epsilon$.}
   \label{tab:params}
@@
 
-After many trials, this combination of parameters best demonstrated the interstep correlation observed from Yildiz's experiment, while still preserving dynein's forward directionality.
+After many trials, this combination of parameters best demonstrated the interhead correlation observed from Yildiz's experiment, while still preserving dynein's forward directionality.
 The two main stepping statistics used to compare with experiment are shown below, where the affinity transition rate ($k_a$) and binding rate ($k_b$) heavily influenced these statistics.
@@
 \textit{Bottom:} One dimensional probability density of step length (step length = $x_f-x_i$).
-Model compared with experimental figures from \citep{Dewitt2012}.}
+Model compared with experimental figure 3A from \citep{Dewitt2012}.}
 	\label{fig:DataFitYildiz}
@@
 However, experiment was unable to detect 0 nm steps.
-This was shown from the dip in Experiment Fig 3A, where the small density at 0 nm were lateral steps in the off-axis.
-Figure (\ref{fig:DataFitYildiz}) suggests that dynein can still achieve forward directed motion from favoring positive steps rather than negative ones, but prefers short stuttered steps with fast one-bound times.
+This was shown from the dip in the experiment's distribution, where the small density at 0 nm were lateral steps in the off-axis.
+Figure (\ref{fig:DataFitYildiz}) suggests that dynein can still achieve forward directed motion from favoring positive steps rather than negative ones, but prefers short, stuttered steps with fast one-bound times.
 A distribution of said one-bound times is shown below in Figure (\ref{fig:OBtime})
@@
 \end{figure}
-
+\newpage
 As the distribution of times in Figure (\ref{fig:OBtime}) indicates, the model dynein frequently spends $<$ 0.1 $\mu s$ in the one-bound state, with the dynein most likely to rebind immediately after the affinity transitions.
@@
 	\centering
-	\includegraphics[width=15.5cm, height = 6cm]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=15.5cm, height = 6.8cm]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
 	\includegraphics[width=15cm, height = 10cm]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Fitting Bothbound Parameters]{\textbf{Fitting Bothbound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
+	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
 the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
@@
 \end{figure}
+\newpage
 
@@
 
-Based on the resemblence with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein.
+Based on the resemblance with experimental observations, we are fairly confident with the model's ability to replicate the stepping patterns of real dynein.
 In our spring model, we assumed each domain to act as springs to influence the powerstroke.
@@
 That is, $c_b=0$ while $c_m=c_t=1$ from Table (\ref{tab:params}).
-This adjustment displays the flexibility within the model and the potential to fine-tune paramters to fit different sets of data.
+This adjustment displays the flexibility within the model and the potential to fine-tune parameters to fit different sets of data.
 
@@
 	\caption[Limiting Case]{\textbf{Limiting Case for Instant Rebinding.} Each plot closely resembled the plots shown before but with the limiting case of $k_a\gg k_b$.
-The steps exhibited instantaneous rebinding, where the lifted domain landed at the same position immediately after unbinding off of the microtubule ($x_f\approx x_i$).
+The steps exhibited instantaneous rebinding, where the lifted domain landed at the same position immediately after unbinding off the microtubule ($x_f\approx x_i$).
 The large majority of one-bound times were recorded within the first time-step where $dt<5$ ns.}
@@
 If we ignored the transition period between low and high affinity, the model dynein would immediately rebind with an average one-bound time of 5 ns.
-The step length plot in Figure (\ref{fig:DataFitYildiz99}) also displayed a lack of directionality when stepping.
+The step length plot in Figure (\ref{fig:DataFitYildiz99}) also displayed a lower sense of directionality when stepping with less large positive steps.
 
-We avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in Experiment Fig 3A (we classifed ``large'' steps as $> 40$ nm).
+We avoided instant rebinding by also prioritizing the large positive step lengths Yildiz observed in his step length plot shown in Figure (\ref{fig:DataFitYildiz}) (we classified ``large'' steps as $> 40$ nm).
 By lowering the binding and affinity transition rates,  the model dynein recorded larger step lengths better and achieved processive motion.

### 2021-05-07 papers/jin-thesis/Chapters/5Conclusion.tex
Finished thesis! kind of...

@@
 With various degrees of freedom controlling the properties of a step, the model was able to flexibly optimize according to experimental results and provide further conclusions for correlated stepping.
-More specifically, we replicated experimentalist Ahmet Yildiz's unique result of an observered stepping correlation between the initial domain separation and final displacement with a 16.5\% error.
+More specifically, we replicated experimentalist Ahmet Yildiz's unique stepping correlation between the initial and final displacement with a 16.5\% error.
 
@@
 
-If time provides, the flexbility of the model allows for a more sufficient optimization process that can minimize the parameter space when replicating experiment.
-Further work can apply this to other experimental hypotheses regarding dynein's stepping pattern and provide further support for new observations.
+If time provides, the flexibility of the model allows for a more sufficient optimization process that can minimize the parameter space when replicating experiment.
+Further work can apply this to other experimental hypotheses regarding dynein's stepping pattern and provide support for new observations.
 As mentioned earlier, most simulations model the ATP transitions during the mechanochemical cycle, while this model focuses on the dynamics within the step.
-Thus, a combined model that incorporates both features may describe natural dynein perfectly and bring us one step closer to engineering a reliable prevention for cell failure.
+Thus, a combined model that incorporates both features may describe natural dynein perfectly and bring us one step closer to preventing neurodegeneration.

### 2021-05-07 papers/jin-thesis/main.tex
Finished thesis! kind of...

@@
 \usepackage{geometry}
-\geometry{margin=1in}
+\geometry{margin=1in, top=0.75in}
 \usepackage{fancyhdr}
@@
 \title{
-	\Large{Simulating Dynein: A Monte Carlo Improvement to a Dynamical Model of the Dynein Motor Protein}\vspace{1em}\\
+	\Large{Simulating the Dynein Motor Protein: A Monte Carlo Approach to Achieve Coordinated Stepping}\vspace{1em}\\
 	\large{by} \\ 
@@
 	\normalsize{B.S. in Physics}\vspace{1.5 em}\\
-	\normalsize{Draft submitted \today}\\
+	\normalsize{Submitted \today}\\
 
@@
 A failed delivery can cause severe damage to the cell’s functionality and lead to neurological diseases.
-Despite dynein's rich history in cellular research, the mechanisms of its motility remains poorly understood due to its large size, flexible structure, and stochastic stepping.
-Unlike its motor protein siblings which posses uniform stepping, dynein's step is unpredictable and can vary in size and direction.
+Despite dynein's rich history in cellular research, the mechanism of its motility remains poorly understood due to its large size, flexible structure, and stochastic stepping.
+Unlike its motor protein siblings which possess uniform stepping, dynein's step is unpredictable and can vary in size and direction.
 However, experimentalist Ahmet Yildiz and colleagues observed a stepping dependence within the interhead separation, indicating a possible correlation during dynein's step.
@@
 After optimizing parameters sets, the model achieved Yildiz's stepping correlation only when the binding rates were significantly large.
-Our simulations indicate that dynein must take many short ($\langle t \rangle < 0.1 \mu s$) and immediate steps, with step lengths close to 0 nm, in order to reproduce a stepping dependence within the interhead domain separation.
-These results demonstrates the model's ability to capture dynamic properties from experimental observations and provide further support for other experimental hypotheses regarding dynein's step.
+Our simulations indicate that dynein must take many short ($\langle t \rangle < 0.1 \mu s$) and immediate steps, with step lengths close to 0 nm, to reproduce a stepping dependence within the interhead domain separation.
+These results demonstrate the model's ability to capture dynamic properties from experimental observations and provide further support for other experimental hypotheses regarding dynein's step.
 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{references}

### 2021-05-23 papers/paper/paper.tex

--- 2020-11-29 papers/paper/paper.tex
@@
 
-\section*{TODO August 2020}
-\begin{enumerate}
-  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
-  \item Articulate data we fit to
-  \begin{enumerate}
-    \item Velocity -> unbinding rate
-    \item Ratio of leading vs trailing steps -> exponential parameter
-    \item Average step length -> other parameters
-    \item Yildiz weird slope -> sticky rate + binding rate
-    \item Avoid instant rebinds -> sticky rate
-    \item Time to kick from MD??
-    \item efficiency (affects instant rebind)
-  \end{enumerate}
-  \item Do the fit (requires 1 above)
-  \item Could have a fixed binding immunity time rather than sticky rate
-  \paragraph{Advantages of immunity time}
-  \begin{enumerate}
-    \item Might accurately reflect a diffusive escape from an energy well
-  \end{enumerate}
-  \paragraph{Advantages of sticky rate}
-  \begin{enumerate}
-    \item Accurately reflects the dynamics of a chemical process
-  \end{enumerate}
-\end{enumerate}
-
-\section*{Plots from MC}
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
-\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:final_disp_prob}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
-\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:step_length_prob}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
-\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
-\label{fig:step_length_prob_den}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
-\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
-\label{fig:prob_lagging}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
-\caption{\textbf{Onebounnd Time} Dimentions: $s$.}
-\label{fig:ob_time}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563}
-\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
-\label{fig:bothbound_time}
-\end{figure}
+%\section*{TODO August 2020}
+%\begin{enumerate}
+%  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
+%  \item Articulate data we fit to
+%  \begin{enumerate}
+%    \item Velocity -> unbinding rate
+%    \item Ratio of leading vs trailing steps -> exponential parameter
+%    \item Average step length -> other parameters
+%    \item Yildiz weird slope -> sticky rate + binding rate
+%    \item Avoid instant rebinds -> sticky rate
+%    \item Time to kick from MD??
+%    \item efficiency (affects instant rebind)
+%  \end{enumerate}
+%  \item Do the fit (requires 1 above)
+%  \item Could have a fixed binding immunity time rather than sticky rate
+%  \paragraph{Advantages of immunity time}
+%  \begin{enumerate}
+%    \item Might accurately reflect a diffusive escape from an energy well
+%  \end{enumerate}
+%  \paragraph{Advantages of sticky rate}
+%  \begin{enumerate}
+%    \item Accurately reflects the dynamics of a chemical process
+%  \end{enumerate}
+%\end{enumerate}
 
@@
 
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+\label{fig:final_disp_prob}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+\label{fig:final_disp_prob}
+\end{figure}
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=\linewidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+\label{fig:final_disp_prob}
+\end{figure}
+
+\begin{figure}[tbhp]
+	\centering
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
+the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
+\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
+Experimental data from \cite{Dewitt2012}.}
+	\label{fig:BBPlots}
+\end{figure}
+
 Motion equations were derived for the pre-stroke and post-stroke states of the model.

### 2021-05-25 papers/paper/paper.tex
Presentation and paper work

@@
     $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
-    $k_b$ & $\kb s^{-1}$&  & \\
-    $k_{ub}$ & $\kub s^{-1}$ & & \\
-    $L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
-    $L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
-    $c$ & $\cexp$ & & \\
+    $k_a$ & $\kstk$  $s^{-1}$ &  & \\
+    $k_b$ & $\kb$  nm $s^{-1}$ &  & \\
+    $\epsilon$ &  $\MTbindingdistance$ nm & & \\
+    $k_{ub}$ & $\kub$ $s^{-1}$ & & \\
+    $C$ & $\cexp$ & & \\
+    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
+    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
     $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
-    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
-    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
+    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
+    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
     $\theta_t$ & $\eqt$ &  & \\
-    $R_t$ & $\radiust$ & 8nm & \cite{burgess-paper}\\
-    $R_m$ & $\radiusm$ & 11nm & \cite{burgess-paper}\\
-    $R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\
+    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
+    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
+    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
     \hline
@@
 Parameters used for all simulations unless otherwise noted}
-  \label{tab:params}
+  \label{table:params}
 \end{table}
@@
 \section{Model}
-This dynein model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex while remaining mathematically simple.
+This model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex, while remaining mathematically simple.
 The structural features of dynein are captured through a two-dimensional geometric model of circular domains connected by rigid rods, shown in Figure \ref{fig:model}.
-The dynamics of dynein are captured by imposing both equilibrium and Brownian forces on each circular domain of the model.
-The chemical properties of dynein are captured by sporadically transitioning the model between two states: a poststroke state where both binding domains are fixed to the microtubule, and a prestroke state where one foot is free to diffuse, as has been done before \cite{zhaomodel}.
+The dynamics of dynein are simulated by imposing both equilibrium and Brownian forces on each circular domain of the model.
+The chemical properties of dynein are emulated by sporadically transitioning the model between two states: a poststroke state where both binding domains are fixed to the microtubule, and a prestroke state where one foot is free to diffuse.
+This was influenced by similar simulations done before \cite{zhaomodel}.
 The poststroke state is meant to represent dynein after rebinding free MTBD and undergoing the motor-MTBD conformational change, but before releasing ADP, according to the Tsygankov scheme \cite{tsygankovscheme}.
@@
 Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the cycle \cite{burgess-paper, burgessknight}.
-In particular, the equilibrium angles governing a motor's tail-motor-MTBD angle change to cause a displacement of the free MTBD towards the MT minus end, producing a forward step.
+In particular, the equilibrium angles governing a tail-motor-MTBD angle change cause a displacement of the free MTBD towards the MT minus end, producing a forward step.
 
@@
 
+\subsection*{Binding}
+Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the prestroke and poststroke states.
+During prestroke, the free MTBD must first release from the MT by transitioning from high to low affinity.
+The affinity transition rate, $k_a$, governs this process.
+Binding can then occur when the prestroke model's unbound foot diffuses near enough the microtubule.
+When within a distance of $\epsilon$, binding occurs at a rate of $k_b$ (Table \ref{table:params}).
+On binding, the prestroke model changes state to a poststroke model while retaining the positions of its domains.
+The previously unbound domain is transported to the microtubule.
+
+\subsection*{Unbinding}
+Unbinding occurs when a poststroke MTBD unbinds from the microtubule.
+This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$.
+To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildizcleary}, we bias forward directionality by influencing a MTBD to unbind based on the separation distance with the opposing MTBD.
+For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $\rho_{ub} = k_{ub}e^{-C\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$, where $C$ is a parameter of the model.
+This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head.
+Values used for parameters $k_{ub}$ and $C$, along with $k_a$ and $k_b$, are shown in Table \ref{table:params}.
+
+The transitions between prestroke and poststroke events in the mechanochemical cycle \cite{cianfrocco} are captured by changing the motor equilibrium angles when a state transition occurs.
+The prestroke state has an unbound motor angle closer to $\pi$ than the prestroke motor\cite{burgess-paper}; thus, on unbinding, the unbound MTBD should experience a restoring force effecting the post-to-pre conformational change.
+On rebinding, the motors transition back to the poststroke equilibrium, producing restoring forces causing the pre-to-post conformational change.
+This shifting of equilibria, coupled with alternating the freedom of the active MTBD, is meant to mimic the coupling of ATPase activity and MTBD affinity in the real dynein motor.
+
 \subsection*{Brownian dynamics}
@@
 
-\subsection*{Binding}
-Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the prestroke and poststroke states.
-Binding can occur when the prestroke model's unbound foot diffuses near enough the microtubule.
-When within a distance of $1 A$, binding occurs at a rate of $k_b$ (Table \ref{table:params}).
-On binding, the prestroke model changes state to a poststroke model while retaining the positions of its domains.
-The previously unbound domain is transported to the microtubule.
-
-\subsection*{Unbinding}
-Unbinding occurs when a poststroke MTBD unbinds from the microtubule.
-This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$.
-To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildizcleary} to allow for interhead communication and bias the motor forward, we use a scheme where an MTBD is more likely to unbind based on its distance behind the other MT, which accords with experiments \cite{yildiz}.
-For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $k_{ub} = k^0_{ub}e^{-c\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$, where $c$ is a parameter of the model.
-This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head.
-Values used for parameters $k^0_{ub}$ and $c$, along with $k_b$, are shown in Table \ref{table:params}.
-
-The transitions between prestroke and poststroke events in the mechanochemical cycle \cite{cianfrocco} are captured by changing the motor equilibrium angles when a state transition occurs.
-The prestroke state has an unbound motor angle closer to $\pi$ than the prestroke motor\cite{burgess-paper}; thus, on unbinding, the unbound MTBD should experience a restoring force effecting the post-to-pre conformational change.
-On rebinding, the motors transition back to the poststroke equilibrium, producing restoring forces causing the pre-to-post conformational change.
-This shifting of equilibria, coupled with alternating the freedom of the active MTBD, meant to mimic the coupling of ATPase activity and MTBD affinity in the real dynein motor.
+\subsection*{Monte Carlo}
+A Monte Carlo algorithm governs the simulation of the step. Starting at
 
 \section*{Fitting $k_b$ and $k_{ub}$}
-To fit the binding and unbinding rate constants $k^0_b$ and $k^0_{ub}$ a simple theoretical model for stepping was used, similar to one previously published \cite{myosindutyratio}.
+To fit the binding and unbinding rate constants $k_b$ and $k_{ub}$ a simple theoretical model for stepping was used, similar to one previously published \cite{myosindutyratio}.
 First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD, that is, that there is no inter-head coordination.
@@
 
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
-\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$.
+%\begin{figure}[tbhp]
+%\centering
+%\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
+%\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$.
 \textit{Middle view:} Cartoon snapshot of model at time indicated by bound binding domain.
@@
 Arrows on top and bottom plots correspond to respective snapshot times.}
-\label{fig:trajectory}
-\end{figure}
+%\label{fig:trajectory}
+%\end{figure}
 
@@
 
-\begin{figure}[tbhp]
-  \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
-\caption{\textbf{Stepping dynamics of model.} \textit{Top: } Average position of near and far MTBDs over 5 seconds of simulation and 8 random seeds.
+%\begin{figure}[tbhp]
+%  \centering
+%  \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
+%\caption{\textbf{Stepping dynamics of model.} \textit{Top: } Average position of near and far MTBDs over 5 seconds of simulation and 8 random seeds.
 Trajectory compared with single-motor-labelled cytoplasmic dynein from DeWitt \textit{et.
@@
 al.} stepping trajectory.}
-\label{fig:behavior}
-\end{figure}
+%\label{fig:behavior}
+%\end{figure}
 
@@
 
-\begin{figure}[tbhp]
-  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
-  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_displacement.pdf}
-  \caption{\textbf{Analysis of foot order on unbinding.} \textit{Top: } Heatmap of initial foot position vs length of ensuing step.
+%\begin{figure}[tbhp]
+%  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
+%  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_displacement.pdf}
+%  \caption{\textbf{Analysis of foot order on unbinding.} \textit{Top: } Heatmap of initial foot position vs length of ensuing step.
 Initial displacement defined as position of the stepping MTBD minus the position of the stationary MTBD, before the step takes place.
@@
 al.} cytoplasmic dynein.}
-  \label{fig:tensiongating}
-\end{figure}
+%  \label{fig:tensiongating}
+%\end{figure}
 
@@
 
-\begin{figure}[tbhp]
-  \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
-\caption{\textbf{Impact of force on model velocity.} Model response to force in the $+\hat{x}$ direction applied to tail domain.
+%\begin{figure}[tbhp]
+%  \centering
+%  \includegraphics[width=\linewidth]{../../plots/paper_force_vs_velocity.pdf}
+%\caption{\textbf{Impact of force on model velocity.} Model response to force in the $+\hat{x}$ direction applied to tail domain.
 Velocity calculated using displacement after 2 seconds of simulation at standard parameters.
@@
 al.} \cite{responsetoload}.}
-\label{fig:force}
-\end{figure}
+%\label{fig:force}
+%\end{figure}
 
@@
 
-\begin{figure}[tbhp]
-  \centering
-  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}\\
-  \includegraphics[width=\linewidth]{../../plots/paper_stacked_displacement_histogram.pdf}
-  \caption{\textbf{Analysis of stepping independence.} \textbf{a.)} Heatmap of MTBD displacement before and after a stepping cycle.
+%\begin{figure}[tbhp]
+%  \centering
+%  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}\\
+%  \includegraphics[width=\linewidth]{../../plots/paper_stacked_displacement_histogram.pdf}
+%  \caption{\textbf{Analysis of stepping independence.} \textbf{a.)} Heatmap of MTBD displacement before and after a stepping cycle.
 Displacement defined as the unbinding MTBD's x coordinate minus the stationary MTBD's x coordinate, calculated before and after the step.
@@
 \textbf{b.)} Compound histogram of final displacement for different ranges of initial displacement.}
-\label{fig:independence}
-\end{figure}
+%\label{fig:independence}
+%\end{figure}
 
-\begin{figure}[tbhp]
-  \centering
-  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
-  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
-  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A.
+%\begin{figure}[tbhp]
+%  \centering
+%  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
+%  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
+%  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
+%  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
+%  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
+%  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
+%  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A.
 left: } Schematic of winch model for dynamics during conformation changes associated with right monomer binding.
@@
 All values plotted as mean $\pm$ SD.}
-\label{fig:stroke}
-\end{figure}
+%\label{fig:stroke}
+%\end{figure}
 

### 2021-06-02 papers/paper/paper.tex
changed plt in paper

@@
 
+\begin{figure}[tbhp]
+	\centering
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
+the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
+\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
+Experimental data from \cite{Dewitt2012}.}
+	\label{fig:ProbLagPlot}
+\end{figure}
+
 \subsection*{$k_b$, $k_{stk}$}
 The sticky rate and binding rate were chosen ... based on the Yildiz initial-vs-final displacement slope?
+
+\begin{figure}[tbhp]
+	\centering
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
+the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
+\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
+Experimental data from \cite{Dewitt2012}.}
+	\label{fig:TrajPlot}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
 \caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
@@
 \label{fig:final_disp_prob}
-\end{figure}
-
-\begin{figure}[tbhp]
-	\centering
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
-the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
-\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
-Experimental data from \cite{Dewitt2012}.}
-	\label{fig:BBPlots}
 \end{figure}

### 2021-06-02 papers/paper/paper.tex
comment out binding angle stuff

--- 2021-05-25 papers/paper/paper.tex
@@
     \hline
-    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
+%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
     $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
@@
     $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
-    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
+%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
     $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\

### 2021-06-02 papers/paper/paper.tex
add comments to paper

@@
 \newpage
+
+\davidsays{Main point: earlier models cannot explain the experimentally observed correlation between
+  the initial displacement and step size.
+
+  Introduce experiment first, esp. Yildiz.
+
+  Explain existing models a bit more.  Not many details about each model, but for every model explain what
+  it does and does not explain.
+
+  QUESTION: Do we want to give the geometric argument for a typical final displacement?
+
+  QUESTION: What predictions can we make?
+
+  There should be many very short-distance steps that are not shown in experiment.
+
+  The typical time spent actually taking a step (i.e. one-bound) should be very short.  (Be quantitative.)
+  It's not been measured, and puts a limit on the time spent getting ready to rebind.  Does this mean we
+  want the onebound time histogram?  I think not, but we do want the average value, and maybe median or similar?
+
+  Power stroke model works? Even if the stalk does not do work by exerting torque.  Does that make
+  it a winch model? This will require discussion early and late.
+
+  Future work: add a backwards force to the model.
+}
 
@@
 \includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
-\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.} \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free.
-Angles are measured from the $+\hat{x}$ direction.
-\textit{Right: } Post-stroke model with both MTBDs bound to microtubule.
-MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail.
-Lengths and radii not to scale.}
+\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
+\davidsays{FIXME remove spring on binding domain and fix caption.}
+\textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule
+and the other free. Angles are measured from the $+\hat{x}$ direction.
+\textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD
+angles are relative to $+\hat{x}$ direction, and motor angles are between stalk
+and tail. Lengths and radii not to scale.}
 \label{fig:model}
@@
 \begin{figure}[tbhp]
-\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
-\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
+  \centering
+\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
+% \includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
-\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-stroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state \cite{burgess-paper}.
-Interdomain lengths and radii scaled to micrograph scale bar.
-No microtubule is present, so $\theta_{nb}$ is arbitrary.
-\textit{Right: } Model with angles at pre-stroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}.
-Interdomain lengths and radii scaled to density map.}
+\caption{\textbf{Scale model compared with experimental images.}
+%  \textit{Left:}
+ Model with angles at pre-stroke equilibrium superimposed over
+ axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state
+ \cite{burgess-paper}. Interdomain lengths and radii scaled to micrograph scale
+ bar. % No microtubule is present, so $\theta_{nb}$ is arbitrary.
+%   \textit{Right: }
+%  Model with angles at pre-stroke equilibrium superimposed over density map of
+%  full-length native cytoplasmic dynein with accessory tail proteins (map ID
+%  EMD-7000) \cite{grotjahn}. Interdomain lengths and radii scaled to density
+%  map.
+ }
 \label{fig:micrographs}
@@
 %    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
-    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
-    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
-    $\theta_t$ & $\eqt$ &  & \\
+    $\theta_m^{\mbox{pre}}$ & $\eqmpre^\circ$ &  197$^\circ$ & \cite{Burgess2003}\\
+    $\theta_m^{\mbox{post}}$ & $\eqmpost^\circ$ & 242$^\circ$ & \cite{Burgess2003}\\
+    $\theta_t$ & $\eqt^\circ$ &  & \\
     $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
@@
 
+\davidsays{Maybe we want to discuss right here the likely step sizes for leading and trailing steps
+\emph{if it goes to its equilibrium configuration}.  It's pretty simple and can serve as a ``validation"
+of our model geometry.}
+
 \subsection*{Equilibrium forces}
-The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$.
-The poststroke state has two: $\theta_{nm}$ and $\theta_{fm}$.
-The model is free to vary across all of these degrees of freedom, depending on its state, barring steric interactions with the microtubule.
-These angles describe a planar model which is not capable of transverse motion.
-To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke.
-Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain.
-These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}.
-These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}.
-Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.
+The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm},
+\theta_{um}$ and $\theta_{ub}$. The poststroke state has two: $\theta_{nm}$ and
+$\theta_{fm}$. The model is free to vary across all of these degrees of freedom,
+depending on its state, barring steric interactions with the microtubule. These
+angles describe a planar model which is not capable of transverse motion.  \davidsays{FIXME edit here.} To
+capture the gross dynamics and interdomain oscillations of the protein,
+restoring forces are imposed on each angle about equilibrium angles
+$\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for
+prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke. Each
+domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$
+which exerts a restoring force pushing it back to equilibrium, where $c_b$,
+$c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles
+are taken to be the average angle occupied by the protein in solution, and are
+thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. These
+angles were extracted from axonemal dynein, but structural similarity suggests
+they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}.
+Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke
+state allow for both pre- and post-stroke equilibrium angles to be found
+\cite{burgess-paper}.
 
@@
 \section{Results}
+
+\davidsays{Discuss each figure, and each parameter (how we got it).}
+
+\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.
+
+Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.
+}
+
+\davidsays{Do not add average both-bound time vs. L? This is a measurable prediction if we can't find an experimental
+result.  Otherwise, we can compare with experiment.  Maybe just add a sentence or two}
+
+\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff,
+    and our angles work out.  Report the average step length.}
+
+\davidsays{contour plot. Gave us the binding rate and the affinity time.  
+Very fast binding required (to get slope right) and need affinity time to avoid instantly
+ rebinding.}
+
+ \davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}
+
+ \davidsays{one-bound time plot. Cut?}
 

### 2021-06-08 papers/paper/paper.tex
Paper work

--- 2021-06-02 papers/paper/paper.tex
@@
 \newpage
+
+\davidsays{Discuss each figure, and each parameter (how we got it).}
+
+\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.
+
+Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.}
+
+\davidsays{Do not add average both-bound time vs.
+L?
+This is a measurable prediction if we can't find an experimental result.
+Otherwise, we can compare with experiment.
+Maybe just add a sentence or two}
+
+\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff, and our angles work out.  Report the average step length.}
+
+\davidsays{contour plot. Gave us the binding rate and the affinity time.  
+Very fast binding required (to get slope right) and need affinity time to avoid instantly rebinding.}
+
+\davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}
+
+\davidsays{one-bound time plot. Cut?}
 
@@
 \centering
-\includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
-\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.} \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free.
+\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
+\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
+\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
+\davidsays{FIXME remove spring on binding domain and fix caption.}
+ \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free.
 Angles are measured from the $+\hat{x}$ direction.
@@
 \begin{figure}[tbhp]
-\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
-\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
+\centering
+\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
+%\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
@@
 
+\davidsays{Maybe we want to discuss right here the likely step sizes for leading and trailing steps \emph{if it goes to its equilibrium configuration}.
+It's pretty simple and can serve as a ``validation" of our model geometry.}
+
 \subsection*{Equilibrium forces}
@@
 Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.
+
+\begin{figure}[tbhp]
+\centering
+\includegraphics[width=1\linewidth]{figures/equilibrium.pdf}
+\caption{\textbf{Equilibrium configuration.} Model with stiff springs in equilibrium configurations.
+}
+\label{fig:OBequil}
+\end{figure}
 
@@
 \subsection*{Monte Carlo}
-A Monte Carlo algorithm governs the simulation of the step. Starting at
+A Monte Carlo algorithm governs the simulation of the step.
+We initialize a two-headed bound configuration of dynein by randomly picking domain angles and calculating the total harmonic energy by summing the energies of each domain.
+A probability of unbinding, $P_{ub}$, is then calculated from a Boltzmann distribution, where $P_{ub}\propto e^{-\beta E_{total}}$.
+If dynein unbinds, then the configuration transitions into the one-headed bound state where Brownian dynamics is performed.
+This process is repeated to generate an ensemble of independent configurations which takes a single step and contributes to a large sample of stepping staistics.
+A partition function, $Z=\sum e^{-\beta E{total}}$, can then calculate ensemble averages of unbinding rates and probability.
 
-\section*{Fitting $k_b$ and $k_{ub}$}
-To fit the binding and unbinding rate constants $k_b$ and $k_{ub}$ a simple theoretical model for stepping was used, similar to one previously published \cite{myosindutyratio}.
+%\section*{Fitting $k_b$ and $k_{ub}$}
+%To fit the binding and unbinding rate constants $k_b$ and $k_{ub}$ a simple theoretical model for stepping was used, similar to one previously published \cite{myosindutyratio}.
 First, it is assumed that the unbinding rate of an MTBD does not depend on the binding state of the other MTBD, that is, that there is no inter-head coordination.
@@
 Finally, using the relation $\bar{t}_{step} = \frac{v}{L_{step}}$ for dynein velocity $v$ and expected tail step length $\bar{L}_{step}$, the following equations are found for prestroke and poststroke time in terms of experimental observables of velocity, run time and step length:
-
-  \begin{align}
-    \bar{t}_{ob} &= \frac{\bar{L}^2}{\bar{v}^2\left(\bar{L}/v+\bar{t}_{run}\right)}\\
-    \bar{t}_{bb} &= \frac{\bar{L}\bar{t}_{run}}{v\left(\bar{t}_{run}+\bar{L}/v\right)}
-  \end{align}
-
-  For estimating prestroke and poststroke times from Yildiz \textit{et al}\cite{yildiz}, a velocity of $124 nm/s$ is used.
+%
+%  \begin{align}
+%    \bar{t}_{ob} &= \frac{\bar{L}^2}{\bar{v}^2\left(\bar{L}/v+\bar{t}_{run}\right)}\\
+%    \bar{t}_{bb} &= \frac{\bar{L}\bar{t}_{run}}{v\left(\bar{t}_{run}+\bar{L}/v\right)}
+%  \end{align}
+%
+%  For estimating prestroke and poststroke times from Yildiz \textit{et al}\cite{yildiz}, a velocity of $124 nm/s$ is used.
 A study with a similar velocity is used to estimate $\bar{t}_{run} = 1060 nm / 134 nm / s = 7.9s$ \cite{weihongpaper}.
@@
 
+\section{Results}
+
+\davidsays{Discuss each figure, and each parameter (how we got it).}
+
+\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.
+
+Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.}
+
+\davidsays{Do not add average both-bound time vs.
+L?
+This is a measurable prediction if we can't find an experimental result.
+Otherwise, we can compare with experiment.
+Maybe just add a sentence or two}
+
+\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff, and our angles work out.  Report the average step length.}
+
+\davidsays{contour plot. Gave us the binding rate and the affinity time. Very fast binding required (to get slope right) and need affinity time to avoid instantly rebinding.}
+
+\davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}
+
+\davidsays{one-bound time plot. Cut?}
+
 \section*{Fitting model parameters}
@@
 al} \cite{grotjahn} density map, both motor domains were taken to be in the post-powerstroke state.
-
-\subsection*{$c_b$, $c_m$, $c_t$}
-Spring constants $c_b$, $c_m$ and $c_t$ were fit using the dynein step length distribution from \cite{yildizpaper}.
-Three spring constants were drawn uniformly from range $[0.0, 4.0]$ and a simulation was run for 10s simulation time with $k_b=X$, $k_{ub}=Y$, $k_{stk}=Z$, and other parameters noted in Table \ref{tab:params}.
-One thousand simulations total were run, and the set of spring constants which yielded the lowest root-mean-squared histogram error between the simulation and experimental step length distributions was chosen.
-\textbf{Probably need to rerun this using our final $k_b$, $k_{ub}$ and $k_{stk}$.}
-
-\subsection*{$k_{ub}$}
-The unbinding rate $k_{ub}$ was estimated from velocity data in the Yildiz \textit{et.
-al.} experiment.
-The $k_{ub}$ value which led to an average velocity of 124 nm/s was chosen, as shown in Figure \ref{fig:behavior}.
 
@@
 
-\subsection*{$k_b$, $k_{stk}$}
-The sticky rate and binding rate were chosen ... based on the Yildiz initial-vs-final displacement slope?
+\subsection*{$k_{ub}$}
+The unbinding rate $k_{ub}$ was estimated from velocity data in the Yildiz \textit{et.
+al.} experiment.
+The $k_{ub}$ value which led to an average velocity of 124 nm/s was chosen, as shown in Figure \ref{fig:behavior}.
 
@@
 
-\section{Results}
+\subsection*{$k_b$, $k_{stk}$}
+The sticky rate and binding rate were chosen ... based on the Yildiz initial-vs-final displacement slope?
 
@@
 \includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:final_disp_prob}
-\end{figure}
-
-\begin{figure}[tbhp]
-\centering
 \includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
@@
 
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:final_disp_prob}
-\end{figure}
+\subsection*{$c_b$, $c_m$, $c_t$}
+Spring constants $c_b$, $c_m$ and $c_t$ were fit using the dynein step length distribution from \cite{yildizpaper}.
+Three spring constants were drawn uniformly from range $[0.0, 4.0]$ and a simulation was run for 10s simulation time with $k_b=X$, $k_{ub}=Y$, $k_{stk}=Z$, and other parameters noted in Table \ref{tab:params}.
+One thousand simulations total were run, and the set of spring constants which yielded the lowest root-mean-squared histogram error between the simulation and experimental step length distributions was chosen.
+\textbf{Probably need to rerun this using our final $k_b$, $k_{ub}$ and $k_{stk}$.}
 
-Motion equations were derived for the pre-stroke and post-stroke states of the model.
+%
+%\begin{figure}[tbhp]
+%\centering
+%\includegraphics[width=\linewidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+%\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
+%\label{fig:final_disp_prob}
+%\end{figure}
+
+%%%%% OLD RESULTS SECTION: %%%%%%
+%Motion equations were derived for the pre-stroke and post-stroke states of the model.
 The model was simulated by starting in the equilibrium post-stroke position and using Euler's method to time-evolve the model, using a timestep of 1e-10 \textit{s}.
@@
 Each simulation was forward directed, took both forward and backward steps, and displayed stepping dynamics similar to that seen in experiment.
-
-As seen in Figure \ref{fig:trajectory}, the model is highly variant in trajectory, but biased to moving in the $+\hat{x}$ direction, corresponding to the microtubule minus-end.
+%
+%As seen in Figure \ref{fig:trajectory}, the model is highly variant in trajectory, but biased to moving in the $+\hat{x}$ direction, corresponding to the microtubule minus-end.
 When unbound the free MTBD diffuses both parallel and perpendicular to the microtubule, reaching up to 50 \textit{nm} above the track.
@@
 
-The model was then compared to TIRF studies of dynein stepping in DeWitt \textit{et.
+%The model was then compared to TIRF studies of dynein stepping in DeWitt \textit{et.
 al.} \cite{yildizpaper}.
@@
 %\end{figure}
-
-The effect of force on the model was then assessed by applying an artificial force on the tail domain of the model in the $+\hat{x}$ direction.
+%
+%The effect of force on the model was then assessed by applying an artificial force on the tail domain of the model in the $+\hat{x}$ direction.
 The results of this study are shown in Figure \ref{fig:force}.
@@
 
-The independence of dynein steps is then studied in Figure \ref{fig:independence}.
+%The independence of dynein steps is then studied in Figure \ref{fig:independence}.
 Whether dynein works like a Markovian process, where each step is a history-free, is an interesting question.
@@
 
-We then examined how the model took its forward steps.
+%%%%%%%%%%%%%% DISCUSSION ABOUT MODELS: %%%%%%%%%%
+%We then examined how the model took its forward steps.
 Two existing theories for motion generation are depicted in Figure \ref{fig:stroke}.a.
@@
 Arrows indicate these predictions in Figure \ref{fig:stroke}.a.
-
-The average change of motor angles and positions during the prestroke-to-poststroke transition is shown in subfigures \ref{fig:stroke}.b-e.
+%
+%The average change of motor angles and positions during the prestroke-to-poststroke transition is shown in subfigures \ref{fig:stroke}.b-e.
 Only positive steps were used for clarity.

### 2021-06-08 scripts/make_mc_plots.py

@@ -161,9 +161,11 @@ def get_bothbound_data(args, bothbound_data_file):
     # bb_rate_trailing = mc_bb_data['rate_trailing']*params.for_simulation['k_ub']
     bb_P_leading = bb_rate_leading/(bb_rate_leading+bb_rate_trailing)
     bb_P_trailing = bb_rate_trailing/(bb_rate_leading+bb_rate_trailing)
+    bb_lt = 1/bb_rate_leading
+    bb_tt = 1/bb_rate_trailing
     bb_avg_t = 1/(bb_rate_leading+bb_rate_trailing)
 
-    return bb_L, bb_P_leading, bb_P_trailing, bb_rate_trailing+bb_rate_leading, bb_avg_t
+    return bb_L, bb_P_leading, bb_P_trailing, bb_rate_trailing+bb_rate_leading, bb_avg_t, bb_lt, bb_tt
 
 
 def make_bins_and_edges(initial_disp):
@@ -612,7 +614,7 @@ def make_ob_time_plot(args, plotpath, time_hists, avg_affinity_time, **_):
                     plotpath+u+'ob_time_probability_density_'+params_string+'.pdf')
 
 
-def make_bothbound_plots(args, plotpath, bb_L, bb_P_trailing, bb_avg_t, **_):
+def make_bothbound_plots(args, plotpath, bb_L, bb_P_trailing, bb_avg_t, bb_lt, bb_tt, **_):
     # Bothbound PLOTS
     # Prob Lagging vs Initial L plot
     plt.figure('Prob lagging vs init L', figsize=(9, 4))
@@ -647,6 +649,30 @@ def make_bothbound_plots(args, plotpath, bb_L, bb_P_trailing, bb_avg_t, **_):
     plt.gca().spines['top'].set_visible(False)
     # plt.title('C = {}'.format(args.C))
     plt.savefig(plotpath+'bb_time_{}.pdf'.format(args.C))
+
+    # # plt.figure('BB time plot')
+    # plt.plot(bb_L, bb_lt, color='red')
+    # plt.xlabel('initial L (nm)')
+    # plt.ylabel('Average time (s)')
+    # plt.xlim(0)
+    # # plt.ylim(0, 0.3)
+    # plt.legend()
+    # plt.gca().spines['right'].set_visible(False)
+    # plt.gca().spines['top'].set_visible(False)
+    # # plt.title('C = {}'.format(args.C))
+    # plt.savefig(plotpath+'bb_time_{}.pdf'.format(args.C))
+    #
[…]

### 2021-06-09 papers/paper/paper.tex
Paper work

@@
 \subsection*{$L_t$, $L_s$, $R_b$, $R_m$, $R_s$, $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$}
-Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}.
+Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\theta_{m}^{pre}$, $\theta_{b}^{post}$, $\theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}.
 In the class average image from Burgess \textit{et.
@@
 
-\subsection*{$c$}
-The exponential unbinding parameter $c$ was estimated using the likelihood of leading/lagging head unbinding vs interhead separation data provided in DeWitt \textit{et.
+\subsection*{$C$}
+The exponential unbinding parameter $C$ was estimated using the likelihood of leading/lagging head unbinding vs interhead separation data provided in DeWitt \textit{et.
 al.} \cite{dewitt}.
-The value of $c$ was chosen which led to the lowest root-mean-squared error in P(lagging step) vs interhead separation between the experiment and the model, as shown in Figure \ref{fig:tensiongating}.
-All other parameters were held at the values in Table \ref{tab:params}.
+The value of $c$ was chosen which led to the lowest root-mean-squared error in P(lagging step) vs interhead separation between the experiment and the model, as shown in Figure \ref{fig:ProbLagPlot}.
+All other parameters were held at the values in Table \ref{table:params}.
 
@@
 	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
-	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
-the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
-\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
-Experimental data from \cite{Dewitt2012}.}
+	\caption[Lagging preferred steps]{\textbf{Lagging preferred steps.} Likelihood of a trailing step vs.
+the initial binding domain distance ($P_{trail.}(L)$.
+Exponential unbinding parameter, $C$, fitted with \cite{Dewitt2012}.}
 	\label{fig:ProbLagPlot}
@@
 \subsection*{$k_{ub}$}
-The unbinding rate $k_{ub}$ was estimated from velocity data in the Yildiz \textit{et.
+The unbinding rate $k_{ub}$ was estimated from stepping trace data in the Yildiz \textit{et.
 al.} experiment.
-The $k_{ub}$ value which led to an average velocity of 124 nm/s was chosen, as shown in Figure \ref{fig:behavior}.
+The $k_{ub}$ value which led to an average velocity of 26 nm/s was chosen, as shown in Figure \ref{fig:TrajPlot}.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Stepping trace of head labeled dynein]{\textbf{Stepping trace of head labeled dynein.} Trajectory of MTBD over 24 seconds of walking.
+Red and blue labeled heads shows independence from each other during processive walking.
+Experimentalal trace from \cite{Dewitt2012} offset by 120 nm to display comparison.
+Average velocity of 26 nm/s for both traces.}
+	\label{fig:TrajPlot}
+\end{figure}
+
+\newpage
+
+\subsection*{$k_b$, $k_{a}$}
+The binding and affinity rates directly influenced the onebond stepping statistics shown in Figure \ref{fig:SteppingPlots}.
+The binding rate controlled the tendency for immediate steps.
+The affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps.
+This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein prefered steps within 8 nm.
 
@@
 \centering
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs.
-the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})).
-\textit{Bottom: }Trajectory of binding domains over 24 seconds of walking.
-Experimental data from \cite{Dewitt2012}.}
-	\label{fig:TrajPlot}
+\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\caption[Stepping statistics of model]{\textbf{Stepping statistics of model.} \textit{Top: } Heatmap of initial foot displacement vs.
+step length.
+Initial displacement defined as position of the stepping MTBD minus the position of the stationary MTBD, before the step takes place.
+Step length defined as final displacement minus initial displacement.
+Linear regression calculated in orange, compared with Yildiz's linear regression plotted in red.
+Contours of 90\%, 50\%, 25\%, and 5\% displayed as white lines.
+\textit{Bottom: } Probability density of model step sizes plotted against Yildiz's distribution of step sizes.
+}
+\label{fig:SteppingPlots}
 \end{figure}
 
-\subsection*{$k_b$, $k_{stk}$}
-The sticky rate and binding rate were chosen ... based on the Yildiz initial-vs-final displacement slope?
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-\includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
-\label{fig:final_disp_prob}
-\end{figure}
+\newpage
 

### 2021-07-04 papers/paper/paper.tex
Updated exp unbinding plot
Made new figures for paper, added wording and content

@@
 \centering
-\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
-\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
+%\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
+%\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
+\includegraphics[width=1\linewidth]{figures/equilibrium-positions-final.pdf}
 \caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
@@
 Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.
-
-\begin{figure}[tbhp]
-\centering
-\includegraphics[width=1\linewidth]{figures/equilibrium.pdf}
-\caption{\textbf{Equilibrium configuration.} Model with stiff springs in equilibrium configurations.
-}
-\label{fig:OBequil}
-\end{figure}
 
@@
 
-\subsection*{$L_t$, $L_s$, $R_b$, $R_m$, $R_s$, $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$}
-Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\theta_{m}^{pre}$, $\theta_{b}^{post}$, $\theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}.
+The model's simplistic nature allowed flexible optimization for each parameter in order to most accurately portray stepping results from experiment.
+We investigated this parameter space by associating each stepping parameter to a property of dynein's step observed from Yildiz's experiment.
+Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns unbound times.
+The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters.
+Consequently, dynein fails to equilibrate during the stepping motion and quickly rebinds shortly after unbinding.
+
+We first estimated structural parameters $L_t$, $L_s$, $R_b$, $R_m$, $R_s$, and equilibrium angles $\theta_{m}^{pre}$, $\theta_{m}^{post}$, and $\theta_{t}$ from cryo-electron microscopy class averages and density maps of cytoplasmic and axonoemal dynein, shown in Figure \ref{fig:micrographs}.
+We defined the tail and motor equilibrium angles from Burgess \textit{et al.
+} class average image, where the left stalk's motor was in the apo post-powerstroke state and right stalk's motor was in the ADP-bound apo pre-powerstroke state.
+
+%Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\theta_{m}^{pre}$, $\theta_{b}^{post}$, $\theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}.
 In the class average image from Burgess \textit{et.
@@
 
-\subsection*{$C$}
-The exponential unbinding parameter $C$ was estimated using the likelihood of leading/lagging head unbinding vs interhead separation data provided in DeWitt \textit{et.
+%
+%\subsection*{$C$}
+We determined the exponential unbinding parameter $C$ based on the likelihood for a lagging head to unbind vs.
+the interhead separation provided from DeWitt \textit{et.
 al.} \cite{dewitt}.
-The value of $c$ was chosen which led to the lowest root-mean-squared error in P(lagging step) vs interhead separation between the experiment and the model, as shown in Figure \ref{fig:ProbLagPlot}.
+A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}.
+This parameter governs the tension-gating between dynein's heads, as the probability of a lagging step increases with $C$.
 All other parameters were held at the values in Table \ref{table:params}.
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.35}
 	\caption[Lagging preferred steps]{\textbf{Lagging preferred steps.} Likelihood of a trailing step vs.
@@
 
-\subsection*{$k_{ub}$}
-The unbinding rate $k_{ub}$ was estimated from stepping trace data in the Yildiz \textit{et.
-al.} experiment.
-The $k_{ub}$ value which led to an average velocity of 26 nm/s was chosen, as shown in Figure \ref{fig:TrajPlot}.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-	\caption[Stepping trace of head labeled dynein]{\textbf{Stepping trace of head labeled dynein.} Trajectory of MTBD over 24 seconds of walking.
-Red and blue labeled heads shows independence from each other during processive walking.
-Experimentalal trace from \cite{Dewitt2012} offset by 120 nm to display comparison.
-Average velocity of 26 nm/s for both traces.}
-	\label{fig:TrajPlot}
-\end{figure}
-
-\newpage
-
-\subsection*{$k_b$, $k_{a}$}
-The binding and affinity rates directly influenced the onebond stepping statistics shown in Figure \ref{fig:SteppingPlots}.
-The binding rate controlled the tendency for immediate steps.
-The affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps.
-This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein prefered steps within 8 nm.
+%\subsection*{$k_b$, $k_{a}$}
+The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}.
+The binding rate controlled the tendency for immediate steps, while the affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps.
+This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein stepped within 8 nm 56\% of the time.
 
@@
 
-\subsection*{$c_b$, $c_m$, $c_t$}
-Spring constants $c_b$, $c_m$ and $c_t$ were fit using the dynein step length distribution from \cite{yildizpaper}.
-Three spring constants were drawn uniformly from range $[0.0, 4.0]$ and a simulation was run for 10s simulation time with $k_b=X$, $k_{ub}=Y$, $k_{stk}=Z$, and other parameters noted in Table \ref{tab:params}.
-One thousand simulations total were run, and the set of spring constants which yielded the lowest root-mean-squared histogram error between the simulation and experimental step length distributions was chosen.
-\textbf{Probably need to rerun this using our final $k_b$, $k_{ub}$ and $k_{stk}$.}
+%\subsection*{$k_{ub}$}
+Due to dynein's step equilibrating during the 2-HB state, the time spent reaching this equilibrium heavily influences the velocity of a walk.
+Similarly, the ATP concentration controls the rate of steps and the time spent in the 2-HB state.
+Thus, we matched the unbinding rate $k_{ub}$ from stepping trace data in the Yildiz \textit{et.
+al.} experiment which led to an average velocity of 26 nm/s.
+The unbinding rate directly correlates to the rate of steps, as the inverse, $k_{ub}^{-1}$, is the average time spent in the 2-HB state.
+This fitting is shown in Figure \ref{fig:TrajPlot}.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\caption[Stepping trace of head labeled dynein]{\textbf{Stepping trace of head labeled dynein.} Trajectory of MTBD over 24 seconds of walking.
+Red and blue labeled heads shows independence from each other during processive walking.
+Experimentalal trace from \cite{Dewitt2012} offset by 120 nm to display comparison.
+Average velocity of 26 nm/s for both traces.}
+	\label{fig:TrajPlot}
+\end{figure}
+
+\newpage
+
+%
+%\subsection*{$c_m$, $c_t$}
+The motor and tail spring constants, $c_m$ and $c_t$, relates to the tendency for equilibrium positions in the 1-HB and 2-HB state.
+We picked these parameters in accordance to the model's ability to perform the powerstroke and achieve processive motion.
+With these spring constants, the model dynein preferred forward steps towards the minus-end rather than backward steps, while still maintaining flexibility within the stalk and stapping variance.
 

### 2021-07-04 scripts/make_mc_pictures.py

@@ -2,15 +2,10 @@ import os
 from os import path
 import numpy as np
 import matplotlib.pyplot as plt
-from matplotlib import gridspec
-from statistics import mean
-import scipy.constants
 import sys
 sys.path.append("../data")
 import importlib
 import argparse
-import subprocess
-from glob import glob
 
 import bb_energy_distribution
 import dynein.draw.cartoon as cartoon

### 2021-07-04 papers/paper/paper.tex
Added pdf to run fac

@@
 \centering
-\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
-\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
+\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
 \caption[Stepping statistics of model]{\textbf{Stepping statistics of model.} \textit{Top: } Heatmap of initial foot displacement vs.
@@
 	\centering
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
 	\caption[Stepping trace of head labeled dynein]{\textbf{Stepping trace of head labeled dynein.} Trajectory of MTBD over 24 seconds of walking.

### 2021-07-04 data/params.py

@@ -1,7 +1,7 @@
 #!/usr/bin/python3
 
 for_simulation= {"k_b": 5.5e10, # 3.4e9, previously 3e6
-                 "k_ub": 2.0,
+                 "k_ub": 2.5,
                  "k_stk": 1e8,  # NEW: Sticky Rate
                  "cb": 0.0, # OLD: 0.08,
                  "cm": 1.0, # OLD: 1.05,

### 2021-07-04 scripts/make_mc_plots.py

@@ -678,7 +678,7 @@ def make_trajectory_plot(args, plotpath, bb_P_trailing, bb_rate_total, hist, ini
     bx_position = np.array([[0.0, L]])
     bb_step_time = np.array([0.0])
     j = 0
-    seed_for_kub_2 = 4000
+    seed_for_kub_2 = 2
     np.random.seed(seed_for_kub_2)
 
     while j < num_steps:
@@ -742,12 +742,16 @@ def make_trajectory_plot(args, plotpath, bb_P_trailing, bb_rate_total, hist, ini
                        cumulative_time[1], color='red', linestyle='--')
     plt.vlines(vline_x, bx_position[:-1, 1], bx_position[1:, 1], color='blue')
     plt.vlines(vline_x, bx_position[:-1, 0], bx_position[1:, 0], color='red')
-    plt.plot(yildiz_data[0], yildiz_data[1]+120, '--',
+    # plt.plot(yildiz_data[0], yildiz_data[1], '--',
+    #          markersize=0, color="blue", alpha=0.8)
+    # plt.plot(yildiz_data[0], yildiz_data[2], '--',
+    #          markersize=0, color="red", alpha=0.8)
+    plt.plot(yildiz_data[0], yildiz_data[1]+80, '--',
              markersize=0, color="blue", alpha=0.8)
-    plt.plot(yildiz_data[0], yildiz_data[2]+120, '--',
+    plt.plot(yildiz_data[0], yildiz_data[2]+80, '--',
              markersize=0, color="red", alpha=0.8)
 
-    x1, x2, y1, y2 = [6, 10, 250, 370]
+    x1, x2, y1, y2 = [6, 9, 190, 320]
     box_v = np.array([x1, x2])
     box_h = np.array([y1, y2])
     plt.hlines(box_h, box_v[0], box_v[1], linewidth=0.5)
@@ -765,7 +769,7 @@ def make_trajectory_plot(args, plotpath, bb_P_trailing, bb_rate_total, hist, ini
     plt.legend([plot1, plot2], ["Model", "Experiment"], loc='upper left')
     plt.grid()
 
-    ax2 = fig.add_axes([0.5, 0.08, 0.35, 0.3])
+    ax2 = fig.add_axes([0.6, 0.08, 0.3, 0.35])
     ax2.hlines(bx_position[:, 1], cumulative_time[:-1],
                cumulative_time[1:], color='blue')
[…]

### 2021-07-05 papers/paper/paper.tex
Changed ls from 20.75 to 21

@@
     \hline
-%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
-    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
-    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
-    $k_a$ & $\kstk$  $s^{-1}$ &  & \\
-    $k_b$ & $\kb$  nm $s^{-1}$ &  & \\
-    $\epsilon$ &  $\MTbindingdistance$ nm & & \\
-    $k_{ub}$ & $\kub$ $s^{-1}$ & & \\
-    $C$ & $\cexp$ & & \\
     $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
@@
     $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
+    \hline
+  \end{tabular}
+  \caption{Parameters used in simulation.
+$c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
+$k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
+$L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
+$c$ is the tension-gating factor.
+The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
+$R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
+Parameters used for all simulations unless otherwise noted}
+  \label{table:params}
+\end{table}
+
+\begin{table}
+  \centering
+  \begin{tabular}{lr}
+    Param & Model  \\
+    \hline
+%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
+    $c_m$ & $\cm \Delta G_{ATP}$  \\
+    $c_t$ & $\ct \Delta G_{ATP}$  \\
+    $k_a$ & $\kstk$  $s^{-1}$  \\
+    $k_b$ & $\kb$  nm $s^{-1}$  \\
+    $\epsilon$ &  $\MTbindingdistance$ nm  \\
+    $k_{ub}$ & $\kub$ $s^{-1}$  \\
+    $C$ & $\cexp$  \\
     \hline

### 2021-07-05 papers/paper/paper.tex
Adding plot

@@
   \end{tabular}
-  \caption{Parameters used in simulation.
-$c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
-$k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
+  \caption{Constant parameters used in simulation.
 $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
-$c$ is the tension-gating factor.
-The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
+The $\theta$ parameters are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
 $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
@@
   \end{tabular}
-  \caption{Parameters used in simulation.
+  \caption{Free parameters used in simulation.
 $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively.
+$k_a$ is the affinity transition rate from high to low affinity when MTBD unbinds.
 $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively.
-$L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers.
-$c$ is the tension-gating factor.
-The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors.
-$R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii.
-Parameters used for all simulations unless otherwise noted}
+$\epsilon$ is the vertical position allowed for rebinding.
+$C$ is the tension-gating factor.}
   \label{table:params}
@@
 
-The model's simplistic nature allowed flexible optimization for each parameter in order to most accurately portray stepping results from experiment.
-We investigated this parameter space by associating each stepping parameter to a property of dynein's step observed from Yildiz's experiment.
-Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns unbound times.
-The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters.
+We present the following results from single step Brownian dynamics simulations at a constant temperature of $T=310.15$ $K$ and with a time step of $\delta t =1 * 10^{-13}$ $s$.
+The Monte Carlo algorithm simulated $>$18000 step cycles for each initial unsigned distance from $L_i\in [1, 72]$.
+The algorithm's fast computation allowed flexible optimization for each parameter in order to most accurately replicate stepping results from experiment.
+We investigated this parameter space by associating each stepping parameter to a property of dynein's step, observed from Yildiz's experiment.
+Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns stepping times.
+%The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters.
 Consequently, dynein fails to equilibrate during the stepping motion and quickly rebinds shortly after unbinding.

### 2021-07-05 papers/paper/paper.tex
More paper content

@@
 Parameters used for all simulations unless otherwise noted}
-  \label{table:params}
+  \label{table:constparams}
 \end{table}
@@
 We present the following results from single step Brownian dynamics simulations at a constant temperature of $T=310.15$ $K$ and with a time step of $\delta t =1 * 10^{-13}$ $s$.
-The Monte Carlo algorithm simulated $>$18000 step cycles for each initial unsigned distance from $L_i\in [1, 72]$.
+The Monte Carlo algorithm simulated $>$18000 step cycles for each initial unsigned distance of $L_i\in [1, 72]$.
 The algorithm's fast computation allowed flexible optimization for each parameter in order to most accurately replicate stepping results from experiment.
@@
 
-%
-%\subsection*{$C$}
-We determined the exponential unbinding parameter $C$ based on the likelihood for a lagging head to unbind vs.
-the interhead separation provided from DeWitt \textit{et.
-al.} \cite{dewitt}.
-A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}.
-This parameter governs the tension-gating between dynein's heads, as the probability of a lagging step increases with $C$.
-All other parameters were held at the values in Table \ref{table:params}.
+%\subsection*{$k_b$, $k_{a}$}
+In order to best replicate experimental observation of correlated stepping between MTBDs, we optimized the binding parameters, $k_a$ and $k_b$, according to the dependence between dynein's step and the initial MTBD positions.
+Figure \ref{fig:SteppingPlots} displays a heat map of initial displacement, defined as the signed distance from the stationary MTBD to the stepping MTBD, vs.
+the step length.
+Yildiz \textit{et al.} supports the idea of tension gating and displays dynein's correlated stepping from their slope of $m = -0.4$.
+The negative slope implies a bias for negative displacements to take forward steps while the positive displacements take negative steps.
+We fit $k_a$ and $k_b$ according to this slope and achieved $m = -0.492$ with values from Table \ref{table:params}.
+The binding parameters largely influenced the dependence between steps by influencing the rate for rebinding and controlling the tendency to equilibriate during the unbound state.
+More specifically, the affinity transition rate, $k_a$, controlled the transition time from high to low affinity when unbinding to introduce a buffer period and prevent instantaneous rebinding.
+The binding rate, $k_b$, controlled the tendency for the MTBD to rebind after being within $\epsilon$ of the MT.
+To achieve Yildiz's slope of -0.4, both binding rates were increased significantly to promote quick and immediate rebinding after unbinding.
+Lower binding rates would lessen the magnitude of the slope and lose the functionality on the MTBD separation.
+The bottom figure in Figure \ref{fig:SteppingPlots} shows the probability density of step lengths compared to a stepping histogram from Yildiz \textit{et al.} experiment.
+The peak near 0 nm displays the effect of the large binding rates, as the model was only able to replciate the desired slope if dynein preferred steps within 8 nm 56\% of the time.
+Despite the fast rebinding, the simulation was still able to achieve forward directionality with larger forward steps than negative ones.
+These results conclude that dynein must take steps within 8 nm in order to achieve proper stepping correlation between the steps and the initial MTBD separaion.
 
-\begin{figure}[tbhp]
-	\centering
-	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.35}
-	\caption[Lagging preferred steps]{\textbf{Lagging preferred steps.} Likelihood of a trailing step vs.
-the initial binding domain distance ($P_{trail.}(L)$.
-Exponential unbinding parameter, $C$, fitted with \cite{Dewitt2012}.}
-	\label{fig:ProbLagPlot}
-\end{figure}
-
-%\subsection*{$k_b$, $k_{a}$}
-The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}.
+%The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}.
 The binding rate controlled the tendency for immediate steps, while the affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps.
@@
 
-\newpage
+%
+%\subsection*{$C$}
+We determined the tension-gating parameter $C$ based on the likelihood for a lagging head to unbind vs.
+the interhead separation, provided from Yildiz \textit{et.
+al.} \cite{yildizpaper}.
+A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}.
+This parameter governs the tension-gating between dynein's heads, as the probability of a lagging step increases with $C$.
+Consequently, $C$ does not affect the dependence on the time spent in the 2-HB state
+
+\begin{figure}[tbhp]
+	\centering
+	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.35}
+	\caption[Lagging preferred steps]{\textbf{Lagging preferred steps.} Likelihood of a trailing step vs.
+the initial binding domain distance ($P_{trail.}(L)$.
+Exponential unbinding parameter, $C$, fitted with \cite{Dewitt2012}.}
+	\label{fig:ProbLagPlot}
+\end{figure}
 
@@
 
-Dependence of the unbinding MTBD on its relation to its partner MTBD is studied in Figure \ref{fig:tensiongating}.
+%Dependence of the unbinding MTBD on its relation to its partner MTBD is studied in Figure \ref{fig:tensiongating}.
 Figure \ref{fig:tensiongating}.a shows a heat map of initial displacement, defined as how much the stepping MTBD is ahead of the stationary MTBD, vs the step size.

### 2021-11-06 scripts/make_mc_plots.py
Figure changes to paper

@@ -493,11 +493,11 @@ def make_step_length_plots(args, plotpath, probability_distribution, initial_dis
     step_length_center)
 
     # 2D hist step_length
-    plt.figure('Step length probability distribution', figsize=(8, 6))
+    plt.figure('Step length probability distribution', figsize=(3.5, 3))
     contours = plt.contour(s_initial_disp_center, s_length_center,
                            s_probability_distribution, levels=sorted(list(quantiles.keys())), colors='white')
-    plt.clabel(contours, quantiles.keys(), fmt=quantiles, inline=True, fontsize=7)
-    plt.pcolor(s_initial_disp_edge, s_length_edge,
+    plt.clabel(contours, quantiles.keys(), fmt=quantiles, inline=True, fontsize=6)
+    pcm = plt.pcolor(s_initial_disp_edge, s_length_edge,
                s_probability_distribution)
     # plt.pcolor(initial_disp_edge, step_length_edge, s_probability_distribution)
     plt.plot(initial_disp, s_lin_fit,
@@ -509,13 +509,18 @@ def make_step_length_plots(args, plotpath, probability_distribution, initial_dis
     plt.gca().set_aspect('equal')
     plt.ylim(-56, 56)
     plt.xlim(-56, 56)
-    plt.colorbar().set_label(r'Probability (1/nm$^2$)')
-    plt.legend(loc='lower left')
+    plt.legend(loc='lower left', fontsize = 8)
+    plt.tight_layout()
     # plt.title('kb = {0:.2e}, kstk = {1:.2e}, cb = {2}, cm = {3}, ct = {4}, eqb = {5}, eqmpre = {6}, eqmpost = {7}, C = {8}'.format(args.k_b,
     #         args.k_stk, args.cb, args.cm, args.ct, args.eqb, args.eqmpre, args.eqmpost, args.C))
     plt.savefig(plotpath+u+'step_length_probability_distribution_' +
-                params_string+'.pdf')
+                params_string+'.pdf', bbox_inches = 'tight')
 
+    fig, ax = plt.subplots(figsize = (3.2, 3.0))
+    plt.colorbar(pcm, orientation = 'vertical', label = r'Probability (1/nm$^2$)')
+    ax.remove()
+    plt.savefig(plotpath+u+'colorbar_' +
+                params_string+'.pdf', bbox_inches = 'tight')
 
[…]

### 2022-01-15 papers/paper/paper.tex
Figure changes to paper
Some amount of progress on paper - rewrote part of the intro, rewrote the discussion, tweaked the results to be in line with the discussion. Current paper status: terrible but the content is hopefully mostly there. Needs lots of editing.

@@
 \usepackage{color}
+\usepackage{subcaption}
 
 \newcommand\davidsays[1]{{\em\color{blue} {\bf DR:} #1}}
+\newcommand\forjin[1]{{\em\color{green} {\bf Jin:} #1}}
+\newcommand\todo[1]{{\em\color{red} #1}}
 
@@
 
-%\section*{TODO August 2020}
-%\begin{enumerate}
-%  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
-%  \item Articulate data we fit to
-%  \begin{enumerate}
-%    \item Velocity -> unbinding rate
-%    \item Ratio of leading vs trailing steps -> exponential parameter
-%    \item Average step length -> other parameters
-%    \item Yildiz weird slope -> sticky rate + binding rate
-%    \item Avoid instant rebinds -> sticky rate
-%    \item Time to kick from MD??
-%    \item efficiency (affects instant rebind)
-%  \end{enumerate}
-%  \item Do the fit (requires 1 above)
-%  \item Could have a fixed binding immunity time rather than sticky rate
-%  \paragraph{Advantages of immunity time}
-%  \begin{enumerate}
-%    \item Might accurately reflect a diffusive escape from an energy well
-%  \end{enumerate}
-%  \paragraph{Advantages of sticky rate}
-%  \begin{enumerate}
-%    \item Accurately reflects the dynamics of a chemical process
-%  \end{enumerate}
-%\end{enumerate}
+\section*{TODO August 2020}
+\begin{enumerate}
+  \item Articulate data we fit to
+  \begin{enumerate}
+    \item Velocity -$\>$ unbinding rate
+    \item Ratio of leading vs trailing steps -> exponential parameter
+    \item Average step length -> other parameters
+    \item Yildiz weird slope -> sticky rate + binding rate
+    \item Avoid instant rebinds -> sticky rate
+    \item Time to kick from MD??
+    \item efficiency (affects instant rebind)
+  \end{enumerate}
+  \item Do the fit (requires 1 above)
+  \paragraph{Advantages of sticky rate}
+  \begin{enumerate}
+    \item Accurately reflects the dynamics of a chemical process
+  \end{enumerate}
+\end{enumerate}
 
-\newpage
+\section*{TODO January 2022}
+\begin{enumerate}
+\item go through and fill in missing citations
+\item add more paper citations to Discussion, should tie in with more recent science. There are plenty of good uncited papers in the bibtex (10+)  
+\item go through model papers and make sure none of them handle correlated stepping, since this is an impt claim we make in the intro
+\item heavily edit to make it sound better, probably pretty bad right now
+  \item meet with David at some point to see what he thinks
+\end{enumerate}
 
-\davidsays{Discuss each figure, and each parameter (how we got it).}
+\section*{Notes}
+\begin{enumerate}
+\item In my head the journal target would be Biophysical Journal; they're pretty open to modeling papers and dynein and one of the dynein modeling papers we cite was published there
+\end{enumerate}
 
+\section*{DR}
 \davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.
-
 Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.}
@@
 
-\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff, and our angles work out.  Report the average step length.}
+\davidsays{one-bound time plot. Cut?}
 
-\davidsays{contour plot. Gave us the binding rate and the affinity time.  
-Very fast binding required (to get slope right) and need affinity time to avoid instantly rebinding.}
-
-\davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}
-
-\davidsays{one-bound time plot. Cut?}
+\newpage
 
@@
 
-%% Dynein has several cofactors which alter its dynamics.
-For example, the motor's stall force is tripled when exposed to dynactin and Bic2D \cite{yildizdynactin}.
-This is odd, since the dynactin- and Bic2D-binding site on dynein is on the tail, far from the motor heads.
-
 Dynein is a motor protein which generates motion for various cellular processes.
@@
 
-This mechanochemical cycle of chemical transitions is well supported by evidence \cite{citemore}.
+One open question is whether cytoplasmic dynein's structure and mechanochemical cycle are sufficient to explain its stepping behavior.
+Several modeling studies have addressed this question \cite{alltheorypapers}.
+\todo{These studies have explained X, and Y, and Z phenomena}.
+However, to our knowledge no studies have fully explained the dynamics of dynein's step; that is, they haven't explained how dynein's highly variant stepping pattern arises.
+In addition, dynein is known to have correlation structure between its steps, where the interhead separation of one step influences the step length of the next step \cite{}; this has not been explained by existing models either.
+Tension gating has been proposed to explain how interhead separation influences step length \cite{}.
+However, this mechanism doesn't explain how lagging steps are forward directed and leading steps are backward direced, only the relative likelihood of unbinding.
+Further, it hasn't been explained exactly how dynein manages to step backward and forward, and whether dynein's size and domain flexibility are sufficient to explain this.
+We put forward that these phenomena can be explained simply by the elastic forces imposed by a dynein motor's domains, and the influence of conformational changes from teh conformational cycle, biasing the diffusive search of the unbound microtubule binding domain.
+Lagging steps tend to have motor domains positioned relatively forward, biasing the MTBD forward; leaing steps similarly bias teh MTBD diffusion backwards.
+Backward and forward stepping come from the relatively loose coordination of dynein's domains relative to the strength of Brownian forces on those domains.
+
+Because this explanation requires an accurate model of both the positioning and interdomain forces in cytoplasmic dynein, to test it we created a detailed model of dynein capturing both the structural relationships between the primary domains in the motor, and also the interdomain tension and elasticity forces acting on each domain.
+We used Brownian dynamics to simulate the diffusive search the motor undergoes as its head unbind and rebind the microtubule.
+Here we report results demonstrating that such a model is capable of reproducing both the varied, forward-and-backward stepping pattern of dynein, and also the interstep correlation.
+
+%This mechanochemical cycle of chemical transitions is well supported by evidence \cite{citemore}.
 However, there is still relatively little known about the dynamic mechanism of domain motion dynein uses to achieve its forward motion by transitioning between these states \cite{lippert}.
@@
 
-Here we use a Monte Carlo simulation that investigates dynein's inter-step correlations as it moves along the MT.
+%Here we use a Monte Carlo simulation that investigates dynein's inter-step correlations as it moves along the MT.
 We model cytoplasmic dynein by reducing the mechanochemical cycle into two states: the pre-stroke and post-stroke states.
@@
 \centering
-%\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
-%\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
 \includegraphics[width=1\linewidth]{figures/equilibrium-positions-final.pdf}
 \caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
-\davidsays{FIXME remove spring on binding domain and fix caption.}
  \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free.
@@
 \includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
-%\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
+%% \includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
 %% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
@@
     $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
-%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
+    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
     $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
@@
     \hline
-%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
+    $c_b$ & $\cb \Delta G_{ATP}$ \\
     $c_m$ & $\cm \Delta G_{ATP}$  \\
@@
 
-\section{Model}
+\section*{Model}
 This model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex, while remaining mathematically simple.
@@
 
-\subsection*{Model geometry}
+\subsubsection*{Model geometry}
 The dynein model represents a full dynein complex consisting of two dynein heavy chains dimerized by a large tail domain.
@@
 
-\davidsays{Maybe we want to discuss right here the likely step sizes for leading and trailing steps \emph{if it goes to its equilibrium configuration}.
-It's pretty simple and can serve as a ``validation" of our model geometry.}
-
-\subsection*{Equilibrium forces}
+\subsubsection*{Equilibrium forces}
 The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$.
@@
 
-\subsection*{Binding}
+The rigid rod geometry and equilibrium angles can be used to calculate the mean step size.
+If all joints except the tail joint are treated as rigid, then two steps are possible: a forward step of $6.3$nm and a backwards step of $73$nm.
+This serves as a validation of the geometry of the model, which reproduces the experimental mean step size of XYZ \cite{xyz}.
+
+\subsubsection*{Binding}
 Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the prestroke and poststroke states.
@@
 
-\subsection*{Unbinding}
+\subsubsection*{Unbinding}
 Unbinding occurs when a poststroke MTBD unbinds from the microtubule.
@@
 
-\subsection*{Brownian dynamics}
+\subsubsection*{Brownian dynamics}
 Brownian dynamics is used to study the model's dynamics in a biophysical manner.
@@
 
-\subsection*{Monte Carlo}
+\subsubsection*{Monte Carlo}
 A Monte Carlo algorithm governs the simulation of the step.
 We initialize a two-headed bound configuration of dynein by randomly picking domain angles and calculating the total harmonic energy by summing the energies of each domain.
-A probability of unbinding, $P_{ub}$, is then calculated from a Boltzmann distribution, where $P_{ub}\propto e^{-\beta E_{total}}$.
+A probability of unbinding, $P_{ub}$, is then calculated from a Boltzmann distribution, where $P_{ub}\propto e^{-\beta E_{total}}$ (\todo{is this right?
+we don't use just the binding angle?}).
 If dynein unbinds, then the configuration transitions into the one-headed bound state where Brownian dynamics is performed.
@@
 A partition function, $Z=\sum e^{-\beta E{total}}$, can then calculate ensemble averages of unbinding rates and probability.
+\todo{maybe a bit more info on how you go from binding to unbinding over the course of a single simulation, especially wrt L; readers may not know how this works}
 
@@
 
-\section*{Prestroke motion equations derivation}
+\subsubsection*{Prestroke motion equations derivation}
 Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:
@@
 
-\section*{Poststroke motion equations derivation}
+\subsubsection*{Poststroke motion equations derivation}
 Brownian dynamics was initially used for the postroke case but was later changed to be simulated with Monte Carlo methods.
@@
 
-\section*{Simulating the model}
+\subsubsection*{Simulating the model}
 Simulations began in the poststroke equilibrium state.
@@
 
-\section{Results}
+\section*{Results}
+Structural parameter lengths $L_t$, $L_s$ and radii $R_b$, $R_m$, and $R_s$ were estimated from crystal structures of cytoplasmic dynein \cite{3vkh-cite, carter-paper}.
+Motor domain equilibrium angles were estimated from EM class averages of axonemal dynein in the absence of neucleotide for the two-head-bound (2HB) angle or in the presence of irreversibly-binding ADP-Vi for the one-head-bound (1HB) angle \cite{Burgess2003}, shown in Figure \ref{fig:micrographs}.
+The binding equilibrium angle $\theta_b$ was estimated from a crystal structure of cytoplasmic dynein bound to tubulin \cite{leschziner}.
 
-\davidsays{Discuss each figure, and each parameter (how we got it).}
+The other parameters shown in Table \ref{tab:params} were estimated by simulating the model and tuning parameters to experimental measurements, as described as follows.
+These single step Brownian dynamics simulations were run at a constant temperature of $T=310.15 K$  with an Euler's method time step of $dt = 10^{-13}$ $s$.
+The Monte Carlo algorithm simulated $>18000$ step cycles for each initial unsigned distance of $L_i \in [1, 72]$.
+The algorithm's fast computation allowed flexible optimization for each parameter in order to most accurately replicate stepping results from experiment.
+We investigated this parameter space by associating stepping parameters to experimental measurements of dynein's step.
+Results are shown for a model with parameters described in Table \ref{tab:params}.
 
-\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.
-
-Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.}
-
-\davidsays{Do not add average both-bound time vs.
-L?
-This is a measurable prediction if we can't find an experimental result.
-Otherwise, we can compare with experiment.
-Maybe just add a sentence or two}
-
-\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff, and our angles work out.  Report the average step length.}
-
-\davidsays{contour plot. Gave us the binding rate and the affinity time. Very fast binding required (to get slope right) and need affinity time to avoid instantly rebinding.}
-
-\davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}
-
-\davidsays{one-bound time plot. Cut?}
-
-\section*{Fitting model parameters}
-
-We present the following results from single step Brownian dynamics simulations at a constant temperature of $T=310.15$ $K$ and with a time step of $\delta t =1 * 10^{-13}$ $s$.
-The Monte Carlo algorithm simulated $>$18000 step cycles for each initial unsigned distance of $L_i\in [1, 72]$.
-The algorithm's fast computation allowed flexible optimization for each parameter in order to most accurately replicate stepping results from experiment.
-We investigated this parameter space by associating each stepping parameter to a property of dynein's step, observed from Yildiz's experiment.
-Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns stepping times.
-%The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters.
-Consequently, dynein fails to equilibrate during the stepping motion and quickly rebinds shortly after unbinding.
-
-We first estimated structural parameters $L_t$, $L_s$, $R_b$, $R_m$, $R_s$, and equilibrium angles $\theta_{m}^{pre}$, $\theta_{m}^{post}$, and $\theta_{t}$ from cryo-electron microscopy class averages and density maps of cytoplasmic and axonoemal dynein, shown in Figure \ref{fig:micrographs}.
-We defined the tail and motor equilibrium angles from Burgess \textit{et al.
-} class average image, where the left stalk's motor was in the apo post-powerstroke state and right stalk's motor was in the ADP-bound apo pre-powerstroke state.
-
-%Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\theta_{m}^{pre}$, $\theta_{b}^{post}$, $\theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}.
-In the class average image from Burgess \textit{et.
-al.} \cite{burgess} the different tail-motor-MTBD angles were taken to indicate that left stalk's motor domain was in the apo post-powerstroke state, and the right stalk's motor domain in the ADP-bound pre-powerstroke state.
-In the Grotjahn \textit{et.
-al} \cite{grotjahn} density map, both motor domains were taken to be in the post-powerstroke state.
-
-%\subsection*{$k_b$, $k_{a}$}
-In order to best replicate experimental observation of correlated stepping between MTBDs, we optimized the binding parameters, $k_a$ and $k_b$, according to the dependence between dynein's step and the initial MTBD positions.
-Figure \ref{fig:SteppingPlots} displays a heat map of initial displacement, defined as the signed distance from the stationary MTBD to the stepping MTBD, vs.
-the step length.
-Yildiz \textit{et al.} supports the idea of tension gating and displays dynein's correlated stepping from their slope of $m = -0.4$.
-The negative slope implies a bias for negative displacements to take forward steps while the positive displacements take negative steps.
-We fit $k_a$ and $k_b$ according to this slope and achieved $m = -0.492$ with values from Table \ref{table:params}.
-The binding parameters largely influenced the dependence between steps by influencing the rate for rebinding and controlling the tendency to equilibriate during the unbound state.
-More specifically, the affinity transition rate, $k_a$, controlled the transition time from high to low affinity when unbinding to introduce a buffer period and prevent instantaneous rebinding.
-The binding rate, $k_b$, controlled the tendency for the MTBD to rebind after being within $\epsilon$ of the MT.
-To achieve Yildiz's slope of -0.4, both binding rates were increased significantly to promote quick and immediate rebinding after unbinding.
-Lower binding rates would lessen the magnitude of the slope and lose the functionality on the MTBD separation.
-The bottom figure in Figure \ref{fig:SteppingPlots} shows the probability density of step lengths compared to a stepping histogram from Yildiz \textit{et al.} experiment.
-The peak near 0 nm displays the effect of the large binding rates, as the model was only able to replciate the desired slope if dynein preferred steps within 8 nm 56\% of the time.
-Despite the fast rebinding, the simulation was still able to achieve forward directionality with larger forward steps than negative ones.
-These results conclude that dynein must take steps within 8 nm in order to achieve proper stepping correlation between the steps and the initial MTBD separaion.
-
-%The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}.
-The binding rate controlled the tendency for immediate steps, while the affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps.
-This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein stepped within 8 nm 56\% of the time.
+Model springs were chosen to reproduce experimental step sizes.
+The model generated forward-directed motion with a mean step size of \forjin{what is the mean step size?
+I think David said somewhere he wanted us to note this - could potentially do the mean while ignoring the small steps?}, as shown in Figure \ref{fig:SteppingPlots}.b.
+The model takes steps in the range of $<-40nm$ to $>55nm$, encompassing the range observed for TIRF microscopy studies of cytoplasmic dynein \cite{}.
+The ratio of short to long steps is comparable for model and experiment.
+The large number of short ($<4nm$) steps the model takes comes from step events where the unbound head quickly rebinds after dissociating from the microtubule.
+We note that fluorescence-based measurements cannot resolve near zero-length steps, so it is impossible to compare experimental and model behavior in this range.
 
@@
 \centering
+\begin{subfigure}{.75\columnwidth}
+	\centering
 	\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
+\end{subfigure}
+\begin{subfigure}{.2\columnwidth}
+	\centering
+	\includegraphics[width=1.3\linewidth]{../../plots/mc_plots/u_colorbar_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
+\end{subfigure}
 \includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
@@
 
-%
-%\subsection*{$C$}
-We determined the tension-gating parameter $C$ based on the likelihood for a lagging head to unbind vs.
-the interhead separation, provided from Yildiz \textit{et.
-al.} \cite{yildizpaper}.
+The interstep correlation, which we define as the correlation between the head separation of one step and the next, was mostly influenced by the dynamics of unbinding and rebinding of the stepping head.
+In order to best replicate experimental observation of interstep correlation, we optimized the binding parameters, $k_a$ and $k_b$, to allow for moderate interstep correlation.
+Figure \ref{fig:SteppingPlots} displays a heat map of initial displacement, defined as the signed distance from the stationary MTBD to the stepping MTBD, vs.
+the step length.
+Experimental data \cite{} measure dynein's interstep correlation at $m = -0.4$.
+The negative slope implies a bias for negative displacements to take forward steps while the positive displacements take negative steps.
+We fit $k_a$ and $k_b$ according to this slope and achieved $m = -0.492$ with values from Table \ref{table:params}.
+The binding parameters largely influenced the dependence between steps by influencing the rate for rebinding and controlling the tendency to equilibriate during the unbound state.
+More specifically, the affinity transition rate, $k_a$, controlled the transition time from high to low affinity when unbinding to introduce a buffer period and prevent instantaneous rebinding.
+The binding rate, $k_b$, controlled the tendency for the MTBD to rebind after being within $\epsilon$ of the MT.
+To achieve experimentally realistic correlations, both binding rates were increased significantly to promote quick and immediate rebinding after unbinding.
+Lower binding rates would allow the 1HB state to reach equilibrium and lose information about the previous step.
+The bottom figure in Figure \ref{fig:SteppingPlots} shows the probability density of step lengths compared to a stepping histogram from Yildiz \textit{et al.} experiment.
+The peak near 0 nm displays the effect of the large binding rates; the model preferred steps within -8 to 8 nm 56\% of the time.
+Despite the fast rebinding, the simulation was still able to achieve forward directionality with larger forward steps than negative ones.
+
+%% The interstep correlation, which we define as the correlation between the head separation of one step and the next, was mostly influenced by the dynamics of unbinding and rebinding of the stepping head.
+If the constant governing unbound head rebinding, $k_b$, was too small then the unbound head would always equilibrate and there would be no correlation between steps.
+If $k_b$ was large then most model steps would be small the the model would be only weakly forward-directed.
+The affinity time $k_a$, which controls how long the unbound head can freely diffuse before rebinding, needed to be high enough to prevent instantaneous rebinding.
+With these parameters properly set, the model generated an interstep correlation of m=-0.492 as in Figure \ref{fig:SteppingPlots}.a, which accords with interstep correlations from experiments \cite{}.
+
+%modifications from jins original: move some discussion stuff into the discussion, change the emphasis to results over choosing parameters
+
+In addition to angular energy, the unbinding process is also governed by a factor $C$.
+Called the tension gating factor, $C$ controls how likely a lagging head is to unbind compared with a leading head.
+By tuning $C$, we managed to reproduce experimentally determined domain unbinding preference \cite{yildizpaper}, as shown in Figure \ref{fig:ProbLagPlot}.
+
+In addition to angular energy, the unbinding process is also governed by a factor $C$.
+Called the tension gating factor, $C$ controls how likely a lagging head is to unbind compared with a leading head.
+We determined $C$ based on the experimental likelihood for a lagging head to unbind vs.
+the interhead separation \cite{yildizpaper}.
 A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}.
@@
 %\subsection*{$k_{ub}$}
-Due to dynein's step equilibrating during the 2-HB state, the time spent reaching this equilibrium heavily influences the velocity of a walk.
-Similarly, the ATP concentration controls the rate of steps and the time spent in the 2-HB state.
-Thus, we matched the unbinding rate $k_{ub}$ from stepping trace data in the Yildiz \textit{et.
-al.} experiment which led to an average velocity of 26 nm/s.
+Dynein has been seen to spend most of its time in the both-heads-bound state \cite{}, and so the duration of this state almost completely determines dynein's velocity.
 The unbinding rate directly correlates to the rate of steps, as the inverse, $k_{ub}^{-1}$, is the average time spent in the 2-HB state.
-This fitting is shown in Figure \ref{fig:TrajPlot}.
+We tuned our unbinding rate $k_{ub}$ such that the model's velocity was 26 nm/s, comparable with experimentally observed velocities from TIRF microscopy \cite{yildizpaper}.
+When sequential steps are stitched together trajectories can be generated, as seen in Figure \ref{fig:TrajPlot}.
+We note that the unbinding parameter is specific to the experimental preparation, as the unbinding process is sensitive to ATP concentration \cite{}.
 
@@
 \newpage
-
-%
-%\subsection*{$c_m$, $c_t$}
-The motor and tail spring constants, $c_m$ and $c_t$, relates to the tendency for equilibrium positions in the 1-HB and 2-HB state.
-We picked these parameters in accordance to the model's ability to perform the powerstroke and achieve processive motion.
-With these spring constants, the model dynein preferred forward steps towards the minus-end rather than backward steps, while still maintaining flexibility within the stalk and stapping variance.
 
@@
 
-\section{Discussion}
-In this study we sought to study dynein's dynamics using a simple model.
-We used imaging data to construct a structurally realistic goemetric model for the motor, then used Brownian dynamics to explore how such a model would behave in a cell.
-We used experimental data on dynein's step length distribution and unbinding likelihood to fit the model's spring and tension-gating constants.
-We used arguments about dynein's run length and velocity to predict the average time the motor spent in the pre-stroke and post-stroke states, and fit the model's binding and unbinding rates to these predictions.
+\section*{Discussion ideas}
+\begin{enumerate}
+    \item something about our kb ka interplay
+    \item is it interesting that we don't have stalk elasticity at all and managed to reproduce dynein's dynamics?
+there was that one paper (find paper) that mentioned that maybe stalk elasticity is super important; maybe this would be a good to mention in the intro as an example of an idea we think is wrong, stalk elasticity is not -necessary- for dynein's walk
+\end{enumerate}
+
+\section*{Discussion}
+In this study we aimed to answer the question of whether dynein's structure, elastic properties, and mechanochemical cycle-induced conformational changes are sufficient to explain the motor's stepping dynamics.
+We modeled dynein as five circular domains representing two microtobule binding domain (MTBD) heads, two motor domains, and a tail domain, connected via rigid rods.
+Angular spring forces were added to the motor and binding domain joints to represent interdomain elasticity, and tension forces were imposed to maintain the rigid rod constraints.
+The mechanochemical cycle was represented in the model as two states: a two-head-bound (2HB) state where both binding domains were constrained to the microtubule, representing the poststroke state, and a one-head-bound (1HB) state where one MTBD is free to diffuse, representing the porestroke state.
+The conformational changes in the linker which occur during the powerstroke were represented by changing the equilibrium angle in the motor joint of the unbound dimer, resulting in a forward kick of the MTBD head.
+The diffusive search of the 1HB state was simulated using Brownian dynamics, and the 2HB state was simulated using a Monte Carlo algorithm for efficiency.
+
+To determine how well this model reproduced dynein's stepping dynamics, we first needed to assess how realistically the model generated single steps.
+We found that by tuning the models spring constants it could generate the proper range of both forward and backward steps, and with the proper ratio of short to medium to long steps as well as negative steps, indicating our Brownian kinetic model successfully captured the rough dynamics of the single step process.
 From fitting we found that relatively loose tail and MTBD spring constants and a stiff motor domain produced the best stepping histogram; this agrees with another simulation which found tail and MTBD flexibility is necessary for large steps \cite{tsygankovemsimulation}.
-We tested the dynamics of this fit model, and found that the model displayed a high level of agreement with the data used to fit; the simulation's velocity and stepping histogram in Figure \ref{fig:behavior} match experiment quite well.
-In addition the model can predict new data it was not fit with, such as force output in Figure \ref{fig:force} and effects of foot displacement on step length in Figure \ref{fig:tensiongating}.
-The model also displays both inchworm and hand-over-hand stepping, as in real dynein \cite{weihongpaper}.
-The ability of our model to replicate basic experimental features indicates that the core of dynein's step is its ability to couple conformational transitions with MT affinity, and no other aspects are needed.
-The major deviation in model and experiment is the step length density of model steps around 0nm, which is possibly caused by an inability of the step detection algorithm to detect small steps in experimental dynein.
-We then examined the mechanism our model used to walk by studying domain positions over many steps.
-We found that the majority of forward displacement occured immediately after a free binding domain bound to the microtubule, when the just-bound stalk swung forward, pulling the attached motor and tail domains toward the minus-end of the microtubule.
 
-One of the main advantages of our study is that it makes predictions with high spatial and temporal resolution using dynamics realistic for a protein of dynein's size and environment.
-This allows us to study mechanistic questions about how dynein walks, which has not been done before.
-Interestingly, our minimal model, with no assumptions about the dynamics of dynein's forward step, appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}.
-As our model transitions from the so-called pre-stroke to post-stroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it.
-This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY-CITATIONS-HERE}.
-The stalk angle remains displaced from equilibrium until the next unbinding.
-Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.
-The fact that our model only assumes a harmonic restoring energy and a transition in equilibrium angles when switching states, yet produces a robust powerstroke, supports the idea that the powerstroke is feasible for a protein of dynein's general shape and size.
-The fact that a winch-like mechanism was not the dominant mechanism may indicate that the winch is more infeasible for a dynein-like protein.
-This may be due to the fact that the winch requires dragging a potentially large tail domain, whereas the powerstroke only requires pushing the motor domain forward.
-(Not sure if this makes sense, re-check).
+We further imposed a tension gating mechanism to bias the motor towards lagging steps; however, this was insufficient to guarantee interstep correlations, since the mechanism only controlled which foot unbound, not how it diffused.
+We needed further tuning to reproduce the interstep correlation.
 
-This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch, lippert} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et.
-al} \cite{lippert}).
-According to this model, on MTBD rebinding, linker swing puts the just-bound head in a high energy state, just like in the powerstroke mdoel.
-However, to relieve this tension the motor instead ``winches'' its tail domain downwards in the direction of the stalk, resulting in a tail which is closer to the MT and further forward.
-To our knowledge, no previous simulation has tested the physical feasibility of either the winch or powerstroke models.
-Although our model is a minimal depiction which does not take into account the acute dynamics of the whole motor, its ability to reproduce the dynamics of the real dynein suggests that it may have some bearing on how the real dynein walks.
-In particular, this model spontaneously exhibits the powerstroke mechanism, suggesting that the powerstroke mechanism is both feasible for the dynein complex to generate and sufficient to explain much experimental data.
-Although this does not rule out the winch mechanism as an explanation, we believe that the lack of any winch-like behavior in our simulation is meaningful.
-Indeed during displacement our model's tail domain actually moves away from the microtubule, the opposite of the winch's prediction.
-Further theoretical studies demonstrating the feasibility and sufficiency of the winch mechanism are needed.
+To assure gross timescale accuracy in addition to spatial accuracy, we tuned the unbinding rate of the model such that our velocity matched experiment.
 
-Recent experimental studies have had strong implications for the winch vs powerstroke mechanisms.
-A key question is whether the just-bound stalk experiences angular displacement as the motor moves forward, as this is necessary for the powerstroke and not the winch.
-This angular displacement was not found by Lippert \textit{et.
-al.} \cite{lippert}, who used polTIRF to study the angle dynein's stalk made with the MT in freely-walking dynein.
-Another study showed that there is no difference in stalk angle between motors locked in the pre- and post-stroke state using special nucleotides and cryo-electron microscopy \cite{uenoem}.
-One key finding of our study which reconciles the powerstroke mechanism with these experimental findings is the timescale on which the predicted stalk angular displacement occurs.
-We find that the average duration of the angular displacement period of the just-bound stalk is on the order of 1 $ms s$ from the prestroke diffusive search, as the actual angular displacement during the powerstroke is negligibly small (see Figure \ref{fig:stroke}).
-According to the powerstroke model the stalk should be displaced after the recovery stroke, during ATP hydrolysis and Pi release, after binding the MT, and during the powerstroke, in the most likely progression through the mechanochemical cycle \cite{tsygankovscheme}.
-Our calculations for the time only one head is bound predict this period to last roughly 1 $ms$.
-Thus, assuming the MT-bound prestroke period is short enough \cite{mogamirate}, it is possible the entire displacement period should be on the order of milliseconds.
-This time could be faster than the 50 $ms$ time resolution of the polTIRF experiment of Lippert \textit{et.
-al.}, which may explain why an angular displacement was not detected.
-Furthermore we note that in our model the stalk angle deviates from equilibrium as the motor and tail move forwards; only much later does the stalk return to equilibrium.
-This suggests that the stalk angular displacement is a non-equilibrium phenomena which could not be detected through cryo-EM, which resolves equilibrium structures.
-This explains why cryo-EM studies have not been able to find the angular displacement \cite{uenoem, nicastro} (REREAD THE UENOEM PAPER TO MAKE SURE THIS IS RIGHT).
-We further hypothesize that previous simulation results \cite{sarlahmodel}, which have shown a winch-like mechanism is capable of generating motion, have only done so because they do not account for drag and diffusion dynamics.
-Our data demonstrate that pushing forward the motor domain in a powerstroke is a more likely means of relieving the high-energy poststroke state than winching down the far off tail.
-We hypothesize that further models which also account for diffusion would find the same.
-We suggest that the powerstroke mechanism has not been disproven by these studies, and that in order to show the powerstroke doesn't exist, an experiment must be done with high enough time-resolution to resolve the fast microsecond phenomena.
+Proper interstep correlation was achieved by tuning the binding rate governing the transition from 1HB to 2HB.
+An exponential rebinding block process prevented instantaneous rebinding of the free MTBD to the microtubule to allow it to diffuse.
+With the proper binding rate our model produced an m=-0.492 interstep correlation, consistent with experimental measurements of m=-0.4 \cite{}.
 
-Our study demonstrates other interesting findings.
-Similar to past simulation work \cite{sarlahmodel}, we demonstrate that our model is capable of achieving minus-end directed motility merely through the way it binds to the microtubule.
-Also interestingly, we demonstrate that our model is capable of taking 12$nm$ (CHANGE ON RERUN) steps in the absence of explicit microtubule binding sites.
-Merely through the size of its stalk and tail and through the magnitude of angular displacement induced by linker swing, our model is capable of taking the right step size.
-It is interesting that in our model a single step is slightly shorter than the experimental 16nm step \cite{find-citation}.
+We note that there was a strong dependence of interstep correlation on the binding time constant.
+Small binding constants allowed the unbound MTBD to reach equilibrium, erasing information from the previous step.
+Large binding constans only allowed very quick steps.
+It is thus a prediction from our findings that dynein's stepping should be highly dependent on MTBD-MT affinity, and that experimentally lowering affinity through mutagenesis should destroy or reduce dynein's interstep correlation.
+
+Another interesting finding is that in our model the mean single step is slightly shorter than the experimental 16nm step \cite{find-citation}.
 This suggests that perhaps the motor requires a diffusive search along the microtubule to find the next binding site.
@@
 
+The model also displays both inchworm and hand-over-hand stepping, as in real dynein \cite{weihongpaper}
+
 Our theoretical work draws upon and extends several past models \cite{sarlahmodel, trottmodel, tsygankovemsimulation, zhaomodel}.
 This paper's approach of using Brownian dynamics to realistically predict the diffusion dynamics of a structural model of dynein is a useful technique for testing mechanistic theories for biological feasibility and sufficiency, and to our knowledge is the first model to combine imaging and kinetics data with Brownian dynamics to quantify the influences of drag on the dynein motor.
-We believe that taking into account diffusion dynamics and drag is necessary to understand dynein's dynamics, and not doing so may explain why previous studies found the winch model to replicate experimental results \cite{sarlahmodel}.
-Our minimal assumptions simplify the model and allow analytical solutions to motion equations.
+We believe that taking into account diffusion dynamics and drag is necessary to understand dynein's dynamics.
 However, our model neglects many features which may be important for real dynein's walk.
@@
 
-In conclusion, our study demonstrates that the powerstroke mechanism is sufficient to explain dynein's velocity, step length histogram, displacement-vs-step length relationship, and force output.
-We demonstrate that the powerstroke arises naturally from minimal structural information about the protein, suggesting it is likely possible for real dynein to exhibit a powerstroke.
-Further, we explain why past studies may have failed to detect this powerstroke.
-We hope that this evidence is sufficient to maintain the powerstroke mechanism as a viable hypothesis for how dynein walks.
-We further hope that experiments with higher spatial and temporal resolution can be conducted in the near future to shed more light on the precise nature of dynein's stepping mechanism.
-
-\section{Papers we should cite}
-This paper says something interesting~\cite{leschziner}.
-
 \bibliographystyle{unsrt}
